### 2021-08-09 06_Paper/ER-ED/method.Rmd
method section first commit

---
title: "method"
author: "Christoph Scheffel"
date: "9 8 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-08-09 06_Paper/ER-ED/method.Rmd
updated

@@
 ---
-title: "method"
-author: "Christoph Scheffel"
-date: "9 8 2021"
-output: pdf_document
+output: 
+  pdf_document:
+    keep_tex: true
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+# Method

### 2021-08-10 06_Paper/ER-ED/_targets.R
added text

@@ -1,23 +1,11 @@
 library(targets)
-# This is an example _targets.R file. Every
-# {targets} pipeline needs one.
-# Use tar_script() to create _targets.R and tar_edit()
-# to open it again for editing.
-# Then, run tar_make() to run the pipeline
-# and tar_read(summary) to view the results.
-
-# Define custom functions and other global objects.
-# This is where you write source(\"R/functions.R\")
-# if you keep your functions in external scripts.
-summ <- function(dataset) {
-  summarize(dataset, mean_x = mean(x))
-}
+library(tarchetypes)
 
 # Set target-specific options such as packages.
-tar_option_set(packages = "dplyr")
+tar_option_set(packages = "tidyverse")
+options(tidyverse.quiet = TRUE)
 
 # End this file with a list of target objects.
 list(
-  tar_target(data, data.frame(x = sample.int(100), y = sample.int(100))),
-  tar_target(summary, summ(data)) # Call your custom functions as needed.
+  tar_target(method.section, "method.Rmd")
 )

### 2021-08-10 06_Paper/ER-ED/method.Rmd
added headlines
updated files
added text
added references

@@
     keep_tex: true
+bibliography: ER_ED.bib
+csl: apa7.csl
 ---
 
-# Method
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+library(targets)
+```
+
+# 2. Method
+
+"We report how we determined our sample size, all data exlusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]
+
+## 2.1 Participants
+
+xxx.
+
+## 2.2
+
+xxx.

### 2021-08-11 06_Paper/ER-ED/method.Rmd
added text

@@
 
-"We report how we determined our sample size, all data exlusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]
+"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]
 
-## 2.1 Participants
+## 2.1 Power analysis and participants
 
@@
 
-## 2.2
+## 2.2 Experimental procedure
+
+All session took place in a shielded cabin with constant lighting. Participants received information about the
+
+## 2.3 Emotion regulation paradigm
 

### 2021-08-12 06_Paper/COG-ED/Manuscript.Rmd
Created Manuscript.Rmd

---
title: "COG-ED Manuscript"
author: "Josephine"
date: "12 8 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-08-12 01_Paradigms/ER-ED/ER_ED/ER_paradigm.py
changed values

@@ -92,22 +92,16 @@ else:
 # create a default keyboard (e.g. to check for escape)
 defaultKeyboard = keyboard.Keyboard()
 
-
-# #################################
-# Define correct number of Trials
-# #################################
-TotalTrialNr = 15  # 120 ?!
-Trials_Block = 3 # 20
-
-
-# #################################
 # Randomize negative picture sets across negative Blocks
-# #################################
-
 # create a list of 4 negative blocks
 Stimuli_Order = list(range(1,6))
 # randomize order
 shuffle(Stimuli_Order)
+
+# create jitter for fixation cross
+
+FIXjitter = [-1,-1,-1-,1,-0.5,-0.5,-0.5,-0.5,0,0,0,0,0.5,0.5,0.5,0.5,1,1,1,1]
+
 
 # Create lists with all the different variable names
 EDstratcompList = ['Ablenken', 'Distanzieren',
@@ -126,6 +120,10 @@ EDrounds = list(range(6))
 # Create array corresponding to every second element in the list of comparisons, which will be randomized for every participant
 EDcomps = [0,2,4]
 shuffle(EDcomps)
+
+############################
+# INITIALIZE ALL COMPONENTS
+############################
 
 # Initialize components for Routine "WelcomeScreen"
 WelcomeScreenClock = core.Clock()
@@ -465,6 +463,11 @@ _timeToFirstFrame = win.getFutureFlipTime(clock="now")
 WelcomeScreenClock.reset(-_timeToFirstFrame)  # t0 is time of first possible flip
 frameN = -1
 
+#########################
+# START EXPERIMENT
+#########################
+
+
 # -------Run Routine "WelcomeScreen"-------
 while continueRoutine:
     # get current time
@@ -670,7 +673,7 @@ for thisBlocks_view in blocks_view:
         
         # ------Prepare to start Routine "Pics_View"-------
         continueRoutine = True
-        routineTimer.add(3.000000)
+        routineTimer.add(6.000000)
         # update component parameters for each repeat
         image_view.setImage(ImageFile)
         # keep track of which components have finished
@@ -707,7 +710,7 @@ for thisBlocks_view in blocks_view:
                 image_view.setAutoDraw(True)
             if image_view.status == STARTED:
                 # is it time to stop? (based on global clock, using actual start)
-                if tThisFlipGlobal > image_view.tStartRefresh + 3.0-frameTolerance:
[…]

### 2021-08-12 06_Paper/COG-ED/Manuscript.Rmd

@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+-	in everyday life, effort and reward are closely intertwined (Botvinik 2009)
+-	a reward is subjectively more valuable if it is obtained with less effort, i.e. “effort sets in place a reference point against which rewards are measured” (Botvinik 2009, p. 1)
+-	research has not yet established which function best describes the relationship of effort and cost (Kool & Botvinick, 2018)
+-	investigating effort and cost is challenging, because “effort is not a property of the target task alone, but also a function of the individual’s cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual’s reward sensitivity” (Kool & Botvinick, 2018, p.
+902)
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+-	the n-back task as it is known today, i.e. a working memory task with up to six levels of n, was developed by Mackworth in 1959
+-	the n-back task is considered a working memory task because it requires simultaneous storage of past stimuli and processing of new stimuli (Jonides et al., 1997)
+-	the n-back task monotonically increases activation in brain areas of working memory (Jonides et al., 1997; Owen et al., 2005)
+-	errors and reaction time increase monotonically with levels of n (Jaeggi et al., 2010)
+-	reliability measures of the n-back task are extremely mixed, presumably caused by ceiling effects in the easiest level, which might be the reason for its debatable validity, i.e.
+inconsistent associations of n-back performance and other measures such as tasks of executive functioning and fluid intelligence (Jaeggi et al., 2010)
 
-```{r cars}
-summary(cars)
-```
+-	higher n-back levels and more difficult signal-to-noise audio comprehension task levels are discounted in similar ways in the COG-ED paradigm -> doesn’t just work for n-back (Crawford et al., 2021)
+-	there are strong within-subjects associations of the SV of different cognitive domains, i.e.
+n-back and audio comprehension, even after controlling for performance d’, and even though the audio task was rated as less mentally demanding and effortful (Crawford et al., 2021)
 
-## Including Plots
+-	n-back performance is not associated with NFC (and neither are a battery of other tasks of executive functioning) -> NFC reflects a motivation, not ability (Gärtner et al., 2021)
+-	however, NFC is associated with brain flexibility on multiple levels (He et al., 2019)
+-	NFC correlates with greater automatic attention allocation (measured in ERPs) in easier tasks and also with greater voluntary attention allocation in more difficult tasks (Enge et al., 2008)
+-	NFC is positively related to gf and gc but not working memory (Hill et al., 2013)
+-	NFC is not associated with memory and gf, and anecdotally with gc (Fleischhauer et al., 2010)
+-	performance, indexed by d’, was not a reliable predictor of SV across SCZ patients and healthy controls (Culbreth et al., 2016)
+-	when adding the performance scores d’ as a mean performance score as a covariate, the effects of NFC on SV disappeared -> willingness to invest effort might have partially been driven by the prospect of success (Kramer et al., 2021)
+-	in a multilevel model, task load was associated with SVs beyond performance d’ (Westbrook et al., 2013)
+-	older adults make the SV decisions more with their performance in mind than young adults (McLaughlin et al., 2021)
 
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+-	higher NFC means higher motivation to voluntarily mobilize effort for the task, because it is perceived as intrinsically rewarding
+-	the SV of n=1 vs n=2 correlates positively with NFC in children, but not of n=1 vs n=3 (Chevalier, 2018)
+-	the SV of n=1 vs n=3 correlates positively with NFC in adolescents, but not of n=1 vs n=2
+(Kramer et al., 2021)
+-	no association of SV and NFC in either n-back or audio comprehension in a sample of 31 adults (Crawford et al., 2021)
+Justifying changes in the COG-ED procedure:
+-	subjective values did not decline between n=4 and n=5 (Culbreth et al., 2016) -> n=5 is too universally difficult to be valid
+-	only higher n-back levels are reliable for performance computation (Jaeggi et al., 2010) -> we will not include n = 1 in our performance measure

### 2021-08-13 06_Paper/COG-ED/Manuscript.Rmd
Started writing introduction

@@
 ---
-title: "COG-ED Manuscript"
-author: "Josephine"
-date: "12 8 2021"
-output: html_document
+title             : "COG-ED Manuscript"
+author            : "Josephine"
+date              : "13 8 2021"
+output            : html_document
+bibliography      : ref_COG-ED.bib
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+library(bibtex)
 ```
 
-## R Markdown
+# Introduction
 
--	in everyday life, effort and reward are closely intertwined (Botvinik 2009)
--	a reward is subjectively more valuable if it is obtained with less effort, i.e. “effort sets in place a reference point against which rewards are measured” (Botvinik 2009, p. 1)
--	research has not yet established which function best describes the relationship of effort and cost (Kool & Botvinick, 2018)
--	investigating effort and cost is challenging, because “effort is not a property of the target task alone, but also a function of the individual’s cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual’s reward sensitivity” (Kool & Botvinick, 2018, p.
-902)
+In everyday life, effort and reward are closely intertwined [@Botvinick2009].
+With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
+A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
+However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
+Investigating effort and cost is challenging because “effort is not a property of the target task alone, but also a function of the individual’s cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual’s reward sensitivity” [@Kool2018, p.
+209].
 
--	the n-back task as it is known today, i.e. a working memory task with up to six levels of n, was developed by Mackworth in 1959
--	the n-back task is considered a working memory task because it requires simultaneous storage of past stimuli and processing of new stimuli (Jonides et al., 1997)
--	the n-back task monotonically increases activation in brain areas of working memory (Jonides et al., 1997; Owen et al., 2005)
--	errors and reaction time increase monotonically with levels of n (Jaeggi et al., 2010)
--	reliability measures of the n-back task are extremely mixed, presumably caused by ceiling effects in the easiest level, which might be the reason for its debatable validity, i.e.
-inconsistent associations of n-back performance and other measures such as tasks of executive functioning and fluid intelligence (Jaeggi et al., 2010)
+One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g.
+letters, is presented on screen and participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
+It requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997], and participants are asked to respond as quickly and as accurately as they can.
+The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates and reaction times [@Jaeggi2010] as well as monotonic increases in brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
+However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level, causing inconsistent associations of n-back performance and measures such as executive functioning and fluid intelligence [@Jaeggi2010].
+
+A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al. [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+First, the participants complete n-back level one to six to familiarize themselves with the task.
+Then, each level two to six is being compared with level one by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.
+It they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
+This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
+The idea is to estimate the participants' subjective cost of the more difficult level by identifying the smallest reward they would still be okay with being paid for doing level one.
+Therefore, the higher the difficult level, the smaller the reward that the participants would accept for level one.
+The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the difficult level.
+Westbrook et al. [-@Westbrook2013] used these SVs to investigate interindividual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
+Younger participants had a larger AUC than older participants, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.
+
+The AUC in the study by Westbrook et al.
+[-@Westbrook2013] was also associated with the participants' Need for Cognition score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
 

### 2021-08-16 06_Paper/COG-ED/Manuscript.Rmd
Wrote more introduction

@@
 Then, each level two to six is being compared with level one by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.
-It they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
+If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
 This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
@@
 Therefore, the higher the difficult level, the smaller the reward that the participants would accept for level one.
-The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the difficult level.
+The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
 Westbrook et al. [-@Westbrook2013] used these SVs to investigate interindividual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
@@
 The AUC in the study by Westbrook et al.
-[-@Westbrook2013] was also associated with the participants' Need for Cognition score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
+[-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
+On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
+However, the relation of NFC and SVs might be confounded with task performance itself, since subjective task values have been shown to depend on both the exerted effort [@Wang2017] and the expected performance [@Yee2021].
+Findings on NFC and n-back performance are heterogenous.
+On one hand individuals with higher NFC neither had better n-back performance [@Gaertner2021] nor better working memory [@Fleischhauer 2010; @Hill2013], on the other hand they showed greater attention allocation [@Enge2008] and brain flexibility [@He2019].
+Nevertheless, a possible association of NFC and task performance might be secondary, since task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019].
+But since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021], more research is needed to shed light on this issue.
+
+The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
 
@@
 
--	n-back performance is not associated with NFC (and neither are a battery of other tasks of executive functioning) -> NFC reflects a motivation, not ability (Gärtner et al., 2021)
--	however, NFC is associated with brain flexibility on multiple levels (He et al., 2019)
--	NFC correlates with greater automatic attention allocation (measured in ERPs) in easier tasks and also with greater voluntary attention allocation in more difficult tasks (Enge et al., 2008)
--	NFC is positively related to gf and gc but not working memory (Hill et al., 2013)
--	NFC is not associated with memory and gf, and anecdotally with gc (Fleischhauer et al., 2010)
--	performance, indexed by d’, was not a reliable predictor of SV across SCZ patients and healthy controls (Culbreth et al., 2016)
--	when adding the performance scores d’ as a mean performance score as a covariate, the effects of NFC on SV disappeared -> willingness to invest effort might have partially been driven by the prospect of success (Kramer et al., 2021)
--	in a multilevel model, task load was associated with SVs beyond performance d’ (Westbrook et al., 2013)
--	older adults make the SV decisions more with their performance in mind than young adults (McLaughlin et al., 2021)
-
--	higher NFC means higher motivation to voluntarily mobilize effort for the task, because it is perceived as intrinsically rewarding
--	the SV of n=1 vs n=2 correlates positively with NFC in children, but not of n=1 vs n=3 (Chevalier, 2018)
--	the SV of n=1 vs n=3 correlates positively with NFC in adolescents, but not of n=1 vs n=2
-(Kramer et al., 2021)
--	no association of SV and NFC in either n-back or audio comprehension in a sample of 31 adults (Crawford et al., 2021)
 Justifying changes in the COG-ED procedure:

### 2021-08-16 06_Paper/COG-ED/Manuscript.Rmd
Finished introduction

@@
 The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
-
--	higher n-back levels and more difficult signal-to-noise audio comprehension task levels are discounted in similar ways in the COG-ED paradigm -> doesn’t just work for n-back (Crawford et al., 2021)
--	there are strong within-subjects associations of the SV of different cognitive domains, i.e.
-n-back and audio comprehension, even after controlling for performance d’, and even though the audio task was rated as less mentally demanding and effortful (Crawford et al., 2021)
-
-Justifying changes in the COG-ED procedure:
--	subjective values did not decline between n=4 and n=5 (Culbreth et al., 2016) -> n=5 is too universally difficult to be valid
--	only higher n-back levels are reliable for performance computation (Jaeggi et al., 2010) -> we will not include n = 1 in our performance measure
+We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer 1-back.
+In fact, our COG-ED adaptation allows the computations of SVs, even if the individual does not have a clear preference for one task level.
+In the present study, we will validate this adaptation by replicating the findings of Westbrook et al. [-@Westbrook2013].
+Additionally, we will apply the adaption to a task with different emotion regulation strategies to establish an effort discounting paradigm for task varieties that have no objective order of task load.
+The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but it has not been applied to tasks without objective task load so far.

### 2021-08-16 06_Paper/COG-ED/Manuscript.Rmd
Tried file import
Cannot access subfolder

@@
 The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but it has not been applied to tasks without objective task load so far.
+
+```{r}
+
+library(here)         # to set a directory without defined paths
+library(tidyverse)    # plotting and managing data
+
+# set top level directory to source file
+here::i_am("Manuscript.Rmd")
+
+# import n-back data into a list
+datalist_nback = lapply(list.files(pattern = "nback.*csv"), read.csv(here("Sampledata")), stringsAsFactors = FALSE, header = TRUE)
+
+```

### 2021-08-17 06_Paper/COG-ED/Manuscript.Rmd
File import functional

--- 2021-08-16 06_Paper/COG-ED/Manuscript.Rmd
@@
 The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but it has not been applied to tasks without objective task load so far.
+
+```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}
+
+  library(here)         # to set a directory without defined paths
+  library(tidyverse)    # plotting and managing data
+
+```
+
+```{r import, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # set top level directory to source file
+
+  here::i_am("Manuscript.Rmd")
+
+  # import n-back and effort discounting data into a list each
+
+  datalist_nback = lapply(list.files(here("Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
+                          read.csv, stringsAsFactors = FALSE, header = TRUE)
+  datalist_ED = lapply(list.files(here("Sampledata"), pattern = '.*ED.*csv', full.names = TRUE),
+                          read.csv, stringsAsFactors = FALSE, header = TRUE)
+
+  # put relevant data into a dataframe
+
+```

### 2021-08-17 06_Paper/COG-ED/Manuscript.Rmd
Added data cleaning code

@@
 
-  # put relevant data into a dataframe
+  # create empty data frames for loops to feed into
+
+  data_nback <- data.frame(subject = character(), level = double(), target = character(),
+                           response = character(), correct = double(), rt = double())
+  data_ED <- data.frame(subject = character(), step = double(), choice = character(),
+                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
+
+  # put relevant data into a dataframes
+
+  for (i in 1:length(datalist_nback)) {
+
+    newdata <- data.frame(datalist_nback[[i]][["Participant"]], datalist_nback[[i]][["currentlevel"]],
+                          datalist_nback[[i]][["Stimulus"]], datalist_nback[[i]][["trial_resp.keys"]],
+                          datalist_nback[[i]][["trial_resp.corr"]], datalist_nback[[i]][["trial_resp.rt"]])
+    colnames(newdata) <- names(data_nback)
+    data_nback <- rbind(data_nback, newdata)
+  }
+
+  for (i in 1:length(datalist_ED)) {
+
+    newdata <- data.frame(datalist_ED[[i]][["Participant"]][2:length(datalist_ED[[i]][["Participant"]])],
+                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
+                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
+                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
+                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
+                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
+                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
+    colnames(newdata) <- names(data_ED)
+    data_ED <- rbind(data_ED, newdata)
+  }
+
+  # replace some columns with 'easy to work with' values
+
+  # the target column will contain 1 for targets and 0 for all non-targets
+  data_nback[data_nback == "Target"] <- 1
+  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
+  data_nback$target <- as.numeric(data_nback$target)
+  # the response column will contain 1 for responses and 0 for all non-responses
+  data_nback[data_nback == "left"|data_nback == "right"] <- 1
+  data_nback[data_nback == "None"] <- 0
+  data_nback$response <- as.numeric(data_nback$response)
+  # the choice column will contain 1 for the left button and 2 for the right button
+  data_ED[data_ED == "EDleftbutton"] <- 1
+  data_ED[data_ED == "EDrightbutton"] <- 2
+  data_ED$choice <- as.numeric(data_ED$choice)
+
+  # since only the last choice of each comparison is relevant, we will keep only those rows
+
+  data_ED <- data_ED[data_ED$step == 6,]
 

### 2021-08-17 06_Paper/COG-ED/Manuscript.Rmd
Calculation of subjective values fully functional

@@
   data_ED <- data_ED[data_ED$step == 6,]
+  data_ED <- subset(data_ED, select = -c(step))
 
 ```
+
+```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # apply the addition or subtraction of 0.015625 to the last choices
+
+  for (i in 1:nrow(data_ED)) {
+
+    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
+    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]
+
+    if (data_ED$choice[i] == 1) {
+      if (data_ED$LBvalue[i] == 2.00) {
+        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
+      } else {
+        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
+      }
+    } else {
+      if (data_ED$RBvalue[i] == 2.00) {
+        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
+      } else {
+        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
+      }
+    }
+
+  }
+
+  # create vector indicating in which rows the data of a new subject begins
+
+  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))
+
+  # create empty data frame for the loop to feed into
+
+  data_SV <- data.frame(subject = character(), sv1 = double(), sv2 = double(), sv3 = double(), sv4 = double())
+
+  # compute subjective values per n-back level and feed into data frame
+
+  for (i in 1:(length(subjectindex)-1)) {
+
+    # initialize empty vectors
+
+    tempone <- double()
+    temptwo <- double()
+    tempthree <- double()
+    tempfour <- double()
+
+    # check for every number, whether it appears in the fixedlevel and flexlevel columns
+    # divide flexvalue by 2 if it appears in the fixedlevel columns
+    # append 1 if it appears in the flexlevel column
+
+    # for 1-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
+          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
+          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
+        } else {
+          # do nothing
+        }
+
+    # for 2-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
+          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
+          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
+        } else {
+          # do nothing
+        }
+
+    # for 3-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
+          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
+          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
+        } else {
+          # do nothing
+        }
+
+    # for 4-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
+          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
+          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
+        } else {
+          # do nothing
+        }
+
+    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame
+
+    newdata <- data.frame(data_ED$subject[subjectindex[i]], mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour))
+    colnames(newdata) <- names(data_SV)
+    data_SV <- rbind(data_SV, newdata)
+
+  }
+```

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
changed one response
So not all participants have the exact same hit rate for 1-back (which would result in a d prime error)

@@
 ```
+
+```{r Hypothesis_1a, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # H1a: Performance measured by signal detection d’ declines with increasing n-back level.
+
+  # set the number of targets and non-targets, so in case the paradigm will be changed it is easily accessible
+  # they are multiplied by 2, because there are two runs per n-back level
+
+  num_targets <- 16*2
+  num_nontargets <- 48*2
+
+  # compute index of rows in which the levels change
+
+  levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))
+
+  # set up empty data frame for the loop to feed into
+
+  dprime <- data.frame(subject = character(), level = double(), hitrate = double(), falsealarmrate = double())
+
+  # calculate hits and false alarms per participant
+
+  for (i in 1:(length(levelindex)-1)) {
+
+    hits <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
+                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
+    falsealarms <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
+                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
+    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
+                          level = data_nback$level[levelindex[i]],
+                          hitrate = hits/num_targets,
+                          falsealarmrate = falsealarms/num_nontargets)
+    dprime <- rbind(dprime, newdata)
+
+  }
+
+  # z-transform the hit rate and the false alarm rate
+
+  for (i in 1:4) {
+
+    mean_hitrate <- mean(dprime$hitrate[dprime$level == i])
+    sd_hitrate <- sd(dprime$hitrate[dprime$level == i])
+    mean_falsealarmrate <- mean(dprime$falsealarmrate[dprime$level == i])
+    sd_falsealarmrate <- sd(dprime$falsealarmrate[dprime$level == i])
+
+    for (j in 1:length(which(dprime$level == i))) {
+
+      dprime$hitrate[which(dprime$level == i)[j]] <- (dprime$hitrate[which(dprime$level == i)[j]] - mean_hitrate)/sd_hitrate
+      dprime$falsealarmrate[which(dprime$level == i)[j]] <- (dprime$falsealarmrate[which(dprime$level == i)[j]] -
+                                                               mean_falsealarmrate)/sd_falsealarmrate
+    }
+  }
+
+  # calculate d'
+
+  dprime$d <- dprime$hitrate - dprime$falsealarmrate
+
+  # ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
+
+```

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
calculated d prime

@@
         if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
-          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
+          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 +
+                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
         } else {
@@
         if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
-          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
+          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 +
+                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
         } else {
@@
         if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
-          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
+          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 +
+                                                             which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
         } else {
@@
         if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
-          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 + which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
+          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 +
+                                                           which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
         } else {
@@
   }
+
+  # remove temporary variables
+
+  remove(tempone, temptwo, tempthree, tempfour)
+
 ```
@@
 
+  # remove temporary variables
+
+  remove(mean_hitrate, sd_hitrate, mean_falsealarmrate, sd_falsealarmrate)
+
   # calculate d'
@@
 
+      # make a temporary copy of the dprime data frame without 1-back
+
+      h1a_data <- dprime[dprime$level != 1,]
+      h1a_data$level <- as.factor(h1a_data$level)
+
+      # define contrasts
+
+      contrasts(h1a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))
+
+      # calculate ANOVA
+
+      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))
+      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))
+      remove(h1a_data)
+
 ```

### 2021-08-18 01_Paradigms/ER-ED/ER_ED/ER_paradigm.py
deleted old jitter

@@ -105,11 +105,6 @@ Stimuli_Order = list(range(1,6))
 # randomize order
 shuffle(Stimuli_Order)
 
-# create jitter for fixation cross
-
-FIXjitter = [-1,-1,-1,-1,-0.5,-0.5,-0.5,-0.5,0,0,0,0,0.5,0.5,0.5,0.5,1,1,1,1]
-
-
 # Create lists with all the different variable names
 EDstratcompList = ['Ablenken', 'Distanzieren',
 'Ablenken', 'Unterdrücken',

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd

@@
     hits <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
-                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
+                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
     falsealarms <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
-                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
+                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
     newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
@@
 
+    # calculate the mean and sd of hit rate and false alarm rate per n-back level i
+
     mean_hitrate <- mean(dprime$hitrate[dprime$level == i])
@@
     for (j in 1:length(which(dprime$level == i))) {
+
+      # z-transform each subject j's hit rate and false alarm rate within the level i
 
@@
 ```
+
+```{r Hypothesis_1b, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # H1b: Performance measured by reaction time declines with increasing n-back level.
+
+  # set up empty data frame for the loop to feed into
+
+  rt <- data.frame(subject = character(), level = double(), meanrt = double())
+
+  # calculate mean reaction time per participant per level
+
+  for (i in 1:(length(levelindex)-1)) {
+
+    meanrt <- mean(data_nback$rt[which(data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
+                                 +(levelindex[i]-1)], na.rm = TRUE)
+
+    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
+                          level = data_nback$level[levelindex[i]],
+                          meanrt = meanrt)
+    rt <- rbind(rt, newdata)
+
+  }
+
+  # ANOVA with three linear contrasts, contrasting the mean rt of two n-back levels (2,3,4) at a time
+
+      # make a temporary copy of the dprime data frame without 1-back
+
+      h2a_data <- rt[rt$level != 1,]
+      h2a_data$level <- as.factor(h2a_data$level)
+
+      # define contrasts
+
+      contrasts(h2a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))
+
+      # calculate ANOVA
+
+      hypothesis2a_anova <- summary(aov(h2a_data$meanrt ~ h2a_data$level))
+      hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$meanrt ~ h2a_data$level))
+      remove(h2a_data)
+
+```

### 2021-08-18 01_Paradigms/ER-ED/ER_ED/ER_paradigm.py
added jitter to fixcross

@@ -2099,8 +2099,12 @@ for thisTrials_choice in trials_choice:
     
     # ------Prepare to start Routine "fixcross"-------
     continueRoutine = True
-    routineTimer.add(1.000000)
     # update component parameters for each repeat
+    # random jitter between 3 and 5 seconds
+        jitter = random.uniform(3,5)
+        jitter = round(jitter, 1)
+        # add jitter to log file
+        thisExp1.addData('jitter', jitter)
     # keep track of which components have finished
     fixcrossComponents = [text_fixcross]
     for thisComponent in fixcrossComponents:
@@ -2117,7 +2121,7 @@ for thisTrials_choice in trials_choice:
     frameN = -1
     
     # -------Run Routine "fixcross"-------
-    while continueRoutine and routineTimer.getTime() > 0:
+    while continueRoutine:
         # get current time
         t = fixcrossClock.getTime()
         tThisFlip = win.getFutureFlipTime(clock=fixcrossClock)
@@ -2136,7 +2140,7 @@ for thisTrials_choice in trials_choice:
             text_fixcross.setAutoDraw(True)
         if text_fixcross.status == STARTED:
             # is it time to stop? (based on global clock, using actual start)
-            if tThisFlipGlobal > text_fixcross.tStartRefresh + 4.0-frameTolerance:
+            if tThisFlipGlobal > text_fixcross.tStartRefresh + jitter-frameTolerance:
                 # keep track of stop time/frame for later
                 text_fixcross.tStop = t  # not accounting for scr refresh
                 text_fixcross.frameNStop = frameN  # exact frame index

### 2021-08-18 01_Paradigms/ER-ED/ER_ED/ER_paradigm.py
fixed typos

@@ -2101,10 +2101,10 @@ for thisTrials_choice in trials_choice:
     continueRoutine = True
     # update component parameters for each repeat
     # random jitter between 3 and 5 seconds
-        jitter = random.uniform(3,5)
-        jitter = round(jitter, 1)
-        # add jitter to log file
-        thisExp1.addData('jitter', jitter)
+    jitter = random.uniform(3,5)
+    jitter = round(jitter, 1)
+    # add jitter to log file
+    thisExp1.addData('jitter', jitter)
     # keep track of which components have finished
     fixcrossComponents = [text_fixcross]
     for thisComponent in fixcrossComponents:

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
imported questionnaire data and prepared hypothesis 1c

@@
   data_ED <- subset(data_ED, select = -c(step))
+
+  # import questionnaire data from RedCap
+
+  data_quest <- read.csv(here("Sampledata","COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
 
@@
 
-      # make a temporary copy of the dprime data frame without 1-back
+      # make a temporary copy of the rt data frame without 1-back
 
@@
 ```
+
+```{r Hypothesis_1c, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
+
+  # H1c: Ratings on all NTLX dimensions increase with increasing n-back level.
+
+  # aggregate NTLX data per participant per level
+
+  data_ntlx <- data.frame(subject = character(), level = double(),
+                          mental = double(), physical = double(), time = double(),
+                          performance = double(), effort = double(), frustration = double())
+
+  # six ANOVAs with six linear contrasts, contrasting the subscale scores of two n-back levels (1,2,3,4) at a time
+
+      # make a temporary copy of the NTLX data frame
+
+      h3a_data <- data_ntlx
+      h3a_data$level <- as.factor(h3a_data$level)
+
+      # define contrasts
+
+      contrasts(h3a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
+                                         c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))
+
+      # calculate ANOVAs
+
+      hypothesis3a1_anova <- summary(aov(h3a_data$mental ~ h3a_data$level))
+      hypothesis3a1_posthoc <- TukeyHSD(aov(h3a_data$mental ~ h3a_data$level))
+
+      hypothesis3a2_anova <- summary(aov(h3a_data$physical ~ h3a_data$level))
+      hypothesis3a2_posthoc <- TukeyHSD(aov(h3a_data$physical ~ h3a_data$level))
+
+      hypothesis3a3_anova <- summary(aov(h3a_data$time ~ h3a_data$level))
+      hypothesis3a3_posthoc <- TukeyHSD(aov(h3a_data$time ~ h3a_data$level))
+
+      hypothesis3a4_anova <- summary(aov(h3a_data$performance ~ h3a_data$level))
+      hypothesis3a4_posthoc <- TukeyHSD(aov(h3a_data$performance ~ h3a_data$level))
+
+      hypothesis3a5_anova <- summary(aov(h3a_data$effort ~ h3a_data$level))
+      hypothesis3a5_posthoc <- TukeyHSD(aov(h3a_data$effort ~ h3a_data$level))
+
+      hypothesis3a6_anova <- summary(aov(h3a_data$frustration ~ h3a_data$level))
+      hypothesis3a6_posthoc <- TukeyHSD(aov(h3a_data$frustration ~ h3a_data$level))
+
+      remove(h3a_data)
+
+```

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Satz in 3 Teile aufgetelit

@@
 
-One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g.
-letters, is presented on screen and participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
+One task that is often used to investigate effort is the n-back task. <!-- Satz war sehr lang, ich ihn aufgeteilt und etwas umgestellt -->
+In this working memory task, a continuous stream of stimuli, e.g. letters, is presented on screen. <!-- zweiter Teilsatz -->
+Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
+<!-- dritter Teilsatz-->
 It requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997], and participants are asked to respond as quickly and as accurately as they can.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Sätze umgestellt

@@
 In this working memory task, a continuous stream of stimuli, e.g. letters, is presented on screen. <!-- zweiter Teilsatz -->
-Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
+Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959]; and are asked to respond as quickly and as accurately as they can.
 <!-- dritter Teilsatz-->
-It requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997], and participants are asked to respond as quickly and as accurately as they can.
+It requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997].
+<!-- Teilsatz nach dem Komma wirkt etwas out of place: der erste Teil beschäftigt sich mit cognitiven Anforderungen an die Teilnehmenden, der zweite aber mit einem Auftrag an die Probanden; Deshalb habe ich den Satz aufgeteilt und den zweiten Teil mit dem ersten verbunden -->
 The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates and reaction times [@Jaeggi2010] as well as monotonic increases in brain activity in areas associated with working memory [@Jonides1997; @Owen2005].

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Changed variable names and added NTLX score computation

--- 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
@@
   data_quest <- read.csv(here("Sampledata","COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
+  colnames(data_quest)[1] <- "set" # rename the first column
 
@@
 
-      h2a_data <- rt[rt$level != 1,]
-      h2a_data$level <- as.factor(h2a_data$level)
+      h1b_data <- rt[rt$level != 1,]
+      h1b_data$level <- as.factor(h1b_data$level)
 
@@
 
-      contrasts(h2a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))
+      contrasts(h1b_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))
 
@@
 
-      hypothesis2a_anova <- summary(aov(h2a_data$meanrt ~ h2a_data$level))
-      hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$meanrt ~ h2a_data$level))
-      remove(h2a_data)
+      hypothesis1b_anova <- summary(aov(h1b_data$meanrt ~ h1b_data$level))
+      hypothesis1b_posthoc <- TukeyHSD(aov(h1b_data$meanrt ~ h1b_data$level))
+      remove(h1b_data)
 
@@
 
-  # aggregate NTLX data per participant per level
+  # compute index of rows in which the data sets change
+
+  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))
+
+  # set up empty data frame for the loop to feed into
 
@@
 
+  # feed NTLX data per participant per level into data frame
+
+  for (i in 1:(length(setindex)-1)) {
+
+    for (j in 1:4) {
+
+      newdata <- data.frame(subject = data_quest$subject[setindex[i]], level = j,
+                            mental = data_quest$nasa_tlx_01[setindex[i]+j+2],
+                            physical = data_quest$nasa_tlx_02[setindex[i]+j+2],
+                            time = data_quest$nasa_tlx_03[setindex[i]+j+2],
+                            performance = data_quest$nasa_tlx_04[setindex[i]+j+2],
+                            effort = data_quest$nasa_tlx_05[setindex[i]+j+2],
+                            frustration = data_quest$nasa_tlx_06[setindex[i]+j+2])
+      data_ntlx <- rbind(data_ntlx, newdata)
+    }
+  }
+
   # six ANOVAs with six linear contrasts, contrasting the subscale scores of two n-back levels (1,2,3,4) at a time
@@
 
-      h3a_data <- data_ntlx
-      h3a_data$level <- as.factor(h3a_data$level)
+      h1c_data <- data_ntlx
+      h1c_data$level <- as.factor(h1c_data$level)
 
@@
 
-      contrasts(h3a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
+      contrasts(h1c_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                          c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))
@@
 
-      hypothesis3a1_anova <- summary(aov(h3a_data$mental ~ h3a_data$level))
-      hypothesis3a1_posthoc <- TukeyHSD(aov(h3a_data$mental ~ h3a_data$level))
+      hypothesis1c1_anova <- summary(aov(h1c_data$mental ~ h1c_data$level))
+      hypothesis1c1_posthoc <- TukeyHSD(aov(h1c_data$mental ~ h1c_data$level))
 
-      hypothesis3a2_anova <- summary(aov(h3a_data$physical ~ h3a_data$level))
-      hypothesis3a2_posthoc <- TukeyHSD(aov(h3a_data$physical ~ h3a_data$level))
+      hypothesis1c2_anova <- summary(aov(h1c_data$physical ~ h1c_data$level))
+      hypothesis1c2_posthoc <- TukeyHSD(aov(h1c_data$physical ~ h1c_data$level))
 
-      hypothesis3a3_anova <- summary(aov(h3a_data$time ~ h3a_data$level))
-      hypothesis3a3_posthoc <- TukeyHSD(aov(h3a_data$time ~ h3a_data$level))
+      hypothesis1c3_anova <- summary(aov(h1c_data$time ~ h1c_data$level))
+      hypothesis1c3_posthoc <- TukeyHSD(aov(h1c_data$time ~ h1c_data$level))
 
-      hypothesis3a4_anova <- summary(aov(h3a_data$performance ~ h3a_data$level))
-      hypothesis3a4_posthoc <- TukeyHSD(aov(h3a_data$performance ~ h3a_data$level))
+      hypothesis1c4_anova <- summary(aov(h1c_data$performance ~ h1c_data$level))
+      hypothesis1c4_posthoc <- TukeyHSD(aov(h1c_data$performance ~ h1c_data$level))
 
-      hypothesis3a5_anova <- summary(aov(h3a_data$effort ~ h3a_data$level))
-      hypothesis3a5_posthoc <- TukeyHSD(aov(h3a_data$effort ~ h3a_data$level))
+      hypothesis1c5_anova <- summary(aov(h1c_data$effort ~ h1c_data$level))
+      hypothesis1c5_posthoc <- TukeyHSD(aov(h1c_data$effort ~ h1c_data$level))
 
-      hypothesis3a6_anova <- summary(aov(h3a_data$frustration ~ h3a_data$level))
-      hypothesis3a6_posthoc <- TukeyHSD(aov(h3a_data$frustration ~ h3a_data$level))
+      hypothesis1c6_anova <- summary(aov(h1c_data$frustration ~ h1c_data$level))
+      hypothesis1c6_posthoc <- TukeyHSD(aov(h1c_data$frustration ~ h1c_data$level))
 
-      remove(h3a_data)
+      remove(h1c_data)
 

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Kommentar
neuer Kommentar

--- 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
@@
 However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level, causing inconsistent associations of n-back performance and measures such as executive functioning and fluid intelligence [@Jaeggi2010].
+<!-- Ist hier als Reliabilität die Korrelation zum Außenkriterium gemeint (EF und gf?); Falls nicht, wären doch fehlende Reliabilitäten und Korrelationen zwei verschiedene Punkte-->
 
-A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al. [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al.
+[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+<!-- gibt es keine Möglichkeit, die Quelle automatisiert pasten zu lassen?
+Sonst müsste man an der Stelle auch zuerst alle drei Autoren nennen, oder?
+-->
 First, the participants complete n-back level one to six to familiarize themselves with the task.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Satz angepasst und neuer Kommentar

@@
 -->
-First, the participants complete n-back level one to six to familiarize themselves with the task.
+First, the participants complete the n-back levels to familiarize themselves with the task. <!-- habe es mal allgemeiner gehalten, da wir selbst auch keine sechs level haben  -->
 Then, each level two to six is being compared with level one by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Satz umgebaut

@@
 First, the participants complete the n-back levels to familiarize themselves with the task. <!-- habe es mal allgemeiner gehalten, da wir selbst auch keine sechs level haben  -->
-Then, each level two to six is being compared with level one by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.
+Then, level one is compared with all following levels by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one. <!-- s. vorheriger Kommentar -->
 If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Aussage kürzer formuliert

@@
 This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
-The idea is to estimate the participants' subjective cost of the more difficult level by identifying the smallest reward they would still be okay with being paid for doing level one.
-Therefore, the higher the difficult level, the smaller the reward that the participants would accept for level one.
+The idea is to estimate subjective equivalence, i.e., both offers are equally preferred [@Westbrook2013]. 
 The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Bindestrich hinzugefügt

@@
 The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
-Westbrook et al. [-@Westbrook2013] used these SVs to investigate interindividual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
+Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
 Younger participants had a larger AUC than older participants, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Aussage auf die Konstruktebene bezogen
Kommentar hinzugefügt
Zwicshenüberschrift eingefügt

@@
 The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
-Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
-Younger participants had a larger AUC than older participants, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.
+Westbrook et al.
+[-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
+<!-- kann man das so sagen?
+Mit dem plotten?
+Vielleicht sollte man einfach nur sagen, die AUC wurde berechnet?
+-->
+Younger participants showed lower effort discounting, i.e.
+they needed a lower monetary incentive for choosing the more difficult levels over level one.
+<!--Würde bei dieser Aussage eine Ebene höher gehen und dann also vom Effort Discounting sprechen -->
 
+## Effort discounting and need for cognition 
+<!-- denke eine Zwischenüberschrift könnte das noch etwas deutlicher unterteilen-->
 The AUC in the study by Westbrook et al.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
neuer Kommentar

@@
 [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
+<!-- Eventuell könnte man als Anfang für diesen Abschnitt nochmal kurz NFC definieren (zweiter Teilsatz) und kurz sagen, womit das assoziiert ist...
+also vor allem mit Traits, die danach klingen, als könnte Effort Discounting eine Rolle spielen; Dann mit Westbrook in Verbindung bringen, aber vielleicht nicht von der AUC reden, sondern lieber wieder von Effort Discounting?
+-->
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Zwischenüberschrift eingefügt

@@
 
+## The present study
+<!-- auch hier eine Zwischenüberschrift um es etwas besser in Blöcke einzuteilen -->
 The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
kleine Umformulierung

@@
 The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
-We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer 1-back.
+We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level (i.e., 1-back).
 In fact, our COG-ED adaptation allows the computations of SVs, even if the individual does not have a clear preference for one task level.

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
neue Kommentare

@@
 In fact, our COG-ED adaptation allows the computations of SVs, even if the individual does not have a clear preference for one task level.
+<!-- vielleicht eher "Additionally, our COG-ED adaption...
+-->
 In the present study, we will validate this adaptation by replicating the findings of Westbrook et al. [-@Westbrook2013].
@@
 The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but it has not been applied to tasks without objective task load so far.
+<!-- Wortwiederholung "apply" und der Satz klingt etwas sperrig...
+vielleicht 2 drauß machen?
+-->
 

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
Kommentar zu den ANOVAS
Leerzeichen gelöscht

@@
 
-      contrasts(h3a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
+      contrasts(h1c_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                          c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))
-
+      ## CS: das sieht mit den Kontrasten usw. irgendwie etwas kompliziert aus... Kannst gern mal beim ESER Code die ANOVAS mit dem aov_ez Package anschauen, vielleicht erleichtert es das Ganze
       # calculate ANOVAs
 
-      hypothesis3a1_anova <- summary(aov(h3a_data$mental ~ h3a_data$level))
-      hypothesis3a1_posthoc <- TukeyHSD(aov(h3a_data$mental ~ h3a_data$level))
+      hypothesis1c1_anova <- summary(aov(h1c_data$mental ~ h1c_data$level))
+      hypothesis1c1_posthoc <- TukeyHSD(aov(h1c_data$mental ~ h1c_data$level))
 
-      hypothesis3a2_anova <- summary(aov(h3a_data$physical ~ h3a_data$level))
-      hypothesis3a2_posthoc <- TukeyHSD(aov(h3a_data$physical ~ h3a_data$level))
+      hypothesis1c2_anova <- summary(aov(h1c_data$physical ~ h1c_data$level))
+      hypothesis1c2_posthoc <- TukeyHSD(aov(h1c_data$physical ~ h1c_data$level))
 
-      hypothesis3a3_anova <- summary(aov(h3a_data$time ~ h3a_data$level))
-      hypothesis3a3_posthoc <- TukeyHSD(aov(h3a_data$time ~ h3a_data$level))
+      hypothesis1c3_anova <- summary(aov(h1c_data$time ~ h1c_data$level))
+      hypothesis1c3_posthoc <- TukeyHSD(aov(h1c_data$time ~ h1c_data$level))
 
-      hypothesis3a4_anova <- summary(aov(h3a_data$performance ~ h3a_data$level))
-      hypothesis3a4_posthoc <- TukeyHSD(aov(h3a_data$performance ~ h3a_data$level))
+      hypothesis1c4_anova <- summary(aov(h1c_data$performance ~ h1c_data$level))
+      hypothesis1c4_posthoc <- TukeyHSD(aov(h1c_data$performance ~ h1c_data$level))
 
-      hypothesis3a5_anova <- summary(aov(h3a_data$effort ~ h3a_data$level))
-      hypothesis3a5_posthoc <- TukeyHSD(aov(h3a_data$effort ~ h3a_data$level))
+      hypothesis1c5_anova <- summary(aov(h1c_data$effort ~ h1c_data$level))
+      hypothesis1c5_posthoc <- TukeyHSD(aov(h1c_data$effort ~ h1c_data$level))
 
-      hypothesis3a6_anova <- summary(aov(h3a_data$frustration ~ h3a_data$level))
-      hypothesis3a6_posthoc <- TukeyHSD(aov(h3a_data$frustration ~ h3a_data$level))
+      hypothesis1c6_anova <- summary(aov(h1c_data$frustration ~ h1c_data$level))
+      hypothesis1c6_posthoc <- TukeyHSD(aov(h1c_data$frustration ~ h1c_data$level))
 
-      remove(h3a_data)
+      remove(h1c_data)
 

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
Implemented some comments (some still open)

@@
 
-One task that is often used to investigate effort is the n-back task. <!-- Satz war sehr lang, ich ihn aufgeteilt und etwas umgestellt -->
-In this working memory task, a continuous stream of stimuli, e.g. letters, is presented on screen. <!-- zweiter Teilsatz -->
+One task that is often used to investigate effort is the n-back task.
+In this working memory task, a continuous stream of stimuli, e.g. letters, is presented on screen.
 Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959]; and are asked to respond as quickly and as accurately as they can.
-<!-- dritter Teilsatz-->
-It requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997].
-<!-- Teilsatz nach dem Komma wirkt etwas out of place: der erste Teil beschäftigt sich mit cognitiven Anforderungen an die Teilnehmenden, der zweite aber mit einem Auftrag an die Probanden; Deshalb habe ich den Satz aufgeteilt und den zweiten Teil mit dem ersten verbunden -->
-The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates and reaction times [@Jaeggi2010] as well as monotonic increases in brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
-However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level, causing inconsistent associations of n-back performance and measures such as executive functioning and fluid intelligence [@Jaeggi2010].
-<!-- Ist hier als Reliabilität die Korrelation zum Außenkriterium gemeint (EF und gf?); Falls nicht, wären doch fehlende Reliabilitäten und Korrelationen zwei verschiedene Punkte-->
+The n-back task requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997].
+It is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates and reaction times [@Jaeggi2010] as well as monotonic increases in brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
+However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level [@Jaeggi2010].
+Additionally, associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
 
-A way to quantify the subjective cost of each n-back level has been developed by Westbrook et al.
-[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
-<!-- gibt es keine Möglichkeit, die Quelle automatisiert pasten zu lassen?
-Sonst müsste man an der Stelle auch zuerst alle drei Autoren nennen, oder?
--->
-First, the participants complete the n-back levels to familiarize themselves with the task. <!-- habe es mal allgemeiner gehalten, da wir selbst auch keine sechs level haben  -->
-Then, level one is compared with all following levels by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one. <!-- s. vorheriger Kommentar -->
+A way to quantify the subjective cost of each n-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+First, the participants complete the n-back levels to familiarize themselves with the task.
+Then, level one is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.
 If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
 This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
-The idea is to estimate subjective equivalence, i.e., both offers are equally preferred [@Westbrook2013]. 
+The idea is to estimate the point of subjective equivalence, i.e. the monetary ratio in which both offers are equally preferred [@Westbrook2013]. 
 The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
-Westbrook et al.
-[-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting by plotting the SVs and computing an area under the curve (AUC).
-<!-- kann man das so sagen?
-Mit dem plotten?
-Vielleicht sollte man einfach nur sagen, die AUC wurde berechnet?
--->
-Younger participants showed lower effort discounting, i.e.
-they needed a lower monetary incentive for choosing the more difficult levels over level one.
-<!--Würde bei dieser Aussage eine Ebene höher gehen und dann also vom Effort Discounting sprechen -->
+Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting (ED) by computing an area under the curve (AUC).
+Younger participants showed lower ED, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.
 
-## Effort discounting and need for cognition 
-<!-- denke eine Zwischenüberschrift könnte das noch etwas deutlicher unterteilen-->
-The AUC in the study by Westbrook et al.
+## Effort discounting and Need for Cognition 
+The individual degree of ED in the study by Westbrook et al.
 [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
@@
 -->
+Westbrook et al.
+[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs ad an objective measure of ED.
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
+*Individuals with higher NFC report more regulation of effort [@Tan2020]*
 However, the relation of NFC and SVs might be confounded with task performance itself, since subjective task values have been shown to depend on both the exerted effort [@Wang2017] and the expected performance [@Yee2021].
@@
 ## The present study
-<!-- auch hier eine Zwischenüberschrift um es etwas besser in Blöcke einzuteilen -->
 The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
 We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level (i.e., 1-back).
-In fact, our COG-ED adaptation allows the computations of SVs, even if the individual does not have a clear preference for one task level.
-<!-- vielleicht eher "Additionally, our COG-ED adaption...
--->
+Additionally, our COG-ED adaptation allows the computations of SVs, even if the individual does not have a clear preference for one task level.
 In the present study, we will validate this adaptation by replicating the findings of Westbrook et al. [-@Westbrook2013].
-Additionally, we will apply the adaption to a task with different emotion regulation strategies to establish an effort discounting paradigm for task varieties that have no objective order of task load.
-The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but it has not been applied to tasks without objective task load so far.
-<!-- Wortwiederholung "apply" und der Satz klingt etwas sperrig...
-vielleicht 2 drauß machen?
--->
+Furthermore, the COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021].
+However, these tasks had an objective order of task load in the form of increasing n-back levels or decreasing intensity of auditory signals.
+In order to establish an ED paradigm for task varieties that do not have an objective order of task load, we will also apply the COG-ED adaption to a task with different emotion regulation strategies.
 

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
Added chunks and notes for each hypothesis

@@
 [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
-<!-- Eventuell könnte man als Anfang für diesen Abschnitt nochmal kurz NFC definieren (zweiter Teilsatz) und kurz sagen, womit das assoziiert ist...
-also vor allem mit Traits, die danach klingen, als könnte Effort Discounting eine Rolle spielen; Dann mit Westbrook in Verbindung bringen, aber vielleicht nicht von der AUC reden, sondern lieber wieder von Effort Discounting?
--->
 Westbrook et al.
-[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs ad an objective measure of ED.
+[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure of ED.
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
-*Individuals with higher NFC report more regulation of effort [@Tan2020]*
 However, the relation of NFC and SVs might be confounded with task performance itself, since subjective task values have been shown to depend on both the exerted effort [@Wang2017] and the expected performance [@Yee2021].
@@
                           read.csv, stringsAsFactors = FALSE, header = TRUE)
-  datalist_ED = lapply(list.files(here("Sampledata"), pattern = '.*ED.*csv', full.names = TRUE),
+  datalist_ED = lapply(list.files(here("Sampledata"), pattern = '.*_ED.*csv', full.names = TRUE),
                           read.csv, stringsAsFactors = FALSE, header = TRUE)
@@
 
-```{r Hypothesis_1c, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
+```{r Hypothesis_1c, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
                                          c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))
-      ## CS: das sieht mit den Kontrasten usw. irgendwie etwas kompliziert aus... Kannst gern mal beim ESER Code die ANOVAS mit dem aov_ez Package anschauen, vielleicht erleichtert es das Ganze
+
       # calculate ANOVAs
@@
 ```
+
+```{r Hypothesis_2a, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # H2a: Subjective values decline with increasing n-back level.
+
+# for each participant subjective values (SVs) for 1-, 2-, 3-, and 4-back will be calculated
+# an ANOVA with six linear contrasts will be calculated, contrasting the SVs of two n-back levels at a time
+
+```
+
+```{r Hypothesis_2b, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # H2b: Subjective values decline with increasing n-back level, even after controlling for declining task
+  # performance measured by signal detection d’ and reaction time.
+
+```
+
+```{r Hypothesis_3a, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # H3a: Subjective values predict individual NCS scores.
+
+# for each participant subjective values for 1-, 2-, 3-, and 4-back will be calculated
+# an area under the curve (AUC) will be calculated per participant
+# regression
+```
+
+```{r Hypothesis_3b, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # H3b: NTLX scores do not predict individual NCS scores.
+
+# per participant, calculate one AUC for each NTLX subscale, then average the AUC within each participant
+# predictor 1 is NTLX-AUC, predictor 2 is SV-AUC
+# multiple regression to predict NFC
+```
+
+```{r Hypothesis_3c, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # H3c: The NTLX dimensions effort and mental load predict individual NCS scores.
+
+# repeat H3b analysis with only the effort NTLX subscale AUC, not the composite of all subscales
+```

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
changed structure of SV data frame
To fit the ANOVA requirements of long data

@@
 
-  data_SV <- data.frame(subject = character(), sv1 = double(), sv2 = double(), sv3 = double(), sv4 = double())
+  data_SV <- data.frame(subject = character(), level = double(), sv = double())
 
@@
 
-    newdata <- data.frame(data_ED$subject[subjectindex[i]], mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour))
-    colnames(newdata) <- names(data_SV)
+    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
+                          level = c(1:4),
+                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
     data_SV <- rbind(data_SV, newdata)

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
calculation of hypothesis 2a

@@
 
-# for each participant subjective values (SVs) for 1-, 2-, 3-, and 4-back will be calculated
-# an ANOVA with six linear contrasts will be calculated, contrasting the SVs of two n-back levels at a time
+  # ANOVA with six linear contrasts, contrasting the SVs of two n-back levels (1,2,3,4) at a time
+
+  # make a temporary copy of the SV data frame
+
+  h2a_data <- data_SV
+  h2a_data$level <- as.factor(h2a_data$level)
+
+  # define contrasts
+
+  contrasts(h2a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
+                                     c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))
+
+  # calculate ANOVAs
+
+  hypothesis2a_anova <- summary(aov(h2a_data$sv ~ h2a_data$level))
+  hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$sv ~ h2a_data$level))
+
+  remove(h2a_data)
 

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
AUC calculation does not work yet

@@
 
-  library(here)         # to set a directory without defined paths
-  library(tidyverse)    # plotting and managing data
+  library(here)         # to set a directory without defined paths, "here" package
+  library(tidyverse)    # plotting and managing data, "tidyverse" package
+  library(bayestestR)   # computing area under the curve, "bayestestR" package
 
@@
 
+#auc(data_SV$level[1:4], data_SV$sv[1:4], method = "trapezoid", sort = FALSE) ->> gives you 2.23, which can't be
+
 # for each participant subjective values for 1-, 2-, 3-, and 4-back will be calculated

### 2021-08-20 06_Paper/COG-ED/Manuscript.Rmd
cleaned questionnaire data and added computation of hypothesis 3a

@@
   colnames(data_quest)[1] <- "set" # rename the first column
+
+  # remove unnecessary variables from questionnaire data frame
+
+  data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
+                                               general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
+                                               researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
+                                               t1_psychopy_ed_psydat, t1_psychopy_nback_csv, t1_psychopy_log, t1_psychopy_nback_psydat,
+                                               t1_psychopy_randch_log, t1_psychopy_randch_psydat, files_coged_complete, record_id_2, vl_er,
+                                               date_er, humid_bef_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
+                                               er_ed_psychopy_txt, er_ed_psychopy_psydat, files_ered_complete, followup_ered_timestamp,
+                                               nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
+                                               nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
+                                               nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
+                                               bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
+                                               who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
+                                               cdrisc_complete, flexer_timestamp, flexer_complete))
 
@@
 
-#auc(data_SV$level[1:4], data_SV$sv[1:4], method = "trapezoid", sort = FALSE) ->> gives you 2.23, which can't be
+  # create an index for the rows in which the participants change
 
-# for each participant subjective values for 1-, 2-, 3-, and 4-back will be calculated
-# an area under the curve (AUC) will be calculated per participant
-# regression
+  subjectindex <- c(1,which(data_SV$subject != dplyr::lag(data_SV$subject)),nrow(data_SV))
+
+  # prepare empty data frame for the loop to feed into
+
+  data_hyp3 <- data.frame(subject = character(), auc = double())
+
+  # calculate AUC of SVs per subject
+
+  for (i in 1:(length(subjectindex)-1)) {
+
+    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
+                         auc = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
+                                   method = "trapezoid", sort = FALSE))
+    data_hyp3 <- rbind(data_hyp3, newdata)
+
+  }
+
+  # prepare temporary data frame for loop to feed into
+
+  data_nfc <- data.frame(subject = character(), nfc = double())
+
+  # calculate NFC scores for every subject
+
+  for (i in 1:(length(setindex)-1)) {
+
+    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
+    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1
+
+    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
+                                           nfc = sum(nfc)))
+  }
+
+  # merge the NFC data frame into the AUC data frame by row
+
+  data_hyp3 <- merge(data_hyp3, data_nfc)
+
+  # delete temporary variables
+
+  remove(nfc, data_nfc)
+
+  # calculate linear model to estimate prediction of NFC by SVs
+
+  hypothesis3a <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc))
+
 ```

### 2021-08-20 06_Paper/COG-ED/Manuscript.Rmd
completed all analysis code except for MLM

@@
 
-  data_hyp3 <- data.frame(subject = character(), auc = double())
+  data_hyp3 <- data.frame(subject = character(), auc_sv = double())
 
@@
     newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
-                         auc = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
+                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                    method = "trapezoid", sort = FALSE))
@@
 
-  hypothesis3a <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc))
+  hypothesis3a <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv))
 
@@
 
-# per participant, calculate one AUC for each NTLX subscale, then average the AUC within each participant
-# predictor 1 is NTLX-AUC, predictor 2 is SV-AUC
-# multiple regression to predict NFC
+  # create an index for the rows in which the participants change
+
+  subjectindex <- c(1,which(data_ntlx$subject != dplyr::lag(data_ntlx$subject)),nrow(data_ntlx))
+
+  # prepare temporary data frame for loop to feed into
+
+  ntlx <- data.frame(subject = character(), auc_mental = double(), auc_physical = double(), auc_time = double(),
+                          auc_performance = double(), auc_effort = double(), auc_frustration = double())
+
+  # calculate AUCs per NTLX subscale per participant
+
+  for (i in 1:(length(subjectindex)-1)) {
+
+    newdata <- data.frame(subject = data_ntlx$subject[subjectindex[i]],
+                          auc_mental = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
+                                           data_ntlx$mental[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
+                          auc_physical = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
+                                           data_ntlx$physical[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
+                          auc_time = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
+                                           data_ntlx$time[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
+                          auc_performance = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
+                                           data_ntlx$performance[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
+                          auc_effort = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
+                                           data_ntlx$effort[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
+                          auc_frustration = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
+                                           data_ntlx$frustration[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE))
+    ntlx <- rbind(ntlx, newdata)
+
+  }
+
+  # add column containing the average of the NTLX subscale AUCs
+
+  ntlx <- cbind(ntlx, auc_ntlx = rowMeans(ntlx[ ,grep("auc", colnames(ntlx))]))
+
+  # merge data frames based on subject
+
+  data_hyp3 <- merge(data_hyp3, ntlx)
+
+  # delete temporary data frame
+
+  remove(ntlx)
+
+  # compute multiple linear regression to predict NCS based on SV AUC and NTLX AUC
+
+  hypothesis3b <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv + data_hyp3$auc_ntlx))
+
 ```
@@
 
-# repeat H3b analysis with only the effort NTLX subscale AUC, not the composite of all subscales
+  # compute multiple linear regression to predict NCS based on SV AUC, Effort AUC and Mental Load AUC
+
+  hypothesis3c <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv + data_hyp3$auc_mental + data_hyp3$auc_effort))
+
 ```

### 2021-08-23 06_Paper/COG-ED/Manuscript.Rmd
removed a temporary variable
added part of the methods section

@@
 ```
+
+# Methods
+
+We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
+
+##Revising the COG-ED paradigm
+The thought process behind this revision is illustrated in Figure 1.
+It shows how different modifications of the COG-ED paradigm by Westbrook et al.
+[-@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back the most, 3-back less, and 1-back the least.
+We adapted the COG-ED paradigm until it accurately reflected this preference, arriving at our version, the Cognitive and Emotion Regulation Effort Discounting Paradigm (COG-ER-ED).
+The COG-ED paradigm sets the SV of 1-back to 1, so regardless of the response pattern, the SV of 1-back does not change.
+Adding an ED round comparing 2-back and 3-back shows more differentiation between the SVs those two levels, but leaves the SV of 1-back unchanged.
+Adding three ED rounds comparing the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
+First, the SVs still contain the non-true SVs returned by the original paradigm, and second, including more task levels would lead to an exponential growth of necessary comparisons.
+Therefore, the solution and our final COG-ER-ED paradigm reduces the number of necessary comparisons by presenting an ED round for each possible pair of levels, and by starting each ED round with a choice between equal prices.
+For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
+The n-back level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
+The n-back level that was not chosen will be set to a fixed value of 2€.
+This procedure allows to compute SVs based on actual individual preference instead of objective task load.
+Each level's SV is calculated as the mean of this level's SVs from each comparison in which it appeared.
+If the participant has a clear preference for one level, this level's SV will be 1.
+If not, then no level's SV will be 1, but each level's SV is still an absolute and a relative value, which allows the computation of an AUC and therefore a quantification of the participant's ED behaviour.
 
@@
 
-  remove(ntlx)
+  remove(ntlx, newdata)
 

### 2021-08-24 06_Paper/COG-ED/Manuscript.Rmd
rwrote last introduction paragraph to include paradigm concept

@@
 We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level (i.e., 1-back).
-Additionally, our COG-ED adaptation allows the computations of SVs, even if the individual does not have a clear preference for one task level.
-In the present study, we will validate this adaptation by replicating the findings of Westbrook et al. [-@Westbrook2013].
-Furthermore, the COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021].
-However, these tasks had an objective order of task load in the form of increasing n-back levels or decreasing intensity of auditory signals.
-In order to establish an ED paradigm for task varieties that do not have an objective order of task load, we will also apply the COG-ED adaption to a task with different emotion regulation strategies.
+Figure 1 illustrates how different modifications of the COG-ED paradigm by Westbrook et al.
+[-@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back the most, 3-back less, and 1-back the least.
+The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
+Adding an ED round comparing 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
+Adding three ED rounds comparing the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
+First, the SVs are still distorted by the non-true SVs returned by the original paradigm, and second, including more task levels would lead to an exponential growth of necessary comparisons.
+Therefore, the solution lies in reducing the number of necessary comparisons by presenting an ED round for each possible pair of levels, and by starting each ED round with a choice between equal prices.
+For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
+The n-back level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
+The n-back level that was not chosen will be set to a fixed value of 2€.
+This procedure allows to compute SVs based on actual individual preference instead of objective task load.
+Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
+If the participant has a clear preference for one level, this level's SV will be 1.
+If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute value and in relation to the other levels' SVs, so the computation of an AUC and therefore the quantification of the participant's ED behaviour is still possible.
+Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
+emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (COG-ER-ED).
+In the present study, we will validate the COG-ER-ED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
+Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task.
+The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load in the form of increasing n-back levels or decreasing intensity of auditory signals.
 

### 2021-08-24 06_Paper/COG-ED/Manuscript.Rmd
Removed methods section about paradigm

@@
 
-## The present study
+## Revising the COG-ED paradigm
 The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
@@
 
-##Revising the COG-ED paradigm
-The thought process behind this revision is illustrated in Figure 1.
-It shows how different modifications of the COG-ED paradigm by Westbrook et al.
-[-@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back the most, 3-back less, and 1-back the least.
-We adapted the COG-ED paradigm until it accurately reflected this preference, arriving at our version, the Cognitive and Emotion Regulation Effort Discounting Paradigm (COG-ER-ED).
-The COG-ED paradigm sets the SV of 1-back to 1, so regardless of the response pattern, the SV of 1-back does not change.
-Adding an ED round comparing 2-back and 3-back shows more differentiation between the SVs those two levels, but leaves the SV of 1-back unchanged.
-Adding three ED rounds comparing the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
-First, the SVs still contain the non-true SVs returned by the original paradigm, and second, including more task levels would lead to an exponential growth of necessary comparisons.
-Therefore, the solution and our final COG-ER-ED paradigm reduces the number of necessary comparisons by presenting an ED round for each possible pair of levels, and by starting each ED round with a choice between equal prices.
-For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
-The n-back level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
-The n-back level that was not chosen will be set to a fixed value of 2€.
-This procedure allows to compute SVs based on actual individual preference instead of objective task load.
-Each level's SV is calculated as the mean of this level's SVs from each comparison in which it appeared.
-If the participant has a clear preference for one level, this level's SV will be 1.
-If not, then no level's SV will be 1, but each level's SV is still an absolute and a relative value, which allows the computation of an AUC and therefore a quantification of the participant's ED behaviour.
+## Procedure
 

### 2021-08-25 01_Paradigms/ER-ED/ER_Training/ER_TRAINING_lastrun.py
changed stimulus order

@@ -2,7 +2,7 @@
 # -*- coding: utf-8 -*-
 """
 This experiment was created using PsychoPy3 Experiment Builder (v2021.1.4),
-    on Juli 23, 2021, at 14:32
+    on August 25, 2021, at 10:44
 If you publish work using this script the most relevant publication is:
 
     Peirce J, Gray JR, Simpson S, MacAskill M, Höchenberger R, Sogo H, Kastman E, Lindeløv JK. (2019) 
@@ -102,6 +102,16 @@ text_instruction = visual.TextStim(win=win, name='text_instruction',
     depth=0.0);
 instr_view_resp = keyboard.Keyboard()
 
+# Initialize components for Routine "fixcross"
+fixcrossClock = core.Clock()
+text = visual.TextStim(win=win, name='text',
+    text='+',
+    font='Open Sans',
+    pos=(0, 0), height=0.1, wrapWidth=None, ori=0.0, 
+    color='black', colorSpace='rgb', opacity=None, 
+    languageStyle='LTR',
+    depth=0.0);
+
 # Initialize components for Routine "Pics"
 PicsClock = core.Clock()
 image_view = visual.ImageStim(
@@ -112,16 +122,6 @@ image_view = visual.ImageStim(
     color=[1,1,1], colorSpace='rgb', opacity=None,
     flipHoriz=False, flipVert=False,
     texRes=128.0, interpolate=True, depth=0.0)
-
-# Initialize components for Routine "fixcross"
-fixcrossClock = core.Clock()
-text = visual.TextStim(win=win, name='text',
-    text='+',
-    font='Open Sans',
-    pos=(0, 0), height=0.1, wrapWidth=None, ori=0.0, 
-    color='black', colorSpace='rgb', opacity=None, 
-    languageStyle='LTR',
-    depth=0.0);
 
 # Initialize components for Routine "Slider_Arousal"
 Slider_ArousalClock = core.Clock()
@@ -290,7 +290,7 @@ for thisBlocks_training in blocks_training:
     # ------Prepare to start Routine "Instruction"-------
     continueRoutine = True
     # update component parameters for each repeat
-    text_instruction.setText(instr_1 + '\n\n' + 'In diesem Block werden Sie eine Reihe von Bildern sehen. Diese sollen Sie aufmerksam ansehen.' + instr_2 + '\n\n' + instr_3 + '\n\n' + 'Zum Starten des Blocks Leertaste dürcken')
[…]

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd

@@
 ## Procedure
+Participants for the pilot study were recruited using the software *ORSEE* [@Greiner2015].
+The final sample consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
+Each participant completed two sessions in the lab one week apart, and a battery of personality questionnaires at least two days after the second session.
+In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
+The paradigm started with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The levels were referred to by colour (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
+After each level, participants filled out the NASA-TLX questionnaire [@Hart1988] on a tablet to assess their perceived task load.
+Then, they completed the ED procedure on screen, where each possible pairing of the four n-back levels was presented in a randomized order.
+Participants were instructed to decide as realistically as possible, because one of their choices from the last iteration steps would be randomly chosen for one final run of n-back.
+The level and its monetary value were presented on screen and participants completed one run, but this was only to incentivise truthful behaviour in the ED procedure, so the n-back data of this part was not analyzed.
+The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
+The paradigm followed the same structure of task, ED procedure, and repetition of a random "level" as in session one.
+There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
+Two days after the second session, participants received a link to the personality questionnaires (only the NFC scale [@Bless1994; @Cacioppo1984] was analyzed in the present study, the full list of questionnaires can be found in Appendix 1).
+Participants received 8€ per hour, about 30€ in total, or course credit for participation.
+Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
 

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd
wrote more introduction

@@
 The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load in the form of increasing n-back levels or decreasing intensity of auditory signals.
+
+## Hypotheses
+Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
+Regarding the associations of subjective and objective task load measures we hypothesized that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
+Regarding the associations of task load and ED we hypothesized that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
+And regarding individual differences in ED we hypothesized that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+However, since NFC is conceptually related to cognitive but not physical effort, we added the hypothesis that (3c) perceived mental load and perceived effort predict individual NFC scores.
 
@@
 
+## Questionnaires
+To assess perceived task load, we used the NASA Task Load Index (NTLX) [@Hart1988], a 6-item questionnaire with the dimensions mental load, physical load, effort, frustration, performance, and time pressure.
+Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
+Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
+A full list of questionnaires and measures can be found in Appendix 1.
+
 ## Procedure
@@
 The levels were referred to by colour (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
-After each level, participants filled out the NASA-TLX questionnaire [@Hart1988] on a tablet to assess their perceived task load.
+After each level, participants filled out the NTLX on a tablet to provide a state measure of cognitive effort.
 Then, they completed the ED procedure on screen, where each possible pairing of the four n-back levels was presented in a randomized order.
@@
 There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
-Two days after the second session, participants received a link to the personality questionnaires (only the NFC scale [@Bless1994; @Cacioppo1984] was analyzed in the present study, the full list of questionnaires can be found in Appendix 1).
-Participants received 8€ per hour, about 30€ in total, or course credit for participation.
+Two days after the second session, participants received a link to the NFC scale and other personality questionnaires to provide a trait measure of preference for cognitive effort.
+Participants received 8€ per hour or course credit for participation, plus payment for the randomly chosen level.
 Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+
+## Analysis
+We conducted all analysis as described in Westbrook et al. [-@Westbrook2013].
+The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
+Declining performance was investigated by calculating an analysis of variance (ANOVA) with three linear contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+Another ANOVA with three linear contrasts was computed to compare the mean reaction time (RT) between two levels of 2-, 3-, and 4-back at a time.
+To investigate changes in NTLX ratings, six ANOVAs were computed, one for each NTLX subscale, and each with six linear contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
+The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
+Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
+An ANOVA with six linear contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
+Each ANOVA in the analysis was followed up by a Tukey's test.
+To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
+**MLM explanation goes here**
 

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd
wrote more methods section

@@
 **MLM explanation goes here**
+The association of ED and NFC was done using three separate regressions.
+One regression used the AUC of each participant's SVs to predict their NFC score.
+The second regression additionally included the mean of the NTLX subscales' AUCs of each participant as a predictor.
+And the last regression used the AUC of each participant's SV, the AUC of the NTLX mental load subscale, and the AUC of the NTLX effort subscale to predict each participant's NFC score.
 

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd
changed file navigation

@@
 
-  here::i_am("Manuscript.Rmd")
+  here::i_am("flag_project_root.txt")
 
@@
 
-  datalist_nback = lapply(list.files(here("Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
+  datalist_nback = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
                           read.csv, stringsAsFactors = FALSE, header = TRUE)
-  datalist_ED = lapply(list.files(here("Sampledata"), pattern = '.*_ED.*csv', full.names = TRUE),
+  datalist_ED = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*_ED.*csv', full.names = TRUE),
                           read.csv, stringsAsFactors = FALSE, header = TRUE)
@@
 
-  data_quest <- read.csv(here("Sampledata","COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
+  data_quest <- read.csv(here("04_RawData", "Sampledata", "COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
   colnames(data_quest)[1] <- "set" # rename the first column

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added crossref

@@
 library(targets)
+library(readxl)
+library(here)
 ```
@@
 
-"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]
+"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]
 
@@
 
-xxx.
+The ER task followed a block design (see Figure X). Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)).
+
+```{r stimvalues, echo = FALSE}
+
+stim
+
+```
+## 2.4. Stimuli
+
+Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008].
+The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = 4.81 $\pm$ 0.52; Arousal (A): _M_ $\pm$ _SD_ = 3.00 $\pm$ 0.65)

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added root directory

@@
 library(here)
+
+# set top level directory to source file
+here::i_am("flag_project_root.txt")
 ```
@@
 
-stim
+StimNeg
 

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added imports

@@
 # set top level directory to source file
-here::i_am("flag_project_root.txt")
+here::i_am("flag_project_root_COGERED.txt")
 ```
@@
 ```{r stimvalues, echo = FALSE}
+# import excel list with neutral and negative pictures
+# lists contain arousal and valence values of each picture
+stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))
 
-StimNeg
+stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")))
 

### 2021-08-25 06_Paper/COG-ED/Manuscript.Rmd
changed flag file name and added explanation
started preparing results section

@@
 emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (COG-ER-ED).
-In the present study, we will validate the COG-ER-ED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
+In the present study, we will validate the COG-ER-ED paradigm by conceptually replicating the ED and NFC findings of Westbrook et al. [-@Westbrook2013].
 Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task.
@@
   library(bayestestR)   # computing area under the curve, "bayestestR" package
+  library(papaja)       # APA conform output, "papaja" package
 
@@
 
-  here::i_am("flag_project_root.txt")
+  here::i_am("flag_project_root_COGERED.txt")
 
@@
 
+# Results
+
+## Associations of subjective and objective task load measures
+We first looked at how performance measures and NTLX ratings change as n-back levels increase.
+Linear contrasts ANOVAs revealed decreasing performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_anova)$full_result`).
+Tukey's test confirmed that *d'* was smaller for *...(and put in row 1/2/3 ->)* (`r hypothesis1a_posthoc[["h1a_data$level"]][1,4]`).
+
 ```{r Hypothesis_1b, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
+
+Likewise, linear contrasts ANOVAs confirmed increases in RT with increasing n-back level (`r apa_print(hypothesis1b_anova)$full_result`).
+Tukey's test showed that this was the case for *...(and put in row 1/2/3 ->)* (`r hypothesis1b_posthoc[["h1b_data$level"]][1,4]`).
+Overall, the decreases in *d'* and increases in RT indicate the increase in objective task load with higher n-back levels.
 
@@
 ```
+
+Increases in subjective task load were investigated with linear contrast ANOVAs for each NTLX subscale, now including 1-back.
+Perceived mental load increased with n-back (`r apa_print(hypothesis1c1_anova)$full_result`), especially from *...(and put in row 1/2/3/4/5/6 ->)* (`r hypothesis1c1_posthoc[["h1c_data$level"]][1,4]`).
+Physical load increased as well, but not as strongly (`r apa_print(hypothesis1c2_anova)$full_result`), mainly from *...(and put in row 1/2/3/4/5/6 ->)* (`r hypothesis1c2_posthoc[["h1c_data$level"]][1,4]`).
 

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added text

@@
 
-stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")))
+stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
 
@@
 Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008].
-The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = 4.81 $\pm$ 0.52; Arousal (A): _M_ $\pm$ _SD_ = 3.00 $\pm$ 0.65)
+The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$Valenz), digits = 2)` $\pm$ `r round(sd(stim_neutral$Valenz), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$Arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$Arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
+Furhter, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
+An evolutionary algorithm () was used to cluster these pictures into five sets with comparable

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added neg values

@@
 Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008]. 
-The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$Valenz), digits = 2)` $\pm$ `r round(sd(stim_neutral$Valenz), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$Arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$Arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
+The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
 Furhter, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
-An evolutionary algorithm () was used to cluster these pictures into five sets with comparable
+An evolutionary algorithm () was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`)

### 2021-08-25 06_Paper/ER-ED/method.Rmd
added values for neg pics

@@
 Furhter, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
-An evolutionary algorithm () was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`)
+An evolutionary algorithm () was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).

### 2021-08-26 06_Paper/ER-ED/method.Rmd
added text
changed output type
added package and comments

@@
 ---
-output: 
-  pdf_document:
-    keep_tex: true
+output: html_document
 bibliography: ER_ED.bib
@@
 knitr::opts_chunk$set(echo = FALSE)
-library(targets)
-library(readxl)
-library(here)
+
+library(targets) # to keep track of all relevant files
+library(readxl) # import excel files
+library(here) # to set directories without defined paths
+library(papaja) # APA conform output
 
@@
 An evolutionary algorithm () was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
+A complete list of all pictures and their classification into sets can be found in supplementary material X.

### 2021-08-26 06_Paper/ER-ED/method.Rmd
added text
each sentence on one line

@@
 
-## 2.1 Power analysis and participants
+## 2.1 Participants
 
-xxx.
+Participants
 
@@
 
-All session took place in a shielded cabin with constant lighting. Participants received information about the
+The study consisted of two sessions, one week apart. 
+Both sessions took place in a shielded cabin with constant lighting. 
+Before each session, participants received information about the respective experimental procedure and signed informed consent. 
+At the beginning of the first session participants filled out a demographic questionnaire. 
+Afterwards the completed an n-Back task
 

### 2021-08-27 06_Paper/COG-ED/Manuscript.Rmd
added a comment

@@
 The paradigm followed the same structure of task, ED procedure, and repetition of a random "level" as in session one.
+<!--CS: Achtung: das wurde verändert: Sie wiederhuolen nicht random ein Level sondern können sich nochmal frei entscheiden!
+-->
 There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.

### 2021-08-27 06_Paper/ER-ED/method.Rmd
added text

@@
 
-"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED. 
+"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]. 
+A complete list of all measures assessed in the study can be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
+All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
 
@@
 At the beginning of the first session participants filled out a demographic questionnaire. 
-Afterwards the completed an n-Back task
+Afterwards the completed an n-Back task with the levels one to four.
 
@@
 stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
-
 ```

### 2021-08-27 06_Paper/ER-ED/method.Rmd
described experimental procedure

@@
 Afterwards the completed an n-Back task with the levels one to four.
+Then, they completed an ED procedure on screen, followed by a random repetition of one n-back level.
+The second session, containing the ER paradigm, took place exactly one week after session one.
+Participants gave signed informed consent for the second session.
+Afterwards the ER paradigm was conducted.
+Participants first received written instructions on the ER paradigm and ER strategies that they should apply.
+A training session was performed to ensure that all participants were able to implement the ER strategies.
+Next, electrodes to measure EMG were attached and the ER paradigm was conducted. 
+Two days after the secon sessoin, participants received a link to an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
 
@@
 
+## 2.4. Stimuli
 ```{r stimvalues, echo = FALSE}
@@
 ```
-## 2.4. Stimuli
 

### 2021-08-27 06_Paper/ER-ED/method.Rmd
added text to 2.3

@@
 
+Participants received 8.00€ per hour or course credit as compensation for participation.
+Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+
 ## 2.3 Emotion regulation paradigm
 
-The ER task followed a block design (see Figure X). Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)).
+The ER paradigm roughly consisted of two parts. 
+Part one could be described as standard ER task that followed a block design (see Figure X). 
+Participants were told to actively view neutral and negative pictures (see [2.4.
+Stimuli](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively.
+Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
+During this block, 20 neutral pictures were presented.
+Participants were asked to "actively view all pictures and permit all emotions that may arise."
+In the second block, participants actively viewed negative pictures.
+During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
 

### 2021-08-27 06_Paper/ER-ED/method.Rmd
added text to 2.3

@@
 The ER paradigm roughly consisted of two parts. 
-Part one could be described as standard ER task that followed a block design (see Figure X). 
+Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
 Participants were told to actively view neutral and negative pictures (see [2.4.
@@
 During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
+In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
+During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
+Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
 

### 2021-08-27 06_Paper/ER-ED/method.Rmd
added text to 2.3 ER paradigm

@@
 
-The ER paradigm roughly consisted of two parts. 
+The ER paradigm roughly consisted of three parts that will be described in the following.
+
+_Part one: ER task._ <br>
 Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
@@
 Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
+During suppression, participants were told to "suppress their emotional facial expression."
+They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
+Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
+All participants received written instruction and completed a training session.
+After the training session, participants were asked about their applied ER strategies to avoid misapplication.
+The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.
+
+_Part two: ER effort discounting._ <br>
+In the second part, ER effort discounting took place.
+Each possible pairing of strategies (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression) was presented in a randomized order.
+Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.
+
+_Part three: ER choice._ <br>
 

### 2021-09-01 06_Paper/COG-ED/Manuscript.Rmd
changed names and file refs

@@
 Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
-emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (COG-ER-ED).
-In the present study, we will validate the COG-ER-ED paradigm by conceptually replicating the ED and NFC findings of Westbrook et al. [-@Westbrook2013].
+emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
+In the present study, we will validate the CERED paradigm by conceptually replicating the ED and NFC findings of Westbrook et al. [-@Westbrook2013].
 Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task.
@@
 
-  data_quest <- read.csv(here("04_RawData", "Sampledata", "COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
+  data_quest <- read.csv(here("04_RawData", "Sampledata", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
   colnames(data_quest)[1] <- "set" # rename the first column
@@
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.
 

### 2021-09-01 01_Paradigms/COG-ED/t1_Paradigm.py

@@ -59,19 +59,19 @@ filename3 = _thisDir + os.sep + u'data/%s_%s_%s' % (expInfo['Participant'], expN
 # For n-back
 thisExp1 = data.ExperimentHandler(name=expName1, version='',
     extraInfo=expInfo, runtimeInfo=None,
-    originPath='C:\\Users\\josep\\Documents\\04_Projekte\\01_COG-ED_Revision\\CogEmotED\\01_Paradigms\\COG-ED\\t1_Paradigm.py',
+    originPath='C:\\Users\\josep\\Documents\\04_Projekte\\01_COG-ED_Revision\\CERED\\01_Paradigms\\COG-ED\\t1_Paradigm.py',
     savePickle=True, saveWideText=True,
     dataFileName=filename1)
 # For Effort Discounting
 thisExp2 = data.ExperimentHandler(name=expName2, version='',
     extraInfo=expInfo, runtimeInfo=None,
-    originPath='C:\\Users\\josep\\Documents\\04_Projekte\\01_COG-ED_Revision\\CogEmotED\\01_Paradigms\\COG-ED\\t1_Paradigm.py',
+    originPath='C:\\Users\\josep\\Documents\\04_Projekte\\01_COG-ED_Revision\\CERED\\01_Paradigms\\COG-ED\\t1_Paradigm.py',
     savePickle=True, saveWideText=True,
     dataFileName=filename2)
 # For the final n-back level at the end that is randomly chosen
 thisExp3 = data.ExperimentHandler(name=expName3, version='',
     extraInfo=expInfo, runtimeInfo=None,
-    originPath='C:\\Users\\josep\\Documents\\04_Projekte\\01_COG-ED_Revision\\CogEmotED\\01_Paradigms\\COG-ED\\t1_Paradigm.py',
+    originPath='C:\\Users\\josep\\Documents\\04_Projekte\\01_COG-ED_Revision\\CERED\\01_Paradigms\\COG-ED\\t1_Paradigm.py',
     savePickle=True, saveWideText=True,
     dataFileName=filename3)
 
@@ -106,18 +106,18 @@ defaultKeyboard = keyboard.Keyboard()
 levelinwordsList = ['direkt', 'zwei', 'drei', 'vier'] # will be used in the instructions
[…]

### 2021-09-01 06_Paper/ER-ED/method.Rmd
added 2.1

@@
 
-## 2.1 Participants
+## 2.1 Sampling plan
 
-Participants
+Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
+Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
 

### 2021-09-01 06_Paper/ER-ED/method.Rmd
added text

@@
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED. 
-"We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012]. 
-A complete list of all measures assessed in the study can be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
+According to the 21-word-solution, "We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
+A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
 All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
@@
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
+We will use all available data in subsequent analyses.
+However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
 
@@
 The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
-Furhter, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
-An evolutionary algorithm () was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
+Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used. 
+An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
 A complete list of all pictures and their classification into sets can be found in supplementary material X.

### 2021-09-02 01_Paradigms/COG-ED/t1_Paradigm.py
corrected computation of feedback

@@ -788,15 +788,18 @@ for nx in nlevel:
         pCorr = (nCorr*100)/64 # percentage of correct trials
         pCorr = round(pCorr, 1) # round the percentage to 1 number after the decimal point
 
-        nCorrTarArray = nback_run.data['trial_resp.keys'][-64:] # extract response data
-        nCorrTarFilter = nCorrTarArray == 'right' # index the data of the targets
-        nCorrTar = sum(nCorrTarFilter) # calculate sum of correct targets aka sum of TRUE output of the filter
+        nCorrTarArray = np.array(nback_run.data['trial_resp.keys'][-64:]) # extract response data as numpy array
+        corrResp = np.array(nback_run.data['trial_resp.corr'][-64:]) # extract correctness data as numpy array
+        nCorrTarFilter = np.where((nCorrTarArray == 'right') & (corrResp == 1)) # index where targets were correctly responded to
+        nCorrTar = corrResp[nCorrTarFilter] # elements of correct responses to targets
+        nCorrTar = len(nCorrTar) # calculate sum of correct responses to targets
         pCorrTar = (nCorrTar*100)/16 # percentage of correct targets
         pCorrTar = np.around(pCorrTar, 1) # round the percentage to the decimal point
 
-        nCorrNonTarArray = nback_run.data['trial_resp.keys'][-64:] # extract response data
-        nCorrNonTarFilter = nCorrNonTarArray == 'left' # index the data of the non-targets
-        nCorrNonTar = sum(nCorrNonTarFilter) # calculate sum of correct non-targets aka sum of TRUE output of the filter
+        nCorrNonTarArray = np.array(nback_run.data['trial_resp.keys'][-64:]) # extract response data as numpy array
+        nCorrNonTarFilter = np.where((nCorrNonTarArray == 'left') & (corrResp == 1)) # index where non-targets were correctly responded to
+        nCorrNonTar = corrResp[nCorrNonTarFilter]  # elements of correct responses to non-targets
+        nCorrNonTar = len(nCorrNonTar) # calculate sum of correct responses to non-targets
         pCorrNonTar = (nCorrNonTar*100)/48 # percentage of correct non-targets
         pCorrNonTar = np.around(pCorrNonTar, 1) # round the percentage to the decimal point
 

### 2021-09-02 01_Paradigms/COG-ED/t1_Paradigm.py
updated string-ification of numpy array type in feedback message

@@ -807,33 +807,33 @@ for nx in nlevel:
         if nx != 3:
             if rx == 0:
                 if pCorrTar >= 50 and pCorrNonTar >= 50:
-                    msg = "In diesem Block haben Sie auf " + str(pCorrTar[0]) + "% der sich wiederholenden und auf "\
-                        + str(pCorrNonTar[0]) + "% der einzelnen Buchstaben korrekt reagiert.\n\nWeiter so!\n\nDrücken Sie die Leertaste, um einen weiteren Durchgang dieses Levels zu beginnen."
+                    msg = "In diesem Block haben Sie auf " + str(pCorrTar) + "% der sich wiederholenden und auf "\
+                        + str(pCorrNonTar) + "% der einzelnen Buchstaben korrekt reagiert.\n\nWeiter so!\n\nDrücken Sie die Leertaste, um einen weiteren Durchgang dieses Levels zu beginnen."
                 else:
-                    msg = "In diesem Block haben Sie auf " + str(pCorrTar[0]) + "% der sich wiederholenden und auf "\
-                        + str(pCorrNonTar[0]) + "% der einzelnen Buchstaben korrekt reagiert.\n\nBitte strengen Sie sich mehr an!\n\nDrücken Sie die Leertaste, um einen weiteren Durchgang dieses Levels zu beginnen."
+                    msg = "In diesem Block haben Sie auf " + str(pCorrTar) + "% der sich wiederholenden und auf "\
+                        + str(pCorrNonTar) + "% der einzelnen Buchstaben korrekt reagiert.\n\nBitte strengen Sie sich mehr an!\n\nDrücken Sie die Leertaste, um einen weiteren Durchgang dieses Levels zu beginnen."
             else:
                 if pCorrTar >= 50 and pCorrNonTar >= 50:
-                    msg = "In diesem Block haben Sie auf " + str(pCorrTar[0]) + "% der sich wiederholenden und auf "\
-                        + str(pCorrNonTar[0]) + "% der einzelnen Buchstaben korrekt reagiert.\n\nWeiter so!\n\nDrücken Sie die Leertaste, um die Instruktion des nächsten Levels zu lesen."
+                    msg = "In diesem Block haben Sie auf " + str(pCorrTar) + "% der sich wiederholenden und auf "\
[…]

### 2021-09-02 06_Paper/ER-ED/intro.Rmd

---
title: "intro"
author: "Christoph Scheffel"
output: html_document
---

Das ist nur eine Test-Intro

### 2021-09-02 06_Paper/ER-ED/method.Rmd

@@
 # set top level directory to source file
-here::i_am("flag_project_root_COGERED.txt")
+here::i_am("flag_project_root_CERED.txt")
 ```
@@
 _Part three: ER choice._ <br>
+After the discounting part, participants could choose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
+Importantly, there were no further instruction, on what basis they should make their decision.
 

### 2021-09-09 06_Paper/COG-ED/Manuscript.Rmd
changed file name of flag file

@@
 
-  here::i_am("flag_project_root_COGERED.txt")
+  here::i_am("flag_project_root_CERED.txt")
 
@@
 
-  data_quest <- read.csv(here("04_RawData", "Sampledata", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
+  data_quest <- read.csv(here("04_RawData", "Sampledata", "COGED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
   colnames(data_quest)[1] <- "set" # rename the first column

### 2021-09-21 06_Paper/ER-ED/method.Rmd
added sections
added text

@@
 In the second part, ER effort discounting took place.
-Each possible pairing of strategies (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression) was presented in a randomized order.
+The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013]
+For each possible pairing, two strategies (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression) with monetary values were presented.
+The order of the comparisons was randomized.
+
 Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.
@@
 A complete list of all pictures and their classification into sets can be found in supplementary material X.
+
+## 2.5 Electromyography
+
+## 2.6 Psychometric measures
+
+## 2.7 Statistics

### 2021-09-21 06_Paper/ER-ED/method.Rmd
added text

@@
 In the second part, ER effort discounting took place.
-The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013]
-For each possible pairing, two strategies (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression) with monetary values were presented.
+The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with an addition to be useful for the current study.
+We used an adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one.
+For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies  with monetary values were presented.
 The order of the comparisons was randomized.
-
+Because there is no strategy that is objectively more difficult, all comparisons began with 
 Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

### 2021-09-22 01_Paradigms/COG-ED/t1_Paradigm.py
changed indentation of buffer screen routine

@@ -1041,106 +1041,106 @@ for edx in EDrounds:
                 exec('{} = thisEDround[paramName]'.format(paramName))
 
         # ------Prepare to start Routine "bufferscreen"-------
-            continueRoutine = True
-            routineTimer.add(0.300000)
-            # update component parameters for each repeat
-            bufferscreenkey.keys = []
-            bufferscreenkey.rt = []
-            _bufferscreenkey_allKeys = []
-            # keep track of which components have finished
-            EDbufferscreenComponents = [EDbufferscreen, bufferscreenkey]
-            for thisComponent in EDbufferscreenComponents:
-                thisComponent.tStart = None
-                thisComponent.tStop = None
-                thisComponent.tStartRefresh = None
-                thisComponent.tStopRefresh = None
-                if hasattr(thisComponent, 'status'):
-                    thisComponent.status = NOT_STARTED
-            # reset timers
-            t = 0
-            _timeToFirstFrame = win.getFutureFlipTime(clock="now")
-            EDbufferscreenClock.reset(-_timeToFirstFrame)  # t0 is time of first possible flip
-            frameN = -1
+        continueRoutine = True
+        routineTimer.add(0.300000)
+        # update component parameters for each repeat
+        bufferscreenkey.keys = []
+        bufferscreenkey.rt = []
+        _bufferscreenkey_allKeys = []
+        # keep track of which components have finished
+        EDbufferscreenComponents = [EDbufferscreen, bufferscreenkey]
+        for thisComponent in EDbufferscreenComponents:
+            thisComponent.tStart = None
+            thisComponent.tStop = None
+            thisComponent.tStartRefresh = None
+            thisComponent.tStopRefresh = None
+            if hasattr(thisComponent, 'status'):
+                thisComponent.status = NOT_STARTED
+        # reset timers
+        t = 0
+        _timeToFirstFrame = win.getFutureFlipTime(clock="now")
+        EDbufferscreenClock.reset(-_timeToFirstFrame)  # t0 is time of first possible flip
+        frameN = -1
+
+        # -------Run Routine "bufferscreen"-------
+        while continueRoutine and routineTimer.getTime() > 0:
+            # get current time
+            t = EDbufferscreenClock.getTime()
+            tThisFlip = win.getFutureFlipTime(clock=EDbufferscreenClock)
+            tThisFlipGlobal = win.getFutureFlipTime(clock=None)
+            frameN = frameN + 1  # number of completed frames (so 0 is the first frame)
+            # update/draw components on each frame
     
[…]

### 2021-10-04 06_Paper/ER-ED/intro.Rmd
added text

@@
 
-Das ist nur eine Test-Intro
+# 1. Introduction
+
+[...]
+Individual subjective values of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
+
+## Adapting an effort discounting paradigm
+
+In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
+Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, variing reward.

### 2021-10-04 06_Paper/ER-ED/intro.Rmd
added text

--- 2021-09-02 06_Paper/ER-ED/intro.Rmd
@@
 
-Das ist nur eine Test-Intro
+# 1. Introduction
+
+[...]
+Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
+
+## Adapting an effort discounting paradigm
+
+In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
+Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
+In the current study, we want to use this paradigm to determine SVs of ER strategies.
+In doing so, we need to make an important change: we have to change the assumption that the easiest *N*-back level has the highest SV.
+That is necessary, because there is nothing like an objectively easier and less effortful strategy.
+As we have shown in previous studies, there are inter-individual differences in the preference of ER strategies [Scheffel2021].

### 2021-10-05 06_Paper/ER-ED/intro.Rmd

@@
 In the current study, we want to use this paradigm to determine SVs of ER strategies.
-In doing so, we need to make an important change: we have to change the assumption that the easiest *N*-back level has the highest SV.
-That is necessary, because there is nothing like an objectively easier and less effortful strategy.
-As we have shown in previous studies, there are inter-individual differences in the preference of ER strategies [Scheffel2021].
+In doing so, we need to make an important change: we have to adapt the assumption that the easiest *N*-back level has the highest SV.
+As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].

### 2021-10-05 06_Paper/ER-ED/method.Rmd

@@
 We used an adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one.
+
+[...]
 For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies  with monetary values were presented.
@@
 _Part three: ER choice._ <br>
-After the discounting part, participants could choose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
+After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
 Importantly, there were no further instruction, on what basis they should make their decision.
@@
 
+[...]
+
 ## 2.6 Psychometric measures
 
+[...]
+
 ## 2.7 Statistics
+
+[...]

### 2021-10-05 06_Paper/ER-ED/method.Rmd
Update method.Rmd
added comment
added text
added ERQ

@@
 
-[...]
+[...] <!-- Anne tried to implement a sentence here. -->
 
@@
 
-[...]
+Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
+This survey contains a number of questionnaires.
+Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
 

### 2021-10-05 06_Paper/ER-ED/method.Rmd
added questionnaires

@@
 Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
-This survey contains a number of questionnaires.
+This survey contained a number of questionnaires:
+General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
 Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
+For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
+To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
 

### 2021-10-05 06_Paper/ER-ED/method.Rmd
added text
added questionnaires

@@
 Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
-This survey contained a number of questionnaires:
-General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
+This survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
 Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
 For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
+Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
 To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
+To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
+Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
 

### 2021-10-06 06_Paper/ER-ED/method.Rmd
added questionnaires
added text

@@
 Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
-Participants were told to actively view neutral and negative pictures (see [2.4.
-Stimuli](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively.
+Participants were told to actively view neutral and negative pictures (see [2.4](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively.
 Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
@@
 In the second part, ER effort discounting took place.
-The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with an addition to be useful for the current study.
-We used an adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one.
-
-[...]
-For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies  with monetary values were presented.
+The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change (see [1.1](##adapting an effort discounting paradigm)).
+We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
+distancing, distraction vs.
+suppression, and distancing vs.
+suppression), two strategies with monetary values were presented.
 The order of the comparisons was randomized.
@@
 
-## 2.4. Stimuli
+## 2.4 Stimuli
 ```{r stimvalues, echo = FALSE}
@@
 This survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
+To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
 Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].

### 2021-10-06 06_Paper/ER-ED/method.Rmd
added text

@@
 The order of the comparisons was randomized.
-Because there is no strategy that is objectively more difficult, all comparisons began with 
+Because there is no strategy that is objectively more difficult, all comparisons began with the option "1 EUR for strategy A or 1 EUR for strategy B".
+
 Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

### 2021-10-06 06_Paper/ER-ED/method.Rmd
added text

--- 2021-10-06 06_Paper/ER-ED/method.Rmd
@@
 In the second part, ER effort discounting took place.
-The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change (see [1.1](##adapting an effort discounting paradigm)).
+The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
 We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
@@
 The order of the comparisons was randomized.
-Because there is no strategy that is objectively more difficult, all comparisons began with 
+Because there is no strategy that is objectively more difficult, we added an initial comparison that began with the option "1 EUR for strategy A or 1 EUR for strategy B".
+The 
 Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

### 2021-10-06 06_Paper/ER-ED/method.Rmd
added description of experiment

@@
 Because there is no strategy that is objectively more difficult, we added an initial comparison that began with the option "1 EUR for strategy A or 1 EUR for strategy B".
-The 
+The strategy that was not chosen was assigned the value 2 EUR.
+From this point on, comparisons between strategies followed the original COG-ED paradigm [@Westbrook2013].
 Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.
@@
 Importantly, there were no further instruction, on what basis they should make their decision.
+Participants should make their decision freely, according to the criteria they considered important for themselves.
+However, participants were asked to state the reasons for the decision afterwards.
+As soon as they had decided, they saw the respective instruction. 
+After, the block with another 20 negative pictures started.
 

### 2021-10-06 06_Paper/ER-ED/intro.Rmd
added text

@@
 
-## Adapting an effort discounting paradigm
+## 1.1 ER strategies discounting
 
@@
 As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
+Moreover, there is nothing like the objectively easiest ER strategy.
+Therefore, we have to add an additional step were the option with the higher subjective value is determined. 
+In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
+The assumption is that participants now choose the option that has the higher SV for them.

### 2021-10-08 06_Paper/ER-ED/intro.Rmd
added text

@@
 The assumption is that participants now choose the option that has the higher SV for them.
+In the next step we return to the original paradigm.
+The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
+In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
+
+## Hypotheses

### 2021-10-08 06_Paper/ER-ED/intro.Rmd
added text to 1.1

@@
 In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
+This procedure will be repeated until all strategies have been compared.
+The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
+In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
+But our paradigm can also account for the case that a person does not have a clear preference.
+Then no SV will be 1, but at least the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs.
 

### 2021-10-08 06_Paper/ER-ED/intro.Rmd
added text
added aims of the study

@@
 [...]
+<!-- SVs wären gut um um besser sachen ausrechnen zu können-->
 Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
@@
 Then no SV will be 1, but at least the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs.
+The aim of the present study is to evaluate, if this paradigm is suitable for determining SVs of ER strategies. 
+We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
 

### 2021-10-08 06_Paper/ER-ED/intro.Rmd
added hypotheses

@@
 Then no SV will be 1, but at least the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs.
+
+## 1.2 The present study
 The aim of the present study is to evaluate, if this paradigm is suitable for determining SVs of ER strategies. 
 We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
-
-## Hypotheses
+We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively effortful than distraction and suppression.
+Regarding SVs of ER strategies we expect that (3a) people chose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
+Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs.

### 2021-10-08 06_Paper/ER-ED/method.Rmd
changed layout

@@
 
-_Part one: ER task._ <br>
+*Part one: ER task.* <br>
 Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
@@
 
-_Part two: ER effort discounting._ <br>
+*Part two: ER effort discounting.* <br>
 In the second part, ER effort discounting took place.
@@
 
-_Part three: ER choice._ <br>
+*Part three: ER choice.* <br>
 After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
@@
 
+Electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
+Passive
 [...] <!-- Anne tried to implement a sentence here. -->

### 2021-10-12 06_Paper/ER-ED/method.Rmd

@@
 
-Electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
-Passive
+Bipolar electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
+Passive surface Ag/AgCl electrodes (XX mm diameter, XX distance between electrodes) filled with electrolyte gel were used.
 [...] <!-- Anne tried to implement a sentence here. -->

### 2021-10-12 06_Paper/COG-ED/Manuscript.Rmd
Update Corinna manuscript & analyses

@@
 knitr::opts_chunk$set(echo = TRUE)
+# FIXME I propose to put the packages required here at the very beginning.
 library(bibtex)
@@
   library(papaja)       # APA conform output, "papaja" package
+  library(nlme)         # fitting nonlinear mixed-effects model
+# we could add the package versions here additionally
 
@@
 
-  # put relevant data into a dataframes
+  # put relevant data into data frames
 
@@
   data_nback$response <- as.numeric(data_nback$response)
+
   # the choice column will contain 1 for the left button and 2 for the right button
@@
   # since only the last choice of each comparison is relevant, we will keep only those rows
-
   data_ED <- data_ED[data_ED$step == 6,]
@@
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
+# FIXME add version no. and packages
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.
@@
 To assess perceived task load, we used the NASA Task Load Index (NTLX) [@Hart1988], a 6-item questionnaire with the dimensions mental load, physical load, effort, frustration, performance, and time pressure.
+FIXME: NTLX seems not to be the commonly used abbreviation. We my refer to NASA TLX / NASA-TLX or just TLX. We may provide more information (see Strobel et al. 2020):
+In the NASA-TLX, participants evaluate their subjective perception of the mental, physical and temporal svs of a particular task, as well as their performance, effort and frustration during the task on a 20-point scale for each dimension.
+In its original, the NASA-TLX also requires comparisons of two dimensions each.
+For this study, we relinquished the comparison due to time restrictions.
+
 Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
+FIXME: We may need to add information on example items, rating scale and reliability (see diffpp):
+_Need for Cognition_ was assessed with the 16-item short version of the German NFC scale [@Bless1994].
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
+The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
+
 Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
@@
   # apply the addition or subtraction of 0.015625 to the last choices
+# FIXME why do we have to do this?
 
@@
   # z-transform the hit rate and the false alarm rate
+  # FIXME: What makes this transformation necessary? Why per n-back level separately? Is this the standard procedure?
+  # FIXME: for z-transformation we could use function scale:
+
+  # # create new variables
+  # dprime$falsealarmrate.z = dprime$hitrate.z =NA
+  # for (i in 1:4) {
+  #    dprime$hitrate.z[which(dprime$level == i)]        <- scale(dprime$hitrate[which(dprime$level == i)])
+  #    dprime$falsealarmrate.z[which(dprime$level == i)] <- scale(dprime$falsealarmrate[which(dprime$level == i)])
+  # }
 
@@
       hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))
+      # TODO  check for posthoc test alternative
+      #       anova calculation
       remove(h1a_data)
@@
   }
+
+# FIXME what about RT preprocessing
+  # correct / postcorrect     *see Westbrook et al. 2013, table 1: correct trials
+  # log-transformation
+  # valid answers: false alarm vs. missing -> plausible responses
 
@@
 
+# define variables -------------------------------------------------------------
+# dependent variable:     SV                    numeric                 data_SV
+# indepenendent variable: n-back level [1-4]    numeric                       
+# controlled regressors:  d'                    numeric                 dprime
+#                         mRT                   numeric                 rt
+
+# get all relevant variables ---------------------------------------------------
+
+h2b_data <- cbind(data_SV, dprime["d"], rt["meanrt"])
+
+# check and specify correct data types -----------------------------------------
+str(h2b_data)
+
+# center predictors ------------------------------------------------------------
+# center level 1 predictors
+# two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
+# level 1 predictor (SV) is of substantive interest
+# > CWC
+
+# d'
+h2b_data$d.mwc <- ave(h2b_data$d, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
+h2b_data$d.cwc <- h2b_data$d - h2b_data$d.mwc
+
+# mRT
+h2b_data$meanrt.mwc <- ave(h2b_data$meanrt, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
+h2b_data$meanrt.cwc <- h2b_data$meanrt - h2b_data$meanrt.mwc
+
+# level
+h2b_data$level.mwc <- ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
+h2b_data$level.cwc <- h2b_data$level - h2b_data$level.mwc
+
+# no level 2 predictors
+
+# change global coding to orthogonal sum-to-zero contrast by -------------------
+options(contrasts = c("contr.sum", "contr.poly"))
+
+# null model -------------------------------------------------------------------
+# m0_h2b <- nlme(model = sv ~ 1,
+#                data = h2b_data,
+#                random = ~ 1 | subject, 
+#                method = "REML")
+
+# full model -------------------------------------------------------------------
+# random intercept vs. random slope ???
+# "subject-specific intercepts" speaks for random-slopes-model, as within this model 
+# the slope is allowed to vary between subjects
+
+# m1_h2b <- nlme(sv ~ d.cwc + meanrt.cwc + level.cwc + (level.cwc| subject),
+#                data = h2b_data,
+#                fixed = ...,
+#                random = ...,
+#                control = ...,
+#                method = "REML")
+
+# initVals <- getInitial(sv ~ d.cwc + meanrt.cwc + level.cwc, data = h2b_data)
+
+# get initial values for mlm start
+fm.lm <- lm(sv ~ d.cwc + meanrt.cwc + level.cwc, h2b_data)
+st <- coef(fm.lm)
+
+m1_h2b <- nlme(sv ~ d.cwc + meanrt.cwc + level.cwc,
+               data = h2b_data,
+               #fixed = d.cwc + meanrt.cwc + level.cwc ~ 1,
+               fixed = list(d.cwc ~ 1, meanrt ~ 1, level.cwc ~ 1),
+               random = level.cwc ~ 1 | subject,
+               start = list(fixed = st[2:4]),
+               method = "REML")
+
+# change global coding to default ----------------------------------------------
+options(contrasts = c("contr.treatment", "contr.poly"))
+
 ```

### 2021-10-12 06_Paper/COG-ED/Manuscript.Rmd
comments on ANOVA

@@
   # ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
+  # FIXME:  actually, I guess, we have a MANOVA here as we look at repeated measures of a subject's reaction time 
+  #         under different load levels (= time points)
 
@@
 
-      h1a_data <- dprime[dprime$level != 1,]
+      h1a_data <- dprime[dprime$level != 1,]      # Westbrook et al. exclude level 1, do you understand why?
       h1a_data$level <- as.factor(h1a_data$level)
@@
 
-      contrasts(h1a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))
+      contrasts(h1a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))     # there are predefined contrasts that may fit like contr.sum(3); contr.treatment(); contr.poly()
 
@@
 
-      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))
-      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))
-      # TODO  check for posthoc test alternative
-      #       anova calculation
+      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))         # this calculates ANOVA without the specified contrasts and might be redundant
+      hypothesis1a_anova.lm <- summary.lm(aov(h1a_data$d ~ h1a_data$level))   # this gives you the contrasted result
+      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))      # post hoc analyses should be redundant as we already contrasted the levels
+
+  # FIXME:  actually, I guess, we have a MANOVA here as we have repeated measures of a subject's reaction time 
+  #         under different load levels (= time points)
+      library(ez) # compute repeated measurement ANOVA
+      h1a_data$subject <- factor(h1a_data$subject)
+      # if there are reasonable concerns that we have NAs within our data set, we need to exclude this data beforehand
+
+      # https://stackoverflow.com/questions/35891062/planned-contrasts-using-ezanova-output-in-r
+      # set orthogonal contrasts
+      options(contrasts = c("contr.sum", "contr.poly"))
+      hypothesis1a_Manova <- ezANOVA(h1a_data, dv = d, wid = subject, within = level, type = 3, return_aov = T) 
+      # I propose to use type-III sums of squares even if we do have a balanced design, but we may discuss that. 
+      # alternatively we could use afex, results might be plotted easier; it is also possible to set up a linear model
+      # TODO: find a way to plot means
+        # if Mauchly's Test for Sphericity is sign > report Greenhouse-Geisser Epsilon (GGe) or Huynh-Feldt-Epsilon (HFe)
+
+      # get emmeans
+      library(emmeans)
+      # this only works without the manually defined contrasts in line 439
+      hypothesis1a_emm <- emmeans(hypothesis1a_Manova$aov, ~ level) 
+      # these means should be used for reporting/ plotting the means per load level
+
+      # get the contrasts
+      pairs(hypothesis1a_emm, adjust = "Holm")
+      # or
+      contrast(hypothesis1a_emm, list(c1 = c(1,-1,0), c2 = c(1,0,-1), c3 = c(0,1,-1)))
+
+      # alternatively, post hoc tests can be run
+      # as we have 3 levels in factor load level, we would run a fisher's least significant differences (FLSD)
+      hypothesis1a_fisher <- ezStats(h1a_data, dv = d, wid = subject, within = level, type = 3)
+
+      #calculate and save mean differences
+      p1.p2 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[2]
+      p1.p3 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[3]
+      p2.p3 <- hypothesis1a_fisher$Mean[2] - hypothesis1a_fisher$Mean[3]
+
+      #if absolute value is higher than fsld, the pairwise comparison is significant
+      abs(p1.p2) > hypothesis1a_fisher$FLSD[1]
+      abs(p1.p3) > hypothesis1a_fisher$FLSD[1]   
+      abs(p2.p3) > hypothesis1a_fisher$FLSD[1]
+
       remove(h1a_data)

### 2021-10-13 06_Paper/COG-ED/Manuscript.Rmd
update analysis

--- 2021-10-12 06_Paper/COG-ED/Manuscript.Rmd
@@
 Each ANOVA in the analysis was followed up by a Tukey's test.
+# would it be possible to compare the originally calculated SV with our new one?
 To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
@@
   # ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
+  # FIXME:  actually, I guess, we have a rmANOVA here as we look at repeated measures of a subject's reaction time 
+  #         under different load levels (= time points), see below
 
@@
 
-      h1a_data <- dprime[dprime$level != 1,]
+      h1a_data <- dprime[dprime$level != 1,]      # FIXME: Westbrook et al. exclude level 1, do you understand why?
       h1a_data$level <- as.factor(h1a_data$level)
@@
 
-      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))
-      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))
-      # TODO  check for posthoc test alternative
-      #       anova calculation
+      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))         # this calculates ANOVA without the specified contrasts and might be redundant
+      hypothesis1a_anova.lm <- summary.lm(aov(h1a_data$d ~ h1a_data$level))   # this gives you the contrasted result
+      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))      # post hoc analyses should be redundant as we already contrasted the levels
+
+  # FIXME:  rmANOVA
+      library(ez) # compute repeated measurement ANOVA
+      h1a_data$subject <- factor(h1a_data$subject)
+      # if there are reasonable concerns that we have NAs within our data set, we need to exclude this data beforehand
+
+      # https://stackoverflow.com/questions/35891062/planned-contrasts-using-ezanova-output-in-r
+      # set orthogonal contrasts
+      options(contrasts = c("contr.sum", "contr.poly"))
+      hypothesis1a_rmanova <- ezANOVA(h1a_data, dv = d, wid = subject, within = level, type = 3, return_aov = T) 
+      # I propose to use type-III sums of squares even if we do have a balanced design, but we may discuss that. 
+      # alternatively we could use afex, results might be plotted easier; it is also possible to set up a linear model
+      # TODO: find a way to plot means
+        # if Mauchly's Test for Sphericity is sign > report Greenhouse-Geisser Epsilon (GGe) or Huynh-Feldt-Epsilon (HFe)
+
+      # get emmeans
+      library(emmeans)
+      # this only works without the manually defined contrasts in line 439
+      hypothesis1a_emm <- emmeans(hypothesis1a_rmanova$aov, ~ level) 
+      # these means should be used for reporting/ plotting the means per load level
+
+      # get the contrasts
+      pairs(hypothesis1a_emm, adjust = "Holm")
+      # or
+      contrast(hypothesis1a_emm, list(c1 = c(1,-1,0), c2 = c(1,0,-1), c3 = c(0,1,-1)))
+
+      # alternatively, post hoc tests can be run
+      # as we have 3 levels in factor load level, we would run a fisher's least significant differences (FLSD)
+      hypothesis1a_fisher <- ezStats(h1a_data, dv = d, wid = subject, within = level, type = 3)
+      # calculate and save mean differences
+      p1.p2 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[2]
+      p1.p3 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[3]
+      p2.p3 <- hypothesis1a_fisher$Mean[2] - hypothesis1a_fisher$Mean[3]
+
+      #if absolute value is higher than fsld, the pairwise comparison is significant
+      abs(p1.p2) > hypothesis1a_fisher$FLSD[1]
+      abs(p1.p3) > hypothesis1a_fisher$FLSD[1]   
+      abs(p2.p3) > hypothesis1a_fisher$FLSD[1]
+
       remove(h1a_data)
@@
 
-# FIXME what about RT preprocessing
+# FIXME what about RT preprocessing?
   # correct / postcorrect     *see Westbrook et al. 2013, table 1: correct trials
@@
       hypothesis1c6_posthoc <- TukeyHSD(aov(h1c_data$frustration ~ h1c_data$level))
+
+      # TODO: see H1a. 
+      num_vars <- c("mental", "physical", "time", "performance", "effort", "frustration")
+      h1c_data[num_vars] <- lapply(h1c_data[num_vars], as.numeric)
+      hypothesis1c_rmanova <- ezANOVA(h1c_data, dv = mental, wid = subject, within = level, 
+                                       type = 3, return_aov = T)
+      #...
+
+      # We may also run a rmMANOVA
+      # https://cran.r-project.org/web/packages/MANOVA.RM/vignettes/Introduction_to_MANOVA.RM.html
+      library(MANOVA.RM)
+      # we need to convert our data frame to clean wide or long format
 
@@
 
-  data_hyp3 <- data.frame(subject = character(), auc_sv = double())
+  h3_data <- data.frame(subject = character(), auc_sv = double())
 
@@
                                    method = "trapezoid", sort = FALSE))
-    data_hyp3 <- rbind(data_hyp3, newdata)
+    h3_data <- rbind(h3_data, newdata)
 
@@
     nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
+    # define and invert items to be recoded
     nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1
@@
 
+# further preprocessing of nfc-data ---------------------------------------------
+  # FIXME: actually we would now
+  # 1. determine deviation from univariate normality using Shapiro Wilk test
+  # 2. normalize and standardize sum scores by Blom's formula (1954)
+  # 3. again determine deviation from univariate normality of data from second step using Shapiro Wilk test
+  # this would mean:
+
+  # required scripts (might be best at the beginning, following the packages) --
+
+  ## for normalizing variables
+normalize.gen <- function(data, whichFormula=2, whichMeanSD=1) {
+  # normalizes DATA using one of the formulae:
+  #
+  # 1 = Van der Waerden (1952): r * / (n + 1)
+  # 2 = Blom (1954):           (r - 3/8) / (n + 1/4) (default)
+  # 3 = Bliss (1956; Rankit):  (r - 1/2) / n
+  # 4 = Tukey (1962):          (r - 1/3) / (n + 1/3)
+  #
+  # Ties will be treated as average, and the output will be rescaled
+  # to have mean = 0 and sd = 1, if you enter 1 for mean0.sd1 (default);
+  # if you want to keep the mean and sd of the original variable, enter 0.
+
+  normalize = function(data,normalize.formula=whichFormula,mean0.sd1=whichMeanSD) {
+    r = rank(data, na.last="keep", ties.method = ("average"))
+    n = sum(!is.na(r))
+
+    if (normalize.formula == 1)
+      x = r/(n+1)
+    if (normalize.formula == 2)
+      x = (r-3/8)/(n+1/4)
+    if (normalize.formula == 3)
+      x = (r-1/2)/n
+    if (normalize.formula == 4)
+      x = (r-1/3)/(n+1/3)
+
+    if (mean0.sd1 == 1)
+      normal = qnorm(x, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
+    else
+      normal = qnorm(x, mean = mean(data,na.rm = T), sd = sd(data,na.rm = T), lower.tail = TRUE, log.p = FALSE)
+  }
+
+  if (class(data)=="numeric") { 
+    normal=normalize(data,whichFormula,whichMeanSD)
+  } else {
+    normal=NULL
+    for (i in 1:dim(data)[2]) {
+      normal=cbind(normal,normalize(data[,i],whichFormula,whichMeanSD))
+    }
+    colnames(normal)=names(data)
+  }
+
+  return(normal)
+
+}
+
+  ## wrapper for shapiro.test() 
+sw <- function(x) {
+  x = data.frame(x)
+  d = dim(x)
+  n = names(x)
+  r = NULL
+  for (i in 1:dim(x)[2]) {
+    y = shapiro.test(x[,i])
+    v = cbind(y$statistic,y$p.value)
+    colnames(v) = c("W","p")
+    rownames(v) = n[i]
+    r = rbind(r,v)
+  }
+  return(round(r,3))
+}
+
+#------------------------------------------------------------------------------------
+
+#determine deviation from univariate normality using Shapiro Wilk test
+shapiro.summary = sw(data_nfc$nfc)
+
+#normalize and standardize sum scores by Blom's formula (1954)
+data_nfc$nnfc = data.frame(normalize.gen(data_nfc$nfc))
+colnames(data_nfc$nnfc) = "nfc.normal"
+
+#determine deviation from univariate normality using Shapiro Wilk test
+shapiro.summary = rbind(shapiro.summary, sw(data_nfc$nnfc))
+
+# end --------------------------------------------------------------------------
+
   # merge the NFC data frame into the AUC data frame by row
 
-  data_hyp3 <- merge(data_hyp3, data_nfc)
+  h3_data <- merge(h3_data, data_nfc)
 
@@
 
-  hypothesis3a <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv))
+  hypothesis3a.lm <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))
+
+  # FIXME: additionally, we could calculate the multiple correlation between both variables
+  hypothesis3a.mcorr <- sqrt(hypothesis3a.lm$r.squared)
+  # this correlation seems surprisingly high ...
 
@@
 
-  data_hyp3 <- merge(data_hyp3, ntlx)
+  h3_data <- merge(h3_data, ntlx)
 
@@
 
-  hypothesis3b <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv + data_hyp3$auc_ntlx))
+  hypothesis3b <- summary(lm(h3_data$nfc ~ h3_data$auc_sv + h3_data$auc_ntlx))
 
@@
 
-  hypothesis3c <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv + data_hyp3$auc_mental + data_hyp3$auc_effort))
+  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv + h3_data$auc_mental + h3_data$auc_effort))
 

### 2021-10-14 06_Paper/COG-ED/Manuscript.Rmd
rearranged packages

@@
 ```{r setup, include=FALSE}
+
   knitr::opts_chunk$set(echo = TRUE)
-# FIXME I propose to put the packages required here at the very beginning.
   library(bibtex)
+  library(here)         # to set a directory without defined paths, "here" package
+  library(tidyverse)    # plotting and managing data, "tidyverse" package
+  library(bayestestR)   # computing area under the curve, "bayestestR" package
+  library(papaja)       # APA conform output, "papaja" package
+  library(nlme)         # fitting nonlinear mixed-effects model
+  # we will add the package versions before submission
+
 ```

### 2021-10-14 06_Paper/COG-ED/Manuscript.Rmd
excluded post-error trials and reaction times below 200 ms

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}
-
-  library(here)         # to set a directory without defined paths, "here" package
-  library(tidyverse)    # plotting and managing data, "tidyverse" package
-  library(bayestestR)   # computing area under the curve, "bayestestR" package
-  library(papaja)       # APA conform output, "papaja" package
-  library(nlme)         # fitting nonlinear mixed-effects model
-# we could add the package versions here additionally
-
-```
-
 ```{r import, echo=FALSE, message=FALSE, warning=FALSE}
@@
   data_nback$response <- as.numeric(data_nback$response)
+
+  # exclude trials after incorrect responses
+
+  data_nback <- data_nback[-c(which(data_nback$correct == 1) + 1), ]
+
+  # exclude trials with reaction times below 200 ms
+
+  data_nback <- data_nback[-c(which(data_nback$rt < 0.2)), ]
 

### 2021-10-14 06_Paper/COG-ED/Manuscript.Rmd
implemented annotations in methods section and changed data frame of RT data

@@
   # the target column will contain 1 for targets and 0 for all non-targets
+
   data_nback[data_nback == "Target"] <- 1
@@
   data_nback$target <- as.numeric(data_nback$target)
+
   # the response column will contain 1 for responses and 0 for all non-responses
+
   data_nback[data_nback == "left"|data_nback == "right"] <- 1
@@
 
-  # exclude trials after incorrect responses
+  # create a new data frame for the data that is being used for reaction time analysis
+  # (we cannot exclude trials from the main data frame because the computation of d prime depends on hit-ratios, not reaction time)
 
-  data_nback <- data_nback[-c(which(data_nback$correct == 1) + 1), ]
+  # exclude trials after incorrect responses and with reaction times below 200 ms
 
-  # exclude trials with reaction times below 200 ms
-
-  data_nback <- data_nback[-c(which(data_nback$rt < 0.2)), ]
+  data_RT <- data_nback[-c(which(data_nback$correct == 1) + 1), ]
+  data_RT <- data_RT[-c(which(data_RT$rt < 0.2)), ]
 
@@
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
-# FIXME add version no. and packages
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.
@@
 ## Questionnaires
-To assess perceived task load, we used the NASA Task Load Index (NTLX) [@Hart1988], a 6-item questionnaire with the dimensions mental load, physical load, effort, frustration, performance, and time pressure.
-FIXME: NTLX seems not to be the commonly used abbreviation. We my refer to NASA TLX / NASA-TLX or just TLX. We may provide more information (see Strobel et al. 2020):
-In the NASA-TLX, participants evaluate their subjective perception of the mental, physical and temporal svs of a particular task, as well as their performance, effort and frustration during the task on a 20-point scale for each dimension.
-In its original, the NASA-TLX also requires comparisons of two dimensions each.
-For this study, we relinquished the comparison due to time restrictions.
-
+To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988].
+In the NASA-TLX, participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
 Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
-FIXME: We may need to add information on example items, rating scale and reliability (see diffpp):
-_Need for Cognition_ was assessed with the 16-item short version of the German NFC scale [@Bless1994].
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
 The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
-
 Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
@@
 The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm followed the same structure of task, ED procedure, and repetition of a random "level" as in session one.
-<!--CS: Achtung: das wurde verändert: Sie wiederhuolen nicht random ein Level sondern können sich nochmal frei entscheiden!
--->
+The paradigm followed the same structure of task and ED procedure, but the emotion regulation strategy at the end was not randomly chosen, instaed participants could decide which strategy they wanted to use again.
 There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
 Two days after the second session, participants received a link to the NFC scale and other personality questionnaires to provide a trait measure of preference for cognitive effort.
-Participants received 8€ per hour or course credit for participation, plus payment for the randomly chosen level.
+Participants received 30€ in total or course credit for participation.
 Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
@@
 ## Analysis
-We conducted all analysis as described in Westbrook et al. [-@Westbrook2013].
+We aimed to conduct all analysis as described in Westbrook et al.
+[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom in the statistical procedures.
 The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].

### 2021-10-14 06_Paper/COG-ED/Manuscript.Rmd
updated z transformation

@@
 The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
+Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Ashby1980; @Whelan2008; @Berger2021].
+Post-error trials were also excluded, because RT on those trials is longer due to more cautious behaviour [@Dutilh2012; @Houtman2012].
 Declining performance was investigated by calculating an analysis of variance (ANOVA) with three linear contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
-Another ANOVA with three linear contrasts was computed to compare the mean reaction time (RT) between two levels of 2-, 3-, and 4-back at a time.
+Another ANOVA with three linear contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
 To investigate changes in NTLX ratings, six ANOVAs were computed, one for each NTLX subscale, and each with six linear contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
@@
 Each ANOVA in the analysis was followed up by a Tukey's test.
-# would it be possible to compare the originally calculated SV with our new one?
 To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
@@
   # apply the addition or subtraction of 0.015625 to the last choices
-# FIXME why do we have to do this?
 
@@
   # z-transform the hit rate and the false alarm rate
-  # FIXME: What makes this transformation necessary? Why per n-back level separately? Is this the standard procedure?
-  # FIXME: for z-transformation we could use function scale:
 
-  # # create new variables
-  # dprime$falsealarmrate.z = dprime$hitrate.z =NA
-  # for (i in 1:4) {
-  #    dprime$hitrate.z[which(dprime$level == i)]        <- scale(dprime$hitrate[which(dprime$level == i)])
-  #    dprime$falsealarmrate.z[which(dprime$level == i)] <- scale(dprime$falsealarmrate[which(dprime$level == i)])
-  # }
+  dprime$falsealarmrate.z = NA
+  dprime$hitrate.z = NA
 
@@
 
-    # calculate the mean and sd of hit rate and false alarm rate per n-back level i
+    dprime$hitrate.z[which(dprime$level == i)]        <- scale(dprime$hitrate[which(dprime$level == i)])
+    dprime$falsealarmrate.z[which(dprime$level == i)] <- scale(dprime$falsealarmrate[which(dprime$level == i)])
 
-    mean_hitrate <- mean(dprime$hitrate[dprime$level == i])
-    sd_hitrate <- sd(dprime$hitrate[dprime$level == i])
-    mean_falsealarmrate <- mean(dprime$falsealarmrate[dprime$level == i])
-    sd_falsealarmrate <- sd(dprime$falsealarmrate[dprime$level == i])
-
-    for (j in 1:length(which(dprime$level == i))) {
-
-      # z-transform each subject j's hit rate and false alarm rate within the level i
-
-      dprime$hitrate[which(dprime$level == i)[j]] <- (dprime$hitrate[which(dprime$level == i)[j]] - mean_hitrate)/sd_hitrate
-      dprime$falsealarmrate[which(dprime$level == i)[j]] <- (dprime$falsealarmrate[which(dprime$level == i)[j]] -
-                                                               mean_falsealarmrate)/sd_falsealarmrate
   }
-  }
-
-  # remove temporary variables
-
-  remove(mean_hitrate, sd_hitrate, mean_falsealarmrate, sd_falsealarmrate)
 

### 2021-10-15 06_Paper/ER-ED/method.Rmd
updated electromyography

@@
 Bipolar electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
-Passive surface Ag/AgCl electrodes (XX mm diameter, XX distance between electrodes) filled with electrolyte gel were used.
+Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel were used. <!-- Stimmt das in etwa, liebe Anne? -->
 [...] <!-- Anne tried to implement a sentence here. -->

### 2021-10-15 06_Paper/ER-ED/intro.Rmd
added comment
added comments

@@
 [...]
-<!-- SVs wären gut um um besser sachen ausrechnen zu können-->
+Associations between subjectively reported habitual use of emotion regulation strategies <!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->  
+ER flexibility has been described as an approach to 
+[...]
+<!-- Überleitung zu SVs-->
 Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
@@
 Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs. 
+<!-- to specific ? to unspecific? -->

### 2021-10-15 06_Paper/ER-ED/intro.Rmd
added text

--- 2021-10-08 06_Paper/ER-ED/intro.Rmd
@@
 [...]
-<!-- SVs wären gut um um besser sachen ausrechnen zu können-->
+<!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->
+Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
+Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
+This postulation was challenged with the concept of ER flexibility [@Aldao2015].
+<!-- flexibility: etwas andere Sichtweise -->
+ER flexibility has been described as an approach to 
+[...]
+<!-- Überleitung zu SVs-->
 Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

### 2021-10-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
   library(nlme)         # fitting nonlinear mixed-effects model
+  library(ez)           # compute repeated measures ANOVA
   # we will add the package versions before submission
@@
 
+  dprime$hitrate.z = NA
   dprime$falsealarmrate.z = NA
-  dprime$hitrate.z = NA
 
@@
 
-  dprime$d <- dprime$hitrate - dprime$falsealarmrate
+  dprime$d <- dprime$hitrate.z - dprime$falsealarmrate.z
 
@@
 
-      h1a_data <- dprime[dprime$level != 1,]      # FIXME: Westbrook et al. exclude level 1, do you understand why?
+      h1a_data <- dprime[dprime$level != 1, ]
       h1a_data$level <- as.factor(h1a_data$level)
@@
   # FIXME:  rmANOVA
-      library(ez) # compute repeated measurement ANOVA
       h1a_data$subject <- factor(h1a_data$subject)

### 2021-10-15 06_Paper/ER-ED/intro.Rmd
added paragraph for ER flexibility

@@
 Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
-This postulation was challenged with the concept of ER flexibility [@Aldao2015].
-<!-- flexibility: etwas andere Sichtweise -->
-ER flexibility has been described as an approach to 
+This postulation was questioned with the concept of ER flexibility [@Aldao2015].
+*Maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals.
+<!-- Kommentare zu  ER Choice -->
 [...]

### 2021-10-15 06_Paper/ER-ED/intro.Rmd
added paragraph on ER flexiblity

@@
 Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
-This postulation was questioned with the concept of ER flexibility [@Aldao2015].
-*Maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals.
+This postulation was questioned with the concept of ER flexibility.
+*Maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
+There was now a greater focus on how ER strategies are being chosen.
+For example it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011].  
 <!-- Kommentare zu  ER Choice -->

### 2021-10-18 06_Paper/COG-ED/Manuscript.Rmd
implemented rmANOVA with linear contrasts

@@
   library(ez)           # compute repeated measures ANOVA
+  library(emmeans)      # for custom contrasts in ANOVAs
+
   # we will add the package versions before submission
@@
 
-  # ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
-  # FIXME:  actually, I guess, we have a rmANOVA here as we look at repeated measures of a subject's reaction time 
-  #         under different load levels (= time points), see below
+  # repeated measures ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
 
@@
 
-      # define contrasts
-
-      contrasts(h1a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))     # there are predefined contrasts that may fit like contr.sum(3); contr.treatment(); contr.poly()
-
       # calculate ANOVA
 
-      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))         # this calculates ANOVA without the specified contrasts and might be redundant
-      hypothesis1a_anova.lm <- summary.lm(aov(h1a_data$d ~ h1a_data$level))   # this gives you the contrasted result
-      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))      # post hoc analyses should be redundant as we already contrasted the levels
+      hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
+                                           dv = "d",
+                                           id = "subject",
+                                           within = "level",
+                                           type = 3,
+                                           include_aov = TRUE)
 
-  # FIXME:  rmANOVA
-      h1a_data$subject <- factor(h1a_data$subject)
-      # if there are reasonable concerns that we have NAs within our data set, we need to exclude this data beforehand
+      # specify contrasts
 
-      # https://stackoverflow.com/questions/35891062/planned-contrasts-using-ezanova-output-in-r
-      # set orthogonal contrasts
-      options(contrasts = c("contr.sum", "contr.poly"))
-      hypothesis1a_rmanova <- ezANOVA(h1a_data, dv = d, wid = subject, within = level, type = 3, return_aov = T) 
-      # I propose to use type-III sums of squares even if we do have a balanced design, but we may discuss that. 
-      # alternatively we could use afex, results might be plotted easier; it is also possible to set up a linear model
-      # TODO: find a way to plot means
-        # if Mauchly's Test for Sphericity is sign > report Greenhouse-Geisser Epsilon (GGe) or Huynh-Feldt-Epsilon (HFe)
+      hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
+                                  specs = "level")
+      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)
 
-      # get emmeans
-      library(emmeans)
-      # this only works without the manually defined contrasts in line 439
-      hypothesis1a_emm <- emmeans(hypothesis1a_rmanova$aov, ~ level) 
-      # these means should be used for reporting/ plotting the means per load level
-
-      # get the contrasts
-      pairs(hypothesis1a_emm, adjust = "Holm")
-      # or
-      contrast(hypothesis1a_emm, list(c1 = c(1,-1,0), c2 = c(1,0,-1), c3 = c(0,1,-1)))
-
-      # alternatively, post hoc tests can be run
-      # as we have 3 levels in factor load level, we would run a fisher's least significant differences (FLSD)
-      hypothesis1a_fisher <- ezStats(h1a_data, dv = d, wid = subject, within = level, type = 3)
-      # calculate and save mean differences
-      p1.p2 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[2]
-      p1.p3 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[3]
-      p2.p3 <- hypothesis1a_fisher$Mean[2] - hypothesis1a_fisher$Mean[3]
-
-      #if absolute value is higher than fsld, the pairwise comparison is significant
-      abs(p1.p2) > hypothesis1a_fisher$FLSD[1]
-      abs(p1.p3) > hypothesis1a_fisher$FLSD[1]   
-      abs(p2.p3) > hypothesis1a_fisher$FLSD[1]
+      # remove the temporary variable
 

### 2021-10-19 06_Paper/COG-ED/Manuscript.Rmd
implemented rmANOVA for more hypotheses

@@
   library(nlme)         # fitting nonlinear mixed-effects model
-  library(ez)           # compute repeated measures ANOVA
-  library(emmeans)      # for custom contrasts in ANOVAs
+  library(afex)         # compute repeated measures ANOVA, "afex" package
+  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
 
@@
 
-# FIXME what about RT preprocessing?
-  # correct / postcorrect     *see Westbrook et al. 2013, table 1: correct trials
-  # log-transformation
-  # valid answers: false alarm vs. missing -> plausible responses
-
   # ANOVA with three linear contrasts, contrasting the mean rt of two n-back levels (2,3,4) at a time
@@
 
-      # define contrasts
-
-      contrasts(h1b_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))
-
       # calculate ANOVA
 
-      hypothesis1b_anova <- summary(aov(h1b_data$meanrt ~ h1b_data$level))
-      hypothesis1b_posthoc <- TukeyHSD(aov(h1b_data$meanrt ~ h1b_data$level))
+      hypothesis1b_rmanova <- afex::aov_ez(data = h1b_data,
+                                           dv = "meanrt",
+                                           id = "subject",
+                                           within = "level",
+                                           type = 3,
+                                           include_aov = TRUE)
+
+      # specify contrasts
+
+      hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
+                                  specs = "level")
+      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)
+
+      # remove the temporary variable
+
       remove(h1b_data)
@@
 
-      # define contrasts
-
-      contrasts(h1c_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
-                                         c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))
-
       # calculate ANOVAs
 
-      hypothesis1c1_anova <- summary(aov(h1c_data$mental ~ h1c_data$level))
-      hypothesis1c1_posthoc <- TukeyHSD(aov(h1c_data$mental ~ h1c_data$level))
+      hypothesis1c_mental_rmanova <- afex::aov_ez(data = h1c_data,
+                                                  dv = "mental", id = "subject", within = "level",
+                                                  type = 3, include_aov = TRUE)
+      hypothesis1c_physical_rmanova <- afex::aov_ez(data = h1c_data,
+                                                  dv = "physical", id = "subject", within = "level",
+                                                  type = 3, include_aov = TRUE)
+      hypothesis1c_time_rmanova <- afex::aov_ez(data = h1c_data,
+                                                  dv = "time", id = "subject", within = "level",
+                                                  type = 3, include_aov = TRUE)
+      hypothesis1c_performance_rmanova <- afex::aov_ez(data = h1c_data,
+                                                  dv = "performance", id = "subject", within = "level",
+                                                  type = 3, include_aov = TRUE)
+      hypothesis1c_effort_rmanova <- afex::aov_ez(data = h1c_data,
+                                                  dv = "effort", id = "subject", within = "level",
+                                                  type = 3, include_aov = TRUE)
+      hypothesis1c_frustration_rmanova <- afex::aov_ez(data = h1c_data,
+                                                  dv = "frustration", id = "subject", within = "level",
+                                                  type = 3, include_aov = TRUE)
 
-      hypothesis1c2_anova <- summary(aov(h1c_data$physical ~ h1c_data$level))
-      hypothesis1c2_posthoc <- TukeyHSD(aov(h1c_data$physical ~ h1c_data$level))
+      # specify contrasts
 
-      hypothesis1c3_anova <- summary(aov(h1c_data$time ~ h1c_data$level))
-      hypothesis1c3_posthoc <- TukeyHSD(aov(h1c_data$time ~ h1c_data$level))
+      hypothesis1c_emm <- emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
+      hypothesis1c_mental_contrasts <- pairs(hypothesis1c_emm)
 
-      hypothesis1c4_anova <- summary(aov(h1c_data$performance ~ h1c_data$level))
-      hypothesis1c4_posthoc <- TukeyHSD(aov(h1c_data$performance ~ h1c_data$level))
+      hypothesis1c_emm <- emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
+      hypothesis1c_physical_contrasts <- pairs(hypothesis1c_emm)
 
-      hypothesis1c5_anova <- summary(aov(h1c_data$effort ~ h1c_data$level))
-      hypothesis1c5_posthoc <- TukeyHSD(aov(h1c_data$effort ~ h1c_data$level))
+      hypothesis1c_emm <- emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
+      hypothesis1c_time_contrasts <- pairs(hypothesis1c_emm)
 
-      hypothesis1c6_anova <- summary(aov(h1c_data$frustration ~ h1c_data$level))
-      hypothesis1c6_posthoc <- TukeyHSD(aov(h1c_data$frustration ~ h1c_data$level))
+      hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
+      hypothesis1c_peformance_contrasts <- pairs(hypothesis1c_emm)
 
-      # TODO: see H1a. 
-      num_vars <- c("mental", "physical", "time", "performance", "effort", "frustration")
-      h1c_data[num_vars] <- lapply(h1c_data[num_vars], as.numeric)
-      hypothesis1c_rmanova <- ezANOVA(h1c_data, dv = mental, wid = subject, within = level, 
-                                       type = 3, return_aov = T)
-      #...
+      hypothesis1c_emm <- emmeans(object = hypothesis1c_effort_rmanova$aov, specs = "level")
+      hypothesis1c_effort_contrasts <- pairs(hypothesis1c_emm)
 
-      # We may also run a rmMANOVA
-      # https://cran.r-project.org/web/packages/MANOVA.RM/vignettes/Introduction_to_MANOVA.RM.html
-      library(MANOVA.RM)
-      # we need to convert our data frame to clean wide or long format
+      hypothesis1c_emm <- emmeans(object = hypothesis1c_frustration_rmanova$aov, specs = "level")
+      hypothesis1c_frustration_contrasts <- pairs(hypothesis1c_emm)
 
-      remove(h1c_data)
+      # remove the temporary variable
+
+      remove(h1c_data, hypothesis1c_emm)
 
@@
 
-  # define contrasts
+  # calculate ANOVA
 
-  contrasts(h2a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
-                                     c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))
+  hypothesis2a_rmanova <- afex::aov_ez(data = h2a_data,
+                                       dv = "sv", id = "subject", within = "level",
+                                       type = 3, include_aov = TRUE)
 
-  # calculate ANOVAs
+  # specify contrasts
 
-  hypothesis2a_anova <- summary(aov(h2a_data$sv ~ h2a_data$level))
-  hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$sv ~ h2a_data$level))
+  hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
+                              specs = "level")
+  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)
+
+  # remove the temporary variable
 
@@
 
-  # create an index for the rows in which the participants change
+  # create an index for the rows in which the participant ID changes
 

### 2021-10-19 06_Paper/COG-ED/Manuscript.Rmd
wrote more results

@@
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.
+The R Markdown file used to analyze the data and write this document is freely available at github.com/ChScheffel/CERED.
+The data can be downloaded from osf.io/vnj8x/.
 
 ## Questionnaires
-To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988].
+To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988].
 In the NASA-TLX, participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
-Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
+Need for Cognition will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
 The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
-Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
+Several other personality questionnaires will be used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
 A full list of questionnaires and measures can be found in Appendix 1.
@@
 The final sample consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
-Each participant completed two sessions in the lab one week apart, and a battery of personality questionnaires at least two days after the second session.
+Each participant completed two sessions in the lab one week apart, and a battery of personality questionnaires two days after the second session.
 In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
 The paradigm started with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels were referred to by colour (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
-After each level, participants filled out the NTLX on a tablet to provide a state measure of cognitive effort.
+The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
+After each level, participants filled out the NASA-TLX on a tablet to provide a state measure of cognitive effort.
 Then, they completed the ED procedure on screen, where each possible pairing of the four n-back levels was presented in a randomized order.
 Participants were instructed to decide as realistically as possible, because one of their choices from the last iteration steps would be randomly chosen for one final run of n-back.
-The level and its monetary value were presented on screen and participants completed one run, but this was only to incentivise truthful behaviour in the ED procedure, so the n-back data of this part was not analyzed.
+The level and its monetary value were presented on screen and participants completed one run, but this was only to incentivise truthful behavior in the ED procedure, so the n-back data of this part was not analyzed.
 The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm followed the same structure of task and ED procedure, but the emotion regulation strategy at the end was not randomly chosen, instaed participants could decide which strategy they wanted to use again.
+The paradigm followed the same structure of task and ED procedure, but the emotion regulation strategy at the end was not randomly chosen, instead participants could decide which strategy they wanted to use again.
 There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
@@
 Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Ashby1980; @Whelan2008; @Berger2021].
-Post-error trials were also excluded, because RT on those trials is longer due to more cautious behaviour [@Dutilh2012; @Houtman2012].
-Declining performance was investigated by calculating an analysis of variance (ANOVA) with three linear contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
-Another ANOVA with three linear contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
-To investigate changes in NTLX ratings, six ANOVAs were computed, one for each NTLX subscale, and each with six linear contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
+Post-error trials were also excluded, because RT on those trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
+To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
 The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
 Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
-An ANOVA with six linear contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
-Each ANOVA in the analysis was followed up by a Tukey's test.
+A rmANOVA with six paired contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
+Tukey method was used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
 To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
 **MLM explanation goes here**
-The association of ED and NFC was done using three separate regressions.
+The association of ED and NFC was examined using three separate regressions.
 One regression used the AUC of each participant's SVs to predict their NFC score.
-The second regression additionally included the mean of the NTLX subscales' AUCs of each participant as a predictor.
-And the last regression used the AUC of each participant's SV, the AUC of the NTLX mental load subscale, and the AUC of the NTLX effort subscale to predict each participant's NFC score.
+The second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
+And the last regression used the AUC of each participant's SV, the AUC of the NASA-TLX mental load subscale, and the AUC of the NASA-TLX effort subscale to predict each participant's NFC score.
 
@@
 
-# Results
+## Results of the pilot study
 
-## Associations of subjective and objective task load measures
-We first looked at how performance measures and NTLX ratings change as n-back levels increase.
-Linear contrasts ANOVAs revealed decreasing performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_anova)$full_result`).
-Tukey's test confirmed that *d'* was smaller for *...(and put in row 1/2/3 ->)* (`r hypothesis1a_posthoc[["h1a_data$level"]][1,4]`).
+### Associations of subjective and objective task load measures
+We first looked at how performance measures and NASA-TLX ratings change as n-back levels increase.
+The rmANOVA revealed decreasing performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).
+Paired contrasts showed that *d'* was smaller for *...(and put in element 1/2/3 ->)* (`r apa_print(hypothesis1a_contrasts)$statistic[1]`).
 
@@
 
-Likewise, linear contrasts ANOVAs confirmed increases in RT with increasing n-back level (`r apa_print(hypothesis1b_anova)$full_result`).
-Tukey's test showed that this was the case for *...(and put in row 1/2/3 ->)* (`r hypothesis1b_posthoc[["h1b_data$level"]][1,4]`).
+Likewise, RT increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
+Here, RTs were longer for *...(and put in element 1/2/3 ->)* (`r apa_print(hypothesis1b_contrasts)$statistic[1]`).
 Overall, the decreases in *d'* and increases in RT indicate the increase in objective task load with higher n-back levels.
@@
 
-  # H1c: Ratings on all NTLX dimensions increase with increasing n-back level.
+  # H1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
 
@@
 
-  # feed NTLX data per participant per level into data frame
+  # feed NASA-TLX data per participant per level into data frame
 
@@
 
-      # make a temporary copy of the NTLX data frame
+      # make a temporary copy of the NASA-TLX data frame
 
@@
 
-Increases in subjective task load were investigated with linear contrast ANOVAs for each NTLX subscale, now including 1-back.
-Perceived mental load increased with n-back (`r apa_print(hypothesis1c1_anova)$full_result`), especially from *...(and put in row 1/2/3/4/5/6 ->)* (`r hypothesis1c1_posthoc[["h1c_data$level"]][1,4]`).
-Physical load increased as well, but not as strongly (`r apa_print(hypothesis1c2_anova)$full_result`), mainly from *...(and put in row 1/2/3/4/5/6 ->)* (`r hypothesis1c2_posthoc[["h1c_data$level"]][1,4]`).
+Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
+All subscales showed increases from 1-back to 4-back (mental: `r apa_print(hypothesis1c_mental_contrasts)$statistic$X1_X4`, physical: `r apa_print(hypothesis1c_pysical_contrasts)$statistic$X1_X4`, time: `r apa_print(hypothesis1c_time_contrasts)$statistic$X1_X4`, performance: `r apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, effort: `r apa_print(hypothesis1c_effort_contrasts)$statistic$X1_X4`, frustration: `r apa_print(hypothesis1c_frustration_contrasts)$statistic$X1_X4`).
 
@@
 ```
+
+### Changes in subjective values depending on n-back level
+While the rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`), paired contrasts indicated that this was not the case for every pair of n-back levels.
+SVs were higher for *n*-back than for *n*-back *insert row!!* (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`) and for *n*-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`).
+The SVs of all other n-back level pairs were not significantly different.
 
@@
 
-# further preprocessing of nfc-data ---------------------------------------------
-  # FIXME: actually we would now
-  # 1. determine deviation from univariate normality using Shapiro Wilk test
-  # 2. normalize and standardize sum scores by Blom's formula (1954)
-  # 3. again determine deviation from univariate normality of data from second step using Shapiro Wilk test
-  # this would mean:
-
-  # required scripts (might be best at the beginning, following the packages) --
-
-  ## for normalizing variables
-normalize.gen <- function(data, whichFormula=2, whichMeanSD=1) {
-  # normalizes DATA using one of the formulae:
-  #
-  # 1 = Van der Waerden (1952): r * / (n + 1)
-  # 2 = Blom (1954):           (r - 3/8) / (n + 1/4) (default)
-  # 3 = Bliss (1956; Rankit):  (r - 1/2) / n
-  # 4 = Tukey (1962):          (r - 1/3) / (n + 1/3)
-  #
-  # Ties will be treated as average, and the output will be rescaled
-  # to have mean = 0 and sd = 1, if you enter 1 for mean0.sd1 (default);
-  # if you want to keep the mean and sd of the original variable, enter 0.
-
-  normalize = function(data,normalize.formula=whichFormula,mean0.sd1=whichMeanSD) {
-    r = rank(data, na.last="keep", ties.method = ("average"))
-    n = sum(!is.na(r))
-
-    if (normalize.formula == 1)
-      x = r/(n+1)
-    if (normalize.formula == 2)
-      x = (r-3/8)/(n+1/4)
-    if (normalize.formula == 3)
-      x = (r-1/2)/n
-    if (normalize.formula == 4)
-      x = (r-1/3)/(n+1/3)
-
-    if (mean0.sd1 == 1)
-      normal = qnorm(x, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
-    else
-      normal = qnorm(x, mean = mean(data,na.rm = T), sd = sd(data,na.rm = T), lower.tail = TRUE, log.p = FALSE)
-  }
-
-  if (class(data)=="numeric") { 
-    normal=normalize(data,whichFormula,whichMeanSD)
-  } else {
-    normal=NULL
-    for (i in 1:dim(data)[2]) {
-      normal=cbind(normal,normalize(data[,i],whichFormula,whichMeanSD))
-    }
-    colnames(normal)=names(data)
-  }
-
-  return(normal)
-
-}
-
-  ## wrapper for shapiro.test() 
-sw <- function(x) {
-  x = data.frame(x)
-  d = dim(x)
-  n = names(x)
-  r = NULL
-  for (i in 1:dim(x)[2]) {
-    y = shapiro.test(x[,i])
-    v = cbind(y$statistic,y$p.value)
-    colnames(v) = c("W","p")
-    rownames(v) = n[i]
-    r = rbind(r,v)
-  }
-  return(round(r,3))
-}
-
-#------------------------------------------------------------------------------------
-
-#determine deviation from univariate normality using Shapiro Wilk test
-shapiro.summary = sw(data_nfc$nfc)
-
-#normalize and standardize sum scores by Blom's formula (1954)
-data_nfc$nnfc = data.frame(normalize.gen(data_nfc$nfc))
-colnames(data_nfc$nnfc) = "nfc.normal"
-
-#determine deviation from univariate normality using Shapiro Wilk test
-shapiro.summary = rbind(shapiro.summary, sw(data_nfc$nnfc))
-
-# end --------------------------------------------------------------------------
-
   # merge the NFC data frame into the AUC data frame by row
@@
 
-  hypothesis3a.lm <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))
-
-  # FIXME: additionally, we could calculate the multiple correlation between both variables
-  hypothesis3a.mcorr <- sqrt(hypothesis3a.lm$r.squared)
-  # this correlation seems surprisingly high ...
+  hypothesis3a <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))
 
@@
 
+The AUC of SVs predicted a significant amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
+An increase in one AUC value corresponded, on average, to an increase of `r round(hypothesis3a$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3a)$estimate$h3_data_auc_sv`).
+
 ```{r Hypothesis_3b, echo=FALSE, message=FALSE, warning=FALSE}
 
-  # H3b: NTLX scores do not predict individual NCS scores.
+  # H3b: NASA-TLX scores do not predict individual NCS scores.
 
-  # create an index for the rows in which the participants change
+  # create an index for the rows in which the participant ID changes
 
@@
 
-  # calculate AUCs per NTLX subscale per participant
+  # calculate AUCs per NASA-TLX subscale per participant
 
@@
 
-  # add column containing the average of the NTLX subscale AUCs
+  # add column containing the average of the NASA-TLX subscale AUCs
 
@@
 
-  # compute multiple linear regression to predict NCS based on SV AUC and NTLX AUC
+  # compute multiple linear regression to predict NCS based on SV AUC and NASA-TLX AUC
 
@@
 
+When including the AUC of all NASA-TLX subscales as a predictor, it could not explain any variance in NFC beyond the one explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
+
 ```{r Hypothesis_3c, echo=FALSE, message=FALSE, warning=FALSE}
 
-  # H3c: The NTLX dimensions effort and mental load predict individual NCS scores.
+  # H3c: The NASA-TLX dimensions effort and mental load predict individual NCS scores.
 
@@
 ```
+
+However, when only taking the AUC of the mental and the AUC of the effort subscale of the NASA-TLX into account, it explained variance in NFC scores beyond SVs (`r apa_print(hypothesis3c)$statistic$modelfit$r2`, `r apa_print(hypothesis3c)$estimate$modelfit$r2`).

### 2021-10-19 06_Paper/COG-ED/Manuscript.Rmd
started the new AUC calculation
Not finished

@@
 And regarding individual differences in ED we hypothesized that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-However, since NFC is conceptually related to cognitive but not physical effort, we added the hypothesis that (3c) perceived mental load and perceived effort predict individual NFC scores.
+However, we propose that (3c) when taking individual preferences for different n-back levels into account, the prediction of NFC scores by SVs can be improved significantly.
 
@@
 The second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
-And the last regression used the AUC of each participant's SV, the AUC of the NASA-TLX mental load subscale, and the AUC of the NASA-TLX effort subscale to predict each participant's NFC score.
+And the last regression **insert method**.
 
@@
 
-  # H3c: The NASA-TLX dimensions effort and mental load predict individual NCS scores.
+  # H3c: When putting the SVs in descending order before computing the AUC, the prediction of NFC scores by SVs can be improved significantly.
 
-  # compute multiple linear regression to predict NCS based on SV AUC, Effort AUC and Mental Load AUC
+  # prepare empty data frame for the loop to feed into
 
-  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv + h3_data$auc_mental + h3_data$auc_effort))
+  h3c_data <- data.frame(subject = character(), auc_sv = double())
+
+  # calculate AUC of SVs per subject
+
+  for (i in 1:(length(subjectindex)-1)) {
+
+    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
+                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
+                                   method = "trapezoid", sort = TRUE))
+    h3c_data <- rbind(h3c_data, newdata)
+
+  }
+
+  # merge the NFC data frame into the AUC data frame by row
+
+  h3_data <- merge(h3_data, data_nfc)
+
+  # compute linear regression to predict NCS based on SV AUC
+
+  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))
 

### 2021-10-20 06_Paper/COG-ED/Manuscript.Rmd
tried to fix AUC sorted
Function ignores argument

@@
 
-  h3c_data <- data.frame(subject = character(), auc_sv = double())
+  h3c_data <- data.frame(subject = character(), auc_sv_sorted = double())
 
@@
     newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
-                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
+                          auc_sv_sorted = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                    method = "trapezoid", sort = TRUE))
@@
 
-  h3_data <- merge(h3_data, data_nfc)
+  h3_data <- merge(h3_data, h3c_data)
+
+  # remove temporary variable
+
+  remove(h3c_data)
 
@@
 
-  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))
+  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv_sorted))
 
 ```
-
-However, when only taking the AUC of the mental and the AUC of the effort subscale of the NASA-TLX into account, it explained variance in NFC scores beyond SVs (`r apa_print(hypothesis3c)$statistic$modelfit$r2`, `r apa_print(hypothesis3c)$estimate$modelfit$r2`).

### 2021-10-21 06_Paper/COG-ED/Manuscript.Rmd
tried fixing AUC

@@
 
+**something is wrong with the AUC calculation**
+
+```{r AUC_demo, echo=FALSE, message=FALSE, warning=FALSE}
+
+require(gtools)
+demo_data = data.frame(level = rep(1:4,24))
+sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
+m = 1
+for (n in 1:nrow(demo_data)) {
+  demo_data$subject[m:(m+3)] = rep(n,4)
+  demo_data$sv[m:(m+3)] = sv[n,]
+  m = m + 4
+}
+subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
+demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
+for (i in 1:(length(subjectindex)-1)) {
+  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
+                          auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i+1]-1)], demo_data$sv[subjectindex[i]:(subjectindex[i+1]-1)],
+                                   method = "trapezoid", sort = FALSE),
+                          auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
+                                               0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
+                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])))
+  demo_sv <- rbind(demo_sv, newdata)
+}
+```
+
 ```{r Hypothesis_3a, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-  h3_data <- data.frame(subject = character(), auc_sv = double())
+  h3_data <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
 
@@
                           auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
-                                   method = "trapezoid", sort = FALSE))
+                                   method = "trapezoid", sort = FALSE),
+                          auc_sv_unsorted = (0.5 * (data_SV$sv[subjectindex[i]] + data_SV$sv[subjectindex[i]+1]) +
+                                               0.5 * (data_SV$sv[subjectindex[i]+1] + data_SV$sv[subjectindex[i]+2]) +
+                                               0.5 * (data_SV$sv[subjectindex[i]+2] + data_SV$sv[subjectindex[i]+3])))
     h3_data <- rbind(h3_data, newdata)

### 2021-10-21 06_Paper/COG-ED/Manuscript.Rmd
created demo data for AUC

@@
 m = 1
-for (n in 1:nrow(demo_data)) {
+for (n in 1:(nrow(demo_data)/4)) {
   demo_data$subject[m:(m+3)] = rep(n,4)
@@
 for (i in 1:(length(subjectindex)-1)) {
+  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
   newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
-                          auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i+1]-1)], demo_data$sv[subjectindex[i]:(subjectindex[i+1]-1)],
-                                   method = "trapezoid", sort = FALSE),
+                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
+                                   method = "trapezoid"),
                         auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
                                                0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
-                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])))
+                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])),
+                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
+                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
+                                           0.5 * (sv_sorted[3] + sv_sorted[4])))
   demo_sv <- rbind(demo_sv, newdata)
 }
+ggplot(demo_data, aes(x=level, y=sv, group=subject)) +
+  geom_line(aes(color=subject), size = 1)
+
+ggplot(demo_data[c((1*4+1):(1*4+4),(4*4+1):(4*4+4),(15*4+1):(15*4+4),(17*4+1):(17*4+4)),], aes(x=level, y=sv, group=subject)) +
+  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
+ggplot(demo_data[c((3*4+1):(3*4+4),(5*4+1):(5*4+4),(9*4+1):(9*4+4),(11*4+1):(11*4+4)),], aes(x=level, y=sv, group=subject)) +
+  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
+ggplot(demo_data[c((0*4+1):(0*4+4),(2*4+1):(2*4+4),(21*4+1):(21*4+4),(23*4+1):(23*4+4)),], aes(x=level, y=sv, group=subject)) +
+  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0, h = 0.03))
 ```

### 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
contrasts
set orthogonal contrasts;
comment on emmeans

@@
   library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
+
+  set_sum_contrasts()   # sets orthogonal contrasts for mixed-effects model 
+                        # and rmANOVA globally in order to get meaningful Type-III tests
 
@@
       # calculate ANOVA
-
       hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
@@
 
-      # specify contrasts
-
+      # obtain estimated marginal means for ANOVA model
       hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
                                   specs = "level")
+      # calculate pairwise comparisons on estimated marginal means
       hypothesis1a_contrasts <- pairs(hypothesis1a_emm)
@@
 
-      # specify contrasts
-
+      # obtain estimated marginal means for ANOVA model
       hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
                                   specs = "level")
+      # calculate pairwise comparisons on estimated marginal means
       hypothesis1b_contrasts <- pairs(hypothesis1b_emm)
@@
 
-      # specify contrasts
+      # obtain estimated marginal means for ANOVA model and
+      # calculate pairwise comparisons on estimated marginal means
 
@@
 
-  # specify contrasts
-
+  # obtain estimated marginal means for ANOVA model
   hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
                               specs = "level")
+  # calculate pairwise comparisons on estimated marginal means
   hypothesis2a_contrasts <- pairs(hypothesis2a_emm)

### 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
fit mlm model with lmerTest

@@
   library(papaja)       # APA conform output, "papaja" package
-  library(nlme)         # fitting nonlinear mixed-effects model
+  library(lmerTest)     # for multilevel modeling
+  library(snow)         # for faster processing
   library(afex)         # compute repeated measures ANOVA, "afex" package
@@
 Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Ashby1980; @Whelan2008; @Berger2021].
-Post-error trials were also excluded, because RT on those trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+Error- and post-error trials were excluded, because RT on the latter trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+#TODO: Tolle Artikel, die schaue ich mir auch noch mal genauer an! Hast du die beiden exclusions schon im script umgesetzt? Falls ja, in welcher Zeile, ich kann es nicht finden...
 Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
@@
 
-  # define variables -------------------------------------------------------------
-  # dependent variable:     SV                    numeric                 data_SV
-  # indepenendent variable: n-back level [1-4]    numeric                       
-  # controlled regressors:  d'                    numeric                 dprime
-  #                         mRT                   numeric                 rt
+  # detach afex in order to user lmerTest
+  detach("package:afex", unload = TRUE)
 
-  # get all relevant variables ---------------------------------------------------
+  # get all relevant variables -------------------------------------------------
 
@@
 
-  # check and specify correct data types -----------------------------------------
-  str(h2b_data)
+  # center predictors ----------------------------------------------------------
 
-  # center predictors ------------------------------------------------------------
-  # center level 1 predictors
+  ## center level 1 predictors
   # two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
@@
 
-  # no level 2 predictors
+  ## no level 2 predictors
 
-  # change global coding to orthogonal sum-to-zero contrast by -------------------
-  options(contrasts = c("contr.sum", "contr.poly"))
+  # null model -----------------------------------------------------------------
+  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
+                 data = h2b_data)
 
-  # null model -------------------------------------------------------------------
-  # m0_h2b <- nlme(model = sv ~ 1,
-  #                data = h2b_data,
-  #                random = ~ 1 | subject, 
-  #                method = "REML")
+  # intraclass correlation (ICC)
+  # % of variance can be explained by differences between persons
+  var_m0_h2b <- as.data.frame(VarCorr(m0_h2b))
+  icc_h2b <- var_m0_h2b$vcov[1] / (var_m0_h2b$vcov[1] + var_m0_h2b$vcov[2])
 
-  # full model -------------------------------------------------------------------
-  # random intercept vs. random slope ???
-  # "subject-specific intercepts" speaks for random-slopes-model, as within this model 
-  # the slope is allowed to vary between subjects
+  # random slopes model --------------------------------------------------------
 
-  # m1_h2b <- nlme(sv ~ d.cwc + meanrt.cwc + level.cwc + (level.cwc| subject),
-  #                data = h2b_data,
-  #                fixed = ...,
-  #                random = ...,
-  #                control = ...,
-  #                method = "REML")
+  ## maximal model ----
 
-  # initVals <- getInitial(sv ~ d.cwc + meanrt.cwc + level.cwc, data = h2b_data)
+  m1_h2b <- lmer(sv ~ level.cwc + d.cwc + meanrt.cwc + (level.cwc|subject), 
+                 data = h2b_data,
+                 REML = T) # parameters estimated by maximizing restricted log-likelihood
 
-  # get initial values for mlm start
-  fm.lm <- lm(sv ~ d.cwc + meanrt.cwc + level.cwc, h2b_data)
-  st <- coef(fm.lm)
+  # (1) if a warning message is produced, check random effects
+    summary(m1_h2b)$varcor
+    # (11) if all SDs are different from 0 and correlations look good (unequal to zero)
+      # this message should be a false positive and this model can be reported
+    # (12) if (11) is not true, check all available optimizers
+      n_cores <- parallel::detectCores()
+      opt_cl <- makeCluster(n_cores, type = "SOCK")
+      clusterEvalQ(opt_cl, library("lme4"))
+      clusterExport(opt_cl, "h2b_data")
+      m1_h2b_all <- allFit(m1_h2b, parallel = "snow", ncpus = n_cores, cl = opt_cl) 
+      stopCluster(opt_cl)
+      summary(m1_h2b_all)$msgs
+      # (121) if an optimizer returns NULL, use this optimizer and recalculate model to get the final model
 
-  m1_h2b <- nlme(sv ~ d.cwc + meanrt.cwc + level.cwc,
-                 data = h2b_data,
-                 #fixed = d.cwc + meanrt.cwc + level.cwc ~ 1,
-                 fixed = list(d.cwc ~ 1, meanrt ~ 1, level.cwc ~ 1),
-                 random = level.cwc ~ 1 | subject,
-                 start = list(fixed = st[2:4]),
-                 method = "REML")
+  # (2) if (121) is not true OR a singular fit message occurs, check for potential outliers and recalculate
+    potential_outliers_m1_h2b <- subset(h2b_data, abs(scale(resid(m1_h2b))) > 3)    
+    percentage_outliers <- 100/nrow(h2b_data) * nrow(potential_outliers_m1_h2b)
+    # get new subset excluding outliers
+    h2b_data_norm <- droplevels(subset(h2b_data, abs(scale(resid(m1_h2b))) < 3))
+    # start with (1) again
 
-  # change global coding to default ----------------------------------------------
-  options(contrasts = c("contr.treatment", "contr.poly"))
+  # (3) if (1) and (2) do not help, start reducing the model stepwise
 

### 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
update mlm

@@
 
+  ## plot model fit of the final model ----
+  plot_model(mfinal_h2b, type = "diag")
+
+  # FIXME: do we want to include  a table like Table 3. in Westbrook et al.?
+    # if we decide to include a table of mlm results, I propose to include a table with
+    # term/parameter - Beta - SE - p-value - random effects (SD)
+
+  # TODO: Corinna go on here :) 
+    # -> get results for reporting
+    # -> get means for plotting, plot results (if requested)
+    # -> write methods
+    # -> write results
+
+  # TODO: it would be easy to integrate NFC as level 2 predictor into the analysis
+    # to identify the personality influence on sv
+    # it goes in the same direction as hypothesis 3a, but would hold some more information
+    # a corresponding hypothesis could be
+    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores" 
+    # What do you think?
+
 ```
+
+### Changes in subjective values depend reliably on n-back level
 

### 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
looked furher into AUCs

--- 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
@@
 
-**something is wrong with the AUC calculation**
-
 ```{r AUC_demo, echo=FALSE, message=FALSE, warning=FALSE}
@@
   demo_data$subject[m:(m+3)] = rep(n,4)
-  demo_data$sv[m:(m+3)] = sv[n,]
+  #demo_data$sv[m:(m+3)] = sv[n,]
+  demo_data$sv[m:(m+3)] = sample(x = c(0.11,0.38,0.45,0.53,0.70,0.85,0.90,1.00), size = 4, replace = FALSE, prob = c(0.025,0.025,0.05,0.05,0.05,0.05,0.05,0.7))
   m = m + 4
@@
 subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
-demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
+demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double(),
+                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double())
 for (i in 1:(length(subjectindex)-1)) {
@@
                                            0.5 * (sv_sorted[2] + sv_sorted[3]) +
-                                           0.5 * (sv_sorted[3] + sv_sorted[4])))
+                                           0.5 * (sv_sorted[3] + sv_sorted[4])),
+                        ascent_mean = ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
+                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
+                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3,
+                        ascent_sum = (demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
+                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
+                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]),
+                        auc_x_ascentmean = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
+                                               method = "trapezoid") * (((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
+                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
+                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3))
   demo_sv <- rbind(demo_sv, newdata)

### 2021-10-25 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd
added "AUC" computation of Westbrook

--- 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
@@
 subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
-demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
+demo_sv <- data.frame(subject = character(), auc_sv = double(),
+                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double(),
+                      auc_westbrook = double())
 for (i in 1:(length(subjectindex)-1)) {
@@
                                    method = "trapezoid"),
-                        auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
-                                               0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
-                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])),
                         auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                            0.5 * (sv_sorted[2] + sv_sorted[3]) +
-                                           0.5 * (sv_sorted[3] + sv_sorted[4])))
+                                           0.5 * (sv_sorted[3] + sv_sorted[4])),
+                        ascent_mean = ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
+                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
+                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3,
+                        ascent_sum = (demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
+                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
+                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]),
+                        auc_x_ascentmean = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
+                                               method = "trapezoid") * (((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
+                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
+                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3),
+                        auc_westbrook = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
+                                           0.5 * (sv_sorted[1] + sv_sorted[3]) +
+                                           0.5 * (sv_sorted[1] + sv_sorted[4]))/3)
   demo_sv <- rbind(demo_sv, newdata)
 }
+demo_cor <- cor(demo_sv$auc_sv, demo_sv$auc_westbrook)
+
 ggplot(demo_data, aes(x=level, y=sv, group=subject)) +

### 2021-10-29 06_Paper/ER-ED/intro.Rmd
added text on maladaptive ER strategies

@@
 Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
-This postulation was questioned with the concept of ER flexibility.
+For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
+Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
+The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
 *Maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
-There was now a greater focus on how ER strategies are being chosen.
+To 
 For example it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011].  

### 2021-10-29 06_Paper/ER-ED/intro.Rmd
added text (Strategy Choice)

@@
 The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
-*Maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
+Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
 To 
@@
 <!-- Überleitung zu SVs-->
+What was missing in this research so far was the information regarding the strategy not chosen. 
+People choose a strategy that they prefer, for whatever reason. 
+However, nothing is revealed about the strategy that is not chosen.
+On the one hand, it could be possible that the chosen strategy is the clear preference, the unchosen strategy is not a realistic option for the individual. 
+On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
+<!-- Evtl. Forschung zum Repertoire --> 
 Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

### 2021-10-29 06_Paper/ER-ED/intro.Rmd
added text on ER flexibility and transition to SVs

@@
 Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
-To 
-For example it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011].  
-<!-- Kommentare zu  ER Choice -->
+First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
+For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
+Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
+This selection of strategies is influenced by numerous facotrs.
+For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
+Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.
+
+<!-- Weitere Einflussfaktoren aufzuählen zu  ER Choice -->
 [...]
-<!-- Überleitung zu SVs-->
+
 What was missing in this research so far was the information regarding the strategy not chosen. 
@@
 On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
-<!-- Evtl. Forschung zum Repertoire --> 
-Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
+This leads to the question of how individual subjective values of ER strategies are characterized an how one can determine them. 
+Individual subjective values (SV) of effortful tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
 

### 2021-11-03 06_Paper/COG-ED/Manuscript.Rmd
updated d prime calculation with trimmed RT data

@@
 
-  # set the number of targets and non-targets, so in case the paradigm will be changed it is easily accessible
-  # they are multiplied by 2, because there are two runs per n-back level
-
-  num_targets <- 16*2
-  num_nontargets <- 48*2
-
   # compute index of rows in which the levels change
 
-  levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))
+  levelindex <- c(1,which(data_RT$level != dplyr::lag(data_RT$level)),nrow(data_RT))
 
@@
 
-    hits <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
-                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
-    falsealarms <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
-                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
-    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
-                          level = data_nback$level[levelindex[i]],
+    # set the number of targets and non-targets
+    num_targets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
+    num_nontargets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
+
+    hits <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
+                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
+    falsealarms <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
+                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
+    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
+                          level = data_RT$level[levelindex[i]],
                           hitrate = hits/num_targets,
@@
 
-    meanrt <- mean(data_nback$rt[which(data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
+    meanrt <- mean(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                  +(levelindex[i]-1)], na.rm = TRUE)
 
-    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
-                          level = data_nback$level[levelindex[i]],
+    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
+                          level = data_RT$level[levelindex[i]],
                           meanrt = meanrt)
@@
 demo_sv <- data.frame(subject = character(), auc_sv = double(),
-                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double(),
+                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double(), auc_x_ascentsum = double(),
                       auc_westbrook = double())
@@
                                         (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3),
+                        auc_x_ascentsum = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
+                                               method = "trapezoid") * ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
+                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
+                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]])),
                         auc_westbrook = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
@@
 
-ggplot(demo_data[c((1*4+1):(1*4+4),(4*4+1):(4*4+4),(15*4+1):(15*4+4),(17*4+1):(17*4+4)),], aes(x=level, y=sv, group=subject)) +
-  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
-ggplot(demo_data[c((3*4+1):(3*4+4),(5*4+1):(5*4+4),(9*4+1):(9*4+4),(11*4+1):(11*4+4)),], aes(x=level, y=sv, group=subject)) +
-  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
-ggplot(demo_data[c((0*4+1):(0*4+4),(2*4+1):(2*4+4),(21*4+1):(21*4+4),(23*4+1):(23*4+4)),], aes(x=level, y=sv, group=subject)) +
-  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0, h = 0.03))
+#library(data.table) for the melt function
+ggplot(melt(setDT(demo_sv), id.vars = "subject", variable.name = "measure"), aes(fill=measure,y=value,x=subject)) + geom_bar(position = "dodge", stat = "identity")
 ```

### 2021-11-05 06_Paper/COG-ED/Manuscript.Rmd
started preparation of pipeline data frames

@@
 
-  # create a new data frame for the data that is being used for reaction time analysis
-  # (we cannot exclude trials from the main data frame because the computation of d prime depends on hit-ratios, not reaction time)
-
-  # exclude trials after incorrect responses and with reaction times below 200 ms
-
-  data_RT <- data_nback[-c(which(data_nback$correct == 1) + 1), ]
-  data_RT <- data_RT[-c(which(data_RT$rt < 0.2)), ]
-
   # the choice column will contain 1 for the left button and 2 for the right button
@@
                                                cdrisc_complete, flexer_timestamp, flexer_complete))
+
+```
+
+```{r preprocessing, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # create new data frames for the specification curve analysis
+  # the data frame names are a combination of three letters from each of these categories, indicating how they will be preprocessed:
+  #
+  # RT transformations:
+  #   (R) raw/none
+  #   (L) log
+  #   (I) inverse
+  #   (S) square-root
+  # RT outlier exclusion:
+  #   (N) none
+  #   (2) 2 SDs from the mean
+  #   (5) 2.5 SDs from the mean
+  #   (3) 3 SDs from the mean
+  #   (T) 0-200 ms after stimulus onset
+  # Post-error trials:
+  #   (E) excluded
+  #   (N) not excluded
+  #
+  # Example: the data frame "RT_L3E" has log-transformed RT data with no data points beyond 3 SD from the mean and with no trials that followed misses/false alarms
+
+  # one data frame without transformations is a simple copy of the original data frame
+  RT_RNN <- data_nback
+
+  # loop across participants and levels for log, inverse and square-root transform
+
+      # make three more copies of the original data frame as a base
+      RT_L <- data_nback
+      RT_I <- data_nback
+      RT_S <- data_nback
+
+      # create index of rows in which the level changes
+      levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))
+
+      for (i in 1:(length(levelindex)-1)) {
+
+        RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- log10(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
+        RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- 1/(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
+        RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- sqrt(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
+      }
+
+  # exclude trials after incorrect responses and with reaction times below 200 ms
+
+  data_RT <- data_nback[-c(which(data_nback$correct == 1) + 1), ]
+  data_RT <- data_RT[-c(which(data_RT$rt < 0.2)), ]
 

### 2021-11-05 06_Paper/ER-ED/intro.Rmd
corrected typo

@@
 
+<!-- Einführung ER -->
 [...]
-<!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->
 Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
@@
 Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
-This selection of strategies is influenced by numerous facotrs.
+This selection of strategies is influenced by numerous factors.
 For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 

### 2021-11-05 06_Paper/ER-ED/intro.Rmd
Added factory of ER choice

@@
 For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
-Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.
+Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction[@Sheppes2011;@Sheppes2014].
+Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
+Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
+In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
+Afterwards they could choose, which strategy they want to use again.
+Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one.
 
-<!-- Weitere Einflussfaktoren aufzuählen zu  ER Choice -->
 [...]

### 2021-11-05 06_Paper/ER-ED/intro.Rmd
corrected paragraph on SVs

@@
 Afterwards they could choose, which strategy they want to use again.
-Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one.
+Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: suppression.
+Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
 
-[...]
-
-What was missing in this research so far was the information regarding the strategy not chosen. 
-People choose a strategy that they prefer, for whatever reason. 
+However, what has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
+People choose a strategy that they prefer, for different, relatively well-known reasons. 
 However, nothing is revealed about the strategy that is not chosen.
-On the one hand, it could be possible that the chosen strategy is the clear preference, the unchosen strategy is not a realistic option for the individual. 
+On the one hand, it could be possible that the chosen strategy represents the clear preference of an individual.
+The strategy that was not chosen is not a realistic option for the individual. 
 On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
-This leads to the question of how individual subjective values of ER strategies are characterized an how one can determine them. 
-Individual subjective values (SV) of effortful tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
+To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
+Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
+Individual subjective values (SV) of effortful cognitive tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
 

### 2021-11-08 06_Paper/COG-ED/Manuscript.Rmd
started pipeline data frame creation

--- 2021-11-03 06_Paper/COG-ED/Manuscript.Rmd
@@
                                                cdrisc_complete, flexer_timestamp, flexer_complete))
+
+```
+
+```{r preprocessing, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # create new data frames for the specification curve analysis
+  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
+  #
+  # across which dimensions the tranformation and outlier exclusion will be done:
+  #   (AA) across subjects, across n-back levels
+  #   (AW) across subjects, within n-back levels
+  #   (WW) within subjects, within n-back levels
+  #   (WA) within subjects, across n-back levels
+  # RT transformations:
+  #   (R) raw/none
+  #   (L) log
+  #   (I) inverse
+  #   (S) square-root
+  # RT outlier exclusion:
+  #   (N) none
+  #   (2) 2 SDs from the mean
+  #   (3) 3 SDs from the mean
+  #   (T) 0-200 ms after stimulus onset
+  # Post-error trials:
+  #   (E) excluded
+  #   (N) not excluded
+  #
+  # Example: the data frame "AWL3E" has log-transformed RT data with no data points beyond 3 SD
+  # from the mean and with no trials that followed misses/false alarms
+  #
+  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R___) with either no outlier
+  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
+  # time-based exclusion is nonsensical for transformed data sets.
+
+  # one data frame without transformations is a simple copy of the original data frame
+  # put that data frame in a list in which all data frames will be and replace the RTs of incorrect trials with NA
+
+  pipelines_data <- list("RNN" = data_nback)
+  pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 0] <- NA
+
+  # add raw version without post-error trials
+
+  pipelines_data[["RNE"]] <- pipelines_data[["RNN"]][-c(which(pipelines_data[["RNN"]]$correct == 0) + 1), ]
+
+  # add raw versions with 0-200ms exclusion
+
+  pipelines_data[["RTN"]] <- pipelines_data[["RNN"]][-c(which(pipelines_data[["RNN"]]$rt < 0.2)), ]
+  pipelines_data[["RTE"]] <- pipelines_data[["RTN"]][-c(which(pipelines_data[["RTN"]]$correct == 0) + 1), ]
+
+  # group 1: across subjects, across conditions
+
+    # raw versions
+
+    tempmean <- mean(pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 1])
+    tempsd <- sd(pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 1])
+
+    pipelines_data[["AAR2N"]] <- pipelines_data[["RNN"]][c(which(pipelines_data[["RNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["RNN"]]$rt > (tempmean-2*tempsd))), ]
+    pipelines_data[["AAR2E"]] <- pipelines_data[["AAR2N"]][-c(which(pipelines_data[["AAR2N"]]$correct == 0) + 1), ]
+    pipelines_data[["AAR3N"]] <- pipelines_data[["RNN"]][c(which(pipelines_data[["RNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["RNN"]]$rt > (tempmean-3*tempsd))), ]
+    pipelines_data[["AAR3E"]] <- pipelines_data[["AAR3N"]][-c(which(pipelines_data[["AAR3N"]]$correct == 0) + 1), ]
+
+    # log transformed versions
+
+    pipelines_data[["AALNN"]] <- pipelines_data[["RNN"]]
+    pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1] <- log10(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])
+
+    tempmean <- mean(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])
+    tempsd <- sd(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])
+
+    pipelines_data[["AALNE"]] <- pipelines_data[["AALNN"]][-c(which(pipelines_data[["AALNN"]]$correct == 0) + 1), ]
+    pipelines_data[["AAL2N"]] <- pipelines_data[["AALNN"]][c(which(pipelines_data[["AALNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AALNN"]]$rt > (tempmean-2*tempsd))), ]
+    pipelines_data[["AAL2E"]] <- pipelines_data[["AAL2N"]][-c(which(pipelines_data[["AAL2N"]]$correct == 0) + 1), ]
+    pipelines_data[["AAL3N"]] <- pipelines_data[["AALNN"]][c(which(pipelines_data[["AALNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AALNN"]]$rt > (tempmean-3*tempsd))), ]
+    pipelines_data[["AAL3E"]] <- pipelines_data[["AAL3N"]][-c(which(pipelines_data[["AAL3N"]]$correct == 0) + 1), ]
+
+    # inverse transformed versions
+
+    pipelines_data[["AAINN"]] <- pipelines_data[["RNN"]]
+    pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1] <- 1/(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])
+
+    tempmean <- mean(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])
+    tempsd <- sd(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])
+
+    pipelines_data[["AAINE"]] <- pipelines_data[["AAINN"]][-c(which(pipelines_data[["AAINN"]]$correct == 0) + 1), ]
+    pipelines_data[["AAI2N"]] <- pipelines_data[["AAINN"]][c(which(pipelines_data[["AAINN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AAINN"]]$rt > (tempmean-2*tempsd))), ]
+    pipelines_data[["AAI2E"]] <- pipelines_data[["AAI2N"]][-c(which(pipelines_data[["AAI2N"]]$correct == 0) + 1), ]
+    pipelines_data[["AAI3N"]] <- pipelines_data[["AAINN"]][c(which(pipelines_data[["AAINN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AAINN"]]$rt > (tempmean-3*tempsd))), ]
+    pipelines_data[["AAI3E"]] <- pipelines_data[["AAI3N"]][-c(which(pipelines_data[["AAI3N"]]$correct == 0) + 1), ]
+
+    # square root transformed versions
+
+    pipelines_data[["AASNN"]] <- pipelines_data[["RNN"]]
+    pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1] <- sqrt(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])
+
+    tempmean <- mean(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])
+    tempsd <- sd(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])
+
+    pipelines_data[["AASNE"]] <- pipelines_data[["AASNN"]][-c(which(pipelines_data[["AASNN"]]$correct == 0) + 1), ]
+    pipelines_data[["AAS2N"]] <- pipelines_data[["AASNN"]][c(which(pipelines_data[["AASNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AASNN"]]$rt > (tempmean-2*tempsd))), ]
+    pipelines_data[["AAS2E"]] <- pipelines_data[["AAS2N"]][-c(which(pipelines_data[["AAS2N"]]$correct == 0) + 1), ]
+    pipelines_data[["AAS3N"]] <- pipelines_data[["AASNN"]][c(which(pipelines_data[["AASNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AASNN"]]$rt > (tempmean-3*tempsd))), ]
+    pipelines_data[["AAS3E"]] <- pipelines_data[["AAS3N"]][-c(which(pipelines_data[["AAS3N"]]$correct == 0) + 1), ]
+
+  # group 2: across subjects, within conditions
+
+  # group 3: within subjects, within conditions
+
+  # group 4: within subjects, across conditions
+
+      # create index of rows in which the level changes
+      #levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))
+
+      #for (i in 1:(length(levelindex)-1)) {
+
+        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- log10(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
+        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- 1/(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
+        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- sqrt(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
+      #}
 

### 2021-11-09 06_Paper/COG-ED/Manuscript.Rmd
added space
started implementing pipeline loop

@@
   # time-based exclusion is nonsensical for transformed data sets.
+
+  # create a list that contains the basic data frame of the n-back data for each of the pipelines
+
+  pipelines_data <- replicate(92, data_nback, simplify = FALSE)
+  pipelines_data <- setNames(pipelines_data, c("AARNN","AARNE","AAR2N","AAR2E","AAR3N","AAR3E","AARTN","AARTE",
+                                               "AALNN","AALNE","AAL2N","AAL2E","AAL3N","AAL3E",
+                                               "AAINN","AAINE","AAI2N","AAI2E","AAI3N","AAI3E",
+                                               "AASNN","AASNE","AAS2N","AAS2E","AAS3N","AAS3E",
+                                               "AWR2N","AWR2E","AWR3N","AWR3E",
+                                               "AWLNN","AWLNE","AWL2N","AWL2E","AWL3N","AWL3E",
+                                               "AWINN","AWINE","AWI2N","AWI2E","AWI3N","AWI3E",
+                                               "AWSNN","AWSNE","AWS2N","AWS2E","AWS3N","AWS3E",
+                                               "WWR2N","WWR2E","WWR3N","WWR3E",
+                                               "WWLNN","WWLNE","WWL2N","WWL2E","WWL3N","WWL3E",
+                                               "WWINN","WWINE","WWI2N","WWI2E","WWI3N","WWI3E",
+                                               "WWSNN","WWSNE","WWS2N","WWS2E","WWS3N","WWS3E",
+                                               "WAR2N","WAR2E","WAR3N","WAR3E",
+                                               "WALNN","WALNE","WAL2N","WAL2E","WAL3N","WAL3E",
+                                               "WAINN","WAINE","WAI2N","WAI2E","WAI3N","WAI3E",
+                                               "WASNN","WASNE","WAS2N","WAS2E","WAS3N","WAS3E"))
+
+  for (i in 1:length(pipeline_data)) {
+
+    # extract the name of the current data frame
+
+    pipeline_name <- strsplit(names(pipelines_data)[i], "")
+
+    # replace the RTs of incorrect trials with NA for better handling
+
+    pipelines_data[[i]]$rt[pipelines_data[[i]]$correct == 0] <- NA
+
+    # the first decision is whether transformations and exclusions will be applied across/within subjects/levels
+
+    if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "A") {
+
+          # the second decision is the type of transformation
+
+          if (pipeline_name[[1]][3] == "L") {
+
+            pipelines_data[[i]]$rt <- log10(pipelines_data[[i]]$rt)
+
+          } else if (pipeline_name[[1]][3] == "I") {
+
+            pipelines_data[[i]]$rt <- 1/(pipelines_data[[i]]$rt)
+
+          } else if (pipeline_name[[1]][3] == "S") {
+
+            pipelines_data[[i]]$rt <- sqrt(pipelines_data[[i]]$rt)
+          }
+
+          # compute mean and standard deviation
+
+          pipemean <- mean(pipelines_data[[i]]$rt, na.rm = TRUE)
+          pipesd <- sd(pipelines_data[[i]]$rt, na.rm = TRUE)
+
+          # the third decision is the outlier exclusion
+
+          if (pipeline_name[[1]][4] == "2") {
+
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemean + 2 * pipesd)
+                                                               & pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))), ]
+
+          } else if (pipeline_name[[1]][4] == "3") {
+
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemean + 3 * pipesd)
+                                                               & pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))), ]
+
+          } else if (pipeline_name[[1]][4] == "T") {
+
+            pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]
+          }
+
+    } else if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "W") {
+
+    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "W") {
+
+    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "A") {
+
+    }
+  }
+
+  #------old version below---
 

### 2021-11-10 06_Paper/ER-ED/intro.Rmd
Added two intro sentences
added intro sentences
Added sentence Added comments for structuring

@@
 
-<!-- Einführung ER -->
+Every day we are confronted with stressful or emotionally demanding situations. 
+The ability to modify emotional experiences, expressions and physiology [@Gross1998antecedent] regulate emotions is an important cognitive skill. 
+It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
+
+<!-- Nun ER Strategies aufzählen -->
+<!-- Wirksamkeit von ER Strategien -> Meta Analyse Webb -->
+<!-- Evtl noch auf einzelne Strategien eingehen (Distancing, Distraction, Suppression) -->
 [...]

### 2021-11-11 06_Paper/ER-ED/intro.Rmd
added text on ER process model

@@
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
+Different strategies can be used to regulate emotions.
+So called antecedent-focused strategies, i.e., situation selection, situation modification, attentional deployment, and cognitive change take effect early in the emotion generation process.
+The strategy response modification, in contrast, takes place late in the process and is therefore conceptualized as response-focused strategy [@Gross1998antecedent].
 

### 2021-11-11 06_Paper/ER-ED/intro.Rmd
added text on ER strategies

--- 2021-11-10 06_Paper/ER-ED/intro.Rmd
@@
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
+Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Power2019], individuals can implement ER strategies by means of different tactics.
+So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
+In contrast, response modification takes place late in the process and is therefore conceptualized as response-focused strategy [@Gross1998antecedent].
 
@@
 <!-- Evtl noch auf einzelne Strategien eingehen (Distancing, Distraction, Suppression) -->
-[...]
+
 Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 

### 2021-11-12 06_Paper/ER-ED/intro.Rmd
added meta analysis
added meta analytic results

@@
 In contrast, response modification takes place late in the process and is therefore conceptualized as response-focused strategy [@Gross1998antecedent].
+This postulated temporal sequence of ER strategies affects their effectiveness.
+It is meta-analytically proven that all mentioned strategies reduce emotional arousal [@Webb2012]. 
+Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on outcomes in measures of emotion experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
+With an effect size of _d~+~_ = 0.45 distancing as tactic of cognitive change showed the highest effectiveness [@Webb2012].
 

### 2021-11-12 06_Paper/ER-ED/intro.Rmd
corrected reference

@@
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
-Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Power2019], individuals can implement ER strategies by means of different tactics.
+Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
 So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].

### 2021-11-12 06_Paper/ER-ED/intro.Rmd
added intro text

@@
 With an effect size of _d~+~_ = 0.45 distancing as tactic of cognitive change showed the highest effectiveness [@Webb2012].
-
-<!-- Nun ER Strategies aufzählen -->
-<!-- Wirksamkeit von ER Strategien -> Meta Analyse Webb -->
-<!-- Evtl noch auf einzelne Strategien eingehen (Distancing, Distraction, Suppression) -->
-
-Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
+So these tactics from three different strategies proved to be effective in the short term. 
+However, in order to be able to make a statement on the general benefit, longer-term consequences must also be considered. 
+Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are suspected of being disadvantageous in the longer term.
+Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
 Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
@@
 Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
+
 The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.

### 2021-11-12 06_Paper/ER-ED/method.Rmd
added import chunk

@@
 here::i_am("flag_project_root_CERED.txt")
+```
+
+```{r stimvalues, echo = FALSE}
+# import excel list with neutral and negative pictures
+# lists contain arousal and valence values of each picture
+stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))
+
+stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
+```
+
+```{r import, echo=FALSE, message=FALSE, warning=FALSE}
+
 ```
@@
 ## 2.4 Stimuli
-```{r stimvalues, echo = FALSE}
-# import excel list with neutral and negative pictures
-# lists contain arousal and valence values of each picture
-stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))
-
-stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
-```
 

### 2021-11-12 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 ```{r import, echo=FALSE, message=FALSE, warning=FALSE}
+# import ER ratings and ER discounting data into lists
 
+datalist_ER = lapply(list.files(here("04_RawData", "Pilot", "ER_ED"), pattern = '.*ER.*csv', full.names = TRUE),
+                          read.csv, stringsAsFactors = FALSE, header = TRUE)
+
+datalist_ED = lapply(list.files(here("04_RawData", "Pilot", "ER_ED"), pattern = '.*_ED.*csv', full.names = TRUE),
+                          read.csv, stringsAsFactors = FALSE, header = TRUE)
 ```

### 2021-11-12 06_Paper/ER-ED/method.Rmd
changed file names and deleted non csv files

--- 2021-11-12 06_Paper/ER-ED/method.Rmd
@@
 ```{r import, echo=FALSE, message=FALSE, warning=FALSE}
+# import ER ratings and ER discounting data into lists
 
+datalist_ER = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ER.*csv', full.names = TRUE),
+                          read.csv, stringsAsFactors = FALSE, header = TRUE)
+
+datalist_ED = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ED.*csv', full.names = TRUE),
+                          read.csv, stringsAsFactors = FALSE, header = TRUE)
 ```

### 2021-11-12 06_Paper/ER-ED/method.Rmd
added empty data fames for ER and ED data

@@
                           read.csv, stringsAsFactors = FALSE, header = TRUE)
+
+# new empty frame to store files into
+data_ER = data.frame(ID = character(), )
+
+data_ED = data.frame(ID = character(), step = double(), choice = character(),
+                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
 ```

### 2021-11-15 06_Paper/COG-ED/Manuscript.Rmd
re-included data frame "data_RT"

@@
   data_ED <- subset(data_ED, select = -c(step))
+
+  # remove trials with RT < 200 ms from the n-back data and exclude trials after incorrect trials
+  data_RT <- data_nback[-c(which(data_nback$rt < 0.2)), ]
+  data_RT <- data_RT[-c(which(data_RT$correct == 0) + 1), ]
 
@@
 The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
-Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Ashby1980; @Whelan2008; @Berger2021].
+Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Whelan2008; @Berger2021].
 Error- and post-error trials were excluded, because RT on the latter trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-#TODO: Tolle Artikel, die schaue ich mir auch noch mal genauer an! Hast du die beiden exclusions schon im script umgesetzt? Falls ja, in welcher Zeile, ich kann es nicht finden...
 Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
@@
 When including the AUC of all NASA-TLX subscales as a predictor, it could not explain any variance in NFC beyond the one explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
-
-```{r Hypothesis_3c, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # H3c: When putting the SVs in descending order before computing the AUC, the prediction of NFC scores by SVs can be improved significantly.
-
-  # prepare empty data frame for the loop to feed into
-
-  h3c_data <- data.frame(subject = character(), auc_sv_sorted = double())
-
-  # calculate AUC of SVs per subject
-
-  for (i in 1:(length(subjectindex)-1)) {
-
-    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
-                          auc_sv_sorted = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
-                                   method = "trapezoid", sort = TRUE))
-    h3c_data <- rbind(h3c_data, newdata)
-
-  }
-
-  # merge the NFC data frame into the AUC data frame by row
-
-  h3_data <- merge(h3_data, h3c_data)
-
-  # remove temporary variable
-
-  remove(h3c_data)
-
-  # compute linear regression to predict NCS based on SV AUC
-
-  hypothesis3c <- summary(lm(h3_data$nfc ~ h3_data$auc_sv_sorted))
-
-```

### 2021-11-15 06_Paper/ER-ED/intro.Rmd
made small changes

@@
 Every day we are confronted with stressful or emotionally demanding situations. 
-The ability to modify emotional experiences, expressions and physiology [@Gross1998antecedent] regulate emotions is an important cognitive skill. 
+The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
@@
 This postulated temporal sequence of ER strategies affects their effectiveness.
-It is meta-analytically proven that all mentioned strategies reduce emotional arousal [@Webb2012]. 
-Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on outcomes in measures of emotion experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
+It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012]. 
+Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on outcomes in measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
 With an effect size of _d~+~_ = 0.45 distancing as tactic of cognitive change showed the highest effectiveness [@Webb2012].
@@
 However, in order to be able to make a statement on the general benefit, longer-term consequences must also be considered. 
-Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are suspected of being disadvantageous in the longer term.
+Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
 Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
 Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
-For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
-Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
+For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
+Also, meta-analytic evidence exists linking a number of ER strategies to psychological disorders [@Aldao2010].
 
@@
 First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
-For example, greater ER variability is related to reduced negative affect and therefore adaptive in daily life [@Blanke2020].
+For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
 Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
@@
 For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
-Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction[@Sheppes2011;@Sheppes2014].
-Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
+Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction [@Sheppes2011;@Sheppes2014].
+Further influencing factors are for example extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
 Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
+### Willst du hier nicht lieber "in our previous work" oder sowas schreiben?
+Wenn die Autoren von sich selbst in der dritten Person sprechen, hab ich immer das Gefühl, dass sie die Lesenden in die Irre führen wollen, indem sie etwas referenzieren, was eigentlich von ihnen selbst ist.
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
 Afterwards they could choose, which strategy they want to use again.
-Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: suppression.
+Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
 Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
@@
 However, nothing is revealed about the strategy that is not chosen.
-On the one hand, it could be possible that the chosen strategy represents the clear preference of an individual.
-The strategy that was not chosen is not a realistic option for the individual. 
+It is possible that the chosen strategy represents the clear preference of an individual, while the strategy that was not chosen is not a realistic option for them. 
 On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
@@
 
-In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
-Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
+In the original study by Westbrook et al.
+[-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
+Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
 In the current study, we want to use this paradigm to determine SVs of ER strategies.
-In doing so, we need to make an important change: we have to adapt the assumption that the easiest *N*-back level has the highest SV.
+In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
 As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
-Moreover, there is nothing like the objectively easiest ER strategy.
-Therefore, we have to add an additional step were the option with the higher subjective value is determined. 
+Moreover, there is nothing like an objectively easiest ER strategy.
+Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
 In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
@@
 But our paradigm can also account for the case that a person does not have a clear preference.
-Then no SV will be 1, but at least the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs.
+Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs.
+### Hier sollte auch noch erwähnt werden, dass wir auch n-back erheben
 
 ## 1.2 The present study
-The aim of the present study is to evaluate, if this paradigm is suitable for determining SVs of ER strategies. 
+
+The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies. 
 We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
-We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively effortful than distraction and suppression.
-Regarding SVs of ER strategies we expect that (3a) people chose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
+We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively more effortful than distraction and suppression.
+Regarding SVs of ER strategies we expect that (3a) people choose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
 Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs. 

### 2021-11-16 06_Paper/COG-ED/Manuscript.Rmd
tried computing the pipeline loop but weird NAs come up

@@
 
-  for (i in 1:length(pipeline_data)) {
+  for (i in 1:length(pipelines_data)) {
 
@@
 
-          # the second decision is the type of transformation
+          # the second decision is the type of transformation, depending on the third letter in the data frame name
 
@@
                                                                & pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))), ]
-
-          } else if (pipeline_name[[1]][4] == "T") {
+          }
+
+    } else if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "W") {
+
+        # apply the transformations and exclusions across subjects but within levels
+
+        for (x in 1:4) {
+
+            # the second decision is the type of transformation, depending on the third letter in the data frame name
+
+            if (pipeline_name[[1]][3] == "L") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])
+
+            } else if (pipeline_name[[1]][3] == "I") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])
+
+            } else if (pipeline_name[[1]][3] == "S") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])
+
+            }
+
+            # compute mean and standard deviation
+
+            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
+            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
+
+            # the third decision is the outlier exclusion
+
+            if (pipeline_name[[1]][4] == "2") {
+
+              pipelines_data[[i]] <-
+                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
+                                           & (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))) | (pipelines_data[[i]]$level != x), ]
+
+            } else if (pipeline_name[[1]][4] == "3") {
+
+              pipelines_data[[i]] <-
+                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
+                                           & (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))) | (pipelines_data[[i]]$level != x), ]
+            }
+        }
+
+    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "W") {
+
+        # apply the transformations and exclusions within subjects and within levels
+
+        for (x in 1:4) {
+
+          for (y in 1:length(table(pipelines_data[[i]]$subject))) {
+
+            # save the name of the subject as a temporary variable
+
+            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]
+
+            # the second decision is the type of transformation, depending on the third letter in the data frame name
+
+            if (pipeline_name[[1]][3] == "L") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                     & pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                                                                                                   & pipelines_data[[i]]$subject == pipesubject])
+
+            } else if (pipeline_name[[1]][3] == "I") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                     & pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                                                                                                & pipelines_data[[i]]$subject == pipesubject])
+
+            } else if (pipeline_name[[1]][3] == "S") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                     & pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                                                                                                  & pipelines_data[[i]]$subject == pipesubject])
+
+            }
+
+            # compute mean and standard deviation
+
+            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+
+            # the third decision is the outlier exclusion
+
+            if (pipeline_name[[1]][4] == "2") {
+
+              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
+                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
+                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
+                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]
+
+            } else if (pipeline_name[[1]][4] == "3") {
+
+              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
+                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
+                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
+                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
+                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
+            }
+          }
+        }
+
+    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "A") {
+
+      # apply the transformations and exclusions within subjects but across levels
+
+        for (y in 1:length(table(pipelines_data[[i]]$subject))) {
+
+            # save the name of the subject as a temporary variable
+
+            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]
+
+            # the second decision is the type of transformation, depending on the third letter in the data frame name
+
+            if (pipeline_name[[1]][3] == "L") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])
+
+            } else if (pipeline_name[[1]][3] == "I") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])
+
+            } else if (pipeline_name[[1]][3] == "S") {
+
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])
+
+            }
+
+            # compute mean and standard deviation
+
+            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+
+            # the third decision is the outlier exclusion
+
+            if (pipeline_name[[1]][4] == "2") {
+
+              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
+                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
+                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
+                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]    
+            } else if (pipeline_name[[1]][4] == "3") {
+
+              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
+                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
+                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
+                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
+            }
+        }
+
+    }
+
+    # the 200-ms-exclusion and the post-error-exclusion are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:
+
+    # exclude RTs fast than 200 ms after stimulus onset if the fourth letter in the data frame name is a "T"
+
+    if (pipeline_name[[1]][4] == "T") {
 
       pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]
-          }
-
-    } else if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "W") {
-
-    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "W") {
-
-    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "A") {
-
-    }
-  }
-
-  #------old version below---
-
-  # one data frame without transformations is a simple copy of the original data frame
-  # put that data frame in a list in which all data frames will be and replace the RTs of incorrect trials with NA
-
-  pipelines_data <- list("RNN" = data_nback)
-  pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 0] <- NA
-
-  # add raw version without post-error trials
-
-  pipelines_data[["RNE"]] <- pipelines_data[["RNN"]][-c(which(pipelines_data[["RNN"]]$correct == 0) + 1), ]
-
-  # add raw versions with 0-200ms exclusion
-
-  pipelines_data[["RTN"]] <- pipelines_data[["RNN"]][-c(which(pipelines_data[["RNN"]]$rt < 0.2)), ]
-  pipelines_data[["RTE"]] <- pipelines_data[["RTN"]][-c(which(pipelines_data[["RTN"]]$correct == 0) + 1), ]
-
-  # group 1: across subjects, across conditions
-
-    # raw versions
-
-    tempmean <- mean(pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 1])
-    tempsd <- sd(pipelines_data[["RNN"]]$rt[pipelines_data[["RNN"]]$correct == 1])
-
-    pipelines_data[["AAR2N"]] <- pipelines_data[["RNN"]][c(which(pipelines_data[["RNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["RNN"]]$rt > (tempmean-2*tempsd))), ]
-    pipelines_data[["AAR2E"]] <- pipelines_data[["AAR2N"]][-c(which(pipelines_data[["AAR2N"]]$correct == 0) + 1), ]
-    pipelines_data[["AAR3N"]] <- pipelines_data[["RNN"]][c(which(pipelines_data[["RNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["RNN"]]$rt > (tempmean-3*tempsd))), ]
-    pipelines_data[["AAR3E"]] <- pipelines_data[["AAR3N"]][-c(which(pipelines_data[["AAR3N"]]$correct == 0) + 1), ]
-
-    # log transformed versions
-
-    pipelines_data[["AALNN"]] <- pipelines_data[["RNN"]]
-    pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1] <- log10(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])
-
-    tempmean <- mean(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])
-    tempsd <- sd(pipelines_data[["AALNN"]]$rt[pipelines_data[["AALNN"]]$correct == 1])
-
-    pipelines_data[["AALNE"]] <- pipelines_data[["AALNN"]][-c(which(pipelines_data[["AALNN"]]$correct == 0) + 1), ]
-    pipelines_data[["AAL2N"]] <- pipelines_data[["AALNN"]][c(which(pipelines_data[["AALNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AALNN"]]$rt > (tempmean-2*tempsd))), ]
-    pipelines_data[["AAL2E"]] <- pipelines_data[["AAL2N"]][-c(which(pipelines_data[["AAL2N"]]$correct == 0) + 1), ]
-    pipelines_data[["AAL3N"]] <- pipelines_data[["AALNN"]][c(which(pipelines_data[["AALNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AALNN"]]$rt > (tempmean-3*tempsd))), ]
-    pipelines_data[["AAL3E"]] <- pipelines_data[["AAL3N"]][-c(which(pipelines_data[["AAL3N"]]$correct == 0) + 1), ]
-
-    # inverse transformed versions
-
-    pipelines_data[["AAINN"]] <- pipelines_data[["RNN"]]
-    pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1] <- 1/(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])
-
-    tempmean <- mean(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])
-    tempsd <- sd(pipelines_data[["AAINN"]]$rt[pipelines_data[["AAINN"]]$correct == 1])
-
-    pipelines_data[["AAINE"]] <- pipelines_data[["AAINN"]][-c(which(pipelines_data[["AAINN"]]$correct == 0) + 1), ]
-    pipelines_data[["AAI2N"]] <- pipelines_data[["AAINN"]][c(which(pipelines_data[["AAINN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AAINN"]]$rt > (tempmean-2*tempsd))), ]
-    pipelines_data[["AAI2E"]] <- pipelines_data[["AAI2N"]][-c(which(pipelines_data[["AAI2N"]]$correct == 0) + 1), ]
-    pipelines_data[["AAI3N"]] <- pipelines_data[["AAINN"]][c(which(pipelines_data[["AAINN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AAINN"]]$rt > (tempmean-3*tempsd))), ]
-    pipelines_data[["AAI3E"]] <- pipelines_data[["AAI3N"]][-c(which(pipelines_data[["AAI3N"]]$correct == 0) + 1), ]
-
-    # square root transformed versions
-
-    pipelines_data[["AASNN"]] <- pipelines_data[["RNN"]]
-    pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1] <- sqrt(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])
-
-    tempmean <- mean(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])
-    tempsd <- sd(pipelines_data[["AASNN"]]$rt[pipelines_data[["AASNN"]]$correct == 1])
-
-    pipelines_data[["AASNE"]] <- pipelines_data[["AASNN"]][-c(which(pipelines_data[["AASNN"]]$correct == 0) + 1), ]
-    pipelines_data[["AAS2N"]] <- pipelines_data[["AASNN"]][c(which(pipelines_data[["AASNN"]]$rt < (tempmean+2*tempsd) & pipelines_data[["AASNN"]]$rt > (tempmean-2*tempsd))), ]
-    pipelines_data[["AAS2E"]] <- pipelines_data[["AAS2N"]][-c(which(pipelines_data[["AAS2N"]]$correct == 0) + 1), ]
-    pipelines_data[["AAS3N"]] <- pipelines_data[["AASNN"]][c(which(pipelines_data[["AASNN"]]$rt < (tempmean+3*tempsd) & pipelines_data[["AASNN"]]$rt > (tempmean-3*tempsd))), ]
-    pipelines_data[["AAS3E"]] <- pipelines_data[["AAS3N"]][-c(which(pipelines_data[["AAS3N"]]$correct == 0) + 1), ]
-
-  # group 2: across subjects, within conditions
-
-  # group 3: within subjects, within conditions
-
-  # group 4: within subjects, across conditions
-
-      # create index of rows in which the level changes
-      #levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))
-
-      #for (i in 1:(length(levelindex)-1)) {
-
-        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- log10(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
-        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- 1/(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
-        #RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- sqrt(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
-      #}
+
+    }
+
+    # exclude post-error trials if the fifth letter in the data frame name is an "E"
+    # also making sure that there are even any error-/post-error-rows left to perform the exclusion, otherwise you get an error message
+
+    if (pipeline_name[[1]][5] == "E") {
+
+      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ]) > 0,
+             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ],
+             pipelines_data[[i]] <- pipelines_data[[i]])
+
+    }
+  }
 

### 2021-11-16 06_Paper/ER-ED/method.Rmd
added data frame

@@
 # new empty frame to store files into
-data_ER = data.frame(ID = character(), )
+data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double())
 
@@
                            LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
+
+# store arousal and effort ratings in data_ER frame
+
+for (i in 1:length(datalist_ER)) {
+
+  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["instr_1"]],datalist_ER[[i]][["slider_arousal.response"]],datalist_ER[[i]][["slider_effort.response"]])
+  colnames(tmp) = names(data_ER)
+  tmp = tmp[(!is.na(tmp$arousal)),]
+
+  data_ER = rbind(tmp, data_ER)
+
+}
+
 ```

### 2021-11-16 06_Paper/COG-ED/Manuscript.Rmd
still not working

@@
               pipelines_data[[i]] <-
-                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
-                                           & (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))) | (pipelines_data[[i]]$level != x), ]
+                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & ((pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
+                                           | (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd)))) | (pipelines_data[[i]]$level != x), ]
 
@@
               pipelines_data[[i]] <-
-                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
-                                           & (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))) | (pipelines_data[[i]]$level != x), ]
+                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & ((pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
+                                           | (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd)))) | (pipelines_data[[i]]$level != x), ]
             }

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
pipelines are functional

--- 2021-11-16 06_Paper/COG-ED/Manuscript.Rmd
@@
 
+              ifelse(length(which(pipelines_data[[i]]$level == x &
+                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
                      pipelines_data[[i]] <-
-                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 2 * pipesd))
-                                           & (pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))) | (pipelines_data[[i]]$level != x), ]
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
+                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
 
@@
 
+              ifelse(length(which(pipelines_data[[i]]$level == x &
+                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
                      pipelines_data[[i]] <-
-                pipelines_data[[i]][((pipelines_data[[i]]$level == x) & (pipelines_data[[i]]$rt < (pipemean + 3 * pipesd))
-                                           & (pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))) | (pipelines_data[[i]]$level != x), ]
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
+                                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
             }
@@
 
-              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
-                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
-                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
-                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
+                     pipelines_data[[i]] <-
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
 
@@
 
-              pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject), ] <-
-                pipelines_data[[i]][which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject)
-                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                                                  & pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
-                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                                                    & pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
+                     pipelines_data[[i]] <-
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                                                      (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
             }
@@
 
-              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
-                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
-                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 2 * pipesd)
-                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 2 * pipesd))], ]    
+              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
+                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
+                     pipelines_data[[i]] <-
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
+                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
+
             } else if (pipeline_name[[1]][4] == "3") {
 
-              pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject), ] <-
-                pipelines_data[[i]][which(pipelines_data[[i]]$subject == pipesubject)
-                                    [which(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] < (pipemean + 3 * pipesd)
-                                           & pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] > (pipemean - 3 * pipesd))], ]
+              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
+                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
+                     pipelines_data[[i]] <-
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
+                                                      (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
             }

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
changed directory to pilot data folder

@@
 
-  datalist_nback = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
+  datalist_nback = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*nback.*csv', full.names = TRUE),
                           read.csv, stringsAsFactors = FALSE, header = TRUE)
-  datalist_ED = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*_ED.*csv', full.names = TRUE),
+  datalist_ED = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*_ED.*csv', full.names = TRUE),
                           read.csv, stringsAsFactors = FALSE, header = TRUE)

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
added pipeline explanation and SVsto methods section

@@
 Tukey method was used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
+
 To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
 **MLM explanation goes here**
-The association of ED and NFC was examined using three separate regressions.
-One regression used the AUC of each participant's SVs to predict their NFC score.
-The second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
-And the last regression **insert method**.
+To ensure the validity of the multi-level model, we conducted a specification curve analysis [@Simonsohn2020], which included 92 possible preprocessing pipelines of the RT data.
+These pipelines specified which transformation has been applied (none, log, inverse, or square-root), which outliers have been excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials have been excluded or not, and across which dimensions the transformations and exclusions have been applied (across/within subjects and across/within n-back levels).
+The multi-level model was run with each of the 92 pipelines, which also included our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials, no decision regarding dimension necessary).
+The ratio of pipelines that lead to significant versus non-significant effects provides and indication of how robust the effect actually is.
+
+The association of ED and NFC was examined with a regression using the AUC of each participant's SVs to predict their NFC score.
+A second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
+Since we did not have a fixed SV of 1 for 1-back, we could not apply the 'AUC' computation of Westbrook et al.
+[-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
+Consequently, we decided on a different way of quantifying the individual degree of ED.
+A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back, but can reflect the overall willingness to exert effort.
+This is the opposite for the sum of the ascent between SVs.
+Therefore, we multiplied both indicators to arrive at a value reflecting both degree and direction of preference, called $AxAUC$.
 

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
corrected questionnaire data import and analysis

@@
 
-  data_quest <- read.csv(here("04_RawData", "Sampledata", "COGED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
+  data_quest <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
   colnames(data_quest)[1] <- "set" # rename the first column
@@
                                                researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
-                                               t1_psychopy_ed_psydat, t1_psychopy_nback_csv, t1_psychopy_log, t1_psychopy_nback_psydat,
-                                               t1_psychopy_randch_log, t1_psychopy_randch_psydat, files_coged_complete, record_id_2, vl_er,
-                                               date_er, humid_bef_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
-                                               er_ed_psychopy_txt, er_ed_psychopy_psydat, files_ered_complete, followup_ered_timestamp,
+                                               t1_psychopy_nback_csv, files_coged_complete, record_id_2, vl_er,
+                                               date_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
+                                               files_ered_complete, followup_ered_timestamp,
                                                nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
@@
 
-  h3_data <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
+  h3_data <- data.frame(subject = character(), axauc = double())
 
@@
     newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
-                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
-                                   method = "trapezoid", sort = FALSE),
-                          auc_sv_unsorted = (0.5 * (data_SV$sv[subjectindex[i]] + data_SV$sv[subjectindex[i]+1]) +
-                                               0.5 * (data_SV$sv[subjectindex[i]+1] + data_SV$sv[subjectindex[i]+2]) +
-                                               0.5 * (data_SV$sv[subjectindex[i]+2] + data_SV$sv[subjectindex[i]+3])))
+                          axauc = auc(data_SV$level[subjectindex[i]:(subjectindex[i]+3)], data_SV$sv[subjectindex[i]:(subjectindex[i]+3)],
+                                               method = "trapezoid") * ((data_SV$sv[subjectindex[i]+3] - data_SV$sv[subjectindex[i]+2]) +
+                                        (data_SV$sv[subjectindex[i]+2] - data_SV$sv[subjectindex[i]+1]) +
+                                        (data_SV$sv[subjectindex[i]+1] - data_SV$sv[subjectindex[i]])))
     h3_data <- rbind(h3_data, newdata)
@@
 
-  hypothesis3a <- summary(lm(h3_data$nfc ~ h3_data$auc_sv))
+  hypothesis3a <- summary(lm(h3_data$nfc ~ h3_data$axauc))
 
@@
 The AUC of SVs predicted a significant amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
-An increase in one AUC value corresponded, on average, to an increase of `r round(hypothesis3a$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3a)$estimate$h3_data_auc_sv`).
+An increase in one AUC value corresponded, on average, to an increase of `r round(hypothesis3a$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3a)$estimate$h3_data_axauc`).
 
@@
 
-  hypothesis3b <- summary(lm(h3_data$nfc ~ h3_data$auc_sv + h3_data$auc_ntlx))
+  hypothesis3b <- summary(lm(h3_data$nfc ~ h3_data$axauc + h3_data$auc_ntlx))
 

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
removed auc demo calculation

@@
 
-```{r AUC_demo, echo=FALSE, message=FALSE, warning=FALSE}
-
-require(gtools)
-demo_data = data.frame(level = rep(1:4,24))
-sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
-m = 1
-for (n in 1:(nrow(demo_data)/4)) {
-  demo_data$subject[m:(m+3)] = rep(n,4)
-  #demo_data$sv[m:(m+3)] = sv[n,]
-  demo_data$sv[m:(m+3)] = sample(x = c(0.11,0.38,0.45,0.53,0.70,0.85,0.90,1.00), size = 4, replace = FALSE, prob = c(0.025,0.025,0.05,0.05,0.05,0.05,0.05,0.7))
-  m = m + 4
-}
-subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
-demo_sv <- data.frame(subject = character(), auc_sv = double(),
-                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double(), auc_x_ascentsum = double(),
-                      auc_westbrook = double())
-for (i in 1:(length(subjectindex)-1)) {
-  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
-  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
-                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
-                                   method = "trapezoid"),
-                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
-                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
-                                           0.5 * (sv_sorted[3] + sv_sorted[4])),
-                        ascent_mean = ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
-                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
-                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3,
-                        ascent_sum = (demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
-                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
-                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]),
-                        auc_x_ascentmean = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
-                                               method = "trapezoid") * (((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
-                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
-                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3),
-                        auc_x_ascentsum = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
-                                               method = "trapezoid") * ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
-                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
-                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]])),
-                        auc_westbrook = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
-                                           0.5 * (sv_sorted[1] + sv_sorted[3]) +
-                                           0.5 * (sv_sorted[1] + sv_sorted[4]))/3)
-  demo_sv <- rbind(demo_sv, newdata)
-}
-demo_cor <- cor(demo_sv$auc_sv, demo_sv$auc_westbrook)
-
-ggplot(demo_data, aes(x=level, y=sv, group=subject)) +
-  geom_line(aes(color=subject), size = 1)
-
-#library(data.table) for the melt function
-ggplot(melt(setDT(demo_sv), id.vars = "subject", variable.name = "measure"), aes(fill=measure,y=value,x=subject)) + geom_bar(position = "dodge", stat = "identity")
-```
-
 ```{r Hypothesis_3a, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-The AUC of SVs predicted a significant amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
-An increase in one AUC value corresponded, on average, to an increase of `r round(hypothesis3a$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3a)$estimate$h3_data_axauc`).
+The $AxAUC$ value did not predict any amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
 
@@
 
-When including the AUC of all NASA-TLX subscales as a predictor, it could not explain any variance in NFC beyond the one explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
+When including the AUC of all NASA-TLX subscales as a predictor, it could explain variance in NFC beyond the one (not) explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
+An increase in one NASA_NTLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
updated results description

@@
 We first looked at how performance measures and NASA-TLX ratings change as n-back levels increase.
-The rmANOVA revealed decreasing performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).
-Paired contrasts showed that *d'* was smaller for *...(and put in element 1/2/3 ->)* (`r apa_print(hypothesis1a_contrasts)$statistic[1]`).
+Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).
 
@@
 
-Likewise, RT increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
-Here, RTs were longer for *...(and put in element 1/2/3 ->)* (`r apa_print(hypothesis1b_contrasts)$statistic[1]`).
-Overall, the decreases in *d'* and increases in RT indicate the increase in objective task load with higher n-back levels.
+As expected, RT increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
+RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not significantly different between 2- and 4-back or 3- and 4-back.
+Even though *d'* did not decrease across n-back levels in this very small sample, the increases in RT indicate an increase in objective task load.
 
@@
 Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
-All subscales showed increases from 1-back to 4-back (mental: `r apa_print(hypothesis1c_mental_contrasts)$statistic$X1_X4`, physical: `r apa_print(hypothesis1c_pysical_contrasts)$statistic$X1_X4`, time: `r apa_print(hypothesis1c_time_contrasts)$statistic$X1_X4`, performance: `r apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, effort: `r apa_print(hypothesis1c_effort_contrasts)$statistic$X1_X4`, frustration: `r apa_print(hypothesis1c_frustration_contrasts)$statistic$X1_X4`).
+Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
+Ratings on the physical load and the performance subscales only increased between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
+Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
+Overall, these ratings showed that the increase in objective task load was also being subjectively perceived by the participants.
 
@@
 While the rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`), paired contrasts indicated that this was not the case for every pair of n-back levels.
-SVs were higher for *n*-back than for *n*-back *insert row!!* (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`) and for *n*-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`).
-The SVs of all other n-back level pairs were not significantly different.
+SVs were higher for 1- than for 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than for 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than for 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
+Since the SVs of 1- and 2-back were not significantly different, we can conclude that when given the choice, not all participants preferred the easiest n-back level.
 

### 2021-11-18 06_Paper/ER-ED/method.Rmd
added data list

@@
 # store arousal and effort ratings in data_ER frame
-
 for (i in 1:length(datalist_ER)) {
@@
 
+}
+
+# store ED data in data_ED frame
+for (i in 1:length(datalist_ED)) {
+
+  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
+                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
+                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
+                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
+                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
+                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
+                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
 }

### 2021-11-19 06_Paper/ER-ED/method.Rmd
added paragraph to statistics

@@
 
-[...]
+All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
+The level of significance was set to $alpha$ = .05.
+To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted.

### 2021-11-19 06_Paper/ER-ED/method.Rmd
added paragraph to statistics

@@
 The level of significance was set to $alpha$ = .05.
-To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted.
+
+*Effects of emotion regulation* <br>
+To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for behavioral data (subjective arousal ratings).

### 2021-11-19 06_Paper/ER-ED/method.Rmd
added text to statistics
added description of ANOVAS

--- 2021-11-18 06_Paper/ER-ED/method.Rmd
@@
 # store ED data in data_ED frame
-for (i in 1:length(datalist_ED)) {
+#for (i in 1:length(datalist_ED)) {
 
-  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
-                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
-                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
-                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
-                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
-                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
-                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
-}
+#  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
+#                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
+#                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
+#                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
+#                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
+#                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
+#                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
+#}
 
@@
 Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel were used. <!-- Stimmt das in etwa, liebe Anne? -->
-[...] <!-- Anne tried to implement a sentence here. -->
+[...] <!-- @Anne please check! =) -->
 
@@
 
-[...]
+All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
+The level of significance was set to $\alpha$ = .05.
+
+*Effects of emotion regulation on arousal and effort* <br>
+To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for behavioral data (subjective arousal ratings).
+To investigate the effect of the tree ER strategies on subjective arousal, another ANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
+To examine the impact of valence on the emotional facial reaction, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
+<!-- @Anne please check!
+=) -->
+A further ANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
+<!-- @Anne please check!
+=) -->
+To examine the effect of ER strategies on cognitive effort, an ANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
+Greenhouse-Geisser-corrected *p*-values and degrees of freedom were reported when assumption of sphericity was violated.
+Proportion of explained variance *\eta²~p~* was reported as a measure of effect size

### 2021-11-22 06_Paper/COG-ED/Manuscript.Rmd
added psychopy info to methods part
added yaml header and made some changes to the text

@@
 ---
-title             : "COG-ED Manuscript"
-author            : "Josephine"
-date              : "13 8 2021"
-output            : html_document
+title             : "When easy is not preferred: A paradigm for estimating subjective values of cognitive tasks"
+
+author: 
+  - name          : "Josephine Zerna"
+    affiliation   : "1,*"
+    corresponding : yes
+    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
+    email         : "josephine.zerna@tu-dresden.de"
+    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - Conceptualization
+      - Methodology
+      - Formal analysis
+      - Investigation
+      - Project administration
+      - Software
+      - Visualization
+      - Writing - original draft preparation
+      - Writing - review & editing
+  - name          : "Christoph Scheffel"
+    affiliation   : "1,*"
+    role:
+      - Conceptualization
+      - Methodology
+      - Funding acquisition
+      - Investigation
+      - Project administration
+      - Software
+      - Writing - review & editing
+  - name          : "Corinna Kührt"
+    affiliation   : "1"
+    role:
+      - Formal analysis
+      - Writing - original draft preparation
+      - Writing - review & editing
+
+affiliation:
+  - id            : "1"
+    institution   : "Faculty of Psychology, Technische Universität Dresden"
+  - id            : "*"
+    note          : "Shared first authorship"
+
+abstract: |
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
+wordcount         : "X"
+
 bibliography      : ref_COG-ED.bib
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
+
+csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
+
+header-includes   :
+    - \usepackage{booktabs}
+    - \usepackage{longtable}
+    - \usepackage{array}
+    - \usepackage{multirow}
+    - \usepackage{wrapfig}
+    - \usepackage{float}
+    - \usepackage{colortbl}
+    - \usepackage{pdflscape}
+    - \usepackage{tabu}
+    - \usepackage{threeparttable}
+    - \usepackage{threeparttablex}
+    - \usepackage[normalem]{ulem}
+    - \usepackage{makecell}
+    - \usepackage{xcolor}
 ---
@@
   # we will add the package versions before submission
+  # we also have the word count add-in by Ben Marwick, which can be installed via
+  # devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
 
@@
 
-One task that is often used to investigate effort is the n-back task.
-In this working memory task, a continuous stream of stimuli, e.g. letters, is presented on screen.
-Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959]; and are asked to respond as quickly and as accurately as they can.
-The n-back task requires simultaneous storage of past stimuli and processing of new stimuli [@Jonides1997].
-It is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates and reaction times [@Jaeggi2010] as well as monotonic increases in brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
+One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
+Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959]; and are asked to respond as quickly and as accurately as possible.
+The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
 However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level [@Jaeggi2010].
@@
 First, the participants complete the n-back levels to familiarize themselves with the task.
-Then, level one is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for level one.
-If they choose the more difficult level, the reward for level one increases by 0.50\$, if the choose level one, it decreases by 0.50\$.
-This is repeated five more times, with each adjustment of the level one reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
+Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
+If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if the choose 1-back, it decreases by 0.50\$.
+This is repeated five more times, with each adjustment of the 1-back reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
 The idea is to estimate the point of subjective equivalence, i.e. the monetary ratio in which both offers are equally preferred [@Westbrook2013]. 
-The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of level one by the fixed 2\$ reward of the more difficult level.
-Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting (ED) by computing an area under the curve (AUC).
-Younger participants showed lower ED, i.e. they needed a lower monetary incentive for choosing the more difficult levels over level one.
+The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
+Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting (ED).
+Younger participants showed lower ED, i.e. they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
 
@@
 However, the relation of NFC and SVs might be confounded with task performance itself, since subjective task values have been shown to depend on both the exerted effort [@Wang2017] and the expected performance [@Yee2021].
-Findings on NFC and n-back performance are heterogenous.
-On one hand individuals with higher NFC neither had better n-back performance [@Gaertner2021] nor better working memory [@Fleischhauer 2010; @Hill2013], on the other hand they showed greater attention allocation [@Enge2008] and brain flexibility [@He2019].
+Findings on NFC and n-back performance are heterogeneous, ranging from no association of NFC and working memory [@Fleischhauer 2010; @Gaertner2021; @Hill2013] to positive associations of NFC with attention allocation [@Enge2008] and brain flexibility [@He2019].
 Nevertheless, a possible association of NFC and task performance might be secondary, since task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019].
@@
 If the participant has a clear preference for one level, this level's SV will be 1.
-If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute value and in relation to the other levels' SVs, so the computation of an AUC and therefore the quantification of the participant's ED behaviour is still possible.
+If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
 Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
@@
 In the present study, we will validate the CERED paradigm by conceptually replicating the ED and NFC findings of Westbrook et al. [-@Westbrook2013].
-Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task.
-The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load in the form of increasing n-back levels or decreasing intensity of auditory signals.
+Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task, the full results of which will be published in a second Registered Report.
+The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for emotion regulation.
 
@@
 Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
-Regarding the associations of subjective and objective task load measures we hypothesized that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
+Regarding the associations of subjective and objective task load we hypothesized that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
 Regarding the associations of task load and ED we hypothesized that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
 And regarding individual differences in ED we hypothesized that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-However, we propose that (3c) when taking individual preferences for different n-back levels into account, the prediction of NFC scores by SVs can be improved significantly.
 
@@
 
+The paradigm was written and presented using Psychopy [@Peirce2019].
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
@@
 The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
+Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
 A full list of questionnaires and measures can be found in Appendix 1.
+
+```{r import_image, out.width="50%", warning=FALSE}
+
+  knitr::include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
+
+```
 
@@
 Therefore, we multiplied both indicators to arrive at a value reflecting both degree and direction of preference, called $AxAUC$.
+
+##Power analysis
+A sample size analysis with GPower [@Faul2007; @Faul2009], using the RT data from the n-back task, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.
 

### 2021-11-23 06_Paper/COG-ED/Manuscript.Rmd
changed tense and shortened text

@@
 One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
-Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959]; and are asked to respond as quickly and as accurately as possible.
+Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
 The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
-However, reliability measures of the n-back task are mixed, presumably due to ceiling effects in performance in the easiest level [@Jaeggi2010].
+However, its reliability measures are mixed, presumably due to ceiling effects in performance in the easiest level [@Jaeggi2010].
 Additionally, associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
@@
 If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if the choose 1-back, it decreases by 0.50\$.
-This is repeated five more times, with each adjustment of the 1-back reward being half as big as in the previous step, while the reward for the more difficult level remains fixed at 2\$.
-The idea is to estimate the point of subjective equivalence, i.e. the monetary ratio in which both offers are equally preferred [@Westbrook2013]. 
+This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
+The idea is to estimate the point of subjective equivalence, i.e. the monetary ratio at which both offers are equally preferred [@Westbrook2013]. 
 The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
@@
 The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
-We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level (i.e., 1-back).
+We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
 Figure 1 illustrates how different modifications of the COG-ED paradigm by Westbrook et al.
-[-@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back the most, 3-back less, and 1-back the least.
+[-@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
 The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
@@
 First, the SVs are still distorted by the non-true SVs returned by the original paradigm, and second, including more task levels would lead to an exponential growth of necessary comparisons.
-Therefore, the solution lies in reducing the number of necessary comparisons by presenting an ED round for each possible pair of levels, and by starting each ED round with a choice between equal prices.
+Therefore, the solution lies in reducing the number of necessary comparisons by presenting an ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
 For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
-The n-back level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
-The n-back level that was not chosen will be set to a fixed value of 2€.
+The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
+The level that was not chosen will be set to a fixed value of 2€.
 This procedure allows to compute SVs based on actual individual preference instead of objective task load.
@@
 In the present study, we will validate the CERED paradigm by conceptually replicating the ED and NFC findings of Westbrook et al. [-@Westbrook2013].
-Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task, the full results of which will be published in a second Registered Report.
+Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task, the full results of the latter will be published in a second Registered Report.
 The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for emotion regulation.
@@
 The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
+Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
 A full list of questionnaires and measures can be found in Appendix 1.
@@
 ## Procedure
-Participants for the pilot study were recruited using the software *ORSEE* [@Greiner2015].
-The final sample consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
-Each participant completed two sessions in the lab one week apart, and a battery of personality questionnaires two days after the second session.
-In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
-The paradigm started with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
-After each level, participants filled out the NASA-TLX on a tablet to provide a state measure of cognitive effort.
-Then, they completed the ED procedure on screen, where each possible pairing of the four n-back levels was presented in a randomized order.
-Participants were instructed to decide as realistically as possible, because one of their choices from the last iteration steps would be randomly chosen for one final run of n-back.
-The level and its monetary value were presented on screen and participants completed one run, but this was only to incentivise truthful behavior in the ED procedure, so the n-back data of this part was not analyzed.
-The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm followed the same structure of task and ED procedure, but the emotion regulation strategy at the end was not randomly chosen, instead participants could decide which strategy they wanted to use again.
-There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
-Two days after the second session, participants received a link to the NFC scale and other personality questionnaires to provide a trait measure of preference for cognitive effort.
-Participants received 30€ in total or course credit for participation.
-Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015].
+Each participant fills out the personality questionnaires online and then visit the lab for two sessions one week apart.
+In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
+The paradigm starts with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
+After each level, participants fill out the NASA-TLX on a tablet to provide a state measure of cognitive effort.
+Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
+Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back.
+This is done to incentivise truthful behavior in the ED procedure, the n-back data of this part is not analyzed.
+The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
+The paradigm follows the same structure of task and ED procedure, but the emotion regulation strategy at the end is not randomly chosen, instead participants can decide which strategy they want to use again.
+Participants receive 30€ in total or course credit for participation.
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
 
 ## Analysis
-We aimed to conduct all analysis as described in Westbrook et al.
-[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom in the statistical procedures.
-The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
-Reaction time (RT) data was trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes could not have been completed before [@Whelan2008; @Berger2021].
-Error- and post-error trials were excluded, because RT on the latter trials is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-Declining performance was investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+We aim to conduct all analysis as described in Westbrook et al.
+[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom.
+The performance measure *d'* is computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
+Reaction time (RT) data is trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes cannot be completed before [@Whelan2008; @Berger2021].
+Error- and post-error trials are excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+Declining performance is investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
 Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
-To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
-Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
-A rmANOVA with six paired contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
-Tukey method was used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
-
-To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
+To investigate changes in NASA-TLX ratings, six rmANOVAs are computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
+The SVs are calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
+Then, the final monetary values are divided by 2€, and the SV of each level per participant is computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
+A rmANOVA with six paired contrasts is computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
+Tukey method is used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
+
+To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
 **MLM explanation goes here**
-To ensure the validity of the multi-level model, we conducted a specification curve analysis [@Simonsohn2020], which included 92 possible preprocessing pipelines of the RT data.
-These pipelines specified which transformation has been applied (none, log, inverse, or square-root), which outliers have been excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials have been excluded or not, and across which dimensions the transformations and exclusions have been applied (across/within subjects and across/within n-back levels).
-The multi-level model was run with each of the 92 pipelines, which also included our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials, no decision regarding dimension necessary).
-The ratio of pipelines that lead to significant versus non-significant effects provides and indication of how robust the effect actually is.
-
-The association of ED and NFC was examined with a regression using the AUC of each participant's SVs to predict their NFC score.
-A second regression additionally included the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
-Since we did not have a fixed SV of 1 for 1-back, we could not apply the 'AUC' computation of Westbrook et al.
+To ensure the validity of the multi-level model, we conduct a specification curve analysis [@Simonsohn2020], which includes 92 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation has been applied (none, log, inverse, or square-root), which outliers have been excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials have been excluded or not, and across which dimensions the transformations and exclusions have been applied (across/within subjects and across/within n-back levels).
+The multi-level model will be run with each of the 92 pipelines, which also includes our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials).
+The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.
+
+The association of ED and NFC is examined with a regression using the AUC of each participant's SVs to predict their NFC score.
+A second regression additionally includes the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
+Since we do not have a fixed SV of 1 for 1-back, we cannot apply the 'AUC' computation of Westbrook et al.
 [-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
@@
 This is the opposite for the sum of the ascent between SVs.
-Therefore, we multiplied both indicators to arrive at a value reflecting both degree and direction of preference, called $AxAUC$.
+Therefore, we multiply both indicators to arrive at a value reflecting both degree and direction of preference, called $AxAUC$.
 
 ##Power analysis
-A sample size analysis with GPower [@Faul2007; @Faul2009], using the RT data from the n-back task, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.
+A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.
 

### 2021-11-24 06_Paper/COG-ED/Manuscript.Rmd
reduced word count to 2713

@@
 The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
-However, its reliability measures are mixed, presumably due to ceiling effects in performance in the easiest level [@Jaeggi2010].
-Additionally, associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
+However, its reliability measures are mixed, and associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
 
@@
 [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
-Westbrook et al.
-[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure of ED.
+Westbrook et al. [-@Westbrook2013] conceptualized NFC as a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure.
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
-However, the relation of NFC and SVs might be confounded with task performance itself, since subjective task values have been shown to depend on both the exerted effort [@Wang2017] and the expected performance [@Yee2021].
-Findings on NFC and n-back performance are heterogeneous, ranging from no association of NFC and working memory [@Fleischhauer 2010; @Gaertner2021; @Hill2013] to positive associations of NFC with attention allocation [@Enge2008] and brain flexibility [@He2019].
-Nevertheless, a possible association of NFC and task performance might be secondary, since task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019].
-But since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021], more research is needed to shed light on this issue.
+However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
+On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.
 
 ## Revising the COG-ED paradigm
-The present study contributes to the investigation of effort and SVs by changing one fundamental assumption of the original COG-ED paradigm: The assumption that the easiest n-back level has the highest SV.
+The present study changes one fundamental assumption of the original COG-ED paradigm: That the easiest n-back level has the highest SV.
 We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
-Figure 1 illustrates how different modifications of the COG-ED paradigm by Westbrook et al.
-[-@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
+Figure 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
 The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
@@
 Adding three ED rounds comparing the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
-First, the SVs are still distorted by the non-true SVs returned by the original paradigm, and second, including more task levels would lead to an exponential growth of necessary comparisons.
-Therefore, the solution lies in reducing the number of necessary comparisons by presenting an ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
+First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
+Therefore, the solution lies in reducing the number of comparisons by presenting an ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
 For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
@@
 emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
-In the present study, we will validate the CERED paradigm by conceptually replicating the ED and NFC findings of Westbrook et al. [-@Westbrook2013].
+In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
 Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task, the full results of the latter will be published in a second Registered Report.
@@
 ## Questionnaires
-To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988].
-In the NASA-TLX, participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-Need for Cognition will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
-Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
-The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
+To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
+NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
+The NFC scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
 Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
-A full list of questionnaires and measures can be found in Appendix 1.
+A full list of measures can be found at osf.io/vnj8x/.
 
@@
 Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015].
-Each participant fills out the personality questionnaires online and then visit the lab for two sessions one week apart.
+Participants fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
 In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
@@
 The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
-After each level, participants fill out the NASA-TLX on a tablet to provide a state measure of cognitive effort.
+After each level, participants fill out the NASA-TLX on a tablet.
 Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
@@
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm follows the same structure of task and ED procedure, but the emotion regulation strategy at the end is not randomly chosen, instead participants can decide which strategy they want to use again.
+The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
 Participants receive 30€ in total or course credit for participation.
@@
 We aim to conduct all analysis as described in Westbrook et al.
-[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom.
+[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
 The performance measure *d'* is computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
@@
 To investigate changes in NASA-TLX ratings, six rmANOVAs are computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-The SVs are calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
-Then, the final monetary values are divided by 2€, and the SV of each level per participant is computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
+For each ED round, SVs are calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
+Then, the final monetary values are divided by 2€, and the SV of each level per participant is computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
 A rmANOVA with six paired contrasts is computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
@@
 To ensure the validity of the multi-level model, we conduct a specification curve analysis [@Simonsohn2020], which includes 92 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation has been applied (none, log, inverse, or square-root), which outliers have been excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials have been excluded or not, and across which dimensions the transformations and exclusions have been applied (across/within subjects and across/within n-back levels).
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
 The multi-level model will be run with each of the 92 pipelines, which also includes our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials).
@@
 [-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
-Consequently, we decided on a different way of quantifying the individual degree of ED.
+Consequently, we chose a different way of quantifying the individual degree of ED.
 A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back, but can reflect the overall willingness to exert effort.
 This is the opposite for the sum of the ascent between SVs.
-Therefore, we multiply both indicators to arrive at a value reflecting both degree and direction of preference, called $AxAUC$.
+Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.
 
@@
 ### Associations of subjective and objective task load measures
-We first looked at how performance measures and NASA-TLX ratings change as n-back levels increase.
 Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).
@@
 
-As expected, RT increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
-RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not significantly different between 2- and 4-back or 3- and 4-back.
-Even though *d'* did not decrease across n-back levels in this very small sample, the increases in RT indicate an increase in objective task load.
+However, RT increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
+RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not different between 2- and 4-back or 3- and 4-back.
+Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.
 
@@
 Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
-Overall, these ratings showed that the increase in objective task load was also being subjectively perceived by the participants.
+Overall, these ratings showed that the increase in task load was being perceived as such.
 
@@
 ### Changes in subjective values depending on n-back level
-While the rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`), paired contrasts indicated that this was not the case for every pair of n-back levels.
-SVs were higher for 1- than for 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than for 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than for 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
-Since the SVs of 1- and 2-back were not significantly different, we can conclude that when given the choice, not all participants preferred the easiest n-back level.
+The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
+SVs were higher for 1- than 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
+The lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
 

### 2021-11-24 06_Paper/ER-ED/method.Rmd
added paragraph
added text to 2.5 electromyography

@@
 
-Bipolar electromyography (EMG) was recorded in the region of the *corrugator supercilii* and the *levator labii* at 1000 Hz sampling rate using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
-Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel were used. <!-- Stimmt das in etwa, liebe Anne? -->
+Two bipolar electromyograph (EMG) measures were recorded in the region of the *corrugator supercilii* and the *levator labii* using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
+Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel were used. 
+Data were sampled at 1000 Hz.
+To measure *corrugator EMG*, electrodes were applied to the abraded and cleaned skin on the left corrugator, and to measure *levator EMG*, electrodes were applied in the region of the *levator labii*.
+The ground electrod were placed at the left *Mastoid*.
+A 10 Hz high pass and a 500 Hz low pass filter were applied to both signals. <!-- liebe Anne, habe das hier von Ray et al 2010 übernommen. Stimmt das für unsere Auswertung? -->
+Afterwards, the signals were rectified.
 [...] <!-- @Anne please check! =) -->
@@
 Greenhouse-Geisser-corrected *p*-values and degrees of freedom were reported when assumption of sphericity was violated.
-Proportion of explained variance *\eta²~p~* was reported as a measure of effect size
+Proportion of explained variance *$\eta$²~p~* was reported as a measure of effect size.
+
+*Subjective values of emotion regulation strategies* <br>

### 2021-11-24 06_Paper/ER-ED/method.Rmd
Added Comment for Anne
added text

@@
 Afterwards, the signals were rectified.
-[...] <!-- @Anne please check! =) -->
+[...] <!-- @Anne hier fehlt noch einiges, bitte dann nach deiner Auswertung ergänzen =) -->
 
@@
 *Effects of emotion regulation on arousal and effort* <br>
-To examine impact of valence of emotional pictures on subjective arousal, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for behavioral data (subjective arousal ratings).
-To investigate the effect of the tree ER strategies on subjective arousal, another ANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
-To examine the impact of valence on the emotional facial reaction, an ANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
+To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing was conducted for behavioral data (subjective arousal ratings).
+To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
+To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
 <!-- @Anne please check!
 =) -->
-A further ANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
+A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
 <!-- @Anne please check!
 =) -->
-To examine the effect of ER strategies on cognitive effort, an ANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
+To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
 Greenhouse-Geisser-corrected *p*-values and degrees of freedom were reported when assumption of sphericity was violated.
@@
 *Subjective values of emotion regulation strategies* <br>
+For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, the resulting (monetary) value was divided by 2.00 €.
+The resulting values were entered in a rmANOVA

### 2021-11-25 06_Paper/COG-ED/Manuscript.Rmd
added sentence to intro

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  Every day, individuals have to weigh the value of the reward when reaching a goal against the required effort.
+  However, effort is not inherently aversive to all individuals, which has often been neglected by previous approaches to quantify the subjective value of effort.
+  One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
+  We argue that adapting the paradigm and the method of computing the willingness to exert effort allows two crucial things: Quantifying subjective values without assuming that the easiest level is preferred, and quantifying subjective values for tasks with no objective order of task load.
+  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).
 
@@
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
+Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; Xu2021].
 However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].

### 2021-11-26 06_Paper/COG-ED/Manuscript.Rmd
adapted formalities and added some sentences

@@
 ---
-title             : "When easy is not preferred: A paradigm for estimating subjective values of cognitive tasks"
-
+title             : "When easy is not preferred: The Cognitive and Emotion Regulation Effort Discounting paradigm (CERED) for estimating subjective values of cognitive tasks"
+shorttitle        : "The CERED paradigm for estimating subjective values"
 author: 
@@
       - Writing - review & editing
-
 affiliation:
   - id            : "1"
-    institution   : "Faculty of Psychology, Technische Universität Dresden"
-  - id            : "*"
-    note          : "Shared first authorship"
-
+    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
+authornote: |
+  * Shared first authorship
 abstract: |
@@
   One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
+  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).
+  The CERED paradigm will likely enable a more insightful investigation of interindividual differences in effort discounting, as well as the investigation of effort discounting for task types for which this is currently not possible due to their high degree of subjectivity.
+
   We argue that adapting the paradigm and the method of computing the willingness to exert effort allows two crucial things: Quantifying subjective values without assuming that the easiest level is preferred, and quantifying subjective values for tasks with no objective order of task load.
-  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).
-
 keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
 wordcount         : "X"
-
 bibliography      : ref_COG-ED.bib
-
 floatsintext      : no
@@
 draft             : no
-
 documentclass     : "apa6"
@@
 output            : papaja::apa6_pdf
-
 csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
-
 header-includes   :
@@
     - \usepackage{xcolor}
+    - \usepackage{setspace}\doublespacing
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 ```
-
-# Introduction
-
-In everyday life, effort and reward are closely intertwined [@Botvinick2009].
-With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
-A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
-However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
-Investigating effort and cost is challenging because “effort is not a property of the target task alone, but also a function of the individual’s cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual’s reward sensitivity” [@Kool2018, p.
-209].
-
-One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
-Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
-The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
-However, its reliability measures are mixed, and associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
-
-A way to quantify the subjective cost of each n-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
-First, the participants complete the n-back levels to familiarize themselves with the task.
-Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
-If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if the choose 1-back, it decreases by 0.50\$.
-This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
-The idea is to estimate the point of subjective equivalence, i.e. the monetary ratio at which both offers are equally preferred [@Westbrook2013]. 
-The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
-Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting (ED).
-Younger participants showed lower ED, i.e. they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
-
-## Effort discounting and Need for Cognition 
-The individual degree of ED in the study by Westbrook et al.
-[-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
-Westbrook et al. [-@Westbrook2013] conceptualized NFC as a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure.
-On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
-Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; Xu2021].
-However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
-On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.
-
-## Revising the COG-ED paradigm
-The present study changes one fundamental assumption of the original COG-ED paradigm: That the easiest n-back level has the highest SV.
-We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
-Figure 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
-The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
-Adding an ED round comparing 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
-Adding three ED rounds comparing the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
-First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
-Therefore, the solution lies in reducing the number of comparisons by presenting an ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
-For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
-The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
-The level that was not chosen will be set to a fixed value of 2€.
-This procedure allows to compute SVs based on actual individual preference instead of objective task load.
-Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
-If the participant has a clear preference for one level, this level's SV will be 1.
-If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
-Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
-emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
-In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
-Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task, the full results of the latter will be published in a second Registered Report.
-The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for emotion regulation.
-
-## Hypotheses
-Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
-Regarding the associations of subjective and objective task load we hypothesized that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
-Regarding the associations of task load and ED we hypothesized that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
-And regarding individual differences in ED we hypothesized that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
 
@@
 ```
+
+# Introduction
+
+In everyday life, effort and reward are closely intertwined [@Botvinick2009].
+With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
+A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
+However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
+Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" [@Kool2018, p.
+209].
+
+One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
+Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
+The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
+However, its reliability measures are mixed, and associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
+
+A way to quantify the subjective cost of each n-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+First, the participants complete the n-back levels to familiarize themselves with the task.
+Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
+If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if the choose 1-back, it decreases by 0.50\$.
+This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
+The idea is to estimate the point of subjective equivalence, i.e. the monetary ratio at which both offers are equally preferred [@Westbrook2013].
+The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
+Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting (ED).
+Younger participants showed lower ED, i.e. they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
+
+## Effort discounting and Need for Cognition
+
+The individual degree of ED in the study by Westbrook et al.
+[-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
+Westbrook et al.
+[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure of ED.
+On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
+Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; Xu2021].
+However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
+On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.
+
+## Revising the COG-ED paradigm
+
+The present study changes one fundamental assumption of the original COG-ED paradigm: That the easiest n-back level has the highest SV.
+We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
+Figure 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
+The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
+Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
+Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
+First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
+Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
+For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
+The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
+The level that was not chosen will be set to a fixed value of 2€.
+This procedure allows to compute SVs based on actual individual preference instead of objective task load.
+Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
+If the participant has a clear preference for one level, this level's SV will be 1.
+If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
+Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
+emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
+In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al.
+[-@Westbrook2013].
+Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task.
+The full results of the latter will be published in a second Registered Report.
+The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for emotion regulation.
+
+*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
+
+## Hypotheses
+
+Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
+Regarding the associations of subjective and objective task load we hypothesize that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
+Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
+And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
 
@@
 
-The paradigm was written and presented using Psychopy [@Peirce2019].
+The paradigm was written and presented using *Psychopy* [@Peirce2019].
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
@@
 ## Questionnaires
+
 To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
@@
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
-The NFC scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
+The NFC scale shows comparably high internal consistency [Cronbach's $\alpha$ \> .80; @Bless1994; @Fleischhauer2010].
 Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
@@
 
-```{r import_image, out.width="50%", warning=FALSE}
-
-  knitr::include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
-
-```
-
 ## Procedure
+
 Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015].
-Participants fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
+Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
 In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
@@
 Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back.
-This is done to incentivise truthful behavior in the ED procedure, the n-back data of this part is not analyzed.
+This is only done to incentivise truthful behavior in the ED procedure, so the n-back data of this part will not be analyzed.
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
 The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
-Participants receive 30€ in total or course credit for participation.
+Participants will receive 30€ in total or course credit for participation.
 Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
 The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
+In the pilot study, the online questionnaires were completed after the two lab sessions, but we will change this as described above, so that the participants do not have to come in again to collect their money or course credit.
 
 ## Analysis
+
 We aim to conduct all analysis as described in Westbrook et al.
 [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
-The performance measure *d'* is computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
-Reaction time (RT) data is trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes cannot be completed before [@Whelan2008; @Berger2021].
-Error- and post-error trials are excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-Declining performance is investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
-Another rmANOVA with three paired contrasts was computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
-To investigate changes in NASA-TLX ratings, six rmANOVAs are computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each ED round, SVs are calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
-Then, the final monetary values are divided by 2€, and the SV of each level per participant is computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
-A rmANOVA with six paired contrasts is computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
-Tukey method is used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
+The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
+Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
+Error- and post-error trials will be excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+Declining performance will be investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
+To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
+For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
+Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
+A rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
+Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
 
 To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
-**MLM explanation goes here**
-To ensure the validity of the multi-level model, we conduct a specification curve analysis [@Simonsohn2020], which includes 92 possible preprocessing pipelines of the RT data.
+**MLM explanation goes here** To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
 These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
-The multi-level model will be run with each of the 92 pipelines, which also includes our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials).
-The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.
-
-The association of ED and NFC is examined with a regression using the AUC of each participant's SVs to predict their NFC score.
-A second regression additionally includes the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
-Since we do not have a fixed SV of 1 for 1-back, we cannot apply the 'AUC' computation of Westbrook et al.
+The multi-level model will be run with each of the 92 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials).
+The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
+
+The association of ED and NFC will be examined with a regression using the AUC of each participant's SVs to predict their NFC score.
+A second regression will additionally include the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
+Since we do not have a fixed SV of 1 for 1-back, we cannot apply the "AUC" computation of Westbrook et al.
 [-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
 Consequently, we chose a different way of quantifying the individual degree of ED.
-A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back, but can reflect the overall willingness to exert effort.
+A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.
 This is the opposite for the sum of the ascent between SVs.
@@
 
-##Power analysis
+## Power analysis
+
 A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.
@@
 ### Associations of subjective and objective task load measures
+
 Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).
@@
 
-However, RT increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
+However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
 RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not different between 2- and 4-back or 3- and 4-back.
@@
 Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
-Ratings on the physical load and the performance subscales only increased between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
+Ratings on the physical load and the performance subscales only increased between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r`apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and`r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
 Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
@@
 ### Changes in subjective values depending on n-back level
+
 The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
 SVs were higher for 1- than 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
-The lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
+Importantly, the lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
+This can be considered preliminary proof-of-concept, as this behavioural pattern can only emerge in the CERED paradigm, but not in the original COG-ED paradigm.
 
@@
 When including the AUC of all NASA-TLX subscales as a predictor, it could explain variance in NFC beyond the one (not) explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
-An increase in one NASA_NTLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).
+An increase in one NASA-TLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).
+
+\newpage
+
+# Acknowledgements
+
+# References
+
+```{=tex}
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
+
+\endgroup

### 2021-12-01 06_Paper/ER-ED/method.Rmd
added rmANOVA description of SVs
added choice data frame

@@
                            LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
+data_choice = data.frame(ID = character(), choice = double())
 
@@
 
+}
+
+# store ER choice in data_choice frame
+
+for (i in 1:length(datalist_ER)) {
+  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["resp_choice.keys"]])
+  colnames(tmp) = names(data_choice)
+  tmp = tmp[(!is.na(tmp$choice)),]
+
+  data_choice = rbind(tmp, data_choice)
 }
@@
 Second, the resulting (monetary) value was divided by 2.00 €.
-The resulting values were entered in a rmANOVA
+The resulting values were entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression).

### 2021-12-02 06_Paper/ER-ED/method.Rmd

@@
 # lists contain arousal and valence values of each picture
-stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))
+stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))
 
-stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","neutral.xlsx")), range = cell_rows(1:21))
+stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
 ```
@@
 
-  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["instr_1"]],datalist_ER[[i]][["slider_arousal.response"]],datalist_ER[[i]][["slider_effort.response"]])
+  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["instr_1"]], datalist_ER[[i]][["slider_arousal.response"]], datalist_ER[[i]][["slider_effort.response"]])
   colnames(tmp) = names(data_ER)
-  tmp = tmp[(!is.na(tmp$arousal)),]
+  tmp = tmp[(!is.na(tmp$arousal)), ]
 
@@
 for (i in 1:length(datalist_ER)) {
-  tmp = data.frame(datalist_ER[[i]][["participant"]],datalist_ER[[i]][["resp_choice.keys"]])
+  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["resp_choice.keys"]])
   colnames(tmp) = names(data_choice)
-  tmp = tmp[(!is.na(tmp$choice)),]
+  tmp = tmp[(!is.na(tmp$choice)), ]
 

### 2021-12-02 06_Paper/COG-ED/Manuscript.Rmd

@@
   # we will add the package versions before submission
-  # we also have the word count add-in by Ben Marwick, which can be installed via
-  # devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
 
@@
 
-  # remove trials with RT < 200 ms from the n-back data and exclude trials after incorrect trials
-  data_RT <- data_nback[-c(which(data_nback$rt < 0.2)), ]
+  # remove trials with RT < 100 ms from the n-back data and exclude trials after incorrect trials
+  data_RT <- data_nback[-c(which(data_nback$rt < 0.1)), ]
   data_RT <- data_RT[-c(which(data_RT$correct == 0) + 1), ]
@@
   #   (3) 3 SDs from the mean
-  #   (T) 0-200 ms after stimulus onset
+  #   (T) 0-100 ms after stimulus onset
   # Post-error trials:
@@
 
-          # compute mean and standard deviation
-
-          pipemean <- mean(pipelines_data[[i]]$rt, na.rm = TRUE)
-          pipesd <- sd(pipelines_data[[i]]$rt, na.rm = TRUE)
+          # compute median and median absolute deviation
+
+          pipemedian <- median(pipelines_data[[i]]$rt, na.rm = TRUE)
+          pipemad <- mad(pipelines_data[[i]]$rt, na.rm = TRUE)
 
@@
 
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemean + 2 * pipesd)
-                                                               & pipelines_data[[i]]$rt > (pipemean - 2 * pipesd))), ]
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 2 * pipemad)
+                                                               & pipelines_data[[i]]$rt > (pipemedian - 2 * pipemad))), ]
 
@@
 
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemean + 3 * pipesd)
-                                                               & pipelines_data[[i]]$rt > (pipemean - 3 * pipesd))), ]
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 3 * pipemad)
+                                                               & pipelines_data[[i]]$rt > (pipemedian - 3 * pipemad))), ]
           }
@@
 
-            # compute mean and standard deviation
-
-            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
-            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
+            # compute median and median absolute deviation
+
+            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
+            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
 
@@
               ifelse(length(which(pipelines_data[[i]]$level == x &
-                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
+                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
                        pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
-                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
+                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                      pipelines_data[[i]] <- pipelines_data[[i]])
@@
               ifelse(length(which(pipelines_data[[i]]$level == x &
-                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
+                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
                        pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
-                                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
+                                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                      pipelines_data[[i]] <- pipelines_data[[i]])
@@
 
-            # compute mean and standard deviation
-
-            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
-            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            # compute median and median absolute deviation
+
+            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
 
@@
               ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
-                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
+                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
                        pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
-                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
+                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                      pipelines_data[[i]] <- pipelines_data[[i]])
@@
               ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
-                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
+                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
                        pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
-                                                      (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
+                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                      pipelines_data[[i]] <- pipelines_data[[i]])
@@
 
-            # compute mean and standard deviation
-
-            pipemean <- mean(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
-            pipesd <- sd(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            # compute median and median absolute deviation
+
+            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
 
@@
               ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
-                                    (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))) > 0,
+                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
                        pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
-                                                      (pipelines_data[[i]]$rt > (pipemean + 2 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 2 * pipesd)))), ],
+                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                      pipelines_data[[i]] <- pipelines_data[[i]])
@@
               ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
-                                    (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))) > 0,
+                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
                        pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
-                                                      (pipelines_data[[i]]$rt > (pipemean + 3 * pipesd) | pipelines_data[[i]]$rt < (pipemean - 3 * pipesd)))), ],
+                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                      pipelines_data[[i]] <- pipelines_data[[i]])
@@
 
-    # the 200-ms-exclusion and the post-error-exclusion are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:
-
-    # exclude RTs fast than 200 ms after stimulus onset if the fourth letter in the data frame name is a "T"
+    # the 100-ms-exclusion and the post-error-exclusion are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:
+
+    # exclude RTs fast than 100 ms after stimulus onset if the fourth letter in the data frame name is a "T"
 
@@
 
-      pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]
+      pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]
 
@@
 The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
-Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 200 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
+Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
 Error- and post-error trials will be excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
@@
 **MLM explanation goes here** To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 200 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
-The multi-level model will be run with each of the 92 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 200 ms, removal of post-error trials).
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 100 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
+The multi-level model will be run with each of the 92 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms, removal of post-error trials).
 The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

### 2021-12-02 06_Paper/COG-ED/Manuscript.Rmd
corrected exclusion of 100ms trials

@@
     # exclude RTs fast than 100 ms after stimulus onset if the fourth letter in the data frame name is a "T"
+    # also making sure that there are even any trials below 100 ms, otherwise you get an error message
 
@@
 
-      pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]
-
+      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]) > 0,
+             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ],
+             pipelines_data[[i]] <- pipelines_data[[i]])
     }

### 2021-12-02 06_Paper/ER-ED/method.Rmd
added library ggplot

@@
 library(papaja) # APA conform output
+library(ggplot2)
 

### 2021-12-02 06_Paper/ER-ED/method.Rmd
added libraries

--- 2021-12-02 06_Paper/ER-ED/method.Rmd
@@
 library(papaja)     # APA conform output
+library(afex)       # for ANOVA
+library(ggplot2)    # for nice plots
 

### 2021-12-02 06_Paper/ER-ED/method.Rmd
added ANOVA for subjective arousal

--- 2021-12-02 06_Paper/ER-ED/method.Rmd
@@
 library(papaja)     # APA conform output
+library(afex)       # for ANOVA
+library(emmeans)
+library(ggplot2)    # for nice plots
 
@@
 The resulting values were entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression).
+
+```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
+
+# ANOVA subjective arousal ratings
+
+aov.arousal = afex::aov_ez(id = "ID",    #ATTENTION: needs pagacke "afex"
+                      dv = "arousal",
+                      data = data_ER,
+                      within = "block",
+                      fun_aggregate = mean) 
+afex::nice(aov.arousal, es = "pes")
+
+# compute posthoc tests for both within measures
+posthoc_test_strategy = emmeans::emmeans(aov.arousal$aov, specs = "block")
+pairs(posthoc_test_strategy, adjust = "bonferroni")
+```

### 2021-12-03 06_Paper/ER-ED/method.Rmd
added ANOVA for effort

@@
 
-aov.arousal = afex::aov_ez(id = "ID",    #ATTENTION: needs pagacke "afex"
+aov.arousal = afex::aov_ez(id = "ID",
                            dv = "arousal",
@@
 
-# compute posthoc tests for both within measures
-posthoc_test_strategy = emmeans::emmeans(aov.arousal$aov, specs = "block")
-pairs(posthoc_test_strategy, adjust = "bonferroni")
+# compute posthoc tests for within measures
+posthoc_arousal = emmeans::emmeans(aov.arousal$aov, specs = "block")
+pairs(posthoc_arousal, adjust = "bonferroni")
+
+# ANOVA subjective effort ratings
+
+aov.effort = afex::aov_ez(id = "ID",
+                          dv = "effort",
+                          data = data_ER,
+                          within = "block",
+                          fun_aggregate = mean)
+
+# compute posthoc tests for within measure
+posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
+pairs(posthoc_effort, adjust = "bonferroni")
 ```

### 2021-12-03 06_Paper/ER-ED/method.Rmd
added ANOVA output
corrected data structures

@@
 
-  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["instr_1"]], datalist_ER[[i]][["slider_arousal.response"]], datalist_ER[[i]][["slider_effort.response"]])
+  tmp = data.frame(datalist_ER[[i]][["participant"]], 
+                   datalist_ER[[i]][["instr_1"]], 
+                   datalist_ER[[i]][["slider_arousal.response"]], 
+                   datalist_ER[[i]][["slider_effort.response"]],
+                   datalist_ER[[i]][["TriggerBlockView"]],
+                   datalist_ER[[i]][["TriggerBlockReg"]])
   colnames(tmp) = names(data_ER)
@@
 ```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
+## Subjective arousal
 
@@
 
+# Figure to visualize arousal ratings
+
+#ggplot2::ggplot
+
+## Subjective effort
+
 # ANOVA subjective effort ratings
@@
                           fun_aggregate = mean)
+afex::nice(aov.effort, es = "pes")
 

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added loop

@@
 # new empty frame to store files into
-data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double())
+data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double(), trigger_view = double(), trigger_reg = double())
 
@@
   data_choice = rbind(tmp, data_choice)
+}
+
+# loop to correct block indicator
+
+for (i in 1:nrow(data_ER)) {
+
+  if (data_ER$trigger_view[i] == 21 & is.na(data_ER$trigger_reg[i])) {
+
+    data_ER$block[i] = "view_neu"
+
+  } else if (data_ER$trigger_view[i] == 22 & is.na(data_ER$trigger_reg[i])) {
+
+    data_ER$block[i] = "view_neg"
+
+  } else if (is.na(data_ER$trigger_view[i]) & data_ER$trigger_reg[i] == 23) {
+
+    data_ER$block[i] = "distraction"
+
+  } else if (is.na(data_ER$trigger_view[i]) & data_ER$trigger_reg[i] == 24) {
+
+    data_ER$block[i] = "distancing"
+
+  } else if (is.na(data_ER$trigger_view[i]) & data_ER$trigger_reg[i] == 25) {
+
+    data_ER$block[i] = "suppression"
+
+  } else if (is.na(data_ER$trigger_view[i]) & is.na(data_ER$trigger_reg[i])) {
+
+    data_ER$block[i] = "choice"
+  }
 }

### 2021-12-06 06_Paper/ER-ED/method.Rmd
corrected loop

--- 2021-12-03 06_Paper/ER-ED/method.Rmd
@@
 # new empty frame to store files into
-data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double())
+data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double(), trigger = double(), trigger_reg = double())
 
@@
 
+}
+
+rownames(data_ER) = 1:nrow(data_ER)
+
+# loop to store trigger in one column
+
+for (i in 1:nrow(data_ER)) {
+  if (is.na(data_ER$trigger[i])) {
+    data_ER$trigger[i] = data_ER$trigger_reg[i]
+  }
+
+  if (is.na(data_ER$trigger[i])) {
+    data_ER$trigger[i] = 26
+  }
+}
+
+# delete old column
+
+data_ER$trigger_reg = NULL
+
+# loop to correct block indicator
+
+for (i in 1:nrow(data_ER)) {
+
+  if (data_ER$trigger[i] == 21) {
+
+    data_ER$block[i] = "view_neu"
+
+  } else if (data_ER$trigger[i] == 22) {
+
+    data_ER$block[i] = "view_neg"
+
+  } else if (data_ER$trigger[i] == 23 ) {
+
+    data_ER$block[i] = "distraction"
+
+  } else if (data_ER$trigger[i] == 24 ) {
+
+    data_ER$block[i] = "distancing"
+
+  } else if (data_ER$trigge[i] == 25 ) {
+
+    data_ER$block[i] = "suppression"
+
+  } else if (data_ER$trigger[i] == 25) {
+
+    data_ER$block[i] = "choice"
+  }
 }

### 2021-12-06 06_Paper/ER-ED/method.Rmd
corrected ANOVA

@@
 library(ggplot2)    # for nice plots
+library(dplyr)
 
@@
 
-  } else if (data_ER$trigger[i] == 25) {
+  } else if (data_ER$trigger[i] == 26) {
 
@@
 # ANOVA subjective arousal ratings
+# View Condition
 
-aov.arousal = afex::aov_ez(id = "ID",
+arousal_view = data_ER %>%
+  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
+
+aov_arousalView = afex::aov_ez(id = "ID",
                            dv = "arousal",
-                           data = data_ER,
+                           data = arousal_view,
                            within = "block",
                            fun_aggregate = mean) 
-afex::nice(aov.arousal, es = "pes")
+afex::nice(aov_arousalView, es = "pes")
 
 # compute posthoc tests for within measures
-posthoc_arousal = emmeans::emmeans(aov.arousal$aov, specs = "block")
-pairs(posthoc_arousal, adjust = "bonferroni")
+posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
+pairs(posthoc_arousalView, adjust = "bonferroni")
 

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added ANOVAS vor arousal and effort

@@
 # ANOVA subjective arousal ratings
-# View Condition
+# View condition
 
@@
 
+# View neg and regulate conditions
+
+arousal_Reg = data_ER %>%
+  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+
+aov_arousalReg = afex::aov_ez(id = "ID",
+                              dv = "arousal",
+                              data = arousal_Reg,
+                              within = "block",
+                              fun_aggregate = mean)
+afex::nice(aov_arousalReg, es = "pes")
+
+# compute posthoc tests for within measures
+posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
+pairs(posthoc_arousalReg, adjust = "bonferroni")
+
 ## Subjective effort
@@
 
+effort_Reg = data_ER %>%
+  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+
 aov.effort = afex::aov_ez(id = "ID",
                           dv = "effort",
-                          data = data_ER,
+                          data = effort_Reg,
                           within = "block",

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added figure arousal view
added graphics

@@
 
-#ggplot2::ggplot
+# figure
+ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neu", "view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Arousal Rating")
 
@@
 
-arousal_Reg = data_ER %>%
+arousal_reg = data_ER %>%
   subset(data_ER$block != "view_neu" & data_ER$block != "choice")
@@
                               dv = "arousal",
-                              data = arousal_Reg,
+                              data = arousal_reg,
                               within = "block",
@@
 pairs(posthoc_arousalReg, adjust = "bonferroni")
+
+# Figure to visualize arousal ratings
+
+# figure
+ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neg", "distraction", "distancing", "suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Arousal Rating")
 

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added figure

@@
 
-effort_Reg = data_ER %>%
+effort_reg = data_ER %>%
   subset(data_ER$block != "view_neu" & data_ER$block != "choice")
@@
                           dv = "effort",
-                          data = effort_Reg,
+                          data = effort_reg,
                           within = "block",
@@
 pairs(posthoc_effort, adjust = "bonferroni")
+
+# Figure to visualize effort ratings
+# figure
+ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neg", "distraction", "distancing", "suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Effort Rating")
 ```

### 2021-12-08 06_Paper/COG-ED/Manuscript.Rmd
update mlm model h2b
expansion of the mlm model
adding simple slopes analysis

@@
 
-  h2b_data <- cbind(data_SV, dprime["d"], rt["meanrt"])
+  agg_vars <- cbind(data_SV, dprime["d"])
+  h2b_data <- merge(agg_vars, data_nback, by = c("subject", "level"))
+
+  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"
+
+  h2b_data <- merge(h2b_data, data_nfc, by = "subject")
+
+  # include new variable for post-correct trials
+  h2b_data$postcorrect = rep(NA, length(h2b_data$correct))    # add empty column
+      for (z in 1:(length(h2b_data$correct)-1)) {             # for all trials except the very last one
+        if (h2b_data$correct[z] == 1) {                       # if correct, paste correct
+          h2b_data$postcorrect[z+1] <- 1
+        } else if (h2b_data$correct[z] == 0) {                # if not correct, paste incorrect
+          h2b_data$postcorrect[z+1] <- 0
+        } else {
+          h2b_data$postcorrect[z+1] <- NA                     # if empty, leave empty
+        } 
+      }
+
+  # 512 trials, 8 blocks á 64 trials
+  i <- 1
+  while (i <= nrow(h2b_data)){
+    for (j in 1:64) {
+      h2b_data$trial <- seq(1, 64, 1)
+    }
+    i <- i + 64
+  }
+
+  h2b_data$postcorrect[h2b_data$trial == "1"] <- 1         # avoid transfer from previous block and subject (first trial of a block is always correct)
+
+  # get subset for MLM
+
+  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
+                               subset = !is.na(rt)
+                               & rt > 0.1))
 
@@
   # d'
-  h2b_data$d.mwc <- ave(h2b_data$d, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_data$d.cwc <- h2b_data$d - h2b_data$d.mwc
-
-  # mRT
-  h2b_data$meanrt.mwc <- ave(h2b_data$meanrt, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_data$meanrt.cwc <- h2b_data$meanrt - h2b_data$meanrt.mwc
+  h2b_sub$d.mwc <- ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
+  h2b_sub$d.cwc <- h2b_sub$d - h2b_sub$d.mwc
+
+  # RT
+  h2b_sub$rt.mwc <- ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
+  h2b_sub$rt.cwc <- h2b_sub$rt - h2b_sub$rt.mwc
 
   # level
-  h2b_data$level.mwc <- ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_data$level.cwc <- h2b_data$level - h2b_data$level.mwc
-
-  ## no level 2 predictors
+  h2b_sub$level.mwc <- ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
+  h2b_sub$level.cwc <- h2b_sub$level - h2b_sub$level.mwc
+
+  # correct 
+  h2b_sub$correct.mwc <- ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
+  h2b_sub$correct.cwc <- h2b_sub$correct - h2b_sub$correct.mwc
+
+  # postcorrect
+  h2b_sub$postcorrect.mwc <- ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
+  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - h2b_sub$postcorrect.mwc
+
+  ## level 2 predictor
+  # > CGM
+
+  # NFC
+  h2b_sub$nfc.cgm <- scale(h2b_sub$nfc, scale = F)
 
@@
   m0_h2b <- lmer(sv ~ 1 + (1|subject), 
-                 data = h2b_data)
+                 data = h2b_sub)
 
@@
 
-  m1_h2b <- lmer(sv ~ level.cwc + d.cwc + meanrt.cwc + (level.cwc|subject), 
-                 data = h2b_data,
+  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
+                 data = h2b_sub,
                  REML = T) # parameters estimated by maximizing restricted log-likelihood
 
-  # (1) if a warning message is produced, check random effects
-    summary(m1_h2b)$varcor
-    # (11) if all SDs are different from 0 and correlations look good (unequal to zero)
-      # this message should be a false positive and this model can be reported
-    # (12) if (11) is not true, check all available optimizers
-      n_cores <- parallel::detectCores()
-      opt_cl <- makeCluster(n_cores, type = "SOCK")
-      clusterEvalQ(opt_cl, library("lme4"))
-      clusterExport(opt_cl, "h2b_data")
-      m1_h2b_all <- allFit(m1_h2b, parallel = "snow", ncpus = n_cores, cl = opt_cl) 
-      stopCluster(opt_cl)
-      summary(m1_h2b_all)$msgs
-      # (121) if an optimizer returns NULL, use this optimizer and recalculate model to get the final model
-
-  # (2) if (121) is not true OR a singular fit message occurs, check for potential outliers and recalculate
-    potential_outliers_m1_h2b <- subset(h2b_data, abs(scale(resid(m1_h2b))) > 3)    
-    percentage_outliers <- 100/nrow(h2b_data) * nrow(potential_outliers_m1_h2b)
-    # get new subset excluding outliers
-    h2b_data_norm <- droplevels(subset(h2b_data, abs(scale(resid(m1_h2b))) < 3))
-    # start with (1) again
-
-  # (3) if (1) and (2) do not help, start reducing the model stepwise
-
   ## plot model fit of the final model ----
-  plot_model(mfinal_h2b, type = "diag")
-
-  # FIXME: do we want to include  a table like Table 3. in Westbrook et al.?
-    # if we decide to include a table of mlm results, I propose to include a table with
-    # term/parameter - Beta - SE - p-value - random effects (SD)
+  library(sjPlot)
+  plot_model(m1_h2b, type = "diag")
+
+  # simple slopes analysis -----------------------------------------------------
+  library(interactions)
+
+  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
+                    cond.int = T,                                       # print conditional intercepts
+                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals, 
+                                                                        # create plot, adjust false discovery rate
+  library(huxtable)
+  as_huxtable(m1_h2b.ss)
+
+  plot(m1_h2b.ss)
+
+  interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                x.label = "n back load level", y.label = "subjective value", legend.main = "NFC", interval = T) + theme_apa()
+
+  names(summary(m1_h2b))
+  m1_h2b.fixef <- summary(m1_h2b)$coefficients
+  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
+  write.csv2(te.norm.fixef, file = "S4_te.norm.fixef.csv")
+  write.csv2(te.norm.ranef, file = "S4_te.norm.ranef.csv")
 
@@
 ### Changes in subjective values depend reliably on n-back level
+
+intraclass correlation "icc_h2b"
+table withterm/parameter - Beta - SE - p-value - random effects (SD)
+huxtable?
 

### 2021-12-08 06_Paper/COG-ED/Manuscript.Rmd
prepare results for report

@@
 
+  # prepare temporary nfc-data frame for loop to feed into
+
+  data_nfc <- data.frame(subject = character(), nfc = double())
+
+  # calculate NFC scores for every subject
+
+  for (i in 1:(length(setindex)-1)) {
+
+    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
+    # define and invert items to be recoded
+    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1
+
+    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
+                                           nfc = sum(nfc)))
+  }
   data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"
@@
   # simple slopes analysis -----------------------------------------------------
+
   library(interactions)
@@
 
+  # FIXME: Do not print all charts
+
+  # prepare results for reporting ----------------------------------------------
+
   names(summary(m1_h2b))
@@
   m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
-  write.csv2(te.norm.fixef, file = "S4_te.norm.fixef.csv")
-  write.csv2(te.norm.ranef, file = "S4_te.norm.ranef.csv")
+
+  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef), 
+                                          m1_h2b.fixef[,c(1, 2, 5)]))
+  h2b_result.table$ranef.sd <- NA
+  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
+  colnames(h2b_result.table)[1] <- "Parameter"
+  colnames(h2b_result.table)[2] <- "Beta"
+  colnames(h2b_result.table)[3] <- "SE"
+  colnames(h2b_result.table)[4] <- "p-Value"
+  colnames(h2b_result.table)[5] <- "Random Effects (SD)"
+
+  row.names(h2b_result.table) <- NULL
+  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "D-Prime", "RT", "Correct", "Post-Correct", "Level x NFC")
+  # FIXME: display control variables? Spelling lower/upper case
+
+  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
+
+  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
+  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)
+
+  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
+    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)],"*")
+  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)] <- 
+    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)],"*")
+  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)] <- 
+    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)],"*")
+
+  # FIXME: display of p = 0.000,  no display of NA
+
+  apa_table(h2b_result.table,
+            caption = "Subjective values decline with increasing n-back level, even after controlling for declining task 
+            performance (d’ and reaction time), correct and postcorrect trials.",
+            note = "")
 
   # TODO: Corinna go on here :) 
-    # -> get results for reporting
-    # -> get means for plotting, plot results (if requested)
+    # -> prepare tables: MLM results + huxtable
     # -> write methods
@@
 
-  # TODO: it would be easy to integrate NFC as level 2 predictor into the analysis
-    # to identify the personality influence on sv
-    # it goes in the same direction as hypothesis 3a, but would hold some more information
-    # a corresponding hypothesis could be
+  # TODO: 
+    # -> check whether we want to include an additional hypothesis
     # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores" 
@@
 
+(`r apa_table(h2b_result.table)`)
+
 intraclass correlation "icc_h2b"
-table withterm/parameter - Beta - SE - p-value - random effects (SD)
+
 huxtable?

### 2021-12-09 06_Paper/COG-ED/Manuscript.Rmd
prepare results display of h2b
prepare tables and figures
start writing resulst and methods
added new hypothesis

@@
 And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+(2c) or (3a) or (3b) "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"
 
@@
 To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
-**MLM explanation goes here** To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
++ NFC
+**MLM explanation goes here**
+
+fit using $lmerTest$ package
+# center level 1 predictors
+ two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
+ level 1 predictor (SV) is of substantive interest
+ CWC
+# level 2 predictor
+ CGM
+null model > ICC
+random slopes model
+  controlled for performance (d', RT), correct and post-correct trials
+parameter estimation REML
+include model?
+simple slopes analysis
+
+To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
 These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 100 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
@@
 
-```{r Hypothesis_2b, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Hypothesis_2b, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
   ## maximal model ---- 
-
   m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
@@
   library(interactions)
-
   m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
@@
                                                                         # create plot, adjust false discovery rate
-  library(huxtable)
-  as_huxtable(m1_h2b.ss)
-
-  plot(m1_h2b.ss)
-
-  interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                x.label = "n back load level", y.label = "subjective value", legend.main = "NFC", interval = T) + theme_apa()
-
-  # FIXME: Do not print all charts
-
-  # prepare results for reporting ----------------------------------------------
-
-  names(summary(m1_h2b))
+
+  # prepare MLM results for reporting ------------------------------------------
+
+  # get random and fixed effects
+  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
   m1_h2b.fixef <- summary(m1_h2b)$coefficients
-  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
-
+
+  # prepare table
   h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef), 
@@
   h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
+
   colnames(h2b_result.table)[1] <- "Parameter"
@@
 
-  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
-    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)],"*")
   h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)] <- 
@@
     paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)],"*")
-
-  # FIXME: display of p = 0.000,  no display of NA
-
-  apa_table(h2b_result.table,
-            caption = "Subjective values decline with increasing n-back level, even after controlling for declining task 
-            performance (d’ and reaction time), correct and postcorrect trials.",
-            note = "")
+  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
+    paste0("<.001***")
+
+  h2b_result.table$`Random Effects (SD)`[3:8] <- paste0("")
+
+  library(kableExtra)
+  #replication_table <-
+    kbl(h2b_result.table,
+    caption = "Effects of n-back load level on subjective value controlled 
+    for task performance (d’ and reaction time), correct and postcorrect trials.",
+    booktabs = T,                          # no vertical lines
+    escape = F,                            # correctly print special characters)
+    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
+            escape = F,                    # correctly print special characters
+            threeparttable = T)            # line breaks in the footnote
+  #FIXME delete leading zero for p-values
+
+  # prepare SSA results for reporting ------------------------------------------
+
+  m1_h2b.ss$slopes
+
+  library(huxtable)
+  h2b_ssa.table <- as_huxtable(m1_h2b.ss)
+  h2b_ssa.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
+  h2b_ssa.table <- h2b_ssa.table[-2,]
+
+  h2b_ssa.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
+
+  # create interaction plot
+  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                                x.label = "n back load level", y.label = "subjective value",
+                                legend.main = "NFC", interval = T) + theme_apa()
 
@@
 
-  # TODO: 
-    # -> check whether we want to include an additional hypothesis
     # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"
-    # What do you think?
 
@@
 
-(`r apa_table(h2b_result.table)`)
-
-intraclass correlation "icc_h2b"
-
-huxtable?
+The multilevel model `r replication_table`
+
+statistically significant effect of n-back load level `r apa_print(m1_h2b)$full_result$level_cwc`
+controlled for performance and correct and post-correct answers
+
+`r apa_print(m1_h2b)$full_result$nfc_cgm`
+`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).
+
+simple slopes analysis `r h2b_ssa.table`, `r h2b_ssa.plot`
+statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC
 
@@
 
+# Discussion
+
+# (summary and interpretation of h2b_results)
+
 # Acknowledgements

### 2021-12-09 06_Paper/ER-ED/method.Rmd
added ED data frame

@@
 # new empty frame to store files into
-data_ER = data.frame(ID = character(), block = character(), arousal = double(), effort = double(), trigger = double(), trigger_reg = double())
+data_ER = data.frame(ID = character(), block = character(), arousal = double(), 
+                     effort = double(), trigger = double(), trigger_reg = double())
 
@@
                      LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
+
 data_choice = data.frame(ID = character(), choice = double())
@@
 # store ED data in data_ED frame
-#for (i in 1:length(datalist_ED)) {
+for (i in 1:length(datalist_ED)) {
 
-#  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
-#                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
-#                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
-#                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
-#                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
-#                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
-#                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
-#}
+  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
+                   datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
+                   datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
+                   datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
+                   datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
+                   datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
+                   datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
+
+  colnames(tmp) = names(data_ED)
+  data_ED = rbind(data_ED, tmp)
+}
 

### 2021-12-09 01_Paradigms/ER-ED/ER_ED/ER_paradigm.py
added info of strats in ED part

@@ -2029,6 +2029,9 @@ for edx in EDrounds:
         # what value was depicted on each button
         EDround.addData('EDleftbutton.value', LB[0:4])
         EDround.addData('EDrightbutton.value', RB[0:4])
+        # what strategy each button had
+        EDround.addData('EDleftbutton.strat', EDstratList[EDcomps[edx]])
+        EDround.addData('EDrightbutton.strat', EDstratList[EDcomps[edx]+1])
                 # store the necessary variables to be able to use it in the iteration process and for the random pick of the last n-back
         EDstorebutton.append(EDclick.clicked_name[0])
         if Currentstep == 0:

### 2021-12-09 06_Paper/COG-ED/Manuscript.Rmd

@@
 
-  rt <- data.frame(subject = character(), level = double(), meanrt = double())
+  rt <- data.frame(subject = character(), level = double(), medianrt = double())
 
@@
 
-    meanrt <- mean(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
+    medianrt <- median(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                  +(levelindex[i]-1)], na.rm = TRUE)
@@
                           level = data_RT$level[levelindex[i]],
-                          meanrt = meanrt)
+                          medianrt = medianrt)
     rt <- rbind(rt, newdata)
@@
       hypothesis1b_rmanova <- afex::aov_ez(data = h1b_data,
-                                           dv = "meanrt",
+                                           dv = "medianrt",
                                            id = "subject",

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
put SV computation at the beginning and added SVs trialwise to nback df
added postcorrect indicator as regressor column to nback data frame

@@
 
+  # for the multi level model to be able to assess the influence of post-error trials, we will include that as a regressor
+  # so the nback data frame will contain a column of ones and zeros
+
+  # add the "correct" column, but shifted down by one row
+
+  data_nback$postcorrect = c(1,data_nback$correct[1:(length(data_nback$correct)-1)])
+
+  # make sure to avoid transfer from the previous block by marking the first trial of each block as correct
+
+  data_nback$postcorrect[c(1,seq(64,length(data_nback$postcorrect),64))] <- 1
+
   # the choice column will contain 1 for the left button and 2 for the right button
+
   data_ED[data_ED == "EDleftbutton"] <- 1
@@
   # since only the last choice of each comparison is relevant, we will keep only those rows
+
   data_ED <- data_ED[data_ED$step == 6,]
@@
   # remove trials with RT < 100 ms from the n-back data and exclude trials after incorrect trials
+
   data_RT <- data_nback[-c(which(data_nback$rt < 0.1)), ]
@@
                                                cdrisc_complete, flexer_timestamp, flexer_complete))
+
+```
+
+```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # apply the addition or subtraction of 0.015625 to the last choices
+
+  for (i in 1:nrow(data_ED)) {
+
+    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
+    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]
+
+    if (data_ED$choice[i] == 1) {
+      if (data_ED$LBvalue[i] == 2.00) {
+        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
+      } else {
+        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
+      }
+    } else {
+      if (data_ED$RBvalue[i] == 2.00) {
+        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
+      } else {
+        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
+      }
+    }
+
+  }
+
+  # create vector indicating in which rows the data of a new subject begins
+
+  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))
+
+  # create empty data frame for the loop to feed into
+
+  data_SV <- data.frame(subject = character(), level = double(), sv = double())
+
+  # compute subjective values per n-back level and feed into data frame
+
+  for (i in 1:(length(subjectindex)-1)) {
+
+    # initialize empty vectors
+
+    tempone <- double()
+    temptwo <- double()
+    tempthree <- double()
+    tempfour <- double()
+
+    # check for every number, whether it appears in the fixedlevel and flexlevel columns
+    # divide flexvalue by 2 if it appears in the fixedlevel columns
+    # append 1 if it appears in the flexlevel column
+
+    # for 1-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
+          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 +
+                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
+          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
+        } else {
+          # do nothing
+        }
+
+    # for 2-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
+          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 +
+                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
+          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
+        } else {
+          # do nothing
+        }
+
+    # for 3-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
+          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 +
+                                                             which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
+          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
+        } else {
+          # do nothing
+        }
+
+    # for 4-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
+          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 +
+                                                           which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
+          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
+        } else {
+          # do nothing
+        }
+
+    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame
+
+    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
+                          level = c(1:4),
+                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
+    data_SV <- rbind(data_SV, newdata)
+
+  }
+
+  # remove temporary variables
+
+  remove(tempone, temptwo, tempthree, tempfour)
+
+  # add the SVs trial-wise to the nback-data-frame for the multi-level-model
+
+  for (i in 1:nrow(data_nback)) {
+
+    data_nback$sv[i] <- data_SV$sv[data_SV$subject == data_nback$subject[i] & data_SV$level == data_nback$level[i]]
+
+  }
 
@@
 
-```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # apply the addition or subtraction of 0.015625 to the last choices
-
-  for (i in 1:nrow(data_ED)) {
-
-    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
-    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]
-
-    if (data_ED$choice[i] == 1) {
-      if (data_ED$LBvalue[i] == 2.00) {
-        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
-      } else {
-        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
-      }
-    } else {
-      if (data_ED$RBvalue[i] == 2.00) {
-        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
-      } else {
-        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
-      }
-    }
-
-  }
-
-  # create vector indicating in which rows the data of a new subject begins
-
-  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))
-
-  # create empty data frame for the loop to feed into
-
-  data_SV <- data.frame(subject = character(), level = double(), sv = double())
-
-  # compute subjective values per n-back level and feed into data frame
-
-  for (i in 1:(length(subjectindex)-1)) {
-
-    # initialize empty vectors
-
-    tempone <- double()
-    temptwo <- double()
-    tempthree <- double()
-    tempfour <- double()
-
-    # check for every number, whether it appears in the fixedlevel and flexlevel columns
-    # divide flexvalue by 2 if it appears in the fixedlevel columns
-    # append 1 if it appears in the flexlevel column
-
-    # for 1-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
-          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 +
-                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
-          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
-        } else {
-          # do nothing
-        }
-
-    # for 2-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
-          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 +
-                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
-          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
-        } else {
-          # do nothing
-        }
-
-    # for 3-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
-          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 +
-                                                             which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
-          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
-        } else {
-          # do nothing
-        }
-
-    # for 4-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
-          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 +
-                                                           which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
-          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
-        } else {
-          # do nothing
-        }
-
-    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame
-
-    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
-                          level = c(1:4),
-                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
-    data_SV <- rbind(data_SV, newdata)
-
-  }
-
-  # remove temporary variables
-
-  remove(tempone, temptwo, tempthree, tempfour)
-
-```
-
 ```{r Hypothesis_1a, echo=FALSE, message=FALSE, warning=FALSE}

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
changed which pipelines will be calculated

@@
   #   (N) none
-  #   (2) 2 SDs from the mean
-  #   (3) 3 SDs from the mean
-  #   (T) 0-100 ms after stimulus onset
-  # Post-error trials:
-  #   (E) excluded
-  #   (N) not excluded
+  #   (2) 2 MADs from the median
+  #   (5) 2.5 MADs from the median
+  #   (3) 3 MADs from the median
+  #   (O) 0-100 ms after stimulus onset
+  #   (T) 0-200 ms after stimulus onset
   #
-  # Example: the data frame "AWL3E" has log-transformed RT data with no data points beyond 3 SD
-  # from the mean and with no trials that followed misses/false alarms
+  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
+  # from the median
   #
-  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R___) with either no outlier
+  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
   # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
@@
 
-  pipelines_data <- replicate(92, data_nback, simplify = FALSE)
-  pipelines_data <- setNames(pipelines_data, c("AARNN","AARNE","AAR2N","AAR2E","AAR3N","AAR3E","AARTN","AARTE",
-                                               "AALNN","AALNE","AAL2N","AAL2E","AAL3N","AAL3E",
-                                               "AAINN","AAINE","AAI2N","AAI2E","AAI3N","AAI3E",
-                                               "AASNN","AASNE","AAS2N","AAS2E","AAS3N","AAS3E",
-                                               "AWR2N","AWR2E","AWR3N","AWR3E",
-                                               "AWLNN","AWLNE","AWL2N","AWL2E","AWL3N","AWL3E",
-                                               "AWINN","AWINE","AWI2N","AWI2E","AWI3N","AWI3E",
-                                               "AWSNN","AWSNE","AWS2N","AWS2E","AWS3N","AWS3E",
-                                               "WWR2N","WWR2E","WWR3N","WWR3E",
-                                               "WWLNN","WWLNE","WWL2N","WWL2E","WWL3N","WWL3E",
-                                               "WWINN","WWINE","WWI2N","WWI2E","WWI3N","WWI3E",
-                                               "WWSNN","WWSNE","WWS2N","WWS2E","WWS3N","WWS3E",
-                                               "WAR2N","WAR2E","WAR3N","WAR3E",
-                                               "WALNN","WALNE","WAL2N","WAL2E","WAL3N","WAL3E",
-                                               "WAINN","WAINE","WAI2N","WAI2E","WAI3N","WAI3E",
-                                               "WASNN","WASNE","WAS2N","WAS2E","WAS3N","WAS3E"))
+  pipelines_data <- replicate(63, data_nback, simplify = FALSE)
+  pipelines_data <- setNames(pipelines_data, c("AARN","AAR2","AAR5","AAR3","AARO","AART",
+                                               "AALN","AAL2","AAL5","AAL3",
+                                               "AAIN","AAI2","AAI5","AAI3",
+                                               "AASN","AAS2","AAS5","AAS3",
+                                               "AWR2","AWR5","AWR3",
+                                               "AWLN","AWL2","AWL5","AWL3",
+                                               "AWIN","AWI2","AWI5","AWI3",
+                                               "AWSN","AWS2","AWS5","AWS3",
+                                               "WWR2","WWR5","WWR3",
+                                               "WWLN","WWL2","WWL5","WWL3",
+                                               "WWIN","WWI2","WWI5","WWI3",
+                                               "WWSN","WWS2","WWS5","WWS3",
+                                               "WAR2","WAR5","WAR3",
+                                               "WALN","WAL2","WAL5","WAL3",
+                                               "WAIN","WAI2","WAI5","WAI3",
+                                               "WASN","WAS2","WAS5","WAS3"))
 
@@
 
+          } else if (pipeline_name[[1]][4] == "5") {
+
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 2.5 * pipemad)
+                                                               & pipelines_data[[i]]$rt > (pipemedian - 2.5 * pipemad))), ]
           } else if (pipeline_name[[1]][4] == "3") {
@@
 
+            } else if (pipeline_name[[1]][4] == "5") {
+
+              ifelse(length(which(pipelines_data[[i]]$level == x &
+                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
+                     pipelines_data[[i]] <-
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
+                                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
+
             } else if (pipeline_name[[1]][4] == "3") {
@@
 
+            } else if (pipeline_name[[1]][4] == "5") {
+
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
+                     pipelines_data[[i]] <-
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
+
             } else if (pipeline_name[[1]][4] == "3") {
@@
 
+            } else if (pipeline_name[[1]][4] == "5") {
+
+              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
+                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
+                     pipelines_data[[i]] <-
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
+                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
+                     pipelines_data[[i]] <- pipelines_data[[i]])
+
             } else if (pipeline_name[[1]][4] == "3") {
@@
 
-    # the 100-ms-exclusion and the post-error-exclusion are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:
-
-    # exclude RTs fast than 100 ms after stimulus onset if the fourth letter in the data frame name is a "T"
-    # also making sure that there are even any trials below 100 ms, otherwise you get an error message
-
-    if (pipeline_name[[1]][4] == "T") {
+    # the time-based exclusions are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:
+
+    # exclude RTs fast than 100 or 200 ms after stimulus onset if the fourth letter in the data frame name is an "O" or a "T"
+    # also making sure that there are even any trials below 100/200 ms, otherwise you get an error message
+
+    if (pipeline_name[[1]][4] == "O") {
 
@@
              pipelines_data[[i]] <- pipelines_data[[i]])
-    }
-
-    # exclude post-error trials if the fifth letter in the data frame name is an "E"
-    # also making sure that there are even any error-/post-error-rows left to perform the exclusion, otherwise you get an error message
-
-    if (pipeline_name[[1]][5] == "E") {
-
-      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ]) > 0,
-             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$correct == 0) + 1), ],
+
+    } else if (pipeline_name[[1]][4] == "T") {
+
+      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]) > 0,
+             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ],
              pipelines_data[[i]] <- pipelines_data[[i]])
@@
     }
+
   }

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
wrote h2b analysis

--- 2021-12-09 06_Paper/COG-ED/Manuscript.Rmd
@@
 
+```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # apply the addition or subtraction of 0.015625 to the last choices
+
+  for (i in 1:nrow(data_ED)) {
+
+    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
+    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]
+
+    if (data_ED$choice[i] == 1) {
+      if (data_ED$LBvalue[i] == 2.00) {
+        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
+      } else {
+        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
+      }
+    } else {
+      if (data_ED$RBvalue[i] == 2.00) {
+        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
+      } else {
+        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
+      }
+    }
+
+  }
+
+  # create vector indicating in which rows the data of a new subject begins
+
+  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))
+
+  # create empty data frame for the loop to feed into
+
+  data_SV <- data.frame(subject = character(), level = double(), sv = double())
+
+  # compute subjective values per n-back level and feed into data frame
+
+  for (i in 1:(length(subjectindex)-1)) {
+
+    # initialize empty vectors
+
+    tempone <- double()
+    temptwo <- double()
+    tempthree <- double()
+    tempfour <- double()
+
+    # check for every number, whether it appears in the fixedlevel and flexlevel columns
+    # divide flexvalue by 2 if it appears in the fixedlevel columns
+    # append 1 if it appears in the flexlevel column
+
+    # for 1-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
+          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 +
+                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
+          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
+        } else {
+          # do nothing
+        }
+
+    # for 2-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
+          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 +
+                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
+          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
+        } else {
+          # do nothing
+        }
+
+    # for 3-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
+          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 +
+                                                             which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
+          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
+        } else {
+          # do nothing
+        }
+
+    # for 4-back
+
+        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
+          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 +
+                                                           which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
+        } else {
+          # do nothing
+        }
+
+        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
+          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
+        } else {
+          # do nothing
+        }
+
+    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame
+
+    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
+                          level = c(1:4),
+                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
+    data_SV <- rbind(data_SV, newdata)
+
+  }
+
+  # remove temporary variables
+
+  remove(tempone, temptwo, tempthree, tempfour)
+
+  # add the SVs trial-wise to the nback-data-frame for the multi-level-model
+
+  for (i in 1:nrow(data_nback)) {
+
+    data_nback$sv[i] <- data_SV$sv[data_SV$subject == data_nback$subject[i] & data_SV$level == data_nback$level[i]]
+
+  }
+
+```
+
 # Introduction
@@
 Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
-Error- and post-error trials will be excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-Declining performance will be investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+To test our hypotheses, we perform a series of rmANOVAs and MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2017]. 
+Declining performance will be investigated by calculating a rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
 Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
@@
 
-To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
-+ NFC
-**MLM explanation goes here**
-
-fit using $lmerTest$ package
-# center level 1 predictors
- two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
- level 1 predictor (SV) is of substantive interest
- CWC
-# level 2 predictor
- CGM
-null model > ICC
-random slopes model
-  controlled for performance (d', RT), correct and post-correct trials
-parameter estimation REML
-include model?
-simple slopes analysis
+To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
+We apply restricted maximum likelihood (REML) to fit the model.
+First, we calculate the intraclass correlation (ICC) on the basis of the null model.
+Second, we estimate a random slopes model of SV including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+Within the model, we control for *d'*, RT, correct and post-correct trials.
+$$
+SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
+$$
+Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007].
+Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
+# TODO: Johnson-Neyman plot
 
@@
 A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.
-
-```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # apply the addition or subtraction of 0.015625 to the last choices
-
-  for (i in 1:nrow(data_ED)) {
-
-    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
-    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]
-
-    if (data_ED$choice[i] == 1) {
-      if (data_ED$LBvalue[i] == 2.00) {
-        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
-      } else {
-        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
-      }
-    } else {
-      if (data_ED$RBvalue[i] == 2.00) {
-        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
-      } else {
-        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
-      }
-    }
-
-  }
-
-  # create vector indicating in which rows the data of a new subject begins
-
-  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))
-
-  # create empty data frame for the loop to feed into
-
-  data_SV <- data.frame(subject = character(), level = double(), sv = double())
-
-  # compute subjective values per n-back level and feed into data frame
-
-  for (i in 1:(length(subjectindex)-1)) {
-
-    # initialize empty vectors
-
-    tempone <- double()
-    temptwo <- double()
-    tempthree <- double()
-    tempfour <- double()
-
-    # check for every number, whether it appears in the fixedlevel and flexlevel columns
-    # divide flexvalue by 2 if it appears in the fixedlevel columns
-    # append 1 if it appears in the flexlevel column
-
-    # for 1-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
-          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 +
-                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
-          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
-        } else {
-          # do nothing
-        }
-
-    # for 2-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
-          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 +
-                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
-          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
-        } else {
-          # do nothing
-        }
-
-    # for 3-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
-          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 +
-                                                             which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
-          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
-        } else {
-          # do nothing
-        }
-
-    # for 4-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
-          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 +
-                                                           which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
-          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
-        } else {
-          # do nothing
-        }
-
-    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame
-
-    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
-                          level = c(1:4),
-                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
-    data_SV <- rbind(data_SV, newdata)
-
-  }
-
-  # remove temporary variables
-
-  remove(tempone, temptwo, tempthree, tempfour)
-
-```
 
@@
                     johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,
-                                                                        # create plot, adjust false discovery rate
 
@@
                                 legend.main = "NFC", interval = T) + theme_apa()
-
-  # TODO: Corinna go on here :) 
-    # -> prepare tables: MLM results + huxtable
-    # -> write methods
-    # -> write results
-
-    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"
 

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
some improvements h2b

@@
   library(lmerTest)     # for multilevel modeling
-  library(snow)         # for faster processing
   library(afex)         # compute repeated measures ANOVA, "afex" package
@@
 Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
+We visually inspect the residuals of the final model. The approximately normal distribution indicates no evidence to perform model criticism.  
 Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
-# TODO: Johnson-Neyman plot
+To evaluate the moderating effect, we calculate the Johnson-Neyman interval.
 
@@
 
-  # detach afex in order to user lmerTest
+  # detach afex in order to use lmerTest
   detach("package:afex", unload = TRUE)
@@
 
-  agg_vars <- cbind(data_SV, dprime["d"])
-  h2b_data <- merge(agg_vars, data_nback, by = c("subject", "level"))
+  h2b_data <- merge(dprime[c("subject", "level", "d")], data_nback, by = c("subject", "level"))
 
@@
   h2b_data <- merge(h2b_data, data_nfc, by = "subject")
-
-  # include new variable for post-correct trials
-  h2b_data$postcorrect = rep(NA, length(h2b_data$correct))  # add empty column
-  for (z in 1:(length(h2b_data$correct)-1)) {               # for all trials except the very last one
-    if (h2b_data$correct[z] == 1) {                         # if correct, paste correct
-      h2b_data$postcorrect[z+1] <- 1
-    } else if (h2b_data$correct[z] == 0) {                  # if not correct, paste incorrect
-      h2b_data$postcorrect[z+1] <- 0
-    } else {
-      h2b_data$postcorrect[z+1] <- NA                       # if empty, leave empty
-    } 
-  }
-
-  # 512 trials, 8 blocks á 64 trials
-  i <- 1
-  while (i <= nrow(h2b_data)){
-    for (j in 1:64) {
-      h2b_data$trial <- seq(1, 64, 1)
-    }
-    i <- i + 64
-  }
-
-  h2b_data$postcorrect[h2b_data$trial == "1"] <- 1         # avoid transfer from previous block and subject (first trial of a block is always correct)
 
@@
   # d'
-  h2b_sub$d.mwc <- ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_sub$d.cwc <- h2b_sub$d - h2b_sub$d.mwc
+  h2b_sub$d.cwc <- h2b_sub$d - (ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # RT
-  h2b_sub$rt.mwc <- ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_sub$rt.cwc <- h2b_sub$rt - h2b_sub$rt.mwc
+  h2b_sub$rt.cwc <- h2b_sub$rt - (ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # level
-  h2b_sub$level.mwc <- ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_sub$level.cwc <- h2b_sub$level - h2b_sub$level.mwc
+  h2b_sub$level.cwc <- h2b_sub$level - (ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # correct 
-  h2b_sub$correct.mwc <- ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_sub$correct.cwc <- h2b_sub$correct - h2b_sub$correct.mwc
+  h2b_sub$correct.cwc <- h2b_sub$correct - (ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # postcorrect
-  h2b_sub$postcorrect.mwc <- ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
-  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - h2b_sub$postcorrect.mwc
+  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - (ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
 
@@
   m0_h2b <- lmer(sv ~ 1 + (1|subject), 
-                 data = h2b_sub)
+                 data = h2b_sub,
+                 REML = T)
 
@@
                  data = h2b_sub,
-                 REML = T) # parameters estimated by maximizing restricted log-likelihood
+                 REML = T) # parameters estimated by restricted log-likelihood maximization
 
@@
   plot_model(m1_h2b, type = "diag")
-
-  # simple slopes analysis -----------------------------------------------------
-
-  library(interactions)
-  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
-                    cond.int = T,                                       # print conditional intercepts
-                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,
 
@@
   colnames(h2b_result.table)[2] <- "Beta"
-  colnames(h2b_result.table)[3] <- "SE"
-  colnames(h2b_result.table)[4] <- "p-Value"
+  colnames(h2b_result.table)[3] <- "$SE$"
+  colnames(h2b_result.table)[4] <- "$p$-value"
   colnames(h2b_result.table)[5] <- "Random Effects (SD)"
@@
   row.names(h2b_result.table) <- NULL
-  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "D-Prime", "RT", "Correct", "Post-Correct", "Level x NFC")
+  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Correct", "Post-Correct", "Level x NFC")
   # FIXME: display control variables? Spelling lower/upper case
@@
 
-  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)] <- 
-    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.01)],"*")
-  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)] <- 
-    paste0(h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.05)],"*")
-  h2b_result.table$`p-Value`[which(h2b_result.table$`p-Value`<.001)] <- 
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
+    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
+    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
     paste0("<.001***")
@@
 
+  # simple slopes analysis -----------------------------------------------------
+
+  library(interactions)
+  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
+                    cond.int = T,                                       # print conditional intercepts
+                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,
+                                                                        # create plot, adjust false discovery rate
+
+  # save Johnson-Neyman plot
+  h2b_jnplot <- m1_h2b.ss$jnplot
+
+  # create interaction plot
+  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                                x.label = "n back level", y.label = "subjective value",
+                                legend.main = "NFC", interval = T) + theme_apa()
+
   # prepare SSA results for reporting ------------------------------------------
-
-  m1_h2b.ss$slopes
 
@@
 
-  # create interaction plot
-  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                                x.label = "n back load level", y.label = "subjective value",
-                                legend.main = "NFC", interval = T) + theme_apa()
-
 ```
@@
 
-simple slopes analysis `r h2b_ssa.table`, `r h2b_ssa.plot`
+simple slopes analysis `r h2b_ssa.table`, `r h2b_jnplot`,`r h2b_ssa.plot`
 statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
added d prime for every single pipeline

--- 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
@@
 
+```{r pipelines_dprime, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # calculate d' for every pipeline because it depends on the total number of target and non-target trials
+
+  for (j in 1:length(pipelines_data)) {
+
+    # compute index of rows in which the levels change
+
+    levelindex <- c(1,which(pipelines_data[[j]]$level != dplyr::lag(pipelines_data[[j]]$level)),nrow(pipelines_data[[j]]))
+
+    # set up empty data frame for the loop to feed into
+
+    dprime <- data.frame(subject = character(), level = double(), hitrate = double(), falsealarmrate = double())
+
+    # calculate hits and false alarms per participant
+
+    for (i in 1:(length(levelindex)-1)) {
+
+      # set the number of targets and non-targets
+      num_targets <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
+      num_nontargets <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
+
+      hits <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
+                             pipelines_data[[j]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
+      falsealarms <- length(which(pipelines_data[[j]]$response[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
+                             pipelines_data[[j]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
+      newdata <- data.frame(subject = pipelines_data[[j]]$subject[levelindex[i]],
+                            level = pipelines_data[[j]]$level[levelindex[i]],
+                            hitrate = hits/num_targets,
+                            falsealarmrate = falsealarms/num_nontargets)
+      dprime <- rbind(dprime, newdata)
+
+    }
+
+    # z-transform the hit rate and the false alarm rate
+
+    dprime$hitrate.z = NA
+    dprime$falsealarmrate.z = NA
+
+    for (i in 1:4) {
+
+      dprime$hitrate.z[which(dprime$level == i)]        <- scale(dprime$hitrate[which(dprime$level == i)])
+      dprime$falsealarmrate.z[which(dprime$level == i)] <- scale(dprime$falsealarmrate[which(dprime$level == i)])
+
+    }
+
+    # calculate d'
+
+    dprime$d <- dprime$hitrate.z - dprime$falsealarmrate.z
+
+    # feed d# trialwise into the pipeline data frame
+
+    for (i in 1:nrow(pipelines_data[[j]])) {
+
+      pipelines_data[[j]]$dprime[i] <- dprime$d[dprime$subject == pipelines_data[[j]]$subject[i] & dprime$level == pipelines_data[[j]]$level[i]]
+
+    }
+  }
+
+```
+
 # Methods
@@
 Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
-Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-To test our hypotheses, we perform a series of rmANOVAs and MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2017]. 
-Declining performance will be investigated by calculating a rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+Error- and post-error trials will be excluded, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+Declining performance will be investigated by calculating a repeated measures analysis of variance (rmANOVA) with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
 Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
@@
 
-To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
-We apply restricted maximum likelihood (REML) to fit the model.
-First, we calculate the intraclass correlation (ICC) on the basis of the null model.
-Second, we estimate a random slopes model of SV including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
-Within the model, we control for *d'*, RT, correct and post-correct trials.
-$$
-SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
-$$
-Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007].
-Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
-# TODO: Johnson-Neyman plot
+To determine the influence of task performance in the association of SVs and n-back level, we will set up a multi-level model.
++ NFC
+**MLM explanation goes here**
+
+fit using $lmerTest$ package
+# center level 1 predictors
+ two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
+ level 1 predictor (SV) is of substantive interest
+ CWC
+# level 2 predictor
+ CGM
+null model > ICC
+random slopes model
+  controlled for performance (d', RT), correct and post-correct trials
+parameter estimation REML
+include model?
+simple slopes analysis
 
@@
 
-  # compute index of rows in which the levels change
-
-  levelindex <- c(1,which(data_RT$level != dplyr::lag(data_RT$level)),nrow(data_RT))
-
-  # set up empty data frame for the loop to feed into
-
-  dprime <- data.frame(subject = character(), level = double(), hitrate = double(), falsealarmrate = double())
-
-  # calculate hits and false alarms per participant
-
-  for (i in 1:(length(levelindex)-1)) {
-
-    # set the number of targets and non-targets
-    num_targets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
-    num_nontargets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
-
-    hits <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
-                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
-    falsealarms <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
-                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
-    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
-                          level = data_RT$level[levelindex[i]],
-                          hitrate = hits/num_targets,
-                          falsealarmrate = falsealarms/num_nontargets)
-    dprime <- rbind(dprime, newdata)
-
-  }
-
-  # z-transform the hit rate and the false alarm rate
-
-  dprime$hitrate.z = NA
-  dprime$falsealarmrate.z = NA
-
-  for (i in 1:4) {
-
-    dprime$hitrate.z[which(dprime$level == i)]        <- scale(dprime$hitrate[which(dprime$level == i)])
-    dprime$falsealarmrate.z[which(dprime$level == i)] <- scale(dprime$falsealarmrate[which(dprime$level == i)])
-
-  }
-
-  # calculate d'
-
-  dprime$d <- dprime$hitrate.z - dprime$falsealarmrate.z
-
   # repeated measures ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
 
-      # make a temporary copy of the dprime data frame without 1-back
-
-      h1a_data <- dprime[dprime$level != 1, ]
+      # make a temporary copy of the data frame without 1-back
+
+      h1a_data <- pipelines_data[["AARN"]][pipelines_data[["AARN"]]$level != 1, ]
       h1a_data$level <- as.factor(h1a_data$level)
@@
       hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
-                                           dv = "d",
+                                           dv = "dprime",
                                            id = "subject",
@@
                     johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals, 
+                                                                        # create plot, adjust false discovery rate
 
@@
                                 legend.main = "NFC", interval = T) + theme_apa()
+
+  # TODO: Corinna go on here :) 
+    # -> prepare tables: MLM results + huxtable
+    # -> write methods
+    # -> write results
+
+    # "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"
 

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
added some line breaks

@@
       # calculate ANOVA
+
       hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
@@
       # obtain estimated marginal means for ANOVA model
+
       hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
                                   specs = "level")
+
       # calculate pairwise comparisons on estimated marginal means
+
       hypothesis1a_contrasts <- pairs(hypothesis1a_emm)
@@
       # obtain estimated marginal means for ANOVA model
+
       hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
@@
       # calculate pairwise comparisons on estimated marginal means
+
       hypothesis1b_contrasts <- pairs(hypothesis1b_emm)
@@
   # obtain estimated marginal means for ANOVA model
+
   hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
                               specs = "level")
+
   # calculate pairwise comparisons on estimated marginal means
+
   hypothesis2a_contrasts <- pairs(hypothesis2a_emm)

### 2021-12-13 06_Paper/COG-ED/Manuscript.Rmd
reintroduced some line breaks in the text

@@
 Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
+Aggregated RT values will be described using the median and the median of absolute deviation (MAD) as robust estimates of center and variability, respectively [@Lachaud2011].
 Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-To test our hypotheses, we perform a series of rmANOVAs and MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2017]. 
-Declining performance will be investigated by calculating a rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2017]. 
+Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
 Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
@@
 Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
-A rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
+An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
 Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
@@
 First, we calculate the intraclass correlation (ICC) on the basis of the null model.
-Second, we estimate a random slopes model of SV including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+Second, we estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
 Within the model, we control for *d'*, RT, correct and post-correct trials.
@@
 Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
-We visually inspect the residuals of the final model. The approximately normal distribution indicates no evidence to perform model criticism.  
+We visually inspect the residuals of the final model.
+The approximately normal distribution indicates no evidence to perform model criticism.  
 Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
@@
 
-To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 92 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, $2 SD$ from the mean, $3 SD$ from the mean, RTs below 100 ms), whether post-error trials were excluded or not, and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
-The multi-level model will be run with each of the 92 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms, removal of post-error trials).
+To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3 $MAD$ from the median, RTs below 100 or 200 ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
+The multi-level model will be run with each of the 63 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms).
 The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
@@
 [-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
-Consequently, we chose a different way of quantifying the individual degree of ED.
+Consequently, we will choose a different way of quantifying the individual degree of ED.
 A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.

### 2021-12-13 06_Paper/COG-ED/Manuscript.Rmd
NHB guidelines: shortened title to less than 100 characters

@@
 ---
-title             : "When easy is not preferred: The Cognitive and Emotion Regulation Effort Discounting paradigm (CERED) for estimating subjective values of cognitive tasks"
+title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
 shorttitle        : "The CERED paradigm for estimating subjective values"

### 2021-12-13 06_Paper/COG-ED/Manuscript.Rmd
NHB guidelines: Rewrote abstract to be < 150 words

@@
       - Writing - review & editing
+      - Visualization
 affiliation:
@@
 abstract: |
-  Every day, individuals have to weigh the value of the reward when reaching a goal against the required effort.
-  However, effort is not inherently aversive to all individuals, which has often been neglected by previous approaches to quantify the subjective value of effort.
-  One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
-  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).
-  The CERED paradigm will likely enable a more insightful investigation of interindividual differences in effort discounting, as well as the investigation of effort discounting for task types for which this is currently not possible due to their high degree of subjectivity.
-
-  We argue that adapting the paradigm and the method of computing the willingness to exert effort allows two crucial things: Quantifying subjective values without assuming that the easiest level is preferred, and quantifying subjective values for tasks with no objective order of task load.
+  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
+  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
+  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
+  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
+  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.
+
 keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"

### 2021-12-13 06_Paper/COG-ED/Manuscript.Rmd
NHB guidelines: added hypothesis 2c

@@
 Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
-Regarding the associations of subjective and objective task load we hypothesize that (1a) performance measured by signal detection *d'* declines with increasing n-back level, (1b) performance measured by reaction time declines with increasing n-back level, and (1c) perceived task load increases with n-back level.
+Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
 Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
+A newly added hypothesis is that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
 And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-(2c) or (3a) or (3b) "SVs decline stronger with increasing load level for individuals with low compared to high NFC scores"
 

### 2021-12-15 06_Paper/COG-ED/Manuscript.Rmd
changed wording in intro
adjustments to pipelines

@@
   library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
+  library(sjPlot)       # plot MLM model fit
 
@@
 
+  # correct subject code
+  data_nback$subject[which(data_nback$subject == "E12K08_neu")] <- "E12K08"
+  data_ED$subject[which(data_ED$subject == "E12K08_neu")] <- "E12K08"
+
   # the choice column will contain 1 for the left button and 2 for the right button
@@
   data_ED <- subset(data_ED, select = -c(step))
-
-  # remove trials with RT < 100 ms from the n-back data and exclude trials after incorrect trials
-
-  data_RT <- data_nback[-c(which(data_nback$rt < 0.1)), ]
-  data_RT <- data_RT[-c(which(data_RT$correct == 0) + 1), ]
 
@@
                                                cdrisc_complete, flexer_timestamp, flexer_complete))
+
+  # compute index of rows in which the data sets change
+
+  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))
 
@@
 Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
-A newly added hypothesis is that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
+Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
 And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
@@
   #
-  # across which dimensions the tranformation and outlier exclusion will be done:
+  # across which dimensions the transformation and outlier exclusion will be done:
   #   (AA) across subjects, across n-back levels
@@
 
-    # exclude RTs fast than 100 or 200 ms after stimulus onset if the fourth letter in the data frame name is an "O" or a "T"
+    # exclude RTs faster than 100 or 200 ms after stimulus onset if the fourth letter in the data frame name is an "O" or a "T"
     # also making sure that there are even any trials below 100/200 ms, otherwise you get an error message
@@
   # H1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
-
-  # compute index of rows in which the data sets change
-
-  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))
 
@@
 
-```{r Hypothesis_2b, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
+```{r Hypothesis_2b_2c, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
 
+  # H2c: SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
+
   # detach afex in order to use lmerTest
@@
 
-  h2b_data <- merge(dprime[c("subject", "level", "d")], data_nback, by = c("subject", "level"))
+  h2b_data <- pipelines_data[["AARO"]]
 
@@
   }
-  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"
 
@@
 
-  # get subset for MLM
-
-  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
-                               subset = !is.na(rt)
-                               & rt > 0.1))
+  # get subset for MLM without RT = NA
+
+  h2b_data <- droplevels(subset(h2b_data[c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
+                               subset = !is.na(rt)))
 
@@
 
-  # d'
-  h2b_sub$d.cwc <- h2b_sub$d - (ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
+  # dprime
+  h2b_data$dprime.cwc <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # RT
-  h2b_sub$rt.cwc <- h2b_sub$rt - (ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
+  h2b_data$rt.cwc <- h2b_data$rt - (ave(h2b_data$rt, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # level
-  h2b_sub$level.cwc <- h2b_sub$level - (ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
+  h2b_data$level.cwc <- h2b_data$level - (ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # correct 
-  h2b_sub$correct.cwc <- h2b_sub$correct - (ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
+  h2b_data$correct.cwc <- h2b_data$correct - (ave(h2b_data$correct, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 
   # postcorrect
-  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - (ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T)))
+  h2b_data$postcorrect.cwc <- h2b_data$postcorrect - (ave(h2b_data$postcorrect, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 
@@
   # NFC
-  h2b_sub$nfc.cgm <- scale(h2b_sub$nfc, scale = F)
+  h2b_data$nfc.cgm <- scale(h2b_data$nfc, scale = F)
 
@@
   m0_h2b <- lmer(sv ~ 1 + (1|subject), 
-                 data = h2b_sub,
+                 data = h2b_data,
                  REML = T)
@@
   ## maximal model ---- 
-  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
-                 data = h2b_sub,
+  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
+                 data = h2b_data,
                  REML = T) # parameters estimated by restricted log-likelihood maximization
@@
   ## plot model fit of the final model ----
-  library(sjPlot)
-  plot_model(m1_h2b, type = "diag")
+  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
 

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd
keep incorrect RTs
wrote results

@@
   library(sjPlot)       # plot MLM model fit
+  library(kableExtra)   # 
+  library(interactions) # for simple slopes analysis
+  library(huxtable)     # create huxtable
 
@@
 
-    # replace the RTs of incorrect trials with NA for better handling
-
-    pipelines_data[[i]]$rt[pipelines_data[[i]]$correct == 0] <- NA
+    # # replace the RTs of incorrect trials with NA for better handling
+    # 
+    # pipelines_data[[i]]$rt[pipelines_data[[i]]$correct == 0] <- NA
 
@@
   # prepare table
-  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef), 
-                                          m1_h2b.fixef[,c(1, 2, 5)]))
+  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef[-c(6,7),]), 
+                                          m1_h2b.fixef[-c(6,7),c(1, 2, 5)]))
   h2b_result.table$ranef.sd <- NA
@@
   row.names(h2b_result.table) <- NULL
-  h2b_result.table$Parameter[1:8] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Correct", "Post-Correct", "Level x NFC")
-  # FIXME: display control variables? Spelling lower/upper case
+  h2b_result.table$Parameter[1:6] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Level x NFC")
 
   h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
-
   h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
@@
 
-  h2b_result.table$`Random Effects (SD)`[3:8] <- paste0("")
-
-  library(kableExtra)
-  #replication_table <-
+  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")
+
+  replication_table <-
     kbl(h2b_result.table,
@@
             threeparttable = T)            # line breaks in the footnote
-  #FIXME delete leading zero for p-values
 
@@
 
-  library(interactions)
   m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                     cond.int = T,                       # print conditional intercepts
-                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals,
-                                                                        # create plot, adjust false discovery rate
-
-  # save Johnson-Neyman plot
-  h2b_jnplot <- m1_h2b.ss$jnplot
+                    control.fdr = T)                    # adjust false discovery rate
+
+  #create table
+  h2b_ss.table <- as_huxtable(m1_h2b.ss)
+  h2b_ss.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
+  h2b_ss.table <- h2b_ss.table[-2,]
+  h2b_ss.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
+
+  # calculate Johnson-Neyman intervals
+  h2b_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
+  h2b_jn.int <- h2b_jn$bounds
+
+  # save plot
+  h2b_jn.plot <- h2b_jn$plot
 
   # create interaction plot
-  h2b_ssa.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                               plot.points = T, point.shape = T,
                                x.label = "n back level", y.label = "subjective value",
                                legend.main = "NFC", interval = T) + theme_apa()    
-
-  # prepare SSA results for reporting ------------------------------------------
-
-  library(huxtable)
-  h2b_ssa.table <- as_huxtable(m1_h2b.ss)
-  h2b_ssa.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
-  h2b_ssa.table <- h2b_ssa.table[-2,]
-
-  h2b_ssa.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
-
 ```
@@
 
-The multilevel model `r replication_table`
-
-statistically significant effect of n-back load level `r apa_print(m1_h2b)$full_result$level_cwc`
-controlled for performance and correct and post-correct answers
-
-`r apa_print(m1_h2b)$full_result$nfc_cgm`
+N-back level is a reliable predictor of subjective value (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (signal detection d’ and reaction time) as well as correct and post-correct answers.
+The results of the multilevel model are detailed in Table X. 
+`r replication_table`
 `r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).
-
-simple slopes analysis `r h2b_ssa.table`, `r h2b_jnplot`,`r h2b_ssa.plot`
-statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC
+However, NFC has no statistically significant effect on subjective value (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
+The simple slopes analysis revealed a significant slope of n-back level for three different expressions of NFC (Table X, Figure X).
+`r h2b_ss.table`
+`r h2b_ss.plot`
+The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC.
+The Johnson-Neyman interval is [`r h2b_jn.int`].
+Consequently, the slope of n-back level is not significant for individuals with very low NFC values.
+`r h2b_jn.plot`
 

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd
implemented all changes for complete pipeline dfs

--- 2021-12-13 06_Paper/COG-ED/Manuscript.Rmd
@@
 
+  # change the name of a subject (it has the suffix "_neu" because the paradigm didn't start properly the first time)
+
+  data_nback$subject[data_nback$subject == "E12K08_neu"] <- "E12K08"
+  data_ED$subject[data_ED$subject == "E12K08_neu"] <- "E12K08"
+
   # replace some columns with 'easy to work with' values
@@
   }
+
+```
+
+```{r NFCcomputation, echo=FALSE, message=FALSE, warning=FALSE}
+
+  # prepare temporary data frame for loop to feed into
+
+  data_nfc <- data.frame(subject = character(), nfc = double())
+
+  # compute index of rows in which the data sets change
+
+  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))
+
+  # calculate NFC scores for every subject
+
+  for (i in 1:(length(setindex)-1)) {
+
+    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
+
+    # define and invert items to be recoded
+
+    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1
+
+    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
+                                           nfc = sum(nfc)))
+  }
+
+  # add the NFC scores trial-wise to the nback-data-frame for the multi-level-model
+
+  for (i in 1:nrow(data_nback)) {
+
+    data_nback$nfc[i] <- data_SV$nfc[data_SV$subject == data_nback$subject[i]]
+
+  }
+
+  # remove the temporary variables
+
+  remove(nfc, data_nfc)
 
@@
 
-    # replace the RTs of incorrect trials with NA for better handling
-
-    pipelines_data[[i]]$rt[pipelines_data[[i]]$correct == 0] <- NA
-
     # the first decision is whether transformations and exclusions will be applied across/within subjects/levels
@@
 
-            pipelines_data[[i]]$rt <- log10(pipelines_data[[i]]$rt)
+            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-            pipelines_data[[i]]$rt <- 1/(pipelines_data[[i]]$rt)
+            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-            pipelines_data[[i]]$rt <- sqrt(pipelines_data[[i]]$rt)
+            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
           }
@@
 
-          pipemedian <- median(pipelines_data[[i]]$rt, na.rm = TRUE)
-          pipemad <- mad(pipelines_data[[i]]$rt, na.rm = TRUE)
+          pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
+          pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
 
@@
 
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 2 * pipemad)
-                                                               & pipelines_data[[i]]$rt > (pipemedian - 2 * pipemad))), ]
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2 * pipemad)
+                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2 * pipemad))), ]
 
@@
 
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 2.5 * pipemad)
-                                                               & pipelines_data[[i]]$rt > (pipemedian - 2.5 * pipemad))), ]
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2.5 * pipemad)
+                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2.5 * pipemad))), ]
           } else if (pipeline_name[[1]][4] == "3") {
 
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt < (pipemedian + 3 * pipemad)
-                                                               & pipelines_data[[i]]$rt > (pipemedian - 3 * pipemad))), ]
+            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 3 * pipemad)
+                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 3 * pipemad))), ]
           }
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
-            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x], na.rm = TRUE)
+            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
+            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
 
@@
 
-              ifelse(length(which(pipelines_data[[i]]$level == x &
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                       (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
@@
 
-              ifelse(length(which(pipelines_data[[i]]$level == x &
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                     (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
@@
 
-              ifelse(length(which(pipelines_data[[i]]$level == x &
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                     (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                     & pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                                                                                                   & pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
+                                       pipelines_data[[i]]$subject == pipesubject] <-
+                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
+                                       pipelines_data[[i]]$subject == pipesubject] <-
+                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
 
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                     & pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                                                                                                & pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
+                                       pipelines_data[[i]]$subject == pipesubject] <-
+                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
+                                       pipelines_data[[i]]$subject == pipesubject] <-
+                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
 
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                     & pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x
-                                                                                                                  & pipelines_data[[i]]$subject == pipesubject])
-
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
+                                       pipelines_data[[i]]$subject == pipesubject] <-
+                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
+                                       pipelines_data[[i]]$subject == pipesubject] <-
+                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
             }
@@
 
-            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
-            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
 
@@
 
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                       (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
@@
 
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                       (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
@@
 
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                       (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- 1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject] <- sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
+                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
+              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
+                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
 
@@
 
-            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
-            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
+            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
+            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
 
@@
 
-              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
+              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                       (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
@@
 
-              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
+              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                       (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
@@
 
-              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject &
+              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                     (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                      pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject &
+                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                       (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
@@
 
-      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ]) > 0,
-             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1)), ],
+      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ]) > 0,
+             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ],
              pipelines_data[[i]] <- pipelines_data[[i]])
@@
 
-      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ]) > 0,
-             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2)), ],
+      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ]) > 0,
+             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ],
              pipelines_data[[i]] <- pipelines_data[[i]])
@@
 
-    medianrt <- median(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
+    medianrt <- median(pipelines_data[["AARO"]]$rt[which(pipelines_data[["AARO"]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                  +(levelindex[i]-1)], na.rm = TRUE)
 
-    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
-                          level = data_RT$level[levelindex[i]],
+    newdata <- data.frame(subject = pipelines_data[["AARO"]]$subject[levelindex[i]],
+                          level = pipelines_data[["AARO"]]$level[levelindex[i]],
                           medianrt = medianrt)
@@
 
-      # make a temporary copy of the rt data frame without 1-back
+      # make a temporary copy of the data frame without 1-back
 
@@
 
-      remove(h1b_data)
+      remove(h1b_data, rt)
 
@@
 
-  # make a temporary copy of the SV data frame
-
-  h2a_data <- data_SV
+  # make a temporary copy of the data frame
+
+  h2a_data <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
   h2a_data$level <- as.factor(h2a_data$level)
@@
 
-  h2b_data <- merge(dprime[c("subject", "level", "d")], data_nback, by = c("subject", "level"))
-
-  # prepare temporary nfc-data frame for loop to feed into
-
-  data_nfc <- data.frame(subject = character(), nfc = double())
-
-  # calculate NFC scores for every subject
-
-  for (i in 1:(length(setindex)-1)) {
-
-    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
-    # define and invert items to be recoded
-    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1
-
-    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
-                                           nfc = sum(nfc)))
-  }
-  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"
-
-  h2b_data <- merge(h2b_data, data_nfc, by = "subject")
+  h2b_data <- pipelines_data[["AARO"]]
 
@@
   h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
-                               subset = !is.na(rt)
-                               & rt > 0.1))
+                               subset = !is.na(rt)))
 
@@
 
+  # make a temporary copy of the data frame
+
+  data_SV <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
+  data_SV$level <- as.factor(data_SV$level)
+
   # create an index for the rows in which the participant ID changes
@@
 
-  # prepare temporary data frame for loop to feed into
-
-  data_nfc <- data.frame(subject = character(), nfc = double())
-
-  # calculate NFC scores for every subject
-
-  for (i in 1:(length(setindex)-1)) {
-
-    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
-    # define and invert items to be recoded
-    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1
-
-    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
-                                           nfc = sum(nfc)))
-  }
-
-  # merge the NFC data frame into the AUC data frame by row
-
-  h3_data <- merge(h3_data, data_nfc)
-
-  # delete temporary variables
-
-  remove(nfc, data_nfc)
+  # add NFC values to data frame
+
+  for (i in 1:(nrow(h3_data))) {
+
+    h3_data$nfc[i] <- pipelines_data[["AARO"]]$nfc[pipelines_data[["AARO"]]$subject == h3_data$subject[i]]
+
+  }
 

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd

@@
   library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
+  library(sjPlot)       # plot MLM model fit
+  library(kableExtra)   # 
+  library(interactions) # for simple slopes analysis
+  library(huxtable)     # create huxtable
 
@@
   data_nback$postcorrect[c(1,seq(64,length(data_nback$postcorrect),64))] <- 1
+
+  # correct subject code
+  data_nback$subject[which(data_nback$subject == "E12K08_neu")] <- "E12K08"
+  data_ED$subject[which(data_ED$subject == "E12K08_neu")] <- "E12K08"
 
@@
 
-  # get subset for MLM
-
-  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
+  # get subset for MLM without RT = NA
+
+  h2b_data <- droplevels(subset(h2b_data[c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
                                subset = !is.na(rt)))
@@
 
-The multilevel model `r replication_table`
-
-statistically significant effect of n-back load level `r apa_print(m1_h2b)$full_result$level_cwc`
-controlled for performance and correct and post-correct answers
-
-`r apa_print(m1_h2b)$full_result$nfc_cgm`
+N-back level is a reliable predictor of subjective value (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (signal detection d’ and reaction time) as well as correct and post-correct answers.
+The results of the multilevel model are detailed in Table X. 
+`r replication_table`
 `r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).
-
-simple slopes analysis `r h2b_ssa.table`, `r h2b_jnplot`,`r h2b_ssa.plot`
-statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC
+However, NFC has no statistically significant effect on subjective value (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
+The simple slopes analysis revealed a significant slope of n-back level for three different expressions of NFC (Table X, Figure X).
+`r h2b_ss.table`
+`r h2b_ss.plot`
+The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC.
+The Johnson-Neyman interval is [`r h2b_jn.int`].
+Consequently, the slope of n-back level is not significant for individuals with very low NFC values.
+`r h2b_jn.plot`
+
+## alternative: `r h2b_jn`
 

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd
fixed some bugs

@@
   library(sjPlot)       # plot MLM model fit
-  library(kableExtra)   # 
+  library(kableExtra)   # for great tables in R Markdown
   library(interactions) # for simple slopes analysis
   library(huxtable)     # create huxtable
+  library(glmmTMB)      # from the glmmTMB package for multi level models
 
@@
 
-    data_nback$nfc[i] <- data_SV$nfc[data_SV$subject == data_nback$subject[i]]
+    data_nback$nfc[i] <- data_nfc$nfc[data_nfc$subject == data_nback$subject[i]]
 
@@
 
-  h2b_data <- droplevels(subset(h2b_data[c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
+  h2b_data <- droplevels(subset(h2b_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
                                subset = !is.na(rt)))
@@
   data_SV <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
-  data_SV$level <- as.factor(data_SV$level)
 
@@
     newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
-                          axauc = auc(data_SV$level[subjectindex[i]:(subjectindex[i]+3)], data_SV$sv[subjectindex[i]:(subjectindex[i]+3)],
-                                               method = "trapezoid") * ((data_SV$sv[subjectindex[i]+3] - data_SV$sv[subjectindex[i]+2]) +
+                          axauc = auc(data_SV$level[subjectindex[i]:(subjectindex[i]+3)], data_SV$sv[subjectindex[i]:(subjectindex[i]+3)], method = "trapezoid") *
+                            ((data_SV$sv[subjectindex[i]+3] - data_SV$sv[subjectindex[i]+2]) +
                                (data_SV$sv[subjectindex[i]+2] - data_SV$sv[subjectindex[i]+1]) +

### 2022-01-03 06_Paper/ER-ED/method.Rmd

@@
 # store ED data in data_ED frame
-for (i in 1:length(datalist_ED)) {
+#for (i in 1:length(datalist_ED)) {
 
-  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
-                   datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
-                   datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
-                   datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
-                   datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
-                   datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
-                   datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
+#  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
+#                   datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
+#                   datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
+#                   datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
+#                   datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
+#                   datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
+#                   datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
 
-  colnames(tmp) = names(data_ED)
-  data_ED = rbind(data_ED, tmp)
-}
+#  colnames(tmp) = names(data_ED)
+#  data_ED = rbind(data_ED, tmp)
+#}
 

### 2022-01-03 06_Paper/COG-ED/Manuscript.Rmd
changed typo

@@
 
-  # calculate mean reaction time per participant per level
+  # calculate median reaction time per participant per level
 
@@
 
-  # ANOVA with three linear contrasts, contrasting the mean rt of two n-back levels (2,3,4) at a time
+  # ANOVA with three linear contrasts, contrasting the median rt of two n-back levels (2,3,4) at a time
 
@@
       hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
-      hypothesis1c_peformance_contrasts <- pairs(hypothesis1c_emm)
+      hypothesis1c_performance_contrasts <- pairs(hypothesis1c_emm)
 

### 2022-01-04 06_Paper/COG-ED/Manuscript.Rmd
corrected typos

@@
 Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
-Ratings on the physical load and the performance subscales only increased between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r`apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and`r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
+Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
 Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
@@
 `r h2b_ss.plot`
-The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC.
-The Johnson-Neyman interval is [`r h2b_jn.int`].
+The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC. The Johnson-Neyman interval is [`r h2b_jn.int`].
 Consequently, the slope of n-back level is not significant for individuals with very low NFC values.    

### 2022-01-05 06_Paper/COG-ED/Manuscript.Rmd
started adding Bayes factors

@@
   library(glmmTMB)      # from the glmmTMB package for multi level models
+  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
 
@@
 
+  # get Bayes factor
+
+  hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
+
   # remove the temporary variable
@@
 
+  # get Bayes factor
+
+  hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)
+
   # remove the temporary variable
@@
 
-  for (i in 1:(length(setindex)-1)) {
+  for (i in c(1:5,7:(length(setindex)-1))) { # we exclude the sixth subject (ID F30T02) here, because their NTLX data for n = 1 is missing
 
@@
 
+  # get Bayes factors
+
+  hypothesis1c_mental_BF <- anovaBF(formula = mental ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_physical_BF <- anovaBF(formula = physical ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_time_BF <- anovaBF(formula = time ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_performance_BF <- anovaBF(formula = performance ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_effort_BF <- anovaBF(formula = effort ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_frustration_BF <- anovaBF(formula = frustration ~ level, data = h1c_data, progress = FALSE)
+
   # remove the temporary variable
@@
   hypothesis2a_contrasts <- pairs(hypothesis2a_emm)
+
+  # get Bayes factor
+
+  hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
 
@@
 
-  # H3a: Subjective values predict individual NCS scores.
+  # H3a: Subjective values positively predict individual NCS scores.
 
@@
 
-  # H3b: NASA-TLX scores do not predict individual NCS scores.
+  # H3b: NASA-TLX scores negatively predict individual NCS scores.
 

### 2022-01-06 06_Paper/COG-ED/Manuscript.Rmd
finished adding BFs & changed apa_print functions

@@
 
-A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 40 participants, assuming $f=0.27$, $\alpha=.05$, $\beta=.80$, and no correlation between levels.
+A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 53 participants, assuming $f=0.20$, $\alpha=.05$, and $\beta=.95$.
 
@@
       h1a_data <- pipelines_data[["AARN"]][pipelines_data[["AARN"]]$level != 1, ]
+      h1a_data <- unique(h1a_data[ ,c("subject","level","dprime")])
       h1a_data$level <- as.factor(h1a_data$level)
@@
 
-      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)
-
-  # get Bayes factor
+      hypothesis1a_contrasts <- as.data.frame(pairs(hypothesis1a_emm))
+
+  # get Bayes factors
 
   hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
+  hypothesis1a_contrasts$BF10 <- c(extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf)
 
@@
 
-### Associations of subjective and objective task load measures
-
+We collected data from $N = 16$ participants,
+One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 15 complete data sets.
 Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).
@@
 
-      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)
-
-  # get Bayes factor
+      hypothesis1b_contrasts <- as.data.frame(pairs(hypothesis1b_emm))
+
+  # get Bayes factors
 
   hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)
+  hypothesis1b_contrasts$BF10 <- c(extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 3], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf)
 
@@
 However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
-RTs were longer for 3- than 2-back (`r apa_print(hypothesis1b_contrasts)$statistic[1]`), but not different between 2- and 4-back or 3- and 4-back.
+RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level"))[1]`), but not different between 2- and 4-back or 3- and 4-back.
 Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.
@@
       hypothesis1c_emm <- emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
-      hypothesis1c_mental_contrasts <- pairs(hypothesis1c_emm)
+      hypothesis1c_mental_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
 
       hypothesis1c_emm <- emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
-      hypothesis1c_physical_contrasts <- pairs(hypothesis1c_emm)
+      hypothesis1c_physical_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
 
       hypothesis1c_emm <- emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
-      hypothesis1c_time_contrasts <- pairs(hypothesis1c_emm)
+      hypothesis1c_time_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
 
       hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
-      hypothesis1c_performance_contrasts <- pairs(hypothesis1c_emm)
+      hypothesis1c_performance_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
 
       hypothesis1c_emm <- emmeans(object = hypothesis1c_effort_rmanova$aov, specs = "level")
-      hypothesis1c_effort_contrasts <- pairs(hypothesis1c_emm)
+      hypothesis1c_effort_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
 
       hypothesis1c_emm <- emmeans(object = hypothesis1c_frustration_rmanova$aov, specs = "level")
-      hypothesis1c_frustration_contrasts <- pairs(hypothesis1c_emm)
+      hypothesis1c_frustration_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
 
@@
   hypothesis1c_mental_BF <- anovaBF(formula = mental ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_mental_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 2], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 3], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf)
   hypothesis1c_physical_BF <- anovaBF(formula = physical ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_physical_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 2], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf)
   hypothesis1c_time_BF <- anovaBF(formula = time ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_time_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 2], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 3], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf)
   hypothesis1c_performance_BF <- anovaBF(formula = performance ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_performance_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 2], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 3], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf)
   hypothesis1c_effort_BF <- anovaBF(formula = effort ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_effort_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf)
   hypothesis1c_frustration_BF <- anovaBF(formula = frustration ~ level, data = h1c_data, progress = FALSE)
+  hypothesis1c_frustration_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 2], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 3], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf)
 
@@
 Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
-Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
+Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X3`, and `r apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X4`, and `r `apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X4`, respectively).
 Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
@@
 
-  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)
-
-  # get Bayes factor
+  hypothesis2a_contrasts <- as.data.frame(pairs(hypothesis2a_emm))
+
+  # get Bayes factors
 
   hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
+  hypothesis2a_contrasts$BF10 <- c(extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf)
 
@@
 
-### Changes in subjective values depending on n-back level
-
 The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
-SVs were higher for 1- than 3-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X3`), for 1- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(hypothesis2a_contrasts)$statistic$X2_X4`).
+SVs were higher for 1- than 3-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X3`), for 1- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X2_X4`).
 Importantly, the lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
@@
 
-  replication_table <-
+  table_1 <-
     kbl(h2b_result.table,
@@
 
-### Changes in subjective values depend reliably on n-back level
-
-N-back level is a reliable predictor of subjective value (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (signal detection d’ and reaction time) as well as correct and post-correct answers.
-The results of the multilevel model are detailed in Table X. 
-`r replication_table`
-`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).
-However, NFC has no statistically significant effect on subjective value (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
-The simple slopes analysis revealed a significant slope of n-back level for three different expressions of NFC (Table X, Figure X).
+The MLM revealed that n-back level was a reliable predictor of SV (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers.
+The results of the MLM are detailed in Table 1. 
+`r table_1`
+Differences between subjects could explain `r round((icc_h2b*100), digits = 0)` % of the total variance in SVs ($ICC =$ `r round(icc_h2b, digits = 2)`).
+However, NFC had no statistically significant effect on SVs (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
+The simple slopes analysis revealed a significant difference in slope of n-back level for three different expressions of NFC (Table 2, Figure 2).
 `r h2b_ss.table`
 `r h2b_ss.plot`
-The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC. The Johnson-Neyman interval is [`r h2b_jn.int`].
-Consequently, the slope of n-back level is not significant for individuals with very low NFC values.    
+The Johnson-Neyman plot (Figure 2) visualizes the significance of the slope of n-back level at different values of NFC.
+The Johnson-Neyman interval is [`r h2b_jn.int`].
+Consequently, the slope of n-back level was not significant for individuals with very low NFC values.    
 `r h2b_jn.plot`
@@
   hypothesis3a <- summary(lm(h3_data$nfc ~ h3_data$axauc))
+
+  # get Bayes factor
+
+  hypothesis3a_BF <- regressionBF(formula = nfc ~ axauc, data = h3_data, progress = FALSE)
 
@@
 
+  # get Bayes factor
+
+  hypothesis3b_BF <- regressionBF(formula = nfc ~ axauc + auc_ntlx, data = h3_data, progress = FALSE)
+
 ```

### 2022-01-07 06_Paper/COG-ED/Manuscript.Rmd
removed subheadings
made BF ttests paired

@@
 
-## Effort discounting and Need for Cognition
-
 The individual degree of ED in the study by Westbrook et al.
@@
 On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.
-
-## Revising the COG-ED paradigm
 
@@
 
-## Hypotheses
-
-Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
+Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013], and detailed in the attached design table..
 Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
@@
 
+The results of each analysis will be assessed on the basis of both *p*-value and the Bayes factor $BF10$.
+
 ## Power analysis
@@
   hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
-  hypothesis1a_contrasts$BF10 <- c(extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE))$bf)
+  hypothesis1a_contrasts$BF10 <- c(extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3],
+                                                     progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
 
@@
   hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)
-  hypothesis1b_contrasts$BF10 <- c(extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 3], y = h1b_data$medianrt[h1b_data$level == 4], progress = FALSE))$bf)
+  hypothesis1b_contrasts$BF10 <- c(extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 3],
+                                                     progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 3], y = h1b_data$medianrt[h1b_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
 
@@
   hypothesis1c_mental_BF <- anovaBF(formula = mental ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_mental_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 2], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 3], y = h1c_data$mental[h1c_data$level == 4], progress = FALSE))$bf)
+  hypothesis1c_mental_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 2],
+                                                            progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 3], y = h1c_data$mental[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
   hypothesis1c_physical_BF <- anovaBF(formula = physical ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_physical_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 2], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE))$bf)
+  hypothesis1c_physical_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 2],
+                                                              progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
   hypothesis1c_time_BF <- anovaBF(formula = time ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_time_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 2], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 3], y = h1c_data$time[h1c_data$level == 4], progress = FALSE))$bf)
+  hypothesis1c_time_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 2],
+                                                          progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 3], y = h1c_data$time[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
   hypothesis1c_performance_BF <- anovaBF(formula = performance ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_performance_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 2], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 3], y = h1c_data$performance[h1c_data$level == 4], progress = FALSE))$bf)
+  hypothesis1c_performance_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 2],
+                                                                 progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 3], y = h1c_data$performance[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
   hypothesis1c_effort_BF <- anovaBF(formula = effort ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_effort_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE))$bf)
+  hypothesis1c_effort_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2],
+                                                            progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
   hypothesis1c_frustration_BF <- anovaBF(formula = frustration ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_frustration_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 2], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 3], y = h1c_data$frustration[h1c_data$level == 4], progress = FALSE))$bf)
+  hypothesis1c_frustration_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 2],
+                                                                 progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 3], y = h1c_data$frustration[h1c_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
 
@@
   hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
-  hypothesis2a_contrasts$BF10 <- c(extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4], progress = FALSE))$bf)
+  hypothesis2a_contrasts$BF10 <- c(extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2],
+                                                     progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf,
+                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4],
+                                                   progress = FALSE, paired = TRUE))$bf)
 

### 2022-01-07 06_Paper/COG-ED/Manuscript.Rmd
updated csl file

@@
 wordcount         : "X"
-bibliography      : ref_COG-ED.bib
+bibliography      : CERED.bib
 floatsintext      : no
@@
 output            : papaja::apa6_pdf
-csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
+csl               : nature.csl
 header-includes   :
@@
 The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
+We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.
 The R Markdown file used to analyze the data and write this document is freely available at github.com/ChScheffel/CERED.

### 2022-01-07 06_Paper/COG-ED/Manuscript.Rmd
updated ref to Singmann

@@
 Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2017]. 
+To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
 Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
BFs for MLM added

@@
   library(huxtable)     # create huxtable
-  library(glmmTMB)      # from the glmmTMB package for multi level models
+# library(glmmTMB)      # from the glmmTMB package for multi level models
   library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
@@
 
+  # get Bayes factors ----------------------------------------------------------
+
+  # the random factor needs to be a factor
+  h2b_data$subject <- factor(h2b_data$subject)
+
+  # H2b
+  h2b_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
+                      data = h2b_data, whichRandom = 'subject')
+  h2b_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
+                      data = h2b_data, whichRandom = 'subject')
+  h2b_BF <- h2b_full_BF / h2b_null_BF
+
+  # H2c
+  h2c_full_BF <- lmBF(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
+                      data = h2b_data, whichRandom = 'subject')
+  h2c_null_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
+                      data = h2b_data, whichRandom = 'subject')
+  h2c_BF <- h2c_full_BF / h2c_null_BF
+
   # prepare MLM results for reporting ------------------------------------------

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
changed some tenses and updated order of methods

--- 2022-01-07 06_Paper/COG-ED/Manuscript.Rmd
@@
   - name          : "Josephine Zerna"
+    orcid         : "0000-0003-2892-884X"
     affiliation   : "1,*"
@@
   - name          : "Christoph Scheffel"
+    orcid         : "0000-0001-5963-9229"
     affiliation   : "1,*"
@@
 We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.
-The R Markdown file used to analyze the data and write this document is freely available at github.com/ChScheffel/CERED.
-The data can be downloaded from osf.io/vnj8x/.
-
-## Questionnaires
-
-To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
+
+## Ethics information
+
+## Pilot data
+
+The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
+
+## Design
+
+Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015].
+Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
 NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
@@
 Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
-A full list of measures can be found at osf.io/vnj8x/.
-
-## Procedure
-
-Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015].
-Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
+A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
 In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
@@
 The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
+To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
 After each level, participants fill out the NASA-TLX on a tablet.
@@
 Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
-The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
-In the pilot study, the online questionnaires were completed after the two lab sessions, but we will change this as described above, so that the participants do not have to come in again to collect their money or course credit.
-
-## Analysis
-
+
+## Sampling plan
+
+A sample size analysis with G*Power [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
+[-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
+The power analyses of all other hypotheses yielded smaller necessary sample sizes.
+To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 60 to 70 participants.
+
+## Analysis plan
+
+Data collection and analysis will not be performed blind to the conditions of the experiments.
 We aim to conduct all analysis as described in Westbrook et al.
@@
 To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
-We apply restricted maximum likelihood (REML) to fit the model.
-First, we calculate the intraclass correlation (ICC) on the basis of the null model.
-Second, we estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
-Within the model, we control for *d'*, RT, correct and post-correct trials.
+We will apply restricted maximum likelihood (REML) to fit the model.
+First, we will calculate the intraclass correlation (ICC) on the basis of the null model.
+Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+Within the model, we will control for *d'*, RT, correct, and post-correct trials.
 $$
@@
 $$
-Level-1-predictors are centered within cluster, whereas the level-2-predictor is centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
-We visually inspect the residuals of the final model.
+Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
+We will visually inspect the residuals of the final model.
 The approximately normal distribution indicates no evidence to perform model criticism.  
-Third, we perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
-To evaluate the moderating effect, we calculate the Johnson-Neyman interval.
-
-To ensure the validity of the multi-level model, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
+Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
+To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
+
+To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
 These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3 $MAD$ from the median, RTs below 100 or 200 ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
-The multi-level model will be run with each of the 63 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms).
+The MLM will be run with each of the 63 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms).
 The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
@@
 
-The results of each analysis will be assessed on the basis of both *p*-value and the Bayes factor $BF10$.
-
-## Power analysis
-
-A sample size analysis with GPower [@Faul2007; @Faul2009], using the pilot RT data, indicated that we should collect data from at least 53 participants, assuming $f=0.20$, $\alpha=.05$, and $\beta=.95$.
+The results of each analysis will be assessed on the basis of both *p*-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].
+
+## Data availability
+
+The data of this study can be downloaded from osf.io/vnj8x/.
+
+## Code availability
+
+The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
 
@@
 
-# Acknowledgements
-
 # References
@@
 
+\newpage
+
+# Acknowledgements
+
+This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
+The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+
+# Author Contributions
+
+# Competing Interests
+
+The authors declare no competing interests.
+
+\newpage
+
+# Figure Captions
+
+\newpage
+
+# Design Table
+
+\newpage
+
+# Supplement
+
 \endgroup

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
excluded subject M28B11

@@
 
+  # remove one subject who did not understand the instructions of the n-back task and reacted only to every n-th stimulus
+
+  data_nback <- data_nback[data_nback$subject != "M28B11", ]
+  data_ED <- data_ED[data_ED$subject != "M28B11", ]
+
   # replace some columns with 'easy to work with' values
@@
   colnames(data_quest)[1] <- "set" # rename the first column
+
+  # remove the subject who misunderstood the instruction
+
+  data_quest <- data_quest[data_quest$set != "M28B11", ]
 
@@
 
-The sample of the pilot study consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
+The sample of the pilot study consisted of $N=$ `r length(setindex)` participants (`r round((table(data_quest$gender)[2]/length(setindex))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
+One participant's data was removed because they misunderstood the instruction.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=$ `r length(setindex)-1` data sets.
 
@@
 
+  # compute index of rows in which the levels change
+
+  levelindex <- c(1,which(pipelines_data[["AARO"]]$level != dplyr::lag(pipelines_data[["AARO"]]$level)),nrow(pipelines_data[["AARO"]]))
+
   # calculate median reaction time per participant per level

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
put full pilot results in supplementary

@@
 
-  # H1a: Performance measured by signal detection d’ declines with increasing n-back level.
+  # H1a: The signal detection measure d’ declines with increasing n-back level.
 
@@
 
-  # H1b: Performance measured by reaction time declines with increasing n-back level.
+  # H1b: Reaction time increases with increasing n-back level.
 
@@
   row.names(h2b_result.table) <- NULL
-  h2b_result.table$Parameter[1:6] <- c("Intercept", "N-Back Level", "NFC", "d'", "RT", "Level x NFC")
+  h2b_result.table$Parameter[1:6] <- c("Intercept", "n-back level", "NFC", "d'", "RT", "level x NFC")
 
@@
     caption = "Effects of n-back load level on subjective value controlled 
-    for task performance (d’ and reaction time), correct and postcorrect trials.",
+    for task performance (d' and reaction time), correct and postcorrect trials.",
     booktabs = T,                          # no vertical lines
@@
 
+## Results of the pilot study
+
+### Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis1a_rmanova)$full_result`
+
+Paired contrasts:
+
+`r hypothesis1a_contrasts`
+
+### Hypothesis 1b: Reaction time increases with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis1b_rmanova)$full_result`
+
+Paired contrasts:
+
+`r hypothesis1b_contrasts`
+
+### Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
+
+Mental subscale ANOVA:
+
+`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_mental_BF)$bf`
+
+Mental subscale paired contrasts:
+
+`r hypothesis1c_mental_contrasts`
+
+Physical subscale ANOVA:
+
+`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_physical_BF)$bf`
+
+Physical subscale paired contrasts:
+
+`r hypothesis1c_physical_contrasts`
+
+Time subscale ANOVA:
+
+`r apa_print(hypothesis1c_time_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_time_BF)$bf`
+
+Time subscale paired contrasts:
+
+`r hypothesis1c_time_contrasts`
+
+Performance subscale ANOVA:
+
+`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_performance_BF)$bf`
+
+Performance subscale paired contrasts:
+
+`r hypothesis1c_performance_contrasts`
+
+Effort subscale ANOVA:
+
+`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`
+
+Effort subscale paired contrasts:
+
+`r hypothesis1c_effort_contrasts`
+
+Frustration subscale ANOVA:
+
+`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`
+
+Frustration subscale paired contrasts:
+
+`r hypothesis1c_frustration_contrasts`
+
+### Hypothesis 2a: Subjective values decline with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis2a_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis2a_BF)$bf`
+
+Paired contrasts:
+
+`r hypothesis2a_contrasts`
+
+### Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
+
+Multi level model:
+
+`r table_1`
+
+### Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
+
+Simple slopes analysis:
+
+`r h2b_ss.table`
+
+Johnson-Neyman intervals:
+
+`r h2b_jn.int`
+
+### Hypothesis 3a: Subjective values positively predict individual NCS scores.
+
+Intercept:
+`r apa_print(hypothesis3a)$estimate$Intercept`
+
+Predictor $AxAUC$:
+`r apa_print(hypothesis3a)$estimate$h3_data_axauc`
+
+Fit:
+`r apa_print(hypothesis3a)$estimate$modelfit$r2`
+
+$BF10=$ `r extractBF(hypothesis3a_BF)$bf`
+
+### Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.
+
+Intercept:
+`r apa_print(hypothesis3b)$estimate$Intercept`
+
+Predictor $AxAUC$:
+`r apa_print(hypothesis3b)$estimate$h3_data_axauc`
+
+Predictor AUC NASA-TLX:
+`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`
+
+Fit:
+`r apa_print(hypothesis3a)$estimate$modelfit$r2`
+
+$BF10=$ `r extractBF(hypothesis3b_BF)$bf`
+
 \endgroup

### 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
added plot to supplementary
started setting up the SCA

@@
 However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
-RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level"))[1]`), but not different between 2- and 4-back or 3- and 4-back.
+RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level")))[1]`), but not different between 2- and 4-back or 3- and 4-back.
 Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.
@@
 
+```{r SpecificationCurveAnalysis, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
+
+  # Here we repeat the multi level model with all analysis pipelines.
+
+  for (i in 1:length(pipelines_data)) {
+
+    # make a temporary copy of the data frame
+
+    sca_data <- pipelines_data[[i]]
+
+    # get a subset without RT = NA
+
+    sca_data <- droplevels(subset(sca_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")], subset = !is.na(rt)))
+
+    # center the predictors
+
+        # centering the level 1 predictors (d', RT, level, correct, postcorrect) within cluster
+
+        sca_data$dprime.cwc       <- sca_data$dprime - (ave(sca_data$dprime, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
+        sca_data$rt.cwc           <- sca_data$rt - (ave(sca_data$rt, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
+        sca_data$level.cwc        <- sca_data$level - (ave(sca_data$level, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
+        sca_data$correct.cwc      <- sca_data$correct - (ave(sca_data$correct, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
+        sca_data$postcorrect.cwc  <- sca_data$postcorrect - (ave(sca_data$postcorrect, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
+
+        # centering the level 2 predictor NFC at the grand mean
+
+        sca_data$nfc.cgm <- scale(sca_data$nfc, scale = F)
+
+    # define the null model
+
+    m0_sca <- lmer(sv ~ 1 + (1|subject), data = sca_data, REML = T)
+
+    # intra-class-correlation
+
+    var_m0_sca <- as.data.frame(VarCorr(m0_sca))
+    icc_sca <- var_m0_sca$vcov[1] / (var_m0_sca$vcov[1] + var_m0_sca$vcov[2])
+
+  }
+
+  # random slopes model --------------------------------------------------------
+
+  ## maximal model ---- 
+  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
+                 data = h2b_data,
+                 REML = T) # parameters estimated by restricted log-likelihood maximization
+
+  ## plot model fit of the final model ----
+  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
+
+  # prepare MLM results for reporting ------------------------------------------
+
+  # get random and fixed effects
+  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
+  m1_h2b.fixef <- summary(m1_h2b)$coefficients
+
+  # prepare table
+  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef[-c(6,7),]), 
+                                          m1_h2b.fixef[-c(6,7),c(1, 2, 5)]))
+  h2b_result.table$ranef.sd <- NA
+  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
+
+  colnames(h2b_result.table)[1] <- "Parameter"
+  colnames(h2b_result.table)[2] <- "Beta"
+  colnames(h2b_result.table)[3] <- "$SE$"
+  colnames(h2b_result.table)[4] <- "$p$-value"
+  colnames(h2b_result.table)[5] <- "Random Effects (SD)"
+
+  row.names(h2b_result.table) <- NULL
+  h2b_result.table$Parameter[1:6] <- c("Intercept", "n-back level", "NFC", "d'", "RT", "level x NFC")
+
+  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
+  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
+  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)
+
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
+    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
+    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
+    paste0("<.001***")
+
+  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")
+
+  table_1 <-
+    kbl(h2b_result.table,
+    caption = "Effects of n-back load level on subjective value controlled 
+    for task performance (d' and reaction time), correct and postcorrect trials.",
+    booktabs = T,                          # no vertical lines
+    escape = F,                            # correctly print special characters)
+    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
+            escape = F,                    # correctly print special characters
+            threeparttable = T)            # line breaks in the footnote
+
+  # simple slopes analysis -----------------------------------------------------
+
+  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
+                    cond.int = T,                       # print conditional intercepts
+                    control.fdr = T)                    # adjust false discovery rate
+
+  #create table
+  h2b_ss.table <- as_huxtable(m1_h2b.ss)
+  h2b_ss.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
+  h2b_ss.table <- h2b_ss.table[-2,]
+  h2b_ss.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
+
+  # calculate Johnson-Neyman intervals
+  h2b_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
+  h2b_jn.int <- h2b_jn$bounds
+
+  # save plot
+  h2b_jn.plot <- h2b_jn$plot
+
+  # create interaction plot
+  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                               plot.points = T, point.shape = T,
+                               x.label = "n back level", y.label = "subjective value",
+                               legend.main = "NFC", interval = T) + theme_apa()    
+```
+
 The MLM revealed that n-back level was a reliable predictor of SV (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers.
@@
 `r h2b_ss.table`
+`r h2b_ss.plot`
 

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
finished loop for SCA (BF10 still missing tho)

--- 2022-01-10 06_Paper/COG-ED/Manuscript.Rmd
@@
 
-  # Here we repeat the multi level model with all analysis pipelines.
+  # here we repeat the multi level model with all analysis pipelines
+
+  # prepare empty data frame for the loop to feed into
+
+  sca_results <- data.frame(pipeline = character(), beta_level = double(), p_level = double(),
+                            beta_nfc = double(), p_nfc = double())
 
@@
 
-    # intra-class-correlation
-
-    var_m0_sca <- as.data.frame(VarCorr(m0_sca))
-    icc_sca <- var_m0_sca$vcov[1] / (var_m0_sca$vcov[1] + var_m0_sca$vcov[2])
-
-  }
-
-  # random slopes model --------------------------------------------------------
-
-  ## maximal model ---- 
-  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
-                 data = h2b_data,
-                 REML = T) # parameters estimated by restricted log-likelihood maximization
-
-  ## plot model fit of the final model ----
-  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
-
-  # prepare MLM results for reporting ------------------------------------------
-
-  # get random and fixed effects
-  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
-  m1_h2b.fixef <- summary(m1_h2b)$coefficients
-
-  # prepare table
-  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef[-c(6,7),]), 
-                                          m1_h2b.fixef[-c(6,7),c(1, 2, 5)]))
-  h2b_result.table$ranef.sd <- NA
-  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
-
-  colnames(h2b_result.table)[1] <- "Parameter"
-  colnames(h2b_result.table)[2] <- "Beta"
-  colnames(h2b_result.table)[3] <- "$SE$"
-  colnames(h2b_result.table)[4] <- "$p$-value"
-  colnames(h2b_result.table)[5] <- "Random Effects (SD)"
-
-  row.names(h2b_result.table) <- NULL
-  h2b_result.table$Parameter[1:6] <- c("Intercept", "n-back level", "NFC", "d'", "RT", "level x NFC")
-
-  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
-  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
-  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)
-
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
-    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
-    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
-    paste0("<.001***")
-
-  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")
-
-  table_1 <-
-    kbl(h2b_result.table,
-    caption = "Effects of n-back load level on subjective value controlled 
-    for task performance (d' and reaction time), correct and postcorrect trials.",
-    booktabs = T,                          # no vertical lines
-    escape = F,                            # correctly print special characters)
-    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
-            escape = F,                    # correctly print special characters
-            threeparttable = T)            # line breaks in the footnote
-
-  # simple slopes analysis -----------------------------------------------------
-
-  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
-                    cond.int = T,                       # print conditional intercepts
-                    control.fdr = T)                    # adjust false discovery rate
-
-  #create table
-  h2b_ss.table <- as_huxtable(m1_h2b.ss)
-  h2b_ss.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
-  h2b_ss.table <- h2b_ss.table[-2,]
-  h2b_ss.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
-
-  # calculate Johnson-Neyman intervals
-  h2b_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
-  h2b_jn.int <- h2b_jn$bounds
-
-  # save plot
-  h2b_jn.plot <- h2b_jn$plot
-
-  # create interaction plot
-  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                               plot.points = T, point.shape = T,
-                               x.label = "n back level", y.label = "subjective value",
-                               legend.main = "NFC", interval = T) + theme_apa()    
+    # random slopes model
+
+    m1_sca <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
+                   data = sca_data, REML = T)
+
+    # combine current results and the bigger data frame
+
+    newdata <- data.frame(pipeline = names(pipelines_data[i]),
+                          beta_level = summary(m1_sca)$coefficients[2,1],
+                          p_level = summary(m1_sca)$coefficients[2,5],
+                          beta_nfc = summary(m1_sca)$coefficients[3,1],
+                          p_nfc = summary(m1_sca)$coefficients[3,5])
+    sca_results <- rbind(sca_results, newdata)
+
+  }
+
+```
+
+```{r SCA_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
+
+  # sort the data frame by the fixed effects estimate of the predictor 'level'
+
+  sca_results <- sca_results[order(beta_level), ]
+
 ```

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
started writing graph code for SCA

@@
   library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
+  library(ggplot2)      # for plotting, "ggplot2" package
 
@@
 
-  sca_results <- data.frame(pipeline = character(), beta_level = double(), p_level = double(),
-                            beta_nfc = double(), p_nfc = double())
+  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character())
+
+  # loop through the pipelines
 
@@
 
-    newdata <- data.frame(pipeline = names(pipelines_data[i]),
-                          beta_level = summary(m1_sca)$coefficients[2,1],
-                          p_level = summary(m1_sca)$coefficients[2,5],
-                          beta_nfc = summary(m1_sca)$coefficients[3,1],
-                          p_nfc = summary(m1_sca)$coefficients[3,5])
+    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
+                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
+                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
+                          predictor = c("Level", "NFC"))
     sca_results <- rbind(sca_results, newdata)
@@
 
-  # sort the data frame by the fixed effects estimate of the predictor 'level'
-
-  sca_results <- sca_results[order(beta_level), ]
+  # add a row number and sort the data frame by the fixed effects estimate of the predictor 'level'
+
+  sca_results <- cbind(sca_results, num = rep(c(1:(nrow(sca_results)/2)), each = 2))
+  sca_results <- sca_results[order(sca_results$predictor, sca_results$beta, decreasing = TRUE), ]
+  sca_results[sca_results$predictor == "NFC", ] <- sca_results[match(sca_results$num[sca_results$predictor == "Level"],
+                                                                     sca_results$num[sca_results$predictor == "NFC"]),]
+
+  # lock it in place by turning it into a factor
+
+  sca_results$num <- factor(sca_results$num, levels = sca_results$num[sca_results$predictor == "NFC"])
+
+  # create the upper panel first, which will show the estimates of 'level' and 'nfc'
+
+  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
+    geom_point() +
+    geom_line() +
+    theme_classic() +
+    labs(x = NULL, y = "Fixed effects estimate") +
+    scale_y_continuous(position = "right") +
+    theme(axis.text.x = element_blank())
 

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd

@@
 
-    # random slopes model
-
-    m1_sca <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
-                   data = sca_data, REML = T)
-
     # combine current results and the bigger data frame
@@
   }
+
+  # random slopes model --------------------------------------------------------
+
+  ## maximal model ---- 
+  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
+                 data = h2b_data,
+                 REML = T) # parameters estimated by restricted log-likelihood maximization
+
+  ## plot model fit of the final model ----
+  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
+
+  # prepare MLM results for reporting ------------------------------------------
+
+  # get random and fixed effects
+  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
+  m1_h2b.fixef <- summary(m1_h2b)$coefficients
+
+  # prepare table
+  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef[-c(6,7),]), 
+                                          m1_h2b.fixef[-c(6,7),c(1, 2, 5)]))
+  h2b_result.table$ranef.sd <- NA
+  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
+
+  colnames(h2b_result.table)[1] <- "Parameter"
+  colnames(h2b_result.table)[2] <- "Beta"
+  colnames(h2b_result.table)[3] <- "$SE$"
+  colnames(h2b_result.table)[4] <- "$p$-value"
+  colnames(h2b_result.table)[5] <- "Random Effects (SD)"
 

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
deleted duplicate lines
table simple slopes analysis adapted

@@
   - name          : "Corinna Kührt"
+    orcid         : "0000-0002-6418-6479"
     affiliation   : "1"
@@
   library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
-  library(ggplot2)      # for plotting, "ggplot2" package
 
@@
 
-  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
+  m1_h2c.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                     cond.int = T,                       # print conditional intercepts
-                    control.fdr = T)                    # adjust false discovery rate
+                    control.fdr = T,                    # adjust false discovery rate
+                    confint = T)                        # add confidence intervals
 
   #create table
-  h2b_ss.table <- as_huxtable(m1_h2b.ss)
-  h2b_ss.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
-  h2b_ss.table <- h2b_ss.table[-2,]
-  h2b_ss.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
+  h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
+                             round(m1_h2c.ss$slopes[c(2:5)], digits = 2),
+                             round(m1_h2c.ss$slopes[7], digits = 3),
+                             round(m1_h2c.ss$ints[c(2,3)], digits = 2))
+  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI - lower", "95% CI - higher", "$p$-value", "Beta", "$SE$" )
+  # columns 2:5 belong to "Slopes of NFC"
+  # columns 6:7 belong to "Conditional Intercept"
+
+  h2c_ss.table$`$p$-value`  [which(h2c_ss.table$`$p$-value`<.01)] <- 
+    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.01)],"*")
+  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)] <- 
+    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)],"*")
+  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.001)] <- 
+    paste0("<.001***")
+
+  table_2 <-
+    kbl(h2c_ss.table,
+    caption = "Interaction between NFC and n-back load level.",
+    # "Slopes of n-back level for different NFC values."
+    booktabs = T,                          # no vertical lines
+    escape = F,                            # correctly print special characters)
+    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
+            escape = F,                    # correctly print special characters
+            threeparttable = T)            # line breaks in the footnote
 
@@
 
-  # here we repeat the multi level model with all analysis pipelines
-
-  # prepare empty data frame for the loop to feed into
-
-  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character())
-
-  # loop through the pipelines
+  # Here we repeat the multi level model with all analysis pipelines.
 
@@
 
-    # combine current results and the bigger data frame
-
-    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
-                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
-                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
-                          predictor = c("Level", "NFC"))
-    sca_results <- rbind(sca_results, newdata)
+    # intra-class-correlation
+
+    var_m0_sca <- as.data.frame(VarCorr(m0_sca))
+    icc_sca <- var_m0_sca$vcov[1] / (var_m0_sca$vcov[1] + var_m0_sca$vcov[2])
 
@@
 
-```
-
-```{r SCA_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
-
-  # add a row number and sort the data frame by the fixed effects estimate of the predictor 'level'
-
-  sca_results <- cbind(sca_results, num = rep(c(1:(nrow(sca_results)/2)), each = 2))
-  sca_results <- sca_results[order(sca_results$predictor, sca_results$beta, decreasing = TRUE), ]
-  sca_results[sca_results$predictor == "NFC", ] <- sca_results[match(sca_results$num[sca_results$predictor == "Level"],
-                                                                     sca_results$num[sca_results$predictor == "NFC"]),]
-
-  # lock it in place by turning it into a factor
-
-  sca_results$num <- factor(sca_results$num, levels = sca_results$num[sca_results$predictor == "NFC"])
-
-  # create the upper panel first, which will show the estimates of 'level' and 'nfc'
-
-  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
-    geom_point() +
-    geom_line() +
-    theme_classic() +
-    labs(x = NULL, y = "Fixed effects estimate") +
-    scale_y_continuous(position = "right") +
-    theme(axis.text.x = element_blank())
-
+  row.names(h2b_result.table) <- NULL
+  h2b_result.table$Parameter[1:6] <- c("Intercept", "n-back level", "NFC", "d'", "RT", "level x NFC")
+
+  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
+  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
+  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)
+
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
+    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
+    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
+  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
+    paste0("<.001***")
+
+  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")
+
+  table_1 <-
+    kbl(h2b_result.table,
+    caption = "Effects of n-back load level on subjective value controlled 
+    for task performance (d' and reaction time), correct and postcorrect trials.",
+    booktabs = T,                          # no vertical lines
+    escape = F,                            # correctly print special characters)
+    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
+            escape = F,                    # correctly print special characters
+            threeparttable = T)            # line breaks in the footnote
+
+  # simple slopes analysis -----------------------------------------------------
+
+  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
+                    cond.int = T,                       # print conditional intercepts
+                    control.fdr = T)                    # adjust false discovery rate
+
+  #create table
+  h2b_ss.table <- as_huxtable(m1_h2b.ss)
+  h2b_ss.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
+  h2b_ss.table <- h2b_ss.table[-2,]
+  h2b_ss.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
+
+  # calculate Johnson-Neyman intervals
+  h2b_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
+  h2b_jn.int <- h2b_jn$bounds
+
+  # save plot
+  h2b_jn.plot <- h2b_jn$plot
+
+  # create interaction plot
+  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                               plot.points = T, point.shape = T,
+                               x.label = "n back level", y.label = "subjective value",
+                               legend.main = "NFC", interval = T) + theme_apa()    
 ```

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd

@@
 
-  # Here we repeat the multi level model with all analysis pipelines.
+  # here we repeat the multi level model with all analysis pipelines
+
+  # prepare empty data frame for the loop to feed into
+
+  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character())
+
+  # loop through the pipelines
 
@@
 
-    # intra-class-correlation
-
-    var_m0_sca <- as.data.frame(VarCorr(m0_sca))
-    icc_sca <- var_m0_sca$vcov[1] / (var_m0_sca$vcov[1] + var_m0_sca$vcov[2])
-
-  }
-
-  # random slopes model --------------------------------------------------------
-
-  ## maximal model ---- 
-  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
-                 data = h2b_data,
-                 REML = T) # parameters estimated by restricted log-likelihood maximization
-
-  ## plot model fit of the final model ----
-  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
-
-  # prepare MLM results for reporting ------------------------------------------
-
-  # get random and fixed effects
-  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
-  m1_h2b.fixef <- summary(m1_h2b)$coefficients
-
-  # prepare table
-  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef[-c(6,7),]), 
-                                          m1_h2b.fixef[-c(6,7),c(1, 2, 5)]))
-  h2b_result.table$ranef.sd <- NA
-  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
-
-  colnames(h2b_result.table)[1] <- "Parameter"
-  colnames(h2b_result.table)[2] <- "Beta"
-  colnames(h2b_result.table)[3] <- "$SE$"
-  colnames(h2b_result.table)[4] <- "$p$-value"
-  colnames(h2b_result.table)[5] <- "Random Effects (SD)"
-
-  row.names(h2b_result.table) <- NULL
-  h2b_result.table$Parameter[1:6] <- c("Intercept", "n-back level", "NFC", "d'", "RT", "level x NFC")
-
-  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
-  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
-  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)
-
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
-    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
-    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
-    paste0("<.001***")
-
-  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")
-
-  table_1 <-
-    kbl(h2b_result.table,
-    caption = "Effects of n-back load level on subjective value controlled 
-    for task performance (d' and reaction time), correct and postcorrect trials.",
-    booktabs = T,                          # no vertical lines
-    escape = F,                            # correctly print special characters)
-    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
-            escape = F,                    # correctly print special characters
-            threeparttable = T)            # line breaks in the footnote
-
-  # simple slopes analysis -----------------------------------------------------
-
-  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
-                    cond.int = T,                       # print conditional intercepts
-                    control.fdr = T)                    # adjust false discovery rate
-
-  #create table
-  h2b_ss.table <- as_huxtable(m1_h2b.ss)
-  h2b_ss.table[1,] <- c("Value of NFC", "Slope of N-Back Level", "Conditional Intercept")
-  h2b_ss.table <- h2b_ss.table[-2,]
-  h2b_ss.table[2:4,1] <- c("- 1 SD", "Mean", "+ 1 SD")
-
-  # calculate Johnson-Neyman intervals
-  h2b_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
-  h2b_jn.int <- h2b_jn$bounds
-
-  # save plot
-  h2b_jn.plot <- h2b_jn$plot
-
-  # create interaction plot
-  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                               plot.points = T, point.shape = T,
-                               x.label = "n back level", y.label = "subjective value",
-                               legend.main = "NFC", interval = T) + theme_apa()    
+    # combine current results and the bigger data frame
+
+    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
+                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
+                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
+                          predictor = c("Level", "NFC"))
+    sca_results <- rbind(sca_results, newdata)
+
+  }
+
+```
+
+```{r SCA_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
+
+  # add a row number and sort the data frame by the fixed effects estimate of the predictor 'level'
+
+  sca_results <- cbind(sca_results, num = rep(c(1:(nrow(sca_results)/2)), each = 2))
+  sca_results <- sca_results[order(sca_results$predictor, sca_results$beta, decreasing = TRUE), ]
+  sca_results[sca_results$predictor == "NFC", ] <- sca_results[match(sca_results$num[sca_results$predictor == "Level"],
+                                                                     sca_results$num[sca_results$predictor == "NFC"]),]
+
+  # lock it in place by turning it into a factor
+
+  sca_results$num <- factor(sca_results$num, levels = sca_results$num[sca_results$predictor == "NFC"])
+
+  # create the upper panel first, which will show the estimates of 'level' and 'nfc'
+
+  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
+    geom_point() +
+    geom_line() +
+    theme_classic() +
+    labs(x = NULL, y = "Fixed effects estimate") +
+    scale_y_continuous(position = "right") +
+    theme(axis.text.x = element_blank())
+
 ```

### 2022-01-11 06_Paper/COG-ED/Manuscript.Rmd
adapted table name

@@
                                plot.points = T, point.shape = T,
-                               x.label = "n back level", y.label = "subjective value",
+                               x.label = "n-back level", y.label = "subjective value",
                                legend.main = "NFC", interval = T) + theme_apa()
+
 ```
@@
 The simple slopes analysis revealed a significant difference in slope of n-back level for three different expressions of NFC (Table 2, Figure 2).
-`r h2b_ss.table`
+`r table_2`
 `r h2b_ss.plot`

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd

@@
   h2b_data <- droplevels(subset(h2b_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
-                               subset = !is.na(rt)))
+                               subset = !is.na(rt)
+                               & level > 1)) #FIXME
 
@@
   # calculate Johnson-Neyman intervals
-  h2b_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
-  h2b_jn.int <- h2b_jn$bounds
+  h2c_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
+  h2c_jn.int <- h2c_jn$bounds
 
   # save plot
-  h2b_jn.plot <- h2b_jn$plot
+  h2c_jn.plot <- h2c_jn$plot
 
   # create interaction plot
-  h2b_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+  h2c_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                                plot.points = T, point.shape = T,
@@
 `r table_2`
-`r h2b_ss.plot`
+`r h2c_ss.plot`
 The Johnson-Neyman plot (Figure 2) visualizes the significance of the slope of n-back level at different values of NFC.
-The Johnson-Neyman interval is [`r h2b_jn.int`].
+The Johnson-Neyman interval is [`r h2c_jn.int`].
 Consequently, the slope of n-back level was not significant for individuals with very low NFC values.    
-`r h2b_jn.plot`
+`r h2c_jn.plot`
 

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
re-added one missing line
put CIs in one column with brackets in table_2

@@
   h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
-                             round(m1_h2c.ss$slopes[c(2:5)], digits = 2),
+                             round(m1_h2c.ss$slopes[c(2:3)], digits = 2),
+                             c(paste0("[", round(m1_h2c.ss$slopes[1,4], digits = 2), ",", round(m1_h2c.ss$slopes[1,5], digits = 2), "]"),
+                               paste0("[", round(m1_h2c.ss$slopes[2,4], digits = 2), ",", round(m1_h2c.ss$slopes[2,5], digits = 2), "]"),
+                               paste0("[", round(m1_h2c.ss$slopes[3,4], digits = 2), ",", round(m1_h2c.ss$slopes[3,5], digits = 2), "]")),
                              round(m1_h2c.ss$slopes[7], digits = 3),
                              round(m1_h2c.ss$ints[c(2,3)], digits = 2))
-  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI - lower", "95% CI - higher", "$p$-value", "Beta", "$SE$" )
-  # columns 2:5 belong to "Slopes of NFC"
-  # columns 6:7 belong to "Conditional Intercept"
+  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI", "$p$-value", "Beta", "$SE$" )
+  # columns 2:4 belong to "Slopes of NFC"
+  # columns 5:6 belong to "Conditional Intercept"
 
@@
     escape = F,                            # correctly print special characters)
-    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
+    align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
     kable_styling(latex_options = c("striped")) %>%
@@
     m0_sca <- lmer(sv ~ 1 + (1|subject), data = sca_data, REML = T)
+
+    # random slopes model
+
+    m1_sca <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
+                   data = sca_data, REML = T)
 

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
removed leading zeros in p-value column table_2
added two headers to table_2

--- 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
@@
   h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
-                             round(m1_h2c.ss$slopes[c(2:5)], digits = 2),
+                             round(m1_h2c.ss$slopes[c(2:3)], digits = 2),
+                             c(paste0("[", round(m1_h2c.ss$slopes[1,4], digits = 2), ",", round(m1_h2c.ss$slopes[1,5], digits = 2), "]"),
+                               paste0("[", round(m1_h2c.ss$slopes[2,4], digits = 2), ",", round(m1_h2c.ss$slopes[2,5], digits = 2), "]"),
+                               paste0("[", round(m1_h2c.ss$slopes[3,4], digits = 2), ",", round(m1_h2c.ss$slopes[3,5], digits = 2), "]")),
                              round(m1_h2c.ss$slopes[7], digits = 3),
                              round(m1_h2c.ss$ints[c(2,3)], digits = 2))
-  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI - lower", "95% CI - higher", "$p$-value", "Beta", "$SE$" )
+  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI", "$p$-value", "Beta", "$SE$" )
   # columns 2:5 belong to "Slopes of NFC"
@@
 
+  # remove leading zeros in the p-value column
+
+  h2c_ss.table$`$p$-value` <- str_replace(h2c_ss.table$`$p$-value`, "0.", ".")
+
   table_2 <-
@@
     escape = F,                            # correctly print special characters)
-    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
+    align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
     kable_styling(latex_options = c("striped")) %>%
+    add_header_above(c(" " = 1, "Slopes of NFC" = 4, "Conditional Intercept" = 2)) %>%
     footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
tried constructing ggplot for SSA (not done yet)

@@
 
+  # add column to data frame, which indexes the Mean+/-SD groups
+  h2b_data$nfc_group <- ifelse(h2b_data$nfc.cgm > (mean(h2b_data$nfc.cgm) + sd(h2b_data$nfc.cgm)), "+1 SD",
+                               ifelse(h2b_data$nfc.cgm < (mean(h2b_data$nfc.cgm) - sd(h2b_data$nfc.cgm)), "-1 SD", "Mean"))
+  # add columns to data frame, which index the max/min value of SV per group
+  h2b_data$sv_groupmax <- ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2,
+                                 max(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2]),
+                                 ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3,
+                                        max(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3]),
+                                        ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4,
+                                               max(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4]),
+                                               ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2,
+                                                      max(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2]),
+                                                      ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3,
+                                                             max(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3]),
+                                                             ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4,
+                                                                    max(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4]),
+                                                                    ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 2,
+                                                                           max(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 2]),
+                                                                           ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 3,
+                                                                                  max(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 3]),
+                                                                                  max(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 4])))))))))
+  h2b_data$sv_groupmax <- ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2,
+                                 min(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 2]),
+                                 ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3,
+                                        min(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 3]),
+                                        ifelse(h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4,
+                                               min(h2b_data$sv[h2b_data$nfc_group == "+1 SD" & h2b_data$level == 4]),
+                                               ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2,
+                                                      min(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 2]),
+                                                      ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3,
+                                                             min(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 3]),
+                                                             ifelse(h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4,
+                                                                    min(h2b_data$sv[h2b_data$nfc_group == "-1 SD" & h2b_data$level == 4]),
+                                                                    ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 2,
+                                                                           min(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 2]),
+                                                                           ifelse(h2b_data$nfc_group == "Mean" & h2b_data$level == 3,
+                                                                                  min(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 3]),
+                                                                                  min(h2b_data$sv[h2b_data$nfc_group == "Mean" & h2b_data$level == 4])))))))))
+
+  h2c_ss.plot <- ggplot(h2b_data, aes(x = level.cwc, y = sv, color = nfc_group, group = nfc_group)) +
+    geom_point() +
+    geom_smooth(method = interactions::sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm,
+                                                  centered = "none", cond.int = T, control.fdr = T, confint = T),
+                data = NULL, mapping = aes(fill = nfc_group, alpha = .15), se = TRUE) # the alpha stands for the opacity of the CIs
+
+  h2c_ss.plot <- ggplot(h2b_data, aes(x = level.cwc, y = sv, color = nfc_group, group = nfc_group)) +
+    geom_point() +
+    geom_ribbon(aes(ymax = sv_groupmax, ymin = sv_groupmin, fill = "band", color = nfc_group), alpha = .15)
+
 ```

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
plot works, also fml

--- 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
@@
   h2b_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject')
+                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
   h2b_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject')
+                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
   h2b_BF <- h2b_full_BF / h2b_null_BF
@@
   h2c_full_BF <- lmBF(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject')
+                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
   h2c_null_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject')
+                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
   h2c_BF <- h2c_full_BF / h2c_null_BF
@@
                                x.label = "n-back level", y.label = "subjective value",
-                               legend.main = "NFC", interval = T) + theme_apa()
+                               legend.main = "NFC", interval = T) + theme_apa() +
+    scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
 
@@
 
-  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character())
+  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character(), BF10 = double())
 
@@
 
+    # convert random factor to type factor
+
+    sca_data$subject <- factor(sca_data$subject)
+
+    # compute Bayes factor
+
+    sca_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
+                        data = sca_data, whichRandom = 'subject', progress = FALSE)
+    sca_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
+                        data = sca_data, whichRandom = 'subject', progress = FALSE)
+    sca_BF <- sca_full_BF / sca_null_BF
+
     # combine current results and the bigger data frame
@@
                           pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
-                          predictor = c("Level", "NFC"))
+                          predictor = c("Level", "NFC"),
+                          BF10 = c(extractBF(sca_BF)$bf, extractBF(sca_BF)$bf))
     sca_results <- rbind(sca_results, newdata)

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
added title to sca plot

@@
     theme_classic() +
-    labs(x = NULL, y = "Fixed effects estimate") +
+    labs(x = NULL, y = NULL) +
     scale_y_continuous(position = "right") +
-    theme(axis.text.x = element_blank())
+    ggtitle("Fixed effects estimate") +
+    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1))
 

### 2022-01-13 06_Paper/COG-ED/Manuscript.Rmd
added point to plot only for sign pipelines

--- 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
@@
 
+  # add a column to plot only points that are significant
+
+  sca_results$sign <- ifelse(sca_results$pvalue < .01, sca_results$beta, NA)
+
   # create the upper panel first, which will show the estimates of 'level' and 'nfc'
@@
   sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
-    geom_point() +
+    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
     geom_line() +
     theme_classic() +
-    labs(x = NULL, y = "Fixed effects estimate") +
+    labs(x = NULL, y = NULL) +
     scale_y_continuous(position = "right") +
-    theme(axis.text.x = element_blank())
+    ggtitle("Fixed effects estimate") +
+    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1))
 

### 2022-01-13 06_Paper/COG-ED/Manuscript.Rmd
started coding lower plot for pipelines

--- 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
@@
   sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
-    geom_point() +
+    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
     geom_line() +
+    geom_text(aes(x = length(pipelines_data)-2, y = -0.01, label = "NFC")) + 
+    geom_text(aes(x = length(pipelines_data)-2, y = -0.12, label = "Level")) +
     theme_classic() +
-    labs(x = NULL, y = "Fixed effects estimate") +
+    labs(x = NULL, y = NULL) +
     scale_y_continuous(position = "right") +
-    theme(axis.text.x = element_blank())
+    ggtitle("Fixed effects estimate") +
+    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1), legend.position = "none")
+
+  # add columns to the data frame that describe the pipeline
+
+  sca_results$Dim <- ifelse(substr(sca_results$pipeline,1,2) == "AA", 2,
+                            ifelse(substr(sca_results$pipeline,1,2) == "AW", 3,
+                                   ifelse(substr(sca_results$pipeline,1,2) == "AW", 3,
+                                          ifelse(substr(sca_results$pipeline,1,2) == "WW", 4,
+                                                 ifelse(substr(sca_results$pipeline,1,2) == "WA", 5, NA)))))
+  sca_results$Trans <- ifelse(substr(sca_results$pipeline,3,3) == "R", 7,
+                              ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
+                                     ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
+                                            ifelse(substr(sca_results$pipeline,3,3) == "I", 9,
+                                                   ifelse(substr(sca_results$pipeline,3,3) == "S", 10, NA)))))
+  sca_results$Excl <- ifelse(substr(sca_results$pipeline,4,4) == "N", 12,
+                             ifelse(substr(sca_results$pipeline,4,4) == "2", 13,
+                                    ifelse(substr(sca_results$pipeline,4,4) == "5", 14,
+                                           ifelse(substr(sca_results$pipeline,4,4) == "3", 15,
+                                                  ifelse(substr(sca_results$pipeline,4,4) == "O", 16, 
+                                                         ifelse(substr(sca_results$pipeline,4,4) == "T", 17, NA))))))
+
+  sca_lowerplot <- ggplot(data = sca_results) +
+    geom_point(aes(x = num, y = Dim, color = "red")) +
+    geom_point(aes(x = num, y = Trans, color = "blue")) +
+    geom_point(aes(x = num, y = Excl, color = "purple")) +
+    theme_classic() +
+    labs(x = NULL, y = NULL) +
+    scale_y_reverse() +
+    theme(axis.text.x = element_blank(), axis.text.y = element_blank(), legend.position = "none")
 

### 2022-01-14 06_Paper/COG-ED/Manuscript.Rmd
finalized lowerplot for SCA

--- 2022-01-13 06_Paper/COG-ED/Manuscript.Rmd
@@
     geom_line() +
+    geom_text(aes(x = length(pipelines_data)-2, y = -0.01, label = "NFC")) + 
+    geom_text(aes(x = length(pipelines_data)-2, y = -0.12, label = "Level")) +
     theme_classic() +
@@
     ggtitle("Fixed effects estimate") +
-    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1))
+    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1), legend.position = "none")
+
+  # add columns to the data frame that describe the pipeline
+
+  sca_results$Dim <- ifelse(substr(sca_results$pipeline,1,2) == "AA", 2,
+                            ifelse(substr(sca_results$pipeline,1,2) == "AW", 3,
+                                   ifelse(substr(sca_results$pipeline,1,2) == "WW", 4,
+                                          ifelse(substr(sca_results$pipeline,1,2) == "WA", 5, NA))))
+  sca_results$Trans <- ifelse(substr(sca_results$pipeline,3,3) == "R", 7,
+                              ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
+                                     ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
+                                            ifelse(substr(sca_results$pipeline,3,3) == "I", 9,
+                                                   ifelse(substr(sca_results$pipeline,3,3) == "S", 10, NA)))))
+  sca_results$Excl <- ifelse(substr(sca_results$pipeline,4,4) == "N", 12,
+                             ifelse(substr(sca_results$pipeline,4,4) == "2", 13,
+                                    ifelse(substr(sca_results$pipeline,4,4) == "5", 14,
+                                           ifelse(substr(sca_results$pipeline,4,4) == "3", 15,
+                                                  ifelse(substr(sca_results$pipeline,4,4) == "O", 16, 
+                                                         ifelse(substr(sca_results$pipeline,4,4) == "T", 17, NA))))))
+
+  # create the lower part of the plot that indicates the pipeline specifications
+
+  sca_lowerplot <- ggplot(data = sca_results) +
+    geom_hline(yintercept = c(1,6,11), color = "grey", size = 0.5) +
+    geom_hline(yintercept = c(2:5,7:10,12:17), color = "grey", linetype = "dashed", size = 0.2) +
+    geom_point(aes(x = num, y = Dim)) +
+    geom_point(aes(x = num, y = Trans)) +
+    geom_point(aes(x = num, y = Excl)) +
+    theme_classic() +
+    labs(x = NULL, y = NULL) +
+    scale_y_reverse(breaks = c(1:17), lim = c(17,0), labels = c(expression(bold("Dimension")),
+                                                                "Across S, across C", "Across S, within C",
+                                                                "Within S, within C", "Within S, across C",
+                                                                expression(bold("Transformation")),
+                                                                "Raw/None", "Log", "Inverse", "Square-root",
+                                                                expression(bold("Exclusion")),
+                                                                "None", "2 MAD from median", "2.5 MAD from median",
+                                                                "3 MAD from median", "100ms after onset", "200ms after onset")) +
+    theme(axis.text.x = element_blank(), legend.position = "none")
 

### 2022-01-14 06_Paper/COG-ED/Manuscript.Rmd
upperplot looks way better now

@@
 
-  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
-    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
-    geom_line() +
-    geom_text(aes(x = length(pipelines_data)-2, y = -0.01, label = "NFC")) + 
-    geom_text(aes(x = length(pipelines_data)-2, y = -0.12, label = "Level")) +
+  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
+    geom_line(aes(group = predictor)) +
+    geom_point(data = sca_results, aes(x = num, y = sign)) +
+    geom_text(x = 3, y = -0.01, label = "NFC") +
+    geom_text(x = 3, y = -0.12, label = "Level") +
     theme_classic() +
     labs(x = NULL, y = NULL) +
-    scale_y_continuous(position = "right") +
-    ggtitle("Fixed effects estimate") +
-    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1), legend.position = "none")
+    scale_y_continuous(lim = c(NA,0.01), breaks = c(-0.10,-0.05,0), labels = c("-0.10", "-0.05", "Fixed effects \u03b2  0.00")) +
+    theme(axis.text.x = element_blank(), legend.position = "none")
 

### 2022-01-14 06_Paper/COG-ED/Manuscript.Rmd
nicely panelled sca plot

@@
   library(ggplot2)      # for plotting, "ggplot2" package
+  library(egg)          # for paneling plots, "egg" package
 
@@
 
-  # create the upper panel first, which will show the estimates of 'level' and 'nfc'
-
-  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
-    geom_line(aes(group = predictor)) +
-    geom_point(data = sca_results, aes(x = num, y = sign)) +
-    geom_text(x = 3, y = -0.01, label = "NFC") +
-    geom_text(x = 3, y = -0.12, label = "Level") +
-    theme_classic() +
-    labs(x = NULL, y = NULL) +
-    scale_y_continuous(lim = c(NA,0.01), breaks = c(-0.10,-0.05,0), labels = c("-0.10", "-0.05", "Fixed effects \u03b2  0.00")) +
-    theme(axis.text.x = element_blank(), legend.position = "none")
-
   # add columns to the data frame that describe the pipeline
@@
 
+  # create the upper panel first, which will show the estimates of 'level' and 'nfc'
+
+  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
+    geom_line(aes(group = predictor)) +
+    geom_point(data = sca_results, aes(x = num, y = sign)) +
+    geom_text(x = 3, y = -0.01, label = "NFC") +
+    geom_text(x = 3, y = -0.12, label = "Level") +
+    theme_classic() +
+    labs(x = NULL, y = "Fixed effects estimate \u03b2") +
+    scale_y_continuous(lim = c(NA,0.01)) +
+    theme(axis.text.x = element_blank(),
+          axis.line.y = element_line(size = 1, color = "black"), axis.title.y = element_text(margin = margin(r = 10)),
+          legend.position = "none")
+
   # create the lower part of the plot that indicates the pipeline specifications
@@
     theme_classic() +
-    labs(x = NULL, y = NULL) +
-    scale_y_reverse(breaks = c(1:17), lim = c(17,0), labels = c(expression(bold("Dimension")),
+    labs(x = "Analysis pipeline", y = NULL) +
+    scale_y_reverse(breaks = c(1:17), lim = c(17,0.5), labels = c(expression(bold("Dimension")),
                                                                 "Across S, across C", "Across S, within C",
@@
                                                                 expression(bold("Exclusion")),
-                                                                "None", "2 MAD from median", "2.5 MAD from median",
+                                                                "None", "2 MAD from median", " 2.5 MAD from median",
                                                                 "3 MAD from median", "100ms after onset", "200ms after onset")) +
-    theme(axis.text.x = element_blank(), legend.position = "none")
+    theme(axis.text.x = element_blank(), axis.title.x = element_text(margin = margin(t = 10)),
+          axis.line.y = element_line(size = 1, color = "black"),
+          legend.position = "none")
+
+  # put both plots into one
+
+  sca_plot <- ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
 

### 2022-01-17 06_Paper/COG-ED/Manuscript.Rmd
included figure 1 (paradigm scheme)

@@
   library(egg)          # for paneling plots, "egg" package
+  library(knitr)        # for including plots and such, "knitr" package
 
@@
 If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
-Since we aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
+Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
 emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
-In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al.
-[-@Westbrook2013].
+In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
 Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task.
@@
 
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE}
+include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
+```
 *Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.

### 2022-01-17 06_Paper/COG-ED/Manuscript.Rmd
shortened the results section a lot

@@
       - Methodology
+      - Funding acquisition
       - Formal analysis
@@
 
-Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013], and detailed in the attached design table..
-Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with n-back level.
+Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
+Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
 Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
@@
 
-The results of each analysis will be assessed on the basis of both *p*-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].
 
@@
 
-## Results of the pilot study
-
-We collected data from $N = 16$ participants,
-One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 15 complete data sets.
-Contrary to our expectations, the rmANOVA revealed no decrease in performance *d'* with increasing n-back level (`r apa_print(hypothesis1a_rmanova)$full_result`).
-
 ```{r Hypothesis_1b, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
-
-However, RTs increased with increasing n-back level (`r apa_print(hypothesis1b_rmanova)$full_result`).
-RTs were longer for 3- than 2-back (`r apa_print(pairs(emmeans(object = hypothesis1b_rmanova$aov,specs = "level")))[1]`), but not different between 2- and 4-back or 3- and 4-back.
-Even though *d'* did not decrease, the increases in RT indicate an increase in objective task load.
 
@@
 
-Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
-Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
-Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X3`, and `r apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(pairs(emmeans(object = hypothesis1c_physical_rmanova$aov,specs = "level")))$statistic$X1_X4`, and `r `apa_print(pairs(emmeans(object = hypothesis1c_performance_rmanova$aov,specs = "level")))$statistic$X1_X4`, respectively).
-Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
-Overall, these ratings showed that the increase in task load was being perceived as such.
-
 ```{r Hypothesis_2a, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
-
-The rmANOVA indicated significant differences between SVs depending on n-back level (`r apa_print(hypothesis2a_rmanova)$full_result`).
-SVs were higher for 1- than 3-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X3`), for 1- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X1_X4`), and for 2- than 4-back (`r apa_print(pairs(emmeans(object = hypothesis2a_rmanova$aov,specs = "level")))$statistic$X2_X4`).
-Importantly, the lack of difference between the SVs of 1- and 2-back indicates that when given the choice, not all participants preferred the easiest level.
-This can be considered preliminary proof-of-concept, as this behavioural pattern can only emerge in the CERED paradigm, but not in the original COG-ED paradigm.
 
@@
   # save plot
-  h2c_jn.plot <- h2c_jn$plot
+  Figure3 <- h2c_jn$plot
 
   # create interaction plot
-  h2c_ss.plot <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+  Figure2 <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                                plot.points = T, point.shape = T,
@@
 
-The MLM revealed that n-back level was a reliable predictor of SV (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers.
-The results of the MLM are detailed in Table 1. 
-`r table_1`
-Differences between subjects could explain `r round((icc_h2b*100), digits = 0)` % of the total variance in SVs ($ICC =$ `r round(icc_h2b, digits = 2)`).
-However, NFC had no statistically significant effect on SVs (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
-The simple slopes analysis revealed a significant difference in slope of n-back level for three different expressions of NFC (Table 2, Figure 2).
-`r table_2`
-`r h2c_ss.plot`
-The Johnson-Neyman plot (Figure 2) visualizes the significance of the slope of n-back level at different values of NFC.
-The Johnson-Neyman interval is [`r h2c_jn.int`].
-Consequently, the slope of n-back level was not significant for individuals with very low NFC values.    
-`r h2c_jn.plot`
-
-## alternative: `r h2b_jn`
-
 ```{r Hypothesis_3a, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
-
-The $AxAUC$ value did not predict any amount of variance in individual NFC scores (`r apa_print(hypothesis3a)$statistic$modelfit$r2`, `r apa_print(hypothesis3a)$estimate$modelfit$r2`).
 
@@
 
-When including the AUC of all NASA-TLX subscales as a predictor, it could explain variance in NFC beyond the one (not) explained by the SVs (`r apa_print(hypothesis3b)$statistic$modelfit$r2`, `r apa_print(hypothesis3b)$estimate$modelfit$r2`).
-An increase in one NASA-TLX AUC value corresponded, on average, to a decrease of `r round(hypothesis3b$coefficients[2], digits = 1)` on the NFC scale (`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`).
+## Results of the pilot study
+
+We collected data from $N = 15$ participants.
+One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 14 complete data sets.
+The results showed increases in subjective and objective task load measures with higher n-back level.
+Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
+The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers.
+And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the AUC of NASA-TLX scores did.
+All results are detailed in the *Supplementary Material*.
 
 \newpage
-
-# Discussion
-
-# (summary and interpretation of h2b_results)
 
@@
 
+JZ and CS conceptualized the study and its methodology, acquired funding, investigated, administered the project, and wrote the software.
+JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
+All authors reviewed, edited, and approved the final version of the manuscript.
+
 # Competing Interests
@@
 
+*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
+
+*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
+
 \newpage
@@
 `r h2b_ss.table`
-`r h2b_ss.plot`
+
+`r Figure2`
+*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
 

### 2022-01-17 06_Paper/COG-ED/Manuscript.Rmd
tried implementing pdf-import for design table

@@
     - \usepackage{setspace}\doublespacing
+    - \usepackage{pdfpages}
 editor_options: 
@@
   # save plot
-  Figure3 <- h2c_jn$plot
+  h2c_jn.plot <- h2c_jn$plot
 
@@
 
-  sca_plot <- ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
+  Figure3 <- ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
 
@@
 Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
-The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers.
+The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not.
+The specification curve analysis showed that this pattern was true for all 63 pipelines.
 And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the AUC of NASA-TLX scores did.
@@
 
-# Figure Captions
-
+# Figures and figure Captions
+
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE}
+
+  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
+
+```
 *Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
 
-*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
+`r Figure2`
+*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
+
+`r Figure3`
+*Supplementary Figure 2* Results of the specification curve analysis for the multi level model.
+The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
+Estimates with $p<.01$ are indicated by a dot on the line.
+The lower panel shows the preprocessing steps of each corresponding pipeline.
+The $BF10$ of each pipeline's multi level model approached infinity.
 
@@
 
+\includepdf[pages={-}]{here("02_Hypotheses", "Design_Table_T1.pdf")}
+
 \newpage
@@
 `r Figure2`
-*Fig.2* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
+*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
 
@@
 `r h2b_jn.int`
+
+Specification curve analysis:
+
+`r Figure3`
+*Supplementary Figure 2* Results of the specification curve analysis for the multi level model.
+The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
+Estimates with $p<.01$ are indicated by a dot on the line.
+The lower panel shows the preprocessing steps of each corresponding pipeline.
+The $BF10$ of each pipeline's multi level model approached infinity.
 

### 2022-01-19 06_Paper/COG-ED/Manuscript.Rmd
changed name of one chunk (knit still incomplete)
removed sentence wrap and added rmarkdown library

@@
     - \usepackage{pdfpages}
-editor_options: 
-  markdown: 
-    wrap: sentence
+
 ---
@@
   library(bibtex)
+  library(rmarkdown)
   library(here)         # to set a directory without defined paths, "here" package
@@
 
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE}
+```{r figure1_appendix, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-`r h2b_ss.table`
+`r h2c_ss.table`
 
@@
 
-`r h2b_jn.int`
+`r h2c_jn.int`
 

### 2022-01-19 06_Paper/COG-ED/Manuscript.Rmd
added package glmmTMB to package list

--- 2022-01-17 06_Paper/COG-ED/Manuscript.Rmd
@@
   library(huxtable)     # create huxtable
-# library(glmmTMB)      # from the glmmTMB package for multi level models
+  library(glmmTMB)      # from the glmmTMB package for multi level models
   library(BayesFactor)  # computing Bayes factors, "BayesFactor" package

### 2022-01-19 06_Paper/COG-ED/Manuscript.Rmd
tried knitting but still error

--- 2022-01-19 06_Paper/COG-ED/Manuscript.Rmd
@@
     orcid         : "0000-0003-2892-884X"
-    affiliation   : "1,*"
+    affiliation   : "1"
     corresponding : yes
@@
     email         : "josephine.zerna@tu-dresden.de"
+    equal_contrib : yes
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
@@
     orcid         : "0000-0001-5963-9229"
-    affiliation   : "1,*"
+    affiliation   : "1"
+    equal_contrib : yes
     role:
@@
     institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
-authornote: |
-  * Shared first authorship
 abstract: |
@@
     - \usepackage{setspace}\doublespacing
-    - \usepackage{pdfpages}
-editor_options: 
-  markdown: 
-    wrap: sentence
+    - \usepackage[final]{pdfpages}
+
 ---
@@
 
-```{r pipelines_dprime, echo=FALSE, message=FALSE, warning=FALSE}
+```{r pipelinesdprime, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r Hypothesis_1a, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Hypothesis1a, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r Hypothesis_1b, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Hypothesis1b, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r Hypothesis_1c, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Hypothesis1c, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r Hypothesis_2a, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Hypothesis2a, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r Hypothesis_2b_2c, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
+```{r Hypothesis2bc, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
 
-```{r SCA_plot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
+```{r SCAplot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
 
@@
 
-```{r Hypothesis_3a, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Hypothesis3a, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{r Hypothesis_3b, echo=FALSE, message=FALSE, warning=FALSE}
+```{r Hypothesis3b, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup
 
@@
 
-```{r figure1_appendix, echo=FALSE, message=FALSE, warning=FALSE}
+```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
-\includepdf[pages={-}]{here("02_Hypotheses", "Design_Table_T1.pdf")}
+\includepdf[pages={-}]{Design_Table_T1.pdf}
 

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
corrected typo (hyptohesis 3a vs 3b)
added caption of figure one to r chunk

@@
 
-```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
+```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back."}
 
@@
 ```
-*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
 
@@
 Fit:
-`r apa_print(hypothesis3a)$estimate$modelfit$r2`
+`r apa_print(hypothesis3b)$estimate$modelfit$r2`
 
 $BF10=$ `r extractBF(hypothesis3b_BF)$bf`
-
-\endgroup

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
changed fig location and caption

@@
 
-```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back."}
+```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}
 
@@
 
-`r Figure2`
-*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
-
-`r Figure3`
-*Supplementary Figure 2* Results of the specification curve analysis for the multi level model.
-The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
+\newpage
+
+# Design Table
+
+\includepdf[pages={-}]{Design_Table_T1.pdf}
+
+\newpage
+
+# Supplement
+
+## Results of the pilot study
+
+### Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis1a_rmanova)$full_result`
+
+Paired contrasts:
+
+`r hypothesis1a_contrasts`
+
+### Hypothesis 1b: Reaction time increases with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis1b_rmanova)$full_result`
+
+Paired contrasts:
+
+`r hypothesis1b_contrasts`
+
+### Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
+
+Mental subscale ANOVA:
+
+`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_mental_BF)$bf`
+
+Mental subscale paired contrasts:
+
+`r hypothesis1c_mental_contrasts`
+
+Physical subscale ANOVA:
+
+`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_physical_BF)$bf`
+
+Physical subscale paired contrasts:
+
+`r hypothesis1c_physical_contrasts`
+
+Time subscale ANOVA:
+
+`r apa_print(hypothesis1c_time_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_time_BF)$bf`
+
+Time subscale paired contrasts:
+
+`r hypothesis1c_time_contrasts`
+
+Performance subscale ANOVA:
+
+`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_performance_BF)$bf`
+
+Performance subscale paired contrasts:
+
+`r hypothesis1c_performance_contrasts`
+
+Effort subscale ANOVA:
+
+`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`
+
+Effort subscale paired contrasts:
+
+`r hypothesis1c_effort_contrasts`
+
+Frustration subscale ANOVA:
+
+`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`
+
+Frustration subscale paired contrasts:
+
+`r hypothesis1c_frustration_contrasts`
+
+### Hypothesis 2a: Subjective values decline with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis2a_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis2a_BF)$bf`
+
+Paired contrasts:
+
+`r hypothesis2a_contrasts`
+
+### Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
+
+Multi level model:
+
+`r table_1`
+
+### Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
+
+Simple slopes analysis:
+
+`r h2c_ss.table`
+
+```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC.
+NFC = Need for Cognition, SD = standard deviation."}
+
+interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                               plot.points = T, point.shape = T,
+                               x.label = "n-back level", y.label = "subjective value",
+                               legend.main = "NFC", interval = T) + theme_apa() +
+scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
+```
+Johnson-Neyman intervals:
+
+`r h2c_jn.int`
+
+Specification curve analysis:
+
+```{r Fig2cSA and n-back level as predictors of subjective values.
 Estimates with $p<.01$ are indicated by a dot on the line.
 The lower panel shows the preprocessing steps of each corresponding pipeline.
-The $BF10$ of each pipeline's multi level model approached infinity.
-
-\newpage
-
-# Design Table
-
-\includepdf[pages={-}]{Design_Table_T1.pdf}
-
-\newpage
-
-# Supplement
-
-## Results of the pilot study
-
-### Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1a_rmanova)$full_result`
-
-Paired contrasts:
-
-`r hypothesis1a_contrasts`
-
-### Hypothesis 1b: Reaction time increases with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1b_rmanova)$full_result`
-
-Paired contrasts:
-
-`r hypothesis1b_contrasts`
-
-### Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
-
-Mental subscale ANOVA:
-
-`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_mental_BF)$bf`
-
-Mental subscale paired contrasts:
-
-`r hypothesis1c_mental_contrasts`
-
-Physical subscale ANOVA:
-
-`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_physical_BF)$bf`
-
-Physical subscale paired contrasts:
-
-`r hypothesis1c_physical_contrasts`
-
-Time subscale ANOVA:
-
-`r apa_print(hypothesis1c_time_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_time_BF)$bf`
-
-Time subscale paired contrasts:
-
-`r hypothesis1c_time_contrasts`
-
-Performance subscale ANOVA:
-
-`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_performance_BF)$bf`
-
-Performance subscale paired contrasts:
-
-`r hypothesis1c_performance_contrasts`
-
-Effort subscale ANOVA:
-
-`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`
-
-Effort subscale paired contrasts:
-
-`r hypothesis1c_effort_contrasts`
-
-Frustration subscale ANOVA:
-
-`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`
-
-Frustration subscale paired contrasts:
-
-`r hypothesis1c_frustration_contrasts`
-
-### Hypothesis 2a: Subjective values decline with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis2a_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis2a_BF)$bf`
-
-Paired contrasts:
-
-`r hypothesis2a_contrasts`
-
-### Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
-
-Multi level model:
-
-`r table_1`
-
-### Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
-
-Simple slopes analysis:
-
-`r h2c_ss.table`
-
-`r Figure2`
-*Supplementary Figure 1* Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC. NFC = Need for Cognition, SD = standard deviation.
-
-Johnson-Neyman intervals:
-
-`r h2c_jn.int`
-
-Specification curve analysis:
-
-`r Figure3`
-*Supplementary Figure 2* Results of the specification curve analysis for the multi level model.
-The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
-Estimates with $p<.01$ are indicated by a dot on the line.
-The lower panel shows the preprocessing steps of each corresponding pipeline.
-The $BF10$ of each pipeline's multi level model approached infinity.
+The $BF10$ of each pipeline's multi level model approached infinity."}
+
+# create the upper panel first, which will show the estimates of 'level' and 'nfc'
+
+  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
+    geom_line(aes(group = predictor)) +
+    geom_point(data = sca_results, aes(x = num, y = sign)) +
+    geom_text(x = 3, y = -0.01, label = "NFC") +
+    geom_text(x = 3, y = -0.12, label = "Level") +
+    theme_classic() +
+    labs(x = NULL, y = "Fixed effects estimate \u03b2") +
+    scale_y_continuous(lim = c(NA,0.01)) +
+    theme(axis.text.x = element_blank(),
+          axis.line.y = element_line(size = 1, color = "black"), axis.title.y = element_text(margin = margin(r = 10)),
+          legend.position = "none")
+
+  # create the lower part of the plot that indicates the pipeline specifications
+
+  sca_lowerplot <- ggplot(data = sca_results) +
+    geom_hline(yintercept = c(1,6,11), color = "grey", size = 0.5) +
+    geom_hline(yintercept = c(2:5,7:10,12:17), color = "grey", linetype = "dashed", size = 0.2) +
+    geom_point(aes(x = num, y = Dim)) +
+    geom_point(aes(x = num, y = Trans)) +
+    geom_point(aes(x = num, y = Excl)) +
+    theme_classic() +
+    labs(x = "Analysis pipeline", y = NULL) +
+    scale_y_reverse(breaks = c(1:17), lim = c(17,0.5), labels = c(expression(bold("Dimension")),
+                                                                "Across S, across C", "Across S, within C",
+                                                                "Within S, within C", "Within S, across C",
+                                                                expression(bold("Transformation")),
+                                                                "Raw/None", "Log", "Inverse", "Square-root",
+                                                                expression(bold("Exclusion")),
+                                                                "None", "2 MAD from median", " 2.5 MAD from median",
+                                                                "3 MAD from median", "100ms after onset", "200ms after onset")) +
+    theme(axis.text.x = element_blank(), axis.title.x = element_text(margin = margin(t = 10)),
+          axis.line.y = element_line(size = 1, color = "black"),
+          legend.position = "none")
+
+  # put both plots into one
+
+  ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
+```
 

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
fixed fig caption issue

@@
 
-```{r Fig2cSA and n-back level as predictors of subjective values.
+<!-- (ref:Fig2cSA-caption) Results of the specification curve analysis for the multi level model.
+The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
+Estimates with $p<.01$ are indicated by a dot on the line.
+The lower panel shows the preprocessing steps of each corresponding pipeline.
+The $BF10$ of each pipeline's multi level model approached infinity.-->
+```{r Fig2cSA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.
+The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
 Estimates with $p<.01$ are indicated by a dot on the line.

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
test without huxtable

@@
   library(interactions) # for simple slopes analysis
-  library(huxtable)     # create huxtable
+  #library(huxtable)     # create huxtable
   library(glmmTMB)      # from the glmmTMB package for multi level models

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
tried to fix contrasts

@@
 
-`r hypothesis1a_contrasts`
+```{r} 
+apa_table(
+  hypothesis1a_contrasts
+)
+```
 
@@
 interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                               plot.points = T, point.shape = T,
+                               plot.points = TRUE, point.shape = TRUE,
                                x.label = "n-back level", y.label = "subjective value",
-                               legend.main = "NFC", interval = T) + theme_apa() +
+                               legend.main = "NFC", interval = TRUE) + theme_apa() +
 scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
fix apa tables second try
apa_table third try
corrected supplement tables
evtl. change table 1!!

@@
 floatsintext      : no
+figsintext        : yes
 figurelist        : no
@@
 
-```{r} 
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 apa_table(
   hypothesis1a_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1a XXX"
+  , note = "XXX."
+  , escape = TRUE
 )
@@
 
-`r hypothesis1b_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  hypothesis1b_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1b XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
+```
 
@@
 
-`r hypothesis1c_mental_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis1c_mental_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
+```
 
@@
 
-`r hypothesis1c_physical_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+ apa_table(
+   hypothesis1c_physical_contrasts
+   , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
+   , note = "XXX."
+   , escape = TRUE
+ )
+```
 
@@
 
-`r hypothesis1c_time_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+ apa_table(
+   hypothesis1c_time_contrasts
+   , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
+   , note = "XXX."
+   , escape = TRUE
+ )
+```
 
@@
 
-`r hypothesis1c_performance_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+ apa_table(
+   hypothesis1c_performance_contrasts
+   , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
+   , note = "XXX."
+   , escape = TRUE
+ )
+```
 
@@
 
-`r hypothesis1c_effort_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+ apa_table(
+   hypothesis1c_effort_contrasts
+   , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
+   , note = "XXX."
+   , escape = TRUE
+ )
+```
 
@@
 
-`r hypothesis1c_frustration_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+ apa_table(
+   hypothesis1c_frustration_contrasts
+   , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
+   , note = "XXX."
+   , escape = TRUE
+ )
+```
 
@@
 
-`r hypothesis2a_contrasts`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+ apa_table(
+   hypothesis2a_contrasts
+   , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
+   , note = "XXX."
+   , escape = TRUE
+ )
+```
 
@@
 
-`r h2c_ss.table`
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  h2c_ss.table
+  , caption = "Simple slope analysis of SVs...XXX"
+  , note = "XXX."
+  , escape = FALSE
+)
+```
 
@@
 
-<!-- (ref:Fig2cSA-caption) Results of the specification curve analysis for the multi level model.
-The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
-Estimates with $p<.01$ are indicated by a dot on the line.
-The lower panel shows the preprocessing steps of each corresponding pipeline.
-The $BF10$ of each pipeline's multi level model approached infinity.-->
 ```{r Fig2cSA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
Error fixen: Tabellen auskommentiert

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_mental_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
-  , note = "XXX."
-  , escape = TRUE
-)
+#apa_table(
+#  hypothesis1c_mental_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
- apa_table(
-   hypothesis1c_physical_contrasts
-   , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
-   , note = "XXX."
-   , escape = TRUE
- )
+#apa_table(
+#  hypothesis1c_physical_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
- apa_table(
-   hypothesis1c_time_contrasts
-   , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
-   , note = "XXX."
-   , escape = TRUE
- )
+#apa_table(
+#  hypothesis1c_time_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
- apa_table(
-   hypothesis1c_performance_contrasts
-   , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
-   , note = "XXX."
-   , escape = TRUE
- )
+#apa_table(
+#  hypothesis1c_performance_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
- apa_table(
-   hypothesis1c_effort_contrasts
-   , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
-   , note = "XXX."
-   , escape = TRUE
- )
+#apa_table(
+#  hypothesis1c_effort_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
- apa_table(
-   hypothesis1c_frustration_contrasts
-   , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
-   , note = "XXX."
-   , escape = TRUE
- )
+#apa_table(
+#  hypothesis1c_frustration_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
- apa_table(
-   hypothesis2a_contrasts
-   , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
-   , note = "XXX."
-   , escape = TRUE
- )
+#apa_table(
+#  hypothesis2a_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  h2c_ss.table
-  , caption = "Simple slope analysis of SVs...XXX"
-  , note = "XXX."
-  , escape = FALSE
-)
+#apa_table(
+#  h2c_ss.table
+#  , caption = "Simple slope analysis of SVs...XXX"
+#  , note = "XXX."
+#  , escape = FALSE
+#)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
Table 1c Mental dazu genommen
Vorher funktioniert alles

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_mental_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis1c_mental_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
1c physical hinzugefügt
1c mental klappt

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_physical_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis1c_physical_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
1c time and performance hinzugefügt
1c physical funktioniert

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_time_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis1c_time_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
1c effort und frustration hinzugefügt
time & performance klappen

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_performance_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis1c_performance_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis2a_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis2a_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#apa_table(
-#  h2c_ss.table
-#  , caption = "Simple slope analysis of SVs...XXX"
-#  , note = "XXX."
-#  , escape = FALSE
-#)
+apa_table(
+  h2c_ss.table
+  , caption = "Simple slope analysis of SVs...XXX"
+  , note = "XXX."
+  , escape = FALSE
+)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
Performance entfernt

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+#apa_table(
+#  hypothesis1c_performance_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
+```
+
+Effort subscale ANOVA:
+
+`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`
+
+Effort subscale paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
-  hypothesis1c_performance_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
+  hypothesis1c_effort_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
   , note = "XXX."
@@
 
-Effort subscale ANOVA:
-
-`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`
-
-Effort subscale paired contrasts:
+Frustration subscale ANOVA:
+
+`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`
+
+Frustration subscale paired contrasts:
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_effort_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
-```
-
-Frustration subscale ANOVA:
-
-`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`
-
-Frustration subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_frustration_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis1c_frustration_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
Performance Effort Frustration rausgenommen

--- 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_performance_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
-  , note = "XXX."
-  , escape = TRUE
-)
+#apa_table(
+#  hypothesis1c_performance_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
performance und effort tables hinzugefügt

--- 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_effort_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis1c_effort_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis2a_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
-  , note = "XXX."
-  , escape = TRUE
-)
+#apa_table(
+#  hypothesis2a_contrasts
+#  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
+#  , note = "XXX."
+#  , escape = TRUE
+#)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
Frustration noch hinzugefügt
Bisher funktionieren alle 1c Tabellen

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-#apa_table(
-#  hypothesis1c_frustration_contrasts
-#  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
-#  , note = "XXX."
-#  , escape = TRUE
-#)
+apa_table(
+  hypothesis1c_frustration_contrasts
+  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#apa_table(
-#  h2c_ss.table
-#  , caption = "Simple slope analysis of SVs...XXX"
-#  , note = "XXX."
-#  , escape = FALSE
-#)
+apa_table(
+  h2c_ss.table
+  , caption = "Simple slope analysis of SVs...XXX"
+  , note = "XXX."
+  , escape = TRUE
+)
 ```

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
knitting successful & pretty :) thanks Christoph

@@
 bibliography      : CERED.bib
-floatsintext      : no
+floatsintext      : yes
 figsintext        : yes
@@
 
-```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
-
-  knitr::opts_chunk$set(echo = TRUE)
+```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
+
+  knitr::opts_chunk$set(out.width = "\\textwidth")
   library(bibtex)
@@
 
+  # rename columns and contrasts for apa_print
+
+  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)
+
   # remove the temporary variable
@@
                                                    progress = FALSE, paired = TRUE))$bf)
+
+  # rename columns and contrasts for apa_print
+
+  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
 
@@
 
+  # rename columns and contrasts for apa_print
+
+  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
+  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
+  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
+  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
+  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
+  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)
+
   # remove the temporary variable
@@
                                                    progress = FALSE, paired = TRUE))$bf)
+
+  # rename columns and contrasts for apa_print
+
+  colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  hypothesis2a_contrasts$Contrast <- gsub("X", "", hypothesis2a_contrasts$Contrast)
 
@@
                              round(m1_h2c.ss$ints[c(2,3)], digits = 2))
-  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI", "$p$-value", "Beta", "$SE$" )
+  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95\\% CI", "$p$-value", "Beta", "$SE$" )
   # columns 2:5 belong to "Slopes of NFC"
@@
     theme_classic() +
-    labs(x = NULL, y = "Fixed effects estimate \u03b2") +
+    labs(x = NULL, y = "Fixed effects\nestimate \u03b2") +
     scale_y_continuous(lim = c(NA,0.01)) +
@@
 
-### Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
+## Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
 
@@
 apa_table(
-  hypothesis1a_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1a XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1a_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 
-### Hypothesis 1b: Reaction time increases with increasing n-back level.
+## Hypothesis 1b: Reaction time increases with increasing n-back level.
 
@@
 apa_table(
-  hypothesis1b_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1b XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1b_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 
-### Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
+## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
 
@@
 apa_table(
-  hypothesis1c_mental_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1c_mental_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 apa_table(
-  hypothesis1c_physical_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1c_physical_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 apa_table(
-  hypothesis1c_time_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1c_time_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 apa_table(
-  hypothesis1c_performance_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1c_performance_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 apa_table(
-  hypothesis1c_effort_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1c_effort_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 apa_table(
-  hypothesis1c_frustration_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis1c_frustration_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 
-### Hypothesis 2a: Subjective values decline with increasing n-back level.
+## Hypothesis 2a: Subjective values decline with increasing n-back level.
 
@@
 apa_table(
-  hypothesis2a_contrasts
-  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
-  , note = "XXX."
-  , escape = TRUE
+  hypothesis2a_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing subjective values between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  escape = FALSE,
+  placement = "H"
 )
@@
 
-### Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
+## Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
 
@@
 
-### Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
+## Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  h2c_ss.table
-  , caption = "Simple slope analysis of SVs...XXX"
-  , note = "XXX."
-  , escape = TRUE
-)
-```
+`r table_2`
 
@@
 ```
+
 Johnson-Neyman intervals:
@@
 
-```{r Fig2cSA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.
+```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.
 The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
@@
   ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
-```
-
-### Hypothesis 3a: Subjective values positively predict individual NCS scores.
+
+```
+
+## Hypothesis 3a: Subjective values positively predict individual NCS scores.
 
@@
 
-### Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.
+## Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.
 

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
added authornote for corresponding author info

@@
     institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
+authornote: |
 abstract: |

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
fixed one citation

@@
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
-Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; Xu2021].
+Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; @Xu2021].
 However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
changed fig1 caption

@@
 ```
-*Fig.1* Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
+*Fig.1* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
 
@@
 
-```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}
+```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}
 

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
changed wording of h2b in intro text

@@
 Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
-Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) SVs decline with increasing n-back level even after controlling for declining task performance.
+Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) they do so even after controlling for declining task performance.
 Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd

@@
 Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) they do so even after controlling for declining task performance.
-Here we added they hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
+Here we added the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
 And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
@@
 
-The sample of the pilot study consisted of $N=$ `r length(setindex)` participants (`r round((table(data_quest$gender)[2]/length(setindex))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
+The sample of the pilot study consisted of $N=$ `r length(setindex)-1` participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)` ($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
 One participant's data was removed because they misunderstood the instruction.
-Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=$ `r length(setindex)-1` data sets.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=$ `r length(setindex)-2` data sets.
 

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
put pilot results into methodsection & fixed typos

@@
 Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
-If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if the choose 1-back, it decreases by 0.50\$.
+If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
 This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
@@
 We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
-Figure 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
+Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
 The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
@@
 
-# Methods
-
-The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.
-
-## Ethics information
-
-## Pilot data
-
-The sample of the pilot study consisted of $N=$ `r length(setindex)-1` participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)` ($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
-One participant's data was removed because they misunderstood the instruction.
-Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=$ `r length(setindex)-2` data sets.
-
-## Design
-
-Healthy participants aged 18 to 30 years will be recruited using the software *ORSEE* [@Greiner2015].
-Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
-NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
-Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
-The NFC scale shows comparably high internal consistency [Cronbach's $\alpha$ \> .80; @Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
-A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
-In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
-The paradigm starts with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
-To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-After each level, participants fill out the NASA-TLX on a tablet.
-Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
-Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back.
-This is only done to incentivise truthful behavior in the ED procedure, so the n-back data of this part will not be analyzed.
-The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
-Participants will receive 30€ in total or course credit for participation.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
-
-## Sampling plan
-
-A sample size analysis with G*Power [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
-[-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
-The power analyses of all other hypotheses yielded smaller necessary sample sizes.
-To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 60 to 70 participants.
-
-## Analysis plan
-
-Data collection and analysis will not be performed blind to the conditions of the experiments.
-We aim to conduct all analysis as described in Westbrook et al.
-[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
-The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
-Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100 ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
-Aggregated RT values will be described using the median and the median of absolute deviation (MAD) as robust estimates of center and variability, respectively [@Lachaud2011].
-Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
-Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
-Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
-To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
-Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
-An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
-Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
-
-To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
-We will apply restricted maximum likelihood (REML) to fit the model.
-First, we will calculate the intraclass correlation (ICC) on the basis of the null model.
-Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
-Within the model, we will control for *d'*, RT, correct, and post-correct trials.
-$$
-SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
-$$
-Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
-We will visually inspect the residuals of the final model.
-The approximately normal distribution indicates no evidence to perform model criticism.  
-Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
-To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
-
-To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3 $MAD$ from the median, RTs below 100 or 200 ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
-The MLM will be run with each of the 63 pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100 ms).
-The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
-
-The association of ED and NFC will be examined with a regression using the AUC of each participant's SVs to predict their NFC score.
-A second regression will additionally include the mean of the NASA-TLX subscales' AUCs of each participant as a predictor.
-Since we do not have a fixed SV of 1 for 1-back, we cannot apply the "AUC" computation of Westbrook et al.
-[-@Westbrook2013], which was the mean of the AUCs of the SVs of each higher n-back level and 1-back, yielding values between 0 and 1.
-Consequently, we will choose a different way of quantifying the individual degree of ED.
-A classic AUC cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.
-This is the opposite for the sum of the ascent between SVs.
-Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.
-
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].
-
-## Data availability
-
-The data of this study can be downloaded from osf.io/vnj8x/.
-
-## Code availability
-
-The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
-
 ```{r Hypothesis1a, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-## Results of the pilot study
-
-We collected data from $N = 15$ participants.
-One participant's NASA-TLX data is incomplete due to a technical error, so hypotheses 1c and 3b are analyzed using the 14 complete data sets.
+# Methods
+
+The paradigm was written and presented using *Psychopy* [@Peirce2019].
+We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.
+
+## Ethics information
+
+## Pilot data
+
+The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old).
+One participant's data was removed because they misunderstood the instruction.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
 The results showed increases in subjective and objective task load measures with higher n-back level.
@@
 The specification curve analysis showed that this pattern was true for all 63 pipelines.
-And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the AUC of NASA-TLX scores did.
+And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
 All results are detailed in the *Supplementary Material*.
+
+## Design
+
+Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE* [@Greiner2015].
+Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
+NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
+The NFC scale shows comparably high internal consistency (Cronbach's $\alpha$ \> .80) [@Bless1994; @Fleischhauer2010].
+Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
+A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
+In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
+The paradigm starts with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
+To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
+After each level, participants fill out the NASA-TLX on a tablet.
+Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
+Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back.
+This is only done to incentivise truthful behavior in the ED procedure, so the n-back data of this part will not be analyzed.
+The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
+The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
+Participants will receive 30€ in total or course credit for participation.
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+
+## Sampling plan
+
+A sample size analysis with *G$\times$Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
+[-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
+The power analyses of all other hypotheses yielded smaller necessary sample sizes.
+To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 60 to 70 participants.
+
+## Analysis plan
+
+Data collection and analysis will not be performed blind to the conditions of the experiments.
+We aim to conduct all analysis as described in Westbrook et al.
+[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
+The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
+Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
+Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
+Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
+Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
+To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
+For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
+Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
+An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
+Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
+
+To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
+We will apply restricted maximum likelihood (REML) to fit the model.
+First, we will calculate the intraclass correlation (ICC) on the basis of the null model.
+Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+Within the model, we will control for *d'*, RT, correct, and post-correct trials.
+$$
+SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
+$$
+Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
+We will visually inspect the residuals of the final model.
+The approximately normal distribution indicates no evidence to perform model criticism.  
+Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
+To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
+
+To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
+The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
+The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
+
+The association of ED and NFC will be examined with a regression using the $AUC$ of each participant's SVs to predict their NFC score.
+A second regression will additionally include the mean of the NASA-TLX subscales' $AUCs$ of each participant as a predictor.
+Since we do not have a fixed SV of 1 for 1-back, we cannot apply the "$AUC$" computation of Westbrook et al.
+[-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
+Consequently, we will choose a different way of quantifying the individual degree of ED.
+A classic $AUC$ cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.
+This is the opposite for the sum of the ascent between SVs.
+Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.
+
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].
+
+## Data availability
+
+The data of this study can be downloaded from [osf.io/vnj8x/](https://osf.io/vnj8x/).
+
+## Code availability
+
+The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
 
@@
 
-Predictor AUC NASA-TLX:
+Predictor $AUC$ NASA-TLX:
 `r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
included effect size and CI for H1a

@@
   library(knitr)        # for including plots and such, "knitr" package
+  library(effectsize)   # for effect sizes and CIs, "effectsize" package
 
@@
 And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
-All results are detailed in the *Supplementary Material*.
+All results are detailed in the Supplementary Material.
 
@@
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+**OR**
+The authors received no specific funding for this work.
 
@@
 
-\includepdf[pages={-}]{Design_Table_T1.pdf}
+(Starts on next page)
+
+\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
 
@@
 
-`r apa_print(hypothesis1a_rmanova)$full_result`
+`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI [`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`]
 

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
corrected double brackets

@@
 
-`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI [`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`]
+`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`
 

### 2022-01-21 06_Paper/COG-ED/Manuscript.Rmd
eta2, CIs, and rounded BFs for all ANOVAs

@@
 
-`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`
+`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis1b_rmanova)$full_result`
+`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_mental_BF)$bf`
+`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_physical_BF)$bf`
+`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis1c_time_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_time_BF)$bf`
+`r apa_print(hypothesis1c_time_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_performance_BF)$bf`
+`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_effort_BF)$bf`
+`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis1c_frustration_BF)$bf`
+`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis2a_rmanova)$full_result`, $BF10=$ `r extractBF(hypothesis2a_BF)$bf`
+`r apa_print(hypothesis2a_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`
 

### 2022-01-24 06_Paper/COG-ED/Manuscript.Rmd
implemented CIs and effect sizes for contrasts

@@
 
-  # rename columns and contrasts for apa_print
-
-  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  # get effect size and confidence interval
+
+  hypothesis1a_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[1], df_error = hypothesis1a_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                     format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[2], df_error = hypothesis1a_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                     format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[3], df_error = hypothesis1a_contrasts$df[3], ci = 0.95), digits = 2)[1,1])
+
+  hypothesis1a_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[1], df_error = hypothesis1a_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[2], df_error = hypothesis1a_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[3], df_error = hypothesis1a_contrasts$df[3], ci = 0.95), digits = 2)[1,2])
+
+  # rename contrasts and column names
+
+  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)
@@
 
-  # rename columns and contrasts for apa_print
-
-  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  # get effect size and confidence interval
+
+  hypothesis1b_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[1], df_error = hypothesis1b_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                     format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[2], df_error = hypothesis1b_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                     format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[3], df_error = hypothesis1b_contrasts$df[3], ci = 0.95), digits = 2)[1,1])
+
+  hypothesis1b_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[1], df_error = hypothesis1b_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[2], df_error = hypothesis1b_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[3], df_error = hypothesis1b_contrasts$df[3], ci = 0.95), digits = 2)[1,2])
+
+  # rename contrasts and column names
+
+  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
@@
 
-      newdata <- data.frame(subject = data_quest$subject[setindex[i]], level = j,
+      newdata <- data.frame(subject = data_quest$subject[setindex[i]],
+                            level = j,
                             mental = data_quest$nasa_tlx_01[setindex[i]+j+2],
@@
 
-  # rename columns and contrasts for apa_print
-
-  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  # get effect sizes and confidence intervals
+
+  hypothesis1c_mental_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[1], df_error = hypothesis1c_mental_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[2], df_error = hypothesis1c_mental_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[3], df_error = hypothesis1c_mental_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[4], df_error = hypothesis1c_mental_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[5], df_error = hypothesis1c_mental_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[6], df_error = hypothesis1c_mental_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
+  hypothesis1c_mental_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[1], df_error = hypothesis1c_mental_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[2], df_error = hypothesis1c_mental_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[3], df_error = hypothesis1c_mental_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[4], df_error = hypothesis1c_mental_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[5], df_error = hypothesis1c_mental_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[6], df_error = hypothesis1c_mental_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+
+  hypothesis1c_physical_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[1], df_error = hypothesis1c_physical_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[2], df_error = hypothesis1c_physical_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[3], df_error = hypothesis1c_physical_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[4], df_error = hypothesis1c_physical_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[5], df_error = hypothesis1c_physical_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[6], df_error = hypothesis1c_physical_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
+  hypothesis1c_physical_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[1], df_error = hypothesis1c_physical_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[2], df_error = hypothesis1c_physical_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[3], df_error = hypothesis1c_physical_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[4], df_error = hypothesis1c_physical_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[5], df_error = hypothesis1c_physical_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[6], df_error = hypothesis1c_physical_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+
+  hypothesis1c_time_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[1], df_error = hypothesis1c_time_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[2], df_error = hypothesis1c_time_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[3], df_error = hypothesis1c_time_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[4], df_error = hypothesis1c_time_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[5], df_error = hypothesis1c_time_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[6], df_error = hypothesis1c_time_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
+  hypothesis1c_time_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[1], df_error = hypothesis1c_time_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[2], df_error = hypothesis1c_time_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[3], df_error = hypothesis1c_time_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[4], df_error = hypothesis1c_time_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[5], df_error = hypothesis1c_time_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[6], df_error = hypothesis1c_time_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+
+  hypothesis1c_effort_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[1], df_error = hypothesis1c_effort_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[2], df_error = hypothesis1c_effort_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[3], df_error = hypothesis1c_effort_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[4], df_error = hypothesis1c_effort_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[5], df_error = hypothesis1c_effort_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[6], df_error = hypothesis1c_effort_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
+  hypothesis1c_effort_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[1], df_error = hypothesis1c_effort_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[2], df_error = hypothesis1c_effort_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[3], df_error = hypothesis1c_effort_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[4], df_error = hypothesis1c_effort_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[5], df_error = hypothesis1c_effort_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[6], df_error = hypothesis1c_effort_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+
+  hypothesis1c_frustration_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[1], df_error = hypothesis1c_frustration_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[2], df_error = hypothesis1c_frustration_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[3], df_error = hypothesis1c_frustration_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[4], df_error = hypothesis1c_frustration_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[5], df_error = hypothesis1c_frustration_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[6], df_error = hypothesis1c_frustration_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
+  hypothesis1c_frustration_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[1], df_error = hypothesis1c_frustration_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[2], df_error = hypothesis1c_frustration_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[3], df_error = hypothesis1c_frustration_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[4], df_error = hypothesis1c_frustration_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[5], df_error = hypothesis1c_frustration_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[6], df_error = hypothesis1c_frustration_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+
+  hypothesis1c_performance_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[1], df_error = hypothesis1c_performance_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[2], df_error = hypothesis1c_performance_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[3], df_error = hypothesis1c_performance_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[4], df_error = hypothesis1c_performance_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[5], df_error = hypothesis1c_performance_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[6], df_error = hypothesis1c_performance_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
+  hypothesis1c_performance_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[1], df_error = hypothesis1c_performance_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[2], df_error = hypothesis1c_performance_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[3], df_error = hypothesis1c_performance_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[4], df_error = hypothesis1c_performance_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[5], df_error = hypothesis1c_performance_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[6], df_error = hypothesis1c_performance_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+
+  # rename columns and contrasts
+
+  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
-  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
-  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
-  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
-  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
-  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
   hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)
@@
 
+Effect size and confidence interval:
+
+$\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
+
+Bayes factor:
+
 $BF10=$ `r extractBF(hypothesis3a_BF)$bf`
@@
 
+Effect size and confidence interval:
+
+$\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
+
+Bayes factor:
+
 $BF10=$ `r extractBF(hypothesis3b_BF)$bf`

### 2022-01-24 06_Paper/COG-ED/Manuscript.Rmd
added CI to footnote of tables
figure numbering is on point

@@
     - \usepackage[final]{pdfpages}
+    - \usepackage{chngcntr}
 
 ---
+\renewcommand\thesection{\Alph{section}}
+\counterwithout{figure}{section}
+\setcounter{figure}{0}
 
@@
 
-  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)
@@
 
-  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
@@
 
-  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
-  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
-  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
-  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
-  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
-  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95% CI$")
+  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)
@@
 
-  # rename columns and contrasts for apa_print
-
-  colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$")
+  # get effect size and confidence intervals
+
+  hypothesis2a_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[1], df_error = hypothesis2a_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[2], df_error = hypothesis2a_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[3], df_error = hypothesis2a_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[4], df_error = hypothesis2a_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[5], df_error = hypothesis2a_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
+                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[6], df_error = hypothesis2a_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
+  hypothesis2a_contrasts$CI <- c(format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[1], df_error = hypothesis2a_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[2], df_error = hypothesis2a_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[3], df_error = hypothesis2a_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[4], df_error = hypothesis2a_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[5], df_error = hypothesis2a_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
+                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[6], df_error = hypothesis2a_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+
+  # rename columns and contrasts
+
+  colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis2a_contrasts$Contrast <- gsub("X", "", hypothesis2a_contrasts$Contrast)
@@
 
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)] <- 
-    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.01)],"*")
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)] <- 
-    paste0(h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.05)],"*")
-  h2b_result.table$`$p$-value`[which(h2b_result.table$`$p$-value`<.001)] <- 
+  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.01)] <- 
+    paste0(h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.01)],"*")
+  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.05)] <- 
+    paste0(h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.05)],"*")
+  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.001)] <- 
     paste0("<.001***")
 
-  h2b_result.table$`Random Effects (SD)`[3:6] <- paste0("")
+  h2b_result.table$ `Random Effects (SD)`[3:6] <- paste0("")
 
@@
 
-  h2c_ss.table$`$p$-value`  [which(h2c_ss.table$`$p$-value`<.01)] <- 
-    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.01)],"*")
-  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)] <- 
-    paste0(h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.05)],"*")
-  h2c_ss.table$`$p$-value`[which(h2c_ss.table$`$p$-value`<.001)] <- 
+  h2c_ss.table$ `$p$-value`  [which(h2c_ss.table$ `$p$-value`<.01)] <- 
+    paste0(h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.01)],"*")
+  h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.05)] <- 
+    paste0(h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.05)],"*")
+  h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.001)] <- 
     paste0("<.001***")
@@
 
-  h2c_ss.table$`$p$-value` <- str_replace(h2c_ss.table$`$p$-value`, "0.", ".")
+  h2c_ss.table$ `$p$-value` <- str_replace(h2c_ss.table$ `$p$-value`, "0.", ".")
 
@@
 
-A sample size analysis with *G$\times$Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
+A sample size analysis with _G*Power_ [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
 [-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
@@
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-**OR**
-The authors received no specific funding for this work.
 
@@
 \newpage
+\setcounter{figure}{0}
 
@@
 
-```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back."}
+```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 
+*Figure 1* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back.
+
 \newpage
@@
 
+\counterwithin{figure}{section}
+\setcounter{section}{19}
+\setcounter{figure}{0}
+
 ## Results of the pilot study
@@
 
-`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis1c_mental_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1c_mental_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis1c_physical_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1c_physical_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis1c_time_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1c_time_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis1c_performance_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1c_performance_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis1c_effort_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1c_effort_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`
+`r apa_print(hypothesis1c_frustration_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-`r apa_print(hypothesis2a_rmanova)$full_result`, $\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$`r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`
+`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`
 
@@
   caption = "Paired contrasts for the rmANOVA comparing subjective values between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 ```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC.
-NFC = Need for Cognition, SD = standard deviation."}
+NFC = Need for Cognition, SD = standard deviation.", fig.pos="H"}
 
@@
 The lower panel shows the preprocessing steps of each corresponding pipeline.
-The $BF10$ of each pipeline's multi level model approached infinity."}
+The $BF10$ of each pipeline's multi level model approached infinity.", fig.pos="H"}
 
@@
     geom_point(data = sca_results, aes(x = num, y = sign)) +
-    geom_text(x = 3, y = -0.01, label = "NFC") +
-    geom_text(x = 3, y = -0.12, label = "Level") +
+    geom_text(x = 3, y = -0.02, label = "NFC", size = 3) +
+    geom_text(x = 3, y = -0.13, label = "Level", size = 3) +
     theme_classic() +
@@
 
-$\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
+$\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
 
@@
 
-$\eta_{p}^{2}=$`r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
-
-Bayes factor:
-
-$BF10=$ `r extractBF(hypothesis3b_BF)$bf`
+$\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
+
+Bayes factors:
+
+$BF10=$ `r extractBF(hypothesis3b_BF)$bf[1]` for predictor $AxAUC$
+
+$BF10=$ `r extractBF(hypothesis3b_BF)$bf[2]` for predictor $AUC$ NASA-TLX

### 2022-01-25 06_Paper/COG-ED/Manuscript.Rmd
implemented conditional loading of packages

@@
 
+  # set the output for figures and tables to the width of the text throughout the entire script
+
   knitr::opts_chunk$set(out.width = "\\textwidth")
-  library(bibtex)
-  library(here)         # to set a directory without defined paths, "here" package
-  library(tidyverse)    # plotting and managing data, "tidyverse" package
-  library(bayestestR)   # computing area under the curve, "bayestestR" package
-  library(papaja)       # APA conform output, "papaja" package
-  library(lmerTest)     # for multilevel modeling
-  library(afex)         # compute repeated measures ANOVA, "afex" package
-  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
-  library(sjPlot)       # plot MLM model fit
-  library(kableExtra)   # for great tables in R Markdown
-  library(interactions) # for simple slopes analysis
-  #library(huxtable)     # create huxtable
-  library(glmmTMB)      # from the glmmTMB package for multi level models
-  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
-  library(ggplot2)      # for plotting, "ggplot2" package
-  library(egg)          # for paneling plots, "egg" package
-  library(knitr)        # for including plots and such, "knitr" package
-  library(effectsize)   # for effect sizes and CIs, "effectsize" package
-
-  set_sum_contrasts()   # sets orthogonal contrasts for mixed-effects model 
-                        # and rmANOVA globally in order to get meaningful Type-III tests
+
+  # define required packages
+
+  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
+               "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize")
+
+  # check whether each package is installed and install and/or load library
+
+  installed_packages <- packages %in% rownames(installed.packages())
+  if (any(installed_packages == FALSE)) {
+    install.packages(packages[!installed_packages])
+  }
+  invisible(lapply(packages, library, character.only = TRUE))
+
+  # sets orthogonal contrasts for mixed-effects model and rmANOVA globally in order to get meaningful Type-III tests
+
+  set_sum_contrasts()
 

### 2022-01-25 06_Paper/COG-ED/Manuscript.Rmd
changed p value for SCA from .01 to .05
updated formatting of JN interval

@@
 
-  sca_results$sign <- ifelse(sca_results$pvalue < .01, sca_results$beta, NA)
+  sca_results$sign <- ifelse(sca_results$pvalue < .05, sca_results$beta, NA)
 
@@
 
-Johnson-Neyman intervals:
-
-`r h2c_jn.int`
+Johnson-Neyman interval:
+
+`r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`
 
@@
 The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
-Estimates with $p<.01$ are indicated by a dot on the line.
+Estimates with $p<.05$ are indicated by a dot on the line.
+$N=15$.
 The lower panel shows the preprocessing steps of each corresponding pipeline.

### 2022-01-25 06_Paper/COG-ED/Manuscript.Rmd
added slope statistics to slope plot caption

@@
 
-```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC.
-NFC = Need for Cognition, SD = standard deviation.", fig.pos="H"}
+```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=paste("Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC.
+Slope of $1SD$ below the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[1], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[1], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[1], digits = 3), ", slope of the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[2], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[2], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[2], digits = 3), " slope of $1SD$ above the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[3], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[3], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[3], digits = 3), ".
+NFC = Need for Cognition, SD = standard deviation.", sep=""), fig.pos="H"}
 

### 2022-01-25 06_Paper/COG-ED/Manuscript.Rmd
changed Fig.1 to Figure 1

@@
 ```
-*Fig.1* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
+*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
 
@@
 
-*Figure 1* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back.
+*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back.
 

### 2022-01-26 06_Paper/ER-ED/method.Rmd
deleted blank spaces

@@
 
+# import EMG data
+
+datalist_EMG = lapply(list.files(here("04_RawData", "pilot", "ER-ED/EMG/analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
+                          read.csv, stringsAsFactors = FALSE, header = TRUE)
+
+# new empty frame to store files into
+data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
+                     Lev = double())
 ```

### 2022-01-26 06_Paper/ER-ED/method.Rmd
added loop for data import

@@
                      Lev = double())
+
+# store EMG data in data_EMG frame
+for (i in 1:length(datalist_EMG)) {
+
+  tmp = data.frame(datalist_EMG[[i]][["participant"]], 
+                   datalist_EMG[[i]][["Segment"]], 
+                   datalist_EMG[[i]][["T0T6000Corr-ASNM"]], 
+                   datalist_EMG[[i]][["T0T6000Lev-ASNM"]])
+  colnames(tmp) = names(data_EMG)
+
+  data_EMG = rbind(tmp, data_EMG)
+
+}
+
+#rownames(data_ER) = 1:nrow(data_ER)
+
 ```

### 2022-01-26 06_Paper/ER-ED/method.Rmd
fixed issues in loop

--- 2022-01-03 06_Paper/ER-ED/method.Rmd
@@
 #}
+
+# import EMG data
+
+datalist_EMG = lapply(list.files(here("04_RawData", "pilot", "ER-ED/EMG/analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
+                          read.table, stringsAsFactors = FALSE, header = TRUE)
+
+# new empty frame to store files into
+data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
+                     Lev = double())
+
+# store EMG data in data_EMG frame
+for (i in 1:length(datalist_EMG)) {
+
+  tmp = data.frame(datalist_EMG[[i]][["Filename"]], 
+                   datalist_EMG[[i]][["Segment"]], 
+                   datalist_EMG[[i]][["T0T6000Corr.ASNM"]], 
+                   datalist_EMG[[i]][["T0T6000Lev.ASNM"]])
+  colnames(tmp) = names(data_EMG)
+
+  data_EMG = rbind(tmp, data_EMG)
+
+}
+
+#rownames(data_ER) = 1:nrow(data_ER)
 

### 2022-01-27 06_Paper/ER-ED/method.Rmd
fixed anova issue

@@
 
-aov_arousalView = afex::aov_ez(id = "ID",
+aov_arousalView = afex::aov_ez(data = arousal_view,
+                               id = "ID",
                                dv = "arousal",
-                           data = arousal_view,
                                within = "block",
-                           fun_aggregate = mean) 
-afex::nice(aov_arousalView, es = "pes")
+                               fun_aggregate = mean,
+                               include_aov = TRUE)
 
@@
 
-aov_arousalReg = afex::aov_ez(id = "ID",
+aov_arousalReg = afex::aov_ez(data = arousal_reg,
+                              id = "ID",
                               dv = "arousal",
-                              data = arousal_reg,
                               within = "block",
-                              fun_aggregate = mean)
+                              fun_aggregate = mean,
+                              include_aov = TRUE)
 afex::nice(aov_arousalReg, es = "pes")
@@
 
-aov.effort = afex::aov_ez(id = "ID",
+aov.effort = afex::aov_ez(data = effort_reg,
+                          id = "ID",
                           dv = "effort",
-                          data = effort_reg,
                           within = "block",
-                          fun_aggregate = mean)
+                          fun_aggregate = mean,
+                          include_aov = TRUE)
 afex::nice(aov.effort, es = "pes")

### 2022-01-27 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
renamed file

---
title             : "Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Subjective values of emotion regulation strategies"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Writing - review & editing 
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
authornote:
abstract:
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
wordcount         : "X"
bibliography      : ER_ED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

---
\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}
---

``` {r child = "intro.Rmd"}
```

```{r child = "method.Rmd"}
```

### 2022-01-27 06_Paper/ER-ED/method.Rmd
named figures

@@
 # figure
-ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
+FigPilot1=ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 # figure
-ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
+FigPilot2 = ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 # figure
-ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
+FigPilot3 = ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+

### 2022-01-27 06_Paper/ER-ED/method.Rmd
restructured R chucks
added questionnaire import

@@
 
-#rownames(data_ER) = 1:nrow(data_ER)
+# import questionnaire data from RedCap
 
+data_quest <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
+colnames(data_quest)[1] <- "set" # rename the first column
+
+# remove unnecessary variables from questionnaire data frame
+
+data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
+                                            general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
+                                            researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
+                                            t1_psychopy_nback_csv, files_coged_complete, record_id_2, vl_er,
+                                            date_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
+                                            files_ered_complete, followup_ered_timestamp,
+                                            nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
+                                            nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
+                                            nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
+                                            bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
+                                            who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
+                                            cdrisc_complete, flexer_timestamp, flexer_complete))
+
+```
+
+```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
+## Subjective arousal
+
+# ANOVA subjective arousal ratings
+# View condition
+
+arousal_view = data_ER %>%
+  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
+
+aov_arousalView = afex::aov_ez(data = arousal_view,
+                               id = "ID",
+                               dv = "arousal",
+                               within = "block",
+                               fun_aggregate = mean,
+                               include_aov = TRUE)
+
+# compute posthoc tests for within measures
+posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
+pairs(posthoc_arousalView, adjust = "bonferroni")
+
+# Figure to visualize arousal ratings
+
+# figure
+FigPilot1=ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neu", "view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Arousal Rating")
+
+# View neg and regulate conditions
+
+arousal_reg = data_ER %>%
+  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+
+aov_arousalReg = afex::aov_ez(data = arousal_reg,
+                              id = "ID",
+                              dv = "arousal",
+                              within = "block",
+                              fun_aggregate = mean,
+                              include_aov = TRUE)
+afex::nice(aov_arousalReg, es = "pes")
+
+# compute posthoc tests for within measures
+posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
+pairs(posthoc_arousalReg, adjust = "bonferroni")
+
+# Figure to visualize arousal ratings
+
+# figure
+FigPilot2 = ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neg", "distraction", "distancing", "suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Arousal Rating")
+
+## Subjective effort
+
+# ANOVA subjective effort ratings
+
+effort_reg = data_ER %>%
+  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+
+aov.effort = afex::aov_ez(data = effort_reg,
+                          id = "ID",
+                          dv = "effort",
+                          within = "block",
+                          fun_aggregate = mean,
+                          include_aov = TRUE)
+afex::nice(aov.effort, es = "pes")
+
+# compute posthoc tests for within measure
+posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
+pairs(posthoc_effort, adjust = "bonferroni")
+
+# Figure to visualize effort ratings
+# figure
+FigPilot3 = ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neg", "distraction", "distancing", "suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Effort Rating")
 ```
@@
 
-```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
-## Subjective arousal
-
-# ANOVA subjective arousal ratings
-# View condition
-
-arousal_view = data_ER %>%
-  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
-
-aov_arousalView = afex::aov_ez(data = arousal_view,
-                               id = "ID",
-                               dv = "arousal",
-                               within = "block",
-                               fun_aggregate = mean,
-                               include_aov = TRUE)
-
-# compute posthoc tests for within measures
-posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
-pairs(posthoc_arousalView, adjust = "bonferroni")
-
-# Figure to visualize arousal ratings
-
-# figure
-FigPilot1=ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("view_neu", "view_neg"),
-                   labels = c("Neutral", "Negative"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Arousal Rating")
-
-# View neg and regulate conditions
-
-arousal_reg = data_ER %>%
-  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
-
-aov_arousalReg = afex::aov_ez(data = arousal_reg,
-                              id = "ID",
-                              dv = "arousal",
-                              within = "block",
-                              fun_aggregate = mean,
-                              include_aov = TRUE)
-afex::nice(aov_arousalReg, es = "pes")
-
-# compute posthoc tests for within measures
-posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
-pairs(posthoc_arousalReg, adjust = "bonferroni")
-
-# Figure to visualize arousal ratings
-
-# figure
-FigPilot2 = ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("view_neg", "distraction", "distancing", "suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Arousal Rating")
-
-## Subjective effort
-
-# ANOVA subjective effort ratings
-
-effort_reg = data_ER %>%
-  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
-
-aov.effort = afex::aov_ez(data = effort_reg,
-                          id = "ID",
-                          dv = "effort",
-                          within = "block",
-                          fun_aggregate = mean,
-                          include_aov = TRUE)
-afex::nice(aov.effort, es = "pes")
-
-# compute posthoc tests for within measure
-posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
-pairs(posthoc_effort, adjust = "bonferroni")
-
-# Figure to visualize effort ratings
-# figure
-FigPilot3 = ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("view_neg", "distraction", "distancing", "suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Effort Rating")
-```
+## 2.8 Pilot study

### 2022-01-28 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

--- 2021-11-15 06_Paper/ER-ED/intro.Rmd
@@
 Further influencing factors are for example extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
-Especially for effort, Scheffel and colleagues [-@Scheffel2021] could show that the choice for an ER strategy is mainly influenced by effort.
-### Willst du hier nicht lieber "in our previous work" oder sowas schreiben?
-Wenn die Autoren von sich selbst in der dritten Person sprechen, hab ich immer das Gefühl, dass sie die Lesenden in die Irre führen wollen, indem sie etwas referenzieren, was eigentlich von ihnen selbst ist.
+Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort [@Scheffel2021].
+
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.

### 2022-01-28 06_Paper/ER-ED/TheoreticalBackground.Rmd
added packages for intro part

@@
 ---
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 
+library(targets)    # to keep track of all relevant files
+library(here)       # to set directories without defined paths
+library(papaja)     # APA conform output
+
+# set top level directory to source file
+here::i_am("flag_project_root_CERED.txt")
+```
 # 1. Introduction
@@
 
-## 1.1 ER strategies discounting
+## 1.1 ER strategy discounting
 

### 2022-01-28 06_Paper/COG-ED/Manuscript.Rmd
added comment on figure 1

@@
 ```{r figure1, echo=FALSE, message=FALSE, warning=FALSE} 
+# comment Christoph: Evtl. lieber mit fig.cap = "..." im Chunk arbeiten? Dann wäre das auf jeden fall immer an die Figure attached
 include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))

### 2022-01-28 06_Paper/ER-ED/TheoreticalBackground.Rmd
added figure 1

@@
 library(targets)    # to keep track of all relevant files
+library(knitr)
 library(here)       # to set directories without defined paths
@@
 But our paradigm can also account for the case that a person does not have a clear preference.
-Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs.
+Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
 ### Hier sollte auch noch erwähnt werden, dass wir auch n-back erheben
-
+```{r fig1, echo=FALSE, message=FALSE, warning=FALSE}
+include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
+```
 ## 1.2 The present study

### 2022-01-28 06_Paper/ER-ED/method.Rmd
renamed chunk

@@
 
-```{r setup, include = FALSE}
+```{r SetupMethod, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 
-All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2020] for Windows.
+All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.
 The level of significance was set to $\alpha$ = .05.

### 2022-01-28 06_Paper/ER-ED/TheoreticalBackground.Rmd
renamed setup chunk

@@
 ---
-```{r setup, include = FALSE}
+```{r SetupIntro, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 ### Hier sollte auch noch erwähnt werden, dass wir auch n-back erheben
-```{r fig1, echo=FALSE, message=FALSE, warning=FALSE}
+```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns.
+In the top half, the person has a clear preference for one of the three strategies.
+In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
+This pattern can also be represented by our paradigm."}
 include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))

### 2022-01-28 06_Paper/ER-ED/Questionnaires.R
Update Questionnaires.R

@@ -11,12 +11,20 @@ here::i_am("flag_project_root_CERED.txt")
 # import questionnaire data from RedCap
   
 data_redcap <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"),
-                        stringsAsFactors = FALSE, header = TRUE)
+                        sep = ",", stringsAsFactors = FALSE, header = TRUE)
 colnames(data_redcap)[1] <- "set" # rename the first column
 
 # remove unnecessary variables from questionnaire data frame
   
-data_quest <- subset(data_REDCap, 
+data_quest <- subset(data_redcap,
                     select = c(subject, age, gender, edu,
                                nfc_01, nfc_02, nfc_03, nfc_04, nfc_05, nfc_06, nfc_07, nfc_08, nfc_09, nfc_10, nfc_11, nfc_12, nfc_13, nfc_14, nfc_15, nfc_16,
-                               bis11_01, bis11_02, bis11_03, bis11_04, bis11_05, bis11_06, bis11_07, bis11_08, bis11_09, bis11_10, bis11_11, bis11_12, bis11_13, bis11_14, bis11_15, bis11_16, bis11_17, bis11_18, bis11_19, bis11_20, bis11_21, bis11_22, bis11_23, bis11_24, bis11_25, bis11_26, bis11_27, bis11_28, bis11_29, bis11_30))
+                               bis11_01, bis11_02, bis11_03, bis11_04, bis11_05, bis11_06, bis11_07, bis11_08, bis11_09, bis11_10, bis11_11, bis11_12, bis11_13, bis11_14, bis11_15, bis11_16, bis11_17, bis11_18, bis11_19, bis11_20, bis11_21, bis11_22, bis11_23, bis11_24, bis11_25, bis11_26, bis11_27, bis11_28, bis11_29, bis11_30,
+                               bscs_1, bscs_2, bscs_3, bscs_4, bscs_5, bscs_6, bscs_7, bscs_8, bscs_9, bscs_10, bscs_11, bscs_12, bscs_13,
+                               srs_01, srs_02, srs_03, srs_04, srs_05, srs_06, srs_07, srs_08, srs_09, srs_10,
+                               erq_01, erq_02, erq_03, erq_04, erq_05, erq_06, erq_07, erq_08, erq_10,
+                               who5_1, who5_2, who5_3, who5_4, who5_5,
[…]

### 2022-01-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd

--- 2022-01-27 06_Paper/ER-ED/method.Rmd
@@
 
-#rownames(data_ER) = 1:nrow(data_ER)
+```
 
+```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
+## Subjective arousal
+
+# ANOVA subjective arousal ratings
+# View condition
+
+arousal_view = data_ER %>%
+  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
+
+aov_arousalView = afex::aov_ez(data = arousal_view,
+                               id = "ID",
+                               dv = "arousal",
+                               within = "block",
+                               fun_aggregate = mean,
+                               include_aov = TRUE)
+
+# compute posthoc tests for within measures
+posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
+pairs(posthoc_arousalView, adjust = "bonferroni")
+
+# Figure to visualize arousal ratings
+
+# figure
+FigPilot1=ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neu", "view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Arousal Rating")
+
+# View neg and regulate conditions
+
+arousal_reg = data_ER %>%
+  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+
+aov_arousalReg = afex::aov_ez(data = arousal_reg,
+                              id = "ID",
+                              dv = "arousal",
+                              within = "block",
+                              fun_aggregate = mean,
+                              include_aov = TRUE)
+afex::nice(aov_arousalReg, es = "pes")
+
+# compute posthoc tests for within measures
+posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
+pairs(posthoc_arousalReg, adjust = "bonferroni")
+
+# Figure to visualize arousal ratings
+
+# figure
+FigPilot2 = ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neg", "distraction", "distancing", "suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Arousal Rating")
+
+## Subjective effort
+
+# ANOVA subjective effort ratings
+
+effort_reg = data_ER %>%
+  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+
+aov.effort = afex::aov_ez(data = effort_reg,
+                          id = "ID",
+                          dv = "effort",
+                          within = "block",
+                          fun_aggregate = mean,
+                          include_aov = TRUE)
+afex::nice(aov.effort, es = "pes")
+
+# compute posthoc tests for within measure
+posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
+pairs(posthoc_effort, adjust = "bonferroni")
+
+# Figure to visualize effort ratings
+# figure
+FigPilot3 = ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("view_neg", "distraction", "distancing", "suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Effort Rating")
 ```
@@
 
-```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
-## Subjective arousal
+## 2.8 Pilot study
 
-# ANOVA subjective arousal ratings
-# View condition
-
-arousal_view = data_ER %>%
-  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
-
-aov_arousalView = afex::aov_ez(data = arousal_view,
-                               id = "ID",
-                               dv = "arousal",
-                               within = "block",
-                               fun_aggregate = mean,
-                               include_aov = TRUE)
-
-# compute posthoc tests for within measures
-posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
-pairs(posthoc_arousalView, adjust = "bonferroni")
-
-# Figure to visualize arousal ratings
-
-# figure
-FigPilot1=ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("view_neu", "view_neg"),
-                   labels = c("Neutral", "Negative"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Arousal Rating")
-
-# View neg and regulate conditions
-
-arousal_reg = data_ER %>%
-  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
-
-aov_arousalReg = afex::aov_ez(data = arousal_reg,
-                              id = "ID",
-                              dv = "arousal",
-                              within = "block",
-                              fun_aggregate = mean,
-                              include_aov = TRUE)
-afex::nice(aov_arousalReg, es = "pes")
-
-# compute posthoc tests for within measures
-posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
-pairs(posthoc_arousalReg, adjust = "bonferroni")
-
-# Figure to visualize arousal ratings
-
-# figure
-FigPilot2 = ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("view_neg", "distraction", "distancing", "suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Arousal Rating")
-
-## Subjective effort
-
-# ANOVA subjective effort ratings
-
-effort_reg = data_ER %>%
-  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
-
-aov.effort = afex::aov_ez(data = effort_reg,
-                          id = "ID",
-                          dv = "effort",
-                          within = "block",
-                          fun_aggregate = mean,
-                          include_aov = TRUE)
-afex::nice(aov.effort, es = "pes")
-
-# compute posthoc tests for within measure
-posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
-pairs(posthoc_effort, adjust = "bonferroni")
-
-# Figure to visualize effort ratings
-# figure
-FigPilot3 = ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("view_neg", "distraction", "distancing", "suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Effort Rating")
-```
+The procedure described above was tested in a pilot study with

### 2022-01-31 06_Paper/COG-ED/Manuscript.Rmd
added funding info

--- 2022-01-25 06_Paper/COG-ED/Manuscript.Rmd
@@
 
-This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
+This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
+Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
+Applications for the centralized funds will be reviewed in May.
+Regardless of whether or not this additional funding will be granted, the study can commence immediately.
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

### 2022-02-01 06_Paper/ER-ED/method.Rmd
restructured methods section

@@
 
-## 2.1 Sampling plan
+## 2.1 Ethics information
 
-Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
-Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-We will use all available data in subsequent analyses.
-However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
+## 2.2 Pilot data
 
-## 2.2 Experimental procedure
+The procedure described above was tested in a pilot study with ...
 
+## 2.3 Design
+
+Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015].
+Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
 The study consisted of two sessions, one week apart. 
@@
 Next, electrodes to measure EMG were attached and the ER paradigm was conducted.
-Two days after the secon sessoin, participants received a link to an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-
-Participants received 8.00€ per hour or course credit as compensation for participation.
-Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
-
-## 2.3 Emotion regulation paradigm
 
@@
 After, the block with another 20 negative pictures started.
+
+Participants received 30.00€ or course credit as compensation for participation.
+Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+
+## 2.4 Sampling plan
+
+Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
+Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
+We will use all available data in subsequent analyses.
+However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
 
@@
 The resulting values were entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression).
-
-## 2.8 Pilot study
-
-The procedure described above was tested in a pilot study with

### 2022-02-01 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 
-Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015].
+Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
 Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
@@
 Next, electrodes to measure EMG were attached and the ER paradigm was conducted. 
+Participants received 30.00€ or course credit as compensation for participation.
+Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+
+### 2.3.1 Psychometric measures
+
+The online survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
+To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
+Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
+For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
+Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
+To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
+To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
+Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
+
+### 2.3.2 Emotion regulation paradigm
 
@@
 Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
-Participants were told to actively view neutral and negative pictures (see [2.4](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively.
+Participants were told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively.
 Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
@@
 
-Participants received 30.00€ or course credit as compensation for participation.
-Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
-
-## 2.4 Sampling plan
-
-Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
-Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-We will use all available data in subsequent analyses.
-However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-
-## 2.4 Stimuli
+### 2.3.3 Stimuli
 
@@
 
-## 2.5 Electromyography
+### 2.3.4 Electromyography
 
@@
 
-## 2.6 Psychometric measures
+## 2.4 Sampling plan
 
-Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
-This survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
-To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
-Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
-For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
-Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
-To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
-To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
-Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
+Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
+Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
+Sample size calculation with _G*Power_ [@Faul2007; @Faul2009]
+However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
 

### 2022-02-02 06_Paper/ER-ED/method.Rmd

@@
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Sample size calculation with _G*Power_ [@Faul2007; @Faul2009]
+Sample size calculation was done using _G*Power_ [@Faul2007; @Faul2009].
+In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
+To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
+Power analyses of all other hypotheses yielded smaller sample sizes.
 However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
+Therefore, we aim to collect data of 90 participants.
 
-## 2.7 Statistics
+## 2.5 Analysis plan
 
 All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.
-The level of significance was set to $\alpha$ = .05.
+The level of significance was set to $\alpha=.05$.
 
@@
 The resulting values were entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression).
+
+## Data availability
+
+The data of this study can be downloaded from [osf.io/vnj8x/](https://osf.io/vnj8x/).
+
+## Code availability
+
+The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
+
+\newpage
+
+# References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup
+
+\newpage
+
+# Acknowledgements
+
+This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
+Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
+Applications for the centralized funds will be reviewed in May.
+Regardless of whether or not this additional funding will be granted, the study can commence immediately.
+The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+
+# Author Contributions
+
+CS, AS, and JZ conceptualized the study and its methodology.
+CS and JZ acquired funding, investigated, administered the project, and wrote the software.
+CS, JZ, and AG did the formal analysis.
+CS and JZ visualized the results, and prepared the original draft.
+All authors reviewed, edited, and approved the final version of the manuscript.
+
+# Competing Interests
+
+The authors declare no competing interests.

### 2022-02-02 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
corrected file names
changed location of acknowledgements etc.

@@
 
-``` {r child = "intro.Rmd"}
+``` {r child = "TheoreticalBackground.Rmd"}
 ```
 
-```{r child = "method.Rmd"}
+```{r child = "Method.Rmd"}
 ```
+
+# References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup
+
+\newpage
+
+# Acknowledgements
+
+This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
+Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
+Applications for the centralized funds will be reviewed in May.
+Regardless of whether or not this additional funding will be granted, the study can commence immediately.
+The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+
+# Author Contributions
+
+CS, AS, and JZ conceptualized the study and its methodology.
+CS and JZ acquired funding, investigated, administered the project, and wrote the software.
+CS, JZ, and AG did the formal analysis.
+CS and JZ visualized the results, and prepared the original draft.
+All authors reviewed, edited, and approved the final version of the manuscript.
+
+# Competing Interests
+
+The authors declare no competing interests.

### 2022-02-02 06_Paper/ER-ED/method.Rmd
changed location of acknowledgements etc.

@@
 The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-
-# Acknowledgements
-
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
-Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-Applications for the centralized funds will be reviewed in May.
-Regardless of whether or not this additional funding will be granted, the study can commence immediately.
-The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-
-# Author Contributions
-
-CS, AS, and JZ conceptualized the study and its methodology.
-CS and JZ acquired funding, investigated, administered the project, and wrote the software.
-CS, JZ, and AG did the formal analysis.
-CS and JZ visualized the results, and prepared the original draft.
-All authors reviewed, edited, and approved the final version of the manuscript.
-
-# Competing Interests
-
-The authors declare no competing interests.

### 2022-02-02 06_Paper/ER-ED/method.Rmd
changed symbols

@@
 To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
-Greenhouse-Geisser-corrected *p*-values and degrees of freedom were reported when assumption of sphericity was violated.
-Proportion of explained variance *$\eta$²~p~* was reported as a measure of effect size.
+Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
+Proportion of explained variance $\eta²~p~$ was reported as a measure of effect size.
 

### 2022-02-02 06_Paper/ER-ED/method.Rmd
changed to future tense

@@
 
-Two bipolar electromyograph (EMG) measures were recorded in the region of the *corrugator supercilii* and the *levator labii* using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
-Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel were used. 
-Data were sampled at 1000 Hz.
-To measure *corrugator EMG*, electrodes were applied to the abraded and cleaned skin on the left corrugator, and to measure *levator EMG*, electrodes were applied in the region of the *levator labii*.
-The ground electrod were placed at the left *Mastoid*.
-A 10 Hz high pass and a 500 Hz low pass filter were applied to both signals. <!-- liebe Anne, habe das hier von Ray et al 2010 übernommen. Stimmt das für unsere Auswertung? -->
-Afterwards, the signals were rectified.
+Two bipolar electromyograph (EMG) measures will be recorded in the region of the *corrugator supercilii* and the *levator labii* using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
+Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel will be used. 
+Data will be sampled at 1000 Hz.
+To measure *corrugator EMG*, electrodes will be applied to the abraded and cleaned skin on the left *corrugator supercilii*, and to measure *levator EMG*, electrodes were applied in the region of the *levator labii*.
+The ground electrode will be placed at the left *Mastoid*.
+A 10 Hz high pass and a 500 Hz low pass filter will be applied to both signals. <!-- liebe Anne, habe das hier von Ray et al 2010 übernommen. Stimmt das für unsere Auswertung? -->
+Afterwards, the signals will be rectified.
 [...] <!-- @Anne hier fehlt noch einiges, bitte dann nach deiner Auswertung ergänzen =) -->
@@
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Sample size calculation was done using _G*Power_ [@Faul2007; @Faul2009].
+Sample size calculation is done using _G*Power_ [@Faul2007; @Faul2009].
 In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
@@
 
-All statistical analyses were perfomed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.
+All statistical analyses will be performed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.
 The level of significance was set to $\alpha=.05$.
@@
 *Effects of emotion regulation on arousal and effort* <br>
-To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing was conducted for behavioral data (subjective arousal ratings).
+To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
 To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
@@
 For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, the resulting (monetary) value was divided by 2.00 €.
-The resulting values were entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression).
+Second, the resulting (monetary) value will be divided by 2.00 €.
+The final SV for each participant will be computed by averaging all final SVs of each strategy.
+The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression).
 

### 2022-02-02 06_Paper/ER-ED/method.Rmd
added to analysis plan

@@
 Proportion of explained variance $\eta²~p~$ was reported as a measure of effect size.
+If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
 
@@
 The final SV for each participant will be computed by averaging all final SVs of each strategy.
-The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression).
+The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
 

### 2022-02-03 06_Paper/COG-ED/Manuscript.Rmd
specified emmeans in methods section
CS added comment

@@
 An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
-Tukey method will be used for the paired contrasts of each rmANOVA, including *p*-value adjustment.
+Estimated marginal means will be used for the paired contrasts of each rmANOVA, including Tukey method for *p*-value adjustment.
 
 To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
+<!--CS: Zitation hinzufügen?
+ @Article{,
+    title = {{lmerTest} Package: Tests in Linear Mixed Effects Models},
+    author = {Alexandra Kuznetsova and Per B. Brockhoff and Rune H. B.
+      Christensen},
+    journal = {Journal of Statistical Software},
+    year = {2017},
+    volume = {82},
+    number = {13},
+    pages = {1--26},
+    doi = {10.18637/jss.v082.i13},
+  }--> 
 We will apply restricted maximum likelihood (REML) to fit the model.

### 2022-02-03 06_Paper/ER-ED/method.Rmd
added MLM

@@
 The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
+Again, estimated, marginal means will be computed as post-hoc contrasts.
+
+To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
+First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+Restricted maximum likelihood (REML) will be applied to fit the model.
+Firstly, intraclass correlation (ICC) will be calculated on the basis of the null model.
+Secondly, a random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological arousal (*corrugator* activity and *levator* activity) as level-1-predictor will be specified.
+$$
+SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
+$$
 

### 2022-02-03 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 $$
+Level-1-predictors will be centered within cluster [Enders2007].
+Residuals of the final model will be inspected visually.
 

### 2022-02-03 06_Paper/COG-ED/Manuscript.Rmd
added comment

@@
 First, we will calculate the intraclass correlation (ICC) on the basis of the null model.
+<!--CS: Wieso wird der ICC nur für das Null Modell berechnet ?
+Man könnte den doch auch für das full-model ebenfalls angeben und sehen, wieviel Varianzaufklärung hinzugekommen ist?
+-->
 Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 

### 2022-02-03 06_Paper/ER-ED/method.Rmd
Update method.Rmd

--- 2022-02-02 06_Paper/ER-ED/method.Rmd
@@
 The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
+Again, estimated, marginal means will be computed as post-hoc contrasts.
+
+To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
+First, ER strategies will be re-coded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+Restricted maximum likelihood (REML) will be applied to fit the model.
+A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological arousal (*corrugator* activity and *levator* activity) as level-1-predictor will be specified.
+$$
+SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
+$$
+Level-1-predictors will be centered within cluster [@Enders2007].
+Residuals of the final model will be inspected visually.
+Intraclass correlation coefficient (ICC), $\rho$,  will be reported for each model (null model, as well as full model).
+
+The influence of personality traits on SVs will be investigated exploratorily. 
+Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
+<!--CS: Weitere Persönlichkeitsfaktoren ins Modell?
+Würde sagen erstmal nicht, denn sonst wird es a) überladen mit Prädiktoren und b) haben wir sonst kein Maß, was meiner Meinung nach mit ALLEN SVs zusammenhängen sollte.
+-->
+
+The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threi FlexER score.
+Therefore, SVs will be ordered by magnitude.
+
+For each result of the analyses both, $p$-values and Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021], will be reported.
 

### 2022-02-03 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threi FlexER score.
-Therefore, SVs will be ordered by magnitude.
+Therefore, SVs will be ordered by magnitude firstly. 
+Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
+<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden?
+-->
 

### 2022-02-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
added theoretical considerations for model

@@
 
+<!--CS: Mit dem Teil bin ich noch nciht ganz zufrieden, freue mich über Anmerkungen, wie man das evtl. strukturieren kann! -->
 The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
@@
 Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort [@Scheffel2021].
-
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
@@
 Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
-
-However, what has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
+What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
 People choose a strategy that they prefer, for different, relatively well-known reasons. 
 However, nothing is revealed about the strategy that is not chosen.
-It is possible that the chosen strategy represents the clear preference of an individual, while the strategy that was not chosen is not a realistic option for them. 
-On the other hand, it could also be that two strategies available for selection could represent almost equivalent options for the individual.
+
+We assume that people choose the strategy that has the highest value for them at that moment.
+The value is determined against the background of goal achievement in the specific situation: a strategy is valued high if it facilitates goal achievement [@Aldao2015]. 
+One certainly central goal is the regulation of negative affect.
+A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
+When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
+We assume that both aspects are intercomputed by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal and is less effortful.
+SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
+Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
+This would mean that all strategies are a good option for goal achievement.
+A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
+This in turn would mean that no strategy is a good choice to achieve goals.
+
+However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
 To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.

### 2022-02-04 06_Paper/ER-ED/TheoreticalBackground.Rmd
updated theoretical background on SVs

@@
 Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
-This selection of strategies is influenced by numerous factors.
+Evidence from other contexts (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
+Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
 For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
-### Hier sollte auch noch erwähnt werden, dass wir auch n-back erheben
+Additionally, We will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
 ```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns.

### 2022-02-04 06_Paper/ER-ED/method.Rmd
fixed typo

@@
 
-The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threi FlexER score.
+The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threir FlexER score.
 Therefore, SVs will be ordered by magnitude firstly. 

### 2022-02-04 06_Paper/COG-ED/Manuscript.Rmd
CS added comment on MLM
added lmerTest ref

@@
 
-To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package. 
-<!--CS: Zitation hinzufügen?
- @Article{,
-    title = {{lmerTest} Package: Tests in Linear Mixed Effects Models},
-    author = {Alexandra Kuznetsova and Per B. Brockhoff and Rune H. B.
-      Christensen},
-    journal = {Journal of Statistical Software},
-    year = {2017},
-    volume = {82},
-    number = {13},
-    pages = {1--26},
-    doi = {10.18637/jss.v082.i13},
-  }--> 
+To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package [@Kuznetsova2017]. 
 We will apply restricted maximum likelihood (REML) to fit the model.
@@
 To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
+<!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  -->
 

### 2022-02-04 06_Paper/ER-ED/Questionnaires.R
Update Questionnaires.R

@@ -36,3 +36,8 @@ data_quest_raw <- data_redcap %>%
 data_quest <- data_redcap %>%
     subset(!is.na(subject), select = c(subject, age, gender, edu))
 
+
+
+# save data frame
+
+write.csv(data_quest, here("04_RawData", "pilot", "ER-ED", "dfs","df_quest.csv"), row.names = FALSE)

### 2022-02-04 06_Paper/COG-ED/Manuscript.Rmd

@@
 
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE} 
-# comment Christoph: Evtl. lieber mit fig.cap = "..." im Chunk arbeiten? Dann wäre das auf jeden fall immer an die Figure attached
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back.", fig.pos="H"}
+
   include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
-```
-*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back \> 3-back \> 1-back.
+
+```
 

### 2022-02-07 06_Paper/COG-ED/Manuscript.Rmd
changed abstract to be more about T1

@@
 abstract: |
-  When individuals set goals, they consider the subjective value (SV) of both the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
-  However, the SV of effort is highly individual, and previous quantification approaches have had two crucial limitations: They presumed a unidirectional relationship between objective task load and the SV of effort, and as a consequence, they could only quantify the SVs of tasks with an objective order of task load.
-  One of these approaches is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013).
-  We aim to replicate their analysis with our adaptation, the Cognitive and Emotion Regulation Effort Discounting (CERED) paradigm.
-  We argue that the CERED paradigm allows two crucial things: Quantifying SVs without assuming that the easiest level is preferred, and quantifying SVs for tasks with no objective order of task load.
+  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
+  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
+  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
+  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
+  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
 

### 2022-02-07 06_Paper/ER-ED/TheoreticalBackground.Rmd
made annotations

@@
 So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
-In contrast, response modification takes place late in the process and is therefore conceptualized as response-focused strategy [@Gross1998antecedent].
-This postulated temporal sequence of ER strategies affects their effectiveness.
+In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy [@Gross1998antecedent].
+This postulated temporal sequence of ER strategies influences their effectiveness.
 It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
+<!--JZ: Das "on outcomes in measures" im folgenden Satz klingt doppelt gemoppelt, das sollte vielleicht noch umformuliert werden -->
 Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on outcomes in measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
-With an effect size of _d~+~_ = 0.45 distancing as tactic of cognitive change showed the highest effectiveness [@Webb2012].
+Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
 So these tactics from three different strategies proved to be effective in the short term. 
-However, in order to be able to make a statement on the general benefit, longer-term consequences must also be considered. 
+However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
 Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
@@
 Also, meta-analytic evidence exists linking a number of ER strategies to psychological disorders [@Aldao2010].
+<!--JZ: Oben formulierst du es als "meta-analytically proven", dass das Arousal reduziert wird, hier als "meta-analytic evidence exists" für den Zsmh mit Disorders; ich finde, man sollte beiden Metaanalysen die gleiche Evidenzstärke zusprechen; macht das Sinn?-->
 
@@
 The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
-Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
+Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
 First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015].
+<!--JZ: Hier mit "First" weiterzumachen, ist nicht so sinnvoll, weil der vorherige Satz keine Argumentation einleitet, die nun durch first, second, etc.
+ausgeführt werden soll-->
 For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
@@
 
+<!-- JZ: Hier mal ein Vorschlag für eine andere Variante des oberen Absatzes, ohne inhaltlich was zu verändern: -->
+The postulation of *adaptive* and *maladaptive* strategies was put into a new perspective with the concept of ER flexibility.
+Similar to other psychological domains such as attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
+In contrast, *adaptive* ER requires having a large repertoire of ER strategies to choose from [@Aldao2015] and choosing the strategy that is useful for goal achieving in a particular situation.
+This greater ER variability has been shown to be related to reduced negative affect [@Blanke2020].
+The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option [@Kable2007].
+Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g.
+monetary incentives), motivational determinants (i.e.
+hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
+Effort in particular appeared to be the main factor in ER choice behaviour in our previous work [@Scheffel2021].
+In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
+Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
+Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
+Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
+However, nothing has been investigated regarding the strategy that is *not* chosen.
+
 We assume that people choose the strategy that has the highest value for them at that moment.
-The value is determined against the background of goal achievement in the specific situation: a strategy is valued high if it facilitates goal achievement [@Aldao2015]. 
+The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
 One certainly central goal is the regulation of negative affect.
@@
 When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
-We assume that both aspects are intercomputed by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal and is less effortful.
+We assume that both aspects are set off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
 SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
@@
 Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
-Individual subjective values (SV) of effortful cognitive tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
+Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED) [@Westbrook2013].
 
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
-Additionally, We will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
+Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
 ```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns.
@@
 <!-- to specific ? to unspecific? -->
+<!--JZ: Hier noch den Zsmh zwischen T1 und T2, oder?-->

### 2022-02-07 06_Paper/ER-ED/method.Rmd
Update method.Rmd
fixed past tense

@@
 
+# import questionnaire df
+
+data_quest = read.csv(here("04_RawData", "pilot", "ER-ED", "dfs", "df_quest.csv"), sep = ",")
+
 ```
@@
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
-According to the 21-word-solution, "We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
+According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
 A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
@@
 
-The procedure described above was tested in a pilot study with ...
+The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants ()
 
@@
 Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-The study consisted of two sessions, one week apart. 
-Both sessions took place in a shielded cabin with constant lighting. 
-Before each session, participants received information about the respective experimental procedure and signed informed consent. 
-At the beginning of the first session participants filled out a demographic questionnaire. 
-Afterwards the completed an n-Back task with the levels one to four.
-Then, they completed an ED procedure on screen, followed by a random repetition of one n-back level.
-The second session, containing the ER paradigm, took place exactly one week after session one.
-Participants gave signed informed consent for the second session.
-Afterwards the ER paradigm was conducted.
-Participants first received written instructions on the ER paradigm and ER strategies that they should apply.
-A training session was performed to ensure that all participants were able to implement the ER strategies.
-Next, electrodes to measure EMG were attached and the ER paradigm was conducted. 
-Participants received 30.00€ or course credit as compensation for participation.
-Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+The study consists of two lab sessions, which take place in a shielded cabin with constant lighting. 
+Before each session, participants receive information about the respective experimental procedure and provide informed consent. 
+At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
+Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level. <!--JZ: Hast du ED schon als Abkürzung eingeführt?-->
+The second session, containing the ER paradigm, takes place exactly one week after session one.
+Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
+A brief training ensures that all participants are able to implement the ER strategies.
+Next, electrodes to measure EMG are being attached and the ER paradigm is conducted. 
+Participants receive 30.00€ or course credit as compensation.
+Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
 
@@
 
-The online survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
-To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
-Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
-For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
-Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
-To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
-To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
-Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
+The online survey contains a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
+To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] is used. 
+Dispositional use of ER is assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
+For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
+Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017].
+To assess Need for Cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] is used.
+To assess self-control, sum scores of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
+Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
 
@@
 
-The ER paradigm roughly consisted of three parts that will be described in the following.
+The ER paradigm roughly consists of three parts that will be described in the following.
 
 *Part one: ER task.* <br>
-Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
-Participants were told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively.
-Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
-During this block, 20 neutral pictures were presented.
-Participants were asked to "actively view all pictures and permit all emotions that may arise."
-In the second block, participants actively viewed negative pictures.
-During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
-In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
-Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants were told to "suppress their emotional facial expression."
+Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
+Participants are told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
+Every participant first has the condition "active viewing-neutral" that serves as a baseline condition.
+During this block, 20 neutral pictures are presented.
+Participants are asked to "actively view all pictures and permit all emotions that may arise."
+In the second block, participants actively viewe negative pictures.
+During the third, fourth, and fifth block, participants see negative pictures and are asked to regulate their emotions using distraction, distancing, and suppression.
+In order to achieve distraction, participants are asked to think of a geometric object or an everyday activity, like brushing their teeth.
+During distancing, participants are asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
+Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
+During suppression, participants are told to "suppress their emotional facial expression."
 They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
-Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
-All participants received written instruction and completed a training session.
-After the training session, participants were asked about their applied ER strategies to avoid misapplication.
-The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.
+Participants are instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
+All participants receive written instruction and complete a training session.
+After the training session, participants are asked about their applied ER strategies to avoid misapplication.
+The order of the three regulation blocks (distraction, distancing, and suppression) is randomized between participants.
 
 *Part two: ER effort discounting.* <br>
-In the second part, ER effort discounting took place.
-The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
-We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
+In the second part, ER effort discounting takes place.
+The procedure of the discounting follows the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
+We use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
 distancing, distraction vs.
 suppression, and distancing vs.
-suppression), two strategies with monetary values were presented.
-The order of the comparisons was randomized.
-Because there is no strategy that is objectively more difficult, we added an initial comparison that began with the option "1 EUR for strategy A or 1 EUR for strategy B".
-The strategy that was not chosen was assigned the value 2 EUR.
-From this point on, comparisons between strategies followed the original COG-ED paradigm [@Westbrook2013].
-Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.
+suppression), two strategies with monetary values are presented.
+The order of the comparisons is randomized.
+Because there is no strategy that is objectively more difficult, we added an initial comparison that begins with the option "1 EUR for strategy A or 1 EUR for strategy B".
+The strategy that is not chosen is assigned the value of 2 EUR.
+From this point on, comparisons between strategies follow the original COG-ED paradigm [@Westbrook2013].
+Participants are instructed to decide as realistically as possible, imagining the displayed money would really be up for election.
 
 *Part three: ER choice.* <br>
-After the discounting part, participants chose which of the three ER strategies (distraction, distancing or suppression) they wanted to reapply.
-Importantly, there were no further instruction, on what basis they should make their decision.
-Participants should make their decision freely, according to the criteria they considered important for themselves.
-However, participants were asked to state the reasons for the decision afterwards.
-As soon as they had decided, they saw the respective instruction. 
-After, the block with another 20 negative pictures started.
+After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
+Importantly, there are no further instruction on what basis they should make their decision.
+Participants should make their decision freely, according to the criteria they consider important for themselves.
+However, participants are asked to state the reasons for the decision afterwards.
+As soon as they have decided, they see the respective instruction and the block with another 20 negative pictures starts.
 
@@
 
-Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. 
+Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. <!--JZ: Das stand oben schon mal-->
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.

### 2022-02-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
edited comment

@@
 Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
-First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015].
-<!--JZ: Hier mit "First" weiterzumachen, ist nicht so sinnvoll, weil der vorherige Satz keine Argumentation einleitet, die nun durch first, second, etc.
-ausgeführt werden soll-->
+Adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015].
 For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
-Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
+Strategies have to be chosen from the repertoire that are useful for goal achieving.
 Evidence from other contexts (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.

### 2022-02-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
edited comment

@@
 It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
-<!--JZ: Das "on outcomes in measures" im folgenden Satz klingt doppelt gemoppelt, das sollte vielleicht noch umformuliert werden -->
-Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on outcomes in measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
+Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].

### 2022-02-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
edited comment

@@
 For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
-Also, meta-analytic evidence exists linking a number of ER strategies to psychological disorders [@Aldao2010].
-<!--JZ: Oben formulierst du es als "meta-analytically proven", dass das Arousal reduziert wird, hier als "meta-analytic evidence exists" für den Zsmh mit Disorders; ich finde, man sollte beiden Metaanalysen die gleiche Evidenzstärke zusprechen; macht das Sinn?-->
+Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see [@Aldao2010]).
 

### 2022-02-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
edited comment

@@
 
-<!-- JZ: Hier mal ein Vorschlag für eine andere Variante des oberen Absatzes, ohne inhaltlich was zu verändern: -->
 The postulation of *adaptive* and *maladaptive* strategies was put into a new perspective with the concept of ER flexibility.

### 2022-02-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
added hypotheses

@@
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
+Moreover it is known that ER strategies reduce physiological arousal, measured via EMG in the region of the *corrugator supercilii* [@Zaehringer2020]. 
 So these tactics from three different strategies proved to be effective in the short term. 
@@
 The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies. 
-We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
-We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively more effortful than distraction and suppression.
-Regarding SVs of ER strategies we expect that (3a) people choose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
-Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs. 
-<!-- to specific ? to unspecific? -->
-<!--JZ: Hier noch den Zsmh zwischen T1 und T2, oder?-->
+As a manipulation check, we want to explore whether ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and require cognitive effort.
+The following hypotheses are proposed for this purpose:
+
+* H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H1b) Physiological arousal (EMG *corrugator* activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H1c) Physiological arousal (EMG *levator* activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2a) Subjective effort (effort ratings) is greater after using an Er strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) The majority of participants ruse the strategy that was least effortful for them.
+
+Further we want to explore which variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
+
+* H3a) Subjective effort ratings negatively predict SVs of ER strategies.
+* H3b) Subjective arousal ratings negatively predict SVs of ER strategies.
+* H3c) EMG *corrugator* activity negatively predict SVs of ER strategies.
+* H3d) EMG *levator* activity negatively predict SVs of ER strategies.
+* H4a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.
+
+We also want to explore whether SVs are related to flexible emotion regulation:
+
+* H5a) The higher the SV, the more likely the respective strategy is chosen.
+* H5b) SVs are lower and decline stronger when ER flexibility is lower.
+
+Exploratorily, we want to investigate whether individual SVs are related to personality traits.

### 2022-02-08 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added design table
added abstract

@@
       - Writing - review & editing 
-affiliation:
+affiliation       :
   - id            : "1"
     institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
-authornote:
-abstract:
+authornote        :
+abstract          : |
+ Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly.
+In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable.
+Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort.
+Perceived costs of ER strategies in form of effort however, are highly subjective.
+Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort.
+However, SVs of ER strategies have not been determined so far.
+We present a paradigm that is suitable for determining individual SVs of ER strategies.
+Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort.
+Relations of SVs to personality traits will be explored
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
@@
 The authors declare no competing interests.
+
+\newpage
+\setcounter{figure}{0}
+
+# Figures and figure captions
+
+\newpage
+
+# Design Table
+
+\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
+
+\newpage
+
+# Supplement

### 2022-02-08 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
-pairs(posthoc_arousalView, adjust = "bonferroni")
+#pairs(posthoc_arousalView, adjust = "bonferroni")
 
@@
                               include_aov = TRUE)
-afex::nice(aov_arousalReg, es = "pes")
+#afex::nice(aov_arousalReg, es = "pes")
 
@@
 posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
-pairs(posthoc_arousalReg, adjust = "bonferroni")
+#pairs(posthoc_arousalReg, adjust = "bonferroni")
 
@@
                           include_aov = TRUE)
-afex::nice(aov.effort, es = "pes")
+#afex::nice(aov.effort, es = "pes")
 
@@
 posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
-pairs(posthoc_effort, adjust = "bonferroni")
+#pairs(posthoc_effort, adjust = "bonferroni")
 
@@
 
-The online survey contains a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
-To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] is used. 
-Dispositional use of ER is assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
+The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
+To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used. 
+Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
 For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
-Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017].
-To assess Need for Cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] is used.
-To assess self-control, sum scores of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
+Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
+To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
 Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
@@
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Sample size calculation is done using _G*Power_ [@Faul2007; @Faul2009].
+Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
 In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  

### 2022-02-08 06_Paper/ER-ED/method.Rmd
BF ANOVA Ratings View

@@
 library(dplyr)
+library(BayesFactor)
 
@@
 
-arousal_view = data_ER %>%
+Ratings_view <- data_ER %>%
   subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
+Ratings_view$block <- as.factor(Ratings_view$block)
 
-aov_arousalView = afex::aov_ez(data = arousal_view,
+SubjArousalView_aov <- afex::aov_ez(data = Ratings_view,
                                id = "ID",
@@
 # compute posthoc tests for within measures
-posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
+SubjArousalView_emm <- emmeans::emmeans(SubjArousalView_aov$aov, specs = "block")
 #pairs(posthoc_arousalView, adjust = "bonferroni")
+
+SubjArousalView_con <- as.data.frame(pairs(SubjArousalView_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
+                                           data = Ratings_view,
+                                           progress = FALSE)
+SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
+                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"]))
 

### 2022-02-08 06_Paper/ER-ED/method.Rmd
added B

@@
 SubjArousalView_emm <- emmeans::emmeans(SubjArousalView_aov$aov, specs = "block")
-#pairs(posthoc_arousalView, adjust = "bonferroni")
 
@@
 SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
-                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"]))
+                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"],
+                                                                        progress = FALSE, paired = TRUE))$bf
 
@@
 
-arousal_reg = data_ER %>%
+Ratings_reg <- data_ER %>%
   subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+Ratings_reg$block <- as.factor(Ratings_reg$block)
 
-aov_arousalReg = afex::aov_ez(data = arousal_reg,
+SubjArousalReg_aov <- afex::aov_ez(data = arousal_reg,
                               id = "ID",
@@
                               include_aov = TRUE)
-#afex::nice(aov_arousalReg, es = "pes")
 
 # compute posthoc tests for within measures
-posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
-#pairs(posthoc_arousalReg, adjust = "bonferroni")
+SubjArousalReg_emm <- emmeans::emmeans(SubjArousalReg_aov$aov, specs = "block")
+
+SubjArousalReg_con <- as.data.frame(pairs(SubjArousalReg_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
+                                           data = Ratings_reg,
+                                           progress = FALSE)
+
+SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
+                                                                         progress = FALSE, paired = TRUE))$bf)
 

### 2022-02-09 06_Paper/ER-ED/method.Rmd
added effect size to ratings

@@
 library(BayesFactor)
+library(effectsize)
 
@@
 
+SubjArousalView_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
+                                                          df_error = SubjArousalView_con$df,
+                                                          ci = 0.95,
+                                                          digits = 2))
+
 # Figure to visualize arousal ratings
@@
 # figure
-FigPilot1=ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
+FigPilot1=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 
-SubjArousalReg_aov <- afex::aov_ez(data = arousal_reg,
+SubjArousalReg_aov <- afex::aov_ez(data = Ratings_reg,
                               id = "ID",
@@
 
+SubjArousalReg_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio, df_error = SubjArousalReg_con$df, ci = 0.95), digits = 2)
+
 # Figure to visualize arousal ratings
@@
 # figure
-FigPilot2 = ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
+FigPilot2 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+

### 2022-02-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd

@@
       - Formal analysis
+      - Writing - review & editing
+  - name          : "Denise Dörfel"
+    orcid         :
+    affiliation   : "1"
+    role          :
+      - Conceptuatlization
       - Writing - review & editing

### 2022-02-09 06_Paper/ER-ED/method.Rmd
updated BF of ANOVAS

@@
 csl: apa7.csl
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 # Bayes Factors
-SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
+SubjArousalReg_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                            data = Ratings_reg,
@@
 
-SubjArousalReg_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio, df_error = SubjArousalReg_con$df, ci = 0.95), digits = 2)
+SubjArousalReg_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio,
+                                                         df_error = SubjArousalReg_con$df,
+                                                         ci = 0.95),
+                                   digits = 2)
 
@@
 # figure
-FigPilot2 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
+FigPilot2 <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 
-# ANOVA subjective effort ratings
-
-effort_reg = data_ER %>%
-  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
-
-aov.effort = afex::aov_ez(data = effort_reg,
+SubjEffort_aov <- afex::aov_ez(data = Ratings_reg,
                           id = "ID",
@@
                           include_aov = TRUE)
-#afex::nice(aov.effort, es = "pes")
 
 # compute posthoc tests for within measure
-posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
-#pairs(posthoc_effort, adjust = "bonferroni")
+SubjEffort_emm <- emmeans::emmeans(SubjEffort_aov$aov, specs = "block")
+
+SubjEffort_con <- as.data.frame(pairs(SubjEffort_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+SubjEffort_BF <- BayesFactor::anovaBF(formula = effort ~ block,
+                                           data = Ratings_reg,
+                                           progress = FALSE)
+
+SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
+                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distraction"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
+                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
+                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
+                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
+                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
+                                                                         progress = FALSE, paired = TRUE))$bf,
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distancing"],
+                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
+                                                                         progress = FALSE, paired = TRUE))$bf)
+
+SubjEffort_con$etasq <- format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
+                                                         df_error = SubjEffort_con$df,
+                                                         ci = 0.95),
+                                   digits = 2)
 
@@
 # figure
-FigPilot3 = ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
+FigPilot3 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
-A complete list of all measures assessed in the study will be found at the OSF (https://osf.io/vnj8x/) and GitHub (github.com/ChScheffel/COG-ER-ED). <!-- Attention! OSF is still private -->
-All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
+A complete list of all measures assessed in the study will be found at the OSF (<https://osf.io/vnj8x/>) and GitHub (github.com/ChScheffel/COG-ER-ED).
+<!-- Attention!
+OSF is still private --> All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
 
@@
 
-The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants ()
+The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
 
@@
 At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
-Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level. <!--JZ: Hast du ED schon als Abkürzung eingeführt?-->
-The second session, containing the ER paradigm, takes place exactly one week after session one.
+Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
+<!--JZ: Hast du ED schon als Abkürzung eingeführt?--> The second session, containing the ER paradigm, takes place exactly one week after session one.
 Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
@@
 
-*Part one: ER task.* <br>
-Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
+*Part one: ER task.* <br> Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021].
 Participants are told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
@@
 During this block, 20 neutral pictures are presented.
-Participants are asked to "actively view all pictures and permit all emotions that may arise."
-In the second block, participants actively viewe negative pictures.
+Participants are asked to "actively view all pictures and permit all emotions that may arise." In the second block, participants actively viewe negative pictures.
 During the third, fourth, and fifth block, participants see negative pictures and are asked to regulate their emotions using distraction, distancing, and suppression.
 In order to achieve distraction, participants are asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants are asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
-Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants are told to "suppress their emotional facial expression."
-They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
+During distancing, participants are asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
+During suppression, participants are told to "suppress their emotional facial expression." They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
 Participants are instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
@@
 
-*Part two: ER effort discounting.* <br>
-In the second part, ER effort discounting takes place.
+*Part two: ER effort discounting.* <br> In the second part, ER effort discounting takes place.
 The procedure of the discounting follows the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
@@
 
-*Part three: ER choice.* <br>
-After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
+*Part three: ER choice.* <br> After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
 Importantly, there are no further instruction on what basis they should make their decision.
@@
 Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008].
-The 20 neutral pictures (Valence (V): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): _M_ $\pm$ _SD_ = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
+The 20 neutral pictures (Valence (V): *M* $\pm$ *SD* = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): *M* $\pm$ *SD* = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
 Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
-An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: _M_ $\pm$ _SD_ = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
+An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
 A complete list of all pictures and their classification into sets can be found in supplementary material X.
@@
 The ground electrode will be placed at the left *Mastoid*.
-A 10 Hz high pass and a 500 Hz low pass filter will be applied to both signals. <!-- liebe Anne, habe das hier von Ray et al 2010 übernommen. Stimmt das für unsere Auswertung? -->
-Afterwards, the signals will be rectified.
+A 10 Hz high pass and a 500 Hz low pass filter will be applied to both signals.
+<!-- liebe Anne, habe das hier von Ray et al 2010 übernommen. Stimmt das für unsere Auswertung? --> Afterwards, the signals will be rectified.
 [...] <!-- @Anne hier fehlt noch einiges, bitte dann nach deiner Auswertung ergänzen =) -->
@@
 
-Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. <!--JZ: Das stand oben schon mal-->
-Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
+Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
+<!--JZ: Das stand oben schon mal--> Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
 Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
-In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
+In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.\
 To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
@@
 
-*Effects of emotion regulation on arousal and effort* <br>
-To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
+*Effects of emotion regulation on arousal and effort* <br> To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
 To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
@@
 <!-- @Anne please check!
-=) -->
-A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
+=) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
 <!-- @Anne please check!
-=) -->
-To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
+=) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
 Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
@@
 
-*Subjective values of emotion regulation strategies* <br>
-For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
 Second, the resulting (monetary) value will be divided by 2.00 €.
@@
 SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
-$$
-Level-1-predictors will be centered within cluster [@Enders2007].
+$$ Level-1-predictors will be centered within cluster [@Enders2007].
 Residuals of the final model will be inspected visually.
@@
 Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
-<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden?
--->
+<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? -->
 

### 2022-02-09 06_Paper/COG-ED/Manuscript.Rmd

@@
 And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+Each hypothesis is detailed in the Design Table in the Appendix.
 
@@
 
-  hypothesis1a_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[1], df_error = hypothesis1a_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                     format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[2], df_error = hypothesis1a_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                     format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[3], df_error = hypothesis1a_contrasts$df[3], ci = 0.95), digits = 2)[1,1])
-
-  hypothesis1a_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[1], df_error = hypothesis1a_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[2], df_error = hypothesis1a_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio[3], df_error = hypothesis1a_contrasts$df[3], ci = 0.95), digits = 2)[1,2])
+  hypothesis1a_contrasts <- cbind(hypothesis1a_contrasts,
+                                  format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio, df_error = hypothesis1a_contrasts$df, ci = 0.95), digits = 2))
 
@@
 
-  hypothesis1b_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[1], df_error = hypothesis1b_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                     format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[2], df_error = hypothesis1b_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                     format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[3], df_error = hypothesis1b_contrasts$df[3], ci = 0.95), digits = 2)[1,1])
-
-  hypothesis1b_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[1], df_error = hypothesis1b_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[2], df_error = hypothesis1b_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio[3], df_error = hypothesis1b_contrasts$df[3], ci = 0.95), digits = 2)[1,2])
+  hypothesis1b_contrasts <- cbind(hypothesis1b_contrasts,
+                                  format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio, df_error = hypothesis1b_contrasts$df, ci = 0.95), digits = 2))
 
@@
 
-  hypothesis1c_mental_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[1], df_error = hypothesis1c_mental_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[2], df_error = hypothesis1c_mental_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[3], df_error = hypothesis1c_mental_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[4], df_error = hypothesis1c_mental_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[5], df_error = hypothesis1c_mental_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[6], df_error = hypothesis1c_mental_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
-  hypothesis1c_mental_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[1], df_error = hypothesis1c_mental_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[2], df_error = hypothesis1c_mental_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[3], df_error = hypothesis1c_mental_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[4], df_error = hypothesis1c_mental_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[5], df_error = hypothesis1c_mental_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio[6], df_error = hypothesis1c_mental_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
-
-  hypothesis1c_physical_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[1], df_error = hypothesis1c_physical_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[2], df_error = hypothesis1c_physical_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[3], df_error = hypothesis1c_physical_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[4], df_error = hypothesis1c_physical_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[5], df_error = hypothesis1c_physical_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[6], df_error = hypothesis1c_physical_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
-  hypothesis1c_physical_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[1], df_error = hypothesis1c_physical_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[2], df_error = hypothesis1c_physical_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[3], df_error = hypothesis1c_physical_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[4], df_error = hypothesis1c_physical_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[5], df_error = hypothesis1c_physical_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio[6], df_error = hypothesis1c_physical_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
-
-  hypothesis1c_time_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[1], df_error = hypothesis1c_time_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[2], df_error = hypothesis1c_time_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[3], df_error = hypothesis1c_time_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[4], df_error = hypothesis1c_time_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[5], df_error = hypothesis1c_time_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[6], df_error = hypothesis1c_time_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
-  hypothesis1c_time_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[1], df_error = hypothesis1c_time_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[2], df_error = hypothesis1c_time_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[3], df_error = hypothesis1c_time_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[4], df_error = hypothesis1c_time_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[5], df_error = hypothesis1c_time_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio[6], df_error = hypothesis1c_time_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
-
-  hypothesis1c_effort_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[1], df_error = hypothesis1c_effort_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[2], df_error = hypothesis1c_effort_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[3], df_error = hypothesis1c_effort_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[4], df_error = hypothesis1c_effort_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[5], df_error = hypothesis1c_effort_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[6], df_error = hypothesis1c_effort_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
-  hypothesis1c_effort_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[1], df_error = hypothesis1c_effort_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[2], df_error = hypothesis1c_effort_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[3], df_error = hypothesis1c_effort_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[4], df_error = hypothesis1c_effort_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[5], df_error = hypothesis1c_effort_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio[6], df_error = hypothesis1c_effort_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
-
-  hypothesis1c_frustration_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[1], df_error = hypothesis1c_frustration_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[2], df_error = hypothesis1c_frustration_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[3], df_error = hypothesis1c_frustration_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[4], df_error = hypothesis1c_frustration_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[5], df_error = hypothesis1c_frustration_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[6], df_error = hypothesis1c_frustration_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
-  hypothesis1c_frustration_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[1], df_error = hypothesis1c_frustration_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[2], df_error = hypothesis1c_frustration_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[3], df_error = hypothesis1c_frustration_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[4], df_error = hypothesis1c_frustration_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[5], df_error = hypothesis1c_frustration_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio[6], df_error = hypothesis1c_frustration_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
-
-  hypothesis1c_performance_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[1], df_error = hypothesis1c_performance_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[2], df_error = hypothesis1c_performance_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[3], df_error = hypothesis1c_performance_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[4], df_error = hypothesis1c_performance_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[5], df_error = hypothesis1c_performance_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[6], df_error = hypothesis1c_performance_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
-  hypothesis1c_performance_contrasts$CI <- c(format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[1], df_error = hypothesis1c_performance_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[2], df_error = hypothesis1c_performance_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[3], df_error = hypothesis1c_performance_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[4], df_error = hypothesis1c_performance_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[5], df_error = hypothesis1c_performance_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio[6], df_error = hypothesis1c_performance_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+  hypothesis1c_mental_contrasts <- cbind(hypothesis1c_mental_contrasts,
+                                         format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio,
+                                                          df_error = hypothesis1c_mental_contrasts$df, ci = 0.95), digits = 2))
+
+  hypothesis1c_physical_contrasts <- cbind(hypothesis1c_physical_contrasts,
+                                         format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio,
+                                                          df_error = hypothesis1c_physical_contrasts$df, ci = 0.95), digits = 2))
+
+  hypothesis1c_time_contrasts <- cbind(hypothesis1c_time_contrasts,
+                                         format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio,
+                                                          df_error = hypothesis1c_time_contrasts$df, ci = 0.95), digits = 2))
+
+  hypothesis1c_effort_contrasts <- cbind(hypothesis1c_effort_contrasts,
+                                         format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio,
+                                                          df_error = hypothesis1c_effort_contrasts$df, ci = 0.95), digits = 2))
+
+  hypothesis1c_frustration_contrasts <- cbind(hypothesis1c_frustration_contrasts,
+                                         format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio,
+                                                          df_error = hypothesis1c_frustration_contrasts$df, ci = 0.95), digits = 2))
+
+  hypothesis1c_performance_contrasts <- cbind(hypothesis1c_performance_contrasts,
+                                         format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio,
+                                                          df_error = hypothesis1c_performance_contrasts$df, ci = 0.95), digits = 2))
 
@@
 
-  hypothesis2a_contrasts$etasq <- c(format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[1], df_error = hypothesis2a_contrasts$df[1], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[2], df_error = hypothesis2a_contrasts$df[2], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[3], df_error = hypothesis2a_contrasts$df[3], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[4], df_error = hypothesis2a_contrasts$df[4], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[5], df_error = hypothesis2a_contrasts$df[5], ci = 0.95), digits = 2)[1,1],
-                                    format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[6], df_error = hypothesis2a_contrasts$df[6], ci = 0.95), digits = 2)[1,1])
-  hypothesis2a_contrasts$CI <- c(format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[1], df_error = hypothesis2a_contrasts$df[1], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[2], df_error = hypothesis2a_contrasts$df[2], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[3], df_error = hypothesis2a_contrasts$df[3], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[4], df_error = hypothesis2a_contrasts$df[4], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[5], df_error = hypothesis2a_contrasts$df[5], ci = 0.95), digits = 2)[1,2],
-                                 format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio[6], df_error = hypothesis2a_contrasts$df[6], ci = 0.95), digits = 2)[1,2])
+  hypothesis2a_contrasts <- cbind(hypothesis2a_contrasts,
+                                  format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio, df_error = hypothesis2a_contrasts$df, ci = 0.95), digits = 2))
 
@@
 
-A sample size analysis with _G*Power_ [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
+A sample size analysis with *G\*Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
 [-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.

### 2022-02-09 06_Paper/ER-ED/method.Rmd
pilot study
colnames - not working yet

@@
 
+colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$")#, "$95\\% CI$")
 # Figure to visualize arousal ratings
@@
 
+colnames(SubjArousalReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 # Figure to visualize arousal ratings
@@
                                    digits = 2)
-
+colnames(SubjEffort_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 # Figure to visualize effort ratings
@@
 The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
+Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
 

### 2022-02-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added supplement

@@
 # Supplement
+
+\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
+
+\newpage
+
+## Pilot study: Subjective arousal in the conditions "active viewing - neutral" and "active viewing - negative"
+
+ANOVA:
+<br>
+`r afex::nice(SubjArousalView_aov)%>% knitr::kable(x = .)`, $BF10=$ `r round(extractBF(SubjArousalView_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  SubjArousalView_con,
+  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition active viewing.",
+  note = , 
+  escape = FALSE,
+  placement = "H"
+)
+```
+Figure:

### 2022-02-09 06_Paper/ER-ED/method.Rmd
fixed columns

--- 2022-02-09 06_Paper/ER-ED/method.Rmd
@@
 
-SubjArousalView_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
+SubjArousalView_con <- cbind(SubjArousalView_con,
+                             format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
                                                           df_error = SubjArousalView_con$df,
-                                                          ci = 0.95,
+                                                          ci = 0.95),
                                                           digits = 2))
+
+colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 
@@
 
-SubjArousalReg_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio,
+SubjArousalReg_con <- cbind(SubjArousalReg_con,
+                            format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio,
                                                          df_error = SubjArousalReg_con$df,
                                                          ci = 0.95),
-                                   digits = 2)
+                                   digits = 2))
+
+colnames(SubjArousalReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 
@@
 
-SubjEffort_con$etasq <- format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
+SubjEffort_con <- cbind(SubjEffort_con,
+                        format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
                                                          df_error = SubjEffort_con$df,
                                                          ci = 0.95),
-                                   digits = 2)
+                                   digits = 2))
+
+colnames(SubjEffort_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 

### 2022-02-10 06_Paper/ER-ED/method.Rmd
fixed table issue

@@
 colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+# rename contrast for table
+SubjArousalView_con[1,1] <- "$View_{neg} - View_{neu}$"
 
@@
 # figure
-FigPilot1=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
+FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+

### 2022-02-10 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
Update Manuscript_ERED_Stage1.Rmd

@@
   caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition active viewing.",
-  note = , 
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
   escape = FALSE,
@@
 Figure:
+```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions "Active viewing - neutral" and "Active viewing - negative"}

### 2022-02-10 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
fertsch

--- 2022-02-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 \newpage
-
+```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE, out.width="90%"}
+include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
+```
+*Figure 1.* Exemplary visualisation of two response patterns.
+In the top half, the person has a clear preference for one of the three strategies.
+In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
+This pattern can also be represented by our paradigm.
 # Design Table
@@
 # Supplement
+
+\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
+
+\newpage
+
+## Pilot study: Subjective arousal in the conditions "active viewing - neutral" and "active viewing - negative"
+ANOVA:
+
+`r afex::nice(SubjArousalView_aov)%>% knitr::kable(x = .)` 
+$BF10=$ `r round(extractBF(SubjArousalView_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  SubjArousalView_con,
+  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
+  escape = FALSE,
+  placement = "H"
+)
+```
+Figure:
+```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
+Each dot represents the effort rating of a single subject.
+Bold dots represent outliers.", fig.pos="H", out.width="75%"}
+
+print(FigSubjArousalViewPilot)
+```
+## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
+ANOVA:
+`r afex::nice(SubjArousalReg_aov)%>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(SubjArousalReg_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  SubjArousalReg_con,
+  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
+  escape = FALSE,
+  placement = "H"
+)
+```
+Figure:
+```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
+Each dot represents the effort rating of a single subject.
+Bold dots represent outliers.", fig.pos="H", out.width="75%"}
+
+print(FigSubjArousalRegPilot)
+```
+## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
+ANOVA:
+`r afex::nice(SubjEffort_aov)%>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(SubjEffort_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  SubjEffort_con,
+  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
+  escape = FALSE,
+  placement = "H"
+)
+```
+Figure:
+```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
+Each dot represents the effort rating of a single subject.
+Bold dots represent outliers.", fig.pos="H", out.width="75%"}
+
+print(FigSubjEffortPilot)
+```

### 2022-02-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
fertsch

@@
 In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can also be represented by our paradigm."}
+This pattern can also be represented by our paradigm.", out.width="90%"}
 include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
@@
 
-Exploratorily, we want to investigate whether individual SVs are related to personality traits.
+Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely *n*-back.

### 2022-02-10 06_Paper/ER-ED/method.Rmd
fertsch

--- 2022-02-09 06_Paper/ER-ED/method.Rmd
@@
 colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+# rename contrast for table
+SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"
 
@@
 # figure
-FigPilot1=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
+FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
+  scale_x_discrete(name = "Active viewing", 
                    limits = c("view_neu", "view_neg"),
@@
 
+SubjArousalReg_con[1,1] <- "$Distancing - Distraction$"
+SubjArousalReg_con[2,1] <- "$Distancing - Suppression$"
+SubjArousalReg_con[3,1] <- "$Distancing - View_{negative}$"
+SubjArousalReg_con[4,1] <- "$Distraction - Suppression$"
+SubjArousalReg_con[5,1] <- "$Distraction - View_{negative}$"
+SubjArousalReg_con[6,1] <- "$Suppression - View_{negative}$"
+
 # Figure to visualize arousal ratings
@@
 # figure
-FigPilot2 <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
+FigSubjArousalRegPilot <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 
+SubjEffort_con[1,1] <- "$Distancing - Distraction$"
+SubjEffort_con[2,1] <- "$Distancing - Suppression$"
+SubjEffort_con[3,1] <- "$Distancing - View_{negative}$"
+SubjEffort_con[4,1] <- "$Distraction - Suppression$"
+SubjEffort_con[5,1] <- "$Distraction - View_{negative}$"
+SubjEffort_con[6,1] <- "$Suppression - View_{negative}$"
+
 # Figure to visualize effort ratings
 # figure
-FigPilot3 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
+FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
+However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
+Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.
 

### 2022-02-10 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
updated image size

@@
 \newpage
-```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE, out.width="90%"}
+```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE, out.width="98%"}
 include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))

### 2022-02-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
updated image size

@@
 In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can also be represented by our paradigm.", out.width="90%"}
+This pattern can also be represented by our paradigm.", out.width="98%"}
 include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))

### 2022-02-10 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
updates on targets

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Estimating individual subjective values of emotion regulation strategies},
  pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Subjective values of emotion regulation strategies}
\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Estimating individual subjective values of emotion regulation strategies}
\author{Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Josephine Zerna\textsuperscript{$\dagger{}$,1}, Anne Gärtner\textsuperscript{1}, Denise Dörfel\textsuperscript{1}, \& Alexander Strobel\textsuperscript{1}}
\date{}

\authornote{

The authors made the following contributions. Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Writing - review \& editing. \textsuperscript{$\dagger{}$} Christoph Scheffel and Josephine Zerna contributed equally to this work.

Correspondence concerning this article should be addressed to Christoph Scheffel, Zellescher Weg 17, 01069 Dresden, Germany. E-mail: \href{mailto:christoph_scheffel@tu-dresden.de}{\nolinkurl{christoph\_scheffel@tu-dresden.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany}

\abstract{
Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. Perceived costs of ER strategies in form of effort however, are highly subjective. Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. However, SVs of ER strategies have not been determined so far. We present a paradigm that is suitable for determining individual SVs of ER strategies. Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. Relations of SVs to personality traits will be explored
}

\begin{document}
\maketitle

\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{introduction}{%
\section{1. Introduction}\label{introduction}}

Every day we are confronted with stressful or emotionally demanding situations.
The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning.\textsuperscript{2}
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification,\textsuperscript{1} and, following the taxonomy of Powers and LaBar,\textsuperscript{3} individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process.\textsuperscript{1}
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy.\textsuperscript{1}
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal.\textsuperscript{4}
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
Moreover it is known that ER strategies reduce physiological arousal, measured via EMG in the region of the \emph{corrugator supercilii}.\textsuperscript{5}
So these tactics from three different strategies proved to be effective in the short term.
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered.
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed.\textsuperscript{6}
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of \emph{adaptive} and \emph{maladaptive} strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see).\textsuperscript{8}

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
Adaptive flexible ER requires having a large repertoire of ER strategies.\textsuperscript{9}
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
Strategies have to be chosen from the repertoire that are useful for goal achieving.
Evidence from other contexts (e.g., intertemporal choice,)\textsuperscript{11} shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{12}
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.\textsuperscript{12,13}
Further influencing factors are for example extrinsic motivation (e.g.~monetary incentives), motivational determinants (i.e.~hedonic regulatory goals), and effort.\textsuperscript{13,14}
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort.\textsuperscript{14}
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
People choose a strategy that they prefer, for different, relatively well-known reasons.
However, nothing is revealed about the strategy that is not chosen.

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put into a new perspective with the concept of ER flexibility.
Similar to other psychological domains such as attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
In contrast, \emph{adaptive} ER requires having a large repertoire of ER strategies to choose from\textsuperscript{9} and choosing the strategy that is useful for goal achieving in a particular situation.
This greater ER variability has been shown to be related to reduced negative affect.\textsuperscript{10}
The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option.\textsuperscript{11}
Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g.~monetary incentives), motivational determinants (i.e.~hedonic regulatory goals), and effort.\textsuperscript{13,14}
Effort in particular appeared to be the main factor in ER choice behaviour in our previous work.\textsuperscript{14}
In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing has been investigated regarding the strategy that is \emph{not} chosen.

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{9}
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort.\textsuperscript{15}
When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
We assume that both aspects are set off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire\textsuperscript{9} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve goals.

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED).\textsuperscript{17}

\hypertarget{er-strategy-discounting}{%
\subsection{1.1 ER strategy discounting}\label{er-strategy-discounting}}

In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward.
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{14}
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{17} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).

\begin{figure}
\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/other/Paradigm_Scheme_T2} \caption{Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm.}\label{fig:fig1}
\end{figure}

\hypertarget{the-present-study}{%
\subsection{1.2 The present study}\label{the-present-study}}

The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies.
As a manipulation check, we want to explore whether ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and require cognitive effort. The following hypotheses are proposed for this purpose:

\begin{itemize}
\tightlist
\item
  H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H1b) Physiological arousal (EMG \emph{corrugator} activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H1c) Physiological arousal (EMG \emph{levator} activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H2a) Subjective effort (effort ratings) is greater after using an Er strategy (distraction, distancing, suppression) compared to active viewing.
\item
  H2b) The majority of participants ruse the strategy that was least effortful for them.
\end{itemize}

Further we want to explore which variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:

\begin{itemize}
\tightlist
\item
  H3a) Subjective effort ratings negatively predict SVs of ER strategies.
\item
  H3b) Subjective arousal ratings negatively predict SVs of ER strategies.
\item
  H3c) EMG \emph{corrugator} activity negatively predict SVs of ER strategies.
\item
  H3d) EMG \emph{levator} activity negatively predict SVs of ER strategies.
\item
  H4a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, \emph{corrugator} and \emph{levator} activity.
\end{itemize}

We also want to explore whether SVs are related to flexible emotion regulation:

\begin{itemize}
\tightlist
\item
  H5a) The higher the SV, the more likely the respective strategy is chosen.
\item
  H5b) SVs are lower and decline stronger when ER flexibility is lower.
\end{itemize}

Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely \emph{n}-back.

\hypertarget{method}{%
\section{2. Method}\label{method}}

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, ``we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study'' in compliance with the 21-word-solution of open science.\textsuperscript{18}
A complete list of all measures assessed in the study will be found at the OSF (\url{https://osf.io/vnj8x/}) and GitHub (github.com/ChScheffel/COG-ER-ED).
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

\hypertarget{ethics-information}{%
\subsection{2.1 Ethics information}\label{ethics-information}}

\hypertarget{pilot-data}{%
\subsection{2.2 Pilot data}\label{pilot-data}}

The procedure described above was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.10\text{ }\pm\text{ }SD = 3.60\)).
Results showed significant higher subjective (\ldots{} and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
Yet we found accordance with our previous studies\textsuperscript{14} that the use of ER strategies compared to active viewing was associated with increased subjective effort.

\hypertarget{design}{%
\subsection{2.3 Design}\label{design}}

Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{19} at the Technische Universität Dresden.
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{20,21}

\hypertarget{psychometric-measures}{%
\subsubsection{2.3.1 Psychometric measures}\label{psychometric-measures}}

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{22,23}
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{26} is used.
Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,27}
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{28}
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{29}
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{30,31} is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{32} the Self-Regulation Scale (SRS),\textsuperscript{33} the Brief Self-Control Scale (BSCS);\textsuperscript{34}{]},\textsuperscript{35} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{36,37}
Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{38}

\hypertarget{emotion-regulation-paradigm}{%
\subsubsection{2.3.2 Emotion regulation paradigm}\label{emotion-regulation-paradigm}}

The ER paradigm roughly consists of three parts that will be described in the following.

\emph{Part one: ER task.} Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group.\textsuperscript{14}
Participants are told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first has the condition ``active viewing-neutral'' that serves as a baseline condition.
During this block, 20 neutral pictures are presented.
Participants are asked to ``actively view all pictures and permit all emotions that may arise.'' In the second block, participants actively viewe negative pictures.
During the third, fourth, and fifth block, participants see negative pictures and are asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants are asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants are asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.'' Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants are told to ``suppress their emotional facial expression.'' They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants are instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{14}
All participants receive written instruction and complete a training session.
After the training session, participants are asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) is randomized between participants.

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting takes place.
The procedure of the discounting follows the COG-ED paradigm by Westbrook et al.\textsuperscript{17} with major change.
We use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values are presented.
The order of the comparisons is randomized.
Because there is no strategy that is objectively more difficult, we added an initial comparison that begins with the option ``1 EUR for strategy A or 1 EUR for strategy B''.
The strategy that is not chosen is assigned the value of 2 EUR.
From this point on, comparisons between strategies follow the original COG-ED paradigm.\textsuperscript{17}
Participants are instructed to decide as realistically as possible, imagining the displayed money would really be up for election.

\emph{Part three: ER choice.} After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
Importantly, there are no further instruction on what basis they should make their decision.
Participants should make their decision freely, according to the criteria they consider important for themselves.
However, participants are asked to state the reasons for the decision afterwards.
As soon as they have decided, they see the respective instruction and the block with another 20 negative pictures starts.

\hypertarget{stimuli}{%
\subsubsection{2.3.3 Stimuli}\label{stimuli}}

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{39} and the International Affective Picture System (IAPS).\textsuperscript{40}
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
An evolutionary algorithm\textsuperscript{41} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material X.

\hypertarget{electromyography}{%
\subsubsection{2.3.4 Electromyography}\label{electromyography}}

Two bipolar electromyograph (EMG) measures will be recorded in the region of the \emph{corrugator supercilii} and the \emph{levator labii} using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel will be used.
Data will be sampled at 1000 Hz.
To measure \emph{corrugator EMG}, electrodes will be applied to the abraded and cleaned skin on the left \emph{corrugator supercilii}, and to measure \emph{levator EMG}, electrodes were applied in the region of the \emph{levator labii}.
The ground electrode will be placed at the left \emph{Mastoid}.
A 10 Hz high pass and a 500 Hz low pass filter will be applied to both signals.
Afterwards, the signals will be rectified.
{[}\ldots{]}

\hypertarget{sampling-plan}{%
\subsection{2.4 Sampling plan}\label{sampling-plan}}

Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{19} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using \emph{G*Power}.\textsuperscript{42,43}
In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.\\
To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of least \(N=85\) have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.

\hypertarget{analysis-plan}{%
\subsection{2.5 Analysis plan}\label{analysis-plan}}

All statistical analyses will be performed using \emph{RStudio} (version 1.4.1717)\textsuperscript{44}and \emph{R} (version 4.1.0)\textsuperscript{45} for Windows.
The level of significance was set to \(\alpha=.05\).

\emph{Effects of emotion regulation on arousal and effort} To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of \emph{corrugator} and \emph{levator}.
A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom were reported when assumption of sphericity was violated.
Proportion of explained variance \(\eta²~p~\) was reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.

\emph{Subjective values of emotion regulation strategies} For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, the resulting (monetary) value will be divided by 2.00 €.
The final SV for each participant will be computed by averaging all final SVs of each strategy.
The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
Again, estimated, marginal means will be computed as post-hoc contrasts.

To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{46}
First, ER strategies will be re-coded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
Restricted maximum likelihood (REML) will be applied to fit the model.
A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological arousal (\emph{corrugator} activity and \emph{levator} activity) as level-1-predictor will be specified.
\[
SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
\] Level-1-predictors will be centered within cluster.\textsuperscript{47}
Residuals of the final model will be inspected visually.
Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).

The influence of personality traits on SVs will be investigated exploratorily.
Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.

The association between flexible ER and SVs of ER strategies will be investigated with a regression using the \(intercept\) and \(slope\) of each participants' SVs to predict threir FlexER score.
Therefore, SVs will be ordered by magnitude firstly.
Secondly, for each participant a linear model will be built to estimate the individual \(intercept\) and \(slope\).

For each result of the analyses both, \(p\)-values and Bayes factor \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{48} will be reported.

\hypertarget{data-availability}{%
\subsection{Data availability}\label{data-availability}}

The data of this study can be downloaded from \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.

\hypertarget{code-availability}{%
\subsection{Code availability}\label{code-availability}}

The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our \href{https://github.com/ChScheffel/CERED}{Github repository}.

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\hypertarget{ref-Gross1998antecedent}{}%
\CSLLeftMargin{1. }
\CSLRightInline{Gross, J. J. Antecedent- and response-focused emotion regulation: Divergent consequences for experience, expression, and physiology. \emph{Journal of Personality and Social Psychology} \textbf{74}, 224--37 (1998).}

\leavevmode\hypertarget{ref-Gross1998emerging}{}%
\CSLLeftMargin{2. }
\CSLRightInline{Gross, J. J. The emerging field of emotion regulation: An integrative review. \emph{Review of General Psychology} \textbf{2}, 271--299 (1998).}

\leavevmode\hypertarget{ref-Powers2019}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Powers, J. P. \& LaBar, K. S. Regulating emotion through distancing: A taxonomy, neurocognitive model, and supporting meta-analysis. \emph{Neuroscience and Biobehavioral Reviews} \textbf{96}, 155--173 (2019).}

\leavevmode\hypertarget{ref-Webb2012}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Webb, T. L., Miles, E. \& Sheeran, P. Dealing with feeling: A meta-analysis of the effectiveness of strategies derived from the process model of emotion regulation. \emph{Psychological Bulletin} \textbf{138}, 775--808 (2012).}

\leavevmode\hypertarget{ref-Zaehringer2020}{}%
\CSLLeftMargin{5. }
\CSLRightInline{Zaehringer, J., Jennen-Steinmetz, C., Schmahl, C., Ende, G. \& Paret, C. Psychophysiological effects of downregulating negative emotions: Insights from a meta-analysis of healthy adults. \emph{Front Psychol} \textbf{11}, 470 (2020).}

\leavevmode\hypertarget{ref-GrossJohn2003}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Gross, J. J. \& John, O. P. Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being. \emph{Journal of Personality and Social Psychology} \textbf{85}, 348--62 (2003).}

\leavevmode\hypertarget{ref-Yoon2013}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Yoon, K. L., Maltby, J. \& Joormann, J. A pathway from neuroticism to depression: Examining the role of emotion regulation. \emph{Anxiety, Stress, \& Coping} \textbf{26}, 558--72 (2013).}

\leavevmode\hypertarget{ref-Aldao2010}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Aldao, A., Nolen-Hoeksema, S. \& Schweizer, S. Emotion-regulation strategies across psychopathology: A meta-analytic review. \emph{Clinical Psychology Review} \textbf{30}, 217--237 (2010).}

\leavevmode\hypertarget{ref-Aldao2015}{}%
\CSLLeftMargin{9. }
\CSLRightInline{Aldao, A., Sheppes, G. \& Gross, J. J. Emotion regulation flexibility. \emph{Cognitive Therapy and Research} \textbf{39}, 263--278 (2015).}

\leavevmode\hypertarget{ref-Blanke2020}{}%
\CSLLeftMargin{10. }
\CSLRightInline{Blanke, E. S. \emph{et al.} Mix it to fix it: Emotion regulation variability in daily life. \emph{Emotion} \textbf{20}, 473--485 (2020).}

\leavevmode\hypertarget{ref-Kable2007}{}%
\CSLLeftMargin{11. }
\CSLRightInline{Kable, J. W. \& Glimcher, P. W. The neural correlates of subjective value during intertemporal choice. \emph{Nat Neurosci} \textbf{10}, 1625--33 (2007).}

\leavevmode\hypertarget{ref-Sheppes2011}{}%
\CSLLeftMargin{12. }
\CSLRightInline{Sheppes, G., Scheibe, S., Suri, G. \& Gross, J. J. Emotion-regulation choice. \emph{Psychological Science} \textbf{22}, 1391--6 (2011).}

\leavevmode\hypertarget{ref-Sheppes2014}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Sheppes, G. \emph{et al.} Emotion regulation choice: A conceptual framework and supporting evidence. \emph{Journal of Experimental Psychology: General} \textbf{143}, 163--81 (2014).}

\leavevmode\hypertarget{ref-Scheffel2021}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Scheffel, C. \emph{et al.} Effort beats effectiveness in emotion regulation choice: Differences between suppression and distancing in subjective and physiological measures. \emph{Psychophysiology} \textbf{00}, e13908 (2021).}

\leavevmode\hypertarget{ref-Inzlicht2018}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Inzlicht, M., Shenhav, A. \& Olivola, C. Y. The effort paradox: Effort is both costly and valued. \emph{Trends Cogn Sci} \textbf{22}, 337--349 (2018).}

\leavevmode\hypertarget{ref-Hull1943}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Hull, C. L. \emph{Principles of behavior: An introduction to behavior theory}. (Appleton-Century-Crofts, 1943).}

\leavevmode\hypertarget{ref-Westbrook2013}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Westbrook, A., Kester, D. \& Braver, T. S. What is the subjective cost of cognitive effort? {Load}, trait, and aging effects revealed by economic preference. \emph{PLOS ONE} \textbf{8}, e68210 (2013).}

\leavevmode\hypertarget{ref-Simmons2012}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}

\leavevmode\hypertarget{ref-Greiner2015}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}

\leavevmode\hypertarget{ref-Harris2009}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Harris, P. A. \emph{et al.} Research electronic data capture ({REDCap})---{A} metadata-driven methodology and workflow process for providing translational research informatics support. \emph{Journal of Biomedical Informatics} \textbf{42}, 377--381 (2009).}

\leavevmode\hypertarget{ref-Harris2019}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Harris, P. A. \emph{et al.} The {REDCap} consortium: {Building} an international community of software platform partners. \emph{Journal of Biomedical Informatics} \textbf{95}, 103208 (2019).}

\leavevmode\hypertarget{ref-Bech2004}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}

\leavevmode\hypertarget{ref-Braehler2007}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Brähler, E., Mühlan, H., Albani, C. \& Schmidt, S. Teststatistische pr{ü}fung und normierung der deutschen versionen des EUROHIS-QOL lebensqualit{ä}t-index und des WHO-5 wohlbefindens-index. \emph{Diagnostica} \textbf{53}, 83--96 (2007).}

\leavevmode\hypertarget{ref-Connor2003}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}

\leavevmode\hypertarget{ref-Sarubin2015}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Sarubin, N. \emph{et al.} First analysis of the 10-and 25-item german version of the connor-davidson resilience scale (CD-RISC) regarding psychometric properties and components. \emph{Zeitschrift Fur Gesundheitspsychologie} \textbf{23}, 112--122 (2015).}

\leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Campbell-Sills, L. \& Stein, M. B. Psychometric analysis and refinement of the connor-davidson resilience scale (CD-RISC): Validation of a 10-item measure of resilience. \emph{Journal of Traumatic Stress} \textbf{20}, 1019--28 (2007).}

\leavevmode\hypertarget{ref-Abler2009}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}

\leavevmode\hypertarget{ref-Doerfel2019}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}

\leavevmode\hypertarget{ref-Bernecker2017}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Bernecker, K. \& Job, V. Implicit theories about willpower in resisting temptations and emotion control. \emph{Zeitschrift Fur Psychologie-Journal of Psychology} \textbf{225}, 157--166 (2017).}

\leavevmode\hypertarget{ref-Cacioppo1982}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}

\leavevmode\hypertarget{ref-Bless1994}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R. F. \& Schwarz, N. Need for cognition - a scale measuring engagement and happiness in cognitive tasks. \emph{Zeitschrift Für Sozialpsychologie} \textbf{25}, 147--154 (1994).}

\leavevmode\hypertarget{ref-Paschke2016}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Paschke, L. M. \emph{et al.} Individual differences in self-reported self-control predict successful emotion regulation. \emph{Social Cognitive and Affective Neuroscience} \textbf{11}, 1193--204 (2016).}

\leavevmode\hypertarget{ref-Schwarzer1999}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}

\leavevmode\hypertarget{ref-Tangney2004}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Tangney, J. P., Baumeister, R. F. \& Boone, A. L. High self-control predicts good adjustment, less pathology, better grades, and interpersonal success. \emph{Journal of Personality} \textbf{72}, 271--324 (2004).}

\leavevmode\hypertarget{ref-Sproesser2011}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H. \& Renner, B. Candy or apple? How self-control resources and motives impact dietary healthiness in women. \emph{Appetite} \textbf{56}, 784--787 (2011).}

\leavevmode\hypertarget{ref-Patton1995}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}

\leavevmode\hypertarget{ref-Hartmann2011}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Hartmann, A. S., Rief, W. \& Hilbert, A. Psychometric properties of the german version of the barratt impulsiveness scale, version 11 (BIS-11) for adolescents. \emph{Perceptual and Motor Skills} \textbf{112}, 353--368 (2011).}

\leavevmode\hypertarget{ref-Derryberry2002}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}

\leavevmode\hypertarget{ref-Wessa2010}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Wessa, M. \emph{et al.} EmoPicS: Subjective und psychophysiologische evalueation neuen bildmaterials für die klinisch-biopsychologische forschung. \emph{Zeitschrift für Klinische Psychologie und Psychotherapie} \textbf{39}, 77 (2010).}

\leavevmode\hypertarget{ref-Lang2008}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Lang, P. J., Bradley, M. M. \& Cuthbert, B. N. \emph{International affective picture system (IAPS): Affective ratings of pictures and instruction manual}. (University of Florida, 2008).}

\leavevmode\hypertarget{ref-Yu2010}{}%
\CSLLeftMargin{41. }
\CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}

\leavevmode\hypertarget{ref-Faul2007}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G. \& Buchner, A. G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences. \emph{Behavior Research Methods} \textbf{39}, 175--191 (2007).}

\leavevmode\hypertarget{ref-Faul2009}{}%
\CSLLeftMargin{43. }
\CSLRightInline{Faul, F., Erdfelder, E., Buchner, A. \& Lang, A.-G. Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses. \emph{Behavior Research Methods} \textbf{41}, 1149--1160 (2009).}

\leavevmode\hypertarget{ref-RStudioTeam2020}{}%
\CSLLeftMargin{44. }
\CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}

\leavevmode\hypertarget{ref-RCore2021}{}%
\CSLLeftMargin{45. }
\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}

\leavevmode\hypertarget{ref-Kuznetsova2017}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}

\leavevmode\hypertarget{ref-Enders2007}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Enders, C. K. \& Tofighi, D. Centering predictor variables in cross-sectional multilevel models: {A} new look at an old issue. \emph{Psychological Methods} \textbf{12}, 121--138 (2007).}

\leavevmode\hypertarget{ref-Morey2021}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}

\end{CSLReferences}

\endgroup

\newpage

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
Applications for the centralized funds will be reviewed in May.
Regardless of whether or not this additional funding will be granted, the study can commence immediately.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

CS, AS, and JZ conceptualized the study and its methodology.
CS and JZ acquired funding, investigated, administered the project, and wrote the software.
CS, JZ, and AG did the formal analysis.
CS and JZ visualized the results, and prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.

\hypertarget{competing-interests}{%
\section{Competing Interests}\label{competing-interests}}

The authors declare no competing interests.

\newpage
\setcounter{figure}{0}

\hypertarget{figures-and-figure-captions}{%
\section{Figures and figure captions}\label{figures-and-figure-captions}}

\newpage
\begin{figure}
\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/other/Paradigm_Scheme_T2} \caption{ }\label{fig:fig1appendix}
\end{figure}

\emph{Figure 1.} Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm.
\# Design Table

\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}

\newpage

\hypertarget{supplement}{%
\section{Supplement}\label{supplement}}

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}

\newpage

\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
\subsection{Pilot study: Subjective arousal in the conditions ``active viewing - neutral'' and ``active viewing - negative''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}

ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 1, 15 & 3895.91 & 34.32 *** & .475 & <.001\\
\hline
\end{tabular}

\(BF10=\) 1,244.99

Paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-3}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - View_{neutral}$ & 129.28 & 22.07 & 15.00 & 5.86 & 0.00 & 794.78 & 0.70 & {}[0.43, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Figure:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjArousalViewPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.}\label{fig:FigSubjArousalViewPilot}
\end{figure}

\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}

ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 2.79, 41.89 & 2238.27 & 1.17 & .011 & .332\\
\hline
\end{tabular}

\(BF10=\) 0.11

Paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$Distancing - Distraction$ & 4.61 & 16.14 & 45.00 & 0.29 & 1.00 & 0.26 & 1.81e-03 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & -20.88 & 16.14 & 45.00 & -1.29 & 1.00 & 0.27 & 0.04 & {}[0.00, 1.00]\\
$Distancing - View_{negative}$ & 5.35 & 16.14 & 45.00 & 0.33 & 1.00 & 1.25 & 2.43e-03 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & -25.49 & 16.14 & 45.00 & -1.58 & 0.73 & 0.26 & 0.05 & {}[0.00, 1.00]\\
$Distraction - View_{negative}$ & 0.74 & 16.14 & 45.00 & 0.05 & 1.00 & 0.77 & 4.68e-05 & {}[0.00, 1.00]\\
$Suppression - View_{negative}$ & 26.23 & 16.14 & 45.00 & 1.63 & 0.67 & 0.52 & 0.06 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Figure:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjArousalRegPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.}\label{fig:FigSubjArousalRegPilot}
\end{figure}

\hypertarget{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
\subsection{Pilot study: Subjective effort in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}

ANOVA:

\begin{tabular}{l|l|l|l|l|l}
\hline
Effect & df & MSE & F & ges & p.value\\
\hline
block & 2.38, 35.66 & 4388.19 & 11.13 *** & .185 & <.001\\
\hline
\end{tabular}

\(BF10=\) 7.40

Paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$Distancing - Distraction$ & -21.00 & 20.85 & 45.00 & -1.01 & 1.00 & 59.77 & 0.02 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 20.49 & 1.27e-04 & {}[0.00, 1.00]\\
$Distancing - View_{negative}$ & 89.72 & 20.85 & 45.00 & 4.30 & 0.00 & 33.13 & 0.29 & {}[0.12, 1.00]\\
$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.50 & 0.03 & {}[0.00, 1.00]\\
$Distraction - View_{negative}$ & 110.72 & 20.85 & 45.00 & 5.31 & 0.00 & 0.57 & 0.39 & {}[0.20, 1.00]\\
$Suppression - View_{negative}$ & 88.15 & 20.85 & 45.00 & 4.23 & 0.00 & 0.26 & 0.28 & {}[0.11, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Figure:

\begin{figure}[H]
\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjEffortPilot-1} \caption{Subjective effort ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.}\label{fig:FigSubjEffortPilot}
\end{figure}

\end{document}

### 2022-02-10 06_Paper/ER-ED/_targets.R

@@ -1,5 +1,9 @@
 library(targets)
 library(tarchetypes)
+library(here)
+
+# set top level directory to source file
+here::i_am("flag_project_root_CERED.txt")
 
 # Set target-specific options such as packages.
 tar_option_set(packages = "tidyverse")
@@ -7,8 +11,12 @@ options(tidyverse.quiet = TRUE)
 
 # End this file with a list of target objects.
 list(
-  tar_target(whole.paper, "Manuscript_ERED_Stage1.Rmd"),
-  tar_target(intro, "TheoreticalBackground.Rmd"),
-  tar_target(method, "Method.Rmd"),
-  tar_target(Quest, "Questionnaires.R")
+  tar_target(intro, "TheoreticalBackground.Rmd", format = "file"),
+  tar_target(method, "Method.Rmd", format = "file"),
+  tar_target(Quest, "Questionnaires.R", format = "file"),
+  tar_target(raw_data_file, here("04_RawData", "pilot", "CERED_DATA.csv"), format = "file"),
+  tar_target(raw_data, read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"),
+                                 stringsAsFactors = FALSE, header = TRUE,
+                                 na.strings = c("", "NA"))),
+  tar_render(whole.paper, "Manuscript_ERED_Stage1.Rmd")
 )

### 2022-02-14 06_Paper/ER-ED/method.Rmd
updates on targets
added infos on EMG

@@
 The ground electrode will be placed at the left *Mastoid*.
-A 10 Hz high pass and a 500 Hz low pass filter will be applied to both signals.
-<!-- liebe Anne, habe das hier von Ray et al 2010 übernommen. Stimmt das für unsere Auswertung? --> Afterwards, the signals will be rectified.
-[...] <!-- @Anne hier fehlt noch einiges, bitte dann nach deiner Auswertung ergänzen =) -->
+A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
+Afterwards, the signals will be rectified and segmented.
+EMG data will be baseline-corrected to -200 ms to 0 ms to stimulus onset.
+Last, the sampling rate is changed to 100 Hz and the AUC for the interval of 6000 ms stimulus presentation extracted for every stimulus.
+<!-- Liebe @Anne, habe das aus dem Analyzer zusammengefasst, stimmt das? -- -->
 
@@
 Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
-In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.\
+In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.
 To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
@@
 Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
-Proportion of explained variance $\eta²~p~$ was reported as a measure of effect size.
+Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 209].
-
-One task that is often used to investigate effort is the n-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
+<!-- In the last sentence, the page number of the quote should appear with the quote, but given nature.csl does not, so perhaps just insert '(p. 209)' after 'reward sensitivity' -->
+
+One task that is often used to investigate effort is the *n*-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
 Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
-The n-back task is well suited to investigate effort because it is an almost continuous manipulation of task load, as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
-However, its reliability measures are mixed, and associations of n-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
+The *n*-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
+However, its reliability measures are mixed, and associations of *n*-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
 

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 
-A way to quantify the subjective cost of each n-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
-First, the participants complete the n-back levels to familiarize themselves with the task.
+A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+First, the participants complete the *n*-back levels to familiarize themselves with the task.
 Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
@@
 This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
-The idea is to estimate the point of subjective equivalence, i.e. the monetary ratio at which both offers are equally preferred [@Westbrook2013].
-The subjective value (SV) of each difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
-Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting (ED).
-Younger participants showed lower ED, i.e. they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
+The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred [@Westbrook2013].
+The subjective value (SV) of each difficulty level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
+Westbrook et al.
+[-@Westbrook2013] <!-- I guess, it is easier to simply write @Westbrook2013 instead of Westbrook et al.
+[-@Westbrook2013], but this may be sinply a matter of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED) <!-- perhaps avoid the abbreviation and simoly always write effort discounting -->.
+Younger participants showed lower ED, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
 
 The individual degree of ED in the study by Westbrook et al.
-[-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
+[-@Westbrook2013] was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
 Westbrook et al.

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 
-The present study changes one fundamental assumption of the original COG-ED paradigm: That the easiest n-back level has the highest SV.
-We adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different n-back levels without presuming that all individuals inherently prefer the easiest level.
+With he present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
+We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
 Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
@@
 If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
-Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g.
-emotion regulation tasks, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
+Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks <!-- perhaps add ref.
+to the other ms.
+on this issue?
+-->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
 In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
-Additionally, we will compare the ED behaviour of participants regarding the n-back task and an emotion regulation task.
-The full results of the latter will be published in a second Registered Report.
-The COG-ED paradigm has been applied to tasks with different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for emotion regulation.
+Additionally, we will compare the ED behaviour of participants regarding the *n*-back task and an emotion regulation task.
+The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
+The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
 

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
       - Visualization
+  - name          : "Alexander Strobel"
+    orcid         : "0000-0002-9426-5397"
+    affiliation   : "1"
+    <!-- to be discussed -->
+    role: 
+      - Formal analysis
+      - Writing - original draft preparation
+      - Writing - review & editing
+      - Visualization
 affiliation:
@@
 
+<!-- wouldn't it be more intellegible if the following code chunks are placed where the respective analyses are introducecommented on? -->
+
 ```{r import, echo=FALSE, message=FALSE, warning=FALSE}
@@
 [-@Westbrook2013] <!-- I guess, it is easier to simply write @Westbrook2013 instead of Westbrook et al.
-[-@Westbrook2013], but this may be sinply a matter of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED) <!-- perhaps avoid the abbreviation and simoly always write effort discounting -->.
+[-@Westbrook2013], but this may be a matter arising because of the use of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED) <!-- perhaps avoid the abbreviation and simply always write effort discounting, we had some issues recently when using abbreviations in a manuscript, but we were using a lot of them, so it may be ok to use one or two here -->.
 Younger participants showed lower ED, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
@@
 -->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
+<!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation, but applies to
 In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
@@
 Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
-Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing n-back level, (1b) reaction time increases with increasing n-back level, and (1c) perceived task load increases with increasing n-back level.
-Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing n-back level, and (2b) they do so even after controlling for declining task performance.
-Here we added the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
-And regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing *n*-back level, (1b) reaction time increases with increasing *n*-back level, and (1c) perceived task load increases with increasing *n*-back level.
+Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
+Here we added <!-- why this 'here we added'? --> the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores,
+and regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
 Each hypothesis is detailed in the Design Table in the Appendix.
@@
 
-  # create new data frames for the specification curve analysis
+  # create new data frames for the specification curve analysis <!-- specification curve analysis has not been mentioned in the ms. so far -->
   # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 
-<!-- wouldn't it be more intellegible if the following code chunks are placed where the respective analyses are introducecommented on? -->
+<!-- wouldn't it be more intellegible if the following code chunks are placed where the respective analyses are introduced/commented on? -->
 
@@
 and regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-Each hypothesis is detailed in the Design Table in the Appendix.
+Each hypothesis is detailed in the Design Table in the Appendix. <!-- regarding the Design Table, I have some questions, especially regarding the effect sizes used, they seem unusually large -->
 

### 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 
-With he present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
+With the present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
 We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.

### 2022-02-15 06_Paper/ER-ED/method.Rmd
added text to SVs

@@
 
+To investigate, whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
+Furthermore, an ordinal logistic regression with dependent variable choice and independent variables SVs of each strategy will be computed.
+
 To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd

@@
 A sample size analysis with *G\*Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
-[-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
+[-@Westbrook2013] which showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
+<!-- but can we really rely on Westbrook et al., 2013, when we know the findings of Kramer et al., 2021, who observed only half of the originally reported effect size, and quite rightfully so, because initiallly reported effect sizes are more likely thasn not inflated -->
 The power analyses of all other hypotheses yielded smaller necessary sample sizes.

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

--- 2022-02-14 06_Paper/COG-ED/Manuscript.Rmd
@@
 -->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
-<!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation, but applies to
+<!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation -->
 In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
@@
 and regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-Each hypothesis is detailed in the Design Table in the Appendix. <!-- regarding the Design Table, I have some questions, especially regarding the effect sizes used, they seem unusually large -->
+Each hypothesis is detailed in the Design Table in the Appendix.
 
@@
 A sample size analysis with *G\*Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
-[-@Westbrook2013] which showed an increase in reaction time with higher n-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
+[-@Westbrook2013] which showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta^2=0.04$, $\alpha=.05$, and $\beta=.95$.
 The power analyses of all other hypotheses yielded smaller necessary sample sizes.

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
incorporated most comments

@@
 However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
-Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" [@Kool2018, p.
-209].
-<!-- In the last sentence, the page number of the quote should appear with the quote, but given nature.csl does not, so perhaps just insert '(p. 209)' after 'reward sensitivity' -->
+Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" (p.
+209) [@Kool2018].
 
@@
 The subjective value (SV) of each difficulty level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
-Westbrook et al.
-[-@Westbrook2013] <!-- I guess, it is easier to simply write @Westbrook2013 instead of Westbrook et al.
-[-@Westbrook2013], but this may be a matter arising because of the use of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED) <!-- perhaps avoid the abbreviation and simply always write effort discounting, we had some issues recently when using abbreviations in a manuscript, but we were using a lot of them, so it may be ok to use one or two here -->.
-Younger participants showed lower ED, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
-
-The individual degree of ED in the study by Westbrook et al.
+Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting.
+Younger participants showed lower effort discounting, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
+
+The individual degree of effort discounting in the study by Westbrook et al.
 [-@Westbrook2013] was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
 Westbrook et al.
-[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure of ED.
+[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of effort discounting for each participant which could then be related to the SVs as an objective measure of effort discounting.
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
@@
 
-With the present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
-We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
+With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
+We therefore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
 Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
@@
 First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
-Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
+Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal prices.
 For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
@@
 If the participant has a clear preference for one level, this level's SV will be 1.
-If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
+If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
 Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks <!-- perhaps add ref.
@@
 In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
-Additionally, we will compare the ED behaviour of participants regarding the *n*-back task and an emotion regulation task.
+Additionally, we will compare the effort discounting behaviour of participants regarding the *n*-back task and an emotion regulation task.
 The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
@@
 Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing *n*-back level, (1b) reaction time increases with increasing *n*-back level, and (1c) perceived task load increases with increasing *n*-back level.
-Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
+Regarding the associations of task load and effort discounting we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
 Here we added <!-- why this 'here we added'? --> the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores,
-and regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-Each hypothesis is detailed in the Design Table in the Appendix.
+and regarding individual differences in effort discounting we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+Each hypothesis is detailed in the Design Table in the Appendix. <!-- regarding the Design Table, I have some questions, especially regarding the effect sizes used, they seem unusually large -->
 
@@
 The paradigm starts with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
+The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
 To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
 After each level, participants fill out the NASA-TLX on a tablet.
-Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
+Then, they complete the effort discounting procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
 Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back.
-This is only done to incentivise truthful behavior in the ED procedure, so the n-back data of this part will not be analyzed.
+This is only done to incentivise truthful behavior in the effort discounting procedure, so the n-back data of this part will not be analyzed.
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
+The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
 Participants will receive 30€ in total or course credit for participation.
@@
 
-A sample size analysis with *G\*Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
-[-@Westbrook2013] which showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta^2=0.04$, $\alpha=.05$, and $\beta=.95$.
+As there is no prior evidence on the magnitude of an interaction between *n*-back level and NFC, we assumed a small to medium effect size of $f=.175$.
+A sample size analysis with *G\*Power* [@Faul2007; @Faul2009] for a repeated measures ANOVA with within-between interaction indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
 The power analyses of all other hypotheses yielded smaller necessary sample sizes.
-To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 60 to 70 participants.
+To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 90 participants.
 
@@
 To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
+For each effort discounting round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
 Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
@@
 
-The association of ED and NFC will be examined with a regression using the $AUC$ of each participant's SVs to predict their NFC score.
+The association of effort discounting and NFC will be examined with a regression using the $AUC$ of each participant's SVs to predict their NFC score.
 A second regression will additionally include the mean of the NASA-TLX subscales' $AUCs$ of each participant as a predictor.
@@
 [-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
-Consequently, we will choose a different way of quantifying the individual degree of ED.
+Consequently, we will choose a different way of quantifying the individual degree of effort discounting.
 A classic $AUC$ cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd

@@
 Here we added <!-- why this 'here we added'? --> the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores,
-and regarding individual differences in effort discounting we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-Each hypothesis is detailed in the Design Table in the Appendix. <!-- regarding the Design Table, I have some questions, especially regarding the effect sizes used, they seem unusually large -->
+and regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+Each hypothesis is detailed in the Design Table in the Appendix.
 

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

--- 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
@@
 
+  <!-- papaja must be installed from GitHub so code above will not work for this package-->
+  # Install devtools package if necessary
+  # if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
+
+  # Install the stable development verions from GitHub
+  # devtools::install_github("crsh/papaja")
+
+  # Install the latest development snapshot from GitHub
+  # devtools::install_github("crsh/papaja@devel")
+
   # sets orthogonal contrasts for mixed-effects model and rmANOVA globally in order to get meaningful Type-III tests
@@
 # Methods
-
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
 The paradigm was written and presented using *Psychopy* [@Peirce2019].
@@
 
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF* corresponding.
+<!-- hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->
 
@@
 
-The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
+The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
 

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
     affiliation   : "1"
-    <!-- to be discussed -->
     role: 
@@
 
+  # the following code does not work for me, gives an error message upon knitting:
+  # > trying to use CRAN without setting a mirror
+  # removing "papaja" from the list of packages (see below) does not solve the 
+  # issue; perhaps we should setup the project using the renv package?
+
   installed_packages <- packages %in% rownames(installed.packages())
@@
 
-  <!-- papaja must be installed from GitHub so code above will not work for this package-->
+  # papaja must be installed from GitHub so code above will not work for this package
   # Install devtools package if necessary
@@
 ```
-
-<!-- wouldn't it be more intellegible if the following code chunks are placed where the respective analyses are introduced/commented on? -->
 

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.
+We used *R* with *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor* [@Morey2021] for all our analyses.
 
@@
 
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
+Prior to testing, written informed consent will be obtained.
+
 ## Pilot data
@@
 The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old).
+<!-- This results in 2 digits after the comma, all second digits are 0, perhaps use papaja::printnum instead of round, it will still be 2 digits, but with exact numbers -->
 One participant's data was removed because they misunderstood the instruction.
 Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
-The results showed increases in subjective and objective task load measures with higher n-back level.
-Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
-The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not.
+The results showed increases in subjective and objective task load measures with higher *n*-back level.
+Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
+The MLM revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
 The specification curve analysis showed that this pattern was true for all 63 pipelines.
-And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
+Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
 All results are detailed in the Supplementary Material.
@@
 
-Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE* [@Greiner2015].
-Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
-NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
+Healthy participants aged 18 to 30\<!-- welchen Effekt hat eigentlich der Backslash --> years will be recruited using the software *ORSEE* [@Greiner2015].
+Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
+NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
-The NFC scale shows comparably high internal consistency (Cronbach's $\alpha$ \> .80) [@Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
+The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
+Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session. <!-- again: add ref. -->
 A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
-The MLM revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
+A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
 The specification curve analysis showed that this pattern was true for all 63 pipelines.
@@
 Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
-Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
 To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 Prior to testing, written informed consent will be obtained.
+Participants will receive 30€ in total or course credit for participation.
 
@@
 After each level, participants fill out the NASA-TLX on a tablet.
-Then, they complete the ED procedure on screen, where each possible pairing of the four n-back levels is presented in a randomized order.
-Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of n-back.
-This is only done to incentivise truthful behavior in the ED procedure, so the n-back data of this part will not be analyzed.
+Then, they complete the ED procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
+Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
+This is only done to incentivise truthful behavior in the ED procedure, so the *n*-back data of this part will not be analyzed.
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
 The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
-Participants will receive 30€ in total or course credit for participation.
 Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
@@
 
-A sample size analysis with *G\*Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
-[-@Westbrook2013] which showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta^2=0.04$, $\alpha=.05$, and $\beta=.95$.
+*A priori* sample size determination was performed using with *G\*Power* [@Faul2007; @Faul2009], mainly based on the results of the analyses of Westbrook et al.
+[-@Westbrook2013] (see Design Table<!-- link this table -->).
+Results of these analyses revealed that ...
+<!-- showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta^2=0.04$, $\alpha=.05$, and $\beta=.95$.
+-->
 The power analyses of all other hypotheses yielded smaller necessary sample sizes.
-To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 60 to 70 participants.
+To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 80 participants.
 

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@
 
-To determine the influence of task performance in the association of SVs and n-back level, we will set up a MLM using the $lmerTest$ package [@Kuznetsova2017]. 
+To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package [@Kuznetsova2017]. 
 We will apply restricted maximum likelihood (REML) to fit the model.
@@
 -->
-Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+Second, we will estimate a random slopes model of SVs including *n*-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
 Within the model, we will control for *d'*, RT, correct, and post-correct trials.
@@
 To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within n-back levels).
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
 The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
@@
 
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF* corresponding.
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
 <!-- hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->

### 2022-02-15 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
Create Manuscript_ERED_Stage1.tex

@@
 The ground electrode will be placed at the left \emph{Mastoid}.
-A 10 Hz high pass and a 500 Hz low pass filter will be applied to both signals.
-Afterwards, the signals will be rectified.
-{[}\ldots{]}
+A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
+Afterwards, the signals will be rectified and segmented.
+EMG data will be baseline-corrected to -200 ms to 0 ms to stimulus onset.
+Last, the sampling rate is changed to 100 Hz and the AUC for the interval of 6000 ms stimulus presentation extracted for every stimulus.
 
@@
 Sample size calculation is done using \emph{G*Power}.\textsuperscript{42,43}
-In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.\\
+In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.
 To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of least \(N=85\) have to be analyzed.
@@
 Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom were reported when assumption of sphericity was violated.
-Proportion of explained variance \(\eta²~p~\) was reported as a measure of effect size.
+Proportion of explained variance \(\eta_{p}^{2}\) was reported as a measure of effect size.
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
@@
 Again, estimated, marginal means will be computed as post-hoc contrasts.
+
+To investigate, whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
+Furthermore, an ordinal logistic regression with dependent variable choice and independent variables SVs of each strategy will be computed.
 

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
effect sizes mlm
worked on comments and added effect sizes for MLM

--- 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
@@
     affiliation   : "1"
+    <!-- to be discussed -->
     role: 
@@
   packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
-               "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize")
+               "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize",
+               "MuMIn")
 
   # check whether each package is installed and install and/or load library
-
-  # the following code does not work for me, gives an error message upon knitting:
-  # > trying to use CRAN without setting a mirror
-  # removing "papaja" from the list of packages (see below) does not solve the 
-  # issue; perhaps we should setup the project using the renv package?
 
@@
 
-  # papaja must be installed from GitHub so code above will not work for this package
-  # Install devtools package if necessary
-  # if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
-
-  # Install the stable development verions from GitHub
-  # devtools::install_github("crsh/papaja")
-
-  # Install the latest development snapshot from GitHub
-  # devtools::install_github("crsh/papaja@devel")
-
   # sets orthogonal contrasts for mixed-effects model and rmANOVA globally in order to get meaningful Type-III tests
@@
 ```
+
+<!-- wouldn't it be more intellegible if the following code chunks are placed where the respective analyses are introduced/commented on? -->
 
@@
 -->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
-<!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation -->
+<!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation, but applies to
 In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
@@
 
+  # get pseudo-r-squared -------------------------------------------------------
+
+  ## for the whole model
+  h2b_total_r2 <- r.squaredGLMM(m1_h2b, pj2014 = T)
+
+  ## H2b: n-back level
+  # according to https://doi.org/10.1186/s40536-018-0061-2 after Aiken and West 1991
+  # model without effect
+  m1_h2b_without <- lmer(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
+                         data = h2b_data,
+                         REML = T)
+  # calculate R²
+  h2b_without_r2 <- r.squaredGLMM(m1_h2b_without, pj2014 = T)
+
+  # calculate f² with conditional R²
+  h2b_r2 <- (h2b_total_r2[1,2] - h2b_without_r2[1,2]) / (1 - h2b_total_r2[1,2])
+
+  ## H2c: NFC score
+  m1_h2c_without <- lmer(sv ~ level.cwc + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
+                         data = h2b_data,
+                         REML = T)
+  # calculate R²
+  h2c_without_r2 <- r.squaredGLMM(m1_h2c_without, pj2014 = T)
+
+  # calculate f² with conditional R²
+  h2c_r2 <- (h2b_total_r2[1,2] - h2c_without_r2[1,2]) / (1 - h2b_total_r2[1,2])
+
   # get Bayes factors ----------------------------------------------------------
@@
 # Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
+
 The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R* with *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor* [@Morey2021] for all our analyses.
+We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.
 
@@
 
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
-Prior to testing, written informed consent will be obtained.
-
 ## Pilot data
@@
 The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old).
-<!-- This results in 2 digits after the comma, all second digits are 0, perhaps use papaja::printnum instead of round, it will still be 2 digits, but with exact numbers -->
 One participant's data was removed because they misunderstood the instruction.
 Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
-The results showed increases in subjective and objective task load measures with higher *n*-back level.
-Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
-A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
+The results showed increases in subjective and objective task load measures with higher n-back level.
+Importantly, SVs were lower for higher n-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
+The MLM revealed that n-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not.
 The specification curve analysis showed that this pattern was true for all 63 pipelines.
-Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
+And finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
 All results are detailed in the Supplementary Material.
@@
 
-Healthy participants aged 18 to 30\<!-- welchen Effekt hat eigentlich der Backslash --> years will be recruited using the software *ORSEE* [@Greiner2015].
-Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
-NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
+Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE* [@Greiner2015].
+Participants will fill out the personality questionnaires online and then visit the lab for two sessions one week apart.
+NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
-The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session. <!-- again: add ref. -->
+The NFC scale shows comparably high internal consistency (Cronbach's $\alpha$ \> .80) [@Bless1994; @Fleischhauer2010].
+Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session.
 A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
@@
 A sample size analysis with *G\*Power* [@Faul2007; @Faul2009], based on the results of the ANOVA of Westbrook et al.
-[-@Westbrook2013] which showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta^2=0.04$, $\alpha=.05$, and $\beta=.95$.
+[-@Westbrook2013] which showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta2=0.04$, $\alpha=.05$, and $\beta=.95$.
+<!-- but can we really rely on Westbrook et al., 2013, when we know the findings of Kramer et al., 2021, who observed only half of the originally reported effect size, and quite rightfully so, because initiallly reported effect sizes are more likely thasn not inflated -->
 The power analyses of all other hypotheses yielded smaller necessary sample sizes.
@@
 Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
-Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in multi-level-model (MLM), because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
 To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
@@
 We will apply restricted maximum likelihood (REML) to fit the model.
-First, we will calculate the intraclass correlation (ICC) on the basis of the null model.
+First, we will calculate the intraclass correlation (ICC) as effect size measure for random effects. 
+ICC displays the proportion of variance that is explained by differences between persons.
 <!--CS: Wieso wird der ICC nur für das Null Modell berechnet ?
@@
 -->
-Second, we will estimate a random slopes model of SVs including n-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+<!--CK: Die Intraklassenkorrelation wird immer auf Grundlage des Nullmodells berechnet.
+Sie gibt an, wieviel der Gesamtvarianz auf Unterschiede zwischen den Personen zurückgeführt werden kann.
+Das Nullmodell zeigt, wie stark sich die einzelnen Ebene-2-Einheiten in ihrer mittleren Ausprägung auf der aV unterscheiden.
+Daher enthält es keine Prädiktoren.
+Ich habe den letzten Teil des Satzes "on the basis of the null model" rausgenommen, da er redundant ist.
+-->
+<!-- werden wie Korrelationskoeffizienten interpretiert (https://doi.org/10.1186/s40536-018-0061-2), könnten wir im Ergebnisteil demnach in der Größe einschätzen --->
+Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor. 
 Within the model, we will control for *d'*, RT, correct, and post-correct trials.
@@
 Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
+By this, the model yields interpretable parameter estimates. 
 We will visually inspect the residuals of the final model.
 The approximately normal distribution indicates no evidence to perform model criticism.
+As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to <!-- please add https://doi.org/10.1186/s40536-018-0061-2 -->.  
 Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
@@
 <!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  --> 
+<!--CK: habe ich jetzt ergänzt -->
 
@@
 
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF* corresponding.
-<!-- hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].
 
@@
 
-The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
+The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
 

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd

--- 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
@@
 The individual degree of ED in the study by Westbrook et al.
-[-@Westbrook2013] was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
+[-@Westbrook2013] was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing an individual's tendency to actively seek out and enjoy effortful cognitive activities [@Cacioppo1982].
 Westbrook et al.
@@
 
-With the present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
+With the present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: that the easiest *n*-back level has the highest SV.
 We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
@@
 In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
-Additionally, we will compare the ED behaviour of participants regarding the *n*-back task and an emotion regulation task.
+Additionally, we will compare the ED behavior of participants regarding the *n*-back task and an emotion regulation task.
 The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.

### 2022-02-16 06_Paper/COG-ED/Manuscript.Rmd
effect sizes mlm 2nd

@@
   packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
-               "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize")
+               "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize",
+               "MuMIn")
 
@@
   # intraclass correlation (ICC)
-  # % of variance can be explained by differences between persons
   var_m0_h2b <- as.data.frame(VarCorr(m0_h2b))
   icc_h2b <- var_m0_h2b$vcov[1] / (var_m0_h2b$vcov[1] + var_m0_h2b$vcov[2])
+
+  # get pseudo-r-squared -------------------------------------------------------
+
+  ## for the whole model
+  h2b_total_r2 <- r.squaredGLMM(m1_h2b, pj2014 = T)
+
+  ## H2b: n-back level
+  # according to https://doi.org/10.1186/s40536-018-0061-2 after Aiken and West 1991
+  # model without effect
+  m1_h2b_without <- lmer(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
+                         data = h2b_data,
+                         REML = T)
+  # calculate R²
+  h2b_without_r2 <- r.squaredGLMM(m1_h2b_without, pj2014 = T)
+
+  # calculate f² with conditional R²
+  h2b_r2 <- (h2b_total_r2[1,2] - h2b_without_r2[1,2]) / (1 - h2b_total_r2[1,2])
+
+  ## H2c: NFC score
+  m1_h2c_without <- lmer(sv ~ level.cwc + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
+                         data = h2b_data,
+                         REML = T)
+  # calculate R²
+  h2c_without_r2 <- r.squaredGLMM(m1_h2c_without, pj2014 = T)
+
+  # calculate f² with conditional R²
+  h2c_r2 <- (h2b_total_r2[1,2] - h2c_without_r2[1,2]) / (1 - h2b_total_r2[1,2])
 
@@
 -->
-Second, we will estimate a random slopes model of SVs including *n*-back load level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+<!--CK: Die Intraklassenkorrelation wird immer auf Grundlage des Nullmodells berechnet.
+Sie gibt an, wieviel der Gesamtvarianz auf Unterschiede zwischen den Personen zurückgeführt werden kann.
+Das Nullmodell zeigt, wie stark sich die einzelnen Ebene-2-Einheiten in ihrer mittleren Ausprägung auf der aV unterscheiden.
+Daher enthält es keine Prädiktoren.
+Ich habe den letzten Teil des Satzes "on the basis of the null model" rausgenommen, da er redundant ist.
+-->
+<!--CK: werden wie Korrelationskoeffizienten interpretiert (https://doi.org/10.1186/s40536-018-0061-2), könnten wir im Ergebnisteil demnach in der Größe einschätzen --->
+Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor. 
 Within the model, we will control for *d'*, RT, correct, and post-correct trials.
@@
 Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
+By this, the model yields interpretable parameter estimates. 
 We will visually inspect the residuals of the final model.
 The approximately normal distribution indicates no evidence to perform model criticism.  
+As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to <!--CK: please add https://doi.org/10.1186/s40536-018-0061-2 -->.
+<!--CK: these are the corresponding values: h2b_total_r2, h2b_r2, h2c_r2 -->
 Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
@@
 <!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  --> 
-
+<!--CK: habe ich jetzt ergänzt -->
 To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.

### 2022-02-16 06_Paper/COG-ED/Manuscript.Rmd
update effect sizes

@@
   ## H2b: n-back level
-  # according to https://doi.org/10.1186/s40536-018-0061-2 after Aiken and West 1991
   # model without effect
@@
 The approximately normal distribution indicates no evidence to perform model criticism.  
-As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to <!--CK: please add https://doi.org/10.1186/s40536-018-0061-2 -->.
+As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to <!--CK: please add https://doi.org/10.1186/s40536-018-0061-2 (after Aiken and West 1991) -->.
 <!--CK: these are the corresponding values: h2b_total_r2, h2b_r2, h2c_r2 -->

### 2022-02-16 06_Paper/COG-ED/Manuscript.Rmd
update effect sizes 2nd
Ms Review

@@
 [-@Westbrook2013] <!-- I guess, it is easier to simply write @Westbrook2013 instead of Westbrook et al.
-[-@Westbrook2013], but this may be a matter arising because of the use of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED) <!-- perhaps avoid the abbreviation and simply always write effort discounting, we had some issues recently when using abbreviations in a manuscript, but we were using a lot of them, so it may be ok to use one or two here -->.
+[-@Westbrook2013], but this may be a matter arising because of the use of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED)<!-- perhaps avoid the abbreviation and simply always write effort discounting, we had some issues recently when using abbreviations in a manuscript, but we were using a lot of them, so it may be ok to use one or two here -->.
 Younger participants showed lower ED, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
@@
 Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
+<!--CK: instead of prices I would prefer reward in this context -->
 For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
@@
 If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
-Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks <!-- perhaps add ref.
+Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks<!-- perhaps add ref.
 to the other ms.
@@
 <!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation -->
-In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
+In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al.
+[-@Westbrook2013].
+<!--CK: note, the knitted doc displays: Westbrook et al..
+7; the quotation should stick to the authors -->
 Additionally, we will compare the ED behavior of participants regarding the *n*-back task and an emotion regulation task.
 The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
-The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
+The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021],<!--CK: the same is here: ",14" --> but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
 
@@
 ```
-
+<!--CK: Within the figure I recommend spaces, e.g. 2-back(1-back) > 2-back (1-back);
+"rewarded" seems more appropriate to me than "priced";
+the text in the small plots in the last line is pretty small and hard to read, is it possible to use a larger the font?
+I understand the figure as you already explained it to me, but I suppose it would be beneficial to add some explanations, e.g.
+to add two headings, i.e 1. calculation of the SVs (in different settings); 2. the resulting preference pattern
+(and to add some explanations/ more details in the figure note) -->
 Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
@@
 
+  # random slopes model --------------------------------------------------------
+
+  ## maximal model ---- 
+  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
+                 data = h2b_data,
+                 REML = T) # parameters estimated by restricted log-likelihood maximization
+
+  ## plot model fit of the final model ----
+  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
+
   # get pseudo-r-squared -------------------------------------------------------
@@
   h2c_r2 <- (h2b_total_r2[1,2] - h2c_without_r2[1,2]) / (1 - h2b_total_r2[1,2])
-
-  # random slopes model --------------------------------------------------------
-
-  ## maximal model ---- 
-  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
-                 data = h2b_data,
-                 REML = T) # parameters estimated by restricted log-likelihood maximization
-
-  ## plot model fit of the final model ----
-  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
 
@@
 
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...)<!--CK: don't forget to add -->.
 Prior to testing, written informed consent will be obtained.
@@
 
-Healthy participants aged 18 to 30\<!-- welchen Effekt hat eigentlich der Backslash --> years will be recruited using the software *ORSEE* [@Greiner2015].
+Healthy participants aged 18 to 30\ <!-- welchen Effekt hat eigentlich der Backslash --> years will be recruited using the software *ORSEE* [@Greiner2015].
 Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
@@
 In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
-The paradigm starts with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The paradigm starts with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
 The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
@@
 To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each ED round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
+For each ED round, SVs will be calculated by adding or subtracting 0.015625 <!--CK: for the reader it might be unclear how we determined this value -->from the last monetary value of the flexible level, depending on the participant's last choice.
 Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
@@
 A second regression will additionally include the mean of the NASA-TLX subscales' $AUCs$ of each participant as a predictor.
-Since we do not have a fixed SV of 1 for 1-back, we cannot apply the "$AUC$" computation of Westbrook et al.
+Since we do not have a fixed SV of 1 for 1-back, we cannot apply the "$AUC$" <!-- CK: it is the only case where "" are used -->computation of Westbrook et al.
 [-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
@@
 The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
+<!--CK: in the knitted document it is hard to see that "Github repository" contains a link, additionally it might be good to have the link visible within the document, also in case of a print version -->
 
@@
 Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-Applications for the centralized funds will be reviewed in May.
+Applications for the centralized funds will be reviewed in May. <!-- I would add the year -->
 Regardless of whether or not this additional funding will be granted, the study can commence immediately.

### 2022-02-16 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
-Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
+Different strategies <!-- Hier heißt es strategies, später dann tactices, dann wieder strategies.
+Das sollte vereinheitlicht werden, bzw.
+muss klar werden ob es einen Unterschied zwischen strategies und tactics gibt und wann das eine oder das andere der korrelte Begrifff ist --> can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
 So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].

### 2022-02-16 06_Paper/COG-ED/Manuscript.Rmd
implemented Corinna's figure recommendations

@@
 However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
-Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" [@Kool2018, p.
+Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" (p.
+209) [@Kool2018, p.
 209].
-<!-- In the last sentence, the page number of the quote should appear with the quote, but given nature.csl does not, so perhaps just insert '(p. 209)' after 'reward sensitivity' -->
 
@@
 The subjective value (SV) of each difficulty level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
-Westbrook et al.
-[-@Westbrook2013] <!-- I guess, it is easier to simply write @Westbrook2013 instead of Westbrook et al.
-[-@Westbrook2013], but this may be a matter arising because of the use of the nature.csl --> used these SVs to investigate inter-individual differences in effort discounting (ED)<!-- perhaps avoid the abbreviation and simply always write effort discounting, we had some issues recently when using abbreviations in a manuscript, but we were using a lot of them, so it may be ok to use one or two here -->.
-Younger participants showed lower ED, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
-
-The individual degree of ED in the study by Westbrook et al.
+Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting.
+Younger participants showed lower effort discounting, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
+
+The individual degree of effort discounting in the study by Westbrook et al.
 [-@Westbrook2013] was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing an individual's tendency to actively seek out and enjoy effortful cognitive activities [@Cacioppo1982].
 Westbrook et al.
-[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure of ED.
+[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of effort discounting for each participant which could then be related to the SVs as an objective measure of effort discounting.
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
@@
 
-With the present study, we change <!-- in my opinion better: alter --> one fundamental assumption of the original COG-ED paradigm: that the easiest *n*-back level has the highest SV.
-We therfore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
+With the present study, we alter one fundamental assumption of the original COG-ED paradigm: that the easiest *n*-back level has the highest SV.
+We therefore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
 Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
@@
 First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
-Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one ED round for each possible pair of levels, and by starting each round with a choice between equal prices.
+Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal prices.
 <!--CK: instead of prices I would prefer reward in this context -->
@@
 If the participant has a clear preference for one level, this level's SV will be 1.
-If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's ED behaviour can still be quantified.
+If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
 Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks<!-- perhaps add ref.
@@
 <!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation -->
-In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al.
-[-@Westbrook2013].
-<!--CK: note, the knitted doc displays: Westbrook et al..
-7; the quotation should stick to the authors -->
-Additionally, we will compare the ED behavior of participants regarding the *n*-back task and an emotion regulation task.
+In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
+Additionally, we will compare the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
 The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
-The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021],<!--CK: the same is here: ",14" --> but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
-
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back.", fig.pos="H"}
+The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
+
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+The grey boxes are the choice options shown to the participant.
+The participant's final reward value of the flexible level is displayed after the first arrow.
+The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice.
+The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}
 
@@
 ```
-<!--CK: Within the figure I recommend spaces, e.g. 2-back(1-back) > 2-back (1-back);
-"rewarded" seems more appropriate to me than "priced";
-the text in the small plots in the last line is pretty small and hard to read, is it possible to use a larger the font?
-I understand the figure as you already explained it to me, but I suppose it would be beneficial to add some explanations, e.g.
-to add two headings, i.e 1. calculation of the SVs (in different settings); 2. the resulting preference pattern
-(and to add some explanations/ more details in the figure note) -->
+
 Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
 Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing *n*-back level, (1b) reaction time increases with increasing *n*-back level, and (1c) perceived task load increases with increasing *n*-back level.
-Regarding the associations of task load and ED we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
+Regarding the associations of task load and effort discounting we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
 Here we added <!-- why this 'here we added'? --> the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores,
-and regarding individual differences in ED we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+and regarding individual differences in effort discounting we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
 Each hypothesis is detailed in the Design Table in the Appendix.
@@
 The paradigm starts with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
+The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
 To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
 After each level, participants fill out the NASA-TLX on a tablet.
-Then, they complete the ED procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
+Then, they complete the effort discounting procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
 Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
-This is only done to incentivise truthful behavior in the ED procedure, so the *n*-back data of this part will not be analyzed.
+This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm follows the same structure of task and ED procedure, but participants can decide which strategy they want to reapply in the last block.
+The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
 Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
@@
 To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each ED round, SVs will be calculated by adding or subtracting 0.015625 <!--CK: for the reader it might be unclear how we determined this value -->from the last monetary value of the flexible level, depending on the participant's last choice.
+For each effort discounting round, SVs will be calculated by adding or subtracting 0.015625 <!--CK: for the reader it might be unclear how we determined this value -->from the last monetary value of the flexible level, depending on the participant's last choice.
 Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
@@
 
-*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a participant with the true preference 2-back > 3-back > 1-back.
+*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+The grey boxes are the choice options shown to the participant.
+The participant's final reward value of the flexible level is displayed after the first arrow.
+The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice.
+The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
 

### 2022-02-16 06_Paper/COG-ED/Manuscript.Rmd
specified why h2c is not Westbrook

@@
 Regarding the associations of task load and effort discounting we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
-Here we added <!-- why this 'here we added'? --> the hypothesis that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores,
-and regarding individual differences in effort discounting we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+A hypothesis that was not investigated in the original study is that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
+And regarding individual differences in effort discounting we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
 Each hypothesis is detailed in the Design Table in the Appendix.
@@
 \counterwithin{figure}{section}
+\counterwithin{table}{section}
 \setcounter{section}{19}
 \setcounter{figure}{0}
+\setcounter{table}{0}
 
@@
 
+\newpage
+
 ## Hypothesis 1b: Reaction time increases with increasing n-back level.
@@
 
+\newpage
+
 ## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
@@
 
+\newpage
+
 ## Hypothesis 2a: Subjective values decline with increasing n-back level.
@@
 
+\newpage
+
 ## Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
@@
 `r table_1`
+
+\newpage
 
@@
 
+\newpage
+
 ## Hypothesis 3a: Subjective values positively predict individual NCS scores.
@@
 
+\newpage
+
 ## Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.

### 2022-02-17 06_Paper/ER-ED/method.Rmd
import marker file

@@
 
-datalist_EMG = lapply(list.files(here("04_RawData", "pilot", "ER-ED/EMG/analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
+datalist_EMG <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                           read.table, stringsAsFactors = FALSE, header = TRUE)
+datalist_EMG_Marker <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = "*.Markers", full.names = TRUE),
+                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL)
 
@@
   tmp = data.frame(datalist_EMG[[i]][["Filename"]], 
-                   datalist_EMG[[i]][["Segment"]], 
+                   datalist_EMG_Marker[[i]][["Description"]], 
                    datalist_EMG[[i]][["T0T6000Corr.ASNM"]], 

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added ANOVA EMG view

@@
 datalist_EMG_Marker <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = "*.Markers", full.names = TRUE),
-                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL)
+                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL, sep = ",")
 
 # new empty frame to store files into
-data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
+data_EMG = data.frame(ID = character(), trigger = double(), Corr = double(), 
                      Lev = double())
@@
   labs(y = "Effort Rating")
+
+### EMG
+
+# effect of valence on EMG
+
+EMG_view <- data_EMG %>%
+  subset(data_EMG$segment == "view_neu" | data_ER$block == "view_neg")
+Ratings_view$block <- as.factor(Ratings_view$block)
+
+SubjArousalView_aov <- afex::aov_ez(data = Ratings_view,
+                               id = "ID",
+                               dv = "arousal",
+                               within = "block",
+                               fun_aggregate = mean,
+                               include_aov = TRUE)
+
 ```

### 2022-02-17 06_Paper/ER-ED/method.Rmd

@@
 # effect of valence on EMG
+# corrugator
 
 EMG_view <- data_EMG %>%
-  subset(data_EMG$segment == "view_neu" | data_ER$block == "view_neg")
-Ratings_view$block <- as.factor(Ratings_view$block)
+  subset(data_EMG$block == "view_neu" | data_EMG$block == "view_neg")
+EMG_view$block <- as.factor(EMG_view$block)
 
-SubjArousalView_aov <- afex::aov_ez(data = Ratings_view,
+EMGCorrView_aov <- afex::aov_ez(data = EMG_view,
                                id = "ID",
-                               dv = "arousal",
+                               dv = "Corr",
                                within = "block",

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added variable block

@@
 library(effectsize)
+library(dplyr)
 
@@
 }
+
+# create variable "block"
+
+data_EMG$block[data_EMG$trigger == " S 21"] <- "view_neg"
+data_EMG$block[data_EMG$trigger == " S 22"] <- "view_neg"
+data_EMG$block[data_EMG$trigger == " S 23"] <- "distraction"
+data_EMG$block[data_EMG$trigger == " S 24"] <- "distancing"
+data_EMG$block[data_EMG$trigger == " S 25"] <- "suppression"
+data_EMG$block[data_EMG$trigger == " S 26"] <- "choice"
 

### 2022-02-17 06_Paper/COG-ED/Manuscript.Rmd

@@
 
-  # define required packages
-
-  packages = c("bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
-               "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize",
-               "MuMIn")
-
-  # check whether each package is installed and install and/or load library
-
-  # the following code does not work for me, gives an error message upon knitting:
-  # > trying to use CRAN without setting a mirror
-  # removing "papaja" from the list of packages (see below) does not solve the 
-  # issue; perhaps we should setup the project using the renv package?
-
-  installed_packages <- packages %in% rownames(installed.packages())
-  if (any(installed_packages == FALSE)) {
-     install.packages(packages[!installed_packages])
-  }
-  invisible(lapply(packages, library, character.only = TRUE))
-
-  # papaja must be installed from GitHub so code above will not work for this package
-  # Install devtools package if necessary
-  # if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")
-
-  # Install the stable development verions from GitHub
-  # devtools::install_github("crsh/papaja")
-
-  # Install the latest development snapshot from GitHub
-  # devtools::install_github("crsh/papaja@devel")
+  # load here-library for path-independent project structure (install here by calling install.packages("here") if necessary)
+  # set top level directory to source file
+
+  library(here)
+
+  here::i_am("flag_project_root_CERED.txt")
+
+  # load reproducible environment library to get all packages with correct versions form the renv.lock file
+  # install renv by calling install.packages("renv") if necessary
+
+  library(renv)
+
+  renv::init(here("06_Paper","COG-ED"))
+
+  # the required packages are:
+  # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
+  # "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize", and "MuMIn"
 
@@
   set_sum_contrasts()
-
-  # we will add the package versions before submission
 
@@
 
+The Bayes Factor $BF10$ of the multi level model approached infinity.
+
 \newpage
@@
 
-Johnson-Neyman interval:
-
-`r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`
-
-Specification curve analysis:
+Johnson-Neyman interval: `r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`
+
+Bayes Factor: $BF10=$ `r format(extractBF(h2c_BF)$bf, digits = 2)`
+
+\newpage
+
+## Specification curve analysis:
 

### 2022-02-17 06_Paper/ER-ED/method.Rmd

--- 2022-02-17 06_Paper/ER-ED/method.Rmd
@@
 }
+
+# create variable "block"
+
+data_EMG$block[data_EMG$trigger == " S 21"] <- "view_neu"
+data_EMG$block[data_EMG$trigger == " S 22"] <- "view_neg"
+data_EMG$block[data_EMG$trigger == " S 23"] <- "distraction"
+data_EMG$block[data_EMG$trigger == " S 24"] <- "distancing"
+data_EMG$block[data_EMG$trigger == " S 25"] <- "suppression"
+data_EMG$block[data_EMG$trigger == " S 26"] <- "choice"
 
@@
 
+EMGLevView_aov <- afex::aov_ez(data = EMG_view,
+                               id = "ID",
+                               dv = "Lev",
+                               within = "block",
+                               fun_aggregate = mean,
+                               include_aov = TRUE)
+
 ```

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
changed graphics directory

@@
 This pattern can also be represented by our paradigm.", out.width="98%"}
-include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
+include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
 ```

### 2022-02-17 06_Paper/COG-ED/Manuscript.Rmd
added r squared to supplement

@@
 
+The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2b_r2, digits = 2)`.
+
 \newpage
@@
 Bayes Factor: $BF10=$ `r format(extractBF(h2c_BF)$bf, digits = 2)`
+
+The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2c_r2, digits = 2)`.
 

### 2022-02-17 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
Update Manuscript_ERED_Stage1.Rmd

@@
  Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
-Perceived costs of ER strategies in form of effort however, are highly subjective.
+ Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
  Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
@@
 ```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE, out.width="98%"}
-include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
+include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
 ```

### 2022-02-17 06_Paper/ER-ED/method.Rmd

@@
 
+# compute posthoc tests for within measures
+EMGCorrView_emm <- emmeans::emmeans(EMGCorrView_aov$aov, specs = "block")
+
+EMGCorrView_con <- as.data.frame(pairs(EMGCorrView_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
+                                       data = EMG_view,
+                                       progress = FALSE)
+EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Coor[EMG_view$block == "view_neu"],
+                                                                    y = EMG_view$Corr[Ratings_view$block == "view_neg"],
+                                                                    progress = FALSE, paired = TRUE))$bf
+
+SubjArousalView_con <- cbind(SubjArousalView_con,
+                             format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
+                                                          df_error = SubjArousalView_con$df,
+                                                          ci = 0.95),
+                                                          digits = 2))
+
+colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+# rename contrast for table
+SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Active viewing", 
+                   limits = c("view_neu", "view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Arousal Rating")
+
+# levator
+
 EMGLevView_aov <- afex::aov_ez(data = EMG_view,

### 2022-02-17 06_Paper/COG-ED/Manuscript.Rmd
incorporated more comments

@@
     role: 
+      - Conceptualization
+      - Methodology
       - Formal analysis
-      - Writing - original draft preparation
       - Writing - review & editing
-      - Visualization
 affiliation:
@@
 First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
-Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal prices.
-<!--CK: instead of prices I would prefer reward in this context -->
+Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal rewards.
 For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
@@
 And regarding individual differences in effort discounting we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
-Each hypothesis is detailed in the Design Table in the Appendix.
+Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.
 
@@
 
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...)<!--CK: don't forget to add -->.
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
 Prior to testing, written informed consent will be obtained.
@@
 
-The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$)\ years old).
-<!-- This results in 2 digits after the comma, all second digits are 0, perhaps use papaja::printnum instead of round, it will still be 2 digits, but with exact numbers -->
+The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
 One participant's data was removed because they misunderstood the instruction.
@@
 
-Healthy participants aged 18 to 30\ <!-- welchen Effekt hat eigentlich der Backslash --> years will be recruited using the software *ORSEE* [@Greiner2015].
+Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE* [@Greiner2015].
 Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
@@
 
-*A priori* sample size determination was performed using with *G\*Power* [@Faul2007; @Faul2009], mainly based on the results of the analyses of Westbrook et al.
-[-@Westbrook2013] (see Design Table<!-- link this table -->).
-Results of these analyses revealed that ...
-<!-- showed an increase in reaction time with higher *n*-back levels, indicated that we should collect data from at least 53 participants, assuming $\eta^2=0.04$, $\alpha=.05$, and $\beta=.95$.
--->
+Sample size determination was mainly based on the results of the analyses of Westbrook et al. [-@Westbrook2013] (see [Design Table](#DesignTableSection)).
+As there was no prior evidence on the magnitude of an interaction between *n*-back level and NFC, we assumed a small to medium effect size of $f=.175$.
+Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] for a repeated measures ANOVA with within-between interaction indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
 The power analyses of all other hypotheses yielded smaller necessary sample sizes.
@@
 To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each effort discounting round, SVs will be calculated by adding or subtracting 0.015625 <!--CK: for the reader it might be unclear how we determined this value -->from the last monetary value of the flexible level, depending on the participant's last choice.
+For each effort discounting round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
+This value is the result of dividing the first adjustment of $0.50€$ by 2 five times, once in each effort discounting round.
 Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
@@
 We will apply restricted maximum likelihood (REML) to fit the model.
-First, we will calculate the intraclass correlation (ICC) as effect size measure for random effects. 
-ICC displays the proportion of variance that is explained by differences between persons.
-<!--CS: Wieso wird der ICC nur für das Null Modell berechnet ?
-Man könnte den doch auch für das full-model ebenfalls angeben und sehen, wieviel Varianzaufklärung hinzugekommen ist?
--->
-<!--CK: Die Intraklassenkorrelation wird immer auf Grundlage des Nullmodells berechnet.
-Sie gibt an, wieviel der Gesamtvarianz auf Unterschiede zwischen den Personen zurückgeführt werden kann.
-Das Nullmodell zeigt, wie stark sich die einzelnen Ebene-2-Einheiten in ihrer mittleren Ausprägung auf der aV unterscheiden.
-Daher enthält es keine Prädiktoren.
-Ich habe den letzten Teil des Satzes "on the basis of the null model" rausgenommen, da er redundant ist.
--->
-<!--CK: werden wie Korrelationskoeffizienten interpretiert (https://doi.org/10.1186/s40536-018-0061-2), könnten wir im Ergebnisteil demnach in der Größe einschätzen --->
+As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
 Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor. 
@@
 
-# Design Table
+# Design Table {#DesignTableSection}
 

### 2022-02-17 06_Paper/ER-ED/method.Rmd

--- 2022-02-17 06_Paper/ER-ED/method.Rmd
@@
 
+# compute posthoc tests for within measures
+EMGCorrView_emm <- emmeans::emmeans(EMGCorrView_aov$aov, specs = "block")
+
+EMGCorrView_con <- as.data.frame(pairs(EMGCorrView_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
+                                       data = EMG_view,
+                                       progress = FALSE)
+EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Coor[EMG_view$block == "view_neu"],
+                                                                    y = EMG_view$Corr[EMG_view$block == "view_neg"],
+                                                                    progress = FALSE, paired = TRUE))$bf
+
+EMGCorrView_con <- cbind(EMGCorrView_con,
+                         format(effectsize::t_to_eta2(t = EMGCorrView_con$t.ratio,
+                                                          df_error = EMGCorrView_con$df,
+                                                          ci = 0.95),
+                                                          digits = 2))
+
+colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+# rename contrast for table
+EMGCorrView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = arousal))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Active viewing", 
+                   limits = c("view_neu", "view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Corrugator activity")
+
+# levator
+
 EMGLevView_aov <- afex::aov_ez(data = EMG_view,

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added condition view for levator

--- 2022-02-17 06_Paper/ER-ED/method.Rmd
@@
 
+# compute posthoc tests for within measures
+EMGCorrView_emm <- emmeans::emmeans(EMGCorrView_aov$aov, specs = "block")
+
+EMGCorrView_con <- as.data.frame(pairs(EMGCorrView_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
+                                       data = EMG_view,
+                                       progress = FALSE)
+EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "view_neu"],
+                                                                    y = EMG_view$Corr[EMG_view$block == "view_neg"],
+                                                                    progress = FALSE, paired = TRUE))$bf
+
+EMGCorrView_con <- cbind(EMGCorrView_con,
+                         format(effectsize::t_to_eta2(t = EMGCorrView_con$t.ratio,
+                                                          df_error = EMGCorrView_con$df,
+                                                          ci = 0.95),
+                                                          digits = 2))
+
+colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+# rename contrast for table
+EMGCorrView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Active viewing", 
+                   limits = c("view_neu", "view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Corrugator activity")
+
+# levator
+
 EMGLevView_aov <- afex::aov_ez(data = EMG_view,
@@
                                include_aov = TRUE)
+
+# compute posthoc tests for within measures
+EMGLevView_emm <- emmeans::emmeans(EMGLevView_aov$aov, specs = "block")
+
+EMGLevView_con <- as.data.frame(pairs(EMGLevView_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
+                                       data = EMG_view,
+                                       progress = FALSE)
+EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "view_neu"],
+                                                                    y = EMG_view$Lev[EMG_view$block == "view_neg"],
+                                                                    progress = FALSE, paired = TRUE))$bf
+
+EMGLevView_con <- cbind(EMGLevView_con,
+                         format(effectsize::t_to_eta2(t = EMGLevView_con$t.ratio,
+                                                          df_error = EMGLevView_con$df,
+                                                          ci = 0.95),
+                                                          digits = 2))
+
+colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+# rename contrast for table
+EMGLevView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Active viewing", 
+                   limits = c("view_neu", "view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Corrugator activity")
 

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added ANOVA vor Corrugator reg conditions

--- 2022-02-17 06_Paper/ER-ED/method.Rmd
@@
 
-data_EMG$block[data_EMG$trigger == " S 21"] <- "view_neu"
-data_EMG$block[data_EMG$trigger == " S 22"] <- "view_neg"
-data_EMG$block[data_EMG$trigger == " S 23"] <- "distraction"
-data_EMG$block[data_EMG$trigger == " S 24"] <- "distancing"
-data_EMG$block[data_EMG$trigger == " S 25"] <- "suppression"
-data_EMG$block[data_EMG$trigger == " S 26"] <- "choice"
+data_EMG$block[data_EMG$trigger == " S 21"] <- "1_view_neu"
+data_EMG$block[data_EMG$trigger == " S 22"] <- "2_view_neg"
+data_EMG$block[data_EMG$trigger == " S 23"] <- "3_distraction"
+data_EMG$block[data_EMG$trigger == " S 24"] <- "4_distancing"
+data_EMG$block[data_EMG$trigger == " S 25"] <- "5_suppression"
+data_EMG$block[data_EMG$trigger == " S 26"] <- "6_choice"
 
@@
 EMG_view <- data_EMG %>%
-  subset(data_EMG$block == "view_neu" | data_EMG$block == "view_neg")
+  subset(data_EMG$block == "1_view_neu" | data_EMG$block == "2_view_neg")
 EMG_view$block <- as.factor(EMG_view$block)
@@
                                        progress = FALSE)
-EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Coor[EMG_view$block == "view_neu"],
-                                                                    y = EMG_view$Corr[Ratings_view$block == "view_neg"],
+EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
+                                                                    y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
                                                                     progress = FALSE, paired = TRUE))$bf
 
-SubjArousalView_con <- cbind(SubjArousalView_con,
-                             format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
-                                                          df_error = SubjArousalView_con$df,
+EMGCorrView_con <- cbind(EMGCorrView_con,
+                         format(effectsize::t_to_eta2(t = EMGCorrView_con$t.ratio,
+                                                          df_error = EMGCorrView_con$df,
                                                           ci = 0.95),
@@
 
-colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 # rename contrast for table
-SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+EMGCorrView_con[1,1] <- "$View_{neutral} - View_{negative}$"
 
@@
 # figure
-FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
+FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
   scale_x_discrete(name = "Active viewing", 
-                   limits = c("view_neu", "view_neg"),
+                   limits = c("1_view_neu", "2_view_neg"),
                    labels = c("Neutral", "Negative"))+
   geom_jitter(size = 0.4)+
-  labs(y = "Arousal Rating")
+  labs(y = "Corrugator activity")
 
@@
                                include_aov = TRUE)
+
+# compute posthoc tests for within measures
+EMGLevView_emm <- emmeans::emmeans(EMGLevView_aov$aov, specs = "block")
+
+EMGLevView_con <- as.data.frame(pairs(EMGLevView_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
+                                       data = EMG_view,
+                                       progress = FALSE)
+EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
+                                                                   y = EMG_view$Lev[EMG_view$block == "2_view_neg"],
+                                                                   progress = FALSE, paired = TRUE))$bf
+
+EMGLevView_con <- cbind(EMGLevView_con,
+                        format(effectsize::t_to_eta2(t = EMGLevView_con$t.ratio,
+                                                     df_error = EMGLevView_con$df,
+                                                     ci = 0.95),
+                                                     digits = 2))
+
+colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+# rename contrast for table
+EMGLevView_con[1,1] <- "$View_{neutral} - View_{negative}$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Active viewing", 
+                   limits = c("1_view_neu", "2_view_neg"),
+                   labels = c("Neutral", "Negative"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Corrugator activity")
+
+# effect of strategy on EMG
+
+EMG_reg <- data_EMG %>%
+  subset(data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
+EMG_reg$block <- as.factor(EMG_reg$block)
+
+# corrugator
+EMGCorrReg_aov <- afex::aov_ez(data = EMG_reg,
+                              id = "ID",
+                              dv = "Corr",
+                              within = "block",
+                              fun_aggregate = mean,
+                              include_aov = TRUE)
+
+# compute posthoc tests for within measures
+EMGCorrReg_emm <- emmeans::emmeans(EMGCorrReg_aov$aov, specs = "block")
+
+EMGCorrReg_con <- as.data.frame(pairs(EMGCorrReg_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
+                                      data = EMG_reg,
+                                      progress = FALSE)
+
+EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf)
+
+EMGCorrReg_con <- cbind(EMGCorrReg_con,
+                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
+                                                     df_error = EMGCorrReg_con$df,
+                                                     ci = 0.95),digits = 2))
+
+colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+
+EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
+EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
+EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
+EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
+EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
+EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Corrugator activity")
+
+# levator
+
+EMGLevReg_aov <- afex::aov_ez(data = EMG_reg,
+                              id = "ID",
+                              dv = "Lev",
+                              within = "block",
+                              fun_aggregate = mean,
+                              include_aov = TRUE)
+
+# compute posthoc tests for within measures
+EMGLevReg_emm <- emmeans::emmeans(EMGLevReg_aov$aov, specs = "block")
+
+EMGLevReg_con <- as.data.frame(pairs(EMGLevReg_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
+                                      data = EMG_reg,
+                                      progress = FALSE)
+
+EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf)
+
+EMGCorrReg_con <- cbind(EMGCorrReg_con,
+                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
+                                                     df_error = EMGCorrReg_con$df,
+                                                     ci = 0.95),digits = 2))
+
+colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+
+EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
+EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
+EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
+EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
+EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
+EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Corrugator activity")
 

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added ANOVA for Levator

@@
 # loop to correct block indicator
+
+data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
+data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
 
@@
   geom_jitter(size = 0.4)+
-  labs(y = "Corrugator activity")
+  labs(y = "Levator activity")
 
@@
 # Bayes Factors
-EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
+EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                       data = EMG_reg,
@@
 
-EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf)
 
-EMGCorrReg_con <- cbind(EMGCorrReg_con,
-                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
-                                                     df_error = EMGCorrReg_con$df,
+EMGLevReg_con <- cbind(EMGLevReg_con,
+                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
+                                                    df_error = EMGLevReg_con$df,
                                                     ci = 0.95),digits = 2))
 
-colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 
-EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
-EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
-EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
-EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
-EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
-EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
+EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
+EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
+EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
+EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
+EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
+EMGLevReg_con[6,1] <- "$Distancing - Suppression$"
 
@@
 # figure
-FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
+FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+

### 2022-02-17 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
Update Manuscript_ERED_Stage1.Rmd

@@
 # Author Contributions
-
+<!-- ist das überhaupt noch erforderlich, wenn doch im YAML header die roles difiniert wurden?
+Habe das bishernoch nicht gemacht, aber ist das nicht dazu da, dass dadurch automatisch ein Role Statement erzeugt wird?
+-->
 CS, AS, and JZ conceptualized the study and its methodology.

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 ---
+
 ```{r SetupIntro, include = FALSE}
@@
 library(targets)    # to keep track of all relevant files
-library(knitr)
+library(knitr)      # basic functions for R markdown documents
 library(here)       # to set directories without defined paths
@@
 ```
+
 # 1. Introduction
@@
 ## 1.1 ER strategy discounting
-
+<!-- NHB template says that there should not be subheadings in the introduction -->
 In the original study by Westbrook et al.

### 2022-02-17 06_Paper/ER-ED/method.Rmd
new way of assignment of blocks

@@
 data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
-data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
-
-for (i in 1:nrow(data_ER)) {
-
-  if (data_ER$trigger[i] == 21) {
-
-    data_ER$block[i] = "view_neu"
-
-  } else if (data_ER$trigger[i] == 22) {
-
-    data_ER$block[i] = "view_neg"
-
-  } else if (data_ER$trigger[i] == 23 ) {
-
-    data_ER$block[i] = "distraction"
-
-  } else if (data_ER$trigger[i] == 24 ) {
-
-    data_ER$block[i] = "distancing"
-
-  } else if (data_ER$trigge[i] == 25 ) {
-
-    data_ER$block[i] = "suppression"
-
-  } else if (data_ER$trigger[i] == 26) {
-
-    data_ER$block[i] = "choice"
-  }
-}
+data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
+data_ER$block[data_ER$trigger == 23] <- "3_distraction"
+data_ER$block[data_ER$trigger == 24] <- "4_distancing"
+data_ER$block[data_ER$trigger == 25] <- "5_suppression"
+data_ER$block[data_ER$trigger == 26] <- "6_choice"
 

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
-Different strategies <!-- Hier heißt es strategies, später dann tactices, dann wieder strategies.
-Das sollte vereinheitlicht werden, bzw.
-muss klar werden ob es einen Unterschied zwischen strategies und tactics gibt und wann das eine oder das andere der korrelte Begrifff ist --> can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
+Different strategies <!-- Ich bin immer noch nicht so richtig dahinter gekommen, was eigentlich der Unterschied zwischen strategies und tactics ist, ich meine, ich weiß, was der Unterschied zwischen einer Strategie und einer Taktik ist, aber inwiefern das in ER eine Rolle spiel, ist mir noch nicht so klar gweorden, aber ich habe auch Powers & LaBar nicht gelesen --> can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
 So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
@@
 For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
-Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see [@Aldao2010]).
+Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]).
 

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 
-<!--CS: Mit dem Teil bin ich noch nciht ganz zufrieden, freue mich über Anmerkungen, wie man das evtl. strukturieren kann! -->
+<!--CS: Mit dem Teil bin ich noch nicht ganz zufrieden, freue mich über Anmerkungen, wie man das evtl.
+strukturieren kann!
+AS: FInde den Teil eigentlich ganz gut gelungen, aber ich bin leider auch nicht os im Thema ER drin.
+-->
 The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
@@
 Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction [@Sheppes2011;@Sheppes2014].
-Further influencing factors are for example extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
-Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort [@Scheffel2021].
+Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
+Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy  [@Scheffel2021].
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option [@Kable2007].
-Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g.
-monetary incentives), motivational determinants (i.e.
-hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
-Effort in particular appeared to be the main factor in ER choice behaviour in our previous work [@Scheffel2021].
+Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
+Effort in particular appeared to be the main factor in ER choice behaviour <!-- chekcne pob bei NHB AE oder BE genutzt wird -->in our previous work [@Scheffel2021].
 In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.

### 2022-02-17 06_Paper/COG-ED/Manuscript.Rmd
moved all analyses to other script

@@
 csl               : nature.csl
+always_allow_html : true
 header-includes   :
@@
 
-  # load here-library for path-independent project structure (install here by calling install.packages("here") if necessary)
+  # load libraries
+
+  library(bibtex)       # for referencing, "bibtex" package
+  library(here)         # for path independent file referencing, "here" package
+  library(papaja)       # APA conform output, "papaja" package
+  library(kableExtra)   # for great tables in R Markdown, "kableExtra" package
+  library(interactions) # for simple slopes plots, "interactions" package
+  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
+  library(ggplot2)      # for plotting, "ggplot2" package
+  library(egg)          # for paneling plots, "egg" package
+  library(knitr)        # for including plots and such, "knitr" package
+  library(effectsize)   # for effect sizes and CIs, "effectsize" package
+
   # set top level directory to source file
 
-  library(here)
-
   here::i_am("flag_project_root_CERED.txt")
 
-  # load reproducible environment library to get all packages with correct versions form the renv.lock file
-  # install renv by calling install.packages("renv") if necessary
-
-  library(renv)
-
-  renv::init(here("06_Paper","COG-ED"))
-
-  # the required packages are:
-  # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
-  # "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize", and "MuMIn"
-
-  # sets orthogonal contrasts for mixed-effects model and rmANOVA globally in order to get meaningful Type-III tests
-
-  set_sum_contrasts()
-
-```
-
-```{r import, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # set top level directory to source file
-
-  here::i_am("flag_project_root_CERED.txt")
-
-  # import n-back and effort discounting data into a list each
-
-  datalist_nback = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*nback.*csv', full.names = TRUE),
-                          read.csv, stringsAsFactors = FALSE, header = TRUE)
-  datalist_ED = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*_ED.*csv', full.names = TRUE),
-                          read.csv, stringsAsFactors = FALSE, header = TRUE)
-
-  # create empty data frames for loops to feed into
-
-  data_nback <- data.frame(subject = character(), level = double(), target = character(),
-                           response = character(), correct = double(), rt = double())
-  data_ED <- data.frame(subject = character(), step = double(), choice = character(),
-                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
-
-  # put relevant data into data frames
-
-  for (i in 1:length(datalist_nback)) {
-
-    newdata <- data.frame(datalist_nback[[i]][["Participant"]], datalist_nback[[i]][["currentlevel"]],
-                          datalist_nback[[i]][["Stimulus"]], datalist_nback[[i]][["trial_resp.keys"]],
-                          datalist_nback[[i]][["trial_resp.corr"]], datalist_nback[[i]][["trial_resp.rt"]])
-    colnames(newdata) <- names(data_nback)
-    data_nback <- rbind(data_nback, newdata)
-  }
-
-  for (i in 1:length(datalist_ED)) {
-
-    newdata <- data.frame(datalist_ED[[i]][["Participant"]][2:length(datalist_ED[[i]][["Participant"]])],
-                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
-                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
-                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
-                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
-                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
-                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
-    colnames(newdata) <- names(data_ED)
-    data_ED <- rbind(data_ED, newdata)
-  }
-
-  # change the name of a subject (it has the suffix "_neu" because the paradigm didn't start properly the first time)
-
-  data_nback$subject[data_nback$subject == "E12K08_neu"] <- "E12K08"
-  data_ED$subject[data_ED$subject == "E12K08_neu"] <- "E12K08"
-
-  # remove one subject who did not understand the instructions of the n-back task and reacted only to every n-th stimulus
-
-  data_nback <- data_nback[data_nback$subject != "M28B11", ]
-  data_ED <- data_ED[data_ED$subject != "M28B11", ]
-
-  # replace some columns with 'easy to work with' values
-
-  # the target column will contain 1 for targets and 0 for all non-targets
-
-  data_nback[data_nback == "Target"] <- 1
-  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
-  data_nback$target <- as.numeric(data_nback$target)
-
-  # the response column will contain 1 for responses and 0 for all non-responses
-
-  data_nback[data_nback == "left"|data_nback == "right"] <- 1
-  data_nback[data_nback == "None"] <- 0
-  data_nback$response <- as.numeric(data_nback$response)
-
-  # for the multi level model to be able to assess the influence of post-error trials, we will include that as a regressor
-  # so the nback data frame will contain a column of ones and zeros
-
-  # add the "correct" column, but shifted down by one row
-
-  data_nback$postcorrect = c(1,data_nback$correct[1:(length(data_nback$correct)-1)])
-
-  # make sure to avoid transfer from the previous block by marking the first trial of each block as correct
-
-  data_nback$postcorrect[c(1,seq(64,length(data_nback$postcorrect),64))] <- 1
-
-  # correct subject code
-  data_nback$subject[which(data_nback$subject == "E12K08_neu")] <- "E12K08"
-  data_ED$subject[which(data_ED$subject == "E12K08_neu")] <- "E12K08"
-
-  # the choice column will contain 1 for the left button and 2 for the right button
-
-  data_ED[data_ED == "EDleftbutton"] <- 1
-  data_ED[data_ED == "EDrightbutton"] <- 2
-  data_ED$choice <- as.numeric(data_ED$choice)
-
-  # since only the last choice of each comparison is relevant, we will keep only those rows
-
-  data_ED <- data_ED[data_ED$step == 6,]
-  data_ED <- subset(data_ED, select = -c(step))
-
-  # import questionnaire data from RedCap
-
-  data_quest <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
-  colnames(data_quest)[1] <- "set" # rename the first column
-
-  # remove the subject who misunderstood the instruction
-
-  data_quest <- data_quest[data_quest$set != "M28B11", ]
-
-  # remove unnecessary variables from questionnaire data frame
-
-  data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
-                                               general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
-                                               researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
-                                               t1_psychopy_nback_csv, files_coged_complete, record_id_2, vl_er,
-                                               date_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
-                                               files_ered_complete, followup_ered_timestamp,
-                                               nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
-                                               nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
-                                               nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
-                                               bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
-                                               who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
-                                               cdrisc_complete, flexer_timestamp, flexer_complete))
-
-  # compute index of rows in which the data sets change
-
-  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))
-
-```
-
-```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # apply the addition or subtraction of 0.015625 to the last choices
-
-  for (i in 1:nrow(data_ED)) {
-
-    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
-    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]
-
-    if (data_ED$choice[i] == 1) {
-      if (data_ED$LBvalue[i] == 2.00) {
-        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
-      } else {
-        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
-      }
-    } else {
-      if (data_ED$RBvalue[i] == 2.00) {
-        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
-      } else {
-        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
-      }
-    }
-
-  }
-
-  # create vector indicating in which rows the data of a new subject begins
-
-  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))
-
-  # create empty data frame for the loop to feed into
-
-  data_SV <- data.frame(subject = character(), level = double(), sv = double())
-
-  # compute subjective values per n-back level and feed into data frame
-
-  for (i in 1:(length(subjectindex)-1)) {
-
-    # initialize empty vectors
-
-    tempone <- double()
-    temptwo <- double()
-    tempthree <- double()
-    tempfour <- double()
-
-    # check for every number, whether it appears in the fixedlevel and flexlevel columns
-    # divide flexvalue by 2 if it appears in the fixedlevel columns
-    # append 1 if it appears in the flexlevel column
-
-    # for 1-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
-          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 +
-                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
-          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
-        } else {
-          # do nothing
-        }
-
-    # for 2-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
-          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 +
-                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
-          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
-        } else {
-          # do nothing
-        }
-
-    # for 3-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
-          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 +
-                                                             which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
-          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
-        } else {
-          # do nothing
-        }
-
-    # for 4-back
-
-        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
-          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 +
-                                                           which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
-        } else {
-          # do nothing
-        }
-
-        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
-          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
-        } else {
-          # do nothing
-        }
-
-    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame
-
-    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
-                          level = c(1:4),
-                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
-    data_SV <- rbind(data_SV, newdata)
-
-  }
-
-  # remove temporary variables
-
-  remove(tempone, temptwo, tempthree, tempfour)
-
-  # add the SVs trial-wise to the nback-data-frame for the multi-level-model
-
-  for (i in 1:nrow(data_nback)) {
-
-    data_nback$sv[i] <- data_SV$sv[data_SV$subject == data_nback$subject[i] & data_SV$level == data_nback$level[i]]
-
-  }
-
-```
-
-```{r NFCcomputation, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # prepare temporary data frame for loop to feed into
-
-  data_nfc <- data.frame(subject = character(), nfc = double())
-
-  # compute index of rows in which the data sets change
-
-  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))
-
-  # calculate NFC scores for every subject
-
-  for (i in 1:(length(setindex)-1)) {
-
-    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]
-
-    # define and invert items to be recoded
-
-    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1
-
-    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
-                                           nfc = sum(nfc)))
-  }
-
-  # add the NFC scores trial-wise to the nback-data-frame for the multi-level-model
-
-  for (i in 1:nrow(data_nback)) {
-
-    data_nback$nfc[i] <- data_nfc$nfc[data_nfc$subject == data_nback$subject[i]]
-
-  }
-
-  # remove the temporary variables
-
-  remove(nfc, data_nfc)
+  # load the workspace variables that have been computed with the Analysis.R script
+
+  load(here("06_Paper","COG-ED","Workspace.RData"))
 
@@
 
-```{r preprocessing, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # create new data frames for the specification curve analysis <!-- specification curve analysis has not been mentioned in the ms. so far -->
-  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
-  #
-  # across which dimensions the transformation and outlier exclusion will be done:
-  #   (AA) across subjects, across n-back levels
-  #   (AW) across subjects, within n-back levels
-  #   (WW) within subjects, within n-back levels
-  #   (WA) within subjects, across n-back levels
-  # RT transformations:
-  #   (R) raw/none
-  #   (L) log
-  #   (I) inverse
-  #   (S) square-root
-  # RT outlier exclusion:
-  #   (N) none
-  #   (2) 2 MADs from the median
-  #   (5) 2.5 MADs from the median
-  #   (3) 3 MADs from the median
-  #   (O) 0-100 ms after stimulus onset
-  #   (T) 0-200 ms after stimulus onset
-  #
-  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
-  # from the median
-  #
-  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
-  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
-  # time-based exclusion is nonsensical for transformed data sets.
-
-  # create a list that contains the basic data frame of the n-back data for each of the pipelines
-
-  pipelines_data <- replicate(63, data_nback, simplify = FALSE)
-  pipelines_data <- setNames(pipelines_data, c("AARN","AAR2","AAR5","AAR3","AARO","AART",
-                                               "AALN","AAL2","AAL5","AAL3",
-                                               "AAIN","AAI2","AAI5","AAI3",
-                                               "AASN","AAS2","AAS5","AAS3",
-                                               "AWR2","AWR5","AWR3",
-                                               "AWLN","AWL2","AWL5","AWL3",
-                                               "AWIN","AWI2","AWI5","AWI3",
-                                               "AWSN","AWS2","AWS5","AWS3",
-                                               "WWR2","WWR5","WWR3",
-                                               "WWLN","WWL2","WWL5","WWL3",
-                                               "WWIN","WWI2","WWI5","WWI3",
-                                               "WWSN","WWS2","WWS5","WWS3",
-                                               "WAR2","WAR5","WAR3",
-                                               "WALN","WAL2","WAL5","WAL3",
-                                               "WAIN","WAI2","WAI5","WAI3",
-                                               "WASN","WAS2","WAS5","WAS3"))
-
-  for (i in 1:length(pipelines_data)) {
-
-    # extract the name of the current data frame
-
-    pipeline_name <- strsplit(names(pipelines_data)[i], "")
-
-    # the first decision is whether transformations and exclusions will be applied across/within subjects/levels
-
-    if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "A") {
-
-          # the second decision is the type of transformation, depending on the third letter in the data frame name
-
-          if (pipeline_name[[1]][3] == "L") {
-
-            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-          } else if (pipeline_name[[1]][3] == "I") {
-
-            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-          } else if (pipeline_name[[1]][3] == "S") {
-
-            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-          }
-
-          # compute median and median absolute deviation
-
-          pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
-          pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
-
-          # the third decision is the outlier exclusion
-
-          if (pipeline_name[[1]][4] == "2") {
-
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2 * pipemad)
-                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2 * pipemad))), ]
-
-          } else if (pipeline_name[[1]][4] == "5") {
-
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2.5 * pipemad)
-                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2.5 * pipemad))), ]
-          } else if (pipeline_name[[1]][4] == "3") {
-
-            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 3 * pipemad)
-                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 3 * pipemad))), ]
-          }
-
-    } else if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "W") {
-
-        # apply the transformations and exclusions across subjects but within levels
-
-        for (x in 1:4) {
-
-            # the second decision is the type of transformation, depending on the third letter in the data frame name
-
-            if (pipeline_name[[1]][3] == "L") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-            } else if (pipeline_name[[1]][3] == "I") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-            } else if (pipeline_name[[1]][3] == "S") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-            }
-
-            # compute median and median absolute deviation
-
-            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
-            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
-
-            # the third decision is the outlier exclusion
-
-            if (pipeline_name[[1]][4] == "2") {
-
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-
-            } else if (pipeline_name[[1]][4] == "5") {
-
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-
-            } else if (pipeline_name[[1]][4] == "3") {
-
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-            }
-        }
-
-    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "W") {
-
-        # apply the transformations and exclusions within subjects and within levels
-
-        for (x in 1:4) {
-
-          for (y in 1:length(table(pipelines_data[[i]]$subject))) {
-
-            # save the name of the subject as a temporary variable
-
-            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]
-
-            # the second decision is the type of transformation, depending on the third letter in the data frame name
-
-            if (pipeline_name[[1]][3] == "L") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                       pipelines_data[[i]]$subject == pipesubject] <-
-                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
-                                       pipelines_data[[i]]$subject == pipesubject] <-
-                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
-
-            } else if (pipeline_name[[1]][3] == "I") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                       pipelines_data[[i]]$subject == pipesubject] <-
-                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
-                                       pipelines_data[[i]]$subject == pipesubject] <-
-                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
-
-            } else if (pipeline_name[[1]][3] == "S") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                       pipelines_data[[i]]$subject == pipesubject] <-
-                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
-                                       pipelines_data[[i]]$subject == pipesubject] <-
-                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
-            }
-
-            # compute median and median absolute deviation
-
-            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
-            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
-
-            # the third decision is the outlier exclusion
-
-            if (pipeline_name[[1]][4] == "2") {
-
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-
-            } else if (pipeline_name[[1]][4] == "5") {
-
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-
-            } else if (pipeline_name[[1]][4] == "3") {
-
-              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-            }
-          }
-        }
-
-    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "A") {
-
-      # apply the transformations and exclusions within subjects but across levels
-
-        for (y in 1:length(table(pipelines_data[[i]]$subject))) {
-
-            # save the name of the subject as a temporary variable
-
-            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]
-
-            # the second decision is the type of transformation, depending on the third letter in the data frame name
-
-            if (pipeline_name[[1]][3] == "L") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-            } else if (pipeline_name[[1]][3] == "I") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-            } else if (pipeline_name[[1]][3] == "S") {
-
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
-                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
-              pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
-                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
-
-            }
-
-            # compute median and median absolute deviation
-
-            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
-            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
-
-            # the third decision is the outlier exclusion
-
-            if (pipeline_name[[1]][4] == "2") {
-
-              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-
-            } else if (pipeline_name[[1]][4] == "5") {
-
-              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-
-            } else if (pipeline_name[[1]][4] == "3") {
-
-              ifelse(length(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
-                     pipelines_data[[i]] <-
-                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
-                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
-                     pipelines_data[[i]] <- pipelines_data[[i]])
-            }
-        }
-
-    }
-
-    # the time-based exclusions are done outside of the A/A-A/W-W/W-W/A-conditions because they are independent of dimension:
-
-    # exclude RTs faster than 100 or 200 ms after stimulus onset if the fourth letter in the data frame name is an "O" or a "T"
-    # also making sure that there are even any trials below 100/200 ms, otherwise you get an error message
-
-    if (pipeline_name[[1]][4] == "O") {
-
-      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ]) > 0,
-             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.1 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ],
-             pipelines_data[[i]] <- pipelines_data[[i]])
-
-    } else if (pipeline_name[[1]][4] == "T") {
-
-      ifelse(nrow(pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ]) > 0,
-             pipelines_data[[i]] <- pipelines_data[[i]][-c(which(pipelines_data[[i]]$rt < 0.2 & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1)), ],
-             pipelines_data[[i]] <- pipelines_data[[i]])
-
-    }
-
-  }
-
-```
-
-```{r pipelinesdprime, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # calculate d' for every pipeline because it depends on the total number of target and non-target trials
-
-  for (j in 1:length(pipelines_data)) {
-
-    # compute index of rows in which the levels change
-
-    levelindex <- c(1,which(pipelines_data[[j]]$level != dplyr::lag(pipelines_data[[j]]$level)),nrow(pipelines_data[[j]]))
-
-    # set up empty data frame for the loop to feed into
-
-    dprime <- data.frame(subject = character(), level = double(), hitrate = double(), falsealarmrate = double())
-
-    # calculate hits and false alarms per participant
-
-    for (i in 1:(length(levelindex)-1)) {
-
-      # set the number of targets and non-targets
-      num_targets <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
-      num_nontargets <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0))
-
-      hits <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
-                             pipelines_data[[j]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
-      falsealarms <- length(which(pipelines_data[[j]]$response[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
-                             pipelines_data[[j]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
-      newdata <- data.frame(subject = pipelines_data[[j]]$subject[levelindex[i]],
-                            level = pipelines_data[[j]]$level[levelindex[i]],
-                            hitrate = hits/num_targets,
-                            falsealarmrate = falsealarms/num_nontargets)
-      dprime <- rbind(dprime, newdata)
-
-    }
-
-    # z-transform the hit rate and the false alarm rate
-
-    dprime$hitrate.z = NA
-    dprime$falsealarmrate.z = NA
-
-    for (i in 1:4) {
-
-      dprime$hitrate.z[which(dprime$level == i)]        <- scale(dprime$hitrate[which(dprime$level == i)])
-      dprime$falsealarmrate.z[which(dprime$level == i)] <- scale(dprime$falsealarmrate[which(dprime$level == i)])
-
-    }
-
-    # calculate d'
-
-    dprime$d <- dprime$hitrate.z - dprime$falsealarmrate.z
-
-    # feed d# trialwise into the pipeline data frame
-
-    for (i in 1:nrow(pipelines_data[[j]])) {
-
-      pipelines_data[[j]]$dprime[i] <- dprime$d[dprime$subject == pipelines_data[[j]]$subject[i] & dprime$level == pipelines_data[[j]]$level[i]]
-
-    }
-  }
-
-```
-
-```{r Hypothesis1a, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # H1a: The signal detection measure d’ declines with increasing n-back level.
-
-  # repeated measures ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
-
-      # make a temporary copy of the data frame without 1-back
-
-      h1a_data <- pipelines_data[["AARN"]][pipelines_data[["AARN"]]$level != 1, ]
-      h1a_data <- unique(h1a_data[ ,c("subject","level","dprime")])
-      h1a_data$level <- as.factor(h1a_data$level)
-
-      # calculate ANOVA
-
-      hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
-                                           dv = "dprime",
-                                           id = "subject",
-                                           within = "level",
-                                           type = 3,
-                                           include_aov = TRUE)
-
-      # obtain estimated marginal means for ANOVA model
-
-      hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
-                                  specs = "level")
-
-      # calculate pairwise comparisons on estimated marginal means
-
-      hypothesis1a_contrasts <- as.data.frame(pairs(hypothesis1a_emm))
-
-  # get Bayes factors
-
-  hypothesis1a_BF <- anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
-  hypothesis1a_contrasts$BF10 <- c(extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-
-  # get effect size and confidence interval
-
-  hypothesis1a_contrasts <- cbind(hypothesis1a_contrasts,
-                                  format(t_to_eta2(t = hypothesis1a_contrasts$t.ratio, df_error = hypothesis1a_contrasts$df, ci = 0.95), digits = 2))
-
-  # rename contrasts and column names
-
-  colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)
-
-  # remove the temporary variable
-
-  remove(h1a_data)
-
-```
-
-```{r Hypothesis1b, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # H1b: Reaction time increases with increasing n-back level.
-
-  # set up empty data frame for the loop to feed into
-
-  rt <- data.frame(subject = character(), level = double(), medianrt = double())
-
-  # compute index of rows in which the levels change
-
-  levelindex <- c(1,which(pipelines_data[["AARO"]]$level != dplyr::lag(pipelines_data[["AARO"]]$level)),nrow(pipelines_data[["AARO"]]))
-
-  # calculate median reaction time per participant per level
-
-  for (i in 1:(length(levelindex)-1)) {
-
-    medianrt <- median(pipelines_data[["AARO"]]$rt[which(pipelines_data[["AARO"]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
-                                 +(levelindex[i]-1)], na.rm = TRUE)
-
-    newdata <- data.frame(subject = pipelines_data[["AARO"]]$subject[levelindex[i]],
-                          level = pipelines_data[["AARO"]]$level[levelindex[i]],
-                          medianrt = medianrt)
-    rt <- rbind(rt, newdata)
-
-  }
-
-  # ANOVA with three linear contrasts, contrasting the median rt of two n-back levels (2,3,4) at a time
-
-      # make a temporary copy of the data frame without 1-back
-
-      h1b_data <- rt[rt$level != 1,]
-      h1b_data$level <- as.factor(h1b_data$level)
-
-      # calculate ANOVA
-
-      hypothesis1b_rmanova <- afex::aov_ez(data = h1b_data,
-                                           dv = "medianrt",
-                                           id = "subject",
-                                           within = "level",
-                                           type = 3,
-                                           include_aov = TRUE)
-
-      # obtain estimated marginal means for ANOVA model
-
-      hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
-                                  specs = "level")
-      # calculate pairwise comparisons on estimated marginal means
-
-      hypothesis1b_contrasts <- as.data.frame(pairs(hypothesis1b_emm))
-
-  # get Bayes factors
-
-  hypothesis1b_BF <- anovaBF(formula = medianrt ~ level, data = h1b_data, progress = FALSE)
-  hypothesis1b_contrasts$BF10 <- c(extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 3],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 2], y = h1b_data$medianrt[h1b_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1b_data$medianrt[h1b_data$level == 3], y = h1b_data$medianrt[h1b_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-
-  # get effect size and confidence interval
-
-  hypothesis1b_contrasts <- cbind(hypothesis1b_contrasts,
-                                  format(t_to_eta2(t = hypothesis1b_contrasts$t.ratio, df_error = hypothesis1b_contrasts$df, ci = 0.95), digits = 2))
-
-  # rename contrasts and column names
-
-  colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
-
-  # remove the temporary variable
-
-  remove(h1b_data, rt)
-
-```
-
-```{r Hypothesis1c, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # H1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
-
-  # set up empty data frame for the loop to feed into
-
-  data_ntlx <- data.frame(subject = character(), level = double(),
-                          mental = double(), physical = double(), time = double(),
-                          performance = double(), effort = double(), frustration = double())
-
-  # feed NASA-TLX data per participant per level into data frame
-
-  for (i in c(1:5,7:(length(setindex)-1))) { # we exclude the sixth subject (ID F30T02) here, because their NTLX data for n = 1 is missing
-
-    for (j in 1:4) {
-
-      newdata <- data.frame(subject = data_quest$subject[setindex[i]],
-                            level = j,
-                            mental = data_quest$nasa_tlx_01[setindex[i]+j+2],
-                            physical = data_quest$nasa_tlx_02[setindex[i]+j+2],
-                            time = data_quest$nasa_tlx_03[setindex[i]+j+2],
-                            performance = data_quest$nasa_tlx_04[setindex[i]+j+2],
-                            effort = data_quest$nasa_tlx_05[setindex[i]+j+2],
-                            frustration = data_quest$nasa_tlx_06[setindex[i]+j+2])
-      data_ntlx <- rbind(data_ntlx, newdata)
-    }
-  }
-
-  # six ANOVAs with six linear contrasts, contrasting the subscale scores of two n-back levels (1,2,3,4) at a time
-
-      # make a temporary copy of the NASA-TLX data frame
-
-      h1c_data <- data_ntlx
-      h1c_data$level <- as.factor(h1c_data$level)
-
-      # calculate ANOVAs
-
-      hypothesis1c_mental_rmanova <- afex::aov_ez(data = h1c_data,
-                                                  dv = "mental", id = "subject", within = "level",
-                                                  type = 3, include_aov = TRUE)
-      hypothesis1c_physical_rmanova <- afex::aov_ez(data = h1c_data,
-                                                  dv = "physical", id = "subject", within = "level",
-                                                  type = 3, include_aov = TRUE)
-      hypothesis1c_time_rmanova <- afex::aov_ez(data = h1c_data,
-                                                  dv = "time", id = "subject", within = "level",
-                                                  type = 3, include_aov = TRUE)
-      hypothesis1c_performance_rmanova <- afex::aov_ez(data = h1c_data,
-                                                  dv = "performance", id = "subject", within = "level",
-                                                  type = 3, include_aov = TRUE)
-      hypothesis1c_effort_rmanova <- afex::aov_ez(data = h1c_data,
-                                                  dv = "effort", id = "subject", within = "level",
-                                                  type = 3, include_aov = TRUE)
-      hypothesis1c_frustration_rmanova <- afex::aov_ez(data = h1c_data,
-                                                  dv = "frustration", id = "subject", within = "level",
-                                                  type = 3, include_aov = TRUE)
-
-      # obtain estimated marginal means for ANOVA model and
-      # calculate pairwise comparisons on estimated marginal means
-
-      hypothesis1c_emm <- emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
-      hypothesis1c_mental_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
-
-      hypothesis1c_emm <- emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
-      hypothesis1c_physical_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
-
-      hypothesis1c_emm <- emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
-      hypothesis1c_time_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
-
-      hypothesis1c_emm <- emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
-      hypothesis1c_performance_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
-
-      hypothesis1c_emm <- emmeans(object = hypothesis1c_effort_rmanova$aov, specs = "level")
-      hypothesis1c_effort_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
-
-      hypothesis1c_emm <- emmeans(object = hypothesis1c_frustration_rmanova$aov, specs = "level")
-      hypothesis1c_frustration_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
-
-  # get Bayes factors
-
-  hypothesis1c_mental_BF <- anovaBF(formula = mental ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_mental_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 2],
-                                                            progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 1], y = h1c_data$mental[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 2], y = h1c_data$mental[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$mental[h1c_data$level == 3], y = h1c_data$mental[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-  hypothesis1c_physical_BF <- anovaBF(formula = physical ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_physical_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 2],
-                                                              progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 1], y = h1c_data$physical[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-  hypothesis1c_time_BF <- anovaBF(formula = time ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_time_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 2],
-                                                          progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 1], y = h1c_data$time[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 2], y = h1c_data$time[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$time[h1c_data$level == 3], y = h1c_data$time[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-  hypothesis1c_performance_BF <- anovaBF(formula = performance ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_performance_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 2],
-                                                                 progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 1], y = h1c_data$performance[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 2], y = h1c_data$performance[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$performance[h1c_data$level == 3], y = h1c_data$performance[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-  hypothesis1c_effort_BF <- anovaBF(formula = effort ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_effort_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2],
-                                                            progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 2], y = h1c_data$effort[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-  hypothesis1c_frustration_BF <- anovaBF(formula = frustration ~ level, data = h1c_data, progress = FALSE)
-  hypothesis1c_frustration_contrasts$BF10 <- c(extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 2],
-                                                                 progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 1], y = h1c_data$frustration[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 2], y = h1c_data$frustration[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h1c_data$frustration[h1c_data$level == 3], y = h1c_data$frustration[h1c_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-
-  # get effect sizes and confidence intervals
-
-  hypothesis1c_mental_contrasts <- cbind(hypothesis1c_mental_contrasts,
-                                         format(t_to_eta2(t = hypothesis1c_mental_contrasts$t.ratio,
-                                                          df_error = hypothesis1c_mental_contrasts$df, ci = 0.95), digits = 2))
-
-  hypothesis1c_physical_contrasts <- cbind(hypothesis1c_physical_contrasts,
-                                         format(t_to_eta2(t = hypothesis1c_physical_contrasts$t.ratio,
-                                                          df_error = hypothesis1c_physical_contrasts$df, ci = 0.95), digits = 2))
-
-  hypothesis1c_time_contrasts <- cbind(hypothesis1c_time_contrasts,
-                                         format(t_to_eta2(t = hypothesis1c_time_contrasts$t.ratio,
-                                                          df_error = hypothesis1c_time_contrasts$df, ci = 0.95), digits = 2))
-
-  hypothesis1c_effort_contrasts <- cbind(hypothesis1c_effort_contrasts,
-                                         format(t_to_eta2(t = hypothesis1c_effort_contrasts$t.ratio,
-                                                          df_error = hypothesis1c_effort_contrasts$df, ci = 0.95), digits = 2))
-
-  hypothesis1c_frustration_contrasts <- cbind(hypothesis1c_frustration_contrasts,
-                                         format(t_to_eta2(t = hypothesis1c_frustration_contrasts$t.ratio,
-                                                          df_error = hypothesis1c_frustration_contrasts$df, ci = 0.95), digits = 2))
-
-  hypothesis1c_performance_contrasts <- cbind(hypothesis1c_performance_contrasts,
-                                         format(t_to_eta2(t = hypothesis1c_performance_contrasts$t.ratio,
-                                                          df_error = hypothesis1c_performance_contrasts$df, ci = 0.95), digits = 2))
-
-  # rename columns and contrasts
-
-  colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
-  colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)
-  colnames(hypothesis1c_performance_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1c_performance_contrasts$Contrast <- gsub("X", "", hypothesis1c_performance_contrasts$Contrast)
-  colnames(hypothesis1c_effort_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1c_effort_contrasts$Contrast <- gsub("X", "", hypothesis1c_effort_contrasts$Contrast)
-  colnames(hypothesis1c_frustration_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1c_frustration_contrasts$Contrast <- gsub("X", "", hypothesis1c_frustration_contrasts$Contrast)
-  colnames(hypothesis1c_time_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis1c_time_contrasts$Contrast <- gsub("X", "", hypothesis1c_time_contrasts$Contrast)
-
-  # remove the temporary variable
-
-  remove(h1c_data, hypothesis1c_emm)
-
-```
-
-```{r Hypothesis2a, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # H2a: Subjective values decline with increasing n-back level.
-
-  # ANOVA with six linear contrasts, contrasting the SVs of two n-back levels (1,2,3,4) at a time
-
-  # make a temporary copy of the data frame
-
-  h2a_data <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
-  h2a_data$level <- as.factor(h2a_data$level)
-
-  # calculate ANOVA
-
-  hypothesis2a_rmanova <- afex::aov_ez(data = h2a_data,
-                                       dv = "sv", id = "subject", within = "level",
-                                       type = 3, include_aov = TRUE)
-
-  # obtain estimated marginal means for ANOVA model
-
-  hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
-                              specs = "level")
-
-  # calculate pairwise comparisons on estimated marginal means
-
-  hypothesis2a_contrasts <- as.data.frame(pairs(hypothesis2a_emm))
-
-  # get Bayes factors
-
-  hypothesis2a_BF <- anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
-  hypothesis2a_contrasts$BF10 <- c(extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf,
-                                 extractBF(ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4],
-                                                   progress = FALSE, paired = TRUE))$bf)
-
-  # get effect size and confidence intervals
-
-  hypothesis2a_contrasts <- cbind(hypothesis2a_contrasts,
-                                  format(t_to_eta2(t = hypothesis2a_contrasts$t.ratio, df_error = hypothesis2a_contrasts$df, ci = 0.95), digits = 2))
-
-  # rename columns and contrasts
-
-  colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-  hypothesis2a_contrasts$Contrast <- gsub("X", "", hypothesis2a_contrasts$Contrast)
-
-  # remove the temporary variable
-
-  remove(h2a_data)
-
-```
-
-```{r Hypothesis2bc, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
-
-  # H2b: Subjective values decline with increasing n-back level, even after controlling for declining task
-  # performance measured by signal detection d’ and reaction time.
-
-  # H2c: SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
-
-  # detach afex in order to use lmerTest
-  detach("package:afex", unload = TRUE)
-
-  # get all relevant variables -------------------------------------------------
-
-  h2b_data <- pipelines_data[["AARO"]]
-
-  # get subset for MLM without RT = NA
-
-  h2b_data <- droplevels(subset(h2b_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
-                               subset = !is.na(rt)
-                               & level > 1)) #FIXME
-
-  # center predictors ----------------------------------------------------------
-
-  ## center level 1 predictors
-  # two ways: centering at the grand mean (CGM) vs. centering within cluster (CWC) = group mean centering
-  # level 1 predictor (SV) is of substantive interest
-  # > CWC
-
-  # dprime
-  h2b_data$dprime.cwc <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-
-  # RT
-  h2b_data$rt.cwc <- h2b_data$rt - (ave(h2b_data$rt, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-
-  # level
-  h2b_data$level.cwc <- h2b_data$level - (ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-
-  # correct 
-  h2b_data$correct.cwc <- h2b_data$correct - (ave(h2b_data$correct, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-
-  # postcorrect
-  h2b_data$postcorrect.cwc <- h2b_data$postcorrect - (ave(h2b_data$postcorrect, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-
-  ## level 2 predictor
-  # > CGM
-
-  # NFC
-  h2b_data$nfc.cgm <- scale(h2b_data$nfc, scale = F)
-
-  # null model -----------------------------------------------------------------
-  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
-                 data = h2b_data,
-                 REML = T)
-
-  # intraclass correlation (ICC)
-  var_m0_h2b <- as.data.frame(VarCorr(m0_h2b))
-  icc_h2b <- var_m0_h2b$vcov[1] / (var_m0_h2b$vcov[1] + var_m0_h2b$vcov[2])
-
-  # random slopes model --------------------------------------------------------
-
-  ## maximal model ---- 
-  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
-                 data = h2b_data,
-                 REML = T) # parameters estimated by restricted log-likelihood maximization
-
-  ## plot model fit of the final model ----
-  m1_h2b_fit <- plot_model(m1_h2b, type = "diag")
-
-  # get pseudo-r-squared -------------------------------------------------------
-
-  ## for the whole model
-  h2b_total_r2 <- r.squaredGLMM(m1_h2b, pj2014 = T)
-
-  ## H2b: n-back level
-  # model without effect
-  m1_h2b_without <- lmer(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
-                         data = h2b_data,
-                         REML = T)
-  # calculate R²
-  h2b_without_r2 <- r.squaredGLMM(m1_h2b_without, pj2014 = T)
-
-  # calculate f² with conditional R²
-  h2b_r2 <- (h2b_total_r2[1,2] - h2b_without_r2[1,2]) / (1 - h2b_total_r2[1,2])
-
-  ## H2c: NFC score
-  m1_h2c_without <- lmer(sv ~ level.cwc + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
-                         data = h2b_data,
-                         REML = T)
-  # calculate R²
-  h2c_without_r2 <- r.squaredGLMM(m1_h2c_without, pj2014 = T)
-
-  # calculate f² with conditional R²
-  h2c_r2 <- (h2b_total_r2[1,2] - h2c_without_r2[1,2]) / (1 - h2b_total_r2[1,2])
-
-  # get Bayes factors ----------------------------------------------------------
-
-  # the random factor needs to be a factor
-  h2b_data$subject <- factor(h2b_data$subject)
-
-  # H2b
-  h2b_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
-  h2b_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
-  h2b_BF <- h2b_full_BF / h2b_null_BF
-
-  # H2c
-  h2c_full_BF <- lmBF(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
-  h2c_null_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                      data = h2b_data, whichRandom = 'subject', progress = FALSE)
-  h2c_BF <- h2c_full_BF / h2c_null_BF
-
-  # prepare MLM results for reporting ------------------------------------------
-
-  # get random and fixed effects
-  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
-  m1_h2b.fixef <- summary(m1_h2b)$coefficients
-
-  # prepare table
-  h2b_result.table <- as.data.frame(cbind(row.names(m1_h2b.fixef[-c(6,7),]), 
-                                          m1_h2b.fixef[-c(6,7),c(1, 2, 5)]))
-  h2b_result.table$ranef.sd <- NA
-  h2b_result.table$ranef.sd[c(1,2)] <- m1_h2b.ranef$sdcor[c(1,2)]
-
-  colnames(h2b_result.table)[1] <- "Parameter"
-  colnames(h2b_result.table)[2] <- "Beta"
-  colnames(h2b_result.table)[3] <- "$SE$"
-  colnames(h2b_result.table)[4] <- "$p$-value"
-  colnames(h2b_result.table)[5] <- "Random Effects (SD)"
-
-  row.names(h2b_result.table) <- NULL
-  h2b_result.table$Parameter[1:6] <- c("Intercept", "n-back level", "NFC", "d'", "RT", "level x NFC")
-
-  h2b_result.table[2:5] <- lapply(h2b_result.table[2:5], as.numeric)
-  h2b_result.table[c(2,3,5)] <- round(h2b_result.table[c(2,3,5)], digits = 2)
-  h2b_result.table[4] <- round(h2b_result.table[4], digits = 3)
-
-  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.01)] <- 
-    paste0(h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.01)],"*")
-  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.05)] <- 
-    paste0(h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.05)],"*")
-  h2b_result.table$ `$p$-value`[which(h2b_result.table$ `$p$-value`<.001)] <- 
-    paste0("<.001***")
-
-  h2b_result.table$ `Random Effects (SD)`[3:6] <- paste0("")
-
-  table_1 <-
-    kbl(h2b_result.table,
+# Methods
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
+The paradigm was written and presented using *Psychopy* [@Peirce2019].
+We used *R* with *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor* [@Morey2021] for all our analyses.
+
+## Ethics information
+
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
+Prior to testing, written informed consent will be obtained.
+Participants will receive 30€ in total or course credit for participation.
+
+## Pilot data
+
+The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
+One participant's data was removed because they misunderstood the instruction.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
+The results showed increases in subjective and objective task load measures with higher *n*-back level.
+Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
+A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
+The specification curve analysis showed that this pattern was true for all 63 pipelines.
+Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
+All results are detailed in the Supplementary Material.
+
+## Design
+
+Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE* [@Greiner2015].
+Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
+NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
+The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
+Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session. <!-- again: add ref. -->
+A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
+In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
+The paradigm starts with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
+To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
+After each level, participants fill out the NASA-TLX on a tablet.
+Then, they complete the effort discounting procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
+Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
+This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
+The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
+The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+
+## Sampling plan
+
+Sample size determination was mainly based on the results of the analyses of Westbrook et al. [-@Westbrook2013] (see [Design Table](#DesignTableSection)).
+As there was no prior evidence on the magnitude of an interaction between *n*-back level and NFC, we assumed a small to medium effect size of $f=.175$.
+Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] for a repeated measures ANOVA with within-between interaction indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
+The power analyses of all other hypotheses yielded smaller necessary sample sizes.
+To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 80 participants.
+
+## Analysis plan
+
+Data collection and analysis will not be performed blind to the conditions of the experiments.
+We aim to conduct all analysis as described in Westbrook et al.
+[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
+The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
+Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
+Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
+Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
+To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
+Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
+Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
+To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
+For each effort discounting round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
+This value is the result of dividing the first adjustment of 0.50€ by 2 five times, once in each effort discounting round.
+Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
+An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
+Estimated marginal means will be used for the paired contrasts of each rmANOVA, including Tukey method for *p*-value adjustment.
+
+To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package [@Kuznetsova2017]. 
+We will apply restricted maximum likelihood (REML) to fit the model.
+As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
+Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor. 
+Within the model, we will control for *d'*, RT, correct, and post-correct trials.
+$$
+SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
+$$
+Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
+By this, the model yields interpretable parameter estimates. 
+We will visually inspect the residuals of the final model.
+The approximately normal distribution indicates no evidence to perform model criticism.  
+As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to Lorah [-@Lorah2018].
+Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
+To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
+To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
+The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
+The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
+
+The association of effort discounting and NFC will be examined with a regression using the $AUC$ of each participant's SVs to predict their NFC score.
+A second regression will additionally include the mean of the NASA-TLX subscales' $AUCs$ of each participant as a predictor.
+Since we do not have a fixed SV of 1 for 1-back, we cannot apply the computation of Westbrook et al.
+[-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
+Consequently, we will choose a different way of quantifying the individual degree of effort discounting.
+A classic $AUC$ cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.
+This is the opposite for the sum of the ascent between SVs.
+Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.
+
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
+
+## Data availability
+
+The data of this study can be downloaded from [osf.io/vnj8x/](https://osf.io/vnj8x/).
+
+## Code availability
+
+The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at [github.com/ChScheffel/CERED](https://github.com/ChScheffel/CERED).
+
+\newpage
+
+# References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup
+
+\newpage
+
+# Acknowledgements
+
+This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
+Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
+Applications for the centralized funds will be reviewed in May of 2022.
+Regardless of whether or not this additional funding will be granted, the study can commence immediately.
+The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+
+# Author Contributions
+
+JZ and CS conceptualized the study and its methodology, acquired funding, investigated, administered the project, and wrote the software.
+JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
+All authors reviewed, edited, and approved the final version of the manuscript.
+
+# Competing Interests
+
+The authors declare no competing interests.
+
+\newpage
+\setcounter{figure}{0}
+
+# Figures and figure Captions
+
+```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
+
+  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
+
+```
+
+*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+The grey boxes are the choice options shown to the participant.
+The participant's final reward value of the flexible level is displayed after the first arrow.
+The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice.
+The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
+
+\newpage
+
+# Design Table {#DesignTableSection}
+
+(Starts on next page)
+
+\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
+
+\newpage
+
+# Supplement
+
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+\setcounter{section}{19}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+## Results of the pilot study
+
+## Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`
+
+Paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  hypothesis1a_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+\newpage
+
+## Hypothesis 1b: Reaction time increases with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`
+
+Paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  hypothesis1b_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+\newpage
+
+## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
+
+Mental subscale ANOVA:
+
+`r apa_print(hypothesis1c_mental_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`
+
+Mental subscale paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis1c_mental_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+Physical subscale ANOVA:
+
+`r apa_print(hypothesis1c_physical_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`
+
+Physical subscale paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis1c_physical_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+Time subscale ANOVA:
+
+`r apa_print(hypothesis1c_time_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`
+
+Time subscale paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis1c_time_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+Performance subscale ANOVA:
+
+`r apa_print(hypothesis1c_performance_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`
+
+Performance subscale paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis1c_performance_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+Effort subscale ANOVA:
+
+`r apa_print(hypothesis1c_effort_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`
+
+Effort subscale paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis1c_effort_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+Frustration subscale ANOVA:
+
+`r apa_print(hypothesis1c_frustration_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`
+
+Frustration subscale paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis1c_frustration_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+\newpage
+
+## Hypothesis 2a: Subjective values decline with increasing n-back level.
+
+ANOVA:
+
+`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`
+
+Paired contrasts:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis2a_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing subjective values between n-back levels",
+  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+\newpage
+
+## Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
+
+Multi level model:
+
+```{r,echo=FALSE, message=FALSE, warning=FALSE}
+kable(h2b_result.table,
         caption = "Effects of n-back load level on subjective value controlled 
@@
              threeparttable = T)            # line breaks in the footnote
-
-  # simple slopes analysis -----------------------------------------------------
-
-  m1_h2c.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
-                    cond.int = T,                       # print conditional intercepts
-                    control.fdr = T,                    # adjust false discovery rate
-                    confint = T)                        # add confidence intervals
-
-  #create table
-  h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
-                             round(m1_h2c.ss$slopes[c(2:3)], digits = 2),
-                             c(paste0("[", round(m1_h2c.ss$slopes[1,4], digits = 2), ",", round(m1_h2c.ss$slopes[1,5], digits = 2), "]"),
-                               paste0("[", round(m1_h2c.ss$slopes[2,4], digits = 2), ",", round(m1_h2c.ss$slopes[2,5], digits = 2), "]"),
-                               paste0("[", round(m1_h2c.ss$slopes[3,4], digits = 2), ",", round(m1_h2c.ss$slopes[3,5], digits = 2), "]")),
-                             round(m1_h2c.ss$slopes[7], digits = 3),
-                             round(m1_h2c.ss$ints[c(2,3)], digits = 2))
-  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95\\% CI", "$p$-value", "Beta", "$SE$" )
-  # columns 2:5 belong to "Slopes of NFC"
-  # columns 6:7 belong to "Conditional Intercept"
-
-  h2c_ss.table$ `$p$-value`  [which(h2c_ss.table$ `$p$-value`<.01)] <- 
-    paste0(h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.01)],"*")
-  h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.05)] <- 
-    paste0(h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.05)],"*")
-  h2c_ss.table$ `$p$-value`[which(h2c_ss.table$ `$p$-value`<.001)] <- 
-    paste0("<.001***")
-
-  # remove leading zeros in the p-value column
-
-  h2c_ss.table$ `$p$-value` <- str_replace(h2c_ss.table$ `$p$-value`, "0.", ".")
-
-  table_2 <-
-    kbl(h2c_ss.table,
+```
+
+The Bayes Factor $BF10$ of the multi level model approached infinity.
+
+The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2b_total_r2[1,2], digits = 2)`.
+
+The effect size is $f^2=$ `r format(h2b_f2, digits = 2)`.
+
+\newpage
+
+## Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
+
+Simple slopes analysis:
+
+```{r,echo=FALSE, message=FALSE, warning=FALSE}
+kable(h2c_ss.table,
         caption = "Interaction between NFC and n-back load level.",
@@
              threeparttable = T)            # line breaks in the footnote
-
-  # calculate Johnson-Neyman intervals
-  h2c_jn <- johnson_neyman(model = m1_h2b, pred = level.cwc, modx = nfc.cgm, control.fdr = T)
-  h2c_jn.int <- h2c_jn$bounds
-
-  # save plot
-  h2c_jn.plot <- h2c_jn$plot
-
-  # create interaction plot
-  Figure2 <- interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                               plot.points = T, point.shape = T,
+```
+
+```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=paste("Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC.
+Slope of $1SD$ below the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[1], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[1], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[1], digits = 3), ", slope of the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[2], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[2], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[2], digits = 3), " slope of $1SD$ above the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[3], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[3], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[3], digits = 3), ".
+NFC = Need for Cognition, SD = standard deviation.", sep=""), fig.pos="H"}
+
+interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
+                               plot.points = TRUE, point.shape = TRUE,
                                x.label = "n-back level", y.label = "subjective value",
-                               legend.main = "NFC", interval = T) + theme_apa() +
+                               legend.main = "NFC", interval = TRUE) + theme_apa() +
 scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
-
-```
-
-```{r SpecificationCurveAnalysis, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
-
-  # here we repeat the multi level model with all analysis pipelines
-
-  # prepare empty data frame for the loop to feed into
-
-  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character(), BF10 = double())
-
-  # loop through the pipelines
-
-  for (i in 1:length(pipelines_data)) {
-
-    # make a temporary copy of the data frame
-
-    sca_data <- pipelines_data[[i]]
-
-    # get a subset without RT = NA
-
-    sca_data <- droplevels(subset(sca_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")], subset = !is.na(rt)))
-
-    # center the predictors
-
-        # centering the level 1 predictors (d', RT, level, correct, postcorrect) within cluster
-
-        sca_data$dprime.cwc       <- sca_data$dprime - (ave(sca_data$dprime, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-        sca_data$rt.cwc           <- sca_data$rt - (ave(sca_data$rt, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-        sca_data$level.cwc        <- sca_data$level - (ave(sca_data$level, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-        sca_data$correct.cwc      <- sca_data$correct - (ave(sca_data$correct, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-        sca_data$postcorrect.cwc  <- sca_data$postcorrect - (ave(sca_data$postcorrect, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-
-        # centering the level 2 predictor NFC at the grand mean
-
-        sca_data$nfc.cgm <- scale(sca_data$nfc, scale = F)
-
-    # define the null model
-
-    m0_sca <- lmer(sv ~ 1 + (1|subject), data = sca_data, REML = T)
-
-    # random slopes model
-
-    m1_sca <- lmer(sv ~ level.cwc * nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject),
-                   data = sca_data, REML = T)
-
-    # convert random factor to type factor
-
-    sca_data$subject <- factor(sca_data$subject)
-
-    # compute Bayes factor
-
-    sca_full_BF <- lmBF(sv ~ level.cwc + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                        data = sca_data, whichRandom = 'subject', progress = FALSE)
-    sca_null_BF <- lmBF(sv ~ 1 + nfc.cgm + dprime.cwc + rt.cwc + correct.cwc + postcorrect.cwc + subject,
-                        data = sca_data, whichRandom = 'subject', progress = FALSE)
-    sca_BF <- sca_full_BF / sca_null_BF
-
-    # combine current results and the bigger data frame
-
-    newdata <- data.frame(pipeline = c(names(pipelines_data[i]),names(pipelines_data[i])),
-                          beta = c(summary(m1_sca)$coefficients[2,1],summary(m1_sca)$coefficients[3,1]),
-                          pvalue = c(summary(m1_sca)$coefficients[2,5],summary(m1_sca)$coefficients[3,5]),
-                          predictor = c("Level", "NFC"),
-                          BF10 = c(extractBF(sca_BF)$bf, extractBF(sca_BF)$bf))
-    sca_results <- rbind(sca_results, newdata)
-
-  }
-
-```
-
-```{r SCAplot, echo=FALSE, message=FALSE, warning=FALSE, fig.show='hide'}
-
-  # add a row number and sort the data frame by the fixed effects estimate of the predictor 'level'
-
-  sca_results <- cbind(sca_results, num = rep(c(1:(nrow(sca_results)/2)), each = 2))
-  sca_results <- sca_results[order(sca_results$predictor, sca_results$beta, decreasing = TRUE), ]
-  sca_results[sca_results$predictor == "NFC", ] <- sca_results[match(sca_results$num[sca_results$predictor == "Level"],
-                                                                     sca_results$num[sca_results$predictor == "NFC"]),]
-
-  # lock it in place by turning it into a factor
-
-  sca_results$num <- factor(sca_results$num, levels = sca_results$num[sca_results$predictor == "NFC"])
-
-  # add a column to plot only points that are significant
-
-  sca_results$sign <- ifelse(sca_results$pvalue < .05, sca_results$beta, NA)
-
-  # add columns to the data frame that describe the pipeline
-
-  sca_results$Dim <- ifelse(substr(sca_results$pipeline,1,2) == "AA", 2,
-                            ifelse(substr(sca_results$pipeline,1,2) == "AW", 3,
-                                   ifelse(substr(sca_results$pipeline,1,2) == "WW", 4,
-                                          ifelse(substr(sca_results$pipeline,1,2) == "WA", 5, NA))))
-  sca_results$Trans <- ifelse(substr(sca_results$pipeline,3,3) == "R", 7,
-                              ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
-                                     ifelse(substr(sca_results$pipeline,3,3) == "L", 8,
-                                            ifelse(substr(sca_results$pipeline,3,3) == "I", 9,
-                                                   ifelse(substr(sca_results$pipeline,3,3) == "S", 10, NA)))))
-  sca_results$Excl <- ifelse(substr(sca_results$pipeline,4,4) == "N", 12,
-                             ifelse(substr(sca_results$pipeline,4,4) == "2", 13,
-                                    ifelse(substr(sca_results$pipeline,4,4) == "5", 14,
-                                           ifelse(substr(sca_results$pipeline,4,4) == "3", 15,
-                                                  ifelse(substr(sca_results$pipeline,4,4) == "O", 16, 
-                                                         ifelse(substr(sca_results$pipeline,4,4) == "T", 17, NA))))))
+```
+
+Johnson-Neyman interval: `r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`
+
+Bayes Factor: $BF10=$ `r format(extractBF(h2c_BF)$bf, digits = 2)`
+
+The effect size is $f^2=$ `r format(h2c_f2, digits = 2)`.
+
+\newpage
+
+## Specification curve analysis:
+
+```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.
+The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
+Estimates with $p<.05$ are indicated by a dot on the line.
+$N=15$.
+The lower panel shows the preprocessing steps of each corresponding pipeline.
+The $BF10$ of each pipeline's multi level model approached infinity.", fig.pos="H"}
 
@@
 
-  Figure3 <- ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
-
-```
-
-```{r Hypothesis3a, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # H3a: Subjective values positively predict individual NCS scores.
-
-  # make a temporary copy of the data frame
-
-  data_SV <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
-
-  # create an index for the rows in which the participant ID changes
-
-  subjectindex <- c(1,which(data_SV$subject != dplyr::lag(data_SV$subject)),nrow(data_SV))
-
-  # prepare empty data frame for the loop to feed into
-
-  h3_data <- data.frame(subject = character(), axauc = double())
-
-  # calculate AUC of SVs per subject
-
-  for (i in 1:(length(subjectindex)-1)) {
-
-    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
-                          axauc = auc(data_SV$level[subjectindex[i]:(subjectindex[i]+3)], data_SV$sv[subjectindex[i]:(subjectindex[i]+3)], method = "trapezoid") *
-                            ((data_SV$sv[subjectindex[i]+3] - data_SV$sv[subjectindex[i]+2]) +
-                               (data_SV$sv[subjectindex[i]+2] - data_SV$sv[subjectindex[i]+1]) +
-                               (data_SV$sv[subjectindex[i]+1] - data_SV$sv[subjectindex[i]])))
-    h3_data <- rbind(h3_data, newdata)
-
-  }
-
-  # add NFC values to data frame
-
-  for (i in 1:(nrow(h3_data))) {
-
-    h3_data$nfc[i] <- pipelines_data[["AARO"]]$nfc[pipelines_data[["AARO"]]$subject == h3_data$subject[i]]
-
-  }
-
-  # calculate linear model to estimate prediction of NFC by SVs
-
-  hypothesis3a <- summary(lm(h3_data$nfc ~ h3_data$axauc))
-
-  # get Bayes factor
-
-  hypothesis3a_BF <- regressionBF(formula = nfc ~ axauc, data = h3_data, progress = FALSE)
-
-```
-
-```{r Hypothesis3b, echo=FALSE, message=FALSE, warning=FALSE}
-
-  # H3b: NASA-TLX scores negatively predict individual NCS scores.
-
-  # create an index for the rows in which the participant ID changes
-
-  subjectindex <- c(1,which(data_ntlx$subject != dplyr::lag(data_ntlx$subject)),nrow(data_ntlx))
-
-  # prepare temporary data frame for loop to feed into
-
-  ntlx <- data.frame(subject = character(), auc_mental = double(), auc_physical = double(), auc_time = double(),
-                          auc_performance = double(), auc_effort = double(), auc_frustration = double())
-
-  # calculate AUCs per NASA-TLX subscale per participant
-
-  for (i in 1:(length(subjectindex)-1)) {
-
-    newdata <- data.frame(subject = data_ntlx$subject[subjectindex[i]],
-                          auc_mental = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
-                                           data_ntlx$mental[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
-                          auc_physical = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
-                                           data_ntlx$physical[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
-                          auc_time = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
-                                           data_ntlx$time[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
-                          auc_performance = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
-                                           data_ntlx$performance[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
-                          auc_effort = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
-                                           data_ntlx$effort[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
-                          auc_frustration = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
-                                           data_ntlx$frustration[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE))
-    ntlx <- rbind(ntlx, newdata)
-
-  }
-
-  # add column containing the average of the NASA-TLX subscale AUCs
-
-  ntlx <- cbind(ntlx, auc_ntlx = rowMeans(ntlx[ ,grep("auc", colnames(ntlx))]))
-
-  # merge data frames based on subject
-
-  h3_data <- merge(h3_data, ntlx)
-
-  # delete temporary data frame
-
-  remove(ntlx, newdata)
-
-  # compute multiple linear regression to predict NCS based on SV AUC and NASA-TLX AUC
-
-  hypothesis3b <- summary(lm(h3_data$nfc ~ h3_data$axauc + h3_data$auc_ntlx))
-
-  # get Bayes factor
-
-  hypothesis3b_BF <- regressionBF(formula = nfc ~ axauc + auc_ntlx, data = h3_data, progress = FALSE)
-
-```
-
-# Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
-The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R* with *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor* [@Morey2021] for all our analyses.
-
-## Ethics information
-
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
-Prior to testing, written informed consent will be obtained.
-Participants will receive 30€ in total or course credit for participation.
-
-## Pilot data
-
-The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
-One participant's data was removed because they misunderstood the instruction.
-Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
-The results showed increases in subjective and objective task load measures with higher *n*-back level.
-Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
-A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
-The specification curve analysis showed that this pattern was true for all 63 pipelines.
-Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
-All results are detailed in the Supplementary Material.
-
-## Design
-
-Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE* [@Greiner2015].
-Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
-NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
-Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
-The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session. <!-- again: add ref. -->
-A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
-In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
-The paradigm starts with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
-To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-After each level, participants fill out the NASA-TLX on a tablet.
-Then, they complete the effort discounting procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
-Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
-This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
-The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
-
-## Sampling plan
-
-Sample size determination was mainly based on the results of the analyses of Westbrook et al. [-@Westbrook2013] (see [Design Table](#DesignTableSection)).
-As there was no prior evidence on the magnitude of an interaction between *n*-back level and NFC, we assumed a small to medium effect size of $f=.175$.
-Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] for a repeated measures ANOVA with within-between interaction indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
-The power analyses of all other hypotheses yielded smaller necessary sample sizes.
-To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 80 participants.
-
-## Analysis plan
-
-Data collection and analysis will not be performed blind to the conditions of the experiments.
-We aim to conduct all analysis as described in Westbrook et al.
-[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
-The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
-Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
-Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
-Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
-Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
-Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
-To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each effort discounting round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
-This value is the result of dividing the first adjustment of $0.50€$ by 2 five times, once in each effort discounting round.
-Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
-An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
-Estimated marginal means will be used for the paired contrasts of each rmANOVA, including Tukey method for *p*-value adjustment.
-
-To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package [@Kuznetsova2017]. 
-We will apply restricted maximum likelihood (REML) to fit the model.
-As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor. 
-Within the model, we will control for *d'*, RT, correct, and post-correct trials.
-$$
-SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
-$$
-Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
-By this, the model yields interpretable parameter estimates. 
-We will visually inspect the residuals of the final model.
-The approximately normal distribution indicates no evidence to perform model criticism.  
-As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to <!--CK: please add https://doi.org/10.1186/s40536-018-0061-2 (after Aiken and West 1991) -->.
-<!--CK: these are the corresponding values: h2b_total_r2, h2b_r2, h2c_r2 -->
-Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
-To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
-<!--CS: Man könnte noch die Effektgröße bestimmen nach: doi: 10.1002/sim.3429 -> semi partial R²  --> 
-<!--CK: habe ich jetzt ergänzt -->
-To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
-The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
-The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
-
-The association of effort discounting and NFC will be examined with a regression using the $AUC$ of each participant's SVs to predict their NFC score.
-A second regression will additionally include the mean of the NASA-TLX subscales' $AUCs$ of each participant as a predictor.
-Since we do not have a fixed SV of 1 for 1-back, we cannot apply the "$AUC$" <!-- CK: it is the only case where "" are used -->computation of Westbrook et al.
-[-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
-Consequently, we will choose a different way of quantifying the individual degree of effort discounting.
-A classic $AUC$ cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.
-This is the opposite for the sum of the ascent between SVs.
-Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.
-
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
-<!-- hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->
-
-## Data availability
-
-The data of this study can be downloaded from [osf.io/vnj8x/](https://osf.io/vnj8x/).
-
-## Code availability
-
-The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
-<!--CK: in the knitted document it is hard to see that "Github repository" contains a link, additionally it might be good to have the link visible within the document, also in case of a print version -->
-
-\newpage
-
-# References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
-
-\newpage
-
-# Acknowledgements
-
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
-Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-Applications for the centralized funds will be reviewed in May. <!-- I would add the year -->
-Regardless of whether or not this additional funding will be granted, the study can commence immediately.
-The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-
-# Author Contributions
-
-JZ and CS conceptualized the study and its methodology, acquired funding, investigated, administered the project, and wrote the software.
-JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
-All authors reviewed, edited, and approved the final version of the manuscript.
-
-# Competing Interests
-
-The authors declare no competing interests.
-
-\newpage
-\setcounter{figure}{0}
-
-# Figures and figure Captions
-
-```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
-
-  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
-
-```
-
-*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
-The grey boxes are the choice options shown to the participant.
-The participant's final reward value of the flexible level is displayed after the first arrow.
-The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice.
-The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
-
-\newpage
-
-# Design Table {#DesignTableSection}
-
-(Starts on next page)
-
-\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
-
-\newpage
-
-# Supplement
-
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\setcounter{section}{19}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-## Results of the pilot study
-
-## Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  hypothesis1a_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 1b: Reaction time increases with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  hypothesis1b_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
-
-Mental subscale ANOVA:
-
-`r apa_print(hypothesis1c_mental_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`
-
-Mental subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_mental_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Physical subscale ANOVA:
-
-`r apa_print(hypothesis1c_physical_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`
-
-Physical subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_physical_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Time subscale ANOVA:
-
-`r apa_print(hypothesis1c_time_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`
-
-Time subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_time_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Performance subscale ANOVA:
-
-`r apa_print(hypothesis1c_performance_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`
-
-Performance subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_performance_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Effort subscale ANOVA:
-
-`r apa_print(hypothesis1c_effort_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`
-
-Effort subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_effort_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Frustration subscale ANOVA:
-
-`r apa_print(hypothesis1c_frustration_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`
-
-Frustration subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_frustration_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 2a: Subjective values decline with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis2a_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing subjective values between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
-
-Multi level model:
-
-`r table_1`
-
-The Bayes Factor $BF10$ of the multi level model approached infinity.
-
-The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2b_r2, digits = 2)`.
-
-\newpage
-
-## Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
-
-Simple slopes analysis:
-
-`r table_2`
-
-```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=paste("Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC.
-Slope of $1SD$ below the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[1], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[1], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[1], digits = 3), ", slope of the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[2], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[2], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[2], digits = 3), " slope of $1SD$ above the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[3], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[3], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[3], digits = 3), ".
-NFC = Need for Cognition, SD = standard deviation.", sep=""), fig.pos="H"}
-
-interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                               plot.points = TRUE, point.shape = TRUE,
-                               x.label = "n-back level", y.label = "subjective value",
-                               legend.main = "NFC", interval = TRUE) + theme_apa() +
-scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
-```
-
-Johnson-Neyman interval: `r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`
-
-Bayes Factor: $BF10=$ `r format(extractBF(h2c_BF)$bf, digits = 2)`
-
-The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2c_r2, digits = 2)`.
-
-\newpage
-
-## Specification curve analysis:
-
-```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.
-The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
-Estimates with $p<.05$ are indicated by a dot on the line.
-$N=15$.
-The lower panel shows the preprocessing steps of each corresponding pipeline.
-The $BF10$ of each pipeline's multi level model approached infinity.", fig.pos="H"}
-
-# create the upper panel first, which will show the estimates of 'level' and 'nfc'
-
-  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
-    geom_line(aes(group = predictor)) +
-    geom_point(data = sca_results, aes(x = num, y = sign)) +
-    geom_text(x = 3, y = -0.02, label = "NFC", size = 3) +
-    geom_text(x = 3, y = -0.13, label = "Level", size = 3) +
-    theme_classic() +
-    labs(x = NULL, y = "Fixed effects\nestimate \u03b2") +
-    scale_y_continuous(lim = c(NA,0.01)) +
-    theme(axis.text.x = element_blank(),
-          axis.line.y = element_line(size = 1, color = "black"), axis.title.y = element_text(margin = margin(r = 10)),
-          legend.position = "none")
-
-  # create the lower part of the plot that indicates the pipeline specifications
-
-  sca_lowerplot <- ggplot(data = sca_results) +
-    geom_hline(yintercept = c(1,6,11), color = "grey", size = 0.5) +
-    geom_hline(yintercept = c(2:5,7:10,12:17), color = "grey", linetype = "dashed", size = 0.2) +
-    geom_point(aes(x = num, y = Dim)) +
-    geom_point(aes(x = num, y = Trans)) +
-    geom_point(aes(x = num, y = Excl)) +
-    theme_classic() +
-    labs(x = "Analysis pipeline", y = NULL) +
-    scale_y_reverse(breaks = c(1:17), lim = c(17,0.5), labels = c(expression(bold("Dimension")),
-                                                                "Across S, across C", "Across S, within C",
-                                                                "Within S, within C", "Within S, across C",
-                                                                expression(bold("Transformation")),
-                                                                "Raw/None", "Log", "Inverse", "Square-root",
-                                                                expression(bold("Exclusion")),
-                                                                "None", "2 MAD from median", " 2.5 MAD from median",
-                                                                "3 MAD from median", "100ms after onset", "200ms after onset")) +
-    theme(axis.text.x = element_blank(), axis.title.x = element_text(margin = margin(t = 10)),
-          axis.line.y = element_line(size = 1, color = "black"),
-          legend.position = "none")
-
-  # put both plots into one
-
   ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))

### 2022-02-17 06_Paper/ER-ED/method.Rmd

@@
 Ratings_view <- data_ER %>%
-  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
+  subset(data_ER$block == "1_view_neu" | data_ER$block == "2_view_neg")
 Ratings_view$block <- as.factor(Ratings_view$block)
@@
                                            progress = FALSE)
-SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
-                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"],
+SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
+                                                                        y = Ratings_view$arousal[Ratings_view$block == "2_view_neg"],
                                                                         progress = FALSE, paired = TRUE))$bf
@@
 # rename contrast for table
-SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+SubjArousalView_con[1,1] <- "$View_{neutral} - View_{negative}$"
 

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 Afterwards they could choose, which strategy they want to use again.
-Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
+Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
 Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
 What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
-People choose a strategy that they prefer, for different, relatively well-known reasons. 
-However, nothing is revealed about the strategy that is not chosen.
+People choose a strategy that they prefer for different, relatively well-known reasons. 
+However, nothing is revealed about the strategy that is *not chosen*.
 

### 2022-02-17 06_Paper/ER-ED/method.Rmd
corrected ANOVAs

@@
   scale_x_discrete(name = "Active viewing", 
-                   limits = c("view_neu", "view_neg"),
+                   limits = c("1_view_neu", "2_view_neg"),
                    labels = c("Neutral", "Negative"))+
@@
 Ratings_reg <- data_ER %>%
-  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
+  subset(data_ER$block != "1_view_neu" & data_ER$block != "6_choice")
 Ratings_reg$block <- as.factor(Ratings_reg$block)
@@
 
-SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
+SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
                                                                          progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                          progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                          progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                          progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                          progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
+                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
+                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                          progress = FALSE, paired = TRUE))$bf)

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 The postulation of *adaptive* and *maladaptive* strategies was put into a new perspective with the concept of ER flexibility.
-Similar to other psychological domains such as attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
-In contrast, *adaptive* ER requires having a large repertoire of ER strategies to choose from [@Aldao2015] and choosing the strategy that is useful for goal achieving in a particular situation.
+Similar to other psychological domains such as attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or the use of strategies that are hindering the achievement of goals [@Aldao2015].
+In contrast, *adaptive* ER requires having a large repertoire of ER strategies to choose from [@Aldao2015] and choosing the strategy that is useful for goal achievement in a particular situation.
 This greater ER variability has been shown to be related to reduced negative affect [@Blanke2020].

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
-We assume that both aspects are set off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
+We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
 SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
-This in turn would mean that no strategy is a good choice to achieve goals.
+This in turn would mean that no strategy is a good choice to achieve ER goals.
 
 However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
-To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
+To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
 Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
@@
 [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
-Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
+Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption taht teh objectively easiest *n*-back level has the highest SV.
 In the current study, we want to use this paradigm to determine SVs of ER strategies.

### 2022-02-17 06_Paper/ER-ED/method.Rmd
corrected ANOVA

@@
 
-SubjArousalReg_con[1,1] <- "$Distancing - Distraction$"
-SubjArousalReg_con[2,1] <- "$Distancing - Suppression$"
-SubjArousalReg_con[3,1] <- "$Distancing - View_{negative}$"
-SubjArousalReg_con[4,1] <- "$Distraction - Suppression$"
-SubjArousalReg_con[5,1] <- "$Distraction - View_{negative}$"
-SubjArousalReg_con[6,1] <- "$Suppression - View_{negative}$"
+SubjArousalReg_con[1,1] <- "$View_{negative} - Distraction$"
+SubjArousalReg_con[2,1] <- "$View_{negative} - Distancing$"
+SubjArousalReg_con[3,1] <- "$View_{negative} - Suppression$"
+SubjArousalReg_con[4,1] <- "$Distraction - Distancing$"
+SubjArousalReg_con[5,1] <- "$Distraction - Suppression$"
+SubjArousalReg_con[6,1] <- "$Distancing - Suppression$"
 
@@
   scale_x_discrete(name = "Strategy", 
-                   limits = c("view_neg", "distraction", "distancing", "suppression"),
+                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                    labels = c("View", "Distraction", "Distancing", "Suppression"))+
@@
 
-SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
-                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distraction"],
+SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
+                                                                     y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
-                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
+                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "view_neg"],
-                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
+                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
-                                                                         y = Ratings_reg$effort[Ratings_reg$block == "distancing"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
+                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distraction"],
-                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
+                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "distancing"],
-                                                                         y = Ratings_reg$effort[Ratings_reg$block == "suppression"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
+                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                      progress = FALSE, paired = TRUE))$bf)
@@
 
-SubjEffort_con[1,1] <- "$Distancing - Distraction$"
-SubjEffort_con[2,1] <- "$Distancing - Suppression$"
-SubjEffort_con[3,1] <- "$Distancing - View_{negative}$"
-SubjEffort_con[4,1] <- "$Distraction - Suppression$"
-SubjEffort_con[5,1] <- "$Distraction - View_{negative}$"
-SubjEffort_con[6,1] <- "$Suppression - View_{negative}$"
+SubjEffort_con[1,1] <- "$View_{negative} - Distancing$"
+SubjEffort_con[2,1] <- "$View_{negative} - Distraction$"
+SubjEffort_con[3,1] <- "$View_{negative} - Suppression$"
+SubjEffort_con[4,1] <- "$Distraction - Distancing$"
+SubjEffort_con[5,1] <- "$Distraction - Suppression$"
+SubjEffort_con[6,1] <- "$Distancing - Suppression$"
 

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

@@
 Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
+
 ```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns.
@@
 ```
+
 ## 1.2 The present study

### 2022-02-17 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added EMG results to suppl

--- 2022-02-17 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 
-## Pilot study: Subjective arousal in the conditions "active viewing - neutral" and "active viewing - negative"
+## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"
 ANOVA:
 
-`r afex::nice(SubjArousalView_aov)%>% knitr::kable(x = .)` 
+`r afex::nice(SubjArousalView_aov) %>% knitr::kable(x = .)` 
 $BF10=$ `r round(extractBF(SubjArousalView_BF)$bf, digits = 2)`
@@
 ANOVA:
-`r afex::nice(SubjArousalReg_aov)%>% knitr::kable(x = .)`
+`r afex::nice(SubjArousalReg_aov) %>% knitr::kable(x = .)`
 $BF10=$ `r round(extractBF(SubjArousalReg_BF)$bf, digits = 2)`
@@
 ```
+## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
+*Corrugator*:
+ANOVA: 
+`r afex::nice(EMGCorrView_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGCorrView_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  EMGCorrView_con,
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of negative and neutral pictures in the condition \"active viewing\".",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
+  escape = FALSE,
+  placement = "H"
+)
+```
+*Levator*:
+ANOVA: 
+`r afex::nice(EMGLevView_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGLevView_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  EMGLevView_con,
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of negative and neutral pictures in the condition \"active viewing\".",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
+  escape = FALSE,
+  placement = "H"
+)
+```
+Figures:
+```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
+Each dot represents the corrugator activity of a single trial.
+Bold dots represent outliers.", fig.pos="H", out.width="75%"}
+
+print(FigEMGCorrViewPilot)
+```
+```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
+Each dot represents the levator activity of a single trial.
+Bold dots represent outliers.", fig.pos="H", out.width="75%"}
+
+print(FigEMGLevViewPilot)
+```
+## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
+*Corrugator*:
+ANOVA: 
+`r afex::nice(EMGCorrReg_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGCorrReg_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  EMGCorrReg_con,
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
+  escape = FALSE,
+  placement = "H"
+)
+```
+*Levator*:
+ANOVA: 
+`r afex::nice(EMGLevReg_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGLevReg_BF)$bf, digits = 2)`
+
+Paired contrasts:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  EMGLevReg_con,
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
+  escape = FALSE,
+  placement = "H"
+)
+```
+Figures:
+```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
+Each dot represents the corrugator activity of a single trial.
+Bold dots represent outliers.", fig.pos="H", out.width="75%"}
+
+print(FigEMGCorrRegPilot)
+```
+```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
+Each dot represents the levator activity of a single trial.
+Bold dots represent outliers.", fig.pos="H", out.width="75%"}
+
+print(FigEMGLevRegPilot)
+```
 ## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
 ANOVA:
-`r afex::nice(SubjEffort_aov)%>% knitr::kable(x = .)`
+`r afex::nice(SubjEffort_aov) %>% knitr::kable(x = .)`
 $BF10=$ `r round(extractBF(SubjEffort_BF)$bf, digits = 2)`

### 2022-02-17 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
deleted * in table caption

@@
   EMGCorrView_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of negative and neutral pictures in the condition \"active viewing\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
@@
   EMGLevView_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of negative and neutral pictures in the condition \"active viewing\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
@@
   EMGCorrReg_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
@@
   EMGLevReg_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update Ms.

--- 2022-02-17 06_Paper/ER-ED/method.Rmd
@@
 
-data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
-data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
-data_ER$block[data_ER$trigger == 23] <- "3_distraction"
-data_ER$block[data_ER$trigger == 24] <- "4_distancing"
-data_ER$block[data_ER$trigger == 25] <- "5_suppression"
-data_ER$block[data_ER$trigger == 26] <- "6_choice"
+for (i in 1:nrow(data_ER)) {
+
+  if (data_ER$trigger[i] == 21) {
+
+    data_ER$block[i] = "view_neu"
+
+  } else if (data_ER$trigger[i] == 22) {
+
+    data_ER$block[i] = "view_neg"
+
+  } else if (data_ER$trigger[i] == 23 ) {
+
+    data_ER$block[i] = "distraction"
+
+  } else if (data_ER$trigger[i] == 24 ) {
+
+    data_ER$block[i] = "distancing"
+
+  } else if (data_ER$trigge[i] == 25 ) {
+
+    data_ER$block[i] = "suppression"
+
+  } else if (data_ER$trigger[i] == 26) {
+
+    data_ER$block[i] = "choice"
+  }
+}
 
@@
 Ratings_view <- data_ER %>%
-  subset(data_ER$block == "1_view_neu" | data_ER$block == "2_view_neg")
+  subset(data_ER$block == "view_neu" | data_ER$block == "view_neg")
 Ratings_view$block <- as.factor(Ratings_view$block)
@@
                                            progress = FALSE)
-SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
-                                                                        y = Ratings_view$arousal[Ratings_view$block == "2_view_neg"],
+SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "view_neu"],
+                                                                        y = Ratings_view$arousal[Ratings_view$block == "view_neg"],
                                                                         progress = FALSE, paired = TRUE))$bf
@@
 # rename contrast for table
-SubjArousalView_con[1,1] <- "$View_{neutral} - View_{negative}$"
+SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"
 
@@
   geom_jitter(size = 0.4)+
-  labs(y = "Levator activity")
+  labs(y = "Corrugator activity")
 
@@
 # Bayes Factors
-EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
+EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                       data = EMG_reg,
@@
 
-EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
+EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                      progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                      progress = FALSE, paired = TRUE))$bf)
 
-EMGLevReg_con <- cbind(EMGLevReg_con,
-                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
-                                                    df_error = EMGLevReg_con$df,
+EMGCorrReg_con <- cbind(EMGCorrReg_con,
+                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
+                                                     df_error = EMGCorrReg_con$df,
                                                      ci = 0.95),digits = 2))
 
-colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 
-EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
-EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
-EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
-EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
-EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
-EMGLevReg_con[6,1] <- "$Distancing - Suppression$"
+EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
+EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
+EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
+EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
+EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
+EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
 
@@
 # figure
-FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
+FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
@@
 
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
-According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
-A complete list of all measures assessed in the study will be found at the OSF (<https://osf.io/vnj8x/>) and GitHub (github.com/ChScheffel/COG-ER-ED).
-<!-- Attention!
-OSF is still private --> All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
+The paradigm was written and presented using *Psychopy* [@Peirce2019].
+We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ...
+<!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al.
+--> for all our analyses.
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED 
+A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
+<!-- Attention! OSF is still private --> 
+## 2.1 Ethics information
 
-## 2.1 Ethics information
+<!-- So liest es sich in Josephines Ms. und so ähnlich liest es sich in publizierten NHB papers. -->
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
+Prior to testing, written informed consent will be obtained.
+Participants will receive 30€ in total or course credit for participation.
 

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 --> for all our analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED 
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
 A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 
-The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
+The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).<!-- This results in two digit numbers, with the last digit being zero.
+Perhaps use papaja::printnun(x, diguts = 1, gt1 = T) instead, this rounds up to 1 digit, but also only displays one digit (at least I hope so) -->
 Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
@@
 Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
-Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
+Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
 The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 A brief training ensures that all participants are able to implement the ER strategies.
-Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
+Next, electrodes to measure EMG <!-- Has abbrev. EMG already are been introduced? -->being attached and the ER paradigm is conducted.
 Participants receive 30.00€ or course credit as compensation.
@@
 Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
-
+<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ...
++3), the relaiability of the measures.
+-->
 ### 2.3.2 Emotion regulation paradigm

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 <!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ...
-+3), the relaiability of the measures.
++3), the reliability of the measures.
 -->
@@
 Therefore, we aim to collect data of 90 participants.
+<!-- somehow refer to the Dign Table here, where everything is detailed -->
 
@@
 
-All statistical analyses will be performed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.
+All statistical analyses will be performed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.<!-- mention the main packages used and list the helper packages in the supplement -->
 The level of significance was set to $\alpha=.05$.
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-
+<!-- perhaps alsway mention which r package will be used to run these proceudres -->
 *Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 *Effects of emotion regulation on arousal and effort* <br> To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
-To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
-To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
+To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA will be conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
+To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing will be conducted for EMG activity of *corrugator* and *levator*.
 <!-- @Anne please check!
-=) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
+=) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) will be conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
 <!-- @Anne please check!
-=) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
-Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
-Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
+=) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
+Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
 <!-- perhaps alsway mention which r package will be used to run these proceudres -->
-*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.<!-- why exactly this value?
+-->
 Second, the resulting (monetary) value will be divided by 2.00 €.
@@
 To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
-First, ER strategies will be re-coded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
 Restricted maximum likelihood (REML) will be applied to fit the model.
@@
 Würde sagen erstmal nicht, denn sonst wird es a) überladen mit Prädiktoren und b) haben wir sonst kein Maß, was meiner Meinung nach mit ALLEN SVs zusammenhängen sollte.
+Anm.
+AS: Ja, erstmal so schlank wie möglic halten.
 -->
@@
 Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
-<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? -->
+<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? AS: Mir ehrlich gesagt erstmal nicht so ... -->
 
 For each result of the analyses both, $p$-values and Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021], will be reported.
+Bayses factors are calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
+<!-- bzw welche Funktionen auch immer Du nutzt, hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->
 

### 2022-02-17 06_Paper/ER-ED/method.Rmd
Update methods EMG
I updated the paragraph on EMG

--- 2022-02-17 06_Paper/ER-ED/method.Rmd
@@
 
-data_EMG$block[data_EMG$trigger == " S 21"] <- "1_view_neu"
-data_EMG$block[data_EMG$trigger == " S 22"] <- "2_view_neg"
-data_EMG$block[data_EMG$trigger == " S 23"] <- "3_distraction"
-data_EMG$block[data_EMG$trigger == " S 24"] <- "4_distancing"
-data_EMG$block[data_EMG$trigger == " S 25"] <- "5_suppression"
-data_EMG$block[data_EMG$trigger == " S 26"] <- "6_choice"
+data_EMG$block[data_EMG$trigger == " S 21"] <- "view_neu"
+data_EMG$block[data_EMG$trigger == " S 22"] <- "view_neg"
+data_EMG$block[data_EMG$trigger == " S 23"] <- "distraction"
+data_EMG$block[data_EMG$trigger == " S 24"] <- "distancing"
+data_EMG$block[data_EMG$trigger == " S 25"] <- "suppression"
+data_EMG$block[data_EMG$trigger == " S 26"] <- "choice"
 
@@
 EMG_view <- data_EMG %>%
-  subset(data_EMG$block == "1_view_neu" | data_EMG$block == "2_view_neg")
+  subset(data_EMG$block == "view_neu" | data_EMG$block == "view_neg")
 EMG_view$block <- as.factor(EMG_view$block)
@@
                                        progress = FALSE)
-EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
-                                                                    y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
+EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "view_neu"],
+                                                                    y = EMG_view$Corr[EMG_view$block == "view_neg"],
                                                                     progress = FALSE, paired = TRUE))$bf
@@
 # rename contrast for table
-EMGCorrView_con[1,1] <- "$View_{neutral} - View_{negative}$"
+EMGCorrView_con[1,1] <- "$View_{negative} - View_{neutral}$"
 
@@
   scale_x_discrete(name = "Active viewing", 
-                   limits = c("1_view_neu", "2_view_neg"),
+                   limits = c("view_neu", "view_neg"),
                    labels = c("Neutral", "Negative"))+
@@
                                        progress = FALSE)
-EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
-                                                                   y = EMG_view$Lev[EMG_view$block == "2_view_neg"],
+EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "view_neu"],
+                                                                    y = EMG_view$Lev[EMG_view$block == "view_neg"],
                                                                     progress = FALSE, paired = TRUE))$bf
@@
 # rename contrast for table
-EMGLevView_con[1,1] <- "$View_{neutral} - View_{negative}$"
+EMGLevView_con[1,1] <- "$View_{negative} - View_{neutral}$"
 
@@
   scale_x_discrete(name = "Active viewing", 
-                   limits = c("1_view_neu", "2_view_neg"),
+                   limits = c("view_neu", "view_neg"),
                    labels = c("Neutral", "Negative"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Corrugator activity")
-
-# effect of strategy on EMG
-
-EMG_reg <- data_EMG %>%
-  subset(data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
-EMG_reg$block <- as.factor(EMG_reg$block)
-
-# corrugator
-EMGCorrReg_aov <- afex::aov_ez(data = EMG_reg,
-                              id = "ID",
-                              dv = "Corr",
-                              within = "block",
-                              fun_aggregate = mean,
-                              include_aov = TRUE)
-
-# compute posthoc tests for within measures
-EMGCorrReg_emm <- emmeans::emmeans(EMGCorrReg_aov$aov, specs = "block")
-
-EMGCorrReg_con <- as.data.frame(pairs(EMGCorrReg_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
-                                      data = EMG_reg,
-                                      progress = FALSE)
-
-EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf)
-
-EMGCorrReg_con <- cbind(EMGCorrReg_con,
-                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
-                                                     df_error = EMGCorrReg_con$df,
-                                                     ci = 0.95),digits = 2))
-
-colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-
-EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
-EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
-EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
-EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
-EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
-EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Corrugator activity")
-
-# levator
-
-EMGLevReg_aov <- afex::aov_ez(data = EMG_reg,
-                              id = "ID",
-                              dv = "Lev",
-                              within = "block",
-                              fun_aggregate = mean,
-                              include_aov = TRUE)
-
-# compute posthoc tests for within measures
-EMGLevReg_emm <- emmeans::emmeans(EMGLevReg_aov$aov, specs = "block")
-
-EMGLevReg_con <- as.data.frame(pairs(EMGLevReg_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
-                                      data = EMG_reg,
-                                      progress = FALSE)
-
-EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf)
-
-EMGCorrReg_con <- cbind(EMGCorrReg_con,
-                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
-                                                     df_error = EMGCorrReg_con$df,
-                                                     ci = 0.95),digits = 2))
-
-colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-
-EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
-EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
-EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
-EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
-EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
-EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
   geom_jitter(size = 0.4)+
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
-The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ...
-<!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al.
---> for all our analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
-A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
-<!-- Attention! OSF is still private --> 
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
+According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
+A complete list of all measures assessed in the study will be found at the OSF (<https://osf.io/vnj8x/>) and GitHub (github.com/ChScheffel/COG-ER-ED).
+<!-- Attention!
+OSF is still private --> All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
+
 ## 2.1 Ethics information
-
-<!-- So liest es sich in Josephines Ms. und so ähnlich liest es sich in publizierten NHB papers. -->
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
-Prior to testing, written informed consent will be obtained.
-Participants will receive 30€ in total or course credit for participation.
 
@@
 
-The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).<!-- This results in two digit numbers, with the last digit being zero.
-Perhaps use papaja::printnun(x, diguts = 1, gt1 = T) instead, this rounds up to 1 digit, but also only displays one digit (at least I hope so) -->
+The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
 Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
@@
 Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
-Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
+Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
 The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
@@
 A brief training ensures that all participants are able to implement the ER strategies.
-Next, electrodes to measure EMG <!-- Has abbrev. EMG already are been introduced? -->being attached and the ER paradigm is conducted.
+Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
 Participants receive 30.00€ or course credit as compensation.
@@
 Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
-<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ...
-+3), the relaiability of the measures.
--->
+
 ### 2.3.2 Emotion regulation paradigm
@@
 
-### 2.3.4 Electromyography
+### 2.3.4 Facial electromyography
 
-Two bipolar electromyograph (EMG) measures will be recorded in the region of the *corrugator supercilii* and the *levator labii* using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
-Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel will be used.
-Data will be sampled at 1000 Hz.
-To measure *corrugator EMG*, electrodes will be applied to the abraded and cleaned skin on the left *corrugator supercilii*, and to measure *levator EMG*, electrodes were applied in the region of the *levator labii*.
-The ground electrode will be placed at the left *Mastoid*.
+Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence (Bradley & Lang, 2000).
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
+The ground electrode will be placed over the left *Mastoid*.
+Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
+Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
+Impedance level will be kept below 10 kΩ. 
+Data will be sampled at 1000 Hz, filtered, rectified and integrated. 
 A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
-Afterwards, the signals will be rectified and segmented.
-EMG data will be baseline-corrected to -200 ms to 0 ms to stimulus onset.
-Last, the sampling rate is changed to 100 Hz and the AUC for the interval of 6000 ms stimulus presentation extracted for every stimulus.
-<!-- Liebe @Anne, habe das aus dem Analyzer zusammengefasst, stimmt das? -- -->
+Corrugator and Levator EMG will be analyzed during the 6 s of picture presenation.
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf. Bradley & Lang, 2000). 
+Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
+<!-- AG: insert references -->
 
@@
 To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
-<!-- @Anne please check!
-=) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
+<!-- @Anne please check! =) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine 
+<!-- AG: hier ein Check!-->
+the effects of ER strategies on the emotional facial reaction.
 <!-- @Anne please check!

### 2022-02-18 06_Paper/ER-ED/method.Rmd

@@
 
-for (i in 1:nrow(data_ER)) {
-
-  if (data_ER$trigger[i] == 21) {
-
-    data_ER$block[i] = "view_neu"
-
-  } else if (data_ER$trigger[i] == 22) {
-
-    data_ER$block[i] = "view_neg"
-
-  } else if (data_ER$trigger[i] == 23 ) {
-
-    data_ER$block[i] = "distraction"
-
-  } else if (data_ER$trigger[i] == 24 ) {
-
-    data_ER$block[i] = "distancing"
-
-  } else if (data_ER$trigge[i] == 25 ) {
-
-    data_ER$block[i] = "suppression"
-
-  } else if (data_ER$trigger[i] == 26) {
-
-    data_ER$block[i] = "choice"
-  }
-}
+data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
+data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
+data_ER$block[data_ER$trigger == 23] <- "3_distraction"
+data_ER$block[data_ER$trigger == 24] <- "4_distancing"
+data_ER$block[data_ER$trigger == 25] <- "5_suppression"
+data_ER$block[data_ER$trigger == 26] <- "6_choice"
 
@@
                                        progress = FALSE)
-EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "view_neu"],
-                                                                    y = EMG_view$Corr[EMG_view$block == "view_neg"],
+EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
+                                                                    y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
                                                                     progress = FALSE, paired = TRUE))$bf
@@
 # rename contrast for table
-EMGCorrView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+EMGCorrView_con[1,1] <- "$View_{neutral} - View_{negative}$"
 
@@
                                        progress = FALSE)
-EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "view_neu"],
-                                                                    y = EMG_view$Lev[EMG_view$block == "view_neg"],
+EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
+                                                                   y = EMG_view$Lev[EMG_view$block == "2_view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf
@@
 # rename contrast for table
-EMGLevView_con[1,1] <- "$View_{negative} - View_{neutral}$"
+EMGLevView_con[1,1] <- "$View_{neutral} - View_{negative}$"
 
@@
   scale_x_discrete(name = "Active viewing", 
-                   limits = c("view_neu", "view_neg"),
+                   limits = c("1_view_neu", "2_view_neg"),
                    labels = c("Neutral", "Negative"))+
   geom_jitter(size = 0.4)+
+  labs(y = "Levator activity")
+
+# effect of strategy on EMG
+
+EMG_reg <- data_EMG %>%
+  subset(data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
+EMG_reg$block <- as.factor(EMG_reg$block)
+
+# corrugator
+EMGCorrReg_aov <- afex::aov_ez(data = EMG_reg,
+                              id = "ID",
+                              dv = "Corr",
+                              within = "block",
+                              fun_aggregate = mean,
+                              include_aov = TRUE)
+
+# compute posthoc tests for within measures
+EMGCorrReg_emm <- emmeans::emmeans(EMGCorrReg_aov$aov, specs = "block")
+
+EMGCorrReg_con <- as.data.frame(pairs(EMGCorrReg_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
+                                      data = EMG_reg,
+                                      progress = FALSE)
+
+EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf,
+                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
+                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
+                                                                     progress = FALSE, paired = TRUE))$bf)
+
+EMGCorrReg_con <- cbind(EMGCorrReg_con,
+                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
+                                                     df_error = EMGCorrReg_con$df,
+                                                     ci = 0.95),digits = 2))
+
+colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+
+EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
+EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
+EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
+EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
+EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
+EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
   labs(y = "Corrugator activity")
+
+# levator
+
+EMGLevReg_aov <- afex::aov_ez(data = EMG_reg,
+                              id = "ID",
+                              dv = "Lev",
+                              within = "block",
+                              fun_aggregate = mean,
+                              include_aov = TRUE)
+
+# compute posthoc tests for within measures
+EMGLevReg_emm <- emmeans::emmeans(EMGLevReg_aov$aov, specs = "block")
+
+EMGLevReg_con <- as.data.frame(pairs(EMGLevReg_emm, adjust = "bonferroni"))
+
+# Bayes Factors
+EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
+                                      data = EMG_reg,
+                                      progress = FALSE)
+
+EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
+                                                                    progress = FALSE, paired = TRUE))$bf,
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
+                                                                    progress = FALSE, paired = TRUE))$bf,
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
+                                                                    progress = FALSE, paired = TRUE))$bf,
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
+                                                                    progress = FALSE, paired = TRUE))$bf,
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
+                                                                    progress = FALSE, paired = TRUE))$bf,
+                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
+                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
+                                                                    progress = FALSE, paired = TRUE))$bf)
+
+EMGLevReg_con <- cbind(EMGLevReg_con,
+                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
+                                                    df_error = EMGLevReg_con$df,
+                                                    ci = 0.95),digits = 2))
+
+colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+
+EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
+EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
+EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
+EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
+EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
+EMGLevReg_con[6,1] <- "$Distancing - Suppression$"
+
+# Figure to visualize arousal ratings
+
+# figure
+FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
+  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
+  scale_x_discrete(name = "Strategy", 
+                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
+                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
+  geom_jitter(size = 0.4)+
+  labs(y = "Levator activity")
 

### 2022-02-18 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex

@@
 Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort.
-Perceived costs of ER strategies in form of effort however, are highly subjective.
+Perceived costs of ER strategies in the form of effort, however, are highly subjective.
 Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort.
@@
 \begin{figure}
-\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/other/Paradigm_Scheme_T2} \caption{Exemplary visualisation of two response patterns.
+\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/Other/Paradigm_Scheme_T2} \caption{Exemplary visualisation of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 \begin{figure}
-\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/other/Paradigm_Scheme_T2} \caption{ }\label{fig:fig1appendix}
+\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/Other/Paradigm_Scheme_T2} \caption{ }\label{fig:fig1appendix}
 \end{figure}
@@
 \hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
-\subsection{Pilot study: Subjective arousal in the conditions ``active viewing - neutral'' and ``active viewing - negative''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
+\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
 
@@
 \midrule
-$View_{negative} - View_{neutral}$ & 129.28 & 22.07 & 15.00 & 5.86 & 0.00 & 794.78 & 0.70 & {}[0.43, 1.00]\\
+$View_{neutral} - View_{negative}$ & -129.28 & 22.07 & 15.00 & -5.86 & 0.00 & 794.78 & 0.70 & {}[0.43, 1.00]\\
 \bottomrule
@@
 \midrule
-$Distancing - Distraction$ & 4.61 & 16.14 & 45.00 & 0.29 & 1.00 & 0.26 & 1.81e-03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -20.88 & 16.14 & 45.00 & -1.29 & 1.00 & 0.27 & 0.04 & {}[0.00, 1.00]\\
-$Distancing - View_{negative}$ & 5.35 & 16.14 & 45.00 & 0.33 & 1.00 & 1.25 & 2.43e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -25.49 & 16.14 & 45.00 & -1.58 & 0.73 & 0.26 & 0.05 & {}[0.00, 1.00]\\
-$Distraction - View_{negative}$ & 0.74 & 16.14 & 45.00 & 0.05 & 1.00 & 0.77 & 4.68e-05 & {}[0.00, 1.00]\\
-$Suppression - View_{negative}$ & 26.23 & 16.14 & 45.00 & 1.63 & 0.67 & 0.52 & 0.06 & {}[0.00, 1.00]\\
+$View_{negative} - Distraction$ & -0.74 & 16.14 & 45.00 & -0.05 & 1.00 & 0.26 & 4.68e-05 & {}[0.00, 1.00]\\
+$View_{negative} - Distancing$ & -5.35 & 16.14 & 45.00 & -0.33 & 1.00 & 0.27 & 2.43e-03 & {}[0.00, 1.00]\\
+$View_{negative} - Suppression$ & -26.23 & 16.14 & 45.00 & -1.63 & 0.67 & 1.25 & 0.06 & {}[0.00, 1.00]\\
+$Distraction - Distancing$ & -4.61 & 16.14 & 45.00 & -0.29 & 1.00 & 0.26 & 1.81e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & -25.49 & 16.14 & 45.00 & -1.58 & 0.73 & 0.77 & 0.05 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & -20.88 & 16.14 & 45.00 & -1.29 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
 \bottomrule
@@
 
-\hypertarget{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{Pilot study: Subjective effort in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}
-
+\hypertarget{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
+\subsection{\texorpdfstring{Pilot study: Physiological arousal (\emph{Corrugator} and \emph{Levator} activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}{Pilot study: Physiological arousal (Corrugator and Levator activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}}\label{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
+
+\emph{Corrugator}:
 ANOVA:
@@
 \hline
-block & 2.38, 35.66 & 4388.19 & 11.13 *** & .185 & <.001\\
-\hline
-\end{tabular}
-
-\(BF10=\) 7.40
+block & 1, 15 & 1.01 & 9.70 ** & .237 & .007\\
+\hline
+\end{tabular}
+
+\(BF10=\) 6,690,401.91
 
@@
 
-\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of negative and neutral pictures in the condition "active viewing".}
 
@@
 \midrule
-$Distancing - Distraction$ & -21.00 & 20.85 & 45.00 & -1.01 & 1.00 & 59.77 & 0.02 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 20.49 & 1.27e-04 & {}[0.00, 1.00]\\
-$Distancing - View_{negative}$ & 89.72 & 20.85 & 45.00 & 4.30 & 0.00 & 33.13 & 0.29 & {}[0.12, 1.00]\\
-$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.50 & 0.03 & {}[0.00, 1.00]\\
-$Distraction - View_{negative}$ & 110.72 & 20.85 & 45.00 & 5.31 & 0.00 & 0.57 & 0.39 & {}[0.20, 1.00]\\
-$Suppression - View_{negative}$ & 88.15 & 20.85 & 45.00 & 4.23 & 0.00 & 0.26 & 0.28 & {}[0.11, 1.00]\\
+$View_{neutral} - View_{negative}$ & -1.11 & 0.36 & 15.00 & -3.11 & 0.01 & 5,019,313.20 & 0.39 & {}[0.09, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\emph{Levator}:
+ANOVA:
+
+\begin{tabular}{l|l|l|l|l|l}
+\hline
+Effect & df & MSE & F & ges & p.value\\
+\hline
+block & 1, 15 & 0.17 & 7.72 * & .162 & .014\\
+\hline
+\end{tabular}
+
+\(BF10=\) 48.44
+
+Paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of negative and neutral pictures in the condition "active viewing".}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+$View_{neutral} - View_{negative}$ & -0.40 & 0.14 & 15.00 & -2.78 & 0.01 & 41.02 & 0.34 & {}[0.05, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Figures:
+
+\begin{figure}[H]
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGCorrViewPilot-1} \caption{Corrugator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
+Each dot represents the corrugator activity of a single trial.
+Bold dots represent outliers.}\label{fig:FigEMGCorrViewPilot}
+\end{figure}
+\begin{figure}[H]
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGLevViewPilot-1} \caption{Levator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
+Each dot represents the levator activity of a single trial.
+Bold dots represent outliers.}\label{fig:FigEMGLevViewPilot}
+\end{figure}
+
+\hypertarget{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}{%
+\subsection{\texorpdfstring{Pilot study: Physiological arousal (\emph{Corrugator} and \emph{Levator} activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological arousal (Corrugator and Levator activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}
+
+\emph{Corrugator}:
+ANOVA:
+
+\begin{tabular}{l|l|l|l|l|l}
+\hline
+Effect & df & MSE & F & ges & p.value\\
+\hline
+block & 1.53, 22.98 & 1.16 & 5.71 * & .189 & .015\\
+\hline
+\end{tabular}
+
+\(BF10=\) 5,257,689.54
+
+Paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 4,962.89 & 0.19 & {}[0.05, 1.00]\\
+$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 616.63 & 0.21 & {}[0.06, 1.00]\\
+$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 11,678.82 & 0.20 & {}[0.06, 1.00]\\
+$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 0.07 & 1.78e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 0.08 & 7.22e-04 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 0.06 & 2.36e-04 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\emph{Levator}:
+ANOVA:
+
+\begin{tabular}{l|l|l|l|l|l}
+\hline
+Effect & df & MSE & F & ges & p.value\\
+\hline
+block & 2.07, 31.00 & 0.20 & 8.27 ** & .225 & .001\\
+\hline
+\end{tabular}
+
+\(BF10=\) 672,341.29
+
+Paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+$View_{negative} - Distraction$ & 0.42 & 0.13 & 45.00 & 3.24 & 0.01 & 58.02 & 0.19 & {}[0.05, 1.00]\\
+$View_{negative} - Distancing$ & 0.45 & 0.13 & 45.00 & 3.46 & 0.01 & 93.49 & 0.21 & {}[0.06, 1.00]\\
+$View_{negative} - Suppression$ & 0.62 & 0.13 & 45.00 & 4.79 & 0.00 & 6,253.91 & 0.34 & {}[0.16, 1.00]\\
+$Distraction - Distancing$ & 0.03 & 0.13 & 45.00 & 0.22 & 1.00 & 0.07 & 1.06e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 0.20 & 0.13 & 45.00 & 1.54 & 0.78 & 1.52 & 0.05 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 0.17 & 0.13 & 45.00 & 1.32 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Figures:
+
+\begin{figure}[H]
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGCorrRegPilot-1} \caption{Corrugator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
+Each dot represents the corrugator activity of a single trial.
+Bold dots represent outliers.}\label{fig:FigEMGCorrRegPilot}
+\end{figure}
+\begin{figure}[H]
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGLevRegPilot-1} \caption{Levator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
+Each dot represents the levator activity of a single trial.
+Bold dots represent outliers.}\label{fig:FigEMGLevRegPilot}
+\end{figure}
+
+\hypertarget{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
+\subsection{Pilot study: Subjective effort in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}
+
+ANOVA:
+
+\begin{tabular}{l|l|l|l|l|l}
+\hline
+Effect & df & MSE & F & ges & p.value\\
+\hline
+block & 2.38, 35.66 & 4388.19 & 11.13 *** & .185 & <.001\\
+\hline
+\end{tabular}
+
+\(BF10=\) 7.40
+
+Paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+$View_{negative} - Distancing$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
+$View_{negative} - Distraction$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
+$View_{negative} - Suppression$ & -88.15 & 20.85 & 45.00 & -4.23 & 0.00 & 33.13 & 0.28 & {}[0.11, 1.00]\\
+$Distraction - Distancing$ & 21.00 & 20.85 & 45.00 & 1.01 & 1.00 & 0.50 & 0.02 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.57 & 0.03 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 0.26 & 1.27e-04 & {}[0.00, 1.00]\\
 \bottomrule

### 2022-02-18 06_Paper/ER-ED/method.Rmd

@@
 
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
-According to the 21-word-solution, "we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@Simmons2012].
-A complete list of all measures assessed in the study will be found at the OSF (<https://osf.io/vnj8x/>) and GitHub (github.com/ChScheffel/COG-ER-ED).
-<!-- Attention!
-OSF is still private --> All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
+The paradigm was written and presented using *Psychopy* [@Peirce2019].
+We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ...
+<!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al.
+--> for all our analyses.
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
+A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
+<!-- Attention! OSF is still private --> 
+## 2.1 Ethics information
 
-## 2.1 Ethics information
+<!-- So liest es sich in Josephines Ms. und so ähnlich liest es sich in publizierten NHB papers. -->
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
+Prior to testing, written informed consent will be obtained.
+Participants will receive 30€ in total or course credit for participation.
 
@@
 Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
-
+<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ...
++3), the reliability of the measures.
+-->
 ### 2.3.2 Emotion regulation paradigm
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-
-*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+<!-- perhaps alsway mention which r package will be used to run these proceudres -->
+*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.<!-- why exactly this value?
+-->
 Second, the resulting (monetary) value will be divided by 2.00 €.

### 2022-02-18 06_Paper/ER-ED/TheoreticalBackground.Rmd
deleted sub headings

@@
 
-<!--CS: Mit dem Teil bin ich noch nicht ganz zufrieden, freue mich über Anmerkungen, wie man das evtl.
-strukturieren kann!
-AS: FInde den Teil eigentlich ganz gut gelungen, aber ich bin leider auch nicht os im Thema ER drin.
--->
 The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
@@
 
-## 1.1 ER strategy discounting
-<!-- NHB template says that there should not be subheadings in the introduction -->
 In the original study by Westbrook et al.

### 2022-02-18 06_Paper/ER-ED/method.Rmd
added comment

@@
 
-Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence (Bradley & Lang, 2000).
+Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence (Bradley & Lang, 2000). <!-- Quelle noch einfügen -->
 Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
+<!-- Quelle einfügen -->
 The ground electrode will be placed over the left *Mastoid*.

### 2022-02-18 06_Paper/ER-ED/method.Rmd

@@
 -->
+
 ### 2.3.2 Emotion regulation paradigm
@@
 A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
-Corrugator and Levator EMG will be analyzed during the 6 s of picture presenation.
+Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
 EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf. Bradley & Lang, 2000). 
@@
 Therefore, we aim to collect data of 90 participants.
-<!-- somehow refer to the Dign Table here, where everything is detailed -->
+<!-- somehow refer to the Design Table here, where everything is detailed -->
 
@@
 All statistical analyses will be performed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.<!-- mention the main packages used and list the helper packages in the supplement -->
-The level of significance was set to $\alpha=.05$.
+The level of significance will be set to $\alpha=.05$.
 
-*Effects of emotion regulation on arousal and effort* <br> To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
-To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
-To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of *corrugator* and *levator*.
-<!-- @Anne please check! =) --> A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine 
-<!-- AG: hier ein Check!-->
-the effects of ER strategies on the emotional facial reaction.
-<!-- @Anne please check!
-=) --> To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
-Greenhouse-Geisser-corrected $p$-values and degrees of freedom were reported when assumption of sphericity was violated.
-Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
+*Effects of emotion regulation on arousal, facial EMG and effort* <br> To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
+To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA  with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
+
+To examine the impact of valence on facial EMG, a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for *corrugator* and *levator* activity.
+To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for *corrugator* and *levator* activity will be conducted.
+<!-- hier werden HE across neg + neu Bedingungen angeschaut, ist das korrekt? -->
+<!-- Habe den Text oben sprachlich vereinheitlicht, weil ich es sonst schwer zu lesen fand. -->
+
+To examine the effect of ER strategies on cognitive effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
+Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
 <!-- perhaps alsway mention which r package will be used to run these proceudres -->
+
 *Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.<!-- why exactly this value?

### 2022-02-18 06_Paper/ER-ED/TheoreticalBackground.Rmd
changed unit

@@
 Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
-In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
+In this step, the same monetary value (i.e., 1 €) is assigned to both options.
 The assumption is that participants now choose the option that has the higher SV for them.
 In the next step we return to the original paradigm.
-The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
+The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
 In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.

### 2022-02-18 06_Paper/ER-ED/TheoreticalBackground.Rmd
deleted comment

@@
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
-Different strategies <!-- Ich bin immer noch nicht so richtig dahinter gekommen, was eigentlich der Unterschied zwischen strategies und tactics ist, ich meine, ich weiß, was der Unterschied zwischen einer Strategie und einer Taktik ist, aber inwiefern das in ER eine Rolle spiel, ist mir noch nicht so klar gweorden, aber ich habe auch Powers & LaBar nicht gelesen --> can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
+Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
 So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].

### 2022-02-18 06_Paper/ER-ED/method.Rmd
added info on ethics

@@
 
-<!-- So liest es sich in Josephines Ms. und so ähnlich liest es sich in publizierten NHB papers. -->
 The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
+<!-- Attention!add EK number, when approved -->
 Prior to testing, written informed consent will be obtained.
@@
 At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
-Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
-<!--JZ: Hast du ED schon als Abkürzung eingeführt?--> The second session, containing the ER paradigm, takes place exactly one week after session one.
+Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
+The second session, containing the ER paradigm, takes place exactly one week after session one.
 Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.

### 2022-02-18 06_Paper/ER-ED/TheoreticalBackground.Rmd
worked on comment: NHB uses BE
added abbr. EMG

@@
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
-Moreover it is known that ER strategies reduce physiological arousal, measured via EMG in the region of the *corrugator supercilii* [@Zaehringer2020]. 
+Moreover it is known that ER strategies reduce physiological arousal, measured via electromyography (EMG) in the region of the *corrugator supercilii* [@Zaehringer2020]. 
 So these tactics from three different strategies proved to be effective in the short term. 
@@
 Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
-Effort in particular appeared to be the main factor in ER choice behaviour <!-- chekcne pob bei NHB AE oder BE genutzt wird -->in our previous work [@Scheffel2021].
+Effort in particular appeared to be the main factor in ER choice behaviour in our previous work [@Scheffel2021].
 In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.

### 2022-02-21 06_Paper/ER-ED/Analyes_ERED.r
save workspace image

@@ -577,8 +577,12 @@ EMGLevReg_con[6,1] <- "$Distancing - Suppression$"
 # figure
 FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
   geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
+  scale_x_discrete(name = "Strategy",
                    limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
+                   labels = c("View", "Distraction", "Distancing", "Suppression")) +
+  geom_jitter(size = 0.4) +
   labs(y = "Levator activity")
+
+##################### SAVE WORKSPACE IMAGE #######################
+
+save.image(file = "Workspace_ERED.RData")

### 2022-02-21 06_Paper/ER-ED/method.Rmd
added abbr. EMG
added renv

@@
 stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
-```
-
-```{r import, echo=FALSE, message=FALSE, warning=FALSE}
-# import ER ratings and ER discounting data into lists
-
-datalist_ER = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ER.*csv', full.names = TRUE),
-                          read.csv, stringsAsFactors = FALSE, header = TRUE)
-
-datalist_ED = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ED.*csv', full.names = TRUE),
-                          read.csv, stringsAsFactors = FALSE, header = TRUE)
-
-# new empty frame to store files into
-data_ER = data.frame(ID = character(), block = character(), arousal = double(), 
-                     effort = double(), trigger = double(), trigger_reg = double())
-
-data_ED = data.frame(ID = character(), step = double(), choice = character(),
-                     LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
-
-data_choice = data.frame(ID = character(), choice = double())
-
-# store arousal and effort ratings in data_ER frame
-for (i in 1:length(datalist_ER)) {
-
-  tmp = data.frame(datalist_ER[[i]][["participant"]], 
-                   datalist_ER[[i]][["instr_1"]], 
-                   datalist_ER[[i]][["slider_arousal.response"]], 
-                   datalist_ER[[i]][["slider_effort.response"]],
-                   datalist_ER[[i]][["TriggerBlockView"]],
-                   datalist_ER[[i]][["TriggerBlockReg"]])
-  colnames(tmp) = names(data_ER)
-  tmp = tmp[(!is.na(tmp$arousal)), ]
-
-  data_ER = rbind(tmp, data_ER)
-
-}
-
-rownames(data_ER) = 1:nrow(data_ER)
-
-# loop to store trigger in one column
-
-for (i in 1:nrow(data_ER)) {
-  if (is.na(data_ER$trigger[i])) {
-    data_ER$trigger[i] = data_ER$trigger_reg[i]
-  }
-
-  if (is.na(data_ER$trigger[i])) {
-    data_ER$trigger[i] = 26
-  }
-}
-
-# delete old column
-
-data_ER$trigger_reg = NULL
-
-# loop to correct block indicator
-
-data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
-data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
-data_ER$block[data_ER$trigger == 23] <- "3_distraction"
-data_ER$block[data_ER$trigger == 24] <- "4_distancing"
-data_ER$block[data_ER$trigger == 25] <- "5_suppression"
-data_ER$block[data_ER$trigger == 26] <- "6_choice"
-
-# store ER choice in data_choice frame
-
-for (i in 1:length(datalist_ER)) {
-  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["resp_choice.keys"]])
-  colnames(tmp) = names(data_choice)
-  tmp = tmp[(!is.na(tmp$choice)), ]
-
-  data_choice = rbind(tmp, data_choice)
-}
-
-# store ED data in data_ED frame
-#for (i in 1:length(datalist_ED)) {
-
-#  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
-#                   datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
-#                   datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
-#                   datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
-#                   datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
-#                   datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
-#                   datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
-
-#  colnames(tmp) = names(data_ED)
-#  data_ED = rbind(data_ED, tmp)
-#}
-
-# import EMG data
-
-datalist_EMG <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
-                          read.table, stringsAsFactors = FALSE, header = TRUE)
-datalist_EMG_Marker <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = "*.Markers", full.names = TRUE),
-                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL, sep = ",")
-
-# new empty frame to store files into
-data_EMG = data.frame(ID = character(), trigger = double(), Corr = double(), 
-                     Lev = double())
-
-# store EMG data in data_EMG frame
-for (i in 1:length(datalist_EMG)) {
-
-  tmp = data.frame(datalist_EMG[[i]][["Filename"]], 
-                   datalist_EMG_Marker[[i]][["Description"]], 
-                   datalist_EMG[[i]][["T0T6000Corr.ASNM"]], 
-                   datalist_EMG[[i]][["T0T6000Lev.ASNM"]])
-  colnames(tmp) = names(data_EMG)
-
-  data_EMG = rbind(tmp, data_EMG)
-
-}
-
-# create variable "block"
-
-data_EMG$block[data_EMG$trigger == " S 21"] <- "1_view_neu"
-data_EMG$block[data_EMG$trigger == " S 22"] <- "2_view_neg"
-data_EMG$block[data_EMG$trigger == " S 23"] <- "3_distraction"
-data_EMG$block[data_EMG$trigger == " S 24"] <- "4_distancing"
-data_EMG$block[data_EMG$trigger == " S 25"] <- "5_suppression"
-data_EMG$block[data_EMG$trigger == " S 26"] <- "6_choice"
-
-# import questionnaire df
-
-data_quest = read.csv(here("04_RawData", "pilot", "ER-ED", "dfs", "df_quest.csv"), sep = ",")
-
-```
-
-```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
-## Subjective arousal
-
-# ANOVA subjective arousal ratings
-# View condition
-
-Ratings_view <- data_ER %>%
-  subset(data_ER$block == "1_view_neu" | data_ER$block == "2_view_neg")
-Ratings_view$block <- as.factor(Ratings_view$block)
-
-SubjArousalView_aov <- afex::aov_ez(data = Ratings_view,
-                               id = "ID",
-                               dv = "arousal",
-                               within = "block",
-                               fun_aggregate = mean,
-                               include_aov = TRUE)
-
-# compute posthoc tests for within measures
-SubjArousalView_emm <- emmeans::emmeans(SubjArousalView_aov$aov, specs = "block")
-
-SubjArousalView_con <- as.data.frame(pairs(SubjArousalView_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
-                                           data = Ratings_view,
-                                           progress = FALSE)
-SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
-                                                                        y = Ratings_view$arousal[Ratings_view$block == "2_view_neg"],
-                                                                        progress = FALSE, paired = TRUE))$bf
-
-SubjArousalView_con <- cbind(SubjArousalView_con,
-                             format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
-                                                          df_error = SubjArousalView_con$df,
-                                                          ci = 0.95),
-                                                          digits = 2))
-
-colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-# rename contrast for table
-SubjArousalView_con[1,1] <- "$View_{neutral} - View_{negative}$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Active viewing", 
-                   limits = c("1_view_neu", "2_view_neg"),
-                   labels = c("Neutral", "Negative"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Arousal Rating")
-
-# View neg and regulate conditions
-
-Ratings_reg <- data_ER %>%
-  subset(data_ER$block != "1_view_neu" & data_ER$block != "6_choice")
-Ratings_reg$block <- as.factor(Ratings_reg$block)
-
-SubjArousalReg_aov <- afex::aov_ez(data = Ratings_reg,
-                              id = "ID",
-                              dv = "arousal",
-                              within = "block",
-                              fun_aggregate = mean,
-                              include_aov = TRUE)
-
-# compute posthoc tests for within measures
-SubjArousalReg_emm <- emmeans::emmeans(SubjArousalReg_aov$aov, specs = "block")
-
-SubjArousalReg_con <- as.data.frame(pairs(SubjArousalReg_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-SubjArousalReg_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
-                                          data = Ratings_reg,
-                                          progress = FALSE)
-
-SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
-                                                                         progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
-                                                                         progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
-                                                                         progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
-                                                                         progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
-                                                                         progress = FALSE, paired = TRUE))$bf,
-                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
-                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
-                                                                         progress = FALSE, paired = TRUE))$bf)
-
-SubjArousalReg_con <- cbind(SubjArousalReg_con,
-                            format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio,
-                                                         df_error = SubjArousalReg_con$df,
-                                                         ci = 0.95),
-                                   digits = 2))
-
-colnames(SubjArousalReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-
-SubjArousalReg_con[1,1] <- "$View_{negative} - Distraction$"
-SubjArousalReg_con[2,1] <- "$View_{negative} - Distancing$"
-SubjArousalReg_con[3,1] <- "$View_{negative} - Suppression$"
-SubjArousalReg_con[4,1] <- "$Distraction - Distancing$"
-SubjArousalReg_con[5,1] <- "$Distraction - Suppression$"
-SubjArousalReg_con[6,1] <- "$Distancing - Suppression$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigSubjArousalRegPilot <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Arousal Rating")
-
-## Subjective effort
-
-SubjEffort_aov <- afex::aov_ez(data = Ratings_reg,
-                          id = "ID",
-                          dv = "effort",
-                          within = "block",
-                          fun_aggregate = mean,
-                          include_aov = TRUE)
-
-# compute posthoc tests for within measure
-SubjEffort_emm <- emmeans::emmeans(SubjEffort_aov$aov, specs = "block")
-
-SubjEffort_con <- as.data.frame(pairs(SubjEffort_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-SubjEffort_BF <- BayesFactor::anovaBF(formula = effort ~ block,
-                                           data = Ratings_reg,
-                                           progress = FALSE)
-
-SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
-                                                                     y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
-                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
-                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
-                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
-                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
-                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf)
-
-SubjEffort_con <- cbind(SubjEffort_con,
-                        format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
-                                                         df_error = SubjEffort_con$df,
-                                                         ci = 0.95),
-                               digits = 2))
-
-colnames(SubjEffort_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-
-SubjEffort_con[1,1] <- "$View_{negative} - Distancing$"
-SubjEffort_con[2,1] <- "$View_{negative} - Distraction$"
-SubjEffort_con[3,1] <- "$View_{negative} - Suppression$"
-SubjEffort_con[4,1] <- "$Distraction - Distancing$"
-SubjEffort_con[5,1] <- "$Distraction - Suppression$"
-SubjEffort_con[6,1] <- "$Distancing - Suppression$"
-
-# Figure to visualize effort ratings
-# figure
-FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Effort Rating")
-
-### EMG
-
-# effect of valence on EMG
-# corrugator
-
-EMG_view <- data_EMG %>%
-  subset(data_EMG$block == "1_view_neu" | data_EMG$block == "2_view_neg")
-EMG_view$block <- as.factor(EMG_view$block)
-
-EMGCorrView_aov <- afex::aov_ez(data = EMG_view,
-                               id = "ID",
-                               dv = "Corr",
-                               within = "block",
-                               fun_aggregate = mean,
-                               include_aov = TRUE)
-
-# compute posthoc tests for within measures
-EMGCorrView_emm <- emmeans::emmeans(EMGCorrView_aov$aov, specs = "block")
-
-EMGCorrView_con <- as.data.frame(pairs(EMGCorrView_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
-                                       data = EMG_view,
-                                       progress = FALSE)
-EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
-                                                                    y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
-                                                                    progress = FALSE, paired = TRUE))$bf
-
-EMGCorrView_con <- cbind(EMGCorrView_con,
-                         format(effectsize::t_to_eta2(t = EMGCorrView_con$t.ratio,
-                                                          df_error = EMGCorrView_con$df,
-                                                          ci = 0.95),
-                                                          digits = 2))
-
-colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-# rename contrast for table
-EMGCorrView_con[1,1] <- "$View_{neutral} - View_{negative}$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Active viewing", 
-                   limits = c("1_view_neu", "2_view_neg"),
-                   labels = c("Neutral", "Negative"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Corrugator activity")
-
-# levator
-
-EMGLevView_aov <- afex::aov_ez(data = EMG_view,
-                               id = "ID",
-                               dv = "Lev",
-                               within = "block",
-                               fun_aggregate = mean,
-                               include_aov = TRUE)
-
-# compute posthoc tests for within measures
-EMGLevView_emm <- emmeans::emmeans(EMGLevView_aov$aov, specs = "block")
-
-EMGLevView_con <- as.data.frame(pairs(EMGLevView_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
-                                       data = EMG_view,
-                                       progress = FALSE)
-EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
-                                                                   y = EMG_view$Lev[EMG_view$block == "2_view_neg"],
-                                                                   progress = FALSE, paired = TRUE))$bf
-
-EMGLevView_con <- cbind(EMGLevView_con,
-                        format(effectsize::t_to_eta2(t = EMGLevView_con$t.ratio,
-                                                     df_error = EMGLevView_con$df,
-                                                     ci = 0.95),
-                                                     digits = 2))
-
-colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-# rename contrast for table
-EMGLevView_con[1,1] <- "$View_{neutral} - View_{negative}$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Active viewing", 
-                   limits = c("1_view_neu", "2_view_neg"),
-                   labels = c("Neutral", "Negative"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Levator activity")
-
-# effect of strategy on EMG
-
-EMG_reg <- data_EMG %>%
-  subset(data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
-EMG_reg$block <- as.factor(EMG_reg$block)
-
-# corrugator
-EMGCorrReg_aov <- afex::aov_ez(data = EMG_reg,
-                              id = "ID",
-                              dv = "Corr",
-                              within = "block",
-                              fun_aggregate = mean,
-                              include_aov = TRUE)
-
-# compute posthoc tests for within measures
-EMGCorrReg_emm <- emmeans::emmeans(EMGCorrReg_aov$aov, specs = "block")
-
-EMGCorrReg_con <- as.data.frame(pairs(EMGCorrReg_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
-                                      data = EMG_reg,
-                                      progress = FALSE)
-
-EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = TRUE))$bf)
-
-EMGCorrReg_con <- cbind(EMGCorrReg_con,
-                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
-                                                     df_error = EMGCorrReg_con$df,
-                                                     ci = 0.95),digits = 2))
-
-colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-
-EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
-EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
-EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
-EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
-EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
-EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Corrugator activity")
-
-# levator
-
-EMGLevReg_aov <- afex::aov_ez(data = EMG_reg,
-                              id = "ID",
-                              dv = "Lev",
-                              within = "block",
-                              fun_aggregate = mean,
-                              include_aov = TRUE)
-
-# compute posthoc tests for within measures
-EMGLevReg_emm <- emmeans::emmeans(EMGLevReg_aov$aov, specs = "block")
-
-EMGLevReg_con <- as.data.frame(pairs(EMGLevReg_emm, adjust = "bonferroni"))
-
-# Bayes Factors
-EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
-                                      data = EMG_reg,
-                                      progress = FALSE)
-
-EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
-                                                                    progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
-                                                                    progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
-                                                                    progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
-                                                                    progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
-                                                                    progress = FALSE, paired = TRUE))$bf,
-                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
-                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
-                                                                    progress = FALSE, paired = TRUE))$bf)
-
-EMGLevReg_con <- cbind(EMGLevReg_con,
-                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
-                                                    df_error = EMGLevReg_con$df,
-                                                    ci = 0.95),digits = 2))
-
-colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-
-EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
-EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
-EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
-EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
-EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
-EMGLevReg_con[6,1] <- "$Distancing - Suppression$"
-
-# Figure to visualize arousal ratings
-
-# figure
-FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
-  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
-  scale_x_discrete(name = "Strategy", 
-                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
-                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
-  geom_jitter(size = 0.4)+
-  labs(y = "Levator activity")
-
 ```
@@
 A brief training ensures that all participants are able to implement the ER strategies.
-Next, electrodes to measure EMG <!-- Has abbrev. EMG already are been introduced? -->being attached and the ER paradigm is conducted.
+Next, electrodes to measure EMG being attached and the ER paradigm is conducted.
 Participants receive 30.00€ or course credit as compensation.

### 2022-02-21 06_Paper/ER-ED/_targets.R
deleted targets

@@ -1,22 +1,0 @@
-library(targets)
-library(tarchetypes)
-library(here)
-
-# set top level directory to source file
-here::i_am("flag_project_root_CERED.txt")
-
-# Set target-specific options such as packages.
-tar_option_set(packages = "tidyverse")
-options(tidyverse.quiet = TRUE)
-
-# End this file with a list of target objects.
-list(
-  tar_target(intro, "TheoreticalBackground.Rmd", format = "file"),
-  tar_target(method, "Method.Rmd", format = "file"),
-  tar_target(Quest, "Questionnaires.R", format = "file"),
-  tar_target(raw_data_file, here("04_RawData", "pilot", "CERED_DATA.csv"), format = "file"),
-  tar_target(raw_data, read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"),
-                                 stringsAsFactors = FALSE, header = TRUE,
-                                 na.strings = c("", "NA"))),
-  tar_render(whole.paper, "Manuscript_ERED_Stage1.Rmd")
-)

### 2022-02-21 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added setup

@@
 ---
+
+```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}
+
+library(knitr)
+# set knitr options
+knitr::opts_chunk$set(out.width = "\\textwidth")
+
+# load libraries
+library(here) # for path independent file referencing
+  # set top level directory to source file
+
+  here::i_am("flag_project_root_CERED.txt")
+library(papaja) # APA conform output
+library(kableExtra) # for tables in R Markdown
+
+```
 

### 2022-02-21 06_Paper/ER-ED/method.Rmd
deleted unnecessary libraries

@@
 
-library(targets)    # to keep track of all relevant files
-library(readxl)     # import excel files
+#library(readxl)     # import excel files
 library(here)       # to set directories without defined paths
-library(papaja)     # APA conform output
-library(afex)       # for ANOVA
-library(emmeans)
-library(ggplot2)    # for nice plots
-library(dplyr)
-library(BayesFactor)
-library(effectsize)
-
 # set top level directory to source file
 here::i_am("flag_project_root_CERED.txt")
+
+library(papaja)     # APA conform output
+#library(afex)       # for ANOVA
+#library(emmeans)
+#library(ggplot2)    # for nice plots
+#library(dplyr)
+#library(BayesFactor)
+#library(effectsize)
+
 ```

### 2022-02-21 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
Import Workspace Data

--- 2022-02-18 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 ---
+
+```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}
+
+library(knitr)
+# set knitr options
+knitr::opts_chunk$set(out.width = "\\textwidth")
+
+# load libraries
+library(here) # for path independent file referencing
+# set top level directory to source file
+here::i_am("flag_project_root_CERED.txt")
+
+library(papaja) # APA conform output
+library(kableExtra) # for tables in R Markdown
+
+# load workspace variables from analyses_ERED.R script
+load(here("06_Paper","ER-ED","WorkspaceERED.RData"))
+
+```
 

### 2022-02-21 06_Paper/ER-ED/method.Rmd
fixed issue with units

@@
 
-#library(readxl)     # import excel files
+library(readxl)     # import excel files
 library(here)       # to set directories without defined paths
@@
 Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
-Impedance level will be kept below 10 kΩ. 
+Impedance level will be kept below 10 $k\Omega$. 
 Data will be sampled at 1000 Hz, filtered, rectified and integrated. 

### 2022-02-21 06_Paper/ER-ED/Analyes_ERED.r
tried to fix renv error

@@ -23,6 +23,10 @@ renv::restore(here("06_Paper","ER-ED"))
 
 library(dplyr)
 library(ggplot2)
+#library(afex)       # for ANOVA
+#library(emmeans)
+#library(BayesFactor)
+#library(effectsize)
 
 ##################### DATA IMPORT #######################
 

### 2022-02-21 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
fixed typo
knitted document

@@
 library(kableExtra) # for tables in R Markdown
+library(BayesFactor) # for bayes factors
 
 # load workspace variables from analyses_ERED.R script
-load(here("06_Paper","ER-ED","WorkspaceERED.RData"))
+load(here("06_Paper","ER-ED","Workspace_ERED.RData"))
 

### 2022-02-21 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
-Moreover it is known that ER strategies reduce physiological arousal, measured via EMG in the region of the \emph{corrugator supercilii}.\textsuperscript{5}
+Moreover it is known that ER strategies reduce physiological arousal, measured via electromyography (EMG) in the region of the \emph{corrugator supercilii}.\textsuperscript{5}
 So these tactics from three different strategies proved to be effective in the short term.
@@
 For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
-Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see).\textsuperscript{8}
+Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see Aldao et al.).\textsuperscript{8}
 
@@
 Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.\textsuperscript{12,13}
-Further influencing factors are for example extrinsic motivation (e.g.~monetary incentives), motivational determinants (i.e.~hedonic regulatory goals), and effort.\textsuperscript{13,14}
-Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort.\textsuperscript{14}
+Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
+Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{14}
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
 Afterwards they could choose, which strategy they want to use again.
-Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
+Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
 Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
 What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
-People choose a strategy that they prefer, for different, relatively well-known reasons.
-However, nothing is revealed about the strategy that is not chosen.
+People choose a strategy that they prefer for different, relatively well-known reasons.
+However, nothing is revealed about the strategy that is \emph{not chosen}.
 
 The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put into a new perspective with the concept of ER flexibility.
-Similar to other psychological domains such as attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
-In contrast, \emph{adaptive} ER requires having a large repertoire of ER strategies to choose from\textsuperscript{9} and choosing the strategy that is useful for goal achieving in a particular situation.
+Similar to other psychological domains such as attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or the use of strategies that are hindering the achievement of goals.\textsuperscript{9}
+In contrast, \emph{adaptive} ER requires having a large repertoire of ER strategies to choose from\textsuperscript{9} and choosing the strategy that is useful for goal achievement in a particular situation.
 This greater ER variability has been shown to be related to reduced negative affect.\textsuperscript{10}
 The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option.\textsuperscript{11}
-Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g.~monetary incentives), motivational determinants (i.e.~hedonic regulatory goals), and effort.\textsuperscript{13,14}
+Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
 Effort in particular appeared to be the main factor in ER choice behaviour in our previous work.\textsuperscript{14}
@@
 When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
-We assume that both aspects are set off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
+We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
 SVs of ER Strategies could be helpful to describe the ER repertoire\textsuperscript{9} more comprehensively.
@@
 A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
-This in turn would mean that no strategy is a good choice to achieve goals.
+This in turn would mean that no strategy is a good choice to achieve ER goals.
 
 However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
-To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
+To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
 Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
@@
 
-\hypertarget{er-strategy-discounting}{%
-\subsection{1.1 ER strategy discounting}\label{er-strategy-discounting}}
-
 In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
-Participants had to decide whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward.
+Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption taht teh objectively easiest \emph{n}-back level has the highest SV.
 In the current study, we want to use this paradigm to determine SVs of ER strategies.
@@
 Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined.
-In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
+In this step, the same monetary value (i.e., 1 €) is assigned to both options.
 The assumption is that participants now choose the option that has the higher SV for them.
 In the next step we return to the original paradigm.
-The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
+The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
 In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{17} until the indifference point is reached.
@@
 
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
-According to the 21-word-solution, ``we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study'' in compliance with the 21-word-solution of open science.\textsuperscript{18}
-A complete list of all measures assessed in the study will be found at the OSF (\url{https://osf.io/vnj8x/}) and GitHub (github.com/ChScheffel/COG-ER-ED).
-All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{18}
+The paradigm was written and presented using \emph{Psychopy}.\textsuperscript{19}
+We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \ldots{} for all our analyses.
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
+A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).
 
@@
 \subsection{2.1 Ethics information}\label{ethics-information}}
+
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK\ldots).
+Prior to testing, written informed consent will be obtained.
+Participants will receive 30€ in total or course credit for participation.
 
@@
 
-Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{19} at the Technische Universität Dresden.
-Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
+Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{22} at the Technische Universität Dresden.
+Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
 The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
@@
 At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
-Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
+Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
 The second session, containing the ER paradigm, takes place exactly one week after session one.
@@
 A brief training ensures that all participants are able to implement the ER strategies.
-Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
+Next, electrodes to measure EMG being attached and the ER paradigm is conducted.
 Participants receive 30.00€ or course credit as compensation.
-Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{20,21}
+Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{23,24}
 
@@
 
-The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{22,23}
-To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{26} is used.
-Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,27}
-For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{28}
-Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{29}
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{30,31} is used.
-To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{32} the Self-Regulation Scale (SRS),\textsuperscript{33} the Brief Self-Control Scale (BSCS);\textsuperscript{34}{]},\textsuperscript{35} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{36,37}
-Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{38}
+The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{25,26}
+To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{29} is used.
+Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,30}
+For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{31}
+Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{32}
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{33,34} is used.
+To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{35} the Self-Regulation Scale (SRS),\textsuperscript{36} the Brief Self-Control Scale (BSCS);\textsuperscript{37}{]},\textsuperscript{38} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{39,40}
+Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{41}
 
@@
 
-Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{39} and the International Affective Picture System (IAPS).\textsuperscript{40}
+Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{42} and the International Affective Picture System (IAPS).\textsuperscript{43}
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
 Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
-An evolutionary algorithm\textsuperscript{41} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+An evolutionary algorithm\textsuperscript{44} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material X.
 
-\hypertarget{electromyography}{%
-\subsubsection{2.3.4 Electromyography}\label{electromyography}}
-
-Two bipolar electromyograph (EMG) measures will be recorded in the region of the \emph{corrugator supercilii} and the \emph{levator labii} using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
-Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel will be used.
-Data will be sampled at 1000 Hz.
-To measure \emph{corrugator EMG}, electrodes will be applied to the abraded and cleaned skin on the left \emph{corrugator supercilii}, and to measure \emph{levator EMG}, electrodes were applied in the region of the \emph{levator labii}.
-The ground electrode will be placed at the left \emph{Mastoid}.
+\hypertarget{facial-electromyography}{%
+\subsubsection{2.3.4 Facial electromyography}\label{facial-electromyography}}
+
+Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence (Bradley \& Lang, 2000).
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
+The ground electrode will be placed over the left \emph{Mastoid}.
+Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
+Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
+Impedance level will be kept below 10 \(k\Omega\).
+Data will be sampled at 1000 Hz, filtered, rectified and integrated.
 A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
-Afterwards, the signals will be rectified and segmented.
-EMG data will be baseline-corrected to -200 ms to 0 ms to stimulus onset.
-Last, the sampling rate is changed to 100 Hz and the AUC for the interval of 6000 ms stimulus presentation extracted for every stimulus.
+Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf.~Bradley \& Lang, 2000).
+Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
 
@@
 
-Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{19} at the Technische Universität Dresden.
+Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{22} at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Sample size calculation is done using \emph{G*Power}.\textsuperscript{42,43}
+Sample size calculation is done using \emph{G*Power}.\textsuperscript{45,46}
 In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.
@@
 
-All statistical analyses will be performed using \emph{RStudio} (version 1.4.1717)\textsuperscript{44}and \emph{R} (version 4.1.0)\textsuperscript{45} for Windows.
-The level of significance was set to \(\alpha=.05\).
-
-\emph{Effects of emotion regulation on arousal and effort} To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
-To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
-To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of \emph{corrugator} and \emph{levator}.
-A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
-To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
-Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom were reported when assumption of sphericity was violated.
-Proportion of explained variance \(\eta_{p}^{2}\) was reported as a measure of effect size.
+All statistical analyses will be performed using \emph{RStudio} (version 1.4.1717)\textsuperscript{21}and \emph{R} (version 4.1.0)\textsuperscript{20} for Windows.
+The level of significance will be set to \(\alpha=.05\).
+
+\emph{Effects of emotion regulation on arousal, facial EMG and effort} To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
+To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
+
+To examine the impact of valence on facial EMG, a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for \emph{corrugator} and \emph{levator} activity.
+To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for \emph{corrugator} and \emph{levator} activity will be conducted.
+
+To examine the effect of ER strategies on cognitive effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
+Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
 
-\emph{Subjective values of emotion regulation strategies} For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+\emph{Subjective values of emotion regulation strategies} For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
 Second, the resulting (monetary) value will be divided by 2.00 €.
@@
 
-To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{46}
-First, ER strategies will be re-coded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{47}
+First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
 Restricted maximum likelihood (REML) will be applied to fit the model.
@@
 SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
-\] Level-1-predictors will be centered within cluster.\textsuperscript{47}
+\] Level-1-predictors will be centered within cluster.\textsuperscript{48}
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses both, \(p\)-values and Bayes factor \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{48} will be reported.
+For each result of the analyses both, \(p\)-values and Bayes factor \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{49} will be reported.
+Bayses factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
 
@@
 
+\leavevmode\hypertarget{ref-Peirce2019}{}%
+\CSLLeftMargin{19. }
+\CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
+
+\leavevmode\hypertarget{ref-RCore2021}{}%
+\CSLLeftMargin{20. }
+\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}
+
+\leavevmode\hypertarget{ref-RStudioTeam2020}{}%
+\CSLLeftMargin{21. }
+\CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}
+
 \leavevmode\hypertarget{ref-Greiner2015}{}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
@@
 \leavevmode\hypertarget{ref-Harris2009}{}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Harris2019}{}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
@@
 \leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
@@
 \leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
@@
 \leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Sarubin, N.
@@
 \leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Campbell-Sills, L.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
@@
 \leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
@@
 \leavevmode\hypertarget{ref-Bernecker2017}{}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Bernecker, K.
@@
 \leavevmode\hypertarget{ref-Cacioppo1982}{}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
@@
 \leavevmode\hypertarget{ref-Bless1994}{}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
@@
 \leavevmode\hypertarget{ref-Paschke2016}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Paschke, L.
@@
 \leavevmode\hypertarget{ref-Schwarzer1999}{}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}
@@
 \leavevmode\hypertarget{ref-Tangney2004}{}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Tangney, J.
@@
 \leavevmode\hypertarget{ref-Sproesser2011}{}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
@@
 \leavevmode\hypertarget{ref-Patton1995}{}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
@@
 \leavevmode\hypertarget{ref-Hartmann2011}{}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Hartmann, A.
@@
 \leavevmode\hypertarget{ref-Derryberry2002}{}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
@@
 \leavevmode\hypertarget{ref-Wessa2010}{}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Wessa, M.
@@
 \leavevmode\hypertarget{ref-Lang2008}{}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Lang, P.
@@
 \leavevmode\hypertarget{ref-Yu2010}{}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
@@
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 
-\leavevmode\hypertarget{ref-RStudioTeam2020}{}%
-\CSLLeftMargin{44. }
-\CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}
-
-\leavevmode\hypertarget{ref-RCore2021}{}%
-\CSLLeftMargin{45. }
-\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}
-
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Enders, C.
@@
 \leavevmode\hypertarget{ref-Morey2021}{}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
@@
 
-\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of negative and neutral pictures in the condition "active viewing".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological arousal (*Corrugator* activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological arousal (*Levator* activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
 

### 2022-02-22 06_Paper/ER-ED/method.Rmd
fixed issue with heading
deleted old packages

@@
 
-library(readxl)     # import excel files
 library(here)       # to set directories without defined paths
@@
 library(papaja)     # APA conform output
-#library(afex)       # for ANOVA
-#library(emmeans)
-#library(ggplot2)    # for nice plots
-#library(dplyr)
-#library(BayesFactor)
-#library(effectsize)
-
+library(readxl)     # import excel files
 ```
@@
 # lists contain arousal and valence values of each picture
-stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))
+stim_negative <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))
 
-stim_neutral = readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
+stim_neutral <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
 ```
@@
 <!-- Attention! OSF is still private -->
+
 ## 2.1 Ethics information

### 2022-02-22 06_Paper/ER-ED/method.Rmd
added main packages

@@
 The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages ...
-<!-- name and reference the main analysis packages, agian for consistentcy with Zerna et al.
---> for all our analyses.
+We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->

### 2022-02-22 06_Paper/ER-ED/method.Rmd
incorporated comment

@@
 
-The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).<!-- This results in two digit numbers, with the last digit being zero.
-Perhaps use papaja::printnun(x, diguts = 1, gt1 = T) instead, this rounds up to 1 digit, but also only displays one digit (at least I hope so) -->
+The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
 Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 The paradigm was written and presented using \emph{Psychopy}.\textsuperscript{19}
-We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \ldots{} for all our analyses.
+We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all analyses.
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
@@
 
-The procedure described above was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.10\text{ }\pm\text{ }SD = 3.60\)).
+The procedure described above was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
 Results showed significant higher subjective (\ldots{} and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
@@
 
-Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{22} at the Technische Universität Dresden.
+Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
 Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
@@
 Participants receive 30.00€ or course credit as compensation.
-Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{23,24}
+Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{25,26}
 
@@
 
-The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{25,26}
-To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{29} is used.
-Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,30}
-For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{31}
-Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{32}
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{33,34} is used.
-To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{35} the Self-Regulation Scale (SRS),\textsuperscript{36} the Brief Self-Control Scale (BSCS);\textsuperscript{37}{]},\textsuperscript{38} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{39,40}
-Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{41}
+The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{27,28}
+To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{31} is used.
+Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
+For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{33}
+Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{34}
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{35,36} is used.
+To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{37} the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS);\textsuperscript{39}{]},\textsuperscript{40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
+Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{43}
 
@@
 
-Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{42} and the International Affective Picture System (IAPS).\textsuperscript{43}
+Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{44} and the International Affective Picture System (IAPS).\textsuperscript{45}
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
 Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
-An evolutionary algorithm\textsuperscript{44} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+An evolutionary algorithm\textsuperscript{46} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material X.
@@
 
-Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{22} at the Technische Universität Dresden.
+Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Sample size calculation is done using \emph{G*Power}.\textsuperscript{45,46}
+Sample size calculation is done using \emph{G*Power}.\textsuperscript{47,48}
 In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.
@@
 
-To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{47}
+To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{49}
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
-\] Level-1-predictors will be centered within cluster.\textsuperscript{48}
+\] Level-1-predictors will be centered within cluster.\textsuperscript{50}
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses both, \(p\)-values and Bayes factor \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{49} will be reported.
+For each result of the analyses both, \(p\)-values and Bayes factor \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{23} will be reported.
 Bayses factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
@@
 
+\leavevmode\hypertarget{ref-Singmann2021}{}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}
+
+\leavevmode\hypertarget{ref-Morey2021}{}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
+
 \leavevmode\hypertarget{ref-Greiner2015}{}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
@@
 \leavevmode\hypertarget{ref-Harris2009}{}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Harris2019}{}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
@@
 \leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
@@
 \leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
@@
 \leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Sarubin, N.
@@
 \leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Campbell-Sills, L.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
@@
 \leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
@@
 \leavevmode\hypertarget{ref-Bernecker2017}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Bernecker, K.
@@
 \leavevmode\hypertarget{ref-Cacioppo1982}{}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
@@
 \leavevmode\hypertarget{ref-Bless1994}{}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
@@
 \leavevmode\hypertarget{ref-Paschke2016}{}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Paschke, L.
@@
 \leavevmode\hypertarget{ref-Schwarzer1999}{}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}
@@
 \leavevmode\hypertarget{ref-Tangney2004}{}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Tangney, J.
@@
 \leavevmode\hypertarget{ref-Sproesser2011}{}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
@@
 \leavevmode\hypertarget{ref-Patton1995}{}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
@@
 \leavevmode\hypertarget{ref-Hartmann2011}{}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Hartmann, A.
@@
 \leavevmode\hypertarget{ref-Derryberry2002}{}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
@@
 \leavevmode\hypertarget{ref-Wessa2010}{}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Wessa, M.
@@
 \leavevmode\hypertarget{ref-Lang2008}{}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Lang, P.
@@
 \leavevmode\hypertarget{ref-Yu2010}{}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
@@
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Enders, C.
@@
 \emph{Psychological Methods} \textbf{12}, 121--138 (2007).}
-
-\leavevmode\hypertarget{ref-Morey2021}{}%
-\CSLLeftMargin{49. }
-\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
 

### 2022-02-22 06_Paper/ER-ED/method.Rmd
Update method.Rmd

@@
 Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
+Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
 Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
@@
 
-Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
-<!--JZ: Das stand oben schon mal--> Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
 Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].

### 2022-02-22 06_Paper/ER-ED/method.Rmd
added bradley 2000

@@
 
-Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence (Bradley & Lang, 2000). <!-- Quelle noch einfügen -->
+Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000].
 Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).

### 2022-02-22 06_Paper/ER-ED/method.Rmd
added reference Fridlund

@@
 Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000].
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
-<!-- Quelle einfügen -->
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of @Fridlund1986.
 The ground electrode will be placed over the left *Mastoid*.

### 2022-02-22 06_Paper/ER-ED/method.Rmd
added missing reference
references design table, corrected reference

@@
 An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
-A complete list of all pictures and their classification into sets can be found in supplementary material X.
+A complete list of all pictures and their classification into sets can be found in supplementary material 1.
 
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf. Bradley & Lang, 2000). 
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset [@Bradley2000]. 
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
-<!-- AG: insert references -->
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
+Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
 Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
@@
 
-Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence (Bradley \& Lang, 2000).
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
+Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence.\textsuperscript{47}
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{48}
 The ground electrode will be placed over the left \emph{Mastoid}.
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf.~Bradley \& Lang, 2000).
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{cf, 47}
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
@@
 
-Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
-Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Sample size calculation is done using \emph{G*Power}.\textsuperscript{47,48}
+Sample size calculation is done using \emph{G*Power}.\textsuperscript{49,50}
 In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.
@@
 
-To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{49}
+To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{51}
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
-\] Level-1-predictors will be centered within cluster.\textsuperscript{50}
+\] Level-1-predictors will be centered within cluster.\textsuperscript{52}
 Residuals of the final model will be inspected visually.
@@
 
+\leavevmode\hypertarget{ref-Bradley2000}{}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Bradley, M.
+M.
+\& Lang, P.
+J.
+Measuring emotion: Behavior, feeling, and physiology.
+in \emph{Cognitive neuroscience of emotion} (eds.
+Lane, R.
+D.
+\& Nadel, L.) 242--276 (Oxford University Press, 2000).}
+
+\leavevmode\hypertarget{ref-Fridlund1986}{}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Fridlund, A. J. \& Cacioppo, J. T. Guidelines for human electromyographic research. \emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
+
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Enders, C.

### 2022-02-22 06_Paper/ER-ED/method.Rmd
referenced design table
incorporated comments

@@
 Therefore, we aim to collect data of 90 participants.
-<!-- somehow refer to the Design Table here, where everything is detailed -->
+Detailed information on power calculation for each hypothesis can be found in the design table.
 
@@
 
-All statistical analyses will be performed using *RStudio* (version 1.4.1717) [@RStudioTeam2020]and *R* (version 4.1.0) [@RCore2021] for Windows.<!-- mention the main packages used and list the helper packages in the supplement -->
+Data collection and analysis will not be performed blind to the conditions of the experiments.
 The level of significance will be set to $\alpha=.05$.
@@
 *Effects of emotion regulation on arousal, facial EMG and effort* <br> To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA  with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
+To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
 
 To examine the impact of valence on facial EMG, a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for *corrugator* and *levator* activity.
-To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for *corrugator* and *levator* activity will be conducted.
-<!-- hier werden HE across neg + neu Bedingungen angeschaut, ist das korrekt? -->
-<!-- Habe den Text oben sprachlich vereinheitlicht, weil ich es sonst schwer zu lesen fand. -->
+To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for *corrugator* and *levator* activity will be conducted.
 
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-<!-- perhaps alsway mention which r package will be used to run these proceudres -->
+rmANOVAS will be run using the *afex* package [@Singmann2021]
 
@@
 Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
-<!--CS: Weitere Persönlichkeitsfaktoren ins Modell?
-Würde sagen erstmal nicht, denn sonst wird es a) überladen mit Prädiktoren und b) haben wir sonst kein Maß, was meiner Meinung nach mit ALLEN SVs zusammenhängen sollte.
-Anm.
-AS: Ja, erstmal so schlank wie möglic halten.
--->
 
-The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict threir FlexER score.
-Therefore, SVs will be ordered by magnitude firstly.
+The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
+Firstly, SVs will be ordered by magnitude.
 Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
@@
 Bayses factors are calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
-<!-- bzw welche Funktionen auch immer Du nutzt, hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->
 

### 2022-02-22 06_Paper/ER-ED/method.Rmd
ignored comment... ;-)
added emg results

@@
 The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
-Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
-However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
-Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+Results showed significant higher subjective arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
+ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
+However, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
+Yet we found in accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.
 
@@
 
-*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.<!-- why exactly this value?
--->
+*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
 Second, the resulting (monetary) value will be divided by 2.00 €.
@@
 Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
-<!--CS: Reicht das so als Beschreibung und wird klar, woher die Slopes und Intercepts kommen werden? AS: Mir ehrlich gesagt erstmal nicht so ... -->
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
knitted document

@@
 ```
-*Figure 1.* Exemplary visualisation of two response patterns.
+*Figure 1.* Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 This pattern can also be represented by our paradigm.
-# Design Table
+
+# Design Table {#DesignTable}
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 The procedure described above was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
-Results showed significant higher subjective (\ldots{} and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
-However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
-Yet we found accordance with our previous studies\textsuperscript{14} that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+Results showed significant higher subjective arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
+ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
+However, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
+Yet we found in accordance with our previous studies\textsuperscript{14} that the use of ER strategies compared to active viewing was associated with increased subjective effort.
 
@@
 An evolutionary algorithm\textsuperscript{46} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
-A complete list of all pictures and their classification into sets can be found in supplementary material X.
+A complete list of all pictures and their classification into sets can be found in supplementary material 1.
 
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{cf, 47}
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{47}
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
@@
 Therefore, we aim to collect data of 90 participants.
+Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.
 
@@
 
-All statistical analyses will be performed using \emph{RStudio} (version 1.4.1717)\textsuperscript{21}and \emph{R} (version 4.1.0)\textsuperscript{20} for Windows.
+Data collection and analysis will not be performed blind to the conditions of the experiments.
 The level of significance will be set to \(\alpha=.05\).
@@
 \emph{Effects of emotion regulation on arousal, facial EMG and effort} To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
+To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
 
 To examine the impact of valence on facial EMG, a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for \emph{corrugator} and \emph{levator} activity.
-To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for \emph{corrugator} and \emph{levator} activity will be conducted.
+To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for \emph{corrugator} and \emph{levator} activity will be conducted.
 
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
+rmANOVAS will be run using the \emph{afex} package\textsuperscript{22}
 
@@
 
-The association between flexible ER and SVs of ER strategies will be investigated with a regression using the \(intercept\) and \(slope\) of each participants' SVs to predict threir FlexER score.
-Therefore, SVs will be ordered by magnitude firstly.
+The association between flexible ER and SVs of ER strategies will be investigated with a regression using the \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
+Firstly, SVs will be ordered by magnitude.
 Secondly, for each participant a linear model will be built to estimate the individual \(intercept\) and \(slope\).
@@
 This pattern can also be represented by our paradigm.
-\# Design Table
+
+\hypertarget{DesignTable}{%
+\section{Design Table}\label{DesignTable}}
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added supplement ERQ

@@
 
+## Detailed information on psychometric measures
+
+*General psychological well-being.*
+
+*Resilience.*
+
+*Habitual use of reappraisal and suppression.* 
+Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003;@Abler2009].
+The scale has items such as "I keep my emotions to myself" (ERQ-suppression) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].
+
+\newpage
 ## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"

### 2022-02-22 06_Paper/ER-ED/method.Rmd
fixed typo
corrected typo

@@
 To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
-Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
+Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
 For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
@@
 Therefore, we aim to collect data of 90 participants.
-Detailed information on power calculation for each hypothesis can be found in the design table.
+Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
cross referenced supplement
added flexER scale

@@
 
-## Detailed information on psychometric measures
+## Detailed information on psychometric measures {#SupplementQuestionnaires}
 
@@
 The scale has items such as "I keep my emotions to myself" (ERQ-suppression) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].
+
+*Emotion regulation flexibility.*
+Flexible use of ER strategies was assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
+Psychometric properties are currently under investigation.
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added NFC description

@@
 
+*Implicit theories of willpower.*
+
+*Need for Cognition.*
+Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale [@Bless1994]. 
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and were summed to the total NFC score.
+The scale shows comparably high internal consistency [Cronbach’s $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
+
 \newpage

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added BSCS scale

@@
 
+*Self-Regulation Scale.*
+
+*Brief Self-Control Scale.* 
+As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] was used. 
+It comprises 13 items (e.g., “I am good at resisting temptations”) with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me). 
+The scale shows acceptable internal consistency (Cronbach’s $\alpha=.81$)[@Sproesser2011] .
+
+*Baratt Impulsiveness Scale.*
+
 \newpage

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
Added SRS

@@
 Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003;@Abler2009].
-The scale has items such as "I keep my emotions to myself" (ERQ-suppression) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].
+The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].
 
@@
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and were summed to the total NFC score.
-The scale shows comparably high internal consistency [Cronbach’s $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
+The scale shows comparably high internal consistency [Cronbach's $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
 
 *Self-Regulation Scale.*
+As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] was used.
+The scale has 10 items (e.g., "It is difficult for me to suppress thoughts that interfere with what I need to do.", recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
+It has high internal consistency [Cronbach's $\alpha>.80$; @Schwarzer1999].
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added BIS-11

@@
 
-*Baratt Impulsiveness Scale.*
+*Barratt Impulsiveness Scale.*
+As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] was used.
+Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
+An internal consistency of Cronbach's $\alpha=.74$ and a retest reliability of $r_{tt}=.56$ for General Impulsiveness and $r_{tt}=.66$ for Total Score across 6 month were reported [@Hartmann2011].
 

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added WHO5

@@
 
-*General psychological well-being.*
+*WHO-5.*
+General psychological well-being is assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
+5 Items such as "Over the past 2 weeks I have felt calm and relaxed." are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
+The german version of the scale showed a high internal consistency (Cronbach's $\alpha=.92$)[@Braehler2007].
 
-*Resilience.*
+*Connor-Davidson Resilience Scale.*
+Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
+10 items such as "I am able to adapt to change." are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
+The 10-item version showed a high internal consistency (Cronbach's $\alpha=.84$) and a satisfactory retest-reliability of $r_{tt}=.81$ across 6 month[@Sarubin2015].
 
-*Habitual use of reappraisal and suppression.* 
-Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003;@Abler2009].
+*Emotion Regulation Questionnaire.* 
+Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003;@Abler2009].
 The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].
 
-*Emotion regulation flexibility.*
-Flexible use of ER strategies was assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
+*FlexER Scale.*
+Flexible use of ER strategies is assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
 Psychometric properties are currently under investigation.
@@
 
-*Need for Cognition.*
-Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale [@Bless1994]. 
-Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and were summed to the total NFC score.
+*Need for Cognition Scale.*
+Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale [@Bless1994]. 
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
 The scale shows comparably high internal consistency [Cronbach's $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
@@
 *Self-Regulation Scale.*
-As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] was used.
+As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] is used.
 The scale has 10 items (e.g., "It is difficult for me to suppress thoughts that interfere with what I need to do.", recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
@@
 *Brief Self-Control Scale.* 
-As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] was used. 
+As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used. 
 It comprises 13 items (e.g., “I am good at resisting temptations”) with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me). 
@@
 *Barratt Impulsiveness Scale.*
-As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] was used.
+As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] is used.
 Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).

### 2022-02-22 06_Paper/ER-ED/method.Rmd
cross referenced supplement
corrected typo

@@
 To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
-To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
+To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
 Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
+For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).
 <!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ...

### 2022-02-23 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
lay beliefs
Update Manuscript_ERED_Stage1.Rmd
added ACS and implicit theories

@@
 
-*Implicit theories of willpower.*
+*Implicit Theories Questionnaire.*
+Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
+4 items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
+The questionnaire showed an internal consistency of Cronbach's $\alpha=.87$[@Bernecker2017].
 
@@
 An internal consistency of Cronbach's $\alpha=.74$ and a retest reliability of $r_{tt}=.56$ for General Impulsiveness and $r_{tt}=.66$ for Total Score across 6 month were reported [@Hartmann2011].
+
+*Attentional Control Scale.*
+Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
+The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
+An internal consistency of Cronbach's $\alpha=.88$ was reported [@Derryberry2002].
 

### 2022-02-23 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
corrected typo

@@
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency [Cronbach's $\alpha>.80$; @Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
+The scale shows comparably high internal consistency (Cronbach's $\alpha>.80$)[@Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
 

### 2022-02-23 06_Paper/ER-ED/Questionnaires.R
Delete Questionnaires.R

@@ -1,44 +1,0 @@
-# Script for preprocessing of questionnaire data
-
-# load packages
-library(targets)
-library(readxl)
-library(here)
-library(dplyr)
-
-# set top level directory to source file
-here::i_am("flag_project_root_CERED.txt")
-
-# import questionnaire data from RedCap
-  
-data_redcap <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"),
-                        stringsAsFactors = FALSE, header = TRUE,
-                        na.strings = c("", "NA"))
-colnames(data_redcap)[1] <- "set" # rename the first column
-
-# remove unnecessary variables from questionnaire data frame
-  
-data_quest_raw <- data_redcap %>%
-    subset(select = c(set, subject, age, gender, edu,
-    nfc_01, nfc_02, nfc_03, nfc_04, nfc_05, nfc_06, nfc_07, nfc_08, nfc_09, nfc_10, nfc_11, nfc_12, nfc_13, nfc_14, nfc_15, nfc_16,
-    bis11_01, bis11_02, bis11_03, bis11_04, bis11_05, bis11_06, bis11_07, bis11_08, bis11_09, bis11_10, bis11_11, bis11_12, bis11_13, bis11_14, bis11_15, bis11_16, bis11_17, bis11_18, bis11_19, bis11_20, bis11_21, bis11_22, bis11_23, bis11_24, bis11_25, bis11_26, bis11_27, bis11_28, bis11_29, bis11_30,
-    bscs_1, bscs_2, bscs_3, bscs_4, bscs_5, bscs_6, bscs_7, bscs_8, bscs_9, bscs_10, bscs_11, bscs_12, bscs_13,
-    srs_01, srs_02, srs_03, srs_04, srs_05, srs_06, srs_07, srs_08, srs_09, srs_10,
-    erq_01, erq_02, erq_03, erq_04, erq_05, erq_06, erq_07, erq_08, erq_10,
-    who5_1, who5_2, who5_3, who5_4, who5_5,
-    acs_01, acs_02, acs_03, acs_04, acs_05, acs_06, acs_07, acs_08, acs_09, acs_10, acs_11, acs_12, acs_13, acs_14, acs_15, acs_16, acs_17, acs_18, acs_19, acs_20,
-    risc_01, risc_04, risc_06, risc_07, risc_08, risc_11, risc_14, risc_16, risc_17, risc_19,
[…]

### 2022-02-23 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added pilot files
changed variable names

@@
 # load workspace variables from analyses_ERED.R script
-load(here("06_Paper","ER-ED","Workspace_ERED.RData"))
+load(here("06_Paper","ER-ED","Workspace_ERED_pilot.RData"))
 
@@
 
-`r afex::nice(SubjArousalView_aov) %>% knitr::kable(x = .)` 
-$BF10=$ `r round(extractBF(SubjArousalView_BF)$bf, digits = 2)`
+`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` 
+$BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`
 
@@
 apa_table(
-  SubjArousalView_con,
+  SubjArousalView_pilot_con,
   caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
@@
 ANOVA:
-`r afex::nice(SubjArousalReg_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(SubjArousalReg_BF)$bf, digits = 2)`
+`r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`
 
@@
 apa_table(
-  SubjArousalReg_con,
+  SubjArousalReg_pilot_con,
   caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
@@
 ANOVA: 
-`r afex::nice(EMGCorrView_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGCorrView_BF)$bf, digits = 2)`
+`r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`
 
@@
 apa_table(
-  EMGCorrView_con,
+  EMGCorrView_pilot_con,
   caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
@@
 ANOVA: 
-`r afex::nice(EMGLevView_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGLevView_BF)$bf, digits = 2)`
+`r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGLevView__pilotBF)$bf, digits = 2)`
 
@@
 apa_table(
-  EMGLevView_con,
+  EMGLevView_pilot_con,
   caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
@@
 ANOVA: 
-`r afex::nice(EMGCorrReg_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGCorrReg_BF)$bf, digits = 2)`
+`r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`
 
@@
 apa_table(
-  EMGCorrReg_con,
+  EMGCorrReg_pilot_con,
   caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
@@
 ANOVA: 
-`r afex::nice(EMGLevReg_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGLevReg_BF)$bf, digits = 2)`
+`r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`
 
@@
 apa_table(
-  EMGLevReg_con,
+  EMGLevReg_pilot_con,
   caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
@@
 ANOVA:
-`r afex::nice(SubjEffort_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(SubjEffort_BF)$bf, digits = 2)`
+`r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)`
+$BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
 
@@
 apa_table(
-  SubjEffort_con,
+  SubjEffort_pilot_con,
   caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",

### 2022-02-23 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
renamed variables

@@
 `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGLevView__pilotBF)$bf, digits = 2)`
+$BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`
 

### 2022-02-23 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
renamed variables

@@
 \begin{figure}
-\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/Other/Paradigm_Scheme_T2} \caption{Exemplary visualisation of two response patterns.
+\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/Other/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{31} is used.
-Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
+Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
 For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{33}
@@
 To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{35,36} is used.
-To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{37} the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS);\textsuperscript{39}{]},\textsuperscript{40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
+To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{37} the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS),\textsuperscript{39,40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
 Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{43}
+For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
 
@@
 
+\leavevmode\hypertarget{ref-Preece2020}{}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Preece, D.
+A., Becerra, R., Robinson, K.
+\& Gross, J.
+J.
+The emotion regulation questionnaire: Psychometric properties in general community samples.
+\emph{J Pers Assess} \textbf{102}, 348--356 (2020).}
+
+\leavevmode\hypertarget{ref-Fleischhauer2010}{}%
+\CSLLeftMargin{54. }
+\CSLRightInline{Fleischhauer, M.
+\emph{et al.} Same or different?
+{Clarifying} the relationship of need for cognition to personality and intelligence.
+\emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}
+
+\leavevmode\hypertarget{ref-Fleischhauer2015}{}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Fleischhauer, M., Strobel, A.
+\& Strobel, A.
+Directly and indirectly assessed {N}eed for {C}ognition differentially predict spontaneous and reflective information processing behavior.
+\emph{Journal of Individual Differences} \textbf{36}, 101--109 (2015).}
+
 \end{CSLReferences}
@@
 
-\emph{Figure 1.} Exemplary visualisation of two response patterns.
+\emph{Figure 1.} Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 \includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
+
+\newpage
+
+\hypertarget{SupplementQuestionnaires}{%
+\subsection{Detailed information on psychometric measures}\label{SupplementQuestionnaires}}
+
+\emph{WHO-5.}
+General psychological well-being is assessed using the WHO-5 scale\textsuperscript{27,28}.
+5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
+The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{28}.
+
+\emph{Connor-Davidson Resilience Scale.}
+Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{29--31}.
+10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{30}.
+
+\emph{Emotion Regulation Questionnaire.}
+Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{6,32}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{53}
+
+\emph{FlexER Scale.}
+Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{33} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+Psychometric properties are currently under investigation.
+
+\emph{Implicit Theories Questionnaire.}
+Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{34}
+4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
+The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{34}.
+
+\emph{Need for Cognition Scale.}
+Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{36}
+Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{36,54} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{55}
+
+\emph{Self-Regulation Scale.}
+As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{38} is used.
+The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
+It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{38}
+
+\emph{Brief Self-Control Scale.}
+As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{39,40} is used.
+It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
+The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{40} .
+
+\emph{Barratt Impulsiveness Scale.}
+As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{41,42} is used.
+Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
+An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{42}
+
+\emph{Attentional Control Scale.}
+Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{43} with items such as ``My concentration is good even if there is music in the room around me''.
+The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
+An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{43}
 
@@
 
-\begin{tabular}{lllllllll}
+\begin{tabular}{llllllll}
 \toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+contrast & \multicolumn{1}{c}{estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{t.ratio} & \multicolumn{1}{c}{p.value} & \multicolumn{1}{c}{Eta2 (partial)} & \multicolumn{1}{c}{95% CI}\\
 \midrule
-$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 4,962.89 & 0.19 & {}[0.05, 1.00]\\
-$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 616.63 & 0.21 & {}[0.06, 1.00]\\
-$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 11,678.82 & 0.20 & {}[0.06, 1.00]\\
-$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 0.07 & 1.78e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 0.08 & 7.22e-04 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 0.06 & 2.36e-04 & {}[0.00, 1.00]\\
+$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 0.19 & {}[0.05, 1.00]\\
+$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 0.21 & {}[0.06, 1.00]\\
+$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 0.20 & {}[0.06, 1.00]\\
+$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 1.78e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 7.22e-04 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 2.36e-04 & {}[0.00, 1.00]\\
 \bottomrule

### 2022-02-23 06_Paper/ER-ED/method.Rmd
renamed variables

@@
 
-The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
+The procedure described above was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
 Results showed significant higher subjective arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.

### 2022-02-23 06_Paper/ER-ED/Analyes_ERED_pilot.r
fixxed error

@@ -484,7 +484,7 @@ EMGCorrReg_pilot_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
 EMGCorrReg_pilot_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg_pilot$Corr[EMG_reg_pilot$block == "2_view_neg"],
                                                                            y = EMG_reg_pilot$Corr[EMG_reg_pilot$block == "3_distraction"],
                                                                            progress = FALSE, paired = TRUE))$bf,
-                               BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg_pilot$Corr[EMG_reg$block == "2_view_neg"],
+                               BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg_pilot$Corr[EMG_reg_pilot$block == "2_view_neg"],
                                                                            y = EMG_reg_pilot$Corr[EMG_reg_pilot$block == "4_distancing"],
                                                                            progress = FALSE, paired = TRUE))$bf,
                                BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg_pilot$Corr[EMG_reg_pilot$block == "2_view_neg"],

### 2022-02-28 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
Typos
Typos and word count in Abstract

@@
  Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
- Relations of SVs to personality traits will be explored
+ Relations of SVs to personality traits will be explored.
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "X"
+wordcount         : "139"
 bibliography      : ER_ED.bib

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update Methods
Typos, Anmerkungen in Methods

@@
 The procedure described above was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
-Results showed significant higher subjective arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
-ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
-However, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
-Yet we found in accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+<!-- direkt "above" wird das nicht beschrieben, die genaue procedure wird eigentlich auch erst unten beschrieben.
+Ich würde eher schreiben "The newly developed ER paradigm was tested in a pilot study" oder so ähnlich.
+-->
+Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
+<!-- Signifikanz beruht auf p-Werten? Würde ich angeben. --> 
+However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
+Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
+In accordance with our previous study [@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+<!-- kann man die Results irgendwo nachvollziehen?
+Ich würde zumindest MW, SD und p-Werte angeben wenn gesagt wird, dass es "signifikant" höher/nierdiger ist.
+Auch um zu zeigen, worauf sich die Aussage stützt.
+könnte man die Ergebnisse sogar in einer Tabelle/Abbildung darstellen? Je nachdem, wie wichtig die Pilotdaten für das Gesamt-Ms. sind...
+
+Ich war etwas verwirrt dass die Pilotdaten schon hier kommen.
+Ich hätte erwartet, dass erst das Paradigma genau beschrieben wird, und dann als "Schmankerl" die ersten Pilotdaten mitgeliefert werden.
+Evtl.
+mit einer extra Überschrift "Introduction / Methods / Pilot study (oder data)".
+So gehen sie m.E.
+etwas unter, weil man sich nachfolgend wieder auf die Details des Paradigmas konzentriert.
+Hier wurde aber auch nicht alles untersucht, wie z.B.
+Fragebögen?
+-->
 
@@
 
-Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
+Young healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
@@
 Before each session, participants receive information about the respective experimental procedure and provide informed consent.
-At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
+At the beginning of the first session participants fill out a demographic questionnaire and complete an n-back task with the levels one to four.
 Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
@@
 Participants receive 30.00€ or course credit as compensation.
+<!-- das steht schon bei Ethics information, evtl. kürzen. -->
 Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd
Typo

@@
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
+Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
 The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd
Zeitformen einheitlich in Futur geändert, sonst Wechsel zwischen Präsens und Futur (finde ich ungünstig).

@@
 Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
-Before each session, participants receive information about the respective experimental procedure and provide informed consent.
-At the beginning of the first session participants fill out a demographic questionnaire and complete an n-back task with the levels one to four.
-Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
-The second session, containing the ER paradigm, takes place exactly one week after session one.
-Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
-A brief training ensures that all participants are able to implement the ER strategies.
-Next, electrodes to measure EMG being attached and the ER paradigm is conducted.
-Participants receive 30.00€ or course credit as compensation.
+The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
+Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
+At the beginning of the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
+Then, they will complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
+The second session will comprise the ER paradigm and take place exactly one week after session one.
+Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
+A brief training will ensure that all participants are able to implement the ER strategies.
+Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
+Participants will receive 30.00€ or course credit as compensation.
 <!-- das steht schon bei Ethics information, evtl. kürzen. -->
-Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
 

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd
minor changes

@@
 The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
-To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
+<!-- Hier und im Folgenden wird wieder Präsens verwendet - vereinheitlichen? -->
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
 Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
-For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
+For the assessment of ER flexibility we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
 Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
@@
 +3), the reliability of the measures.
--->
+AG: im Paper würde man das hier angeben, bei RR reicht vielleicht Supplememt? -->
 
@@
 
-The ER paradigm roughly consists of three parts that will be described in the following.
+The ER paradigm consists of three parts that will be described in the following.
 
@@
 During distancing, participants are asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants are told to "suppress their emotional facial expression." They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
+During suppression, participants are told to "suppress their emotional facial expression." They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
 Participants are instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
@@
 *Part two: ER effort discounting.* <br> In the second part, ER effort discounting takes place.
-The procedure of the discounting follows the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change.
+The procedure of the discounting follows the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with a major change.
 We use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
@@
 From this point on, comparisons between strategies follow the original COG-ED paradigm [@Westbrook2013].
-Participants are instructed to decide as realistically as possible, imagining the displayed money would really be up for election.
+Participants are instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
 
 *Part three: ER choice.* <br> After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
-Importantly, there are no further instruction on what basis they should make their decision.
-Participants should make their decision freely, according to the criteria they consider important for themselves.
+Importantly, there is no further instruction on what basis they should make their decision.
+Participants should make their decision freely, according to criteria they consider important for themselves.
 However, participants are asked to state the reasons for the decision afterwards.

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd
added reference for EMG

@@
 
-Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000].
+Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000], similar to previous work by our group [@Gärtner, Jawinski, Strobel, 2021].
+<!-- da wir das ja sogar schon gemacht haben, fände ich es cool die Studie zu erwähnen.
+:-) Zeigt ja auch, dass wir keine Neulinge auf dem Gebiet sind.
+Referenz muss glaub noch in Bib eingefügt werden!
+-->
 Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of @Fridlund1986.

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd
Anmerkung sampling plan

@@
 Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
-In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.
-To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
+In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
+To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of at least $N=85$ have to be analyzed.
 Power analyses of all other hypotheses yielded smaller sample sizes.
@@
 Therefore, we aim to collect data of 90 participants.
-Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
+Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable) in the Supplement.
+<!-- hier würde ich den Verweis zur Design Table ganz explizit machen, also sagen, wo diese zu finden ist. -->
 

### 2022-02-28 06_Paper/ER-ED/method.Rmd
Update method.Rmd
Update Analysis plan

@@
 ## 2.5 Analysis plan
+<!-- hier wird wieder durchgehend Futur verwendet - würde das in Methods vereinheitlichen. -->
 
@@
 
-*Effects of emotion regulation on arousal, facial EMG and effort* <br> To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
+<!-- Bei den krusiven Zwischenüberschriften wie in der nächsten Zeile würde ich Punkte setzen, sieht sonst im PDF sehr eng zusammen aus. ;-)  -->
+*Effects of emotion regulation on arousal, facial EMG and effort.* <br> To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
 To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
@@
 
-*Subjective values of emotion regulation strategies* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
 Second, the resulting (monetary) value will be divided by 2.00 €.
 The final SV for each participant will be computed by averaging all final SVs of each strategy.
-The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
-Again, estimated, marginal means will be computed as post-hoc contrasts.
+The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) and explore group effects.
+Again, estimated marginal means will be computed as post-hoc contrasts.
 
-To investigate, whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
-Furthermore, an ordinal logistic regression with dependent variable choice and independent variables SVs of each strategy will be computed.
+To investigate whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
+Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
 
-To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
+To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
 Restricted maximum likelihood (REML) will be applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological arousal (*corrugator* activity and *levator* activity) as level-1-predictor will be specified.
+A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors will be specified.
 $$
@@
 
-For each result of the analyses both, $p$-values and Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021], will be reported.
-Bayses factors are calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
+For each result of the analyses, both $p$-values and Bayes factors $BF10$, calculated using the *BayesFactor* package [@Morey2021], will be reported.
+Bayes factors are calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
 

### 2022-03-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
fixed typo

@@
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
-Moreover it is known that ER strategies reduce physiological arousal, measured via electromyography (EMG) in the region of the *corrugator supercilii* [@Zaehringer2020]. 
+Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG). [@Zaehringer2020]. 
+<!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
+Corrugator habe ich raus genommen, weil auch Levator untersucht wird (müssten sonst m.E.
+beide genannt werden.) Generell fehlt noch etwas die Einbettung, warum die beiden ausgewählt wurden.
+Soll ich da noch etwas ergänzen?
+bei Zaehringer wird der Levator überhaupt nicht genannt, die Metaanalyse bezieht sich nur auf den Corrugator.
+Wir hatten damals gesagt, dass viele der negativen Bilder primär auch recht eklig sind und daher der Levator passender sein könnte, weil er speuzifisch auf Ekel zu reagieren scheint, der Corrugator hingegen auf negative Bilder im Allgemeinen.
+Prinzipiell haben wir aber für beide die gleichen Hypothesen.
+Können aber auch warten, was die Reviewer sagen.-->
 So these tactics from three different strategies proved to be effective in the short term. 
 However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
-Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
-Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
-For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
-Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]).
+In particluar, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
+<!-- Wortwiederholung --> 
+Long-term consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed [@GrossJohn2003]. 
+<!-- würde einheitlich "ER" (wenn vorher eingeführt, wurde hier aber gemacht) oder "emotion regulation" schreiben. --> 
+Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
+For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
+In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]).
 
-The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
-Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
-Adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015].
-For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
+The postulation of *adaptive* and *maladaptive* ER strategies was put in a new perspective with the concept of ER flexibility.
+Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015].
+Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
+For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
+<!-- was ist hier mit ER variablitiy gemeint? würde Begriffe einheitlich verwenden, denke, hier ist ER flexibility gemeint. --> 
 Strategies have to be chosen from the repertoire that are useful for goal achieving.
@@
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
-Afterwards they could choose, which strategy they want to use again.
+Afterwards, they choose which strategy they wanted to use again.
 Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
-Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
+Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
 What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
@@
 
-The postulation of *adaptive* and *maladaptive* strategies was put into a new perspective with the concept of ER flexibility.
-Similar to other psychological domains such as attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or the use of strategies that are hindering the achievement of goals [@Aldao2015].
-In contrast, *adaptive* ER requires having a large repertoire of ER strategies to choose from [@Aldao2015] and choosing the strategy that is useful for goal achievement in a particular situation.
-This greater ER variability has been shown to be related to reduced negative affect [@Blanke2020].
-The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option [@Kable2007].
-Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
-Effort in particular appeared to be the main factor in ER choice behaviour in our previous work [@Scheffel2021].
-In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
-Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
-Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
-Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
-However, nothing has been investigated regarding the strategy that is *not* chosen.
+<!-- der nächste Absatz hier ist doppelt, daher gelöscht. -->
 
-We assume that people choose the strategy that has the highest value for them at that moment.
+We assume that people choose the strategy that has the highest value for them at the moment.
 The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
 One certainly central goal is the regulation of negative affect.
-A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
+A second, intrinsic and less obvious goal is the avoidance of effort [@Inzlicht2018].
 When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
@@
 [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
-Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption taht teh objectively easiest *n*-back level has the highest SV.
-In the current study, we want to use this paradigm to determine SVs of ER strategies.
+Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
+In the present study, we want to use this paradigm to determine SVs of ER strategies.
 In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
@@
 
-```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns.
+```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
 In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can also be represented by our paradigm.", out.width="98%"}
+This pattern can be represented by our paradigm.", out.width="98%"}
 include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
@@
 
-The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies. 
-As a manipulation check, we want to explore whether ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and require cognitive effort.
-The following hypotheses are proposed for this purpose:
+The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
+As a manipulation check, we want to investigate whether the ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and physiologicall responses as well as whether they require cognitive effort.
+The following hypotheses are proposed:
+<!-- ich würde hier  investigate schreiben, oder wird hier tatsächlich "nur" exploriert? 
+es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen.
+Z.B.: Warum wird Corrugator und Levator untersucht?
+m.E.
+müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.-->
 
 * H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H1b) Physiological arousal (EMG *corrugator* activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H1c) Physiological arousal (EMG *levator* activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2a) Subjective effort (effort ratings) is greater after using an Er strategy (distraction, distancing, suppression) compared to active viewing.
-* H2b) The majority of participants ruse the strategy that was least effortful for them.
+* H1b) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H1c) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) The majority of participants re-uses the strategy that was least effortful for them.
 
-Further we want to explore which variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
+<!-- die letzte Hypothese finde ich etwas unklar formuliert, z.B. was heißt "majority", lässt sich das spezifieren (z.B. > 50%?) -->
+
+Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
 
@@
 * H3b) Subjective arousal ratings negatively predict SVs of ER strategies.
-* H3c) EMG *corrugator* activity negatively predict SVs of ER strategies.
-* H3d) EMG *levator* activity negatively predict SVs of ER strategies.
+* H3c) EMG *corrugator* activity negatively predicts SVs of ER strategies.
+* H3d) EMG *levator* activity negatively predicts SVs of ER strategies.
 * H4a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.
+
+<!-- beim Lesen hatte ich den Eindruck, dass bis hierhin klare Hypothesen stehen und erst danach der exploratorische Teil kommt.
+habe mich hier auch wieder kurz gefragt, warum wir die EDA nicht erfassen.
+in der MA von Zaehringer sieht man, dass die Effektgröße für SCR nahe Null liegt.
+besser sieht es aber für die SCL aus.
+wenn deine Strategien erneut in Blöcken dargeboten werden, könnte man überlegen die SCL über die verschiedenen Blöcke zu erheben.
+Man könnte dann Zulassen vs.
+einzelne ER Strategien vs.
+Choice Block untersuchen.
+Können aber nach wie vor gern auf die Reviewer Anmerkung warten, vielleicht schlagen sie das vor.
+-->
 
@@
 Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely *n*-back.
+<!-- bei den exploratorischen Hypothesen sollte auf multiples Testen korrigiert werden (oder auch insgesamt...). wird darauf bei den Methoden ausreichend eingegangen? -->

### 2022-03-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
changed numbers of Hs

@@
 * H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H1b) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H1c) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2b) The majority of participants re-uses the strategy that was least effortful for them.
+* H2a) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H3a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H3b) The majority of participants re-uses the strategy that was least effortful for them.
 
@@
 
-* H3a) Subjective effort ratings negatively predict SVs of ER strategies.
-* H3b) Subjective arousal ratings negatively predict SVs of ER strategies.
-* H3c) EMG *corrugator* activity negatively predicts SVs of ER strategies.
-* H3d) EMG *levator* activity negatively predicts SVs of ER strategies.
-* H4a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.
+* H4a) Subjective effort ratings negatively predict SVs of ER strategies.
+* H4b) Subjective arousal ratings negatively predict SVs of ER strategies.
+* H4c) EMG *corrugator* activity negatively predicts SVs of ER strategies.
+* H4d) EMG *levator* activity negatively predicts SVs of ER strategies.
+* H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.
 
@@
 
-* H5a) The higher the SV, the more likely the respective strategy is chosen.
-* H5b) SVs are lower and decline stronger when ER flexibility is lower.
+* H6a) The higher the SV, the more likely the respective strategy is chosen.
+* H6b) SVs are lower and decline stronger when ER flexibility is lower.
 

### 2022-03-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
worked on comments

@@
 However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
-In particluar, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
+In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
 <!-- Wortwiederholung --> 
 Long-term consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed [@GrossJohn2003]. 
-<!-- würde einheitlich "ER" (wenn vorher eingeführt, wurde hier aber gemacht) oder "emotion regulation" schreiben. --> 
 Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
@@
 For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
-<!-- was ist hier mit ER variablitiy gemeint? würde Begriffe einheitlich verwenden, denke, hier ist ER flexibility gemeint. --> 
 Strategies have to be chosen from the repertoire that are useful for goal achieving.

### 2022-03-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
worked on comment
worked on comments

@@
 In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-<!-- Wortwiederholung --> 
-Long-term consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed [@GrossJohn2003]. 
+Longer lasting consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed [@GrossJohn2003]. 
 Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
@@
 However, nothing is revealed about the strategy that is *not chosen*.
-
-<!-- der nächste Absatz hier ist doppelt, daher gelöscht. -->
 
@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
-As a manipulation check, we want to investigate whether the ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and physiologicall responses as well as whether they require cognitive effort.
+As a manipulation check, we want to investigate whether the ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and physiological responses as well as whether they require cognitive effort.
 The following hypotheses are proposed:
-<!-- ich würde hier  investigate schreiben, oder wird hier tatsächlich "nur" exploriert? 
-es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen.
+<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen.
 Z.B.: Warum wird Corrugator und Levator untersucht?
@@
 
-<!-- die letzte Hypothese finde ich etwas unklar formuliert, z.B. was heißt "majority", lässt sich das spezifieren (z.B. > 50%?) -->
-
 Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
@@
 
-<!-- beim Lesen hatte ich den Eindruck, dass bis hierhin klare Hypothesen stehen und erst danach der exploratorische Teil kommt.
-habe mich hier auch wieder kurz gefragt, warum wir die EDA nicht erfassen.
-in der MA von Zaehringer sieht man, dass die Effektgröße für SCR nahe Null liegt.
-besser sieht es aber für die SCL aus.
-wenn deine Strategien erneut in Blöcken dargeboten werden, könnte man überlegen die SCL über die verschiedenen Blöcke zu erheben.
-Man könnte dann Zulassen vs.
-einzelne ER Strategien vs.
-Choice Block untersuchen.
-Können aber nach wie vor gern auf die Reviewer Anmerkung warten, vielleicht schlagen sie das vor.
--->
-
-We also want to explore whether SVs are related to flexible emotion regulation:
+We also want to investigate whether SVs are related to flexible emotion regulation:
 
@@
 Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely *n*-back.
-<!-- bei den exploratorischen Hypothesen sollte auf multiples Testen korrigiert werden (oder auch insgesamt...). wird darauf bei den Methoden ausreichend eingegangen? -->

### 2022-03-03 06_Paper/ER-ED/method.Rmd
accepted comment

@@
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
-The paradigm was written and presented using *Psychopy* [@Peirce2019].
+The paradigm was written and presented using *PsychoPy* [@Peirce2019].
 We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
@@
 
-The procedure described above was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
-<!-- direkt "above" wird das nicht beschrieben, die genaue procedure wird eigentlich auch erst unten beschrieben.
-Ich würde eher schreiben "The newly developed ER paradigm was tested in a pilot study" oder so ähnlich.
--->
+The newly developed ER paradigm was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
 Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.

### 2022-03-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
updated documents

@@
 \newpage
-```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE, out.width="98%"}
+```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE}
 include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
@@
 
-# Supplement
+# Supplementary Material {#SupplementaryMaterial}
 

### 2022-03-03 06_Paper/ER-ED/method.Rmd
updated documents

@@
 Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
-<!-- Signifikanz beruht auf p-Werten? Würde ich angeben. --> 
 However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
@@
 In accordance with our previous study [@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
-<!-- kann man die Results irgendwo nachvollziehen?
-Ich würde zumindest MW, SD und p-Werte angeben wenn gesagt wird, dass es "signifikant" höher/nierdiger ist.
-Auch um zu zeigen, worauf sich die Aussage stützt.
-könnte man die Ergebnisse sogar in einer Tabelle/Abbildung darstellen? Je nachdem, wie wichtig die Pilotdaten für das Gesamt-Ms. sind...
-
-Ich war etwas verwirrt dass die Pilotdaten schon hier kommen.
-Ich hätte erwartet, dass erst das Paradigma genau beschrieben wird, und dann als "Schmankerl" die ersten Pilotdaten mitgeliefert werden.
-Evtl.
-mit einer extra Überschrift "Introduction / Methods / Pilot study (oder data)".
-So gehen sie m.E.
-etwas unter, weil man sich nachfolgend wieder auf die Details des Paradigmas konzentriert.
-Hier wurde aber auch nicht alles untersucht, wie z.B.
-Fragebögen?
--->
+All results are detailed in the [Supplementary Material](#SupplementaryMaterial)
 
@@
 Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
-Participants will receive 30.00€ or course credit as compensation.
-<!-- das steht schon bei Ethics information, evtl. kürzen. -->
 Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

### 2022-03-03 06_Paper/ER-ED/method.Rmd
added future tense

@@
 
-The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
-<!-- Hier und im Folgenden wird wieder Präsens verwendet - vereinheitlichen? -->
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used.
-Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
-For the assessment of ER flexibility we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
-Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
-To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
-Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
+The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
+For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
+Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from @Bernecker2017.
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] will be used.
+To assess self-control, sum scores of the German versions of the following questionnaires will be used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
+Attentional control will be assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
 For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).
-<!-- Not sure whether you can state this so briefly without giving more detailed information on, e.g., sample items, the scale on which answers are recorded (e.g., -3 ...
-+3), the reliability of the measures.
-AG: im Paper würde man das hier angeben, bei RR reicht vielleicht Supplememt? -->
 
@@
 
-The ER paradigm consists of three parts that will be described in the following.
+The ER paradigm will consist of three parts that will be described in the following.
 
-*Part one: ER task.* <br> Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021].
-Participants are told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
-Every participant first has the condition "active viewing-neutral" that serves as a baseline condition.
-During this block, 20 neutral pictures are presented.
-Participants are asked to "actively view all pictures and permit all emotions that may arise." In the second block, participants actively viewe negative pictures.
-During the third, fourth, and fifth block, participants see negative pictures and are asked to regulate their emotions using distraction, distancing, and suppression.
-In order to achieve distraction, participants are asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants are asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants are told to "suppress their emotional facial expression." They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants are instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
-All participants receive written instruction and complete a training session.
-After the training session, participants are asked about their applied ER strategies to avoid misapplication.
-The order of the three regulation blocks (distraction, distancing, and suppression) is randomized between participants.
+*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021].
+Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
+Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
+During this block, 20 neutral pictures will be presented.
+Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
+In the second block, participants will actively view negative pictures.
+During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
+In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
+During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
+Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
+During suppression, participants will be told to "suppress their emotional facial expression." 
+They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
+Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
+All participants will receive written instruction and complete a training session.
+After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
+The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
 
-*Part two: ER effort discounting.* <br> In the second part, ER effort discounting takes place.
-The procedure of the discounting follows the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with a major change.
-We use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
+*Part two: ER effort discounting.* <br> In the second part, ER effort discounting will take place.
+The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with a major change.
+We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
 distancing, distraction vs.
 suppression, and distancing vs.
-suppression), two strategies with monetary values are presented.
-The order of the comparisons is randomized.
-Because there is no strategy that is objectively more difficult, we added an initial comparison that begins with the option "1 EUR for strategy A or 1 EUR for strategy B".
-The strategy that is not chosen is assigned the value of 2 EUR.
-From this point on, comparisons between strategies follow the original COG-ED paradigm [@Westbrook2013].
-Participants are instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
+suppression), two strategies with monetary values will be presented.
+The order of the comparisons will be randomized.
+Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option "1 EUR for strategy A or 1 EUR for strategy B".
+The strategy that is not chosen will be assigned the value of 2 EUR.
+From this point on, comparisons between strategies will follow the original COG-ED paradigm [@Westbrook2013].
+Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
 
-*Part three: ER choice.* <br> After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
-Importantly, there is no further instruction on what basis they should make their decision.
+*Part three: ER choice.* <br> After the discounting part, participants will choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
+Importantly, there will be no further instruction on what basis they should make their decision.
 Participants should make their decision freely, according to criteria they consider important for themselves.
-However, participants are asked to state the reasons for the decision afterwards.
-As soon as they have decided, they see the respective instruction and the block with another 20 negative pictures starts.
+However, participants will be asked to state the reasons for the decision afterwards.
+As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
 
@@
 
-Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008].
+Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008].
 The 20 neutral pictures (Valence (V): *M* $\pm$ *SD* = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): *M* $\pm$ *SD* = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
-Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
-An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
+Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
+An evolutionary algorithm [@Yu2010] is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
 A complete list of all pictures and their classification into sets can be found in supplementary material 1.
@@
 
-Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000], similar to previous work by our group [@Gärtner, Jawinski, Strobel, 2021].
-<!-- da wir das ja sogar schon gemacht haben, fände ich es cool die Studie zu erwähnen.
-:-) Zeigt ja auch, dass wir keine Neulinge auf dem Gebiet sind.
-Referenz muss glaub noch in Bib eingefügt werden!
--->
+Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000], similar to previous work by our group [@Gaertner2021].
 Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of @Fridlund1986.
@@
 However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aim to collect data of 90 participants.
-Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable) in the Supplement.
-<!-- hier würde ich den Verweis zur Design Table ganz explizit machen, also sagen, wo diese zu finden ist. -->
+Therefore, we aim to collect data of XX participants.
+Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
 
 ## 2.5 Analysis plan
-<!-- hier wird wieder durchgehend Futur verwendet - würde das in Methods vereinheitlichen. -->
 
@@
 
-<!-- Bei den krusiven Zwischenüberschriften wie in der nächsten Zeile würde ich Punkte setzen, sieht sonst im PDF sehr eng zusammen aus. ;-)  -->
 *Effects of emotion regulation on arousal, facial EMG and effort.* <br> To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
@@
 SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
-$$ Level-1-predictors will be centered within cluster [@Enders2007].
+$$ 
+Level-1-predictors will be centered within cluster [@Enders2007].
 Residuals of the final model will be inspected visually.

### 2022-03-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
deleted author contributions

@@
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-
-# Author Contributions
-<!-- ist das überhaupt noch erforderlich, wenn doch im YAML header die roles difiniert wurden?
-Habe das bishernoch nicht gemacht, aber ist das nicht dazu da, dass dadurch automatisch ein Role Statement erzeugt wird?
--->
-CS, AS, and JZ conceptualized the study and its methodology.
-CS and JZ acquired funding, investigated, administered the project, and wrote the software.
-CS, JZ, and AG did the formal analysis.
-CS and JZ visualized the results, and prepared the original draft.
-All authors reviewed, edited, and approved the final version of the manuscript.
 

### 2022-03-03 06_Paper/ER-ED/method.Rmd
added ER ED Design and cross referencing

@@
 Prior to testing, written informed consent will be obtained.
-Participants will receive 30€ in total or course credit for participation.
+Participants will receive 30 € in total or course credit for participation.
 
@@
 To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] will be used.
-To assess self-control, sum scores of the German versions of the following questionnaires will be used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
+To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
 Attentional control will be assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
@@
 
-*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021].
+*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:Design_ER-ED)), similar to paradigms previously used by our group [@Scheffel2021].
 Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
@@
 The order of the comparisons will be randomized.
-Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option "1 EUR for strategy A or 1 EUR for strategy B".
-The strategy that is not chosen will be assigned the value of 2 EUR.
+Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option "1 € for strategy A or 1 € for strategy B".
+The strategy that is not chosen will be assigned the value of 2 €.
 From this point on, comparisons between strategies will follow the original COG-ED paradigm [@Westbrook2013].
@@
 As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
+
+```{r Design_ER-ED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap="Block design of the paradigm.
+Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
+Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
+After, the discounting procedure takes place.
+All three regulation strategies are pairwise compared.
+Before the last block, participants can decide which regulation strategy they want to reapply.
+Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
+include_graphics(here("0g_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
+```
 

### 2022-03-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
updated documents
changed file location and added cross referencing

@@
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
-Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG). [@Zaehringer2020]. 
+Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
 <!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
@@
 But our paradigm can also account for the case that a person does not have a clear preference.
-Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
+Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
 Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
 
-```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.
+```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
 In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can be represented by our paradigm.", out.width="98%"}
-include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
+This pattern can be represented by our paradigm."}
+include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
 ```
-
-## 1.2 The present study
 

### 2022-03-03 06_Paper/ER-ED/method.Rmd
corrected Typo

@@
 Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
-include_graphics(here("0g_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
+include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
 ```

### 2022-03-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added fig 2 to supplement

@@
 \newpage
-```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE}
-include_graphics(here("99_Thinktank","Other","Paradigm_Scheme_T2.png" ))
+```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
+include_graphics(here("06_Paper","ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
 ```
-*Figure 1.* Exemplary visualization of two response patterns.
+*Figure 1.* 
+Exemplary visualization of two response patterns. 
 In the top half, the person has a clear preference for one of the three strategies. 
@@
 This pattern can also be represented by our paradigm.
+
+```{r Design_ER-ED_appendix, echo=FALSE, message=FALSE, warning=FALSE}
+include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
+```
+*Figure 2.* 
+Block design of the paradigm. 
+Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures. 
+Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place.
+All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. 
+Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
 
@@
 ```
-## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
+## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
 *Corrugator*:
@@
   EMGCorrView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
@@
   EMGLevView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
@@
 ```
-## Pilot study: Physiological arousal (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
+## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
 *Corrugator*:
@@
   EMGCorrReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
@@
   EMGLevReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
+  caption = "Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 

### 2022-03-03 06_Paper/ER-ED/method.Rmd
changed escape

@@
 
-*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:Design_ER-ED)), similar to paradigms previously used by our group [@Scheffel2021].
+*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group [@Scheffel2021].
 Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
@@
 
-```{r Design_ER-ED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap="Block design of the paradigm.
-Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
+```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm.
+Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
 Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.

### 2022-03-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
changed name of figure

@@
 
-```{r Design_ER-ED_appendix, echo=FALSE, message=FALSE, warning=FALSE}
+```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE}
 include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))

### 2022-03-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
everything works now
knitted document

@@
 \shorttitle{Subjective values of emotion regulation strategies}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: X}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 139}
 \usepackage{lineno}
@@
 Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort.
-Relations of SVs to personality traits will be explored
+Relations of SVs to personality traits will be explored.
 }
@@
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
-Moreover it is known that ER strategies reduce physiological arousal, measured via electromyography (EMG) in the region of the \emph{corrugator supercilii}.\textsuperscript{5}
+Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)\textsuperscript{5} .
 So these tactics from three different strategies proved to be effective in the short term.
 However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered.
-Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed.\textsuperscript{6}
-Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of \emph{adaptive} and \emph{maladaptive} strategies.
-For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
-Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see Aldao et al.).\textsuperscript{8}
-
-The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put in a new perspective with the concept of ER flexibility.
-Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
-Adaptive flexible ER requires having a large repertoire of ER strategies.\textsuperscript{9}
-For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
+In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
+Longer lasting consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed.\textsuperscript{6}
+Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of \emph{adaptive} and \emph{maladaptive} ER strategies.
+For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
+In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al.).\textsuperscript{8}
+
+The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies was put in a new perspective with the concept of ER flexibility.
+Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible ER strategy use or use of strategies that are hindering goal achievement.\textsuperscript{9}
+Adaptive flexible ER requires a large repertoire of ER strategies.\textsuperscript{9}
+For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
 Strategies have to be chosen from the repertoire that are useful for goal achieving.
@@
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
-Afterwards they could choose, which strategy they want to use again.
+Afterwards, they choose which strategy they wanted to use again.
 Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
-Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
+Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
 What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
@@
 
-The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put into a new perspective with the concept of ER flexibility.
-Similar to other psychological domains such as attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or the use of strategies that are hindering the achievement of goals.\textsuperscript{9}
-In contrast, \emph{adaptive} ER requires having a large repertoire of ER strategies to choose from\textsuperscript{9} and choosing the strategy that is useful for goal achievement in a particular situation.
-This greater ER variability has been shown to be related to reduced negative affect.\textsuperscript{10}
-The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option.\textsuperscript{11}
-Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
-Effort in particular appeared to be the main factor in ER choice behaviour in our previous work.\textsuperscript{14}
-In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
-Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
-Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
-Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
-However, nothing has been investigated regarding the strategy that is \emph{not} chosen.
-
-We assume that people choose the strategy that has the highest value for them at that moment.
+We assume that people choose the strategy that has the highest value for them at the moment.
 The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{9}
 One certainly central goal is the regulation of negative affect.
-A second, intrinsic and rather less obvious goal is the avoidance of effort.\textsuperscript{15}
+A second, intrinsic and less obvious goal is the avoidance of effort.\textsuperscript{15}
 When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
@@
 In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
-Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption taht teh objectively easiest \emph{n}-back level has the highest SV.
-In the current study, we want to use this paradigm to determine SVs of ER strategies.
+Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
+In the present study, we want to use this paradigm to determine SVs of ER strategies.
 In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
@@
 But our paradigm can also account for the case that a person does not have a clear preference.
-Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
+Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
 Additionally, we will test our adapted paradigm in a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).
@@
 \begin{figure}
-\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/Other/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
 In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can also be represented by our paradigm.}\label{fig:fig1}
+This pattern can be represented by our paradigm.}\label{fig:ResponsePatterns}
 \end{figure}
 
-\hypertarget{the-present-study}{%
-\subsection{1.2 The present study}\label{the-present-study}}
-
-The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies.
-As a manipulation check, we want to explore whether ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and require cognitive effort.
-The following hypotheses are proposed for this purpose:
+The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies.
+As a manipulation check, we want to investigate whether the ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and physiological responses as well as whether they require cognitive effort.
+The following hypotheses are proposed:
 
@@
 \item
-  H1b) Physiological arousal (EMG \emph{corrugator} activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+  H2a) Physiological responses in facial EMG that is sensitive to negative emotion (\emph{corrugator} activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 \item
-  H1c) Physiological arousal (EMG \emph{levator} activity) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+  H2b) Physiological responses in facial EMG that is sensitive to negative emotion (\emph{levator} activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 \item
-  H2a) Subjective effort (effort ratings) is greater after using an Er strategy (distraction, distancing, suppression) compared to active viewing.
+  H3a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 \item
-  H2b) The majority of participants ruse the strategy that was least effortful for them.
+  H3b) The majority of participants re-uses the strategy that was least effortful for them.
 \end{itemize}
 
-Further we want to explore which variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
+Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
 
@@
 \item
-  H3a) Subjective effort ratings negatively predict SVs of ER strategies.
+  H4a) Subjective effort ratings negatively predict SVs of ER strategies.
 \item
-  H3b) Subjective arousal ratings negatively predict SVs of ER strategies.
+  H4b) Subjective arousal ratings negatively predict SVs of ER strategies.
 \item
-  H3c) EMG \emph{corrugator} activity negatively predict SVs of ER strategies.
+  H4c) EMG \emph{corrugator} activity negatively predicts SVs of ER strategies.
 \item
-  H3d) EMG \emph{levator} activity negatively predict SVs of ER strategies.
+  H4d) EMG \emph{levator} activity negatively predicts SVs of ER strategies.
 \item
-  H4a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, \emph{corrugator} and \emph{levator} activity.
+  H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, \emph{corrugator} and \emph{levator} activity.
 \end{itemize}
 
-We also want to explore whether SVs are related to flexible emotion regulation:
+We also want to investigate whether SVs are related to flexible emotion regulation:
 
@@
 \item
-  H5a) The higher the SV, the more likely the respective strategy is chosen.
+  H6a) The higher the SV, the more likely the respective strategy is chosen.
 \item
-  H5b) SVs are lower and decline stronger when ER flexibility is lower.
+  H6b) SVs are lower and decline stronger when ER flexibility is lower.
 \end{itemize}
@@
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{18}
-The paradigm was written and presented using \emph{Psychopy}.\textsuperscript{19}
+The paradigm was written and presented using \emph{PsychoPy}.\textsuperscript{19}
 We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all analyses.
@@
 
-The procedure described above was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
-Results showed significant higher subjective arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
-ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
-However, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
-Yet we found in accordance with our previous studies\textsuperscript{14} that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+The newly developed ER paradigm was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
+Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
+However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
+Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
+In accordance with our previous study,\textsuperscript{14} we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}
 
@@
 
-Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
+Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
-Before each session, participants receive information about the respective experimental procedure and provide informed consent.
-At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
-Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
-The second session, containing the ER paradigm, takes place exactly one week after session one.
-Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
-A brief training ensures that all participants are able to implement the ER strategies.
-Next, electrodes to measure EMG being attached and the ER paradigm is conducted.
-Participants receive 30.00€ or course credit as compensation.
-Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{25,26}
+Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
+The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
+Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
+At the beginning of the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
+Then, they will complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
+The second session will comprise the ER paradigm and take place exactly one week after session one.
+Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
+A brief training will ensure that all participants are able to implement the ER strategies.
+Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{25,26}
 
@@
 
-The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{27,28}
-To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{31} is used.
-Habitual use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
-For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{33}
-Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{34}
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{35,36} is used.
-To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{37} the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS),\textsuperscript{39,40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
-Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{43}
+The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale.\textsuperscript{27,28}
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{31} will be used.
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
+For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{33}
+Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from.\textsuperscript{34}
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{35,36} will be used.
+To assess self-control,\textsuperscript{37} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS),\textsuperscript{39,40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
+Attentional control will be assessed using the Attentional Control Scale (ACS).\textsuperscript{43}
 For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
@@
 
-The ER paradigm roughly consists of three parts that will be described in the following.
-
-\emph{Part one: ER task.} Part one is a standard ER task in a block design (see Figure X), similar to paradigms previously used by our group.\textsuperscript{14}
-Participants are told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
-Every participant first has the condition ``active viewing-neutral'' that serves as a baseline condition.
-During this block, 20 neutral pictures are presented.
-Participants are asked to ``actively view all pictures and permit all emotions that may arise.'' In the second block, participants actively viewe negative pictures.
-During the third, fourth, and fifth block, participants see negative pictures and are asked to regulate their emotions using distraction, distancing, and suppression.
-In order to achieve distraction, participants are asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants are asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.'' Participants are told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants are told to ``suppress their emotional facial expression.'' They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
-Participants are instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{14}
-All participants receive written instruction and complete a training session.
-After the training session, participants are asked about their applied ER strategies to avoid misapplication.
-The order of the three regulation blocks (distraction, distancing, and suppression) is randomized between participants.
-
-\emph{Part two: ER effort discounting.} In the second part, ER effort discounting takes place.
-The procedure of the discounting follows the COG-ED paradigm by Westbrook et al.\textsuperscript{17} with major change.
-We use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values are presented.
-The order of the comparisons is randomized.
-Because there is no strategy that is objectively more difficult, we added an initial comparison that begins with the option ``1 EUR for strategy A or 1 EUR for strategy B''.
-The strategy that is not chosen is assigned the value of 2 EUR.
-From this point on, comparisons between strategies follow the original COG-ED paradigm.\textsuperscript{17}
-Participants are instructed to decide as realistically as possible, imagining the displayed money would really be up for election.
-
-\emph{Part three: ER choice.} After the discounting part, participants choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
-Importantly, there are no further instruction on what basis they should make their decision.
-Participants should make their decision freely, according to the criteria they consider important for themselves.
-However, participants are asked to state the reasons for the decision afterwards.
-As soon as they have decided, they see the respective instruction and the block with another 20 negative pictures starts.
+The ER paradigm will consist of three parts that will be described in the following.
+
+\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group.\textsuperscript{14}
+Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
+Every participant first will have the condition ``active viewing-neutral'' that serves as a baseline condition.
+During this block, 20 neutral pictures will be presented.
+Participants will be asked to ``actively view all pictures and permit all emotions that may arise.''
+In the second block, participants will actively view negative pictures.
+During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
+In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
+During distancing, participants will be asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
+Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
+During suppression, participants will be told to ``suppress their emotional facial expression.''
+They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
+Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{14}
+All participants will receive written instruction and complete a training session.
+After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
+The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
+
+\emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
+The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{17} with a major change.
+We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values will be presented.
+The order of the comparisons will be randomized.
+Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
+The strategy that is not chosen will be assigned the value of 2 €.
+From this point on, comparisons between strategies will follow the original COG-ED paradigm.\textsuperscript{17}
+Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
+
+\emph{Part three: ER choice.} After the discounting part, participants will choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
+Importantly, there will be no further instruction on what basis they should make their decision.
+Participants should make their decision freely, according to criteria they consider important for themselves.
+However, participants will be asked to state the reasons for the decision afterwards.
+As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Design_ER-ED} \caption{Block design of the paradigm.
+Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
+Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
+After, the discounting procedure takes place.
+All three regulation strategies are pairwise compared.
+Before the last block, participants can decide which regulation strategy they want to reapply.
+Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.}\label{fig:DesignERED}
+\end{figure}
 
@@
 
-Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{44} and the International Affective Picture System (IAPS).\textsuperscript{45}
+Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{44} and the International Affective Picture System (IAPS).\textsuperscript{45}
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
-Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
-An evolutionary algorithm\textsuperscript{46} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
+An evolutionary algorithm\textsuperscript{46} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material 1.
@@
 
-Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence.\textsuperscript{47}
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{48}
+Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence,\textsuperscript{47} similar to previous work by our group.\textsuperscript{48}
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{49}
 The ground electrode will be placed over the left \emph{Mastoid}.
@@
 
-Sample size calculation is done using \emph{G*Power}.\textsuperscript{49,50}
-In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.
-To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of least \(N=85\) have to be analyzed.
+Sample size calculation is done using \emph{G*Power}.\textsuperscript{50,51}
+In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported:
+To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of at least \(N=85\) have to be analyzed.
 Power analyses of all other hypotheses yielded smaller sample sizes.
 However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aim to collect data of 90 participants.
+Therefore, we aim to collect data of XX participants.
 Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.
@@
 
-\emph{Effects of emotion regulation on arousal, facial EMG and effort} To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
+\emph{Effects of emotion regulation on arousal, facial EMG and effort.} To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
 To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
@@
 
-\emph{Subjective values of emotion regulation strategies} For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
 Second, the resulting (monetary) value will be divided by 2.00 €.
 The final SV for each participant will be computed by averaging all final SVs of each strategy.
-The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
-Again, estimated, marginal means will be computed as post-hoc contrasts.
-
-To investigate, whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
-Furthermore, an ordinal logistic regression with dependent variable choice and independent variables SVs of each strategy will be computed.
-
-To explore the association between subjective arousal, physiological arousal, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{51}
+The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) and explore group effects.
+Again, estimated marginal means will be computed as post-hoc contrasts.
+
+To investigate whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
+Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
+
+To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{52}
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
 Restricted maximum likelihood (REML) will be applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological arousal (\emph{corrugator} activity and \emph{levator} activity) as level-1-predictor will be specified.
+A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
 \[
 SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
-\] Level-1-predictors will be centered within cluster.\textsuperscript{52}
+\]
+Level-1-predictors will be centered within cluster.\textsuperscript{53}
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses both, \(p\)-values and Bayes factor \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{23} will be reported.
-Bayses factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
+For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{23} will be reported.
+Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
 
@@
 
+\leavevmode\hypertarget{ref-Gaertner2021}{}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Gärtner, A., Jawinski, P.
+\& Strobel, A.
+Individual differences in inhibitory control are not related to emotion regulation.
+\emph{PsyArXiv} (2021) doi:\href{https://doi.org/10.31234/osf.io/cd8rx}{10.31234/osf.io/cd8rx}.}
+
 \leavevmode\hypertarget{ref-Fridlund1986}{}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Fridlund, A. J. \& Cacioppo, J. T. Guidelines for human electromyographic research. \emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
@@
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Enders, C.
@@
 \leavevmode\hypertarget{ref-Preece2020}{}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Preece, D.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2010}{}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2015}{}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 
-\hypertarget{author-contributions}{%
-\section{Author Contributions}\label{author-contributions}}
-
-CS, AS, and JZ conceptualized the study and its methodology.
-CS and JZ acquired funding, investigated, administered the project, and wrote the software.
-CS, JZ, and AG did the formal analysis.
-CS and JZ visualized the results, and prepared the original draft.
-All authors reviewed, edited, and approved the final version of the manuscript.
-
 \hypertarget{competing-interests}{%
@@
 \begin{figure}
-\includegraphics[width=0.98\linewidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/99_Thinktank/Other/Paradigm_Scheme_T2} \caption{ }\label{fig:fig1appendix}
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
 \end{figure}
 
-\emph{Figure 1.} Exemplary visualization of two response patterns.
+\emph{Figure 1.}
+Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
+\end{figure}
+
+\emph{Figure 2.}
+Block design of the paradigm.
+Every participant starts with two ``active viewing'' blocks continaing neutral (Block 1) and negative (Block 2) pictures.
+Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place.
+All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply.
+Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
+
 \hypertarget{DesignTable}{%
@@
 
-\hypertarget{supplement}{%
-\section{Supplement}\label{supplement}}
+\hypertarget{SupplementaryMaterial}{%
+\section{Supplementary Material}\label{SupplementaryMaterial}}
 
@@
 Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{6,32}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{53}
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{54}
 
@@
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{36,54} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{55}
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{36,55} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{56}
 
@@
 
-\hypertarget{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
-\subsection{\texorpdfstring{Pilot study: Physiological arousal (\emph{Corrugator} and \emph{Levator} activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}{Pilot study: Physiological arousal (Corrugator and Levator activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}}\label{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
+\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
+\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
 
@@
 
-\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}
 
@@
 
-\hypertarget{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{\texorpdfstring{Pilot study: Physiological arousal (\emph{Corrugator} and \emph{Levator} activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological arousal (Corrugator and Levator activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-arousal-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}
+\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}{%
+\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}
 
@@
 
-\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological arousal (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{llllllll}
+\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+
+\begin{tabular}{lllllllll}
 \toprule
-contrast & \multicolumn{1}{c}{estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{t.ratio} & \multicolumn{1}{c}{p.value} & \multicolumn{1}{c}{Eta2 (partial)} & \multicolumn{1}{c}{95% CI}\\
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
 \midrule
-$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 0.19 & {}[0.05, 1.00]\\
-$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 0.21 & {}[0.06, 1.00]\\
-$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 0.20 & {}[0.06, 1.00]\\
-$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 1.78e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 7.22e-04 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 2.36e-04 & {}[0.00, 1.00]\\
+$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 4,962.89 & 0.19 & {}[0.05, 1.00]\\
+$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 616.63 & 0.21 & {}[0.06, 1.00]\\
+$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 11,678.82 & 0.20 & {}[0.06, 1.00]\\
+$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 0.07 & 1.78e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 0.08 & 7.22e-04 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 0.06 & 2.36e-04 & {}[0.00, 1.00]\\
 \bottomrule
@@
 
-\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological arousal (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
 

### 2022-03-03 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd
finalized sample size calculation

@@
 # Methods
+
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
@@
 Sample size determination was mainly based on the results of the analyses of Westbrook et al. [-@Westbrook2013] (see [Design Table](#DesignTableSection)).
-As there was no prior evidence on the magnitude of an interaction between *n*-back level and NFC, we assumed a small to medium effect size of $f=.175$.
-Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] for a repeated measures ANOVA with within-between interaction indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
-The power analyses of all other hypotheses yielded smaller necessary sample sizes.
-To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 80 participants.
+The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and *n*-back level influencing SVs.
+Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
+However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
+To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aim to collect about $50\%$ more data sets than necessary, $N=120$ in total.
 

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Comment on Hypotheses, changed intro to hypotheses section

@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
-As a manipulation check, we want to investigate whether the ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and physiological responses as well as whether they require cognitive effort.
+As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological arousal (EMG).
+<!-- Denise: "or/and physiological valence" see comment below --> Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological arousal as well as whether they require cognitive effort.
 The following hypotheses are proposed:
@@
 m.E.
-müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.-->
+müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal?
+Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen.
+oder steht corrugator für arousal und levator für valence?
+dann auch so benennen.
+Außerdem subjective ratings auch immer konsistent benennen.
+Ich schlage vor hier in den hypothesen immer von subjective arousal zu sprechen, dies dann im Methodenteil über die subjective ratings operationalisieren (fehlt übrigens im Methodenteil noch.-->
 

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hypotheses
Added Hypotheses on valence manipulation check, changed numbering of hypotheses

@@
 As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological arousal (EMG).
-<!-- Denise: "or/and physiological valence" see comment below --> Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological arousal as well as whether they require cognitive effort.
+<!-- Denise: "or/and physiological valence" see comment below --> Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological arousal as well as, third, whether they require cognitive effort.
 The following hypotheses are proposed:
@@
 Ich schlage vor hier in den hypothesen immer von subjective arousal zu sprechen, dies dann im Methodenteil über die subjective ratings operationalisieren (fehlt übrigens im Methodenteil noch.-->
+<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
 
-* H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2a) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2b) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
+* H1b) Physiological arousal (EMG *corrugator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
+* H1c) Physiological arousal (EMG *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures. 
+<!-- Denise: or physiological valence, see comment above -->
+
+* H2a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2c) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 * H3a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Updates to Hypotheses 2-3
reformulated Hypothses 2-3, updated comments on hypotheses

@@
 dann auch so benennen.
-Außerdem subjective ratings auch immer konsistent benennen.
-Ich schlage vor hier in den hypothesen immer von subjective arousal zu sprechen, dies dann im Methodenteil über die subjective ratings operationalisieren (fehlt übrigens im Methodenteil noch.-->
+Außerdem subjective arousal/ subjective effort auch immer konsistent benennen.
+Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
 <!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
@@
 
-* H2a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2b) Physiological responses in facial EMG that is sensitive to negative emotion (*corrugator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2c) Physiological responses in facial EMG that is sensitive to negative emotion (*levator* activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H3a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2a) Subjective arousal is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) Physiological arousal <!-- Denise: or physiological valence, see comment above --> (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2c) Physiological arousal <!-- Denise: or physiological valence, see comment above --> (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+
+* H3a) Subjective effort is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 * H3b) The majority of participants re-uses the strategy that was least effortful for them.

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hypotheses 4
comment on Hyp. 4, reformulated Hyp. 4

@@
 
-* H4a) Subjective effort ratings negatively predict SVs of ER strategies.
-* H4b) Subjective arousal ratings negatively predict SVs of ER strategies.
-* H4c) EMG *corrugator* activity negatively predicts SVs of ER strategies.
-* H4d) EMG *levator* activity negatively predicts SVs of ER strategies.
+* H4a) Subjective effort negatively predicts SVs of ER strategies.
+* H4b) Subjective arousal negatively predicts SVs of ER strategies.
+* H4c) Physiological arousal / valence (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
+* H4d) Physiological arousal / valence (EMG *levator* activity) negatively predicts SVs of ER strategies.
+
+<!-- Denise: Für Hyp. 4 kann ich leider ganz schlecht beurteilen, ob eure stat. Analyse diese Hyp. beantwortet, da ich die stat. Analyse noch nicht so richtig verstanden habe -->
+
 * H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hypoth. 3b
comment on statistical testing and recomendation for alternative formulation of Hyp. 3
Hypoth. 5
added comment

@@
 * H3b) The majority of participants re-uses the strategy that was least effortful for them.
+<!-- Könnt ihr diese Hypothese statistisch testen?
+Finde im 'Analysis Plan' nicht, wie ihr das testen möchtet, das muss dort noch erklärt werden.
+Mein Vorschlag für diese Hypothese: When having free choice, participants re-use the strategy with less subjective effort.-->
 
@@
 
+<!-- Gibt es zu Hyp.
+5 einen Abschnitt im 'Analysis Plan'?
+Das MLM?
+Ich schlage vor, dass der Analysis Plan streng nach den Hypothesen geordnet wird, dann ist es viel leichter zu lesen, zu verstehen und ihr vergesst auch nichts.-->
+
 We also want to investigate whether SVs are related to flexible emotion regulation:

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hyp. 5
reformulated Hyp. 5

@@
 
-* H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.
+* H5a) SVs decline with increasing effort, even after controlling for task performance (decline in subjective arousal after ER), and physiological arousal (EMF *corrugator* and *levator* activity).
 

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hyp. 6
comments on Hyp. 6a and 6b

@@
 
-We also want to investigate whether SVs are related to flexible emotion regulation:
+We also want to investigate whether SVs are related to flexible emotion regulation: <!-- Denise: Ihr habt ER Flex schon im Theoretischen Hintergrund eingeführt, aber mir fehlt noch bischen der differentielle Aspekt, den ihr ja hier untersuchen wollt.
+Ich versuche, dies mal oben reinzuformulieren.
+-->
 
-* H6a) The higher the SV, the more likely the respective strategy is chosen.
+* H6a) The higher the SV, the more likely the respective strategy is chosen. <!-- warum ist diese Hyp. hier bei ER Flexbility?-->
 * H6b) SVs are lower and decline stronger when ER flexibility is lower.
 
+<!-- Denise: Hyp.
+6b Was heißt "decline stronger?" Meint ihr "decline stronger with increasing effort" oder "decline from strategy A to stratey B"?
+Mein Problem ist, dass ich immer noch nicht 100% durch das ERED Paradigma durchsteige und die Auswertung der SVs auch noch nicht 100% verstehe.
+Das liegt nicht unbedingt an eurem Methodenteil, aber eventuell muss das noch etwas ausführlicher beschrieben werden.
+Da es anderen Reviewers ja auch so gehen könnte.-->
+
 Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely *n*-back.

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Deleted and changed sentences in the first paragraphs.

@@
 
-Every day we are confronted with stressful or emotionally demanding situations. 
 The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
@@
 This postulated temporal sequence of ER strategies influences their effectiveness.
-It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
-Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
+Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27) [@Webb2012].
 Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Comments Theoretical Background
Comments on EMG part

@@
 This postulated temporal sequence of ER strategies influences their effectiveness.
-Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27) [@Webb2012].
-Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
-Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
+Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
+In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
+
+Moreover, it is known that ER strategies <!-- all these strategies?--> reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
 <!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
@@
 Können aber auch warten, was die Reviewer sagen.-->
+<!-- Denise: Ja das ist noch ein schwächerer Punkt in der Intro.
+Ich habe auch nur Paper gefunden, die EMG corrugator und levator für negative valence berichten, levator eher für Ekel, aber das muss hier kommen.
+Ein Satz für EMG reicht nicht aus.
+Wenn ihr weder auf Valence noch auf Arousal (so wie ich bei den Hypothesen noch vorgeschlagen hatte) hier gehen möchtet, dann könnte man das Konstrukt ja muscle activation o.ä.
+nennen und dies dann im Methodenteil über EMG corrugator und levator operationalisieren.
+Ich denke aber, dass die getrennte Analyse der beiden Muskelgruppen nivht gerechtfertig ist, da ihr ja keine getrennten Effekte annehmt, sondern der levator eventuel noch sinnvoll ist, da wir viele Ekelbilder haben.
+Habt ihr schonmal überlegt einen index über beide Aktivierungen zu bilden und dann darüber die Muskelaktivierung zu operationalisieren?
+Würde die Hypothesen und auch die Interpretation einfacher machen.
+Falls das nichts bringt, kann man explorativ immer noch die beiden EMGs getrennt analysieren und dies dann so berichten.
+-->
 So these tactics from three different strategies proved to be effective in the short term. 

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Theoretical Background
Rephrased a paragraph on short and long term consequences

@@
 -->
-So these tactics from three different strategies proved to be effective in the short term. 
-However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
-In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-Longer lasting consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed [@GrossJohn2003]. 
-Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
+Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences. 
+In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
+Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
+In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al.
+[@Aldao2010]), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
 For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
-In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al. [@Aldao2010]).
 

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Theoretical Background - Flexibility, Repertoire
rephrased paragraph, added literature suggestions, added comments

@@
 
-The postulation of *adaptive* and *maladaptive* ER strategies was put in a new perspective with the concept of ER flexibility.
-Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015].
+The postulation of *adaptive* and *maladaptive* ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
+Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015] <!--Tamir, M.
+(2016).
+Why do people regulate their emotions?
+A taxonomy of motives in emotion regulation.
+Personality and Social Psychology Review, 20(3), 199-222.
+doi:10.1177/1088868315586325 ;  Tamir, M., Bigman, Y.
+E., Rhodes, E., Salerno, J., & Schreier, J.
+(2015).
+An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making.
+Emotion, 15(1), 90-103.
+doi:10.1037/emo0000021  Könnte vor allem das 2.
+Paper noch hilfreich sein um mehr auf die Values hinzuargumentieren?
+Ist schon länger her, als ich das gelesen hab.
+Aber evtl.
+lohnt es sich, Tamir sagt hier, dass reguliert wird, wenn Personen annehmen, dass die Emotion die sie erzielen möchten, useful ist, also einen Wert hat.
+Das ist schon anders als die subjective Values, die ihr den ER Strategien zuschreiben möchtet, aber zeigt ja, dass die Analyse von Values im Rahmen von ER als Decision Making schon untersucht wurde, nur eben nicht direkt Values den Strategien zugeschrieben wurde-->.
 Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
+The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities (Bonanno & Burton, 2013 p.594).
+<!-- Bonanno, G.
+A., & Burton, C.
+L.
+(2013).
+Regulatory flexibility: An individual differences perspective on coping and emotion regulation.
+Perspect Psychol Sci, 8(6), 591-612.
+doi:10.1177/1745691613504116 -->
+A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology (Dixon-Gordon, Aldao, & De Los Reyes, 2015; Lougheed & Hollenstein, 2012; Southward, Altenburger, Moss, Cregg, & Cheavens, 2018).
+<!-- Dixon-Gordon, K.
+L., Aldao, A., & De Los Reyes, A.
+(2015).
+Repertoires of emotion regulation: A person-centered approach to assessing emotion regulation strategies and links to psychopathology.
+Cogn Emot, 29(7), 1314-1325.
+doi:10.1080/02699931.2014.983046
+Lougheed, J.
+P., & Hollenstein, T.
+(2012).
+A limited repertoire of emotion regulation strategies is associated with internalizing problems in adolescence.
+Social Development, 21(4), 704-721.
+doi:10.1111/j.1467-9507.2012.00663.x
+Southward, M.
+W., Altenburger, E.
+M., Moss, S.
+A., Cregg, D.
+R., & Cheavens, J.
+S.
+(2018).
+Flexible, yet firm: A model of healthy emotion regulation.
+Journal of Social and Clinical Psychology, 37(4), 231-251.
+doi:10.1521/jscp.2018.37.4.231-->
 For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Rephrased sentences to link ER flexibility/ER repertoire to ER choice and subjective values

@@
 doi:10.1521/jscp.2018.37.4.231-->
-For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
-Strategies have to be chosen from the repertoire that are useful for goal achieving.
+Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
+How do people choose strategies from their repertoire? 
+Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
 Evidence from other contexts (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
comments and rephrasing in ER choice paragraph,

@@
 Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
+
 How do people choose strategies from their repertoire? 
 Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
-Evidence from other contexts (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
+Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
+<!-- Der letzte Teil des Satzes klingt komisch, weiß aber nicht so richtig, was ihr sagen wollt.-->
 Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
-For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
-Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction [@Sheppes2011;@Sheppes2014].
-Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
-Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
+For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
+Higher intensity of the (negative) stimulus lead to a choice of rather disengaging strategies <!-- oder 'of tactics of attentional deployment'?-->, like distraction [@Sheppes2011;@Sheppes2014].
+ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
+With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
 In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.

### 2022-03-11 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
comment on argumentation towards SVs, some rephrasing of this argumenation

@@
 With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
-In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
+In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
 Afterwards, they choose which strategy they wanted to use again.
@@
 Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
-What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
+What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
 People choose a strategy that they prefer for different, relatively well-known reasons.
+<!-- Denise: Ist das so?
+Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason?
+Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert.
+Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde.
+Und das ihr deshalb nun so vorgeht?
+-->
 However, nothing is revealed about the strategy that is *not chosen*.
@@
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
-SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
+<!-- Genau, die Argumentation ist super, nur braucht ihr dafür oben den Hinweis auf die nicht gewählte Strategie?-->
+SVs of ER Strategies could therefore be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
 Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
 This would mean that all strategies are a good option for goal achievement.
-A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
-This in turn would mean that no strategy is a good choice to achieve ER goals.
+A second person with less flexibility, however, would show high SVs only for one or very few strategies.
+This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from. 
+Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.
 

### 2022-03-14 06_Paper/ER-ED/TheoreticalBackground.Rmd

@@
 Moreover, there is nothing like an objectively easiest ER strategy.
-Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
+Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 
 In this step, the same monetary value (i.e., 1 €) is assigned to both options.
@@
 The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
-In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
+In the following steps, the lower value is changed in every iteration according to Westbrook et al.
+[-@Westbrook2013] until the indifference point is reached.
+<!-- Hier komme ich noch nicht so ganz mit, könntet ihr das noch klarer beschreiben, was hier passiert?
+Meint ihr folgendes?: ...
+The lower monetary value is assigned to different options?
+oder The lower monetary value is further lowered?
+Also wird geschaut, wie tief der Wert sein muss, damit die andere Strategie gewählt wird?
+Sorry, obwohl ihr es schon so oft erklärt habt, bin ich hier immer noch lost, aber das könnte ja anderen Reviewers auch so gehen.
+Und das die Revs genau in Westbrook schauen, das könnt ihr leider nicht erwarten.
+-->
 This procedure will be repeated until all strategies have been compared.
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
-Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
-
+In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
+<!-- Figure 1 macht das Paradigma schon deutlicher, aber alles verstehe ich noch nicht, z.B.
+es könnte deutlicher werden, dass der monetäre Wert für die gewählte Strategie sich über die mehreren durchläufe ergibt (übrigens sprecht ihr manchmal von € manchmal von $ das sollte einheitlich sein).
+Und was ich leider gar nicht verstehe, ist wie sich immer der Wert 1 für die am Ende preferierte Strategie ergibt (also z.B.
+in der oberen Hälfte SV StrategyB(Strategy A) = 1)-->
 ```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
added reference bonanno

@@
 Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
-The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities (Bonanno & Burton, 2013 p.594).
-<!-- Bonanno, G.
-A., & Burton, C.
-L.
-(2013).
-Regulatory flexibility: An individual differences perspective on coping and emotion regulation.
-Perspect Psychol Sci, 8(6), 591-612.
-doi:10.1177/1745691613504116 -->
+The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities [@Bonanno2013].
 A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology (Dixon-Gordon, Aldao, & De Los Reyes, 2015; Lougheed & Hollenstein, 2012; Southward, Altenburger, Moss, Cregg, & Cheavens, 2018).

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
added references

@@
 The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities [@Bonanno2013].
-A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology (Dixon-Gordon, Aldao, & De Los Reyes, 2015; Lougheed & Hollenstein, 2012; Southward, Altenburger, Moss, Cregg, & Cheavens, 2018).
-<!-- Dixon-Gordon, K.
-L., Aldao, A., & De Los Reyes, A.
-(2015).
-Repertoires of emotion regulation: A person-centered approach to assessing emotion regulation strategies and links to psychopathology.
-Cogn Emot, 29(7), 1314-1325.
-doi:10.1080/02699931.2014.983046
-Lougheed, J.
-P., & Hollenstein, T.
-(2012).
-A limited repertoire of emotion regulation strategies is associated with internalizing problems in adolescence.
-Social Development, 21(4), 704-721.
-doi:10.1111/j.1467-9507.2012.00663.x
-Southward, M.
-W., Altenburger, E.
-M., Moss, S.
-A., Cregg, D.
-R., & Cheavens, J.
-S.
-(2018).
-Flexible, yet firm: A model of healthy emotion regulation.
-Journal of Social and Clinical Psychology, 37(4), 231-251.
-doi:10.1521/jscp.2018.37.4.231-->
+A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology [@DixonGordon2015;@Lougheed2012;@Southward2018]. 
 Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
@@
 For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
-Higher intensity of the (negative) stimulus lead to a choice of rather disengaging strategies <!-- oder 'of tactics of attentional deployment'?-->, like distraction [@Sheppes2011;@Sheppes2014].
+Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
 ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
deleted comment

@@
 What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
-People choose a strategy that they prefer for different, relatively well-known reasons.
+People choose a strategy that they prefer for different, relatively well-known reasons[@Sheppes2014].
 <!-- Denise: Ist das so?
@@
 In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
-<!-- Figure 1 macht das Paradigma schon deutlicher, aber alles verstehe ich noch nicht, z.B.
-es könnte deutlicher werden, dass der monetäre Wert für die gewählte Strategie sich über die mehreren durchläufe ergibt (übrigens sprecht ihr manchmal von € manchmal von $ das sollte einheitlich sein).
-Und was ich leider gar nicht verstehe, ist wie sich immer der Wert 1 für die am Ende preferierte Strategie ergibt (also z.B.
-in der oberen Hälfte SV StrategyB(Strategy A) = 1)-->
+
 ```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.
@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
-As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological arousal (EMG).
-<!-- Denise: "or/and physiological valence" see comment below --> Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological arousal as well as, third, whether they require cognitive effort.
+As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
+Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort.
 The following hypotheses are proposed:

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
added reference

@@
 How do people choose strategies from their repertoire? 
-Similarly to the expectancy-value model of emotion regulation <!-- Tamir et al, siehe comment oben --> it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
+Similarly to the expectancy-value model of emotion regulation [@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
 Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
-<!-- Der letzte Teil des Satzes klingt komisch, weiß aber nicht so richtig, was ihr sagen wollt.-->
 Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
@@
 -->
-However, nothing is revealed about the strategy that is *not chosen*.
 
@@
 * H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
-* H1b) Physiological arousal (EMG *corrugator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
-* H1c) Physiological arousal (EMG *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures. 
-<!-- Denise: or physiological valence, see comment above -->
+* H1b) Physiological responding (EMG *corrugator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
+* H1c) Physiological responding (EMG *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
 
 * H2a) Subjective arousal is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2b) Physiological arousal <!-- Denise: or physiological valence, see comment above --> (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2c) Physiological arousal <!-- Denise: or physiological valence, see comment above --> (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) Physiological responding (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2c) Physiological responding (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 
@@
 * H4b) Subjective arousal negatively predicts SVs of ER strategies.
-* H4c) Physiological arousal / valence (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
-* H4d) Physiological arousal / valence (EMG *levator* activity) negatively predicts SVs of ER strategies.
+* H4c) Physiological responding (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
+* H4d) Physiological responding (EMG *levator* activity) negatively predicts SVs of ER strategies.
 
-<!-- Denise: Für Hyp. 4 kann ich leider ganz schlecht beurteilen, ob eure stat. Analyse diese Hyp. beantwortet, da ich die stat. Analyse noch nicht so richtig verstanden habe -->
+* H5a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF *corrugator* and *levator* activity).
 
-* H5a) SVs decline with increasing effort, even after controlling for task performance (decline in subjective arousal after ER), and physiological arousal (EMF *corrugator* and *levator* activity).
+We also want to investigate whether SVs are related to flexible emotion regulation:
 
-<!-- Gibt es zu Hyp.
-5 einen Abschnitt im 'Analysis Plan'?
-Das MLM?
-Ich schlage vor, dass der Analysis Plan streng nach den Hypothesen geordnet wird, dann ist es viel leichter zu lesen, zu verstehen und ihr vergesst auch nichts.-->
-
-We also want to investigate whether SVs are related to flexible emotion regulation: <!-- Denise: Ihr habt ER Flex schon im Theoretischen Hintergrund eingeführt, aber mir fehlt noch bischen der differentielle Aspekt, den ihr ja hier untersuchen wollt.
-Ich versuche, dies mal oben reinzuformulieren.
--->
-
-* H6a) The higher the SV, the more likely the respective strategy is chosen. <!-- warum ist diese Hyp. hier bei ER Flexbility?-->
+* H6a) The higher the SV, the more likely the respective strategy is chosen.
 * H6b) SVs are lower and decline stronger when ER flexibility is lower.
 
-<!-- Denise: Hyp.
-6b Was heißt "decline stronger?" Meint ihr "decline stronger with increasing effort" oder "decline from strategy A to stratey B"?
-Mein Problem ist, dass ich immer noch nicht 100% durch das ERED Paradigma durchsteige und die Auswertung der SVs auch noch nicht 100% verstehe.
-Das liegt nicht unbedingt an eurem Methodenteil, aber eventuell muss das noch etwas ausführlicher beschrieben werden.
-Da es anderen Reviewers ja auch so gehen könnte.-->
-
 Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely *n*-back.

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
Theory
Updates

@@
 
-Moreover, it is known that ER strategies <!-- all these strategies?--> reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
+Moreover, it is known that ER strategies <!-- all these strategies?--> reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020].
+In particular, for Corrugator has been shwon...
+However, related to eklige Bilder as negative IAPS are mostly be... Levator
+(nur short term Effekte berichten wg. Überleitung)
 <!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
@@
 -->
+
 Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences. 
@@
 Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
-In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al.
-[@Aldao2010]), which led to the postulation of *adaptive* and *maladaptive* ER strategies.
-For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
+In addition, a number of ER strategies <!-- Anne: welche?
+siehe auch nöchster Kommentar, an irgendeiner Stelle würde ich ein zwei Beispiele nennen.--> have been associated with mental disorders (for meta-analytic review, see Aldao et al.
+[@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
+For example, it was shown that maladaptive ER strategies <!-- Anne: hier würde ich die konkrete Strategie(n) in Klammer nennen--> mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
 

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Theory
Update EMG

@@
 
-Moreover, it is known that ER strategies <!-- all these strategies?--> reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020].
-In particular, for Corrugator has been shwon...
-However, related to eklige Bilder as negative IAPS are mostly be... Levator
-(nur short term Effekte berichten wg. Überleitung)
+Psychophysiology provides further important information on the effectiveness of emotion regulation strategies.
+Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromoygraphy has been reported consistently across studies to be influenced by emotion regluation with even medium effect sizes [@Zaehringer2020].
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the Corrugtor muscle (associated with anger, sadness, and fear) and the levator muscle (associated with disgust) with _d~-~_ = 0.32 ([@Zaehringer2020]) and _d~-~_ = XXX (XXX), respectively.
+Similar effects have been reported for suppression (XXX) and distancing/distraction (XXX).
+
+einführen als Valenz: hier und/oder weiter unten!!!
+
 <!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
@@
 -->
+<!-- Anne: EMG wird ganz eindeutig in der Literatur für Valenz verwendet (und EDA oder pupil dilation für Arousal), ich finde, das sollten wir hier auch so labeln.
+Falls das aus irgendeinenm Grund blöd erscheint, würde ich alternativ überall von physiological responses sprechen.
+Aber "physiological valence" passt m.E.
+am besten.-->
 
@@
 <!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
+<!-- Anne: Ich habe jetzt Corrugator und Levator mal zusammengefasst-->
 
 * H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
-* H1b) Physiological responding (EMG *corrugator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
-* H1c) Physiological responding (EMG *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
+* H1b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
 
 * H2a) Subjective arousal is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2b) Physiological responding (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2c) Physiological responding (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 
@@
 * H4b) Subjective arousal negatively predicts SVs of ER strategies.
-* H4c) Physiological responding (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
-* H4d) Physiological responding (EMG *levator* activity) negatively predicts SVs of ER strategies.
+* H4c) Physiological responding (EMG *corrugator* and *levator* activity) negatively predicts SVs of ER strategies.
 

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
updated hypotheses

--- 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
-Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
+Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs[@Sheppes2014]. 
 For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
@@
 Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
-What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
-People choose a strategy that they prefer for different, relatively well-known reasons[@Sheppes2014].
+This could be seen as an indirect evidence that subjective effort has an influence on SVs of ER strategies
  <!-- Denise: Ist das so?
@@
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
-<!-- Genau, die Argumentation ist super, nur braucht ihr dafür oben den Hinweis auf die nicht gewählte Strategie?-->
 SVs of ER Strategies could therefore be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
@@
 
-* H2a) Subjective arousal is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2b) Physiological responding (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H2c) Physiological responding (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2a) Subjective arousal (arousal rating) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H3a) Physiological responding (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H3b) Physiological responding (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 
-* H3a) Subjective effort is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 * H3b) The majority of participants re-uses the strategy that was least effortful for them.
-<!-- Könnt ihr diese Hypothese statistisch testen?
-Finde im 'Analysis Plan' nicht, wie ihr das testen möchtet, das muss dort noch erklärt werden.
-Mein Vorschlag für diese Hypothese: When having free choice, participants re-use the strategy with less subjective effort.-->
 

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
updated hypotheses

@@
 * H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H3b) The majority of participants re-uses the strategy that was least effortful for them.
+* H5b) The majority of participants re-uses the strategy that was least effortful for them.
 
@@
 
-* H4a) Subjective effort negatively predicts SVs of ER strategies.
-* H4b) Subjective arousal negatively predicts SVs of ER strategies.
-* H4c) Physiological responding (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
-* H4d) Physiological responding (EMG *levator* activity) negatively predicts SVs of ER strategies.
+* H5a) Subjective effort (effort ratings) negatively predicts SVs of ER strategies.
+* H5b) Subjective arousal (arousal ratings) negatively predicts SVs of ER strategies.
+* H5c) Physiological responding (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
+* H5d) Physiological responding (EMG *levator* activity) negatively predicts SVs of ER strategies.
 
-* H5a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF *corrugator* and *levator* activity).
+* H6a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF *corrugator* and *levator* activity).
 
@@
 
-* H6a) The higher the SV, the more likely the respective strategy is chosen.
-* H6b) SVs are lower and decline stronger when ER flexibility is lower.
+* H7a) The higher the SV, the more likely the respective strategy is chosen.
+* H7b) SVs are lower and decline stronger when ER flexibility is lower.
 

### 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
edited comments

@@
 The postulation of *adaptive* and *maladaptive* ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
-Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015] <!--Tamir, M.
-(2016).
-Why do people regulate their emotions?
-A taxonomy of motives in emotion regulation.
-Personality and Social Psychology Review, 20(3), 199-222.
-doi:10.1177/1088868315586325 ;  Tamir, M., Bigman, Y.
-E., Rhodes, E., Salerno, J., & Schreier, J.
-(2015).
-An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making.
-Emotion, 15(1), 90-103.
-doi:10.1037/emo0000021  Könnte vor allem das 2.
-Paper noch hilfreich sein um mehr auf die Values hinzuargumentieren?
-Ist schon länger her, als ich das gelesen hab.
-Aber evtl.
-lohnt es sich, Tamir sagt hier, dass reguliert wird, wenn Personen annehmen, dass die Emotion die sie erzielen möchten, useful ist, also einen Wert hat.
-Das ist schon anders als die subjective Values, die ihr den ER Strategien zuschreiben möchtet, aber zeigt ja, dass die Analyse von Values im Rahmen von ER als Decision Making schon untersucht wurde, nur eben nicht direkt Values den Strategien zugeschrieben wurde-->.
+Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015].
 Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
@@
 Similarly to the expectancy-value model of emotion regulation [@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
-Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
+Evidence from other psychological domains (e.g., intertemporal choice[@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. 
 Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs[@Sheppes2014]. 
@@
 Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
-This could be seen as an indirect evidence that subjective effort has an influence on SVs of ER strategies
- <!-- Denise: Ist das so?
-Na gut, es gibt schon einiges an Choice und Goals, aber zu Effort als reason?
-Ich bin nicht ganz überzeugt davon, dass die Argumentation sich ab hier vor allem auf die nicht gewählte Strategie fokussiert.
-Kann man nicht auch sagen, dass es noch zu wenig zu effort gibt, das Scheffel2021 eine der ersten war, die mehrere Strategien hinsichtlich effort mit subjektiven, physiologischen und Verhaltensmaßen untersucht hat, dass sich nun die Frage stellt, was genau der subjektive Effort macht, nämlich den Subjective Value beeinflussen, dass dies eben auch für die gewählte Strategie oder im Vergleich mehrerer Taktiken noch nicht untersucht wurde.
-Und das ihr deshalb nun so vorgeht?
--->
+Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
+Furthermore, the research on ER choice lacks information regarding the strategies that were *not* chosen in each case.
+It is unclear whether people had clear preferences or whether the choice options were similarly attractive.
 
@@
 
-However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
+So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
+However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
 To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
@@
 The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
-In the following steps, the lower value is changed in every iteration according to Westbrook et al.
-[-@Westbrook2013] until the indifference point is reached.
-<!-- Hier komme ich noch nicht so ganz mit, könntet ihr das noch klarer beschreiben, was hier passiert?
-Meint ihr folgendes?: ...
-The lower monetary value is assigned to different options?
-oder The lower monetary value is further lowered?
-Also wird geschaut, wie tief der Wert sein muss, damit die andere Strategie gewählt wird?
-Sorry, obwohl ihr es schon so oft erklärt habt, bin ich hier immer noch lost, aber das könnte ja anderen Reviewers auch so gehen.
-Und das die Revs genau in Westbrook schauen, das könnt ihr leider nicht erwarten.
--->
+In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
 This procedure will be repeated until all strategies have been compared.
@@
 Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
-<!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
 

### 2022-03-15 06_Paper/ER-ED/method.Rmd
edited comments

@@
 The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
+Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
+Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
 
@@
 However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aim to collect data of XX participants.
+Therefore, we aim to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
 Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).

### 2022-03-16 06_Paper/ER-ED/TheoreticalBackground.Rmd
test
test

--- 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 
-Moreover, it is known that ER strategies <!-- all these strategies?--> reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
+Psychophysiology provides further important information on the effectiveness of emotion regulation strategies.
+Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromoygraphy has been reported consistently across studies to be influenced by emotion regluation with even medium effect sizes [@Zaehringer2020].
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the Corrugtor muscle (associated with anger, sadness, and fear) and the levator muscle (associated with disgust) with _d~-~_ = 0.32 ([@Zaehringer2020]) and _d~-~_ = XXX (XXX), respectively.
+Similar effects have been reported for suppression (XXX) and distancing/distraction (XXX).
+
+einführen als Valenz: hier und/oder weiter unten!!!
+test von heute
+
 <!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
@@
 -->
+<!-- Anne: EMG wird ganz eindeutig in der Literatur für Valenz verwendet (und EDA oder pupil dilation für Arousal), ich finde, das sollten wir hier auch so labeln.
+Falls das aus irgendeinenm Grund blöd erscheint, würde ich alternativ überall von physiological responses sprechen.
+Aber "physiological valence" passt m.E.
+am besten.-->
+
 Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences. 
@@
 Evidence from other psychological domains (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
-Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs[@Sheppes2014]. 
+Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
 For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
@@
 Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
-This could be seen as an indirect evidence that subjective effort has an influence on SVs of ER strategies
+What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.<!-- Denise: und fehlen nicht auch noch mehr Studien, die speziell effort im Blick haben? -->
+People choose a strategy that they prefer for different, relatively well-known reasons[@Sheppes2014].
 <!-- Denise: Ist das so?
@@
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
+<!-- Genau, die Argumentation ist super, nur braucht ihr dafür oben den Hinweis auf die nicht gewählte Strategie?-->
 SVs of ER Strategies could therefore be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
@@
 <!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
+<!-- Anne: Ich habe jetzt Corrugator und Levator mal zusammengefasst-->
 
 * H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
-* H1b) Physiological responding (EMG *corrugator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
-* H1c) Physiological responding (EMG *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
+* H1b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
 
-* H2a) Subjective arousal (arousal rating) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H3a) Physiological responding (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H3b) Physiological responding (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2a) Subjective arousal is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H2b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 
-* H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+* H3a) Subjective effort is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
 * H3b) The majority of participants re-uses the strategy that was least effortful for them.
+<!-- Könnt ihr diese Hypothese statistisch testen?
+Finde im 'Analysis Plan' nicht, wie ihr das testen möchtet, das muss dort noch erklärt werden.
+Mein Vorschlag für diese Hypothese: When having free choice, participants re-use the strategy with less subjective effort.-->
 

### 2022-03-16 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Update EMG Teil

@@
 
-Psychophysiology provides further important information on the effectiveness of emotion regulation strategies.
-Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromoygraphy has been reported consistently across studies to be influenced by emotion regluation with even medium effect sizes [@Zaehringer2020].
-For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the Corrugtor muscle (associated with anger, sadness, and fear) and the levator muscle (associated with disgust) with _d~-~_ = 0.32 ([@Zaehringer2020]) and _d~-~_ = XXX (XXX), respectively.
-Similar effects have been reported for suppression (XXX) and distancing/distraction (XXX).
-
-einführen als Valenz: hier und/oder weiter unten!!!
-test von heute
+Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see [@Zaehringer2020]).
+Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 ([@Zaehringer2020]).
+In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal (Burr et al., 2021; https://doi.org/10.1371/journal.pone.0247246).
+Similar effects have been reported for suppression (Burr et al., 2021), distancing (Gärtner et al., 2021), and distraction (Schönfelder et al., 2014 DOI: 10.1093/scan/nst116).
+Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
+<!-- Anne: please add references-->
 
@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
-As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
+As a manipulation check, we first want to investigate whether the valence of the pictures (neutral, negative) is effecting subjective and physiological responding (EMG).
 Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort.
@@
 m.E.
-müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal?
+müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.-->
+<!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal?
 Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen.
@@
 <!-- Denise: im analysis plan habt ihr auch den vergleich negative vs. neutral (active viewing) beschrieben, deshalb hab ich das hier mal als Hypothese aufgenommen-->
-<!-- Anne: Ich habe jetzt Corrugator und Levator mal zusammengefasst-->
+<!-- Anne: Ich habe jetzt Corrugator und Levator mal zusammengefasst.
+Ich habe noch keine ausführliche Begründung fürs EMG eingefügt =  würde ich nur machen, wenn das für die anderen Maße auch geplant ist, sonst sieht es m.E.
+komisch aus.-->
 

### 2022-03-16 06_Paper/ER-ED/TheoreticalBackground.Rmd

--- 2022-03-15 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 
-Moreover, it is known that ER strategies <!-- all these strategies?--> reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)[@Zaehringer2020] .
+Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see [@Zaehringer2020]).
+Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 ([@Zaehringer2020]).
+In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal (Burr et al., 2021; https://doi.org/10.1371/journal.pone.0247246).
+Similar effects have been reported for suppression (Burr et al., 2021), distancing (Gärtner et al., 2021), and distraction (Schönfelder et al., 2014 DOI: 10.1093/scan/nst116).
+Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
+<!-- Anne: please add references-->
+
 <!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
-As a manipulation check, we first want to investigate whether the valence (neutral, negative) of the pictures is effecting subjective and physiological responding (EMG).
+As a manipulation check, we first want to investigate whether the valence of the pictures (neutral, negative) is effecting subjective and physiological responding (EMG).
 Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort.
 The following hypotheses are proposed:
-<!-- es gibt bisher noch keine Begründnung/Einbettung der nachfolgenden Hypothesen.
-Z.B.: Warum wird Corrugator und Levator untersucht?
-m.E.
-müsste oben jeweils noch ein Satz ergänzt werden, warum genau diese Variable in der aktuellen Studie untersucht werden soll.--> <!-- Denise: ja, das hab ich auch bemerkt, ist EMG auch arousal?
-Dann dies erstens noch einführen und argumentieren und dann auch als physiological arousal aufführen.
-oder steht corrugator für arousal und levator für valence?
-dann auch so benennen.
-Außerdem subjective arousal/ subjective effort auch immer konsistent benennen.
-Ich schlage vor hier in den hypothesen immer von subjective arousal / effort zu sprechen, dies dann im Methodenteil über die subjective ratings / effort ratings zu operationalisieren (fehlt übrigens im Methodenteil noch.-->
 
 * H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
-* H1b) Physiological responding (EMG *corrugator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
-* H1c) Physiological responding (EMG *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
+* H1b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
 

### 2022-03-16 06_Paper/ER-ED/method.Rmd

@@
 Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
+It was followed by neutral or negative picture for a total of 6 seconds.
+After each block, participants retrospectively rated their subjective emotional arousal on a continous scale (ranging from "not at all aroused" to "very highly aroused") and their subjective effort (ranging from "not very exhausting" to "very exhausting") using a slider on screen.
 
@@
 
-*Effects of emotion regulation on arousal, facial EMG and effort.* <br> To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
+*Effect of valence on arousal and facial EMG.*<br> 
+To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
 
-To examine the impact of valence on facial EMG, a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for *corrugator* and *levator* activity.
-To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for *corrugator* and *levator* activity will be conducted.
-
-To examine the effect of ER strategies on cognitive effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG *corrugator* and *levator* activity.
 Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the *afex* package [@Singmann2021]
+rmANOVAS will be run using the *afex* package [@Singmann2021].
+
+*Effects of emotion regulation on arousal, facial EMG and effort.* <br> 
+To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
+
+To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity will be conducted.
+
+To examine the effect of ER strategies on subjective effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
+Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
+If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
+rmANOVAS will be run using the *afex* package [@Singmann2021].
 

### 2022-03-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
deleted comments

@@
 
-Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see [@Zaehringer2020]).
+Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see Zaehringer et al.[@Zaehringer2020]).
 Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
@@
 <!-- Anne: please add references-->
-
-<!-- hier ist noch der Bezug zum Arousal drin gewesen, habe ich angepasst.
-Corrugator habe ich raus genommen, weil auch Levator untersucht wird (müssten sonst m.E.
-beide genannt werden.) Generell fehlt noch etwas die Einbettung, warum die beiden ausgewählt wurden.
-Soll ich da noch etwas ergänzen?
-bei Zaehringer wird der Levator überhaupt nicht genannt, die Metaanalyse bezieht sich nur auf den Corrugator.
-Wir hatten damals gesagt, dass viele der negativen Bilder primär auch recht eklig sind und daher der Levator passender sein könnte, weil er speuzifisch auf Ekel zu reagieren scheint, der Corrugator hingegen auf negative Bilder im Allgemeinen.
-Prinzipiell haben wir aber für beide die gleichen Hypothesen.
-Können aber auch warten, was die Reviewer sagen.-->
-<!-- Denise: Ja das ist noch ein schwächerer Punkt in der Intro.
-Ich habe auch nur Paper gefunden, die EMG corrugator und levator für negative valence berichten, levator eher für Ekel, aber das muss hier kommen.
-Ein Satz für EMG reicht nicht aus.
-Wenn ihr weder auf Valence noch auf Arousal (so wie ich bei den Hypothesen noch vorgeschlagen hatte) hier gehen möchtet, dann könnte man das Konstrukt ja muscle activation o.ä.
-nennen und dies dann im Methodenteil über EMG corrugator und levator operationalisieren.
-Ich denke aber, dass die getrennte Analyse der beiden Muskelgruppen nivht gerechtfertig ist, da ihr ja keine getrennten Effekte annehmt, sondern der levator eventuel noch sinnvoll ist, da wir viele Ekelbilder haben.
-Habt ihr schonmal überlegt einen index über beide Aktivierungen zu bilden und dann darüber die Muskelaktivierung zu operationalisieren?
-Würde die Hypothesen und auch die Interpretation einfacher machen.
-Falls das nichts bringt, kann man explorativ immer noch die beiden EMGs getrennt analysieren und dies dann so berichten.
--->
-<!-- Anne: EMG wird ganz eindeutig in der Literatur für Valenz verwendet (und EDA oder pupil dilation für Arousal), ich finde, das sollten wir hier auch so labeln.
-Falls das aus irgendeinenm Grund blöd erscheint, würde ich alternativ überall von physiological responses sprechen.
-Aber "physiological valence" passt m.E.
-am besten.-->
 

### 2022-03-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
added references

@@
 Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
-For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 ([@Zaehringer2020]).
-In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal (Burr et al., 2021; https://doi.org/10.1371/journal.pone.0247246).
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 [@Zaehringer2020].
+In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal [@Burr2021]. 
 Similar effects have been reported for suppression (Burr et al., 2021), distancing (Gärtner et al., 2021), and distraction (Schönfelder et al., 2014 DOI: 10.1093/scan/nst116).

### 2022-03-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
added references

@@
 In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal [@Burr2021]. 
-Similar effects have been reported for suppression (Burr et al., 2021), distancing (Gärtner et al., 2021), and distraction (Schönfelder et al., 2014 DOI: 10.1093/scan/nst116).
+Similar effects have been reported for suppression [@Burr2021], distancing [@Gaertner2021], and distraction [@Schoenfelder2014].
 Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.

### 2022-03-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
deleted comment
added examples to psychopathology

@@
 Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
-<!-- Anne: please add references-->
 
@@
 Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
-In addition, a number of ER strategies <!-- Anne: welche?
-siehe auch nöchster Kommentar, an irgendeiner Stelle würde ich ein zwei Beispiele nennen.--> have been associated with mental disorders (for meta-analytic review, see Aldao et al.
+In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.
 [@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.

### 2022-03-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
added exmaples of maladaptive strategies

@@
 [@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
-For example, it was shown that maladaptive ER strategies <!-- Anne: hier würde ich die konkrete Strategie(n) in Klammer nennen--> mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
+For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
 

### 2022-03-17 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
changed figure orientation
knitted document, fixed figure placement

@@
 
-```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE}
+```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
 include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))

### 2022-03-17 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document, fixed figure placement

@@
 
-Every day we are confronted with stressful or emotionally demanding situations.
 The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
@@
 This postulated temporal sequence of ER strategies influences their effectiveness.
-It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal.\textsuperscript{4}
-Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
-Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
-Moreover, it is known that ER strategies reduce physiological responses of emotions, especially emotional valence as measured via facial electromyography (EMG)\textsuperscript{5} .
-So these tactics from three different strategies proved to be effective in the short term.
-However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered.
-In particular, strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-Longer lasting consequences of self-reported habitual use of ER strategies for affect and well-being have been discussed.\textsuperscript{6}
-Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the postulation of \emph{adaptive} and \emph{maladaptive} ER strategies.
-For example, it was shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
-In addition, a number of ER strategies have been associated with mental disorders (for meta-analytic review, see Aldao et al.).\textsuperscript{8}
-
-The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies was put in a new perspective with the concept of ER flexibility.
-Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible ER strategy use or use of strategies that are hindering goal achievement.\textsuperscript{9}
-Adaptive flexible ER requires a large repertoire of ER strategies.\textsuperscript{9}
-For example, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
-Strategies have to be chosen from the repertoire that are useful for goal achieving.
-Evidence from other contexts (e.g., intertemporal choice,)\textsuperscript{11} shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
-Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs.
-For example, it was shown that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{12}
-Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.\textsuperscript{12,13}
-Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
-Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{14}
-In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
+Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
+In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
+
+Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see Zaehringer et al.\textsuperscript{5}).
+Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with \emph{d\textsubscript{-}} = 0.32.\textsuperscript{5}
+In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal.\textsuperscript{6}
+Similar effects have been reported for suppression,\textsuperscript{6} distancing,\textsuperscript{7} and distraction.\textsuperscript{8}
+Importantly, results on electromyographic measures seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
+
+Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences.
+In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
+Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being.\textsuperscript{9}
+In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.),\textsuperscript{10} which led to the postulation of \emph{adaptive} (such as reappraisal, acceptance) and \emph{maladaptive} (such as suppression, rumination) ER strategies.
+For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms.\textsuperscript{11}
+
+The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
+Within this framework, \emph{maladaptive} refers to inflexible ER strategy use or use of strategies that are hindering goal achievement.\textsuperscript{12}
+Adaptive flexible ER requires a large repertoire of ER strategies.\textsuperscript{12}
+The term ``repertoire'' can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities.\textsuperscript{13}
+A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology.\textsuperscript{14--16}
+Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{17}
+
+How do people choose strategies from their repertoire?
+Similarly to the expectancy-value model of emotion regulation\textsuperscript{18} it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
+Evidence from other psychological domains (e.g., intertemporal choice\textsuperscript{19}) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
+Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs\textsuperscript{20}.
+For example, a study found that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{21}
+Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction.\textsuperscript{20,21}
+ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{20,22}
+With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{22}
+In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
 Afterwards, they choose which strategy they wanted to use again.
@@
 Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
-What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
-People choose a strategy that they prefer for different, relatively well-known reasons.
-However, nothing is revealed about the strategy that is \emph{not chosen}.
+Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
+Furthermore, the research on ER choice lacks information regarding the strategies that were \emph{not} chosen in each case.
+It is unclear whether people had clear preferences or whether the choice options were similarly attractive.
 
 We assume that people choose the strategy that has the highest value for them at the moment.
-The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{9}
+The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{12}
 One certainly central goal is the regulation of negative affect.
-A second, intrinsic and less obvious goal is the avoidance of effort.\textsuperscript{15}
-When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
+A second, intrinsic and less obvious goal is the avoidance of effort.\textsuperscript{23}
+When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{24}
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
-SVs of ER Strategies could be helpful to describe the ER repertoire\textsuperscript{9} more comprehensively.
+SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
 Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
 This would mean that all strategies are a good option for goal achievement.
-A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
-This in turn would mean that no strategy is a good choice to achieve ER goals.
-
-However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
+A second person with less flexibility, however, would show high SVs only for one or very few strategies.
+This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
+Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.
+
+So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
+However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
 To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
 Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
-Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED).\textsuperscript{17}
-
-In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
+Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED).\textsuperscript{25}
+
+In the original study by Westbrook et al.,\textsuperscript{25} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
 Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
@@
 In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
-As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{14}
+As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{22}
 Moreover, there is nothing like an objectively easiest ER strategy.
-Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined.
+Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
 In this step, the same monetary value (i.e., 1 €) is assigned to both options.
@@
 The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
-In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{17} until the indifference point is reached.
+In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{25} until the indifference point is reached.
 This procedure will be repeated until all strategies have been compared.
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
-Additionally, we will test our adapted paradigm in a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).
+In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).
 
@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies.
-As a manipulation check, we want to investigate whether the ER strategies distraction, distancing, and suppression effectively reduce emotional arousal and physiological responses as well as whether they require cognitive effort.
+As a manipulation check, we first want to investigate whether the valence of the pictures (neutral, negative) is effecting subjective and physiological responding (EMG).
+Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort.
 The following hypotheses are proposed:
+
+\begin{itemize}
+\item
+  H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures.
+\item
+  H1b) Physiological responding (EMG \emph{corrugator} and \emph{levator} activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
+\item
+  H2a) Subjective arousal (arousal rating) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+\item
+  H3a) Physiological responding (EMG \emph{corrugator} activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+\item
+  H3b) Physiological responding (EMG \emph{levator} activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+\item
+  H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+\item
+  H5b) The majority of participants re-uses the strategy that was least effortful for them.
+\end{itemize}
+
+Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
+
+\begin{itemize}
+\item
+  H5a) Subjective effort (effort ratings) negatively predicts SVs of ER strategies.
+\item
+  H5b) Subjective arousal (arousal ratings) negatively predicts SVs of ER strategies.
+\item
+  H5c) Physiological responding (EMG \emph{corrugator} activity) negatively predicts SVs of ER strategies.
+\item
+  H5d) Physiological responding (EMG \emph{levator} activity) negatively predicts SVs of ER strategies.
+\item
+  H6a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF \emph{corrugator} and \emph{levator} activity).
+\end{itemize}
+
+We also want to investigate whether SVs are related to flexible emotion regulation:
 
@@
 \item
-  H1a) Subjective arousal (arousal ratings) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
+  H7a) The higher the SV, the more likely the respective strategy is chosen.
 \item
-  H2a) Physiological responses in facial EMG that is sensitive to negative emotion (\emph{corrugator} activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-\item
-  H2b) Physiological responses in facial EMG that is sensitive to negative emotion (\emph{levator} activity) are lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-\item
-  H3a) Subjective effort (effort ratings) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-\item
-  H3b) The majority of participants re-uses the strategy that was least effortful for them.
-\end{itemize}
-
-Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
-
-\begin{itemize}
-\tightlist
-\item
-  H4a) Subjective effort ratings negatively predict SVs of ER strategies.
-\item
-  H4b) Subjective arousal ratings negatively predict SVs of ER strategies.
-\item
-  H4c) EMG \emph{corrugator} activity negatively predicts SVs of ER strategies.
-\item
-  H4d) EMG \emph{levator} activity negatively predicts SVs of ER strategies.
-\item
-  H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, \emph{corrugator} and \emph{levator} activity.
-\end{itemize}
-
-We also want to investigate whether SVs are related to flexible emotion regulation:
-
-\begin{itemize}
-\tightlist
-\item
-  H6a) The higher the SV, the more likely the respective strategy is chosen.
-\item
-  H6b) SVs are lower and decline stronger when ER flexibility is lower.
+  H7b) SVs are lower and decline stronger when ER flexibility is lower.
 \end{itemize}
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{18}
-The paradigm was written and presented using \emph{PsychoPy}.\textsuperscript{19}
-We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all analyses.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{26}
+The paradigm was written and presented using \emph{PsychoPy}.\textsuperscript{27}
+We used \emph{R} with \emph{R Studio}\textsuperscript{28,29} with the main packages \emph{afex}\textsuperscript{30} and \emph{BayesFactor}\textsuperscript{31} for all analyses.
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
@@
 Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
-In accordance with our previous study,\textsuperscript{14} we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+In accordance with our previous study,\textsuperscript{22} we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
 All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}
@@
 
-Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{24} at the Technische Universität Dresden.
+Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{32} at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
@@
 Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{25,26}
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{33,34}
 
@@
 
-The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale.\textsuperscript{27,28}
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{31} will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,32}
-For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{33}
-Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from.\textsuperscript{34}
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{35,36} will be used.
-To assess self-control,\textsuperscript{37} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS),\textsuperscript{38} the Brief Self-Control Scale (BSCS),\textsuperscript{39,40} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{41,42}
-Attentional control will be assessed using the Attentional Control Scale (ACS).\textsuperscript{43}
+The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale.\textsuperscript{35,36}
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{39} will be used.
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{9,40}
+For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{41}
+Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from.\textsuperscript{42}
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{43,44} will be used.
+To assess self-control,\textsuperscript{45} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS),\textsuperscript{46} the Brief Self-Control Scale (BSCS),\textsuperscript{47,48} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{49,50}
+Attentional control will be assessed using the Attentional Control Scale (ACS).\textsuperscript{51}
 For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
@@
 
-\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group.\textsuperscript{14}
+\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group.\textsuperscript{22}
 Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
@@
 They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{14}
+Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{22}
 All participants will receive written instruction and complete a training session.
@@
 The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
+Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
+Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
+It was followed by neutral or negative picture for a total of 6 seconds.
+After each block, participants retrospectively rated their subjective emotional arousal on a continous scale (ranging from ``not at all aroused'' to ``very highly aroused'') and their subjective effort (ranging from ``not very exhausting'' to ``very exhausting'') using a slider on screen.
 
 \emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
-The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{17} with a major change.
+The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{25} with a major change.
 We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values will be presented.
@@
 The strategy that is not chosen will be assigned the value of 2 €.
-From this point on, comparisons between strategies will follow the original COG-ED paradigm.\textsuperscript{17}
+From this point on, comparisons between strategies will follow the original COG-ED paradigm.\textsuperscript{25}
 Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
@@
 
-Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{44} and the International Affective Picture System (IAPS).\textsuperscript{45}
+Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{52} and the International Affective Picture System (IAPS).\textsuperscript{53}
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
 Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
-An evolutionary algorithm\textsuperscript{46} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+An evolutionary algorithm\textsuperscript{54} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material 1.
@@
 
-Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence,\textsuperscript{47} similar to previous work by our group.\textsuperscript{48}
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{49}
+Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence,\textsuperscript{55} similar to previous work by our group.\textsuperscript{7}
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{56}
 The ground electrode will be placed over the left \emph{Mastoid}.
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{47}
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{55}
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
@@
 
-Sample size calculation is done using \emph{G*Power}.\textsuperscript{50,51}
+Sample size calculation is done using \emph{G*Power}.\textsuperscript{57,58}
 In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported:
@@
 However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aim to collect data of XX participants.
+Therefore, we aim to collect data of \(N=120\) participants, about \(50%
+\) more data sets, than necessary.
 Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.
@@
 
-\emph{Effects of emotion regulation on arousal, facial EMG and effort.} To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
-
-To examine the impact of valence on facial EMG, a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for \emph{corrugator} and \emph{levator} activity.
-To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for \emph{corrugator} and \emph{levator} activity will be conducted.
-
-To examine the effect of ER strategies on cognitive effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+\emph{Effect of valence on arousal and facial EMG.}
+To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
+
+To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG \emph{corrugator} and \emph{levator} activity.
 Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the \emph{afex} package\textsuperscript{22}
+rmANOVAS will be run using the \emph{afex} package.\textsuperscript{30}
+
+\emph{Effects of emotion regulation on arousal, facial EMG and effort.}
+To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
+
+To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity will be conducted.
+
+To examine the effect of ER strategies on subjective effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
+Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
+If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
+rmANOVAS will be run using the \emph{afex} package.\textsuperscript{30}
 
@@
 
-To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{52}
+To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{59}
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 \]
-Level-1-predictors will be centered within cluster.\textsuperscript{53}
+Level-1-predictors will be centered within cluster.\textsuperscript{60}
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{23} will be reported.
+For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{31} will be reported.
 Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
@@
 
+\leavevmode\hypertarget{ref-Burr2021}{}%
+\CSLLeftMargin{6. }
+\CSLRightInline{Burr, D.
+A., Pizzie, R.
+G.
+\& Kraemer, D.
+J.
+M.
+Anxiety, not regulation tendency, predicts how individuals regulate in the laboratory: An exploratory comparison of self-report and psychophysiology.
+\emph{Plos One} \textbf{16}, (2021).}
+
+\leavevmode\hypertarget{ref-Gaertner2021}{}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Gärtner, A., Jawinski, P.
+\& Strobel, A.
+Individual differences in inhibitory control are not related to emotion regulation.
+\emph{PsyArXiv} (2021) doi:\href{https://doi.org/10.31234/osf.io/cd8rx}{10.31234/osf.io/cd8rx}.}
+
+\leavevmode\hypertarget{ref-Schoenfelder2014}{}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Schönfelder, S., Kanske, P., Heissler, J.
+\& Wessa, M.
+Time course of emotion-related responding during distraction and reappraisal.
+\emph{Social Cognitive and Affective Neuroscience} \textbf{9}, 1310--9 (2014).}
+
 \leavevmode\hypertarget{ref-GrossJohn2003}{}%
-\CSLLeftMargin{6. }
+\CSLLeftMargin{9. }
 \CSLRightInline{Gross, J.
@@
 
+\leavevmode\hypertarget{ref-Aldao2010}{}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Aldao, A., Nolen-Hoeksema, S.
+\& Schweizer, S.
+Emotion-regulation strategies across psychopathology: A meta-analytic review.
+\emph{Clinical Psychology Review} \textbf{30}, 217--237 (2010).}
+
 \leavevmode\hypertarget{ref-Yoon2013}{}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{11. }
 \CSLRightInline{Yoon, K.
@@
 
-\leavevmode\hypertarget{ref-Aldao2010}{}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Aldao, A., Nolen-Hoeksema, S.
-\& Schweizer, S.
-Emotion-regulation strategies across psychopathology: A meta-analytic review.
-\emph{Clinical Psychology Review} \textbf{30}, 217--237 (2010).}
-
 \leavevmode\hypertarget{ref-Aldao2015}{}%
-\CSLLeftMargin{9. }
+\CSLLeftMargin{12. }
 \CSLRightInline{Aldao, A., Sheppes, G. \& Gross, J. J. Emotion regulation flexibility. \emph{Cognitive Therapy and Research} \textbf{39}, 263--278 (2015).}
 
+\leavevmode\hypertarget{ref-Bonanno2013}{}%
+\CSLLeftMargin{13. }
+\CSLRightInline{Bonanno, G.
+A.
+\& Burton, C.
+L.
+Regulatory flexibility: An individual differences perspective on coping and emotion regulation.
+\emph{Perspectives on Psychological Science} \textbf{8}, 591--612 (2013).}
+
+\leavevmode\hypertarget{ref-DixonGordon2015}{}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Dixon-Gordon, K.
+L., Aldao, A.
+\& De Los Reyes, A.
+Repertoires of emotion regulation: A person-centered approach to assessing emotion regulation strategies and links to psychopathology.
+\emph{Cogn Emot} \textbf{29}, 1314--25 (2015).}
+
+\leavevmode\hypertarget{ref-Lougheed2012}{}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Lougheed, J.
+P.
+\& Hollenstein, T.
+A limited repertoire of emotion regulation strategies is associated with internalizing problems in adolescence.
+\emph{Social Development} \textbf{21}, 704--721 (2012).}
+
+\leavevmode\hypertarget{ref-Southward2018}{}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Southward, M.
+W., Altenburger, E.
+M., Moss, S.
+A., Cregg, D.
+R.
+\& Cheavens, J.
+S.
+Flexible, yet firm: A model of healthy emotion regulation.
+\emph{Journal of Social and Clinical Psychology} \textbf{37}, 231--251 (2018).}
+
 \leavevmode\hypertarget{ref-Blanke2020}{}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{17. }
 \CSLRightInline{Blanke, E. S. \emph{et al.} Mix it to fix it: Emotion regulation variability in daily life. \emph{Emotion} \textbf{20}, 473--485 (2020).}
 
+\leavevmode\hypertarget{ref-Tamir2015}{}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Tamir, M., Bigman, Y.
+E., Rhodes, E., Salerno, J.
+\& Schreier, J.
+An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making.
+\emph{Emotion} \textbf{15}, 90--103 (2015).}
+
 \leavevmode\hypertarget{ref-Kable2007}{}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{19. }
 \CSLRightInline{Kable, J. W. \& Glimcher, P. W. The neural correlates of subjective value during intertemporal choice. \emph{Nat Neurosci} \textbf{10}, 1625--33 (2007).}
 
+\leavevmode\hypertarget{ref-Sheppes2014}{}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Sheppes, G. \emph{et al.} Emotion regulation choice: A conceptual framework and supporting evidence. \emph{Journal of Experimental Psychology: General} \textbf{143}, 163--81 (2014).}
+
 \leavevmode\hypertarget{ref-Sheppes2011}{}%
-\CSLLeftMargin{12. }
+\CSLLeftMargin{21. }
 \CSLRightInline{Sheppes, G., Scheibe, S., Suri, G. \& Gross, J. J. Emotion-regulation choice. \emph{Psychological Science} \textbf{22}, 1391--6 (2011).}
 
-\leavevmode\hypertarget{ref-Sheppes2014}{}%
-\CSLLeftMargin{13. }
-\CSLRightInline{Sheppes, G. \emph{et al.} Emotion regulation choice: A conceptual framework and supporting evidence. \emph{Journal of Experimental Psychology: General} \textbf{143}, 163--81 (2014).}
-
 \leavevmode\hypertarget{ref-Scheffel2021}{}%
-\CSLLeftMargin{14. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Scheffel, C.
@@
 \leavevmode\hypertarget{ref-Inzlicht2018}{}%
-\CSLLeftMargin{15. }
+\CSLLeftMargin{23. }
 \CSLRightInline{Inzlicht, M., Shenhav, A. \& Olivola, C. Y. The effort paradox: Effort is both costly and valued. \emph{Trends Cogn Sci} \textbf{22}, 337--349 (2018).}
@@
 \leavevmode\hypertarget{ref-Hull1943}{}%
-\CSLLeftMargin{16. }
+\CSLLeftMargin{24. }
 \CSLRightInline{Hull, C. L. \emph{Principles of behavior: An introduction to behavior theory}. (Appleton-Century-Crofts, 1943).}
@@
 \leavevmode\hypertarget{ref-Westbrook2013}{}%
-\CSLLeftMargin{17. }
+\CSLLeftMargin{25. }
 \CSLRightInline{Westbrook, A., Kester, D.
@@
 \leavevmode\hypertarget{ref-Simmons2012}{}%
-\CSLLeftMargin{18. }
+\CSLLeftMargin{26. }
 \CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}
@@
 \leavevmode\hypertarget{ref-Peirce2019}{}%
-\CSLLeftMargin{19. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
@@
 \leavevmode\hypertarget{ref-RCore2021}{}%
-\CSLLeftMargin{20. }
+\CSLLeftMargin{28. }
 \CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}
@@
 \leavevmode\hypertarget{ref-RStudioTeam2020}{}%
-\CSLLeftMargin{21. }
+\CSLLeftMargin{29. }
 \CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}
@@
 \leavevmode\hypertarget{ref-Singmann2021}{}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{30. }
 \CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}
@@
 \leavevmode\hypertarget{ref-Morey2021}{}%
-\CSLLeftMargin{23. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
@@
 \leavevmode\hypertarget{ref-Greiner2015}{}%
-\CSLLeftMargin{24. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
@@
 \leavevmode\hypertarget{ref-Harris2009}{}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Harris2019}{}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
@@
 \leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
@@
 \leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
@@
 \leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Sarubin, N.
@@
 \leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Campbell-Sills, L.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
@@
 \leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
@@
 \leavevmode\hypertarget{ref-Bernecker2017}{}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Bernecker, K.
@@
 \leavevmode\hypertarget{ref-Cacioppo1982}{}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
@@
 \leavevmode\hypertarget{ref-Bless1994}{}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
@@
 \leavevmode\hypertarget{ref-Paschke2016}{}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Paschke, L.
@@
 \leavevmode\hypertarget{ref-Schwarzer1999}{}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}
@@
 \leavevmode\hypertarget{ref-Tangney2004}{}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Tangney, J.
@@
 \leavevmode\hypertarget{ref-Sproesser2011}{}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
@@
 \leavevmode\hypertarget{ref-Patton1995}{}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
@@
 \leavevmode\hypertarget{ref-Hartmann2011}{}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Hartmann, A.
@@
 \leavevmode\hypertarget{ref-Derryberry2002}{}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
@@
 \leavevmode\hypertarget{ref-Wessa2010}{}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Wessa, M.
@@
 \leavevmode\hypertarget{ref-Lang2008}{}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Lang, P.
@@
 \leavevmode\hypertarget{ref-Yu2010}{}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
@@
 \leavevmode\hypertarget{ref-Bradley2000}{}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Bradley, M.
@@
 
-\leavevmode\hypertarget{ref-Gaertner2021}{}%
-\CSLLeftMargin{48. }
-\CSLRightInline{Gärtner, A., Jawinski, P.
-\& Strobel, A.
-Individual differences in inhibitory control are not related to emotion regulation.
-\emph{PsyArXiv} (2021) doi:\href{https://doi.org/10.31234/osf.io/cd8rx}{10.31234/osf.io/cd8rx}.}
-
 \leavevmode\hypertarget{ref-Fridlund1986}{}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Fridlund, A. J. \& Cacioppo, J. T. Guidelines for human electromyographic research. \emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
@@
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Enders, C.
@@
 \leavevmode\hypertarget{ref-Preece2020}{}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Preece, D.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2010}{}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2015}{}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
@@
 \emph{WHO-5.}
-General psychological well-being is assessed using the WHO-5 scale\textsuperscript{27,28}.
+General psychological well-being is assessed using the WHO-5 scale\textsuperscript{35,36}.
 5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{28}.
+The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{36}.
 
 \emph{Connor-Davidson Resilience Scale.}
-Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{29--31}.
+Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{37--39}.
 10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{30}.
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{38}.
 
 \emph{Emotion Regulation Questionnaire.}
-Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{6,32}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{54}
+Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,40}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{61}
 
 \emph{FlexER Scale.}
-Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{33} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{41} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 Psychometric properties are currently under investigation.
@@
 \emph{Implicit Theories Questionnaire.}
-Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{34}
+Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{42}
 4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{34}.
+The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{42}.
 
 \emph{Need for Cognition Scale.}
-Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{36}
+Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{44}
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{36,55} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{56}
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{44,62} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{63}
 
 \emph{Self-Regulation Scale.}
-As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{38} is used.
+As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{46} is used.
 The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{38}
+It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{46}
 
 \emph{Brief Self-Control Scale.}
-As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{39,40} is used.
+As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{47,48} is used.
 It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{40} .
+The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{48} .
 
 \emph{Barratt Impulsiveness Scale.}
-As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{41,42} is used.
+As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{49,50} is used.
 Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{42}
+An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{50}
 
 \emph{Attentional Control Scale.}
-Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{43} with items such as ``My concentration is good even if there is music in the room around me''.
+Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{51} with items such as ``My concentration is good even if there is music in the room around me''.
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{43}
+An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{51}
 

### 2022-03-23 06_Paper/COG-ED/Manuscript.Rmd
changed contribs and added data exclusion sentence

@@
       - Conceptualization
-      - Methodology
-      - Formal analysis
+      - Funding acquistion
       - Writing - review & editing
@@
 Data collection and analysis will not be performed blind to the conditions of the experiments.
+We will exclude the data of a participant from all analyses, if the participant states that they did not follow the instructions or if the investigator notes that the participant misunderstood the instructions.
+No data will be replaced.
 We aim to conduct all analysis as described in Westbrook et al.
@@
 
-JZ and CS conceptualized the study and its methodology, acquired funding, investigated, administered the project, and wrote the software.
+JZ, CS, and AS conceptualized the study and acquired funding.
+JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
 JZ and CK did the formal analysis, visualized the results, and prepared the original draft.

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
author roles

@@
       - Software
+      - Visualization
       - Writing - review & editing

### 2022-03-24 06_Paper/COG-ED/Manuscript.Rmd
added ethics

@@
       - Formal analysis
-      - Writing - original draft preparation
       - Writing - review & editing
@@
 
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number SR-EK-50012022).
 Prior to testing, written informed consent will be obtained.
@@
 JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
+JZ prepared the original draft.
 All authors reviewed, edited, and approved the final version of the manuscript.

### 2022-03-24 06_Paper/ER-ED/method.Rmd
added data exclusions and ek number

@@
 We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.<!-- eventually perhaps refer to the _script and R Markdown file_ -->
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.
 A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
-<!-- Attention! OSF is still private -->
 
@@
 
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK...).
-<!-- Attention!add EK number, when approved -->
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022). 
 Prior to testing, written informed consent will be obtained.
@@
 Data collection and analysis will not be performed blind to the conditions of the experiments.
+Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
+EMG data of subjects will be excluded from analysis if errors occured during recording.
+No further data exclusions are planned.
 The level of significance will be set to $\alpha=.05$.

### 2022-03-24 06_Paper/COG-ED/Manuscript.Rmd

@@
 Data collection and analysis will not be performed blind to the conditions of the experiments.
-We will exclude the data of a participant from all analyses, if the participant states that they did not follow the instructions or if the investigator notes that the participant misunderstood the instructions.
+We will exclude the data of a participant from all analyses, if the participant states that they did not follow the instructions, if the investigator notes that the participant misunderstood the instructions, or if the participant withdraws their consent.
 No data will be replaced.

### 2022-03-24 06_Paper/COG-ED/Manuscript.Rmd
added word count

@@
 keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
-wordcount         : "X"
+wordcount         : "~ 3,700"
 bibliography      : CERED.bib
@@
 
+\newpage
+
 Physical subscale ANOVA:
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 Performance subscale ANOVA:
@@
 
+\newpage
+
 Effort subscale ANOVA:

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd

@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "139"
+wordcount         : "5583"
 bibliography      : ER_ED.bib

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex

@@
 \shorttitle{Subjective values of emotion regulation strategies}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 139}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5583}
 \usepackage{lineno}
@@
 The authors made the following contributions.
-Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Writing - review \& editing.
+Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Visualization, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Writing - review \& editing.
 \textsuperscript{$\dagger{}$} Christoph Scheffel and Josephine Zerna contributed equally to this work.

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
knitted document

--- 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "139"
+wordcount         : "5627"
 bibliography      : ER_ED.bib

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK\ldots).
+The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022).
 Prior to testing, written informed consent will be obtained.
@@
 Data collection and analysis will not be performed blind to the conditions of the experiments.
+Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
+EMG data of subjects will be excluded from analysis if errors occured during recording.
+No further data exclusions are planned.
 The level of significance will be set to \(\alpha=.05\).

### 2022-03-24 06_Paper/ER-ED/TheoreticalBackground.Rmd
knitted document

@@
 Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
-In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.
-[@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
+In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.[@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
 For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms [@Yoon2013].

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 \shorttitle{Subjective values of emotion regulation strategies}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5583}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5627}
 \usepackage{lineno}
@@
 Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being.\textsuperscript{9}
-In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.),\textsuperscript{10} which led to the postulation of \emph{adaptive} (such as reappraisal, acceptance) and \emph{maladaptive} (such as suppression, rumination) ER strategies.
+In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.\textsuperscript{10}), which led to the postulation of \emph{adaptive} (such as reappraisal, acceptance) and \emph{maladaptive} (such as suppression, rumination) ER strategies.
 For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms.\textsuperscript{11}

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
knitted document

--- 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "139"
+wordcount         : "5630"
 bibliography      : ER_ED.bib

### 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 \shorttitle{Subjective values of emotion regulation strategies}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5627}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5630}
 \usepackage{lineno}
@@
 The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
-It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning.\textsuperscript{2}
-Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification,\textsuperscript{1} and, following the taxonomy of Powers and LaBar,\textsuperscript{3} individuals can implement ER strategies by means of different tactics.
-So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process.\textsuperscript{1}
-In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy.\textsuperscript{1}
+It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning\textsuperscript{2}.
+Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification\textsuperscript{1}, and, following the taxonomy of Powers and LaBar\textsuperscript{3}, individuals can implement ER strategies by means of different tactics.
+So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process\textsuperscript{1}.
+In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy\textsuperscript{1}.
 This postulated temporal sequence of ER strategies influences their effectiveness.
 Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
-In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
+In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45\textsuperscript{4}.
 
@@
 Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
-For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with \emph{d\textsubscript{-}} = 0.32.\textsuperscript{5}
-In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal.\textsuperscript{6}
-Similar effects have been reported for suppression,\textsuperscript{6} distancing,\textsuperscript{7} and distraction.\textsuperscript{8}
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with \emph{d\textsubscript{-}} = 0.32\textsuperscript{5}.
+In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal\textsuperscript{6}.
+Similar effects have been reported for suppression\textsuperscript{6}, distancing\textsuperscript{7}, and distraction\textsuperscript{8}.
 Importantly, results on electromyographic measures seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
@@
 In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being.\textsuperscript{9}
+Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being\textsuperscript{9}.
 In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.\textsuperscript{10}), which led to the postulation of \emph{adaptive} (such as reappraisal, acceptance) and \emph{maladaptive} (such as suppression, rumination) ER strategies.
-For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms.\textsuperscript{11}
+For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms\textsuperscript{11}.
 
 The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
-Within this framework, \emph{maladaptive} refers to inflexible ER strategy use or use of strategies that are hindering goal achievement.\textsuperscript{12}
-Adaptive flexible ER requires a large repertoire of ER strategies.\textsuperscript{12}
-The term ``repertoire'' can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities.\textsuperscript{13}
-A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology.\textsuperscript{14--16}
-Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{17}
+Within this framework, \emph{maladaptive} refers to inflexible ER strategy use or use of strategies that are hindering goal achievement\textsuperscript{12}.
+Adaptive flexible ER requires a large repertoire of ER strategies\textsuperscript{12}.
+The term ``repertoire'' can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities\textsuperscript{13}.
+A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology\textsuperscript{14--16}.
+Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life\textsuperscript{17}.
 
@@
 Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs\textsuperscript{20}.
-For example, a study found that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{21}
-Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction.\textsuperscript{20,21}
-ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{20,22}
-With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{22}
+For example, a study found that the intensity of a stimulus or situation plays a role in the choice\textsuperscript{21}.
+Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction\textsuperscript{20,21}.
+ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort\textsuperscript{20,22}.
+With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy\textsuperscript{22}.
 In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
@@
 We assume that people choose the strategy that has the highest value for them at the moment.
-The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{12}
+The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement\textsuperscript{12}.
 One certainly central goal is the regulation of negative affect.
-A second, intrinsic and less obvious goal is the avoidance of effort.\textsuperscript{23}
-When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{24}
+A second, intrinsic and less obvious goal is the avoidance of effort\textsuperscript{23}.
+When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24}.
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
@@
 Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
-Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED).\textsuperscript{25}
-
-In the original study by Westbrook et al.,\textsuperscript{25} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
+Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)\textsuperscript{25}.
+
+In the original study by Westbrook et al.\textsuperscript{25}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
 Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
@@
 In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
-As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{22}
+As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies\textsuperscript{22}.
 Moreover, there is nothing like an objectively easiest ER strategy.
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
-In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).
+In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{26}).
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{26}
-The paradigm was written and presented using \emph{PsychoPy}.\textsuperscript{27}
-We used \emph{R} with \emph{R Studio}\textsuperscript{28,29} with the main packages \emph{afex}\textsuperscript{30} and \emph{BayesFactor}\textsuperscript{31} for all analyses.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{27}.
+The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{28}.
+We used \emph{R} with \emph{R Studio}\textsuperscript{29,30} with the main packages \emph{afex}\textsuperscript{31} and \emph{BayesFactor}\textsuperscript{32} for all analyses.
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
@@
 Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
-In accordance with our previous study,\textsuperscript{22} we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+In accordance with our previous study\textsuperscript{22}, we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
 All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}
@@
 
-Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{32} at the Technische Universität Dresden.
+Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{33} at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
@@
 Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{33,34}
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{34,35}.
 
@@
 
-The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale.\textsuperscript{35,36}
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{39} will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{9,40}
-For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{41}
-Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from.\textsuperscript{42}
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{43,44} will be used.
-To assess self-control,\textsuperscript{45} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS),\textsuperscript{46} the Brief Self-Control Scale (BSCS),\textsuperscript{47,48} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{49,50}
-Attentional control will be assessed using the Attentional Control Scale (ACS).\textsuperscript{51}
+The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{36,37}.
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{40} will be used.
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,41}.
+For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{42}.
+Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{43}.
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{44,45} will be used.
+To assess self-control,\textsuperscript{46} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{47}, the Brief Self-Control Scale (BSCS)\textsuperscript{48,49}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{50,51}.
+Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{52}.
 For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
@@
 
-\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group.\textsuperscript{22}
+\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
 Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
@@
 They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite.\textsuperscript{22}
+Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite\textsuperscript{22}.
 All participants will receive written instruction and complete a training session.
@@
 The strategy that is not chosen will be assigned the value of 2 €.
-From this point on, comparisons between strategies will follow the original COG-ED paradigm.\textsuperscript{25}
+From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{25}.
 Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
@@
 
-Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{52} and the International Affective Picture System (IAPS).\textsuperscript{53}
+Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{53} and the International Affective Picture System (IAPS)\textsuperscript{54}.
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
 Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
-An evolutionary algorithm\textsuperscript{54} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+An evolutionary algorithm\textsuperscript{55} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material 1.
@@
 
-Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence,\textsuperscript{55} similar to previous work by our group.\textsuperscript{7}
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{56}
+Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{56}, similar to previous work by our group\textsuperscript{7}.
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{57}
 The ground electrode will be placed over the left \emph{Mastoid}.
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{55}
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{56}
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
@@
 
-Sample size calculation is done using \emph{G*Power}.\textsuperscript{57,58}
-In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported:
+Sample size calculation is done using \emph{G*Power}\textsuperscript{58,59}.
+In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
 To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of at least \(N=85\) have to be analyzed.
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the \emph{afex} package.\textsuperscript{30}
+rmANOVAS will be run using the \emph{afex} package\textsuperscript{31}.
 
@@
 
-To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package.\textsuperscript{59}
+To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{60}.
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 \]
-Level-1-predictors will be centered within cluster.\textsuperscript{60}
+Level-1-predictors will be centered within cluster\textsuperscript{61}.
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package,\textsuperscript{31} will be reported.
+For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{32}, will be reported.
 Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
@@
 
+\leavevmode\hypertarget{ref-Zerna2022}{}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Zerna, S., J.
+\& Strobel, A.
+When easy is not preferred: An effort discounting for estimating subjective values of taks.
+\emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}
+
 \leavevmode\hypertarget{ref-Simmons2012}{}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{27. }
 \CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}
@@
 \leavevmode\hypertarget{ref-Peirce2019}{}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{28. }
 \CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
@@
 \leavevmode\hypertarget{ref-RCore2021}{}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{29. }
 \CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}
@@
 \leavevmode\hypertarget{ref-RStudioTeam2020}{}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{30. }
 \CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}
@@
 \leavevmode\hypertarget{ref-Singmann2021}{}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}
@@
 \leavevmode\hypertarget{ref-Morey2021}{}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
@@
 \leavevmode\hypertarget{ref-Greiner2015}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
@@
 \leavevmode\hypertarget{ref-Harris2009}{}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Harris2019}{}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
@@
 \leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
@@
 \leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
@@
 \leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Sarubin, N.
@@
 \leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Campbell-Sills, L.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
@@
 \leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
@@
 \leavevmode\hypertarget{ref-Bernecker2017}{}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Bernecker, K.
@@
 \leavevmode\hypertarget{ref-Cacioppo1982}{}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
@@
 \leavevmode\hypertarget{ref-Bless1994}{}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
@@
 \leavevmode\hypertarget{ref-Paschke2016}{}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Paschke, L.
@@
 \leavevmode\hypertarget{ref-Schwarzer1999}{}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}
@@
 \leavevmode\hypertarget{ref-Tangney2004}{}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Tangney, J.
@@
 \leavevmode\hypertarget{ref-Sproesser2011}{}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
@@
 \leavevmode\hypertarget{ref-Patton1995}{}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
@@
 \leavevmode\hypertarget{ref-Hartmann2011}{}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Hartmann, A.
@@
 \leavevmode\hypertarget{ref-Derryberry2002}{}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
@@
 \leavevmode\hypertarget{ref-Wessa2010}{}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Wessa, M.
@@
 \leavevmode\hypertarget{ref-Lang2008}{}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Lang, P.
@@
 \leavevmode\hypertarget{ref-Yu2010}{}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
@@
 \leavevmode\hypertarget{ref-Bradley2000}{}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Bradley, M.
@@
 \leavevmode\hypertarget{ref-Fridlund1986}{}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Fridlund, A. J. \& Cacioppo, J. T. Guidelines for human electromyographic research. \emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
@@
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Enders, C.
@@
 \leavevmode\hypertarget{ref-Preece2020}{}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Preece, D.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2010}{}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2015}{}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 \emph{WHO-5.}
-General psychological well-being is assessed using the WHO-5 scale\textsuperscript{35,36}.
+General psychological well-being is assessed using the WHO-5 scale\textsuperscript{36,37}.
 5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{36}.
+The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{37}.
 
 \emph{Connor-Davidson Resilience Scale.}
-Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{37--39}.
+Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{38--40}.
 10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{38}.
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{39}.
 
 \emph{Emotion Regulation Questionnaire.}
-Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,40}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{61}
+Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,41}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{62}
 
 \emph{FlexER Scale.}
-Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{41} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{42} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 Psychometric properties are currently under investigation.
@@
 \emph{Implicit Theories Questionnaire.}
-Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{42}
+Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{43}
 4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{42}.
+The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{43}.
 
 \emph{Need for Cognition Scale.}
-Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{44}
+Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{45}
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{44,62} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{63}
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{45,63} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{64}
 
 \emph{Self-Regulation Scale.}
-As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{46} is used.
+As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{47} is used.
 The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{46}
+It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{47}
 
 \emph{Brief Self-Control Scale.}
-As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{47,48} is used.
+As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{48,49} is used.
 It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{48} .
+The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{49} .
 
 \emph{Barratt Impulsiveness Scale.}
-As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{49,50} is used.
+As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{50,51} is used.
 Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{50}
+An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{51}
 
 \emph{Attentional Control Scale.}
-Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{51} with items such as ``My concentration is good even if there is music in the room around me''.
+Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{52} with items such as ``My concentration is good even if there is music in the room around me''.
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{51}
+An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{52}
 

### 2022-03-24 06_Paper/ER-ED/method.Rmd
knitted document

@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@Simmons2012].
-The paradigm was written and presented using *PsychoPy* [@Peirce2019].
-We used *R* with *R Studio* [@RCore2021; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study[@Simmons2012].
+The paradigm was written and presented using *PsychoPy*[@Peirce2019].
+We used *R* with *R Studio*[@RCore2021; @RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.
@@
 Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
-In accordance with our previous study [@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
+In accordance with our previous study[@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
 All results are detailed in the [Supplementary Material](#SupplementaryMaterial)
@@
 
-Young healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
+Young healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
@@
 Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].
 
@@
 
-The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
+The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
 To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
-For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
-Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from @Bernecker2017.
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] will be used.
-To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) [@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
-Attentional control will be assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
+For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].
+Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] will be used.
+To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
+Attentional control will be assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
 For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).
@@
 
-*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group [@Scheffel2021].
+*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group[@Scheffel2021].
 Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
@@
 They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
+Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite[@Scheffel2021].
 All participants will receive written instruction and complete a training session.
@@
 *Part two: ER effort discounting.* <br> In the second part, ER effort discounting will take place.
-The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with a major change.
+The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.[-@Westbrook2013] with a major change.
 We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
@@
 The strategy that is not chosen will be assigned the value of 2 €.
-From this point on, comparisons between strategies will follow the original COG-ED paradigm [@Westbrook2013].
+From this point on, comparisons between strategies will follow the original COG-ED paradigm[@Westbrook2013].
 Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
@@
 
-Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS) [@Lang2008].
+Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS)[@Lang2008].
 The 20 neutral pictures (Valence (V): *M* $\pm$ *SD* = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): *M* $\pm$ *SD* = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
@@
 
-Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence [@Bradley2000], similar to previous work by our group [@Gaertner2021].
+Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence[@Bradley2000], similar to previous work by our group[@Gaertner2021].
 Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of @Fridlund1986.
@@
 
-Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
-In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
+Sample size calculation is done using *G\*Power*[@Faul2007; @Faul2009].
+In a meta-analysis of Zaehringer and colleagues[-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
 To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of at least $N=85$ have to be analyzed.
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the *afex* package [@Singmann2021].
+rmANOVAS will be run using the *afex* package[@Singmann2021].
 
@@
 
-To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package [@Kuznetsova2017].
+To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 $$ 
-Level-1-predictors will be centered within cluster [@Enders2007].
+Level-1-predictors will be centered within cluster[@Enders2007].
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses, both $p$-values and Bayes factors $BF10$, calculated using the *BayesFactor* package [@Morey2021], will be reported. 
+For each result of the analyses, both $p$-values and Bayes factors $BF10$, calculated using the *BayesFactor* package[@Morey2021], will be reported. 
 Bayes factors are calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.

### 2022-03-24 06_Paper/COG-ED/Manuscript.Rmd
includes citation of T2

@@
 
-In everyday life, effort and reward are closely intertwined [@Botvinick2009].
+In everyday life, effort and reward are closely intertwined[@Botvinick2009].
 With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
-A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value [@Botvinick2009].
-However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost [@Kool2018].
+A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value[@Botvinick2009].
+However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost[@Kool2018].
 Investigating effort and cost is challenging because "effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity" (p.
-209) [@Kool2018, p.
-209].
+209)[@Kool2018].
 
 One task that is often used to investigate effort is the *n*-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
-Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six [@Mackworth1959].
-The *n*-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times [@Jaeggi2010], and brain activity in areas associated with working memory [@Jonides1997; @Owen2005].
-However, its reliability measures are mixed, and associations of *n*-back performance and measures such as executive functioning and fluid intelligence are often inconsistent [@Jaeggi2010].
+Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six[@Mackworth1959].
+The *n*-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times[@Jaeggi2010], and brain activity in areas associated with working memory[@Jonides1997; @Owen2005].
+However, its reliability measures are mixed, and associations of *n*-back performance and measures such as executive functioning and fluid intelligence are often inconsistent[@Jaeggi2010].
 
-A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver [-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
 First, the participants complete the *n*-back levels to familiarize themselves with the task.
@@
 This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
-The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred [@Westbrook2013].
+The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred[@Westbrook2013].
 The subjective value (SV) of each difficulty level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
-Westbrook et al. [-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting.
+Westbrook et al.[-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting.
 Younger participants showed lower effort discounting, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.
 
-The individual degree of effort discounting in the study by Westbrook et al.
-[-@Westbrook2013] was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing an individual's tendency to actively seek out and enjoy effortful cognitive activities [@Cacioppo1982].
-Westbrook et al.
-[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of effort discounting for each participant which could then be related to the SVs as an objective measure of effort discounting.
+The individual degree of effort discounting in the study by Westbrook et al.[-@Westbrook2013] was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing an individual's tendency to actively seek out and enjoy effortful cognitive activities[@Cacioppo1982].
+Westbrook et al.[-@Westbrook2013] conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of effort discounting for each participant which could then be related to the SVs as an objective measure of effort discounting.
 On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
-Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; @Xu2021].
-However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
-On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.
+Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control[@Wu2021], a trait more prominent in individuals with high NFC[@Bertrams2012; @Nishiguchi2016; @Xu2021].
+However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance[@Kramer2021] or found no association of NFC and SVs at all[@Crawford2021].
+On the other hand, task load has been shown to be a better predictor of SVs than task performance[@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.
 
@@
 If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
-Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks<!-- perhaps add ref.
-to the other ms.
-on this issue?
--->, we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
-<!-- not sure whether you should call it like this; while it reflects the so-called "Entstehungszusammenhang", it does not necessarily reflect the so-called "Begründungszusammenhang", i.e., the proposed approach goes beyond emotion regulation -->
-In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al. [-@Westbrook2013].
+Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
+In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
 Additionally, we will compare the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
-The full results of the latter will be published in a second Registered Report<!-- again: add (interim) ref. -->.
+The full results of the latter will be published in a second Registered Report[@ScheffelZerna2022].
 The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
@@
 
-Our hypotheses were derived from the results of Westbrook et al. [-@Westbrook2013].
+Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
 Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing *n*-back level, (1b) reaction time increases with increasing *n*-back level, and (1c) perceived task load increases with increasing *n*-back level.
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
-The paradigm was written and presented using *Psychopy* [@Peirce2019].
-We used *R* with *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor* [@Morey2021] for all our analyses.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study[cf. @Simmons2012].
+The paradigm was written and presented using *Psychopy*[@Peirce2019].
+We used *R* with *R Studio*[@RCT2020; @RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all our analyses.
 
@@
 
-Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE* [@Greiner2015].
+Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE*[@Greiner2015].
 Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
@@
 The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session. <!-- again: add ref. -->
+Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
 A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
@@
 The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
-To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
+To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
 After each level, participants fill out the NASA-TLX on a tablet.
@@
 The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].
 
@@
 
-Sample size determination was mainly based on the results of the analyses of Westbrook et al. [-@Westbrook2013] (see [Design Table](#DesignTableSection)).
+Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)).
 The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and *n*-back level influencing SVs.
-Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
+Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
 However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
@@
 No data will be replaced.
-We aim to conduct all analysis as described in Westbrook et al.
-[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
-The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
-Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before [@Whelan2008; @Berger2021].
-Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively [@Lachaud2011].
-Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior [@Dutilh2012; @Houtman2012].
-To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results [@Singmann2019]. 
+We aim to conduct all analysis as described in Westbrook et al.[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
+The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
+Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
+Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
+Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
+To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019]. 
 Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
@@
 
-To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package [@Kuznetsova2017]. 
+To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package[@Kuznetsova2017]. 
 We will apply restricted maximum likelihood (REML) to fit the model.
@@
 $$
-Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi [-@Enders2007]. 
+Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi[-@Enders2007]. 
 By this, the model yields interpretable parameter estimates. 
@@
 The approximately normal distribution indicates no evidence to perform model criticism.  
-As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to Lorah [-@Lorah2018].
+As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to Lorah[-@Lorah2018].
 Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
 To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
-To ensure the validity of the MLM, we will conduct a specification curve analysis [@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
+To ensure the validity of the MLM, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
 These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
@@
 A second regression will additionally include the mean of the NASA-TLX subscales' $AUCs$ of each participant as a predictor.
-Since we do not have a fixed SV of 1 for 1-back, we cannot apply the computation of Westbrook et al.
-[-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
+Since we do not have a fixed SV of 1 for 1-back, we cannot apply the computation of Westbrook et al.[-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
 Consequently, we will choose a different way of quantifying the individual degree of effort discounting.
@@
 
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
 

### 2022-03-24 06_Paper/ER-ED/TheoreticalBackground.Rmd

@@
 The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
-It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
-Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
-So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
-In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy [@Gross1998antecedent].
+It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning[@Gross1998emerging].
+Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification[@Gross1998antecedent], and, following the taxonomy of Powers and LaBar[-@Powers2019], individuals can implement ER strategies by means of different tactics.
+So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process[@Gross1998antecedent].
+In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy[@Gross1998antecedent].
 This postulated temporal sequence of ER strategies influences their effectiveness.
 Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
-In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
+In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45[@Webb2012].
 
@@
 Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
-For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32 [@Zaehringer2020].
-In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal [@Burr2021]. 
-Similar effects have been reported for suppression [@Burr2021], distancing [@Gaertner2021], and distraction [@Schoenfelder2014].
+For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with _d~-~_ = 0.32[@Zaehringer2020].
+In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal[@Burr2021]. 
+Similar effects have been reported for suppression[@Burr2021], distancing[@Gaertner2021], and distraction[@Schoenfelder2014].
 Importantly, results on electromyographic measures  seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
@@
 In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being [@GrossJohn2003]. 
+Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being[@GrossJohn2003]. 
 In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.[@Aldao2010]), which led to the postulation of *adaptive* (such as reappraisal, acceptance) and *maladaptive* (such as suppression, rumination) ER strategies.
-For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
+For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms[@Yoon2013].
 
 The postulation of *adaptive* and *maladaptive* ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
-Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement [@Aldao2015].
-Adaptive flexible ER requires a large repertoire of ER strategies [@Aldao2015].
-The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities [@Bonanno2013].
-A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology [@DixonGordon2015;@Lougheed2012;@Southward2018]. 
-Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
+Within this framework, *maladaptive*  refers to inflexible ER strategy use or use of strategies that are hindering goal achievement[@Aldao2015].
+Adaptive flexible ER requires a large repertoire of ER strategies[@Aldao2015].
+The term “repertoire” can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities[@Bonanno2013].
+A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology[@DixonGordon2015;@Lougheed2012;@Southward2018]. 
+Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life[@Blanke2020].
 
 How do people choose strategies from their repertoire? 
-Similarly to the expectancy-value model of emotion regulation [@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
+Similarly to the expectancy-value model of emotion regulation[@Tamir2015] it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
 Evidence from other psychological domains (e.g., intertemporal choice[@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made. 
 Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs[@Sheppes2014]. 
-For example, a study found that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
-Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction [@Sheppes2011;@Sheppes2014].
-ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
-With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy [@Scheffel2021].
+For example, a study found that the intensity of a stimulus or situation plays a role in the choice[@Sheppes2011]. 
+Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction[@Sheppes2011;@Sheppes2014].
+ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort[@Sheppes2014;@Scheffel2021].
+With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy[@Scheffel2021].
 In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
@@
 We assume that people choose the strategy that has the highest value for them at the moment.
-The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
+The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement[@Aldao2015]. 
 One certainly central goal is the regulation of negative affect.
-A second, intrinsic and less obvious goal is the avoidance of effort [@Inzlicht2018].
-When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
+A second, intrinsic and less obvious goal is the avoidance of effort[@Inzlicht2018].
+When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
-SVs of ER Strategies could therefore be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
+SVs of ER Strategies could therefore be helpful to describe the ER repertoire[@Aldao2015] more comprehensively.
 Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
@@
 Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
-Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED) [@Westbrook2013].
+Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)[@Westbrook2013].
 
-In the original study by Westbrook et al.
-[-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
+In the original study by Westbrook et al.[-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
 Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
@@
 In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
-As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
+As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies[@Scheffel2021].
 Moreover, there is nothing like an objectively easiest ER strategy.
@@
 The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
-In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
+In the following steps, the lower value is changed in every iteration according to Westbrook et al.[-@Westbrook2013] until the indifference point is reached.
 This procedure will be repeated until all strategies have been compared.
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
-In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
+In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al.[@Zerna2022]).
 

### 2022-05-17 06_Paper/ER-ED/Revision/method.Rmd
added revision folder and changed file paths

--- 2022-03-24 06_Paper/ER-ED/method.Rmd
@@
 Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
+include_graphics(here("06_Paper", "ER-ED", "Revision", "figures", "Design_ER-ED.png"))
 ```

### 2022-05-17 06_Paper/ER-ED/Revision/Analyes_ERED_pilot.r

@@ -1,0 +1,593 @@
+######################################################
+# R Script for analyses of the Registered Report
+# "Estimating individual subjective values of emotion regulation strategies"
+# Scheffel, C., Zerna, J., Gärtner, A., Dörfel, D., & Strobel, A. (2022)
+#
+# Christoph Scheffel
+# (christoph_scheffel@tu-dresden.de)
+#
+######################################################
+
+#################### SETUP ###########################
+
+# Open relevant packages
+
+library(here)       # to set directories without defined paths
+
+# set top level directory to source file
+here::i_am("flag_project_root_CERED.txt")
+
+library(renv)
+renv::activate(here("06_Paper", "ER-ED", "Revision"))
+renv::restore(here("06_Paper", "ER-ED", "Revision"))
+
+library(dplyr)
+library(ggplot2)
+
+##################### DATA IMPORT #######################
+
+# import ER ratings and ER discounting data into lists
+
+datalist_ER_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
+                                       pattern = "*_ER.*csv", full.names = TRUE),
+                                       read.csv, stringsAsFactors = FALSE,
+                                       header = TRUE)
+  
+datalist_ED_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
+                                       pattern = "*_ED.*csv", full.names = TRUE),
+                                       read.csv, stringsAsFactors = FALSE,
+                                       header = TRUE)
+
+# new empty frame to store files into
+data_ER_pilot <- data.frame(ID = character(), block = character(),
+                            arousal = double(), effort = double(),
+                            trigger = double(), trigger_reg = double())
+
+data_ED_pilot <- data.frame(ID = character(), step = double(),
+                            choice = character(), LBvalue = double(),
+                            LBlevel = double(), RBvalue = double(),
+                            RBlevel = double())
+
[…]

### 2022-05-18 06_Paper/ER-ED/Revision/method.Rmd
addressed comment 1.2.

@@
 Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
-At the beginning of the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
-Then, they will complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
-The second session will comprise the ER paradigm and take place exactly one week after session one.
+In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
+Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
+The second session will take place exactly one week after session one.
 Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
 A brief training will ensure that all participants are able to implement the ER strategies.
-Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
+Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
+After that, participants will choose one ER strategy to repeat one more time.
 Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].

### 2022-05-18 06_Paper/ER-ED/Revision/method.Rmd
implemented comment 1.5.

@@
 suppression, and distancing vs.
-suppression), two strategies with monetary values will be presented.
-The order of the comparisons will be randomized.
+suppression), each of the two strategies will be presented with a monetary reward.
+The order of the pairings will be randomized.
 Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option "1 € for strategy A or 1 € for strategy B".
-The strategy that is not chosen will be assigned the value of 2 €.
+The participants decide by clicking the on-screen button of the respective option.
+The strategy that is not chosen will be assigned the fixed value of 2 €, the chosen strategy will be assigned a starting value of 1 €.
 From this point on, comparisons between strategies will follow the original COG-ED paradigm[@Westbrook2013].
-Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
+Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
+The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
+If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
+The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
+Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.
 
@@
 
-*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, the resulting (monetary) value will be divided by 2.00 €.
+*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV, which is between 0 and 1.
 The final SV for each participant will be computed by averaging all final SVs of each strategy.

### 2022-05-18 06_Paper/ER-ED/Revision/method.Rmd
implemented comment 1.9.

@@
 *Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV, which is between 0 and 1.
-The final SV for each participant will be computed by averaging all final SVs of each strategy.
+Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV of the opposite strategy in each pairing.
+Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.
+The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
+The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.
 The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) and explore group effects.

### 2022-05-19 06_Paper/ER-ED/Revision/method.Rmd
fixed typo

@@
 It was followed by neutral or negative picture for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal on a continous scale (ranging from "not at all aroused" to "very highly aroused") and their subjective effort (ranging from "not very exhausting" to "very exhausting") using a slider on screen.
+After each block, participants retrospectively rated their subjective emotional arousal on a continuous scale (ranging from "not at all aroused" to "very highly aroused") and their subjective effort (ranging from "not very exhausting" to "very exhausting") using a slider on screen.
 

### 2022-05-20 06_Paper/ER-ED/Revision/method.Rmd
worked on comment 1.14

@@
 A complete list of all pictures and their classification into sets can be found in supplementary material 1.
+The five sets of negative pictures will be assigned randomly to the blocks.
 
@@
 
-To examine the effect of ER strategies on subjective effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
 Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
@@
 The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.
-The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) and explore group effects.
-Again, estimated marginal means will be computed as post-hoc contrasts.
 
-To investigate whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
-Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
-
-To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
+To explore the association between subjective effort (H5a), subjective arousal (H5b), and physiological responding (H5c,d) on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 
+To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
+Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
+
+The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
+Firstly, SVs will be ordered by magnitude.
+Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
+
 The influence of personality traits on SVs will be investigated exploratorily.
 Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
-
-The association between flexible ER and SVs of ER strategies will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
-Firstly, SVs will be ordered by magnitude.
-Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
 

### 2022-05-24 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 1.5.

@@
 Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
-Regarding the associations of subjective and objective task load we hypothesize that (1a) the signal detection parameter *d'* declines with increasing *n*-back level, (1b) reaction time increases with increasing *n*-back level, and (1c) perceived task load increases with increasing *n*-back level.
+As a manipulation check, we hypothesize that with increasing *n*-back level the (1a) the signal detection parameter *d'* declines, while (1b) reaction time and (1c) perceived task load increase.
 Regarding the associations of task load and effort discounting we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.

### 2022-05-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
changed file locations

@@
 # load workspace variables from analyses_ERED.R script
-load(here("06_Paper","ER-ED","Workspace_ERED_pilot.RData"))
+load(here("06_Paper","ER-ED","Revision","Workspace_ERED_pilot.RData"))
 
@@
 ```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
-include_graphics(here("06_Paper","ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
+include_graphics(here("06_Paper","ER-ED", "Revision", "figures", "Paradigm_Scheme_T2.png" ))
 ```
@@
 ```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
+include_graphics(here("06_Paper", "ER-ED", "Revision", "figures", "Design_ER-ED.png"))
 ```

### 2022-05-24 06_Paper/ER-ED/TheoreticalBackground.Rmd
changed file locations

@@
 This pattern can be represented by our paradigm."}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
+include_graphics(here("06_Paper", "ER-ED", "Revision", "figures", "Paradigm_Scheme_T2.png" ))
 ```
@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies. 
-As a manipulation check, we first want to investigate whether the valence of the pictures (neutral, negative) is effecting subjective and physiological responding (EMG).
-Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort.
-The following hypotheses are proposed:
-
-* H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures. 
-* H1b) Physiological responding (EMG *corrugator* and *levator* activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
-
-* H2a) Subjective arousal (arousal rating) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H3a) Physiological responding (EMG *corrugator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H3b) Physiological responding (EMG *levator* activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-
-* H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-* H5b) The majority of participants re-uses the strategy that was least effortful for them.
-
-Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
-
-* H5a) Subjective effort (effort ratings) negatively predicts SVs of ER strategies.
-* H5b) Subjective arousal (arousal ratings) negatively predicts SVs of ER strategies.
-* H5c) Physiological responding (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
-* H5d) Physiological responding (EMG *levator* activity) negatively predicts SVs of ER strategies.
-
-* H6a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF *corrugator* and *levator* activity).
-
-We also want to investigate whether SVs are related to flexible emotion regulation:
-
-* H7a) The higher the SV, the more likely the respective strategy is chosen.
-* H7b) SVs are lower and decline stronger when ER flexibility is lower.
-
+As a manipulation check, we first want to investigate whether the valence of the pictures is affecting subjective and physiological responding, resulting in lower subjective arousal ratings after and lower EMG activity during neutral compared to negative pictures.
+Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective arousal and physiological responding compared to the active viewing condition.
+Third, we want to see whether the strategies subjectively require more cognitive effort than the active viewing condition, and whether participants re-apply the for them least effortful strategy. 
+Furthermore, we want to investigate whether subjective effort and arousal ratings, and EMG activity predict individual subjective values of ER strategies.
+And lastly, we want to check whether the SV of a strategy is associated with its likelihood of being chosen again, and whether SVs reflect participants' self-reported ER flexibility.
+All hypotheses are detailed in the [design table](#DesignTable).
 Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely *n*-back.

### 2022-05-24 06_Paper/ER-ED/method.Rmd
changed file locations

@@
 
-The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
+The online survey will contain a number of questionnaires. In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
+It assess flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this." 
+The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".
+
+Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
+General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
 To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
 Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
-For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].
 Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
@@
 
-*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, the resulting (monetary) value will be divided by 2.00 €.
-The final SV for each participant will be computed by averaging all final SVs of each strategy.
-The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) and explore group effects.
-Again, estimated marginal means will be computed as post-hoc contrasts.
+*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV of the opposite strategy in each pairing.
+Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.
+The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
+The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.
 
-To investigate whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
-Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
-
-To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
+To explore the association between subjective effort (H5a), subjective arousal (H5b), and physiological responding (H5c,d) on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.

### 2022-05-24 06_Paper/ER-ED/Analyes_ERED_pilot.r

@@ -18,8 +18,8 @@ library(here)       # to set directories without defined paths
 here::i_am("flag_project_root_CERED.txt")
 
 library(renv)
-renv::activate(here("06_Paper", "ER-ED"))
-renv::restore(here("06_Paper", "ER-ED"))
+renv::activate(here("06_Paper", "ER-ED", "Revision"))
+renv::restore(here("06_Paper", "ER-ED", "Revision"))
 
 library(dplyr)
 library(ggplot2)

### 2022-05-24 06_Paper/ER-ED/Revision/Analyes_ERED_pilot.r

@@ -1,593 +1,0 @@
-######################################################
-# R Script for analyses of the Registered Report
-# "Estimating individual subjective values of emotion regulation strategies"
-# Scheffel, C., Zerna, J., Gärtner, A., Dörfel, D., & Strobel, A. (2022)
-#
-# Christoph Scheffel
-# (christoph_scheffel@tu-dresden.de)
-#
-######################################################
-
-#################### SETUP ###########################
-
-# Open relevant packages
-
-library(here)       # to set directories without defined paths
-
-# set top level directory to source file
-here::i_am("flag_project_root_CERED.txt")
-
-library(renv)
-renv::activate(here("06_Paper", "ER-ED", "Revision"))
-renv::restore(here("06_Paper", "ER-ED", "Revision"))
-
-library(dplyr)
-library(ggplot2)
-
-##################### DATA IMPORT #######################
-
-# import ER ratings and ER discounting data into lists
-
-datalist_ER_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
-                                       pattern = "*_ER.*csv", full.names = TRUE),
-                                       read.csv, stringsAsFactors = FALSE,
-                                       header = TRUE)
-  
-datalist_ED_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
-                                       pattern = "*_ED.*csv", full.names = TRUE),
-                                       read.csv, stringsAsFactors = FALSE,
-                                       header = TRUE)
-
-# new empty frame to store files into
-data_ER_pilot <- data.frame(ID = character(), block = character(),
-                            arousal = double(), effort = double(),
-                            trigger = double(), trigger_reg = double())
-
-data_ED_pilot <- data.frame(ID = character(), step = double(),
-                            choice = character(), LBvalue = double(),
-                            LBlevel = double(), RBvalue = double(),
-                            RBlevel = double())
-
[…]

### 2022-05-24 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Added a paragraph on why there is no objectively easiest strategy

@@
 Moreover, there is nothing like an objectively easiest ER strategy.
+<!-- Kommentar Denise: ich pack jetzt erstmal das AO Paper zu der  Energie, die die Strategien brauchen, und andere Überlegungen hier her.
+bin mir aber nicht sicher, ob das woanders nicht besser passt.--> It could be assumed, that the antecedent-focused strategies, i.e.
+attentional deployment and cognitive change, require less effort, because according to Gross [-@Gross1998antecedent] these strategies apply when the emotional reaction has not fully developed, yet.
+In contrast, suppression would need ongoing effort, because it takes effect late in the emotion generating process and does not alter the emotion itself. 
+A similar assumption has been made by Mesmer-Magnus et al.
+<!--Mesmer-Magnus, J.
+R., DeChurch, L.
+A., & Wax, A.
+(2012).
+Moving emotional labor beyond surface and deep acting: A discordance-congruence perspective.
+Organizational Psychology Review, 2(1), 6-53.
+https://doi.org/10.1177/2041386611417746 -->, who state that Surface Acting (the equivalent to expressive suppression in emotional labor research) is supposed to continuously require high levels of energy (hence effort).
+Deep Acting (which refers to reappraisal), in turn, only initially needs the use of energy.
+This would be in conflict with findings in our prevoius studies, that showed that many people choose expressive suppression because they evaluated it as less effortful, hence easy[@Scheffel2021].
+Others define emotion regulation on a continuum from explicit, conscious, and effortful to implicit, unconscious, automatic and effortless <!--Gyurak, A., Gross, J.
+J., & Etkin, A.
+(2011).
+Explicit and implicit emotion regulation: a dual-process framework.
+Cogn Emot, 25(3), 400-412.
+https://doi.org/10.1080/02699931.2010.544160-->.
+This would mean, that all explicit strategies that have been proposed by the process model of emotion regulation are similarly effortful[@Gross1998antecedent].
+<!--Schaut mal, ob ihr mit dieser Argumentation einverstanden seid-->
+Similarly, the flexibility approach of emotion regulation also states, that there is no "best" strategy <!-- Gross, J.
+J.
+(2015).
+Emotion Regulation: Current Status and Future Prospects.
+Psychological Inquiry, 26(1), 1-26.
+https://doi.org/10.1080/1047840x.2014.940781-->.
+An emotion regulation attempt is adaptive, when the intended, individual goal is reached.
+Those attempts could also consist of sequences of regulatory efforts using different strategies, which might be effective and effortless only in this specific context.
+
 Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 

### 2022-05-25 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 2.7.

@@
 Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
-First, the SVs are still distorted by the SVs returned by the original paradigm, and second, having more task levels would lead to an exponential increase in comparisons.
+First, the SVs are still quite alike among levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels would lead to an exponential increase in comparisons.
 Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal rewards.

### 2022-05-30 06_Paper/ER-ED/method.Rmd
added utility to SV model

@@
 It was followed by neutral or negative picture for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal on a continuous scale (ranging from "not at all aroused" to "very highly aroused") and their subjective effort (ranging from "not very exhausting" to "very exhausting") using a slider on screen.
+After each block, participants retrospectively rated their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and the utility of each strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
 
@@
 $$
-SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
+SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
 $$ 

### 2022-05-30 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 1.2.
implemented comment 2.1.
implemented comment 2.2

@@
 title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
-shorttitle        : "The CERED paradigm for estimating subjective values"
+shorttitle        : "The CAD paradigm for estimating subjective values"
 author: 
@@
 wordcount         : "~ 3,700"
-bibliography      : CERED.bib
+bibliography      : CAD.bib
 floatsintext      : yes
@@
 
-  here::i_am("flag_project_root_CERED.txt")
+  here::i_am("flag_project_root_CAD.txt")
 
@@
 If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
-Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Emotion Regulation Effort Discounting Paradigm (CERED).
-In the present study, we will validate the CERED paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
+Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
+In the present study, we will validate the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
 Additionally, we will compare the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
@@
 
-## Pilot data
-
-The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
-One participant's data was removed because they misunderstood the instruction.
-Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
-The results showed increases in subjective and objective task load measures with higher *n*-back level.
-Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
-A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
-The specification curve analysis showed that this pattern was true for all 63 pipelines.
-Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
-All results are detailed in the Supplementary Material.
-
 ## Design
@@
 Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
-A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CERED).
+A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CAD).
 In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
@@
 This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
+After the computer paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the ED procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
@@
 
+## Pilot data
+
+The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
+One participant's data was removed because they misunderstood the instruction.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
+The results showed increases in subjective and objective task load measures with higher *n*-back level.
+Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
+A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
+The specification curve analysis showed that this pattern was true for all 63 pipelines.
+Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
+All results are detailed in the Supplementary Material.
+
 ## Data availability
@@
 
-The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at [github.com/ChScheffel/CERED](https://github.com/ChScheffel/CERED).
+The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at [github.com/ChScheffel/CAD](https://github.com/ChScheffel/CAD).
 

### 2022-05-30 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 2.3

@@
 After each level, participants fill out the NASA-TLX on a tablet.
-Then, they complete the effort discounting procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
-Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
-This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
-After the computer paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the ED procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
+Then, they complete the effort discounting procedure on screen and are instructed to do so as realistically as possible, even though the displayed rewards will not be paid out on top of their compensation.
+They are told that one of their choices will be randomly picked for the final run of *n*-back, the data of which will not be analyzed as it serves to incentivise truthful behavior.
+The procedure starts with a presentation of each possible pair of *n*-back levels, and the participants click on the level they would rather do for a reward of 1\ €.
+Each pair is presented three times in total, with the order of presentation and the matter of which level is presented left/right fully randomized between participants.
+After these 18 decisions, the paradigm assigns which level is flexible or fixed within each pair, based on which level was chosen at least twice or at the maximum once, respectively.
+Then the effort discounting sensu Westbrook [@Westbrook2013] begins, with the pairs being presented in randomized order.
+Each pair goes through all six iteration steps before moving on to the next pair.
+After the computer paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.

### 2022-05-30 06_Paper/ER-ED/method.Rmd
added "utility" in design table (and respective text parts)

@@
 
-To explore the association between subjective effort (H5a), subjective arousal (H5b), and physiological responding (H5c,d) on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
+To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.

### 2022-05-30 06_Paper/ER-ED/TheoreticalBackground.Rmd
added two sentences on utility

--- 2022-05-24 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 A second, intrinsic and less obvious goal is the avoidance of effort[@Inzlicht2018].
-When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
+When given the choice, most individuals prefer tasks that are less effortful[@Hull1943] and chose strategies that were less effortful[@Scheffel2021].
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
-SVs of ER Strategies could therefore be helpful to describe the ER repertoire[@Aldao2015] more comprehensively.
+In addition, perceived utility should have an impact on SVs. 
+A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
+Moreover, SVs of ER Strategies could therefore be helpful to describe the ER repertoire[@Aldao2015] more comprehensively.
 Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.

### 2022-05-30 06_Paper/ER-ED/method.Rmd

@@
 It was followed by neutral or negative picture for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and the utility of each strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
+After each block, participants retrospectively rated their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the ragulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
 

### 2022-05-31 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 1.1

--- 2022-05-30 06_Paper/COG-ED/Manuscript.Rmd
@@
 First, the participants complete the *n*-back levels to familiarize themselves with the task.
-Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving 2\$ for the more difficult level or 1\$ for 1-back.
+Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
 If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
@@
 
-With the present study, we alter one fundamental assumption of the original COG-ED paradigm: that the easiest *n*-back level has the highest SV.
-We therefore adapted the COG-ED paradigm in such a way that it allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
-Figure\ 1 illustrates how different modifications of the COG-ED paradigm return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least.
-The COG-ED paradigm sets the SV of 1-back to 1, regardless of the response pattern.
-Adding a comparison of 2-back and 3-back allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
-Adding three more comparisons of the same levels but using the easier level as reference does approach the true preference, but has two disadvantages.
-First, the SVs are still quite alike among levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels would lead to an exponential increase in comparisons.
-Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels, and by starting each round with a choice between equal rewards.
-For example, the participant is presented with the choice of receiving 1€ for 2-back or 1€ for 4-back.
-The level chosen by the participant will then be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
-The level that was not chosen will be set to a fixed value of 2€.
-This procedure allows to compute SVs based on actual individual preference instead of objective task load.
-Each level's SV is calculated as the mean of this level's SVs from all comparisons in which it appeared.
-If the participant has a clear preference for one level, this level's SV will be 1.
-If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
+With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
+We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
 Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
@@
 The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
-
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
-The grey boxes are the choice options shown to the participant.
-The participant's final reward value of the flexible level is displayed after the first arrow.
-The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice.
-The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}
-
-  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
-
-```
 
@@
 
+### CAD Paradigm
+Figure\ 1 illustrates how different modifications of the COG-ED paradigm [@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
+The COG-ED paradigm, which compares every more difficult level with 1-back sets the SV of 1-back to 1, regardless of the response pattern.
+Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
+Adding those same pairs again, but with the oppositve assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
+First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
+Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
+In each pair, the level chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
+The other level in the pair will be set to a fixed value of 2€.
+Then, the effort discounting sensu Westbrook [-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
+The order in which the pairs are presented will be fully randomized, and each pair will go through all iteration steps of adding/subtracting 0.50\ €, 0.25\ €, 0.13\ €, 0.06\ €, 0.03\ €, 0.02\ € to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
+This procedure allows to compute SVs based on actual individual preference instead of objective task load.
+For each pair, the SV of the flexible level is 1, as it was preferred when faced with equal rewards, and the SV of the fixed level is the final reward of the flexible level divided by 2\ €.
+Each level's "global" SV is calculated as the mean of this level's SVs from all pairs in which it appeared.
+If the participant has a clear preference for one level, this level's SV will be 1.
+If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
+The interpretation of SVs in Westbrook [-@Westbrook2013] was "The minimum relative reward required for me to choose 1-back over this level".
+So if the SV of 3-back was 0.6, the participant would need to be rewarded with at least 60\ % of what they are being offered for doing 3-back to do 1-back instead, forgoing the higher reward for 3-back.
+In this study, the SV can be interpreted as "The minimum relative reward required for me to choose any other level over this level".
+Therefore, an SV of 1 indicates that this level is preferred over all others, while SVs lower than 1 indicate that in at least one pair, a different level was preferred over this one.
+
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+The grey boxes are the choice options shown to the participant.
+The participant's final reward value of the flexible level is displayed after the first arrow.
+The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice.
+The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}
+
+  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
+
+```
+
+### Study procedure
 Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE*[@Greiner2015].
@@
 To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-After each level, participants fill out the NASA-TLX on a tablet.
-Then, they complete the effort discounting procedure on screen, where each possible pairing of the four *n*-back levels is presented in a randomized order.
-Participants are instructed to decide as realistically as possible, because one of their choices from the last iteration steps will be randomly chosen for one final run of *n*-back.
-This is only done to incentivise truthful behavior in the effort discounting procedure, so the *n*-back data of this part will not be analyzed.
-After the computer paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the ED procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
+At the end of each level, participants fill out the NASA-TLX on a tablet.
+After the *n*-back task, participants complete the CAD paradigm on screen and are instructed to do so as realistically as possible, even though the displayed rewards will not be paid out on top of their compensation.
+They are told that one of their choices will be randomly picked for the final run of *n*-back, the data of which will not be analyzed as it only serves to incentivise truthful behavior and stay close to the design of Westbrook [-@Westbrook2013].
+After the CAD paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
 The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.

### 2022-06-01 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
knitted document

--- 2022-03-24 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 # set top level directory to source file
-here::i_am("flag_project_root_CERED.txt")
+here::i_am("flag_project_root_CAD.txt")
 

### 2022-06-01 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 A second, intrinsic and less obvious goal is the avoidance of effort\textsuperscript{23}.
-When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24}.
+When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24} and chose strategies that were less effortful\textsuperscript{22}.
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
-SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
+In addition, perceived utility should have an impact on SVs.
+A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
+Moreover, SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
 Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
 This would mean that all strategies are a good option for goal achievement.
-A second person with less flexibility, however, would show high SVs only for one or very few strategies.
+A second person with less flexibility, however, would show high SVs only for only one strategy or low SVs for all of the strategies.
 This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies.
-As a manipulation check, we first want to investigate whether the valence of the pictures (neutral, negative) is effecting subjective and physiological responding (EMG).
-Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective and physiological responding as well as, third, whether they require cognitive effort.
-The following hypotheses are proposed:
-
-\begin{itemize}
-\item
-  H1a) Subjective arousal is lower after actively viewing neutral pictures compared to actively viewing negative pictures.
-\item
-  H1b) Physiological responding (EMG \emph{corrugator} and \emph{levator} activity) is lower while actively viewing neutral pictures compared to actively viewing negative pictures.
-\item
-  H2a) Subjective arousal (arousal rating) is lower after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-\item
-  H3a) Physiological responding (EMG \emph{corrugator} activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-\item
-  H3b) Physiological responding (EMG \emph{levator} activity) is lower while using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-\item
-  H4a) Subjective effort (effort rating) is greater after using an ER strategy (distraction, distancing, suppression) compared to active viewing.
-\item
-  H5b) The majority of participants re-uses the strategy that was least effortful for them.
-\end{itemize}
-
-Furthermore, we want to investigate whether the following variables predict individual subjective values of ER strategies and whether effort is the best predictor for SVs of ER strategies with the following hypotheses:
-
-\begin{itemize}
-\item
-  H5a) Subjective effort (effort ratings) negatively predicts SVs of ER strategies.
-\item
-  H5b) Subjective arousal (arousal ratings) negatively predicts SVs of ER strategies.
-\item
-  H5c) Physiological responding (EMG \emph{corrugator} activity) negatively predicts SVs of ER strategies.
-\item
-  H5d) Physiological responding (EMG \emph{levator} activity) negatively predicts SVs of ER strategies.
-\item
-  H6a) SVs decline with increasing effort, even after controlling for task performance (subjective arousal ratings), and physiological responding (EMF \emph{corrugator} and \emph{levator} activity).
-\end{itemize}
-
-We also want to investigate whether SVs are related to flexible emotion regulation:
-
-\begin{itemize}
-\tightlist
-\item
-  H7a) The higher the SV, the more likely the respective strategy is chosen.
-\item
-  H7b) SVs are lower and decline stronger when ER flexibility is lower.
-\end{itemize}
-
+As a manipulation check, we first want to investigate whether the valence of the pictures is affecting subjective and physiological responding, resulting in lower subjective arousal ratings after and lower EMG activity during neutral compared to negative pictures.
+Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective arousal and physiological responding compared to the active viewing condition.
+Third, we want to see whether the strategies subjectively require more cognitive effort than the active viewing condition, and whether participants re-apply the for them least effortful strategy.
+Furthermore, we want to investigate whether subjective effort, arousal ratings, subjective utility, and EMG activity predict individual subjective values of ER strategies.
+And lastly, we want to check whether the SV of a strategy is associated with its likelihood of being chosen again, and whether SVs reflect participants' self-reported ER flexibility.
+All hypotheses are detailed in the \protect\hyperlink{DesignTable}{design table}.
 Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely \emph{n}-back.
@@
 Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
-At the beginning of the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
-Then, they will complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
-The second session will comprise the ER paradigm and take place exactly one week after session one.
+In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
+Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
+The second session will take place exactly one week after session one.
 Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
 A brief training will ensure that all participants are able to implement the ER strategies.
-Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted.
+Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
+After that, participants will choose one ER strategy to repeat one more time.
 Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{34,35}.
@@
 
-The online survey will contain a number of questionnaires: General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{36,37}.
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{40} will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,41}.
-For the assessment of ER flexibility we will use the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{42}.
+The online survey will contain a number of questionnaires.
+In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{36}.\\
+It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
+The items are rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+
+Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
+General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{37,38}.
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{41} will be used.
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,42}.
 Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{43}.
@@
 It was followed by neutral or negative picture for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal on a continous scale (ranging from ``not at all aroused'' to ``very highly aroused'') and their subjective effort (ranging from ``not very exhausting'' to ``very exhausting'') using a slider on screen.
+After each block, participants retrospectively rated their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the ragulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.
 
@@
 The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{25} with a major change.
-We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), two strategies with monetary values will be presented.
-The order of the comparisons will be randomized.
+We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies will be presented with a monetary reward.
+The order of the pairings will be randomized.
 Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
-The strategy that is not chosen will be assigned the value of 2 €.
+The participants decide by clicking the on-screen button of the respective option.
+The strategy that is not chosen will be assigned the fixed value of 2 €, the chosen strategy will be assigned a starting value of 1 €.
 From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{25}.
-Participants will be instructed to decide as realistically as possible by imagining that the money displayed is actually available for choice.
+Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
+The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
+If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
+The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
+Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Design_ER-ED} \caption{Block design of the paradigm.
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{Block design of the paradigm.
 Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
@@
 
-To examine the effect of ER strategies on subjective effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
 Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
@@
 
-\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, the resulting (monetary) value will be divided by 2.00 €.
-The final SV for each participant will be computed by averaging all final SVs of each strategy.
-The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) and explore group effects.
-Again, estimated marginal means will be computed as post-hoc contrasts.
-
-To investigate whether individual SVs predict ER choice, a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
-Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
-
-To explore the association between subjective arousal, physiological responses, and subjective effort on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{60}.
+\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV of the opposite strategy in each pairing.
+Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.
+The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
+The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.
+
+To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{60}.
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 \[
-SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
+SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
 \]
@@
 
+To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
+Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
+
+The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a regression using the \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
+Firstly, SVs will be ordered by magnitude.
+Secondly, for each participant a linear model will be built to estimate the individual \(intercept\) and \(slope\).
+
 The influence of personality traits on SVs will be investigated exploratorily.
 Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
-
-The association between flexible ER and SVs of ER strategies will be investigated with a regression using the \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
-Firstly, SVs will be ordered by magnitude.
-Secondly, for each participant a linear model will be built to estimate the individual \(intercept\) and \(slope\).
 
@@
 \CSLLeftMargin{26. }
-\CSLRightInline{Zerna, S., J.
+\CSLRightInline{Zerna, J., Scheffel, C., Kührt, C.
 \& Strobel, A.
@@
 
+\leavevmode\hypertarget{ref-Doerfel2019}{}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
+
 \leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
@@
 \leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
@@
 \leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
@@
 \leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Sarubin, N.
@@
 \leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Campbell-Sills, L.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
-
-\leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{42. }
-\CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CERED/06_Paper/ER-ED/figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
+\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
 \end{figure}
@@
 \emph{WHO-5.}
-General psychological well-being is assessed using the WHO-5 scale\textsuperscript{36,37}.
+General psychological well-being is assessed using the WHO-5 scale\textsuperscript{37,38}.
 5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{37}.
+The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{38}.
 
 \emph{Connor-Davidson Resilience Scale.}
-Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{38--40}.
+Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{39--41}.
 10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{39}.
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{40}.
 
 \emph{Emotion Regulation Questionnaire.}
-Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,41}.
+Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,42}.
 The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{62}
@@
 \emph{FlexER Scale.}
-Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{42} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{36} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 Psychometric properties are currently under investigation.

### 2022-06-01 06_Paper/ER-ED/TheoreticalBackground.Rmd
knitted document

@@
 # set top level directory to source file
-here::i_am("flag_project_root_CERED.txt")
+here::i_am("flag_project_root_CAD.txt")
 ```
@@
 This would mean that all strategies are a good option for goal achievement.
-A second person with less flexibility, however, would show high SVs only for one or very few strategies.
+A second person with less flexibility, however, would show high SVs only for only one strategy or low SVs for all of the strategies.
 This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from. 
@@
 This pattern can be represented by our paradigm."}
-include_graphics(here("06_Paper", "ER-ED", "Revision", "figures", "Paradigm_Scheme_T2.png" ))
+include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
 ```
@@
 Third, we want to see whether the strategies subjectively require more cognitive effort than the active viewing condition, and whether participants re-apply the for them least effortful strategy. 
-Furthermore, we want to investigate whether subjective effort and arousal ratings, and EMG activity predict individual subjective values of ER strategies.
+Furthermore, we want to investigate whether subjective effort, arousal ratings, subjective utility, and EMG activity predict individual subjective values of ER strategies.
 And lastly, we want to check whether the SV of a strategy is associated with its likelihood of being chosen again, and whether SVs reflect participants' self-reported ER flexibility.

### 2022-06-01 06_Paper/COG-ED/Analysis.R
added median RT to SCA pipelines

@@ -326,7 +326,7 @@
   
 ##### Preprocessing pipelines for the SCA ######################################
   
-  # create new data frames for the specification curve analysis <!-- specification curve analysis has not been mentioned in the ms. so far -->
+  # create new data frames for the specification curve analysis
   # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
   #
   # across which dimensions the transformation and outlier exclusion will be done:
@@ -722,11 +722,56 @@
     
     dprime$d <- dprime$hitrate.z - dprime$falsealarmrate.z
     
-    # feed d# trialwise into the pipeline data frame
+    # feed d' trialwise into the pipeline data frame
     
     for (i in 1:nrow(pipelines_data[[j]])) {
       
       pipelines_data[[j]]$dprime[i] <- dprime$d[dprime$subject == pipelines_data[[j]]$subject[i] & dprime$level == pipelines_data[[j]]$level[i]]
+      
+    }
+  }
+
+##### median RT for every pipeline #############################################
+  
+  # calculate the median RT for correct and post-correct trials for every pipeline
+  # per subject and per condition
+  # the median RT will be another column in the data frames, and will be the same
+  # within one subject and level, just like the SVs and d prime
+  
+  for (j in 1:length(pipelines_data)) {
+    
+    # compute index of rows in which the levels change
+    
+    levelindex <- c(1,which(pipelines_data[[j]]$level != dplyr::lag(pipelines_data[[j]]$level)),nrow(pipelines_data[[j]]))
+    
+    # set up empty data frame for the loop to feed into
+    
+    medianRT <- data.frame(subject = character(), level = double(), medianRT = double())
+    
+    # calculate median RT per subject and level (only for correct & post-correct trials)
+    
+    for (i in 1:(length(levelindex)-1)) {
+      
+      # current level and current subject
+      x <- pipelines_data[[j]]$level[levelindex[i]]
+      mysubject <- pipelines_data[[j]]$subject[levelindex[i]]
+      
+      # compute median reaction time
+      mymedianRT <- median(pipelines_data[[j]]$rt[pipelines_data[[j]]$level == x & pipelines_data[[j]]$response == 1 & pipelines_data[[j]]$correct == 1 & pipelines_data[[j]]$subject == mysubject], na.rm = TRUE)
+
+      # bind data to data frame
[…]

### 2022-06-01 06_Paper/ER-ED/method.Rmd

@@
 
-The online survey will contain a number of questionnaires. In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
-It assess flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this." 
+The online survey will contain a number of questionnaires. 
+In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
+It assess flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
 The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".
@@
 Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
-include_graphics(here("06_Paper", "ER-ED", "Revision", "figures", "Design_ER-ED.png"))
+include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
 ```

### 2022-06-02 06_Paper/ER-ED/TheoreticalBackground.Rmd
added a comma
worked on reviewer 1.1

@@
 ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort[@Sheppes2014;@Scheffel2021].
-With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy[@Scheffel2021].
-In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
-Afterwards, they choose which strategy they wanted to use again.
-Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
-Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
 Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
@@
 One certainly central goal is the regulation of negative affect.
-A second, intrinsic and less obvious goal is the avoidance of effort[@Inzlicht2018].
-When given the choice, most individuals prefer tasks that are less effortful[@Hull1943] and chose strategies that were less effortful[@Scheffel2021].
+The effectiveness of ER strategies should therefore influence the respective SV.
+A second, intrinsic, and less obvious goal is the avoidance of effort[@Inzlicht2018].
+When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
+This relatively consistent finding could be demonstrated in various domains, for example in the area of affective science[@Gonzalez-Garcia2021], in the area of executive functions, decision behaviour and cognitive control.
+
+and chose strategies that were less effortful[@Scheffel2021].
+
+With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy[@Scheffel2021].
+In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
+Afterwards, they choose which strategy they wanted to use again.
+Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
+Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
+
 We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
+
 In addition, perceived utility should have an impact on SVs. 

### 2022-06-02 06_Paper/ER-ED/TheoreticalBackground.Rmd
worked on reviewer 1.1

@@
 When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
-This relatively consistent finding could be demonstrated in various domains, for example in the area of affective science[@Gonzalez-Garcia2021], in the area of executive functions, decision behaviour and cognitive control.
+Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and could even be deescribed as trait-like characteristic[@Kool2014].
 

### 2022-06-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
corrected typo

--- 2022-06-02 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
-This relatively consistent finding could be demonstrated in various domains, for example in the area of affective science[@Gonzalez-Garcia2021], in the area of executive functions, decision behaviour and cognitive control.
+Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and could even be described as trait-like characteristic[@Kool2014].
 

### 2022-06-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
restructed TB for review 1.1

--- 2022-06-02 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
-This relatively consistent finding could be demonstrated in various domains, for example in the area of affective science[@Gonzalez-Garcia2021], in the area of executive functions, decision behaviour and cognitive control.
-
-and chose strategies that were less effortful[@Scheffel2021].
-
-With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy[@Scheffel2021].
-In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
+Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and is associated with Need for Cognition (NFC)[@Caccioppo1982], a stable measure of the individual pursuit and enjoyment of cognitive effort[@Westbrook2013;@Strobel2020].
+In the area of emotion regulation, too, there are initial indications that people show a tendency towards effort avoidance.
+Across two studies, we could show in previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy[@Scheffel2021].
+In our studies, participants used the strategies distancing and suppression while inspecting emotional pictures.
 Afterwards, they choose which strategy they wanted to use again.
 Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
-Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
-
-We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
-
+Moreover, the majority of participants stated afterwards the main reason for their choice was effort.
+We assume therefore that, although individuals trade off both factors - effectiveness and effort - against each other, effort should be the more important predictor for SVs of ER strategies.
 In addition, perceived utility should have an impact on SVs. 
 A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
-Moreover, SVs of ER Strategies could therefore be helpful to describe the ER repertoire[@Aldao2015] more comprehensively.
+SVs of ER Strategies could therefore be helpful to describe the ER repertoire[@Aldao2015] more comprehensively.
 Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.

### 2022-06-03 06_Paper/ER-ED/method.Rmd
updated analysis secttion

@@
 The level of significance will be set to $\alpha=.05$.
+For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the *afex* package[@Singmann2021].
+Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values and will be reported when the assumption of sphericity is violated.
+If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
+Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
 
 *Effect of valence on arousal and facial EMG.*<br> 
-To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-
+To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
 To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG *corrugator* and *levator* activity.
-Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
-Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
-If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the *afex* package[@Singmann2021].
 
@@
 To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
-
 To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity will be conducted.
-
 To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
-Greenhouse-Geisser-corrected $p$-values and degrees of freedom will be reported when the assumption of sphericity is violated.
-Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
-If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the *afex* package[@Singmann2021].
 
@@
 
-The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a regression using the $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
-Firstly, SVs will be ordered by magnitude.
-Secondly, for each participant a linear model will be built to estimate the individual $intercept$ and $slope$.
+The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual $intercept$ (i.e., the extent to which an invididual considers any of the ER strategies useful) and $slope$ (i.e., the extent to which one strategy is preferred over others, indicating less flexibility) of each participants' SVs to predict their FlexER score.
+To estimate individual $intercepts$ and $slopes$, SVs will first be sorted by magnitude in descending order.
+Values will be fitted in a linear model to estimate individual $intercepts$ and $slopes$.
 

### 2022-06-03 06_Paper/ER-ED/method.Rmd
added description of linear model for FlexER

@@
 
-The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual $intercept$ (i.e., the extent to which an invididual considers any of the ER strategies useful) and $slope$ (i.e., the extent to which one strategy is preferred over others, indicating less flexibility) of each participants' SVs to predict their FlexER score.
-To estimate individual $intercepts$ and $slopes$, SVs will first be sorted by magnitude in descending order.
-Values will be fitted in a linear model to estimate individual $intercepts$ and $slopes$.
+The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
+To this end, for each participant, SVs will be sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
+The resulting $intercept$ informs about the extent to which an individual considers any or all of the ER strategies as useful for regulation their emotion, while the $slope$ informs about the flexibility in the use of emotion regulation strategies.
+The individual intercepts and slopes will then be entered as predictors in a regression model with the FlexER score as dependent variable. 
+A positive association with the predictor $intercept$ would indicate that overall higher SVs attached to ER strategies predicts higher scores on the FlexER scale. 
+A positive association with the predictor $slope$ would indicate that less negative slopes, i.e., a smaller preference for a given ER strategy, would be associated with a higher score of the FlexER scale.
 

### 2022-06-03 06_Paper/COG-ED/Analysis.R
changed contrasts in H2a

@@ -1109,7 +1109,10 @@
   
   # calculate pairwise comparisons on estimated marginal means
   
-  hypothesis2a_contrasts <- as.data.frame(pairs(hypothesis2a_emm))
+  hypothesis2a_contrasts <- emmeans::contrast(hypothesis2a_emm, method = list("Declining Linear" = c(3,1,-1,-3),
+                                                                              "Ascending Quadratic" = c(-1,1,1,-1),
+                                                                              "Declining Logistic" = c(3,2,-2,-3),
+                                                                              "Positively Skewed Normal" = c(1,2,-1,-2)))
   
   # get Bayes factors
   

### 2022-06-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex

@@
 ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort\textsuperscript{20,22}.
-With regard to effort, we could show in our previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy\textsuperscript{22}.
-In our study, participants used the strategies distancing and suppression while inspecting emotional pictures.
-Afterwards, they choose which strategy they wanted to use again.
-Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
-Interestingly, the choice was independent of self-reported habitual use of suppression and reappraisal.
 Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
@@
 One certainly central goal is the regulation of negative affect.
-A second, intrinsic and less obvious goal is the avoidance of effort\textsuperscript{23}.
-When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24} and chose strategies that were less effortful\textsuperscript{22}.
-We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
+The effectiveness of ER strategies should therefore influence the respective SV.
+A second, intrinsic, and less obvious goal is the avoidance of effort\textsuperscript{23}.
+When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24}.
+Cognitive effort avoidance has been reported in many contexts, for example in affective context\textsuperscript{25}, the context of decision making\textsuperscript{26}, and executive functions\textsuperscript{27}, and is associated with Need for Cognition (NFC)\textsuperscript{28}, a stable measure of the individual pursuit and enjoyment of cognitive effort\textsuperscript{29,30}.
+In the area of emotion regulation, too, there are initial indications that people show a tendency towards effort avoidance.
+Across two studies, we could show in previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy\textsuperscript{22}.
+In our studies, participants used the strategies distancing and suppression while inspecting emotional pictures.
+Afterwards, they choose which strategy they wanted to use again.
+Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
+Moreover, the majority of participants stated afterwards the main reason for their choice was effort.
+We assume therefore that, although individuals trade off both factors - effectiveness and effort - against each other, effort should be the more important predictor for SVs of ER strategies.
 In addition, perceived utility should have an impact on SVs.
 A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
-Moreover, SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
+SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
 Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
 This would mean that all strategies are a good option for goal achievement.
-A second person with less flexibility, however, would show high SVs only for only one strategy or low SVs for all of the strategies.
+A second person with less flexibility, however, would show high SVs only for one strategy or low SVs for all of the strategies.
 This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
@@
 Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
-Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)\textsuperscript{25}.
-
-In the original study by Westbrook et al.\textsuperscript{25}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
+Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)\textsuperscript{29}.
+
+In the original study by Westbrook et al.\textsuperscript{29}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
 Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
@@
 The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
-In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{25} until the indifference point is reached.
+In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{29} until the indifference point is reached.
 This procedure will be repeated until all strategies have been compared.
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
-In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{26}).
+In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{31}).
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{27}.
-The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{28}.
-We used \emph{R} with \emph{R Studio}\textsuperscript{29,30} with the main packages \emph{afex}\textsuperscript{31} and \emph{BayesFactor}\textsuperscript{32} for all analyses.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{32}.
+The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{33}.
+We used \emph{R} with \emph{R Studio}\textsuperscript{34,35} with the main packages \emph{afex}\textsuperscript{36} and \emph{BayesFactor}\textsuperscript{37} for all analyses.
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
@@
 
-Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{33} at the Technische Universität Dresden.
+Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{38} at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
@@
 After that, participants will choose one ER strategy to repeat one more time.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{34,35}.
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{39,40}.
 
@@
 The online survey will contain a number of questionnaires.
-In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{36}.\\
+In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{41}.\\
 It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
@@
 Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
-General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{37,38}.
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{41} will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,42}.
-Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{43}.
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{44,45} will be used.
-To assess self-control,\textsuperscript{46} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{47}, the Brief Self-Control Scale (BSCS)\textsuperscript{48,49}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{50,51}.
-Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{52}.
+General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{42,43}.
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{46} will be used.
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,47}.
+Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{48}.
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,49} will be used.
+To assess self-control,\textsuperscript{50} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{51}, the Brief Self-Control Scale (BSCS)\textsuperscript{52,53}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{54,55}.
+Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{56}.
 For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
@@
 \emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
-The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{25} with a major change.
+The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{29} with a major change.
 We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies will be presented with a monetary reward.
@@
 The strategy that is not chosen will be assigned the fixed value of 2 €, the chosen strategy will be assigned a starting value of 1 €.
-From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{25}.
+From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{29}.
 Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
@@
 
-Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{53} and the International Affective Picture System (IAPS)\textsuperscript{54}.
+Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{57} and the International Affective Picture System (IAPS)\textsuperscript{58}.
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
 Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
-An evolutionary algorithm\textsuperscript{55} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+An evolutionary algorithm\textsuperscript{59} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material 1.
@@
 
-Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{56}, similar to previous work by our group\textsuperscript{7}.
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{57}
+Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{60}, similar to previous work by our group\textsuperscript{7}.
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{61}
 The ground electrode will be placed over the left \emph{Mastoid}.
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{56}
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{60}
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
@@
 
-Sample size calculation is done using \emph{G*Power}\textsuperscript{58,59}.
+Sample size calculation is done using \emph{G*Power}\textsuperscript{62,63}.
 In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
@@
 If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the \emph{afex} package\textsuperscript{31}.
+rmANOVAS will be run using the \emph{afex} package\textsuperscript{36}.
 
@@
 
-To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{60}.
+To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{64}.
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 \]
-Level-1-predictors will be centered within cluster\textsuperscript{61}.
+Level-1-predictors will be centered within cluster\textsuperscript{65}.
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{32}, will be reported.
+For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{37}, will be reported.
 Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
@@
 
+\leavevmode\hypertarget{ref-Gonzalez-Garcia2021}{}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Gonzalez-Garcia, C. \emph{et al.} Induced affective states do not modulate effort avoidance. \emph{Psychol Res} \textbf{85}, 1016--1028 (2021).}
+
+\leavevmode\hypertarget{ref-Kool2010}{}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Kool, W., McGuire, J. T., Rosen, Z. B. \& Botvinick, M. M. Decision making and the avoidance of cognitive demand. \emph{J Exp Psychol Gen} \textbf{139}, 665--82 (2010).}
+
+\leavevmode\hypertarget{ref-Cheval2020}{}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Cheval, B. \emph{et al.} Higher inhibitory control is required to escape the innate attraction to effort minimization. \emph{Psychology of Sport and Exercise} \textbf{51}, (2020).}
+
+\leavevmode\hypertarget{ref-Cacioppo1982}{}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
+
 \leavevmode\hypertarget{ref-Westbrook2013}{}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Westbrook, A., Kester, D.
@@
 
+\leavevmode\hypertarget{ref-Strobel2020}{}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Strobel, A. \emph{et al.} Dispositional cognitive effort investment and behavioral demand avoidance: Are they related? \emph{PLoS One} \textbf{15}, e0239817 (2020).}
+
 \leavevmode\hypertarget{ref-Zerna2022}{}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Zerna, J., Scheffel, C., Kührt, C.
@@
 \leavevmode\hypertarget{ref-Simmons2012}{}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{32. }
 \CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}
@@
 \leavevmode\hypertarget{ref-Peirce2019}{}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{33. }
 \CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
@@
 \leavevmode\hypertarget{ref-RCore2021}{}%
-\CSLLeftMargin{29. }
+\CSLLeftMargin{34. }
 \CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}
@@
 \leavevmode\hypertarget{ref-RStudioTeam2020}{}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{35. }
 \CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}
@@
 \leavevmode\hypertarget{ref-Singmann2021}{}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}
@@
 \leavevmode\hypertarget{ref-Morey2021}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{37. }
 \CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
@@
 \leavevmode\hypertarget{ref-Greiner2015}{}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
@@
 \leavevmode\hypertarget{ref-Harris2009}{}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Harris2019}{}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
@@
 \leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
@@
 \leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
@@
 \leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
@@
 \leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Sarubin, N.
@@
 \leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Campbell-Sills, L.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
@@
 \leavevmode\hypertarget{ref-Bernecker2017}{}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Bernecker, K.
@@
 
-\leavevmode\hypertarget{ref-Cacioppo1982}{}%
-\CSLLeftMargin{44. }
-\CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
-
 \leavevmode\hypertarget{ref-Bless1994}{}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
@@
 \leavevmode\hypertarget{ref-Paschke2016}{}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Paschke, L.
@@
 \leavevmode\hypertarget{ref-Schwarzer1999}{}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}
@@
 \leavevmode\hypertarget{ref-Tangney2004}{}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Tangney, J.
@@
 \leavevmode\hypertarget{ref-Sproesser2011}{}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
@@
 \leavevmode\hypertarget{ref-Patton1995}{}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
@@
 \leavevmode\hypertarget{ref-Hartmann2011}{}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Hartmann, A.
@@
 \leavevmode\hypertarget{ref-Derryberry2002}{}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
@@
 \leavevmode\hypertarget{ref-Wessa2010}{}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Wessa, M.
@@
 \leavevmode\hypertarget{ref-Lang2008}{}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Lang, P.
@@
 \leavevmode\hypertarget{ref-Yu2010}{}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
@@
 \leavevmode\hypertarget{ref-Bradley2000}{}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Bradley, M.
@@
 \leavevmode\hypertarget{ref-Fridlund1986}{}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Fridlund, A. J. \& Cacioppo, J. T. Guidelines for human electromyographic research. \emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
@@
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Enders, C.
@@
 \leavevmode\hypertarget{ref-Preece2020}{}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Preece, D.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2010}{}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2015}{}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{68. }
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 \emph{WHO-5.}
-General psychological well-being is assessed using the WHO-5 scale\textsuperscript{37,38}.
+General psychological well-being is assessed using the WHO-5 scale\textsuperscript{42,43}.
 5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{38}.
+The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{43}.
 
 \emph{Connor-Davidson Resilience Scale.}
-Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{39--41}.
+Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{44--46}.
 10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{40}.
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{45}.
 
 \emph{Emotion Regulation Questionnaire.}
-Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,42}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{62}
+Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,47}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{66}
 
 \emph{FlexER Scale.}
-Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{36} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{41} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 Psychometric properties are currently under investigation.
@@
 \emph{Implicit Theories Questionnaire.}
-Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{43}
+Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{48}
 4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{43}.
+The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{48}.
 
 \emph{Need for Cognition Scale.}
-Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{45}
+Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{49}
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{45,63} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{64}
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{49,67} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{68}
 
 \emph{Self-Regulation Scale.}
-As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{47} is used.
+As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{51} is used.
 The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{47}
+It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{51}
 
 \emph{Brief Self-Control Scale.}
-As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{48,49} is used.
+As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{52,53} is used.
 It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{49} .
+The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{53} .
 
 \emph{Barratt Impulsiveness Scale.}
-As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{50,51} is used.
+As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{54,55} is used.
 Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{51}
+An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{55}
 
 \emph{Attentional Control Scale.}
-Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{52} with items such as ``My concentration is good even if there is music in the room around me''.
+Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{56} with items such as ``My concentration is good even if there is music in the room around me''.
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{52}
+An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{56}
 

### 2022-06-03 06_Paper/ER-ED/TheoreticalBackground.Rmd
corrected typo

@@
 When given the choice, most individuals prefer tasks that are less effortful[@Hull1943].
-Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and is associated with Need for Cognition (NFC)[@Caccioppo1982], a stable measure of the individual pursuit and enjoyment of cognitive effort[@Westbrook2013;@Strobel2020].
+Cognitive effort avoidance has been reported in many contexts, for example in affective context[@Gonzalez-Garcia2021], the context of decision making[@Kool2010], and executive functions[@Cheval2020], and is associated with Need for Cognition (NFC)[@Cacioppo1982], a stable measure of the individual pursuit and enjoyment of cognitive effort[@Westbrook2013;@Strobel2020].
 In the area of emotion regulation, too, there are initial indications that people show a tendency towards effort avoidance.
@@
 This would mean that all strategies are a good option for goal achievement.
-A second person with less flexibility, however, would show high SVs only for only one strategy or low SVs for all of the strategies.
+A second person with less flexibility, however, would show high SVs only for one strategy or low SVs for all of the strategies.
 This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from. 

### 2022-06-03 06_Paper/COG-ED/Analysis.R
added BFs for H1a and H2a

@@ -809,7 +809,13 @@
   # get Bayes factors
   
   hypothesis1a_BF <- BayesFactor::anovaBF(formula = dprime ~ level, data = h1a_data, progress = FALSE)
-  hypothesis1a_contrasts$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3],
+  hypothesis1a_contrasts$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 1], y = h1a_data$dprime[h1a_data$level == 2],
+                                                     progress = FALSE, paired = TRUE))$bf,
+                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 1], y = h1a_data$dprime[h1a_data$level == 3],
+                                                     progress = FALSE, paired = TRUE))$bf,
+                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 1], y = h1a_data$dprime[h1a_data$level == 4],
+                                                     progress = FALSE, paired = TRUE))$bf,
+                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3],
                                                      progress = FALSE, paired = TRUE))$bf,
                                    BayesFactor::extractBF(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 4],
                                                      progress = FALSE, paired = TRUE))$bf,
@@ -861,7 +867,13 @@
   # get Bayes factors
   
   hypothesis1b_BF <- BayesFactor::anovaBF(formula = medianRT ~ level, data = h1b_data, progress = FALSE)
-  hypothesis1b_contrasts$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 2], y = h1b_data$medianRT[h1b_data$level == 3],
+  hypothesis1b_contrasts$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 1], y = h1b_data$medianRT[h1b_data$level == 2],
[…]

### 2022-06-03 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 The level of significance will be set to \(\alpha=.05\).
+For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the \emph{afex} package\textsuperscript{36}.
+Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values and will be reported when the assumption of sphericity is violated.
+If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
+Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
 
 \emph{Effect of valence on arousal and facial EMG.}
-To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-
+To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
 To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG \emph{corrugator} and \emph{levator} activity.
-Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
-Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
-If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the \emph{afex} package\textsuperscript{36}.
 
@@
 To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
-
 To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity will be conducted.
-
 To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
-Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
-Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
-If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.
-rmANOVAS will be run using the \emph{afex} package\textsuperscript{36}.
 
@@
 
-The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a regression using the \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
-Firstly, SVs will be ordered by magnitude.
-Secondly, for each participant a linear model will be built to estimate the individual \(intercept\) and \(slope\).
+The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
+To this end, for each participant, SVs will be sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
+The resulting \(intercept\) informs about the extent to which an individual considers any or all of the ER strategies as useful for regulation their emotion, while the \(slope\) informs about the flexibility in the use of emotion regulation strategies.
+The individual intercepts and slopes will then be entered as predictors in a regression model with the FlexER score as dependent variable.
+A positive association with the predictor \(intercept\) would indicate that overall higher SVs attached to ER strategies predicts higher scores on the FlexER scale.
+A positive association with the predictor \(slope\) would indicate that less negative slopes, i.e., a smaller preference for a given ER strategy, would be associated with a higher score of the FlexER scale.
 

### 2022-06-07 06_Paper/COG-ED/Analysis.R
changed H3a to SV-diffscores ANOVA

@@ -1469,48 +1469,39 @@
   
 ##### Hypothesis 3a ############################################################
   
-  # H3a: Subjective values positively predict individual NCS scores.
+  # H3a: Subjective values positively predict individual NFC scores.
   
   # make a temporary copy of the data frame
 
-  data_SV <- pipelines_data[["AARO"]][ ,c("subject","level","sv")]
+  data_SV <- pipelines_data[["AARO"]][ ,c("subject","level","sv","nfc")]
   
-  # create an index for the rows in which the participant ID changes
+  # create a data frame with the difference scores per subject (2-1,3-2,4-3)
   
-  subjectindex <- c(1,which(data_SV$subject != dplyr::lag(data_SV$subject)),nrow(data_SV))
+  diffscores <- diff(data_SV$sv)
+  h3_data <- data.frame(subject = data_SV$subject[-c(seq(from = 4, to = nrow(data_SV), by = 4))],
+                        nlevels = as.factor(rep(c("1-2","2-3","3-4"), nrow(data_SV)/4)),
+                        svdiff = diffscores[-c(seq(from = 4, to = nrow(data_SV)-4, by = 4))],
+                        nfc = data_SV$nfc[-c(seq(from = 4, to = nrow(data_SV), by = 4))])
   
-  # prepare empty data frame for the loop to feed into
+  # add column indicating NFC score above or below median
   
-  h3_data <- data.frame(subject = character(), axauc = double())
+  mediannfc <- median(h3_data$nfc)
+  h3_data$nfcmedian <- ifelse(h3_data$nfc < mediannfc, "low", "high")
+  h3_data$nfcmedian <- as.factor(h3_data$nfcmedian)
   
-  # calculate AUC of SVs per subject
+  # compute two-way ANOVA
   
-  for (i in 1:(length(subjectindex)-1)) {
-    
-    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
-                          axauc = bayestestR::auc(data_SV$level[subjectindex[i]:(subjectindex[i]+3)], data_SV$sv[subjectindex[i]:(subjectindex[i]+3)], method = "trapezoid") *
-                            ((data_SV$sv[subjectindex[i]+3] - data_SV$sv[subjectindex[i]+2]) +
-                               (data_SV$sv[subjectindex[i]+2] - data_SV$sv[subjectindex[i]+1]) +
[…]

### 2022-06-07 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex

@@
 
-\emph{Part three: ER choice.} After the discounting part, participants will choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
+\emph{Part three: ER choice.} After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
 Importantly, there will be no further instruction on what basis they should make their decision.

### 2022-06-07 06_Paper/ER-ED/method.Rmd

@@
 
-*Part three: ER choice.* <br> After the discounting part, participants will choose which of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
+*Part three: ER choice.* <br> After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
 Importantly, there will be no further instruction on what basis they should make their decision.

### 2022-06-07 06_Paper/COG-ED/Manuscript.Rmd
implemented comment 2.9

@@
 Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor.
-Within the model, we will control for *d'*, RT, correct, and post-correct trials.
+As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
+Within the model, we will therefore control for *d'*, RT, correct, and post-correct trials.
 $$

### 2022-06-07 06_Paper/ER-ED/method.Rmd
Update method.Rmd
4 Sätze vom Präteritum ins Präsens/Futur umformuliert

@@
 The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
-Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
-Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
-It was followed by neutral or negative picture for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the ragulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
+<!-- Kommentar Denise: Die folgenden Sätze waren im Präteritum formuliert, ich hab es einfach umformuliert-->Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
+Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
+It is followed by neutral or negative pictures for a total of 6 seconds.
+After each block, participants retrospectively will rate their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the ragulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
 

### 2022-06-07 06_Paper/ER-ED/method.Rmd
Update method.Rmd
under analyis plan: changed "active viewing" to "active viewing - negative" in H4a to make it consistent to the other Hypotheses

@@
 To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity will be conducted.
-To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
 

### 2022-06-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
incorporated changes and added references

@@
 Moreover, there is nothing like an objectively easiest ER strategy.
+It could be assumed, that the antecedent-focused strategies, i.e.
+attentional deployment and cognitive change, require less effort, because according to Gross[-@Gross1998antecedent] these strategies apply when the emotional reaction has not fully developed, yet.
+In contrast, suppression would need ongoing effort, because it takes effect late in the emotion generating process and does not alter the emotion itself. 
+A similar assumption has been made by Mesmer-Magnus et al.[-@MesmerMagnus2012], who state that Surface Acting (the equivalent to expressive suppression in emotional labor research) is supposed to continuously require high levels of energy (hence effort).
+Deep Acting (which refers to reappraisal), in turn, only initially needs the use of energy. 
+This would be in conflict with findings in our previous studies, that showed that many people choose expressive suppression because they evaluated it as less effortful, hence easy[@Scheffel2021].
+Others define emotion regulation on a continuum from explicit, conscious, and effortful to implicit, unconscious, automatic and effortless[@Gyurak2011].
+This would mean, that all explicit strategies that have been proposed by the process model of emotion regulation are similarly effortful[@Gross1998antecedent].
+Similarly, the flexibility approach of emotion regulation also states, that there is no "best" strategy[@Gross2015].
+An emotion regulation attempt is adaptive, when the intended, individual goal is reached.
+Those attempts could also consist of sequences of regulatory efforts using different strategies, which might be effective and effortless only in this specific context.
 Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 

### 2022-06-08 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 Moreover, there is nothing like an objectively easiest ER strategy.
+It could be assumed, that the antecedent-focused strategies, i.e.~attentional deployment and cognitive change, require less effort, because according to Gross\textsuperscript{1} these strategies apply when the emotional reaction has not fully developed, yet.
+In contrast, suppression would need ongoing effort, because it takes effect late in the emotion generating process and does not alter the emotion itself.
+A similar assumption has been made by Mesmer-Magnus et al.\textsuperscript{31}, who state that Surface Acting (the equivalent to expressive suppression in emotional labor research) is supposed to continuously require high levels of energy (hence effort).
+Deep Acting (which refers to reappraisal), in turn, only initially needs the use of energy.
+This would be in conflict with findings in our previous studies, that showed that many people choose expressive suppression because they evaluated it as less effortful, hence easy\textsuperscript{22}.
+Others define emotion regulation on a continuum from explicit, conscious, and effortful to implicit, unconscious, automatic and effortless\textsuperscript{32}.
+This would mean, that all explicit strategies that have been proposed by the process model of emotion regulation are similarly effortful\textsuperscript{1}.
+Similarly, the flexibility approach of emotion regulation also states, that there is no ``best'' strategy\textsuperscript{33}.
+An emotion regulation attempt is adaptive, when the intended, individual goal is reached.
+Those attempts could also consist of sequences of regulatory efforts using different strategies, which might be effective and effortless only in this specific context.
 Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
-In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{31}).
+In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{34}).
 
@@
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{32}.
-The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{33}.
-We used \emph{R} with \emph{R Studio}\textsuperscript{34,35} with the main packages \emph{afex}\textsuperscript{36} and \emph{BayesFactor}\textsuperscript{37} for all analyses.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{35}.
+The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{36}.
+We used \emph{R} with \emph{R Studio}\textsuperscript{37,38} with the main packages \emph{afex}\textsuperscript{39} and \emph{BayesFactor}\textsuperscript{40} for all analyses.
 The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
@@
 
-Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{38} at the Technische Universität Dresden.
+Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{41} at the Technische Universität Dresden.
 Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
@@
 After that, participants will choose one ER strategy to repeat one more time.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{39,40}.
+Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{42,43}.
 
@@
 The online survey will contain a number of questionnaires.
-In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{41}.\\
+In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{44}.\\
 It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
@@
 Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
-General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{42,43}.
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{46} will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,47}.
-Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{48}.
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,49} will be used.
-To assess self-control,\textsuperscript{50} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{51}, the Brief Self-Control Scale (BSCS)\textsuperscript{52,53}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{54,55}.
-Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{56}.
+General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{49} will be used.
+Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
+Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} will be used.
+To assess self-control,\textsuperscript{53} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
+Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
 For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
@@
 The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
-Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
-Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
-It was followed by neutral or negative picture for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the ragulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.
+Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
+Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
+It is followed by neutral or negative pictures for a total of 6 seconds.
+After each block, participants retrospectively will rate their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the ragulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.
 
@@
 
-Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{57} and the International Affective Picture System (IAPS)\textsuperscript{58}.
+Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{60} and the International Affective Picture System (IAPS)\textsuperscript{61}.
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
 Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
-An evolutionary algorithm\textsuperscript{59} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+An evolutionary algorithm\textsuperscript{62} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material 1.
@@
 
-Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{60}, similar to previous work by our group\textsuperscript{7}.
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{61}
+Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{63}, similar to previous work by our group\textsuperscript{7}.
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{64}
 The ground electrode will be placed over the left \emph{Mastoid}.
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{60}
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{63}
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
@@
 
-Sample size calculation is done using \emph{G*Power}\textsuperscript{62,63}.
+Sample size calculation is done using \emph{G*Power}\textsuperscript{65,66}.
 In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
@@
 The level of significance will be set to \(\alpha=.05\).
-For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the \emph{afex} package\textsuperscript{36}.
+For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the \emph{afex} package\textsuperscript{39}.
 Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values and will be reported when the assumption of sphericity is violated.
@@
 To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity will be conducted.
-To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
 
@@
 
-To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{64}.
+To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{67}.
 First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
@@
 \]
-Level-1-predictors will be centered within cluster\textsuperscript{65}.
+Level-1-predictors will be centered within cluster\textsuperscript{68}.
 Residuals of the final model will be inspected visually.
@@
 
-For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{37}, will be reported.
+For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{40}, will be reported.
 Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
@@
 
+\leavevmode\hypertarget{ref-MesmerMagnus2012}{}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Mesmer-Magnus, J.
+R., DeChurch, L.
+A.
+\& Wax, A.
+Moving emotional labor beyond surface and deep acting: A discordance-congruence perspective.
+\emph{Organizational Psychology Review} \textbf{2}, 6--53 (2012).}
+
+\leavevmode\hypertarget{ref-Gyurak2011}{}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Gyurak, A., Gross, J. J. \& Etkin, A. Explicit and implicit emotion regulation: A dual-process framework. \emph{Cogn Emot} \textbf{25}, 400--12 (2011).}
+
+\leavevmode\hypertarget{ref-Gross2015}{}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Gross, J. J. Emotion regulation: Current status and future prospects. \emph{Psychological Inquiry} \textbf{26}, 1--26 (2015).}
+
 \leavevmode\hypertarget{ref-Zerna2022}{}%
-\CSLLeftMargin{31. }
+\CSLLeftMargin{34. }
 \CSLRightInline{Zerna, J., Scheffel, C., Kührt, C.
@@
 \leavevmode\hypertarget{ref-Simmons2012}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{35. }
 \CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}
@@
 \leavevmode\hypertarget{ref-Peirce2019}{}%
-\CSLLeftMargin{33. }
+\CSLLeftMargin{36. }
 \CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
@@
 \leavevmode\hypertarget{ref-RCore2021}{}%
-\CSLLeftMargin{34. }
+\CSLLeftMargin{37. }
 \CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}
@@
 \leavevmode\hypertarget{ref-RStudioTeam2020}{}%
-\CSLLeftMargin{35. }
+\CSLLeftMargin{38. }
 \CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}
@@
 \leavevmode\hypertarget{ref-Singmann2021}{}%
-\CSLLeftMargin{36. }
+\CSLLeftMargin{39. }
 \CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}
@@
 \leavevmode\hypertarget{ref-Morey2021}{}%
-\CSLLeftMargin{37. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
@@
 \leavevmode\hypertarget{ref-Greiner2015}{}%
-\CSLLeftMargin{38. }
+\CSLLeftMargin{41. }
 \CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
@@
 \leavevmode\hypertarget{ref-Harris2009}{}%
-\CSLLeftMargin{39. }
+\CSLLeftMargin{42. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Harris2019}{}%
-\CSLLeftMargin{40. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Harris, P.
@@
 \leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{41. }
+\CSLLeftMargin{44. }
 \CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
@@
 \leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{42. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
@@
 \leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{43. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
@@
 \leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{44. }
+\CSLLeftMargin{47. }
 \CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
@@
 \leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{45. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Sarubin, N.
@@
 \leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{46. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Campbell-Sills, L.
@@
 \leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{47. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
@@
 \leavevmode\hypertarget{ref-Bernecker2017}{}%
-\CSLLeftMargin{48. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Bernecker, K.
@@
 \leavevmode\hypertarget{ref-Bless1994}{}%
-\CSLLeftMargin{49. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
@@
 \leavevmode\hypertarget{ref-Paschke2016}{}%
-\CSLLeftMargin{50. }
+\CSLLeftMargin{53. }
 \CSLRightInline{Paschke, L.
@@
 \leavevmode\hypertarget{ref-Schwarzer1999}{}%
-\CSLLeftMargin{51. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}
@@
 \leavevmode\hypertarget{ref-Tangney2004}{}%
-\CSLLeftMargin{52. }
+\CSLLeftMargin{55. }
 \CSLRightInline{Tangney, J.
@@
 \leavevmode\hypertarget{ref-Sproesser2011}{}%
-\CSLLeftMargin{53. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
@@
 \leavevmode\hypertarget{ref-Patton1995}{}%
-\CSLLeftMargin{54. }
+\CSLLeftMargin{57. }
 \CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
@@
 \leavevmode\hypertarget{ref-Hartmann2011}{}%
-\CSLLeftMargin{55. }
+\CSLLeftMargin{58. }
 \CSLRightInline{Hartmann, A.
@@
 \leavevmode\hypertarget{ref-Derryberry2002}{}%
-\CSLLeftMargin{56. }
+\CSLLeftMargin{59. }
 \CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
@@
 \leavevmode\hypertarget{ref-Wessa2010}{}%
-\CSLLeftMargin{57. }
+\CSLLeftMargin{60. }
 \CSLRightInline{Wessa, M.
@@
 \leavevmode\hypertarget{ref-Lang2008}{}%
-\CSLLeftMargin{58. }
+\CSLLeftMargin{61. }
 \CSLRightInline{Lang, P.
@@
 \leavevmode\hypertarget{ref-Yu2010}{}%
-\CSLLeftMargin{59. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
@@
 \leavevmode\hypertarget{ref-Bradley2000}{}%
-\CSLLeftMargin{60. }
+\CSLLeftMargin{63. }
 \CSLRightInline{Bradley, M.
@@
 \leavevmode\hypertarget{ref-Fridlund1986}{}%
-\CSLLeftMargin{61. }
+\CSLLeftMargin{64. }
 \CSLRightInline{Fridlund, A. J. \& Cacioppo, J. T. Guidelines for human electromyographic research. \emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
@@
 \leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{62. }
+\CSLLeftMargin{65. }
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{63. }
+\CSLLeftMargin{66. }
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{64. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
@@
 \leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{65. }
+\CSLLeftMargin{68. }
 \CSLRightInline{Enders, C.
@@
 \leavevmode\hypertarget{ref-Preece2020}{}%
-\CSLLeftMargin{66. }
+\CSLLeftMargin{69. }
 \CSLRightInline{Preece, D.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2010}{}%
-\CSLLeftMargin{67. }
+\CSLLeftMargin{70. }
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\hypertarget{ref-Fleischhauer2015}{}%
-\CSLLeftMargin{68. }
+\CSLLeftMargin{71. }
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 \emph{WHO-5.}
-General psychological well-being is assessed using the WHO-5 scale\textsuperscript{42,43}.
+General psychological well-being is assessed using the WHO-5 scale\textsuperscript{45,46}.
 5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{43}.
+The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{46}.
 
 \emph{Connor-Davidson Resilience Scale.}
-Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{44--46}.
+Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
 10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{45}.
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{48}.
 
 \emph{Emotion Regulation Questionnaire.}
-Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,47}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{66}
+Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{69}
 
 \emph{FlexER Scale.}
-Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{41} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{44} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 Psychometric properties are currently under investigation.
@@
 \emph{Implicit Theories Questionnaire.}
-Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{48}
+Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{51}
 4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{48}.
+The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{51}.
 
 \emph{Need for Cognition Scale.}
-Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{49}
+Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{52}
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{49,67} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{68}
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,70} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{71}
 
 \emph{Self-Regulation Scale.}
-As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{51} is used.
+As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} is used.
 The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{51}
+It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{54}
 
 \emph{Brief Self-Control Scale.}
-As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{52,53} is used.
+As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} is used.
 It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{53} .
+The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{56} .
 
 \emph{Barratt Impulsiveness Scale.}
-As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{54,55} is used.
+As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} is used.
 Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{55}
+An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{58}
 
 \emph{Attentional Control Scale.}
-Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{56} with items such as ``My concentration is good even if there is music in the room around me''.
+Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{56}
+An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{59}
 

### 2022-06-08 06_Paper/ER-ED/method.Rmd
added explanation on free text field
knitted document

@@
 In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
-It assess flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
+It assesses flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
 The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".
@@
 Participants should make their decision freely, according to criteria they consider important for themselves.
-However, participants will be asked to state the reasons for the decision afterwards.
+However, participants will be asked to state the reasons for the decision afterwards in RedCap using a free text field.
 As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.

### 2022-06-08 06_Paper/ER-ED/method.Rmd
corrected typo

@@
 
-Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
+Further psychological constructs will be assessed but have no clear hypotheses in the present work and are therefore investigated only exploratory:
 General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].

### 2022-06-09 06_Paper/ER-ED/method.Rmd
changed github repo

@@
 We used *R* with *R Studio*[@RCore2021; @RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.
-A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CAD.
+A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CAD).
 
@@
 The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
-<!-- Kommentar Denise: Die folgenden Sätze waren im Präteritum formuliert, ich hab es einfach umformuliert-->Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
+Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
 Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
@@
 
-The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
+The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CAD).

### 2022-06-09 06_Paper/ER-ED/method.Rmd
described 1vs1 comparisons

@@
 The order of the pairings will be randomized.
-Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option "1 € for strategy A or 1 € for strategy B".
-The participants decide by clicking the on-screen button of the respective option.
-The strategy that is not chosen will be assigned the fixed value of 2 €, the chosen strategy will be assigned a starting value of 1 €.
-From this point on, comparisons between strategies will follow the original COG-ED paradigm[@Westbrook2013].
+Because there is no strategy that is objectively more difficult, we will add initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
+They decide by clicking the on-screen button of the respective option.
+Each of the three strategy pairs will be presented three times in total, in a randomized order and randomly assigned which strategy appears on the left or right side of the screen.
+For each pair, the strategy that was chosen at least two out of three times will be assigned the flexible starting value of 1 €, the other strategy will be assigned the fixed value of 2 €.
+After this, comparisons between strategies will follow the original COG-ED paradigm[@Westbrook2013].
 Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).

### 2022-06-09 06_Paper/COG-ED/Manuscript.Rmd
implemented Editor's comment
added 1vs1 description

@@
 Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
-In each pair, the level chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1€ and is changed in every iteration.
-The other level in the pair will be set to a fixed value of 2€.
+This will be determined by presenting each possible pair of levels on screen with the question "Would you prefer 1\ € for level A or 1\ € for level B?".
+Participants respond by clicking the respective on-screen button.
+Each pair will be presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
+For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1\ € and is changed in every iteration.
+The other level in the pair will be set to a fixed value of 2\ €.
 Then, the effort discounting sensu Westbrook [-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
@@
 The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
+We will consider a $BF10$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF10$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].
 

### 2022-06-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document
fixed errors and knitted document

@@
 \documentclass[
-  english,
   man,floatsintext]{apa6}
@@
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Estimating individual subjective values of emotion regulation strategies},
-  pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1, \& Alexander Strobel1},
-  pdflang={en-EN},
-  pdfkeywords={emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
 
@@
 \makeatother
-\shorttitle{Subjective values of emotion regulation strategies}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 5630}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6233}
 \usepackage{lineno}
@@
 \usepackage{chngcntr}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Estimating individual subjective values of emotion regulation strategies},
+  pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1, \& Alexander Strobel1},
+  pdflang={en-EN},
+  pdfkeywords={emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
+\shorttitle{Subjective values of emotion regulation strategies}
+
 \authornote{
@@
 
-\abstract{
+\abstract{%
 Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly.
@@
 We used \emph{R} with \emph{R Studio}\textsuperscript{37,38} with the main packages \emph{afex}\textsuperscript{39} and \emph{BayesFactor}\textsuperscript{40} for all analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
-A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).
+The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CAD}.
+A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CAD}).
 
@@
 In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{44}.\\
-It assess flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
+It assesses flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
 The items are rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 
-Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
+Further psychological constructs will be assessed but have no clear hypotheses in the present work and are therefore investigated only exploratory:
 General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
@@
 To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} will be used.
-To assess self-control,\textsuperscript{53} sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
+To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
 Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
@@
 We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies will be presented with a monetary reward.
-The order of the pairings will be randomized.
-Because there is no strategy that is objectively more difficult, we will add an initial comparison that begins with the option ``1 € for strategy A or 1 € for strategy B''.
-The participants decide by clicking the on-screen button of the respective option.
-The strategy that is not chosen will be assigned the fixed value of 2 €, the chosen strategy will be assigned a starting value of 1 €.
-From this point on, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{29}.
+Because there is no strategy that is objectively more difficult, we will add initial comparisons asking the participants to choose between ``1 € for strategy A or 1 € for strategy B''.
+They decide by clicking the on-screen button of the respective option.
+Each of the three strategy pairs will be presented three times in total, in a randomized order and randomly assigned which strategy appears on the left or right side of the screen.
+For each pair, the strategy that was chosen at least two out of three times will be assigned the flexible starting value of 1 €, the other strategy will be assigned the fixed value of 2 €.
+After this, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{29}.
 Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
@@
 Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{63}, similar to previous work by our group\textsuperscript{7}.
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of.\textsuperscript{64}
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of\textsuperscript{64}.
 The ground electrode will be placed over the left \emph{Mastoid}.
@@
 Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset.\textsuperscript{63}
+EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset\textsuperscript{63}.
 Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
@@
 
-The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our \href{https://github.com/ChScheffel/CERED}{Github repository}.
+The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our \href{https://github.com/ChScheffel/CAD}{Github repository}.
 
@@
 \begin{CSLReferences}{0}{0}
-\leavevmode\hypertarget{ref-Gross1998antecedent}{}%
-\CSLLeftMargin{1. }
+\leavevmode\vadjust pre{\hypertarget{ref-Gross1998antecedent}{}}%
+\CSLLeftMargin{1. }%
 \CSLRightInline{Gross, J.
 J.
-Antecedent- and response-focused emotion regulation: Divergent consequences for experience, expression, and physiology.
+\href{https://doi.org/10.1037/0022-3514.74.1.224}{Antecedent- and response-focused emotion regulation: Divergent consequences for experience, expression, and physiology}.
 \emph{Journal of Personality and Social Psychology} \textbf{74}, 224--37 (1998).}
 
-\leavevmode\hypertarget{ref-Gross1998emerging}{}%
-\CSLLeftMargin{2. }
-\CSLRightInline{Gross, J. J. The emerging field of emotion regulation: An integrative review. \emph{Review of General Psychology} \textbf{2}, 271--299 (1998).}
-
-\leavevmode\hypertarget{ref-Powers2019}{}%
-\CSLLeftMargin{3. }
+\leavevmode\vadjust pre{\hypertarget{ref-Gross1998emerging}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Gross, J.
+J.
+\href{https://doi.org/10.1037/1089-2680.2.3.271}{The emerging field of emotion regulation: An integrative review}.
+\emph{Review of General Psychology} \textbf{2}, 271--299 (1998).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Powers2019}{}}%
+\CSLLeftMargin{3. }%
 \CSLRightInline{Powers, J.
@@
 S.
-Regulating emotion through distancing: A taxonomy, neurocognitive model, and supporting meta-analysis.
+\href{https://doi.org/10.1016/j.neubiorev.2018.04.023}{Regulating emotion through distancing: A taxonomy, neurocognitive model, and supporting meta-analysis}.
 \emph{Neuroscience and Biobehavioral Reviews} \textbf{96}, 155--173 (2019).}
 
-\leavevmode\hypertarget{ref-Webb2012}{}%
-\CSLLeftMargin{4. }
+\leavevmode\vadjust pre{\hypertarget{ref-Webb2012}{}}%
+\CSLLeftMargin{4. }%
 \CSLRightInline{Webb, T.
@@
 \& Sheeran, P.
-Dealing with feeling: A meta-analysis of the effectiveness of strategies derived from the process model of emotion regulation.
+\href{https://doi.org/10.1037/a0027600}{Dealing with feeling: A meta-analysis of the effectiveness of strategies derived from the process model of emotion regulation}.
 \emph{Psychological Bulletin} \textbf{138}, 775--808 (2012).}
 
-\leavevmode\hypertarget{ref-Zaehringer2020}{}%
-\CSLLeftMargin{5. }
+\leavevmode\vadjust pre{\hypertarget{ref-Zaehringer2020}{}}%
+\CSLLeftMargin{5. }%
 \CSLRightInline{Zaehringer, J., Jennen-Steinmetz, C., Schmahl, C., Ende, G.
 \& Paret, C.
-Psychophysiological effects of downregulating negative emotions: Insights from a meta-analysis of healthy adults.
+\href{https://doi.org/10.3389/fpsyg.2020.00470}{Psychophysiological effects of downregulating negative emotions: Insights from a meta-analysis of healthy adults}.
 \emph{Front Psychol} \textbf{11}, 470 (2020).}
 
-\leavevmode\hypertarget{ref-Burr2021}{}%
-\CSLLeftMargin{6. }
+\leavevmode\vadjust pre{\hypertarget{ref-Burr2021}{}}%
+\CSLLeftMargin{6. }%
 \CSLRightInline{Burr, D.
@@
 M.
-Anxiety, not regulation tendency, predicts how individuals regulate in the laboratory: An exploratory comparison of self-report and psychophysiology.
+\href{https://doi.org/ARTN\%20e0247246\%0A10.1371/journal.pone.0247246}{Anxiety, not regulation tendency, predicts how individuals regulate in the laboratory: An exploratory comparison of self-report and psychophysiology}.
 \emph{Plos One} \textbf{16}, (2021).}
 
-\leavevmode\hypertarget{ref-Gaertner2021}{}%
-\CSLLeftMargin{7. }
+\leavevmode\vadjust pre{\hypertarget{ref-Gaertner2021}{}}%
+\CSLLeftMargin{7. }%
 \CSLRightInline{Gärtner, A., Jawinski, P.
@@
 
-\leavevmode\hypertarget{ref-Schoenfelder2014}{}%
-\CSLLeftMargin{8. }
+\leavevmode\vadjust pre{\hypertarget{ref-Schoenfelder2014}{}}%
+\CSLLeftMargin{8. }%
 \CSLRightInline{Schönfelder, S., Kanske, P., Heissler, J.
 \& Wessa, M.
-Time course of emotion-related responding during distraction and reappraisal.
+\href{https://doi.org/10.1093/scan/nst116}{Time course of emotion-related responding during distraction and reappraisal}.
 \emph{Social Cognitive and Affective Neuroscience} \textbf{9}, 1310--9 (2014).}
 
-\leavevmode\hypertarget{ref-GrossJohn2003}{}%
-\CSLLeftMargin{9. }
+\leavevmode\vadjust pre{\hypertarget{ref-GrossJohn2003}{}}%
+\CSLLeftMargin{9. }%
 \CSLRightInline{Gross, J.
@@
 P.
-Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being.
+\href{https://doi.org/10.1037/0022-3514.85.2.348}{Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being}.
 \emph{Journal of Personality and Social Psychology} \textbf{85}, 348--62 (2003).}
 
-\leavevmode\hypertarget{ref-Aldao2010}{}%
-\CSLLeftMargin{10. }
+\leavevmode\vadjust pre{\hypertarget{ref-Aldao2010}{}}%
+\CSLLeftMargin{10. }%
 \CSLRightInline{Aldao, A., Nolen-Hoeksema, S.
 \& Schweizer, S.
-Emotion-regulation strategies across psychopathology: A meta-analytic review.
+\href{https://doi.org/10.1016/j.cpr.2009.11.004}{Emotion-regulation strategies across psychopathology: A meta-analytic review}.
 \emph{Clinical Psychology Review} \textbf{30}, 217--237 (2010).}
 
-\leavevmode\hypertarget{ref-Yoon2013}{}%
-\CSLLeftMargin{11. }
+\leavevmode\vadjust pre{\hypertarget{ref-Yoon2013}{}}%
+\CSLLeftMargin{11. }%
 \CSLRightInline{Yoon, K.
@@
 \& Joormann, J.
-A pathway from neuroticism to depression: Examining the role of emotion regulation.
+\href{https://doi.org/10.1080/10615806.2012.734810}{A pathway from neuroticism to depression: Examining the role of emotion regulation}.
 \emph{Anxiety, Stress, \& Coping} \textbf{26}, 558--72 (2013).}
 
-\leavevmode\hypertarget{ref-Aldao2015}{}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Aldao, A., Sheppes, G. \& Gross, J. J. Emotion regulation flexibility. \emph{Cognitive Therapy and Research} \textbf{39}, 263--278 (2015).}
-
-\leavevmode\hypertarget{ref-Bonanno2013}{}%
-\CSLLeftMargin{13. }
+\leavevmode\vadjust pre{\hypertarget{ref-Aldao2015}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Aldao, A., Sheppes, G.
+\& Gross, J.
+J.
+\href{https://doi.org/10.1007/s10608-014-9662-4}{Emotion regulation flexibility}.
+\emph{Cognitive Therapy and Research} \textbf{39}, 263--278 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bonanno2013}{}}%
+\CSLLeftMargin{13. }%
 \CSLRightInline{Bonanno, G.
@@
 L.
-Regulatory flexibility: An individual differences perspective on coping and emotion regulation.
+\href{https://doi.org/10.1177/1745691613504116}{Regulatory flexibility: An individual differences perspective on coping and emotion regulation}.
 \emph{Perspectives on Psychological Science} \textbf{8}, 591--612 (2013).}
 
-\leavevmode\hypertarget{ref-DixonGordon2015}{}%
-\CSLLeftMargin{14. }
+\leavevmode\vadjust pre{\hypertarget{ref-DixonGordon2015}{}}%
+\CSLLeftMargin{14. }%
 \CSLRightInline{Dixon-Gordon, K.
@@
 \& De Los Reyes, A.
-Repertoires of emotion regulation: A person-centered approach to assessing emotion regulation strategies and links to psychopathology.
+\href{https://doi.org/10.1080/02699931.2014.983046}{Repertoires of emotion regulation: A person-centered approach to assessing emotion regulation strategies and links to psychopathology}.
 \emph{Cogn Emot} \textbf{29}, 1314--25 (2015).}
 
-\leavevmode\hypertarget{ref-Lougheed2012}{}%
-\CSLLeftMargin{15. }
+\leavevmode\vadjust pre{\hypertarget{ref-Lougheed2012}{}}%
+\CSLLeftMargin{15. }%
 \CSLRightInline{Lougheed, J.
@@
 \& Hollenstein, T.
-A limited repertoire of emotion regulation strategies is associated with internalizing problems in adolescence.
+\href{https://doi.org/10.1111/j.1467-9507.2012.00663.x}{A limited repertoire of emotion regulation strategies is associated with internalizing problems in adolescence}.
 \emph{Social Development} \textbf{21}, 704--721 (2012).}
 
-\leavevmode\hypertarget{ref-Southward2018}{}%
-\CSLLeftMargin{16. }
+\leavevmode\vadjust pre{\hypertarget{ref-Southward2018}{}}%
+\CSLLeftMargin{16. }%
 \CSLRightInline{Southward, M.
@@
 S.
-Flexible, yet firm: A model of healthy emotion regulation.
+\href{https://doi.org/DOI\%2010.1521/jscp.2018.37.4.231}{Flexible, yet firm: A model of healthy emotion regulation}.
 \emph{Journal of Social and Clinical Psychology} \textbf{37}, 231--251 (2018).}
 
-\leavevmode\hypertarget{ref-Blanke2020}{}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Blanke, E. S. \emph{et al.} Mix it to fix it: Emotion regulation variability in daily life. \emph{Emotion} \textbf{20}, 473--485 (2020).}
-
-\leavevmode\hypertarget{ref-Tamir2015}{}%
-\CSLLeftMargin{18. }
+\leavevmode\vadjust pre{\hypertarget{ref-Blanke2020}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Blanke, E. S. \emph{et al.} \href{https://doi.org/10.1037/emo0000566}{Mix it to fix it: Emotion regulation variability in daily life}. \emph{Emotion} \textbf{20}, 473--485 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tamir2015}{}}%
+\CSLLeftMargin{18. }%
 \CSLRightInline{Tamir, M., Bigman, Y.
@@
 \& Schreier, J.
-An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making.
+\href{https://doi.org/10.1037/emo0000021}{An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making}.
 \emph{Emotion} \textbf{15}, 90--103 (2015).}
 
-\leavevmode\hypertarget{ref-Kable2007}{}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Kable, J. W. \& Glimcher, P. W. The neural correlates of subjective value during intertemporal choice. \emph{Nat Neurosci} \textbf{10}, 1625--33 (2007).}
-
-\leavevmode\hypertarget{ref-Sheppes2014}{}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Sheppes, G. \emph{et al.} Emotion regulation choice: A conceptual framework and supporting evidence. \emph{Journal of Experimental Psychology: General} \textbf{143}, 163--81 (2014).}
-
-\leavevmode\hypertarget{ref-Sheppes2011}{}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Sheppes, G., Scheibe, S., Suri, G. \& Gross, J. J. Emotion-regulation choice. \emph{Psychological Science} \textbf{22}, 1391--6 (2011).}
-
-\leavevmode\hypertarget{ref-Scheffel2021}{}%
-\CSLLeftMargin{22. }
+\leavevmode\vadjust pre{\hypertarget{ref-Kable2007}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Kable, J.
+W.
+\& Glimcher, P.
+W.
+\href{https://doi.org/10.1038/nn2007}{The neural correlates of subjective value during intertemporal choice}.
+\emph{Nat Neurosci} \textbf{10}, 1625--33 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sheppes2014}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Sheppes, G.
+\emph{et al.} \href{https://doi.org/10.1037/a0030831}{Emotion regulation choice: A conceptual framework and supporting evidence}.
+\emph{Journal of Experimental Psychology: General} \textbf{143}, 163--81 (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sheppes2011}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Sheppes, G., Scheibe, S., Suri, G.
+\& Gross, J.
+J.
+\href{https://doi.org/10.1177/0956797611418350}{Emotion-regulation choice}.
+\emph{Psychological Science} \textbf{22}, 1391--6 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Scheffel2021}{}}%
+\CSLLeftMargin{22. }%
 \CSLRightInline{Scheffel, C.
-\emph{et al.} Effort beats effectiveness in emotion regulation choice: Differences between suppression and distancing in subjective and physiological measures.
+\emph{et al.} \href{https://doi.org/10.1111/psyp.13908}{Effort beats effectiveness in emotion regulation choice: Differences between suppression and distancing in subjective and physiological measures}.
 \emph{Psychophysiology} \textbf{00}, e13908 (2021).}
 
-\leavevmode\hypertarget{ref-Inzlicht2018}{}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Inzlicht, M., Shenhav, A. \& Olivola, C. Y. The effort paradox: Effort is both costly and valued. \emph{Trends Cogn Sci} \textbf{22}, 337--349 (2018).}
-
-\leavevmode\hypertarget{ref-Hull1943}{}%
-\CSLLeftMargin{24. }
+\leavevmode\vadjust pre{\hypertarget{ref-Inzlicht2018}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Inzlicht, M., Shenhav, A.
+\& Olivola, C.
+Y.
+\href{https://doi.org/10.1016/j.tics.2018.01.007}{The effort paradox: Effort is both costly and valued}.
+\emph{Trends Cogn Sci} \textbf{22}, 337--349 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hull1943}{}}%
+\CSLLeftMargin{24. }%
 \CSLRightInline{Hull, C. L. \emph{Principles of behavior: An introduction to behavior theory}. (Appleton-Century-Crofts, 1943).}
 
-\leavevmode\hypertarget{ref-Gonzalez-Garcia2021}{}%
-\CSLLeftMargin{25. }
-\CSLRightInline{Gonzalez-Garcia, C. \emph{et al.} Induced affective states do not modulate effort avoidance. \emph{Psychol Res} \textbf{85}, 1016--1028 (2021).}
-
-\leavevmode\hypertarget{ref-Kool2010}{}%
-\CSLLeftMargin{26. }
-\CSLRightInline{Kool, W., McGuire, J. T., Rosen, Z. B. \& Botvinick, M. M. Decision making and the avoidance of cognitive demand. \emph{J Exp Psychol Gen} \textbf{139}, 665--82 (2010).}
-
-\leavevmode\hypertarget{ref-Cheval2020}{}%
-\CSLLeftMargin{27. }
-\CSLRightInline{Cheval, B. \emph{et al.} Higher inhibitory control is required to escape the innate attraction to effort minimization. \emph{Psychology of Sport and Exercise} \textbf{51}, (2020).}
-
-\leavevmode\hypertarget{ref-Cacioppo1982}{}%
-\CSLLeftMargin{28. }
-\CSLRightInline{Cacioppo, J. T. \& Petty, R. E. The need for cognition. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
-
-\leavevmode\hypertarget{ref-Westbrook2013}{}%
-\CSLLeftMargin{29. }
+\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Garcia2021}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Gonzalez-Garcia, C.
+\emph{et al.} \href{https://doi.org/10.1007/s00426-020-01300-9}{Induced affective states do not modulate effort avoidance}.
+\emph{Psychol Res} \textbf{85}, 1016--1028 (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kool2010}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Kool, W., McGuire, J.
+T., Rosen, Z.
+B.
+\& Botvinick, M.
+M.
+\href{https://doi.org/10.1037/a0020198}{Decision making and the avoidance of cognitive demand}.
+\emph{J Exp Psychol Gen} \textbf{139}, 665--82 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cheval2020}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{Cheval, B.
+\emph{et al.} \href{https://doi.org/ARTN\%20101781\%0A10.1016/j.psychsport.2020.101781}{Higher inhibitory control is required to escape the innate attraction to effort minimization}.
+\emph{Psychology of Sport and Exercise} \textbf{51}, (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cacioppo1982}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Cacioppo, J.
+T.
+\& Petty, R.
+E.
+\href{https://doi.org/10.1037//0022-3514.42.1.116}{The need for cognition}.
+\emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Westbrook2013}{}}%
+\CSLLeftMargin{29. }%
 \CSLRightInline{Westbrook, A., Kester, D.
@@
 S.
-What is the subjective cost of cognitive effort?
-{Load}, trait, and aging effects revealed by economic preference.
+\href{https://doi.org/10.1371/journal.pone.0068210}{What is the subjective cost of cognitive effort?
+{Load}, trait, and aging effects revealed by economic preference}.
 \emph{PLOS ONE} \textbf{8}, e68210 (2013).}
 
-\leavevmode\hypertarget{ref-Strobel2020}{}%
-\CSLLeftMargin{30. }
-\CSLRightInline{Strobel, A. \emph{et al.} Dispositional cognitive effort investment and behavioral demand avoidance: Are they related? \emph{PLoS One} \textbf{15}, e0239817 (2020).}
-
-\leavevmode\hypertarget{ref-MesmerMagnus2012}{}%
-\CSLLeftMargin{31. }
+\leavevmode\vadjust pre{\hypertarget{ref-Strobel2020}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Strobel, A.
+\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0239817}{Dispositional cognitive effort investment and behavioral demand avoidance: Are they related?} \emph{PLoS One} \textbf{15}, e0239817 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-MesmerMagnus2012}{}}%
+\CSLLeftMargin{31. }%
 \CSLRightInline{Mesmer-Magnus, J.
@@
 \& Wax, A.
-Moving emotional labor beyond surface and deep acting: A discordance-congruence perspective.
+\href{https://doi.org/10.1177/2041386611417746}{Moving emotional labor beyond surface and deep acting: A discordance-congruence perspective}.
 \emph{Organizational Psychology Review} \textbf{2}, 6--53 (2012).}
 
-\leavevmode\hypertarget{ref-Gyurak2011}{}%
-\CSLLeftMargin{32. }
-\CSLRightInline{Gyurak, A., Gross, J. J. \& Etkin, A. Explicit and implicit emotion regulation: A dual-process framework. \emph{Cogn Emot} \textbf{25}, 400--12 (2011).}
-
-\leavevmode\hypertarget{ref-Gross2015}{}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Gross, J. J. Emotion regulation: Current status and future prospects. \emph{Psychological Inquiry} \textbf{26}, 1--26 (2015).}
-
-\leavevmode\hypertarget{ref-Zerna2022}{}%
-\CSLLeftMargin{34. }
+\leavevmode\vadjust pre{\hypertarget{ref-Gyurak2011}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Gyurak, A., Gross, J.
+J.
+\& Etkin, A.
+\href{https://doi.org/10.1080/02699931.2010.544160}{Explicit and implicit emotion regulation: A dual-process framework}.
+\emph{Cogn Emot} \textbf{25}, 400--12 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Gross2015}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Gross, J. J. \href{https://doi.org/10.1080/1047840x.2014.940781}{Emotion regulation: Current status and future prospects}. \emph{Psychological Inquiry} \textbf{26}, 1--26 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Zerna2022}{}}%
+\CSLLeftMargin{34. }%
 \CSLRightInline{Zerna, J., Scheffel, C., Kührt, C.
@@
 
-\leavevmode\hypertarget{ref-Simmons2012}{}%
-\CSLLeftMargin{35. }
+\leavevmode\vadjust pre{\hypertarget{ref-Simmons2012}{}}%
+\CSLLeftMargin{35. }%
 \CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}
 
-\leavevmode\hypertarget{ref-Peirce2019}{}%
-\CSLLeftMargin{36. }
-\CSLRightInline{Peirce, J. \emph{et al.} {PsychoPy2}: {Experiments} in behavior made easy. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
-
-\leavevmode\hypertarget{ref-RCore2021}{}%
-\CSLLeftMargin{37. }
-\CSLRightInline{R Core Team. \emph{R: A language and environment for statistical computing}. (R Foundation for Statistical Computing, 2021).}
-
-\leavevmode\hypertarget{ref-RStudioTeam2020}{}%
-\CSLLeftMargin{38. }
-\CSLRightInline{RStudio Team. {RStudio}: {Integrated} development for {R}. (2020).}
-
-\leavevmode\hypertarget{ref-Singmann2021}{}%
-\CSLLeftMargin{39. }
-\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{Afex: {A}nalysis of factorial experiments}. (2021).}
-
-\leavevmode\hypertarget{ref-Morey2021}{}%
-\CSLLeftMargin{40. }
-\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{{BayesFactor}: {Computation} of {Bayes} factors for common designs}. (2021).}
-
-\leavevmode\hypertarget{ref-Greiner2015}{}%
-\CSLLeftMargin{41. }
-\CSLRightInline{Greiner, B. Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
-
-\leavevmode\hypertarget{ref-Harris2009}{}%
-\CSLLeftMargin{42. }
+\leavevmode\vadjust pre{\hypertarget{ref-Peirce2019}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Peirce, J.
+\emph{et al.} \href{https://doi.org/10.3758/s13428-018-01193-y}{{PsychoPy2}: {Experiments} in behavior made easy}.
+\emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RCore2021}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RStudioTeam2020}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{RStudio Team. \href{http://www.rstudio.com}{{RStudio}: {Integrated} development for {R}}. (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Singmann2021}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{\href{https://CRAN.R-project.org/package=afex}{Afex: {A}nalysis of factorial experiments}}. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Morey2021}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{\href{https://CRAN.R-project.org/package=BayesFactor}{{BayesFactor}: {Computation} of {Bayes} factors for common designs}}. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Greiner2015}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{Greiner, B.
+\href{https://doi.org/10.1007/s40881-015-0004-4}{Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}}.
+\emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Harris2009}{}}%
+\CSLLeftMargin{42. }%
 \CSLRightInline{Harris, P.
 A.
-\emph{et al.} Research electronic data capture ({REDCap})---{A} metadata-driven methodology and workflow process for providing translational research informatics support.
+\emph{et al.} \href{https://doi.org/10.1016/j.jbi.2008.08.010}{Research electronic data capture ({REDCap})---{A} metadata-driven methodology and workflow process for providing translational research informatics support}.
 \emph{Journal of Biomedical Informatics} \textbf{42}, 377--381 (2009).}
 
-\leavevmode\hypertarget{ref-Harris2019}{}%
-\CSLLeftMargin{43. }
+\leavevmode\vadjust pre{\hypertarget{ref-Harris2019}{}}%
+\CSLLeftMargin{43. }%
 \CSLRightInline{Harris, P.
 A.
-\emph{et al.} The {REDCap} consortium: {Building} an international community of software platform partners.
+\emph{et al.} \href{https://doi.org/10.1016/j.jbi.2019.103208}{The {REDCap} consortium: {Building} an international community of software platform partners}.
 \emph{Journal of Biomedical Informatics} \textbf{95}, 103208 (2019).}
 
-\leavevmode\hypertarget{ref-Doerfel2019}{}%
-\CSLLeftMargin{44. }
+\leavevmode\vadjust pre{\hypertarget{ref-Doerfel2019}{}}%
+\CSLLeftMargin{44. }%
 \CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
 
-\leavevmode\hypertarget{ref-Bech2004}{}%
-\CSLLeftMargin{45. }
+\leavevmode\vadjust pre{\hypertarget{ref-Bech2004}{}}%
+\CSLLeftMargin{45. }%
 \CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
 
-\leavevmode\hypertarget{ref-Braehler2007}{}%
-\CSLLeftMargin{46. }
+\leavevmode\vadjust pre{\hypertarget{ref-Braehler2007}{}}%
+\CSLLeftMargin{46. }%
 \CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
 \& Schmidt, S.
-Teststatistische pr{ü}fung und normierung der deutschen versionen des EUROHIS-QOL lebensqualit{ä}t-index und des WHO-5 wohlbefindens-index.
+\href{https://doi.org/10.1026/0012-1924.53.2.83}{Teststatistische pr{ü}fung und normierung der deutschen versionen des EUROHIS-QOL lebensqualit{ä}t-index und des WHO-5 wohlbefindens-index}.
 \emph{Diagnostica} \textbf{53}, 83--96 (2007).}
 
-\leavevmode\hypertarget{ref-Connor2003}{}%
-\CSLLeftMargin{47. }
-\CSLRightInline{Connor, K. M. \& Davidson, J. R. Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC). \emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
-
-\leavevmode\hypertarget{ref-Sarubin2015}{}%
-\CSLLeftMargin{48. }
+\leavevmode\vadjust pre{\hypertarget{ref-Connor2003}{}}%
+\CSLLeftMargin{47. }%
+\CSLRightInline{Connor, K.
+M.
+\& Davidson, J.
+R.
+\href{https://doi.org/10.1002/da.10113}{Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC)}.
+\emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sarubin2015}{}}%
+\CSLLeftMargin{48. }%
 \CSLRightInline{Sarubin, N.
-\emph{et al.} First analysis of the 10-and 25-item german version of the connor-davidson resilience scale (CD-RISC) regarding psychometric properties and components.
+\emph{et al.} \href{https://doi.org/10.1026/0943-8149/a000142}{First analysis of the 10-and 25-item german version of the connor-davidson resilience scale (CD-RISC) regarding psychometric properties and components}.
 \emph{Zeitschrift Fur Gesundheitspsychologie} \textbf{23}, 112--122 (2015).}
 
-\leavevmode\hypertarget{ref-Campbell-Sills2007}{}%
-\CSLLeftMargin{49. }
+\leavevmode\vadjust pre{\hypertarget{ref-Campbell-Sills2007}{}}%
+\CSLLeftMargin{49. }%
 \CSLRightInline{Campbell-Sills, L.
@@
 B.
-Psychometric analysis and refinement of the connor-davidson resilience scale (CD-RISC): Validation of a 10-item measure of resilience.
+\href{https://doi.org/10.1002/jts.20271}{Psychometric analysis and refinement of the connor-davidson resilience scale (CD-RISC): Validation of a 10-item measure of resilience}.
 \emph{Journal of Traumatic Stress} \textbf{20}, 1019--28 (2007).}
 
-\leavevmode\hypertarget{ref-Abler2009}{}%
-\CSLLeftMargin{50. }
-\CSLRightInline{Abler, B. \& Kessler, H. Emotion regulation questionnaire - a german version of the ERQ by gross and john. \emph{Diagnostica} \textbf{55}, 144--152 (2009).}
-
-\leavevmode\hypertarget{ref-Bernecker2017}{}%
-\CSLLeftMargin{51. }
+\leavevmode\vadjust pre{\hypertarget{ref-Abler2009}{}}%
+\CSLLeftMargin{50. }%
+\CSLRightInline{Abler, B.
+\& Kessler, H.
+\href{https://doi.org/10.1026/0012-1924.55.3.144}{Emotion regulation questionnaire - a german version of the ERQ by gross and john}.
+\emph{Diagnostica} \textbf{55}, 144--152 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bernecker2017}{}}%
+\CSLLeftMargin{51. }%
 \CSLRightInline{Bernecker, K.
 \& Job, V.
-Implicit theories about willpower in resisting temptations and emotion control.
+\href{https://doi.org/10.1027/2151-2604/a000292}{Implicit theories about willpower in resisting temptations and emotion control}.
 \emph{Zeitschrift Fur Psychologie-Journal of Psychology} \textbf{225}, 157--166 (2017).}
 
-\leavevmode\hypertarget{ref-Bless1994}{}%
-\CSLLeftMargin{52. }
+\leavevmode\vadjust pre{\hypertarget{ref-Bless1994}{}}%
+\CSLLeftMargin{52. }%
 \CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
@@
 \& Schwarz, N.
-Need for cognition - a scale measuring engagement and happiness in cognitive tasks.
+\href{\%3CGo\%20to\%20ISI\%3E://WOS:A1994NR83900004}{Need for cognition - a scale measuring engagement and happiness in cognitive tasks}.
 \emph{Zeitschrift Für Sozialpsychologie} \textbf{25}, 147--154 (1994).}
 
-\leavevmode\hypertarget{ref-Paschke2016}{}%
-\CSLLeftMargin{53. }
+\leavevmode\vadjust pre{\hypertarget{ref-Paschke2016}{}}%
+\CSLLeftMargin{53. }%
 \CSLRightInline{Paschke, L.
 M.
-\emph{et al.} Individual differences in self-reported self-control predict successful emotion regulation.
+\emph{et al.} \href{https://doi.org/10.1093/scan/nsw036}{Individual differences in self-reported self-control predict successful emotion regulation}.
 \emph{Social Cognitive and Affective Neuroscience} \textbf{11}, 1193--204 (2016).}
 
-\leavevmode\hypertarget{ref-Schwarzer1999}{}%
-\CSLLeftMargin{54. }
-\CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. Self-regulation scale. (1999).}
-
-\leavevmode\hypertarget{ref-Tangney2004}{}%
-\CSLLeftMargin{55. }
+\leavevmode\vadjust pre{\hypertarget{ref-Schwarzer1999}{}}%
+\CSLLeftMargin{54. }%
+\CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. \href{http://userpage.fu-berlin.de/~health/selfreg_g.htm}{Self-regulation scale}. (1999).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tangney2004}{}}%
+\CSLLeftMargin{55. }%
 \CSLRightInline{Tangney, J.
@@
 L.
-High self-control predicts good adjustment, less pathology, better grades, and interpersonal success.
+\href{https://doi.org/10.1111/j.0022-3506.2004.00263.x}{High self-control predicts good adjustment, less pathology, better grades, and interpersonal success}.
 \emph{Journal of Personality} \textbf{72}, 271--324 (2004).}
 
-\leavevmode\hypertarget{ref-Sproesser2011}{}%
-\CSLLeftMargin{56. }
+\leavevmode\vadjust pre{\hypertarget{ref-Sproesser2011}{}}%
+\CSLLeftMargin{56. }%
 \CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
 \& Renner, B.
-Candy or apple?
-How self-control resources and motives impact dietary healthiness in women.
+\href{https://doi.org/10.1016/j.appet.2011.01.028}{Candy or apple?
+How self-control resources and motives impact dietary healthiness in women}.
 \emph{Appetite} \textbf{56}, 784--787 (2011).}
 
-\leavevmode\hypertarget{ref-Patton1995}{}%
-\CSLLeftMargin{57. }
-\CSLRightInline{Patton, J. H., Stanford, M. S. \& Barratt, E. S. Factor structure of the barratt impulsiveness scale. \emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
-
-\leavevmode\hypertarget{ref-Hartmann2011}{}%
-\CSLLeftMargin{58. }
+\leavevmode\vadjust pre{\hypertarget{ref-Patton1995}{}}%
+\CSLLeftMargin{57. }%
+\CSLRightInline{Patton, J.
+H., Stanford, M.
+S.
+\& Barratt, E.
+S.
+\href{https://doi.org/10.1002/1097-4679(199511)51:6\%3C768::aid-jclp2270510607\%3E3.0.co;2-1}{Factor structure of the barratt impulsiveness scale}.
+\emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hartmann2011}{}}%
+\CSLLeftMargin{58. }%
 \CSLRightInline{Hartmann, A.
@@
 \& Hilbert, A.
-Psychometric properties of the german version of the barratt impulsiveness scale, version 11 (BIS-11) for adolescents.
+\href{https://doi.org/10.2466/08.09.10.PMS.112.2.353-368}{Psychometric properties of the german version of the barratt impulsiveness scale, version 11 (BIS-11) for adolescents}.
 \emph{Perceptual and Motor Skills} \textbf{112}, 353--368 (2011).}
 
-\leavevmode\hypertarget{ref-Derryberry2002}{}%
-\CSLLeftMargin{59. }
-\CSLRightInline{Derryberry, D. \& Reed, M. A. Anxiety-related attentional biases and their regulation by attentional control. \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
-
-\leavevmode\hypertarget{ref-Wessa2010}{}%
-\CSLLeftMargin{60. }
+\leavevmode\vadjust pre{\hypertarget{ref-Derryberry2002}{}}%
+\CSLLeftMargin{59. }%
+\CSLRightInline{Derryberry, D.
+\& Reed, M.
+A.
+\href{https://doi.org/10.1037//0021-843X.111.2.225}{Anxiety-related attentional biases and their regulation by attentional control.} \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wessa2010}{}}%
+\CSLLeftMargin{60. }%
 \CSLRightInline{Wessa, M.
@@
 
-\leavevmode\hypertarget{ref-Lang2008}{}%
-\CSLLeftMargin{61. }
+\leavevmode\vadjust pre{\hypertarget{ref-Lang2008}{}}%
+\CSLLeftMargin{61. }%
 \CSLRightInline{Lang, P.
@@
 
-\leavevmode\hypertarget{ref-Yu2010}{}%
-\CSLLeftMargin{62. }
+\leavevmode\vadjust pre{\hypertarget{ref-Yu2010}{}}%
+\CSLLeftMargin{62. }%
 \CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
 
-\leavevmode\hypertarget{ref-Bradley2000}{}%
-\CSLLeftMargin{63. }
+\leavevmode\vadjust pre{\hypertarget{ref-Bradley2000}{}}%
+\CSLLeftMargin{63. }%
 \CSLRightInline{Bradley, M.
@@
 
-\leavevmode\hypertarget{ref-Fridlund1986}{}%
-\CSLLeftMargin{64. }
-\CSLRightInline{Fridlund, A. J. \& Cacioppo, J. T. Guidelines for human electromyographic research. \emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
-
-\leavevmode\hypertarget{ref-Faul2007}{}%
-\CSLLeftMargin{65. }
+\leavevmode\vadjust pre{\hypertarget{ref-Fridlund1986}{}}%
+\CSLLeftMargin{64. }%
+\CSLRightInline{Fridlund, A.
+J.
+\& Cacioppo, J.
+T.
+\href{https://doi.org/10.1111/j.1469-8986.1986.tb00676.x}{Guidelines for human electromyographic research}.
+\emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Faul2007}{}}%
+\CSLLeftMargin{65. }%
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
 \& Buchner, A.
-G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences.
+\href{https://doi.org/10.3758/BF03193146}{G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences}.
 \emph{Behavior Research Methods} \textbf{39}, 175--191 (2007).}
 
-\leavevmode\hypertarget{ref-Faul2009}{}%
-\CSLLeftMargin{66. }
+\leavevmode\vadjust pre{\hypertarget{ref-Faul2009}{}}%
+\CSLLeftMargin{66. }%
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
 \& Lang, A.-G.
-Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses.
+\href{https://doi.org/10.3758/BRM.41.4.1149}{Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses}.
 \emph{Behavior Research Methods} \textbf{41}, 1149--1160 (2009).}
 
-\leavevmode\hypertarget{ref-Kuznetsova2017}{}%
-\CSLLeftMargin{67. }
-\CSLRightInline{Kuznetsova, A., Brockhoff, P. B. \& Christensen, R. H. B. {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
-
-\leavevmode\hypertarget{ref-Enders2007}{}%
-\CSLLeftMargin{68. }
+\leavevmode\vadjust pre{\hypertarget{ref-Kuznetsova2017}{}}%
+\CSLLeftMargin{67. }%
+\CSLRightInline{Kuznetsova, A., Brockhoff, P.
+B.
+\& Christensen, R.
+H.
+B.
+\href{https://doi.org/10.18637/jss.v082.i13}{{lmerTest} package: Tests in linear mixed effects models}.
+\emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Enders2007}{}}%
+\CSLLeftMargin{68. }%
 \CSLRightInline{Enders, C.
@@
 \& Tofighi, D.
-Centering predictor variables in cross-sectional multilevel models: {A} new look at an old issue.
-\emph{Psychological Methods} \textbf{12}, 121--138 (2007).}
-
-\leavevmode\hypertarget{ref-Preece2020}{}%
-\CSLLeftMargin{69. }
+\href{https://doi.org/10.1037/1082-989x.12.2.121}{Centering predictor variables in cross-sectional multilevel models: {A} new look at an old issue.} \emph{Psychological Methods} \textbf{12}, 121--138 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
+\CSLLeftMargin{69. }%
 \CSLRightInline{Preece, D.
@@
 J.
-The emotion regulation questionnaire: Psychometric properties in general community samples.
+\href{https://doi.org/10.1080/00223891.2018.1564319}{The emotion regulation questionnaire: Psychometric properties in general community samples}.
 \emph{J Pers Assess} \textbf{102}, 348--356 (2020).}
 
-\leavevmode\hypertarget{ref-Fleischhauer2010}{}%
-\CSLLeftMargin{70. }
+\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
+\CSLLeftMargin{70. }%
 \CSLRightInline{Fleischhauer, M.
-\emph{et al.} Same or different?
-{Clarifying} the relationship of need for cognition to personality and intelligence.
+\emph{et al.} \href{https://doi.org/10.1177/0146167209351886}{Same or different?
+{Clarifying} the relationship of need for cognition to personality and intelligence}.
 \emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}
 
-\leavevmode\hypertarget{ref-Fleischhauer2015}{}%
-\CSLLeftMargin{71. }
+\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
+\CSLLeftMargin{71. }%
 \CSLRightInline{Fleischhauer, M., Strobel, A.
 \& Strobel, A.
-Directly and indirectly assessed {N}eed for {C}ognition differentially predict spontaneous and reflective information processing behavior.
+\href{https://doi.org/10.1027/1614-0001/a000161}{Directly and indirectly assessed {N}eed for {C}ognition differentially predict spontaneous and reflective information processing behavior}.
 \emph{Journal of Individual Differences} \textbf{36}, 101--109 (2015).}
@@
 \newpage
+
 \begin{figure}
@@
 
-\emph{Figure 1.}
-Exemplary visualization of two response patterns.
+\emph{Figure 1.} Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 
-\emph{Figure 2.}
-Block design of the paradigm.
-Every participant starts with two ``active viewing'' blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply.
+\emph{Figure 2.} Block design of the paradigm.
+Every participant starts with two ``active viewing'' blocks containing neutral (Block 1) and negative (Block 2) pictures.
+Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
+After, the discounting procedure takes place.
+All three regulation strategies are pairwise compared.
+Before the last block, participants can decide which regulation strategy they want to reapply.
 Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
@@
 
-\emph{WHO-5.}
-General psychological well-being is assessed using the WHO-5 scale\textsuperscript{45,46}.
+\emph{WHO-5.} General psychological well-being is assessed using the WHO-5 scale\textsuperscript{45,46}.
 5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
@@
 
-\emph{Connor-Davidson Resilience Scale.}
-Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
+\emph{Connor-Davidson Resilience Scale.} Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
 10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
@@
 
-\emph{Emotion Regulation Questionnaire.}
-Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)).\textsuperscript{69}
-
-\emph{FlexER Scale.}
-Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{44} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+\emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{69}.
+
+\emph{FlexER Scale.} Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{44} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 Psychometric properties are currently under investigation.
 
-\emph{Implicit Theories Questionnaire.}
-Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of.\textsuperscript{51}
+\emph{Implicit Theories Questionnaire.} Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of\textsuperscript{51}.
 4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
@@
 
-\emph{Need for Cognition Scale.}
-Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale.\textsuperscript{52}
+\emph{Need for Cognition Scale.} Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale\textsuperscript{52}.
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,70} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks.\textsuperscript{71}
-
-\emph{Self-Regulation Scale.}
-As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} is used.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,70} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{71}.
+
+\emph{Self-Regulation Scale.} As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} is used.
 The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency {[}Cronbach's \(\alpha>.80\);{]}.\textsuperscript{54}
-
-\emph{Brief Self-Control Scale.}
-As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} is used.
+It has high internal consistency {[}Cronbach's \(\alpha>.80\);\textsuperscript{54}{]}.
+
+\emph{Brief Self-Control Scale.} As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} is used.
 It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
@@
 
-\emph{Barratt Impulsiveness Scale.}
-As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} is used.
+\emph{Barratt Impulsiveness Scale.} As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} is used.
 Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported.\textsuperscript{58}
-
-\emph{Attentional Control Scale.}
-Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
+An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported\textsuperscript{58}.
+
+\emph{Attentional Control Scale.} Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported.\textsuperscript{59}
+An internal consistency of Cronbach's \(\alpha=.88\) was reported\textsuperscript{59}.
 
@@
 
-\emph{Corrugator}:
-ANOVA:
+\emph{Corrugator}: ANOVA:
 
@@
 
-\emph{Levator}:
-ANOVA:
+\emph{Levator}: ANOVA:
 
@@
 \end{figure}
+
 \begin{figure}[H]
@@
 \hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}
-
-\emph{Corrugator}:
-ANOVA:
+\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}
+
+\emph{Corrugator}: ANOVA:
 

### 2022-06-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

@@
 A brief training will ensure that all participants are able to implement the ER strategies.
-Next, electrodes to measure facial EMG will be attached and the ER paradigm will be conducted, followed by an ED procedure regarding the ER strategies.
+Next, electrodes to measure facial EMG will be attached and the ER task will be conducted, followed by an ED procedure regarding the ER strategies.
 After that, participants will choose one ER strategy to repeat one more time.
@@
 For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the \emph{afex} package\textsuperscript{39}.
-Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values and will be reported when the assumption of sphericity is violated.
+Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values will be reported when the assumption of sphericity is violated.
 If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
@@
 \emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV of the opposite strategy in each pairing.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy will be divided by 2 €.
 Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.

### 2022-06-09 06_Paper/COG-ED/Manuscript.Rmd
added SV calc description

@@
 To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
-For each effort discounting round, SVs will be calculated by adding or subtracting 0.015625 from the last monetary value of the flexible level, depending on the participant's last choice.
-This value is the result of dividing the first adjustment of 0.50€ by 2 five times, once in each effort discounting round.
-Then, these final monetary values will be divided by 2€, and the SV of each level per participant will be computed by averaging all final values of each level, regardless of whether it was fixed or flexible.
+For each effort discounting round, the SV of the fixed level will be calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
+This yields an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level is 1.
+The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
+All SVs of each level will be averaged to compute one "global" SV for each level.
 An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.

### 2022-06-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd

@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "5630"
-bibliography      : ER_ED.bib
+wordcount         : "6233"
+bibliography      : ["ER_ED.bib"]
 floatsintext      : yes
@@
     - \usepackage{chngcntr}
+editor_options: 
+  markdown: 
+    wrap: sentence
+---
 
----
+```{=tex}
 \renewcommand\thesection{\Alph{section}}
@@
 \setcounter{figure}{0}
----
+```
+
+------------------------------------------------------------------------
 
@@
 
-``` {r child = "TheoreticalBackground.Rmd"}
+```{r child = "TheoreticalBackground.Rmd"}
 ```
@@
 
+```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
+```
+::: {#refs custom-style="Bibliography"}
+:::
 
-<div id="refs" custom-style="Bibliography"></div>
+```{=tex}
 \endgroup
-
+```
 \newpage
@@
 
+```{=tex}
 \newpage
 \setcounter{figure}{0}
-
+```
 # Figures and figure captions
@@
 \newpage
+
 ```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
@@
 ```
-*Figure 1.* 
-Exemplary visualization of two response patterns. 
+
+*Figure 1.* Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 ```
-*Figure 2.* 
-Block design of the paradigm. 
-Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures. 
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. 
+
+*Figure 2.* Block design of the paradigm.
+Every participant starts with two "active viewing" blocks containing neutral (Block 1) and negative (Block 2) pictures.
+Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
+After, the discounting procedure takes place.
+All three regulation strategies are pairwise compared.
+Before the last block, participants can decide which regulation strategy they want to reapply.
 Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
@@
 
-*WHO-5.*
-General psychological well-being is assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
+*WHO-5.* General psychological well-being is assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
 5 Items such as "Over the past 2 weeks I have felt calm and relaxed." are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
@@
 
-*Connor-Davidson Resilience Scale.*
-Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
+*Connor-Davidson Resilience Scale.* Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
 10 items such as "I am able to adapt to change." are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
@@
 
-*Emotion Regulation Questionnaire.* 
-Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003;@Abler2009].
-The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].
+*Emotion Regulation Questionnaire.* Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
+The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's $\alpha>.75$) [@Preece2020].
 
-*FlexER Scale.*
-Flexible use of ER strategies is assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
+*FlexER Scale.* Flexible use of ER strategies is assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
 Psychometric properties are currently under investigation.
 
-*Implicit Theories Questionnaire.*
-Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
+*Implicit Theories Questionnaire.* Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
 4 items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
@@
 
-*Need for Cognition Scale.*
-Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale [@Bless1994]. 
+*Need for Cognition Scale.* Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale [@Bless1994].
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
@@
 
-*Self-Regulation Scale.*
-As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] is used.
+*Self-Regulation Scale.* As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] is used.
 The scale has 10 items (e.g., "It is difficult for me to suppress thoughts that interfere with what I need to do.", recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
@@
 
-*Brief Self-Control Scale.* 
-As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used. 
-It comprises 13 items (e.g., “I am good at resisting temptations”) with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me). 
-The scale shows acceptable internal consistency (Cronbach’s $\alpha=.81$)[@Sproesser2011] .
+*Brief Self-Control Scale.* As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used.
+It comprises 13 items (e.g., "I am good at resisting temptations") with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
+The scale shows acceptable internal consistency (Cronbach's $\alpha=.81$)[@Sproesser2011] .
 
-*Barratt Impulsiveness Scale.*
-As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] is used.
+*Barratt Impulsiveness Scale.* As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] is used.
 Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
@@
 
-*Attentional Control Scale.*
-Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
+*Attentional Control Scale.* Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
@@
 \newpage
+
 ## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"
+
 ANOVA:
 
-`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` 
-$BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`
+`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`
 
 Paired contrasts:
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
+
 Figure:
+
 ```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
@@
 ```
+
 ## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-ANOVA:
-`r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`
+
+ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`
 
 Paired contrasts:
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
+
 Figure:
+
 ```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
@@
 ```
+
 ## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
-*Corrugator*:
-ANOVA: 
-`r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`
+
+*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`
 
 Paired contrasts:
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
-*Levator*:
-ANOVA: 
-`r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`
+
+*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`
 
 Paired contrasts:
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
+
 Figures:
+
 ```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
@@
 ```
+
 ```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
@@
 ```
+
 ## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-*Corrugator*:
-ANOVA: 
-`r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`
+
+*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`
 
 Paired contrasts:
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
-*Levator*:
-ANOVA: 
-`r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`
+
+*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`
 
 Paired contrasts:
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
+
 Figures:
+
 ```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
@@
 ```
+
 ```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
@@
 ```
+
 ## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-ANOVA:
-`r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)`
-$BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
+
+ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
 
 Paired contrasts:
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 ```
+
 Figure:
+
 ```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.

### 2022-06-09 06_Paper/ER-ED/method.Rmd
removed one sentence

@@
 suppression), each of the two strategies will be presented with a monetary reward.
-The order of the pairings will be randomized.
 Because there is no strategy that is objectively more difficult, we will add initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
@@
 For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the *afex* package[@Singmann2021].
-Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values and will be reported when the assumption of sphericity is violated.
+Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values will be reported when the assumption of sphericity is violated.
 If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
@@
 *Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, the resulting monetary value will be divided by 2.00 € to arrive at the SV of the opposite strategy in each pairing.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy will be divided by 2 €.
 Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.

### 2022-06-09 06_Paper/COG-ED/Manuscript.Rmd
described new analyses for H3a-c

@@
 To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-At the end of each level, participants fill out the NASA-TLX on a tablet.
+At the end of each level, participants fill out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this *n*-back level.
 After the *n*-back task, participants complete the CAD paradigm on screen and are instructed to do so as realistically as possible, even though the displayed rewards will not be paid out on top of their compensation.
@@
 
-The association of effort discounting and NFC will be examined with a regression using the $AUC$ of each participant's SVs to predict their NFC score.
-A second regression will additionally include the mean of the NASA-TLX subscales' $AUCs$ of each participant as a predictor.
-Since we do not have a fixed SV of 1 for 1-back, we cannot apply the computation of Westbrook et al.[-@Westbrook2013], which was the mean of the $AUCs$ of the SVs of each higher n-back level and 1-back, yielding values between 0\ and\ 1.
-Consequently, we will choose a different way of quantifying the individual degree of effort discounting.
-A classic $AUC$ cannot differentiate between a subject who prefers 1-back and a subject who prefers 4-back if the magnitude of the ascent is the same, but it can reflect the overall willingness to exert effort.
-This is the opposite for the sum of the ascent between SVs.
-Therefore, we multiply both indicators, arriving at a value reflecting both degree and direction of preference, called $AxAUC$.
+The association of SVs and NFC will be examined with an rmANOVA.
+We will subtract the SV of 1- from 2-back, 2- from 3-back, and 3- from 4-back per participant, yielding three SV difference scores per participant.
+The sample will be divided into participants with low and high NFC using a median split.
+We will then compute an rmANOVA with the within-factor n-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
+Post-hoc tests will be computed depending on which effect reaches significance at $p<.01$.
+
+The association of subjective task load with NFC will be examined similarly.
+We will calculate NASA-TLX sum scores per participant per level and compute an rmANOVA with the within-factor n-back level and the between-factor NFC group, and apply post-hoc tests based on which effect reaches significance at $p<.01$.
+And the association of subjective aversiveness of the task with NFC will be examined with difference scores as well, since we expect this curve to mirror the SV curve, i.e.
+as the SV rises, the aversiveness declines, and vice versa.
+We will subtract the aversiveness ratings of 1- from 2-back, 2- from 3-back, and 3- from 4-back per participant, yielding three aversiveness difference scores per participant.
+Then, we will compute an rmANOVA with the within-factor n-back level and the between-factor NFC group, and apply post-hoc tests based on which effect reaches significance at $p<.01$.
 

### 2022-06-09 06_Paper/COG-ED/Analysis.R
corrected H3c

@@ -1565,9 +1565,9 @@
   
 ##### Hypothesis 3c ############################################################
   
-  # Here we will repeat the same method of hypothesis 3b, but with the aversiveness-scores
-  # in place of the NTLX scores. Since we did not assess those in the pilot study, we
-  # cannot have the data to analyze it at the moment.
+  # Here we will repeat the same method of hypothesis 3a, but with the aversiveness-scores
+  # in place of the SV scores. Since we did not assess those in the pilot study, we
+  # do not have the data to analyze it at the moment.
   
 ##### Save variables ###########################################################
   

### 2022-06-09 06_Paper/COG-ED/Manuscript.Rmd
corrected ANOVA descriptions

@@
 Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
-To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019]. 
-Declining performance will be investigated by calculating an rmANOVA with three paired contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
-Another rmANOVA with three paired contrasts will be computed to compare the mean RT between two levels of 2-, 3-, and 4-back at a time.
-To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
+To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].<br>
+*Manipulation check.*
+Declining performance will be investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
+Another rmANOVA with six paired contrasts will be computed to compare the median RT between two levels of 1- to 4-back at a time.
+To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.<br>
+*Subjective values.*
 For each effort discounting round, the SV of the fixed level will be calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
@@
 All SVs of each level will be averaged to compute one "global" SV for each level.
-An rmANOVA with six paired contrasts will be computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
-Estimated marginal means will be used for the paired contrasts of each rmANOVA, including Tukey method for *p*-value adjustment.
+An rmANOVA with four different contrasts will be computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
+Depending on whether the linear or one of the other three contrasts fits the curve best, we will apply a linear or nonlinear multi-level model in the next step, respectively.
 

### 2022-06-10 06_Paper/COG-ED/Manuscript.Rmd

@@
 
-To determine the influence of task performance on the association of SVs and *n*-back level, we will set up an MLM using the $lmerTest$ package[@Kuznetsova2017]. 
+To determine the influence of task performance on the association of SVs and *n*-back level, we will perform MLM. 
 We will apply restricted maximum likelihood (REML) to fit the model.
 As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we will estimate a random slopes model of SVs including n-back level as level-1-predictor and, additionally, NFC as level-2-predictor.
+Second, we will estimate a random slopes model of n-back level (level 1, fixed and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
 As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
-Within the model, we will therefore control for *d'*, RT, correct, and post-correct trials.
+We control for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
 $$
-SV \sim level\ * NFC + d' + RT + correct + postcorrect + (level|subject)
+SV \sim level\ + d' + median RT + (level|subject)
 $$
-Level-1-predictors will be centered within cluster, whereas the level-2-predictor will be centered at the grand mean as recommended by Enders & Tofighi[-@Enders2007]. 
+Level-1-predictors will be centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
 By this, the model yields interpretable parameter estimates. 
-We will visually inspect the residuals of the final model.
-The approximately normal distribution indicates no evidence to perform model criticism.  
-As effect size measures, we calculate pseudo *R²* for our model and *f²* to estimate the effects of n-back level and NFC according to Lorah[-@Lorah2018].
-Third, we will perform a simple slopes analysis with n-back level as predictor and NFC as moderator. 
-To evaluate the moderating effect, we will calculate the Johnson-Neyman interval.
+If necessary, we will adjusted the optimization algorithm to improve model fit. 
+We will visually inspect the residuals of the model for evidence to perform model criticism. 
+This will be done by excluding all data points with absolute standardized residuals above 3 SD. 
+As effect size measures, we will calculate pseudo *R²* for our model and *f²* to estimate the effect of n-back level according to Lorah[-@Lorah2018].
 To ensure the validity of the MLM, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
@@
 The results showed increases in subjective and objective task load measures with higher *n*-back level.
-Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomon can only emerge in this version of the paradigm.
-A multi-level model (MLM) revealed that *n*-back level was a reliable predictor of SV, even after controlling for declining task performance (d’ and RT) as well as correct and post-correct answers, while NFC was not, most likely due to the small sample size for individual differences analyses.
+Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomenon can only emerge in this version of the paradigm.
+The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
 The specification curve analysis showed that this pattern was true for all 63 pipelines.
@@
         caption = "Effects of n-back load level on subjective value controlled 
-    for task performance (d' and reaction time), correct and postcorrect trials.",
+    for task performance (d' and reaction time).",
         booktabs = T,                          # no vertical lines
@@
 ```
+The intraclass correlation equals `r format(icc_h2b, digits = 2)`.
 
@@
 
-## Hypothesis 2c: Subjective values decline stronger with increasing task load for individuals with low compared to high NFC scores.
-
-Simple slopes analysis:
-
-```{r,echo=FALSE, message=FALSE, warning=FALSE}
-kable(h2c_ss.table,
-        caption = "Interaction between NFC and n-back load level.",
-        # "Slopes of n-back level for different NFC values."
-        booktabs = T,                          # no vertical lines
-        escape = F,                            # correctly print special characters)
-        align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    add_header_above(c(" " = 1, "Slopes of NFC" = 4, "Conditional Intercept" = 2)) %>%
-    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
-             escape = F,                    # correctly print special characters
-             threeparttable = T)            # line breaks in the footnote
-```
-
-```{r FigHyp2c, echo=FALSE, message=FALSE, warning=FALSE, fig.cap=paste("Simple slopes analysis for how n-back level predicts the subjective value, depending on the participant's NFC.
-Slope of $1SD$ below the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[1], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[1], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[1], digits = 3), ", slope of the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[2], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[2], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[2], digits = 3), " slope of $1SD$ above the mean: $\\beta=$ ", round(m1_h2c.ss$slopes$Est.[3], digits = 2), ", $SE=$ ", round(m1_h2c.ss$slopes$S.E.[3], digits = 2), ", $p=$ ", round(m1_h2c.ss$slopes$p[3], digits = 3), ".
-NFC = Need for Cognition, SD = standard deviation.", sep=""), fig.pos="H"}
-
-interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
-                               plot.points = TRUE, point.shape = TRUE,
-                               x.label = "n-back level", y.label = "subjective value",
-                               legend.main = "NFC", interval = TRUE) + theme_apa() +
-scale_x_continuous(breaks = c(-1,0,1), labels = c("2","3","4"))
-```
-
-Johnson-Neyman interval: `r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`
-
-Bayes Factor: $BF10=$ `r format(extractBF(h2c_BF)$bf, digits = 2)`
-
-The effect size is $f^2=$ `r format(h2c_f2, digits = 2)`.
-
-\newpage
-
 ## Specification curve analysis:
-
 ```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.

### 2022-06-10 06_Paper/COG-ED/Analysis.R
deleted SCA for H2b

@@ -1334,108 +1334,7 @@
   ## D - declining logistic relation (nonlinear mixed model) -------------------
   ## E - positively skewed normal (nonlinear mixed model) ----------------------
   
-  
-##### Specification Curve Analysis #############################################
-  
-  # here we repeat the multi level model with all analysis pipelines
-  
-  # prepare empty data frame for the loop to feed into
-  
-  sca_results <- data.frame(pipeline = character(), beta = double(), pvalue = double(), predictor = character(), BF10 = double())
-  
-  # loop through the pipelines
-  
-  for (i in 1:length(pipelines_data)) {
-    
-    # make a temporary copy of the data frame
-    
-    sca_data <- pipelines_data[[i]]
-    
-    # get a subset without RT = NA
-    
-    sca_data <- droplevels(subset(sca_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")], subset = !is.na(rt)))
-    
-    # center the predictors
-    
-    # centering the level 1 predictors (d', RT, level, correct, postcorrect) within cluster
-    
-    sca_data$dprime.cwc       <- sca_data$dprime - (ave(sca_data$dprime, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-    sca_data$rt.cwc           <- sca_data$rt - (ave(sca_data$rt, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-    sca_data$level.cwc        <- sca_data$level - (ave(sca_data$level, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-    sca_data$correct.cwc      <- sca_data$correct - (ave(sca_data$correct, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-    sca_data$postcorrect.cwc  <- sca_data$postcorrect - (ave(sca_data$postcorrect, sca_data$subject, FUN = function(x) mean(x, na.rm = T)))
-    
-    # centering the level 2 predictor NFC at the grand mean
-    
-    sca_data$nfc.cgm <- scale(sca_data$nfc, scale = F)
-    
-    # define the null model
-    
-    m0_sca <- lmerTest::lmer(sv ~ 1 + (1|subject), data = sca_data, REML = T)
-    
-    # random slopes model
-    
[…]

### 2022-06-10 06_Paper/COG-ED/Manuscript.Rmd
moved SCA to H3a

@@
 As effect size measures, we will calculate pseudo *R²* for our model and *f²* to estimate the effect of n-back level according to Lorah[-@Lorah2018].
-To ensure the validity of the MLM, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
-The MLM will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
-The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
 
@@
 Post-hoc tests will be computed depending on which effect reaches significance at $p<.01$.
+To ensure the validity of this association, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
+The rmANOVA will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
+The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
 

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
changed MLM description

--- 2022-06-10 06_Paper/COG-ED/Manuscript.Rmd
@@
 As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we will estimate a random slopes model of n-back level (level 1, fixed and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
+Second, we will estimate a random slopes model of n-back level (level 1, fixed and random factor: 1-back, 2-back, 3-back, 4-back) predicting SV nested within subjects.
 As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.

### 2022-06-13 06_Paper/COG-ED/Analysis.R
formatted results H2a

@@ -1155,31 +1155,21 @@
                                                                               "Declining Logistic" = c(3,2,-2,-3),
                                                                               "Positively Skewed Normal" = c(1,2,-1,-2)))
   
-  # get Bayes factors
-  
-  hypothesis2a_BF <- BayesFactor::anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
-  hypothesis2a_contrasts$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 2],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 3],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h2a_data$sv[h2a_data$level == 1], y = h2a_data$sv[h2a_data$level == 4],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 3],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h2a_data$sv[h2a_data$level == 2], y = h2a_data$sv[h2a_data$level == 4],
-                                                     progress = FALSE, paired = TRUE))$bf,
-                                   BayesFactor::extractBF(BayesFactor::ttestBF(x = h2a_data$sv[h2a_data$level == 3], y = h2a_data$sv[h2a_data$level == 4],
-                                                     progress = FALSE, paired = TRUE))$bf)
+  # we still have to get the Bayes Factors here, but we'll do that in the main study
   
   # get effect size and confidence intervals
   
+  hypothesis2a_contrasts <- as.data.frame(hypothesis2a_contrasts)
[…]

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
removed BF from pilot results H2a

--- 2022-06-10 06_Paper/COG-ED/Manuscript.Rmd
@@
 
-`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis2a_BF)$bf, digits = 2)`
+`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`
 
@@
   hypothesis2a_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing subjective values between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Different contrasts for the rmANOVA comparing subjective values between n-back levels",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,

### 2022-06-13 06_Paper/COG-ED/Analysis.R
removed BF from pilot H3a

@@ -1383,18 +1383,18 @@
   
   # obtain estimated marginal means for ANOVA model
   
-  hypothesis3a_emm <- emmeans::emmeans(object = hypothesis3a_rmanova, c("nfcmedian","nlevels"))
+  #hypothesis3a_emm <- emmeans::emmeans(object = hypothesis3a_rmanova, c("nfcmedian","nlevels"))
   
   # calculate pairwise comparisons on estimated marginal means
   
-  hypothesis3a_contrasts <- as.data.frame(pairs(hypothesis3a_emm))
+  #hypothesis3a_contrasts <- as.data.frame(pairs(hypothesis3a_emm))
   
   # get Bayes factors
   
-  hypothesis3a_BF <- anovaBF(formula = svdiff ~ nlevels * nfcmedian, data = h3a_data, progress = FALSE)
-  hypothesis3a_contrasts$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = h3a_data$svdiff[h3a_data$nfcmedian == "high"],
-                                                                             y = h3a_data$svdiff[h3a_data$nfcmedian == "low"],
-                                                                             progress = FALSE, paired = FALSE))$bf
+  #hypothesis3a_BF <- anovaBF(formula = svdiff ~ nlevels * nfcmedian, data = h3a_data, progress = FALSE)
+  #hypothesis3a_contrasts$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = h3a_data$svdiff[h3a_data$nfcmedian == "high"],
+  #                                                                           y = h3a_data$svdiff[h3a_data$nfcmedian == "low"],
+  #                                                                           progress = FALSE, paired = FALSE))$bf
   
   # remove temporary variables
   

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
removed SCA from pilot results

@@
 
-## Specification curve analysis:
-```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model.
-The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values.
-Estimates with $p<.05$ are indicated by a dot on the line.
-$N=15$.
-The lower panel shows the preprocessing steps of each corresponding pipeline.
-The $BF10$ of each pipeline's multi level model approached infinity.", fig.pos="H"}
-
-# create the upper panel first, which will show the estimates of 'level' and 'nfc'
-
-  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
-    geom_line(aes(group = predictor)) +
-    geom_point(data = sca_results, aes(x = num, y = sign)) +
-    geom_text(x = 3, y = -0.02, label = "NFC", size = 3) +
-    geom_text(x = 3, y = -0.13, label = "Level", size = 3) +
-    theme_classic() +
-    labs(x = NULL, y = "Fixed effects\nestimate \u03b2") +
-    scale_y_continuous(lim = c(NA,0.01)) +
-    theme(axis.text.x = element_blank(),
-          axis.line.y = element_line(size = 1, color = "black"), axis.title.y = element_text(margin = margin(r = 10)),
-          legend.position = "none")
-
-  # create the lower part of the plot that indicates the pipeline specifications
-
-  sca_lowerplot <- ggplot(data = sca_results) +
-    geom_hline(yintercept = c(1,6,11), color = "grey", size = 0.5) +
-    geom_hline(yintercept = c(2:5,7:10,12:17), color = "grey", linetype = "dashed", size = 0.2) +
-    geom_point(aes(x = num, y = Dim)) +
-    geom_point(aes(x = num, y = Trans)) +
-    geom_point(aes(x = num, y = Excl)) +
-    theme_classic() +
-    labs(x = "Analysis pipeline", y = NULL) +
-    scale_y_reverse(breaks = c(1:17), lim = c(17,0.5), labels = c(expression(bold("Dimension")),
-                                                                "Across S, across C", "Across S, within C",
-                                                                "Within S, within C", "Within S, across C",
-                                                                expression(bold("Transformation")),
-                                                                "Raw/None", "Log", "Inverse", "Square-root",
-                                                                expression(bold("Exclusion")),
-                                                                "None", "2 MAD from median", " 2.5 MAD from median",
-                                                                "3 MAD from median", "100ms after onset", "200ms after onset")) +
-    theme(axis.text.x = element_blank(), axis.title.x = element_text(margin = margin(t = 10)),
-          axis.line.y = element_line(size = 1, color = "black"),
-          legend.position = "none")
-
-  # put both plots into one
-
-  ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
-
-```
-
-\newpage
-
 ## Hypothesis 3a: Subjective values positively predict individual NCS scores.

### 2022-06-13 06_Paper/COG-ED/Analysis.R
reformatted results for 3a

@@ -28,7 +28,7 @@
   
   
   # the required packages are:
-  # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot", "purrr",
+  # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot", "purrr", "broom",
   # "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize", "pracma", and "MuMIn"
   
   # sets orthogonal contrasts for mixed-effects model and rmANOVA globally in order to get meaningful Type-III tests
@@ -1380,14 +1380,19 @@
   
   hypothesis3a_rmanova <- afex::aov_ez("subject", "svdiff", h3a_data,
                                        between = c("nfcmedian"), within = c("nlevels"))
+  
+  # format S3 class into data frame
+  
   hypothesis3a_rmanova <- summary(hypothesis3a_rmanova)
   hypothesis3a_rmanova <- hypothesis3a_rmanova[["univariate.tests"]]
+  hypothesis3a_rmanova <- as.data.frame(matrix(hypothesis3a_rmanova, nrow = 4, ncol = 6))
+  
   
   # get effect size
   
-  hypothesis3a_rmanova <- c(hypothesis3a_rmanova,
-                            format(effectsize::F_to_eta2(f = hypothesis3a_rmanova[,"F value"], df = hypothesis3a_rmanova[,"num Df"],
-                                                         df_error = hypothesis3a_rmanova[,"den Df"], ci = 0.95), digits = 2))
+  hypothesis3a_rmanova <- cbind(hypothesis3a_rmanova,
+                            format(effectsize::F_to_eta2(f = hypothesis3a_rmanova[,5], df = hypothesis3a_rmanova[,2],
+                                                         df_error = hypothesis3a_rmanova[,4], ci = 0.95), digits = 2))
   
   # formatting
   

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
modified H3a results output

@@
 
-## Hypothesis 3a: Subjective values positively predict individual NCS scores.
+## Hypothesis 3a: Participants with high NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with low NFC scores.
 
-Intercept:
-`r apa_print(hypothesis3a)$estimate$Intercept`
+ANOVA:
 
-Predictor $AxAUC$:
-`r apa_print(hypothesis3a)$estimate$h3_data_axauc`
-
-Fit:
-`r apa_print(hypothesis3a)$estimate$modelfit$r2`
-
-Effect size and confidence interval:
-
-$\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3a$fstatistic[1], df = hypothesis3a$fstatistic[2], df_error = hypothesis3a$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
-
-Bayes factor:
-
-$BF10=$ `r extractBF(hypothesis3a_BF)$bf`
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis3a_rmanova,
+  caption = "Main effects and interaction of NFC group and n-back level on subjective values",
+  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
 

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
finished results reporting for 3b

@@
 
-## Hypothesis 3b: NASA-TLX scores negatively predict individual NFC scores.
+## Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every n-back level than participants with low NFC scores.
 
-Intercept:
-`r apa_print(hypothesis3b)$estimate$Intercept`
+ANOVA:
 
-Predictor $AxAUC$:
-`r apa_print(hypothesis3b)$estimate$h3_data_axauc`
+Main effect of the NFC group:
 
-Predictor $AUC$ NASA-TLX:
-`r apa_print(hypothesis3b)$estimate$h3_data_auc_ntlx`
+`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, §BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`
 
-Fit:
-`r apa_print(hypothesis3b)$estimate$modelfit$r2`
+Main effect of the n-back level:
 
-Effect size and confidence interval:
+`r apa_print(hypothesis3b_model)$full_result$level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`
 
-$\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis3b$fstatistic[1], df = hypothesis3b$fstatistic[2], df_error = hypothesis3b$fstatistic[3], ci = 0.95), digits = 2)[1,2]`
+Interaction effect of NFC group and n-back level:
 
-Bayes factors:
+`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`
 
-$BF10=$ `r extractBF(hypothesis3b_BF)$bf[1]` for predictor $AxAUC$
+Paired contrasts for the main effect of n-back level:
 
-$BF10=$ `r extractBF(hypothesis3b_BF)$bf[2]` for predictor $AUC$ NASA-TLX
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  hypothesis3b_rmanova,
+  caption = "Main effects and interaction of NFC group and n-back level on NASA-TLX scores",
+  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```

### 2022-06-13 06_Paper/COG-ED/Analysis.R
corrected scientific formatting of decimals

@@ -831,9 +831,9 @@
   
   colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)
-  hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")] <- format(round(hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")], digits = 2), nsmall = 2)
+  hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")] <- signif(hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")], digits = 3)
   hypothesis1a_contrasts$`$p$` <- format(round(hypothesis1a_contrasts$`$p$`, digits = 3), nsmall = 2)
-  hypothesis1a_contrasts$`$p$`[hypothesis1a_contrasts$`$p$` == 0.000] <- "<.001"
+  hypothesis1a_contrasts$`$p$`[hypothesis1a_contrasts$`$p$` == "0.000"] <- "<.001"
   
   # remove the temporary variable
   
@@ -892,7 +892,7 @@
   
   colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
   hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
-  hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")] <- format(round(hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")], digits = 2), nsmall = 2)
+  hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")] <- signif(hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")], digits = 3)
   hypothesis1b_contrasts$`$p$` <- format(round(hypothesis1b_contrasts$`$p$`, digits = 3), nsmall = 2)
   hypothesis1b_contrasts$`$p$`[hypothesis1b_contrasts$`$p$` == 0.000] <- "<.001"
   
[…]

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
removed paired contrast of H1a

@@
 
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  hypothesis1a_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing $d'$ between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
 \newpage
@@
 
-`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, §BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`
+`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, $BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis3b_model)$full_result$level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`
+`r apa_print(hypothesis3b_model)$full_result$level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`
 
@@
 
-`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, §BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`
+`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`
 

### 2022-06-13 06_Paper/COG-ED/Analysis.R
added package specifier to H2b

@@ -1254,7 +1254,7 @@
   m2_h2b <- lmerTest::lmer(sv ~ level.cwc + dprime.cwc + medianRT.cwc + (level.cwc|subject), 
                            data = h2b_data,
                            REML = T, # parameters estimated by restricted log-likelihood maximization
-                           control = lmerControl(optimizer = "nloptwrap", optCtrl = list(algorithm = "NLOPT_LN_NELDERMEAD")))
+                           control = lme4::lmerControl(optimizer = "nloptwrap", optCtrl = list(algorithm = "NLOPT_LN_NELDERMEAD")))
 
   ## perform model criticism
   
@@ -1275,7 +1275,7 @@
   m4_h2b <- lmerTest::lmer(sv ~ level.cwc + dprime.cwc + medianRT.cwc + (level.cwc|subject),
                            data = h2b_data_norm,
                            REML = T,
-                           control = lmerControl(optimizer = "nmkbw"))
+                           control = lme4::lmerControl(optimizer = "nmkbw"))
     # m4_h2b is the final model
   
   ## plot model fit of the final model
@@ -1291,7 +1291,7 @@
   # model without effect
   m4_h2b_without <- lmerTest::lmer(sv ~ 1 + dprime.cwc + medianRT.cwc + (level.cwc|subject),
                                    data = h2b_data_norm,
-                                   control = lmerControl(optimizer = "nmkbw"))
+                                   control = lme4::lmerControl(optimizer = "nmkbw"))
   # calculate R²
   h2b_without_r2 <- MuMIn::r.squaredGLMM(m4_h2b_without, pj2014 = T)
   

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
corrected formal errors

@@
 
-  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))
+  include_graphics(here("06_Paper", "Inkscape Figures", "Paradigm_Scheme.png"))
 
@@
 Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
-To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].<br>
+To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].
+
 *Manipulation check.*
@@
 Another rmANOVA with six paired contrasts will be computed to compare the median RT between two levels of 1- to 4-back at a time.
-To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.<br>
+To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.
+
 *Subjective values.*
@@
 The results showed increases in subjective and objective task load measures with higher *n*-back level.
-Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomenon can only emerge in this version of the paradigm.
+Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
 The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
@@
   escape = FALSE,
-  placement = "H"
+  placement = "H",
+  font_size = "footnotesize"
 )
@@
   escape = FALSE,
-  placement = "H"
-)
+  placement = "H",
+  font_size = "footnotesize")
 ```

### 2022-06-13 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
fixed model equation

@@
 \[
-SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
+\begin{split}
+SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
+\end{split}
 \]

### 2022-06-13 06_Paper/ER-ED/method.Rmd
fixed model equation

@@
 $$
-SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
+\begin{split}
+SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
+\end{split}
 $$ 

### 2022-06-20 06_Paper/ER-ED/method.Rmd
added utility ratings

@@
 Restricted maximum likelihood (REML) will be applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors will be specified.
+A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors will be specified.
 $$

### 2022-06-20 06_Paper/ER-ED/method.Rmd
corrected numbering of supplement figures and tables

@@
 In accordance with our previous study[@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
-All results are detailed in the [Supplementary Material](#SupplementaryMaterial)
+All results are detailed in the [Supplementary Material](#SupplementaryMaterial), figures S1 to S7 and table S2 to S8.
 
@@
 An evolutionary algorithm [@Yu2010] is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
-A complete list of all pictures and their classification into sets can be found in supplementary material 1.
+A complete list of all pictures and their classification into sets can be found in supplementary material table S1.
 The five sets of negative pictures will be assigned randomly to the blocks.

### 2022-06-20 06_Paper/COG-ED/Analysis.R
added preliminary SCA plot

@@ -1557,9 +1557,7 @@
   
   # prepare empty data frame for the loop to feed into
   
-  sca_results <- data.frame(pipeline = double(), nfc_f = double(), nfc_p = double(), nfc_BF10 = double(),
-                            level_f = double(), level_p = double(), level_BF10 = double(),
-                            interaction_f = double(), interaction_p = double(), interaction_BF10 = double())
+  sca_results <- data.frame(pipeline = double(), effect = character(), fvalue = double(), pvalue = double(), BF10 = double())
   
   for (i in 1:length(pipelines_data)) {
     
@@ -1593,14 +1591,14 @@
 
     # pull relevant results from data frame and add Bayes Factors
     
-    sca_rmanova <- data.frame(pipeline = i,
-                              nfc_f = sca_rmanova["nfcmedian","F value"], nfc_p = sca_rmanova["nfcmedian","Pr(>F)"],
-                              nfc_BF10 = extractBF(anovaBF(formula = svdiff ~ nlevels * nfcmedian, data = sca_data, progress = FALSE))["nfcmedian","bf"],
-                              level_f = sca_rmanova["nlevels","F value"], level_p = sca_rmanova["nlevels","Pr(>F)"],
-                              level_BF10 = extractBF(anovaBF(formula = svdiff ~ nlevels * nfcmedian, data = sca_data, progress = FALSE))["nlevels","bf"],
-                              interaction_f = sca_rmanova["nfcmedian:nlevels","F value"], interaction_p = sca_rmanova["nfcmedian:nlevels","Pr(>F)"],
-                              interaction_BF10 = extractBF(anovaBF(formula = svdiff ~ nlevels * nfcmedian, data = sca_data, progress = FALSE))["nlevels + nfcmedian + nlevels:nfcmedian","bf"]/
-                                extractBF(anovaBF(formula = svdiff ~ nlevels * nfcmedian, data = sca_data, progress = FALSE))["nlevels + nfcmedian","bf"])
+    sca_rmanova <- data.frame(pipeline = rep(names(pipelines_data)[i],3),
+                              effect = c("NFC", "Level", "Interaction"),
+                              fvalue = c(sca_rmanova["nfcmedian","F value"], sca_rmanova["nlevels","F value"], sca_rmanova["nfcmedian:nlevels","F value"]),
[…]

### 2022-06-20 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd

@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "6233"
+wordcount         : "6289"
 bibliography      : ["ER_ED.bib"]
@@
 \includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+\setcounter{section}{19}
+\setcounter{figure}{0}
+\setcounter{table}{1}
 

### 2022-06-20 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex

--- 2022-06-09 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
@@
 {}{\PatchFailed}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6233}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6289}
 \usepackage{lineno}
@@
 In accordance with our previous study\textsuperscript{22}, we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
-All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}
+All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}, figures S1 to S7 and table S2 to S8.
 
@@
 An evolutionary algorithm\textsuperscript{62} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
-A complete list of all pictures and their classification into sets can be found in supplementary material 1.
+A complete list of all pictures and their classification into sets can be found in supplementary material table S1.
 The five sets of negative pictures will be assigned randomly to the blocks.
@@
 Restricted maximum likelihood (REML) will be applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
+A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
 \[
-SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility} + corrugator \text{ activity} + levator \text{ activity} + (strategy|subject)
+\begin{split}
+SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
+\end{split}
 \]

### 2022-06-22 06_Paper/COG-ED/Manuscript_without_supplement.tex
created version without supplement f re-submission

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{effort discounting, registered report, specification curve analysis, need for cognition, n-back\newline\indent Word count: ~ 4,300}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={When easy is not preferred: A discounting paradigm to assess load-independent task preference},
  pdfauthor={Josephine Zerna,1, Christoph Scheffel,1, Corinna Kührt1, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={effort discounting, registered report, specification curve analysis, need for cognition, n-back},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{When easy is not preferred: A discounting paradigm to assess load-independent task preference}
\author{Josephine Zerna\textsuperscript{$\dagger{}$,1}, Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Corinna Kührt\textsuperscript{1}, \& Alexander Strobel\textsuperscript{1}}
\date{}

\shorttitle{The CAD paradigm to assess task preference}

\authornote{

The authors made the following contributions. Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Writing - review \& editing; Corinna Kührt: Formal analysis, Writing - review \& editing, Visualization; Alexander Strobel: Conceptualization, Funding acquistion, Writing - review \& editing. \textsuperscript{$\dagger{}$} Josephine Zerna and Christoph Scheffel contributed equally to this work.

Correspondence concerning this article should be addressed to Josephine Zerna, Zellescher Weg 17, 01069 Dresden, Germany. E-mail: \href{mailto:josephine.zerna@tu-dresden.de}{\nolinkurl{josephine.zerna@tu-dresden.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany}

\abstract{%
When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
}

\begin{document}
\maketitle

\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In everyday life, effort and reward are closely intertwined\textsuperscript{1}.
With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value\textsuperscript{1}.
However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost\textsuperscript{2}.
Investigating effort and cost is challenging because ``effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity'' (p.~209)\textsuperscript{2}.

One task that is often used to investigate effort is the \emph{n}-back task, a working memory task in which a continuous stream of stimuli, e.g.~letters, is presented on screen.
Participants indicate via button press whether the current stimulus is the same as \emph{n} stimuli before, with \emph{n} being the level of difficulty between one and six\textsuperscript{3}.
The \emph{n}-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times\textsuperscript{4}, and brain activity in areas associated with working memory\textsuperscript{5,6}.
However, its reliability measures are mixed, and associations of \emph{n}-back performance and measures such as executive functioning and fluid intelligence are often inconsistent\textsuperscript{4}.

A way to quantify the subjective cost of each \emph{n}-back level has been developed by Westbrook, Kester, and Braver\textsuperscript{7}, called the Cognitive Effort Discounting Paradigm (COG-ED).
First, the participants complete the \emph{n}-back levels to familiarize themselves with the task.
Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred\textsuperscript{7}.
The subjective value (SV) of each more difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
Westbrook et al.\textsuperscript{7} used these SVs to investigate inter-individual differences in effort discounting.
Younger participants showed lower effort discounting, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.

The individual degree of effort discounting in the study by Westbrook et al.\textsuperscript{7} was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing an individual's tendency to actively seek out and enjoy effortful cognitive activities\textsuperscript{8}.
Westbrook et al.\textsuperscript{7} conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of effort discounting for each participant which could then be related to the SVs as an objective measure of effort discounting.
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control\textsuperscript{9}, a trait more prominent in individuals with high NFC\textsuperscript{10--12}.
However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance\textsuperscript{13} or found no association of NFC and SVs at all\textsuperscript{14}.
On the other hand, task load has been shown to be a better predictor of SVs than task performance\textsuperscript{7,15,16}, so more research is needed to shed light on this issue.

With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest \emph{n}-back level has the highest SV.
We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different \emph{n}-back levels without presuming that all individuals inherently prefer the easiest level.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks\textsuperscript{17}, we call it the Cognitive and Affective Discounting Paradigm (CAD).
In the present study, we will validate the CAD paradigm by conceptually replicating the findings of Westbrook et al.\textsuperscript{7}.
Additionally, we will compare the effort discounting behavior of participants regarding the \emph{n}-back task and an emotion regulation task.
The full results of the latter will be published in a second Registered Report\textsuperscript{17}.
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate\textsuperscript{14}, but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

Our hypotheses were derived from the results of Westbrook et al.\textsuperscript{7}.
As a manipulation check, we hypothesize that with increasing \emph{n}-back level the (1a) the signal detection parameter \emph{d'} declines, while (1b) reaction time and (1c) perceived task load increase.
Regarding the associations of task load and effort discounting we hypothesize that (2a) SVs decline with increasing \emph{n}-back level, and (2b) they do so even after controlling for declining task performance.
And finally, we hypothesize that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
Each hypothesis is detailed in the \protect\hyperlink{DesignTableSection}{Design Table} in the Appendix.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{cf. 18}.
The paradigm was written and presented using \emph{Psychopy}\textsuperscript{19}.
We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all our analyses.

\hypertarget{ethics-information}{%
\subsection{Ethics information}\label{ethics-information}}

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number SR-EK-50012022).
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.

\hypertarget{design}{%
\subsection{Design}\label{design}}

\hypertarget{cad-paradigm}{%
\subsubsection{CAD Paradigm}\label{cad-paradigm}}

Figure~1 illustrates how different modifications of the COG-ED paradigm\textsuperscript{7} return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
The COG-ED paradigm, which compares every more difficult level with 1-back sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding those same pairs again, but with the opposite assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
This will be determined by presenting each possible pair of levels on screen with the question ``Would you prefer 1~€ for level A or 1~€ for level B?''.
Participants respond by clicking the respective on-screen button.
Each pair will be presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1~€ and is changed in every iteration.
The other level in the pair will be set to a fixed value of 2~€.
Then, the effort discounting sensu Westbrook et al.\textsuperscript{7} begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
The order in which the pairs are presented will be fully randomized, and each pair will go through all iteration steps of adding/subtracting 0.50~€, 0.25~€, 0.13~€, 0.06~€, 0.03~€, 0.02~€ to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
For each pair, the SV of the flexible level is 1, as it was preferred when faced with equal rewards, and the SV of the fixed level is the final reward of the flexible level divided by 2~€.
Each level's ``global'' SV is calculated as the mean of this level's SVs from all pairs in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
The interpretation of SVs in Westbrook et al.\textsuperscript{7} was ``The minimum relative reward required for me to choose 1-back over this level''.
So if the SV of 3-back was 0.6, the participant would need to be rewarded with at least 60~\% of what they are being offered for doing 3-back to do 1-back instead, forgoing the higher reward for 3-back.
In this study, the SV can be interpreted as ``The minimum relative reward required for me to choose any other level over this level''.
Therefore, an SV of 1 indicates that this level is preferred over all others, while SVs lower than 1 indicate that in at least one pair, a different level was preferred over this one.

\begin{figure}[H]
\includegraphics[width=\textwidth]{../Inkscape Figures/Paradigm_Scheme} \caption{An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.}\label{fig:figure1}
\end{figure}

\hypertarget{study-procedure}{%
\subsubsection{Study procedure}\label{study-procedure}}

Healthy participants aged 18 to 30~years will be recruited using the software \emph{ORSEE}\textsuperscript{24}.
Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
NFC will be assessed using the 16-item short form of the Need for Cognition Scale\textsuperscript{25,26}.
Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) will be recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{26,27}.
Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session\textsuperscript{17}.
A full list of measures can be found in our \href{https://github.com/ChScheffel/CAD}{Github repository}.
In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
The paradigm starts with the \emph{n}-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX)\textsuperscript{28}, where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
At the end of each level, participants fill out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this \emph{n}-back level.
After the \emph{n}-back task, participants complete the CAD paradigm on screen and are instructed to do so as realistically as possible, even though the displayed rewards will not be paid out on top of their compensation.
They are told that one of their choices will be randomly picked for the final run of \emph{n}-back, the data of which will not be analyzed as it only serves to incentivise truthful behavior and stay close to the design of Westbrook et al.\textsuperscript{7}.
After the CAD paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).\\
The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{29,30}.

\hypertarget{sampling-plan}{%
\subsection{Sampling plan}\label{sampling-plan}}

Sample size determination was mainly based on the results of the analyses of Westbrook et al.\textsuperscript{7} (see \protect\hyperlink{DesignTableSection}{Design Table}).
The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and \emph{n}-back level influencing SVs.
Sample size analysis with \emph{G*Power}\textsuperscript{31,32} indicated that we should collect data from at least 72 participants, assuming \(\alpha=.05\) and \(\beta=.95\).
However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of \(d=-0.32\) of emotion regulation on facial muscle activity with \(\alpha=.05\) and \(\beta=.95\).
To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aim to collect about \(50\%\) more data sets than necessary, \(N=120\) in total.

\hypertarget{analysis-plan}{%
\subsection{Analysis plan}\label{analysis-plan}}

Data collection and analysis will not be performed blind to the conditions of the experiments.
We will exclude the data of a participant from all analyses, if the participant states that they did not follow the instructions, if the investigator notes that the participant misunderstood the instructions, or if the participant withdraws their consent.
No data will be replaced.
The performance measure \emph{d'} will be computed as the difference of the \emph{z}-transformed hit rate and the \emph{z}-transformed false alarm rate\textsuperscript{33}.
Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100~ms, as the relevant cognitive processes cannot have been completed before\textsuperscript{34,35}.
Aggregated RT values will be described using the median and the median of absolute deviation (\(MAD\)) as robust estimates of center and variability, respectively\textsuperscript{36}.
Error- and post-error trials will be excluded, because RT in the latter is longer due to more cautious behavior\textsuperscript{37,38}.
To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results\textsuperscript{39}.

\emph{Manipulation check.}
Declining performance will be investigated by calculating an rmANOVA with six paired contrasts comparing \emph{d'} between two levels of 1- to 4-back at a time.
Another rmANOVA with six paired contrasts will be computed to compare the median RT between two levels of 1- to 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.

\emph{Subjective values.}
For each effort discounting round, the SV of the fixed level will be calculated by adding or subtracting the last adjustment of 0.02~€ from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2~€.
This yields an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level is 1.
The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
All SVs of each level will be averaged to compute one ``global'' SV for each level.
An rmANOVA with four different contrasts will be computed to investigate the association of SVs and the \emph{n}-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
Depending on whether the linear or one of the other three contrasts fits the curve best, we will apply a linear or nonlinear multi-level model in the next step, respectively.

To determine the influence of task performance on the association of SVs and \emph{n}-back level, we will perform MLM.
We will apply restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we will estimate a random slopes model of n-back level (level 1, fixed and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
As Mussel et al.\textsuperscript{40} could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We control for performance, i.e., \emph{d'} (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
\[
SV \sim level\ + d' + median RT + (level|subject)
\]
Level-1-predictors will be centered within cluster as recommended by Enders \& Tofighi\textsuperscript{41}.
By this, the model yields interpretable parameter estimates.
If necessary, we will adjusted the optimization algorithm to improve model fit.
We will visually inspect the residuals of the model for evidence to perform model criticism.
This will be done by excluding all data points with absolute standardized residuals above 3 SD.
As effect size measures, we will calculate pseudo \emph{R²} for our model and \emph{f²} to estimate the effect of n-back level according to Lorah\textsuperscript{42}.

The association of SVs and NFC will be examined with an rmANOVA.
We will subtract the SV of 1- from 2-back, 2- from 3-back, and 3- from 4-back per participant, yielding three SV difference scores per participant.
The sample will be divided into participants with low and high NFC using a median split.
We will then compute an rmANOVA with the within-factor n-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
Post-hoc tests will be computed depending on which effect reaches significance at \(p<.01\).
To ensure the validity of this association, we will conduct a specification curve analysis\textsuperscript{43}, which will include 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3~\(MAD\) from the median, RTs below 100~or~200~ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within \emph{n}-back levels).
The rmANOVA will be run with each of the 63~pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100~ms).
The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.

The association of subjective task load with NFC will be examined similarly.
We will calculate NASA-TLX sum scores per participant per level and compute an rmANOVA with the within-factor n-back level and the between-factor NFC group, and apply post-hoc tests based on which effect reaches significance at \(p<.01\).
And the association of subjective aversiveness of the task with NFC will be examined with difference scores as well, since we expect this curve to mirror the SV curve, i.e.~as the SV rises, the aversiveness declines, and vice versa.
We will subtract the aversiveness ratings of 1- from 2-back, 2- from 3-back, and 3- from 4-back per participant, yielding three aversiveness difference scores per participant.
Then, we will compute an rmANOVA with the within-factor n-back level and the between-factor NFC group, and apply post-hoc tests based on which effect reaches significance at \(p<.01\).

The results of each analysis will be assessed on the basis of both \(p\)-value and the Bayes factor \(BF10\), calculated with the \emph{BayesFactor} package\textsuperscript{23} using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{ttestBF}.
We will consider a \(BF10\) close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a \(BF10\) close to or below .33/.10 as moderate/strong evidence for the null hypothesis\textsuperscript{44}.

\hypertarget{pilot-data}{%
\subsection{Pilot data}\label{pilot-data}}

The sample of the pilot study consisted of \(N=15\) participants (53.30\% female, \(M=24.43\) (\(SD=3.59\))~years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with \(n=14\) data sets.
The results showed increases in subjective and objective task load measures with higher \emph{n}-back level.
Importantly, SVs were lower for higher \emph{n}-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed \emph{n}-back level as a reliable predictor of SV, even after controlling for declining task performance (\emph{d'} and median RT).
NASA-TLX scores were higher with higher \emph{n}, and lower for the group with lower NFC scores, but NFC and \emph{n}-back level did not interact.
All results are detailed in the Supplementary Material.

\hypertarget{data-availability}{%
\subsection{Data availability}\label{data-availability}}

The data of this study can be downloaded from \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.

\hypertarget{code-availability}{%
\subsection{Code availability}\label{code-availability}}

The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at \href{https://github.com/ChScheffel/CAD}{github.com/ChScheffel/CAD}.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Botvinick2009}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Botvinick, M. M., Huffstetler, S. \& McGuire, J. T. \href{https://doi.org/10.3758/CABN.9.1.16}{Effort discounting in human nucleus accumbens}. \emph{Cognitive, affective \& behavioral neuroscience} \textbf{9}, 16--27 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Kool2018}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Kool, W. \& Botvinick, M. \href{https://doi.org/10.1038/s41562-018-0401-9}{Mental labour}. \emph{Nature Human Behaviour} \textbf{2}, 899--908 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Mackworth1959}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Mackworth, J. F. \href{https://doi.org/10.1037/h0049090}{Paced memorizing in a continuous task}. \emph{Journal of Experimental Psychology} \textbf{58}, 206--211 (1959).}

\leavevmode\vadjust pre{\hypertarget{ref-Jaeggi2010}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Jaeggi, S. M., Buschkuehl, M., Perrig, W. J. \& Meier, B. \href{https://doi.org/10.1080/09658211003702171}{The concurrent validity of the {N}-back task as a working memory measure}. \emph{Memory} \textbf{18}, 394--412 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Jonides1997}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Jonides, J. \emph{et al.} \href{https://doi.org/10.1162/jocn.1997.9.4.462}{Verbal {Working} {Memory} {Load} {Affects} {Regional} {Brain} {Activation} as {Measured} by {PET}}. \emph{Journal of Cognitive Neuroscience} \textbf{9}, 462--475 (1997).}

\leavevmode\vadjust pre{\hypertarget{ref-Owen2005}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Owen, A. M., McMillan, K. M., Laird, A. R. \& Bullmore, E. \href{https://doi.org/10.1002/hbm.20131}{N-back working memory paradigm: A meta-analysis of normative functional neuroimaging studies}. \emph{Human Brain Mapping} \textbf{25}, 46--59 (2005).}

\leavevmode\vadjust pre{\hypertarget{ref-Westbrook2013}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Westbrook, A., Kester, D. \& Braver, T. S. \href{https://doi.org/10.1371/journal.pone.0068210}{What is the subjective cost of cognitive effort? {Load}, trait, and aging effects revealed by economic preference}. \emph{PLOS ONE} \textbf{8}, e68210 (2013).}

\leavevmode\vadjust pre{\hypertarget{ref-Cacioppo1982}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Cacioppo, J. T. \& Petty, R. E. \href{https://doi.org/10.1037//0022-3514.42.1.116}{The {Need} for {Cognition}}. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}

\leavevmode\vadjust pre{\hypertarget{ref-Wu2021}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Wu, R., Ferguson, A. \& Inzlicht, M. \emph{Do humans prefer cognitive effort over doing nothing?} \url{https://psyarxiv.com/d2gkf/} (2021) doi:\href{https://doi.org/10.31234/osf.io/d2gkf}{10.31234/osf.io/d2gkf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Bertrams2012}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Bertrams, A. \& Dickhäuser, O. \href{https://doi.org/10.1027/1614-0001/a000081}{Passionate thinkers feel better}. \emph{Journal of Individual Differences} \textbf{33}, 69--75 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Nishiguchi2016}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Nishiguchi, Y., Takano, K. \& Tanno, Y. \href{https://doi.org/10.1016/j.psychres.2016.04.092}{The {Need} for {Cognition} mediates and moderates the association between depressive symptoms and impaired {Effortful} {Control}}. \emph{Psychiatry Research} \textbf{241}, 8--13 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Xu2021}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Xu, P. \& Cheng, J. \href{https://doi.org/10.1016/j.paid.2021.110706}{Individual differences in social distancing and mask-wearing in the pandemic of {COVID}-19: {The} role of need for cognition, self-control and risk attitude}. \emph{Personality and Individual Differences} \textbf{175}, 110706 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Kramer2021}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Kramer, A.-W., Van Duijvenvoorde, A. C. K., Krabbendam, L. \& Huizenga, H. M. \href{https://doi.org/10.1016/j.cogdev.2020.100978}{Individual differences in adolescents' willingness to invest cognitive effort: {Relation} to need for cognition, motivation and cognitive capacity}. \emph{Cognitive Development} \textbf{57}, 100978 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Crawford2021}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Crawford, J. L., Eisenstein, S. A., Peelle, J. E. \& Braver, T. S. \href{https://doi.org/10.1186/s41235-021-00272-7}{Domain-general cognitive motivation: Evidence from economic decision-making}. \emph{Cognitive Research: Principles and Implications} \textbf{6}, 4 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Culbreth2016}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Culbreth, A., Westbrook, A. \& Barch, D. \href{https://doi.org/10.1037/abn0000153}{Negative symptoms are associated with an increased subjective cost of cognitive effort}. \emph{Journal of Abnormal Psychology} \textbf{125}, 528--536 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Westbrook2019}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Westbrook, A., Lamichhane, B. \& Braver, T. \href{https://doi.org/10.1523/jneurosci.3071-18.2019}{The subjective value of cognitive effort is encoded by a domain-general valuation network}. \emph{The Journal of Neuroscience} \textbf{39}, 3934--3947 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-ScheffelZerna2022}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Scheffel, C., Zerna, J., Gärtner, A., Dörfel, D. \& Strobel, A. \href{https://psyarxiv.com/wr8qx}{Estimating individual subjective values of emotion regulation strategies}. (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-Simmons2012}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A 21 word solution. (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}

\leavevmode\vadjust pre{\hypertarget{ref-Peirce2019}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{Peirce, J. \emph{et al.} \href{https://doi.org/10.3758/s13428-018-01193-y}{{PsychoPy2}: {Experiments} in behavior made easy}. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-RCT2020}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: {A} language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2020).}

\leavevmode\vadjust pre{\hypertarget{ref-RStudioTeam2020}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{RStudio Team. \href{http://www.rstudio.com}{{RStudio}: {Integrated} development for {R}}. (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Singmann2021}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{\href{https://CRAN.R-project.org/package=afex}{Afex: {A}nalysis of factorial experiments}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Morey2021}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{\href{https://CRAN.R-project.org/package=BayesFactor}{{BayesFactor}: {Computation} of {Bayes} factors for common designs}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Greiner2015}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{Greiner, B. \href{https://doi.org/10.1007/s40881-015-0004-4}{Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}

\leavevmode\vadjust pre{\hypertarget{ref-Cacioppo1984}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{Cacioppo, J. T., Petty, R. E. \& Kao, C. F. \href{https://doi.org/10.1207/s15327752jpa4803_13}{The {Efficient} {Assessment} of {Need} for {Cognition}}. \emph{Journal of Personality Assessment} \textbf{48}, 306--307 (1984).}

\leavevmode\vadjust pre{\hypertarget{ref-Bless1994}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Bless, H., Wänke, M., Bohner, G., Fellhauer, R. F. \& Schwarz, N. \href{https://doi.org/1779110}{Need for {Cognition}: {Eine} {Skala} zur {Erfassung} von {Engagement} und {Freude} bei {Denkaufgaben}}. \emph{Zeitschrift für Sozialpsychologie} \textbf{25}, (1994).}

\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{Fleischhauer, M. \emph{et al.} \href{https://doi.org/10.1177/0146167209351886}{Same or different? {Clarifying} the relationship of need for cognition to personality and intelligence}. \emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Hart1988}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{Hart, S. G. \& Staveland, L. E. \href{https://doi.org/10.1016/S0166-4115(08)62386-9}{Development of {NASA}-{TLX} ({Task} {Load} {Index}): {Results} of empirical and theoretical research}. \textbf{52}, 139--183 (1988).}

\leavevmode\vadjust pre{\hypertarget{ref-Harris2009}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{Harris, P. A. \emph{et al.} \href{https://doi.org/10.1016/j.jbi.2008.08.010}{Research electronic data capture ({REDCap})---{A} metadata-driven methodology and workflow process for providing translational research informatics support}. \emph{Journal of Biomedical Informatics} \textbf{42}, 377--381 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Harris2019}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{Harris, P. A. \emph{et al.} \href{https://doi.org/10.1016/j.jbi.2019.103208}{The {REDCap} consortium: {Building} an international community of software platform partners}. \emph{Journal of Biomedical Informatics} \textbf{95}, 103208 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-Faul2007}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G. \& Buchner, A. \href{https://doi.org/10.3758/BF03193146}{G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences}. \emph{Behavior Research Methods} \textbf{39}, 175--191 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-Faul2009}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{Faul, F., Erdfelder, E., Buchner, A. \& Lang, A.-G. \href{https://doi.org/10.3758/BRM.41.4.1149}{Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses}. \emph{Behavior Research Methods} \textbf{41}, 1149--1160 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Macmillan1990}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{Macmillan, N. A. \& Creelman, C. D. \href{https://doi.org/10.1037/0033-2909.107.3.401}{Response bias: {Characteristics} of detection theory, threshold theory, and "nonparametric" indexes}. \emph{Psychological Bulletin} \textbf{107}, 401--413 (1990).}

\leavevmode\vadjust pre{\hypertarget{ref-Whelan2008}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Whelan, R. \href{https://doi.org/10.1007/BF03395630}{Effective {Analysis} of {Reaction} {Time} {Data}}. \emph{The Psychological Record} \textbf{58}, 475--482 (2008).}

\leavevmode\vadjust pre{\hypertarget{ref-Berger2021}{}}%
\CSLLeftMargin{35. }%
\CSLRightInline{Berger, A. \& Kiefer, M. \href{https://doi.org/10.3389/fpsyg.2021.675558}{Comparison of {Different} {Response} {Time} {Outlier} {Exclusion} {Methods}: {A} {Simulation} {Study}}. \emph{Frontiers in Psychology} \textbf{12}, 2194 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Lachaud2011}{}}%
\CSLLeftMargin{36. }%
\CSLRightInline{Lachaud, C. M. \& Renaud, O. \href{https://doi.org/10.1017/s0142716410000457}{A tutorial for analyzing human reaction times: {How} to filter data, manage missing values, and choose a statistical model}. \emph{Applied Psycholinguistics} \textbf{32}, 389--416 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-Dutilh2012}{}}%
\CSLLeftMargin{37. }%
\CSLRightInline{Dutilh, G. \emph{et al.} \href{https://doi.org/10.3758/s13414-011-0243-2}{Testing theories of post-error slowing}. \emph{Attention, Perception, \& Psychophysics} \textbf{74}, 454--465 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Houtman2012}{}}%
\CSLLeftMargin{38. }%
\CSLRightInline{Houtman, F., Castellar, E. N. \& Notebaert, W. \href{https://doi.org/10.1080/20445911.2011.617301}{Orienting to errors with and without immediate feedback}. \emph{Journal of Cognitive Psychology} \textbf{24}, 278--285 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Singmann2019}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Singmann, H. \& Kellen, D. An introduction to mixed models for experimental psychology. in \emph{New methods in cognitive psychology} 4--31 (Routledge, 2019). doi:\href{https://doi.org/10.4324/9780429318405-2}{10.4324/9780429318405-2}.}

\leavevmode\vadjust pre{\hypertarget{ref-Mussel2016}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{Mussel, P., Ulrich, N., Allen, J. J. B., Osinsky, R. \& Hewig, J. \href{https://doi.org/10.1038/srep29245}{Patterns of theta oscillation reflect the neural basis of individual differences in epistemic motivation}. \emph{Scientific Reports} \textbf{6}, (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Enders2007}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{Enders, C. K. \& Tofighi, D. \href{https://doi.org/10.1037/1082-989x.12.2.121}{Centering predictor variables in cross-sectional multilevel models: {A} new look at an old issue.} \emph{Psychological Methods} \textbf{12}, 121--138 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-Lorah2018}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Lorah, J. \href{https://doi.org/10.1186/s40536-018-0061-2}{Effect size measures for multilevel models: Definition, interpretation, and {TIMSS} example}. \emph{Large-scale Assessments in Education} \textbf{6}, (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Simonsohn2020}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Simonsohn, U., Simmons, J. P. \& Nelson, L. D. \href{https://doi.org/10.1038/s41562-020-0912-z}{Specification curve analysis}. \emph{Nature Human Behaviour} \textbf{4}, 1208--1214 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Wetzels2015}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Wetzels, R., Ravenzwaaij, D. van \& Wagenmakers, E.-J. Bayesian analysis. 1--11 (2015) doi:\href{https://doi.org/10.1002/9781118625392.wbecp453}{10.1002/9781118625392.wbecp453}.}

\end{CSLReferences}

\endgroup

\newpage

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

JZ, CS, and AS conceptualized the study and acquired funding.
JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.

\hypertarget{competing-interests}{%
\section{Competing Interests}\label{competing-interests}}

The authors declare no competing interests.

\newpage
\setcounter{figure}{0}

\hypertarget{figures-and-figure-captions}{%
\section{Figures and figure Captions}\label{figures-and-figure-captions}}

\begin{figure}
\includegraphics[width=\textwidth]{../Inkscape Figures/Paradigm_Scheme} \caption{ }\label{fig:figure1appendix}
\end{figure}

\emph{Figure 1.} An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back \textgreater{} 3-back \textgreater{} 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation ``SV 3-back(1-back)'' for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.

\newpage

\hypertarget{DesignTableSection}{%
\section{Design Table}\label{DesignTableSection}}

(Starts on next page)

\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}

\end{document}

### 2022-06-26 06_Paper/ER-ED/Manuscript_ERED_Stage1_rev.Rmd
created manuscript without figures for revision

--- 2022-06-20 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 
-```{r child = "TheoreticalBackground.Rmd"}
+```{r child = "TheoreticalBackground_rev.Rmd"}
 ```
 
-```{r child = "Method.Rmd"}
+```{r child = "method_rev.Rmd"}
 ```
@@
 
-```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
-include_graphics(here("06_Paper","ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
-```
+INSERT FIGURE 1 HERE
 
@@
 
-```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
-```
+INSERT FIGURE 2 HERE
 
@@
 
-\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
+INSERT DESIGN TABLE HERE
 
+<!--
 \newpage
@@
 ```
+-->

### 2022-06-26 06_Paper/ER-ED/Manuscript_ERED_Stage1_rev.tex
created manuscript without figures for revision

--- 2022-06-20 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
-In the top half, the person has a clear preference for one of the three strategies.
-In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can be represented by our paradigm.}\label{fig:ResponsePatterns}
-\end{figure}
+INSERT FIGURE 1 HERE
 
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{Block design of the paradigm.
-Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
-After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared.
-Before the last block, participants can decide which regulation strategy they want to reapply.
-Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.}\label{fig:DesignERED}
-\end{figure}
+INSERT FIGURE 2 HERE
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{Preece, D.
-A., Becerra, R., Robinson, K.
-\& Gross, J.
-J.
-\href{https://doi.org/10.1080/00223891.2018.1564319}{The emotion regulation questionnaire: Psychometric properties in general community samples}.
-\emph{J Pers Assess} \textbf{102}, 348--356 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{Fleischhauer, M.
-\emph{et al.} \href{https://doi.org/10.1177/0146167209351886}{Same or different?
-{Clarifying} the relationship of need for cognition to personality and intelligence}.
-\emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Fleischhauer, M., Strobel, A.
-\& Strobel, A.
-\href{https://doi.org/10.1027/1614-0001/a000161}{Directly and indirectly assessed {N}eed for {C}ognition differentially predict spontaneous and reflective information processing behavior}.
-\emph{Journal of Individual Differences} \textbf{36}, 101--109 (2015).}
-
 \end{CSLReferences}
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
-\end{figure}
+INSERT FIGURE 1 HERE
 
@@
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
-\end{figure}
+INSERT FIGURE 2 HERE
 
@@
 
-\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
-
-\newpage
-
-\hypertarget{SupplementaryMaterial}{%
-\section{Supplementary Material}\label{SupplementaryMaterial}}
-
-\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\setcounter{section}{19}
-\setcounter{figure}{0}
-\setcounter{table}{1}
-
-\newpage
-
-\hypertarget{SupplementQuestionnaires}{%
-\subsection{Detailed information on psychometric measures}\label{SupplementQuestionnaires}}
-
-\emph{WHO-5.} General psychological well-being is assessed using the WHO-5 scale\textsuperscript{45,46}.
-5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{46}.
-
-\emph{Connor-Davidson Resilience Scale.} Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
-10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{48}.
-
-\emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{69}.
-
-\emph{FlexER Scale.} Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{44} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
-Psychometric properties are currently under investigation.
-
-\emph{Implicit Theories Questionnaire.} Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of\textsuperscript{51}.
-4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{51}.
-
-\emph{Need for Cognition Scale.} Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale\textsuperscript{52}.
-Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,70} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{71}.
-
-\emph{Self-Regulation Scale.} As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} is used.
-The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency {[}Cronbach's \(\alpha>.80\);\textsuperscript{54}{]}.
-
-\emph{Brief Self-Control Scale.} As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} is used.
-It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{56} .
-
-\emph{Barratt Impulsiveness Scale.} As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} is used.
-Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported\textsuperscript{58}.
-
-\emph{Attentional Control Scale.} Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
-The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported\textsuperscript{59}.
-
-\newpage
-
-\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
-\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
-
-ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1, 15 & 3895.91 & 34.32 *** & .475 & <.001\\
-\hline
-\end{tabular}
-
-\(BF10=\) 1,244.99
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-3}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neutral} - View_{negative}$ & -129.28 & 22.07 & 15.00 & -5.86 & 0.00 & 794.78 & 0.70 & {}[0.43, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figure:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjArousalViewPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.}\label{fig:FigSubjArousalViewPilot}
-\end{figure}
-
-\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}
-
-ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 2.79, 41.89 & 2238.27 & 1.17 & .011 & .332\\
-\hline
-\end{tabular}
-
-\(BF10=\) 0.11
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{negative} - Distraction$ & -0.74 & 16.14 & 45.00 & -0.05 & 1.00 & 0.26 & 4.68e-05 & {}[0.00, 1.00]\\
-$View_{negative} - Distancing$ & -5.35 & 16.14 & 45.00 & -0.33 & 1.00 & 0.27 & 2.43e-03 & {}[0.00, 1.00]\\
-$View_{negative} - Suppression$ & -26.23 & 16.14 & 45.00 & -1.63 & 0.67 & 1.25 & 0.06 & {}[0.00, 1.00]\\
-$Distraction - Distancing$ & -4.61 & 16.14 & 45.00 & -0.29 & 1.00 & 0.26 & 1.81e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -25.49 & 16.14 & 45.00 & -1.58 & 0.73 & 0.77 & 0.05 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -20.88 & 16.14 & 45.00 & -1.29 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figure:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjArousalRegPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.}\label{fig:FigSubjArousalRegPilot}
-\end{figure}
-
-\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
-\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
-
-\emph{Corrugator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1, 15 & 1.01 & 9.70 ** & .237 & .007\\
-\hline
-\end{tabular}
-
-\(BF10=\) 6,690,401.91
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neutral} - View_{negative}$ & -1.11 & 0.36 & 15.00 & -3.11 & 0.01 & 5,019,313.20 & 0.39 & {}[0.09, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\emph{Levator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1, 15 & 0.17 & 7.72 * & .162 & .014\\
-\hline
-\end{tabular}
-
-\(BF10=\) 48.44
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neutral} - View_{negative}$ & -0.40 & 0.14 & 15.00 & -2.78 & 0.01 & 41.02 & 0.34 & {}[0.05, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figures:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGCorrViewPilot-1} \caption{Corrugator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGCorrViewPilot}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGLevViewPilot-1} \caption{Levator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGLevViewPilot}
-\end{figure}
-
-\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}
-
-\emph{Corrugator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1.53, 22.98 & 1.16 & 5.71 * & .189 & .015\\
-\hline
-\end{tabular}
-
-\(BF10=\) 5,257,689.54
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 4,962.89 & 0.19 & {}[0.05, 1.00]\\
-$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 616.63 & 0.21 & {}[0.06, 1.00]\\
-$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 11,678.82 & 0.20 & {}[0.06, 1.00]\\
-$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 0.07 & 1.78e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 0.08 & 7.22e-04 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 0.06 & 2.36e-04 & {}[0.00, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\emph{Levator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 2.07, 31.00 & 0.20 & 8.27 ** & .225 & .001\\
-\hline
-\end{tabular}
-
-\(BF10=\) 672,341.29
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{negative} - Distraction$ & 0.42 & 0.13 & 45.00 & 3.24 & 0.01 & 58.02 & 0.19 & {}[0.05, 1.00]\\
-$View_{negative} - Distancing$ & 0.45 & 0.13 & 45.00 & 3.46 & 0.01 & 93.49 & 0.21 & {}[0.06, 1.00]\\
-$View_{negative} - Suppression$ & 0.62 & 0.13 & 45.00 & 4.79 & 0.00 & 6,253.91 & 0.34 & {}[0.16, 1.00]\\
-$Distraction - Distancing$ & 0.03 & 0.13 & 45.00 & 0.22 & 1.00 & 0.07 & 1.06e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.20 & 0.13 & 45.00 & 1.54 & 0.78 & 1.52 & 0.05 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.17 & 0.13 & 45.00 & 1.32 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figures:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGCorrRegPilot-1} \caption{Corrugator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGCorrRegPilot}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGLevRegPilot-1} \caption{Levator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGLevRegPilot}
-\end{figure}
-
-\hypertarget{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{Pilot study: Subjective effort in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}
-
-ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 2.38, 35.66 & 4388.19 & 11.13 *** & .185 & <.001\\
-\hline
-\end{tabular}
-
-\(BF10=\) 7.40
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{negative} - Distancing$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
-$View_{negative} - Distraction$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
-$View_{negative} - Suppression$ & -88.15 & 20.85 & 45.00 & -4.23 & 0.00 & 33.13 & 0.28 & {}[0.11, 1.00]\\
-$Distraction - Distancing$ & 21.00 & 20.85 & 45.00 & 1.01 & 1.00 & 0.50 & 0.02 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.57 & 0.03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 0.26 & 1.27e-04 & {}[0.00, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figure:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjEffortPilot-1} \caption{Subjective effort ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.}\label{fig:FigSubjEffortPilot}
-\end{figure}
+INSERT DESIGN TABLE HERE
 

### 2022-06-26 06_Paper/ER-ED/TheoreticalBackground_rev.Rmd
created manuscript without figures for revision

--- 2022-06-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 
+INSERT FIGURE 1 HERE
+<!--
 ```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.
@@
 ```
+-->
 

### 2022-06-26 06_Paper/ER-ED/method_rev.Rmd
created manuscript without figures for revision

--- 2022-06-20 06_Paper/ER-ED/method.Rmd
@@
 
+INSERT FIGURE 2 HERE
+<!--
 ```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm.

### 2022-06-26 06_Paper/COG-ED/Manuscript_rev.Rmd
created manuscript file without supplement and figures

--- 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
@@
 ---
-title             : "When easy is not preferred: An effort discounting paradigm for estimating subjective values of tasks"
-shorttitle        : "The CAD paradigm for estimating subjective values"
+title             : "When easy is not preferred: A discounting paradigm to assess load-independent task preference"
+shorttitle        : "The CAD paradigm to assess task preference"
 author: 
@@
   Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
-  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
+  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
 
 keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
-wordcount         : "~ 3,700"
+wordcount         : "~ 4,300"
 bibliography      : CAD.bib
@@
 The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred[@Westbrook2013].
-The subjective value (SV) of each difficulty level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
+The subjective value (SV) of each more difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
 Westbrook et al.[-@Westbrook2013] used these SVs to investigate inter-individual differences in effort discounting.
@@
 Regarding the associations of task load and effort discounting we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
-A hypothesis that was not investigated in the original study is that (2c) SVs decline stronger with increasing task load for individuals with low compared to high NFC scores.
-And regarding individual differences in effort discounting we hypothesize that (3a) SVs predict individual NFC scores, and (3b) perceived task load does not predict individual NFC scores.
+And finally, we hypothesize that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
 Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.
@@
 Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
-Adding those same pairs again, but with the oppositve assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
+Adding those same pairs again, but with the opposite assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
 First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
@@
 The other level in the pair will be set to a fixed value of 2\ €.
-Then, the effort discounting sensu Westbrook [-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
+Then, the effort discounting sensu Westbrook et al.[-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
 The order in which the pairs are presented will be fully randomized, and each pair will go through all iteration steps of adding/subtracting 0.50\ €, 0.25\ €, 0.13\ €, 0.06\ €, 0.03\ €, 0.02\ € to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
@@
 If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
-The interpretation of SVs in Westbrook [-@Westbrook2013] was "The minimum relative reward required for me to choose 1-back over this level".
+The interpretation of SVs in Westbrook et al.[-@Westbrook2013] was "The minimum relative reward required for me to choose 1-back over this level".
 So if the SV of 3-back was 0.6, the participant would need to be rewarded with at least 60\ % of what they are being offered for doing 3-back to do 1-back instead, forgoing the higher reward for 3-back.
@@
 
+INSERT FIGURE 1 HERE
+<!--
 ```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
@@
 After the *n*-back task, participants complete the CAD paradigm on screen and are instructed to do so as realistically as possible, even though the displayed rewards will not be paid out on top of their compensation.
-They are told that one of their choices will be randomly picked for the final run of *n*-back, the data of which will not be analyzed as it only serves to incentivise truthful behavior and stay close to the design of Westbrook [-@Westbrook2013].
+They are told that one of their choices will be randomly picked for the final run of *n*-back, the data of which will not be analyzed as it only serves to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
 After the CAD paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
@@
 No data will be replaced.
-We aim to conduct all analysis as described in Westbrook et al.[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
 The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
@@
 Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
-Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
+Error- and post-error trials will be excluded, because RT in the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
 To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].
@@
 
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
+The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *ttestBF*.
 We will consider a $BF10$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF10$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].
@@
 The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
-The specification curve analysis showed that this pattern was true for all 63 pipelines.
-Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
+NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
 All results are detailed in the Supplementary Material.
@@
 
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
-Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-Applications for the centralized funds will be reviewed in May of 2022.
-Regardless of whether or not this additional funding will be granted, the study can commence immediately.
+This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
@@
 JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
-JZ prepared the original draft.
 All authors reviewed, edited, and approved the final version of the manuscript.
@@
 
+INSERT FIGURE 1 HERE
+<!--
 ```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
+INSERT DESIGN TABLE HERE
+<!--
 \includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
-
+-->
 \newpage
@@
 
+INSERT SUPPLEMENT HERE
+<!--
 \counterwithin{figure}{section}
@@
 
-Paired contrasts:
+Contrasts:
 

### 2022-06-28 06_Paper/ER-ED/TheoreticalBackground_rev.Rmd
created tex version without figures

@@
 But our paradigm can also account for the case that a person does not have a clear preference.
-Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
+Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure 1).
 In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al.[@Zerna2022]).

### 2022-06-28 06_Paper/ER-ED/method_rev.Rmd
created tex version without figures

@@
 
-*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group[@Scheffel2021].
+*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure 2), similar to paradigms previously used by our group[@Scheffel2021].
 Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.

### 2022-06-28 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted new revision file with design table

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
+\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
 In the top half, the person has a clear preference for one of the three strategies.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{Block design of the paradigm.
+\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{Block design of the paradigm.
 Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
+\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
 \end{figure}
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{C:/Users/scheffel/Scheffel/Forschung/A_Projects/2021_CERED/CAD/06_Paper/ER-ED/figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
+\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
 \end{figure}

### 2022-07-11 06_Paper/ER-ED/Manuscript_ERED_Stage1_rev.tex

@@
 \keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6289}
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 But our paradigm can also account for the case that a person does not have a clear preference.
-Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
+Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure 1).
 In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{34}).
@@
 
-\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
+\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure 2), similar to paradigms previously used by our group\textsuperscript{22}.
 Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
@@
 
-INSERT DESIGN TABLE HERE
+\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
+
+\newpage
+
+\hypertarget{SupplementaryMaterial}{%
+\section{Supplementary Material}\label{SupplementaryMaterial}}
+
+INCLUDE SUPPLEMENT HERE
 

### 2022-07-19 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
corrected word count

@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "6289"
+wordcount         : "6303"
 bibliography      : ["ER_ED.bib"]

### 2022-08-05 06_Paper/ER-ED/ERED_Stage1/Manuscript_ERED_Stage1.tex
renamed directories

--- 2022-06-28 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
@@
 {}{\PatchFailed}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6289}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6303}
 \usepackage{lineno}
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
-In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al.\textsuperscript{34}).
+In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna, Scheffel et al.\textsuperscript{34}).
 
@@
 Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).
+The presented MLM follows the conceptualization of Zerna, Scheffel, et al.\textsuperscript{34}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Zerna2022}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-ZernaScheffel2022}{}}%
 \CSLLeftMargin{34. }%

### 2022-08-05 06_Paper/ER-ED/ERED_Stage1/Stage1_revision/TheoreticalBackground_rev.Rmd
renamed directories

--- 2022-06-28 06_Paper/ER-ED/TheoreticalBackground_rev.Rmd
@@
 
-The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
+The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] is an important cognitive skill. 
 It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning[@Gross1998emerging].

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/TheoreticalBackground.Rmd
renamed directories

--- 2022-06-08 06_Paper/ER-ED/TheoreticalBackground.Rmd
@@
 Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
-In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al.[@Zerna2022]).
+In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna, Scheffel et al.[@ZernaScheffel2022]).
 

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
renamed documents

@@ -18,11 +18,8 @@ library(here)       # to set directories without defined paths
 here::i_am("flag_project_root_CAD.txt")
 
 library(renv)
-renv::activate(here("06_Paper", "ER-ED"))
-renv::restore(here("06_Paper", "ER-ED"))
-
-library(dplyr)
-library(ggplot2)
+renv::activate(here("06_Paper", "ER-ED", "ERED_Stage2"))
+renv::restore(here("06_Paper", "ER-ED", "ERED_Stage2"))
 
 ##################### DATA IMPORT #######################
 

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
changed file paths

--- 2022-07-19 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "6303"
+wordcount         : "XXXXX"
 bibliography      : ["ER_ED.bib"]
@@
 # load workspace variables from analyses_ERED.R script
-load(here("06_Paper","ER-ED","Workspace_ERED_pilot.RData"))
+load(here("06_Paper","ER-ED","Workspace_ERED.RData"))
 
@@
 ```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
-include_graphics(here("06_Paper","ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
+include_graphics(here("06_Paper","ER-ED", "ERED_Stage2", "figures", "Paradigm_Scheme_T2.png" ))
 ```
@@
 ```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
+include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
 ```

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/method.Rmd
past tense

--- 2022-06-20 06_Paper/ER-ED/method.Rmd
@@
 
-library(papaja)     # APA conform output
-library(readxl)     # import excel files
+#library(papaja)     # APA conform output
+#library(readxl)     # import excel files
 ```
@@
 The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022). 
-Prior to testing, written informed consent will be obtained.
-Participants will receive 30 € in total or course credit for participation.
+Prior to testing, written informed consent was obtained.
+Participants received 24 € in total or course credit for participation.
 
@@
 
-Young healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
-Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
-Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
-In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
-Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
-The second session will take place exactly one week after session one.
-Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
-A brief training will ensure that all participants are able to implement the ER strategies.
-Next, electrodes to measure facial EMG will be attached and the ER task will be conducted, followed by an ED procedure regarding the ER strategies.
-After that, participants will choose one ER strategy to repeat one more time.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].
+Young healthy participants (aged 18 to 30 years) were recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
+Participants were excluded from participation if they do not fluently speak German, had current or a history of psychological disorders or neurological trauma, or reported to take medication.
+Participants were invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
+The study consisted of two lab sessions, which took place in a shielded cabin with constant lighting.
+Before each session, participants received information about the respective experimental procedure and provided informed consent.
+In the first session participants filled out a demographic questionnaire and completed an *n*-back task with the levels one to four.
+Then, they completed an effort discounting (ED) procedure regarding the *n*-back levels on screen, followed by a random repetition of one *n*-back level [@ZernaScheffel2022].
+The second session took place exactly one week after session one.
+Participants provided informed consent and received written instructions on the ER paradigm and ER strategies that they should apply.
+A brief training ensured that all participants were able to implement the ER strategies.
+Next, electrodes to measure facial EMG were attached and the ER task was conducted, followed by an ED procedure regarding the ER strategies.
+After that, participants chose one ER strategy to repeat one more time.
+Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].
 
@@
 
-The online survey will contain a number of questionnaires. 
-In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
+The online survey contained a number of questionnaires. 
+In the focus of the current project was the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
 It assesses flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
-The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".
+The items were rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".
 
-Further psychological constructs will be assessed but have no clear hypotheses in the present work and are therefore investigated only exploratory:
-General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
-Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] will be used.
-To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
-Attentional control will be assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
+Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
+General psychological well-being was assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] was used.
+Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
+Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] was used.
+To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
+Attentional control were assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
 For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).
@@
 
-The ER paradigm will consist of three parts that will be described in the following.
+The ER paradigm consisted of three parts that will be described in the following.
 
@@
 Intraclass correlation coefficient (ICC), $\rho$, will be reported for each model (null model, as well as full model).
+The presented MLM follows the conceptualization of Zerna, Scheffel, et al.[@ZernaScheffel2022]
 

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/method.Rmd
past tense

@@
 
-*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group[@Scheffel2021].
-Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
-Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
-During this block, 20 neutral pictures will be presented.
-Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
-In the second block, participants will actively view negative pictures.
-During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
-In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
-Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants will be told to "suppress their emotional facial expression." 
+*Part one: ER task.* <br> Part one was a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group[@Scheffel2021].
+Participants were told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
+Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
+During this block, 20 neutral pictures were presented.
+Participants were asked to "actively view all pictures and permit all emotions that may arise." 
+In the second block, participants actively viewed negative pictures.
+During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
+In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
+During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
+Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
+During suppression, participants were told to "suppress their emotional facial expression." 
 They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite[@Scheffel2021].
-All participants will receive written instruction and complete a training session.
-After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
-The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
-Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
-Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
-It is followed by neutral or negative pictures for a total of 6 seconds.
-After each block, participants retrospectively will rate their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the ragulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
+Participants were instructed not to suppress their thoughts or change their facial expression to the opposite[@Scheffel2021].
+All participants received written instruction and completed a training session.
+After the training session, participants were asked about their applied ER strategies to avoid misapplication.
+The order of the three regulation blocks (distraction, distancing, and suppression) were randomized between participants.
+Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
+Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
+It was followed by neutral or negative pictures for a total of 6 seconds.
+After each block, participants retrospectively rated their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the regulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
 
-*Part two: ER effort discounting.* <br> In the second part, ER effort discounting will take place.
+*Part two: ER effort discounting.* <br> In the second part, ER effort discounting took place.
 The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.[-@Westbrook2013] with a major change.
-We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
+We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
 distancing, distraction vs.
 suppression, and distancing vs.
-suppression), each of the two strategies will be presented with a monetary reward.
-Because there is no strategy that is objectively more difficult, we will add initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
-They decide by clicking the on-screen button of the respective option.
-Each of the three strategy pairs will be presented three times in total, in a randomized order and randomly assigned which strategy appears on the left or right side of the screen.
-For each pair, the strategy that was chosen at least two out of three times will be assigned the flexible starting value of 1 €, the other strategy will be assigned the fixed value of 2 €.
-After this, comparisons between strategies will follow the original COG-ED paradigm[@Westbrook2013].
-Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
-The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
-If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
-The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
-Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.
+suppression), each of the two strategies were presented with a monetary reward.
+Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
+They decided by clicking the on-screen button of the respective option.
+Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
+For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1 €, the other strategy was assigned the fixed value of 2 €.
+After this, comparisons between strategies followed the original COG-ED paradigm[@Westbrook2013].
+Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
+The adjustment started at 0.50 € and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
+If a participant always chose the strategy with the fixed 2 € reward, the other strategy's last value on display was 1.97 €, if they always choose the lower strategy, its last value was 0.03 €.
+The sixth adjustment of 0.02 € was done during data analysis, based on the participants' decision in the last display of the pairing.
+Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.
 

### 2022-08-05 06_Paper/ER-ED/ERED_Stage2/method.Rmd
past tense

@@
 
-*Part three: ER choice.* <br> After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
-Importantly, there will be no further instruction on what basis they should make their decision.
+*Part three: ER choice.* <br> After the discounting part, participants chose which one of the three ER strategies (distraction, distancing or suppression) they wanted to re-apply.
+Importantly, there was no further instruction on what basis they should make their decision.
 Participants should make their decision freely, according to criteria they consider important for themselves.
-However, participants will be asked to state the reasons for the decision afterwards in RedCap using a free text field.
-As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
+However, participants were asked to state the reasons for the decision afterwards in RedCap using a free text field.
+As soon as they have decided, they saw the respective instruction and the block with another 20 negative pictures started.
 
@@
 Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
+include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
 ```
@@
 
-Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS)[@Lang2008].
+Pictures that were used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS)[@Lang2008].
 The 20 neutral pictures (Valence (V): *M* $\pm$ *SD* = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): *M* $\pm$ *SD* = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
-Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
-An evolutionary algorithm [@Yu2010] is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
+Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
+An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
 A complete list of all pictures and their classification into sets can be found in supplementary material table S1.
-The five sets of negative pictures will be assigned randomly to the blocks.
+The five sets of negative pictures were assigned randomly to the blocks.
 
@@
 
-Bipolar facial electromyography (EMG) will be measured for *corrugator supercilii* and *levator labii* as indices of affective valence[@Bradley2000], similar to previous work by our group[@Gaertner2021].
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of @Fridlund1986.
-The ground electrode will be placed over the left *Mastoid*.
-Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
-Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
-Impedance level will be kept below 10 $k\Omega$. 
-Data will be sampled at 1000 Hz, filtered, rectified and integrated. 
-A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
-Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset [@Bradley2000]. 
-Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
+Bipolar facial electromyography (EMG) were measured for *corrugator supercilii* and *levator labii* as indices of affective valence[@Bradley2000], similar to previous work by our group[@Gaertner2021].
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) were placed over each left muscle according to the guidelines of Fridlund and Cacioppo[@Fridlund1986].
+The ground electrode was placed over the left *Mastoid*.
+Before electrode placement, the skin was abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
+Raw signals were amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
+Impedance level were kept below 10 $k\Omega$. 
+Data were sampled at 1000 Hz, filtered, rectified and integrated. 
+A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter was applied to both signals.
+*Corrugator* and *levator* EMG was analyzed during the 6 s of picture presentation.
+EMG data were baseline-corrected using a time window of 2 s prior to stimulus onset [@Bradley2000]. 
+Last, the sampling rate was changed to 100 Hz, and EMG data were averaged for each condition and each participant.
 
@@
 
-Sample size calculation is done using *G\*Power*[@Faul2007; @Faul2009].
+Sample size calculation was done using *G\*Power*[@Faul2007; @Faul2009].
 In a meta-analysis of Zaehringer and colleagues[-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
@@
 However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aim to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
+Therefore, we aimed to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
 Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
@@
 
-Data collection and analysis will not be performed blind to the conditions of the experiments.
-Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
-EMG data of subjects will be excluded from analysis if errors occured during recording.
-No further data exclusions are planned.
-The level of significance will be set to $\alpha=.05$.
-For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the *afex* package[@Singmann2021].
-Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values will be reported when the assumption of sphericity is violated.
-If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
-Proportion of explained variance $\eta_{p}^{2}$ will be reported as a measure of effect size.
+Data collection and analysis were not performed blind to the conditions of the experiments.
+Data of whole participants were excluded from analysis if participants withdraw their consent or they stated that they did not follow experimental instructions.
+EMG data of subjects were excluded from analysis if errors occured during recording.
+No further data exclusions were planned.
+The level of significance was set to $\alpha=.05$.
+For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) were conducted and estimated marginal means were computed using the *afex* package[@Singmann2021].
+Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values were reported when the assumption of sphericity was violated.
+If the within-subjects factor of interest was significant, pairwise contrasts were calculated using Bonferroni adjustment for multiple testing.
+Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
 
 *Effect of valence on arousal and facial EMG.*<br> 
-To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG *corrugator* and *levator* activity.
+To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted.
+To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted for EMG *corrugator* and *levator* activity.
 
 *Effects of emotion regulation on arousal, facial EMG and effort.* <br> 
-To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
-To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity will be conducted.
-To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
+To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings was conducted.
+To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity was conducted.
+To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings was conducted.
 
-*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy will be divided by 2 €.
-Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.
+*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.02 € was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2 €.
+Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
 The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
-The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.
+The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.
 
-To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the $lmerTest$ package[@Kuznetsova2017].
-First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
-Restricted maximum likelihood (REML) will be applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors will be specified.
+To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the $lmerTest$ package[@Kuznetsova2017].
+First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+Restricted maximum likelihood (REML) was applied to fit the model.
+A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors was specified.
 $$
@@
 $$ 
-Level-1-predictors will be centered within cluster[@Enders2007].
-Residuals of the final model will be inspected visually.
-Intraclass correlation coefficient (ICC), $\rho$, will be reported for each model (null model, as well as full model).
-The presented MLM follows the conceptualization of Zerna, Scheffel, et al.[@ZernaScheffel2022]
+Level-1-predictors were centered within cluster[@Enders2007].
+Residuals of the final model were inspected visually.
+Intraclass correlation coefficient (ICC), $\rho$, was reported for each model (null model, as well as full model).
+The presented MLM followed the conceptualization of Zerna, Scheffel, et al.[@ZernaScheffel2022]
 
-To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
-Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
+To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice was computed.
+Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.
 
-The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
-To this end, for each participant, SVs will be sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
+The association between flexible ER and SVs of ER strategies (H7b) was investigated with a linear regression using the individual $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
+To this end, for each participant, SVs were sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
 The resulting $intercept$ informs about the extent to which an individual considers any or all of the ER strategies as useful for regulation their emotion, while the $slope$ informs about the flexibility in the use of emotion regulation strategies.
-The individual intercepts and slopes will then be entered as predictors in a regression model with the FlexER score as dependent variable. 
+The individual intercepts and slopes were entered as predictors in a regression model with the FlexER score as dependent variable. 
 A positive association with the predictor $intercept$ would indicate that overall higher SVs attached to ER strategies predicts higher scores on the FlexER scale. 
@@
 
-The influence of personality traits on SVs will be investigated exploratorily.
-Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
+The influence of personality traits on SVs were investigated exploratorily.
+Therefore, the MLM specified above was extended by the level-2-predictors NFC and self-control.
 
-For each result of the analyses, both $p$-values and Bayes factors $BF10$, calculated using the *BayesFactor* package[@Morey2021], will be reported. 
-Bayes factors are calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
+For each result of the analyses, both $p$-values and Bayes factors $BF10$, calculated using the *BayesFactor* package[@Morey2021], were reported. 
+Bayes factors were calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
 

### 2022-08-09 06_Paper/ER-ED/ERED_Stage1/Stage1_revision/Manuscript_ERED_Stage1_rev.Rmd

--- 2022-06-26 06_Paper/ER-ED/Manuscript_ERED_Stage1_rev.Rmd
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 
-INSERT DESIGN TABLE HERE
+\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
 
-<!--
 \newpage
@@
 
+INCLUDE SUPPLEMENT HERE
+
+<!--
 \includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
@@
 \setcounter{table}{1}
-
 \newpage

### 2022-08-09 06_Paper/ER-ED/ERED_Stage2/TheoreticalBackground.Rmd
corrected file paths

@@
 In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can be represented by our paradigm."}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
+This pattern can be represented by our paradigm.
+Figure available at \url{https://osf.io/vnj8x/}, under a CC-BY4.0 license."}
+include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Paradigm_Scheme_T2.png" ))
 ```

### 2022-08-09 06_Paper/ER-ED/ERED_Stage2/method.Rmd

@@
 Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
-After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared.
-Before the last block, participants can decide which regulation strategy they want to reapply.
-Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
+Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
+After, the discounting procedure took place.
+All three regulation strategies were compared pairwise.
+Before the last block, participants could decide which regulation strategy they wanted to reapply.
+Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
 include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))

### 2022-08-09 06_Paper/ER-ED/ERED_Stage2/method.Rmd
added comma

@@
 
-*Effects of emotion regulation on arousal, facial EMG and effort.* <br> 
+*Effects of emotion regulation on arousal, facial EMG, and effort.* <br> 
 To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings was conducted.

### 2022-08-15 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED_Pilot.r
added violin plots

@@ -1,0 +1,622 @@
+######################################################
+# R Script for analyses of the Registered Report
+# "Estimating individual subjective values of emotion regulation strategies"
+# Scheffel, C., Zerna, J., Gärtner, A., Dörfel, D., & Strobel, A. (2022)
+#
+# Christoph Scheffel
+# (christoph_scheffel@tu-dresden.de)
+#
+######################################################
+
+#################### SETUP ###########################
+
+# Open relevant packages
+
+library(here)       # to set directories without defined paths
+
+# set top level directory to source file
+here::i_am("flag_project_root_CAD.txt")
+
+library(renv)
+renv::activate(here("06_Paper", "ER-ED", "ERED_Stage2"))
+renv::restore(here("06_Paper", "ER-ED", "ERED_Stage2"))
+
+##################### DATA IMPORT #######################
+
+# import ER ratings and ER discounting data into lists
+
+datalist_ER_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
+                                       pattern = "*_ER.*csv", full.names = TRUE),
+                                       read.csv, stringsAsFactors = FALSE,
+                                       header = TRUE)
+  
+datalist_ED_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
+                                       pattern = "*_ED.*csv", full.names = TRUE),
+                                       read.csv, stringsAsFactors = FALSE,
+                                       header = TRUE)
+
+# new empty frame to store files into
+data_ER_pilot <- data.frame(ID = character(), block = character(),
+                            arousal = double(), effort = double(),
+                            trigger = double(), trigger_reg = double())
+
+data_ED_pilot <- data.frame(ID = character(), step = double(),
+                            choice = character(), LBvalue = double(),
+                            LBlevel = double(), RBvalue = double(),
+                            RBlevel = double())
+
[…]

### 2022-08-15 06_Paper/ER-ED/ERED_Stage2/method.Rmd
corrected package

@@
 # lists contain arousal and valence values of each picture
-stim_negative <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))
+stim_negative <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Trials", "negative.xlsx")), range = cellranger::cell_cols("A:D"))
 
-stim_neutral <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
+stim_neutral <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Trials", "neutral.xlsx")), range = cellranger::cell_rows(1:21))
 ```

### 2022-08-15 06_Paper/ER-ED/ERED_Stage2/TheoreticalBackground.Rmd
corrected url

@@
 This pattern can be represented by our paradigm.
-Figure available at \url{https://osf.io/vnj8x/}, under a CC-BY4.0 license."}
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
 include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Paradigm_Scheme_T2.png" ))

### 2022-08-15 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

--- 2022-08-05 06_Paper/ER-ED/ERED_Stage1/Manuscript_ERED_Stage1.tex
@@
 {}{\PatchFailed}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: 6303}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: XXXXX}
 \usepackage{lineno}
@@
 In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can be represented by our paradigm.}\label{fig:ResponsePatterns}
+This pattern can be represented by our paradigm.
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:ResponsePatterns}
 \end{figure}
@@
 The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022).
-Prior to testing, written informed consent will be obtained.
-Participants will receive 30 € in total or course credit for participation.
+Prior to testing, written informed consent was obtained.
+Participants received 24 € in total or course credit for participation.
 
@@
 
-Young healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{41} at the Technische Universität Dresden.
-Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
-Participants will be invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-The study consists of two lab sessions, which will take place in a shielded cabin with constant lighting.
-Before each session, participants will receive information about the respective experimental procedure and provide informed consent.
-In the first session participants will fill out a demographic questionnaire and complete an n-back task with the levels one to four.
-Then, they will complete an effort discounting (ED) procedure regarding the n-back levels on screen, followed by a random repetition of one n-back level.
-The second session will take place exactly one week after session one.
-Participants will provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
-A brief training will ensure that all participants are able to implement the ER strategies.
-Next, electrodes to measure facial EMG will be attached and the ER task will be conducted, followed by an ED procedure regarding the ER strategies.
-After that, participants will choose one ER strategy to repeat one more time.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{42,43}.
+Young healthy participants (aged 18 to 30 years) were recruited using the software \emph{ORSEE}\textsuperscript{41} at the Technische Universität Dresden.
+Participants were excluded from participation if they do not fluently speak German, had current or a history of psychological disorders or neurological trauma, or reported to take medication.
+Participants were invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
+The study consisted of two lab sessions, which took place in a shielded cabin with constant lighting.
+Before each session, participants received information about the respective experimental procedure and provided informed consent.
+In the first session participants filled out a demographic questionnaire and completed an \emph{n}-back task with the levels one to four.
+Then, they completed an effort discounting (ED) procedure regarding the \emph{n}-back levels on screen, followed by a random repetition of one \emph{n}-back level\textsuperscript{34}.
+The second session took place exactly one week after session one.
+Participants provided informed consent and received written instructions on the ER paradigm and ER strategies that they should apply.
+A brief training ensured that all participants were able to implement the ER strategies.
+Next, electrodes to measure facial EMG were attached and the ER task was conducted, followed by an ED procedure regarding the ER strategies.
+After that, participants chose one ER strategy to repeat one more time.
+Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{42,43}.
 
@@
 
-The online survey will contain a number of questionnaires.
-In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{44}.\\
+The online survey contained a number of questionnaires.
+In the focus of the current project was the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{44}.\\
 It assesses flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
-The items are rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
-
-Further psychological constructs will be assessed but have no clear hypotheses in the present work and are therefore investigated only exploratory:
-General psychological well-being will be assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{49} will be used.
-Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} will be used.
-To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
-Attentional control will be assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
+The items were rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+
+Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
+General psychological well-being was assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{49} was used.
+Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
+Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
+To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} was used.
+To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
+Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
 For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
@@
 
-The ER paradigm will consist of three parts that will be described in the following.
-
-\emph{Part one: ER task.} Part one will be a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
-Participants will be told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
-Every participant first will have the condition ``active viewing-neutral'' that serves as a baseline condition.
-During this block, 20 neutral pictures will be presented.
-Participants will be asked to ``actively view all pictures and permit all emotions that may arise.''
-In the second block, participants will actively view negative pictures.
-During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
-In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants will be asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
-Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants will be told to ``suppress their emotional facial expression.''
+The ER paradigm consisted of three parts that will be described in the following.
+
+\emph{Part one: ER task.} Part one was a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
+Participants were told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
+Every participant first had the condition ``active viewing-neutral'' that served as a baseline condition.
+During this block, 20 neutral pictures were presented.
+Participants were asked to ``actively view all pictures and permit all emotions that may arise.''
+In the second block, participants actively viewed negative pictures.
+During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
+In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
+During distancing, participants were asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
+Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
+During suppression, participants were told to ``suppress their emotional facial expression.''
 They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite\textsuperscript{22}.
-All participants will receive written instruction and complete a training session.
-After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
-The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
-Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
-Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
-It is followed by neutral or negative pictures for a total of 6 seconds.
-After each block, participants retrospectively will rate their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the ragulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.
-
-\emph{Part two: ER effort discounting.} In the second part, ER effort discounting will take place.
+Participants were instructed not to suppress their thoughts or change their facial expression to the opposite\textsuperscript{22}.
+All participants received written instruction and completed a training session.
+After the training session, participants were asked about their applied ER strategies to avoid misapplication.
+The order of the three regulation blocks (distraction, distancing, and suppression) were randomized between participants.
+Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
+Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
+It was followed by neutral or negative pictures for a total of 6 seconds.
+After each block, participants retrospectively rated their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the regulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.
+
+\emph{Part two: ER effort discounting.} In the second part, ER effort discounting took place.
 The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{29} with a major change.
-We will use the following adaption that allows the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies will be presented with a monetary reward.
-Because there is no strategy that is objectively more difficult, we will add initial comparisons asking the participants to choose between ``1 € for strategy A or 1 € for strategy B''.
-They decide by clicking the on-screen button of the respective option.
-Each of the three strategy pairs will be presented three times in total, in a randomized order and randomly assigned which strategy appears on the left or right side of the screen.
-For each pair, the strategy that was chosen at least two out of three times will be assigned the flexible starting value of 1 €, the other strategy will be assigned the fixed value of 2 €.
-After this, comparisons between strategies will follow the original COG-ED paradigm\textsuperscript{29}.
-Each pairing is presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € is either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
-The adjustment starts at 0.50 € and each is half the adjustment of the previous step, rounded to two digits after the decimal point.
-If a participant always chooses the strategy with the fixed 2 € reward, the other strategy's last value on display will be 1.97 €, if they always choose the lower strategy, its last value will be 0.03 €.
-The sixth adjustment of 0.02 € will be done during data analysis, based on the participants' decision in the last display of the pairing.
-Participants will be instructed to decide as realistically as possible by imagining that the monetary reward is actually available for choice.
-
-\emph{Part three: ER choice.} After the discounting part, participants will choose which one of the three ER strategies (distraction, distancing or suppression) they want to re-apply.
-Importantly, there will be no further instruction on what basis they should make their decision.
+We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies were presented with a monetary reward.
+Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between ``1 € for strategy A or 1 € for strategy B''.
+They decided by clicking the on-screen button of the respective option.
+Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
+For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1 €, the other strategy was assigned the fixed value of 2 €.
+After this, comparisons between strategies followed the original COG-ED paradigm\textsuperscript{29}.
+Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
+The adjustment started at 0.50 € and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
+If a participant always chose the strategy with the fixed 2 € reward, the other strategy's last value on display was 1.97 €, if they always choose the lower strategy, its last value was 0.03 €.
+The sixth adjustment of 0.02 € was done during data analysis, based on the participants' decision in the last display of the pairing.
+Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.
+
+\emph{Part three: ER choice.} After the discounting part, participants chose which one of the three ER strategies (distraction, distancing or suppression) they wanted to re-apply.
+Importantly, there was no further instruction on what basis they should make their decision.
 Participants should make their decision freely, according to criteria they consider important for themselves.
-However, participants will be asked to state the reasons for the decision afterwards in RedCap using a free text field.
-As soon as they have decided, they will see the respective instruction and the block with another 20 negative pictures starts.
+However, participants were asked to state the reasons for the decision afterwards in RedCap using a free text field.
+As soon as they have decided, they saw the respective instruction and the block with another 20 negative pictures started.
 
@@
 Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
-After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared.
-Before the last block, participants can decide which regulation strategy they want to reapply.
-Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.}\label{fig:DesignERED}
+Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
+After, the discounting procedure took place.
+All three regulation strategies were compared pairwise.
+Before the last block, participants could decide which regulation strategy they wanted to reapply.
+Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:DesignERED}
 \end{figure}
@@
 
-Pictures that will be used in the paradigm are selected from the Emotional Picture Set (EmoPicS)\textsuperscript{60} and the International Affective Picture System (IAPS)\textsuperscript{61}.
+Pictures that were used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{60} and the International Affective Picture System (IAPS)\textsuperscript{61}.
 The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
-Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, will be used.
-An evolutionary algorithm\textsuperscript{62} is used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
+Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
+An evolutionary algorithm\textsuperscript{62} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
 A complete list of all pictures and their classification into sets can be found in supplementary material table S1.
-The five sets of negative pictures will be assigned randomly to the blocks.
+The five sets of negative pictures were assigned randomly to the blocks.
 
@@
 
-Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{63}, similar to previous work by our group\textsuperscript{7}.
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of\textsuperscript{64}.
-The ground electrode will be placed over the left \emph{Mastoid}.
-Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
-Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
-Impedance level will be kept below 10 \(k\Omega\).
-Data will be sampled at 1000 Hz, filtered, rectified and integrated.
-A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
-Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
-EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset\textsuperscript{63}.
-Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.
+Bipolar facial electromyography (EMG) were measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{63}, similar to previous work by our group\textsuperscript{7}.
+Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) were placed over each left muscle according to the guidelines of Fridlund and Cacioppo\textsuperscript{64}.
+The ground electrode was placed over the left \emph{Mastoid}.
+Before electrode placement, the skin was abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
+Raw signals were amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
+Impedance level were kept below 10 \(k\Omega\).
+Data were sampled at 1000 Hz, filtered, rectified and integrated.
+A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter was applied to both signals.
+\emph{Corrugator} and \emph{levator} EMG was analyzed during the 6 s of picture presentation.
+EMG data were baseline-corrected using a time window of 2 s prior to stimulus onset\textsuperscript{63}.
+Last, the sampling rate was changed to 100 Hz, and EMG data were averaged for each condition and each participant.
 
@@
 
-Sample size calculation is done using \emph{G*Power}\textsuperscript{65,66}.
+Sample size calculation was done using \emph{G*Power}\textsuperscript{65,66}.
 In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
@@
 However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aim to collect data of \(N=120\) participants, about \(50%
+Therefore, we aimed to collect data of \(N=120\) participants, about \(50%
 \) more data sets, than necessary.
@@
 
-Data collection and analysis will not be performed blind to the conditions of the experiments.
-Data of whole participants will be excluded from analysis if participants withdraw their consent or they state that they did not follow experimental instructions.
-EMG data of subjects will be excluded from analysis if errors occured during recording.
-No further data exclusions are planned.
-The level of significance will be set to \(\alpha=.05\).
-For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) will be conducted and estimated marginal means will be computed using the \emph{afex} package\textsuperscript{39}.
-Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values will be reported when the assumption of sphericity is violated.
-If the within-subjects factor of interest is significant, pairwise contrasts will be calculated using Bonferroni adjustment for multiple testing.
-Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
+Data collection and analysis were not performed blind to the conditions of the experiments.
+Data of whole participants were excluded from analysis if participants withdraw their consent or they stated that they did not follow experimental instructions.
+EMG data of subjects were excluded from analysis if errors occured during recording.
+No further data exclusions were planned.
+The level of significance was set to \(\alpha=.05\).
+For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) were conducted and estimated marginal means were computed using the \emph{afex} package\textsuperscript{39}.
+Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values were reported when the assumption of sphericity was violated.
+If the within-subjects factor of interest was significant, pairwise contrasts were calculated using Bonferroni adjustment for multiple testing.
+Proportion of explained variance \(\eta_{p}^{2}\) was reported as a measure of effect size.
 
 \emph{Effect of valence on arousal and facial EMG.}
-To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
-To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for EMG \emph{corrugator} and \emph{levator} activity.
-
-\emph{Effects of emotion regulation on arousal, facial EMG and effort.}
-To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.
-To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity will be conducted.
-To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
-
-\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs will be calculated as follows: first, the value 0.02 € will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy will be divided by 2 €.
-Therefore, the SVs of the flexible strategies are 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they are the preferred strategy of each pairing.
+To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted.
+To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted for EMG \emph{corrugator} and \emph{levator} activity.
+
+\emph{Effects of emotion regulation on arousal, facial EMG, and effort.}
+To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings was conducted.
+To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity was conducted.
+To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings was conducted.
+
+\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02 € was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2 €.
+Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
 The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
-The final SV per strategy for each participant will be computed by averaging the SVs of each strategy across pairings.
-
-To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) will be specified using the \(lmerTest\) package\textsuperscript{67}.
-First, ER strategies will be recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
-Restricted maximum likelihood (REML) will be applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors will be specified.
+The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.
+
+To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the \(lmerTest\) package\textsuperscript{67}.
+First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+Restricted maximum likelihood (REML) was applied to fit the model.
+A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors was specified.
 \[
@@
 \]
-Level-1-predictors will be centered within cluster\textsuperscript{68}.
-Residuals of the final model will be inspected visually.
-Intraclass correlation coefficient (ICC), \(\rho\), will be reported for each model (null model, as well as full model).
-The presented MLM follows the conceptualization of Zerna, Scheffel, et al.\textsuperscript{34}
-
-To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice will be computed.
-Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy will be computed.
-
-The association between flexible ER and SVs of ER strategies (H7b) will be investigated with a linear regression using the individual \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
-To this end, for each participant, SVs will be sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
+Level-1-predictors were centered within cluster\textsuperscript{68}.
+Residuals of the final model were inspected visually.
+Intraclass correlation coefficient (ICC), \(\rho\), was reported for each model (null model, as well as full model).
+The presented MLM followed the conceptualization of Zerna, Scheffel, et al.\textsuperscript{34}
+
+To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice was computed.
+Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.
+
+The association between flexible ER and SVs of ER strategies (H7b) was investigated with a linear regression using the individual \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
+To this end, for each participant, SVs were sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
 The resulting \(intercept\) informs about the extent to which an individual considers any or all of the ER strategies as useful for regulation their emotion, while the \(slope\) informs about the flexibility in the use of emotion regulation strategies.
-The individual intercepts and slopes will then be entered as predictors in a regression model with the FlexER score as dependent variable.
+The individual intercepts and slopes were entered as predictors in a regression model with the FlexER score as dependent variable.
 A positive association with the predictor \(intercept\) would indicate that overall higher SVs attached to ER strategies predicts higher scores on the FlexER scale.
@@
 
-The influence of personality traits on SVs will be investigated exploratorily.
-Therefore, the MLM specified above will be extended by the level-2-predictors NFC and self-control.
-
-For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{40}, will be reported.
-Bayes factors are calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
+The influence of personality traits on SVs were investigated exploratorily.
+Therefore, the MLM specified above was extended by the level-2-predictors NFC and self-control.
+
+For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{40}, were reported.
+Bayes factors were calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
 
@@
 \begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjArousalViewPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjArousalViewPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
+Each dot represents the arousal rating of a single subject.
 Bold dots represent outliers.}\label{fig:FigSubjArousalViewPilot}
@@
 \begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjArousalRegPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjArousalRegPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
+Each dot represents the arousal rating of a single subject.
 Bold dots represent outliers.}\label{fig:FigSubjArousalRegPilot}
@@
 \begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGCorrViewPilot-1} \caption{Corrugator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGCorrViewPilot-1} \caption{Corrugator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
 Each dot represents the corrugator activity of a single trial.
@@
 \begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGLevViewPilot-1} \caption{Levator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGLevViewPilot-1} \caption{Levator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
 Each dot represents the levator activity of a single trial.
@@
 \begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGCorrRegPilot-1} \caption{Corrugator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGCorrRegPilot-1} \caption{Corrugator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
 Each dot represents the corrugator activity of a single trial.
@@
 \begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigEMGLevRegPilot-1} \caption{Levator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGLevRegPilot-1} \caption{Levator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
 Each dot represents the levator activity of a single trial.
@@
 \begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage1_files/figure-latex/FigSubjEffortPilot-1} \caption{Subjective effort ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
+\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjEffortPilot-1} \caption{Subjective effort ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
 Each dot represents the effort rating of a single subject.

### 2022-08-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
corrected mistake in figure caption
knitted document
Update Manuscript_ERED_Stage2.Rmd

@@
       - Conceptualization
+      - Methodology
       - Writing - review & editing 
@@
 # load workspace variables from analyses_ERED.R script
-load(here("06_Paper","ER-ED","Workspace_ERED.RData"))
+load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
 
@@
 ```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
+Each dot represents the arousal rating of a single subject.
 Bold dots represent outliers.", fig.pos="H", out.width="75%"}
@@
 ```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
+Each dot represents the arousal rating of a single subject.
 Bold dots represent outliers.", fig.pos="H", out.width="75%"}

### 2023-01-13 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED_Pilot.r
Update Analyes_ERED_Pilot.r

@@ -21,19 +21,24 @@ library(renv)
 renv::activate(here("06_Paper", "ER-ED", "ERED_Stage2"))
 renv::restore(here("06_Paper", "ER-ED", "ERED_Stage2"))
 
-##################### DATA IMPORT #######################
+#################### PACKAGES ########################
+library(tidyverse)
+
+#################### PILOT ###########################
+
+#################### DATA IMPORT #####################
 
 # import ER ratings and ER discounting data into lists
 
 datalist_ER_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
                                        pattern = "*_ER.*csv", full.names = TRUE),
-                                       read.csv, stringsAsFactors = FALSE,
-                                       header = TRUE)
-  
+                            read.csv, stringsAsFactors = FALSE,
+                            header = TRUE)
+
 datalist_ED_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
                                        pattern = "*_ED.*csv", full.names = TRUE),
-                                       read.csv, stringsAsFactors = FALSE,
-                                       header = TRUE)
+                            read.csv, stringsAsFactors = FALSE,
+                            header = TRUE)
 
 # new empty frame to store files into
 data_ER_pilot <- data.frame(ID = character(), block = character(),
@@ -49,17 +54,17 @@ data_choice_pilot <- data.frame(ID = character(), choice = double())
 
 # store arousal and effort ratings in data_ER frame
 for (i in seq_len(length(datalist_ER_pilot))) {
-    tmp <- data.frame(datalist_ER_pilot[[i]][["participant"]],
-                     datalist_ER_pilot[[i]][["instr_1"]],
-                     datalist_ER_pilot[[i]][["slider_arousal.response"]],
-                     datalist_ER_pilot[[i]][["slider_effort.response"]],
-                     datalist_ER_pilot[[i]][["TriggerBlockView"]],
-                     datalist_ER_pilot[[i]][["TriggerBlockReg"]])
-    colnames(tmp) <- names(data_ER_pilot)
[…]

### 2023-01-13 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
deleted pilot analyses

@@ -26,578 +26,6 @@ renv::restore(here("06_Paper", "ER-ED", "ERED_Stage2"))
 #################### PACKAGES ########################
 library(tidyverse)
 
-#################### PILOT ###########################
-
-#################### DATA IMPORT #####################
-
-# import ER ratings and ER discounting data into lists
-
-datalist_ER_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
-                                       pattern = "*_ER.*csv", full.names = TRUE),
-                                       read.csv, stringsAsFactors = FALSE,
-                                       header = TRUE)
-  
-datalist_ED_pilot <- lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"),
-                                       pattern = "*_ED.*csv", full.names = TRUE),
-                                       read.csv, stringsAsFactors = FALSE,
-                                       header = TRUE)
-
-# new empty frame to store files into
-data_ER_pilot <- data.frame(ID = character(), block = character(),
-                            arousal = double(), effort = double(),
-                            trigger = double(), trigger_reg = double())
-
-data_ED_pilot <- data.frame(ID = character(), step = double(),
-                            choice = character(), LBvalue = double(),
-                            LBlevel = double(), RBvalue = double(),
-                            RBlevel = double())
-
-data_choice_pilot <- data.frame(ID = character(), choice = double())
-
-# store arousal and effort ratings in data_ER frame
-for (i in seq_len(length(datalist_ER_pilot))) {
-    tmp <- data.frame(datalist_ER_pilot[[i]][["participant"]],
-                     datalist_ER_pilot[[i]][["instr_1"]],
-                     datalist_ER_pilot[[i]][["slider_arousal.response"]],
-                     datalist_ER_pilot[[i]][["slider_effort.response"]],
-                     datalist_ER_pilot[[i]][["TriggerBlockView"]],
-                     datalist_ER_pilot[[i]][["TriggerBlockReg"]])
-    colnames(tmp) <- names(data_ER_pilot)
-    tmp <- tmp[(!is.na(tmp$arousal)), ]
-    
-    data_ER_pilot <- rbind(tmp, data_ER_pilot)
-   }
-
[…]

### 2023-01-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
updated workspace load

@@
 # load workspace variables from analyses_ERED.R script
-load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
+base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
+base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
 

### 2023-01-16 06_Paper/COG-ED/Stage 1/Manuscript.Rmd
move files into Stage 1 folder

--- 2022-06-26 06_Paper/COG-ED/Manuscript_rev.Rmd
@@
 
-INSERT FIGURE 1 HERE
-<!--
 ```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
@@
 ```
--->
 
@@
 
-INSERT FIGURE 1 HERE
-<!--
 ```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
@@
 
-INSERT DESIGN TABLE HERE
-<!--
 \includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
--->
+
 \newpage
@@
 
-INSERT SUPPLEMENT HERE
-<!--
 \counterwithin{figure}{section}
@@
 ```
--->

### 2023-01-16 06_Paper/COG-ED/Stage 1/Manuscript_rev.tex
move files into Stage 1 folder

--- 2022-06-22 06_Paper/COG-ED/Manuscript_without_supplement.tex
@@
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{../Inkscape Figures/Paradigm_Scheme} \caption{An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
-The grey boxes are the choice options shown to the participant.
-The participant's final reward value of the flexible level is displayed after the first arrow.
-The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice.
-The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.}\label{fig:figure1}
-\end{figure}
+INSERT FIGURE 1 HERE
 
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{../Inkscape Figures/Paradigm_Scheme} \caption{ }\label{fig:figure1appendix}
-\end{figure}
+INSERT FIGURE 1 HERE
 
@@
 
-(Starts on next page)
+INSERT DESIGN TABLE HERE
+\newpage
 
-\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
+\hypertarget{supplement}{%
+\section{Supplement}\label{supplement}}
+
+INSERT SUPPLEMENT HERE
 

### 2023-01-16 06_Paper/COG-ED/Stage 1/Manuscript_without_supplement.Rmd
move files into Stage 1 folder

--- 2023-01-16 06_Paper/COG-ED/Stage 1/Manuscript.Rmd
@@
 \includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
-
-\newpage
-
-# Supplement
-
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\setcounter{section}{19}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-## Results of the pilot study
-
-## Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`
-
-\newpage
-
-## Hypothesis 1b: Reaction time increases with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  hypothesis1b_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
-
-Mental subscale ANOVA:
-
-`r apa_print(hypothesis1c_mental_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`
-
-Mental subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_mental_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Physical subscale ANOVA:
-
-`r apa_print(hypothesis1c_physical_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`
-
-Physical subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_physical_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Time subscale ANOVA:
-
-`r apa_print(hypothesis1c_time_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`
-
-Time subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_time_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Performance subscale ANOVA:
-
-`r apa_print(hypothesis1c_performance_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`
-
-Performance subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_performance_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Effort subscale ANOVA:
-
-`r apa_print(hypothesis1c_effort_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`
-
-Effort subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_effort_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Frustration subscale ANOVA:
-
-`r apa_print(hypothesis1c_frustration_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`
-
-Frustration subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_frustration_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 2a: Subjective values decline with increasing n-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`
-
-Contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis2a_contrasts,
-  caption = "Different contrasts for the rmANOVA comparing subjective values between n-back levels",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
-
-Multi level model:
-
-```{r,echo=FALSE, message=FALSE, warning=FALSE}
-kable(h2b_result.table,
-        caption = "Effects of n-back load level on subjective value controlled 
-    for task performance (d' and reaction time).",
-        booktabs = T,                          # no vertical lines
-        escape = F,                            # correctly print special characters)
-        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
-             escape = F,                    # correctly print special characters
-             threeparttable = T)            # line breaks in the footnote
-```
-The intraclass correlation equals `r format(icc_h2b, digits = 2)`.
-
-The Bayes Factor $BF10$ of the multi level model approached infinity.
-
-The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2b_total_r2[1,2], digits = 2)`.
-
-The effect size is $f^2=$ `r format(h2b_f2, digits = 2)`.
-
-\newpage
-
-## Hypothesis 3a: Participants with high NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with low NFC scores.
-
-ANOVA:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis3a_rmanova,
-  caption = "Main effects and interaction of NFC group and n-back level on subjective values",
-  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H",
-  font_size = "footnotesize"
-)
-```
-
-\newpage
-
-## Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every n-back level than participants with low NFC scores.
-
-ANOVA:
-
-Main effect of the NFC group:
-
-`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, $BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`
-
-Main effect of the n-back level:
-
-`r apa_print(hypothesis3b_model)$full_result$level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`
-
-Interaction effect of NFC group and n-back level:
-
-`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`
-
-Paired contrasts for the main effect of n-back level:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis3b_rmanova,
-  caption = "Main effects and interaction of NFC group and n-back level on NASA-TLX scores",
-  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H",
-  font_size = "footnotesize")
-```

### 2023-01-16 06_Paper/COG-ED/Stage 1/Analysis.R
added Stage 1 subfolder to 'here' paths

@@ -24,7 +24,7 @@
   # install renv by calling install.packages("renv") if necessary
   
   library(renv)
-  source(here("06_Paper","COG-ED", "renv", "activate.R"))
+  source(here("06_Paper","COG-ED", "Stage 1", "renv", "activate.R"))
   
   
   # the required packages are:
@@ -1592,7 +1592,7 @@
   # save the plot as an eps file with high resolution
   
   ggsave(filename = "Figure_4.eps", plot = plot_h3b, device = "eps",
-         path = here("06_Paper","COG-ED","Figures"),
+         path = here("06_Paper","COG-ED","Stage 1","Figures"),
          dpi = "retina", bg = NULL)
   
   # delete temporary data frame

### 2023-01-19 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
Update Analyes_ERED.r

@@ -308,6 +308,7 @@ data_quest <- merge(data_quest, srs_items[,c("set","srs_sum")], by = "set")
 # remove temporary dfs
 
 base::remove(nfc_items, flexer_items, bis11_items, bscs_items, srs_items)
+
 #################### PREPARATION: SUBJECTIVE VALUES ############
 
 # the choice column in df data_ED will contain 1 for the left button and 2 for the right button

### 2023-01-19 06_Paper/COG-ED/Stage 1/Manuscript.tex

--- 2022-06-22 06_Paper/COG-ED/Manuscript_without_supplement.tex
@@
 
+\newpage
+
+\hypertarget{supplement}{%
+\section{Supplement}\label{supplement}}
+
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+\setcounter{section}{19}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\hypertarget{results-of-the-pilot-study}{%
+\subsection{Results of the pilot study}\label{results-of-the-pilot-study}}
+
+\hypertarget{hypothesis-1a-the-signal-detection-measure-d-declines-with-increasing-n-back-level.}{%
+\subsection{Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.}\label{hypothesis-1a-the-signal-detection-measure-d-declines-with-increasing-n-back-level.}}
+
+ANOVA:
+
+\(F(2.30, 32.20) = 0.00\), \(p > .999\), \(\eta_{p}^{2}=\) 2.16e-32, 95\%~CI {[}0.00, 1.00{]}, \(BF10=\) 0.09
+
+\newpage
+
+\hypertarget{hypothesis-1b-reaction-time-increases-with-increasing-n-back-level.}{%
+\subsection{Hypothesis 1b: Reaction time increases with increasing n-back level.}\label{hypothesis-1b-reaction-time-increases-with-increasing-n-back-level.}}
+
+ANOVA:
+
+\(F(2.14, 30.00) = 17.18\), \(p < .001\), \(\eta_{p}^{2}=\) 0.55, 95\%~CI {[}0.33, 1.00{]}, \(BF10=\) 125.61
+
+Paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-1}Paired contrasts for the rmANOVA comparing reaction time between n-back levels}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+1 - 2 & -0.14 & 0.03 & 42.00 & -4.15 & 0.001 & 249.00 & 0.29 & {}[0.11, 1.00]\\
+1 - 3 & -0.24 & 0.03 & 42.00 & -7.00 & 0.000 & 994.00 & 0.54 & {}[0.36, 1.00]\\
+1 - 4 & -0.16 & 0.03 & 42.00 & -4.86 & 0.000 & 27.90 & 0.36 & {}[0.17, 1.00]\\
+2 - 3 & -0.10 & 0.03 & 42.00 & -2.85 & 0.033 & 5.94 & 0.16 & {}[0.03, 1.00]\\
+2 - 4 & -0.02 & 0.03 & 42.00 & -0.72 & 0.891 & 0.32 & 0.01 & {}[0.00, 1.00]\\
+3 - 4 & 0.07 & 0.03 & 42.00 & 2.14 & 0.158 & 4.41 & 0.10 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{hypothesis-1c-ratings-on-all-nasa-tlx-dimensions-increase-with-increasing-n-back-level.}{%
+\subsection{Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.}\label{hypothesis-1c-ratings-on-all-nasa-tlx-dimensions-increase-with-increasing-n-back-level.}}
+
+Mental subscale ANOVA:
+
+\(F(2.08, 27.03) = 69.96\), \(p < .001\), \(\eta_{p}^{2}=\) 0.84, 95\%~CI {[}0.74, 1.00{]}, \(BF10=\) 240,305,851.21
+
+Mental subscale paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-2}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+1 - 2 & -4.43 & 0.80 & 39.00 & -5.53 & <.001 & 1,400.00 & 0.44 & {}[0.25, 1.00]\\
+1 - 3 & -8.43 & 0.80 & 39.00 & -10.50 & <.001 & 35,700.00 & 0.74 & {}[0.62, 1.00]\\
+1 - 4 & -10.80 & 0.80 & 39.00 & -13.50 & <.001 & 190,000.00 & 0.82 & {}[0.74, 1.00]\\
+2 - 3 & -4.00 & 0.80 & 39.00 & -5.00 & <.001 & 373.00 & 0.39 & {}[0.20, 1.00]\\
+2 - 4 & -6.36 & 0.80 & 39.00 & -7.94 & <.001 & 3,330.00 & 0.62 & {}[0.45, 1.00]\\
+3 - 4 & -2.36 & 0.80 & 39.00 & -2.94 & 0.027 & 38.10 & 0.18 & {}[0.04, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+Physical subscale ANOVA:
+
+\(F(1.61, 20.96) = 7.86\), \(p = .005\), \(\eta_{p}^{2}=\) 0.38, 95\%~CI {[}0.10, 1.00{]}, \(BF10=\) 0.34
+
+Physical subscale paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-3}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+1 - 2 & -1.64 & 0.80 & 39.00 & -2.06 & 0.185 & 3.51 & 0.10 & {}[0.00, 1.00]\\
+1 - 3 & -3.07 & 0.80 & 39.00 & -3.85 & 0.002 & 6.50 & 0.28 & {}[0.10, 1.00]\\
+1 - 4 & -3.50 & 0.80 & 39.00 & -4.38 & <.001 & 7.66 & 0.33 & {}[0.14, 1.00]\\
+2 - 3 & -1.43 & 0.80 & 39.00 & -1.79 & 0.294 & 1.79 & 0.08 & {}[0.00, 1.00]\\
+2 - 4 & -1.86 & 0.80 & 39.00 & -2.33 & 0.110 & 2.00 & 0.12 & {}[0.01, 1.00]\\
+3 - 4 & -0.43 & 0.80 & 39.00 & -0.54 & 0.950 & 0.38 & 7.33e-03 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+Time subscale ANOVA:
+
+\(F(2.14, 27.86) = 31.25\), \(p < .001\), \(\eta_{p}^{2}=\) 0.71, 95\%~CI {[}0.53, 1.00{]}, \(BF10=\) 24.80
+
+Time subscale paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+1 - 2 & -1.64 & 0.82 & 39.00 & -2.00 & 0.206 & 11.40 & 0.09 & {}[0.00, 1.00]\\
+1 - 3 & -5.14 & 0.82 & 39.00 & -6.26 & <.001 & 278.00 & 0.50 & {}[0.31, 1.00]\\
+1 - 4 & -7.14 & 0.82 & 39.00 & -8.69 & <.001 & 3,710.00 & 0.66 & {}[0.51, 1.00]\\
+2 - 3 & -3.50 & 0.82 & 39.00 & -4.26 & 0.001 & 38.80 & 0.32 & {}[0.13, 1.00]\\
+2 - 4 & -5.50 & 0.82 & 39.00 & -6.69 & <.001 & 1,060.00 & 0.53 & {}[0.35, 1.00]\\
+3 - 4 & -2.00 & 0.82 & 39.00 & -2.43 & 0.087 & 3.09 & 0.13 & {}[0.01, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+Performance subscale ANOVA:
+
+\(F(2.12, 27.59) = 6.78\), \(p = .004\), \(\eta_{p}^{2}=\) 0.34, 95\%~CI {[}0.09, 1.00{]}, \(BF10=\) 1.82
+
+Performance subscale paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+1 - 2 & 1.50 & 1.10 & 39.00 & 1.37 & 0.526 & 1.00 & 0.05 & {}[0.00, 1.00]\\
+1 - 3 & 3.93 & 1.10 & 39.00 & 3.59 & 0.005 & 33.70 & 0.25 & {}[0.08, 1.00]\\
+1 - 4 & 4.21 & 1.10 & 39.00 & 3.85 & 0.002 & 5.32 & 0.28 & {}[0.10, 1.00]\\
+2 - 3 & 2.43 & 1.10 & 39.00 & 2.22 & 0.136 & 11.00 & 0.11 & {}[0.01, 1.00]\\
+2 - 4 & 2.71 & 1.10 & 39.00 & 2.48 & 0.079 & 1.83 & 0.14 & {}[0.01, 1.00]\\
+3 - 4 & 0.29 & 1.10 & 39.00 & 0.26 & 0.994 & 0.28 & 1.74e-03 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+Effort subscale ANOVA:
+
+\(F(1.57, 20.43) = 28.65\), \(p < .001\), \(\eta_{p}^{2}=\) 0.69, 95\%~CI {[}0.47, 1.00{]}, \(BF10=\) 10,733.57
+
+Effort subscale paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+1 - 2 & -2.71 & 0.96 & 39.00 & -2.84 & 0.035 & 1,020.00 & 0.17 & {}[0.03, 1.00]\\
+1 - 3 & -6.79 & 0.96 & 39.00 & -7.09 & <.001 & 774.00 & 0.56 & {}[0.39, 1.00]\\
+1 - 4 & -7.79 & 0.96 & 39.00 & -8.14 & <.001 & 1,380.00 & 0.63 & {}[0.47, 1.00]\\
+2 - 3 & -4.07 & 0.96 & 39.00 & -4.26 & 0.001 & 55.60 & 0.32 & {}[0.13, 1.00]\\
+2 - 4 & -5.07 & 0.96 & 39.00 & -5.30 & <.001 & 44.60 & 0.42 & {}[0.22, 1.00]\\
+3 - 4 & -1.00 & 0.96 & 39.00 & -1.05 & 0.724 & 0.62 & 0.03 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+Frustration subscale ANOVA:
+
+\(F(2.53, 32.94) = 35.31\), \(p < .001\), \(\eta_{p}^{2}=\) 0.73, 95\%~CI {[}0.58, 1.00{]}, \(BF10=\) 17,679.16
+
+Frustration subscale paired contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels}
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+1 - 2 & -1.57 & 0.91 & 39.00 & -1.73 & 0.323 & 3.52 & 0.07 & {}[0.00, 1.00]\\
+1 - 3 & -5.71 & 0.91 & 39.00 & -6.28 & <.001 & 590.00 & 0.50 & {}[0.32, 1.00]\\
+1 - 4 & -8.36 & 0.91 & 39.00 & -9.19 & <.001 & 27,000.00 & 0.68 & {}[0.54, 1.00]\\
+2 - 3 & -4.14 & 0.91 & 39.00 & -4.56 & <.001 & 71.10 & 0.35 & {}[0.16, 1.00]\\
+2 - 4 & -6.79 & 0.91 & 39.00 & -7.46 & <.001 & 2,660.00 & 0.59 & {}[0.42, 1.00]\\
+3 - 4 & -2.64 & 0.91 & 39.00 & -2.91 & 0.029 & 2.54 & 0.18 & {}[0.03, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{hypothesis-2a-subjective-values-decline-with-increasing-n-back-level.}{%
+\subsection{Hypothesis 2a: Subjective values decline with increasing n-back level.}\label{hypothesis-2a-subjective-values-decline-with-increasing-n-back-level.}}
+
+ANOVA:
+
+\(F(1.80, 25.26) = 7.80\), \(p = .003\), \(\eta_{p}^{2}=\) 0.36, 95\%~CI {[}0.10, 1.00{]}
+
+Contrasts:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-8}Different contrasts for the rmANOVA comparing subjective values between n-back levels}
+
+\begin{tabular}{llllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+Declining Linear & 1.06 & 0.22 & 42.00 & 4.78 & <.001 & 0.35 & {}[0.17, 1.00]\\
+Ascending Quadratic & 0.07 & 0.10 & 42.00 & 0.72 & 0.475 & 0.01 & {}[0.00, 1.00]\\
+Declining Logistic & 1.16 & 0.25 & 42.00 & 4.56 & <.001 & 0.33 & {}[0.15, 1.00]\\
+Positively Skewed Normal & 0.66 & 0.16 & 42.00 & 4.21 & <.001 & 0.30 & {}[0.12, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{hypothesis-2b-subjective-values-decline-with-increasing-n-back-level-even-after-controlling-for-declining-task-performance-measured-by-signal-detection-d-and-reaction-time.}{%
+\subsection{Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d' and reaction time.}\label{hypothesis-2b-subjective-values-decline-with-increasing-n-back-level-even-after-controlling-for-declining-task-performance-measured-by-signal-detection-d-and-reaction-time.}}
+
+Multi level model:
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-9}Effects of n-back load level on subjective value controlled 
+    for task performance (d' and reaction time).}
+\centering
+\begin{threeparttable}
+\begin{tabular}[t]{lrrrr}
+\toprule
+Parameter & Beta & $SE$ & $p$-value & Random Effects (SD)\\
+\midrule
+\cellcolor{gray!6}{Intercept} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{0.03} & \cellcolor{gray!6}{<.001***} & \cellcolor{gray!6}{0.09}\\
+$N$-back level & -0.12 & 0.04 & 0.003** & 0.12\\
+\cellcolor{gray!6}{d'} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{0.238} & \cellcolor{gray!6}{}\\
+median RT & 0.25 & 0.19 & 0.21 & \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item \textit{Note: } 
+\item NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+The intraclass correlation equals 0.015.
+
+The Bayes Factor \(BF10\) of the multi level model approached infinity.
+
+The conditional \(R^2\) of the model describes the proportion of variance explained by both fixed and random effects, and is \(R^2=\) 0.74.
+
+The effect size is \(f^2=\) -0.075.
+
+\newpage
+
+\hypertarget{hypothesis-3a-participants-with-high-nfc-scores-have-higher-subjective-values-for-2--and-3-back-but-lower-subjective-values-for-1-back-than-participants-with-low-nfc-scores.}{%
+\subsection{Hypothesis 3a: Participants with high NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with low NFC scores.}\label{hypothesis-3a-participants-with-high-nfc-scores-have-higher-subjective-values-for-2--and-3-back-but-lower-subjective-values-for-1-back-than-participants-with-low-nfc-scores.}}
+
+ANOVA:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-10}Main effects and interaction of NFC group and n-back level on subjective values}
+
+\footnotesize{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{Sum Sq} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{error Sum Sq} & \multicolumn{1}{c}{error $df$} & \multicolumn{1}{c}{$F$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+Intercept & 0.52 & 1.00 & 0.71 & 13.00 & 9.41 & 0.009 & 0.42 & {}[0.09, 1.00]\\
+NFC group & 0.00 & 1.00 & 0.71 & 13.00 & 0.01 & 0.931 & 5.96e-04 & {}[0.00, 1.00]\\
+n-back level & 0.04 & 2.00 & 1.66 & 26.00 & 0.32 & 0.726 & 0.02 & {}[0.00, 1.00]\\
+NFC group x n-back level & 0.02 & 2.00 & 1.66 & 26.00 & 0.19 & 0.829 & 0.01 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{hypothesis-3b-participants-with-high-nfc-scores-have-lower-nasa-tlx-scores-in-every-n-back-level-than-participants-with-low-nfc-scores.}{%
+\subsection{Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every n-back level than participants with low NFC scores.}\label{hypothesis-3b-participants-with-high-nfc-scores-have-lower-nasa-tlx-scores-in-every-n-back-level-than-participants-with-low-nfc-scores.}}
+
+ANOVA:
+
+Main effect of the NFC group:
+
+\(F(1, 12) = 7.57\), \(p = .018\), \(\hat{\eta}^2_G = .348\), 90\% CI \([.030, .610]\), \(BF10=\) 88
+
+Main effect of the n-back level:
+
+\(F(1.56, 18.71) = 68.33\), \(p < .001\), \(\hat{\eta}^2_G = .466\), 90\% CI \([.239, .603]\), \(BF10=\) 1000
+
+Interaction effect of NFC group and n-back level:
+
+\(F(1.56, 18.71) = 0.84\), \(p = .422\), \(\hat{\eta}^2_G = .011\), 90\% CI \([.000, .008]\), \(BF10=\) 3398060
+
+Paired contrasts for the main effect of n-back level:
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-11}Main effects and interaction of NFC group and n-back level on NASA-TLX scores}
+
+\footnotesize{
+
+\begin{tabular}{lllllllll}
+\toprule
+ & \multicolumn{1}{c}{Sum Sq} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{error Sum Sq} & \multicolumn{1}{c}{error $df$} & \multicolumn{1}{c}{$F$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+Intercept & 5,770.00 & 1.00 & 241.00 & 12.00 & 287.00 & <.001 & 0.96 & {}[0.91, 1.00]\\
+NFC group & 152.00 & 1.00 & 241.00 & 12.00 & 7.57 & 0.018 & 0.39 & {}[0.05, 1.00]\\
+n-back level & 249.00 & 3.00 & 43.70 & 36.00 & 68.30 & <.001 & 0.85 & {}[0.77, 1.00]\\
+NFC group x n-back level & 3.04 & 3.00 & 43.70 & 36.00 & 0.84 & 0.483 & 0.07 & {}[0.00, 1.00]\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \end{document}

### 2023-01-19 06_Paper/COG-ED/Stage 2/Manuscript_rev.Rmd

--- 2022-06-26 06_Paper/COG-ED/Manuscript_rev.Rmd
@@
   Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
-  We aim to replicate the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
+  We replicated the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
 
@@
 
-  load(here("06_Paper","COG-ED","Workspace.RData"))
+  load(here("06_Paper","COG-ED","Stage 1","Workspace.RData"))
 
@@
 Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
-In the present study, we will validate the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
-Additionally, we will compare the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
-The full results of the latter will be published in a second Registered Report[@ScheffelZerna2022].
-The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate [@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
+In the present study, we validated the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
+Additionally, we compared the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
+The full results of the latter are published in a second Registered Report[@ScheffelZerna2022].
+The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate[@Crawford2021], but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.
 
 Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
-As a manipulation check, we hypothesize that with increasing *n*-back level the (1a) the signal detection parameter *d'* declines, while (1b) reaction time and (1c) perceived task load increase.
-Regarding the associations of task load and effort discounting we hypothesize that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
-And finally, we hypothesize that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
+As a manipulation check, we hypothesized that with increasing *n*-back level the (1a) the signal detection parameter *d'* declines, while (1b) reaction time and (1c) perceived task load increase.
+Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
+And finally, we hypothesized that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
 Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.
@@
 The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number SR-EK-50012022).
-Prior to testing, written informed consent will be obtained.
-Participants will receive 30€ in total or course credit for participation.
+Prior to testing, written informed consent was obtained.
+Participants received 24€ in total or course credit for participation.
 
@@
 Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
-This will be determined by presenting each possible pair of levels on screen with the question "Would you prefer 1\ € for level A or 1\ € for level B?".
+This is determined by presenting each possible pair of levels on screen with the question "Would you prefer 1\ € for level A or 1\ € for level B?".
 Participants respond by clicking the respective on-screen button.
-Each pair will be presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
+Each pair is presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
 For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1\ € and is changed in every iteration.
@@
 Then, the effort discounting sensu Westbrook et al.[-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
-The order in which the pairs are presented will be fully randomized, and each pair will go through all iteration steps of adding/subtracting 0.50\ €, 0.25\ €, 0.13\ €, 0.06\ €, 0.03\ €, 0.02\ € to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
+The order in which the pairs are presented is fully randomized, and each pair goes through all iteration steps of adding/subtracting 0.50\ €, 0.25\ €, 0.13\ €, 0.06\ €, 0.03\ €, 0.02\ € to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
 This procedure allows to compute SVs based on actual individual preference instead of objective task load.
@@
 ### Study procedure
-Healthy participants aged 18 to 30\ years will be recruited using the software *ORSEE*[@Greiner2015].
-Participants will complete the personality questionnaires online and then visit the lab for two sessions one week apart.
-NFC will be assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
-Responses to each item (e.g., "Thinking is not my idea of fun", recoded) will be recorded on a 7-point Likert scale.
+Healthy participants aged 18 to 30\ years were recruited using the software *ORSEE*[@Greiner2015].
+Participants completed the personality questionnaires online and then visited the lab for two sessions one week apart.
+NFC was assessed using the 16-item short form of the Need for Cognition Scale [@Cacioppo1984; @Bless1994].
+Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale.
 The NFC scale shows comparably high internal consistency (Cronbach's $\alpha>.80$) [@Bless1994; @Fleischhauer2010].
-Several other personality questionnaires will be used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
+Several other personality questionnaires were used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
 A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CAD).
-In the first session, participants provide informed consent and demographic data before completing the computer-based paradigm.
-The paradigm starts with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels are referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
-To assess perceived task load, we will use the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-At the end of each level, participants fill out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this *n*-back level.
-After the *n*-back task, participants complete the CAD paradigm on screen and are instructed to do so as realistically as possible, even though the displayed rewards will not be paid out on top of their compensation.
-They are told that one of their choices will be randomly picked for the final run of *n*-back, the data of which will not be analyzed as it only serves to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
-After the CAD paradigm, participants will fill out a short questionnaire on the tablet, indicating whether they have adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
-The second session consists of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
-The paradigm follows the same structure of task and effort discounting procedure, but participants can decide which strategy they want to reapply in the last block.
-Study data will be collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].
+In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
+The paradigm started with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
+To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
+At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this *n*-back level.
+After the *n*-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
+They were told that one of their choices would be randomly picked for the final run of *n*-back, the data of which was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
+After the CAD paradigm, participants filled out a short questionnaire on the tablet, indicating whether they adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
+The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
+The paradigm followed the same structure of task and effort discounting procedure, but participants could decide which strategy they wanted to reapply in the last block.
+Study data was collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].
 
@@
 However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
-To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aim to collect about $50\%$ more data sets than necessary, $N=120$ in total.
+To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aimed to collect about $50\%$ more data sets than necessary, $N=120$ in total.
 
@@
 
-Data collection and analysis will not be performed blind to the conditions of the experiments.
-We will exclude the data of a participant from all analyses, if the participant states that they did not follow the instructions, if the investigator notes that the participant misunderstood the instructions, or if the participant withdraws their consent.
-No data will be replaced.
-The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
-Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
-Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
-Error- and post-error trials will be excluded, because RT in the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
-To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].
+Data collection and analysis were not performed blind to the conditions of the experiments.
+We excluded the data of a participant from all analyses, if the participant stated that they did not follow the instructions, if the investigator noted that the participant misunderstood the instructions, or if the participant withdrew their consent.
+No data was replaced.
+The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
+Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
+Aggregated RT values were described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
+Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
+To test our hypotheses, we performed a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].
 
 *Manipulation check.*
-Declining performance will be investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
-Another rmANOVA with six paired contrasts will be computed to compare the median RT between two levels of 1- to 4-back at a time.
-To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.
+Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
+Another rmANOVA with six paired contrasts was computed to compare the median RT between two levels of 1- to 4-back at a time.
+To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.
 
 *Subjective values.*
-For each effort discounting round, the SV of the fixed level will be calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
-This yields an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level is 1.
+For each effort discounting round, the SV of the fixed level was calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
+This yielded an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level was 1.
 The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
-All SVs of each level will be averaged to compute one "global" SV for each level.
-An rmANOVA with four different contrasts will be computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
-Depending on whether the linear or one of the other three contrasts fits the curve best, we will apply a linear or nonlinear multi-level model in the next step, respectively.
+All SVs of each level were averaged to compute one "global" SV for each level.
+An rmANOVA with four different contrasts were computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
+Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.
 
-To determine the influence of task performance on the association of SVs and *n*-back level, we will perform MLM. 
-We will apply restricted maximum likelihood (REML) to fit the model.
-As an effect size measure for random effects we will firstly calculate the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we will estimate a random slopes model of n-back level (level 1, fixed and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
+To determine the influence of task performance on the association of SVs and *n*-back level, we performed MLM. 
+We applied restricted maximum likelihood (REML) to fit the model.
+As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
+Second, we estimated a random slopes model of n-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
 As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
-We control for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
+We controlled for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
 $$
@@
 $$
-Level-1-predictors will be centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
+Level-1-predictors were centered within cluster as recommended by Enders & Tofighi[-@Enders2007]. 
 By this, the model yields interpretable parameter estimates. 
 If necessary, we will adjusted the optimization algorithm to improve model fit. 
-We will visually inspect the residuals of the model for evidence to perform model criticism. 
-This will be done by excluding all data points with absolute standardized residuals above 3 SD. 
-As effect size measures, we will calculate pseudo *R²* for our model and *f²* to estimate the effect of n-back level according to Lorah[-@Lorah2018].
+We visually inspected the residuals of the model for evidence to perform model criticism. 
+This was done by excluding all data points with absolute standardized residuals above 3 SD. 
+As effect size measures, we calculated pseudo *R²* for our model and *f²* to estimate the effect of n-back level according to Lorah[-@Lorah2018].
+To ensure the validity of the association of SVs and *n*-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
+The rmANOVA was run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
+The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.
+The specification curve analysis was linked to the MLM in the initial submission, and was assigned to hypothesis 3a during the review process and in the Stage 1 report.
+Afterwards, we noticed that 3a does not contain any RT data, so the specification curve analysis was reassigned to the MLM with the agreement of the editor.
 
-The association of SVs and NFC will be examined with an rmANOVA.
-We will subtract the SV of 1- from 2-back, 2- from 3-back, and 3- from 4-back per participant, yielding three SV difference scores per participant.
-The sample will be divided into participants with low and high NFC using a median split.
-We will then compute an rmANOVA with the within-factor n-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
-Post-hoc tests will be computed depending on which effect reaches significance at $p<.01$.
-To ensure the validity of this association, we will conduct a specification curve analysis[@Simonsohn2020], which will include 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
-The rmANOVA will be run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
-The ratio of pipelines that lead to significant versus non-significant effects will provide an indication of how robust the effect actually is.
+The association of SVs and NFC was examined with an rmANOVA.
+We subtracted the SV of 1- from 2-back and 2- from 3-back, yielding two SV difference scores per participant.
+The sample was divided into participants with low and high NFC using a median split.
+We then computed an rmANOVA with the within-factor n-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
+Post-hoc tests were computed depending on which effect reached significance at $p<.01$.
 
-The association of subjective task load with NFC will be examined similarly.
-We will calculate NASA-TLX sum scores per participant per level and compute an rmANOVA with the within-factor n-back level and the between-factor NFC group, and apply post-hoc tests based on which effect reaches significance at $p<.01$.
-And the association of subjective aversiveness of the task with NFC will be examined with difference scores as well, since we expect this curve to mirror the SV curve, i.e.
+The association of subjective task load with NFC was examined similarly.
+We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor n-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
+And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e.
 as the SV rises, the aversiveness declines, and vice versa.
-We will subtract the aversiveness ratings of 1- from 2-back, 2- from 3-back, and 3- from 4-back per participant, yielding three aversiveness difference scores per participant.
-Then, we will compute an rmANOVA with the within-factor n-back level and the between-factor NFC group, and apply post-hoc tests based on which effect reaches significance at $p<.01$.
+We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
+Then, we computed an rmANOVA with the within-factor n-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
 
-The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *ttestBF*.
-We will consider a $BF10$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF10$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].
+The results of each analysis was assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *ttestBF*.
+We considered a $BF10$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF10$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].
 
@@
 INSERT FIGURE 1 HERE
+
 <!--
@@
 # Design Table {#DesignTableSection}
-
-(Starts on next page)
 

### 2023-01-25 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
some n were not italic

--- 2023-01-19 06_Paper/COG-ED/Stage 2/Manuscript_rev.Rmd
@@
 
-keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
+keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, *n*-back"
 wordcount         : "~ 4,300"
@@
 <!--
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an *n*-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we estimated a random slopes model of n-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
-As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher n-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
+Second, we estimated a random slopes model of *n*-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
+As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher *n*-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
 We controlled for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
@@
 This was done by excluding all data points with absolute standardized residuals above 3 SD. 
-As effect size measures, we calculated pseudo *R²* for our model and *f²* to estimate the effect of n-back level according to Lorah[-@Lorah2018].
+As effect size measures, we calculated pseudo *R²* for our model and *f²* to estimate the effect of *n*-back level according to Lorah[-@Lorah2018].
 To ensure the validity of the association of SVs and *n*-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
@@
 The sample was divided into participants with low and high NFC using a median split.
-We then computed an rmANOVA with the within-factor n-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
+We then computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
 Post-hoc tests were computed depending on which effect reached significance at $p<.01$.
@@
 The association of subjective task load with NFC was examined similarly.
-We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor n-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
+We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
 And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e.
@@
 We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
-Then, we computed an rmANOVA with the within-factor n-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
+Then, we computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
 
@@
 
-*Figure 1.* An example for subjective values for an n-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+*Figure 1.* An example for subjective values for an *n*-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 
-## Hypothesis 1a: The signal detection measure d' declines with increasing n-back level.
+## Hypothesis 1a: The signal detection measure d' declines with increasing *n*-back level.
 
@@
 
-## Hypothesis 1b: Reaction time increases with increasing n-back level.
+## Hypothesis 1b: Reaction time increases with increasing *n*-back level.
 
@@
   hypothesis1b_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing reaction time between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing reaction time between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.
+## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing *n*-back level.
 
@@
   hypothesis1c_mental_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
   hypothesis1c_physical_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
   hypothesis1c_time_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
   hypothesis1c_performance_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
   hypothesis1c_effort_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
   hypothesis1c_frustration_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between n-back levels",
-  note = "The column Contrast contains the $n$ of the n-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-## Hypothesis 2a: Subjective values decline with increasing n-back level.
+## Hypothesis 2a: Subjective values decline with increasing *n*-back level.
 
@@
   hypothesis2a_contrasts,
-  caption = "Different contrasts for the rmANOVA comparing subjective values between n-back levels",
+  caption = "Different contrasts for the rmANOVA comparing subjective values between *n*-back levels",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
 
-## Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
+## Hypothesis 2b: Subjective values decline with increasing *n*-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
 
@@
 kable(h2b_result.table,
-        caption = "Effects of n-back load level on subjective value controlled 
+        caption = "Effects of *n*-back load level on subjective value controlled 
     for task performance (d' and reaction time).",
@@
   hypothesis3a_rmanova,
-  caption = "Main effects and interaction of NFC group and n-back level on subjective values",
+  caption = "Main effects and interaction of NFC group and *n*-back level on subjective values",
   note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
 
-## Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every n-back level than participants with low NFC scores.
+## Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every *n*-back level than participants with low NFC scores.
 
@@
 
-Main effect of the n-back level:
+Main effect of the *n*-back level:
 
@@
 
-Interaction effect of NFC group and n-back level:
+Interaction effect of NFC group and *n*-back level:
 
@@
 
-Paired contrasts for the main effect of n-back level:
+Paired contrasts for the main effect of *n*-back level:
 
@@
   hypothesis3b_rmanova,
-  caption = "Main effects and interaction of NFC group and n-back level on NASA-TLX scores",
+  caption = "Main effects and interaction of NFC group and *n*-back level on NASA-TLX scores",
   note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",

### 2023-02-08 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
started results part

@@
 
-The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at [github.com/ChScheffel/CAD](https://github.com/ChScheffel/CAD).
+The paradigm code as well as the R Markdown file used to analyze the data and write this document are available at [github.com/ChScheffel/CAD](https://github.com/ChScheffel/CAD).
+
+# Results
+
+Data was collected between the 16th of August 2022 and the 3rd of February 2023.
+Of the $N=$ participants who filled out the online questionnaires, $n=$ came to the first lab session.
+Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
+Our final data set therefore included $N=$ participants.
 

### 2023-02-08 06_Paper/COG-ED/Stage 2/Analysis.R
added calls to MetBrewer and ggprism

@@ -1468,7 +1468,7 @@ raincloudplots::raincloud_2x2_repmes(data_2x2 = plot_h3a_data,
                                  spread_x_ticks = FALSE) +
   xlab("n-back levels") + 
   ylab("Difference in subjective values") +
-  scale_fill_manual(values = met.brewer("Hiroshige", 2), labels = c("NFC above median", "NFC below median")) +
+  scale_fill_manual(values = MetBrewer::met.brewer("Hiroshige", 2), labels = c("NFC above median", "NFC below median")) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
   scale_x_continuous(breaks=c(1,2), labels=c("1-2", "2-3"), limits=c(0, 3))
 
@@ -1609,12 +1609,12 @@ plot_h3b_pvalue <- data.frame(
 
 plot_h3b <- ggplot(h3b_data, aes(x = level, y = ntlx, fill = nfcmedian)) +
   geom_violin(color = NA) +
-  scale_fill_manual(values = met.brewer("Homer2", 2), labels = c("NFC above median", "NFC below median")) +
+  scale_fill_manual(values = MetBrewer::met.brewer("Homer2", 2), labels = c("NFC above median", "NFC below median")) +
   labs(x = "n-back levels", y = "NASA-TLX sum score") +
   geom_boxplot(width = 0.1, position = position_dodge(0.9)) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
   scale_x_discrete(guide = "prism_bracket") +
-  add_pvalue(plot_h3b_pvalue, tip.length = 0)
+  ggprism::add_pvalue(plot_h3b_pvalue, tip.length = 0)
 
 # save the plot as an eps file with high resolution
 

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
corrected missing data

@@ -203,6 +203,7 @@ data_survey <- as.data.frame(data_survey)
 # T14G09 F14A01
 
 data_ER <- data_ER[!data_ER$ID == "T14G09",]
+data_choice <- data_choice[!data_choice$ID == "T14G09",]
 
 data_ED <- data_ED[!data_ED$ID == "T14G09",]
 
@@ -1010,8 +1011,8 @@ FigSubjEffort <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort, fill = 
 #   https://quantdev.ssri.psu.edu/tutorials/r-bootcamp-introduction-multilevel-model-and-interactions
 
 # build new df for MLM
-data_MLM <- data_EMG %>%
-  subset(data_EMG$block != "2_view_neg" & data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
+data_MLM <- data_EMG.new %>%
+  subset(data_EMG.new$block != "2_view_neg" & data_EMG.new$block != "1_view_neu" & data_EMG.new$block != "6_choice")
 
 # drop unnecessary columns
 data_MLM$trigger <- NULL

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
Create Results.Rmd

--- 2022-08-09 06_Paper/ER-ED/ERED_Stage2/method.Rmd
@@
 
-```{r stimvalues, echo = FALSE}
-# import excel list with neutral and negative pictures
-# lists contain arousal and valence values of each picture
-stim_negative <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "negative.xlsx")), range = cell_cols("A:D"))
-
-stim_neutral <- readxl::read_xlsx(file.path(here("01_Paradigms", "ER-ED", "ER_ED", "Stimuli", "neutral.xlsx")), range = cell_rows(1:21))
-```
-
-# 2. Method
-
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study[@Simmons2012].
-The paradigm was written and presented using *PsychoPy*[@Peirce2019].
-We used *R* with *R Studio*[@RCore2021; @RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CAD.
-A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CAD).
-
-## 2.1 Ethics information
-
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022). 
-Prior to testing, written informed consent was obtained.
-Participants received 24 € in total or course credit for participation.
-
-## 2.2 Pilot data
-
-The newly developed ER paradigm was tested in a pilot study with $N=`r nrow(data_quest_pilot)`$ participants (`r length(which(data_quest_pilot$gender == 2))` female; age: $M = `r papaja::printnum(mean(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_quest_pilot[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
-Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
-However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
-Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the *corrugator* and *levator* compared to active viewing of negative pictures.
-In accordance with our previous study[@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
-All results are detailed in the [Supplementary Material](#SupplementaryMaterial), figures S1 to S7 and table S2 to S8.
-
-## 2.3 Design
-
-Young healthy participants (aged 18 to 30 years) were recruited using the software *ORSEE*[@Greiner2015] at the Technische Universität Dresden.
-Participants were excluded from participation if they do not fluently speak German, had current or a history of psychological disorders or neurological trauma, or reported to take medication.
-Participants were invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-The study consisted of two lab sessions, which took place in a shielded cabin with constant lighting.
-Before each session, participants received information about the respective experimental procedure and provided informed consent.
-In the first session participants filled out a demographic questionnaire and completed an *n*-back task with the levels one to four.
-Then, they completed an effort discounting (ED) procedure regarding the *n*-back levels on screen, followed by a random repetition of one *n*-back level [@ZernaScheffel2022].
-The second session took place exactly one week after session one.
-Participants provided informed consent and received written instructions on the ER paradigm and ER strategies that they should apply.
-A brief training ensured that all participants were able to implement the ER strategies.
-Next, electrodes to measure facial EMG were attached and the ER task was conducted, followed by an ED procedure regarding the ER strategies.
-After that, participants chose one ER strategy to repeat one more time.
-Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden[@Harris2009; @Harris2019].
-
-### 2.3.1 Psychometric measures
-
-The online survey contained a number of questionnaires. 
-In the focus of the current project was the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
-It assesses flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
-The items were rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".
-
-Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
-General psychological well-being was assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] was used.
-Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
-Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] was used.
-To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
-Attentional control were assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
-For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).
-
-### 2.3.2 Emotion regulation paradigm
-
-The ER paradigm consisted of three parts that will be described in the following.
-
-*Part one: ER task.* <br> Part one was a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group[@Scheffel2021].
-Participants were told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
-Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
-During this block, 20 neutral pictures were presented.
-Participants were asked to "actively view all pictures and permit all emotions that may arise." 
-In the second block, participants actively viewed negative pictures.
-During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
-In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
-Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants were told to "suppress their emotional facial expression." 
-They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants were instructed not to suppress their thoughts or change their facial expression to the opposite[@Scheffel2021].
-All participants received written instruction and completed a training session.
-After the training session, participants were asked about their applied ER strategies to avoid misapplication.
-The order of the three regulation blocks (distraction, distancing, and suppression) were randomized between participants.
-Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
-Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
-It was followed by neutral or negative pictures for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the regulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.
-
-*Part two: ER effort discounting.* <br> In the second part, ER effort discounting took place.
-The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.[-@Westbrook2013] with a major change.
-We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.
-distancing, distraction vs.
-suppression, and distancing vs.
-suppression), each of the two strategies were presented with a monetary reward.
-Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
-They decided by clicking the on-screen button of the respective option.
-Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
-For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1 €, the other strategy was assigned the fixed value of 2 €.
-After this, comparisons between strategies followed the original COG-ED paradigm[@Westbrook2013].
-Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
-The adjustment started at 0.50 € and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
-If a participant always chose the strategy with the fixed 2 € reward, the other strategy's last value on display was 1.97 €, if they always choose the lower strategy, its last value was 0.03 €.
-The sixth adjustment of 0.02 € was done during data analysis, based on the participants' decision in the last display of the pairing.
-Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.
-
-*Part three: ER choice.* <br> After the discounting part, participants chose which one of the three ER strategies (distraction, distancing or suppression) they wanted to re-apply.
-Importantly, there was no further instruction on what basis they should make their decision.
-Participants should make their decision freely, according to criteria they consider important for themselves.
-However, participants were asked to state the reasons for the decision afterwards in RedCap using a free text field.
-As soon as they have decided, they saw the respective instruction and the block with another 20 negative pictures started.
-
-```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm.
-Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
-After, the discounting procedure took place.
-All three regulation strategies were compared pairwise.
-Before the last block, participants could decide which regulation strategy they wanted to reapply.
-Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
-include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
-```
-
-### 2.3.3 Stimuli
-
-Pictures that were used in the paradigm were selected from the Emotional Picture Set (EmoPicS) [@Wessa2010] and the International Affective Picture System (IAPS)[@Lang2008].
-The 20 neutral pictures (Valence (V): *M* $\pm$ *SD* = `r round(mean(stim_neutral$valence), digits = 2)` $\pm$ `r round(sd(stim_neutral$valence), digits = 2)`; Arousal (A): *M* $\pm$ *SD* = `r round(mean(stim_neutral$arousal), digits = 2)` $\pm$ `r round(sd(stim_neutral$arousal), digits = 2)`) depicted content related to the categories persons, objects, and scenes.
-Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
-An evolutionary algorithm [@Yu2010] was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 1]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 1]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 1]), digits = 2)`; set two: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 2]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 2]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 2]), digits = 2)`; set three: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 3]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 3]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 3]), digits = 2)`; set four: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 4]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 4]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 4]), digits = 2)`; set five: V: *M* $\pm$ *SD* = `r round(mean(stim_negative$valence[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$valence[stim_negative$set == 5]), digits = 2)`, A: *M* $\pm$ *SD* = `r round(mean(stim_negative$arousal[stim_negative$set == 5]), digits = 2)` $\pm$ `r round(sd(stim_negative$arousal[stim_negative$set == 5]), digits = 2)`).
-A complete list of all pictures and their classification into sets can be found in supplementary material table S1.
-The five sets of negative pictures were assigned randomly to the blocks.
-
-### 2.3.4 Facial electromyography
-
-Bipolar facial electromyography (EMG) were measured for *corrugator supercilii* and *levator labii* as indices of affective valence[@Bradley2000], similar to previous work by our group[@Gaertner2021].
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) were placed over each left muscle according to the guidelines of Fridlund and Cacioppo[@Fridlund1986].
-The ground electrode was placed over the left *Mastoid*.
-Before electrode placement, the skin was abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
-Raw signals were amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
-Impedance level were kept below 10 $k\Omega$. 
-Data were sampled at 1000 Hz, filtered, rectified and integrated. 
-A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter was applied to both signals.
-*Corrugator* and *levator* EMG was analyzed during the 6 s of picture presentation.
-EMG data were baseline-corrected using a time window of 2 s prior to stimulus onset [@Bradley2000]. 
-Last, the sampling rate was changed to 100 Hz, and EMG data were averaged for each condition and each participant.
-
-## 2.4 Sampling plan
-
-Sample size calculation was done using *G\*Power*[@Faul2007; @Faul2009].
-In a meta-analysis of Zaehringer and colleagues[-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported:
-To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of at least $N=85$ have to be analyzed.
-Power analyses of all other hypotheses yielded smaller sample sizes.
-However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aimed to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
-Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
-
-## 2.5 Analysis plan
-
-Data collection and analysis were not performed blind to the conditions of the experiments.
-Data of whole participants were excluded from analysis if participants withdraw their consent or they stated that they did not follow experimental instructions.
-EMG data of subjects were excluded from analysis if errors occured during recording.
-No further data exclusions were planned.
-The level of significance was set to $\alpha=.05$.
-For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) were conducted and estimated marginal means were computed using the *afex* package[@Singmann2021].
-Greenhouse-Geisser-corrected degrees of freedom and associated $p$-values were reported when the assumption of sphericity was violated.
-If the within-subjects factor of interest was significant, pairwise contrasts were calculated using Bonferroni adjustment for multiple testing.
-Proportion of explained variance $\eta_{p}^{2}$ was reported as a measure of effect size.
-
-*Effect of valence on arousal and facial EMG.*<br> 
-To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted.
-To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted for EMG *corrugator* and *levator* activity.
-
-*Effects of emotion regulation on arousal, facial EMG and effort.* <br> 
-To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA  with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings was conducted.
-To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG *corrugator* and *levator* activity was conducted.
-To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings was conducted.
-
-*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.02 € was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2 €.
-Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
-The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
-The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.
-
-To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the $lmerTest$ package[@Kuznetsova2017].
-First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
-Restricted maximum likelihood (REML) was applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (*corrugator* and *levator* activity) as level-1-predictors was specified.
-$$
-\begin{split}
-SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
-\end{split}
-$$ 
-Level-1-predictors were centered within cluster[@Enders2007].
-Residuals of the final model were inspected visually.
-Intraclass correlation coefficient (ICC), $\rho$, was reported for each model (null model, as well as full model).
-The presented MLM followed the conceptualization of Zerna, Scheffel, et al.[@ZernaScheffel2022]
-
-To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice was computed.
-Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.
-
-The association between flexible ER and SVs of ER strategies (H7b) was investigated with a linear regression using the individual $intercept$ and $slope$ of each participants' SVs to predict their FlexER score.
-To this end, for each participant, SVs were sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
-The resulting $intercept$ informs about the extent to which an individual considers any or all of the ER strategies as useful for regulation their emotion, while the $slope$ informs about the flexibility in the use of emotion regulation strategies.
-The individual intercepts and slopes were entered as predictors in a regression model with the FlexER score as dependent variable. 
-A positive association with the predictor $intercept$ would indicate that overall higher SVs attached to ER strategies predicts higher scores on the FlexER scale. 
-A positive association with the predictor $slope$ would indicate that less negative slopes, i.e., a smaller preference for a given ER strategy, would be associated with a higher score of the FlexER scale.
-
-The influence of personality traits on SVs were investigated exploratorily.
-Therefore, the MLM specified above was extended by the level-2-predictors NFC and self-control.
-
-For each result of the analyses, both $p$-values and Bayes factors $BF10$, calculated using the *BayesFactor* package[@Morey2021], were reported. 
-Bayes factors were calculated using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF*.
-
-## Data availability
-
-The data of this study can be downloaded from [osf.io/vnj8x/](https://osf.io/vnj8x/).
-
-## Code availability
-
-The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CAD).
+# 3. Method

### 2023-02-13 06_Paper/COG-ED/Stage 2/Analysis.R
created plots for H3a

@@ -1430,38 +1430,52 @@ hypothesis3a_contrasts_nlevel <- as.data.frame(pairs(hypothesis3a_emm_nlevel))
 # get Bayes factors
 
 hypothesis3a_BF_nlevel <- BayesFactor::anovaBF(formula = svdiff ~ nlevels * nfcmedian, data = h3a_data, progress = FALSE)
-#hypothesis3a_contrasts_nlevel$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = h3a_data$svdiff[h3a_data$nlevels == "1-2"], y = h3a_data$svdiff[h3a_data$nlevels == "2-3"],
-#                                                                                    progress = FALSE, paired = TRUE))$bf)
+hypothesis3a_contrasts_nlevel$BF10 <- extractBF(hypothesis3a_BF_nlevel[1])$bf
 
 # get effect size
 
-#hypothesis3a_contrasts_nlevel <- cbind(hypothesis3a_contrasts_nlevel,
-#                                    format(effectsize::t_to_eta2(t = hypothesis3a_contrasts_nlevel$t.ratio,
-#                                                                 df_error = hypothesis3a_contrasts_nlevel$df, ci = 0.95), digits = 2))
+hypothesis3a_contrasts_nlevel <- cbind(hypothesis3a_contrasts_nlevel,
+                                    format(effectsize::t_to_eta2(t = hypothesis3a_contrasts_nlevel$t.ratio,
+                                                                 df_error = hypothesis3a_contrasts_nlevel$df, ci = 0.95), digits = 2))
 
 # rename columns and contrasts, round to two decimals
 
 colnames(hypothesis3a_contrasts_nlevel) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
-hypothesis3a_contrasts_nlevel$Contrast <- gsub("X", "", hypothesis3a_contrasts$Contrast)
+hypothesis3a_contrasts_nlevel$Contrast <- c("1-2 - 2-3")
 hypothesis3a_contrasts_nlevel[ ,c("Estimate","$SE$","$t$","$BF10$")] <- format(round(hypothesis3a_contrasts_nlevel[ ,c("Estimate","$SE$","$t$","$BF10$")], digits = 2), nsmall = 2)
[…]

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 The authors made the following contributions.
-Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Visualization, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Writing - review \& editing.
+Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Visualization, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Methodology, Writing - review \& editing.
 \textsuperscript{$\dagger{}$} Christoph Scheffel and Josephine Zerna contributed equally to this work.
@@
 
+\hypertarget{results}{%
+\section{3. Results}\label{results}}
+
+\hypertarget{participants-and-descriptive-statistics}{%
+\subsection{3.1 Participants and descriptive statistics}\label{participants-and-descriptive-statistics}}
+
+Data collection took place between 2022-08-16 and 2023-02-03.
+
+\hypertarget{confirmatory-analyses}{%
+\subsection{3.2. Confirmatory analyses}\label{confirmatory-analyses}}
+
+\hypertarget{exploratory-analyses}{%
+\subsection{3.3. Exploratory analyses}\label{exploratory-analyses}}
+
 \hypertarget{references}{%
@@
 
-\caption{\label{tab:unnamed-chunk-3}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
 
@@
 
-\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:unnamed-chunk-10}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
 
@@
 \midrule
-$View_{negative} - Distancing$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
-$View_{negative} - Distraction$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
+$View_{negative} - Distraction$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
+$View_{negative} - Distancing$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
 $View_{negative} - Suppression$ & -88.15 & 20.85 & 45.00 & -4.23 & 0.00 & 33.13 & 0.28 & {}[0.11, 1.00]\\

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
added package name

@@
 library(kableExtra) # for tables in R Markdown
-library(BayesFactor) # for bayes factors
+#library(BayesFactor) # for bayes factors
 
@@
 ```{r child = "Method.Rmd"}
+```
+
+```{r child = "Results.Rmd"}
 ```
@@
 
-`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`
+`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`
 
@@
 
-ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`
+ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`
 
@@
 
-*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`
+*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`
 
@@
 
-*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`
+*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`
 
@@
 
-*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`
+*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`
 
@@
 
-*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`
+*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`
 
@@
 
-ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
+ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
 

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added text
corrected document title

@@
 ---
+title: "results"
+author: "Christoph Scheffel"
 output: html_document
-bibliography: ER_ED.bib
-csl: apa7.csl
-editor_options: 
-  markdown: 
-    wrap: sentence
 ---
 
-```{r SetupMethod, include = FALSE}
+```{r SetupResults, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
 
-# 3. Method
+# 3. Results
+
+## 3.1 Participants and descriptive statistics
+
+Data collection took place between `r acqui_time[1]` and `r acqui_time[2]`.
+
+## 3.2. Confirmatory analyses
+
+## 3.3. Exploratory analyses

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added participant info

@@
 ---
-title: "results"
+title: "Results"
 author: "Christoph Scheffel"
@@
 
-#library(papaja)     # APA conform output
-#library(readxl)     # import excel files
+# load workspace variables from analyses_ERED.R script
+base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
+base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
 ```
@@
 
-Data collection took place between `r acqui_time[1]` and `r acqui_time[2]`.
+Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
+A total of $N=`r sum(data_survey$lay_beliefs_complete == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
+Of these, $N=`r sum(data_survey$files_coged_complete == 2)`$ participated in the first laboratory session and $N=`r sum(data_survey$followup_ered_complete == 2)`$ completed the second laboratory session.
+Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
 

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added manipulation checks

@@
 
+library(tidyverse)
+
 # load workspace variables from analyses_ERED.R script
@@
 Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
-A total of $N=`r sum(data_survey$lay_beliefs_complete == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
-Of these, $N=`r sum(data_survey$files_coged_complete == 2)`$ participated in the first laboratory session and $N=`r sum(data_survey$followup_ered_complete == 2)`$ completed the second laboratory session.
+A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
+Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
 Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
+The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female ; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
+Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).
 
@@
 
+### Manipulation checks
+
+To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
+We found a highly significant main effect of valence (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), indicating that negative pictures were perceived as more arousing than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalView_con[,7], format = "e")`).
+To explore the effect of valence on facial muscle activity(*Corrugator* and *Levator*), we conducted two ANOVA for the active viewing condition.
+For *Corrugator* activity, we found a significant main effect of valence (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), indicating that negative pictures evoked greater *Corrugator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrView_con[,7], format = "e")`).
+In line with previously reported results, there was a significant main effect of valence for *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures evoked greater *Levator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGLevView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGLevView_con[,7], format = "e")`).
+
+To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).
+
 ## 3.3. Exploratory analyses

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added results till H3

@@
 A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
-Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
+Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
 Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
@@
 
+#### Subjective arousal and physiological responding
 To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
@@
 To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`).
+Post-hoc test showed significantly reduced subjective arousal after use of distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[1,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[2,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[3,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[3,7], format = "e")`) compared with active viewing.
+However, there were no significant differences between strategies (all $p>.05$).
+To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVAS comparing *Corrugator* activity and *Levator* activity of four the strategies.
+Regarding *Corrugator* activity, we found a significant main effect of factor strategy (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`).
+Post-hoc test revealed reduced *Corrugator* activity during distraction ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[1,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[2,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[3,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrReg_con[3,7], format = "e")`) compared to active viewing.
+There were no significant differences between regulation strategies (all $p>.05$).
 

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 
-Data collection took place between 2022-08-16 and 2023-02-03.
+Data collection took place between 2022-08 and 2023-02.
+A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
+Of these, \(N=125\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
+Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
+The final sample consisted of \(N=120\) participants (100 female ; age: \(M=22.5\text{ }\pm\text{ }SD = 3.0\)).
+Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).
 
@@
 \subsection{3.2. Confirmatory analyses}\label{confirmatory-analyses}}
+
+\hypertarget{manipulation-checks}{%
+\subsubsection{Manipulation checks}\label{manipulation-checks}}
+
+\hypertarget{subjective-arousal-and-physiological-responding}{%
+\paragraph{Subjective arousal and physiological responding}\label{subjective-arousal-and-physiological-responding}}
+
+To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition.
+We found a highly significant main effect of valence (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), indicating that negative pictures were perceived as more arousing than neutral pictures (\(\eta_{p}^{2}=0.77, [0.72, 1.00]\), \(BF_{10}=\)\(3.22 \times 10^{36}\)).
+To explore the effect of valence on facial muscle activity(\emph{Corrugator} and \emph{Levator}), we conducted two ANOVA for the active viewing condition.
+For \emph{Corrugator} activity, we found a significant main effect of valence (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), indicating that negative pictures evoked greater \emph{Corrugator} activity than neutral pictures (\(\eta_{p}^{2}=0.19, [0.10, 1.00]\), \(BF_{10}=\)\(8.67 \times 10^{16}\)).
+In line with previously reported results, there was a significant main effect of valence for \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\)´, \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures evoked greater \emph{Levator} activity than neutral pictures (\(\eta_{p}^{2}=0.07, [0.01, 1.00]\), \(BF_{10}=\)\(1.89 \times 10^{2}\)).
+
+To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)).
+Post-hoc test showed significantly reduced subjective arousal after use of distraction (\(\eta_{p}^{2}=0.05, [0.02, 1.00]\), \(BF_{10}=\)\(1.68 \times 10^{2}\)), distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\)\(6.30 \times 10^{1}\)), and suppression (\(\eta_{p}^{2}=0.02, [0.00, 1.00]\), \(BF_{10}=\)\(1.97\)) compared with active viewing.
+However, there were no significant differences between strategies (all \(p>.05\)).
+To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVAS comparing \emph{Corrugator} activity and \emph{Levator} activity of four the strategies.
+Regarding \emph{Corrugator} activity, we found a significant main effect of factor strategy (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)).
+Post-hoc test revealed reduced \emph{Corrugator} activity during distraction (\(\eta_{p}^{2}=0.06, [0.03, 1.00]\), \(BF_{10}=\)\(2.19 \times 10^{4}\)), distancing (\(\eta_{p}^{2}=0.07, [0.03, 1.00]\), \(BF_{10}=\)\(1.40 \times 10^{5}\)), and suppression (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\)\(1.84 \times 10^{7}\)) compared to active viewing.
+There were no significant differences between regulation strategies (all \(p>.05\)).
 

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/method.Rmd

@@
 bibliography: ER_ED.bib
-csl: apa7.csl
+csl: nature.csl
 editor_options: 
@@
 Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
-include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
 ```

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added results H4

@@
 #### Subjective arousal and physiological responding
+
 To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
@@
 We found a significant effect of strategy (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`).
-Post-hoc test showed significantly reduced subjective arousal after use of distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[1,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[2,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[3,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[3,7], format = "e")`) compared with active viewing.
+Post-hoc test showed significantly reduced subjective arousal after use of distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[1,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[2,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[3,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalReg_con[3,7], format = "e")`) compared to active viewing.
 However, there were no significant differences between strategies (all $p>.05$).
-To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVAS comparing *Corrugator* activity and *Levator* activity of four the strategies.
+To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVA comparing *Corrugator* activity and *Levator* activity of four the strategies.
 Regarding *Corrugator* activity, we found a significant main effect of factor strategy (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`).
@@
 
+#### Subjective effort of ER strategies
+
+To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
+Post-hoc test showed significant higher subjective effort for distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[1,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjEffort_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[2,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjEffort_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[3,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjEffort_con[3,7], format = "e")`) compared to active viewing.
+Moreover, we found significantly lower effort during suppression compared with distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[5,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjEffort_con[5,7], format = "e")`) and distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[6,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjEffort_con[6,7], format = "e")`).
 ## 3.3. Exploratory analyses

### 2023-02-14 06_Paper/COG-ED/Stage 2/Analysis.R
added ICC

@@ -1407,9 +1407,15 @@ contrasts(h2b_data$level.cwc) <- cbind(h2b_contrasts)
 
 m0_h2b <- lmerTest::lmer(sv ~ 1 + (1|subject), data = h2b_data, REML = T)
 
-# random slopes model
+# get intraclass correlation (ICC)
 
-m1_h2b <- lmerTest::lmer(sv ~ level.cwc * dprime.cwc + medianRT.cwc + (level.cwc|subject),
+var_m0_h2b <- as.data.frame(lme4::VarCorr(m0_h2b))
+icc_h2b <- var_m0_h2b$vcov[1] / (var_m0_h2b$vcov[1] + var_m0_h2b$vcov[2]) 
+
+# our model (this is not a random slopes model, because we have to replace (level.cwc|subject) with (1|subject), because
+# this model contains the level as a factor which does not allow repeated measures)
+
+m1_h2b <- lmerTest::lmer(sv ~ level.cwc * dprime.cwc + medianRT.cwc + (1|subject),
                          data = h2b_data, REML = T)
 
 

### 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

@@
 We found a significant effect of strategy (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)).
-Post-hoc test showed significantly reduced subjective arousal after use of distraction (\(\eta_{p}^{2}=0.05, [0.02, 1.00]\), \(BF_{10}=\)\(1.68 \times 10^{2}\)), distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\)\(6.30 \times 10^{1}\)), and suppression (\(\eta_{p}^{2}=0.02, [0.00, 1.00]\), \(BF_{10}=\)\(1.97\)) compared with active viewing.
+Post-hoc test showed significantly reduced subjective arousal after use of distraction (\(\eta_{p}^{2}=0.05, [0.02, 1.00]\), \(BF_{10}=\)\(1.68 \times 10^{2}\)), distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\)\(6.30 \times 10^{1}\)), and suppression (\(\eta_{p}^{2}=0.02, [0.00, 1.00]\), \(BF_{10}=\)\(1.97\)) compared to active viewing.
 However, there were no significant differences between strategies (all \(p>.05\)).
-To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVAS comparing \emph{Corrugator} activity and \emph{Levator} activity of four the strategies.
+To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVA comparing \emph{Corrugator} activity and \emph{Levator} activity of four the strategies.
 Regarding \emph{Corrugator} activity, we found a significant main effect of factor strategy (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)).
@@
 There were no significant differences between regulation strategies (all \(p>.05\)).
+
+\hypertarget{subjective-effort-of-er-strategies}{%
+\paragraph{Subjective effort of ER strategies}\label{subjective-effort-of-er-strategies}}
+
+To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\)).
+Post-hoc test showed significant higher subjective effort for distraction (\(\eta_{p}^{2}=0.47, [0.42, 1.00]\), \(BF_{10}=\)\(3.61 \times 10^{30}\)), distancing (\(\eta_{p}^{2}=0.41, [0.35, 1.00]\), \(BF_{10}=\)\(1.60 \times 10^{28}\)), and suppression (\(\eta_{p}^{2}=0.30, [0.23, 1.00]\), \(BF_{10}=\)\(1.27 \times 10^{19}\)) compared to active viewing.
+Moreover, we found significantly lower effort during suppression compared with distraction (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\)\(1.61 \times 10^{6}\)) and distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\)\(2.92 \times 10^{1}\)).
 

### 2023-02-15 06_Paper/ER-ED/ERED_Stage2/method.Rmd
Chi-squared

@@
 
-To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice was computed.
+To investigate whether individual SVs predict ER choice (H7a), a $\chi{2}$ test with predicted choice (highest SV of each participant) and actual choice was computed.
 Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.

### 2023-02-15 06_Paper/COG-ED/Stage 2/Analysis.R
added new plot for H3b

@@ -1690,13 +1690,16 @@ hypothesis3b_contrasts_interact$`$p$`[hypothesis3b_contrasts_interact$`$p$` == "
 
 # plot these results
 
-plot_h3b <- ggplot(h3b_data, aes(x = level, y = ntlx, fill = nfcmedian)) +
-  geom_violin(color = NA) +
-  scale_fill_manual(values = MetBrewer::met.brewer("Homer2", 2), labels = c("NFC above median", "NFC below median")) +
-  labs(x = "n-back levels", y = "NASA-TLX sum score") +
-  geom_boxplot(width = 0.1, position = position_dodge(0.9)) +
-  ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
-  scale_x_discrete(guide = "prism_bracket")
+plot_h3b <- ggplot(h3b_data, aes(level, ntlx, fill = nfcmedian, color = nfcmedian)) +
+            geom_rain(alpha = .5,
+                      violin.args = list(color = NA, alpha = .7), # removes the lines around the violins
+                      boxplot.args.pos = list(width = .1, position = ggpp::position_dodgenudge(
+                                                x = rep(-.13,8)))) +
+            ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
+            scale_fill_manual(values=c("#B30B0B", "#0941DB")) +
+            scale_color_manual(values=c("#B30B0B", "#0941DB")) +
+            labs(x = "n-back levels", y = "NASA-TLX sum score") +
+            guides(fill = 'none', color = 'none')
 
 # save the plot as an eps file with high resolution
 

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
replaced calls with values in pilot section

@@
 
-The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
+The sample of the pilot study consisted of $N=15$ participants (53.3% female, $M=24.43$ ($SD=3.59$) years old).
 One participant's data was removed because they misunderstood the instruction.
@@
 Data was collected between the 16th of August 2022 and the 3rd of February 2023.
-Of the $N=$ participants who filled out the online questionnaires, $n=$ came to the first lab session.
+Of the $N=`r n_quest`$ participants who filled out the online questionnaires, $n=`r length(datalist_nback)`$ came to the first lab session.
 Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
-Our final data set therefore included $N=$ participants.
+Our final data set therefore included $N=`r nrow(data_quest)`$ participants.
 

### 2023-02-15 06_Paper/COG-ED/Stage 2/Analysis.R
added variable to count questionnaires

@@ -150,6 +150,14 @@ data_quest <- cbind(data_quest, adherence = all_quest$followup_adherence[setinde
                     motivation = all_quest$followup_motivation[setindex+1],
                     motivation_other = all_quest$followup_motivation_other[setindex+1])
 
+# some participants started filling out the questionnaires two times, so their code appears twice
+
+data_quest <- data_quest %>% filter(complete.cases(.))
+
+# make a copy for counting the amount of participants who filled out the questionnaires
+
+n_quest <- data_quest
+
 # remove the following subjects for misunderstanding the instruction: E17T12, Z15R03, C18D18, H25N04, D24A05, T14G09, D29N05
 # remove the following subject for not remembering the level colours correctly during effort discounting: W16C01
 # sets 2, 6, and 7 were dummy sets to test the NASA TLX iterations
@@ -162,10 +170,6 @@ data_quest <- data_quest[!(data_quest$subject == "E17T12" | data_quest$subject =
 showups <- intersect(data_quest$subject, data_nback$subject)
 data_quest <- data_quest[data_quest$subject %in% showups, ]
 
-# some participants started filling out the questionnaires two times, so their code appears twice
-
-data_quest <- data_quest %>% filter(complete.cases(.))
-
 # describe when data acquisition took place
 
 acqui_time <- data.frame(dates = c(t(data_quest[,grep("time", colnames(data_quest))])), stringsAsFactors = FALSE)
@@ -177,6 +181,11 @@ acqui_time <- range(acqui_time, na.rm = TRUE)
 
 data_quest <- data_quest[grep("_final", data_quest$set), ]
 data_quest <- subset(data_quest, select = -c(set, time_quest, time_lab))
+
+# remove them from the counting variable as well
+
+n_quest <- n_quest[grep("_final", n_quest$set), ]
+n_quest <- nrow(n_quest)
 
 # remove temporary variables
 

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
replaced one more pilot thing

@@
 One participant's data was removed because they misunderstood the instruction.
-Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=14$ data sets.
 The results showed increases in subjective and objective task load measures with higher *n*-back level.

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added protocol registration section

@@
 
+## Protocol registration
+
+The Stage 1 Registered Report protocol has been approved and is available at [osf.io/qa2bg/](https://osf.io/qa2bg/).
+
 # Results
@@
 Our final data set therefore included $N=`r nrow(data_quest)`$ participants.
+
+## Manipulation checks
+
+The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`).
+Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
+The median RT did not differ between 2-back and 4-back, and the median RT was higher for 3-back than for 4-back (Table\ \@ref(tab:H1b-contrasts)).
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  hypothesis1b_contrasts,
+  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels",
+  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+## Decline of subjective values
+
+## Differences between NFC groups
 

### 2023-02-15 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
Chi-squared

--- 2023-02-14 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 
+#### Subjective arousal and physiological responding
+
 To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
-We found a highly significant main effect of valence (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), indicating that negative pictures were perceived as more arousing than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(SubjArousalView_con[,7], format = "e")`).
+We found a highly significant main effect of valence (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), indicating that negative pictures were perceived as more arousing than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalView_con[,7], format = "e")`).
 To explore the effect of valence on facial muscle activity(*Corrugator* and *Levator*), we conducted two ANOVA for the active viewing condition.
-For *Corrugator* activity, we found a significant main effect of valence (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), indicating that negative pictures evoked greater *Corrugator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGCorrView_con[,7], format = "e")`).
-In line with previously reported results, there was a significant main effect of valence for *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures evoked greater *Levator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGLevView_con[,8:9])`$, $BF_{10}=$`r papaja::printnum(EMGLevView_con[,7], format = "e")`).
+For *Corrugator* activity, we found a significant main effect of valence (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), indicating that negative pictures evoked greater *Corrugator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrView_con[,7], format = "e")`).
+In line with previously reported results, there was a significant main effect of valence for *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures evoked greater *Levator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGLevView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGLevView_con[,7], format = "e")`).
 
 To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`).
+Post-hoc test showed significantly reduced subjective arousal after use of distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[2,7])`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[3,7], format = "e")`) compared to active viewing.
+However, there were no significant differences between strategies (all $p>.05$).
+To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVA comparing *Corrugator* activity and *Levator* activity of four the strategies.
+Regarding *Corrugator* activity, we found a significant main effect of factor strategy (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`).
+Post-hoc test revealed reduced *Corrugator* activity during distraction ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[3,7], format = "e")`) compared to active viewing.
+There were no significant differences between regulation strategies (all $p>.05$).
+
+#### Subjective effort of ER strategies
+
+To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
+Post-hoc test showed significant higher subjective effort for distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[3,7], format = "e")`) compared to active viewing.
+Moreover, we found significantly lower effort during suppression compared with distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[5,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[5,7], format = "e")`) and distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[6,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[6,7])`).
+
+#### Subjective values of ER strategies
+
+[to be filled]
+
+#### Associations between subjective values and flexible ER
+
+To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
+Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
+There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`).
 

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
inserted H1b table

@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+```{r H1b-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
 apa_table(

### 2023-02-15 06_Paper/COG-ED/Stage 2/Analysis.R
revived variables for reporting in manuscript

@@ -981,23 +981,23 @@ hypothesis1c_frustration_rmanova <- afex::aov_ez(data = h1c_data,
 # obtain estimated marginal means for ANOVA model and
 # calculate pairwise comparisons on estimated marginal means
 
-hypothesis1c_emm <- emmeans::emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
-hypothesis1c_mental_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
+hypothesis1c_mental_emm <- emmeans::emmeans(object = hypothesis1c_mental_rmanova$aov, specs = "level")
+hypothesis1c_mental_contrasts <- as.data.frame(pairs(hypothesis1c_mental_emm))
 
-hypothesis1c_emm <- emmeans::emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
-hypothesis1c_physical_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
+hypothesis1c_physical_emm <- emmeans::emmeans(object = hypothesis1c_physical_rmanova$aov, specs = "level")
+hypothesis1c_physical_contrasts <- as.data.frame(pairs(hypothesis1c_physical_emm))
 
-hypothesis1c_emm <- emmeans::emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
-hypothesis1c_time_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
+hypothesis1c_time_emm <- emmeans::emmeans(object = hypothesis1c_time_rmanova$aov, specs = "level")
+hypothesis1c_time_contrasts <- as.data.frame(pairs(hypothesis1c_time_emm))
 
-hypothesis1c_emm <- emmeans::emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
-hypothesis1c_performance_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
+hypothesis1c_performance_emm <- emmeans::emmeans(object = hypothesis1c_performance_rmanova$aov, specs = "level")
+hypothesis1c_performance_contrasts <- as.data.frame(pairs(hypothesis1c_performance_emm))
 
-hypothesis1c_emm <- emmeans::emmeans(object = hypothesis1c_effort_rmanova$aov, specs = "level")
-hypothesis1c_effort_contrasts <- as.data.frame(pairs(hypothesis1c_emm))
[…]

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote NASA effort H1c

@@
 
-The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`).
+The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level, apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level, apa_print(hypothesis1b_BF)$statistic`).
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
@@
 ```
+
+All NASA-TLX subscale scores increased across *n*-back levels.
+The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level, apa_print(hypothesis1c_effort__BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2, apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4, apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
 

### 2023-02-15 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added flexer regression (H7b)

@@
 
+[ HIER FEHLT NOCH DIE ORDINALE REGRESSION ]
+
+Last, we investigated whether SVs are associated with ER flexibility.
+We conducted a logistic regression to inspect whether participants' individual $slopes$ and $intercepts$ of ordered SVs could predict their ER flexibility score.
+We found neither a significant associations between $slopes$ of SVs and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$slope`, `r papaja::apa_print(Flex_LM_BF)$full_result$slope`), nor between $intercepts$ and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$intercept`, `r papaja::apa_print(Flex_LM_BF)$full_result$intercept`).
+However, model fit was relatively low (`r papaja::apa_print(Flex_LM)$full_result$modelfit$r2`).
+
 ## 3.3. Exploratory analyses

### 2023-02-15 06_Paper/COG-ED/Stage 2/Analysis.R
tried contrasts

@@ -1144,15 +1144,12 @@ hypothesis1c_time_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")] <- signif(hyp
 hypothesis1c_time_contrasts$`$p$` <- format(round(hypothesis1c_time_contrasts$`$p$`, digits = 3), nsmall = 2)
 hypothesis1c_time_contrasts$`$p$`[hypothesis1c_time_contrasts$`$p$` == "0.000"] <- "<.001"
 
-# remove the temporary variable
-
-base::remove(h1c_data, hypothesis1c_emm)
 
 ##### Hypothesis 2a ############################################################
 
 # H2a: Subjective values decline with increasing n-back level.
 
-# ANOVA with six linear contrasts, contrasting the SVs of two n-back levels (1,2,3,4) at a time
+# ANOVA with six linear contrasts, contrasting the SVs of two n-back levels (1,2,3,4) at a time2
 
 # make a temporary copy of the data frame
 
@@ -1399,18 +1396,23 @@ h2b_data <- pipelines_data[["AARO"]]
 
 h2b_data <- droplevels(subset(h2b_data[ ,c("subject", "level", "sv", "dprime", "medianRT")]))
 
-# centering the level 1 predictors (d', medianRT, level) within cluster
+# turn n-back levels into contrasts
 
-h2b_data$dprime.cwc       <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-h2b_data$medianRT.cwc     <- h2b_data$medianRT - (ave(h2b_data$medianRT, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-h2b_data$level.cwc        <- h2b_data$level - (ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
+h2b_data$levelcontrast <- rep(c(3,2,-2,-3),nrow(h2b_data)/4)
+
+# center the level 1 predictors within cluster
+
+h2b_data$dprime.cwc         <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
+h2b_data$medianRT.cwc       <- h2b_data$medianRT - (ave(h2b_data$medianRT, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
[…]

### 2023-02-16 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
one more sentence in H1c
inserted commas into apaprint

--- 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
@@
 
-The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`).
+The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`).
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
@@
 ```
+
+All NASA-TLX subscale scores increased across *n*-back levels.
+The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort__BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
+Three subscales had significant differences between all contrasts except for 3- versus 4-back:
+The frustration subscale
 

### 2023-02-16 06_Paper/COG-ED/Stage 2/Analysis.R
added nlraa package

@@ -30,7 +30,7 @@ source(here("06_Paper","COG-ED", "Stage 2", "renv", "activate.R"))
 # the required packages are:
 # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot", "purrr", "broom",
 # "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize", "pracma", "MuMIn",
-# "MetBrewer", "lubridate" and "ggprism"
+# "MetBrewer", "lubridate", "nlraa" and "ggprism"
 library(tidyverse) # as an explicit call because renv somehow refuses to remember it
 
 # sets orthogonal contrasts for mixed-effects model and rmANOVA globally in order to get meaningful Type-III tests

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
added test for NV of predictors

@@ -546,6 +546,74 @@ for (i in seq_len(nrow(data_descr))) {
 
 #data_descr <- reshape(data = data_descr, idvar = "ID", timevar = "strategy", direction = "wide")
 
+#################### STATISTICS: ASSUMPTIONS ############
+
+# test NV of predictors
+
+# wrapper for shapiro.test(), works with data.frames
+sw <- function(x) {
+  x = data.frame(x)                                             # make data.frame
+  n = colnames(x)                                               # get variable names
+  r = NULL                                                      # create container
+  for (i in 1:dim(x)[2]) {                                      # for every variable in data ...
+    y = shapiro.test(x[,i])                                     # perform Shapiro-Wilks test ...
+    v = cbind(y$statistic,y$p.value)                            # get statistic and p-value ...
+    colnames(v) = c("W","p")                                    # assign names for columns ...
+    rownames(v) = n[i]                                          # and rows, i.e., variable names ...
+    r = rbind(r,v)                                              # and add to container
+  }
+  return(round(r,3))
+}
+
+# prepare df for reporting results of shapiro wilk test
+df.NV.subj <- data.frame(M = double(), SD = double(), W = double(), p = double())
+
+# mean and sd of every variable without choice block
+# arousal
+for (i in seq_len(length(unique(data_ER$block))-1)) {
+  
+  df.NV.subj[i,1] <-mean(data_ER$arousal[data_ER$block == unique(data_ER$block)[i]])
+  df.NV.subj[i,2] <-sd(data_ER$arousal[data_ER$block == unique(data_ER$block)[i]])
+  df.NV.subj[i,3:4] <- sw(data_ER$arousal[data_ER$block == unique(data_ER$block)[i]])
+  
+}
+
+# arousal
+for (i in seq_len(length(unique(data_ER$block))-1)) {
+  
+  df.NV.subj[i+(length(unique(data_ER$block))-1),1] <-mean(data_ER$effort[data_ER$block == unique(data_ER$block)[i]])
+  df.NV.subj[i+(length(unique(data_ER$block))-1),2] <-sd(data_ER$effort[data_ER$block == unique(data_ER$block)[i]])
[…]

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
created separate file for supplement

--- 2022-06-26 06_Paper/ER-ED/Manuscript_ERED_Stage1_rev.Rmd
@@
 ---
-title             : "Estimating individual subjective values of emotion regulation strategies"
-shorttitle        : "Subjective values of emotion regulation strategies"
-author:
-  - name          : "Christoph Scheffel"
-    orcid         : "0000-0001-5963-9229"
-    affiliation   : "1"
-    corresponding : yes
-    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
-    email         : "christoph_scheffel@tu-dresden.de"
-    equal_contrib : yes
-    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Methodology
-      - Funding acquisition
-      - Formal analysis
-      - Investigation
-      - Project administration
-      - Software
-      - Visualization
-      - Writing - original draft preparation
-      - Writing - review & editing
-  - name          : "Josephine Zerna"
-    orcid         : "0000-0003-2892-884X"
-    affiliation   : "1"
-    equal_contrib : yes
-    role          :
-      - Conceptualization
-      - Methodology
-      - Funding acquisition
-      - Investigation
-      - Project administration
-      - Software
-      - Visualization
-      - Writing - review & editing
-  - name          : "Anne Gärtner"
-    orcid         : "0000-0003-4296-963X"
-    affiliation   : "1"
-    role          :
-      - Formal analysis
-      - Writing - review & editing
-  - name          : "Denise Dörfel"
-    orcid         :
-    affiliation   : "1"
-    role          :
-      - Conceptuatlization
-      - Writing - review & editing
-  - name          : "Alexander Strobel"
-    orcid         : "0000-0002-9426-5397"
-    affiliation   : "1"
-    role          :
-      - Conceptualization
-      - Writing - review & editing 
-affiliation       :
-  - id            : "1"
-    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
-authornote        :
-abstract          : |
- Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
- In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
- Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
- Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
- Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
- However, SVs of ER strategies have not been determined so far. 
- We present a paradigm that is suitable for determining individual SVs of ER strategies. 
- Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
- Relations of SVs to personality traits will be explored.
-keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "6289"
-bibliography      : ["ER_ED.bib"]
-floatsintext      : yes
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-csl               : nature.csl
-header-includes   :
-    - \usepackage{booktabs}
-    - \usepackage{longtable}
-    - \usepackage{array}
-    - \usepackage{multirow}
-    - \usepackage{wrapfig}
-    - \usepackage{float}
-    - \usepackage{colortbl}
-    - \usepackage{pdflscape}
-    - \usepackage{tabu}
-    - \usepackage{threeparttable}
-    - \usepackage{threeparttablex}
-    - \usepackage[normalem]{ulem}
-    - \usepackage{makecell}
-    - \usepackage{xcolor}
-    - \usepackage{setspace}\doublespacing
-    - \usepackage[final]{pdfpages}
-    - \usepackage{chngcntr}
-editor_options: 
-  markdown: 
-    wrap: sentence
+title: "Supplement"
+author: "Christoph Scheffel"
+date: "2023-02-16"
+output: html_document
 ---
 
-```{=tex}
-\renewcommand\thesection{\Alph{section}}
-\counterwithout{figure}{section}
-\setcounter{figure}{0}
-```
+```{r SetupSupplement, include = FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 
-------------------------------------------------------------------------
-
-```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}
-
-library(knitr)
-# set knitr options
-knitr::opts_chunk$set(out.width = "\\textwidth")
-
-# load libraries
-library(here) # for path independent file referencing
+library(here)       # to set directories without defined paths
 # set top level directory to source file
@@
 
-library(papaja) # APA conform output
-library(kableExtra) # for tables in R Markdown
-library(BayesFactor) # for bayes factors
+library(tidyverse)
 
 # load workspace variables from analyses_ERED.R script
-load(here("06_Paper","ER-ED","Workspace_ERED_pilot.RData"))
-
+base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
+base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
 ```
-
-```{r child = "TheoreticalBackground_rev.Rmd"}
-```
-
-```{r child = "method_rev.Rmd"}
-```
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-```{=tex}
-\endgroup
-```
-\newpage
-
-# Acknowledgements
-
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
-Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-Applications for the centralized funds will be reviewed in May.
-Regardless of whether or not this additional funding will be granted, the study can commence immediately.
-The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-
-# Competing Interests
-
-The authors declare no competing interests.
-
-```{=tex}
-\newpage
-\setcounter{figure}{0}
-```
-# Figures and figure captions
-
-\newpage
-
-INSERT FIGURE 1 HERE
-
-*Figure 1.* Exemplary visualization of two response patterns.
-In the top half, the person has a clear preference for one of the three strategies.
-In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can also be represented by our paradigm.
-
-INSERT FIGURE 2 HERE
-
-*Figure 2.* Block design of the paradigm.
-Every participant starts with two "active viewing" blocks containing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
-After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared.
-Before the last block, participants can decide which regulation strategy they want to reapply.
-Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
-
-# Design Table {#DesignTable}
-
-INSERT DESIGN TABLE HERE
-
-<!--
-\newpage
 
@@
 
-## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"
+## Test for normal distribution of predictor variables
 
-ANOVA:
+``` {r TabNV, echo=FALSE, message=FALSE, warning=FALSE}
 
-`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`
+papaja::apa_table(
+  df.NV.subj,
+  caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
+  escape = FALSE)
 
-Paired contrasts:
+papaja::apa_table(
+  df.NV.EMG,
+  caption = "Results of Shapiro-Wilk test for normal distribution of *Corrugator* and *Levator* activity for all strategies.",
+  escape = FALSE)
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  SubjArousalView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
 ```
 
-Figure:
-
-```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigSubjArousalViewPilot)
-```
-
-## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-
-ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  SubjArousalReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figure:
-
-```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigSubjArousalRegPilot)
-```
-
-## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
-
-*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGCorrView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGLevView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figures:
-
-```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGCorrViewPilot)
-```
-
-```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGLevViewPilot)
-```
-
-## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-
-*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGCorrReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGLevReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figures:
-
-```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGCorrRegPilot)
-```
-
-```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGLevRegPilot)
-```
-
-## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-
-ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  SubjEffort_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figure:
-
-```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigSubjEffortPilot)
-```
--->
+\newpage

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
corrected column names of NV df

@@ -589,7 +589,9 @@ for (i in seq_len(length(unique(data_ER$block))-1)) {
 
 rownames(df.NV.subj) <- c("Arousal View Neu", "Arousal View Neg", "Arousal Distraction", "Arousal Distancing", "Arousal Suppression",
                      "Effort View Neu", "Effort View Neg", "Effort Distraction", "Effort Distancing", "Effort Suppression")
+colnames(df.NV.subj) <- c("$M$", "$SD$", "$W$", "$p$")
 
+# EMG activity
 df.NV.EMG <- data.frame(M = double(), SD = double(), W = double(), p = double())
 
 # mean and sd of every variable without choice block
@@ -613,6 +615,7 @@ for (i in seq_len(length(unique(data_EMG$block))-1)) {
 
 rownames(df.NV.EMG) <- c("Corrgator View Neu", "Corrgator View Neg", "Corrgator Distraction", "Corrgator Distancing", "Corrgator Suppression",
                           "Levator View Neu", "Levator View Neg", "Levator Distraction", "Levator Distancing", "Levator Suppression")
+colnames(df.NV.EMG) <- c("$M$", "$SD$", "$W$", "$p$")
 
 #################### STATISTICAL ANALYSES: KONFIRMATORY ANALYSES ############
 

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
added placement

@@
   caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
-  escape = FALSE)
+  escape = FALSE,
+  placement = "H")
 
@@
   df.NV.EMG,
-  caption = "Results of Shapiro-Wilk test for normal distribution of *Corrugator* and *Levator* activity for all strategies.",
-  escape = FALSE)
+  caption = "Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.",
+  escape = FALSE,
+  placement = "H")
 

### 2023-02-16 06_Paper/COG-ED/Stage 2/Analysis.R
tried nlmer and will set her laptop on fire

@@ -1398,57 +1398,81 @@ h2b_data <- droplevels(subset(h2b_data[ ,c("subject", "level", "sv", "dprime", "
 
 # turn n-back levels into contrasts
 
-h2b_data$levelcontrast <- rep(c(3,2,-2,-3),nrow(h2b_data)/4)
+#h2b_data$levelcontrast <- rep(c(3,2,-2,-3),nrow(h2b_data)/4)
 
 # center the level 1 predictors within cluster
 
 h2b_data$dprime.cwc         <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 h2b_data$medianRT.cwc       <- h2b_data$medianRT - (ave(h2b_data$medianRT, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
-h2b_data$levelcontrast.cwc  <- h2b_data$levelcontrast - (ave(h2b_data$levelcontrast, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
+#h2b_data$levelcontrast.cwc  <- h2b_data$levelcontrast - (ave(h2b_data$levelcontrast, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 h2b_data$level.cwc          <- h2b_data$level - (ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 
-h2b_data$level.cwc <- as.factor(h2b_data$level.cwc)
+#h2b_data$level.cwc <- as.factor(h2b_data$level.cwc)
 
 # define contrasts
 
-h2b_contrasts <- c(3,2,-2,-3)
-contrasts(h2b_data$level.cwc) <- cbind(h2b_contrasts, c(-1,1,0,0), c(0,0,-1,1))
+#h2b_contrasts <- c(3,2,-2,-3)
+#contrasts(h2b_data$level.cwc) <- cbind(h2b_contrasts, c(-1,1,0,0), c(0,0,-1,1))
 
 # define the null model
 
-m0_h2b <- lmerTest::lmer(sv ~ 1 + (1|subject), data = h2b_data, REML = T)
+#m0_h2b <- lmerTest::lmer(sv ~ 1 + (1|subject), data = h2b_data, REML = T)
 
 # get intraclass correlation (ICC)
 
[…]

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
Update Supplement.Rmd

@@
 
-## Test for normal distribution of predictor variables
+## Test for normal distribution of predictor variables {#SupplementNV}
 
@@
 \newpage
+
+## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}
+
+``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
+papaja::apa_table(
+  SubjArousalReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
+  escape = FALSE,
+  placement = "H",
+  format.args = list(format = "e"))
+
+papaja::apa_table(
+  EMGCorrReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
+  escape = FALSE,
+  placement = "H",
+  )
+
+papaja::apa_table(
+  EMGLevReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
+  escape = FALSE,
+  placement = "H")
+
+```

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

--- 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
@@
 In accordance with our previous study\textsuperscript{22}, we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
-All results are detailed in the \protect\hyperlink{SupplementaryMaterial}{Supplementary Material}, figures S1 to S7 and table S2 to S8.
+All results are detailed in the OSF repository (\url{https://osf.io/vnj8x/}).
 
@@
 
-To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice was computed.
+To investigate whether individual SVs predict ER choice (H7a), a \(\chi{2}\) test with predicted choice (highest SV of each participant) and actual choice was computed.
 Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.
@@
 \subsection{3.2. Confirmatory analyses}\label{confirmatory-analyses}}
+
+\hypertarget{manipulation-checks}{%
+\subsubsection{Manipulation checks}\label{manipulation-checks}}
+
+\hypertarget{subjective-arousal-and-physiological-responding}{%
+\paragraph{Subjective arousal and physiological responding}\label{subjective-arousal-and-physiological-responding}}
+
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator}, and \emph{Levator} activity.
+We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\)´, \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully evoked emotional arousal and physiological responding.
+
+To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator}, and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
+For detailed information on post-hoc tests, please see \protect\hyperlink{SupplementEffectER}{supplementary material}.
+
+\hypertarget{subjective-effort-of-er-strategies}{%
+\paragraph{Subjective effort of ER strategies}\label{subjective-effort-of-er-strategies}}
+
+To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\)).
+Post-hoc test showed significant higher subjective effort for distraction (\(\eta_{p}^{2}=0.47, [0.42, 1.00]\), \(BF_{10}=\) \(3.61 \times 10^{30}\)), distancing (\(\eta_{p}^{2}=0.41, [0.35, 1.00]\), \(BF_{10}=\) \(1.60 \times 10^{28}\)), and suppression (\(\eta_{p}^{2}=0.30, [0.23, 1.00]\), \(BF_{10}=\) \(1.27 \times 10^{19}\)) compared to active viewing.
+Moreover, we found significantly lower effort during suppression compared with distraction (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\) \(1.61 \times 10^{6}\)) and distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\) 29.19).
+
+\hypertarget{subjective-values-of-er-strategies}{%
+\paragraph{Subjective values of ER strategies}\label{subjective-values-of-er-strategies}}
+
+{[}to be filled{]}
+
+\hypertarget{associations-between-subjective-values-and-flexible-er}{%
+\paragraph{Associations between subjective values and flexible ER}\label{associations-between-subjective-values-and-flexible-er}}
+
+To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
+Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
+There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 120) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
+
+{[} HIER FEHLT NOCH DIE ORDINALE REGRESSION {]}
+
+Last, we investigated whether SVs are associated with ER flexibility.
+We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
+We found neither a significant associations between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
+However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).
 
@@
 
-\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
-\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
-
-ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1, 15 & 3895.91 & 34.32 *** & .475 & <.001\\
-\hline
-\end{tabular}
-
-\(BF10=\) 1,244.99
-
-Paired contrasts:
+\hypertarget{SupplementNV}{%
+\subsection{Test for normal distribution of predictor variables}\label{SupplementNV}}
 
@@
 
-\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:TabNV}Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.}
+
+\begin{tabular}{lllll}
+\toprule
+ & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{$W$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Arousal View Neu & 26.63 & 39.12 & 0.68 & 0.00\\
+Arousal View Neg & 187.78 & 87.31 & 0.98 & 0.06\\
+Arousal Distraction & 158.13 & 92.49 & 0.97 & 0.01\\
+Arousal Distancing & 168.62 & 95.75 & 0.98 & 0.04\\
+Arousal Suppression & 163.96 & 87.17 & 0.98 & 0.07\\
+Effort View Neu & 18.15 & 27.37 & 0.65 & 0.00\\
+Effort View Neg & 49.40 & 62.26 & 0.74 & 0.00\\
+Effort Distraction & 208.46 & 96.15 & 0.98 & 0.13\\
+Effort Distancing & 158.26 & 99.50 & 0.97 & 0.01\\
+Effort Suppression & 189.80 & 92.34 & 0.98 & 0.12\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:TabNV}Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.}
+
+\begin{tabular}{lllll}
+\toprule
+ & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{$W$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Corrgator View Neu & 0.04 & 6.99 & 0.05 & 0.00\\
+Corrgator View Neg & 1.03 & 7.21 & 0.19 & 0.00\\
+Corrgator Distraction & 0.00 & 7.67 & 0.04 & 0.00\\
+Corrgator Distancing & 0.07 & 3.78 & 0.08 & 0.00\\
+Corrgator Suppression & 0.25 & 1.92 & 0.35 & 0.00\\
+Levator View Neu & 0.09 & 1.84 & 0.38 & 0.00\\
+Levator View Neg & 0.58 & 3.20 & 0.43 & 0.00\\
+Levator Distraction & -0.05 & 1.16 & 0.52 & 0.00\\
+Levator Distancing & -0.03 & 0.92 & 0.48 & 0.00\\
+Levator Suppression & 0.01 & 1.00 & 0.55 & 0.00\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\newpage
+
+\hypertarget{SupplementEffectER}{%
+\subsection{Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding}\label{SupplementEffectER}}
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on subjective arousal ratings.}
 
@@
 \midrule
-$View_{neutral} - View_{negative}$ & -129.28 & 22.07 & 15.00 & -5.86 & 0.00 & 794.78 & 0.70 & {}[0.43, 1.00]\\
+$View_{negative} - Distraction$ & 29.65 & 6.68 & 357.00 & 4.44 & 0.00 & 168.48 & 0.05 & {}[0.02, 1.00]\\
+$View_{negative} - Distancing$ & 23.82 & 6.68 & 357.00 & 3.57 & 0.00 & 62.99 & 0.03 & {}[0.01, 1.00]\\
+$View_{negative} - Suppression$ & 19.16 & 6.68 & 357.00 & 2.87 & 0.03 & 1.97 & 0.02 & {}[0.00, 1.00]\\
+$Distraction - Distancing$ & -5.83 & 6.68 & 357.00 & -0.87 & 1.00 & 0.18 & 2.13e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & -10.49 & 6.68 & 357.00 & -1.57 & 0.70 & 0.31 & 6.86e-03 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & -4.66 & 6.68 & 357.00 & -0.70 & 1.00 & 0.14 & 1.36e-03 & {}[0.00, 1.00]\\
 \bottomrule
-\addlinespace
 \end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
 
@@
 
-Figure:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjArousalViewPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
-Each dot represents the arousal rating of a single subject.
-Bold dots represent outliers.}\label{fig:FigSubjArousalViewPilot}
-\end{figure}
-
-\hypertarget{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{Pilot study: Subjective arousal in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-arousal-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}
-
-ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 2.79, 41.89 & 2238.27 & 1.17 & .011 & .332\\
-\hline
-\end{tabular}
-
-\(BF10=\) 0.11
-
-Paired contrasts:
-
 \begin{table}[H]
@@
 
-\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
+\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Corrugator activity}
 
@@
 \midrule
-$View_{negative} - Distraction$ & -0.74 & 16.14 & 45.00 & -0.05 & 1.00 & 0.26 & 4.68e-05 & {}[0.00, 1.00]\\
-$View_{negative} - Distancing$ & -5.35 & 16.14 & 45.00 & -0.33 & 1.00 & 0.27 & 2.43e-03 & {}[0.00, 1.00]\\
-$View_{negative} - Suppression$ & -26.23 & 16.14 & 45.00 & -1.63 & 0.67 & 1.25 & 0.06 & {}[0.00, 1.00]\\
-$Distraction - Distancing$ & -4.61 & 16.14 & 45.00 & -0.29 & 1.00 & 0.26 & 1.81e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -25.49 & 16.14 & 45.00 & -1.58 & 0.73 & 0.77 & 0.05 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -20.88 & 16.14 & 45.00 & -1.29 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
+$View_{negative} - Distraction$ & 0.18 & 0.04 & 351.00 & 4.79 & 0.00 & 21,919.73 & 0.06 & {}[0.03, 1.00]\\
+$View_{negative} - Distancing$ & 0.19 & 0.04 & 351.00 & 5.09 & 0.00 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
+$View_{negative} - Suppression$ & 0.21 & 0.04 & 351.00 & 5.67 & 0.00 & 18,426,055.49 & 0.08 & {}[0.04, 1.00]\\
+$Distraction - Distancing$ & 0.01 & 0.04 & 351.00 & 0.30 & 1.00 & 0.04 & 2.61e-04 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 0.03 & 0.04 & 351.00 & 0.88 & 1.00 & 0.08 & 2.21e-03 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 0.02 & 0.04 & 351.00 & 0.58 & 1.00 & 0.05 & 9.51e-04 & {}[0.00, 1.00]\\
 \bottomrule
-\addlinespace
 \end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
 
@@
 
-Figure:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjArousalRegPilot-1} \caption{Subjective arousal ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the arousal rating of a single subject.
-Bold dots represent outliers.}\label{fig:FigSubjArousalRegPilot}
-\end{figure}
-
-\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}{%
-\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions ``Active viewing - neutral'' and ``Active viewing - negative''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditions-active-viewing---neutral-and-active-viewing---negative}}
-
-\emph{Corrugator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1, 15 & 1.01 & 9.70 ** & .237 & .007\\
-\hline
-\end{tabular}
-
-\(BF10=\) 6,690,401.91
-
-Paired contrasts:
-
 \begin{table}[H]
@@
 
-\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}
+\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Levator activity}
 
@@
 \midrule
-$View_{neutral} - View_{negative}$ & -1.11 & 0.36 & 15.00 & -3.11 & 0.01 & 5,019,313.20 & 0.39 & {}[0.09, 1.00]\\
+$View_{negative} - Distraction$ & 0.34 & 0.05 & 351.00 & 6.73 & 0.00 & 202,428,623,285.88 & 0.11 & {}[0.07, 1.00]\\
+$View_{negative} - Distancing$ & 0.28 & 0.05 & 351.00 & 5.66 & 0.00 & 39,887,367.63 & 0.08 & {}[0.04, 1.00]\\
+$View_{negative} - Suppression$ & 0.32 & 0.05 & 351.00 & 6.37 & 0.00 & 86,036,487,908.69 & 0.10 & {}[0.06, 1.00]\\
+$Distraction - Distancing$ & -0.05 & 0.05 & 351.00 & -1.07 & 1.00 & 0.22 & 3.26e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & -0.02 & 0.05 & 351.00 & -0.36 & 1.00 & 0.04 & 3.70e-04 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 0.04 & 0.05 & 351.00 & 0.71 & 1.00 & 0.10 & 1.44e-03 & {}[0.00, 1.00]\\
 \bottomrule
-\addlinespace
 \end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
 
@@
 
-\emph{Levator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1, 15 & 0.17 & 7.72 * & .162 & .014\\
-\hline
-\end{tabular}
-
-\(BF10=\) 48.44
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neutral} - View_{negative}$ & -0.40 & 0.14 & 15.00 & -2.78 & 0.01 & 41.02 & 0.34 & {}[0.05, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figures:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGCorrViewPilot-1} \caption{Corrugator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGCorrViewPilot}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGLevViewPilot-1} \caption{Levator activity for the conditions "Active viewing - neutral" and "Active viewing - negative" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGLevViewPilot}
-\end{figure}
-
-\hypertarget{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{\texorpdfstring{Pilot study: Physiological responding (\emph{Corrugator} and \emph{Levator} activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}{Pilot study: Physiological responding (Corrugator and Levator activity) in the conditions''Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}}\label{pilot-study-physiological-responding-corrugator-and-levator-activity-in-the-conditionsactive-viewing---negative-distraction-distancing-and-suppression}}
-
-\emph{Corrugator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 1.53, 22.98 & 1.16 & 5.71 * & .189 & .015\\
-\hline
-\end{tabular}
-
-\(BF10=\) 5,257,689.54
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{negative} - Distraction$ & 0.88 & 0.27 & 45.00 & 3.22 & 0.01 & 4,962.89 & 0.19 & {}[0.05, 1.00]\\
-$View_{negative} - Distancing$ & 0.95 & 0.27 & 45.00 & 3.50 & 0.01 & 616.63 & 0.21 & {}[0.06, 1.00]\\
-$View_{negative} - Suppression$ & 0.92 & 0.27 & 45.00 & 3.40 & 0.01 & 11,678.82 & 0.20 & {}[0.06, 1.00]\\
-$Distraction - Distancing$ & 0.08 & 0.27 & 45.00 & 0.28 & 1.00 & 0.07 & 1.78e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.05 & 0.27 & 45.00 & 0.18 & 1.00 & 0.08 & 7.22e-04 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -0.03 & 0.27 & 45.00 & -0.10 & 1.00 & 0.06 & 2.36e-04 & {}[0.00, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\emph{Levator}: ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 2.07, 31.00 & 0.20 & 8.27 ** & .225 & .001\\
-\hline
-\end{tabular}
-
-\(BF10=\) 672,341.29
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{negative} - Distraction$ & 0.42 & 0.13 & 45.00 & 3.24 & 0.01 & 58.02 & 0.19 & {}[0.05, 1.00]\\
-$View_{negative} - Distancing$ & 0.45 & 0.13 & 45.00 & 3.46 & 0.01 & 93.49 & 0.21 & {}[0.06, 1.00]\\
-$View_{negative} - Suppression$ & 0.62 & 0.13 & 45.00 & 4.79 & 0.00 & 6,253.91 & 0.34 & {}[0.16, 1.00]\\
-$Distraction - Distancing$ & 0.03 & 0.13 & 45.00 & 0.22 & 1.00 & 0.07 & 1.06e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.20 & 0.13 & 45.00 & 1.54 & 0.78 & 1.52 & 0.05 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.17 & 0.13 & 45.00 & 1.32 & 1.00 & 0.52 & 0.04 & {}[0.00, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figures:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGCorrRegPilot-1} \caption{Corrugator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGCorrRegPilot}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigEMGLevRegPilot-1} \caption{Levator activity for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.}\label{fig:FigEMGLevRegPilot}
-\end{figure}
-
-\hypertarget{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}{%
-\subsection{Pilot study: Subjective effort in the conditions ``Active viewing - negative'', ``Distraction'', ``Distancing'', and ``Suppression''}\label{pilot-study-subjective-effort-in-the-conditions-active-viewing---negative-distraction-distancing-and-suppression}}
-
-ANOVA:
-
-\begin{tabular}{l|l|l|l|l|l}
-\hline
-Effect & df & MSE & F & ges & p.value\\
-\hline
-block & 2.38, 35.66 & 4388.19 & 11.13 *** & .185 & <.001\\
-\hline
-\end{tabular}
-
-\(BF10=\) 7.40
-
-Paired contrasts:
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:unnamed-chunk-10}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{negative} - Distraction$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
-$View_{negative} - Distancing$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
-$View_{negative} - Suppression$ & -88.15 & 20.85 & 45.00 & -4.23 & 0.00 & 33.13 & 0.28 & {}[0.11, 1.00]\\
-$Distraction - Distancing$ & 21.00 & 20.85 & 45.00 & 1.01 & 1.00 & 0.50 & 0.02 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.57 & 0.03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 0.26 & 1.27e-04 & {}[0.00, 1.00]\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Figure:
-
-\begin{figure}[H]
-\includegraphics[width=0.75\linewidth]{Manuscript_ERED_Stage2_files/figure-latex/FigSubjEffortPilot-1} \caption{Subjective effort ratings for the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.}\label{fig:FigSubjEffortPilot}
-\end{figure}
-
 \end{document}

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd

@@
 
-# Supplementary Material {#SupplementaryMaterial}
-
-\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\setcounter{section}{19}
-\setcounter{figure}{0}
-\setcounter{table}{1}
-
-\newpage
-
-## Detailed information on psychometric measures {#SupplementQuestionnaires}
-
-*WHO-5.* General psychological well-being is assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
-5 Items such as "Over the past 2 weeks I have felt calm and relaxed." are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's $\alpha=.92$)[@Braehler2007].
-
-*Connor-Davidson Resilience Scale.* Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
-10 items such as "I am able to adapt to change." are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's $\alpha=.84$) and a satisfactory retest-reliability of $r_{tt}=.81$ across 6 month[@Sarubin2015].
-
-*Emotion Regulation Questionnaire.* Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
-The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's $\alpha>.75$) [@Preece2020].
-
-*FlexER Scale.* Flexible use of ER strategies is assessed using the FlexER Scale [@Doerfel2019] with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which are answered on a 4-point scale ranging from "strongly agree" to "strongly disagree".
-Psychometric properties are currently under investigation.
-
-*Implicit Theories Questionnaire.* Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
-4 items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's $\alpha=.87$[@Bernecker2017].
-
-*Need for Cognition Scale.* Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale [@Bless1994].
-Responses to each item (e.g., "Thinking is not my idea of fun", recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's $\alpha>.80$)[@Bless1994; @Fleischhauer2010] and a retest reliability of $r_{tt}=.83$ across 8 to 18 weeks [@Fleischhauer2015].
-
-*Self-Regulation Scale.* As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] is used.
-The scale has 10 items (e.g., "It is difficult for me to suppress thoughts that interfere with what I need to do.", recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency [Cronbach's $\alpha>.80$; @Schwarzer1999].
-
-*Brief Self-Control Scale.* As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used.
-It comprises 13 items (e.g., "I am good at resisting temptations") with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's $\alpha=.81$)[@Sproesser2011] .
-
-*Barratt Impulsiveness Scale.* As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] is used.
-Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's $\alpha=.74$ and a retest reliability of $r_{tt}=.56$ for General Impulsiveness and $r_{tt}=.66$ for Total Score across 6 month were reported [@Hartmann2011].
-
-*Attentional Control Scale.* Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
-The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's $\alpha=.88$ was reported [@Derryberry2002].
-
-\newpage
-
-## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"
-
-ANOVA:
-
-`r afex::nice(SubjArousalView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalView_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  SubjArousalView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
+```{r child = "Supplement.Rmd"}
 ```
-
-Figure:
-
-```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
-Each dot represents the arousal rating of a single subject.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigSubjArousalViewPilot)
-```
-
-## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-
-ANOVA: `r afex::nice(SubjArousalReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjArousalReg_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  SubjArousalReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figure:
-
-```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the arousal rating of a single subject.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigSubjArousalRegPilot)
-```
-
-## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions "Active viewing - neutral" and "Active viewing - negative"
-
-*Corrugator*: ANOVA: `r afex::nice(EMGCorrView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrView_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGCorrView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition \"active viewing\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-*Levator*: ANOVA: `r afex::nice(EMGLevView_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevView_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGLevView_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition \"active viewing\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figures:
-
-```{r FigEMGCorrViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGCorrViewPilot)
-```
-
-```{r FigEMGLevViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGLevViewPilot)
-```
-
-## Pilot study: Physiological responding (*Corrugator* and *Levator* activity) in the conditions"Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-
-*Corrugator*: ANOVA: `r afex::nice(EMGCorrReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGCorrReg_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGCorrReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-*Levator*: ANOVA: `r afex::nice(EMGLevReg_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(EMGLevReg_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  EMGLevReg_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figures:
-
-```{r FigEMGCorrRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the corrugator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGCorrRegPilot)
-```
-
-```{r FigEMGLevRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the levator activity of a single trial.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigEMGLevRegPilot)
-```
-
-## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
-
-ANOVA: `r afex::nice(SubjEffort_pilot_aov) %>% knitr::kable(x = .)` $BF10=$ `r round(BayesFactor::extractBF(SubjEffort_pilot_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  SubjEffort_pilot_con,
-  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-Figure:
-
-```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots.
-Each dot represents the effort rating of a single subject.
-Bold dots represent outliers.", fig.pos="H", out.width="75%"}
-
-print(FigSubjEffortPilot)
-```

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 
-To explore whether negative pictures evoke emotional arousal, we conducted an ANOVA for the active viewing condition. 
-We found a highly significant main effect of valence (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), indicating that negative pictures were perceived as more arousing than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalView_con[,7], format = "e")`).
-To explore the effect of valence on facial muscle activity(*Corrugator* and *Levator*), we conducted two ANOVA for the active viewing condition.
-For *Corrugator* activity, we found a significant main effect of valence (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), indicating that negative pictures evoked greater *Corrugator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrView_con[,7], format = "e")`).
-In line with previously reported results, there was a significant main effect of valence for *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures evoked greater *Levator* activity than neutral pictures ($\eta_{p}^{2}=`r papaja::printnum(EMGLevView_con[,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGLevView_con[,7], format = "e")`).
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator*, and *Levator* activity.
+We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully evoked emotional arousal and physiological responding.
 
-To investigate whether ER strategies reduce emotional arousal, we conducted an rmANOVA comparing the subjective arousal ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`).
-Post-hoc test showed significantly reduced subjective arousal after use of distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[2,7])`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjArousalReg_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjArousalReg_con[3,7], format = "e")`) compared to active viewing.
-However, there were no significant differences between strategies (all $p>.05$).
-To explore whether ER strategies reduce physiological responding, we conducted another two rmANOVA comparing *Corrugator* activity and *Levator* activity of four the strategies.
-Regarding *Corrugator* activity, we found a significant main effect of factor strategy (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`).
-Post-hoc test revealed reduced *Corrugator* activity during distraction ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(EMGCorrReg_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(EMGCorrReg_con[3,7], format = "e")`) compared to active viewing.
-There were no significant differences between regulation strategies (all $p>.05$).
+To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, *Corrugator*, and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
+For detailed information on post-hoc tests, please see [supplementary material](#SupplementEffectER).
 

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd

--- 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
@@
 \newpage
+
+## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}
+
+``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
+papaja::apa_table(
+  SubjArousalReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
+  escape = FALSE,
+  placement = "H")
+
+papaja::apa_table(
+  EMGCorrReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
+  escape = FALSE,
+  placement = "H")
+
+papaja::apa_table(
+  EMGLevReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
+  escape = FALSE,
+  placement = "H")
+
+```

### 2023-02-16 06_Paper/COG-ED/Stage 2/Analysis.R
undid weird changes

@@ -1149,7 +1149,7 @@ hypothesis1c_time_contrasts$`$p$`[hypothesis1c_time_contrasts$`$p$` == "0.000"] 
 
 # H2a: Subjective values decline with increasing n-back level.
 
-# ANOVA with six linear contrasts, contrasting the SVs of two n-back levels (1,2,3,4) at a time2
+# ANOVA with six linear contrasts, contrasting the SVs of two n-back levels (1,2,3,4) at a time
 
 # make a temporary copy of the data frame
 
@@ -1396,6 +1396,7 @@ h2b_data <- pipelines_data[["AARO"]]
 
 h2b_data <- droplevels(subset(h2b_data[ ,c("subject", "level", "sv", "dprime", "medianRT")]))
 
+
 # turn n-back levels into contrasts
 
 #h2b_data$levelcontrast <- rep(c(3,2,-2,-3),nrow(h2b_data)/4)
@@ -1423,7 +1424,9 @@ h2b_data$level.cwc          <- h2b_data$level - (ave(h2b_data$level, h2b_data$su
 #var_m0_h2b <- as.data.frame(lme4::VarCorr(m0_h2b))
 #icc_h2b <- var_m0_h2b$vcov[1] / (var_m0_h2b$vcov[1] + var_m0_h2b$vcov[2]) 
 
-# model 1 with the n-back levels as 'contrasts'
+# our model (this is not a random slopes model, because we have to replace (level.cwc|subject) with (1|subject), because
+# this model contains the level as a factor which does not allow repeated measures)
+
 
 #m1_h2b <- lmerTest::lmer(sv ~ levelcontrast.cwc + dprime.cwc + medianRT.cwc + (levelcontrast.cwc|subject),
 #                         data = h2b_data, REML = T)

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
updated row names

@@ -838,9 +838,9 @@ SubjArousalReg_con <- cbind(SubjArousalReg_con,
 
 colnames(SubjArousalReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 
-SubjArousalReg_con[1, 1] <- "$View_{negative} - Distraction$"
-SubjArousalReg_con[2, 1] <- "$View_{negative} - Distancing$"
-SubjArousalReg_con[3, 1] <- "$View_{negative} - Suppression$"
+SubjArousalReg_con[1, 1] <- "$View_{neg} - Distraction$"
+SubjArousalReg_con[2, 1] <- "$View_{neg} - Distancing$"
+SubjArousalReg_con[3, 1] <- "$View_{neg} - Suppression$"
 SubjArousalReg_con[4, 1] <- "$Distraction - Distancing$"
 SubjArousalReg_con[5, 1] <- "$Distraction - Suppression$"
 SubjArousalReg_con[6, 1] <- "$Distancing - Suppression$"
@@ -917,9 +917,9 @@ EMGCorrReg_con <- cbind(EMGCorrReg_con,
 
 colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 
-EMGCorrReg_con[1, 1] <- "$View_{negative} - Distraction$"
-EMGCorrReg_con[2, 1] <- "$View_{negative} - Distancing$"
-EMGCorrReg_con[3, 1] <- "$View_{negative} - Suppression$"
+EMGCorrReg_con[1, 1] <- "$View_{neg} - Distraction$"
+EMGCorrReg_con[2, 1] <- "$View_{neg} - Distancing$"
+EMGCorrReg_con[3, 1] <- "$View_{neg} - Suppression$"
 EMGCorrReg_con[4, 1] <- "$Distraction - Distancing$"
 EMGCorrReg_con[5, 1] <- "$Distraction - Suppression$"
 EMGCorrReg_con[6, 1] <- "$Distancing - Suppression$"
@@ -988,9 +988,9 @@ EMGLevReg_con <- cbind(EMGLevReg_con,
 
[…]

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd

--- 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
@@
 \newpage
+
+## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}
+
+``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
+papaja::apa_table(
+  SubjArousalReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
+  escape = FALSE,
+  placement = "H",
+  font_size = "footnotesize"
+  )
+
+papaja::apa_table(
+  EMGCorrReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
+  escape = FALSE,
+  placement = "H",
+  font_size = "footnotesize"
+  )
+
+papaja::apa_table(
+  EMGLevReg_con,
+  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
+  escape = FALSE,
+  placement = "H",
+  font_size = "footnotesize"
+  )
+
+```

### 2023-02-21 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
added model fit and BFs to ordinal regression

@@ -1256,8 +1256,15 @@ choice_chisq_BF <- BayesFactor::contingencyTableBF(x = choice_chisq[["observed"]
 # ORDINAL REGRESSION
 
 # https://marissabarlaz.github.io/portfolio/ols/
-Choice_OrdReg <- ordinal::clm(as.factor(choice) ~ distraction.sv + distancing.sv + suppression.sv, data = data_choice, link = "logit")
 
+data_choice$choice <- as.factor(data_choice$choice)
+
+Choice_OrdReg <- glm(choice ~ distraction.sv + distancing.sv + suppression.sv, data = data_choice, family = "binomial")
+
+Choice_OrdReg_R2 <- with(summary(Choice_OrdReg), 1 - deviance/null.deviance)
+
+# Bayes Factors
+Choice_OrdReg_Posterior <- BFpack::BF(Choice_OrdReg)
 
 #### HYPOTHESIS 7b
 

### 2023-02-21 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added ordinal regression results

@@
 There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`). 
-
-[ HIER FEHLT NOCH DIE ORDINALE REGRESSION ]
+We then conducted a ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
+Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
+The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$estimate$distraction_sv`).
 

### 2023-02-22 06_Paper/COG-ED/Stage 2/Analysis.R
added BF for H2a

@@ -1206,7 +1206,9 @@ hypothesis2a_contrasts <- emmeans::contrast(hypothesis2a_emm, method = list("Dec
                                                                             "Declining Logistic" = c(3,2,-2,-3),
                                                                             "Positively Skewed Normal" = c(1,2,-1,-2)))
 
-# we still have to get the Bayes Factors here, but we'll do that in the main study
+# get Bayes factors
+
+hypothesis2a_BF <- BayesFactor::anovaBF(formula = sv ~ level, data = h2a_data, progress = FALSE)
 
 # get effect size and confidence intervals
 

### 2023-02-22 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote NASA results

--- 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
@@
 
+All NASA-TLX subscale scores increased across *n*-back levels.
+The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
+Three subscales had significant differences between all contrasts except for 3- versus 4-back:
+While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher *n* (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
+Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
+Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
+
 ## Decline of subjective values
+
+The rmANOVA showed a significant difference between the SVs across *n*-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
 

### 2023-02-22 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
-The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$estimate$distraction_sv`).
+The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
+The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
+Additionally, the predictor SV of strategy suppression was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
+The estimated odds ration indicated that is more likely to later choose suppression, when SV of strategy suppression is higher.
 

### 2023-02-22 06_Paper/COG-ED/Stage 2/Analysis.R
corrected pvalue display in H2a

@@ -1222,7 +1222,7 @@ colnames(hypothesis2a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$
 hypothesis2a_contrasts$Contrast <- gsub("X", "", hypothesis2a_contrasts$Contrast)
 hypothesis2a_contrasts[ ,c("Estimate","$SE$","$t$")] <- signif(hypothesis2a_contrasts[ ,c("Estimate","$SE$","$t$")], digits = 3)
 hypothesis2a_contrasts$`$p$` <- format(round(hypothesis2a_contrasts$`$p$`, digits = 3), nsmall = 2)
-hypothesis2a_contrasts$`$p$`[hypothesis2a_contrasts$`$p$` == "0.000"] <- "<.001"
+hypothesis2a_contrasts$`$p$`[hypothesis2a_contrasts$`$p$` == "0.00"] <- "<.001"
 
 # remove the temporary variable
 

### 2023-02-22 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote results for H2a

@@
 The rmANOVA showed a significant difference between the SVs across *n*-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
+All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.
+
+```{r H2a-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
+apa_table(
+  hypothesis2a_contrasts,
+  caption = "Contrasts for the rmANOVA comparing the subjective values between *n*-back levels",
+  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("decl_log" =c(3,2,-2,-3))))$full_result`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
 

### 2023-02-22 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
added second MLM without strat

@@ -1168,11 +1168,79 @@ MLM_1 <- lmerTest::lmer(formula = sv ~ strat_c + effort.cwc + arousal.cwc + util
                         data = data_MLM,
                         REML = TRUE)
 
+MLM_2 <- lmerTest::lmer(formula = sv ~ effort.cwc + arousal.cwc + utility.cwc + Corr.cwc + Lev.cwc + (1 | ID),
+                        data = data_MLM,
+                        REML = TRUE)
+
+test <- lmerTest::lmer(formula = sv ~ effort.cwc + strat_c + arousal.cwc + utility.cwc + Corr.cwc + Lev.cwc + (strat_c | ID),
+                       data = df.MLM.test,
+                       REML = TRUE)
 ### Effect size R-squared for MLM
 
 # credits to: https://www.learn-mlms.com/11-module-11.html
 
 MLM_1_r2 <- r2mlm::r2mlm(MLM_1)
+
+MLM_2_r2 <- r2mlm::r2mlm(MLM_2)
+
+MLM1_r2 <- MuMIn::r.squaredGLMM(MLM_1, pj2014 = T)
+MLM2_r2 <- MuMIn::r.squaredGLMM(MLM_2, pj2014 = T)
+
+# f2
+
+# the pj argument uses the formula of Johnson (2014)
+# the marginal RGLMM2 represents the variance explained by the fixed effects
+# the conditional RGLMM2 is interpreted as a variance explained by the entire model, including both fixed and random effects
+
+# model without effect of effort
+
+MLM2_e_no_effect <- lmerTest::lmer(sv ~ 1 + arousal.cwc + utility.cwc + Corr.cwc + Lev.cwc + (1 | ID),
+                                       data = data_MLM, REML = T)
+# compute R²
+
+MLM2_e_no_effect_r2 <- MuMIn::r.squaredGLMM(MLM2_e_no_effect, pj2014 = T)
+
+# compute f² with conditional R²
+
+e_f2 <- (MLM2_r2[1,2] - MLM2_e_no_effect_r2[1,2]) / (1 - MLM2_r2[1,2])
+
+# model without effect of utility
+
+MLM2_u_no_effect <- lmerTest::lmer(sv ~ effort.cwc + arousal.cwc + 1 + Corr.cwc + Lev.cwc + (1 | ID),
[…]

### 2023-02-22 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

@@
 This was done by excluding all data points with absolute standardized residuals above 3 SD. 
-As effect size measures, we calculated pseudo *R²* for our model and *f²* to estimate the effect of *n*-back level according to Lorah[-@Lorah2018].
+As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of *n*-back level according to Lorah[-@Lorah2018].
 To ensure the validity of the association of SVs and *n*-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
@@
 The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("decl_log" =c(3,2,-2,-3))))$full_result`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
+
+Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
+To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
+Centered variables cannot be turned into factors, so we entered the variables in their raw form, and factors cannot be used as random slopes, so the model is now defined as:
+$$
+SV \sim level\ + d' + median RT + (1|subject)
+$$
+This means that the intercept still varies between subjects, but there are no random slopes anymore.
+To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
+The ICC of the null model indicated that there is a correlation of `r $r=round(model0_h2b_ICC, digits = 3)$` between the SVs of a subject, i.e.
+that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
+We did not use an optimization algorithm to improve the fit of the random intercept model.
+A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
+The final model had an effect size of `r $f^{2} = round(h2b_level_f2, digits = 2)$` for the *n*-back levels and `r $f^{2} = round(h2b_dprime_f2, digits = 2)$` for *d'*, which are considered large and small, respectively [@Cohen1992].
+The effect size of the median RT was `r $f^{2} = format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)$`.
 

### 2023-02-23 06_Paper/COG-ED/Stage 2/Analysis.R
changed SCA output variables

@@ -1362,7 +1362,7 @@ model1_h2b <- lmerTest::lmer(sv ~ level + dprime + medianRT + (1|subject),
   h2b_result.table[,c(2:5,7)] <- round(h2b_result.table[,c(2:5,7)], digits = 2)
   h2b_result.table[,6] <- signif(h2b_result.table[,6], digits = 3)
   
-  h2b_result.table$ `$p$-value`[1:3] <- paste0("<.001***")
+  h2b_result.table$ `$p$-value`[1:3] <- paste0("<.001")
   
   h2b_result.table$ `Random Effects (SD)`[2:4] <- paste0("")
 
@@ -1789,7 +1789,11 @@ base::remove(diffscores, mediannfc, h3c_data)
 
 # prepare empty data frame for the loop to feed into
 
-sca_results <- data.frame(pipeline = character(), beta = double(), SE = double(), pvalue = double(), BF10 = double())
+sca_results <- data.frame(pipeline = character(),
+                          beta_n = double(), SE_n = double(), pvalue_n = double(), # values for n-back level
+                          beta_d = double(), SE_d = double(), pvalue_d = double(), # values for dprime
+                          beta_r = double(), SE_r = double(), pvalue_r = double(), # values for reaction time
+                          BF10 = double())
 
 # loop through the pipelines
 
@@ -1833,9 +1837,15 @@ for (i in 1:length(pipelines_data)) {
   # combine current results and the bigger data frame
   
   newdata <- data.frame(pipeline = c(names(pipelines_data[i])),
-                        beta = c(base::summary(model1_sca)$coefficients[2,1]),
-                        SE = c(base::summary(model1_sca)$coefficients[2,2]),
-                        pvalue = c(base::summary(model1_sca)$coefficients[2,5]),
+                        beta_n = c(base::summary(model1_sca)$coefficients[2,1]),
+                        SE_n = c(base::summary(model1_sca)$coefficients[2,2]),
+                        pvalue_n = c(base::summary(model1_sca)$coefficients[2,5]),
+                        beta_d = c(base::summary(model1_sca)$coefficients[5,1]),
+                        SE_d = c(base::summary(model1_sca)$coefficients[5,2]),
+                        pvalue_d = c(base::summary(model1_sca)$coefficients[5,5]),
+                        beta_r = c(base::summary(model1_sca)$coefficients[6,1]),
[…]

### 2023-02-23 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
inserted SCA plot

@@
 A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
-The final model had an effect size of `r $f^{2} = round(h2b_level_f2, digits = 2)$` for the *n*-back levels and `r $f^{2} = round(h2b_dprime_f2, digits = 2)$` for *d'*, which are considered large and small, respectively [@Cohen1992].
+The results of the final model are displayed in Table\ \@ref(tab:H2b-results)
+
+```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
+kable(h2b_result.table,
+        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
+        booktabs = T,                          # no vertical lines
+        escape = F,                            # correctly print special characters)
+        align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
+    kable_styling(latex_options = c("striped")) %>%
+    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
+             escape = F,                    # correctly print special characters
+             threeparttable = T)            # line breaks in the footnote
+```
+
+The model had an effect size of `r $f^{2} = round(h2b_level_f2, digits = 2)$` for the *n*-back levels and `r $f^{2} = round(h2b_dprime_f2, digits = 2)$` for *d'*, which are considered large and small, respectively [@Cohen1992].
+This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
 The effect size of the median RT was `r $f^{2} = format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)$`.
+
+To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis.
+
+INSERT FIGURE 2 HERE
+
+```{r sca-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Results of the multi level model for each of the 63 preprocessing pipelines.
+The lower panel indicates the type of preprocessing, the middle panel shows the p-value of the full model, and the upper panel the beta coefficient as a line and its standard deviation as a vertical box.
+The colourbar indicates the BF10.", fig.pos="H"}
+
+  print(sca_plot)
+
+```
 
@@
 JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
-JZ and CK did the formal analysis, visualized the results, and prepared the original draft.
+JZ, CS, and CK did the formal analysis.
+JZ visualized the results, and prepared the original draft.
 All authors reviewed, edited, and approved the final version of the manuscript.

### 2023-02-23 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 
+[... WAHLVERHALTEN FEHLT NOCH ...]
+
 #### Subjective values of ER strategies
 
-[to be filled]
+To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
+The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
+The preregistered model
+
+``` {r TabMLM_H5, echo=FALSE, message=FALSE, warning=FALSE}
+papaja::apa_table(
+  H5_table,
+  caption = "Results of multilevel model predicting subjective values of ER strategies.",
+  escape = FALSE,
+  placement = "H")
+```
 

### 2023-02-23 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote SCA results

@@
 A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
-The results of the final model are displayed in Table\ \@ref(tab:H2b-results)
+The results of the final model are displayed in Table\ \@ref(tab:H2b-results).
 
@@
 
-To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis.
+To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis (Figure\ \@ref(fig:sca-plot)).
 
@@
 ```{r sca-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Results of the multi level model for each of the 63 preprocessing pipelines.
-The lower panel indicates the type of preprocessing, the middle panel shows the p-value of the full model, and the upper panel the beta coefficient as a line and its standard deviation as a vertical box.
-The colourbar indicates the BF10.", fig.pos="H"}
+The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value.
+The colourbar indicates the BF10.
+The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}
 
@@
 ```
+
+Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
+The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors and the largest effect of *n*-back level.
+These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
+The two "spikes" in the beta of the median RT in Figure\ \@ref(fig:sca-plot) are from the other two pipelines that used inverse transformation.
 

### 2023-02-23 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
Update Analyes_ERED.r

@@ -1192,11 +1192,9 @@ MLM2_r2 <- MuMIn::r.squaredGLMM(MLM_2, pj2014 = T)
 # the conditional RGLMM2 is interpreted as a variance explained by the entire model, including both fixed and random effects
 
 # model without effect of effort
-
 MLM2_e_no_effect <- lmerTest::lmer(sv ~ 1 + arousal.cwc + utility.cwc + Corr.cwc + Lev.cwc + (1 | ID),
                                        data = data_MLM, REML = T)
 # compute R²
-
 MLM2_e_no_effect_r2 <- MuMIn::r.squaredGLMM(MLM2_e_no_effect, pj2014 = T)
 
 # compute f² with conditional R²

### 2023-02-23 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
described new model

@@
 The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
-The preregistered model
+The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy.
+In addition with the estimation that our model explained `r papaja::printnum(MLM1_r2[2])` percent of variance, we assumed our model was overfitted due to inclueding recoded strategy as random slope.
+We therefore set a new model without the recoded strategy as random slope factor, that follew the specification:
+
+$$
+\begin{split}
+SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
+\end{split}
+$$
 

### 2023-02-24 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added some results

--- 2023-02-23 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
-The preregistered model
+The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
+Our model explained `r papaja::printnum(MLM1_r2[2])` percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
+We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
+The second model followed the specification:
+
+$$
+\begin{split}
+SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
+\end{split}
+$$
+
+The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance.
 
@@
 papaja::apa_table(
-  H5_table,
+  H5_M2_table,
   caption = "Results of multilevel model predicting subjective values of ER strategies.",

### 2023-02-24 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
corrected sentence

@@
 These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
-The two "spikes" in the beta of the median RT in Figure\ \@ref(fig:sca-plot) are from the other two pipelines that used inverse transformation.
+The by far highest values of the beta of the median RT in Figure\ \@ref(fig:sca-plot) are all from the pipelines that used inverse transformation.
 
 ## Differences between NFC groups
+
+We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
+There was a main effect of the *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$full_result`), but there are large interindividual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
+This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.
+
+INSERT FIGURE 3 HERE
+
+```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}
+
+  print(plot_h3a)
+
+```
 

### 2023-02-24 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
found p values of model

@@
 The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance. 
+All results of the second model are in table\ \@ref(tab:TabMLM_H5).
 
@@
   caption = "Results of multilevel model predicting subjective values of ER strategies.",
+  booktabs = TRUE,
   escape = FALSE,
@@
 ```
+
+The predictors effort ($p=$ `r papaja::printnum(summary(MLM_2)$coefficients[1,5])`), ...
 

### 2023-02-24 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote H3b results

@@
 
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of *n*-back level (`r apa_print(hypothesis3b_model)$full_result$level`) and an interaction between *n*-back level and NFC scores (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`).
+Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$full_result$X3_High_low`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$full_result$X4_High_low`) than those with NFC scores above the median.
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of *n*-back levels (**Supplement**).
+
 \newpage

### 2023-02-24 06_Paper/COG-ED/Stage 2/Analysis.R
changed some plot things

@@ -1485,6 +1485,16 @@ raincloudplots::raincloud_2x2_repmes(data_2x2 = plot_h3a_data_nfc,
   ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
   scale_x_continuous(breaks=c(1,2), labels=c("1-2", "2-3"), limits=c(0, 3))
 
+ggplot(h3a_data[h3a_data$nlevels %in% c("1-2", "2-3"),], aes(nlevels, svdiff, fill = nfcmedian, color = nfcmedian)) +
+  geom_rain(alpha = .5, rain.side = 'f2x2', id.long.var = "subject",
+            violin.args = list(color = NA, alpha = .7)) +
+  ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
+  scale_fill_manual(values=c("gold3", "cornflowerblue")) +
+  scale_color_manual(values=c("gold3", "cornflowerblue")) +
+  guides(fill = 'none', color = 'none') +
+  xlab("n-back levels") + 
+  ylab("Difference in subjective values")
+
 # remove temporary variables
 
 base::remove(diffscores, mediannfc, h3a_data, plot_h3a_data)

### 2023-02-24 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 
+{[}\ldots{} WAHLVERHALTEN FEHLT NOCH \ldots{]}
+
 \hypertarget{subjective-values-of-er-strategies}{%
@@
 
-{[}to be filled{]}
+To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
+The ICC of the null model was \(ICC=\) 0.19, indicating that level-2 predictor subject accounted for 19.10 percent of total variance.
+The preregistered model showed a correlation of \(r=\) 0.95 of the random effects subjects and recoded strategy.
+In addition with the estimation that our model explained 0.90 percent of variance, we assumed our model was overfitted due to inclueding recoded strategy as random slope.
+We therefore set a new model without the recoded strategy as random slope factor, that followed the specification:
+
+\[
+\begin{split}
+SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
+\end{split}
+\]
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:TabMLM_H5}Results of multilevel model predicting subjective values of ER strategies.}
+
+\begin{tabular}{lllll}
+\toprule
+Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{Random Effects (SD)}\\
+\midrule
+Intercept & 0.80 & 0.01 & 0.00 & 0.12\\
+Strategy & -0.22 & 0.01 & 0.00 & 0.14\\
+Effort & 0.00 & 0.00 & 0.00 & \\
+Arousal & 0.00 & 0.00 & 0.00 & \\
+Utility & 0.00 & 0.00 & 0.00 & \\
+Corrugator activity & 0.00 & 0.00 & 0.17 & \\
+Levator activity & 0.00 & 0.00 & 0.90 & \\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 120) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
-
-{[} HIER FEHLT NOCH DIE ORDINALE REGRESSION {]}
+We then conducted a ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
+Overall model fit was fair with \(R^{2}=\) 0.27.
+The predictor SV of strategy distraction was found to contribute to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
+The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
+Additionally, the predictor SV of strategy suppression was found to contribute to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
+The estimated odds ration indicated that is more likely to later choose suppression, when SV of strategy suppression is higher.
 
@@
 
+\footnotesize{
+
 \begin{tabular}{lllllllll}
@@
 \midrule
-$View_{negative} - Distraction$ & 29.65 & 6.68 & 357.00 & 4.44 & 0.00 & 168.48 & 0.05 & {}[0.02, 1.00]\\
-$View_{negative} - Distancing$ & 23.82 & 6.68 & 357.00 & 3.57 & 0.00 & 62.99 & 0.03 & {}[0.01, 1.00]\\
-$View_{negative} - Suppression$ & 19.16 & 6.68 & 357.00 & 2.87 & 0.03 & 1.97 & 0.02 & {}[0.00, 1.00]\\
+$View_{neg} - Distraction$ & 29.65 & 6.68 & 357.00 & 4.44 & 0.00 & 168.48 & 0.05 & {}[0.02, 1.00]\\
+$View_{neg} - Distancing$ & 23.82 & 6.68 & 357.00 & 3.57 & 0.00 & 62.99 & 0.03 & {}[0.01, 1.00]\\
+$View_{neg} - Suppression$ & 19.16 & 6.68 & 357.00 & 2.87 & 0.03 & 1.97 & 0.02 & {}[0.00, 1.00]\\
 $Distraction - Distancing$ & -5.83 & 6.68 & 357.00 & -0.87 & 1.00 & 0.18 & 2.13e-03 & {}[0.00, 1.00]\\
@@
 
+}
+
 \end{threeparttable}
@@
 \caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Corrugator activity}
+
+\footnotesize{
 
@@
 \midrule
-$View_{negative} - Distraction$ & 0.18 & 0.04 & 351.00 & 4.79 & 0.00 & 21,919.73 & 0.06 & {}[0.03, 1.00]\\
-$View_{negative} - Distancing$ & 0.19 & 0.04 & 351.00 & 5.09 & 0.00 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
-$View_{negative} - Suppression$ & 0.21 & 0.04 & 351.00 & 5.67 & 0.00 & 18,426,055.49 & 0.08 & {}[0.04, 1.00]\\
+$View_{neg} - Distraction$ & 0.18 & 0.04 & 351.00 & 4.79 & 0.00 & 21,919.73 & 0.06 & {}[0.03, 1.00]\\
+$View_{neg} - Distancing$ & 0.19 & 0.04 & 351.00 & 5.09 & 0.00 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
+$View_{neg} - Suppression$ & 0.21 & 0.04 & 351.00 & 5.67 & 0.00 & 18,426,055.49 & 0.08 & {}[0.04, 1.00]\\
 $Distraction - Distancing$ & 0.01 & 0.04 & 351.00 & 0.30 & 1.00 & 0.04 & 2.61e-04 & {}[0.00, 1.00]\\
@@
 \caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Levator activity}
+
+\footnotesize{
 
@@
 \midrule
-$View_{negative} - Distraction$ & 0.34 & 0.05 & 351.00 & 6.73 & 0.00 & 202,428,623,285.88 & 0.11 & {}[0.07, 1.00]\\
-$View_{negative} - Distancing$ & 0.28 & 0.05 & 351.00 & 5.66 & 0.00 & 39,887,367.63 & 0.08 & {}[0.04, 1.00]\\
-$View_{negative} - Suppression$ & 0.32 & 0.05 & 351.00 & 6.37 & 0.00 & 86,036,487,908.69 & 0.10 & {}[0.06, 1.00]\\
+$View_{neg} - Distraction$ & 0.34 & 0.05 & 351.00 & 6.73 & 0.00 & 202,428,623,285.88 & 0.11 & {}[0.07, 1.00]\\
+$View_{neg} - Distancing$ & 0.28 & 0.05 & 351.00 & 5.66 & 0.00 & 39,887,367.63 & 0.08 & {}[0.04, 1.00]\\
+$View_{neg} - Suppression$ & 0.32 & 0.05 & 351.00 & 6.37 & 0.00 & 86,036,487,908.69 & 0.10 & {}[0.06, 1.00]\\
 $Distraction - Distancing$ & -0.05 & 0.05 & 351.00 & -1.07 & 1.00 & 0.22 & 3.26e-03 & {}[0.00, 1.00]\\

### 2023-02-27 06_Paper/COG-ED/Stage 2/Analysis.R
added call to ggrain and kept mediannfc var

@@ -1486,7 +1486,7 @@ raincloudplots::raincloud_2x2_repmes(data_2x2 = plot_h3a_data_nfc,
   scale_x_continuous(breaks=c(1,2), labels=c("1-2", "2-3"), limits=c(0, 3))
 
 ggplot(h3a_data[h3a_data$nlevels %in% c("1-2", "2-3"),], aes(nlevels, svdiff, fill = nfcmedian, color = nfcmedian)) +
-  geom_rain(alpha = .5, rain.side = 'f2x2', id.long.var = "subject",
+  ggrain::geom_rain(alpha = .5, rain.side = 'f2x2', id.long.var = "subject",
             violin.args = list(color = NA, alpha = .7)) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
   scale_fill_manual(values=c("gold3", "cornflowerblue")) +
@@ -1497,7 +1497,7 @@ ggplot(h3a_data[h3a_data$nlevels %in% c("1-2", "2-3"),], aes(nlevels, svdiff, fi
 
 # remove temporary variables
 
-base::remove(diffscores, mediannfc, h3a_data, plot_h3a_data)
+base::remove(diffscores, h3a_data)
 
 ##### Hypothesis 3b ############################################################
 

### 2023-02-27 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
removed old supplement and started discussion

--- 2023-02-24 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
@@
 
-  load(here("06_Paper","COG-ED","Stage 1","Workspace.RData"))
+  load(here("06_Paper","COG-ED","Stage 2","Workspace.RData"))
 
@@
 To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
-The ICC of the null model indicated that there is a correlation of `r $r=round(model0_h2b_ICC, digits = 3)$` between the SVs of a subject, i.e.
+The ICC of the null model indicated that there is a correlation of $r=$`r round(model0_h2b_ICC, digits = 3)` between the SVs of a subject, i.e.
 that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
@@
 
-The model had an effect size of `r $f^{2} = round(h2b_level_f2, digits = 2)$` for the *n*-back levels and `r $f^{2} = round(h2b_dprime_f2, digits = 2)$` for *d'*, which are considered large and small, respectively [@Cohen1992].
+The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
 This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
-The effect size of the median RT was `r $f^{2} = format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)$`.
+The effect size of the median RT was $f^{2}=$`r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
 
@@
 
+The median NFC was `r mediannfc`, with $n=$`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))` subjects below and $n=$`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))` above the median.
 We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
 There was a main effect of the *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$full_result`), but there are large interindividual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$full_result`), but there were large interindividual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.
@@
 
-  print(plot_h3a)
+  #print(plot_h3a)
 
 ```
+
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of *n*-back level (`r apa_print(hypothesis3b_model)$full_result$level`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3b_BF_levels)$bf[1], digits = 2)`) and an interaction between *n*-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3b_BF_levels)$bf[2], digits = 2)`).
+Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$full_result$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$full_result$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of *n*-back levels (**Supplement**).
+
+With another rmANOVA was used to investigate whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
+There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3a_BF_nlevel)$bf[2], digits = 2)`) and a main effect of the *n*-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3a_BF_nlevel)$bf[1], digits = 2)`), but no interaction.
+Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$full_result`).
+Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$full_result`), but again, there were large interindividual differences.
+
+# Discussion
+
+This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.
+[-@Westbrook2013], which can estimate subjective values of different *n*-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate subjective values of tasks without assuming that the easiest level is inherently preferred.
+For this purpose, we changed the way in which the discounting options are presented to the participants, basing the anchor on their own choices rather than on the objective task load.
+The analyses were closely aligned with those in Westbrook et al. [-@Westbrook2013] to demonstrate the changes in SVs brought about by the new paradigm.
+This study also applied the CAD paradigm to an emotion regulation task, the results of which are detailed in **Scheffel et al.**.
+
+## Manipulation checks
+
+The performance measure *d'* did not differ across *n*-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
+This disparity of accuracy and speed has been observed before [@Meule2017] and shows different associations with various measures of intelligence [@Jaeggi2010].
 
@@
 INSERT DESIGN TABLE HERE
-<!--
-\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
--->
+
 \newpage
@@
 INSERT SUPPLEMENT HERE
-<!--
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\setcounter{section}{19}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-## Results of the pilot study
-
-## Hypothesis 1a: The signal detection measure d' declines with increasing *n*-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1a_rmanova$anova_table[1,"F"], df = hypothesis1a_rmanova$anova_table[1,"num Df"], df_error = hypothesis1a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1a_BF)$bf, digits = 2)`
-
-\newpage
-
-## Hypothesis 1b: Reaction time increases with increasing *n*-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis1b_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1b_rmanova$anova_table[1,"F"], df = hypothesis1b_rmanova$anova_table[1,"num Df"], df_error = hypothesis1b_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1b_BF)$bf, digits = 2)`
-
-Paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-apa_table(
-  hypothesis1b_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing reaction time between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing *n*-back level.
-
-Mental subscale ANOVA:
-
-`r apa_print(hypothesis1c_mental_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_mental_rmanova$anova_table[1,"F"], df = hypothesis1c_mental_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_mental_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_mental_BF)$bf, digits = 2)`
-
-Mental subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_mental_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Physical subscale ANOVA:
-
-`r apa_print(hypothesis1c_physical_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_physical_rmanova$anova_table[1,"F"], df = hypothesis1c_physical_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_physical_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_physical_BF)$bf, digits = 2)`
-
-Physical subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_physical_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Time subscale ANOVA:
-
-`r apa_print(hypothesis1c_time_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_time_rmanova$anova_table[1,"F"], df = hypothesis1c_time_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_time_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_time_BF)$bf, digits = 2)`
-
-Time subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_time_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Performance subscale ANOVA:
-
-`r apa_print(hypothesis1c_performance_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_performance_rmanova$anova_table[1,"F"], df = hypothesis1c_performance_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_performance_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_performance_BF)$bf, digits = 2)`
-
-Performance subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_performance_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Effort subscale ANOVA:
-
-`r apa_print(hypothesis1c_effort_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_effort_rmanova$anova_table[1,"F"], df = hypothesis1c_effort_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_effort_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_effort_BF)$bf, digits = 2)`
-
-Effort subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_effort_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-Frustration subscale ANOVA:
-
-`r apa_print(hypothesis1c_frustration_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis1c_frustration_rmanova$anova_table[1,"F"], df = hypothesis1c_frustration_rmanova$anova_table[1,"num Df"], df_error = hypothesis1c_frustration_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`, $BF10=$ `r round(extractBF(hypothesis1c_frustration_BF)$bf, digits = 2)`
-
-Frustration subscale paired contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis1c_frustration_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 2a: Subjective values decline with increasing *n*-back level.
-
-ANOVA:
-
-`r apa_print(hypothesis2a_rmanova)$statistic`, $\eta_{p}^{2}=$ `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,1]`, 95%\ CI `r format(F_to_eta2(f = hypothesis2a_rmanova$anova_table[1,"F"], df = hypothesis2a_rmanova$anova_table[1,"num Df"], df_error = hypothesis2a_rmanova$anova_table[1,"den Df"]), digits = 2)[1,2]`
-
-Contrasts:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis2a_contrasts,
-  caption = "Different contrasts for the rmANOVA comparing subjective values between *n*-back levels",
-  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H"
-)
-```
-
-\newpage
-
-## Hypothesis 2b: Subjective values decline with increasing *n*-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.
-
-Multi level model:
-
-```{r,echo=FALSE, message=FALSE, warning=FALSE}
-kable(h2b_result.table,
-        caption = "Effects of *n*-back load level on subjective value controlled 
-    for task performance (d' and reaction time).",
-        booktabs = T,                          # no vertical lines
-        escape = F,                            # correctly print special characters)
-        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
-    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
-             escape = F,                    # correctly print special characters
-             threeparttable = T)            # line breaks in the footnote
-```
-The intraclass correlation equals `r format(icc_h2b, digits = 2)`.
-
-The Bayes Factor $BF10$ of the multi level model approached infinity.
-
-The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2b_total_r2[1,2], digits = 2)`.
-
-The effect size is $f^2=$ `r format(h2b_f2, digits = 2)`.
-
-\newpage
-
-## Hypothesis 3a: Participants with high NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with low NFC scores.
-
-ANOVA:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis3a_rmanova,
-  caption = "Main effects and interaction of NFC group and *n*-back level on subjective values",
-  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H",
-  font_size = "footnotesize"
-)
-```
-
-\newpage
-
-## Hypothesis 3b: Participants with high NFC scores have lower NASA-TLX scores in every *n*-back level than participants with low NFC scores.
-
-ANOVA:
-
-Main effect of the NFC group:
-
-`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, $BF10=$ `r format(extractBF(hypothesis3b_BF["nfcmedian"])$bf, digits = 2)`
-
-Main effect of the *n*-back level:
-
-`r apa_print(hypothesis3b_model)$full_result$level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level"])$bf, digits = 2)`
-
-Interaction effect of NFC group and *n*-back level:
-
-`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`, $BF10=$ `r format(extractBF(hypothesis3b_BF["level + nfcmedian"])$bf, digits = 2)`
-
-Paired contrasts for the main effect of *n*-back level:
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE} 
-apa_table(
-  hypothesis3b_rmanova,
-  caption = "Main effects and interaction of NFC group and *n*-back level on NASA-TLX scores",
-  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
-  escape = FALSE,
-  placement = "H",
-  font_size = "footnotesize")
-```
--->

### 2023-02-27 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote more discussion for manip checks

@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.
-[-@Westbrook2013], which can estimate subjective values of different *n*-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate subjective values of tasks without assuming that the easiest level is inherently preferred.
+This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate subjective values of different *n*-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate subjective values of tasks without assuming that the easiest level is inherently preferred.
 For this purpose, we changed the way in which the discounting options are presented to the participants, basing the anchor on their own choices rather than on the objective task load.
-The analyses were closely aligned with those in Westbrook et al. [-@Westbrook2013] to demonstrate the changes in SVs brought about by the new paradigm.
+The analyses were closely aligned with those in Westbrook et al.[-@Westbrook2013] to demonstrate the changes in SVs brought about by the new paradigm.
 This study also applied the CAD paradigm to an emotion regulation task, the results of which are detailed in **Scheffel et al.**.
@@
 The performance measure *d'* did not differ across *n*-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
-This disparity of accuracy and speed has been observed before [@Meule2017] and shows different associations with various measures of intelligence [@Jaeggi2010].
+This points to three important characteristics of the *n*-back task in this context.
+Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate interindividual differences for $n>3$.
+Secondly, there is a speed-accuracy tradeoff in the first three levels, that might re-emerge in higher levels, where *d'* would decline and RT would remain stable.
+And lastly, the fact that neither accuracy and nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010].
 

### 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote about individual SVs

@@
 INSERT FIGURE 2 HERE
-
-```{r sca-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Results of the multi level model for each of the 63 preprocessing pipelines.
+<!--
+```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
 The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value.
@@
 
-  print(sca_plot)
+  include_graphics(here("06_Paper", "Stage 2", "Figures", "sca-plot.png"))
 
 ```
+-->
 
@@
 
+Figure\ \@ref(fig:nfc-sv) shows a scatterplot of SVs per *n*-back level, colored depending on the participant's NFC score.
+There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across *n*-back levels.
+At the same time, there is a subtle separation of SVs across *n*-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
+Specifically, $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` participants had an absolute preference for 1-back, $n=$`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])` for 2-back, $n=$`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])` for 3-back, and $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` for 4-back.
+There were $n=$`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))` participants who did not have an absolute preference for any *n*-back level, i.e. none of their SVs was 1.
+
+INSERT FIGURE 3 HERE
+<!--
+```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level.
+Each dot indicates a participant, the colours indicate their Need for Cognition score.
+$N=116$.
+There is a horizontal jitter of 0.4 and a vertical jitter of 0.05.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "Stage 2", "Figures", "nfc-sv.png"))
+
+```
+-->
+
 The median NFC was `r mediannfc`, with $n=$`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))` subjects below and $n=$`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))` above the median.
@@
 
-INSERT FIGURE 3 HERE
-
+INSERT FIGURE 4 HERE
+<!--
 ```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}
 
-  #print(plot_h3a)
+  include_graphics(here("06_Paper", "Stage 2", "Figures", "h3a-plot.png"))
 
 ```
+-->
 

### 2023-02-28 06_Paper/COG-ED/Stage 2/Analysis.R
changed plot specs

@@ -1962,11 +1962,14 @@ sca_plot <- egg::ggarrange(sca_plot_upper, sca_plot_lower,
 
 # plot showing SVs per subject, colors depend on NFC
 
-ggplot2::ggplot(pipelines_data[["AARO"]], aes(x = level, y = sv, group = subject, color = nfc)) +
-  geom_point(size = 3, alpha = 0.5, position = position_jitter(w = 0.2)) +
-  scale_color_gradient2(midpoint = 0, low = "blue", mid = "grey", high = "red", space = "Lab" ) +
-  ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans")
-
+plot_sv <-
+  ggplot2::ggplot(pipelines_data[["AARO"]], aes(x = level, y = sv, group = subject, color = nfc)) +
+    geom_point(size = 3, alpha = 0.5, position = position_jitter(w = 0.4, h = 0.05)) +
+    ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
+    scale_color_gradient2(midpoint = mediannfc, low = "deepskyblue", mid = "gray", high = "firebrick2", space = "Lab") +
+    geom_vline(xintercept = c(0.5,1.5,2.5,3.5,4.5), colour = "grey", linetype = 3) +
+    xlab("n-back level") + 
+    ylab("Subjective values")
 
 ##### Save variables ###########################################################
 

### 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote more disc & added motivation to results

@@
 
+When asking participants what motivated their decisions in the effort discounting, `r round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted to avoid boredom, `r round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted a challenge, `r round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted to avoid effort, and `r round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted to relax.
+The remaining `r round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
 The rmANOVA showed a significant difference between the SVs across *n*-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
@@
 We did not use an optimization algorithm to improve the fit of the random intercept model.
-A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
+A total of `r nrow(excl_cases_h2b)` data points from `r length(unique(excl_cases_h2b$subject))` participants were excluded, because the residuals exceeded 3 SD above the mean.
 The results of the final model are displayed in Table\ \@ref(tab:H2b-results).
@@
 At the same time, there is a subtle separation of SVs across *n*-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
-Specifically, $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` participants had an absolute preference for 1-back, $n=$`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])` for 2-back, $n=$`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])` for 3-back, and $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` for 4-back.
+Specifically, $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` participants had an absolute preference for 1-back, $n=$`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])` for 2-back, $n=$`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])` for 3-back, and $n=$`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])` for 4-back.
 There were $n=$`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))` participants who did not have an absolute preference for any *n*-back level, i.e. none of their SVs was 1.
@@
 $N=116$.
-There is a horizontal jitter of 0.4 and a vertical jitter of 0.05.", fig.pos="H"}
+There is a horizontal jitter of 0.4 and a vertical jitter of 0.05for visual clarity.", fig.pos="H"}
 
@@
 Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate interindividual differences for $n>3$.
-Secondly, there is a speed-accuracy tradeoff in the first three levels, that might re-emerge in higher levels, where *d'* would decline and RT would remain stable.
-And lastly, the fact that neither accuracy and nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010].
+Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where *d'* would decline and RT would remain stable.
+And lastly, the fact that neither accuracy and nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010], suggesting that they should always be reported as separate indices.
+
+All NASA-TLX subscales differed across *n*-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
+This would support the notion of the *n*-back task offering a continuous manipulation of task load, as least subjectively.
+Ratings on the frustration and time subscales increased and ratings on the performance subscale decreased until 3-back and then remained stable.
+This pattern is akin to the RT, which also increased and then remained stable.
+Ratings on the physical load subscale increased with *n*-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.
+
+## Decline of subjective values
+
+The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across *n*-back levels.
+The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
+The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit small.
+In both cases, the SVs decreased when the value of the predictor increased.
+The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not *d'* yielded significant differences across levels in the manipulation checks.
+However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
+This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they perform well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
 
@@
 JZ, CS, and CK did the formal analysis.
-JZ visualized the results, and prepared the original draft.
+JZ visualized the results.
+JZ and CK prepared the original draft.
 All authors reviewed, edited, and approved the final version of the manuscript.

### 2023-02-28 06_Paper/COG-ED/Stage 2/Analysis.R
added adherence removal (all adhered)

@@ -177,6 +177,10 @@ n_quest <- data_quest
 data_quest <- data_quest[!(data_quest$subject == "E17T12" | data_quest$subject == "Z15R03" | data_quest$subject == "C18D18" | data_quest$subject == "H25N04" |
                              data_quest$subject == "D24A05" | data_quest$subject == "T14G09" | data_quest$subject == "D29N05" | data_quest$subject == "W16C01"), ]
 
+# remove any subject who states that they did not adhere to the instructions
+
+data_quest <- data_quest[data_quest$adherence == 1,]
+
 # keep only the data from participants who have both questionnaire and behavioural data
 
 showups <- intersect(data_quest$subject, data_nback$subject)
@@ -1352,18 +1356,19 @@ model1_h2b <- lmerTest::lmer(sv ~ level + dprime + medianRT + (1|subject),
                                  df = as.numeric(model1_h2b_fixef[,3]),
                                  t = as.numeric(model1_h2b_fixef[,4]),
                                  p = as.numeric(model1_h2b_fixef[,5]),
-                                 Random = as.numeric(model1_h2b_ranef$sdcor[1],NA,NA,NA))
+                                 f = as.numeric(c(NA,h2b_level_f2,NA,NA,h2b_dprime_f2,h2b_medianRT_f2)),
+                                 Random = as.numeric(model1_h2b_ranef$sdcor[1],NA,NA,NA,NA,NA))
   
-  colnames(h2b_result.table) <- c("Parameter","Beta","$SE$","$df$","$t$-value","$p$-value","Random Effects (SD)")
+  colnames(h2b_result.table) <- c("Parameter","Beta","$SE$","$df$","$t$-value","$p$-value","$f^{2}$","Random Effects (SD)")
   
   h2b_result.table <- h2b_result.table[c(1,2,5,6),]
-  h2b_result.table$Parameter[1:4] <- c("Intercept", "Declining logistic contrast", "d'", "median RT")
+  h2b_result.table$Parameter[1:4] <- c("Intercept", "n-back level", "d'", "median RT")
   
-  h2b_result.table[,c(2:5,7)] <- round(h2b_result.table[,c(2:5,7)], digits = 2)
+  h2b_result.table[,c(2:5,7,8)] <- format(round(h2b_result.table[,c(2:5,7,8)], digits = 2), nsmall = 2)
[…]

### 2023-02-28 06_Paper/COG-ED/Stage 2/Analysis.R
reincluded cwc in MLM

@@ -1255,6 +1255,11 @@ detach_package(afex)
 
 h2b_data <- pipelines_data[["AARO"]][ ,c("subject","level","round","sv","dprime","medianRT")]
 
+# center within cluster
+
+h2b_data$dprime.cwc <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
+h2b_data$medianRT.cwc <- h2b_data$medianRT - (ave(h2b_data$medianRT, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
+
 # turn into factor
 
 h2b_data$level <- as.factor(h2b_data$level)
@@ -1283,7 +1288,7 @@ model0_h2b_ICC <- ICC.Model(model0_h2b)
 
 # model 2 with the contrast matrix
 
-model1_h2b_raw <- lmerTest::lmer(sv ~ level + dprime + medianRT + (1|subject),
+model1_h2b_raw <- lmerTest::lmer(sv ~ level + dprime.cwc + medianRT.cwc + (1|subject),
                          data = h2b_data, REML = T)
 
 # exclude cases with residuals three SDs above mean
@@ -1296,7 +1301,7 @@ h2b_data_excl <- droplevels(subset(h2b_data, abs(scale(resid(model1_h2b_raw))) <
 
 # recompute model 2
 
-model1_h2b <- lmerTest::lmer(sv ~ level + dprime + medianRT + (1|subject),
+model1_h2b <- lmerTest::lmer(sv ~ level + dprime.cwc + medianRT.cwc + (1|subject),
                              data = h2b_data_excl, REML = T)
 
 # to plot some fit indices if you like
@@ -1311,11 +1316,11 @@ model1_h2b <- lmerTest::lmer(sv ~ level + dprime + medianRT + (1|subject),
   
   # models without effects of each variable
   
-  model1_h2b_no_effect_level <- lmerTest::lmer(sv ~ 1 + dprime + medianRT + (1|subject),
+  model1_h2b_no_effect_level <- lmerTest::lmer(sv ~ 1 + dprime.cwc + medianRT.cwc + (1|subject),
                                                data = h2b_data_excl, REML = T)
-  model1_h2b_no_effect_dprime <- lmerTest::lmer(sv ~ level + 1 + medianRT + (1|subject),
+  model1_h2b_no_effect_dprime <- lmerTest::lmer(sv ~ level + 1 + medianRT.cwc + (1|subject),
[…]

### 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
explained MLM betas

@@
 To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
-Centered variables cannot be turned into factors, so we entered the variables in their raw form, and factors cannot be used as random slopes, so the model is now defined as:
+Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
 $$
@@
         escape = F,                            # correctly print special characters)
-        align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
+        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
     kable_styling(latex_options = c("striped")) %>%
@@
 The effect size of the median RT was $f^{2}=$`r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
+The beta coefficients indicated that with every *n*-back level, the SV decreased by `r as.numeric(h2b_result.table[2,"Beta"])`, and for every 1-unit increase in *d'*, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
 
@@
 However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
-This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they perform well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
+This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
+Since more participants reported effort avoidance as their motivation in the effort discounting than those who reported seeking a challenge, we can assume that they were more motivated to repeat a task in which they performed well because their good performance coincided with low effort.
 

### 2023-02-28 06_Paper/COG-ED/Stage 2/Analysis.R
changed plot colors

@@ -1649,11 +1649,9 @@ plot_h3b <- ggplot(h3b_data, aes(level, ntlx, fill = nfcmedian, color = nfcmedia
                       boxplot.args.pos = list(width = .1, position = ggpp::position_dodgenudge(
                                                 x = rep(-.13,8)))) +
             ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
-            # scale_fill_manual(values=c("#B30B0B", "#0941DB")) +
-            # scale_color_manual(values=c("#B30B0B", "#0941DB")) +
-  scale_fill_manual(values=c("gold3", "cornflowerblue")) +
-  scale_color_manual(values=c("gold3", "cornflowerblue")) +
-            labs(x = "n-back levels", y = "NASA-TLX sum score") +
+            scale_fill_manual(values=c("darkorchid3", "chartreuse3")) +
+            scale_color_manual(values=c("darkorchid3", "chartreuse3")) +
+            labs(x = "n-back level", y = "NASA-TLX sum score") +
             guides(fill = 'none', color = 'none')
 
 # save the plot as an eps file with high resolution
@@ -1963,9 +1961,9 @@ sca_plot_upper <-
   ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
   labs(x = NULL, y = "beta") +
   scale_x_continuous(labels = NULL) +
-  scale_color_manual(labels = c("p > .05", "p < .05", "p < .01", "p < .001"), values = MetBrewer::met.brewer("Hokusai2",4)) +
+  scale_color_manual(labels = c("p > .05", "p < .05", "p < .01"), values = c("darkslategray3","darkslategray4","darkslategray")) +
   scale_shape_manual(labels = c("d'","n-back level","median RT"), values = c(18,17,19)) +
-  scale_y_continuous(breaks = c(-0.05,0,0.05))
+  scale_y_continuous(breaks = c(0,0.05,0.1))
 
 # combine into panel
 
@@ -1979,9 +1977,9 @@ sca_plot <- egg::ggarrange(sca_plot_upper, sca_plot_lower,
 
 plot_sv <-
   ggplot2::ggplot(pipelines_data[["AARO"]], aes(x = level, y = sv, group = subject, color = nfc)) +
[…]

### 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
corrected sca reporting

@@
 INSERT FIGURE 2 HERE
-<!--
 ```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
@@
 
-  include_graphics(here("06_Paper", "Stage 2", "Figures", "sca-plot.png"))
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
 
 ```
--->
 
 Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
-The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors and the largest effect of *n*-back level.
+The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors.
 These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
-The by far highest values of the beta of the median RT in Figure\ \@ref(fig:sca-plot) are all from the pipelines that used inverse transformation.
 
@@
 INSERT FIGURE 3 HERE
-<!--
+
 ```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level.
@@
 
-  include_graphics(here("06_Paper", "Stage 2", "Figures", "nfc-sv.png"))
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfc-sv.png"))
 
 ```
--->
 
@@
 
-  include_graphics(here("06_Paper", "Stage 2", "Figures", "h3a-plot.png"))
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))
 
@@
 The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
-The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit small.
-In both cases, the SVs decreased when the value of the predictor increased.
+The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit less.
+With increasing *n*-back level and decreasing *d'*, the SV decreased.
 The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not *d'* yielded significant differences across levels in the manipulation checks.

### 2023-03-01 06_Paper/COG-ED/Stage 2/Analysis.R
added model comparison anova

@@ -1259,6 +1259,7 @@ h2b_data <- pipelines_data[["AARO"]][ ,c("subject","level","round","sv","dprime"
 
 h2b_data$dprime.cwc <- h2b_data$dprime - (ave(h2b_data$dprime, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
 h2b_data$medianRT.cwc <- h2b_data$medianRT - (ave(h2b_data$medianRT, h2b_data$subject, FUN = function(x) mean(x, na.rm = T)))
+h2b_data$levellin <- h2b_data$level
 
 # turn into factor
 
@@ -1303,6 +1304,15 @@ h2b_data_excl <- droplevels(subset(h2b_data, abs(scale(resid(model1_h2b_raw))) <
 
 model1_h2b <- lmerTest::lmer(sv ~ level + dprime.cwc + medianRT.cwc + (1|subject),
                              data = h2b_data_excl, REML = T)
+
+# compute linear model to compare it with logistic model
+
+linmodel_h2b <- lmerTest::lmer(sv ~ levellin + dprime.cwc + medianRT.cwc + (1|subject),
+                               data = h2b_data_excl, REML = T, control = lmerControl(optimizer = "bobyqa"))
+
+# compare the linear and the logistic model
+
+compare_h2b <- anova(linmodel_h2b, model1_h2b)
 
 # to plot some fit indices if you like
 #sjPlot::plot_model(model1_h2b, type = "diag")

### 2023-03-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added model comparison anova results

@@
 
+We used an ANOVA to compare the fit of the final model with a linear random intercept model.
+The two models were different from each other ($\chi^2(`r compare_h2b$Df[2]`)=compare_h2b$Chisq[2]$, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model is superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
 The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
@@
 INSERT FIGURE 4 HERE
-<!--
-```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))
-
-```
--->
 

### 2023-03-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
outcommented one plot bc error

@@
 The two models were different from each other ($\chi^2(`r compare_h2b$Df[2]`)=compare_h2b$Chisq[2]$, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model is superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
-The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
+The final model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
 This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
@@
 
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
+  #include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
 

### 2023-03-01 06_Paper/COG-ED/Stage 2/Analysis.R
changed formatting of BF10 in table

@@ -930,18 +930,18 @@ hypothesis1b_contrasts <- as.data.frame(pairs(hypothesis1b_emm))
 # get Bayes factors
 
 hypothesis1b_BF <- BayesFactor::anovaBF(formula = medianRT ~ level, data = h1b_data, progress = FALSE)
-hypothesis1b_contrasts$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 1], y = h1b_data$medianRT[h1b_data$level == 2],
-                                                                             progress = FALSE, paired = TRUE))$bf,
-                                 BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 1], y = h1b_data$medianRT[h1b_data$level == 3],
-                                                                             progress = FALSE, paired = TRUE))$bf,
-                                 BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 1], y = h1b_data$medianRT[h1b_data$level == 4],
-                                                                             progress = FALSE, paired = TRUE))$bf,
-                                 BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 2], y = h1b_data$medianRT[h1b_data$level == 3],
-                                                                             progress = FALSE, paired = TRUE))$bf,
-                                 BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 2], y = h1b_data$medianRT[h1b_data$level == 4],
-                                                                             progress = FALSE, paired = TRUE))$bf,
-                                 BayesFactor::extractBF(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 3], y = h1b_data$medianRT[h1b_data$level == 4],
-                                                                             progress = FALSE, paired = TRUE))$bf)
+hypothesis1b_contrasts$BF10 <- c(apa_print(BayesFactor::ttestBF(x = h1b_data$medianRT[h1b_data$level == 1], y = h1b_data$medianRT[h1b_data$level == 2],
+                                                                             progress = FALSE, paired = TRUE))$table[1,"statistic"],
[…]

### 2023-03-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed cursive formatting

--- 2023-02-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
@@
 
-keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, *n*-back"
+keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, $n$-back"
 wordcount         : "~ 4,300"
@@
 
-One task that is often used to investigate effort is the *n*-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
-Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six[@Mackworth1959].
-The *n*-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times[@Jaeggi2010], and brain activity in areas associated with working memory[@Jonides1997; @Owen2005].
-However, its reliability measures are mixed, and associations of *n*-back performance and measures such as executive functioning and fluid intelligence are often inconsistent[@Jaeggi2010].
+One task that is often used to investigate effort is the $n$-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
+Participants indicate via button press whether the current stimulus is the same as $n$ stimuli before, with $n$ being the level of difficulty between one and six[@Mackworth1959].
+The $n$-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times[@Jaeggi2010], and brain activity in areas associated with working memory[@Jonides1997; @Owen2005].
+However, its reliability measures are mixed, and associations of $n$-back performance and measures such as executive functioning and fluid intelligence are often inconsistent[@Jaeggi2010].
 
-A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
-First, the participants complete the *n*-back levels to familiarize themselves with the task.
+A way to quantify the subjective cost of each $n$-back level has been developed by Westbrook, Kester, and Braver[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+First, the participants complete the $n$-back levels to familiarize themselves with the task.
 Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
@@
 
-With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
-We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
+With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest $n$-back level has the highest SV.
+We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different $n$-back levels without presuming that all individuals inherently prefer the easiest level.
 Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
 In the present study, we validated the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
-Additionally, we compared the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
+Additionally, we compared the effort discounting behavior of participants regarding the $n$-back task and an emotion regulation task.
 The full results of the latter are published in a second Registered Report[@ScheffelZerna2022].
@@
 Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
-As a manipulation check, we hypothesized that with increasing *n*-back level the (1a) the signal detection parameter *d'* declines, while (1b) reaction time and (1c) perceived task load increase.
-Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
+As a manipulation check, we hypothesized that with increasing $n$-back level the (1a) the signal detection parameter $d'$ declines, while (1b) reaction time and (1c) perceived task load increase.
+Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing $n$-back level, and (2b) they do so even after controlling for declining task performance.
 And finally, we hypothesized that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
@@
 <!--
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an *n*-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
-The paradigm started with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The paradigm started with the $n$-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
 The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
 To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this *n*-back level.
-After the *n*-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
-They were told that one of their choices would be randomly picked for the final run of *n*-back, the data of which was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
+At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this $n$-back level.
+After the $n$-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
+They were told that one of their choices would be randomly picked for the final run of $n$-back, the data of which was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
 After the CAD paradigm, participants filled out a short questionnaire on the tablet, indicating whether they adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
@@
 Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)).
-The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and *n*-back level influencing SVs.
+The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and $n$-back level influencing SVs.
 Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
@@
 No data was replaced.
-The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
+The performance measure $d'$ was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
 Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
@@
 *Manipulation check.*
-Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
+Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing $d'$ between two levels of 1- to 4-back at a time.
 Another rmANOVA with six paired contrasts was computed to compare the median RT between two levels of 1- to 4-back at a time.
@@
 All SVs of each level were averaged to compute one "global" SV for each level.
-An rmANOVA with four different contrasts were computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
+An rmANOVA with four different contrasts were computed to investigate the association of SVs and the $n$-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
 Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.
 
-To determine the influence of task performance on the association of SVs and *n*-back level, we performed MLM. 
+To determine the influence of task performance on the association of SVs and $n$-back level, we performed MLM. 
 We applied restricted maximum likelihood (REML) to fit the model.
 As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we estimated a random slopes model of *n*-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
-As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher *n*-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
-We controlled for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
+Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
+As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher $n$-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
+We controlled for performance, i.e., $d'$ (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
 $$
@@
 This was done by excluding all data points with absolute standardized residuals above 3 SD. 
-As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of *n*-back level according to Lorah[-@Lorah2018].
-To ensure the validity of the association of SVs and *n*-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
+As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].
+To ensure the validity of the association of SVs and $n$-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within $n$-back levels).
 The rmANOVA was run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
@@
 The sample was divided into participants with low and high NFC using a median split.
-We then computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
+We then computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
 Post-hoc tests were computed depending on which effect reached significance at $p<.01$.
@@
 The association of subjective task load with NFC was examined similarly.
-We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
+We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
 And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e.
@@
 We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
-Then, we computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
+Then, we computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
 
-The results of each analysis was assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *ttestBF*.
-We considered a $BF10$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF10$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].
+The results of each analysis was assessed on the basis of both $p$-value and the Bayes factor $BF_{10}$, calculated with the *BayesFactor* package[@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *ttestBF*.
+We considered a $BF_{10}$ close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a $BF_{10}$ close to or below .33/.10 as moderate/strong evidence for the null hypothesis [@Wetzels2015].
 
@@
 Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=14$ data sets.
-The results showed increases in subjective and objective task load measures with higher *n*-back level.
-Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
-The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
-NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
+The results showed increases in subjective and objective task load measures with higher $n$-back level.
+Importantly, SVs were lower for higher $n$-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
+The LMM revealed $n$-back level as a reliable predictor of SV, even after controlling for declining task performance ($d'$ and median RT).
+NASA-TLX scores were higher with higher $n$, and lower for the group with lower NFC scores, but NFC and $n$-back level did not interact.
 All results are detailed in the Supplementary Material.
@@
 Data was collected between the 16th of August 2022 and the 3rd of February 2023.
-Of the $N=`r n_quest`$ participants who filled out the online questionnaires, $n=`r length(datalist_nback)`$ came to the first lab session.
-Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
+All of the $N=`r n_quest`$ participants who filled out the online questionnaires came to the first lab session.
+Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
 Our final data set therefore included $N=`r nrow(data_quest)`$ participants.
@@
 
-The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`).
+The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`).
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
-The median RT did not differ between 2-back and 4-back, and the median RT was higher for 3-back than for 4-back (Table\ \@ref(tab:H1b-contrasts)).
+It did not differ between 2- and 4-back, and it was higher for 3- than for 4-back (Table\ \@ref(tab:H1b-contrasts)).
 
@@
   hypothesis1b_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels",
-  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels",
+  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-All NASA-TLX subscale scores increased across *n*-back levels.
+All NASA-TLX subscale scores increased across $n$-back levels.
 The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
 Three subscales had significant differences between all contrasts except for 3- versus 4-back:
-While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher *n* (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
+While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
 Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
@@
 
-When asking participants what motivated their decisions in the effort discounting, `r round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted to avoid boredom, `r round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted a challenge, `r round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted to avoid effort, and `r round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1)`% stated that they wanted to relax.
-The remaining `r round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
-The rmANOVA showed a significant difference between the SVs across *n*-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
+When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
+The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
+The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
 All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.
@@
   hypothesis2a_contrasts,
-  caption = "Contrasts for the rmANOVA comparing the subjective values between *n*-back levels",
+  caption = "Contrasts for the rmANOVA comparing the subjective values between $n$-back levels",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
 
-The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("decl_log" =c(3,2,-2,-3))))$full_result`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
+The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("Declining Linear" = c(3,1,-1,-3),"Ascending Quadratic" = c(-1,1,1,-1),"Declining Logistic" = c(3,2,-2,-3),"Positively Skewed Normal" = c(1,2,-1,-2))))$statistic$DecliningLogistic`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
 
 Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
-To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
+To apply the contrast to the $n$-back levels, we had to turn the variables into a factor, with two consequences:
 Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
@@
 This means that the intercept still varies between subjects, but there are no random slopes anymore.
-To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
-The ICC of the null model indicated that there is a correlation of $r=$`r round(model0_h2b_ICC, digits = 3)` between the SVs of a subject, i.e.
+To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
+The ICC of the null model indicated that there is a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
 that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
@@
 
-The model had an effect size of $f^{2}=$`r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$`r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered large and small, respectively [@Cohen1992].
-This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
-The effect size of the median RT was $f^{2}=$`r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
-The beta coefficients indicated that with every *n*-back level, the SV decreased by `r as.numeric(h2b_result.table[2,"Beta"])`, and for every 1-unit increase in *d'*, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
+An exploratory was used ANOVA to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
+The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
+This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
+The beta coefficients indicated that with every $n$-back level, the SV decreased by `r as.numeric(h2b_result.table[2,"Beta"])`, and for every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
+The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
 
@@
 
-Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
-The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors.
-These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
+Regardless of the preprocessing pipeline, $n$-back level and $d'$ were significant predictors of SVs, and had stable effect estimates across all pipelines.
+The only pipelines in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors.
+These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an $n$-back level.
 
@@
 
-Figure\ \@ref(fig:nfc-sv) shows a scatterplot of SVs per *n*-back level, colored depending on the participant's NFC score.
-There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across *n*-back levels.
-At the same time, there is a subtle separation of SVs across *n*-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
-Specifically, $n=$`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])` participants had an absolute preference for 1-back, $n=$`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])` for 2-back, $n=$`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])` for 3-back, and $n=$`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])` for 4-back.
-There were $n=$`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))` participants who did not have an absolute preference for any *n*-back level, i.e. none of their SVs was 1.
+Figure\ \@ref(fig:nfc-sv) shows a scatterplot of SVs per $n$-back level, colored depending on the participant's NFC score.
+There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across $n$-back levels.
+At the same time, there is a subtle separation of SVs across $n$-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
+Specifically, $n=`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])`$ participants had an absolute preference for 1-back, $n=`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])`$ for 2-back, $n=`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])`$ for 3-back, and $n=`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])`$ for 4-back.
+There were $n=`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))`$ participants who did not have an absolute preference for any $n$-back level, i.e. none of their SVs was 1.
 
@@
 $N=116$.
-There is a horizontal jitter of 0.4 and a vertical jitter of 0.05for visual clarity.", fig.pos="H"}
+There is a horizontal jitter of 0.4 and a vertical jitter of 0.05 for visual clarity.", fig.pos="H"}
 
@@
 
-The median NFC was `r mediannfc`, with $n=$`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))` subjects below and $n=$`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))` above the median.
+The median NFC was `r mediannfc`, with $n=`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ subjects below and $n=`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ above the median.
 We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of the *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$full_result`), but there were large interindividual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
+There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large interindividual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.
@@
 INSERT FIGURE 4 HERE
-<!--
-```{r h3a-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Difference scores in the subjective values of 1- minus 2-back and of 2- minus 3-back.", fig.pos="H"}
 
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))
-
-```
--->
-
-The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of *n*-back level (`r apa_print(hypothesis3b_model)$full_result$level`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3b_BF_levels)$bf[1], digits = 2)`) and an interaction between *n*-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3b_BF_levels)$bf[2], digits = 2)`).
-Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$full_result$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$full_result$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
-Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of *n*-back levels (**Supplement**).
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
+Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (**Supplement**).
 
 With another rmANOVA was used to investigate whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3a_BF_nlevel)$bf[2], digits = 2)`) and a main effect of the *n*-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, $BF10=$`r round(BayesFactor::extractBF(hypothesis3a_BF_nlevel)$bf[1], digits = 2)`), but no interaction.
-Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$full_result`).
-Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$full_result`), but again, there were large interindividual differences.
+There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction.
+Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`).
+Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large interindividual differences.
 
@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate subjective values of different *n*-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate subjective values of tasks without assuming that the easiest level is inherently preferred.
+This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate subjective values of tasks without assuming that the easiest level is inherently preferred.
 For this purpose, we changed the way in which the discounting options are presented to the participants, basing the anchor on their own choices rather than on the objective task load.
@@
 
-The performance measure *d'* did not differ across *n*-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
-This points to three important characteristics of the *n*-back task in this context.
+The performance measure $d'$ did not differ across $n$-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
+This points to three important characteristics of the $n$-back task in this context.
 Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate interindividual differences for $n>3$.
-Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where *d'* would decline and RT would remain stable.
+Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where $d'$ would decline and RT would remain stable.
 And lastly, the fact that neither accuracy and nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010], suggesting that they should always be reported as separate indices.
 
-All NASA-TLX subscales differed across *n*-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
-This would support the notion of the *n*-back task offering a continuous manipulation of task load, as least subjectively.
+All NASA-TLX subscales differed across $n$-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
+This would support the notion of the $n$-back task offering a continuous manipulation of task load, as least subjectively.
 Ratings on the frustration and time subscales increased and ratings on the performance subscale decreased until 3-back and then remained stable.
 This pattern is akin to the RT, which also increased and then remained stable.
-Ratings on the physical load subscale increased with *n*-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.
+Ratings on the physical load subscale increased with $n$-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.
 
@@
 
-The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across *n*-back levels.
+The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across $n$-back levels.
 The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
-The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit less.
-With increasing *n*-back level and decreasing *d'*, the SV decreased.
-The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not *d'* yielded significant differences across levels in the manipulation checks.
-However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
+The MLM with the logistic contrast showed that the $n$-back level explained the majority of variance in SVs, while the performance measure $d'$ also explained some variance in SVs, albeit less.
+With increasing $n$-back level and decreasing $d'$, the SV decreased.
+The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not $d'$ yielded significant differences across levels in the manipulation checks.
+However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per $n$-back level, as an anchor during the effort discounting.
 This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
@@
 
-*Figure 1.* An example for subjective values for an *n*-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+*Figure 1.* An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.

### 2023-03-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
with plots

@@
 INSERT FIGURE 1 HERE
-<!--
+
 ```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
@@
 
-  #include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
 

### 2023-03-02 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote SCA discussion

@@
 
+The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis, with betas that varied by less than 0.01.
+In contrast to this stood the variability of the median RT betas, which ranged from about 0.11 to -0.01, and reached significance in only three pipelines.
+These three pipelines had the highest $BF_{10}$ and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data based on the MAD.
+Interestingly, the curve of median RT betas in the upper panel of Figure\ \@ref(fig:sca-plot) mirrored the rectangular pipeline indicators in the transformation rows of the lower panel, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
+As Fernandez et al.[-@Fernandez2020] found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond $\alpha=.05$, and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
+Our data seems to corroborate this finding for $n$-back tasks as well.
+
 \newpage

### 2023-03-02 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
set papaja options

@@
   library(papaja)       # APA conform output, "papaja" package
+  options(papaja.na_string = "")
   library(kableExtra)   # for great tables in R Markdown, "kableExtra" package

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
set papaja na options

@@
 base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))
+
+options(papaja.na_string = "")
 ```

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
corrected tables

@@ -891,24 +891,24 @@ EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                        data = EMG_reg,
                                        progress = FALSE)
 
-EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     progress = FALSE, paired = FALSE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = FALSE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = FALSE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     progress = FALSE, paired = FALSE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = FALSE))$bf,
-                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
-                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
-                                                                     progress = FALSE, paired = FALSE))$bf)
+EMGCorrReg_con$BF10 <- c(papaja::apa_print(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
+                                                                y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
[…]

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
update supplement

--- 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
@@
   escape = FALSE,
-  placement = "H")
+  placement = "H"
+  )
 

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
described results for MLM

@@
 We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
-Post-hoc test showed significant higher subjective effort for distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[1,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[1,7], format = "e")`), distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[2,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[2,7], format = "e")`), and suppression ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[3,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[3,7], format = "e")`) compared to active viewing.
-Moreover, we found significantly lower effort during suppression compared with distraction ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[5,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[5,7], format = "e")`) and distancing ($\eta_{p}^{2}=`r papaja::printnum(SubjEffort_con[6,8:9])`$, $BF_{10}=$ `r papaja::printnum(SubjEffort_con[6,7])`).
+Post-hoc test showed significant higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
+Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).
 
@@
 
-The predictors effort ($p=$ `r papaja::printnum(summary(MLM_2)$coefficients[1,5])`), ...
+The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`) showed a significant association with SVs.
+The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
+Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.
+Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.
+The effect sizes of all other predictors were negligibly small ($f^{2}< 0.01$).
 

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
added MLM 3

@@ -1405,7 +1405,27 @@ Flex_LM_BF <- BayesFactor::regressionBF(formula = FlexER ~ intercept + slope, da
 
 PCA.SC <- psych::principal(data_quest[,c("bscs_sum","srs_sum","bis11_sum")], rotate="none")
 
+# fill self-control value in data_quest
 
+data_quest$SC <- PCA.SC[["scores"]][,1]
+
+# fill SC values in df data_MLM
+
+for (i in seq_len(nrow(data_MLM))) {
+  
+  data_MLM$SC[i] <- data_quest$SC[data_quest$record_id_2 == data_MLM$ID[i]]
+  data_MLM$NFC[i] <- data_quest$nfc_sum[data_quest$record_id_2 == data_MLM$ID[i]]
+}
+
+# grand mean centering of SC
+# https://philippmasur.de/2018/05/23/how-to-center-in-multilevel-models/
+
+data_MLM$SC.gmc <- data_MLM$SC - mean(data_MLM$SC)
+data_MLM$NFC.gmc <- data_MLM$NFC - mean(data_MLM$NFC)
+
+MLM_3 <- lmerTest::lmer(formula = sv ~ effort.cwc + utility.cwc + Corr.cwc + SC.gmc + (1 | ID),
+                     data = data_MLM,
+                     REML = TRUE)
 #################### SAVE WORKSPACE IMAGE #######################
 
 save.image(file = "Workspace_ERED.RData")

### 2023-03-02 06_Paper/COG-ED/Stage 2/Analysis.R
added plot and data frame for motivation

@@ -358,11 +358,17 @@ for (i in 1:nrow(data_quest)) {
 
 # add the NFC scores trial-wise to the nback data-frame
 
-data_nback <- left_join(data_nback, data_nfc, by = "subject")
+data_nback <- dplyr::left_join(data_nback, data_nfc, by = "subject")
 
 # remove the temporary variables
 
 base::remove(nfc, data_nfc)
+
+##### Motivation data frame ####################################################
+
+# combine NFC, SVs, and motivation
+
+data_motiv <- dplyr::left_join(data_SV, data_quest[,c("subject","motivation")], by = "subject")
 
 ##### Preprocessing pipelines for the SCA ######################################
 
@@ -1986,7 +1992,6 @@ sca_plot <- egg::ggarrange(sca_plot_upper, sca_plot_lower,
 
 # plot showing SVs per subject, colors depend on NFC
 
-plot_sv <-
   ggplot2::ggplot(pipelines_data[["AARO"]], aes(x = level, y = sv, group = subject, color = nfc)) +
     geom_point(size = 3, alpha = 0.8, position = position_jitter(w = 0.4, h = 0.05)) +
     ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
@@ -1994,6 +1999,15 @@ plot_sv <-
     geom_vline(xintercept = c(0.5,1.5,2.5,3.5,4.5), colour = "grey", linetype = 3) +
     xlab("n-back level") + 
     ylab("Subjective values")
+
+# plot showing SVs per level, colors depend on motivation
+
+  ggplot2::ggplot(data_motiv, aes(as.factor(level), sv, fill = as.factor(motivation), color = as.factor(motivation))) +
+    geom_boxplot(alpha = .7) +
+    ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
+    scale_fill_manual(values=c("lightskyblue", "skyblue3","blue1","blue4","gray20")) +
+    scale_color_manual(values=c("lightskyblue", "skyblue3","blue1","blue4","gray20")) +
+    labs(x = "n-back level", y = "Subjective value")
 
 ##### Save variables ###########################################################
 

### 2023-03-02 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote one more sentence in SCA disc
started NFC diff section

@@
 Our data seems to corroborate this finding for $n$-back tasks as well.
+Surprisingly, the $d'$ betas appear almost unaffected by the preprocessing pipeline, even though $d'$ was computed after the outlier exclusion.
+This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.
+
+## Differences between NFC groups
+
+The majority of participants (`r round(100*((nrow(data_SV[data_SV$level==1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ %) had an absolute preference for 1-back over the other levels, but that also means that there were `r round(100*((nrow(data_SV[data_SV$level!=1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ % who had an absolute preference for 2-, 3-, or 4-back, and `r round(100*((length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1])))/nrow(data_quest)), digits = 1)`\ % who preferred no specific level over all others.
 

### 2023-03-02 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 The second model followed the specification: 
-
 $$
@@
 ## 3.3. Exploratory analyses
+
+We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
+The starting point for this was the model reported before. 
+Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
+The third model followed the specification:
+$$
+\begin{split}
+SV \sim \text{effort rating} + \\text{utility rating} + corrugator \text{ activity} \\\ self-control + NFC + (1 |subject)
+\end{split}
+$$

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
exploratory MLM

@@ -1423,9 +1423,105 @@ for (i in seq_len(nrow(data_MLM))) {
 data_MLM$SC.gmc <- data_MLM$SC - mean(data_MLM$SC)
 data_MLM$NFC.gmc <- data_MLM$NFC - mean(data_MLM$NFC)
 
-MLM_3 <- lmerTest::lmer(formula = sv ~ effort.cwc + utility.cwc + Corr.cwc + SC.gmc + (1 | ID),
+MLM_3 <- lmerTest::lmer(formula = sv ~ effort.cwc + utility.cwc + Corr.cwc + SC.gmc + NFC.gmc + (1 | ID),
                      data = data_MLM,
                      REML = TRUE)
+
+MLM_3_r2 <- r2mlm::r2mlm(MLM_3)
+MLM3_r2 <- MuMIn::r.squaredGLMM(MLM_3, pj2014 = T)
+
+##### f² of predictors
+
+# create lists for no effect models (for better clarity)
+
+# for Models
+MLM3_no_effect <- list()
+# for R²
+MLM3_no_effect_r2 <- list()
+
+#df for f²
+MLM3_f2 <- data.frame(f2 = double())
+
+# EFFORT
+MLM3_no_effect[["e"]] <- lmerTest::lmer(sv ~ 1 + utility.cwc + Corr.cwc + SC.gmc + NFC.gmc + (1 | ID),
+                                        data = data_MLM, REML = T)
+
+MLM3_no_effect_r2[["e"]] <- MuMIn::r.squaredGLMM(MLM3_no_effect[["e"]], pj2014 = T)
+
+# compute f² with conditional R²
+
+MLM3_f2 <- rbind(MLM3_f2, (MLM3_r2[1,2] - MLM3_no_effect_r2[["e"]][1,2]) / (1 - MLM3_r2[1,2]))
+
+# UTILITY
+MLM3_no_effect[["u"]] <- lmerTest::lmer(sv ~ effort.cwc + 1 + Corr.cwc + SC.gmc + NFC.gmc + (1 | ID),
+                                        data = data_MLM, REML = T)
+
+MLM3_no_effect_r2[["u"]] <- MuMIn::r.squaredGLMM(MLM3_no_effect[["u"]], pj2014 = T)
+
+# compute f² with conditional R²
+
+MLM3_f2 <- rbind(MLM3_f2, (MLM3_r2[1,2] - MLM3_no_effect_r2[["u"]][1,2]) / (1 - MLM3_r2[1,2]))
+
[…]

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
exploratory analyses

@@
 
-The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`) showed a significant association with SVs.
+The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
@@
 $$
+As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
+In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
+However, effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
+Detailed information can be found in the [supplementary material](#SupplementExploratory).

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
table MLM exploratory

@@
 ```
+
+\newpage
+
+## Exploratory analysis: Association between SVs and self-control and NFC
+
+``` {r TabExp, echo=FALSE, message=FALSE, warning=FALSE} 
+papaja::apa_table(
+  Exp_M3_table,
+  caption = "Exploratory analysis: Results of MLM predicting SVs of ER strategies with level 2 predictors self-control and NFC.",
+  booktabs = TRUE,
+  escape = FALSE,
+  placement = "H")
+```

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\)).
-Post-hoc test showed significant higher subjective effort for distraction (\(\eta_{p}^{2}=0.47, [0.42, 1.00]\), \(BF_{10}=\) \(3.61 \times 10^{30}\)), distancing (\(\eta_{p}^{2}=0.41, [0.35, 1.00]\), \(BF_{10}=\) \(1.60 \times 10^{28}\)), and suppression (\(\eta_{p}^{2}=0.30, [0.23, 1.00]\), \(BF_{10}=\) \(1.27 \times 10^{19}\)) compared to active viewing.
-Moreover, we found significantly lower effort during suppression compared with distraction (\(\eta_{p}^{2}=0.08, [0.04, 1.00]\), \(BF_{10}=\) \(1.61 \times 10^{6}\)) and distancing (\(\eta_{p}^{2}=0.03, [0.01, 1.00]\), \(BF_{10}=\) 29.19).
+Post-hoc test showed significant higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
+Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).
 
@@
 The ICC of the null model was \(ICC=\) 0.19, indicating that level-2 predictor subject accounted for 19.10 percent of total variance.
-The preregistered model showed a correlation of \(r=\) 0.95 of the random effects subjects and recoded strategy.
-In addition with the estimation that our model explained 0.90 percent of variance, we assumed our model was overfitted due to inclueding recoded strategy as random slope.
-We therefore set a new model without the recoded strategy as random slope factor, that followed the specification:
-
+The preregistered model showed a correlation of \(r=\) 0.95 of the random effects subjects and recoded strategy (\(BF10\) of the variable strategy: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
+Our model explained 0.90 percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
+We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
+The second model followed the specification:
 \[
@@
 
+The second model explained 0.41 percent of variance.
+All results of the second model are in table~@ref(tab:TabMLM\_H5).
+
 \begin{table}[H]
@@
 
-\begin{tabular}{lllll}
+\begin{tabular}{llllll}
 \toprule
-Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{Random Effects (SD)}\\
+Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
 \midrule
-Intercept & 0.80 & 0.01 & 0.00 & 0.12\\
-Strategy & -0.22 & 0.01 & 0.00 & 0.14\\
-Effort & 0.00 & 0.00 & 0.00 & \\
-Arousal & 0.00 & 0.00 & 0.00 & \\
-Utility & 0.00 & 0.00 & 0.00 & \\
-Corrugator activity & 0.00 & 0.00 & 0.17 & \\
-Levator activity & 0.00 & 0.00 & 0.90 & \\
+Intercept & $8.03 \times 10^{-1}$ & 0.01 & 0.00 &  & 0.11\\
+Effort & $-6.85 \times 10^{-4}$ & 0.00 & 0.00 & 0.03 & \\
+Arousal & $-7.84 \times 10^{-5}$ & 0.00 & 0.32 & 0.00 & \\
+Utility & $1.42 \times 10^{-3}$ & 0.00 & 0.00 & 0.15 & \\
+Corrugator activity & $7.45 \times 10^{-3}$ & 0.00 & 0.04 & 0.00 & \\
+Levator activity & $5.32 \times 10^{-3}$ & 0.00 & 0.07 & 0.00 & \\
 \bottomrule
@@
 \end{table}
+
+The predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
+The values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
+Interestingly, utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5 percent of variance in SVs.
+Effort rating showed an effect size of \(f^{2}=\) 0.035.
+The effect sizes of all other predictors were negligibly small (\(f^{2}< 0.01\)).
 
@@
 \subsection{3.3. Exploratory analyses}\label{exploratory-analyses}}
+
+We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
+The starting point for this was the model reported before.
+Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
+The third model followed the specification:
+\[
+\begin{split}
+SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
+\end{split}
+\]
+As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant association with SVs.
+In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
+However, effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
+Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.
 
@@
 
-\footnotesize{
+\small{
 
@@
 $View_{neg} - Distancing$ & 0.19 & 0.04 & 351.00 & 5.09 & 0.00 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
-$View_{neg} - Suppression$ & 0.21 & 0.04 & 351.00 & 5.67 & 0.00 & 18,426,055.49 & 0.08 & {}[0.04, 1.00]\\
-$Distraction - Distancing$ & 0.01 & 0.04 & 351.00 & 0.30 & 1.00 & 0.04 & 2.61e-04 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.03 & 0.04 & 351.00 & 0.88 & 1.00 & 0.08 & 2.21e-03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.02 & 0.04 & 351.00 & 0.58 & 1.00 & 0.05 & 9.51e-04 & {}[0.00, 1.00]\\
+$View_{neg} - Suppression$ & 0.21 & 0.04 & 351.00 & 5.67 & 0.00 & $1.84 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
+$Distraction - Distancing$ & 0.01 & 0.04 & 351.00 & 0.30 & 1.00 & $3.77 \times 10^{-2}$ & 2.61e-04 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 0.03 & 0.04 & 351.00 & 0.88 & 1.00 & $8.02 \times 10^{-2}$ & 2.21e-03 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 0.02 & 0.04 & 351.00 & 0.58 & 1.00 & $4.79 \times 10^{-2}$ & 9.51e-04 & {}[0.00, 1.00]\\
 \bottomrule
@@
 \midrule
-$View_{neg} - Distraction$ & 0.34 & 0.05 & 351.00 & 6.73 & 0.00 & 202,428,623,285.88 & 0.11 & {}[0.07, 1.00]\\
-$View_{neg} - Distancing$ & 0.28 & 0.05 & 351.00 & 5.66 & 0.00 & 39,887,367.63 & 0.08 & {}[0.04, 1.00]\\
-$View_{neg} - Suppression$ & 0.32 & 0.05 & 351.00 & 6.37 & 0.00 & 86,036,487,908.69 & 0.10 & {}[0.06, 1.00]\\
+$View_{neg} - Distraction$ & 0.34 & 0.05 & 351.00 & 6.73 & 0.00 & $2.02 \times 10^{11}$ & 0.11 & {}[0.07, 1.00]\\
+$View_{neg} - Distancing$ & 0.28 & 0.05 & 351.00 & 5.66 & 0.00 & $3.99 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
+$View_{neg} - Suppression$ & 0.32 & 0.05 & 351.00 & 6.37 & 0.00 & $8.60 \times 10^{10}$ & 0.10 & {}[0.06, 1.00]\\
 $Distraction - Distancing$ & -0.05 & 0.05 & 351.00 & -1.07 & 1.00 & 0.22 & 3.26e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -0.02 & 0.05 & 351.00 & -0.36 & 1.00 & 0.04 & 3.70e-04 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.04 & 0.05 & 351.00 & 0.71 & 1.00 & 0.10 & 1.44e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & -0.02 & 0.05 & 351.00 & -0.36 & 1.00 & $3.91 \times 10^{-2}$ & 3.70e-04 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 0.04 & 0.05 & 351.00 & 0.71 & 1.00 & $9.86 \times 10^{-2}$ & 1.44e-03 & {}[0.00, 1.00]\\
 \bottomrule
@@
 
+\newpage
+
+\hypertarget{exploratory-analysis-association-between-svs-and-self-control-and-nfc}{%
+\subsection{Exploratory analysis: Association between SVs and self-control and NFC}\label{exploratory-analysis-association-between-svs-and-self-control-and-nfc}}
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:TabExp}Exploratory analysis: Results of MLM predicting SVs of ER strategies with level 2 predictors self-control and NFC.}
+
+\begin{tabular}{llllll}
+\toprule
+Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
+\midrule
+Intercept & $8.03 \times 10^{-1}$ & 0.01 & 0.00 &  & 0.11\\
+Effort & $-6.93 \times 10^{-4}$ & 0.00 & 0.00 & 0.04 & \\
+Utility & $1.44 \times 10^{-3}$ & 0.00 & 0.00 & 0.20 & \\
+Corrugator activity & $7.54 \times 10^{-3}$ & 0.00 & 0.03 & 0.00 & \\
+Self-Control & $2.44 \times 10^{-2}$ & 0.01 & 0.04 & 0.00 & \\
+NFC & $7.58 \times 10^{-4}$ & 0.00 & 0.44 & 0.00 & \\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \end{document}

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected formula
added descriptive information on SVs

@@
 
+Individual SVs could be determined for `r nrow(data_SV)/3` participants for all three ER strategies.
+SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
+In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had a SVs of 1.0, indicating a clear preference for one ER strategy.
+Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`.
+
 To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
@@
 \begin{split}
-SV \sim \text{effort rating} + \\text{utility rating} + corrugator \text{ activity} \\\ self-control + NFC + (1 |subject)
+SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
 \end{split}

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
Cross referece for Table 1

@@
 In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had a SVs of 1.0, indicating a clear preference for one ER strategy.
+Absolute preferences for ER strategies were relatively equally distributed.
 Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`.
@@
 The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance. 
-All results of the second model are in table\ \@ref(tab:TabMLM_H5).
+All results of the second model are in table\ \@ref(tab:TabMLMH5).
 
-``` {r TabMLM_H5, echo=FALSE, message=FALSE, warning=FALSE}
+[INSERT TABLE 1 HERE]
+
+``` {r TabMLMH5, echo=FALSE, message=FALSE, warning=FALSE}
 papaja::apa_table(

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 
+{[}INSERT FIGURE 1 HERE{]}
+
 \begin{figure}
@@
 
+{[}INSERT FIGURE 2 HERE{]}
+
 \begin{figure}
@@
 
+Individual SVs could be determined for 120 participants for all three ER strategies.
+SVs ranged between 0.005 and 1.00.
+In sum, \(n=\) 119 had a SVs of 1.0, indicating a clear preference for one ER strategy.
+Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 36.
+
 To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
@@
 The second model explained 0.41 percent of variance.
-All results of the second model are in table~@ref(tab:TabMLM\_H5).
+All results of the second model are in table~\ref{tab:TabMLMH5}.
+
+{[}INSERT TABLE 1 HERE{]}
 
@@
 
-\caption{\label{tab:TabMLM_H5}Results of multilevel model predicting subjective values of ER strategies.}
+\caption{\label{tab:TabMLMH5}Results of multilevel model predicting subjective values of ER strategies.}
 
@@
 
-\small{
+\footnotesize{
 

### 2023-03-03 06_Paper/COG-ED/Stage 2/Analysis.R
added legend title code

@@ -1951,7 +1951,8 @@ sca_plot_lower <-
                                                                 "None", "2 MAD from median", " 2.5 MAD from median",
                                                                 "3 MAD from median", "100ms after onset", "200ms after onset")) +
     scale_fill_gradientn(colors = MetBrewer::met.brewer("Homer2")) +
-    guides(fill = guide_colourbar(barwidth = 1, barheight = 15, title = "BF10"))
+    guides(fill = guide_colourbar(barwidth = 1, barheight = 15, title = expression(BF[10]))) +
+    theme(legend.title = element_text())
 
 # reshape into useful format
 
@@ -1976,11 +1977,12 @@ sca_plot_upper <-
   geom_point(aes(x = xaxis, y = beta, color = as.factor(sign), shape = predictor),
              size = 3) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
-  labs(x = NULL, y = "beta") +
+  labs(x = NULL, y = "beta", color = "p-value", shape = "Predictor") +
   scale_x_continuous(labels = NULL) +
   scale_color_manual(labels = c("p > .05", "p < .05", "p < .01"), values = c("darkgray","darkturquoise","deepskyblue4")) +
   scale_shape_manual(labels = c("d'","n-back level","median RT"), values = c(18,17,19)) +
-  scale_y_continuous(breaks = c(0,0.05,0.1))
+  scale_y_continuous(breaks = c(0,0.05,0.1)) +
+  theme(legend.title = element_text())
 
 # combine into panel
 
@@ -1995,10 +1997,11 @@ sca_plot <- egg::ggarrange(sca_plot_upper, sca_plot_lower,
   ggplot2::ggplot(pipelines_data[["AARO"]], aes(x = level, y = sv, group = subject, color = nfc)) +
     geom_point(size = 3, alpha = 0.8, position = position_jitter(w = 0.4, h = 0.05)) +
     ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
-    scale_color_gradient2(midpoint = mediannfc, low = "chartreuse3", mid = "lightgray", high = "darkorchid3", space = "Lab") +
+    scale_color_gradient2(midpoint = mediannfc, low = "chartreuse3", mid = "lightgray", high = "darkorchid3", space = "Lab", name = "NFC") +
[…]

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`). 
+There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).
+
+[INSERT FIGURE 3 HERE]
+
+```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block.
+Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
+$N=120$", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
+```
+
 We then conducted a ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added figure effort

@@
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
+We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref{fig:FigSubjEffort}).
 Post-hoc test showed significant higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).
+
+```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Boxplot visualizing subjective effort ratings for $N=120$", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
+```
 

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
updated figures
look how beautiful they are!

@@ -849,15 +849,17 @@ SubjArousalReg_con[6, 1] <- "$Distancing - Suppression$"
 
 # figure
 FigSubjArousalReg <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal, fill = factor(block))) +
-  ggdist::stat_halfeye(adjust = 0.5, justification = -0.2, .width = 0, point_colour = NA, limits = c(.05, .95)) +
+  ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.7, color = NA) +
+  ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
   geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.5)+
-  geom_point(size = 1, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2), aes(col = factor(block)))+
+  #geom_point(size = 1, alpha = 0.75, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2), aes(col = factor(block)))+
   ggthemes::scale_fill_tableau(palette = "Tableau 10")+
   ggthemes::scale_color_tableau(palette = "Tableau 10")+
+  #geom_vline(xintercept = c(1.5,2.5,3.5,4.5), colour = "grey", linetype = 3) +
   scale_x_discrete(name = "Strategy",
                    limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                    labels = c("View", "Distraction", "Distancing", "Suppression")) +
-  theme_minimal() +
+  ylab("Arousal rating")+
   theme(legend.position = "none")
 
 
@@ -929,16 +931,18 @@ EMGCorrReg_con[6, 1] <- "$Distancing - Suppression$"
 # 
 EMG_reg_plot <- EMG_reg %>% group_by(ID, block) %>% summarise_at(vars("Corr","Lev"), list(mean))
 
-FigEMGCorrReg <- ggplot2::ggplot(EMG_reg_plot, aes(x = block, y = Corr, fill = block)) +
-  geom_boxplot(width = 0.2, alpha = .95) +
-  geom_jitter(size = .3, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2), alpha = .3)+
-  see::geom_violinhalf(position = position_nudge(x = .12), alpha = .3) +
[…]

### 2023-03-03 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

@@
 The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
+**Figure XX in the Supplement** shows the different motivations in the context of the SVs per $n$-back level.
+
 The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
@@
         align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
-    kable_styling(latex_options = c("striped")) %>%
     footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
@@
 
-With another rmANOVA was used to investigate whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
+With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
 There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction.
@@
 The majority of participants (`r round(100*((nrow(data_SV[data_SV$level==1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ %) had an absolute preference for 1-back over the other levels, but that also means that there were `r round(100*((nrow(data_SV[data_SV$level!=1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ % who had an absolute preference for 2-, 3-, or 4-back, and `r round(100*((length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1])))/nrow(data_quest)), digits = 1)`\ % who preferred no specific level over all others.
+It shows that when given the choice, there is a large number of participants who do not prefer the easiest level, confirming the necessity of an effort discounting paradigm that works independent of the objective task load.
+The CAD paradigm provides the means to depict these preferences.
+
+Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
+This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for $4$-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
+The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
+This demonstrates that higher $n$-back levels have a higher discriminatory power regarding interindividual differences in subjective effort perception.
+This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
 

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
updated ggdist args

@@ -932,7 +932,7 @@ EMGCorrReg_con[6, 1] <- "$Distancing - Suppression$"
 EMG_reg_plot <- EMG_reg %>% group_by(ID, block) %>% summarise_at(vars("Corr","Lev"), list(mean))
 
 FigEMGCorrReg <- ggplot2::ggplot(EMG_reg_plot, aes(x = block, y = Corr, fill = factor(block))) +
-  ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.7, color = NA) +
+  ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.8, color = NA) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
   geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.5)+
   #geom_point(size = 1, alpha = 0.75, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2), aes(col = factor(block)))+
@@ -1003,7 +1003,7 @@ EMGLevReg_con[6, 1] <- "$Distancing - Suppression$"
 
 # figure
 FigEMGLevReg <- ggplot2::ggplot(EMG_reg_plot, aes(x = block, y = Lev, fill = factor(block))) +
-  ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.7, color = NA) +
+  ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.9, color = NA) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
   geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.5)+
   #geom_point(size = 1, alpha = 0.75, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2), aes(col = factor(block)))+
@@ -1080,7 +1080,7 @@ SubjEffort_con[6, 1] <- "$Distancing - Suppression$"
 # Figure to visualize effort ratings across blocks
 
 FigSubjEffort <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort, fill = factor(block))) +
-  ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.7, color = NA) +
[…]

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Figures.Rmd
created rmd file for figures

--- 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
@@
 ---
-title             : "Estimating individual subjective values of emotion regulation strategies"
-shorttitle        : "Subjective values of emotion regulation strategies"
-author:
-  - name          : "Christoph Scheffel"
-    orcid         : "0000-0001-5963-9229"
-    affiliation   : "1"
-    corresponding : yes
-    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
-    email         : "christoph_scheffel@tu-dresden.de"
-    equal_contrib : yes
-    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Methodology
-      - Funding acquisition
-      - Formal analysis
-      - Investigation
-      - Project administration
-      - Software
-      - Visualization
-      - Writing - original draft preparation
-      - Writing - review & editing
-  - name          : "Josephine Zerna"
-    orcid         : "0000-0003-2892-884X"
-    affiliation   : "1"
-    equal_contrib : yes
-    role          :
-      - Conceptualization
-      - Methodology
-      - Funding acquisition
-      - Investigation
-      - Project administration
-      - Software
-      - Visualization
-      - Writing - review & editing
-  - name          : "Anne Gärtner"
-    orcid         : "0000-0003-4296-963X"
-    affiliation   : "1"
-    role          :
-      - Formal analysis
-      - Writing - review & editing
-  - name          : "Denise Dörfel"
-    orcid         :
-    affiliation   : "1"
-    role          :
-      - Conceptuatlization
-      - Writing - review & editing
-  - name          : "Alexander Strobel"
-    orcid         : "0000-0002-9426-5397"
-    affiliation   : "1"
-    role          :
-      - Conceptualization
-      - Methodology
-      - Writing - review & editing 
-affiliation       :
-  - id            : "1"
-    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
-authornote        :
-abstract          : |
- Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly. 
- In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable. 
- Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort. 
- Perceived costs of ER strategies in the form of effort, however, are highly subjective. 
- Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort. 
- However, SVs of ER strategies have not been determined so far. 
- We present a paradigm that is suitable for determining individual SVs of ER strategies. 
- Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
- Relations of SVs to personality traits will be explored.
-keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "XXXXX"
-bibliography      : ["ER_ED.bib"]
-floatsintext      : yes
-figsintext        : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
-csl               : nature.csl
-header-includes   :
-    - \usepackage{booktabs}
-    - \usepackage{longtable}
-    - \usepackage{array}
-    - \usepackage{multirow}
-    - \usepackage{wrapfig}
-    - \usepackage{float}
-    - \usepackage{colortbl}
-    - \usepackage{pdflscape}
-    - \usepackage{tabu}
-    - \usepackage{threeparttable}
-    - \usepackage{threeparttablex}
-    - \usepackage[normalem]{ulem}
-    - \usepackage{makecell}
-    - \usepackage{xcolor}
-    - \usepackage{setspace}\doublespacing
-    - \usepackage[final]{pdfpages}
-    - \usepackage{chngcntr}
-editor_options: 
-  markdown: 
-    wrap: sentence
+title: "Figures"
+author: "Christoph Scheffel"
+output: html_document
 ---
 
-```{=tex}
-\renewcommand\thesection{\Alph{section}}
-\counterwithout{figure}{section}
-\setcounter{figure}{0}
-```
+```{r SetupFigures, include = FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 
-------------------------------------------------------------------------
-
-```{r setupManuscript, echo=FALSE, message=FALSE, warning=FALSE}
-
-library(knitr)
-# set knitr options
-knitr::opts_chunk$set(out.width = "\\textwidth")
-
-# load libraries
-library(here) # for path independent file referencing
+library(here)       # to set directories without defined paths
 # set top level directory to source file
@@
 
-library(papaja) # APA conform output
-library(kableExtra) # for tables in R Markdown
-#library(BayesFactor) # for bayes factors
+library(tidyverse)
 
@@
 
+options(papaja.na_string = "")
 ```
 
-```{r child = "TheoreticalBackground.Rmd"}
-```
-
-```{r child = "Method.Rmd"}
-```
-
-```{r child = "Results.Rmd"}
-```
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-```{=tex}
-\endgroup
-```
-\newpage
-
-# Acknowledgements
-
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
-Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-Applications for the centralized funds will be reviewed in May.
-Regardless of whether or not this additional funding will be granted, the study can commence immediately.
-The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-
-# Competing Interests
-
-The authors declare no competing interests.
-
-```{=tex}
-\newpage
-\setcounter{figure}{0}
-```
 # Figures and figure captions
-
-\newpage
 
@@
 Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
-
-# Design Table {#DesignTable}
-
-\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
-
-\newpage
-
-```{r child = "Supplement.Rmd"}
-```

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added figures

--- 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see [supplementary material](#SupplementEffectER).
+For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in [supplementary material](#SupplementEffectER).
 
@@
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`).
+We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
 Post-hoc test showed significant higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).
+
+[INSERT FIGURE 3 HERE]
+
+```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 qantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
+```
 
@@
 
-[INSERT FIGURE 3 HERE]
+[INSERT FIGURE 4 HERE]
 
@@
 $$
-As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
+As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
 In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).

### 2023-03-03 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added even vs odd to discussion

@@
 Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing $n$-back level, and (2b) they do so even after controlling for declining task performance.
-And finally, we hypothesized that the CAD paradigm can show interindividual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
+And finally, we hypothesized that the CAD paradigm can show inter-individual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
 Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.
@@
 There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large interindividual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.
@@
 Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`).
-Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large interindividual differences.
+Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
 
@@
 This points to three important characteristics of the $n$-back task in this context.
-Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate interindividual differences for $n>3$.
+Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate inter-individual differences for $n>3$.
 Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where $d'$ would decline and RT would remain stable.
 And lastly, the fact that neither accuracy and nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010], suggesting that they should always be reported as separate indices.
+Additionally, $d'$ might not have differed across $n$-back levels because the manipulation of task load is not strictly continuous.
+Several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when $n$ was an even number than when $n$ was an odd number.
 
@@
 The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across $n$-back levels.
-The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more interindividual variance for 3- and 4-back.
+The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more inter-individual variance for 3- and 4-back.
 The MLM with the logistic contrast showed that the $n$-back level explained the majority of variance in SVs, while the performance measure $d'$ also explained some variance in SVs, albeit less.
@@
 The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
-This demonstrates that higher $n$-back levels have a higher discriminatory power regarding interindividual differences in subjective effort perception.
+This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
 This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd

@@
 ```
-# Figures and figure captions
 
-\newpage
-
-```{r ResponsePatternsAppendix, echo = FALSE, message = FALSE, warning = FALSE}
-include_graphics(here("06_Paper","ER-ED", "ERED_Stage2", "figures", "Paradigm_Scheme_T2.png" ))
+```{r child = "Figures.Rmd"}
 ```
-
-*Figure 1.* Exemplary visualization of two response patterns.
-In the top half, the person has a clear preference for one of the three strategies.
-In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can also be represented by our paradigm.
-
-```{r DesignEREDappendix, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
-include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
-```
-
-*Figure 2.* Block design of the paradigm.
-Every participant starts with two "active viewing" blocks containing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
-After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared.
-Before the last block, participants can decide which regulation strategy they want to reapply.
-Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
 

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

@@
 We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see \protect\hyperlink{SupplementEffectER}{supplementary material}.
+For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in \protect\hyperlink{SupplementEffectER}{supplementary material}.
 
@@
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\)).
+We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\); see figure~\ref{fig:FigSubjEffort}).
 Post-hoc test showed significant higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).
+
+{[}INSERT FIGURE 3 HERE{]}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigSubjEffort} \caption{Subjective effort ratings vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 qantiles.}\label{fig:FigSubjEffort}
+\end{figure}
 
@@
 In sum, \(n=\) 119 had a SVs of 1.0, indicating a clear preference for one ER strategy.
+Absolute preferences for ER strategies were relatively equally distributed.
 Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 36.
@@
 Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 120) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
+There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 120) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see figure~\ref{fig:FigSVchoice}).
+
+{[}INSERT FIGURE 4 HERE{]}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigSVChoice} \caption{Individual subjective values per ER strategy, grouped by choice in last experimental block.
+Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
+$N=120$}\label{fig:FigSVChoice}
+\end{figure}
+
 We then conducted a ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
@@
 \]
-As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant association with SVs.
+As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant association with SVs.
 In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
@@
 \section{Figures and figure captions}\label{figures-and-figure-captions}}
-
-\newpage
 
@@
 
-\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on subjective arousal ratings.}
+\caption{\label{tab:SupplEffectArousalReg}Post-hoc tests for effects of ER strategies on subjective arousal ratings.}
 
@@
 
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigSubjArousal} \caption{Subjective arousal ratings vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 qantiles.}\label{fig:SupplFigArousalReg}
+\end{figure}
+
 \begin{table}[H]
@@
 
-\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Corrugator activity}
+\caption{\label{tab:SupplEffectCorrReg}Post-hoc tests for effects of ER strategies on Corrugator activity}
 
@@
 
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigCorrReg} \caption{Corrugator activity in mV vizalized as boxplots.
+Dots represent individual Levatorr activity measures placed in 150 qantiles.}\label{fig:SupplFigCorrReg}
+\end{figure}
+
 \begin{table}[H]
@@
 
-\caption{\label{tab:SupplEffectER}Post-hoc tests for effects of ER strategies on Levator activity}
+\caption{\label{tab:SupplEffectLevReg}Post-hoc tests for effects of ER strategies on Levator activity}
 
@@
 
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigLevReg} \caption{Levator activity in mV vizalized as boxplots.
+Dots represent individual Levator activity measures placed in 150 qantiles.}\label{fig:SupplFigLevReg}
+\end{figure}
+
 \newpage

### 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd

--- 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
@@
 
-``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
+``` {r SupplEffectArousalReg, echo=FALSE, message=FALSE, warning=FALSE} 
 papaja::apa_table(
@@
   escape = FALSE,
-  placement = "H"
+  placement = "H",
+  font_size = "footnotesize"
   )
+```
 
+``` {r SupplFigArousalReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 qantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjArousal.png"))
+```
+
+``` {r SupplEffectCorrReg, echo=FALSE, message=FALSE, warning=FALSE}
 papaja::apa_table(
@@
   escape = FALSE,
-  placement = "H"
+  placement = "H",
+  font_size = "footnotesize"
   )
+```
 
+``` {r SupplFigCorrReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV vizalized as boxplots.
+Dots represent individual Levatorr activity measures placed in 150 qantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigCorrReg.png"))
+```
+
+``` {r SupplEffectLevReg, echo=FALSE, message=FALSE, warning=FALSE}
 papaja::apa_table(
@@
   escape = FALSE,
-  placement = "H"
+  placement = "H",
+  font_size = "footnotesize"
   )
 
+```
+
+``` {r SupplFigLevReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV vizalized as boxplots.
+Dots represent individual Levator activity measures placed in 150 qantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigLevReg.png"))
 ```

### 2023-03-03 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
limitations

@@
 This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
-The beta coefficients indicated that with every $n$-back level, the SV decreased by `r as.numeric(h2b_result.table[2,"Beta"])`, and for every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
+The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
 The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
@@
 
+## Limitations
+
+When developing a new paradigm, it is challenging to decide on the optimal analysis strategy, as every hypothesis is based on the expected data patterns.
+While the Stage 1 review process helped greatly in making the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
+For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
+Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
+Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
+We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction or a training next time.
+And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot ensure that they did so.
+
 \newpage

### 2023-03-06 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote conclusion

@@
 Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)).
-The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and $n$-back level influencing SVs.
-Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
+The hypothesis that yielded the largest necessary sample size was a repeated measures, within-factors ANOVA of reaction time and $n$-back level.
+Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 53 participants, assuming $\alpha=.05$ and $\beta=.95$.
 However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
@@
 Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
-Our final data set therefore included $N=`r nrow(data_quest)`$ participants.
+Our final data set therefore included $N=`r nrow(data_quest)`$ participants, which is `r round(nrow(data_quest)/53, digits = 1)` times more than what the highest sample size calculation required.
 
@@
 
-When developing a new paradigm, it is challenging to decide on the optimal analysis strategy, as every hypothesis is based on the expected data patterns.
-While the Stage 1 review process helped greatly in making the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
+When developing a new paradigm, it is challenging to decide on the optimal analysis strategy, as every hypothesis is based on expected data patterns rather than previous findings.
+While the Stage 1 review process made the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
 For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
@@
 We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction or a training next time.
-And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot ensure that they did so.
+And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
+Nevertheless, we exceeded the largest required sample size by `r round(nrow(data_quest)/53, digits = 1)` times, which gives our analyses high statistical power, and we adhered to the agreed upon analyses of Stage 1.
+
+## Conclusion
+
+Effort and reward are two highly subjective concepts with relevance in daily life.
+With each decision an individual makes, they must weigh the required effort against the expected reward to decide if and how to behave in that situation.
+So far, effort discounting paradigms have relied on the assumption that the task that is objectively easiest is the one that is preferred by everyone, and each more difficult task is simply being devalued compared to the easy one.
+However, effort-related traits such as NFC suggest that this is not the case.
+Therefore, we developed a paradigm that allows effort discounting independent of objective task load, which we tested using an $n$-back task.
+The results showed that many participants indeed preferred a more or even the most difficult $n$-back level.
+Spanning the entire sample, these preferences took the shape of a declining logistic curve across $n$-back levels.
+While the subjective value declined with increasing levels, it increased with better performance as measured in $d'$, and was unaffected by the reaction time.
+Participants with NFC scores above the median reported lower subjective task load in and less aversion to more difficult levels.
+However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
+In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for a flexible effort discounting paradigm.
+The CAD paradigm offers this flexibility, and we encourage future studies to question traditional assumptions in the field of effort discounting in the light of these findings.
 

### 2023-03-06 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
included h3a and h3b plots

@@
 
+```{r h3a-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values when subtracting 2- from 1-back and 3- from 2-back.
+Each line indicates a participant, the colours indicate their Need for Cognition score.
+$N=116$.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))
+
+```
+
 The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
-Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (**Supplement**).
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).
+
+INSERT FIGURE 5 HERE
+
+```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
+Colours indicate Need for Cognition (NFC) score above or below the median.
+$N=116$.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3b-plot.png"))
+
+```
 

### 2023-03-06 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote more abstract

@@
     equal_contrib : yes
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+    role:         # Contributorship roles (e.g., CRediT, credit.niso.org)
       - Conceptualization
+      - Data curation
       - Methodology
@@
       - Visualization
-      - Writing - original draft preparation
+      - Writing - original draft
       - Writing - review & editing
@@
       - Writing - review & editing
-      - Visualization
   - name          : "Alexander Strobel"
@@
       - Conceptualization
+      - Resources
+      - Supervision
       - Funding acquistion
@@
   We replicated the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
+  Results show that many participants preferred a more or the most difficult level.
+  Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
+  Participants with higher Need for Cognition scores perceived higher levels as less effortful and found them less aversive.
+  Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences mainly emerged in higher levels.
 
@@
 Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)).
-The hypothesis that yielded the largest necessary sample size was a repeated measures, within-factors ANOVA of reaction time and $n$-back level.
-Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 53 participants, assuming $\alpha=.05$ and $\beta=.95$.
+The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and $n$-back level influencing SVs.
+Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
 However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
@@
 As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].
-To ensure the validity of the association of SVs and $n$-back level, we conducted a specification curve analysis[@Simonsohn2020], which includes 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within $n$-back levels).
-The rmANOVA was run with each of the 63\ pipelines, which will also include our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
-The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.
-The specification curve analysis was linked to the MLM in the initial submission, and was assigned to hypothesis 3a during the review process and in the Stage 1 report.
-Afterwards, we noticed that 3a does not contain any RT data, so the specification curve analysis was reassigned to the MLM with the agreement of the editor.
 
@@
 Post-hoc tests were computed depending on which effect reached significance at $p<.01$.
+To ensure the validity of this association, we conducted a specification curve analysis[@Simonsohn2020], which included 63 possible preprocessing pipelines of the RT data.
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within $n$-back levels).
+The rmANOVA was run with each of the 63\ pipelines, which also included our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
+The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.
 
@@
 
+## Adjustments for Stage 2
+
+There were two necessary adjustments of the methods.
+First, we failed to update the necessary sample size after the analyses changed with the first review round.
+Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the **Design Table**).
+And secondly, we needed to re-assign the SCA to the MLM in hypothesis 2b, to which it belonged in the initial submission.
+Following the advice of the reviewers, we had separated the NFC analysis from the MLM, and wanted to apply the SCA to the new NFC analysis (hypothesis 3a), as this was one of our main points of interest.
+However, since hypothesis 3a does not contain any RT data and the SCA is therefore only useful for the MLM in hypothesis 2b, we applied it to the MLM.
+
+## Sample
+
 Data was collected between the 16th of August 2022 and the 3rd of February 2023.
@@
 Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
-Our final data set therefore included $N=`r nrow(data_quest)`$ participants, which is `r round(nrow(data_quest)/53, digits = 1)` times more than what the highest sample size calculation required.
+Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"]), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r round(nrow(data_quest)/53, digits = 1)` times more than what the highest sample size calculation required.
 
@@
 There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3a-plot)).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (left panel of Figure\ \@ref(fig:h3ac-plot)).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.
@@
 
-```{r h3a-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values when subtracting 2- from 1-back and 3- from 2-back.
-Each line indicates a participant, the colours indicate their Need for Cognition score.
+```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (left) and aversiveness ratings (right) when subtracting 2- from 1-back and 3- from 2-back.
+Each line indicates a participant, the colours indicate their Need for Cognition (NFC) score.
 $N=116$.", fig.pos="H"}
 
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3a-plot.png"))
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3ac-plot.png"))
 
@@
 There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction.
-Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`).
+Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
 Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
@@
 The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more inter-individual variance for 3- and 4-back.
+Thomson and Oppenheimer[-@Thomson2022] argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
+For example, the $n$-back task is likely not a continuous manipulation of task load, as discussed above.
+However, the declining logistic curve is similar to the sigmoidal curve that had the best fit in a different effort paradigm[@KleinFluegge2015], which the authors explained with the low effect of low energy costs, suggesting there are still common features of effort across different tasks and domains.
 The MLM with the logistic contrast showed that the $n$-back level explained the majority of variance in SVs, while the performance measure $d'$ also explained some variance in SVs, albeit less.
@@
 And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
+One might also argue that the 2\ € reward range was not large enough to be an incentive for effort expenditure.
+However, findings by Bialaszek et al.[-@Bialaszek2017] suggest that participants are actually more sensitive to effort when the reward is small
 Nevertheless, we exceeded the largest required sample size by `r round(nrow(data_quest)/53, digits = 1)` times, which gives our analyses high statistical power, and we adhered to the agreed upon analyses of Stage 1.

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

@@
   Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
-  Participants with higher Need for Cognition scores perceived higher levels as less effortful and found them less aversive.
+  Participants with higher Need for Cognition scores perceived higher $n$-back levels as less effortful and found them less aversive.
   Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences mainly emerged in higher levels.
+  The CAD Paradigm appears to be well suited for assessing and analysing task preferences independent of the supposed objective task difficulty.
 
 keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, $n$-back"
-wordcount         : "~ 4,300"
+wordcount         : "~ 7000"
 bibliography      : CAD.bib
@@
 First, we failed to update the necessary sample size after the analyses changed with the first review round.
-Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the **Design Table**).
+Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the **Supplementary Material**).
 And secondly, we needed to re-assign the SCA to the MLM in hypothesis 2b, to which it belonged in the initial submission.
@@
 Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
-Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"]), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r round(nrow(data_quest)/53, digits = 1)` times more than what the highest sample size calculation required.
+Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"]), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
 
@@
 ```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level.
-Each dot indicates a participant, the colours indicate their Need for Cognition score.
+Each dot indicates a participant, the colours indicate their Need for Cognition (NFC) score.
 $N=116$.
@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate subjective values of tasks without assuming that the easiest level is inherently preferred.
-For this purpose, we changed the way in which the discounting options are presented to the participants, basing the anchor on their own choices rather than on the objective task load.
+This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate SVs of tasks without defaulting to the objective task load as a benchmark.
+For this purpose, we changed the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
 The analyses were closely aligned with those in Westbrook et al.[-@Westbrook2013] to demonstrate the changes in SVs brought about by the new paradigm.
-This study also applied the CAD paradigm to an emotion regulation task, the results of which are detailed in **Scheffel et al.**.
+This study also applied the CAD paradigm to an emotion regulation task, the results of which are detailed in a second Registered Report[@ScheffelZerna2022].
 
@@
 Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
+Future studies could create a stronger separation between the concepts investigated in this study, and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
 Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
@@
 So far, effort discounting paradigms have relied on the assumption that the task that is objectively easiest is the one that is preferred by everyone, and each more difficult task is simply being devalued compared to the easy one.
-However, effort-related traits such as NFC suggest that this is not the case.
+However, effort-related traits such as Need for Cognition suggest that this is not the case.
 Therefore, we developed a paradigm that allows effort discounting independent of objective task load, which we tested using an $n$-back task.
@@
 While the subjective value declined with increasing levels, it increased with better performance as measured in $d'$, and was unaffected by the reaction time.
-Participants with NFC scores above the median reported lower subjective task load in and less aversion to more difficult levels.
+Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
 However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
 In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for a flexible effort discounting paradigm.
-The CAD paradigm offers this flexibility, and we encourage future studies to question traditional assumptions in the field of effort discounting in the light of these findings.
+The CAD paradigm offers this flexibility, and we encourage future studies to question traditional assumptions in the field of effort discounting in the light of these findings, and to re-use this data set for exploratory analyses.
 
@@
 
+JZ and CS contributed equally to this work.
 JZ, CS, and AS conceptualized the study and acquired funding.

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
removed supplement heading

@@
 The authors declare no competing interests.
-
-\newpage
-\setcounter{figure}{0}
-
-# Figures and figure Captions
-
-INSERT FIGURE 1 HERE
-
-<!--
-```{r figure1appendix, echo=FALSE, message=FALSE, warning=FALSE}
-
-  include_graphics(here("06_Paper", "Inkscape Figures", "Paradigm_Scheme.png"))
-
-```
--->
-
-*Figure 1.* An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
-The grey boxes are the choice options shown to the participant.
-The participant's final reward value of the flexible level is displayed after the first arrow.
-The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice.
-The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
-
-\newpage
-
-# Design Table {#DesignTableSection}
-
-INSERT DESIGN TABLE HERE
-
-\newpage
-
-# Supplement
-
-INSERT SUPPLEMENT HERE

### 2023-03-07 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd

---
title: "Discussion"
author: "Christoph Scheffel"
output: html_document
---

```{r SetupDiscussion, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

library(tidyverse)

# load workspace variables from analyses_ERED.R script
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED_pilot.RData"))
base::load(here("06_Paper","ER-ED","ERED_Stage2","Workspace_ERED.RData"))

options(papaja.na_string = "")
```

# Discussion

The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of emotion regulation strategies.
We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al. [@Westbrook2013] in a way that it is now possible to determine SVs for tasks that have no objective order of difficulty levels. 
The new paradigm was tested on an *n*-back task [@ZernaScheffel2022] and a classic ER paradigm with the strategies distraction, distancing, and suppression.
The latter was completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ participants.

## Limitations

## Conclusion

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
corrected typo

@@
 
-An exploratory was used ANOVA to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
+An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
 The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added BF10 to H3a

@@
 We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
+There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
 Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (left panel of Figure\ \@ref(fig:h3ac-plot)).

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added interaction results of H3c

@@
 With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction.
+There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
 Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).

### 2023-03-07 06_Paper/COG-ED/Stage 2/Analysis.R
updated BF10 formatting in tables

@@ -894,9 +894,9 @@ hypothesis1a_contrasts <- cbind(hypothesis1a_contrasts,
 
 # rename contrasts and column names, round to two decimals
 
-colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$\\mathrm{BF}_{\\textrm{10}}$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)
-hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")] <- signif(hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$BF10$")], digits = 3)
+hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$\\mathrm{BF}_{\\textrm{10}}$")] <- signif(hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$","$\\mathrm{BF}_{\\textrm{10}}$")], digits = 3)
 hypothesis1a_contrasts$`$p$` <- format(round(hypothesis1a_contrasts$`$p$`, digits = 3), nsmall = 2)
 hypothesis1a_contrasts$`$p$`[hypothesis1a_contrasts$`$p$` == "0.000"] <- "<.001"
 
@@ -956,7 +956,7 @@ hypothesis1b_contrasts <- cbind(hypothesis1b_contrasts,
 
 # rename contrasts and column names, round to two decimals
 
-colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$\\mathrm{BF}_{\\textrm{10}}$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
[…]

### 2023-03-07 06_Paper/COG-ED/Stage 2/Supplement.Rmd
created supplement

---
title             : "Supplementary Material for the Registered Report titled: 'When easy is not preferred: A discounting paradigm to assess load-independent task preference'"
shorttitle        : "Supplement for CAD Paradigm"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, credit.niso.org)
      - Conceptualization
      - Data curation
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Resources
      - Supervision
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, $n$-back"
bibliography      : CAD.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
always_allow_html : true
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

---
\newpage
\renewcommand\thesection{\Alph{section}}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{0}

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}

  # set the output for figures and tables to the width of the text throughout the entire script

  knitr::opts_chunk$set(out.width = "\\textwidth")

  # load libraries

  library(bibtex)       # for referencing, "bibtex" package
  library(here)         # for path independent file referencing, "here" package
  library(papaja)       # APA conform output, "papaja" package
  options(papaja.na_string = "")
  library(kableExtra)   # for great tables in R Markdown, "kableExtra" package
  library(interactions) # for simple slopes plots, "interactions" package
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(knitr)        # for including plots and such, "knitr" package
  library(effectsize)   # for effect sizes and CIs, "effectsize" package

  # set top level directory to source file

  here::i_am("flag_project_root_CAD.txt")

  # load the workspace variables that have been computed with the Analysis.R script

  load(here("06_Paper","COG-ED","Stage 2","Workspace.RData"))

```

## Design Table

(Starts on next page)

\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}

\newpage

## Hypothesis 1a: The signal detection measure $d'$ declines with increasing $n$-back level.

ANOVA:

`r apa_print(hypothesis1a_rmanova)$full_result`, `r apa_print(hypothesis1a_BF)$statistic`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing $d'$ between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

## Hypothesis 1b: The median reaction time increases with increasing $n$-back level.

ANOVA:

`r apa_print(hypothesis1b_rmanova)$full_result`, `r apa_print(hypothesis1b_BF)$statistic`

Paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

## Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing $n$-back level.

Mental subscale ANOVA:

`r apa_print(hypothesis1c_mental_rmanova)$full_result`, `r apa_print(hypothesis1c_mental_BF)$statistic`

Mental subscale paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

Physical subscale ANOVA:

`r apa_print(hypothesis1c_physical_rmanova)$full_result`, `r apa_print(hypothesis1c_physical_BF)$statistic`

Physical subscale paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_physical_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

Time subscale ANOVA:

`r apa_print(hypothesis1c_time_rmanova)$full_result`, `r apa_print(hypothesis1c_time_BF)$statistic`

Time subscale paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

Performance subscale ANOVA:

`r apa_print(hypothesis1c_performance_rmanova)$full_result`, `r apa_print(hypothesis1c_performance_BF)$statistic`

Performance subscale paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_performance_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

Effort subscale ANOVA:

`r apa_print(hypothesis1c_effort_rmanova)$full_result`, `r apa_print(hypothesis1c_effort_BF)$statistic`

Effort subscale paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_effort_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

Frustration subscale ANOVA:

`r apa_print(hypothesis1c_frustration_rmanova)$full_result`, `r apa_print(hypothesis1c_frustration_BF)$statistic`

Frustration subscale paired contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_frustration_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between $n$-back levels",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

## Motivations for effort discounting behaviour

```{r motiv-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm. $N=116$", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "motivation.png"))

```

\newpage

## Hypothesis 2a: Subjective values decline with increasing $n$-back level.

ANOVA:

`r apa_print(hypothesis2a_rmanova)$full_result`, `r apa_print(hypothesis2a_BF)$statistic`

Pre-defined contrasts:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis2a_contrasts,
  caption = "Contrasts for the rmANOVA comparing the subjective values between $n$-back levels",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

## Hypothesis 2b: Subjective values decline with increasing $n$-back level, even after controlling for declining task performance measured by signal detection d’ and reaction time.

Multi level model:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        escape = FALSE,
        note = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
        placement = "H")
```

The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$.
This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
The Bayes Factor of the full model against the null model was `r apa_print(h2b_BF)$statistic`.

\newpage

## Hypothesis 3a: Participants with higher NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with lower NFC scores.

ANOVA:

Main effect level: `r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`

Main effect NFC group: `r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`

Interaction: `r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`

Contrast for main effect level:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3a_contrasts_nlevel,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of subjective values",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

## Hypothesis 3b: Participants with higher NFC scores have lower NASA-TLX scores in every n-back level than participants with lower NFC scores.

ANOVA:

Main effect level: `r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`

Main effect NFC group: `r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`

Interaction: `r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`

Contrast for main effect level:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_contrasts_levels,
  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

Contrast for interaction:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_contrasts_interact,
  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores",
  note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

## Hypothesis 3c: Participants with higher NFC scores have lower aversiveness ratings for 2- and 3-back but higher higher aversiveness ratings for 1-back than participants with lower NFC scores.

ANOVA:

Main effect level: `r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`

Main effect NFC group: `r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`

Interaction: `r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`

Contrast for main effect level:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3c_contrasts_levels,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of aversiveness ratings",
  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

Contrast for main effect NFC group:

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3c_contrasts_nfc,
  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition (NFC) group and $n$-back level on difference scores of aversiveness ratings",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

\newpage

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added refs to supplementary material

@@
 And finally, we hypothesized that the CAD paradigm can show inter-individual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
-Each hypothesis is detailed in the [Design Table](#DesignTableSection) in the Appendix.
+Each hypothesis is detailed in the Design Table in the Supplementary Material.
 
@@
 Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
+The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.
 
@@
 The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
-**Figure XX in the Supplement** shows the different motivations in the context of the SVs per $n$-back level.
+Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per $n$-back level.
 
@@
 ```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
-kable(h2b_result.table,
+apa_table(h2b_result.table,
         caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
-        booktabs = T,                          # no vertical lines
-        escape = F,                            # correctly print special characters)
-        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
-    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
-             escape = F,                    # correctly print special characters
-             threeparttable = T)            # line breaks in the footnote
+        escape = FALSE,
+        note = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
+        placement = "H")
 ```
@@
 Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
+The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.
 

### 2023-03-07 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
first draft of summary

@@
 
-The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of emotion regulation strategies.
+The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
 We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al.
-[@Westbrook2013] in a way that it is now possible to determine SVs for tasks that have no objective order of difficulty levels.
-The new paradigm was tested on an *n*-back task [@ZernaScheffel2022] and a classic ER paradigm with the strategies distraction, distancing, and suppression.
+[-@Westbrook2013] in a way that it is now possible to determine SVs for tasks that have no objective order of difficulty levels.
+The new paradigm was tested on an *n*-back task [@ZernaScheffel2022] and a classic ER paradigm.
 The latter was completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ participants. 
+As expected, use of ER strategies was associated with decreased subjective and physiological arousal.
+This finding is in line with previous meta-analytic findings, indicating the effectiveness of ER strategies, both on subjective as well as physiological levels [@Webb2012;@Zaehringer2020].
+Further, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
+This allows us to replicate previous findings from our research group and show that the use of strategies is associated with cognitive effort [@Scheffel2021].
+Both measures also showed great variability between individuals.
+Taken together, this means that the ER strategies had an effect on the participants as intended: Individuals were able to reduce subjective and physiological responding effectively at the expense of cognitive effort.
+We assume that there was a good basis on which individual SVs of ER strategies could be determined.
+
+Almost all participants showed an absolut preference for one strategy, indicated by a SV of 1.
+
+Subjective effort, utility, and *Corrugator* muscle activity significantly predicted individual SVs.
+Contrary to our hypothesis, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.
+However, individual SVs did not show associations with ER flexibility.
+
+## Validity of subjective values of ER strategies
 

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
started exploratory

@@
 
+# Exploratory analysis
+
+To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level and the between-factor NFC group.
+There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
+Post-hoc tests showed that
+
 # Discussion

### 2023-03-07 06_Paper/COG-ED/Stage 2/Analysis.R
added exploratory

@@ -1977,6 +1977,94 @@ sca_plot <- egg::ggarrange(sca_plot_upper, sca_plot_lower,
     theme(legend.title = element_text()) +
     guides(fill = 'none')
 
+##### Exploratory analyses #####################################################
+
+# make a copy
+  
+explor_data <- data_SV
+
+# add column indicating NFC score above or below median
+
+mediannfc <- median(explor_data$nfc)
+explor_data$nfcmedian <- ifelse(explor_data$nfc < median(explor_data$nfc), "low", "high")
+explor_data$nfcmedian <- as.factor(explor_data$nfcmedian)
+explor_data$level <- as.factor(explor_data$level)
+
+# compute two-way ANOVA
+
+explor_model <- afex::aov_ez("subject", "sv", explor_data,
+                                   between = c("nfcmedian"), within = c("level"),
+                             fun_aggregate = mean)
+explor_rmanova <- base::summary(explor_model)
+explor_rmanova <- explor_rmanova[["univariate.tests"]]
+explor_rmanova <- as.data.frame(matrix(explor_rmanova, nrow = 4, ncol = 6))
+
+
+# get effect size and BF10
+
+explor_rmanova <- cbind(explor_rmanova,
+                        format(effectsize::F_to_eta2(f = explor_rmanova[,5], df = explor_rmanova[,2],
+                                                     df_error = explor_rmanova[,4], ci = 0.95), digits = 2))
+explor_BF <- BayesFactor::anovaBF(formula = sv ~ level * nfcmedian, data = explor_data, progress = FALSE)
+
+# formatting
+
+colnames(explor_rmanova) <- c("Sum Sq", "$df$", "error Sum Sq", "error $df$", "$F$", "$p$", "$\\eta_{p}^{2}$", "$95\\% CI$")
+rownames(explor_rmanova) <- c("Intercept", "NFC group", "n-back level", "NFC group x n-back level")
+explor_rmanova[ ,c("Sum Sq","error Sum Sq","$F$")] <- signif(explor_rmanova[ ,c("Sum Sq","error Sum Sq","$F$")], digits = 3)
+explor_rmanova$`$p$` <- format(round(explor_rmanova$`$p$`, digits = 3), nsmall = 2)
+explor_rmanova$`$p$`[explor_rmanova$`$p$` == "0.000"] <- "<.001"
+
+## post-hoc tests for the n-back levels
+
[…]

### 2023-03-07 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added exploratory results

@@
   Participants with higher Need for Cognition scores perceived higher $n$-back levels as less effortful and found them less aversive.
-  Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences mainly emerged in higher levels.
+  Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences only emerged in higher levels.
   The CAD Paradigm appears to be well suited for assessing and analysing task preferences independent of the supposed objective task difficulty.
@@
 
-To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level and the between-factor NFC group.
+To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
 There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
-Post-hoc tests showed that
+Post-hoc tests for the main effect of level showed that Svs were lower for the more difficult $n$-back level in each paired contrast except for 1- versus 2-back.
+Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (`r apa_print(pairs(explor_emm_interact))$full_result$X4_High_low`).
+Despite not reaching significance, 1-back was the only level in which participants with NFC scores above the median seemed to have lower SVs than those with scores below the median (`r apa_print(pairs(explor_emm_interact))$full_result$X1_High_low`).
+The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
 
@@
 Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
-This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for $4$-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
+This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
+As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
 The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
@@
 However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
-In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for a flexible effort discounting paradigm.
+In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for tasks with high discriminatory power and effort discounting paradigms with flexible, participant-centered mechanisms.
 The CAD paradigm offers this flexibility, and we encourage future studies to question traditional assumptions in the field of effort discounting in the light of these findings, and to re-use this data set for exploratory analyses.

### 2023-03-07 06_Paper/COG-ED/Stage 2/Supplement.Rmd
added exploratory results

@@
   hypothesis1a_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing $d'$ between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing $d'$ between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis1b_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis1c_mental_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis1c_physical_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis1c_time_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis1c_performance_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis1c_effort_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis1c_frustration_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between $n$-back levels",
+  caption = "Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between $n$-back levels.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis2a_contrasts,
-  caption = "Contrasts for the rmANOVA comparing the subjective values between $n$-back levels",
+  caption = "Contrasts for the rmANOVA comparing the subjective values between $n$-back levels.",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis3a_contrasts_nlevel,
-  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of subjective values",
+  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of subjective values.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis3b_contrasts_levels,
-  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores",
+  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis3b_contrasts_interact,
-  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores",
+  caption = "Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores.",
   note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median.
@@
   hypothesis3c_contrasts_levels,
-  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of aversiveness ratings",
+  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of aversiveness ratings.",
   note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
   hypothesis3c_contrasts_nfc,
-  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition (NFC) group and $n$-back level on difference scores of aversiveness ratings",
+  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition (NFC) group and $n$-back level on difference scores of aversiveness ratings.",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
 \newpage
+
+## Exploratory analyses
+
+ANOVA:
+
+Main effect level: `r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`
+
+Main effect NFC group: `r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`
+
+Interaction: `r apa_print(explor_model)$full_result$nfcmedian_level`
+
+Contrasts for main effect level:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  explor_contrasts_nlevel,
+  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjective values.",
+  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+Contrasts for the interaction:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  explor_contrasts_interact,
+  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjectvie values.",
+  note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median.
+The column Level contains the $n$ of the $n$-back levels.
+$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
summary of study results

@@
 We assume that there was a good basis on which individual SVs of ER strategies could be determined.
+All in all, our hypotheses H1 to H5 were confirmed.
 
-Almost all participants showed an absolut preference for one strategy, indicated by a SV of 1.
-
+Almost all participants showed an absolute preference for one strategy, indicated by a SV of 1. 
+We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals prefer strategies to different extents.
+There was a significant relationship between SVs and choice of strategy. 
+Overly frequent the strategy would be chosen by the persons for whom the highest subjective value had been determined before, which confirms our hypothesis H7.
+Further, we found associations between individual SVs and different predictors.
 Subjective effort, utility, and *Corrugator* muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.
-However, individual SVs did not show associations with ER flexibility.
+Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.
+However, individual SVs did not show associations with ER flexibility, we therefore found no evidence for hypothesis H7.
 
@@
 
+Our findings must be considered in light of several limitions.
+
 ## Conclusion

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 
-[... WAHLVERHALTEN FEHLT NOCH ...]
+The cognitive effort expended also plays the most important role in the subsequent choice decision, which resembles previous findings of our group[@Scheffel2021]. 
+Here, `r round((54/119)*100, digits = 1)` percent stated that they again chose the strategy that was easiest for them to implement.
+`r round((29/119)*100, digits = 1)` percent stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)` percent stated their chosen strategy was the easiest and most effective.
+A more detailed list of all reasons can be found in table XX in [supplementary material](#SupplementReasonChoice).
 

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
first limitation

@@
 
-Our findings must be considered in light of several limitions.
+Our findings must be considered in light of several limitations.
+First, it must be mentioned that a block design was used.
+This is important for two reasons: first, because this allows for habituation effects of EMG activity within the block, and second, because this is how the subjective ratings were made retrospectively.
+This may have led to the fact that the correlations we found between SVs and predictors were lower than if we had used an event-related design.
+However, block designs are common in ER research [@Barreiros2019] and were used in previous studies [@Scheffel2019].
+Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.s
 

### 2023-03-08 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed Github to OSF link

@@
 
-The paradigm code as well as the R Markdown file used to analyze the data and write this document are available at [github.com/ChScheffel/CAD](https://github.com/ChScheffel/CAD).
+The paradigm code, the R script for analysis, and the R Markdown file used to compile this document are available at [osf.io/vnj8x/](https://osf.io/vnj8x/).
 
@@
 First, we failed to update the necessary sample size after the analyses changed with the first review round.
-Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the **Supplementary Material**).
+Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the Supplementary Material).
 And secondly, we needed to re-assign the SCA to the MLM in hypothesis 2b, to which it belonged in the initial submission.

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd

--- 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
@@
 
-Our findings must be considered in light of several limitions.
+Our findings must be considered in light of several limitations.
+First, it must be mentioned that a block design was used.
+This allows for habituation effects of EMG activity within the block.
+However, block designs are common in ER research [@Barreiros2019] and were used in previous studies [@Scheffel2019]. 
+Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
+It is also known that affect labeling might attenuate emotional experience [@Liebermann2007;@Torre2018]. 
+That is why we decided not to have the ratings done after every image.
+Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.
+Taken together, these two facts may have led to slightly lower associations between SVs and predictors.
+
+Third, it is a major limitation that participants had to use three given ER strategies.
 

### 2023-03-08 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
last limitations

@@
 Third, it is a major limitation that participants had to use three given ER strategies.
+It could be that some of the participants did not implement or were used to any of the three strategies in everyday life.
+So it may be that none of the strategies has a really high subjective value for the person.
+However, strategies for attentional deployment, cognitive change, and response modulation were chosen that meta-analytically proved to be most effective [@Webb2012]. 
+Related to that, individual SVs of each person have to be interpreted with caution. 
+They depend on the specific context: The stimulus material presented and the strategies that are compared with each other.
+Thus, it could be that SVs for one ER strategy would be higher or lower when using other stimuli or valences of stimuli and other comparison strategies.
+That is because the computation of SVs is inseparable form the other SVs.
+
+Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
+Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
+One might argue that 2 € as an incentive to repeat an entire block is quite low.
+However, we chose this amount because, first, we have followed the original paradigm of Westbrook[@Westbrook2013].
+Further it was shown that
 

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added limitation

@@
 Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
-One might argue that 2 € as an incentive to repeat an entire block is quite low.
+Thus, 2 € as an incentive to repeat an entire regulation block could be quite low.
 However, we chose this amount because, first, we have followed the original paradigm of Westbrook[@Westbrook2013].
-Further it was shown that
+Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort[@Bialaszek2017].
+n the future, however, it should be examined how the level of incentives affects subjective values.
 

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected typo

@@
 
-The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
+The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.

### 2023-03-10 06_Paper/COG-ED/Stage 2/Analysis.R
updated plots and colors

@@ -1482,16 +1482,19 @@ hypothesis3a_contrasts_nlevel$`$p$`[hypothesis3a_contrasts_nlevel$`$p$` == "0.00
 ggplot(h3a_data, aes(nlevels, svdiff, fill = nfcmedian, color = nfcmedian)) +
   ggrain::geom_rain(alpha = .5, rain.side = 'f2x2', id.long.var = "subject", likert = FALSE,
             violin.args = list(color = NA, alpha = .7, scale = "count", adjust = 1.3, width = 0.8),
-            line.args = list(size = .6, alpha = .5),
+            line.args = list(size = .9, alpha = .5),
             line.args.pos = list(position = position_jitter(width = 0, height = 0.1)),
             point.args = list(alpha = 0)) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
-  scale_fill_manual(values=c("darkorchid3", "chartreuse3")) +
-  scale_color_manual(values=c("darkorchid3", "chartreuse3"), name = "NFC group", labels = c("Above median","Below median")) +
-  guides(fill = 'none') +
+  scale_fill_manual(values = MetBrewer::met.brewer("Hiroshige",2), name = "NFC group", labels = c("Above median","Below median")) +
+  scale_color_manual(values = MetBrewer::met.brewer("Hiroshige",2)) +
+  guides(color = 'none') +
   xlab("n-back levels") + 
   ylab("Difference in subjective values") +
   theme(legend.title = element_text())
+
+ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 7, height = 5, units = "in",
+       device = "tiff", dpi = 900, filename = "h3a-plot.eps")
 
 # remove temporary variables
 
@@ -1637,11 +1640,14 @@ ggplot(h3b_data, aes(level, ntlx, fill = nfcmedian, color = nfcmedian)) +
                 boxplot.args.pos = list(width = .1, position = ggpp::position_dodgenudge(
                                           x = rep(-.13,8)))) +
       ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
-      scale_fill_manual(values=c("darkorchid3", "chartreuse3")) +
-      scale_color_manual(values=c("darkorchid3", "chartreuse3"), name = "NFC group", labels = c("Above median","Below median")) +
[…]

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd

@@
 
-## Validity of subjective values of ER strategies
+## Ecological validity of subjective values of ER strategies
+
+Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
+Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022]. 
+Greater variability might even adaptive [@Blanke2020;@Aldao2015].
+In addition, a wide variety of factors that influence the choice of stratgies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020].
+Thus, different factors have only rarely been studied together[@Young2020].
+Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) cannot be used to determine what internal subjective value the subjects associated with the strategies.
+However, we succeeded in this with our new CAD paradigm.
+On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
+
+## Trait character of SVs
+Hat das Trait-Charakter?
 

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=120)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).
+There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).
 

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added thoughts on validity of ER

@@
 On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
+The highest SVs of the individuals were associated with the choice made by the participants. 
+Until now, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020].
+This could be due to the fact that the strategies that have to be chosen between are often fixed in laboratory tests by the experimental design[@Sheppes2011;@Sheppes2014;@Scheffel2021].
+It was therefore attempted to investigate ER choice and influencing factors in everyday life.
+However, even there, certain strategies were often prescribed (for example studies, see English et al.[@Englisch2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]). 
+Although these covered a large area of the emotion-genesis process[@Gross1998emerging], they were nevertheless ultimately fixed.
+Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
+However, it would be possible to use ecological momentary assessment to capture ER strategies[@Koval2020].
+This would allow all strategies of the ER repertoire to be recorded for each individual[@Aldao2015]. 
+Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination[@Pena-Sarrionandia2015].
+
+Dynamic processes in emotion regulation choice
+Jonathan W. Murphy
+& Michael A. Young
 
@@
 Hat das Trait-Charakter?
+
+State character of goals @Wilms2020
 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
Update Manuscript_ERED_Stage2.Rmd
changed acknowledgements section

@@
 
+```{r child = "Discussion.Rmd"}
+```
+
 # References
@@
 
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940.
-Additionally, we have applied for funding of the participants' compensation from centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-Applications for the centralized funds will be reviewed in May.
-Regardless of whether or not this additional funding will be granted, the study can commence immediately.
-The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
+The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection.
 

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
thanked JK and MH in acknowledgements
review CK

@@
 affiliation:
-  - id            : "1"
-    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
+  - id            : "1" <!-- CK: im Prinzip kann diese Fußnote weggelassen werden, da wir alle die gleich Affilliation haben -->
+    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany" <!-- CK: Postfach ist 01062 Dresden -->
 authornote: |
 abstract: |
-  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
-  One approach to quantify the SVs of levels of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
-  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
+  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, <!-- CK: "-" statt "," --> a trade-off that is of great interest to psychological research.
+  One approach to quantify the SVs of levels of a cognitive task <!-- CK: Was meint hier levels? --> is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
+  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a <!-- CK: "an" --> unidirectional, inverse relationship between task load and SVs.
   Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
   We replicated the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
+<!-- CK: Ich würde hier zwei Sätze draus machen und den Punkt nach Paradigm setzen.
+Dadurch bekommt der erste Satz also die Entwicklung der Task mehr Gewicht.
+Als Vorschlag statt "our adaptation": "...with an adapted version of their paragigm, the ..." -->
   Results show that many participants preferred a more or the most difficult level.
@@
 The paradigm was written and presented using *Psychopy*[@Peirce2019].
-We used *R* with *R Studio*[@RCT2020; @RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all our analyses.
+We used *R* with *R Studio*[@RCT2020; @RStudioTeam2020] <!-- CK: die Refernz für "R" würde ich an "R" setzen --> with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all our analyses.
 
@@
 Prior to testing, written informed consent was obtained.
-Participants received 24€ in total or course credit for participation.
+Participants received 24€ <!-- CK: €24, auch für die nachfolgenden Geldbeträge :) --> in total or course credit for participation.
 
@@
 Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
-Adding those same pairs again, but with the opposite assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
+Adding those same pairs again, but with the opposite assignment of fixed and flexible level, does approach the true preference, but has two disadvantages. <!-- CK: hier fehlt das Subjekt. it? -->
 First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
@@
 Each pair is presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
-For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1\ € and is changed in every iteration.
+For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1\ € and is changed <!-- CK: "changes"  -->in every iteration.
 The other level in the pair will be set to a fixed value of 2\ €.
@@
 
-INSERT FIGURE 1 HERE
+INSERT FIGURE 1 HERE <!-- CK: das kann raus, oder? -->
 
@@
 Several other personality questionnaires were used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
+<!-- CK: ich würde an dieser Stelle (oder gleich im zweiten Satz) kurz auflisten, welche anderen FB zum Einsatz kamen entsprechend des Simmons Statements -->
 A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CAD).
 In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
-The paradigm started with the $n$-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the effort discounting procedure.
+The paradigm started with the $n$-back levels one to four, presented sequentially with two runs per level, <!-- CK: and --> consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green <!-- CK: nach back würde ich ":" setzen oder vieleicht auch "-" -->) to avoid anchor effects in the effort discounting procedure.
 To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
@@
 After the $n$-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
-They were told that one of their choices would be randomly picked for the final run of $n$-back, the data of which was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
+They were told that one of their choices would be randomly picked for the final run of $n$-back, the data of which <!-- CK: ".However, the data was not analyzed ..." --> was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
 After the CAD paradigm, participants filled out a short questionnaire on the tablet, indicating whether they adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).
@@
 
-Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)).
+Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)). <!-- CK: ...in Supplementary Material -->
 The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and $n$-back level influencing SVs.
@@
 As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
+Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back <!-- CK: der random factor ist nicht mehr enthalten -->) predicting SV nested within subjects.
 As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher $n$-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
+<!-- CK: der Zusammenhang der Aussage mit dem Rest wird nicht klar -->
 We controlled for performance, i.e., $d'$ (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
 $$
-SV \sim level\ + d' + median RT + (level|subject)
+SV \sim level\ + d' + median RT + (1|subject)
 $$
@@
 By this, the model yields interpretable parameter estimates. 
-If necessary, we will adjusted the optimization algorithm to improve model fit. 
-We visually inspected the residuals of the model for evidence to perform model criticism. 
-This was done by excluding all data points with absolute standardized residuals above 3 SD. 
+If necessary, we will adjusted the optimization algorithm to improve model fit.<!-- CK: anpassen an was gemacht wurde --> 
+We visually inspected the residuals of the model. <!-- CK: zum Model criticism: das ist nicht mehr up to date und sollte so nicht gemacht werden. bitte auch in den Analysen anpassen /rausnehmen -->
 As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].
+<!-- CK: hier müssten noch eure Anpassungen mit rein: Kontraste etc., rounds?  -->
 
@@
 One participant's data was removed because they misunderstood the instruction.
-Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=14$ data sets.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index <!-- CK: TLX --> were analyzed with $n=14$ data sets.
 The results showed increases in subjective and objective task load measures with higher $n$-back level.
 Importantly, SVs were lower for higher $n$-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
-The LMM revealed $n$-back level as a reliable predictor of SV, even after controlling for declining task performance ($d'$ and median RT).
+The LMM <!-- CK: Konsitenz: LMM oder MLM -->revealed $n$-back level as a reliable predictor of SV, even after controlling for declining task performance ($d'$ and median RT).
 NASA-TLX scores were higher with higher $n$, and lower for the group with lower NFC scores, but NFC and $n$-back level did not interact.
@@
 
-When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
+When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% <!-- CK: zwischen Zahl und % braucht es ein Leerzeichen -->stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
 The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
@@
 
-The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("Declining Linear" = c(3,1,-1,-3),"Ascending Quadratic" = c(-1,1,1,-1),"Declining Logistic" = c(3,2,-2,-3),"Positively Skewed Normal" = c(1,2,-1,-2))))$statistic$DecliningLogistic`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
+The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("Declining Linear" = c(3,1,-1,-3),"Ascending Quadratic" = c(-1,1,1,-1),"Declining Logistic" = c(3,2,-2,-3),"Positively Skewed Normal" = c(1,2,-1,-2))))$statistic$DecliningLogistic`), <!-- CK: stimmt irgendwie nciht mit der Table 2 überein -->suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
 
-Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
+Consequently, we had to adapt the multi level model <!-- CK: "MLM" --> to incorporate this non-linear trend.
 To apply the contrast to the $n$-back levels, we had to turn the variables into a factor, with two consequences:
@@
 To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
+<!-- CK: ok, ich sehe gerade, dass hier die Änderungen erklärt werden. -->
 The ICC of the null model indicated that there is a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
 that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
-We did not use an optimization algorithm to improve the fit of the random intercept model.
+We did not use an optimization algorithm to improve the fit of the random intercept model. <!-- CK: ist das ncoh so und warum nicht? -->
 A total of `r nrow(excl_cases_h2b)` data points from `r length(unique(excl_cases_h2b$subject))` participants were excluded, because the residuals exceeded 3 SD above the mean.
+<!-- CK: wie gesagt, das sollte noch angepasst bzw.
+rausgenommen werden.
+Vielleicht könnten wir so etwas schreiben wie: "We did not perform model criticism because we now believe that model-compliant exclusion of data is not a good scientific practice." -->
 The results of the final model are displayed in Table\ \@ref(tab:H2b-results).
@@
 To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis (Figure\ \@ref(fig:sca-plot)).
+<!-- CK: ich dachte, das wäre raus und die SCA wäre nur für H3?
+-->
 
@@
 The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
-Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
+Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX <!-- CK: Konsistenz: NASA-TLX oder NASA TLX --> scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
 Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).
@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting Paradigm (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate SVs of tasks without defaulting to the objective task load as a benchmark.
+This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate <!-- CK: which estimates or estimating --> subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate <!-- CK: s.o.
+--> SVs of tasks without defaulting to the objective task load as a benchmark.
 For this purpose, we changed the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
@@
 Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate inter-individual differences for $n>3$.
+<!-- CK: Warum für n größer 3?
+-->
 Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where $d'$ would decline and RT would remain stable.
-And lastly, the fact that neither accuracy and nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010], suggesting that they should always be reported as separate indices.
+And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010], suggesting that they should always be reported as separate indices.
 Additionally, $d'$ might not have differed across $n$-back levels because the manipulation of task load is not strictly continuous.
@@
 All NASA-TLX subscales differed across $n$-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
-This would support the notion of the $n$-back task offering a continuous manipulation of task load, as least subjectively.
+This would support the notion of the $n$-back task offering a continuous manipulation of task load, as <!-- CK: "at"? --> least subjectively.
 Ratings on the frustration and time subscales increased and ratings on the performance subscale decreased until 3-back and then remained stable.
@@
 This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
+<!-- CK: für die Diskussion wäre es noch gut, eine Entscheidung zu treffen, ob die jeweilige Hypothese angenommen oder abgelehnt wurde und das klar hinzuschreiben. -->
 
@@
 Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
-Future studies could create a stronger separation between the concepts investigated in this study, and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
+Future studies could create a stronger separation between the concepts investigated <!-- CK: welche Konzepte sind das?
+-->in this study, and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
 Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
@@
 One might also argue that the 2\ € reward range was not large enough to be an incentive for effort expenditure.
-However, findings by Bialaszek et al.[-@Bialaszek2017] suggest that participants are actually more sensitive to effort when the reward is small
+However, findings by Bialaszek et al.[-@Bialaszek2017] suggest that participants are actually more sensitive to effort when the reward is small.
 Nevertheless, we exceeded the largest required sample size by `r round(nrow(data_quest)/53, digits = 1)` times, which gives our analyses high statistical power, and we adhered to the agreed upon analyses of Stage 1.
@@
 Therefore, we developed a paradigm that allows effort discounting independent of objective task load, which we tested using an $n$-back task.
-The results showed that many participants indeed preferred a more or even the most difficult $n$-back level.
+The results showed that many participants <!-- CK: 34.5 % würde ich nicht als "many" verstehen --> indeed preferred a more or even the most difficult $n$-back level.
 Spanning the entire sample, these preferences took the shape of a declining logistic curve across $n$-back levels.

### 2023-03-13 06_Paper/COG-ED/Stage 2/Analysis.R

@@ -1298,7 +1298,7 @@ model0_h2b_ICC <- ICC.Model(model0_h2b)
 model1_h2b_raw <- lmerTest::lmer(sv ~ level + dprime.cwc + medianRT.cwc + (1|subject),
                          data = h2b_data, REML = T)
 
-# exclude cases with residuals three SDs above mean
+# exclude cases with residuals three SDs above mean <!-- CK: Ist das noch von mir drin? Das sollte unbedingt raus. ist nicht mehr up to date -->
 
 excl_cases_h2b <- as.data.frame(subset(h2b_data, abs(scale(resid(model1_h2b_raw))) > 3))
 

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
started implementing comments

@@
 affiliation:
-  - id            : "1" <!-- CK: im Prinzip kann diese Fußnote weggelassen werden, da wir alle die gleich Affilliation haben -->
-    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany" <!-- CK: Postfach ist 01062 Dresden -->
+  - id            : "1"
+    institution   : "Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany"
 authornote: |
 abstract: |
-  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, <!-- CK: "-" statt "," --> a trade-off that is of great interest to psychological research.
-  One approach to quantify the SVs of levels of a cognitive task <!-- CK: Was meint hier levels? --> is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
-  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a <!-- CK: "an" --> unidirectional, inverse relationship between task load and SVs.
+  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
+  One approach to quantify the SVs of levels of difficulty of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
+  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
   Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
-  We replicated the analysis of Westbrook and colleagues with our adaptation, the Cognitive and Affective Discounting (CAD) Paradigm, which quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
-<!-- CK: Ich würde hier zwei Sätze draus machen und den Punkt nach Paradigm setzen.
-Dadurch bekommt der erste Satz also die Entwicklung der Task mehr Gewicht.
-Als Vorschlag statt "our adaptation": "...with an adapted version of their paragigm, the ..." -->
+  We replicated the analysis of Westbrook and colleagues with an adapted version, the Cognitive and Affective Discounting (CAD) Paradigm.
+  It quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
   Results show that many participants preferred a more or the most difficult level.
@@
 The paradigm was written and presented using *Psychopy*[@Peirce2019].
-We used *R* with *R Studio*[@RCT2020; @RStudioTeam2020] <!-- CK: die Refernz für "R" würde ich an "R" setzen --> with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all our analyses.
+We used *R*[@RCT2020] with *R Studio*[@RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all our analyses.
 
@@
 Prior to testing, written informed consent was obtained.
-Participants received 24€ <!-- CK: €24, auch für die nachfolgenden Geldbeträge :) --> in total or course credit for participation.
+Participants received 24€ in total or course credit for participation.
 
@@
 Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
-Adding those same pairs again, but with the opposite assignment of fixed and flexible level, does approach the true preference, but has two disadvantages. <!-- CK: hier fehlt das Subjekt. it? -->
+Adding those same pairs again, but with the opposite assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
 First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
 Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
-This is determined by presenting each possible pair of levels on screen with the question "Would you prefer 1\ € for level A or 1\ € for level B?".
+This is determined by presenting each possible pair of levels on screen with the question "Would you prefer 1€ for level A or 1€ for level B?".
 Participants respond by clicking the respective on-screen button.
 Each pair is presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
-For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1\ € and is changed <!-- CK: "changes"  -->in every iteration.
-The other level in the pair will be set to a fixed value of 2\ €.
+For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1€ and changes in every iteration.
+The other level in the pair will be set to a fixed value of 2€.
 Then, the effort discounting sensu Westbrook et al.[-@Westbrook2013] begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
-The order in which the pairs are presented is fully randomized, and each pair goes through all iteration steps of adding/subtracting 0.50\ €, 0.25\ €, 0.13\ €, 0.06\ €, 0.03\ €, 0.02\ € to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
+The order in which the pairs are presented is fully randomized, and each pair goes through all iteration steps of adding/subtracting 0.50€, 0.25€, 0.13€, 0.06€, 0.03€, 0.02€ to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
 This procedure allows to compute SVs based on actual individual preference instead of objective task load.
-For each pair, the SV of the flexible level is 1, as it was preferred when faced with equal rewards, and the SV of the fixed level is the final reward of the flexible level divided by 2\ €.
+For each pair, the SV of the flexible level is 1, as it was preferred when faced with equal rewards, and the SV of the fixed level is the final reward of the flexible level divided by 2€.
 Each level's "global" SV is calculated as the mean of this level's SVs from all pairs in which it appeared.
@@
 Therefore, an SV of 1 indicates that this level is preferred over all others, while SVs lower than 1 indicate that in at least one pair, a different level was preferred over this one.
-
-INSERT FIGURE 1 HERE <!-- CK: das kann raus, oder? -->
 
@@
 *Subjective values.*
-For each effort discounting round, the SV of the fixed level was calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
+For each effort discounting round, the SV of the fixed level was calculated by adding or subtracting the last adjustment of 0.02€ from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2€.
 This yielded an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level was 1.
@@
 
-INSERT FIGURE 2 HERE 
 ```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
@@
 
-INSERT FIGURE 3 HERE
-
 ```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level.
@@
 
-INSERT FIGURE 4 HERE
-
 ```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (left) and aversiveness ratings (right) when subtracting 2- from 1-back and 3- from 2-back.
@@
 Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).
-
-INSERT FIGURE 5 HERE
 
@@
 And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
-One might also argue that the 2\ € reward range was not large enough to be an incentive for effort expenditure.
+One might also argue that the 2€ reward range was not large enough to be an incentive for effort expenditure.
 However, findings by Bialaszek et al.[-@Bialaszek2017] suggest that participants are actually more sensitive to effort when the reward is small.
@@
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
+The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection.
 

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
continued comments

@@
 Several other personality questionnaires were used in this study but are the topic of the Registered Report for the second lab session[@ScheffelZerna2022].
-<!-- CK: ich würde an dieser Stelle (oder gleich im zweiten Satz) kurz auflisten, welche anderen FB zum Einsatz kamen entsprechend des Simmons Statements -->
 A full list of measures can be found in our [Github repository](https://github.com/ChScheffel/CAD).
 In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
-The paradigm started with the $n$-back levels one to four, presented sequentially with two runs per level, <!-- CK: and --> consisting of 64 consonants (16 targets, 48 non-targets) per run.
-The levels were referred to by color (1-back black, 2-back red, 3-back blue, 4-back green <!-- CK: nach back würde ich ":" setzen oder vieleicht auch "-" -->) to avoid anchor effects in the effort discounting procedure.
+The paradigm started with the $n$-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The levels were referred to by color (1-back: black, 2-back: red, 3-back: blue, 4-back: green) to avoid anchor effects in the effort discounting procedure.
 To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
@@
 After the $n$-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
-They were told that one of their choices would be randomly picked for the final run of $n$-back, the data of which <!-- CK: ".However, the data was not analyzed ..." --> was not analyzed as it only served to incentivise truthful behavior and stay close to the design of Westbrook et al.[-@Westbrook2013].
+They were told that one of their choices would be randomly picked for the final run of $n$-back.
+However, this data was not analyzed as it only served to incentivise truthful behavior and to stay close to the design of Westbrook et al.[-@Westbrook2013].
 After the CAD paradigm, participants filled out a short questionnaire on the tablet, indicating whether they adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
continued comments

@@
 
-Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see [Design Table](#DesignTableSection)). <!-- CK: ...in Supplementary Material -->
+Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see Design Table in the Supplementary Material).
 The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and $n$-back level influencing SVs.
@@
 As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back <!-- CK: der random factor ist nicht mehr enthalten -->) predicting SV nested within subjects.
+Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
 As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher $n$-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
-<!-- CK: der Zusammenhang der Aussage mit dem Rest wird nicht klar -->
 We controlled for performance, i.e., $d'$ (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
 $$
-SV \sim level\ + d' + median RT + (1|subject)
+SV \sim level\ + d' + median RT + (level|subject)
 $$
@@
 By this, the model yields interpretable parameter estimates. 
-If necessary, we will adjusted the optimization algorithm to improve model fit.<!-- CK: anpassen an was gemacht wurde --> 
-We visually inspected the residuals of the model. <!-- CK: zum Model criticism: das ist nicht mehr up to date und sollte so nicht gemacht werden. bitte auch in den Analysen anpassen /rausnehmen -->
+If necessary, we will adjusted the optimization algorithm to improve model fit. 
+We visually inspected the residuals of the model for evidence to perform model criticism. 
+This was done by excluding all data points with absolute standardized residuals above 3 SD. 
 As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].
-<!-- CK: hier müssten noch eure Anpassungen mit rein: Kontraste etc., rounds?  -->
 

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
continued comments

@@
 One participant's data was removed because they misunderstood the instruction.
-Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index <!-- CK: TLX --> were analyzed with $n=14$ data sets.
+Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA-TLX were analyzed with $n=14$ data sets.
 The results showed increases in subjective and objective task load measures with higher $n$-back level.
 Importantly, SVs were lower for higher $n$-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
-The LMM <!-- CK: Konsitenz: LMM oder MLM -->revealed $n$-back level as a reliable predictor of SV, even after controlling for declining task performance ($d'$ and median RT).
+The MLM revealed $n$-back level as a reliable predictor of SV, even after controlling for declining task performance ($d'$ and median RT).
 NASA-TLX scores were higher with higher $n$, and lower for the group with lower NFC scores, but NFC and $n$-back level did not interact.
@@
 
-When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% <!-- CK: zwischen Zahl und % braucht es ein Leerzeichen -->stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
+When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
 The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
@@
 
-Consequently, we had to adapt the multi level model <!-- CK: "MLM" --> to incorporate this non-linear trend.
+Consequently, we had to adapt the MLM to incorporate this non-linear trend.
 To apply the contrast to the $n$-back levels, we had to turn the variables into a factor, with two consequences:
@@
 To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
-<!-- CK: ok, ich sehe gerade, dass hier die Änderungen erklärt werden. -->
 The ICC of the null model indicated that there is a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
 that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
-We did not use an optimization algorithm to improve the fit of the random intercept model. <!-- CK: ist das ncoh so und warum nicht? -->
-A total of `r nrow(excl_cases_h2b)` data points from `r length(unique(excl_cases_h2b$subject))` participants were excluded, because the residuals exceeded 3 SD above the mean.
-<!-- CK: wie gesagt, das sollte noch angepasst bzw.
-rausgenommen werden.
-Vielleicht könnten wir so etwas schreiben wie: "We did not perform model criticism because we now believe that model-compliant exclusion of data is not a good scientific practice." -->
+We did not use an optimization algorithm to improve the fit of the random intercept model.
+We did not exclude any data points.
 The results of the final model are displayed in Table\ \@ref(tab:H2b-results).
@@
 To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis (Figure\ \@ref(fig:sca-plot)).
-<!-- CK: ich dachte, das wäre raus und die SCA wäre nur für H3?
--->
 
@@
 The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
-Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX <!-- CK: Konsistenz: NASA-TLX oder NASA TLX --> scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
+Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
 Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).
@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which can estimate <!-- CK: which estimates or estimating --> subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which can estimate <!-- CK: s.o.
---> SVs of tasks without defaulting to the objective task load as a benchmark.
+This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which estimates subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which estimates SVs of tasks without defaulting to the objective task load as a benchmark.
 For this purpose, we changed the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
@@
 Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate inter-individual differences for $n>3$.
-<!-- CK: Warum für n größer 3?
--->
 Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where $d'$ would decline and RT would remain stable.
@@
 All NASA-TLX subscales differed across $n$-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
-This would support the notion of the $n$-back task offering a continuous manipulation of task load, as <!-- CK: "at"? --> least subjectively.
+This would support the notion of the $n$-back task offering a continuous manipulation of task load, at least subjectively.
 Ratings on the frustration and time subscales increased and ratings on the performance subscale decreased until 3-back and then remained stable.
@@
 Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
-Future studies could create a stronger separation between the concepts investigated <!-- CK: welche Konzepte sind das?
--->in this study, and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
+Future studies could create a stronger separation between the concepts investigated in this study (discounting curve, effort perception, performance, SV computation, NFC), and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
 Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
@@
 Therefore, we developed a paradigm that allows effort discounting independent of objective task load, which we tested using an $n$-back task.
-The results showed that many participants <!-- CK: 34.5 % würde ich nicht als "many" verstehen --> indeed preferred a more or even the most difficult $n$-back level.
+The results showed that many participants indeed preferred a more or even the most difficult $n$-back level.
 Spanning the entire sample, these preferences took the shape of a declining logistic curve across $n$-back levels.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/method.Rmd
placeholder for figures
added Protocol Registration section

@@
 In accordance with our previous study[@Scheffel2021], we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
-All results are detailed in the [Supplementary Material](#SupplementaryMaterial), figures S1 to S7 and table S2 to S8.
+All results are detailed in the OSF repository (<https://osf.io/vnj8x/>).
 
@@
 As soon as they have decided, they saw the respective instruction and the block with another 20 negative pictures started.
+
+[INSERT FIGURE 2 HERE]
 
@@
 
-The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CAD).
+The paradigm code, the R script for analysis, and the R Markdown file used to compile this document are available at [osf.io/vnj8x/](https://osf.io/vnj8x/).
+
+## Protocol registration
+
+The Stage 1 Registered Report protocol has been approved and is available at [osf.io/d6sc9/](https://osf.io/d6sc9/).

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added equal contrib in authornote

@@
     institution   : "Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany"
-authornote: |
-abstract: |
+authornote        :
+abstract          : |
   When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/method.Rmd
removed spaces before currency symbol

@@
 Prior to testing, written informed consent was obtained.
-Participants received 24 € in total or course credit for participation.
+Participants received 24€ in total or course credit for participation.
 
@@
 suppression), each of the two strategies were presented with a monetary reward.
-Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between "1 € for strategy A or 1 € for strategy B".
+Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between "1€ for strategy A or 1€ for strategy B".
 They decided by clicking the on-screen button of the respective option.
 Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
-For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1 €, the other strategy was assigned the fixed value of 2 €.
+For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1€, the other strategy was assigned the fixed value of 2€.
 After this, comparisons between strategies followed the original COG-ED paradigm[@Westbrook2013].
-Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
-The adjustment started at 0.50 € and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
-If a participant always chose the strategy with the fixed 2 € reward, the other strategy's last value on display was 1.97 €, if they always choose the lower strategy, its last value was 0.03 €.
-The sixth adjustment of 0.02 € was done during data analysis, based on the participants' decision in the last display of the pairing.
+Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1€ was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2€ reward was chosen).
+The adjustment started at 0.50€ and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
+If a participant always chose the strategy with the fixed 2€ reward, the other strategy's last value on display was 1.97€, if they always choose the lower strategy, its last value was 0.03€.
+The sixth adjustment of 0.02€ was done during data analysis, based on the participants' decision in the last display of the pairing.
 Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.
@@
 
-*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.02 € was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2 €.
+*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
 Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected typo

@@
 Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female ; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
+The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
 Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).
@@
 
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator*, and *Levator* activity.
-We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`´, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully evoked emotional arousal and physiological responding.
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
+We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully evoked emotional arousal and physiological responding.<!--JZ: Am besten auch die Richtung angeben, also "...valence for an increase in subjective..."-->
 
-To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, *Corrugator*, and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
+To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected typo

@@
 
-To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added 'the'

@@
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in [supplementary material](#SupplementEffectER).
+For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added -ly

@@
 We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
-Post-hoc test showed significant higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
+Post-hoc test showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
changed tense

@@
 
-The cognitive effort expended also plays the most important role in the subsequent choice decision, which resembles previous findings of our group[@Scheffel2021]. 
-Here, `r round((54/119)*100, digits = 1)` percent stated that they again chose the strategy that was easiest for them to implement.
+The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
+Here, `r round((54/119)*100, digits = 1)` percent stated that they chose the strategy that was easiest for them to implement.
 `r round((29/119)*100, digits = 1)` percent stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)` percent stated their chosen strategy was the easiest and most effective.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
changed typo
removed word again (sorry)
changed function call to suppression

@@
 SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
-In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had a SVs of 1.0, indicating a clear preference for one ER strategy.
+In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had one SV of 1.0, indicating a clear preference for one ER strategy.
 Absolute preferences for ER strategies were relatively equally distributed.
-Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`.
+Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "suppression"] == -1))`.
 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added 'the'

@@
 To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
-The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
+The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
 The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
replaced 'percent' with '%'

--- 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
-Here, `r round((54/119)*100, digits = 1)` percent stated that they chose the strategy that was easiest for them to implement.
-`r round((29/119)*100, digits = 1)` percent stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)` percent stated their chosen strategy was the easiest and most effective.
+Here, `r round((54/119)*100, digits = 1)`% stated that they chose the strategy that was easiest for them to implement.
+`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
 A more detailed list of all reasons can be found in table XX in [supplementary material](#SupplementReasonChoice).
@@
 To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
-The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
+The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
 The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
-Our model explained `r papaja::printnum(MLM1_r2[2])` percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
+Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
 We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
@@
 
-The second model explained `r papaja::printnum(MLM2_r2[2])` percent of variance. 
+The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance. 
 All results of the second model are in table\ \@ref(tab:TabMLMH5).
@@
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
-Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.
+Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
 Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added 'the'

@@
 The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
-Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
-We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
+Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
+We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
 The second model followed the specification: 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
capitalized Table

@@
 `r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found in table XX in [supplementary material](#SupplementReasonChoice).
+A more detailed list of all reasons can be found in Table XX in [supplementary material](#SupplementReasonChoice).
 
@@
 The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance. 
-All results of the second model are in table\ \@ref(tab:TabMLMH5).
+All results of the second model are in Table\ \@ref(tab:TabMLMH5).
 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added comment

@@
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
-Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
+Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.<!--JZ: Mir wurde mal die Verwendung von Worten wie "interestingly" im Ergebnisteil angekreidet, also die Bewertung vielleicht bis zum Diskussionsteil aufheben-->
 Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
replaced 'looked to see'

@@
 
-To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
+To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
changed figure ref typo

@@
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVchoice)).
+There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)).
 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added comment
added word

@@
 There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)).
+<!--JZ: Vielleicht wäre hier eine Heatmap auch ganz nice, das scheint wohl eine gute Visualisierung für einen Chi Square Test zu sein (https://www.analyticsvidhya.com/blog/2021/06/decoding-the-chi-square-test%E2%80%8A-%E2%80%8Ause-along-with-implementation-and-visualization/)-->
 
@@
 
-We then conducted a ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
+We then conducted an ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
 Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
@@
 Additionally, the predictor SV of strategy suppression was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
-The estimated odds ration indicated that is more likely to later choose suppression, when SV of strategy suppression is higher.
+The estimated odds ration indicated that a participant is more likely to later choose suppression, when SV of strategy suppression is higher.
 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
changed typo

@@
 We conducted a logistic regression to inspect whether participants' individual $slopes$ and $intercepts$ of ordered SVs could predict their ER flexibility score.
-We found neither a significant associations between $slopes$ of SVs and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$slope`, `r papaja::apa_print(Flex_LM_BF)$full_result$slope`), nor between $intercepts$ and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$intercept`, `r papaja::apa_print(Flex_LM_BF)$full_result$intercept`).
+We found neither a significant association between $slopes$ of SVs and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$slope`, `r papaja::apa_print(Flex_LM_BF)$full_result$slope`), nor between $intercepts$ and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$intercept`, `r papaja::apa_print(Flex_LM_BF)$full_result$intercept`).
 However, model fit was relatively low (`r papaja::apa_print(Flex_LM)$full_result$modelfit$r2`).

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
changed typo

@@
 
-We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
+We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
 The starting point for this was the model reported before. 

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added hyphen

@@
 The starting point for this was the model reported before. 
-Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
+Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
 The third model followed the specification:

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added comment

@@
 As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
-In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
+In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).<!--JZ: Auch hier gern die Richtung des Effekts mit hinschreiben-->
 However, effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
changed comment

--- 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
-In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
+In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).<!--JZ: Auch hier gern die Richtung des Effekts mit hinschreiben (dass Corrugator und Utility beide mit höheren SVs zusammenhängen, ist ja eher unerwartet-->
 However, effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added 'the'

--- 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
-In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
-However, effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
+In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).<!--JZ: Auch hier gern die Richtung des Effekts mit hinschreiben (dass Corrugator und Utility beide mit höheren SVs zusammenhängen, ist ja eher unerwartet-->
+However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
 Detailed information can be found in the [supplementary material](#SupplementExploratory).

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
changed word
subtracted 1 participant (because final N is 120)

@@
 The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
-We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al.
-[-@Westbrook2013] in a way that it is now possible to determine SVs for tasks that have no objective order of difficulty levels.
+We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al. [-@Westbrook2013] in a way that allows to determine SVs for tasks that have no objective order of difficulty levels. 
 The new paradigm was tested on an *n*-back task [@ZernaScheffel2022] and a classic ER paradigm.
-The latter was completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ participants. 
+The latter was completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
 As expected, use of ER strategies was associated with decreased subjective and physiological arousal.

### 2023-03-13 06_Paper/COG-ED/Stage 2/Analysis.R
replaced signif() with round()

@@ -896,7 +896,7 @@ hypothesis1a_contrasts <- cbind(hypothesis1a_contrasts,
 
 colnames(hypothesis1a_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$\\mathrm{BF}_{\\textrm{10}}$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 hypothesis1a_contrasts$Contrast <- gsub("X", "", hypothesis1a_contrasts$Contrast)
-hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$")] <- signif(hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$")], digits = 3)
+hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$")] <- round(hypothesis1a_contrasts[ ,c("Estimate","$SE$","$t$")], digits = 2)
 hypothesis1a_contrasts$`$p$` <- format(round(hypothesis1a_contrasts$`$p$`, digits = 3), nsmall = 2)
 hypothesis1a_contrasts$`$p$`[hypothesis1a_contrasts$`$p$` == "0.000"] <- "<.001"
 
@@ -958,7 +958,7 @@ hypothesis1b_contrasts <- cbind(hypothesis1b_contrasts,
 
 colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$\\mathrm{BF}_{\\textrm{10}}$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
-hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$")] <- signif(hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$")], digits = 3)
+hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$")] <- round(hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$")], digits = 2)
 hypothesis1b_contrasts$`$p$` <- format(round(hypothesis1b_contrasts$`$p$`, digits = 3), nsmall = 2)
 hypothesis1b_contrasts$`$p$`[hypothesis1b_contrasts$`$p$` == 0.000] <- "<.001"
 
[…]

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
removed comment

@@
 
-The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("Declining Linear" = c(3,1,-1,-3),"Ascending Quadratic" = c(-1,1,1,-1),"Declining Logistic" = c(3,2,-2,-3),"Positively Skewed Normal" = c(1,2,-1,-2))))$statistic$DecliningLogistic`), <!-- CK: stimmt irgendwie nciht mit der Table 2 überein -->suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
+The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("Declining Linear" = c(3,1,-1,-3),"Ascending Quadratic" = c(-1,1,1,-1),"Declining Logistic" = c(3,2,-2,-3),"Positively Skewed Normal" = c(1,2,-1,-2))))$statistic$DecliningLogistic`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
 

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed tense

@@
 $$
-This means that the intercept still varies between subjects, but there are no random slopes anymore.
+This means that the intercept still varied between subjects, but there were no random slopes anymore.
 To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
-The ICC of the null model indicated that there is a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
-that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
+The ICC of the null model indicated that there was a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
+that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs could be explained by differences between participants.
 We did not use an optimization algorithm to improve the fit of the random intercept model.

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added Hxx confirmations

@@
 
-The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`).
+We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across $n$-back levels.
+The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`), evidence was not in favour of H1a but in favour of H1b.
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
@@
 
-All NASA-TLX subscale scores increased across $n$-back levels.
+All NASA-TLX subscale scores increased across $n$-back levels, so evidence was in favour of H1c.
 The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
@@
 
-The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
+The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`), so evidence was in favour of H2a.
 All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.
@@
 The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
+Since SVs decline with increasing level, beyond the variance explained by $d'$, evidence was in favour of H2b.
 
@@
 We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`).
+There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
 Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (left panel of Figure\ \@ref(fig:h3ac-plot)).
@@
 The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
-Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median.
+Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.
 Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).
@@
 There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
-Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
+In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
 Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.

### 2023-03-13 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added n
changed 'confirms' to 'evidence in favour of'

@@
 We assume that there was a good basis on which individual SVs of ER strategies could be determined.
-All in all, our hypotheses H1 to H5 were confirmed.
+All in all, evidence was in favour of hypotheses H1 to H5.
 
-Almost all participants showed an absolute preference for one strategy, indicated by a SV of 1. 
+Almost all participants showed an absolute preference for one strategy, indicated by an SV of 1. 
 We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals prefer strategies to different extents.
 There was a significant relationship between SVs and choice of strategy. 
-Overly frequent the strategy would be chosen by the persons for whom the highest subjective value had been determined before, which confirms our hypothesis H7.
+Overly frequent the strategy would be chosen by the persons for whom the highest subjective value had been determined before, which speaks in favour of hypothesis H7.
 Further, we found associations between individual SVs and different predictors.

### 2023-03-14 06_Paper/ER-ED/ERED_Stage2/method.Rmd
added semicolon in citation

@@
 General psychological well-being was assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] was used.
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015] was used.
 Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].

### 2023-03-14 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
removed comment
typo

@@
 By this, the model yields interpretable parameter estimates. 
-If necessary, we will adjusted the optimization algorithm to improve model fit. 
+If necessary, we adjusted the optimization algorithm to improve model fit. 
 We visually inspected the residuals of the model for evidence to perform model criticism. 
@@
 This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
-<!-- CK: für die Diskussion wäre es noch gut, eine Entscheidung zu treffen, ob die jeweilige Hypothese angenommen oder abgelehnt wurde und das klar hinzuschreiben. -->
 

### 2023-03-14 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
typo in references

@@
 It was therefore attempted to investigate ER choice and influencing factors in everyday life.
-However, even there, certain strategies were often prescribed (for example studies, see English et al.[@Englisch2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]). 
+However, even there, certain strategies were often prescribed (for example studies, see English et al.[@English2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]). 
 Although these covered a large area of the emotion-genesis process[@Gross1998emerging], they were nevertheless ultimately fixed.
@@
 Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
-It is also known that affect labeling might attenuate emotional experience [@Liebermann2007;@Torre2018]. 
+It is also known that affect labeling might attenuate emotional experience [@Lieberman2007;@Torre2018]. 
 That is why we decided not to have the ratings done after every image.

### 2023-03-14 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
some new discussion points

@@
 Greater variability might even adaptive [@Blanke2020;@Aldao2015].
-In addition, a wide variety of factors that influence the choice of stratgies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020].
-Thus, different factors have only rarely been studied together[@Young2020].
-Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) cannot be used to determine what internal subjective value the subjects associated with the strategies.
-However, we succeeded in this with our new CAD paradigm.
+In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020], including intensity of the situation and effort.
+However, these factors have often been studied separately.
+Only rarely have effects of the factors been studied in combination[@Young2020].
+Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
+However, it cannot be determined in this way what internal subjective value individuals attribute to the choice options.
+We are confident that we have succeeded in this with the present paradigm.
 On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
@@
 Until now, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020].
-This could be due to the fact that the strategies that have to be chosen between are often fixed in laboratory tests by the experimental design[@Sheppes2011;@Sheppes2014;@Scheffel2021].
+This may be due to the fact that in laboratory studies, the choice options are often predetermined by the design of the experiment [@Sheppes2011;@Sheppes2014;@Scheffel2021].
 It was therefore attempted to investigate ER choice and influencing factors in everyday life.
@@
 
-Dynamic processes in emotion regulation choice
-Jonathan W. Murphy
-& Michael A. Young
+In order to draw a more comprehensive picture on ER, dynamic or cyclic processes have to be considered.
+The extended process model of emotion regulation[@Gross2015] postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
+If it is determined that the regulation goal is not being achieved, the ER strategy can be maintained, stopped or switched[@Gross2015].
+Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context[@Gross2015;@AldaoChristensen2015;@Murphy2018].
+This means that for studies on ER Choice, not only situational factors should be taken into account, but also contextual factors[@Murphy2018].
+For example, Murphy and Young[@Murphy2018] could show that in a classic ER choice paradigm[@Sheppes2011], strategy selection was singificantly influenced by strategy selection and negative affect of the preceding trial.
+
+- Unser paradigma bezieht das aber mit ein, dennindem die SVs auf Grundlage vorheriger Erfahrungen gebildet werden.
 

### 2023-03-14 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added reference

@@
 If it is determined that the regulation goal is not being achieved, the ER strategy can be maintained, stopped or switched[@Gross2015].
-Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context[@Gross2015;@AldaoChristensen2015;@Murphy2018].
+Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context[@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
 This means that for studies on ER Choice, not only situational factors should be taken into account, but also contextual factors[@Murphy2018].
-For example, Murphy and Young[@Murphy2018] could show that in a classic ER choice paradigm[@Sheppes2011], strategy selection was singificantly influenced by strategy selection and negative affect of the preceding trial.
+For example, Murphy and Young[@Murphy2018] could show that in a classic ER choice paradigm[@Sheppes2011], strategy selection was significantly influenced by strategy selection and negative affect of the preceding trial.
 

### 2023-03-14 06_Paper/COG-ED/Stage 2/Analysis.R
kept H3bdata

@@ -1651,7 +1651,7 @@ ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 7, height =
 
 # delete temporary data frame
 
-base::remove(ntlx, h3b_data)
+base::remove(ntlx)
 
 ##### Hypothesis 3c ############################################################
 

### 2023-03-14 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd

@@
 Greater variability might even adaptive [@Blanke2020;@Aldao2015].
-In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020], including intensity of the situation and effort.
+In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020;@Matthews2021], including intensity of the situation and effort.
 However, these factors have often been studied separately.
@@
 For example, Murphy and Young[@Murphy2018] could show that in a classic ER choice paradigm[@Sheppes2011], strategy selection was significantly influenced by strategy selection and negative affect of the preceding trial.
-
-- Unser paradigma bezieht das aber mit ein, dennindem die SVs auf Grundlage vorheriger Erfahrungen gebildet werden.
+This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
+Our newly developed paradigm also makes an important contribution here.
+The information and experiences that participants gather when using strategies subsequently flow implicitly into the calculation of subjective values.
+That is, because the participants first go through all the strategies and then make the monetary decisions on the basis that they should repeat the strategies again. 
+The decisions are made on the basis of the stimulus material that the individuals previously viewed. 
+Therefore, the question arises as to how stable these individual SVs are.
 
 ## Trait character of SVs
+From relatively early on in ER research, the question was asked whether the use of certain strategies is habitual, i.e. whether they have a trait character[@GrossJohn2003].
+Although 
+The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
+
 Hat das Trait-Charakter?

### 2023-03-14 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

@@
 General psychological well-being was assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{49} was used.
+To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{47--49} was used.
 Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
@@
 We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies were presented with a monetary reward.
-Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between ``1 € for strategy A or 1 € for strategy B''.
+Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between ``1€ for strategy A or 1€ for strategy B''.
 They decided by clicking the on-screen button of the respective option.
 Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
-For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1 €, the other strategy was assigned the fixed value of 2 €.
+For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1€, the other strategy was assigned the fixed value of 2€.
 After this, comparisons between strategies followed the original COG-ED paradigm\textsuperscript{29}.
-Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
-The adjustment started at 0.50 € and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
-If a participant always chose the strategy with the fixed 2 € reward, the other strategy's last value on display was 1.97 €, if they always choose the lower strategy, its last value was 0.03 €.
-The sixth adjustment of 0.02 € was done during data analysis, based on the participants' decision in the last display of the pairing.
+Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1€ was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2€ reward was chosen).
+The adjustment started at 0.50€ and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
+If a participant always chose the strategy with the fixed 2€ reward, the other strategy's last value on display was 1.97€, if they always choose the lower strategy, its last value was 0.03€.
+The sixth adjustment of 0.02€ was done during data analysis, based on the participants' decision in the last display of the pairing.
 Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.
@@
 
-\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02 € was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2 €.
+\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
 Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
@@
 
-The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our \href{https://github.com/ChScheffel/CAD}{Github repository}.
+The paradigm code, the R script for analysis, and the R Markdown file used to compile this document are available at \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.
+
+\hypertarget{protocol-registration}{%
+\subsection{Protocol registration}\label{protocol-registration}}
+
+The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/d6sc9/}{osf.io/d6sc9/}.
 
@@
 Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of \(N=120\) participants (100 female ; age: \(M=22.5\text{ }\pm\text{ }SD = 3.0\)).
+The final sample consisted of \(N=120\) participants (100 female; age: \(M=22.5\text{ }\pm\text{ }SD = 3.0\)).
 Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).
@@
 
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator}, and \emph{Levator} activity.
-We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\)´, \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully evoked emotional arousal and physiological responding.
-
-To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator}, and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator} and \emph{Levator} activity.
+We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully evoked emotional arousal and physiological responding.
+
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator} and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
 We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in \protect\hyperlink{SupplementEffectER}{supplementary material}.
+For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
 
@@
 We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\); see figure~\ref{fig:FigSubjEffort}).
-Post-hoc test showed significant higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
+Post-hoc test showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).
@@
 
-{[}\ldots{} WAHLVERHALTEN FEHLT NOCH \ldots{]}
+The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
+Here, 45.40\% stated that they chose the strategy that was easiest for them to implement.
+24.40\% stated they chose the strategy that was most effective and 11.80\% stated their chosen strategy was the easiest and most effective.
+A more detailed list of all reasons can be found in Table XX in \protect\hyperlink{SupplementReasonChoice}{supplementary material}.
 
@@
 SVs ranged between 0.005 and 1.00.
-In sum, \(n=\) 119 had a SVs of 1.0, indicating a clear preference for one ER strategy.
+In sum, \(n=\) 119 had one SV of 1.0, indicating a clear preference for one ER strategy.
 Absolute preferences for ER strategies were relatively equally distributed.
-Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 36.
+Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 43.
 
 To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
-The ICC of the null model was \(ICC=\) 0.19, indicating that level-2 predictor subject accounted for 19.10 percent of total variance.
+The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor subject accounted for 19.10\% of total variance.
 The preregistered model showed a correlation of \(r=\) 0.95 of the random effects subjects and recoded strategy (\(BF10\) of the variable strategy: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
-Our model explained 0.90 percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
-We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
+Our model explained 0.90\% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
+We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
 The second model followed the specification:
@@
 
-The second model explained 0.41 percent of variance.
-All results of the second model are in table~\ref{tab:TabMLMH5}.
+The second model explained 0.41\% of variance.
+All results of the second model are in Table~\ref{tab:TabMLMH5}.
 
@@
 
-The predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
+The predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = 29.49\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
 The values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
-Interestingly, utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5 percent of variance in SVs.
+Interestingly, utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5\% of variance in SVs.
 Effort rating showed an effect size of \(f^{2}=\) 0.035.
@@
 
-To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
+To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
 Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 120) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see figure~\ref{fig:FigSVchoice}).
+There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 119) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see figure~\ref{fig:FigSVChoice}).
 
@@
 
-We then conducted a ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
+We then conducted an ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
 Overall model fit was fair with \(R^{2}=\) 0.27.
@@
 Additionally, the predictor SV of strategy suppression was found to contribute to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
-The estimated odds ration indicated that is more likely to later choose suppression, when SV of strategy suppression is higher.
+The estimated odds ration indicated that a participant is more likely to later choose suppression, when SV of strategy suppression is higher.
 
@@
 We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
-We found neither a significant associations between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
+We found neither a significant association between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
 However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).
@@
 
-We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
+We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
 The starting point for this was the model reported before.
-Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
+Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
 The third model followed the specification:
@@
 In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
-However, effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
+However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
 Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
+We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al.\textsuperscript{29} in a way that allows to determine SVs for tasks that have no objective order of difficulty levels.
+The new paradigm was tested on an \emph{n}-back task\textsuperscript{34} and a classic ER paradigm.
+The latter was completed by \(N=120\) participants.
+As expected, use of ER strategies was associated with decreased subjective and physiological arousal.
+This finding is in line with previous meta-analytic findings, indicating the effectiveness of ER strategies, both on subjective as well as physiological levels\textsuperscript{4,5}.
+Further, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing.
+This allows us to replicate previous findings from our research group and show that the use of strategies is associated with cognitive effort\textsuperscript{22}.
+Both measures also showed great variability between individuals.
+Taken together, this means that the ER strategies had an effect on the participants as intended: Individuals were able to reduce subjective and physiological responding effectively at the expense of cognitive effort.
+We assume that there was a good basis on which individual SVs of ER strategies could be determined.
+All in all, evidence was in favour of hypotheses H1 to H5.
+
+Almost all participants showed an absolute preference for one strategy, indicated by an SV of 1.
+We also found a wide range of SVs (between 0.005 and 1.00), suggesting that individuals prefer strategies to different extents.
+There was a significant relationship between SVs and choice of strategy.
+Overly frequent the strategy would be chosen by the persons for whom the highest subjective value had been determined before, which speaks in favour of hypothesis H7.
+Further, we found associations between individual SVs and different predictors.
+Subjective effort, utility, and \emph{Corrugator} muscle activity significantly predicted individual SVs.
+Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining 15.5 percent of variance in SVs.
+However, individual SVs did not show associations with ER flexibility, we therefore found no evidence for hypothesis H7.
+
+\hypertarget{ecological-validity-of-subjective-values-of-er-strategies}{%
+\subsection{Ecological validity of subjective values of ER strategies}\label{ecological-validity-of-subjective-values-of-er-strategies}}
+
+Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
+Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy\textsuperscript{17,69,70}.
+Greater variability might even adaptive\textsuperscript{12,17}.
+In addition, a wide variety of factors that influence the choice of stratgies in specific situations were examined\textsuperscript{20--22,71,72}.
+Thus, different factors have only rarely been studied together\textsuperscript{72}.
+Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) cannot be used to determine what internal subjective value the subjects associated with the strategies.
+However, we succeeded in this with our new CAD paradigm.
+On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
+The highest SVs of the individuals were associated with the choice made by the participants.
+Until now, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{71}.
+This could be due to the fact that the strategies that have to be chosen between are often fixed in laboratory tests by the experimental design\textsuperscript{20--22}.
+It was therefore attempted to investigate ER choice and influencing factors in everyday life.
+However, even there, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{73}, Millgram et al.\textsuperscript{74}, Wilms et al.\textsuperscript{71}).
+Although these covered a large area of the emotion-genesis process\textsuperscript{2}, they were nevertheless ultimately fixed.
+Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
+However, it would be possible to use ecological momentary assessment to capture ER strategies\textsuperscript{75}.
+This would allow all strategies of the ER repertoire to be recorded for each individual\textsuperscript{12}.
+Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination\textsuperscript{76}.
+
+Dynamic processes in emotion regulation choice
+Jonathan W. Murphy
+\& Michael A. Young
+
+\hypertarget{trait-character-of-svs}{%
+\subsection{Trait character of SVs}\label{trait-character-of-svs}}
+
+Hat das Trait-Charakter?
+
+State character of goals\textsuperscript{71}
+
+\hypertarget{limitations}{%
+\subsection{Limitations}\label{limitations}}
+
+Our findings must be considered in light of several limitations.
+First, it must be mentioned that a block design was used.
+This allows for habituation effects of EMG activity within the block.
+However, block designs are common in ER research\textsuperscript{77} and were used in previous studies\textsuperscript{78}.
+Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
+It is also known that affect labeling might attenuate emotional experience\textsuperscript{79,80}.
+That is why we decided not to have the ratings done after every image.
+Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.
+Taken together, these two facts may have led to slightly lower associations between SVs and predictors.
+
+Third, it is a major limitation that participants had to use three given ER strategies.
+It could be that some of the participants did not implement or were used to any of the three strategies in everyday life.
+So it may be that none of the strategies has a really high subjective value for the person.
+However, strategies for attentional deployment, cognitive change, and response modulation were chosen that meta-analytically proved to be most effective\textsuperscript{4}.
+Related to that, individual SVs of each person have to be interpreted with caution.
+They depend on the specific context: The stimulus material presented and the strategies that are compared with each other.
+Thus, it could be that SVs for one ER strategy would be higher or lower when using other stimuli or valences of stimuli and other comparison strategies.
+That is because the computation of SVs is inseparable form the other SVs.
+
+Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
+Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
+Thus, 2 € as an incentive to repeat an entire regulation block could be quite low.
+However, we chose this amount because, first, we have followed the original paradigm of Westbrook\textsuperscript{29}.
+Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{81}.
+n the future, however, it should be examined how the level of incentives affects subjective values.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Sarubin2015}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Campbell-Sills2007}{}}%
 \CSLLeftMargin{48. }%
-\CSLRightInline{Sarubin, N.
-\emph{et al.} \href{https://doi.org/10.1026/0943-8149/a000142}{First analysis of the 10-and 25-item german version of the connor-davidson resilience scale (CD-RISC) regarding psychometric properties and components}.
-\emph{Zeitschrift Fur Gesundheitspsychologie} \textbf{23}, 112--122 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell-Sills2007}{}}%
-\CSLLeftMargin{49. }%
 \CSLRightInline{Campbell-Sills, L.
@@
 \emph{Journal of Traumatic Stress} \textbf{20}, 1019--28 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sarubin2015}{}}%
+\CSLLeftMargin{49. }%
+\CSLRightInline{Sarubin, N.
+\emph{et al.} \href{https://doi.org/10.1026/0943-8149/a000142}{First analysis of the 10-and 25-item german version of the connor-davidson resilience scale (CD-RISC) regarding psychometric properties and components}.
+\emph{Zeitschrift Fur Gesundheitspsychologie} \textbf{23}, 112--122 (2015).}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Burr2020}{}}%
+\CSLLeftMargin{69. }%
+\CSLRightInline{Burr, D.
+A.
+\& Samanez-Larkin, G.
+R.
+\href{https://doi.org/10.1016/j.tics.2020.02.008}{Advances in emotion regulation choice from experience sampling}.
+\emph{Trends in Cognitive Sciences} \textbf{24}, 344--346 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Elkjaer2022}{}}%
+\CSLLeftMargin{70. }%
+\CSLRightInline{Elkjaer, E., Mikkelsen, M.
+B.
+\& O'Toole, M.
+S.
+\href{https://doi.org/10.1111/sjop.12808}{Emotion regulation patterns: Capturing variability and flexibility in emotion regulation in an experience sampling study}.
+\emph{Scandinavian Journal of Psychology} \textbf{63}, 297--307 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wilms2020}{}}%
+\CSLLeftMargin{71. }%
+\CSLRightInline{Wilms, R., Lanwehr, R.
+\& Kastenmuller, A.
+\href{https://doi.org/ARTN\%20877\%0A10.3389/fpsyg.2020.00877}{Emotion regulation in everyday life: The role of goals and situational factors}.
+\emph{Frontiers in Psychology} \textbf{11}, (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Young2020}{}}%
+\CSLLeftMargin{72. }%
+\CSLRightInline{Young, G.
+\& Suri, G.
+\href{https://doi.org/10.1080/02699931.2019.1611544}{Emotion regulation choice: A broad examination of external factors}.
+\emph{Cognition \& Emotion} \textbf{34}, 242--261 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-English2017}{}}%
+\CSLLeftMargin{73. }%
+\CSLRightInline{English, T., Lee, I.
+A., John, O.
+P.
+\& Gross, J.
+J.
+\href{https://doi.org/10.1007/s11031-016-9597-z}{Emotion regulation strategy selection in daily life: The role of social context and goals}.
+\emph{Motivation and Emotion} \textbf{41}, 230--242 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Millgram2019}{}}%
+\CSLLeftMargin{74. }%
+\CSLRightInline{Millgram, Y., Sheppes, G., Kalokerinos, E.
+K., Kuppens, P.
+\& Tamir, M.
+\href{https://doi.org/10.1037/xge0000477}{Do the ends dictate the means in emotion regulation?} \emph{Journal of Experimental Psychology-General} \textbf{148}, 80--96 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Koval2020}{}}%
+\CSLLeftMargin{75. }%
+\CSLRightInline{Koval, P., Kalokerinos, E.
+K., Verduyn, P.
+\& Greiff, S.
+\href{https://doi.org/10.1027/1015-5759/a000599}{Introduction to the special issue capturing the dynamics of emotion and emotion regulation in daily life with ambulatory assessment}.
+\emph{European Journal of Psychological Assessment} \textbf{36}, 433--436 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Pena-Sarrionandia2015}{}}%
+\CSLLeftMargin{76. }%
+\CSLRightInline{Pena-Sarrionandia, A., Mikolajczak, M.
+\& Gross, J.
+J.
+\href{https://doi.org/ARTN\%20160\%0A10.3389/fpsyg.2015.00160}{Integrating emotion regulation and emotional intelligence traditions: A meta-analysis}.
+\emph{Frontiers in Psychology} \textbf{6}, (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Barreiros2019}{}}%
+\CSLLeftMargin{77. }%
+\CSLRightInline{Barreiros, A.
+R., Almeida, I., Baia, B.
+C.
+\& Castelo-Branco, M.
+\href{https://doi.org/10.3389/fnhum.2019.00089}{Amygdala modulation during emotion regulation training with fMRI-based neurofeedback}.
+\emph{Frontiers in Human Neuroscience} \textbf{13}, 89 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Scheffel2019}{}}%
+\CSLLeftMargin{78. }%
+\CSLRightInline{Scheffel, C.
+\emph{et al.} \href{https://doi.org/10.1017/pen.2019.11}{Cognitive emotion regulation and personality: An analysis of individual differences in the neural and behavioral correlates of successful reappraisal}.
+\emph{Personality Neuroscience} \textbf{2}, e11 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Lieberman2007}{}}%
+\CSLLeftMargin{79. }%
+\CSLRightInline{Lieberman, M.
+D.
+\emph{et al.} \href{https://doi.org/10.1111/j.1467-9280.2007.01916.x}{Putting feelings into words - affect labeling disrupts amygdala activity in response to affective stimuli}.
+\emph{Psychological Science} \textbf{18}, 421--428 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Torre2018}{}}%
+\CSLLeftMargin{80. }%
+\CSLRightInline{Torre, J.
+B.
+\& Lieberman, M.
+D.
+\href{https://doi.org/10.1177/1754073917742706}{Putting feelings into words: Affect labeling as implicit emotion regulation}.
+\emph{Emotion Review} \textbf{10}, 116--124 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
+\CSLLeftMargin{81. }%
+\CSLRightInline{Bialaszek, W., Marcowski, P.
+\& Ostaszewski, P.
+\href{https://doi.org/ARTN\%20e0182353\%0A10.1371/journal.pone.0182353}{Physical and cognitive effort discounting across different reward magnitudes: Tests of discounting models}.
+\emph{Plos One} \textbf{12}, (2017).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{69. }%
+\CSLLeftMargin{82. }%
 \CSLRightInline{Preece, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{70. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{71. }%
+\CSLLeftMargin{84. }%
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{48}.
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{49}.
 
 \emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{69}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{82}.
 
@@
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,70} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{71}.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,83} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{84}.
 
@@
 \end{figure}
+\newpage
+
+\hypertarget{reasons-for-decision-made-by-the-participants-in-the-last-regulation-block}{%
+\subsection{Reasons for decision made by the participants in the last regulation block}\label{reasons-for-decision-made-by-the-participants-in-the-last-regulation-block}}
 

### 2023-03-15 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
updated affiliations and orcid

@@
   - name          : "Denise Dörfel"
-    orcid         :
-    affiliation   : "1"
+    orcid         : "0000-0002-5632-419X"
+    affiliation   : "1", "2"
     role          :
@@
   - id            : "1"
-    institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
+    institution   : "Chair of Differential and Personality Psychology, Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
+  - id            : "2"
+    institution   : "Center for Information Services and High Performance Computing, Technische Universität Dresden, 01069 Dresden, Germany"
 authornote        :

### 2023-03-15 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
   pdftitle={Estimating individual subjective values of emotion regulation strategies},
-  pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1, \& Alexander Strobel1},
+  pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1,2, \& Alexander Strobel1},
   pdflang={en-EN},
@@
 \title{Estimating individual subjective values of emotion regulation strategies}
-\author{Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Josephine Zerna\textsuperscript{$\dagger{}$,1}, Anne Gärtner\textsuperscript{1}, Denise Dörfel\textsuperscript{1}, \& Alexander Strobel\textsuperscript{1}}
+\author{Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Josephine Zerna\textsuperscript{$\dagger{}$,1}, Anne Gärtner\textsuperscript{1}, Denise Dörfel\textsuperscript{1,2}, \& Alexander Strobel\textsuperscript{1}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Chair of Differential and Personality Psychology, Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany\\\textsuperscript{2} Center for Information Services and High Performance Computing, Technische Universität Dresden, 01069 Dresden, Germany}
 
@@
 Greater variability might even adaptive\textsuperscript{12,17}.
-In addition, a wide variety of factors that influence the choice of stratgies in specific situations were examined\textsuperscript{20--22,71,72}.
-Thus, different factors have only rarely been studied together\textsuperscript{72}.
-Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) cannot be used to determine what internal subjective value the subjects associated with the strategies.
-However, we succeeded in this with our new CAD paradigm.
+In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined\textsuperscript{20--22,71--73}, including intensity of the situation and effort.
+However, these factors have often been studied separately.
+Only rarely have effects of the factors been studied in combination\textsuperscript{72}.
+Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) can only estimate how a factor tends to drive the choice in one direction or the other.
+However, it cannot be determined in this way what internal subjective value individuals attribute to the choice options.
+We are confident that we have succeeded in this with the present paradigm.
 On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
@@
 Until now, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{71}.
-This could be due to the fact that the strategies that have to be chosen between are often fixed in laboratory tests by the experimental design\textsuperscript{20--22}.
+This may be due to the fact that in laboratory studies, the choice options are often predetermined by the design of the experiment\textsuperscript{20--22}.
 It was therefore attempted to investigate ER choice and influencing factors in everyday life.
-However, even there, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{73}, Millgram et al.\textsuperscript{74}, Wilms et al.\textsuperscript{71}).
+However, even there, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{74}, Millgram et al.\textsuperscript{75}, Wilms et al.\textsuperscript{71}).
 Although these covered a large area of the emotion-genesis process\textsuperscript{2}, they were nevertheless ultimately fixed.
 Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
-However, it would be possible to use ecological momentary assessment to capture ER strategies\textsuperscript{75}.
+However, it would be possible to use ecological momentary assessment to capture ER strategies\textsuperscript{76}.
 This would allow all strategies of the ER repertoire to be recorded for each individual\textsuperscript{12}.
-Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination\textsuperscript{76}.
-
-Dynamic processes in emotion regulation choice
-Jonathan W. Murphy
-\& Michael A. Young
+Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination\textsuperscript{77}.
+
+In order to draw a more comprehensive picture on ER, dynamic or cyclic processes have to be considered.
+The extended process model of emotion regulation\textsuperscript{33} postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
+If it is determined that the regulation goal is not being achieved, the ER strategy can be maintained, stopped or switched\textsuperscript{33}.
+Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context\textsuperscript{33,78--80}.
+This means that for studies on ER Choice, not only situational factors should be taken into account, but also contextual factors\textsuperscript{79}.
+For example, Murphy and Young\textsuperscript{79} could show that in a classic ER choice paradigm\textsuperscript{21}, strategy selection was significantly influenced by strategy selection and negative affect of the preceding trial.
+This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
+Our newly developed paradigm also makes an important contribution here.
+The information and experiences that participants gather when using strategies subsequently flow implicitly into the calculation of subjective values.
+That is, because the participants first go through all the strategies and then make the monetary decisions on the basis that they should repeat the strategies again.
+The decisions are made on the basis of the stimulus material that the individuals previously viewed.
+Therefore, the question arises as to how stable these individual SVs are.
 
@@
 
-Hat das Trait-Charakter?
+From relatively early on in ER research, the question was asked whether the use of certain strategies is habitual, i.e.~whether they have a trait character\textsuperscript{9}.
+
+The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
 
@@
 This allows for habituation effects of EMG activity within the block.
-However, block designs are common in ER research\textsuperscript{77} and were used in previous studies\textsuperscript{78}.
+However, block designs are common in ER research\textsuperscript{81} and were used in previous studies\textsuperscript{82}.
 Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
-It is also known that affect labeling might attenuate emotional experience\textsuperscript{79,80}.
+It is also known that affect labeling might attenuate emotional experience\textsuperscript{83,84}.
 That is why we decided not to have the ratings done after every image.
@@
 However, we chose this amount because, first, we have followed the original paradigm of Westbrook\textsuperscript{29}.
-Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{81}.
+Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{85}.
 n the future, however, it should be examined how the level of incentives affects subjective values.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Matthews2021}{}}%
+\CSLLeftMargin{73. }%
+\CSLRightInline{Matthews, M., Webb, T.
+L., Shafir, R., Snow, M.
+\& Sheppes, G.
+Identifying the determinants of emotion regulation choice: A systematic review with meta-analysis.
+\emph{Cognition and Emotion} 1--29 (2021) doi:\href{https://doi.org/10.1080/02699931.2021.1945538}{10.1080/02699931.2021.1945538}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-English2017}{}}%
-\CSLLeftMargin{73. }%
+\CSLLeftMargin{74. }%
 \CSLRightInline{English, T., Lee, I.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Millgram2019}{}}%
-\CSLLeftMargin{74. }%
+\CSLLeftMargin{75. }%
 \CSLRightInline{Millgram, Y., Sheppes, G., Kalokerinos, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Koval2020}{}}%
-\CSLLeftMargin{75. }%
+\CSLLeftMargin{76. }%
 \CSLRightInline{Koval, P., Kalokerinos, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Pena-Sarrionandia2015}{}}%
-\CSLLeftMargin{76. }%
+\CSLLeftMargin{77. }%
 \CSLRightInline{Pena-Sarrionandia, A., Mikolajczak, M.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-AldaoChristensen2015}{}}%
+\CSLLeftMargin{78. }%
+\CSLRightInline{Aldao, A.
+\& Christensen, K.
+\href{https://doi.org/10.1080/1047840x.2015.962399}{Linking the expanded process model of emotion regulation to psychopathology by focusing on behavioral outcomes of regulation}.
+\emph{Psychological Inquiry} \textbf{26}, 27--36 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Murphy2018}{}}%
+\CSLLeftMargin{79. }%
+\CSLRightInline{Murphy, J.
+W.
+\& Young, M.
+A.
+\href{https://doi.org/10.1080/02699931.2017.1419935}{Dynamic processes in emotion regulation choice}.
+\emph{Cognition \& Emotion} \textbf{32}, 1654--1662 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sheppes2020}{}}%
+\CSLLeftMargin{80. }%
+\CSLRightInline{Sheppes, G.
+\href{https://doi.org/10.1016/bs.aesp.2019.09.003}{Transcending the "good \& bad" and "here \& now" in emotion regulation: Costs and benefits of strategies across regulatory stages}.
+\emph{Advances in Experimental Social Psychology, Vol 61} \textbf{61}, 185--236 (2020).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Barreiros2019}{}}%
-\CSLLeftMargin{77. }%
+\CSLLeftMargin{81. }%
 \CSLRightInline{Barreiros, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Scheffel2019}{}}%
-\CSLLeftMargin{78. }%
+\CSLLeftMargin{82. }%
 \CSLRightInline{Scheffel, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lieberman2007}{}}%
-\CSLLeftMargin{79. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{Lieberman, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Torre2018}{}}%
-\CSLLeftMargin{80. }%
+\CSLLeftMargin{84. }%
 \CSLRightInline{Torre, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{81. }%
+\CSLLeftMargin{85. }%
 \CSLRightInline{Bialaszek, W., Marcowski, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{82. }%
+\CSLLeftMargin{86. }%
 \CSLRightInline{Preece, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{83. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{84. }%
+\CSLLeftMargin{88. }%
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 \emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{82}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{86}.
 
@@
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,83} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{84}.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,87} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{88}.
 

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
deleted some notes
thoughts on states and traits

@@
 ## Trait character of SVs
-From relatively early on in ER research, the question was asked whether the use of certain strategies is habitual, i.e. whether they have a trait character[@GrossJohn2003].
-Although 
+
+In order to further assess the relevance of the calculated individual SVs, it would be important to know how stable the values are, i.e. whether they would show trait character.
+In other words, do the values we calculate represent a stable value within the individual?
+This conclusion cannot be drawn from the present study alone.
 The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
+By definition, this represents a state.
+As previously noted, personal regulation goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
+We belief that these goals, factors and demands also influence individual SVs of ER strategies.
+Our data presented in this study support this idea.
+However, this also means that SVs should differ according to situational factors (e.g., intensity of stimuli).
+It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
 
-Hat das Trait-Charakter?
+has been noted by Wilms and colleagues[@Wilms2020] that situational factors and ER goals should be treated as states.
 

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
finished discussion

@@
 It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
-
-has been noted by Wilms and colleagues[@Wilms2020] that situational factors and ER goals should be treated as states.
-
-State character of goals @Wilms2020
+In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals[@Tamir2016].
+Wilms and colleagues[@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
+In another situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, another strategy might appear more helpful and thus have a higher SV.
+It should also be noted that the computation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
+Therefore, SVs could vary if other reference strategies are used.
+It is conceivable that the subjective values are likely to correlate very highly in situations with similar demands and goals. 
+They would thus reflect habits, or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
+However, our data are not suitable for answering this question.
+In future, the SVs should therefore be collected in several similar situations. 
+Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].
 
@@
 Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort[@Bialaszek2017].
-n the future, however, it should be examined how the level of incentives affects subjective values.
+In the future, however, it should be examined how the level of incentives affects subjective values.
 

### 2023-03-16 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

@@
 We did not use an optimization algorithm to improve the fit of the random intercept model.
-We did not exclude any data points.
+A total of `r nrow(excl_cases_h2b)` data points from `r length(unique(excl_cases_h2b$subject))` participants were excluded, because the residuals exceeded 3 SD above the mean.
 The results of the final model are displayed in Table\ \@ref(tab:H2b-results).
@@
 The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
+Due to the coding scheme of the logistic contrast, the beta coefficient of the $n$-back level has to be interpreted inversely, so SVs decline with increasing $n$-back level.
 The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
@@
 Regardless of the preprocessing pipeline, $n$-back level and $d'$ were significant predictors of SVs, and had stable effect estimates across all pipelines.
-The only pipelines in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors.
-These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an $n$-back level.
+There was only one pipeline in which the median RT was a significant predictor of SVs.
+This pipeline contained data that had been inverse transformed across subjects but within conditions, i.e.
+within the round of an $n$-back level, and RTs beyond 2 $MAD$ from the median had been excluded.
 
@@
 The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis, with betas that varied by less than 0.01.
-In contrast to this stood the variability of the median RT betas, which ranged from about 0.11 to -0.01, and reached significance in only three pipelines.
-These three pipelines had the highest $BF_{10}$ and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data based on the MAD.
+In contrast to this stood the variability of the median RT betas, which ranged from about `r round(max(sca_results$beta_r), digits = 2)` to `r round(min(sca_results$beta_r), digits = 2)`, and reached significance in only one pipeline.
+This pipeline was among the three pipelines with the highest $BF_{10}$, and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 $MAD$ from the median.
 Interestingly, the curve of median RT betas in the upper panel of Figure\ \@ref(fig:sca-plot) mirrored the rectangular pipeline indicators in the transformation rows of the lower panel, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added conclusion

@@
 They would thus reflect habits, or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
+The other way round, of course, it is also conceivable that such habits influence the internal formation of these subjective values.
 However, our data are not suitable for answering this question.
@@
 ## Conclusion
+
+In order to cope with changing emotional demands, individuals can flexibly select and apply strategies from their repertoire[@Bonanno2013;@Aldao2015].
+The strategy that is most suitable for dealing with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
+The combination of influencing factors should be reflected in subjective values, which are formed for all alternatives and serve as a basis for decision-making.
+So far, such subjective values for ER strategies have not been determined.
+Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values. 
+This provides a more detailed investigation of factors influencing the internal generation of these SVs of ER strategies.
+It seems that it is primarily the perceived usefulness and the effort expended that determine the subjective value attributed to a strategy.
+Finally, further research is needed to investigate the factors influencing subjective values and whether these values represent habitual use of ER strategies by individuals.

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
abstract

@@
     orcid         : "0000-0002-5632-419X"
-    affiliation   : "1", "2"
+    affiliation   : "1,2"
     role          :
@@
  However, SVs of ER strategies have not been determined so far. 
- We present a paradigm that is suitable for determining individual SVs of ER strategies. 
- Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort. 
- Relations of SVs to personality traits will be explored.
-keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis"
-wordcount         : "XXXXX"
+ We present a new paradigm for quantifying individual SVs of ER strategies by offering monetary values for ER strategies in an iterative process. 
+ $N=120$ participants first conducted an ER paradigm with the strategies distraction, distancing, and suppression.
+ Afterwards, individual SVs were determined using the new CAD paradigm.
+ SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $BF10=1.62*1021$).
+ Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<0.001$), subjective effort ($t(5, 618.96)=-13.98$, $p<.001$, $f^2=0.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=0.155$).
+ SVs were further associated with self-control ($t(97.97)=2.04$, $p=.044$, $f^2=0.002$), but not with flexible ER. 
+ With our paradigm, we were able to determine subjective values. 
+ The trait character of the values will be discussed.
+keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography"
+wordcount         : "about 9000"
 bibliography      : ["ER_ED.bib"]

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 {}{\PatchFailed}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis\newline\indent Word count: XXXXX}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography\newline\indent Word count: about 9000}
 \usepackage{lineno}
@@
   pdflang={en-EN},
-  pdfkeywords={emotion regulation, regulatory effort, effort discounting, registered report, specification curve analysis},
+  pdfkeywords={emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography},
   hidelinks,
@@
 However, SVs of ER strategies have not been determined so far.
-We present a paradigm that is suitable for determining individual SVs of ER strategies.
-Using a multilevel modelling approach, it will be investigated whether individual SVs can be explained by effectiveness (subjective arousal, facial muscle activity) and subjective effort.
-Relations of SVs to personality traits will be explored.
+We present a new paradigm for quantifying individual SVs of ER strategies by offering monetary values for ER strategies in an iterative process.
+\(N=120\) participants first conducted an ER paradigm with the strategies distraction, distancing, and suppression.
+Afterwards, individual SVs were determined using the new CAD paradigm.
+SVs significantly predicted later choice for an ER strategy (\(\chi^2(4, \textit{n} = 119)=115.40\), \(p<.001\), \(BF10=1.62*1021\)).
+Further, SVs were associated with Corrugator activity (\(t(5, 618.96)=2.09\), \(p=.037\), \(f^2<0.001\)), subjective effort (\(t(5, 618.96)=-13.98\), \(p<.001\), \(f^2=0.035\)), and self-reported utility (\(t(5, 618.96)=29.49\), \(p<.001\), \(f^2=0.155\)).
+SVs were further associated with self-control (\(t(97.97)=2.04\), \(p=.044\), \(f^2=0.002\)), but not with flexible ER.
+With our paradigm, we were able to determine subjective values.
+The trait character of the values will be discussed.
 }
@@
 
-From relatively early on in ER research, the question was asked whether the use of certain strategies is habitual, i.e.~whether they have a trait character\textsuperscript{9}.
-
+In order to further assess the relevance of the calculated individual SVs, it would be important to know how stable the values are, i.e.~whether they would show trait character.
+In other words, do the values we calculate represent a stable value within the individual?
+This conclusion cannot be drawn from the present study alone.
 The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
-
-State character of goals\textsuperscript{71}
+By definition, this represents a state.
+As previously noted, personal regulation goals, situational factors, and contextual demands influence the choice for or against ER strategies\textsuperscript{21}.
+We belief that these goals, factors and demands also influence individual SVs of ER strategies.
+Our data presented in this study support this idea.
+However, this also means that SVs should differ according to situational factors (e.g., intensity of stimuli).
+It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
+In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals\textsuperscript{82}.
+Wilms and colleagues\textsuperscript{71} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
+In another situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, another strategy might appear more helpful and thus have a higher SV.
+It should also be noted that the computation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also \protect\hyperlink{Limitations}{Limitations}).
+Therefore, SVs could vary if other reference strategies are used.
+It is conceivable that the subjective values are likely to correlate very highly in situations with similar demands and goals.
+They would thus reflect habits, or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires\textsuperscript{9}.
+The other way round, of course, it is also conceivable that such habits influence the internal formation of these subjective values.
+However, our data are not suitable for answering this question.
+In future, the SVs should therefore be collected in several similar situations.
+Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being\textsuperscript{9}.
 
@@
 This allows for habituation effects of EMG activity within the block.
-However, block designs are common in ER research\textsuperscript{81} and were used in previous studies\textsuperscript{82}.
+However, block designs are common in ER research\textsuperscript{83} and were used in previous studies\textsuperscript{84}.
 Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
-It is also known that affect labeling might attenuate emotional experience\textsuperscript{83,84}.
+It is also known that affect labeling might attenuate emotional experience\textsuperscript{85,86}.
 That is why we decided not to have the ratings done after every image.
@@
 However, we chose this amount because, first, we have followed the original paradigm of Westbrook\textsuperscript{29}.
-Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{85}.
-n the future, however, it should be examined how the level of incentives affects subjective values.
+Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{87}.
+In the future, however, it should be examined how the level of incentives affects subjective values.
 
@@
 \subsection{Conclusion}\label{conclusion}}
+
+In order to cope with changing emotional demands, individuals can flexibly select and apply strategies from their repertoire\textsuperscript{12,13}.
+The strategy that is most suitable for dealing with contextual demands and achieving regulatory goals is selected\textsuperscript{12,82}.
+The combination of influencing factors should be reflected in subjective values, which are formed for all alternatives and serve as a basis for decision-making.
+So far, such subjective values for ER strategies have not been determined.
+Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values.
+This provides a more detailed investigation of factors influencing the internal generation of these SVs of ER strategies.
+It seems that it is primarily the perceived usefulness and the effort expended that determine the subjective value attributed to a strategy.
+Finally, further research is needed to investigate the factors influencing subjective values and whether these values represent habitual use of ER strategies by individuals.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Haines2016}{}}%
+\CSLLeftMargin{81. }%
+\CSLRightInline{Haines, S.
+J.
+\emph{et al.} \href{https://doi.org/10.1177/0956797616669086}{The wisdom to know the difference: Strategy-situation fit in emotion regulation in daily life is associated with well-being}.
+\emph{Psychological Science} \textbf{27}, 1651--1659 (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tamir2016}{}}%
+\CSLLeftMargin{82. }%
+\CSLRightInline{Tamir, M.
+\href{https://doi.org/10.1177/1088868315586325}{Why do people regulate their emotions?
+A taxonomy of motives in emotion regulation}.
+\emph{Personality and Social Psychology Review} \textbf{20}, 199--222 (2016).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Barreiros2019}{}}%
-\CSLLeftMargin{81. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{Barreiros, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Scheffel2019}{}}%
-\CSLLeftMargin{82. }%
+\CSLLeftMargin{84. }%
 \CSLRightInline{Scheffel, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lieberman2007}{}}%
-\CSLLeftMargin{83. }%
+\CSLLeftMargin{85. }%
 \CSLRightInline{Lieberman, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Torre2018}{}}%
-\CSLLeftMargin{84. }%
+\CSLLeftMargin{86. }%
 \CSLRightInline{Torre, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{85. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{Bialaszek, W., Marcowski, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{86. }%
+\CSLLeftMargin{88. }%
 \CSLRightInline{Preece, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{87. }%
+\CSLLeftMargin{89. }%
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{88. }%
+\CSLLeftMargin{90. }%
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 \emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{86}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{88}.
 
@@
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,87} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{88}.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,89} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{90}.
 

### 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
added descr table

@@ -544,7 +544,50 @@ for (i in seq_len(nrow(data_descr))) {
   data_descr$gender[i] <- data_quest$gender[data_quest$record_id_2 == data_descr$ID[i]]
 }
 
-#data_descr <- reshape(data = data_descr, idvar = "ID", timevar = "strategy", direction = "wide")
+# Table for reporting descriptive values for each block
+
+df.descr <- data.frame(arousal = double(), effort = double(), utility = double(),
+                       Corr = double(), Lev = double())
+
+# fill mean and sd values for each block and each measure
+
+# arousal
+df.descr[1,1] <- paste0(round(mean(data_ER$arousal[data_ER$block=="1_view_neu"]), digits = 1), " \U00B1 " , round(sd(data_ER$arousal[data_ER$block=="1_view_neu"]),digits = 1))
+df.descr[2,1] <- paste0(round(mean(data_ER$arousal[data_ER$block=="2_view_neg"]), digits = 1), " \U00B1 " , round(sd(data_ER$arousal[data_ER$block=="2_view_neg"]),digits = 1))
+df.descr[3,1] <- paste0(round(mean(data_ER$arousal[data_ER$block=="3_distraction"]), digits = 1), " \U00B1 " , round(sd(data_ER$arousal[data_ER$block=="3_distraction"]),digits = 1))
+df.descr[4,1] <- paste0(round(mean(data_ER$arousal[data_ER$block=="4_distancing"]), digits = 1), " \U00B1 " , round(sd(data_ER$arousal[data_ER$block=="4_distancing"]),digits = 1))
+df.descr[5,1] <- paste0(round(mean(data_ER$arousal[data_ER$block=="5_suppression"]), digits = 1), " \U00B1 " , round(sd(data_ER$arousal[data_ER$block=="5_suppression"]),digits = 1))
+
+# effort
+df.descr[1,2] <- paste0(round(mean(data_ER$effort[data_ER$block=="1_view_neu"]), digits = 1), " \U00B1 " , round(sd(data_ER$effort[data_ER$block=="1_view_neu"]),digits = 1))
+df.descr[2,2] <- paste0(round(mean(data_ER$effort[data_ER$block=="2_view_neg"]), digits = 1), " \U00B1 " , round(sd(data_ER$effort[data_ER$block=="2_view_neg"]),digits = 1))
[…]

### 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added descr table

@@
 To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
-We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully evoked emotional arousal and physiological responding.<!--JZ: Am besten auch die Richtung angeben, also "...valence for an increase in subjective..."-->
+Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
+We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.
 
@@
 For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
+[INSERT TABLE 1 HERE]
+
+``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
+papaja::apa_table(
+  df.descr,
+  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
+  booktabs = TRUE,
+  escape = FALSE,
+  placement = "H")
+```
 
@@
 
-[INSERT TABLE 1 HERE]
+[INSERT TABLE 2 HERE]
 
@@
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
-Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.<!--JZ: Mir wurde mal die Verwendung von Worten wie "interestingly" im Ergebnisteil angekreidet, also die Bewertung vielleicht bis zum Diskussionsteil aufheben-->
+The predictor utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
 Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.

### 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Analyes_ERED.r
some comments

@@ -1386,6 +1386,11 @@ choice_chisq <- stats::chisq.test(data_choice$choice, data_choice$pred_choice)
 choice_chisq_BF <- BayesFactor::contingencyTableBF(x = choice_chisq[["observed"]],
                                                    sampleType = "jointMulti")
 
+# Heat Map
+
+# Chisq.Map <- ggplot2::ggplot(data = choice_chisq$observed, aes(x))
+# heatmap(choice_chisq$observed, Colv = NA, Rowv = NA, scale = "column")
+
 # build df in long format
 
 data_choice_long <- data_SV[,1:3]
@@ -1468,12 +1473,6 @@ Flex_LM <- stats::lm(formula = FlexER ~ intercept + slope, data = data_flex)
 
 Flex_LM_BF <- BayesFactor::regressionBF(formula = FlexER ~ intercept + slope, data = data_flex)
 
-
-# ggplot2::ggplot(data_SV, aes(x = strat_r, y = sv, color  = ID))+
-#   geom_point(color = "black") +
-#   geom_smooth(method = "lm", fill = NA)+
-#   theme(legend.position = "none")+
-#   ylim(0,1.5)
 
 #################### STATISTICAL ANALYSES: EXPLORATORY ANALYSES ############
 

### 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator} and \emph{Levator} activity.
-We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully evoked emotional arousal and physiological responding.
+Descriptive values of each predictor for each condition can be found in table \ref{tab:TabDescr}.
+We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully increased emotional arousal and physiological responding.
 
@@
 For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
+{[}INSERT TABLE 1 HERE{]}
+
+\begin{lltable}
+
+\begin{longtable}{llllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.}\\
+\toprule
+ & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:TabDescr} continued}}\\
+\toprule
+ & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
+\midrule
+\endhead
+$View_{neu}$ & 26.6 ± 39.1 & 18.1 ± 27.4 &  & 0.04 ± 6.99 & 0.09 ± 1.84\\
+$View_{neg}$ & 187.8 ± 87.3 & 49.4 ± 62.3 &  & 1.03 ± 7.21 & 0.58 ± 3.2\\
+Distraction & 158.1 ± 92.5 & 208.5 ± 96.1 & 216.6 ± 93.2 & 0 ± 7.67 & -0.05 ± 1.16\\
+Distancing & 164 ± 87.2 & 189.8 ± 92.3 & 214.8 ± 78.6 & 0.25 ± 1.92 & 0.01 ± 1\\
+Suppression & 168.6 ± 95.8 & 158.3 ± 99.5 & 229.3 ± 95 & 0.07 ± 3.78 & -0.03 ± 0.92\\
+\bottomrule
+\end{longtable}
+
+\end{lltable}
 
@@
 
-{[}INSERT TABLE 1 HERE{]}
+{[}INSERT TABLE 2 HERE{]}
 
@@
 The values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
-Interestingly, utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5\% of variance in SVs.
+The predictor utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5\% of variance in SVs.
 Effort rating showed an effect size of \(f^{2}=\) 0.035.
@@
 The authors declare no competing interests.
-
-\newpage
-\setcounter{figure}{0}
-
-\hypertarget{figures-and-figure-captions}{%
-\section{Figures and figure captions}\label{figures-and-figure-captions}}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{ }\label{fig:ResponsePatternsAppendix}
-\end{figure}
-
-\emph{Figure 1.} Exemplary visualization of two response patterns.
-In the top half, the person has a clear preference for one of the three strategies.
-In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can also be represented by our paradigm.
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{ }\label{fig:DesignEREDappendix}
-\end{figure}
-
-\emph{Figure 2.} Block design of the paradigm.
-Every participant starts with two ``active viewing'' blocks containing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants.
-After, the discounting procedure takes place.
-All three regulation strategies are pairwise compared.
-Before the last block, participants can decide which regulation strategy they want to reapply.
-Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale.
-
-\hypertarget{DesignTable}{%
-\section{Design Table}\label{DesignTable}}
+\# Design Table \{\#DesignTable\}
 

### 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added direction of results

@@
   caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
-  booktabs = TRUE,
   escape = FALSE,
-  placement = "H")
+  placement = "H",
+  landscape = TRUE)
 ```
@@
 $$
-As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant association with SVs.
-In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).<!--JZ: Auch hier gern die Richtung des Effekts mit hinschreiben (dass Corrugator und Utility beide mit höheren SVs zusammenhängen, ist ja eher unerwartet-->
+As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
 However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).

### 2023-03-28 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
table 1 is the anti hero

@@
 For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
+
 {[}INSERT TABLE 1 HERE{]}
 
-\begin{lltable}
-
-\begin{longtable}{llllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.}\\
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.}
+
+\footnotesize{
+
+\begin{tabular}{lccccl}
 \toprule
@@
 \midrule
-\endfirsthead
-\caption*{\normalfont{Table \ref{tab:TabDescr} continued}}\\
-\toprule
- & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
-\midrule
-\endhead
 $View_{neu}$ & 26.6 ± 39.1 & 18.1 ± 27.4 &  & 0.04 ± 6.99 & 0.09 ± 1.84\\
@@
 \bottomrule
-\end{longtable}
-
-\end{lltable}
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 
@@
 \]
-As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant association with SVs.
+As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).

### 2023-03-28 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added blank space
table 1 is the anti hero

@@
 For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
+
 [INSERT TABLE 1 HERE]
@@
   placement = "H",
-  landscape = TRUE)
+  font_size = "footnotesize",
+  align = c("l","c","c","c","c"))
 ```

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added license to plots

@@
 The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice.
-The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.", fig.pos="H"}
+The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 The colourbar indicates the BF10.
-The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}
+The pipelines are sorted in descending order of the magnitude of the n-back level beta.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 $N=116$.
-There is a horizontal jitter of 0.4 and a vertical jitter of 0.05 for visual clarity.", fig.pos="H"}
+There is a horizontal jitter of 0.4 and a vertical jitter of 0.05 for visual clarity.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 Each line indicates a participant, the colours indicate their Need for Cognition (NFC) score.
-$N=116$.", fig.pos="H"}
+$N=116$.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 Colours indicate Need for Cognition (NFC) score above or below the median.
-$N=116$.", fig.pos="H"}
+$N=116$.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 

### 2023-03-28 06_Paper/COG-ED/Stage 2/Analysis.R
added new plot

@@ -1654,7 +1654,7 @@ ggplot(h3b_data, aes(level, ntlx, fill = nfcmedian, color = nfcmedian)) +
       theme(legend.title = element_text())
 
 ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 7, height = 4.5, units = "in",
-       device = "tiff", dpi = 900, filename = "h3b-plot.eps")
+       device = "tiff", dpi = 500, filename = "h3b-plot.eps")
 
 # delete temporary data frame
 
@@ -2104,6 +2104,24 @@ explor_contrasts_interact[ ,c("Estimate","$SE$","$t$")] <- format(round(explor_c
 explor_contrasts_interact$`$p$` <- format(round(explor_contrasts_interact$`$p$`, digits = 3), nsmall = 2)
 explor_contrasts_interact$`$p$`[explor_contrasts_interact$`$p$` == "0.000"] <- "<.001" 
   
+# plot results
+
+ggplot2::ggplot(explor_data, aes(x = level, y = sv, fill = nfcmedian)) +
+  geom_smooth(aes(group = nfcmedian, color = nfcmedian), method = "loess") +
+  geom_boxplot(alpha = .4, outlier.shape = NA, width = .45, position = position_dodge(width = 0.7)) +
+  geom_jitter(aes(color = nfcmedian, fill = NA), shape = 1, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.7)) +
+  ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
+  scale_fill_manual(values = MetBrewer::met.brewer("Hiroshige",2), name = "NFC group", labels = c("Above median","Below median")) +
+  scale_color_manual(values = MetBrewer::met.brewer("Hiroshige",2)) +
+  guides(color = "none") +
+  geom_vline(xintercept = c(0.5,1.5,2.5,3.5,4.5), colour = "grey", linetype = 3) +
+  xlab("n-back level") + 
+  ylab("Subjective values") +
+  theme(legend.title = element_text())
+
+ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 7, height = 5, units = "in",
+       device = "tiff", dpi = 500, filename = "nfcgroups-sv.eps")
+
 ##### Save variables ###########################################################
 
 save.image(file = "Workspace.RData")

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
rewrote adjustments section & replaced NFC SV plot

@@
 Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the Supplementary Material).
-And secondly, we needed to re-assign the SCA to the MLM in hypothesis 2b, to which it belonged in the initial submission.
-Following the advice of the reviewers, we had separated the NFC analysis from the MLM, and wanted to apply the SCA to the new NFC analysis (hypothesis 3a), as this was one of our main points of interest.
-However, since hypothesis 3a does not contain any RT data and the SCA is therefore only useful for the MLM in hypothesis 2b, we applied it to the MLM.
+And secondly, we changed to which hypothesis we applied the specification curve analysis (SCA).
+In the initial Stage 1 submission, we had applied it to the MLM of hypothesis 2b, which at this point included NFC as a predictor.
+Following the advice of the reviewers, we removed NFC from the MLM, and analyzed NFC in an rmANOVA (hypothesis 3a) instead.
+Since NFC was of great interest to us, we decided to apply the SCA to hypothesis 3a rather than 2b to provide a measure of robustness.
+However, hypothesis 3a does not contain any RT data, so the SCA is only useful for the MLM in hypothesis 2b.
+Therefore, we applied it to the MLM.
 
@@
 
+For each rmANOVA we report the generalized eta squared $\\hat{\\eta}^2_G$, which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
 We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across $n$-back levels.
@@
 
-Figure\ \@ref(fig:nfc-sv) shows a scatterplot of SVs per $n$-back level, colored depending on the participant's NFC score.
+Figure\ \@ref(fig:nfcgroups-sv) shows the SVs per $n$-back level for participants with NFC scores above and below the median.
 There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across $n$-back levels.
@@
 
-```{r nfc-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level.
-Each dot indicates a participant, the colours indicate their Need for Cognition (NFC) score.
+```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
 $N=116$.
-There is a horizontal jitter of 0.4 and a vertical jitter of 0.05 for visual clarity.
+The scatter has a horizontal jitter of 0.2.
+Smoothing of conditional means with Loess method.
 Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfc-sv.png"))
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfcgroups-sv.png"))
 

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated description of SCA plot

@@
 All NASA-TLX subscale scores increased across $n$-back levels, so evidence was in favour of H1c.
-The effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
+Ratings on the effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
 Three subscales had significant differences between all contrasts except for 3- versus 4-back:
@@
 Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
-Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(pairs(hypothesis1c_physical_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
+Ratings on the physical subscale were higher for more difficult levels (`r apa_print(hypothesis1c_physical_rmanova)$full_result$level`, `r apa_print(hypothesis1c_physical_BF)$statistic`), apart from the contrasts 2- versus 3-back (`r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 2], y = h1c_data$physical[h1c_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) and 3- versus 4-back (`r apa_print(BayesFactor::ttestBF(x = h1c_data$physical[h1c_data$level == 3], y = h1c_data$physical[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
 The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.
@@
 
-When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
+When asking participants what motivated their decisions in the cognitive effort discounting paradigm, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
 The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
@@
 ```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
-The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value.
-The colourbar indicates the BF10.
-The pipelines are sorted in descending order of the magnitude of the n-back level beta.
+Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a).
+The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
+The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level.
 Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed panel mentions to a and b

@@
 There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (left panel of Figure\ \@ref(fig:h3ac-plot)).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3ac-plot)a).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.
@@
 There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
-In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
+In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (Figure\ \@ref(fig:h3ac-plot)b).
 Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
@@
 This pipeline was among the three pipelines with the highest $BF_{10}$, and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 $MAD$ from the median.
-Interestingly, the curve of median RT betas in the upper panel of Figure\ \@ref(fig:sca-plot) mirrored the rectangular pipeline indicators in the transformation rows of the lower panel, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
+Interestingly, the curve of median RT betas in Figure\ \@ref(fig:sca-plot)a mirrored the rectangular pipeline indicators in the transformation rows of Figure\ \@ref(fig:sca-plot)b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
 As Fernandez et al.[-@Fernandez2020] found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond $\alpha=.05$, and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.

### 2023-03-28 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
I knew tables in markdown were trouble when i walked in

--- 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
@@
 For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
+
 {[}INSERT TABLE 1 HERE{]}
@@
 
-\begin{longtable}{llllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\begin{longtable}{rccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
 \caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.}\\

### 2023-03-28 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
I knew tables in markdown were trouble when i walked in

--- 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
   placement = "H",
+  align = c("r","c","c","c","c","c"),
   landscape = TRUE)

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which estimates subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm, which estimates SVs of tasks without defaulting to the objective task load as a benchmark.
-For this purpose, we changed the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
+This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which estimates subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm to estimate SVs of tasks without defaulting to the assumed objective task load as a benchmark.
+For this purpose, we adapted the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
 The analyses were closely aligned with those in Westbrook et al.[-@Westbrook2013] to demonstrate the changes in SVs brought about by the new paradigm.
@@
 
-Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
+In the analysis of SV difference scores, the NFC group did not reach significance as a predictor.
 This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
@@
 While the Stage 1 review process made the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
-For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
+For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, or even more promising, as a continuous measure, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
 Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
@@
 However, findings by Bialaszek et al.[-@Bialaszek2017] suggest that participants are actually more sensitive to effort when the reward is small.
-Nevertheless, we exceeded the largest required sample size by `r round(nrow(data_quest)/53, digits = 1)` times, which gives our analyses high statistical power, and we adhered to the agreed upon analyses of Stage 1.
+Nevertheless, we exceeded the largest required sample size by `r round(nrow(data_quest)/53, digits = 1)` times, which gives our analyses high statistical power.
 
@@
 
-Effort and reward are two highly subjective concepts with relevance in daily life.
+Effort and reward are relevant in everyday life, yet these constructs vary in their conceptualization across individuals and even studies.
 With each decision an individual makes, they must weigh the required effort against the expected reward to decide if and how to behave in that situation.
@@
 However, effort-related traits such as Need for Cognition suggest that this is not the case.
-Therefore, we developed a paradigm that allows effort discounting independent of objective task load, which we tested using an $n$-back task.
+Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an $n$-back task.
 The results showed that many participants indeed preferred a more or even the most difficult $n$-back level.

### 2023-03-29 06_Paper/COG-ED/Stage 2/Analysis.R
corrected n_quest computation

@@ -164,7 +164,7 @@ data_quest <- cbind(data_quest, adherence = all_quest$followup_adherence[setinde
 
 # some participants started filling out the questionnaires two times, so their code appears twice
 
-data_quest <- data_quest %>% filter(complete.cases(.))
+data_quest <- data_quest %>% filter(!is.na(nfc_16))
 
 # make a copy for counting the amount of participants who filled out the questionnaires
 

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated number of participants
made M plusminus SD

@@
 Data was collected between the 16th of August 2022 and the 3rd of February 2023.
-All of the $N=`r n_quest`$ participants who filled out the online questionnaires came to the first lab session.
+Of the $N=`r n_quest`$ participants who filled out the online questionnaires, $n=`r nrow(data_quest)`$ came to the first lab session.
 Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
-Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M=`r round(mean(data_quest[,"age"]), digits = 1)`$ ($SD=`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
+Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M±SD=`r format(round(mean(data_quest[,"age"]), digits = 1), nsmall = 1)`±`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
 

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote about BIC/AIC and stop rules

@@
 An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other ($\chi^2 (`r compare_h2b$Df[2]`)$ = `r compare_h2b$Chisq[2]`, $p<.001$), and with an Akaike Information Criterion of $AIC=`r compare_h2b$AIC[2]`$ and a Bayesian Information Criterion of $BIC=`r compare_h2b$BIC[2]`$ the declining logistic model was superior to the linear model ($AIC=`r compare_h2b$AIC[1]`$, $BIC=`r compare_h2b$BIC[1]`$).
+Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
 The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
@@
 For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, or even more promising, as a continuous measure, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
+To arrive at a sample with more balanced NFC scores, recruitment efforts should be focused on representative population samples and/or collecting data with an NFC-based stop rule.
 Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote about NIPS

@@
 This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
+Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmidt et al.
+(2013)[-@Schmidt2013] and Blum et al.
+(2018)[-@Blum2018] in the same-named NIPS model.
+The NIPS model describes behaviour as a function of situational affordance which is mediated by personality traits.
+The behavioural variability follows an s-shaped curve that is shifted along the y-axis depending on the trait level, such that "strong" situations with low or high situational affordance elicit the least behavioural variability, while "weak" situations with moderate affordance maximize individual differences.
+In our study, the situational affordance is the $n$-back level and the behaviour is the SV.
+Hence, the variability in SVs increased from 1- to 4-back, and participants with higher NFC showed a more shallow decline in SVs as the situational affordance approached moderate values.
+According to the NIPS model, we can expect the SVs of participants with higher and lower NFC to converge again in levels of $n>4$, since behavioural variability decreases when situational affordance is high.
+The declining logistic contrast of SVs across levels resembles the asymptotic s-shaped curve of the NIPS model[@Schmidt2013;@Blum2018] and should be tested in a setting with $n$-back levels exceeding $n=4$.
 

### 2023-03-29 06_Paper/COG-ED/Stage 2/Analysis.R
updated H3ac plot

@@ -1487,21 +1487,19 @@ hypothesis3a_contrasts_nlevel$`$p$`[hypothesis3a_contrasts_nlevel$`$p$` == "0.00
 # plot
 
 ggplot(h3a_data, aes(nlevels, svdiff, fill = nfcmedian, color = nfcmedian)) +
-  ggrain::geom_rain(alpha = .5, rain.side = 'f2x2', id.long.var = "subject", likert = FALSE,
-            violin.args = list(color = NA, alpha = .7, scale = "count", adjust = 1.3, width = 0.8),
-            line.args = list(size = .9, alpha = .5),
-            line.args.pos = list(position = position_jitter(width = 0, height = 0.1)),
-            point.args = list(alpha = 0)) +
+  geom_violin(alpha = .5, scale = "count", adjust = 2.5) +
+  geom_boxplot(alpha = .5, width = .1, color = "black", position = position_dodge(.9)) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
   scale_fill_manual(values = MetBrewer::met.brewer("Hiroshige",2), name = "NFC group", labels = c("Above median","Below median")) +
   scale_color_manual(values = MetBrewer::met.brewer("Hiroshige",2)) +
   guides(color = 'none') +
+  geom_vline(xintercept = 1.5, colour = "darkgrey", linetype = 3) +
   xlab("n-back levels") + 
   ylab("Difference in subjective values") +
   theme(legend.title = element_text())
 
 ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 7, height = 5, units = "in",
-       device = "tiff", dpi = 900, filename = "h3a-plot.eps")
+       device = "tiff", dpi = 500, filename = "h3a-plot.eps")
 
 # remove temporary variables
 
@@ -1776,21 +1774,19 @@ hypothesis3c_contrasts_levels$`$p$`[hypothesis3c_contrasts_levels$`$p$` == "0.00
 # plot
 
 ggplot(h3c_data, aes(nlevels, aversdiff, fill = nfcmedian, color = nfcmedian)) +
-  ggrain::geom_rain(alpha = .5, rain.side = 'f2x2', id.long.var = "subject", likert = FALSE,
-                    violin.args = list(color = NA, alpha = .7, scale = "count", adjust = 1.3, width = 0.8),
-                    line.args = list(size = .9, alpha = .5),
[…]

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
explained diffscores

@@
 Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3ac-plot)a).
-This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.
+This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.
 
@@
 In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (Figure\ \@ref(fig:h3ac-plot)b).
-Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
+Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), indicating that in the same way in which the SVs decreased more strongly from 2- to 3-back than from 1- to 2-back, the aversion increased more strongly.
 The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated plot description H3ac

@@
 There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3ac-plot)a).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences (Figure\ \@ref(fig:h3ac-plot)a).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.
 
-```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (left) and aversiveness ratings (right) when subtracting 2- from 1-back and 3- from 2-back.
-Each line indicates a participant, the colours indicate their Need for Cognition (NFC) score.
+```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
+Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
+NFC = Need for Cognition score.
 $N=116$.
@@
 The NIPS model describes behaviour as a function of situational affordance which is mediated by personality traits.
-The behavioural variability follows an s-shaped curve that is shifted along the y-axis depending on the trait level, such that "strong" situations with low or high situational affordance elicit the least behavioural variability, while "weak" situations with moderate affordance maximize individual differences.
-In our study, the situational affordance is the $n$-back level and the behaviour is the SV.
+The behavioural variability follows an s-shaped curve, such that "strong" situations with low or high situational affordance elicit the least behavioural variability, while "weak" situations with moderate affordance maximize individual differences.
+These differences are caused by a person's expression of a certain trait, which shifts the curve along the y-axis.
+In our study, the situational affordance is the $n$-back level and the behaviour is the SV, following a declining logistic curve, i.e. a mirrored s-shape.
 Hence, the variability in SVs increased from 1- to 4-back, and participants with higher NFC showed a more shallow decline in SVs as the situational affordance approached moderate values.
 According to the NIPS model, we can expect the SVs of participants with higher and lower NFC to converge again in levels of $n>4$, since behavioural variability decreases when situational affordance is high.
-The declining logistic contrast of SVs across levels resembles the asymptotic s-shaped curve of the NIPS model[@Schmidt2013;@Blum2018] and should be tested in a setting with $n$-back levels exceeding $n=4$.
+An investigation of this relationship using the COG-ED paradigm[-@Westbrook2013] had been encouraged by Strobel et al.[@Strobel2020] based on their findings on demand avoidance and cognitive effort investment.
+With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model[@Schmidt2013;@Blum2018] and should be tested further in a setting with $n$-back levels exceeding $n=4$.
 

### 2023-03-29 06_Paper/COG-ED/Stage 2/Analysis.R
0.000 to <.001 in table 1

@@ -960,7 +960,7 @@ colnames(hypothesis1b_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$
 hypothesis1b_contrasts$Contrast <- gsub("X", "", hypothesis1b_contrasts$Contrast)
 hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$")] <- round(hypothesis1b_contrasts[ ,c("Estimate","$SE$","$t$")], digits = 2)
 hypothesis1b_contrasts$`$p$` <- format(round(hypothesis1b_contrasts$`$p$`, digits = 3), nsmall = 2)
-hypothesis1b_contrasts$`$p$`[hypothesis1b_contrasts$`$p$` == 0.000] <- "<.001"
+hypothesis1b_contrasts$`$p$`[hypothesis1b_contrasts$`$p$` == "0.000"] <- "<.001"
 
 # remove the temporary variable
 

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
removed +-0.00 from BF in H3b (scandalously)

@@
 Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
-Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M±SD=`r format(round(mean(data_quest[,"age"]), digits = 1), nsmall = 1)`±`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
+Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M\\pmSD=`r format(round(mean(data_quest[,"age"]), digits = 1), nsmall = 1)`\\pm`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
 
@@
 
-The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$level, split=' \\pm', fixed=TRUE))[1]`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian, split=' \\pm', fixed=TRUE))[1]`).
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
some final adjustments

--- 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
@@
   One approach to quantify the SVs of levels of difficulty of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
-  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
+  However, it fails to acknowledge the highly individual nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
   Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
   We replicated the analysis of Westbrook and colleagues with an adapted version, the Cognitive and Affective Discounting (CAD) Paradigm.
-  It quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
+  It quantifies SVs without assuming that the easiest level is preferred, thereby enabling the assessment of SVs for tasks without objective order of task load.
   Results show that many participants preferred a more or the most difficult level.
@@
 The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 
-For each rmANOVA we report the generalized eta squared $\\hat{\\eta}^2_G$, which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
 We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across $n$-back levels.
+For each rmANOVA we report the generalized eta squared $\hat{\eta}^2_G$, which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
 The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`), evidence was not in favour of H1a but in favour of H1b.
@@
 To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
-The ICC of the null model indicated that there was a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.2f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
+The ICC of the null model indicated that there was a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.3f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
 that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs could be explained by differences between participants.
@@
 The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 Smoothing of conditional means with Loess method.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 $N=116$.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
@@
 
-The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r paste(unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$level, split='} \\pm', fixed=TRUE))[1],"}$")`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r paste(unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian, split='} \\pm', fixed=TRUE))[1],"}$")`).
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.
@@
 This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
-Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmidt et al.
-(2013)[-@Schmidt2013] and Blum et al.
+Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmitt et al.
+(2013)[-@Schmitt2013] and Blum et al.
 (2018)[-@Blum2018] in the same-named NIPS model.
@@
 An investigation of this relationship using the COG-ED paradigm[-@Westbrook2013] had been encouraged by Strobel et al.[@Strobel2020] based on their findings on demand avoidance and cognitive effort investment.
-With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model[@Schmidt2013;@Blum2018] and should be tested further in a setting with $n$-back levels exceeding $n=4$.
+With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model[@Schmitt2013;@Blum2018] and should be tested further in a setting with $n$-back levels exceeding $n=4$.
 

### 2023-03-29 06_Paper/COG-ED/Stage 2/Analysis.R
0.000 to <.001

@@ -1154,7 +1154,7 @@ colnames(hypothesis1c_mental_contrasts) <- c("Contrast", "Estimate", "$SE$", "$d
 hypothesis1c_mental_contrasts$Contrast <- gsub("X", "", hypothesis1c_mental_contrasts$Contrast)
 hypothesis1c_mental_contrasts[ ,c("Estimate","$SE$","$t$")] <- round(hypothesis1c_mental_contrasts[ ,c("Estimate","$SE$","$t$")], digits = 2)
 hypothesis1c_mental_contrasts$`$p$` <- format(round(hypothesis1c_mental_contrasts$`$p$`, digits = 3), nsmall = 2)
-hypothesis1c_mental_contrasts$`$p$`[hypothesis1c_mental_contrasts$`$p$` == "0.000"] <- "<.001"
+hypothesis1c_mental_contrasts$`$p$`[hypothesis1c_mental_contrasts$`$p$` == "0.00"] <- "<.001"
 
 colnames(hypothesis1c_physical_contrasts) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$\\mathrm{BF}_{\\textrm{10}}$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 hypothesis1c_physical_contrasts$Contrast <- gsub("X", "", hypothesis1c_physical_contrasts$Contrast)

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added figures to end as well

@@
 ### CAD Paradigm
-Figure\ 1 illustrates how different modifications of the COG-ED paradigm [@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
+Figure \@ref(fig:cadparadigm) illustrates how different modifications of the COG-ED paradigm [@Westbrook2013] return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
 The COG-ED paradigm, which compares every more difficult level with 1-back sets the SV of 1-back to 1, regardless of the response pattern.
@@
 
-```{r figure1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+```{r cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 The authors declare no competing interests.
+
+\newpage
+\setcounter{figure}{0}
+
+# Figures
+
+```{r cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+The grey boxes are the choice options shown to the participant.
+The participant's final reward value of the flexible level is displayed after the first arrow.
+The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice.
+The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "Inkscape Figures", "Paradigm_Scheme.png"))
+
+```
+
+```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
+Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a).
+The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
+The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
+
+```
+
+```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
+$N=116$.
+The scatter has a horizontal jitter of 0.2.
+Smoothing of conditional means with Loess method.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfcgroups-sv.png"))
+
+```
+
+```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
+Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
+NFC = Need for Cognition score.
+$N=116$.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3ac-plot.png"))
+
+```
+
+```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
+Colours indicate Need for Cognition (NFC) score above or below the median.
+$N=116$.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3b-plot.png"))
+
+```

### 2023-03-29 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed code chunk names of figures

@@
 
-```{r cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+```{r apx-cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 
-```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
+```{r apx-sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
 Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a).
@@
 
-```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
+```{r apx-nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
 $N=116$.
@@
 
-```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
+```{r apx-h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
 Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
@@
 
-```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
+```{r apx-h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
 Colours indicate Need for Cognition (NFC) score above or below the median.

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
adapted participants

@@
 
-Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
+Data collection took place between 16th of August 2022 and the 3rd of February 2023.
 A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
@@
 Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
+The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M\text{ }\pm\text{ }SD =`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }`r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$ years old), which is `r format(round((sum(data_survey[,"followup_ered_complete"] == 2)-1)/85, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
 Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).

### 2023-03-30 06_Paper/COG-ED/Stage 2/Analysis.R
corrected n_quest

@@ -146,7 +146,7 @@ colnames(all_quest)[1] <- "set" # rename the first column
 
 # compute index of rows in which the data sets change
 
-setindex <- c(1,which(all_quest$set != dplyr::lag(all_quest$set)),nrow(all_quest))
+setindex <- c(1,which(all_quest$set != dplyr::lag(all_quest$set)))
 
 # reshape the data frame for better handling (currently three rows per subject, lots of NAs)
 
@@ -162,20 +162,23 @@ data_quest <- cbind(data_quest, adherence = all_quest$followup_adherence[setinde
                     motivation = all_quest$followup_motivation[setindex+1],
                     motivation_other = all_quest$followup_motivation_other[setindex+1])
 
-# some participants started filling out the questionnaires two times, so their code appears twice
+# keep only those who answered all NFC items
 
 data_quest <- data_quest %>% filter(!is.na(nfc_16))
+
+# sets 2, 6, and 7 were dummy sets to test the NASA TLX iterations
+
+data_quest <- data_quest[!(data_quest$set == "2" | data_quest$set == "2_final" | data_quest$set == "6" | data_quest$set == "6_final" |
+                             data_quest$set == "7" | data_quest$set == "7_final"), ]
 
 # make a copy for counting the amount of participants who filled out the questionnaires
 
 n_quest <- data_quest
 
-# remove the following subjects for misunderstanding the instruction: E17T12, Z15R03, C18D18, H25N04, D24A05, T14G09, D29N05
-# remove the following subject for not remembering the level colours correctly during effort discounting: W16C01
-# sets 2, 6, and 7 were dummy sets to test the NASA TLX iterations
+# now remove the original data sets (which we needed for the time stamps) and keep only the edited sets
 
-data_quest <- data_quest[!(data_quest$subject == "E17T12" | data_quest$subject == "Z15R03" | data_quest$subject == "C18D18" | data_quest$subject == "H25N04" |
-                             data_quest$subject == "D24A05" | data_quest$subject == "T14G09" | data_quest$subject == "D29N05" | data_quest$subject == "W16C01"), ]
+n_quest <- n_quest[grep("_final", n_quest$set), ]
+n_quest <- nrow(n_quest)
 
 # remove any subject who states that they did not adhere to the instructions
 
@@ -197,11 +200,6 @@ acqui_time <- range(acqui_time, na.rm = TRUE)
 
[…]

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
-We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.
+We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.
 

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Analyses_ERED.r
bayes factors

@@ -695,9 +695,9 @@ SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block + ID,
                                            data = Ratings_view,
                                            whichRandom = "ID",
                                            progress = FALSE)
-SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
+SubjArousalView_con$BF10 <- papaja::apa_print(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
                                                                         y = Ratings_view$arousal[Ratings_view$block == "2_view_neg"],
-                                                                        progress = FALSE, paired = TRUE))$bf
+                                                                        progress = FALSE, paired = TRUE))$table[1,"statistic"]
 
 SubjArousalView_con <- cbind(SubjArousalView_con,
                              format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
@@ -751,9 +751,9 @@ EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block + ID,
                                        data = EMG_view,
                                        whichRandom = "ID",
                                        progress = FALSE)
-EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
+EMGCorrView_con$BF10 <- papaja::apa_print(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
                                                                     y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
-                                                                    progress = FALSE, paired = FALSE))$bf
+                                                                    progress = FALSE, paired = FALSE))$table[1,"statistic"]
 
 EMGCorrView_con <- cbind(EMGCorrView_con,
                          format(effectsize::t_to_eta2(t = EMGCorrView_con$t.ratio,
@@ -804,9 +804,10 @@ EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block + ID,
                                       data = EMG_view,
                                       whichRandom = "ID",
                                       progress = FALSE)
-EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
[…]

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
added reasons for choice
post hoc contrasts view

--- 2023-03-03 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
@@
 
-``` {r TabNV, echo=FALSE, message=FALSE, warning=FALSE}
+``` {r TabNVRatings, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
   placement = "H") 
+```
 
+```{r TabNCEMG}
 papaja::apa_table(
@@
 
-## Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding {#SupplementEffectER}
+## Post-hoc contrasts for effects of valence on subjective arousal and physiological responding {#SupplementEffectValence}
 
-``` {r SupplEffectER, echo=FALSE, message=FALSE, warning=FALSE} 
+``` {r SupplEffectArousalView, echo=FALSE, message=FALSE, warning=FALSE} 
+papaja::apa_table(
+  SubjArousalView_con,
+  caption = "Post-hoc contrasts for effects of valence on subjective arousal ratings in the active viewing conditions.",
+  escape = FALSE,
+  placement = "H",
+  font_size = "footnotesize"
+  )
+```
+
+``` {r SupplFigArousalView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings of the active viewing conditions vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjArousalView.png"))
+```
+
+``` {r SupplEffectCorrView, echo=FALSE, message=FALSE, warning=FALSE}
+papaja::apa_table(
+  EMGCorrView_con,
+  caption = "Post-hoc contrasts for effects of valence on Corrugator activity in the active viewing conditions.",
+  escape = FALSE,
+  placement = "H",
+  font_size = "footnotesize"
+  )
+```
+
+``` {r SupplFigCorrView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV during the active viewing conditions, vizalized as boxplots.
+Dots represent individual Corrugator activity measures placed in 150 quantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigCorrView.png"))
+```
+
+``` {r SupplEffectLevView, echo=FALSE, message=FALSE, warning=FALSE}
+papaja::apa_table(
+  EMGLevView_con,
+  caption = "Post-hoc contrasts for effects of valence on Levator activity in the active viewing conditions.",
+  escape = FALSE,
+  placement = "H",
+  font_size = "footnotesize"
+  )
+```
+
+``` {r SupplFigLevView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV during the active viewing conditions, vizalized as boxplots.
+Dots represent individual Levator activity measures placed in 150 quantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigLevView.png"))
+```
+
+\newpage
+
+## Post-hoc contrasts for effects of ER strategies on subjective arousal and physiological responding {#SupplementEffectER}
+
+``` {r SupplEffectArousalReg, echo=FALSE, message=FALSE, warning=FALSE} 
 papaja::apa_table(
   SubjArousalReg_con,
-  caption = "Post-hoc tests for effects of ER strategies on subjective arousal ratings.",
+  caption = "Post-hoc contrasts for effects of ER strategies on subjective arousal ratings.",
   escape = FALSE,
-  placement = "H"
+  placement = "H",
+  font_size = "footnotesize"
   )
+```
 
+``` {r SupplFigArousalReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjArousalReg.png"))
+```
+
+``` {r SupplEffectCorrReg, echo=FALSE, message=FALSE, warning=FALSE}
 papaja::apa_table(
   EMGCorrReg_con,
-  caption = "Post-hoc tests for effects of ER strategies on Corrugator activity",
+  caption = "Post-hoc contrasts for effects of ER strategies on Corrugator activity",
   escape = FALSE,
-  placement = "H"
+  placement = "H",
+  font_size = "footnotesize"
   )
+```
 
+``` {r SupplFigCorrReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV vizalized as boxplots.
+Dots represent individual Levatorr activity measures placed in 150 quantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigCorrReg.png"))
+```
+
+``` {r SupplEffectLevReg, echo=FALSE, message=FALSE, warning=FALSE}
 papaja::apa_table(
   EMGLevReg_con,
-  caption = "Post-hoc tests for effects of ER strategies on Levator activity",
+  caption = "Post-hoc contrasts for effects of ER strategies on Levator activity",
   escape = FALSE,
-  placement = "H"
+  placement = "H",
+  font_size = "footnotesize"
   )
@@
 ```
+
+``` {r SupplFigLevReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV vizalized as boxplots.
+Dots represent individual Levator activity measures placed in 150 quantiles.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigLevReg.png"))
+```
+\newpage
+
+## Reasons for decision made by the participants in the last regulation block
 

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
reference to supplement

@@
 Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
-We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.
+We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
+Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView).
 
@@
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
+For detailed information on post-hoc tests, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
 
@@
 \begin{split}
-SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
+SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
 \end{split}

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Analyses_ERED.r
changed color palette

@@ -714,11 +714,9 @@ SubjArousalView_con[1, 1] <- "$View_{neutral} - View_{negative}$"
 FigSubjArousalView <- ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal, fill = factor(block))) +
   ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.7, color = NA) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
-  geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.5)+
-  #geom_point(size = 1, alpha = 0.75, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2), aes(col = factor(block)))+
-  ggthemes::scale_fill_tableau(palette = "Tableau 10")+
-  ggthemes::scale_color_tableau(palette = "Tableau 10")+
-  #geom_vline(xintercept = c(1.5,2.5,3.5,4.5), colour = "grey", linetype = 3) +
+  geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.8)+
+  scale_fill_manual(values = c("#006666","#CC3300"))+
+  scale_color_manual(values = c("#006666","#CC3300"))+
   scale_x_discrete(name = "Active viewing",
                    limits = c("1_view_neu", "2_view_neg"),
                    labels = c("Neutral", "Negative")) +
@@ -772,11 +770,9 @@ EMG_view_plot <- EMG_view %>% group_by(ID, block) %>% summarise_at(vars("Corr","
 FigEMGCorrView <- ggplot2::ggplot(EMG_view_plot, aes(x = block, y = Corr, fill = factor(block))) +
   ggdist::stat_dots(justification = -0.2, quantiles = 150, limits = c(.05, .95), scale = 0.8, color = NA) +
   ggprism::theme_prism(base_size = 12, base_line_size = 0.5, base_fontface = "plain", base_family = "sans") +
-  geom_boxplot(width = 0.12, outlier.color = NA, alpha = 0.5)+
-  #geom_point(size = 1, alpha = 0.75, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.2), aes(col = factor(block)))+
-  ggthemes::scale_fill_tableau(palette = "Tableau 10")+
-  ggthemes::scale_color_tableau(palette = "Tableau 10")+
[…]

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
contrasts and ref to suppl

@@
 We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
-Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView).
+Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).
 
@@
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
+For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
 
@@
 We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
-Post-hoc test showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
+Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).
@@
 
-```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 qantiles.", fig.pos="H"}
+```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected percentage of variance

@@
 The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
-Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
+Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
 We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
@@
 
-The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance. 
+The second model explained `r papaja::printnum(MLM2_r2[2]*100, digits=1)`% of variance. 
 All results of the second model are in Table\ \@ref(tab:TabMLMH5).

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Analyses_ERED.r
formatted table

@@ -1344,6 +1344,9 @@ H5_M2_table$Parameter[1:6] <- c("Intercept", "Effort", "Arousal", "Utility", "Co
 
 H5_M2_table[3:6] <- lapply(H5_M2_table[3:6], as.numeric)
 
+H5_M2_table$`$p$-value` <- format(round(H5_M2_table$`$p$-value`, digits = 3), nsmall = 2)
+H5_M2_table$`$p$-value`[H5_M2_table$`$p$-value` == "0.000"] <-  "<.001"
+
 ######## HYPOTHESIS 6
 
 # 

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added licence to pics

@@
 ```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
+Dots represent individual effort ratings placed in 150 quantiles.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
@@
   escape = FALSE,
-  placement = "H")
+  placement = "H",
+  digits = 3)
 ```
 
-The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
+The predictors effort rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2, digits = 3)$full_result$Corr_cwc`) showed a significant association with SVs.
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
@@
 There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)).
-<!--JZ: Vielleicht wäre hier eine Heatmap auch ganz nice, das scheint wohl eine gute Visualisierung für einen Chi Square Test zu sein (https://www.analyticsvidhya.com/blog/2021/06/decoding-the-chi-square-test%E2%80%8A-%E2%80%8Ause-along-with-implementation-and-visualization/)-->
 
@@
 Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
-$N=120$", fig.pos="H"}
+The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
+$N=120$".
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license., fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
justification for expl analyses

@@
 To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
-Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
+Descriptive values of each predictor for each condition can be found in Table \@ref(tab:TabDescr).
 We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
@@
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
+We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see Figure\ \@ref(fig:FigSubjEffort)).
 Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
@@
 
-We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
+Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
 The starting point for this was the model reported before. 

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
number of digits set to 3 for betas

@@
 $$
-As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
-In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
+As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
 However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
comments and 2 letters
added rm before ANOVA

--- 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 
-Data collection took place between 16th of August 2022 and the 3rd of February 2023.
+Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
+<!-- hier wird "2022-08 and 2023-02" geschrieben, finde ich im Lesefluss nicht so schön.
+Wie wäre es mit "August 2022 and February 2023"?-->
 A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
@@
 Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M\text{ }\pm\text{ }SD =`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }`r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$ years old), which is `r format(round((sum(data_survey[,"followup_ered_complete"] == 2)-1)/85, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
+The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
 Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).
@@
 
-### Manipulation checks
+### Manipulation checks <!-- es gibt keine weitere Überschrift auf dieser Ebene, würde ich jedoch erwarten.-->
 
-#### Subjective arousal and physiological responding
+#### Subjective arousal and physiological responding <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effect of valence on arousal and facial EMG." -->
 
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
+<!-- in den Methods habt ihr es klein und kursiv geschrieben.
+-->
 Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
-We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
-Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).
+We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.
 
@@
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
+For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
 
@@
 We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
-Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
+Post-hoc test showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).
@@
 
-```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 qantiles.", fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
@@
 The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
-Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
+Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
 We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
@@
 
-The second model explained `r papaja::printnum(MLM2_r2[2]*100, digits=1)`% of variance. 
+The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance. 
 All results of the second model are in Table\ \@ref(tab:TabMLMH5).
@@
   escape = FALSE,
-  placement = "H",
-  digits = 3)
+  placement = "H")
 ```
 
-The predictors effort rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2, digits = 3)$full_result$Corr_cwc`) showed a significant association with SVs.
+The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
@@
 Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
-The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
-$N=120$".
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license., fig.pos="H"}
+$N=120$", fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
@@
 \begin{split}
-SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
+SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
 \end{split}

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
slight change in one sentence

@@
 
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
rephrasing of some sentences

@@
 
-#### Subjective arousal and physiological responding <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effect of valence on arousal and facial EMG." -->
+#### Subjective arousal and physiological responding <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effect of valence and emotion regulation on arousal and facial EMG." -->
 
@@
 
-#### Subjective effort of ER strategies
+#### Subjective effort of ER strategies <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effects of emotion regulation on effort" -->
 
@@
 We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
-Post-hoc test showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
+Post-hoc tests showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).
@@
 
-The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
-Here, `r round((54/119)*100, digits = 1)`% stated that they chose the strategy that was easiest for them to implement.
+Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
+`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
 `r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found in Table XX in [supplementary material](#SupplementReasonChoice).
+A more detailed list of all reasons can be found in Table XX <!-- Nummer noch ergänzen --> in [supplementary material](#SupplementReasonChoice).
 

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
Some rephrasing

@@
 
+### Neue Überschrift? <!-- ab hier sind es doch keine Manipulation Checks mehr, oder? -->
 #### Subjective values of ER strategies
@@
 SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
-In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had one SV of 1.0, indicating a clear preference for one ER strategy.
+$n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had one SV of 1.0, indicating a clear preference for one ER strategy.
 Absolute preferences for ER strategies were relatively equally distributed.

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
minor rephrasing and comments

@@
 ### Neue Überschrift? <!-- ab hier sind es doch keine Manipulation Checks mehr, oder? -->
-#### Subjective values of ER strategies
+#### Subjective values of ER strategies and their predictors
 
@@
 The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
-The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
-Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
+The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` between the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
+<!-- für die Lesbarkeit wäre es besser, wenn die Variablen irgendwie anders formatiert wären, kursiv oder in Anführungszeichen.
+-->
+Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance <!-- im PDF steht dasnn 0.90% of variance, aber ihr meint doch 90% of variance, oder?
+--> and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
 We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
@@
 
-The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance. 
+The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance <!-- im PDF steht dasnn 0.41% of variance, aber ihr meint doch 41% of variance, oder? --> . 
 All results of the second model are in Table\ \@ref(tab:TabMLMH5).
@@
 The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
-The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
+The values <!-- welche? Beta? --> were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
 The predictor utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
rephrasing one sentence

@@
 
-To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
+To investigate the ecological validity of the calculated subjective values of ER strategies, we tested whether SVs were associated with the actual choice of participants in the last experimental block.
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
rephrasing 2 sentences

@@
 Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
-The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
-The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
-Additionally, the predictor SV of strategy suppression was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
-The estimated odds ration indicated that a participant is more likely to later choose suppression, when SV of strategy suppression is higher.
+The SV of the strategy distraction contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
+The estimated odds ratio indicated a higher chance of choosing distraction, when the SV of that strategy is higher.
+Additionally, the SV of the strategy suppression contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
+The estimated odds ration indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
 

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
deleted one letter
minor rephrasing and some comments

@@
 Additionally, the SV of the strategy suppression contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
-The estimated odds ration indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
+The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
 
@@
 We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
-The starting point for this was the model reported before. 
+The starting point for this was the model reported before. <!-- welches model genau? -->
 Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
+<!-- ist das wirklich zulässig?
+Ich hab mich gefragt, ob das nich zu Kritik von den Reviewern führen könnte, dass ihr hier nur die vorher sign.
+predictors auswählt.-->
 The third model followed the specification:
@@
 $$
-As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+As expected, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).

### 2023-04-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
adapted headings to methods part

--- 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
@@
 
-Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
-<!-- hier wird "2022-08 and 2023-02" geschrieben, finde ich im Lesefluss nicht so schön.
-Wie wäre es mit "August 2022 and February 2023"?-->
+Data collection took place between 16th of August 2022 and the 3rd of February 2023.
 A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
@@
 
-### Manipulation checks <!-- es gibt keine weitere Überschrift auf dieser Ebene, würde ich jedoch erwarten.-->
+### Manipulation checks
 
-#### Subjective arousal and physiological responding <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effect of valence and emotion regulation on arousal and facial EMG." -->
+#### Effect of valence on arousal and facial EMG
 
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
-<!-- in den Methods habt ihr es klein und kursiv geschrieben.
--->
-Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
-We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
+Descriptive values of each predictor for each condition can be found in Table \@ref(tab:TabDescr).
+We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
+Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).
 
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
+#### Effect of emotion regulation on arousal and facial EMG
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
+For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
 
@@
 
-#### Subjective effort of ER strategies <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effects of emotion regulation on effort" -->
+#### Effect of emotion regulation of effort
 
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
-Post-hoc tests showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
+We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see Figure\ \@ref(fig:FigSubjEffort)).
+Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).
@@
 
-```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots. Dots represent individual effort ratings placed in 150 qantiles.", fig.pos="H"}
+```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
@@
 
-Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
-`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
+The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
+Here, `r round((54/119)*100, digits = 1)`% stated that they chose the strategy that was easiest for them to implement.
 `r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found in Table XX <!-- Nummer noch ergänzen --> in [supplementary material](#SupplementReasonChoice).
+A more detailed list of all reasons can be found in Table XX in [supplementary material](#SupplementReasonChoice).
 
-### Neue Überschrift? <!-- ab hier sind es doch keine Manipulation Checks mehr, oder? -->
-#### Subjective values of ER strategies and their predictors
+### Subjective values of ER strategies
 
@@
 SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
-$n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had one SV of 1.0, indicating a clear preference for one ER strategy.
+In sum, $n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had one SV of 1.0, indicating a clear preference for one ER strategy.
 Absolute preferences for ER strategies were relatively equally distributed.
@@
 The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
-The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` between the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
-<!-- für die Lesbarkeit wäre es besser, wenn die Variablen irgendwie anders formatiert wären, kursiv oder in Anführungszeichen.
--->
-Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance <!-- im PDF steht dasnn 0.90% of variance, aber ihr meint doch 90% of variance, oder?
---> and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
+The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
+Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
 We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
@@
 
-The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance <!-- im PDF steht dasnn 0.41% of variance, aber ihr meint doch 41% of variance, oder? --> . 
+The second model explained `r papaja::printnum(MLM2_r2[2]*100, digits=1)`% of variance. 
 All results of the second model are in Table\ \@ref(tab:TabMLMH5).
@@
   escape = FALSE,
-  placement = "H")
+  placement = "H",
+  digits = 3)
 ```
 
-The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
-The values <!-- welche? Beta? --> were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
+The predictors effort rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2, digits = 3)$full_result$Corr_cwc`) showed a significant association with SVs.
+The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
 The predictor utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
@@
 
-To investigate the ecological validity of the calculated subjective values of ER strategies, we tested whether SVs were associated with the actual choice of participants in the last experimental block.
+To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
 There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)).
-<!--JZ: Vielleicht wäre hier eine Heatmap auch ganz nice, das scheint wohl eine gute Visualisierung für einen Chi Square Test zu sein (https://www.analyticsvidhya.com/blog/2021/06/decoding-the-chi-square-test%E2%80%8A-%E2%80%8Ause-along-with-implementation-and-visualization/)-->
 
@@
 \begin{split}
-SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
+SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
 \end{split}
 $$
-As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
-In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
+As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
 However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).

### 2023-04-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
first letter of EMG muscle small

@@
 
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, *corrugator* and *levator* activity.
 Descriptive values of each predictor for each condition can be found in Table \@ref(tab:TabDescr).
-We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
+We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
 Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).
@@
 #### Effect of emotion regulation on arousal and facial EMG
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *corrugator* and *levator* activity of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
 For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
@@
 
-### Subjective values of ER strategies
+### Subjective values of ER strategies and their predictors
 
@@
 
-The predictors effort rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2, digits = 3)$full_result$Corr_cwc`) showed a significant association with SVs.
+The predictors effort rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$utility_cwc`), and *corrugator* activity (`r papaja::apa_print(MLM_2, digits = 3)$full_result$Corr_cwc`) showed a significant association with SVs.
 The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.

### 2023-04-03 06_Paper/ER-ED/ERED_Stage2/Analyses_ERED.r
corrected row names

@@ -659,7 +659,7 @@ for (i in seq_len(length(unique(data_EMG$block))-1)) {
   
 }
 
-rownames(df.NV.EMG) <- c("Corrgator View Neu", "Corrgator View Neg", "Corrgator Distraction", "Corrgator Distancing", "Corrgator Suppression",
+rownames(df.NV.EMG) <- c("Corrugator View Neu", "Corrugator View Neg", "Corrugator Distraction", "Corrugator Distancing", "Corrugator Suppression",
                           "Levator View Neu", "Levator View Neg", "Levator Distraction", "Levator Distancing", "Levator Suppression")
 colnames(df.NV.EMG) <- c("$M$", "$SD$", "$W$", "$p$")
 

### 2023-04-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
incorporated review of DD

@@
 output: html_document
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 #### Effect of emotion regulation on arousal and facial EMG
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *corrugator* and *levator* activity of four strategies (active viewing, distraction, distancing, suppression).
+
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
@@
 
-``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
+```{r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
 papaja::apa_table(
@@
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see Figure\ \@ref(fig:FigSubjEffort)).
+We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see Figure \@ref(fig:FigSubjEffort)).
 Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
@@
 
-The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
-Here, `r round((54/119)*100, digits = 1)`% stated that they chose the strategy that was easiest for them to implement.
+Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
+`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
 `r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
@@
 We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
-The second model followed the specification: 
-$$
+The second model followed the specification: $$
 \begin{split}
@@
 The second model explained `r papaja::printnum(MLM2_r2[2]*100, digits=1)`% of variance.
-All results of the second model are in Table\ \@ref(tab:TabMLMH5).
+All results of the second model are in Table \@ref(tab:TabMLMH5).
 
@@
 
-``` {r TabMLMH5, echo=FALSE, message=FALSE, warning=FALSE}
+```{r TabMLMH5, echo=FALSE, message=FALSE, warning=FALSE}
 papaja::apa_table(
@@
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure\ \@ref(fig:FigSVChoice)).
+There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure \@ref(fig:FigSVChoice)).
 
@@
 
-Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
+Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022; @Westbrook2013; @Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
 The starting point for this was the model reported before.
 Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
-The third model followed the specification:
-$$
+The third model followed the specification: $$
 \begin{split}
@@
 \end{split}
-$$
-As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+$$ As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).

### 2023-04-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
incorporated comments of DD

@@
 The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
-The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
+The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` between the random effects *subjects* and *recoded strategy* ($BF10$ of the variable *strategy*: `r papaja::apa_print(MLM_1_BF)$statistic`).
 Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
 We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
-The second model followed the specification: $$
+The second model followed the specification: 
+$$
 \begin{split}
@@
 The predictors effort rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2, digits = 3)$full_result$utility_cwc`), and *corrugator* activity (`r papaja::apa_print(MLM_2, digits = 3)$full_result$Corr_cwc`) showed a significant association with SVs.
-The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
+Beta values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
 The predictor utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
@@
 
-To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
+To investigate the ecological validity of the calculated subjective values of ER strategies, we tested whether SVs were associated with the actual choice of participants in the last experimental block.
 Therefore, a $\chi^{2}$ test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see figure \@ref(fig:FigSVChoice)).
+There was a significant association between predicted choice and actual choice (`r papaja::apa_print(choice_chisq, n=119)$statistic[[1]]`, `r papaja::apa_print(choice_chisq_BF)$statistic`; see Figure \@ref(fig:FigSVChoice)).
 
@@
 Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
-The predictor SV of strategy distraction was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
-The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
-Additionally, the predictor SV of strategy suppression was found to contribute to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
-The estimated odds ration indicated that a participant is more likely to later choose suppression, when SV of strategy suppression is higher.
+The SV of the strategy distraction contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
+The estimated odds ratio indicated a higher chance of choosing strategy distraction, when the SV of that strategy is higher.
+Additionally, the predictor SV of the strategy suppression contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
+The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
 
@@
 Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022; @Westbrook2013; @Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
-The starting point for this was the model reported before.
+The starting point for this was the adapted MLM, we reported before.
 Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
@@
 \end{split}
-$$ As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+$$ As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).

### 2023-04-03 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected citation

@@
 
-Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022; @Westbrook2013; @Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
+Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
 The starting point for this was the adapted MLM, we reported before.

### 2023-04-04 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

@@
 Data was collected between the 16th of August 2022 and the 3rd of February 2023.
-Of the $N=`r n_quest`$ participants who filled out the online questionnaires, $n=`r nrow(data_quest)`$ came to the first lab session.
+Of the $N=`r n_quest`$ participants who filled out the NFC questionnaire, $n=`r length(datalist_nback)`$ completed the first lab session.
 Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
-Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M±SD=`r format(round(mean(data_quest[,"age"]), digits = 1), nsmall = 1)`±`r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
+Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M \pm SD=`r format(round(mean(data_quest[,"age"]), digits = 1), nsmall = 1)` \pm `r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
 

### 2023-04-04 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

@@
 Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
-For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
+For more detailed information on psychometric properties of the questionnaires, please see the \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
 
@@
 
-Data collection took place between 2022-08 and 2023-02.
+Data collection took place between 16th of August 2022 and the 3rd of February 2023.
 A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
-Of these, \(N=125\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
+Of these, \(N=124\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
 Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of \(N=120\) participants (100 female; age: \(M=22.5\text{ }\pm\text{ }SD = 3.0\)).
+The final sample consisted of \(N=120\) participants (100 female; age: \(M\text{ }\pm\text{ }SD =22.5\text{ }\pm\text{ }3.0\) years old), which is 1.4 times more than what the highest sample size calculation required.
 Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).
@@
 Descriptive values of each predictor for each condition can be found in table \ref{tab:TabDescr}.
-We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully increased emotional arousal and physiological responding.
+We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.73 \times 10^{48}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.03 \times 10^{18}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 258.85\)).
+Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \ref{tab:SupplEffectArousalView} to @ref(tab:SupplEffectLevView and Figures \ref{fig:SupplFigArousalView} to \ref{fig:SupplFigLevView} in the {[}supplement{]}).
 
 To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator} and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
+We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 156.94\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.97 \times 10^{10}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.68 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
+For detailed information on post-hoc contrasts, please see Tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and Figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
 
@@
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\); see figure~\ref{fig:FigSubjEffort}).
-Post-hoc test showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
+We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.74 \times 10^{53}\); see figure~\ref{fig:FigSubjEffort}).
+Post-hoc contrasts showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
 Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).
@@
 \includegraphics[width=\textwidth]{figures/FigSubjEffort} \caption{Subjective effort ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 qantiles.}\label{fig:FigSubjEffort}
+Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:FigSubjEffort}
 \end{figure}
@@
 
-\caption{\label{tab:TabNV}Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.}
+\caption{\label{tab:TabNVRatings}Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.}
 
@@
 
-\caption{\label{tab:TabNV}Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.}
+\caption{\label{tab:TabNCEMG}Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.}
 
@@
 
-\hypertarget{SupplementEffectER}{%
-\subsection{Post-hoc tests of strategies for effects of ER on subjective arousal and physiological responding}\label{SupplementEffectER}}
+\hypertarget{SupplementEffectValence}{%
+\subsection{Post-hoc contrasts for effects of valence on subjective arousal and physiological responding}\label{SupplementEffectValence}}
 
@@
 
-\caption{\label{tab:SupplEffectArousalReg}Post-hoc tests for effects of ER strategies on subjective arousal ratings.}
+\caption{\label{tab:SupplEffectArousalView}Post-hoc contrasts for effects of valence on subjective arousal ratings in the active viewing conditions.}
+
+\footnotesize{
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+$View_{neutral} - View_{negative}$ & -161.15 & 8.06 & 119.00 & -20.00 & 0.00 & $3.22 \times 10^{36}$ & 0.77 & {}[0.72, 1.00]\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigSubjArousalView} \caption{Subjective arousal ratings of the active viewing conditions vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:SupplFigArousalView}
+\end{figure}
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:SupplEffectCorrView}Post-hoc contrasts for effects of valence on Corrugator activity in the active viewing conditions.}
+
+\footnotesize{
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+$View_{neutral} - View_{negative}$ & -0.27 & 0.05 & 117.00 & -5.27 & 0.00 & $8.67 \times 10^{16}$ & 0.19 & {}[0.10, 1.00]\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigCorrView} \caption{Corrugator activity in mV during the active viewing conditions, vizalized as boxplots.
+Dots represent individual Corrugator activity measures placed in 150 quantiles.}\label{fig:SupplFigCorrView}
+\end{figure}
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:SupplEffectLevView}Post-hoc contrasts for effects of valence on Levator activity in the active viewing conditions.}
+
+\footnotesize{
+
+\begin{tabular}{lllllllll}
+\toprule
+Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
+\midrule
+$View_{neutral} - View_{negative}$ & -0.23 & 0.08 & 117.00 & -2.98 & 0.00 & 188.72 & 0.07 & {}[0.01, 1.00]\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{figures/FigLevView} \caption{Levator activity in mV during the active viewing conditions, vizalized as boxplots.
+Dots represent individual Levator activity measures placed in 150 quantiles.}\label{fig:SupplFigLevView}
+\end{figure}
+
+\newpage
+
+\hypertarget{SupplementEffectER}{%
+\subsection{Post-hoc contrasts for effects of ER strategies on subjective arousal and physiological responding}\label{SupplementEffectER}}
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:SupplEffectArousalReg}Post-hoc contrasts for effects of ER strategies on subjective arousal ratings.}
 
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSubjArousal} \caption{Subjective arousal ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 qantiles.}\label{fig:SupplFigArousalReg}
+\includegraphics[width=\textwidth]{figures/FigSubjArousalReg} \caption{Subjective arousal ratings vizalized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:SupplFigArousalReg}
 \end{figure}
@@
 
-\caption{\label{tab:SupplEffectCorrReg}Post-hoc tests for effects of ER strategies on Corrugator activity}
+\caption{\label{tab:SupplEffectCorrReg}Post-hoc contrasts for effects of ER strategies on Corrugator activity}
 
@@
 \includegraphics[width=\textwidth]{figures/FigCorrReg} \caption{Corrugator activity in mV vizalized as boxplots.
-Dots represent individual Levatorr activity measures placed in 150 qantiles.}\label{fig:SupplFigCorrReg}
+Dots represent individual Levatorr activity measures placed in 150 quantiles.}\label{fig:SupplFigCorrReg}
 \end{figure}
@@
 
-\caption{\label{tab:SupplEffectLevReg}Post-hoc tests for effects of ER strategies on Levator activity}
+\caption{\label{tab:SupplEffectLevReg}Post-hoc contrasts for effects of ER strategies on Levator activity}
 
@@
 \includegraphics[width=\textwidth]{figures/FigLevReg} \caption{Levator activity in mV vizalized as boxplots.
-Dots represent individual Levator activity measures placed in 150 qantiles.}\label{fig:SupplFigLevReg}
+Dots represent individual Levator activity measures placed in 150 quantiles.}\label{fig:SupplFigLevReg}
 \end{figure}

### 2023-04-04 06_Paper/ER-ED/ERED_Stage2/Results.Rmd

@@
 
-### Manipulation checks
+### Manipulation checks <!-- es gibt keine weitere Überschrift auf dieser Ebene, würde ich jedoch erwarten.-->
 
@@
 ```
-
 Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
@@
 `r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found in Table XX in [supplementary material](#SupplementReasonChoice).
+A more detailed list of all reasons can be found in Table XX <!-- Nummer noch ergänzen --> in [supplementary material](#SupplementReasonChoice).
 

### 2023-04-05 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected figure caption

@@
 The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
-$N=120$".
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license., fig.pos="H"}
+$N=120$.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))

### 2023-04-05 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
knitted document
corrected BFs in abstract

@@
     role          :
-      - Conceptuatlization
+      - Conceptualization
       - Writing - review & editing
@@
  Afterwards, individual SVs were determined using the new CAD paradigm.
- SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $BF10=1.62*1021$).
+ SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $\mathrm{BF}_{\textrm{10}} = 1.62   \times 10^{21}$).
  Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<0.001$), subjective effort ($t(5, 618.96)=-13.98$,    $p<.001$, $f^2=0.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=0.155$).
@@
 The authors declare no competing interests.
-
+<!--
 ```{=tex}
@@
 ```
-
+-->
 # Design Table {#DesignTable}

### 2023-04-05 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

@@
 The authors made the following contributions.
-Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Visualization, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Methodology, Writing - review \& editing.
+Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Visualization, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptualization, Writing - review \& editing; Alexander Strobel: Conceptualization, Methodology, Writing - review \& editing.
 \textsuperscript{$\dagger{}$} Christoph Scheffel and Josephine Zerna contributed equally to this work.
@@
 Afterwards, individual SVs were determined using the new CAD paradigm.
-SVs significantly predicted later choice for an ER strategy (\(\chi^2(4, \textit{n} = 119)=115.40\), \(p<.001\), \(BF10=1.62*1021\)).
+SVs significantly predicted later choice for an ER strategy (\(\chi^2(4, \textit{n} = 119)=115.40\), \(p<.001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
 Further, SVs were associated with Corrugator activity (\(t(5, 618.96)=2.09\), \(p=.037\), \(f^2<0.001\)), subjective effort (\(t(5, 618.96)=-13.98\), \(p<.001\), \(f^2=0.035\)), and self-reported utility (\(t(5, 618.96)=29.49\), \(p<.001\), \(f^2=0.155\)).
@@
 \hypertarget{manipulation-checks}{%
-\subsubsection{Manipulation checks}\label{manipulation-checks}}
-
-\hypertarget{subjective-arousal-and-physiological-responding}{%
-\paragraph{Subjective arousal and physiological responding}\label{subjective-arousal-and-physiological-responding}}
-
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator} and \emph{Levator} activity.
-Descriptive values of each predictor for each condition can be found in table \ref{tab:TabDescr}.
-We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.73 \times 10^{48}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.03 \times 10^{18}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 258.85\)).
+\subsubsection{\texorpdfstring{Manipulation checks }{Manipulation checks }}\label{manipulation-checks}}
+
+\hypertarget{effect-of-valence-on-arousal-and-facial-emg}{%
+\paragraph{Effect of valence on arousal and facial EMG}\label{effect-of-valence-on-arousal-and-facial-emg}}
+
+To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, \emph{corrugator} and \emph{levator} activity.
+Descriptive values of each predictor for each condition can be found in Table \ref{tab:TabDescr}.
+We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.88 \times 10^{48} \pm 5.95\%\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.21 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 260.22\)).
 Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \ref{tab:SupplEffectArousalView} to @ref(tab:SupplEffectLevView and Figures \ref{fig:SupplFigArousalView} to \ref{fig:SupplFigLevView} in the {[}supplement{]}).
 
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator} and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 156.94\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.97 \times 10^{10}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.68 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
+\hypertarget{effect-of-emotion-regulation-on-arousal-and-facial-emg}{%
+\paragraph{Effect of emotion regulation on arousal and facial EMG}\label{effect-of-emotion-regulation-on-arousal-and-facial-emg}}
+
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
+We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 156.92\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.70 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
 For detailed information on post-hoc contrasts, please see Tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and Figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
@@
 
-\hypertarget{subjective-effort-of-er-strategies}{%
-\paragraph{Subjective effort of ER strategies}\label{subjective-effort-of-er-strategies}}
+\hypertarget{effect-of-emotion-regulation-of-effort}{%
+\paragraph{Effect of emotion regulation of effort}\label{effect-of-emotion-regulation-of-effort}}
 
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.74 \times 10^{53}\); see figure~\ref{fig:FigSubjEffort}).
+We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.76 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
 Post-hoc contrasts showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
@@
 \includegraphics[width=\textwidth]{figures/FigSubjEffort} \caption{Subjective effort ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:FigSubjEffort}
+Dots represent individual effort ratings placed in 150 quantiles.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSubjEffort}
 \end{figure}
 
-The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
-Here, 45.40\% stated that they chose the strategy that was easiest for them to implement.
+Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
+45.40\% of the participants stated that they chose the strategy that was easiest for them to implement.
 24.40\% stated they chose the strategy that was most effective and 11.80\% stated their chosen strategy was the easiest and most effective.
@@
 
-\hypertarget{subjective-values-of-er-strategies}{%
-\paragraph{Subjective values of ER strategies}\label{subjective-values-of-er-strategies}}
+\hypertarget{subjective-values-of-er-strategies-and-their-predictors}{%
+\subsubsection{Subjective values of ER strategies and their predictors}\label{subjective-values-of-er-strategies-and-their-predictors}}
 
@@
 SVs ranged between 0.005 and 1.00.
-In sum, \(n=\) 119 had one SV of 1.0, indicating a clear preference for one ER strategy.
+\(n=\) 119 had one SV of 1.0, indicating a clear preference for one ER strategy.
 Absolute preferences for ER strategies were relatively equally distributed.
@@
 The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor subject accounted for 19.10\% of total variance.
-The preregistered model showed a correlation of \(r=\) 0.95 of the random effects subjects and recoded strategy (\(BF10\) of the variable strategy: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
-Our model explained 0.90\% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
+The preregistered model showed a correlation of \(r=\) 0.95 between the random effects \emph{subjects} and \emph{recoded strategy} (\(BF10\) of the variable \emph{strategy}: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
+Our model explained 90.4\% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
 We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
@@
 
-The second model explained 0.41\% of variance.
-All results of the second model are in Table~\ref{tab:TabMLMH5}.
+The second model explained 41.5\% of variance.
+All results of the second model are in Table \ref{tab:TabMLMH5}.
 
@@
 \midrule
-Intercept & $8.03 \times 10^{-1}$ & 0.01 & 0.00 &  & 0.11\\
-Effort & $-6.85 \times 10^{-4}$ & 0.00 & 0.00 & 0.03 & \\
-Arousal & $-7.84 \times 10^{-5}$ & 0.00 & 0.32 & 0.00 & \\
-Utility & $1.42 \times 10^{-3}$ & 0.00 & 0.00 & 0.15 & \\
-Corrugator activity & $7.45 \times 10^{-3}$ & 0.00 & 0.04 & 0.00 & \\
-Levator activity & $5.32 \times 10^{-3}$ & 0.00 & 0.07 & 0.00 & \\
+Intercept & $8.03 \times 10^{-1}$ & 0.012 & <.001 &  & 0.114\\
+Effort & $-6.85 \times 10^{-4}$ & 0.000 & <.001 & 0.035 & \\
+Arousal & $-7.84 \times 10^{-5}$ & 0.000 & 0.317 & 0.000 & \\
+Utility & $1.42 \times 10^{-3}$ & 0.000 & <.001 & 0.155 & \\
+Corrugator activity & $7.45 \times 10^{-3}$ & 0.004 & 0.037 & 0.001 & \\
+Levator activity & $5.32 \times 10^{-3}$ & 0.003 & 0.070 & 0.001 & \\
 \bottomrule
@@
 
-The predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = 29.49\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
-The values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
+The predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,618.96) = 29.49\), \(p < .001\)), and \emph{corrugator} activity (\(\hat{\beta} = 0.007\), 95\% CI \([0.000, 0.014]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
+Beta values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
 The predictor utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5\% of variance in SVs.
@@
 
-To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
+To investigate the ecological validity of the calculated subjective values of ER strategies, we tested whether SVs were associated with the actual choice of participants in the last experimental block.
 Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 119) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see figure~\ref{fig:FigSVChoice}).
+There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 119) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see Figure \ref{fig:FigSVChoice}).
 
@@
 Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
-$N=120$}\label{fig:FigSVChoice}
+The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
+$N=120$.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSVChoice}
 \end{figure}
@@
 Overall model fit was fair with \(R^{2}=\) 0.27.
-The predictor SV of strategy distraction was found to contribute to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
-The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
-Additionally, the predictor SV of strategy suppression was found to contribute to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
-The estimated odds ration indicated that a participant is more likely to later choose suppression, when SV of strategy suppression is higher.
+The SV of the strategy distraction contributed significantly to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
+The estimated odds ratio indicated a higher chance of choosing strategy distraction, when the SV of that strategy is higher.
+Additionally, the predictor SV of the strategy suppression contributed significantly to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
+The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
 
@@
 
-We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
-The starting point for this was the model reported before.
+Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported\textsuperscript{29,34,69}, we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
+The starting point for this was the adapted MLM, we reported before.
 Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
-The third model followed the specification:
-\[
+The third model followed the specification: \[
 \begin{split}
@@
 \end{split}
-\]
-As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
-In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
+\] As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
+In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.024\), 95\% CI \([0.001, 0.048]\), \(t(97.97) = 2.04\), \(p = .044\)).
 However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
@@
 Further, we found associations between individual SVs and different predictors.
-Subjective effort, utility, and \emph{Corrugator} muscle activity significantly predicted individual SVs.
+Subjective effort, utility, and \emph{corrugator} muscle activity significantly predicted individual SVs.
 Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining 15.5 percent of variance in SVs.
@@
 Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
-Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy\textsuperscript{17,69,70}.
+Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy\textsuperscript{17,70,71}.
 Greater variability might even adaptive\textsuperscript{12,17}.
-In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined\textsuperscript{20--22,71--73}, including intensity of the situation and effort.
+In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined\textsuperscript{20--22,72--74}, including intensity of the situation and effort.
 However, these factors have often been studied separately.
-Only rarely have effects of the factors been studied in combination\textsuperscript{72}.
+Only rarely have effects of the factors been studied in combination\textsuperscript{73}.
 Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) can only estimate how a factor tends to drive the choice in one direction or the other.
@@
 The highest SVs of the individuals were associated with the choice made by the participants.
-Until now, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{71}.
+Until now, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{72}.
 This may be due to the fact that in laboratory studies, the choice options are often predetermined by the design of the experiment\textsuperscript{20--22}.
 It was therefore attempted to investigate ER choice and influencing factors in everyday life.
-However, even there, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{74}, Millgram et al.\textsuperscript{75}, Wilms et al.\textsuperscript{71}).
+However, even there, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{75}, Millgram et al.\textsuperscript{76}, Wilms et al.\textsuperscript{72}).
 Although these covered a large area of the emotion-genesis process\textsuperscript{2}, they were nevertheless ultimately fixed.
 Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
-However, it would be possible to use ecological momentary assessment to capture ER strategies\textsuperscript{76}.
+However, it would be possible to use ecological momentary assessment to capture ER strategies\textsuperscript{77}.
 This would allow all strategies of the ER repertoire to be recorded for each individual\textsuperscript{12}.
-Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination\textsuperscript{77}.
+Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination\textsuperscript{78}.
 
@@
 If it is determined that the regulation goal is not being achieved, the ER strategy can be maintained, stopped or switched\textsuperscript{33}.
-Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context\textsuperscript{33,78--80}.
-This means that for studies on ER Choice, not only situational factors should be taken into account, but also contextual factors\textsuperscript{79}.
-For example, Murphy and Young\textsuperscript{79} could show that in a classic ER choice paradigm\textsuperscript{21}, strategy selection was significantly influenced by strategy selection and negative affect of the preceding trial.
+Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context\textsuperscript{33,79--81}.
+This means that for studies on ER Choice, not only situational factors should be taken into account, but also contextual factors\textsuperscript{80}.
+For example, Murphy and Young\textsuperscript{80} could show that in a classic ER choice paradigm\textsuperscript{21}, strategy selection was significantly influenced by strategy selection and negative affect of the preceding trial.
 This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
@@
 It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
-In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals\textsuperscript{82}.
-Wilms and colleagues\textsuperscript{71} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
+In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals\textsuperscript{83}.
+Wilms and colleagues\textsuperscript{72} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
 In another situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, another strategy might appear more helpful and thus have a higher SV.
@@
 This allows for habituation effects of EMG activity within the block.
-However, block designs are common in ER research\textsuperscript{83} and were used in previous studies\textsuperscript{84}.
+However, block designs are common in ER research\textsuperscript{84} and were used in previous studies\textsuperscript{85}.
 Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
-It is also known that affect labeling might attenuate emotional experience\textsuperscript{85,86}.
+It is also known that affect labeling might attenuate emotional experience\textsuperscript{86,87}.
 That is why we decided not to have the ratings done after every image.
@@
 However, we chose this amount because, first, we have followed the original paradigm of Westbrook\textsuperscript{29}.
-Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{87}.
+Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{88}.
 In the future, however, it should be examined how the level of incentives affects subjective values.
@@
 In order to cope with changing emotional demands, individuals can flexibly select and apply strategies from their repertoire\textsuperscript{12,13}.
-The strategy that is most suitable for dealing with contextual demands and achieving regulatory goals is selected\textsuperscript{12,82}.
+The strategy that is most suitable for dealing with contextual demands and achieving regulatory goals is selected\textsuperscript{12,83}.
 The combination of influencing factors should be reflected in subjective values, which are formed for all alternatives and serve as a basis for decision-making.
@@
 \& Strobel, A.
-When easy is not preferred: An effort discounting for estimating subjective values of taks.
+When easy is not preferred: A discounting paradigm to assess load-independent task preference.
 \emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kool2013}{}}%
+\CSLLeftMargin{69. }%
+\CSLRightInline{Kool, W., McGuire, J.
+T., Wang, G.
+J.
+\& Botvinick, M.
+M.
+\href{https://doi.org/10.1371/journal.pone.0072626}{Neural and behavioral evidence for an intrinsic cost of self-control}.
+\emph{Plos One} \textbf{8}, (2013).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Burr2020}{}}%
-\CSLLeftMargin{69. }%
+\CSLLeftMargin{70. }%
 \CSLRightInline{Burr, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Elkjaer2022}{}}%
-\CSLLeftMargin{70. }%
+\CSLLeftMargin{71. }%
 \CSLRightInline{Elkjaer, E., Mikkelsen, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wilms2020}{}}%
-\CSLLeftMargin{71. }%
+\CSLLeftMargin{72. }%
 \CSLRightInline{Wilms, R., Lanwehr, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Young2020}{}}%
-\CSLLeftMargin{72. }%
+\CSLLeftMargin{73. }%
 \CSLRightInline{Young, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Matthews2021}{}}%
-\CSLLeftMargin{73. }%
+\CSLLeftMargin{74. }%
 \CSLRightInline{Matthews, M., Webb, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-English2017}{}}%
-\CSLLeftMargin{74. }%
+\CSLLeftMargin{75. }%
 \CSLRightInline{English, T., Lee, I.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Millgram2019}{}}%
-\CSLLeftMargin{75. }%
+\CSLLeftMargin{76. }%
 \CSLRightInline{Millgram, Y., Sheppes, G., Kalokerinos, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Koval2020}{}}%
-\CSLLeftMargin{76. }%
+\CSLLeftMargin{77. }%
 \CSLRightInline{Koval, P., Kalokerinos, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Pena-Sarrionandia2015}{}}%
-\CSLLeftMargin{77. }%
+\CSLLeftMargin{78. }%
 \CSLRightInline{Pena-Sarrionandia, A., Mikolajczak, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-AldaoChristensen2015}{}}%
-\CSLLeftMargin{78. }%
+\CSLLeftMargin{79. }%
 \CSLRightInline{Aldao, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Murphy2018}{}}%
-\CSLLeftMargin{79. }%
+\CSLLeftMargin{80. }%
 \CSLRightInline{Murphy, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sheppes2020}{}}%
-\CSLLeftMargin{80. }%
+\CSLLeftMargin{81. }%
 \CSLRightInline{Sheppes, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Haines2016}{}}%
-\CSLLeftMargin{81. }%
+\CSLLeftMargin{82. }%
 \CSLRightInline{Haines, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Tamir2016}{}}%
-\CSLLeftMargin{82. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{Tamir, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Barreiros2019}{}}%
-\CSLLeftMargin{83. }%
+\CSLLeftMargin{84. }%
 \CSLRightInline{Barreiros, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Scheffel2019}{}}%
-\CSLLeftMargin{84. }%
+\CSLLeftMargin{85. }%
 \CSLRightInline{Scheffel, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lieberman2007}{}}%
-\CSLLeftMargin{85. }%
+\CSLLeftMargin{86. }%
 \CSLRightInline{Lieberman, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Torre2018}{}}%
-\CSLLeftMargin{86. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{Torre, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{87. }%
+\CSLLeftMargin{88. }%
 \CSLRightInline{Bialaszek, W., Marcowski, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{88. }%
+\CSLLeftMargin{89. }%
 \CSLRightInline{Preece, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{89. }%
+\CSLLeftMargin{90. }%
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{90. }%
+\CSLLeftMargin{91. }%
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 \emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{88}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{89}.
 
@@
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,89} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{90}.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,90} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{91}.
 
@@
 \midrule
-Corrgator View Neu & 0.04 & 6.99 & 0.05 & 0.00\\
-Corrgator View Neg & 1.03 & 7.21 & 0.19 & 0.00\\
-Corrgator Distraction & 0.00 & 7.67 & 0.04 & 0.00\\
-Corrgator Distancing & 0.07 & 3.78 & 0.08 & 0.00\\
-Corrgator Suppression & 0.25 & 1.92 & 0.35 & 0.00\\
+Corrugator View Neu & 0.04 & 6.99 & 0.05 & 0.00\\
+Corrugator View Neg & 1.03 & 7.21 & 0.19 & 0.00\\
+Corrugator Distraction & 0.00 & 7.67 & 0.04 & 0.00\\
+Corrugator Distancing & 0.07 & 3.78 & 0.08 & 0.00\\
+Corrugator Suppression & 0.25 & 1.92 & 0.35 & 0.00\\
 Levator View Neu & 0.09 & 1.84 & 0.38 & 0.00\\

### 2023-04-05 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
Changes in summary of results

@@
 
-The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
-We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al. [-@Westbrook2013] in a way that allows to determine SVs for tasks that have no objective order of difficulty levels. 
-The new paradigm was tested on an *n*-back task [@ZernaScheffel2022] and a classic ER paradigm.
+The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
+We adapted et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
+The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
 The latter was completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
-As expected, use of ER strategies was associated with decreased subjective and physiological arousal.
-This finding is in line with previous meta-analytic findings, indicating the effectiveness of ER strategies, both on subjective as well as physiological levels [@Webb2012;@Zaehringer2020].
-Further, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
-This allows us to replicate previous findings from our research group and show that the use of strategies is associated with cognitive effort [@Scheffel2021].
-Both measures also showed great variability between individuals.
-Taken together, this means that the ER strategies had an effect on the participants as intended: Individuals were able to reduce subjective and physiological responding effectively at the expense of cognitive effort.
-We assume that there was a good basis on which individual SVs of ER strategies could be determined.
-All in all, evidence was in favour of hypotheses H1 to H5.
+As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
+This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020].
+<!-- evtl.
+Einwand warum Suppression am erfolgreichsten war -->
+Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
+This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort [@Scheffel2021].
+Both measures also showed high variability between individuals.
+Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
+We believe that there was a good basis on which individual SVs of ER strategies could be determined.
+Overall, there was evidence to support hypotheses H1 to H5.
 
-Almost all participants showed an absolute preference for one strategy, indicated by an SV of 1. 
-We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals prefer strategies to different extents.
-There was a significant relationship between SVs and choice of strategy. 
-Overly frequent the strategy would be chosen by the persons for whom the highest subjective value had been determined before, which speaks in favour of hypothesis H7.
+Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1. 
+We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals have varying degrees of strategy preference.
+There was a significant relationship between SVs and strategy choice. 
+Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
 Further, we found associations between individual SVs and different predictors.
-Subjective effort, utility, and *Corrugator* muscle activity significantly predicted individual SVs.
+Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
 Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
updated results summary

@@
 Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
-Further, we found associations between individual SVs and different predictors.
+We also found associations between individual SVs and various predictors.
 Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
 Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.
-However, individual SVs did not show associations with ER flexibility, we therefore found no evidence for hypothesis H7.
+However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
 

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
rephrasing

@@
 
-Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
-Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022]. 
-Greater variability might even adaptive [@Blanke2020;@Aldao2015].
-In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020;@Matthews2021], including intensity of the situation and effort.
+Our aim was to calculate individual subjective values in order to develop a better understanding of ER strategy selection.
+Most individuals show large variability in strategy choice, both within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022]. 
+Greater variability may even be adaptive[@Blanke2020;@Aldao2015].
+In addition, a variety of factors that influence strategy choice in specific situations have been examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020;@Matthews2021], including situation intensity and effort.
 However, these factors have often been studied separately.

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
incorporated changes of DD in second paragraph

@@
 In addition, a variety of factors that influence strategy choice in specific situations have been examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020;@Matthews2021], including situation intensity and effort.
-However, these factors have often been studied separately.
-Only rarely have effects of the factors been studied in combination[@Young2020].
-Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
-However, it cannot be determined in this way what internal subjective value individuals attribute to the choice options.
-We are confident that we have succeeded in this with the present paradigm.
-On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
-The highest SVs of the individuals were associated with the choice made by the participants. 
-Until now, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020].
-This may be due to the fact that in laboratory studies, the choice options are often predetermined by the design of the experiment [@Sheppes2011;@Sheppes2014;@Scheffel2021].
-It was therefore attempted to investigate ER choice and influencing factors in everyday life.
-However, even there, certain strategies were often prescribed (for example studies, see English et al.[@English2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]). 
-Although these covered a large area of the emotion-genesis process[@Gross1998emerging], they were nevertheless ultimately fixed.
-Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
-However, it would be possible to use ecological momentary assessment to capture ER strategies[@Koval2020].
-This would allow all strategies of the ER repertoire to be recorded for each individual[@Aldao2015]. 
-Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination[@Pena-Sarrionandia2015].
+However, these factors have often been studied in isolation from each other.
+Rarely have their combined effects been investigated[@Young2020].
+Furthermore, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
+They cannot determine the internal subjective value individuals attribute to the choice options.
+We are confident that we have achieved this with the present paradigm.
+On the one hand, we were able to show which factors have an influence the values, and on the other hand, we were able to show the actual practical relevance of the values.
+The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block. 
+So far, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020].
+This may be because in laboratory studies the choice options are often predetermined by the experimental design[@Sheppes2011;@Sheppes2014;@Scheffel2021].
+Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life, in previous studies.
+Even there, however, certain strategies were often prescribed (for example studies, see English et al.[@English2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].
+Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
+To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment[@Aldao2015;@Koval2020].
+This would also capture strategies that are rarely used or even considered maladaptive, such as alcohol consumption or rumination[@Pena-Sarrionandia2015].
 
-In order to draw a more comprehensive picture on ER, dynamic or cyclic processes have to be considered.
+In order to gain a more comprehensive picture of ER, dynamic or cyclic processes have to be considered.
 The extended process model of emotion regulation[@Gross2015] postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
-If it is determined that the regulation goal is not being achieved, the ER strategy can be maintained, stopped or switched[@Gross2015].
-Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context[@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
-This means that for studies on ER Choice, not only situational factors should be taken into account, but also contextual factors[@Murphy2018].
-For example, Murphy and Young[@Murphy2018] could show that in a classic ER choice paradigm[@Sheppes2011], strategy selection was significantly influenced by strategy selection and negative affect of the preceding trial.
+If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped[@Gross2015].
+Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback [@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
+This means that studies on ER Choice should consider not only situational factors, but also contextual factors[@Murphy2018].
+For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect on the previous trial.
 This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
 Our newly developed paradigm also makes an important contribution here.
-The information and experiences that participants gather when using strategies subsequently flow implicitly into the calculation of subjective values.
-That is, because the participants first go through all the strategies and then make the monetary decisions on the basis that they should repeat the strategies again. 
-The decisions are made on the basis of the stimulus material that the individuals previously viewed. 
-Therefore, the question arises as to how stable these individual SVs are.
+The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of subjective values.
+That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.
+This raises the question of how stable these individual SVs are.
 

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
changes of DD on trait character

@@
 Rarely have their combined effects been investigated[@Young2020].
-Furthermore, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
+Furthermore, the usual paradigms used in ER choice research (e.g., Sheppes et al.[-@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
 They cannot determine the internal subjective value individuals attribute to the choice options.
@@
 Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life, in previous studies.
-Even there, however, certain strategies were often prescribed (for example studies, see English et al.[@English2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].
+Even there, however, certain strategies were often prescribed (for example studies, see English et al.[-@English2017], Millgram et al.[-@Millgram2019], Wilms et al.[-@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].
 Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
@@
 This means that studies on ER Choice should consider not only situational factors, but also contextual factors[@Murphy2018].
-For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect on the previous trial.
+For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect on the previous trial.
 This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
@@
 
-In order to further assess the relevance of the calculated individual SVs, it would be important to know how stable the values are, i.e. whether they would show trait character.
-In other words, do the values we calculate represent a stable value within the individual?
+Knowing, whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
+However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
 This conclusion cannot be drawn from the present study alone.
-The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
+The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
 By definition, this represents a state.
-As previously noted, personal regulation goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
-We belief that these goals, factors and demands also influence individual SVs of ER strategies.
+As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
+We belief that these goals, factors, and demands also influence individual SVs of ER strategies.
 Our data presented in this study support this idea.
-However, this also means that SVs should differ according to situational factors (e.g., intensity of stimuli).
-It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
-In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals[@Tamir2016].
-Wilms and colleagues[@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
-In another situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, another strategy might appear more helpful and thus have a higher SV.
-It should also be noted that the computation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
-Therefore, SVs could vary if other reference strategies are used.
-It is conceivable that the subjective values are likely to correlate very highly in situations with similar demands and goals. 
-They would thus reflect habits, or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
-The other way round, of course, it is also conceivable that such habits influence the internal formation of these subjective values.
+However, this also implies that SVs should differ according to situational factors (e.g., stimulus intensity).
+The ER goals that individuals pursue in a given situation must also be taken into account.
+In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals[@Tamir2016].
+Wilms and colleagues[-@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
+In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
+It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
+Therefore, SVs may vary when different reference strategies are used.
+It is conceivable that subjective values are likely to be highly correlated in situations with similar demands and goals. 
+They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
+Of course, it is also possible that such habits influence the internal formation of these subjective values.
 However, our data are not suitable for answering this question.
-In future, the SVs should therefore be collected in several similar situations. 
+In the future, SVs should therefore be collected in several similar situations. 
 Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
changes of DD on limitations and conclusion

@@
 This conclusion cannot be drawn from the present study alone.
+To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020]
 The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
@@
 
-Our findings must be considered in light of several limitations.
-First, it must be mentioned that a block design was used.
+A number of limitations must be taken into account when considering our findings. 
+First, it should be noted that a block design was used.
 This allows for habituation effects of EMG activity within the block.
-However, block designs are common in ER research [@Barreiros2019] and were used in previous studies [@Scheffel2019]. 
-Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
-It is also known that affect labeling might attenuate emotional experience [@Lieberman2007;@Torre2018]. 
-That is why we decided not to have the ratings done after every image.
-Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.
-Taken together, these two facts may have led to slightly lower associations between SVs and predictors.
+However, block designs are common in ER research [@Barreiros2019] and have been used in previous studies [@Scheffel2019]. 
+Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block.
+It is also known that affect labeling can attenuate emotional experience [@Lieberman2007;@Torre2018]. 
+Therefore, we decided not to conduct ratings after each image.
+Furthermore, we were able to confirm that the implementation of ER strategies was successful at both subjective and physiological levels.
+Still, these features of our research design may have led to slightly lower associations between SVs and predictors.
 
-Third, it is a major limitation that participants had to use three given ER strategies.
-It could be that some of the participants did not implement or were used to any of the three strategies in everyday life.
-So it may be that none of the strategies has a really high subjective value for the person.
-However, strategies for attentional deployment, cognitive change, and response modulation were chosen that meta-analytically proved to be most effective [@Webb2012]. 
-Related to that, individual SVs of each person have to be interpreted with caution. 
-They depend on the specific context: The stimulus material presented and the strategies that are compared with each other.
-Thus, it could be that SVs for one ER strategy would be higher or lower when using other stimuli or valences of stimuli and other comparison strategies.
-That is because the computation of SVs is inseparable form the other SVs.
+Third, a major limitation is that participants had to use three prescribed ER strategies.
+It may be that some of the participants were not used to any of these strategies in everyday life.
+So it could be that none of the strategies has a really high subjective value for the person.
+However, the strategies selected for attentional deployment, cognitive change, and response modulation have been shown meta-analytically to be most effective[@Webb2012]. 
+In this context, the individual SVs of each person must be interpreted with caution. 
+They depend on the specific context: The stimuli presented and the strategies compared.
+For example, SVs for an ER strategy might be higher or lower when different stimuli or stimulus valences and different comparison strategies are used, because the calculation of SVs is inseparable form the other SVs.
 
 Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
-Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
-Thus, 2 € as an incentive to repeat an entire regulation block could be quite low.
-However, we chose this amount because, first, we have followed the original paradigm of Westbrook[@Westbrook2013].
-Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort[@Bialaszek2017].
-In the future, however, it should be examined how the level of incentives affects subjective values.
+Participants were asked to imagine that this was the amount of money they would receive if they repeated this strategy.
+Thus, 2 € could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
+However, we chose this amount because, firstly, we have followed the original paradigm of Westbrook[@Westbrook2013].
+Secondly, it has been shown that, at least in the case of cognitive effort discounting, a lower incentive might even increase participants' sensitivity to effort differences[@Bialaszek2017].
+In the future, however, it should be investigated how the level of incentives affects subjective values.
 
@@
 
-In order to cope with changing emotional demands, individuals can flexibly select and apply strategies from their repertoire[@Bonanno2013;@Aldao2015].
-The strategy that is most suitable for dealing with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
-The combination of influencing factors should be reflected in subjective values, which are formed for all alternatives and serve as a basis for decision-making.
-So far, such subjective values for ER strategies have not been determined.
+In order to cope with changing emotional demands, individuals my flexibly select and apply strategies from their repertoire[@Bonanno2013;@Aldao2015].
+The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
+The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
+To date, such subjective values hace not been established for ER strategies.
 Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values. 
-This provides a more detailed investigation of factors influencing the internal generation of these SVs of ER strategies.
-It seems that it is primarily the perceived usefulness and the effort expended that determine the subjective value attributed to a strategy.
-Finally, further research is needed to investigate the factors influencing subjective values and whether these values represent habitual use of ER strategies by individuals.
+This allows to investigate in more detail the factors influencing the internal generation of these SVs of ER strategies.
+It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and the effort.
+Finally, further research is needed to investigate the factors that influence subjective values and whether these values represent habitual use of ER strategies by individuals.

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

@@
 
-The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
-We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al.\textsuperscript{29} in a way that allows to determine SVs for tasks that have no objective order of difficulty levels.
+The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
+We adapted et al.'s\textsuperscript{29} Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order.
 The new paradigm was tested on an \emph{n}-back task\textsuperscript{34} and a classic ER paradigm.
 The latter was completed by \(N=120\) participants.
-As expected, use of ER strategies was associated with decreased subjective and physiological arousal.
-This finding is in line with previous meta-analytic findings, indicating the effectiveness of ER strategies, both on subjective as well as physiological levels\textsuperscript{4,5}.
-Further, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing.
-This allows us to replicate previous findings from our research group and show that the use of strategies is associated with cognitive effort\textsuperscript{22}.
-Both measures also showed great variability between individuals.
-Taken together, this means that the ER strategies had an effect on the participants as intended: Individuals were able to reduce subjective and physiological responding effectively at the expense of cognitive effort.
-We assume that there was a good basis on which individual SVs of ER strategies could be determined.
-All in all, evidence was in favour of hypotheses H1 to H5.
-
-Almost all participants showed an absolute preference for one strategy, indicated by an SV of 1.
-We also found a wide range of SVs (between 0.005 and 1.00), suggesting that individuals prefer strategies to different extents.
-There was a significant relationship between SVs and choice of strategy.
-Overly frequent the strategy would be chosen by the persons for whom the highest subjective value had been determined before, which speaks in favour of hypothesis H7.
-Further, we found associations between individual SVs and different predictors.
+As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
+This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels\textsuperscript{4,5}.
+Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing.
+This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort\textsuperscript{22}.
+Both measures also showed high variability between individuals.
+Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
+We believe that there was a good basis on which individual SVs of ER strategies could be determined.
+Overall, there was evidence to support hypotheses H1 to H5.
+
+Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1.
+We also found a wide range of SVs (between 0.005 and 1.00), suggesting that individuals have varying degrees of strategy preference.
+There was a significant relationship between SVs and strategy choice.
+Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
+We also found associations between individual SVs and various predictors.
 Subjective effort, utility, and \emph{corrugator} muscle activity significantly predicted individual SVs.
 Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining 15.5 percent of variance in SVs.
-However, individual SVs did not show associations with ER flexibility, we therefore found no evidence for hypothesis H7.
+However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
 
@@
 
-Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
-Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy\textsuperscript{17,70,71}.
-Greater variability might even adaptive\textsuperscript{12,17}.
-In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined\textsuperscript{20--22,72--74}, including intensity of the situation and effort.
-However, these factors have often been studied separately.
-Only rarely have effects of the factors been studied in combination\textsuperscript{73}.
-Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) can only estimate how a factor tends to drive the choice in one direction or the other.
-However, it cannot be determined in this way what internal subjective value individuals attribute to the choice options.
-We are confident that we have succeeded in this with the present paradigm.
-On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
-The highest SVs of the individuals were associated with the choice made by the participants.
-Until now, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{72}.
-This may be due to the fact that in laboratory studies, the choice options are often predetermined by the design of the experiment\textsuperscript{20--22}.
-It was therefore attempted to investigate ER choice and influencing factors in everyday life.
-However, even there, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{75}, Millgram et al.\textsuperscript{76}, Wilms et al.\textsuperscript{72}).
-Although these covered a large area of the emotion-genesis process\textsuperscript{2}, they were nevertheless ultimately fixed.
-Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
-However, it would be possible to use ecological momentary assessment to capture ER strategies\textsuperscript{77}.
-This would allow all strategies of the ER repertoire to be recorded for each individual\textsuperscript{12}.
-Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination\textsuperscript{78}.
-
-In order to draw a more comprehensive picture on ER, dynamic or cyclic processes have to be considered.
+Our aim was to calculate individual subjective values in order to develop a better understanding of ER strategy selection.
+Most individuals show large variability in strategy choice, both within-strategy and between-strategy\textsuperscript{17,70,71}.
+Greater variability may even be adaptive\textsuperscript{12,17}.
+In addition, a variety of factors that influence strategy choice in specific situations have been examined\textsuperscript{20--22,72--74}, including situation intensity and effort.
+However, these factors have often been studied in isolation from each other.
+Rarely have their combined effects been investigated\textsuperscript{73}.
+Furthermore, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) can only estimate how a factor tends to drive the choice in one direction or the other.
+They cannot determine the internal subjective value individuals attribute to the choice options.
+We are confident that we have achieved this with the present paradigm.
+On the one hand, we were able to show which factors have an influence the values, and on the other hand, we were able to show the actual practical relevance of the values.
+The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block.
+So far, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{72}.
+This may be because in laboratory studies the choice options are often predetermined by the experimental design\textsuperscript{20--22}.
+Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life, in previous studies.
+Even there, however, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{75}, Millgram et al.\textsuperscript{76}, Wilms et al.\textsuperscript{72}), although covering a large part of the process of emotion generation\textsuperscript{2}.
+Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
+To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment\textsuperscript{12,77}.
+This would also capture strategies that are rarely used or even considered maladaptive, such as alcohol consumption or rumination\textsuperscript{78}.
+
+In order to gain a more comprehensive picture of ER, dynamic or cyclic processes have to be considered.
 The extended process model of emotion regulation\textsuperscript{33} postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
-If it is determined that the regulation goal is not being achieved, the ER strategy can be maintained, stopped or switched\textsuperscript{33}.
-Importantly, information about the effects of implementing ER strategies influences the choice of ER strategies in future situations, due to contextual feedback even changes the context\textsuperscript{33,79--81}.
-This means that for studies on ER Choice, not only situational factors should be taken into account, but also contextual factors\textsuperscript{80}.
-For example, Murphy and Young\textsuperscript{80} could show that in a classic ER choice paradigm\textsuperscript{21}, strategy selection was significantly influenced by strategy selection and negative affect of the preceding trial.
+If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped\textsuperscript{33}.
+Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback\textsuperscript{33,79--81}.
+This means that studies on ER Choice should consider not only situational factors, but also contextual factors\textsuperscript{80}.
+For example, in a classic ER choice paradigm\textsuperscript{21}, Murphy and Young\textsuperscript{80} showed that strategy choice was significantly influenced by strategy choice and negative affect on the previous trial.
 This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
 Our newly developed paradigm also makes an important contribution here.
-The information and experiences that participants gather when using strategies subsequently flow implicitly into the calculation of subjective values.
-That is, because the participants first go through all the strategies and then make the monetary decisions on the basis that they should repeat the strategies again.
-The decisions are made on the basis of the stimulus material that the individuals previously viewed.
-Therefore, the question arises as to how stable these individual SVs are.
+The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of subjective values.
+That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.
+This raises the question of how stable these individual SVs are.
 
@@
 
-In order to further assess the relevance of the calculated individual SVs, it would be important to know how stable the values are, i.e.~whether they would show trait character.
-In other words, do the values we calculate represent a stable value within the individual?
+Knowing, whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
+However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
 This conclusion cannot be drawn from the present study alone.
-The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
+To establish the \emph{trait} nature of a measure, one could for instance resort to latent state trait modeling\textsuperscript{82}, as recently employed by our group in a related context\textsuperscript{30}
+The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation.
 By definition, this represents a state.
-As previously noted, personal regulation goals, situational factors, and contextual demands influence the choice for or against ER strategies\textsuperscript{21}.
-We belief that these goals, factors and demands also influence individual SVs of ER strategies.
+As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies\textsuperscript{21}.
+We belief that these goals, factors, and demands also influence individual SVs of ER strategies.
 Our data presented in this study support this idea.
-However, this also means that SVs should differ according to situational factors (e.g., intensity of stimuli).
-It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
-In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals\textsuperscript{83}.
-Wilms and colleagues\textsuperscript{72} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
-In another situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, another strategy might appear more helpful and thus have a higher SV.
-It should also be noted that the computation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also \protect\hyperlink{Limitations}{Limitations}).
-Therefore, SVs could vary if other reference strategies are used.
-It is conceivable that the subjective values are likely to correlate very highly in situations with similar demands and goals.
-They would thus reflect habits, or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires\textsuperscript{9}.
-The other way round, of course, it is also conceivable that such habits influence the internal formation of these subjective values.
+However, this also implies that SVs should differ according to situational factors (e.g., stimulus intensity).
+The ER goals that individuals pursue in a given situation must also be taken into account.
+In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals\textsuperscript{84}.
+Wilms and colleagues\textsuperscript{72} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
+In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
+It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also \protect\hyperlink{Limitations}{Limitations}).
+Therefore, SVs may vary when different reference strategies are used.
+It is conceivable that subjective values are likely to be highly correlated in situations with similar demands and goals.
+They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires\textsuperscript{9}.
+Of course, it is also possible that such habits influence the internal formation of these subjective values.
 However, our data are not suitable for answering this question.
-In future, the SVs should therefore be collected in several similar situations.
+In the future, SVs should therefore be collected in several similar situations.
 Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being\textsuperscript{9}.
@@
 
-Our findings must be considered in light of several limitations.
-First, it must be mentioned that a block design was used.
+A number of limitations must be taken into account when considering our findings.
+First, it should be noted that a block design was used.
 This allows for habituation effects of EMG activity within the block.
-However, block designs are common in ER research\textsuperscript{84} and were used in previous studies\textsuperscript{85}.
-Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
-It is also known that affect labeling might attenuate emotional experience\textsuperscript{86,87}.
-That is why we decided not to have the ratings done after every image.
-Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.
-Taken together, these two facts may have led to slightly lower associations between SVs and predictors.
-
-Third, it is a major limitation that participants had to use three given ER strategies.
-It could be that some of the participants did not implement or were used to any of the three strategies in everyday life.
-So it may be that none of the strategies has a really high subjective value for the person.
-However, strategies for attentional deployment, cognitive change, and response modulation were chosen that meta-analytically proved to be most effective\textsuperscript{4}.
-Related to that, individual SVs of each person have to be interpreted with caution.
-They depend on the specific context: The stimulus material presented and the strategies that are compared with each other.
-Thus, it could be that SVs for one ER strategy would be higher or lower when using other stimuli or valences of stimuli and other comparison strategies.
-That is because the computation of SVs is inseparable form the other SVs.
+However, block designs are common in ER research\textsuperscript{85} and have been used in previous studies\textsuperscript{86}.
+Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block.
+It is also known that affect labeling can attenuate emotional experience\textsuperscript{87,88}.
+Therefore, we decided not to conduct ratings after each image.
+Furthermore, we were able to confirm that the implementation of ER strategies was successful at both subjective and physiological levels.
+Still, these features of our research design may have led to slightly lower associations between SVs and predictors.
+
+Third, a major limitation is that participants had to use three prescribed ER strategies.
+It may be that some of the participants were not used to any of these strategies in everyday life.
+So it could be that none of the strategies has a really high subjective value for the person.
+However, the strategies selected for attentional deployment, cognitive change, and response modulation have been shown meta-analytically to be most effective\textsuperscript{4}.
+In this context, the individual SVs of each person must be interpreted with caution.
+They depend on the specific context: The stimuli presented and the strategies compared.
+For example, SVs for an ER strategy might be higher or lower when different stimuli or stimulus valences and different comparison strategies are used, because the calculation of SVs is inseparable form the other SVs.
 
 Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
-Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
-Thus, 2 € as an incentive to repeat an entire regulation block could be quite low.
-However, we chose this amount because, first, we have followed the original paradigm of Westbrook\textsuperscript{29}.
-Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{88}.
-In the future, however, it should be examined how the level of incentives affects subjective values.
+Participants were asked to imagine that this was the amount of money they would receive if they repeated this strategy.
+Thus, 2 € could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
+However, we chose this amount because, firstly, we have followed the original paradigm of Westbrook\textsuperscript{29}.
+Secondly, it has been shown that, at least in the case of cognitive effort discounting, a lower incentive might even increase participants' sensitivity to effort differences\textsuperscript{89}.
+In the future, however, it should be investigated how the level of incentives affects subjective values.
 
@@
 
-In order to cope with changing emotional demands, individuals can flexibly select and apply strategies from their repertoire\textsuperscript{12,13}.
-The strategy that is most suitable for dealing with contextual demands and achieving regulatory goals is selected\textsuperscript{12,83}.
-The combination of influencing factors should be reflected in subjective values, which are formed for all alternatives and serve as a basis for decision-making.
-So far, such subjective values for ER strategies have not been determined.
+In order to cope with changing emotional demands, individuals my flexibly select and apply strategies from their repertoire\textsuperscript{12,13}.
+The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected\textsuperscript{12,84}.
+The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
+To date, such subjective values hace not been established for ER strategies.
 Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values.
-This provides a more detailed investigation of factors influencing the internal generation of these SVs of ER strategies.
-It seems that it is primarily the perceived usefulness and the effort expended that determine the subjective value attributed to a strategy.
-Finally, further research is needed to investigate the factors influencing subjective values and whether these values represent habitual use of ER strategies by individuals.
+This allows to investigate in more detail the factors influencing the internal generation of these SVs of ER strategies.
+It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and the effort.
+Finally, further research is needed to investigate the factors that influence subjective values and whether these values represent habitual use of ER strategies by individuals.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Steyer2015}{}}%
+\CSLLeftMargin{82. }%
+\CSLRightInline{Steyer, R., Mayer, A., Geiser, C.
+\& Cole, D.
+A.
+\href{https://doi.org/10.1146/annurev-clinpsy-032813-153719}{A theory of states and traits-revised}.
+\emph{Annual Review of Clinical Psychology} \textbf{11}, 71--+ (2015).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Haines2016}{}}%
-\CSLLeftMargin{82. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{Haines, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Tamir2016}{}}%
-\CSLLeftMargin{83. }%
+\CSLLeftMargin{84. }%
 \CSLRightInline{Tamir, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Barreiros2019}{}}%
-\CSLLeftMargin{84. }%
+\CSLLeftMargin{85. }%
 \CSLRightInline{Barreiros, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Scheffel2019}{}}%
-\CSLLeftMargin{85. }%
+\CSLLeftMargin{86. }%
 \CSLRightInline{Scheffel, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lieberman2007}{}}%
-\CSLLeftMargin{86. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{Lieberman, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Torre2018}{}}%
-\CSLLeftMargin{87. }%
+\CSLLeftMargin{88. }%
 \CSLRightInline{Torre, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{88. }%
+\CSLLeftMargin{89. }%
 \CSLRightInline{Bialaszek, W., Marcowski, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{89. }%
+\CSLLeftMargin{90. }%
 \CSLRightInline{Preece, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{90. }%
+\CSLLeftMargin{91. }%
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{91. }%
+\CSLLeftMargin{92. }%
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 \emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{89}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{90}.
 
@@
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,90} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{91}.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,91} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{92}.
 

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
short discussion on suppression

@@
 
-The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
-We adapted et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
+The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
+We adapted Westbrook et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
 The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
-The latter was completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
+The latter was goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
 As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
@@
 Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
-This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort [@Scheffel2021].
+This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
 Both measures also showed high variability between individuals.
@@
 Overall, there was evidence to support hypotheses H1 to H5.
+It was nevertheless surprising that the strategy suppression showed on average the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
+In the case of the EEG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly.
+This also indicates why the required effort is the lowest. 
+The direct instruction to implement the strategy reduces the complexity of the generation process.
+By comparison, distancing increases the complexity, for example, because it requires a distanced reappraisal of the stimulus.
+Ultimately, these two aspects are expressed in terms of greater utility: The implementation of the instructions requires comparatively less effort. 
+In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
+In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess the utility of the strategies.
 
@@
 Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` percent of variance in SVs.
+Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` % of variance in SVs.
 However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
@@
 We are confident that we have achieved this with the present paradigm.
-On the one hand, we were able to show which factors have an influence the values, and on the other hand, we were able to show the actual practical relevance of the values.
+On the one hand, we were able to show which factors have an influence on the values, and on the other hand, we were able to show the actual practical relevance of the values.
+<!-- Argumentation Corrugator nicht zw.
+Lvl unterschiedlich, aber trotzdem einfluss, weil man da eine relativ direkte Rückmeldung hat + Levator eher nicht -> alle Bilder negativ aber nur einige eklig, wenn man also nur diese Bilder reinnimmt, wird vielleicht Levator signifikant;
+Effort Ergebnisse bestätigen ESER Paper, dass man nach Effort-Minimierung strebt;
+Utility: Subjektive Einschätzung der Strategie als Mittel zur Zielerreichung, was eine überschneidung mit dem SV darstellt und außerdem evtl. eine Interaktion von Effektivität und Effort -->
 The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block. 
@@
 This may be because in laboratory studies the choice options are often predetermined by the experimental design[@Sheppes2011;@Sheppes2014;@Scheffel2021].
-Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life, in previous studies.
+Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life in previous studies.
 Even there, however, certain strategies were often prescribed (for example studies, see English et al.[-@English2017], Millgram et al.[-@Millgram2019], Wilms et al.[-@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].
@@
 This means that studies on ER Choice should consider not only situational factors, but also contextual factors[@Murphy2018].
-For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect on the previous trial.
+For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
 This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
@@
 
-Knowing, whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
+Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
 However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
-This conclusion cannot be drawn from the present study alone.
-To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020]
+To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
 The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
@@
 First, it should be noted that a block design was used.
-This allows for habituation effects of EMG activity within the block.
+This might have resulted in habituation effects of EMG activity within the block.
 However, block designs are common in ER research [@Barreiros2019] and have been used in previous studies [@Scheffel2019]. 
 Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block.
-It is also known that affect labeling can attenuate emotional experience [@Lieberman2007;@Torre2018]. 
+It is known that affect labeling can attenuate emotional experience [@Lieberman2007;@Torre2018]. 
 Therefore, we decided not to conduct ratings after each image.
@@
 
-In order to cope with changing emotional demands, individuals my flexibly select and apply strategies from their repertoire[@Bonanno2013;@Aldao2015].
+In order to cope with changing emotional demands, individuals may flexibly select and apply ER strategies from their repertoire[@Bonanno2013;@Aldao2015].
 The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
 The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
-To date, such subjective values hace not been established for ER strategies.
+To date, such subjective values have not been established for ER strategies.
 Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values. 
-This allows to investigate in more detail the factors influencing the internal generation of these SVs of ER strategies.
-It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and the effort.
+This further enables to investigate in more detail the factors influencing the internal generation of these subjective values of ER strategies.
+It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and effort.
 Finally, further research is needed to investigate the factors that influence subjective values and whether these values represent habitual use of ER strategies by individuals.

### 2023-04-06 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated file for revision style submission

@@
   It quantifies SVs without assuming that the easiest level is preferred, thereby enabling the assessment of SVs for tasks without objective order of task load.
-  Results show that many participants preferred a more or the most difficult level.
+  Results show that many of the 116 participants preferred a more or the most difficult level.
   Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
@@
 
-```{r cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
-The grey boxes are the choice options shown to the participant.
-The participant's final reward value of the flexible level is displayed after the first arrow.
-The resulting subjective value of each level is displayed after the second arrow, in the notation \"SV 3-back(1-back)\" for the subjective value of 3-back when 1-back is the other choice.
-The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "Inkscape Figures", "Paradigm_Scheme.png"))
-
-```
+[FIGURE \@ref(fig:cadparadigm) HERE]
 
@@
 
-```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
-Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a).
-The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
-The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sca-plot.png"))
-
-```
+[FIGURE \@ref(fig:sca-plot) HERE]
 
@@
 
-```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
-$N=116$.
-The scatter has a horizontal jitter of 0.2.
-Smoothing of conditional means with Loess method.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfcgroups-sv.png"))
-
-```
+[FIGURE \@ref(fig:nfcgroups-sv) HERE]
 
@@
 
-```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
-Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
-NFC = Need for Cognition score.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3ac-plot.png"))
-
-```
+[FIGURE \@ref(fig:h3ac-plot) HERE]
 
@@
 
-```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
-Colours indicate Need for Cognition (NFC) score above or below the median.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3b-plot.png"))
-
-```
+[FIGURE \@ref(fig:h3b-plot) HERE]
 
@@
 \newpage
-\setcounter{figure}{0}
 
@@
 
-```{r apx-cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+```{r cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 
-```{r apx-sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
+```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.
 Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a).
@@
 
-```{r apx-nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
+```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
 $N=116$.
@@
 
-```{r apx-h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
+```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
 Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
@@
 
-```{r apx-h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
+```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
 Colours indicate Need for Cognition (NFC) score above or below the median.

### 2023-04-06 06_Paper/COG-ED/Stage 2/Manuscript.tex
updated file for revision style submission

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{effort discounting, registered report, specification curve analysis, need for cognition, $n$-back\newline\indent Word count: ~ 7000}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={When easy is not preferred: A discounting paradigm to assess load-independent task preference},
  pdfauthor={Josephine Zerna,1, Christoph Scheffel,1, Corinna Kührt1, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={effort discounting, registered report, specification curve analysis, need for cognition, \(n\)-back},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{When easy is not preferred: A discounting paradigm to assess load-independent task preference}
\author{Josephine Zerna\textsuperscript{$\dagger{}$,1}, Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Corinna Kührt\textsuperscript{1}, \& Alexander Strobel\textsuperscript{1}}
\date{}

\shorttitle{The CAD paradigm to assess task preference}

\authornote{

The authors made the following contributions. Josephine Zerna: Conceptualization, Data curation, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft, Writing - review \& editing; Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Writing - review \& editing; Corinna Kührt: Formal analysis, Writing - review \& editing; Alexander Strobel: Conceptualization, Resources, Supervision, Funding acquistion, Writing - review \& editing. \textsuperscript{$\dagger{}$} Josephine Zerna and Christoph Scheffel contributed equally to this work.

Correspondence concerning this article should be addressed to Josephine Zerna, Zellescher Weg 17, 01069 Dresden, Germany. E-mail: \href{mailto:josephine.zerna@tu-dresden.de}{\nolinkurl{josephine.zerna@tu-dresden.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany}

\abstract{%
When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
One approach to quantify the SVs of levels of difficulty of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
However, it fails to acknowledge the highly individual nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
We replicated the analysis of Westbrook and colleagues with an adapted version, the Cognitive and Affective Discounting (CAD) Paradigm.
It quantifies SVs without assuming that the easiest level is preferred, thereby enabling the assessment of SVs for tasks without objective order of task load.
Results show that many of the 116 participants preferred a more or the most difficult level.
Variance in SVs was best explained by a declining logistic contrast of the \(n\)-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
Participants with higher Need for Cognition scores perceived higher \(n\)-back levels as less effortful and found them less aversive.
Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences only emerged in higher levels.
The CAD Paradigm appears to be well suited for assessing and analysing task preferences independent of the supposed objective task difficulty.
}

\begin{document}
\maketitle

\renewcommand\thesection{\Alph{section}}
\counterwithout{figure}{section}
\setcounter{figure}{0}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In everyday life, effort and reward are closely intertwined\textsuperscript{1}.
With each decision a person makes, they have to evaluate whether the effort required to reach a goal is worth being exerted, given the reward they receive when reaching the goal.
A reward is subjectively more valuable if it is obtained with less effort, so the required effort is used as a reference point for estimating the reward value\textsuperscript{1}.
However, the cost of the effort itself is also subjective, and research has not yet established which function best describes the relationship between effort and cost\textsuperscript{2}.
Investigating effort and cost is challenging because ``effort is not a property of the target task alone, but also a function of the individual's cognitive capacities, as well as the degree of effort voluntarily mobilized for the task, which in turn is a function of the individual's reward sensitivity'' (p.~209)\textsuperscript{2}.

One task that is often used to investigate effort is the \(n\)-back task, a working memory task in which a continuous stream of stimuli, e.g.~letters, is presented on screen.
Participants indicate via button press whether the current stimulus is the same as \(n\) stimuli before, with \(n\) being the level of difficulty between one and six\textsuperscript{3}.
The \(n\)-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times\textsuperscript{4}, and brain activity in areas associated with working memory\textsuperscript{5,6}.
However, its reliability measures are mixed, and associations of \(n\)-back performance and measures such as executive functioning and fluid intelligence are often inconsistent\textsuperscript{4}.

A way to quantify the subjective cost of each \(n\)-back level has been developed by Westbrook, Kester, and Braver\textsuperscript{7}, called the Cognitive Effort Discounting Paradigm (COG-ED).
First, the participants complete the \(n\)-back levels to familiarize themselves with the task.
Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
If they choose the more difficult level, the reward for 1-back increases by 0.50\$, if they choose 1-back, it decreases by 0.50\$.
This is repeated five more times, with each adjustment of the 1-back reward being half of the previous step, while the reward for the more difficult level remains fixed at 2\$.
The idea is to estimate the point of subjective equivalence, i.e., the monetary ratio at which both offers are equally preferred\textsuperscript{7}.
The subjective value (SV) of each more difficult level is then calculated by dividing the final reward value of 1-back by the fixed 2\$ reward.
Westbrook et al.\textsuperscript{7} used these SVs to investigate inter-individual differences in effort discounting.
Younger participants showed lower effort discounting, i.e., they needed a lower monetary incentive for choosing the more difficult levels over 1-back.

The individual degree of effort discounting in the study by Westbrook et al.\textsuperscript{7} was also associated with the participants' scores in Need for Cognition (NFC), a personality trait describing an individual's tendency to actively seek out and enjoy effortful cognitive activities\textsuperscript{8}.
Westbrook et al.\textsuperscript{7} conceptualized NFC as a trait measure of effortful task engagement, providing a subjective self-report of effort discounting for each participant which could then be related to the SVs as an objective measure of effort discounting.
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control\textsuperscript{9}, a trait more prominent in individuals with high NFC\textsuperscript{10--12}.
However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance\textsuperscript{13} or found no association of NFC and SVs at all\textsuperscript{14}.
On the other hand, task load has been shown to be a better predictor of SVs than task performance\textsuperscript{7,15,16}, so more research is needed to shed light on this issue.

With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest \(n\)-back level has the highest SV.
We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different \(n\)-back levels without presuming that all individuals inherently prefer the easiest level.
Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks\textsuperscript{17}, we call it the Cognitive and Affective Discounting Paradigm (CAD).
In the present study, we validated the CAD paradigm by conceptually replicating the findings of Westbrook et al.\textsuperscript{7}.
Additionally, we compared the effort discounting behavior of participants regarding the \(n\)-back task and an emotion regulation task.
The full results of the latter are published in a second Registered Report\textsuperscript{17}.
The COG-ED paradigm has been applied to tasks in different domains before, showing that SVs across task domains correlate\textsuperscript{14}, but these tasks had an objective order of task load, which is not the case for the choice of emotion regulation strategies or other paradigms where there is no objective order of task load.

Our hypotheses were derived from the results of Westbrook et al.\textsuperscript{7}.
As a manipulation check, we hypothesized that with increasing \(n\)-back level the (1a) the signal detection parameter \(d'\) declines, while (1b) reaction time and (1c) perceived task load increase.
Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing \(n\)-back level, and (2b) they do so even after controlling for declining task performance.
And finally, we hypothesized that the CAD paradigm can show inter-individual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
Each hypothesis is detailed in the Design Table in the Supplementary Material.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{cf. 18}.
The paradigm was written and presented using \emph{Psychopy}\textsuperscript{19}.
We used \emph{R}\textsuperscript{20} with \emph{R Studio}\textsuperscript{21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all our analyses.

\hypertarget{ethics-information}{%
\subsection{Ethics information}\label{ethics-information}}

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number SR-EK-50012022).
Prior to testing, written informed consent was obtained.
Participants received 24€ in total or course credit for participation.

\hypertarget{design}{%
\subsection{Design}\label{design}}

\hypertarget{cad-paradigm}{%
\subsubsection{CAD Paradigm}\label{cad-paradigm}}

Figure \ref{fig:cadparadigm} illustrates how different modifications of the COG-ED paradigm\textsuperscript{7} return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
The COG-ED paradigm, which compares every more difficult level with 1-back sets the SV of 1-back to 1, regardless of the response pattern.
Adding a comparison of the more difficult levels with each other allows the SVs of those two levels to be more differentiated, but leaves the SV of 1-back unchanged.
Adding those same pairs again, but with the opposite assignment of fixed and flexible level, does approach the true preference, but has two disadvantages.
First, the SVs are still quite alike across levels due to the fact that every more difficult level has only been compared with the easiest level, and second, having more task levels than just three would lead to an exponential increase in comparisons.
Therefore, the solution lies in reducing the number of necessary comparisons by presenting only one effort discounting round for each possible pair of levels after determining for each pair which level should be fixed and which should be flexible.
This is determined by presenting each possible pair of levels on screen with the question ``Would you prefer 1€ for level A or 1€ for level B?''.
Participants respond by clicking the respective on-screen button.
Each pair is presented three times, resulting in 18 presented pairs, which are fully randomized in order and in the assignment of which level is on the left or right of the screen.
For each pair, the level that was chosen by the participant at least two out of three times will be used as the level with a flexible value, which starts at 1€ and changes in every iteration.
The other level in the pair will be set to a fixed value of 2€.
Then, the effort discounting sensu Westbrook et al.\textsuperscript{7} begins, but with all possible pairs and with the individually determined assignment of fixed and flexible level.
The order in which the pairs are presented is fully randomized, and each pair goes through all iteration steps of adding/subtracting 0.50€, 0.25€, 0.13€, 0.06€, 0.03€, 0.02€ to/from the flexible level's reward (each adjustment half of the previous one, rounded to two decimals) before moving on to the next one.
This procedure allows to compute SVs based on actual individual preference instead of objective task load.
For each pair, the SV of the flexible level is 1, as it was preferred when faced with equal rewards, and the SV of the fixed level is the final reward of the flexible level divided by 2€.
Each level's ``global'' SV is calculated as the mean of this level's SVs from all pairs in which it appeared.
If the participant has a clear preference for one level, this level's SV will be 1.
If not, then no level's SV will be 1, but each level's SV can still be interpreted as an absolute and relative value, so each participant's effort discounting behaviour can still be quantified.
The interpretation of SVs in Westbrook et al.\textsuperscript{7} was ``The minimum relative reward required for me to choose 1-back over this level''.
So if the SV of 3-back was 0.6, the participant would need to be rewarded with at least 60~\% of what they are being offered for doing 3-back to do 1-back instead, forgoing the higher reward for 3-back.
In this study, the SV can be interpreted as ``The minimum relative reward required for me to choose any other level over this level''.
Therefore, an SV of 1 indicates that this level is preferred over all others, while SVs lower than 1 indicate that in at least one pair, a different level was preferred over this one.

{[}FIGURE \ref{fig:cadparadigm} HERE{]}

\hypertarget{study-procedure}{%
\subsubsection{Study procedure}\label{study-procedure}}

Healthy participants aged 18 to 30~years were recruited using the software \emph{ORSEE}\textsuperscript{24}.
Participants completed the personality questionnaires online and then visited the lab for two sessions one week apart.
NFC was assessed using the 16-item short form of the Need for Cognition Scale\textsuperscript{25,26}.
Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) were recorded on a 7-point Likert scale.
The NFC scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{26,27}.
Several other personality questionnaires were used in this study but are the topic of the Registered Report for the second lab session\textsuperscript{17}.
A full list of measures can be found in our \href{https://github.com/ChScheffel/CAD}{Github repository}.
In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
The paradigm started with the \(n\)-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels were referred to by color (1-back: black, 2-back: red, 3-back: blue, 4-back: green) to avoid anchor effects in the effort discounting procedure.
To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)\textsuperscript{28}, where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this \(n\)-back level.
After the \(n\)-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
They were told that one of their choices would be randomly picked for the final run of \(n\)-back.
However, this data was not analyzed as it only served to incentivise truthful behavior and to stay close to the design of Westbrook et al.\textsuperscript{7}.
After the CAD paradigm, participants filled out a short questionnaire on the tablet, indicating whether they adhered to the instructions (yes/no) and what the primary motivation for their decisions during the effort discounting procedure was (avoid boredom/relax/avoid effort/seek challenge/other).\\
The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm followed the same structure of task and effort discounting procedure, but participants could decide which strategy they wanted to reapply in the last block.
Study data was collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{29,30}.

\hypertarget{sampling-plan}{%
\subsection{Sampling plan}\label{sampling-plan}}

Sample size determination was mainly based on the results of the analyses of Westbrook et al.\textsuperscript{7} (see Design Table in the Supplementary Material).
The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and \(n\)-back level influencing SVs.
Sample size analysis with \emph{G*Power}\textsuperscript{31,32} indicated that we should collect data from at least 72 participants, assuming \(\alpha=.05\) and \(\beta=.95\).
However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of \(d=-0.32\) of emotion regulation on facial muscle activity with \(\alpha=.05\) and \(\beta=.95\).
To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aimed to collect about \(50\%\) more data sets than necessary, \(N=120\) in total.

\hypertarget{analysis-plan}{%
\subsection{Analysis plan}\label{analysis-plan}}

Data collection and analysis were not performed blind to the conditions of the experiments.
We excluded the data of a participant from all analyses, if the participant stated that they did not follow the instructions, if the investigator noted that the participant misunderstood the instructions, or if the participant withdrew their consent.
No data was replaced.
The performance measure \(d'\) was computed as the difference of the \emph{z}-transformed hit rate and the \emph{z}-transformed false alarm rate\textsuperscript{33}.
Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100~ms, as the relevant cognitive processes cannot have been completed before\textsuperscript{34,35}.
Aggregated RT values were described using the median and the median of absolute deviation (\(MAD\)) as robust estimates of center and variability, respectively\textsuperscript{36}.
Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior\textsuperscript{37,38}.
To test our hypotheses, we performed a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results\textsuperscript{39}.

\emph{Manipulation check.}
Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing \(d'\) between two levels of 1- to 4-back at a time.
Another rmANOVA with six paired contrasts was computed to compare the median RT between two levels of 1- to 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs were computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.

\emph{Subjective values.}
For each effort discounting round, the SV of the fixed level was calculated by adding or subtracting the last adjustment of 0.02€ from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2€.
This yielded an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level was 1.
The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
All SVs of each level were averaged to compute one ``global'' SV for each level.
An rmANOVA with four different contrasts were computed to investigate the association of SVs and the \(n\)-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.

To determine the influence of task performance on the association of SVs and \(n\)-back level, we performed MLM.
We applied restricted maximum likelihood (REML) to fit the model.
As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
Second, we estimated a random slopes model of \(n\)-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
As Mussel et al.\textsuperscript{40} could show, participants with high versus low NFC not only have a more shallow decline in performance with higher \(n\)-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
We controlled for performance, i.e., \(d'\) (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
\[
SV \sim level\ + d' + median RT + (level|subject)
\]
Level-1-predictors were centered within cluster as recommended by Enders \& Tofighi\textsuperscript{41}.
By this, the model yields interpretable parameter estimates.
If necessary, we adjusted the optimization algorithm to improve model fit.
We visually inspected the residuals of the model for evidence to perform model criticism.
This was done by excluding all data points with absolute standardized residuals above 3 SD.
As effect size measures, we calculated pseudo \(R^{2}\) for our model and \(f^{2}\) to estimate the effect of \(n\)-back level according to Lorah\textsuperscript{42}.

The association of SVs and NFC was examined with an rmANOVA.
We subtracted the SV of 1- from 2-back and 2- from 3-back, yielding two SV difference scores per participant.
The sample was divided into participants with low and high NFC using a median split.
We then computed an rmANOVA with the within-factor \(n\)-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
Post-hoc tests were computed depending on which effect reached significance at \(p<.01\).
To ensure the validity of this association, we conducted a specification curve analysis\textsuperscript{43}, which included 63 possible preprocessing pipelines of the RT data.
These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3~\(MAD\) from the median, RTs below 100~or~200~ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within \(n\)-back levels).
The rmANOVA was run with each of the 63~pipelines, which also included our main pipeline (untransformed data, exclusion of RTs below 100~ms).
The ratio of pipelines that lead to significant versus non-significant effects provides an indication of how robust the effect actually is.

The association of subjective task load with NFC was examined similarly.
We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor \(n\)-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at \(p<.01\).
And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e.~as the SV rises, the aversiveness declines, and vice versa.
We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
Then, we computed an rmANOVA with the within-factor \(n\)-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at \(p<.01\).

The results of each analysis was assessed on the basis of both \(p\)-value and the Bayes factor \(BF_{10}\), calculated with the \emph{BayesFactor} package\textsuperscript{23} using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{ttestBF}.
We considered a \(BF_{10}\) close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a \(BF_{10}\) close to or below .33/.10 as moderate/strong evidence for the null hypothesis\textsuperscript{44}.

\hypertarget{pilot-data}{%
\subsection{Pilot data}\label{pilot-data}}

The sample of the pilot study consisted of \(N=15\) participants (53.3\% female, \(M=24.43\) (\(SD=3.59\)) years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA-TLX were analyzed with \(n=14\) data sets.
The results showed increases in subjective and objective task load measures with higher \(n\)-back level.
Importantly, SVs were lower for higher \(n\)-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The MLM revealed \(n\)-back level as a reliable predictor of SV, even after controlling for declining task performance (\(d'\) and median RT).
NASA-TLX scores were higher with higher \(n\), and lower for the group with lower NFC scores, but NFC and \(n\)-back level did not interact.
All results are detailed in the Supplementary Material.

\hypertarget{data-availability}{%
\subsection{Data availability}\label{data-availability}}

The data of this study can be downloaded from \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.

\hypertarget{code-availability}{%
\subsection{Code availability}\label{code-availability}}

The paradigm code, the R script for analysis, and the R Markdown file used to compile this document are available at \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.

\hypertarget{protocol-registration}{%
\subsection{Protocol registration}\label{protocol-registration}}

The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/qa2bg/}{osf.io/qa2bg/}.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{adjustments-for-stage-2}{%
\subsection{Adjustments for Stage 2}\label{adjustments-for-stage-2}}

There were two necessary adjustments of the methods.
First, we failed to update the necessary sample size after the analyses changed with the first review round.
Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the Supplementary Material).
And secondly, we changed to which hypothesis we applied the specification curve analysis (SCA).
In the initial Stage 1 submission, we had applied it to the MLM of hypothesis 2b, which at this point included NFC as a predictor.
Following the advice of the reviewers, we removed NFC from the MLM, and analyzed NFC in an rmANOVA (hypothesis 3a) instead.
Since NFC was of great interest to us, we decided to apply the SCA to hypothesis 3a rather than 2b to provide a measure of robustness.
However, hypothesis 3a does not contain any RT data, so the SCA is only useful for the MLM in hypothesis 2b.
Therefore, we applied it to the MLM.

\hypertarget{sample}{%
\subsection{Sample}\label{sample}}

Data was collected between the 16th of August 2022 and the 3rd of February 2023.
Of the \(N=176\) participants who filled out the NFC questionnaire, \(n=124\) completed the first lab session.
Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the \(n\)-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
Our final data set therefore included \(N=116\) participants (83.60\% female, \(M \pm SD=22.4 \pm 3\))~years old), which is 2.2 times more than what the highest sample size calculation required.

\hypertarget{manipulation-checks}{%
\subsection{Manipulation checks}\label{manipulation-checks}}

We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across \(n\)-back levels.
For each rmANOVA we report the generalized eta squared \(\hat{\eta}^2_G\), which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
The performance measure \(d'\) did not change across \(n\)-back levels (\(F(2.85, 327.28) = 0.01\), \(p = .999\), \(\hat{\eta}^2_G = .000\), 90\% CI \([.000, .000]\), \(\mathrm{BF}_{\textrm{10}} = 3.31 \times 10^{-3}\)), but the median RT did (\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)), evidence was not in favour of H1a but in favour of H1b.
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
It did not differ between 2- and 4-back, and it was higher for 3- than for 4-back (Table~\ref{tab:H1b-contrasts}).

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:H1b-contrasts}Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -0.11 & 0.01 & 345.00 & -11.76 & <.001 & $1.75 \times 10^{30}$ & 0.29 & {}[0.22, 1.00]\\
1 - 3 & -0.16 & 0.01 & 345.00 & -16.23 & <.001 & $8.80 \times 10^{45}$ & 0.43 & {}[0.37, 1.00]\\
1 - 4 & -0.12 & 0.01 & 345.00 & -12.47 & <.001 & $4.79 \times 10^{34}$ & 0.31 & {}[0.25, 1.00]\\
2 - 3 & -0.04 & 0.01 & 345.00 & -4.47 & <.001 & 5,538.45 & 0.05 & {}[0.02, 1.00]\\
2 - 4 & -0.01 & 0.01 & 345.00 & -0.71 & 0.894 & 0.10 & 1.45e-03 & {}[0.00, 1.00]\\
3 - 4 & 0.04 & 0.01 & 345.00 & 3.76 & 0.001 & $6.35 \times 10^{6}$ & 0.04 & {}[0.01, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

All NASA-TLX subscale scores increased across \(n\)-back levels, so evidence was in favour of H1c.
Ratings on the effort subscale (\(F(2.20, 253.06) = 203.82\), \(p < .001\), \(\hat{\eta}^2_G = .316\), 90\% CI \([.250, .375]\), \(\mathrm{BF}_{\textrm{10}} = 2.47 \times 10^{34}\)) increased across all levels, but the magnitude of change decreased from 1- to 2-back (\(t(345) = -12.35\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 4.24 \times 10^{19}\)) to 3- to 4-back (\(t(345) = -2.72\), \(p_\mathrm{\scriptsize Tukey(4)} = .035\), \(\mathrm{BF}_{\textrm{10}} = 174.38\)).
Three subscales had significant differences between all contrasts except for 3- versus 4-back:
While ratings on the frustration and time subscales were higher for more difficult levels (\(F(2.50, 287.66) = 68.06\), \(p < .001\), \(\hat{\eta}^2_G = .172\), 90\% CI \([.112, .227]\), \(\mathrm{BF}_{\textrm{10}} = 5.26 \times 10^{15}\), and \(F(2.21, 254.65) = 51.08\), \(p < .001\), \(\hat{\eta}^2_G = .117\), 90\% CI \([.065, .168]\), \(\mathrm{BF}_{\textrm{10}} = 3.94 \times 10^{9}\), respectively), ratings on the performance subscale decreased with higher \(n\) (\(F(2.49, 285.97) = 95.33\), \(p < .001\), \(\hat{\eta}^2_G = .241\), 90\% CI \([.176, .299]\), \(\mathrm{BF}_{\textrm{10}} = 1.55 \times 10^{24}\)).
Ratings on the mental subscale consistently increased across all levels (\(F(1.99, 228.35) = 274.47\), \(p < .001\), \(\hat{\eta}^2_G = .375\), 90\% CI \([.309, .432]\), \(\mathrm{BF}_{\textrm{10}} = 1.64 \times 10^{43}\)).
Ratings on the physical subscale were higher for more difficult levels (\(F(1.68, 192.93) = 15.91\), \(p < .001\), \(\hat{\eta}^2_G = .041\), 90\% CI \([.009, .075]\), \(\mathrm{BF}_{\textrm{10}} = 60.54\)), apart from the contrasts 2- versus 3-back (\(\mathrm{BF}_{\textrm{10}} = 10.45\)) and 3- versus 4-back (\(\mathrm{BF}_{\textrm{10}} = 0.47\)).
The full results of these manipulation checks are listed in Table S.1 to S.8 in the Supplementary Material.

\hypertarget{decline-of-subjective-values}{%
\subsection{Decline of subjective values}\label{decline-of-subjective-values}}

When asking participants what motivated their decisions in the cognitive effort discounting paradigm, 11.2\% stated that they wanted to avoid boredom, 22.4\% stated that they wanted a challenge, 34.5\% stated that they wanted to avoid effort, and 4.3\% stated that they wanted to relax.
The remaining 27.6\% of participants used the free text field and provided reasons such as ``I wanted a fair relation of effort and reward.'', ``I wanted the fun that I had in the more challenging levels.'', ``I wanted to maximize reward first and minimize effort second.'', or ``I did not want to perform poorly when I was being paid for it.''.
Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per \(n\)-back level.

The rmANOVA showed a significant difference between the SVs across \(n\)-back levels (\(F(1.98, 227.98) = 65.65\), \(p < .001\), \(\hat{\eta}^2_G = .288\), 90\% CI \([.222, .347]\), \(\mathrm{BF}_{\textrm{10}} = 1.58 \times 10^{64}\)), so evidence was in favour of H2a.
All four pre-defined contrasts reached significance (Table~\ref{tab:H2a-contrasts}), so a purely linear contrast can be rejected.

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:H2a-contrasts}Contrasts for the rmANOVA comparing the subjective values between $n$-back levels}

\begin{tabular}{llllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
Declining Linear & 1.11 & 0.08 & 345.00 & 13.41 & <.001 & 0.34 & {}[0.28, 1.00]\\
Ascending Quadratic & 0.15 & 0.04 & 345.00 & 4.14 & <.001 & 0.05 & {}[0.02, 1.00]\\
Declining Logistic & 1.22 & 0.09 & 345.00 & 12.97 & <.001 & 0.33 & {}[0.26, 1.00]\\
Positively Skewed Normal & 0.75 & 0.06 & 345.00 & 12.74 & <.001 & 0.32 & {}[0.26, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

The declining logistic contrast had the highest effect estimate (\(t(345) = 12.97\), \(p < .001\)), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.

Consequently, we had to adapt the MLM to incorporate this non-linear trend.
To apply the contrast to the \(n\)-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
\[
SV \sim level\ + d' + median RT + (1|subject)
\]
This means that the intercept still varied between subjects, but there were no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per \(n\)-back level per subject, rather than \(n\)-back levels per subject.
The ICC of the null model indicated that there was a correlation of \(r=\) .096 between the SVs of a subject, i.e.~that 9.59\% of variance in SVs could be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of 9 data points from 6 participants were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table~\ref{tab:H2b-results}.

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:H2b-results}Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.}

\begin{tabular}{llllllll}
\toprule
Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$-value} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
\midrule
Intercept & 0.81 & 0.01 & 114.82 & 78.34 & <.001 &  & 0.09\\
n-back level & 0.05 & 0.00 & 799.38 & 18.22 & <.001 & 0.64 & \\
d' & 0.02 & 0.00 & 798.75 & 5.60 & <.001 & 0.04 & \\
median RT & 0.02 & 0.07 & 798.58 & 0.30 & 0.768 & 0.00 & \\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other (\(\chi^2 (2)\) = 34.48, \(p<.001\)), and with an Akaike Information Criterion of \(AIC=-492.61\) and a Bayesian Information Criterion of \(BIC=-454.02\) the declining logistic model was superior to the linear model (\(AIC=-462.12\), \(BIC=-433.18\)).
Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
The final model had an effect size of \(f^{2}=\) 0.64 for the \(n\)-back levels and \(f^{2}=\) 0.04 for \(d'\), which are considered large and small, respectively\textsuperscript{45}.
This means that the \(n\)-back level explained 64.20\% and \(d'\) explained 3.95\% of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in \(d'\), the SV increased by 0.02.
Due to the coding scheme of the logistic contrast, the beta coefficient of the \(n\)-back level has to be interpreted inversely, so SVs decline with increasing \(n\)-back level.
The effect size of the median RT was \(f^{2}=\) 0.00.
Since SVs decline with increasing level, beyond the variance explained by \(d'\), evidence was in favour of H2b.

To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis (Figure~\ref{fig:sca-plot}).

{[}FIGURE \ref{fig:sca-plot} HERE{]}

Regardless of the preprocessing pipeline, \(n\)-back level and \(d'\) were significant predictors of SVs, and had stable effect estimates across all pipelines.
There was only one pipeline in which the median RT was a significant predictor of SVs.
This pipeline contained data that had been inverse transformed across subjects but within conditions, i.e.~within the round of an \(n\)-back level, and RTs beyond 2 \(MAD\) from the median had been excluded.

\hypertarget{differences-between-nfc-groups}{%
\subsection{Differences between NFC groups}\label{differences-between-nfc-groups}}

Figure~\ref{fig:nfcgroups-sv} shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.
There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across \(n\)-back levels.
At the same time, there is a subtle separation of SVs across \(n\)-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
Specifically, \(n=71\) participants had an absolute preference for 1-back, \(n=18\) for 2-back, \(n=9\) for 3-back, and \(n=13\) for 4-back.
There were \(n=5\) participants who did not have an absolute preference for any \(n\)-back level, i.e.~none of their SVs was 1.

{[}FIGURE \ref{fig:nfcgroups-sv} HERE{]}

The median NFC was 16, with \(n=57\) subjects below and \(n=59\) above the median.
We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the \(n\)-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56\)) nor an interaction of NFC group and \(n\)-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Figure~\ref{fig:h3ac-plot}a).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.

{[}FIGURE \ref{fig:h3ac-plot} HERE{]}

The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\) \}\$) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\) \}\(). Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\)t(114) = -2.15\$, \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Figure~\ref{fig:h3b-plot}).

{[}FIGURE \ref{fig:h3b-plot} HERE{]}

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (\(F(1, 114) = 8.43\), \(p = .004\), \(\hat{\eta}^2_G = .043\), 90\% CI \([.003, .119]\), \(\mathrm{BF}_{\textrm{10}} = 14.26\)) and a main effect of the \(n\)-back level (\(F(1, 114) = 10.21\), \(p = .002\), \(\hat{\eta}^2_G = .034\), 90\% CI \([.000, .105]\), ), but no interaction (\(F(1, 114) = 2.59\), \(p = .110\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .058]\)).
In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (\(t(114) = 2.90\), \(p = .004\)) (Figure~\ref{fig:h3ac-plot}b).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was more negative than that of 1- and 2-back (\(t(114) = 3.20\), \(p = .002\)), indicating that in the same way in which the SVs decreased more strongly from 2- to 3-back than from 1- to 2-back, the aversion increased more strongly.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.

\hypertarget{exploratory-analysis}{%
\section{Exploratory analysis}\label{exploratory-analysis}}

To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher \(n\)-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
There was no main effect of NFC group (\(F(1, 114) = 2.63\), \(p = .108\), \(\hat{\eta}^2_G = .007\), 90\% CI \([.000, .053]\), \(2.95 \times 10^{-1}\)), but a main effect of the \(n\)-back level (\(F(2.01, 229.39) = 67.39\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(2.70 \times 10^{30}\)) and an interaction (\(F(2.01, 229.39) = 3.24\), \(p = .041\), \(\hat{\eta}^2_G = .020\), 90\% CI \([.000, .044]\)).
Post-hoc tests for the main effect of level showed that Svs were lower for the more difficult \(n\)-back level in each paired contrast except for 1- versus 2-back.
Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (\(\Delta M = 0.11\), 95\% CI \([0.01, 0.22]\), \(t(114) = 2.13\), \(p = .036\)).
Despite not reaching significance, 1-back was the only level in which participants with NFC scores above the median seemed to have lower SVs than those with scores below the median (\(\Delta M = -0.05\), 95\% CI \([-0.11, 0.01]\), \(t(114) = -1.50\), \(p = .136\)).
The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.\textsuperscript{7}, which estimates subjective values of different \(n\)-back levels, into the Cognitive and Affective Discounting (CAD) paradigm to estimate SVs of tasks without defaulting to the assumed objective task load as a benchmark.
For this purpose, we adapted the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
The analyses were closely aligned with those in Westbrook et al.\textsuperscript{7} to demonstrate the changes in SVs brought about by the new paradigm.
This study also applied the CAD paradigm to an emotion regulation task, the results of which are detailed in a second Registered Report\textsuperscript{17}.

\hypertarget{manipulation-checks-1}{%
\subsection{Manipulation checks}\label{manipulation-checks-1}}

The performance measure \(d'\) did not differ across \(n\)-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
This points to three important characteristics of the \(n\)-back task in this context.
Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to \(n=3\), and could be used to investigate inter-individual differences for \(n>3\).
Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where \(d'\) would decline and RT would remain stable.
And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before\textsuperscript{46} and both show different associations with various measures of intelligence\textsuperscript{4}, suggesting that they should always be reported as separate indices.
Additionally, \(d'\) might not have differed across \(n\)-back levels because the manipulation of task load is not strictly continuous.
Several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when \(n\) was an even number than when \(n\) was an odd number.

All NASA-TLX subscales differed across \(n\)-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
This would support the notion of the \(n\)-back task offering a continuous manipulation of task load, at least subjectively.
Ratings on the frustration and time subscales increased and ratings on the performance subscale decreased until 3-back and then remained stable.
This pattern is akin to the RT, which also increased and then remained stable.
Ratings on the physical load subscale increased with \(n\)-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.

\hypertarget{decline-of-subjective-values-1}{%
\subsection{Decline of subjective values}\label{decline-of-subjective-values-1}}

The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across \(n\)-back levels.
The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more inter-individual variance for 3- and 4-back.
Thomson and Oppenheimer\textsuperscript{47} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
For example, the \(n\)-back task is likely not a continuous manipulation of task load, as discussed above.
However, the declining logistic curve is similar to the sigmoidal curve that had the best fit in a different effort paradigm\textsuperscript{48}, which the authors explained with the low effect of low energy costs, suggesting there are still common features of effort across different tasks and domains.
The MLM with the logistic contrast showed that the \(n\)-back level explained the majority of variance in SVs, while the performance measure \(d'\) also explained some variance in SVs, albeit less.
With increasing \(n\)-back level and decreasing \(d'\), the SV decreased.
The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not \(d'\) yielded significant differences across levels in the manipulation checks.
However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e.~twice per \(n\)-back level, as an anchor during the effort discounting.
This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
Since more participants reported effort avoidance as their motivation in the effort discounting than those who reported seeking a challenge, we can assume that they were more motivated to repeat a task in which they performed well because their good performance coincided with low effort.

The declining logistic \(n\)-back levels and \(d'\) remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis, with betas that varied by less than 0.01.
In contrast to this stood the variability of the median RT betas, which ranged from about 0.10 to -0.03, and reached significance in only one pipeline.
This pipeline was among the three pipelines with the highest \(BF_{10}\), and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 \(MAD\) from the median.
Interestingly, the curve of median RT betas in Figure~\ref{fig:sca-plot}a mirrored the rectangular pipeline indicators in the transformation rows of Figure~\ref{fig:sca-plot}b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
As Fernandez et al.\textsuperscript{49} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
Our data seems to corroborate this finding for \(n\)-back tasks as well.
Surprisingly, the \(d'\) betas appear almost unaffected by the preprocessing pipeline, even though \(d'\) was computed after the outlier exclusion.
This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.

\hypertarget{differences-between-nfc-groups-1}{%
\subsection{Differences between NFC groups}\label{differences-between-nfc-groups-1}}

The majority of participants (61.20~\%) had an absolute preference for 1-back over the other levels, but that also means that there were 34.50~\% who had an absolute preference for 2-, 3-, or 4-back, and 4.30~\% who preferred no specific level over all others.
It shows that when given the choice, there is a large number of participants who do not prefer the easiest level, confirming the necessity of an effort discounting paradigm that works independent of the objective task load.
The CAD paradigm provides the means to depict these preferences.

In the analysis of SV difference scores, the NFC group did not reach significance as a predictor.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
The analysis of NASA-TLX scores showed that the sum score increased with every \(n\)-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher \(n\)-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
This was also supported by the fact that higher \(n\)-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmitt et al.~(2013)\textsuperscript{50} and Blum et al.~(2018)\textsuperscript{51} in the same-named NIPS model.
The NIPS model describes behaviour as a function of situational affordance which is mediated by personality traits.
The behavioural variability follows an s-shaped curve, such that ``strong'' situations with low or high situational affordance elicit the least behavioural variability, while ``weak'' situations with moderate affordance maximize individual differences.
These differences are caused by a person's expression of a certain trait, which shifts the curve along the y-axis.
In our study, the situational affordance is the \(n\)-back level and the behaviour is the SV, following a declining logistic curve, i.e.~a mirrored s-shape.
Hence, the variability in SVs increased from 1- to 4-back, and participants with higher NFC showed a more shallow decline in SVs as the situational affordance approached moderate values.
According to the NIPS model, we can expect the SVs of participants with higher and lower NFC to converge again in levels of \(n>4\), since behavioural variability decreases when situational affordance is high.
An investigation of this relationship using the COG-ED paradigm\textsuperscript{7} had been encouraged by Strobel et al.\textsuperscript{52} based on their findings on demand avoidance and cognitive effort investment.
With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model\textsuperscript{50,51} and should be tested further in a setting with \(n\)-back levels exceeding \(n=4\).

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

When developing a new paradigm, it is challenging to decide on the optimal analysis strategy, as every hypothesis is based on expected data patterns rather than previous findings.
While the Stage 1 review process made the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, or even more promising, as a continuous measure, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
To arrive at a sample with more balanced NFC scores, recruitment efforts should be focused on representative population samples and/or collecting data with an NFC-based stop rule.
Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher \(n\)-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
Future studies could create a stronger separation between the concepts investigated in this study (discounting curve, effort perception, performance, SV computation, NFC), and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
Another important point is the instruction, not just for the \(n\)-back task, but for the effort discounting as well.
We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction or a training next time.
And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
One might also argue that the 2€ reward range was not large enough to be an incentive for effort expenditure.
However, findings by Bialaszek et al.\textsuperscript{53} suggest that participants are actually more sensitive to effort when the reward is small.
Nevertheless, we exceeded the largest required sample size by 2.20 times, which gives our analyses high statistical power.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

Effort and reward are relevant in everyday life, yet these constructs vary in their conceptualization across individuals and even studies.
With each decision an individual makes, they must weigh the required effort against the expected reward to decide if and how to behave in that situation.
So far, effort discounting paradigms have relied on the assumption that the task that is objectively easiest is the one that is preferred by everyone, and each more difficult task is simply being devalued compared to the easy one.
However, effort-related traits such as Need for Cognition suggest that this is not the case.
Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an \(n\)-back task.
The results showed that many participants indeed preferred a more or even the most difficult \(n\)-back level.
Spanning the entire sample, these preferences took the shape of a declining logistic curve across \(n\)-back levels.
While the subjective value declined with increasing levels, it increased with better performance as measured in \(d'\), and was unaffected by the reaction time.
Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for tasks with high discriminatory power and effort discounting paradigms with flexible, participant-centered mechanisms.
The CAD paradigm offers this flexibility, and we encourage future studies to question traditional assumptions in the field of effort discounting in the light of these findings, and to re-use this data set for exploratory analyses.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Botvinick2009}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Botvinick, M. M., Huffstetler, S. \& McGuire, J. T. \href{https://doi.org/10.3758/CABN.9.1.16}{Effort discounting in human nucleus accumbens}. \emph{Cognitive, affective \& behavioral neuroscience} \textbf{9}, 16--27 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Kool2018}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Kool, W. \& Botvinick, M. \href{https://doi.org/10.1038/s41562-018-0401-9}{Mental labour}. \emph{Nature Human Behaviour} \textbf{2}, 899--908 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Mackworth1959}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Mackworth, J. F. \href{https://doi.org/10.1037/h0049090}{Paced memorizing in a continuous task}. \emph{Journal of Experimental Psychology} \textbf{58}, 206--211 (1959).}

\leavevmode\vadjust pre{\hypertarget{ref-Jaeggi2010}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Jaeggi, S. M., Buschkuehl, M., Perrig, W. J. \& Meier, B. \href{https://doi.org/10.1080/09658211003702171}{The concurrent validity of the {N}-back task as a working memory measure}. \emph{Memory} \textbf{18}, 394--412 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Jonides1997}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Jonides, J. \emph{et al.} \href{https://doi.org/10.1162/jocn.1997.9.4.462}{Verbal working memory load affects regional brain activation as measured by {PET}}. \emph{Journal of Cognitive Neuroscience} \textbf{9}, 462--475 (1997).}

\leavevmode\vadjust pre{\hypertarget{ref-Owen2005}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Owen, A. M., McMillan, K. M., Laird, A. R. \& Bullmore, E. \href{https://doi.org/10.1002/hbm.20131}{N-back working memory paradigm: A meta-analysis of normative functional neuroimaging studies}. \emph{Human Brain Mapping} \textbf{25}, 46--59 (2005).}

\leavevmode\vadjust pre{\hypertarget{ref-Westbrook2013}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Westbrook, A., Kester, D. \& Braver, T. S. \href{https://doi.org/10.1371/journal.pone.0068210}{What is the subjective cost of cognitive effort? {Load}, trait, and aging effects revealed by economic preference}. \emph{PLOS ONE} \textbf{8}, e68210 (2013).}

\leavevmode\vadjust pre{\hypertarget{ref-Cacioppo1982}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Cacioppo, J. T. \& Petty, R. E. \href{https://doi.org/10.1037//0022-3514.42.1.116}{The {Need} for {Cognition}}. \emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}

\leavevmode\vadjust pre{\hypertarget{ref-Wu2021}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Wu, R., Ferguson, A. \& Inzlicht, M. \emph{Do humans prefer cognitive effort over doing nothing?} \url{https://psyarxiv.com/d2gkf/} (2021) doi:\href{https://doi.org/10.31234/osf.io/d2gkf}{10.31234/osf.io/d2gkf}.}

\leavevmode\vadjust pre{\hypertarget{ref-Bertrams2012}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Bertrams, A. \& Dickhäuser, O. \href{https://doi.org/10.1027/1614-0001/a000081}{Passionate thinkers feel better}. \emph{Journal of Individual Differences} \textbf{33}, 69--75 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Nishiguchi2016}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Nishiguchi, Y., Takano, K. \& Tanno, Y. \href{https://doi.org/10.1016/j.psychres.2016.04.092}{The {Need} for {Cognition} mediates and moderates the association between depressive symptoms and impaired {Effortful} {Control}}. \emph{Psychiatry Research} \textbf{241}, 8--13 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Xu2021}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Xu, P. \& Cheng, J. \href{https://doi.org/10.1016/j.paid.2021.110706}{Individual differences in social distancing and mask-wearing in the pandemic of {COVID}-19: {The} role of need for cognition, self-control and risk attitude}. \emph{Personality and Individual Differences} \textbf{175}, 110706 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Kramer2021}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Kramer, A.-W., Van Duijvenvoorde, A. C. K., Krabbendam, L. \& Huizenga, H. M. \href{https://doi.org/10.1016/j.cogdev.2020.100978}{Individual differences in adolescents' willingness to invest cognitive effort: {Relation} to need for cognition, motivation and cognitive capacity}. \emph{Cognitive Development} \textbf{57}, 100978 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Crawford2021}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Crawford, J. L., Eisenstein, S. A., Peelle, J. E. \& Braver, T. S. \href{https://doi.org/10.1186/s41235-021-00272-7}{Domain-general cognitive motivation: Evidence from economic decision-making}. \emph{Cognitive Research: Principles and Implications} \textbf{6}, 4 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Culbreth2016}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Culbreth, A., Westbrook, A. \& Barch, D. \href{https://doi.org/10.1037/abn0000153}{Negative symptoms are associated with an increased subjective cost of cognitive effort}. \emph{Journal of Abnormal Psychology} \textbf{125}, 528--536 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Westbrook2019}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Westbrook, A., Lamichhane, B. \& Braver, T. \href{https://doi.org/10.1523/jneurosci.3071-18.2019}{The subjective value of cognitive effort is encoded by a domain-general valuation network}. \emph{The Journal of Neuroscience} \textbf{39}, 3934--3947 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-ScheffelZerna2022}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Scheffel, C., Zerna, J., Gärtner, A., Dörfel, D. \& Strobel, A. \href{https://psyarxiv.com/wr8qx}{Estimating individual subjective values of emotion regulation strategies}. (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-Simmons2012}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A 21 word solution. (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}

\leavevmode\vadjust pre{\hypertarget{ref-Peirce2019}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{Peirce, J. \emph{et al.} \href{https://doi.org/10.3758/s13428-018-01193-y}{{PsychoPy2}: {Experiments} in behavior made easy}. \emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-RCT2020}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: {A} language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2020).}

\leavevmode\vadjust pre{\hypertarget{ref-RStudioTeam2020}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{RStudio Team. \emph{\href{http://www.rstudio.com/}{{RStudio: Integrated development environment for R}}}. (RStudio, PBC., 2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Singmann2021}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{\href{https://CRAN.R-project.org/package=afex}{Afex: {A}nalysis of factorial experiments}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Morey2021}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{\href{https://CRAN.R-project.org/package=BayesFactor}{{BayesFactor}: {Computation} of {Bayes} factors for common designs}}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Greiner2015}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{Greiner, B. \href{https://doi.org/10.1007/s40881-015-0004-4}{Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}}. \emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}

\leavevmode\vadjust pre{\hypertarget{ref-Cacioppo1984}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{Cacioppo, J. T., Petty, R. E. \& Kao, C. F. \href{https://doi.org/10.1207/s15327752jpa4803_13}{The efficient assessment of {Need} for {Cognition}}. \emph{Journal of Personality Assessment} \textbf{48}, 306--307 (1984).}

\leavevmode\vadjust pre{\hypertarget{ref-Bless1994}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Bless, H., Wänke, M., Bohner, G., Fellhauer, R. F. \& Schwarz, N. \href{https://doi.org/1779110}{Need for {Cognition}: {Eine} {Skala} zur {Erfassung} von {Engagement} und {Freude} bei {Denkaufgaben}}. \emph{Zeitschrift für Sozialpsychologie} \textbf{25}, (1994).}

\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{Fleischhauer, M. \emph{et al.} \href{https://doi.org/10.1177/0146167209351886}{Same or different? {Clarifying} the relationship of need for cognition to personality and intelligence}. \emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-Hart1988}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{Hart, S. G. \& Staveland, L. E. \href{https://doi.org/10.1016/S0166-4115(08)62386-9}{Development of {NASA}-{TLX} ({Task} {Load} {Index}): {Results} of empirical and theoretical research}. \textbf{52}, 139--183 (1988).}

\leavevmode\vadjust pre{\hypertarget{ref-Harris2009}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{Harris, P. A. \emph{et al.} \href{https://doi.org/10.1016/j.jbi.2008.08.010}{Research electronic data capture ({REDCap})---{A} metadata-driven methodology and workflow process for providing translational research informatics support}. \emph{Journal of Biomedical Informatics} \textbf{42}, 377--381 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Harris2019}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{Harris, P. A. \emph{et al.} \href{https://doi.org/10.1016/j.jbi.2019.103208}{The {REDCap} consortium: {Building} an international community of software platform partners}. \emph{Journal of Biomedical Informatics} \textbf{95}, 103208 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-Faul2007}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G. \& Buchner, A. \href{https://doi.org/10.3758/BF03193146}{G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences}. \emph{Behavior Research Methods} \textbf{39}, 175--191 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-Faul2009}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{Faul, F., Erdfelder, E., Buchner, A. \& Lang, A.-G. \href{https://doi.org/10.3758/BRM.41.4.1149}{Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses}. \emph{Behavior Research Methods} \textbf{41}, 1149--1160 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-Macmillan1990}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{Macmillan, N. A. \& Creelman, C. D. \href{https://doi.org/10.1037/0033-2909.107.3.401}{Response bias: {Characteristics} of detection theory, threshold theory, and "nonparametric" indexes}. \emph{Psychological Bulletin} \textbf{107}, 401--413 (1990).}

\leavevmode\vadjust pre{\hypertarget{ref-Whelan2008}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Whelan, R. \href{https://doi.org/10.1007/BF03395630}{Effective analysis of reaction time data}. \emph{The Psychological Record} \textbf{58}, 475--482 (2008).}

\leavevmode\vadjust pre{\hypertarget{ref-Berger2021}{}}%
\CSLLeftMargin{35. }%
\CSLRightInline{Berger, A. \& Kiefer, M. \href{https://doi.org/10.3389/fpsyg.2021.675558}{Comparison of different response time outlier exclusion methods: {A} simulation study}. \emph{Frontiers in Psychology} \textbf{12}, 2194 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Lachaud2011}{}}%
\CSLLeftMargin{36. }%
\CSLRightInline{Lachaud, C. M. \& Renaud, O. \href{https://doi.org/10.1017/s0142716410000457}{A tutorial for analyzing human reaction times: {How} to filter data, manage missing values, and choose a statistical model}. \emph{Applied Psycholinguistics} \textbf{32}, 389--416 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-Dutilh2012}{}}%
\CSLLeftMargin{37. }%
\CSLRightInline{Dutilh, G. \emph{et al.} \href{https://doi.org/10.3758/s13414-011-0243-2}{Testing theories of post-error slowing}. \emph{Attention, Perception, \& Psychophysics} \textbf{74}, 454--465 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Houtman2012}{}}%
\CSLLeftMargin{38. }%
\CSLRightInline{Houtman, F., Castellar, E. N. \& Notebaert, W. \href{https://doi.org/10.1080/20445911.2011.617301}{Orienting to errors with and without immediate feedback}. \emph{Journal of Cognitive Psychology} \textbf{24}, 278--285 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-Singmann2019}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Singmann, H. \& Kellen, D. An introduction to mixed models for experimental psychology. in \emph{New methods in cognitive psychology} 4--31 (Routledge, 2019). doi:\href{https://doi.org/10.4324/9780429318405-2}{10.4324/9780429318405-2}.}

\leavevmode\vadjust pre{\hypertarget{ref-Mussel2016}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{Mussel, P., Ulrich, N., Allen, J. J. B., Osinsky, R. \& Hewig, J. \href{https://doi.org/10.1038/srep29245}{Patterns of theta oscillation reflect the neural basis of individual differences in epistemic motivation}. \emph{Scientific Reports} \textbf{6}, (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-Enders2007}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{Enders, C. K. \& Tofighi, D. \href{https://doi.org/10.1037/1082-989x.12.2.121}{Centering predictor variables in cross-sectional multilevel models: {A} new look at an old issue.} \emph{Psychological Methods} \textbf{12}, 121--138 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-Lorah2018}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Lorah, J. \href{https://doi.org/10.1186/s40536-018-0061-2}{Effect size measures for multilevel models: Definition, interpretation, and {TIMSS} example}. \emph{Large-scale Assessments in Education} \textbf{6}, (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Simonsohn2020}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Simonsohn, U., Simmons, J. P. \& Nelson, L. D. \href{https://doi.org/10.1038/s41562-020-0912-z}{Specification curve analysis}. \emph{Nature Human Behaviour} \textbf{4}, 1208--1214 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Wetzels2015}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Wetzels, R., Ravenzwaaij, D. van \& Wagenmakers, E.-J. Bayesian analysis. 1--11 (2015) doi:\href{https://doi.org/10.1002/9781118625392.wbecp453}{10.1002/9781118625392.wbecp453}.}

\leavevmode\vadjust pre{\hypertarget{ref-Cohen1992}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{Cohen, J. \href{https://doi.org/10.1037/0033-2909.112.1.155}{A power primer.} \emph{Psychological Bulletin} \textbf{112}, 155--159 (1992).}

\leavevmode\vadjust pre{\hypertarget{ref-Meule2017}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{Meule, A. \href{https://doi.org/10.3389/fpsyg.2017.00352}{Reporting and interpreting working memory performance in n-back tasks}. \emph{Frontiers in Psychology} \textbf{8}, (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-Thomson2022}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{Thomson, K. S. \& Oppenheimer, D. M. \href{https://doi.org/10.1177/17456916211064896}{The {``}{E}ffort {E}lephant{''} in the room: {W}hat is effort, anyway?} \emph{Perspectives on Psychological Science} \textbf{17}, 1633--1652 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-KleinFluegge2015}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Klein-Flügge, M. C., Kennerley, S. W., Saraiva, A. C., Penny, W. D. \& Bestmann, S. \href{https://doi.org/10.1371/journal.pcbi.1004116}{Behavioral modeling of human choices reveals dissociable effects of physical effort and temporal delay on reward devaluation}. \emph{{PLOS} Computational Biology} \textbf{11}, e1004116 (2015).}

\leavevmode\vadjust pre{\hypertarget{ref-Fernandez2020}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Fernández, L. M. \& Vadillo, M. A. \href{https://doi.org/10.1098/rsos.190831}{Flexibility in reaction time analysis: Many roads to a false positive?} \emph{Royal Society Open Science} \textbf{7}, 190831 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Schmitt2013}{}}%
\CSLLeftMargin{50. }%
\CSLRightInline{Schmitt, M. \emph{et al.} \href{https://doi.org/10.3389/fpsyg.2013.00499}{Proposal of a nonlinear interaction of person and situation ({NIPS}) model}. \emph{Frontiers in Psychology} \textbf{4}, (2013).}

\leavevmode\vadjust pre{\hypertarget{ref-Blum2018}{}}%
\CSLLeftMargin{51. }%
\CSLRightInline{Blum, G. S., Rauthmann, J. F., Göllner, R., Lischetzke, T. \& Schmitt, M. \href{https://doi.org/10.1002/per.2138}{The nonlinear interaction of person and situation ({NIPS)} model: {Theory} and empirical evidence}. \emph{European Journal of Personality} \textbf{32}, 286--305 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-Strobel2020}{}}%
\CSLLeftMargin{52. }%
\CSLRightInline{Strobel, A. \emph{et al.} \href{https://doi.org/10.1371/journal.pone.0239817}{Dispositional cognitive effort investment and behavioral demand avoidance: {Are} they related?} \emph{PLOS ONE} \textbf{15}, e0239817 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
\CSLLeftMargin{53. }%
\CSLRightInline{Białaszek, W., Marcowski, P. \& Ostaszewski, P. \href{https://doi.org/10.1371/journal.pone.0182353}{Physical and cognitive effort discounting across different reward magnitudes: Tests of discounting models}. \emph{{PLOS} {ONE}} \textbf{12}, e0182353 (2017).}

\end{CSLReferences}

\endgroup

\newpage

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection.

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

JZ and CS contributed equally to this work.
JZ, CS, and AS conceptualized the study and acquired funding.
JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
JZ, CS, and CK did the formal analysis.
JZ visualized the results.
JZ and CK prepared the original draft.
All authors reviewed, edited, and approved the final version of the manuscript.

\hypertarget{competing-interests}{%
\section{Competing Interests}\label{competing-interests}}

The authors declare no competing interests.

\newpage

\hypertarget{figures}{%
\section{Figures}\label{figures}}

\begin{figure}[H]
\includegraphics[width=\textwidth]{../../Inkscape Figures/Paradigm_Scheme} \caption{An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back. The grey boxes are the choice options shown to the participant. The participant's final reward value of the flexible level is displayed after the first arrow. The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice. The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:cadparadigm}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/sca-plot} \caption{Results of the multi level model for each of the 63 preprocessing pipelines. Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a). The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect. The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:sca-plot}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/nfcgroups-sv} \caption{Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median. $N=116$. The scatter has a horizontal jitter of 0.2. Smoothing of conditional means with Loess method. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:nfcgroups-sv}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/h3ac-plot} \caption{Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back. Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges. NFC = Need for Cognition score. $N=116$. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3ac-plot}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/h3b-plot} \caption{NASA-TLX sum scores for each $n$-back level. Colours indicate Need for Cognition (NFC) score above or below the median. $N=116$. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3b-plot}
\end{figure}

\end{document}

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected reasons for choice
corrected missing letters

@@
 
-### Manipulation checks <!-- es gibt keine weitere Überschrift auf dieser Ebene, würde ich jedoch erwarten.-->
+### Manipulation checks
 
@@
 
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
@@
 `r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found in Table XX <!-- Nummer noch ergänzen --> in [supplementary material](#SupplementReasonChoice).
+A more detailed list of all reasons can be found online on OSF (<https://osf.io/vnj8x/>).
 
@@
 Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
-The starting point for this was the adapted MLM, we reported before.
+The starting point for this was the adapted MLM, which we have reported before.
 Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
-The third model followed the specification: $$
+The third model followed the specification: 
+$$
 \begin{split}
@@
 \end{split}
-$$ As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+$$ 
+As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
short discussion on self-control and NFC

@@
 However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
+In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
+This is consistant with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].
+However, we did not find an association between NFC and SVs. 
+This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance[@ZernaScheffel2022;@Westbrook2013].
+However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.
 
@@
 On the one hand, we were able to show which factors have an influence on the values, and on the other hand, we were able to show the actual practical relevance of the values.
+
 <!-- Argumentation Corrugator nicht zw.
@@
 Utility: Subjektive Einschätzung der Strategie als Mittel zur Zielerreichung, was eine überschneidung mit dem SV darstellt und außerdem evtl. eine Interaktion von Effektivität und Effort -->
+
 The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block. 

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Analyses_ERED.r
p values of tables

@@ -637,6 +637,8 @@ rownames(df.NV.subj) <- c("Arousal View Neu", "Arousal View Neg", "Arousal Distr
                      "Effort View Neu", "Effort View Neg", "Effort Distraction", "Effort Distancing", "Effort Suppression")
 colnames(df.NV.subj) <- c("$M$", "$SD$", "$W$", "$p$")
 
+df.NV.subj$`$p$`[df.NV.subj$`$p$` == "0.000"] <- "<.001"
+
 # EMG activity
 df.NV.EMG <- data.frame(M = double(), SD = double(), W = double(), p = double())
 
@@ -663,6 +665,7 @@ rownames(df.NV.EMG) <- c("Corrugator View Neu", "Corrugator View Neg", "Corrugat
                           "Levator View Neu", "Levator View Neg", "Levator Distraction", "Levator Distancing", "Levator Suppression")
 colnames(df.NV.EMG) <- c("$M$", "$SD$", "$W$", "$p$")
 
+df.NV.EMG$`$p$`[df.NV.EMG$`$p$` == "0"] <- "<.001"
 #################### STATISTICAL ANALYSES: KONFIRMATORY ANALYSES ############
 
 ######## HYPOTHESIS 1
@@ -708,6 +711,8 @@ SubjArousalView_con <- cbind(SubjArousalView_con,
 colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
 # rename contrast for table
 SubjArousalView_con[1, 1] <- "$View_{neutral} - View_{negative}$"
+
+SubjArousalView_con$`$p$` <- "<.001"
 
 # Figure to visualize arousal ratings
 
@@ -763,6 +768,8 @@ colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$
 # rename contrast for table
 EMGCorrView_con[1, 1] <- "$View_{neutral} - View_{negative}$"
 
+EMGCorrView_con$`$p$` <- "<.001"
+
 # Figure to visualize corrugator activity across view conditions
 
 EMG_view_plot <- EMG_view %>% group_by(ID, block) %>% summarise_at(vars("Corr","Lev"), list(mean))
@@ -814,6 +821,8 @@ EMGLevView_con <- cbind(EMGLevView_con,
[…]

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
corrected reasons for choice
typos in supplement

@@
 
-*WHO-5.* General psychological well-being is assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
-5 Items such as "Over the past 2 weeks I have felt calm and relaxed." are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's $\alpha=.92$)[@Braehler2007].
+*WHO-5.* General psychological well-being was assessed using the WHO-5 scale[@Bech2004; @Braehler2007].
+Five items such as "Over the past 2 weeks I have felt calm and relaxed." are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
+The German version of the scale showed a high internal consistency (Cronbach's $\alpha=.92$)[@Braehler2007].
 
-*Connor-Davidson Resilience Scale.* Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
-10 items such as "I am able to adapt to change." are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's $\alpha=.84$) and a satisfactory retest-reliability of $r_{tt}=.81$ across 6 month[@Sarubin2015].
+*Connor-Davidson Resilience Scale.* Resilience was assessed using the Connor-Davidson Resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015].
+Ten items such as "I am able to adapt to change." are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
+The 10-item version showed a high internal consistency (Cronbach's $\alpha=.84$) and a satisfactory retest-reliability of $r_{tt}=.81$ across 6 months[@Sarubin2015].
 
-*Emotion Regulation Questionnaire.* Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
+*Emotion Regulation Questionnaire.* Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
 The scale has items such as "I keep my emotions to myself" (ERQ-suppression - 4 items) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's $\alpha>.75$) [@Preece2020].
@@
 
-*Implicit Theories Questionnaire.* Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
-4 items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
+*Implicit Theories Questionnaire.* Implicit theories of willpower in emotional control were assessed using the Implicit Theories Questionnaire of Bernecker and Job[-@Bernecker2017].
+Four items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
 The questionnaire showed an internal consistency of Cronbach's $\alpha=.87$[@Bernecker2017].
 
-*Need for Cognition Scale.* Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale [@Bless1994].
+*Need for Cognition Scale.* Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale [@Bless1994]. 
 Responses to each item (e.g., "Thinking is not my idea of fun", recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
@@
 
-*Self-Regulation Scale.* As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] is used.
+*Self-Regulation Scale.* As one measure of self-control, the Self-Regulation Scale (SRS)[@Schwarzer1999] was used.
 The scale has 10 items (e.g., "It is difficult for me to suppress thoughts that interfere with what I need to do.", recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency [Cronbach's $\alpha>.80$; @Schwarzer1999].
+It has high internal consistency (Cronbach's $\alpha>.80$)[@Schwarzer1999].
 
-*Brief Self-Control Scale.* As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] is used.
+*Brief Self-Control Scale.* As a second measure of self-control, the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011] was used.
 It comprises 13 items (e.g., "I am good at resisting temptations") with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's $\alpha=.81$)[@Sproesser2011] .
+The scale shows acceptable internal consistency (Cronbach's $\alpha=.81$)[@Sproesser2011].
 
-*Barratt Impulsiveness Scale.* As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] is used.
+*Barratt Impulsiveness Scale.* As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] was used.
 Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
@@
 
-*Attentional Control Scale.* Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
+*Attentional Control Scale.* Attentional control was measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
@@
   escape = FALSE,
-  placement = "H") 
+  placement = "H",
+  digits = 3) 
 ```
@@
   escape = FALSE,
-  placement = "H")
+  placement = "H",
+  digits = 3)
 
@@
 
-``` {r SupplFigArousalView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings of the active viewing conditions vizalized as boxplots.
+``` {r SupplFigArousalView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings of the active viewing conditions visualized as boxplots.
 Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
@@
 
-``` {r SupplFigCorrView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV during the active viewing conditions, vizalized as boxplots.
+``` {r SupplFigCorrView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV during the active viewing conditions, visualized as boxplots.
 Dots represent individual Corrugator activity measures placed in 150 quantiles.", fig.pos="H"}
@@
 
-``` {r SupplFigLevView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV during the active viewing conditions, vizalized as boxplots.
+``` {r SupplFigLevView, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV during the active viewing conditions, visualized as boxplots.
 Dots represent individual Levator activity measures placed in 150 quantiles.", fig.pos="H"}
@@
   placement = "H",
-  font_size = "footnotesize"
+  font_size = "footnotesize",
+  digits = 3
   )
@@
 
-``` {r SupplFigArousalReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings vizalized as boxplots.
+``` {r SupplFigArousalReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings visualized as boxplots.
 Dots represent individual effort ratings placed in 150 quantiles.", fig.pos="H"}
@@
 
-``` {r SupplFigCorrReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV vizalized as boxplots.
+``` {r SupplFigCorrReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Corrugator activity in mV visualized as boxplots.
 Dots represent individual Levatorr activity measures placed in 150 quantiles.", fig.pos="H"}
@@
 
-``` {r SupplFigLevReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV vizalized as boxplots.
+``` {r SupplFigLevReg, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Levator activity in mV visualized as boxplots.
 Dots represent individual Levator activity measures placed in 150 quantiles.", fig.pos="H"}
@@
 ```
-\newpage
-
-## Reasons for decision made by the participants in the last regulation block
 
@@
   escape = FALSE,
-  placement = "H")
+  placement = "H",
+  digits = 3)
 ```

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Analyses_ERED.r
p value

@@ -637,7 +637,7 @@ rownames(df.NV.subj) <- c("Arousal View Neu", "Arousal View Neg", "Arousal Distr
                      "Effort View Neu", "Effort View Neg", "Effort Distraction", "Effort Distancing", "Effort Suppression")
 colnames(df.NV.subj) <- c("$M$", "$SD$", "$W$", "$p$")
 
-df.NV.subj$`$p$`[df.NV.subj$`$p$` == "0.000"] <- "<.001"
+df.NV.subj$`$p$`[df.NV.subj$`$p$` == "0"] <- "<.001"
 
 # EMG activity
 df.NV.EMG <- data.frame(M = double(), SD = double(), W = double(), p = double())

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
discussion on Corrugator as predictor of SVs

@@
 Overall, there was evidence to support hypotheses H1 to H5.
-It was nevertheless surprising that the strategy suppression showed on average the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
+It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
 In the case of the EEG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly.
@@
 
-<!-- Argumentation Corrugator nicht zw.
-Lvl unterschiedlich, aber trotzdem einfluss, weil man da eine relativ direkte Rückmeldung hat + Levator eher nicht -> alle Bilder negativ aber nur einige eklig, wenn man also nur diese Bilder reinnimmt, wird vielleicht Levator signifikant;
+As a predictor of ER effectiveness, *corrugator* activity showed a significant association with SVs, but not *levator* activity or subjective arousal.
+With regard to the EMG measures, this could be because all the pictures we used were negative, i.e.
+elicited *corrugator* activity, but only a small proportion of the pictures were perceived as disgusting and thus elicited relatively specific *levator* activity.
+However, *corrugator* activity did not differ significantly between ER strategies, but was still associated with SVs. 
+One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current stragey, much more direct than, for example, the subjective arousal rating at the end of each experimental block.
+
+<!--  
 Effort Ergebnisse bestätigen ESER Paper, dass man nach Effort-Minimierung strebt;

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
short discussion on predictors of SVs

@@
 Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)` % of variance in SVs.
+Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
 However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
@@
 On the one hand, we were able to show which factors have an influence on the values, and on the other hand, we were able to show the actual practical relevance of the values. 
-
 As a predictor of ER effectiveness, *corrugator* activity showed a significant association with SVs, but not *levator* activity or subjective arousal.
@@
 However, *corrugator* activity did not differ significantly between ER strategies, but was still associated with SVs. 
-One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current stragey, much more direct than, for example, the subjective arousal rating at the end of each experimental block.
-
-<!--  
-Effort Ergebnisse bestätigen ESER Paper, dass man nach Effort-Minimierung strebt;
-Utility: Subjektive Einschätzung der Strategie als Mittel zur Zielerreichung, was eine überschneidung mit dem SV darstellt und außerdem evtl. eine Interaktion von Effektivität und Effort -->
+One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current strategy, much more direct than, for example, the subjective arousal rating at the end of each experimental block.
+Furthermore, the finding that effort is associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies[@Scheffel2021].
+Finally, the subjective utility ratings showed the greatest explanation for the variance in the SVs.
+This relationship is highly plausible as it involves individuals assessing the utility of the strategy as a means of achieving external and internal regulatory goals.
+This is likely to overlap with subjective values - some literature argues that utility and subjective values are the same thing[@Schultz2015].
+However, this is contradicted by our data, as subjective utility could only explain `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of the variance in SVs.
 

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

@@
 \hypertarget{manipulation-checks}{%
-\subsubsection{\texorpdfstring{Manipulation checks }{Manipulation checks }}\label{manipulation-checks}}
+\subsubsection{Manipulation checks}\label{manipulation-checks}}
 
@@
 Descriptive values of each predictor for each condition can be found in Table \ref{tab:TabDescr}.
-We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.88 \times 10^{48} \pm 5.95\%\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.21 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 260.22\)).
+We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.76 \times 10^{48}\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.05 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 251.32\)).
 Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \ref{tab:SupplEffectArousalView} to @ref(tab:SupplEffectLevView and Figures \ref{fig:SupplFigArousalView} to \ref{fig:SupplFigLevView} in the {[}supplement{]}).
@@
 
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
-We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 156.92\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.70 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
+To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
+We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 157.74\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.82 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
 For detailed information on post-hoc contrasts, please see Tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and Figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
@@
 To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.76 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
+We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.77 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
 Post-hoc contrasts showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
@@
 24.40\% stated they chose the strategy that was most effective and 11.80\% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found in Table XX in \protect\hyperlink{SupplementReasonChoice}{supplementary material}.
+A more detailed list of all reasons can be found online on OSF (\url{https://osf.io/vnj8x/}).
 
@@
 Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported\textsuperscript{29,34,69}, we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
-The starting point for this was the adapted MLM, we reported before.
+The starting point for this was the adapted MLM, which we have reported before.
 Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
-The third model followed the specification: \[
+The third model followed the specification:
+\[
 \begin{split}
@@
 \end{split}
-\] As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
+\]
+As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.024\), 95\% CI \([0.001, 0.048]\), \(t(97.97) = 2.04\), \(p = .044\)).
@@
 
-The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
-We adapted et al.'s\textsuperscript{29} Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order.
+The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
+We adapted Westbrook et al.'s\textsuperscript{29} Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order.
 The new paradigm was tested on an \emph{n}-back task\textsuperscript{34} and a classic ER paradigm.
-The latter was completed by \(N=120\) participants.
+The latter was goal of the present study and completed by \(N=120\) participants.
 As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
@@
 Overall, there was evidence to support hypotheses H1 to H5.
+It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest \emph{corrugator} activity, the lowest effort ratings and the highest utility ratings.
+In the case of the EEG measurement, this could be due to the fact that the result of the implementation of the instructions (``Maintain a neutral facial expression'') is measured directly.
+This also indicates why the required effort is the lowest.
+The direct instruction to implement the strategy reduces the complexity of the generation process.
+By comparison, distancing increases the complexity, for example, because it requires a distanced reappraisal of the stimulus.
+Ultimately, these two aspects are expressed in terms of greater utility: The implementation of the instructions requires comparatively less effort.
+In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
+In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess the utility of the strategies.
 
@@
 Subjective effort, utility, and \emph{corrugator} muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining 15.5 percent of variance in SVs.
+Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining 15.5\% of variance in SVs.
 However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
+In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
+This is consistant with the literature, which has already reported correlations between self-control and demand avoidance\textsuperscript{69}.
+However, we did not find an association between NFC and SVs.
+This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance\textsuperscript{29,34}.
+However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.
 
@@
 We are confident that we have achieved this with the present paradigm.
-On the one hand, we were able to show which factors have an influence the values, and on the other hand, we were able to show the actual practical relevance of the values.
+On the one hand, we were able to show which factors have an influence on the values, and on the other hand, we were able to show the actual practical relevance of the values.
+As a predictor of ER effectiveness, \emph{corrugator} activity showed a significant association with SVs, but not \emph{levator} activity or subjective arousal.
+With regard to the EMG measures, this could be because all the pictures we used were negative, i.e.~elicited \emph{corrugator} activity, but only a small proportion of the pictures were perceived as disgusting and thus elicited relatively specific \emph{levator} activity.
+However, \emph{corrugator} activity did not differ significantly between ER strategies, but was still associated with SVs.
+One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current strategy, much more direct than, for example, the subjective arousal rating at the end of each experimental block.
+Furthermore, the finding that effort is associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies\textsuperscript{22}.
+Finally, the subjective utility ratings showed the greatest explanation for the variance in the SVs.
+This relationship is highly plausible as it involves individuals assessing the utility of the strategy as a means of achieving external and internal regulatory goals.
+This is likely to overlap with subjective values - some literature argues that utility and subjective values are the same thing\textsuperscript{75}.
+However, this is contradicted by our data, as subjective utility could only explain 15.5\% of the variance in SVs.
+
 The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block.
@@
 This may be because in laboratory studies the choice options are often predetermined by the experimental design\textsuperscript{20--22}.
-Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life, in previous studies.
-Even there, however, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{75}, Millgram et al.\textsuperscript{76}, Wilms et al.\textsuperscript{72}), although covering a large part of the process of emotion generation\textsuperscript{2}.
+Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life in previous studies.
+Even there, however, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{76}, Millgram et al.\textsuperscript{77}, Wilms et al.\textsuperscript{72}), although covering a large part of the process of emotion generation\textsuperscript{2}.
 Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
-To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment\textsuperscript{12,77}.
-This would also capture strategies that are rarely used or even considered maladaptive, such as alcohol consumption or rumination\textsuperscript{78}.
+To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment\textsuperscript{12,78}.
+This would also capture strategies that are rarely used or even considered maladaptive, such as alcohol consumption or rumination\textsuperscript{79}.
 
@@
 If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped\textsuperscript{33}.
-Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback\textsuperscript{33,79--81}.
-This means that studies on ER Choice should consider not only situational factors, but also contextual factors\textsuperscript{80}.
-For example, in a classic ER choice paradigm\textsuperscript{21}, Murphy and Young\textsuperscript{80} showed that strategy choice was significantly influenced by strategy choice and negative affect on the previous trial.
+Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback\textsuperscript{33,80--82}.
+This means that studies on ER Choice should consider not only situational factors, but also contextual factors\textsuperscript{81}.
+For example, in a classic ER choice paradigm\textsuperscript{21}, Murphy and Young\textsuperscript{81} showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
 This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
@@
 
-Knowing, whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
+Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
 However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
-This conclusion cannot be drawn from the present study alone.
-To establish the \emph{trait} nature of a measure, one could for instance resort to latent state trait modeling\textsuperscript{82}, as recently employed by our group in a related context\textsuperscript{30}
+To establish the \emph{trait} nature of a measure, one could for instance resort to latent state trait modeling\textsuperscript{83}, as recently employed by our group in a related context\textsuperscript{30}.
 The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation.
@@
 The ER goals that individuals pursue in a given situation must also be taken into account.
-In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals\textsuperscript{84}.
+In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals\textsuperscript{85}.
 Wilms and colleagues\textsuperscript{72} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
@@
 First, it should be noted that a block design was used.
-This allows for habituation effects of EMG activity within the block.
-However, block designs are common in ER research\textsuperscript{85} and have been used in previous studies\textsuperscript{86}.
+This might have resulted in habituation effects of EMG activity within the block.
+However, block designs are common in ER research\textsuperscript{86} and have been used in previous studies\textsuperscript{87}.
 Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block.
-It is also known that affect labeling can attenuate emotional experience\textsuperscript{87,88}.
+It is known that affect labeling can attenuate emotional experience\textsuperscript{88,89}.
 Therefore, we decided not to conduct ratings after each image.
@@
 However, we chose this amount because, firstly, we have followed the original paradigm of Westbrook\textsuperscript{29}.
-Secondly, it has been shown that, at least in the case of cognitive effort discounting, a lower incentive might even increase participants' sensitivity to effort differences\textsuperscript{89}.
+Secondly, it has been shown that, at least in the case of cognitive effort discounting, a lower incentive might even increase participants' sensitivity to effort differences\textsuperscript{90}.
 In the future, however, it should be investigated how the level of incentives affects subjective values.
@@
 
-In order to cope with changing emotional demands, individuals my flexibly select and apply strategies from their repertoire\textsuperscript{12,13}.
-The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected\textsuperscript{12,84}.
+In order to cope with changing emotional demands, individuals may flexibly select and apply ER strategies from their repertoire\textsuperscript{12,13}.
+The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected\textsuperscript{12,85}.
 The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
-To date, such subjective values hace not been established for ER strategies.
+To date, such subjective values have not been established for ER strategies.
 Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values.
-This allows to investigate in more detail the factors influencing the internal generation of these SVs of ER strategies.
-It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and the effort.
+This further enables to investigate in more detail the factors influencing the internal generation of these subjective values of ER strategies.
+It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and effort.
 Finally, further research is needed to investigate the factors that influence subjective values and whether these values represent habitual use of ER strategies by individuals.
@@
 \& Strobel, A.
-Individual differences in inhibitory control are not related to emotion regulation.
-\emph{PsyArXiv} (2021) doi:\href{https://doi.org/10.31234/osf.io/cd8rx}{10.31234/osf.io/cd8rx}.}
+\href{https://doi.org/10.1037/emo0001135}{Individual differences in inhibitory control are not related to emotion regulation}.
+\emph{Emotion} \textbf{Advance online publication}, (2022).}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Schultz2015}{}}%
+\CSLLeftMargin{75. }%
+\CSLRightInline{Schultz, W. \href{https://doi.org/10.1152/physrev.00023.2014}{Neuronal reward and decision signals: From theories to data}. \emph{Physiological Reviews} \textbf{95}, 853--951 (2015).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-English2017}{}}%
-\CSLLeftMargin{75. }%
+\CSLLeftMargin{76. }%
 \CSLRightInline{English, T., Lee, I.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Millgram2019}{}}%
-\CSLLeftMargin{76. }%
+\CSLLeftMargin{77. }%
 \CSLRightInline{Millgram, Y., Sheppes, G., Kalokerinos, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Koval2020}{}}%
-\CSLLeftMargin{77. }%
+\CSLLeftMargin{78. }%
 \CSLRightInline{Koval, P., Kalokerinos, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Pena-Sarrionandia2015}{}}%
-\CSLLeftMargin{78. }%
+\CSLLeftMargin{79. }%
 \CSLRightInline{Pena-Sarrionandia, A., Mikolajczak, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-AldaoChristensen2015}{}}%
-\CSLLeftMargin{79. }%
+\CSLLeftMargin{80. }%
 \CSLRightInline{Aldao, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Murphy2018}{}}%
-\CSLLeftMargin{80. }%
+\CSLLeftMargin{81. }%
 \CSLRightInline{Murphy, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Sheppes2020}{}}%
-\CSLLeftMargin{81. }%
+\CSLLeftMargin{82. }%
 \CSLRightInline{Sheppes, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Steyer2015}{}}%
-\CSLLeftMargin{82. }%
+\CSLLeftMargin{83. }%
 \CSLRightInline{Steyer, R., Mayer, A., Geiser, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Haines2016}{}}%
-\CSLLeftMargin{83. }%
+\CSLLeftMargin{84. }%
 \CSLRightInline{Haines, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Tamir2016}{}}%
-\CSLLeftMargin{84. }%
+\CSLLeftMargin{85. }%
 \CSLRightInline{Tamir, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Barreiros2019}{}}%
-\CSLLeftMargin{85. }%
+\CSLLeftMargin{86. }%
 \CSLRightInline{Barreiros, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Scheffel2019}{}}%
-\CSLLeftMargin{86. }%
+\CSLLeftMargin{87. }%
 \CSLRightInline{Scheffel, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lieberman2007}{}}%
-\CSLLeftMargin{87. }%
+\CSLLeftMargin{88. }%
 \CSLRightInline{Lieberman, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Torre2018}{}}%
-\CSLLeftMargin{88. }%
+\CSLLeftMargin{89. }%
 \CSLRightInline{Torre, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{89. }%
+\CSLLeftMargin{90. }%
 \CSLRightInline{Bialaszek, W., Marcowski, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{90. }%
+\CSLLeftMargin{91. }%
 \CSLRightInline{Preece, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{91. }%
+\CSLLeftMargin{92. }%
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{92. }%
+\CSLLeftMargin{93. }%
 \CSLRightInline{Fleischhauer, M., Strobel, A.
@@
 
-\emph{WHO-5.} General psychological well-being is assessed using the WHO-5 scale\textsuperscript{45,46}.
-5 Items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The german version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{46}.
-
-\emph{Connor-Davidson Resilience Scale.} Resilience is assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
-10 items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 month\textsuperscript{49}.
-
-\emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression is measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{90}.
+\emph{WHO-5.} General psychological well-being was assessed using the WHO-5 scale\textsuperscript{45,46}.
+Five items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
+The German version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{46}.
+
+\emph{Connor-Davidson Resilience Scale.} Resilience was assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
+Ten items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 months\textsuperscript{49}.
+
+\emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{91}.
 
@@
 
-\emph{Implicit Theories Questionnaire.} Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of\textsuperscript{51}.
-4 items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
+\emph{Implicit Theories Questionnaire.} Implicit theories of willpower in emotional control were assessed using the Implicit Theories Questionnaire of Bernecker and Job\textsuperscript{51}.
+Four items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
 The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{51}.
 
-\emph{Need for Cognition Scale.} Need for Cognition (NFC) is assessed with the 16-item short version of the German NFC scale\textsuperscript{52}.
+\emph{Need for Cognition Scale.} Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale\textsuperscript{52}.
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,91} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{92}.
-
-\emph{Self-Regulation Scale.} As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} is used.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,92} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{93}.
+
+\emph{Self-Regulation Scale.} As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} was used.
 The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency {[}Cronbach's \(\alpha>.80\);\textsuperscript{54}{]}.
-
-\emph{Brief Self-Control Scale.} As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} is used.
+It has high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{54}.
+
+\emph{Brief Self-Control Scale.} As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} was used.
 It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{56} .
-
-\emph{Barratt Impulsiveness Scale.} As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} is used.
+The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{56}.
+
+\emph{Barratt Impulsiveness Scale.} As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} was used.
 Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
@@
 
-\emph{Attentional Control Scale.} Attentional control is measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
+\emph{Attentional Control Scale.} Attentional control was measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
@@
 \midrule
-Arousal View Neu & 26.63 & 39.12 & 0.68 & 0.00\\
-Arousal View Neg & 187.78 & 87.31 & 0.98 & 0.06\\
-Arousal Distraction & 158.13 & 92.49 & 0.97 & 0.01\\
-Arousal Distancing & 168.62 & 95.75 & 0.98 & 0.04\\
-Arousal Suppression & 163.96 & 87.17 & 0.98 & 0.07\\
-Effort View Neu & 18.15 & 27.37 & 0.65 & 0.00\\
-Effort View Neg & 49.40 & 62.26 & 0.74 & 0.00\\
-Effort Distraction & 208.46 & 96.15 & 0.98 & 0.13\\
-Effort Distancing & 158.26 & 99.50 & 0.97 & 0.01\\
-Effort Suppression & 189.80 & 92.34 & 0.98 & 0.12\\
+Arousal View Neu & 26.629 & 39.116 & 0.677 & <.001\\
+Arousal View Neg & 187.778 & 87.308 & 0.979 & 0.057\\
+Arousal Distraction & 158.129 & 92.492 & 0.972 & 0.014\\
+Arousal Distancing & 168.617 & 95.754 & 0.978 & 0.043\\
+Arousal Suppression & 163.957 & 87.165 & 0.980 & 0.073\\
+Effort View Neu & 18.147 & 27.372 & 0.651 & <.001\\
+Effort View Neg & 49.396 & 62.262 & 0.740 & <.001\\
+Effort Distraction & 208.465 & 96.149 & 0.983 & 0.132\\
+Effort Distancing & 158.259 & 99.505 & 0.969 & 0.007\\
+Effort Suppression & 189.800 & 92.338 & 0.983 & 0.123\\
 \bottomrule
@@
 \midrule
-Corrugator View Neu & 0.04 & 6.99 & 0.05 & 0.00\\
-Corrugator View Neg & 1.03 & 7.21 & 0.19 & 0.00\\
-Corrugator Distraction & 0.00 & 7.67 & 0.04 & 0.00\\
-Corrugator Distancing & 0.07 & 3.78 & 0.08 & 0.00\\
-Corrugator Suppression & 0.25 & 1.92 & 0.35 & 0.00\\
-Levator View Neu & 0.09 & 1.84 & 0.38 & 0.00\\
-Levator View Neg & 0.58 & 3.20 & 0.43 & 0.00\\
-Levator Distraction & -0.05 & 1.16 & 0.52 & 0.00\\
-Levator Distancing & -0.03 & 0.92 & 0.48 & 0.00\\
-Levator Suppression & 0.01 & 1.00 & 0.55 & 0.00\\
+Corrugator View Neu & 0.041 & 6.991 & 0.046 & <.001\\
+Corrugator View Neg & 1.030 & 7.213 & 0.194 & <.001\\
+Corrugator Distraction & 0.004 & 7.668 & 0.040 & <.001\\
+Corrugator Distancing & 0.066 & 3.784 & 0.083 & <.001\\
+Corrugator Suppression & 0.246 & 1.924 & 0.354 & <.001\\
+Levator View Neu & 0.090 & 1.838 & 0.384 & <.001\\
+Levator View Neg & 0.580 & 3.198 & 0.429 & <.001\\
+Levator Distraction & -0.050 & 1.157 & 0.520 & <.001\\
+Levator Distancing & -0.027 & 0.917 & 0.481 & <.001\\
+Levator Suppression & 0.010 & 0.996 & 0.554 & <.001\\
 \bottomrule
@@
 \midrule
-$View_{neutral} - View_{negative}$ & -161.15 & 8.06 & 119.00 & -20.00 & 0.00 & $3.22 \times 10^{36}$ & 0.77 & {}[0.72, 1.00]\\
+$View_{neutral} - View_{negative}$ & -161.15 & 8.06 & 119.00 & -20.00 & <.001 & $3.22 \times 10^{36}$ & 0.77 & {}[0.72, 1.00]\\
 \bottomrule
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSubjArousalView} \caption{Subjective arousal ratings of the active viewing conditions vizalized as boxplots.
+\includegraphics[width=\textwidth]{figures/FigSubjArousalView} \caption{Subjective arousal ratings of the active viewing conditions visualized as boxplots.
 Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:SupplFigArousalView}
@@
 \midrule
-$View_{neutral} - View_{negative}$ & -0.27 & 0.05 & 117.00 & -5.27 & 0.00 & $8.67 \times 10^{16}$ & 0.19 & {}[0.10, 1.00]\\
+$View_{neutral} - View_{negative}$ & -0.27 & 0.05 & 117.00 & -5.27 & <.001 & $8.67 \times 10^{16}$ & 0.19 & {}[0.10, 1.00]\\
 \bottomrule
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigCorrView} \caption{Corrugator activity in mV during the active viewing conditions, vizalized as boxplots.
+\includegraphics[width=\textwidth]{figures/FigCorrView} \caption{Corrugator activity in mV during the active viewing conditions, visualized as boxplots.
 Dots represent individual Corrugator activity measures placed in 150 quantiles.}\label{fig:SupplFigCorrView}
@@
 \midrule
-$View_{neutral} - View_{negative}$ & -0.23 & 0.08 & 117.00 & -2.98 & 0.00 & 188.72 & 0.07 & {}[0.01, 1.00]\\
+$View_{neutral} - View_{negative}$ & -0.23 & 0.08 & 117.00 & -2.98 & <.001 & 188.72 & 0.07 & {}[0.01, 1.00]\\
 \bottomrule
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigLevView} \caption{Levator activity in mV during the active viewing conditions, vizalized as boxplots.
+\includegraphics[width=\textwidth]{figures/FigLevView} \caption{Levator activity in mV during the active viewing conditions, visualized as boxplots.
 Dots represent individual Levator activity measures placed in 150 quantiles.}\label{fig:SupplFigLevView}
@@
 \midrule
-$View_{neg} - Distraction$ & 29.65 & 6.68 & 357.00 & 4.44 & 0.00 & 168.48 & 0.05 & {}[0.02, 1.00]\\
-$View_{neg} - Distancing$ & 23.82 & 6.68 & 357.00 & 3.57 & 0.00 & 62.99 & 0.03 & {}[0.01, 1.00]\\
-$View_{neg} - Suppression$ & 19.16 & 6.68 & 357.00 & 2.87 & 0.03 & 1.97 & 0.02 & {}[0.00, 1.00]\\
-$Distraction - Distancing$ & -5.83 & 6.68 & 357.00 & -0.87 & 1.00 & 0.18 & 2.13e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -10.49 & 6.68 & 357.00 & -1.57 & 0.70 & 0.31 & 6.86e-03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -4.66 & 6.68 & 357.00 & -0.70 & 1.00 & 0.14 & 1.36e-03 & {}[0.00, 1.00]\\
+$View_{neg} - Distraction$ & 29.649 & 6.680 & 357.000 & 4.439 & 0.000 & 168.484 & 0.05 & {}[0.02, 1.00]\\
+$View_{neg} - Distancing$ & 23.820 & 6.680 & 357.000 & 3.566 & 0.002 & 62.990 & 0.03 & {}[0.01, 1.00]\\
+$View_{neg} - Suppression$ & 19.161 & 6.680 & 357.000 & 2.869 & 0.026 & 1.965 & 0.02 & {}[0.00, 1.00]\\
+$Distraction - Distancing$ & -5.828 & 6.680 & 357.000 & -0.873 & 1.000 & 0.179 & 2.13e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & -10.488 & 6.680 & 357.000 & -1.570 & 0.704 & 0.309 & 6.86e-03 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & -4.659 & 6.680 & 357.000 & -0.698 & 1.000 & 0.135 & 1.36e-03 & {}[0.00, 1.00]\\
 \bottomrule
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSubjArousalReg} \caption{Subjective arousal ratings vizalized as boxplots.
+\includegraphics[width=\textwidth]{figures/FigSubjArousalReg} \caption{Subjective arousal ratings visualized as boxplots.
 Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:SupplFigArousalReg}
@@
 \midrule
-$View_{neg} - Distraction$ & 0.18 & 0.04 & 351.00 & 4.79 & 0.00 & 21,919.73 & 0.06 & {}[0.03, 1.00]\\
-$View_{neg} - Distancing$ & 0.19 & 0.04 & 351.00 & 5.09 & 0.00 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
-$View_{neg} - Suppression$ & 0.21 & 0.04 & 351.00 & 5.67 & 0.00 & $1.84 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
-$Distraction - Distancing$ & 0.01 & 0.04 & 351.00 & 0.30 & 1.00 & $3.77 \times 10^{-2}$ & 2.61e-04 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.03 & 0.04 & 351.00 & 0.88 & 1.00 & $8.02 \times 10^{-2}$ & 2.21e-03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.02 & 0.04 & 351.00 & 0.58 & 1.00 & $4.79 \times 10^{-2}$ & 9.51e-04 & {}[0.00, 1.00]\\
+$View_{neg} - Distraction$ & 0.178 & 0.037 & 351.000 & 4.788 & 0.000 & 21,919.73 & 0.06 & {}[0.03, 1.00]\\
+$View_{neg} - Distancing$ & 0.189 & 0.037 & 351.000 & 5.091 & 0.000 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
+$View_{neg} - Suppression$ & 0.210 & 0.037 & 351.000 & 5.669 & 0.000 & $1.84 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
+$Distraction - Distancing$ & 0.011 & 0.037 & 351.000 & 0.303 & 1.000 & $3.77 \times 10^{-2}$ & 2.61e-04 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & 0.033 & 0.037 & 351.000 & 0.881 & 1.000 & $8.02 \times 10^{-2}$ & 2.21e-03 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 0.021 & 0.037 & 351.000 & 0.578 & 1.000 & $4.79 \times 10^{-2}$ & 9.51e-04 & {}[0.00, 1.00]\\
 \bottomrule
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigCorrReg} \caption{Corrugator activity in mV vizalized as boxplots.
+\includegraphics[width=\textwidth]{figures/FigCorrReg} \caption{Corrugator activity in mV visualized as boxplots.
 Dots represent individual Levatorr activity measures placed in 150 quantiles.}\label{fig:SupplFigCorrReg}
@@
 \midrule
-$View_{neg} - Distraction$ & 0.34 & 0.05 & 351.00 & 6.73 & 0.00 & $2.02 \times 10^{11}$ & 0.11 & {}[0.07, 1.00]\\
-$View_{neg} - Distancing$ & 0.28 & 0.05 & 351.00 & 5.66 & 0.00 & $3.99 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
-$View_{neg} - Suppression$ & 0.32 & 0.05 & 351.00 & 6.37 & 0.00 & $8.60 \times 10^{10}$ & 0.10 & {}[0.06, 1.00]\\
-$Distraction - Distancing$ & -0.05 & 0.05 & 351.00 & -1.07 & 1.00 & 0.22 & 3.26e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -0.02 & 0.05 & 351.00 & -0.36 & 1.00 & $3.91 \times 10^{-2}$ & 3.70e-04 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.04 & 0.05 & 351.00 & 0.71 & 1.00 & $9.86 \times 10^{-2}$ & 1.44e-03 & {}[0.00, 1.00]\\
+$View_{neg} - Distraction$ & 0.336 & 0.050 & 351.000 & 6.731 & 0.000 & $2.02 \times 10^{11}$ & 0.11 & {}[0.07, 1.00]\\
+$View_{neg} - Distancing$ & 0.282 & 0.050 & 351.000 & 5.659 & 0.000 & $3.99 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
+$View_{neg} - Suppression$ & 0.318 & 0.050 & 351.000 & 6.370 & 0.000 & $8.60 \times 10^{10}$ & 0.10 & {}[0.06, 1.00]\\
+$Distraction - Distancing$ & -0.053 & 0.050 & 351.000 & -1.072 & 1.000 & 0.22 & 3.26e-03 & {}[0.00, 1.00]\\
+$Distraction - Suppression$ & -0.018 & 0.050 & 351.000 & -0.361 & 1.000 & $3.91 \times 10^{-2}$ & 3.70e-04 & {}[0.00, 1.00]\\
+$Distancing - Suppression$ & 0.035 & 0.050 & 351.000 & 0.711 & 1.000 & $9.86 \times 10^{-2}$ & 1.44e-03 & {}[0.00, 1.00]\\
 \bottomrule
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigLevReg} \caption{Levator activity in mV vizalized as boxplots.
+\includegraphics[width=\textwidth]{figures/FigLevReg} \caption{Levator activity in mV visualized as boxplots.
 Dots represent individual Levator activity measures placed in 150 quantiles.}\label{fig:SupplFigLevReg}
 \end{figure}
-\newpage
-
-\hypertarget{reasons-for-decision-made-by-the-participants-in-the-last-regulation-block}{%
-\subsection{Reasons for decision made by the participants in the last regulation block}\label{reasons-for-decision-made-by-the-participants-in-the-last-regulation-block}}
 
@@
 \midrule
-Intercept & $8.03 \times 10^{-1}$ & 0.01 & 0.00 &  & 0.11\\
-Effort & $-6.93 \times 10^{-4}$ & 0.00 & 0.00 & 0.04 & \\
-Utility & $1.44 \times 10^{-3}$ & 0.00 & 0.00 & 0.20 & \\
-Corrugator activity & $7.54 \times 10^{-3}$ & 0.00 & 0.03 & 0.00 & \\
-Self-Control & $2.44 \times 10^{-2}$ & 0.01 & 0.04 & 0.00 & \\
-NFC & $7.58 \times 10^{-4}$ & 0.00 & 0.44 & 0.00 & \\
+Intercept & $8.03 \times 10^{-1}$ & 0.011 & 0.000 &  & 0.112\\
+Effort & $-6.93 \times 10^{-4}$ & 0.000 & 0.000 & 0.036 & \\
+Utility & $1.44 \times 10^{-3}$ & 0.000 & 0.000 & 0.197 & \\
+Corrugator activity & $7.54 \times 10^{-3}$ & 0.004 & 0.034 & 0.001 & \\
+Self-Control & $2.44 \times 10^{-2}$ & 0.012 & 0.044 & 0.002 & \\
+NFC & $7.58 \times 10^{-4}$ & 0.001 & 0.436 & 0.002 & \\
 \bottomrule

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added "the"
removed 2 lines and added one

@@
 The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
-The latter was goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
+The latter was the goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
 As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
@@
 Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
-We believe that there was a good basis on which individual SVs of ER strategies could be determined.
-Overall, there was evidence to support hypotheses H1 to H5.
 It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
@@
 In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess the utility of the strategies.
+Since these manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.
 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
changed EEG to EMG

@@
 It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
-In the case of the EEG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly.
+In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly.
 This also indicates why the required effort is the lowest. 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
removed for example
replaced "distanced" with "impersonal"
switched 2 sentences

@@
 In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly. 
-This also indicates why the required effort is the lowest. 
-The direct instruction to implement the strategy reduces the complexity of the generation process.
-By comparison, distancing increases the complexity, for example, because it requires a distanced reappraisal of the stimulus.
+The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
+By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
 Ultimately, these two aspects are expressed in terms of greater utility: The implementation of the instructions requires comparatively less effort. 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
removed double effort sentence
changed wording

@@
 By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
-Ultimately, these two aspects are expressed in terms of greater utility: The implementation of the instructions requires comparatively less effort. 
+Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy. 
 In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
-In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess the utility of the strategies.
-Since these manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.
+In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
+Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.
 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added lil info about h7

@@
 Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
+Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
 However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added since
corrected typo

@@
 Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
-However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
+However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
 In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
-This is consistant with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].
+This is consistent with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].
 However, we did not find an association between NFC and SVs. 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
made 2 "Corrugator" lowercase like the others

@@
   df.descr,
-  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
+  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.",
   escape = FALSE,
@@
 $$ 
-As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
removed comment (we talked about suppression)
added "positive"

@@
 This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020].
-<!-- evtl.
-Einwand warum Suppression am erfolgreichsten war -->
 Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
@@
 However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
-In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
+In a subsequent exploratory analyses, we found a positive association between individual SVs and self-control.
 This is consistent with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
made wording less definitive
changed "explanation of" to "explained"
added its

@@
 This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance[@ZernaScheffel2022;@Westbrook2013].
-However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.
+However, these were all cognitive tasks. The role of NFC in affective tasks is not well known yet.
 
@@
 Furthermore, the finding that effort is associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies[@Scheffel2021].
-Finally, the subjective utility ratings showed the greatest explanation for the variance in the SVs.
+Finally, the subjective utility ratings showed the greatest explained variance in the SVs.
 This relationship is highly plausible as it involves individuals assessing the utility of the strategy as a means of achieving external and internal regulatory goals.
@@
 This may be because in laboratory studies the choice options are often predetermined by the experimental design[@Sheppes2011;@Sheppes2014;@Scheffel2021].
-Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life in previous studies.
+Therefore, attempts have been made to investigate ER choice and its influencing factors in everyday life in previous studies.
 Even there, however, certain strategies were often prescribed (for example studies, see English et al.[-@English2017], Millgram et al.[-@Millgram2019], Wilms et al.[-@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
removed comma

@@
 Therefore, attempts have been made to investigate ER choice and its influencing factors in everyday life in previous studies.
-Even there, however, certain strategies were often prescribed (for example studies, see English et al.[-@English2017], Millgram et al.[-@Millgram2019], Wilms et al.[-@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].
+Even there, however, certain strategies were often prescribed (for example studies see English et al.[-@English2017], Millgram et al.[-@Millgram2019], Wilms et al.[-@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].
 Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added are

@@
 To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment[@Aldao2015;@Koval2020].
-This would also capture strategies that are rarely used or even considered maladaptive, such as alcohol consumption or rumination[@Pena-Sarrionandia2015].
+This would also capture strategies that are rarely used or are even considered maladaptive, such as alcohol consumption or rumination[@Pena-Sarrionandia2015].
 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added CAD
changed subjective values to SVs

@@
 This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
-Our newly developed paradigm also makes an important contribution here.
-The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of subjective values.
+Our newly developed CAD paradigm also makes an important contribution here.
+The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of SVs.
 That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
changed belief to believe
removed comma (bc British)

@@
 As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
-We belief that these goals, factors, and demands also influence individual SVs of ER strategies.
+We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
 Our data presented in this study support this idea.
-However, this also implies that SVs should differ according to situational factors (e.g., stimulus intensity).
+However, this also implies that SVs should differ according to situational factors (e.g. stimulus intensity).
 The ER goals that individuals pursue in a given situation must also be taken into account.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
changed subjective values to SVs
put 2 sentences into 1

@@
 Therefore, SVs may vary when different reference strategies are used.
-It is conceivable that subjective values are likely to be highly correlated in situations with similar demands and goals. 
+It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals. 
 They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
@@
 Third, a major limitation is that participants had to use three prescribed ER strategies.
-It may be that some of the participants were not used to any of these strategies in everyday life.
-So it could be that none of the strategies has a really high subjective value for the person.
+It may be that some of the participants were not used to any of these strategies in everyday life, so none of the strategies actually had a high subjective value for them.
 However, the strategies selected for attentional deployment, cognitive change, and response modulation have been shown meta-analytically to be most effective[@Webb2012]. 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
removed space before currency symbol

@@
 
-Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
+Fourth, the highest value during the discounting paradigm was set to 2€ as fixed value.
 Participants were asked to imagine that this was the amount of money they would receive if they repeated this strategy.
-Thus, 2 € could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
+Thus, 2€ could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
 However, we chose this amount because, firstly, we have followed the original paradigm of Westbrook[@Westbrook2013].

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
made 2 sentences into 1

@@
 Thus, 2€ could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
-However, we chose this amount because, firstly, we have followed the original paradigm of Westbrook[@Westbrook2013].
-Secondly, it has been shown that, at least in the case of cognitive effort discounting, a lower incentive might even increase participants' sensitivity to effort differences[@Bialaszek2017].
+However, we chose this amount because, firstly, we followed the original paradigm of Westbrook[@Westbrook2013], and secondly, it has been shown in the context of cognitive effort discounting, that a lower incentive increases participants' sensitivity to effort differences[@Bialaszek2017].
 In the future, however, it should be investigated how the level of incentives affects subjective values.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

@@
 {}{\PatchFailed}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography\newline\indent Word count: about 9000}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography\newline\indent Word count: 9432}
 \usepackage{lineno}
@@
 \begin{longtable}{rccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.}\\
+\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.}\\
 \toprule
@@
 \]
-As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
+As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.024\), 95\% CI \([0.001, 0.048]\), \(t(97.97) = 2.04\), \(p = .044\)).
@@
 The new paradigm was tested on an \emph{n}-back task\textsuperscript{34} and a classic ER paradigm.
-The latter was goal of the present study and completed by \(N=120\) participants.
+The latter was the goal of the present study and completed by \(N=120\) participants.
 As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
@@
 Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
-We believe that there was a good basis on which individual SVs of ER strategies could be determined.
-Overall, there was evidence to support hypotheses H1 to H5.
 It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest \emph{corrugator} activity, the lowest effort ratings and the highest utility ratings.
-In the case of the EEG measurement, this could be due to the fact that the result of the implementation of the instructions (``Maintain a neutral facial expression'') is measured directly.
-This also indicates why the required effort is the lowest.
-The direct instruction to implement the strategy reduces the complexity of the generation process.
-By comparison, distancing increases the complexity, for example, because it requires a distanced reappraisal of the stimulus.
-Ultimately, these two aspects are expressed in terms of greater utility: The implementation of the instructions requires comparatively less effort.
+In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions (``Maintain a neutral facial expression'') is measured directly.
+The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
+By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
+Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy.
 In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
-In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess the utility of the strategies.
+In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
+Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.
 
@@
 Subjective effort, utility, and \emph{corrugator} muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining 15.5\% of variance in SVs.
-However, individual SVs did not show associations with self-reported ER flexibility, we therefore found no evidence for hypothesis H7.
-In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
-This is consistant with the literature, which has already reported correlations between self-control and demand avoidance\textsuperscript{69}.
+Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining 15.5\% of variance in SVs.
+However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
+In a subsequent exploratory analyses, we found a positive association between individual SVs and self-control.
+This is consistent with the literature, which has already reported correlations between self-control and demand avoidance\textsuperscript{69}.
 However, we did not find an association between NFC and SVs.
 This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance\textsuperscript{29,34}.
-However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.
+However, these were all cognitive tasks. The role of NFC in affective tasks is not well known yet.
 
@@
 Furthermore, the finding that effort is associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies\textsuperscript{22}.
-Finally, the subjective utility ratings showed the greatest explanation for the variance in the SVs.
+Finally, the subjective utility ratings showed the greatest explained variance in the SVs.
 This relationship is highly plausible as it involves individuals assessing the utility of the strategy as a means of achieving external and internal regulatory goals.
@@
 This may be because in laboratory studies the choice options are often predetermined by the experimental design\textsuperscript{20--22}.
-Therefore, attempts have been made to investigate ER choice and influencing factors in everyday life in previous studies.
-Even there, however, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{76}, Millgram et al.\textsuperscript{77}, Wilms et al.\textsuperscript{72}), although covering a large part of the process of emotion generation\textsuperscript{2}.
+Therefore, attempts have been made to investigate ER choice and its influencing factors in everyday life in previous studies.
+Even there, however, certain strategies were often prescribed (for example studies see English et al.\textsuperscript{76}, Millgram et al.\textsuperscript{77}, Wilms et al.\textsuperscript{72}), although covering a large part of the process of emotion generation\textsuperscript{2}.
 Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
 To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment\textsuperscript{12,78}.
-This would also capture strategies that are rarely used or even considered maladaptive, such as alcohol consumption or rumination\textsuperscript{79}.
+This would also capture strategies that are rarely used or are even considered maladaptive, such as alcohol consumption or rumination\textsuperscript{79}.
 
@@
 As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies\textsuperscript{21}.
-We belief that these goals, factors, and demands also influence individual SVs of ER strategies.
+We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
 Our data presented in this study support this idea.
-However, this also implies that SVs should differ according to situational factors (e.g., stimulus intensity).
+However, this also implies that SVs should differ according to situational factors (e.g.~stimulus intensity).
 The ER goals that individuals pursue in a given situation must also be taken into account.
@@
 Therefore, SVs may vary when different reference strategies are used.
-It is conceivable that subjective values are likely to be highly correlated in situations with similar demands and goals.
+It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals.
 They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires\textsuperscript{9}.
@@
 Third, a major limitation is that participants had to use three prescribed ER strategies.
-It may be that some of the participants were not used to any of these strategies in everyday life.
-So it could be that none of the strategies has a really high subjective value for the person.
+It may be that some of the participants were not used to any of these strategies in everyday life, so none of the strategies actually had a high subjective value for them.
 However, the strategies selected for attentional deployment, cognitive change, and response modulation have been shown meta-analytically to be most effective\textsuperscript{4}.
@@
 
-Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
+Fourth, the highest value during the discounting paradigm was set to 2€ as fixed value.
 Participants were asked to imagine that this was the amount of money they would receive if they repeated this strategy.
-Thus, 2 € could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
-However, we chose this amount because, firstly, we have followed the original paradigm of Westbrook\textsuperscript{29}.
-Secondly, it has been shown that, at least in the case of cognitive effort discounting, a lower incentive might even increase participants' sensitivity to effort differences\textsuperscript{90}.
+Thus, 2€ could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
+However, we chose this amount because, firstly, we followed the original paradigm of Westbrook\textsuperscript{29}, and secondly, it has been shown in the context of cognitive effort discounting, that a lower incentive increases participants' sensitivity to effort differences\textsuperscript{90}.
 In the future, however, it should be investigated how the level of incentives affects subjective values.
@@
 Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values.
-This further enables to investigate in more detail the factors influencing the internal generation of these subjective values of ER strategies.
+This further enables to investigate the factors influencing the internal generation of these subjective values of ER strategies in more detail.
 It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and effort.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
knitted document
knitted doc

@@
  SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $\mathrm{BF}_{\textrm{10}} = 1.62   \times 10^{21}$).
- Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<0.001$), subjective effort ($t(5, 618.96)=-13.98$,    $p<.001$, $f^2=0.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=0.155$).
- SVs were further associated with self-control ($t(97.97)=2.04$, $p=.044$, $f^2=0.002$), but not with flexible ER. 
+ Further, SVs were associated with Corrugator activity ($t(5, 618.96)=2.09$, $p=.037$, $f^2<.001$), subjective effort ($t(5, 618.96)=-13.98$,    $p<.001$, $f^2=.035$), and self-reported utility ($t(5, 618.96)=29.49$, $p<.001$, $f^2=.155$).
+ SVs were further associated with self-control ($t(97.97)=2.04$, $p=.044$, $f^2=.002$), but not with flexible ER. 
  With our paradigm, we were able to determine subjective values. 
@@
 keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography"
-wordcount         : "about 9000"
+wordcount         : "9432"
 bibliography      : ["ER_ED.bib"]

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

@@
 SVs significantly predicted later choice for an ER strategy (\(\chi^2(4, \textit{n} = 119)=115.40\), \(p<.001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
-Further, SVs were associated with Corrugator activity (\(t(5, 618.96)=2.09\), \(p=.037\), \(f^2<0.001\)), subjective effort (\(t(5, 618.96)=-13.98\), \(p<.001\), \(f^2=0.035\)), and self-reported utility (\(t(5, 618.96)=29.49\), \(p<.001\), \(f^2=0.155\)).
-SVs were further associated with self-control (\(t(97.97)=2.04\), \(p=.044\), \(f^2=0.002\)), but not with flexible ER.
+Further, SVs were associated with Corrugator activity (\(t(5, 618.96)=2.09\), \(p=.037\), \(f^2<.001\)), subjective effort (\(t(5, 618.96)=-13.98\), \(p<.001\), \(f^2=.035\)), and self-reported utility (\(t(5, 618.96)=29.49\), \(p<.001\), \(f^2=.155\)).
+SVs were further associated with self-control (\(t(97.97)=2.04\), \(p=.044\), \(f^2=.002\)), but not with flexible ER.
 With our paradigm, we were able to determine subjective values.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
created supplement

@@
 ---
-title: "Supplement"
-author: "Christoph Scheffel"
-date: "2023-02-16"
-output: html_document
+title             : "Supplementary Material for the Registered Report: Estimating individual subjective values of emotion regulation strategies"
+shorttitle        : "Supplementary Material"
+author:
+  - name          : "Christoph Scheffel"
+    orcid         : "0000-0001-5963-9229"
+    affiliation   : "1"
+    corresponding : yes
+    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
+    email         : "christoph_scheffel@tu-dresden.de"
+    equal_contrib : yes
+    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - Conceptualization
+      - Methodology
+      - Funding acquisition
+      - Formal analysis
+      - Investigation
+      - Project administration
+      - Software
+      - Visualization
+      - Writing - original draft preparation
+      - Writing - review & editing
+  - name          : "Josephine Zerna"
+    orcid         : "0000-0003-2892-884X"
+    affiliation   : "1"
+    equal_contrib : yes
+    role          :
+      - Conceptualization
+      - Methodology
+      - Funding acquisition
+      - Investigation
+      - Project administration
+      - Software
+      - Visualization
+      - Writing - review & editing
+  - name          : "Anne Gärtner"
+    orcid         : "0000-0003-4296-963X"
+    affiliation   : "1"
+    role          :
+      - Formal analysis
+      - Writing - review & editing
+  - name          : "Denise Dörfel"
+    orcid         : "0000-0002-5632-419X"
+    affiliation   : "1,2"
+    role          :
+      - Conceptualization
+      - Writing - review & editing
+  - name          : "Alexander Strobel"
+    orcid         : "0000-0002-9426-5397"
+    affiliation   : "1"
+    role          :
+      - Conceptualization
+      - Methodology
+      - Writing - review & editing 
+affiliation       :
+  - id            : "1"
+    institution   : "Chair of Differential and Personality Psychology, Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
+  - id            : "2"
+    institution   : "Center for Information Services and High Performance Computing, Technische Universität Dresden, 01069 Dresden, Germany"
+authornote        :
+keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography"
+wordcount         : "9432"
+bibliography      : ["ER_ED.bib"]
+floatsintext      : yes
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
+csl               : nature.csl
+header-includes   :
+    - \usepackage{booktabs}
+    - \usepackage{longtable}
+    - \usepackage{array}
+    - \usepackage{multirow}
+    - \usepackage{wrapfig}
+    - \usepackage{float}
+    - \usepackage{colortbl}
+    - \usepackage{pdflscape}
+    - \usepackage{tabu}
+    - \usepackage{threeparttable}
+    - \usepackage{threeparttablex}
+    - \usepackage[normalem]{ulem}
+    - \usepackage{makecell}
+    - \usepackage{xcolor}
+    - \usepackage{setspace}\doublespacing
+    - \usepackage[final]{pdfpages}
+    - \usepackage{chngcntr}
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(out.width = "\\textwidth")
 
@@
 
-# Supplementary Material {#SupplementaryMaterial}
+## Design Table {#DesignTable}
+
+\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
+\newpage
+
+## Stimuli used in ER paradigm
 
 \includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
+
+\renewcommand\thesection{\Alph{section}}
 \counterwithin{figure}{section}

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Supplement.tex
created supplement

--- 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
@@
 \hypersetup{
-  pdftitle={Estimating individual subjective values of emotion regulation strategies},
+  pdftitle={Supplementary Material for the Registered Report: Estimating individual subjective values of emotion regulation strategies},
   pdfauthor={Christoph Scheffel,1, Josephine Zerna,1, Anne Gärtner1, Denise Dörfel1,2, \& Alexander Strobel1},
@@
 
-\title{Estimating individual subjective values of emotion regulation strategies}
+\title{Supplementary Material for the Registered Report: Estimating individual subjective values of emotion regulation strategies}
 \author{Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Josephine Zerna\textsuperscript{$\dagger{}$,1}, Anne Gärtner\textsuperscript{1}, Denise Dörfel\textsuperscript{1,2}, \& Alexander Strobel\textsuperscript{1}}
@@
 
-\shorttitle{Subjective values of emotion regulation strategies}
+\shorttitle{Supplementary Material}
 
@@
 
-\abstract{%
-Individuals have a repertoire of emotion regulation (ER) strategies at their disposal, which they can use more or less flexibly.
-In ER flexibility research, strategies that facilitate goal achievement are considered adaptive and therefore are subjectively valuable.
-Individuals are motivated to reduce their emotional arousal effectively and to avoid cognitive effort.
-Perceived costs of ER strategies in the form of effort, however, are highly subjective.
-Subjective values (SVs) should therefore represent a trade-off between effectiveness and subjectively required cognitive effort.
-However, SVs of ER strategies have not been determined so far.
-We present a new paradigm for quantifying individual SVs of ER strategies by offering monetary values for ER strategies in an iterative process.
-\(N=120\) participants first conducted an ER paradigm with the strategies distraction, distancing, and suppression.
-Afterwards, individual SVs were determined using the new CAD paradigm.
-SVs significantly predicted later choice for an ER strategy (\(\chi^2(4, \textit{n} = 119)=115.40\), \(p<.001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\)).
-Further, SVs were associated with Corrugator activity (\(t(5, 618.96)=2.09\), \(p=.037\), \(f^2<.001\)), subjective effort (\(t(5, 618.96)=-13.98\), \(p<.001\), \(f^2=.035\)), and self-reported utility (\(t(5, 618.96)=29.49\), \(p<.001\), \(f^2=.155\)).
-SVs were further associated with self-control (\(t(97.97)=2.04\), \(p=.044\), \(f^2=.002\)), but not with flexible ER.
-With our paradigm, we were able to determine subjective values.
-The trait character of the values will be discussed.
-}
-
 \begin{document}
@@
 
+\hypertarget{DesignTable}{%
+\subsection{Design Table}\label{DesignTable}}
+
+\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
+\newpage
+
+\hypertarget{stimuli-used-in-er-paradigm}{%
+\subsection{Stimuli used in ER paradigm}\label{stimuli-used-in-er-paradigm}}
+
+\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
+
 \renewcommand\thesection{\Alph{section}}
-\counterwithout{figure}{section}
-\setcounter{figure}{0}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\hypertarget{introduction}{%
-\section{1. Introduction}\label{introduction}}
-
-The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
-It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning\textsuperscript{2}.
-Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification\textsuperscript{1}, and, following the taxonomy of Powers and LaBar\textsuperscript{3}, individuals can implement ER strategies by means of different tactics.
-So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process\textsuperscript{1}.
-In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy\textsuperscript{1}.
-This postulated temporal sequence of ER strategies influences their effectiveness.
-Albeit it is meta-analytically proven that all mentioned strategies reduce subjective emotional experience, distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed only small to medium effect sizes (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
-In contrast, distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45\textsuperscript{4}.
-
-Psychophysiological measures provide further important information on the effectiveness of emotion regulation strategies (for an overview, see Zaehringer et al.\textsuperscript{5}).
-Compared to cardiovascular, electrodermal, and pupillometric autonomic responses, facial electromyography has been reported consistently across studies to be influenced by emotion regulation with even medium effect sizes.
-For example, studies have shown that reappraisal of negative emotion is associated with reduced activity of the corrugator supercilii (associated with anger, sadness, and fear) with \emph{d\textsubscript{-}} = 0.32\textsuperscript{5}.
-In addition, the levator labii superioris (associated with disgust) has also been associated with reduced activity during reappraisal\textsuperscript{6}.
-Similar effects have been reported for suppression\textsuperscript{6}, distancing\textsuperscript{7}, and distraction\textsuperscript{8}.
-Importantly, results on electromyographic measures seem to be more consistent compared to other autonomic measures, likely because they are specific to emotional valence and its changes.
-
-Similarly to the differences in short term effectiveness, these tactics from three different strategies are also related to different medium and long-term consequences.
-In particular, strategies that do not change the emotional content of the situation, for instance by taking a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
-Thus, the self-reported habitual use of suppression is associated with more negative affect and lower general well-being\textsuperscript{9}.
-In addition, a number of ER strategies, e.g., rumination and suppression, have been associated with mental disorders (for meta-analytic review, see Aldao et al.\textsuperscript{10}), which led to the postulation of \emph{adaptive} (such as reappraisal, acceptance) and \emph{maladaptive} (such as suppression, rumination) ER strategies.
-For example, it was shown that maladaptive ER strategies (rumination and suppression) mediate the effect between neuroticism and depressive symptoms\textsuperscript{11}.
-
-The postulation of \emph{adaptive} and \emph{maladaptive} ER strategies has been challenged by the concepts of ER repertoire and ER flexibility.
-Within this framework, \emph{maladaptive} refers to inflexible ER strategy use or use of strategies that are hindering goal achievement\textsuperscript{12}.
-Adaptive flexible ER requires a large repertoire of ER strategies\textsuperscript{12}.
-The term ``repertoire'' can be defined as the ability to utilize a wide range of regulatory strategies in divergent contextual demands and opportunities\textsuperscript{13}.
-A growing number of studies report findings about the repertoire of emotion regulation strategies and its relationship to psychopathology\textsuperscript{14--16}.
-Additionally, greater ER flexibility is related to reduced negative affect and therefore beneficial in daily life\textsuperscript{17}.
-
-How do people choose strategies from their repertoire?
-Similarly to the expectancy-value model of emotion regulation\textsuperscript{18} it could be assumed, that people also assign a value to an ER strategy reflecting the usefulness of this strategy for goal achieving.
-Evidence from other psychological domains (e.g., intertemporal choice\textsuperscript{19}) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
-Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs\textsuperscript{20}.
-For example, a study found that the intensity of a stimulus or situation plays a role in the choice\textsuperscript{21}.
-Higher intensity of the (negative) stimulus lead to a choice of rather disengaging tactics of attentional deployment, like distraction\textsuperscript{20,21}.
-ER choice was further influenced by, among others, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort\textsuperscript{20,22}.
-Nonetheless, there are only few studies to date that examined the required effort of several strategies in more detail and compared them with each other.
-Furthermore, the research on ER choice lacks information regarding the strategies that were \emph{not} chosen in each case.
-It is unclear whether people had clear preferences or whether the choice options were similarly attractive.
-
-We assume that people choose the strategy that has the highest value for them at the moment.
-The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement\textsuperscript{12}.
-One certainly central goal is the regulation of negative affect.
-The effectiveness of ER strategies should therefore influence the respective SV.
-A second, intrinsic, and less obvious goal is the avoidance of effort\textsuperscript{23}.
-When given the choice, most individuals prefer tasks that are less effortful\textsuperscript{24}.
-Cognitive effort avoidance has been reported in many contexts, for example in affective context\textsuperscript{25}, the context of decision making\textsuperscript{26}, and executive functions\textsuperscript{27}, and is associated with Need for Cognition (NFC)\textsuperscript{28}, a stable measure of the individual pursuit and enjoyment of cognitive effort\textsuperscript{29,30}.
-In the area of emotion regulation, too, there are initial indications that people show a tendency towards effort avoidance.
-Across two studies, we could show in previous work that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy\textsuperscript{22}.
-In our studies, participants used the strategies distancing and suppression while inspecting emotional pictures.
-Afterwards, they choose which strategy they wanted to use again.
-Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
-Moreover, the majority of participants stated afterwards the main reason for their choice was effort.
-We assume therefore that, although individuals trade off both factors - effectiveness and effort - against each other, effort should be the more important predictor for SVs of ER strategies.
-In addition, perceived utility should have an impact on SVs.
-A strategy that is less effortful and can objectively regulate arousal (i.e., is effective), but is not subjectively perceived as useful, should have a low SV.
-SVs of ER Strategies could therefore be helpful to describe the ER repertoire\textsuperscript{12} more comprehensively.
-Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
-This would mean that all strategies are a good option for goal achievement.
-A second person with less flexibility, however, would show high SVs only for one strategy or low SVs for all of the strategies.
-This in turn would mean that there is only a limited amount of strategies in the repertoire to choose from.
-Subsequently, the ability to choose an appropriate strategy for a specific situation is also limited.
-
-So far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
-However, this would be useful to describe interindividual differences in the preference of ER strategies and the ER repertoire more comprehensively.
-To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
-Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
-Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED)\textsuperscript{29}.
-
-In the original study by Westbrook et al.\textsuperscript{29}, cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
-Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest \emph{n}-back level has the highest SV.
-In the present study, we want to use this paradigm to determine SVs of ER strategies.
-In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
-As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies\textsuperscript{22}.
-Moreover, there is nothing like an objectively easiest ER strategy.
-It could be assumed, that the antecedent-focused strategies, i.e.~attentional deployment and cognitive change, require less effort, because according to Gross\textsuperscript{1} these strategies apply when the emotional reaction has not fully developed, yet.
-In contrast, suppression would need ongoing effort, because it takes effect late in the emotion generating process and does not alter the emotion itself.
-A similar assumption has been made by Mesmer-Magnus et al.\textsuperscript{31}, who state that Surface Acting (the equivalent to expressive suppression in emotional labor research) is supposed to continuously require high levels of energy (hence effort).
-Deep Acting (which refers to reappraisal), in turn, only initially needs the use of energy.
-This would be in conflict with findings in our previous studies, that showed that many people choose expressive suppression because they evaluated it as less effortful, hence easy\textsuperscript{22}.
-Others define emotion regulation on a continuum from explicit, conscious, and effortful to implicit, unconscious, automatic and effortless\textsuperscript{32}.
-This would mean, that all explicit strategies that have been proposed by the process model of emotion regulation are similarly effortful\textsuperscript{1}.
-Similarly, the flexibility approach of emotion regulation also states, that there is no ``best'' strategy\textsuperscript{33}.
-An emotion regulation attempt is adaptive, when the intended, individual goal is reached.
-Those attempts could also consist of sequences of regulatory efforts using different strategies, which might be effective and effortless only in this specific context.
-Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined.
-In this step, the same monetary value (i.e., 1 €) is assigned to both options.
-The assumption is that participants now choose the option that has the higher SV for them.
-In the next step we return to the original paradigm.
-The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
-In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{29} until the indifference point is reached.
-This procedure will be repeated until all strategies have been compared.
-The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
-In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
-But our paradigm can also account for the case that a person does not have a clear preference.
-Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \ref{fig:ResponsePatterns}).
-In a separate study, we will test our adapted paradigm together with a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna, Scheffel et al.\textsuperscript{34}).
-
-{[}INSERT FIGURE 1 HERE{]}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
-In the top half, the person has a clear preference for one of the three strategies.
-In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can be represented by our paradigm.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:ResponsePatterns}
-\end{figure}
-
-The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies.
-As a manipulation check, we first want to investigate whether the valence of the pictures is affecting subjective and physiological responding, resulting in lower subjective arousal ratings after and lower EMG activity during neutral compared to negative pictures.
-Second, we want to check whether the ER strategies distraction, distancing, and suppression effectively reduce subjective arousal and physiological responding compared to the active viewing condition.
-Third, we want to see whether the strategies subjectively require more cognitive effort than the active viewing condition, and whether participants re-apply the for them least effortful strategy.
-Furthermore, we want to investigate whether subjective effort, arousal ratings, subjective utility, and EMG activity predict individual subjective values of ER strategies.
-And lastly, we want to check whether the SV of a strategy is associated with its likelihood of being chosen again, and whether SVs reflect participants' self-reported ER flexibility.
-All hypotheses are detailed in the \protect\hyperlink{DesignTable}{design table}.
-Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely \emph{n}-back.
-
-\hypertarget{method}{%
-\section{2. Method}\label{method}}
-
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study\textsuperscript{35}.
-The paradigm was written and presented using \emph{PsychoPy}\textsuperscript{36}.
-We used \emph{R} with \emph{R Studio}\textsuperscript{37,38} with the main packages \emph{afex}\textsuperscript{39} and \emph{BayesFactor}\textsuperscript{40} for all analyses.
-The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CAD}.
-A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CAD}).
-
-\hypertarget{ethics-information}{%
-\subsection{2.1 Ethics information}\label{ethics-information}}
-
-The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK50012022).
-Prior to testing, written informed consent was obtained.
-Participants received 24€ in total or course credit for participation.
-
-\hypertarget{pilot-data}{%
-\subsection{2.2 Pilot data}\label{pilot-data}}
-
-The newly developed ER paradigm was tested in a pilot study with \(N=16\) participants (9 female; age: \(M = 24.1\text{ }\pm\text{ }SD = 3.6\)).
-Regarding self-reported arousal, results showed significant higher subjective arousal for active viewing of negative compared to neutral pictures.
-However, ER strategies did not lead to a reduction of subjective arousal compared to active viewing of negative pictures.
-Regarding physiological responses, ER strategies were associated with reduced facial muscle activity of the \emph{corrugator} and \emph{levator} compared to active viewing of negative pictures.
-In accordance with our previous study\textsuperscript{22}, we found that the use of ER strategies compared to active viewing was associated with increased subjective effort.
-All results are detailed in the OSF repository (\url{https://osf.io/vnj8x/}).
-
-\hypertarget{design}{%
-\subsection{2.3 Design}\label{design}}
-
-Young healthy participants (aged 18 to 30 years) were recruited using the software \emph{ORSEE}\textsuperscript{41} at the Technische Universität Dresden.
-Participants were excluded from participation if they do not fluently speak German, had current or a history of psychological disorders or neurological trauma, or reported to take medication.
-Participants were invited to complete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
-The study consisted of two lab sessions, which took place in a shielded cabin with constant lighting.
-Before each session, participants received information about the respective experimental procedure and provided informed consent.
-In the first session participants filled out a demographic questionnaire and completed an \emph{n}-back task with the levels one to four.
-Then, they completed an effort discounting (ED) procedure regarding the \emph{n}-back levels on screen, followed by a random repetition of one \emph{n}-back level\textsuperscript{34}.
-The second session took place exactly one week after session one.
-Participants provided informed consent and received written instructions on the ER paradigm and ER strategies that they should apply.
-A brief training ensured that all participants were able to implement the ER strategies.
-Next, electrodes to measure facial EMG were attached and the ER task was conducted, followed by an ED procedure regarding the ER strategies.
-After that, participants chose one ER strategy to repeat one more time.
-Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{42,43}.
-
-\hypertarget{psychometric-measures}{%
-\subsubsection{2.3.1 Psychometric measures}\label{psychometric-measures}}
-
-The online survey contained a number of questionnaires.
-In the focus of the current project was the Flexible Emotion Regulation Scale (FlexER)\textsuperscript{44}.\\
-It assesses flexible use of ER strategies with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which we define as ER flexibility.
-The items were rated on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
-
-Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
-General psychological well-being was assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
-To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{47--49} was used.
-Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
-To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} was used.
-To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
-Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
-For more detailed information on psychometric properties of the questionnaires, please see the \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
-
-\hypertarget{emotion-regulation-paradigm}{%
-\subsubsection{2.3.2 Emotion regulation paradigm}\label{emotion-regulation-paradigm}}
-
-The ER paradigm consisted of three parts that will be described in the following.
-
-\emph{Part one: ER task.} Part one was a standard ER task in a block design (see Figure \ref{fig:DesignERED}), similar to paradigms previously used by our group\textsuperscript{22}.
-Participants were told to actively view neutral and negative pictures (see \protect\hyperlink{ux5cux23stimuli}{2.3.3}) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
-Every participant first had the condition ``active viewing-neutral'' that served as a baseline condition.
-During this block, 20 neutral pictures were presented.
-Participants were asked to ``actively view all pictures and permit all emotions that may arise.''
-In the second block, participants actively viewed negative pictures.
-During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
-In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
-During distancing, participants were asked to ``take the position of a non-involved observer, thinking about the picture in a neutral way.''
-Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
-During suppression, participants were told to ``suppress their emotional facial expression.''
-They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
-Participants were instructed not to suppress their thoughts or change their facial expression to the opposite\textsuperscript{22}.
-All participants received written instruction and completed a training session.
-After the training session, participants were asked about their applied ER strategies to avoid misapplication.
-The order of the three regulation blocks (distraction, distancing, and suppression) were randomized between participants.
-Each of the blocks consisted of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
-Each trial began with a fixation cross that lasted 3 to 5 seconds (random uniform distributed).
-It was followed by neutral or negative pictures for a total of 6 seconds.
-After each block, participants retrospectively rated their subjective emotional arousal (``not at all aroused'' to ``very highly aroused''), their subjective effort (``not very exhausting'' to ``very exhausting''), and - after the regulation blocks - the utility of the respective strategy (``not useful at all'' to ``very useful'') on a continuous scale using a slider on screen.
-
-\emph{Part two: ER effort discounting.} In the second part, ER effort discounting took place.
-The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{29} with a major change.
-We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies were presented with a monetary reward.
-Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between ``1€ for strategy A or 1€ for strategy B''.
-They decided by clicking the on-screen button of the respective option.
-Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
-For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1€, the other strategy was assigned the fixed value of 2€.
-After this, comparisons between strategies followed the original COG-ED paradigm\textsuperscript{29}.
-Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1€ was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2€ reward was chosen).
-The adjustment started at 0.50€ and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
-If a participant always chose the strategy with the fixed 2€ reward, the other strategy's last value on display was 1.97€, if they always choose the lower strategy, its last value was 0.03€.
-The sixth adjustment of 0.02€ was done during data analysis, based on the participants' decision in the last display of the pairing.
-Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.
-
-\emph{Part three: ER choice.} After the discounting part, participants chose which one of the three ER strategies (distraction, distancing or suppression) they wanted to re-apply.
-Importantly, there was no further instruction on what basis they should make their decision.
-Participants should make their decision freely, according to criteria they consider important for themselves.
-However, participants were asked to state the reasons for the decision afterwards in RedCap using a free text field.
-As soon as they have decided, they saw the respective instruction and the block with another 20 negative pictures started.
-
-{[}INSERT FIGURE 2 HERE{]}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{Block design of the paradigm.
-Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
-After, the discounting procedure took place.
-All three regulation strategies were compared pairwise.
-Before the last block, participants could decide which regulation strategy they wanted to reapply.
-Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:DesignERED}
-\end{figure}
-
-\hypertarget{stimuli}{%
-\subsubsection{2.3.3 Stimuli}\label{stimuli}}
-
-Pictures that were used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{60} and the International Affective Picture System (IAPS)\textsuperscript{61}.
-The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
-Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
-An evolutionary algorithm\textsuperscript{62} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
-A complete list of all pictures and their classification into sets can be found in supplementary material table S1.
-The five sets of negative pictures were assigned randomly to the blocks.
-
-\hypertarget{facial-electromyography}{%
-\subsubsection{2.3.4 Facial electromyography}\label{facial-electromyography}}
-
-Bipolar facial electromyography (EMG) were measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence\textsuperscript{63}, similar to previous work by our group\textsuperscript{7}.
-Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) were placed over each left muscle according to the guidelines of Fridlund and Cacioppo\textsuperscript{64}.
-The ground electrode was placed over the left \emph{Mastoid}.
-Before electrode placement, the skin was abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
-Raw signals were amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
-Impedance level were kept below 10 \(k\Omega\).
-Data were sampled at 1000 Hz, filtered, rectified and integrated.
-A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter was applied to both signals.
-\emph{Corrugator} and \emph{levator} EMG was analyzed during the 6 s of picture presentation.
-EMG data were baseline-corrected using a time window of 2 s prior to stimulus onset\textsuperscript{63}.
-Last, the sampling rate was changed to 100 Hz, and EMG data were averaged for each condition and each participant.
-
-\hypertarget{sampling-plan}{%
-\subsection{2.4 Sampling plan}\label{sampling-plan}}
-
-Sample size calculation was done using \emph{G*Power}\textsuperscript{65,66}.
-In a meta-analysis of Zaehringer and colleagues\textsuperscript{5}, effect sizes of ER on peripheral-physiological measures were reported:
-To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of at least \(N=85\) have to be analyzed.
-Power analyses of all other hypotheses yielded smaller sample sizes.
-However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
-Therefore, we aimed to collect data of \(N=120\) participants, about \(50%
-\) more data sets, than necessary.
-Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.
-
-\hypertarget{analysis-plan}{%
-\subsection{2.5 Analysis plan}\label{analysis-plan}}
-
-Data collection and analysis were not performed blind to the conditions of the experiments.
-Data of whole participants were excluded from analysis if participants withdraw their consent or they stated that they did not follow experimental instructions.
-EMG data of subjects were excluded from analysis if errors occured during recording.
-No further data exclusions were planned.
-The level of significance was set to \(\alpha=.05\).
-For hypotheses H1-4, repeated measures analysis of variance (rmANOVA) were conducted and estimated marginal means were computed using the \emph{afex} package\textsuperscript{39}.
-Greenhouse-Geisser-corrected degrees of freedom and associated \(p\)-values were reported when the assumption of sphericity was violated.
-If the within-subjects factor of interest was significant, pairwise contrasts were calculated using Bonferroni adjustment for multiple testing.
-Proportion of explained variance \(\eta_{p}^{2}\) was reported as a measure of effect size.
-
-\emph{Effect of valence on arousal and facial EMG.}
-To examine the impact of valence of emotional pictures on subjective arousal ratings (H1a), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted.
-To examine the impact of valence on physiolocigal responding (H1b and H1c), a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing was conducted for EMG \emph{corrugator} and \emph{levator} activity.
-
-\emph{Effects of emotion regulation on arousal, facial EMG, and effort.}
-To investigate the effects of the three ER strategies on subjective arousal (H2a), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective arousal ratings was conducted.
-To examine the effects of the three ER strategies on physiological responding (H3a and H3b), another rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for EMG \emph{corrugator} and \emph{levator} activity was conducted.
-To examine the effect of ER strategies on subjective effort (H4a), a rmANOVA with the factor strategy (active viewing - negative, distraction, distancing, and suppression) for subjective effort ratings was conducted.
-
-\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
-Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
-The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
-The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.
-
-To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the \(lmerTest\) package\textsuperscript{67}.
-First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
-Restricted maximum likelihood (REML) was applied to fit the model.
-A random slopes model of SVs including subjective effort (effort ratings), subjective arousal (arousal ratings), utility (utility ratings), and physiological responses (\emph{corrugator} and \emph{levator} activity) as level-1-predictors was specified.
-\[
-\begin{split}
-SV \sim strategy\ + \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (strategy|subject)
-\end{split}
-\]
-Level-1-predictors were centered within cluster\textsuperscript{68}.
-Residuals of the final model were inspected visually.
-Intraclass correlation coefficient (ICC), \(\rho\), was reported for each model (null model, as well as full model).
-The presented MLM followed the conceptualization of Zerna, Scheffel, et al.\textsuperscript{34}
-
-To investigate whether individual SVs predict ER choice (H7a), a \(\chi{2}\) test with predicted choice (highest SV of each participant) and actual choice was computed.
-Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.
-
-The association between flexible ER and SVs of ER strategies (H7b) was investigated with a linear regression using the individual \(intercept\) and \(slope\) of each participants' SVs to predict their FlexER score.
-To this end, for each participant, SVs were sorted by magnitude in descending order and entered as dependent variable in a linear model, with strategy (centered, i.e., -1, 0, 1) as independent variable.
-The resulting \(intercept\) informs about the extent to which an individual considers any or all of the ER strategies as useful for regulation their emotion, while the \(slope\) informs about the flexibility in the use of emotion regulation strategies.
-The individual intercepts and slopes were entered as predictors in a regression model with the FlexER score as dependent variable.
-A positive association with the predictor \(intercept\) would indicate that overall higher SVs attached to ER strategies predicts higher scores on the FlexER scale.
-A positive association with the predictor \(slope\) would indicate that less negative slopes, i.e., a smaller preference for a given ER strategy, would be associated with a higher score of the FlexER scale.
-
-The influence of personality traits on SVs were investigated exploratorily.
-Therefore, the MLM specified above was extended by the level-2-predictors NFC and self-control.
-
-For each result of the analyses, both \(p\)-values and Bayes factors \(BF10\), calculated using the \emph{BayesFactor} package\textsuperscript{40}, were reported.
-Bayes factors were calculated using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{regressionBF}.
-
-\hypertarget{data-availability}{%
-\subsection{Data availability}\label{data-availability}}
-
-The data of this study can be downloaded from \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.
-
-\hypertarget{code-availability}{%
-\subsection{Code availability}\label{code-availability}}
-
-The paradigm code, the R script for analysis, and the R Markdown file used to compile this document are available at \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.
-
-\hypertarget{protocol-registration}{%
-\subsection{Protocol registration}\label{protocol-registration}}
-
-The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/d6sc9/}{osf.io/d6sc9/}.
-
-\hypertarget{results}{%
-\section{3. Results}\label{results}}
-
-\hypertarget{participants-and-descriptive-statistics}{%
-\subsection{3.1 Participants and descriptive statistics}\label{participants-and-descriptive-statistics}}
-
-Data collection took place between 16th of August 2022 and the 3rd of February 2023.
-A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
-Of these, \(N=124\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
-Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of \(N=120\) participants (100 female; age: \(M\text{ }\pm\text{ }SD =22.5\text{ }\pm\text{ }3.0\) years old), which is 1.4 times more than what the highest sample size calculation required.
-Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).
-
-\hypertarget{confirmatory-analyses}{%
-\subsection{3.2. Confirmatory analyses}\label{confirmatory-analyses}}
-
-\hypertarget{manipulation-checks}{%
-\subsubsection{Manipulation checks}\label{manipulation-checks}}
-
-\hypertarget{effect-of-valence-on-arousal-and-facial-emg}{%
-\paragraph{Effect of valence on arousal and facial EMG}\label{effect-of-valence-on-arousal-and-facial-emg}}
-
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, \emph{corrugator} and \emph{levator} activity.
-Descriptive values of each predictor for each condition can be found in Table \ref{tab:TabDescr}.
-We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.76 \times 10^{48}\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.05 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 251.32\)).
-Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \ref{tab:SupplEffectArousalView} to @ref(tab:SupplEffectLevView and Figures \ref{fig:SupplFigArousalView} to \ref{fig:SupplFigLevView} in the {[}supplement{]}).
-
-\hypertarget{effect-of-emotion-regulation-on-arousal-and-facial-emg}{%
-\paragraph{Effect of emotion regulation on arousal and facial EMG}\label{effect-of-emotion-regulation-on-arousal-and-facial-emg}}
-
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
-We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 157.74\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.82 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc contrasts, please see Tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and Figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
-
-{[}INSERT TABLE 1 HERE{]}
-
-\begin{lltable}
-
-\begin{longtable}{rccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.}\\
-\toprule
- & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
-\midrule
-\endfirsthead
-\caption*{\normalfont{Table \ref{tab:TabDescr} continued}}\\
-\toprule
- & \multicolumn{1}{c}{Subjective Arousal} & \multicolumn{1}{c}{Subjective Effort} & \multicolumn{1}{c}{Subjective Utility} & \multicolumn{1}{c}{Corrugator activity (in mV)} & \multicolumn{1}{c}{Levator activity (in mV)}\\
-\midrule
-\endhead
-$View_{neu}$ & 26.6 ± 39.1 & 18.1 ± 27.4 &  & 0.04 ± 6.99 & 0.09 ± 1.84\\
-$View_{neg}$ & 187.8 ± 87.3 & 49.4 ± 62.3 &  & 1.03 ± 7.21 & 0.58 ± 3.2\\
-Distraction & 158.1 ± 92.5 & 208.5 ± 96.1 & 216.6 ± 93.2 & 0 ± 7.67 & -0.05 ± 1.16\\
-Distancing & 164 ± 87.2 & 189.8 ± 92.3 & 214.8 ± 78.6 & 0.25 ± 1.92 & 0.01 ± 1\\
-Suppression & 168.6 ± 95.8 & 158.3 ± 99.5 & 229.3 ± 95 & 0.07 ± 3.78 & -0.03 ± 0.92\\
-\bottomrule
-\end{longtable}
-
-\end{lltable}
-
-\hypertarget{effect-of-emotion-regulation-of-effort}{%
-\paragraph{Effect of emotion regulation of effort}\label{effect-of-emotion-regulation-of-effort}}
-
-To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.77 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
-Post-hoc contrasts showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
-Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).
-
-{[}INSERT FIGURE 3 HERE{]}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSubjEffort} \caption{Subjective effort ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSubjEffort}
-\end{figure}
-
-Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
-45.40\% of the participants stated that they chose the strategy that was easiest for them to implement.
-24.40\% stated they chose the strategy that was most effective and 11.80\% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found online on OSF (\url{https://osf.io/vnj8x/}).
-
-\hypertarget{subjective-values-of-er-strategies-and-their-predictors}{%
-\subsubsection{Subjective values of ER strategies and their predictors}\label{subjective-values-of-er-strategies-and-their-predictors}}
-
-Individual SVs could be determined for 120 participants for all three ER strategies.
-SVs ranged between 0.005 and 1.00.
-\(n=\) 119 had one SV of 1.0, indicating a clear preference for one ER strategy.
-Absolute preferences for ER strategies were relatively equally distributed.
-Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 43.
-
-To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
-The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor subject accounted for 19.10\% of total variance.
-The preregistered model showed a correlation of \(r=\) 0.95 between the random effects \emph{subjects} and \emph{recoded strategy} (\(BF10\) of the variable \emph{strategy}: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
-Our model explained 90.4\% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
-We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
-The second model followed the specification:
-\[
-\begin{split}
-SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
-\end{split}
-\]
-
-The second model explained 41.5\% of variance.
-All results of the second model are in Table \ref{tab:TabMLMH5}.
-
-{[}INSERT TABLE 2 HERE{]}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:TabMLMH5}Results of multilevel model predicting subjective values of ER strategies.}
-
-\begin{tabular}{llllll}
-\toprule
-Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
-\midrule
-Intercept & $8.03 \times 10^{-1}$ & 0.012 & <.001 &  & 0.114\\
-Effort & $-6.85 \times 10^{-4}$ & 0.000 & <.001 & 0.035 & \\
-Arousal & $-7.84 \times 10^{-5}$ & 0.000 & 0.317 & 0.000 & \\
-Utility & $1.42 \times 10^{-3}$ & 0.000 & <.001 & 0.155 & \\
-Corrugator activity & $7.45 \times 10^{-3}$ & 0.004 & 0.037 & 0.001 & \\
-Levator activity & $5.32 \times 10^{-3}$ & 0.003 & 0.070 & 0.001 & \\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-The predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,618.96) = 29.49\), \(p < .001\)), and \emph{corrugator} activity (\(\hat{\beta} = 0.007\), 95\% CI \([0.000, 0.014]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
-Beta values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
-The predictor utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5\% of variance in SVs.
-Effort rating showed an effect size of \(f^{2}=\) 0.035.
-The effect sizes of all other predictors were negligibly small (\(f^{2}< 0.01\)).
-
-\hypertarget{associations-between-subjective-values-and-flexible-er}{%
-\paragraph{Associations between subjective values and flexible ER}\label{associations-between-subjective-values-and-flexible-er}}
-
-To investigate the ecological validity of the calculated subjective values of ER strategies, we tested whether SVs were associated with the actual choice of participants in the last experimental block.
-Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
-There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 119) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see Figure \ref{fig:FigSVChoice}).
-
-{[}INSERT FIGURE 4 HERE{]}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSVChoice} \caption{Individual subjective values per ER strategy, grouped by choice in last experimental block.
-Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
-The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
-$N=120$.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSVChoice}
-\end{figure}
-
-We then conducted an ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
-Overall model fit was fair with \(R^{2}=\) 0.27.
-The SV of the strategy distraction contributed significantly to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
-The estimated odds ratio indicated a higher chance of choosing strategy distraction, when the SV of that strategy is higher.
-Additionally, the predictor SV of the strategy suppression contributed significantly to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
-The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
-
-Last, we investigated whether SVs are associated with ER flexibility.
-We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
-We found neither a significant association between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
-However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).
-
-\hypertarget{exploratory-analyses}{%
-\subsection{3.3. Exploratory analyses}\label{exploratory-analyses}}
-
-Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported\textsuperscript{29,34,69}, we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
-The starting point for this was the adapted MLM, which we have reported before.
-Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
-The third model followed the specification:
-\[
-\begin{split}
-SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ + \text{self-control} + \text{NFC} + (1 |subject)
-\end{split}
-\]
-As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
-In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.024\), 95\% CI \([0.001, 0.048]\), \(t(97.97) = 2.04\), \(p = .044\)).
-However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
-Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
-We adapted Westbrook et al.'s\textsuperscript{29} Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order.
-The new paradigm was tested on an \emph{n}-back task\textsuperscript{34} and a classic ER paradigm.
-The latter was the goal of the present study and completed by \(N=120\) participants.
-As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
-This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels\textsuperscript{4,5}.
-Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing.
-This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort\textsuperscript{22}.
-Both measures also showed high variability between individuals.
-Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
-It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest \emph{corrugator} activity, the lowest effort ratings and the highest utility ratings.
-In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions (``Maintain a neutral facial expression'') is measured directly.
-The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
-By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
-Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy.
-In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
-In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
-Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.
-
-Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1.
-We also found a wide range of SVs (between 0.005 and 1.00), suggesting that individuals have varying degrees of strategy preference.
-There was a significant relationship between SVs and strategy choice.
-Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
-We also found associations between individual SVs and various predictors.
-Subjective effort, utility, and \emph{corrugator} muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining 15.5\% of variance in SVs.
-However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
-In a subsequent exploratory analyses, we found a positive association between individual SVs and self-control.
-This is consistent with the literature, which has already reported correlations between self-control and demand avoidance\textsuperscript{69}.
-However, we did not find an association between NFC and SVs.
-This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance\textsuperscript{29,34}.
-However, these were all cognitive tasks. The role of NFC in affective tasks is not well known yet.
-
-\hypertarget{ecological-validity-of-subjective-values-of-er-strategies}{%
-\subsection{Ecological validity of subjective values of ER strategies}\label{ecological-validity-of-subjective-values-of-er-strategies}}
-
-Our aim was to calculate individual subjective values in order to develop a better understanding of ER strategy selection.
-Most individuals show large variability in strategy choice, both within-strategy and between-strategy\textsuperscript{17,70,71}.
-Greater variability may even be adaptive\textsuperscript{12,17}.
-In addition, a variety of factors that influence strategy choice in specific situations have been examined\textsuperscript{20--22,72--74}, including situation intensity and effort.
-However, these factors have often been studied in isolation from each other.
-Rarely have their combined effects been investigated\textsuperscript{73}.
-Furthermore, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) can only estimate how a factor tends to drive the choice in one direction or the other.
-They cannot determine the internal subjective value individuals attribute to the choice options.
-We are confident that we have achieved this with the present paradigm.
-On the one hand, we were able to show which factors have an influence on the values, and on the other hand, we were able to show the actual practical relevance of the values.
-As a predictor of ER effectiveness, \emph{corrugator} activity showed a significant association with SVs, but not \emph{levator} activity or subjective arousal.
-With regard to the EMG measures, this could be because all the pictures we used were negative, i.e.~elicited \emph{corrugator} activity, but only a small proportion of the pictures were perceived as disgusting and thus elicited relatively specific \emph{levator} activity.
-However, \emph{corrugator} activity did not differ significantly between ER strategies, but was still associated with SVs.
-One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current strategy, much more direct than, for example, the subjective arousal rating at the end of each experimental block.
-Furthermore, the finding that effort is associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies\textsuperscript{22}.
-Finally, the subjective utility ratings showed the greatest explained variance in the SVs.
-This relationship is highly plausible as it involves individuals assessing the utility of the strategy as a means of achieving external and internal regulatory goals.
-This is likely to overlap with subjective values - some literature argues that utility and subjective values are the same thing\textsuperscript{75}.
-However, this is contradicted by our data, as subjective utility could only explain 15.5\% of the variance in SVs.
-
-The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block.
-So far, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{72}.
-This may be because in laboratory studies the choice options are often predetermined by the experimental design\textsuperscript{20--22}.
-Therefore, attempts have been made to investigate ER choice and its influencing factors in everyday life in previous studies.
-Even there, however, certain strategies were often prescribed (for example studies see English et al.\textsuperscript{76}, Millgram et al.\textsuperscript{77}, Wilms et al.\textsuperscript{72}), although covering a large part of the process of emotion generation\textsuperscript{2}.
-Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
-To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment\textsuperscript{12,78}.
-This would also capture strategies that are rarely used or are even considered maladaptive, such as alcohol consumption or rumination\textsuperscript{79}.
-
-In order to gain a more comprehensive picture of ER, dynamic or cyclic processes have to be considered.
-The extended process model of emotion regulation\textsuperscript{33} postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
-If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped\textsuperscript{33}.
-Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback\textsuperscript{33,80--82}.
-This means that studies on ER Choice should consider not only situational factors, but also contextual factors\textsuperscript{81}.
-For example, in a classic ER choice paradigm\textsuperscript{21}, Murphy and Young\textsuperscript{81} showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
-This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
-Our newly developed CAD paradigm also makes an important contribution here.
-The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of SVs.
-That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.
-This raises the question of how stable these individual SVs are.
-
-\hypertarget{trait-character-of-svs}{%
-\subsection{Trait character of SVs}\label{trait-character-of-svs}}
-
-Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
-However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
-To establish the \emph{trait} nature of a measure, one could for instance resort to latent state trait modeling\textsuperscript{83}, as recently employed by our group in a related context\textsuperscript{30}.
-The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation.
-By definition, this represents a state.
-As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies\textsuperscript{21}.
-We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
-Our data presented in this study support this idea.
-However, this also implies that SVs should differ according to situational factors (e.g.~stimulus intensity).
-The ER goals that individuals pursue in a given situation must also be taken into account.
-In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals\textsuperscript{85}.
-Wilms and colleagues\textsuperscript{72} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
-In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
-It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also \protect\hyperlink{Limitations}{Limitations}).
-Therefore, SVs may vary when different reference strategies are used.
-It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals.
-They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires\textsuperscript{9}.
-Of course, it is also possible that such habits influence the internal formation of these subjective values.
-However, our data are not suitable for answering this question.
-In the future, SVs should therefore be collected in several similar situations.
-Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being\textsuperscript{9}.
-
-\hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
-
-A number of limitations must be taken into account when considering our findings.
-First, it should be noted that a block design was used.
-This might have resulted in habituation effects of EMG activity within the block.
-However, block designs are common in ER research\textsuperscript{86} and have been used in previous studies\textsuperscript{87}.
-Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block.
-It is known that affect labeling can attenuate emotional experience\textsuperscript{88,89}.
-Therefore, we decided not to conduct ratings after each image.
-Furthermore, we were able to confirm that the implementation of ER strategies was successful at both subjective and physiological levels.
-Still, these features of our research design may have led to slightly lower associations between SVs and predictors.
-
-Third, a major limitation is that participants had to use three prescribed ER strategies.
-It may be that some of the participants were not used to any of these strategies in everyday life, so none of the strategies actually had a high subjective value for them.
-However, the strategies selected for attentional deployment, cognitive change, and response modulation have been shown meta-analytically to be most effective\textsuperscript{4}.
-In this context, the individual SVs of each person must be interpreted with caution.
-They depend on the specific context: The stimuli presented and the strategies compared.
-For example, SVs for an ER strategy might be higher or lower when different stimuli or stimulus valences and different comparison strategies are used, because the calculation of SVs is inseparable form the other SVs.
-
-Fourth, the highest value during the discounting paradigm was set to 2€ as fixed value.
-Participants were asked to imagine that this was the amount of money they would receive if they repeated this strategy.
-Thus, 2€ could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
-However, we chose this amount because, firstly, we followed the original paradigm of Westbrook\textsuperscript{29}, and secondly, it has been shown in the context of cognitive effort discounting, that a lower incentive increases participants' sensitivity to effort differences\textsuperscript{90}.
-In the future, however, it should be investigated how the level of incentives affects subjective values.
-
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
-
-In order to cope with changing emotional demands, individuals may flexibly select and apply ER strategies from their repertoire\textsuperscript{12,13}.
-The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected\textsuperscript{12,85}.
-The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
-To date, such subjective values have not been established for ER strategies.
-Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values.
-This further enables to investigate the factors influencing the internal generation of these subjective values of ER strategies in more detail.
-It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and effort.
-Finally, further research is needed to investigate the factors that influence subjective values and whether these values represent habitual use of ER strategies by individuals.
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Gross1998antecedent}{}}%
-\CSLLeftMargin{1. }%
-\CSLRightInline{Gross, J.
-J.
-\href{https://doi.org/10.1037/0022-3514.74.1.224}{Antecedent- and response-focused emotion regulation: Divergent consequences for experience, expression, and physiology}.
-\emph{Journal of Personality and Social Psychology} \textbf{74}, 224--37 (1998).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gross1998emerging}{}}%
-\CSLLeftMargin{2. }%
-\CSLRightInline{Gross, J.
-J.
-\href{https://doi.org/10.1037/1089-2680.2.3.271}{The emerging field of emotion regulation: An integrative review}.
-\emph{Review of General Psychology} \textbf{2}, 271--299 (1998).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Powers2019}{}}%
-\CSLLeftMargin{3. }%
-\CSLRightInline{Powers, J.
-P.
-\& LaBar, K.
-S.
-\href{https://doi.org/10.1016/j.neubiorev.2018.04.023}{Regulating emotion through distancing: A taxonomy, neurocognitive model, and supporting meta-analysis}.
-\emph{Neuroscience and Biobehavioral Reviews} \textbf{96}, 155--173 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Webb2012}{}}%
-\CSLLeftMargin{4. }%
-\CSLRightInline{Webb, T.
-L., Miles, E.
-\& Sheeran, P.
-\href{https://doi.org/10.1037/a0027600}{Dealing with feeling: A meta-analysis of the effectiveness of strategies derived from the process model of emotion regulation}.
-\emph{Psychological Bulletin} \textbf{138}, 775--808 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Zaehringer2020}{}}%
-\CSLLeftMargin{5. }%
-\CSLRightInline{Zaehringer, J., Jennen-Steinmetz, C., Schmahl, C., Ende, G.
-\& Paret, C.
-\href{https://doi.org/10.3389/fpsyg.2020.00470}{Psychophysiological effects of downregulating negative emotions: Insights from a meta-analysis of healthy adults}.
-\emph{Front Psychol} \textbf{11}, 470 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Burr2021}{}}%
-\CSLLeftMargin{6. }%
-\CSLRightInline{Burr, D.
-A., Pizzie, R.
-G.
-\& Kraemer, D.
-J.
-M.
-\href{https://doi.org/ARTN\%20e0247246\%0A10.1371/journal.pone.0247246}{Anxiety, not regulation tendency, predicts how individuals regulate in the laboratory: An exploratory comparison of self-report and psychophysiology}.
-\emph{Plos One} \textbf{16}, (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gaertner2021}{}}%
-\CSLLeftMargin{7. }%
-\CSLRightInline{Gärtner, A., Jawinski, P.
-\& Strobel, A.
-\href{https://doi.org/10.1037/emo0001135}{Individual differences in inhibitory control are not related to emotion regulation}.
-\emph{Emotion} \textbf{Advance online publication}, (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schoenfelder2014}{}}%
-\CSLLeftMargin{8. }%
-\CSLRightInline{Schönfelder, S., Kanske, P., Heissler, J.
-\& Wessa, M.
-\href{https://doi.org/10.1093/scan/nst116}{Time course of emotion-related responding during distraction and reappraisal}.
-\emph{Social Cognitive and Affective Neuroscience} \textbf{9}, 1310--9 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-GrossJohn2003}{}}%
-\CSLLeftMargin{9. }%
-\CSLRightInline{Gross, J.
-J.
-\& John, O.
-P.
-\href{https://doi.org/10.1037/0022-3514.85.2.348}{Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being}.
-\emph{Journal of Personality and Social Psychology} \textbf{85}, 348--62 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Aldao2010}{}}%
-\CSLLeftMargin{10. }%
-\CSLRightInline{Aldao, A., Nolen-Hoeksema, S.
-\& Schweizer, S.
-\href{https://doi.org/10.1016/j.cpr.2009.11.004}{Emotion-regulation strategies across psychopathology: A meta-analytic review}.
-\emph{Clinical Psychology Review} \textbf{30}, 217--237 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Yoon2013}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Yoon, K.
-L., Maltby, J.
-\& Joormann, J.
-\href{https://doi.org/10.1080/10615806.2012.734810}{A pathway from neuroticism to depression: Examining the role of emotion regulation}.
-\emph{Anxiety, Stress, \& Coping} \textbf{26}, 558--72 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Aldao2015}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Aldao, A., Sheppes, G.
-\& Gross, J.
-J.
-\href{https://doi.org/10.1007/s10608-014-9662-4}{Emotion regulation flexibility}.
-\emph{Cognitive Therapy and Research} \textbf{39}, 263--278 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bonanno2013}{}}%
-\CSLLeftMargin{13. }%
-\CSLRightInline{Bonanno, G.
-A.
-\& Burton, C.
-L.
-\href{https://doi.org/10.1177/1745691613504116}{Regulatory flexibility: An individual differences perspective on coping and emotion regulation}.
-\emph{Perspectives on Psychological Science} \textbf{8}, 591--612 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-DixonGordon2015}{}}%
-\CSLLeftMargin{14. }%
-\CSLRightInline{Dixon-Gordon, K.
-L., Aldao, A.
-\& De Los Reyes, A.
-\href{https://doi.org/10.1080/02699931.2014.983046}{Repertoires of emotion regulation: A person-centered approach to assessing emotion regulation strategies and links to psychopathology}.
-\emph{Cogn Emot} \textbf{29}, 1314--25 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lougheed2012}{}}%
-\CSLLeftMargin{15. }%
-\CSLRightInline{Lougheed, J.
-P.
-\& Hollenstein, T.
-\href{https://doi.org/10.1111/j.1467-9507.2012.00663.x}{A limited repertoire of emotion regulation strategies is associated with internalizing problems in adolescence}.
-\emph{Social Development} \textbf{21}, 704--721 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Southward2018}{}}%
-\CSLLeftMargin{16. }%
-\CSLRightInline{Southward, M.
-W., Altenburger, E.
-M., Moss, S.
-A., Cregg, D.
-R.
-\& Cheavens, J.
-S.
-\href{https://doi.org/DOI\%2010.1521/jscp.2018.37.4.231}{Flexible, yet firm: A model of healthy emotion regulation}.
-\emph{Journal of Social and Clinical Psychology} \textbf{37}, 231--251 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Blanke2020}{}}%
-\CSLLeftMargin{17. }%
-\CSLRightInline{Blanke, E. S. \emph{et al.} \href{https://doi.org/10.1037/emo0000566}{Mix it to fix it: Emotion regulation variability in daily life}. \emph{Emotion} \textbf{20}, 473--485 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tamir2015}{}}%
-\CSLLeftMargin{18. }%
-\CSLRightInline{Tamir, M., Bigman, Y.
-E., Rhodes, E., Salerno, J.
-\& Schreier, J.
-\href{https://doi.org/10.1037/emo0000021}{An expectancy-value model of emotion regulation: Implications for motivation, emotional experience, and decision making}.
-\emph{Emotion} \textbf{15}, 90--103 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kable2007}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Kable, J.
-W.
-\& Glimcher, P.
-W.
-\href{https://doi.org/10.1038/nn2007}{The neural correlates of subjective value during intertemporal choice}.
-\emph{Nat Neurosci} \textbf{10}, 1625--33 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sheppes2014}{}}%
-\CSLLeftMargin{20. }%
-\CSLRightInline{Sheppes, G.
-\emph{et al.} \href{https://doi.org/10.1037/a0030831}{Emotion regulation choice: A conceptual framework and supporting evidence}.
-\emph{Journal of Experimental Psychology: General} \textbf{143}, 163--81 (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sheppes2011}{}}%
-\CSLLeftMargin{21. }%
-\CSLRightInline{Sheppes, G., Scheibe, S., Suri, G.
-\& Gross, J.
-J.
-\href{https://doi.org/10.1177/0956797611418350}{Emotion-regulation choice}.
-\emph{Psychological Science} \textbf{22}, 1391--6 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Scheffel2021}{}}%
-\CSLLeftMargin{22. }%
-\CSLRightInline{Scheffel, C.
-\emph{et al.} \href{https://doi.org/10.1111/psyp.13908}{Effort beats effectiveness in emotion regulation choice: Differences between suppression and distancing in subjective and physiological measures}.
-\emph{Psychophysiology} \textbf{00}, e13908 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Inzlicht2018}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Inzlicht, M., Shenhav, A.
-\& Olivola, C.
-Y.
-\href{https://doi.org/10.1016/j.tics.2018.01.007}{The effort paradox: Effort is both costly and valued}.
-\emph{Trends Cogn Sci} \textbf{22}, 337--349 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hull1943}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{Hull, C. L. \emph{Principles of behavior: An introduction to behavior theory}. (Appleton-Century-Crofts, 1943).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gonzalez-Garcia2021}{}}%
-\CSLLeftMargin{25. }%
-\CSLRightInline{Gonzalez-Garcia, C.
-\emph{et al.} \href{https://doi.org/10.1007/s00426-020-01300-9}{Induced affective states do not modulate effort avoidance}.
-\emph{Psychol Res} \textbf{85}, 1016--1028 (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kool2010}{}}%
-\CSLLeftMargin{26. }%
-\CSLRightInline{Kool, W., McGuire, J.
-T., Rosen, Z.
-B.
-\& Botvinick, M.
-M.
-\href{https://doi.org/10.1037/a0020198}{Decision making and the avoidance of cognitive demand}.
-\emph{J Exp Psychol Gen} \textbf{139}, 665--82 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Cheval2020}{}}%
-\CSLLeftMargin{27. }%
-\CSLRightInline{Cheval, B.
-\emph{et al.} \href{https://doi.org/ARTN\%20101781\%0A10.1016/j.psychsport.2020.101781}{Higher inhibitory control is required to escape the innate attraction to effort minimization}.
-\emph{Psychology of Sport and Exercise} \textbf{51}, (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Cacioppo1982}{}}%
-\CSLLeftMargin{28. }%
-\CSLRightInline{Cacioppo, J.
-T.
-\& Petty, R.
-E.
-\href{https://doi.org/10.1037//0022-3514.42.1.116}{The need for cognition}.
-\emph{Journal of Personality and Social Psychology} \textbf{42}, 116--131 (1982).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Westbrook2013}{}}%
-\CSLLeftMargin{29. }%
-\CSLRightInline{Westbrook, A., Kester, D.
-\& Braver, T.
-S.
-\href{https://doi.org/10.1371/journal.pone.0068210}{What is the subjective cost of cognitive effort?
-{Load}, trait, and aging effects revealed by economic preference}.
-\emph{PLOS ONE} \textbf{8}, e68210 (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Strobel2020}{}}%
-\CSLLeftMargin{30. }%
-\CSLRightInline{Strobel, A.
-\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0239817}{Dispositional cognitive effort investment and behavioral demand avoidance: Are they related?} \emph{PLoS One} \textbf{15}, e0239817 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-MesmerMagnus2012}{}}%
-\CSLLeftMargin{31. }%
-\CSLRightInline{Mesmer-Magnus, J.
-R., DeChurch, L.
-A.
-\& Wax, A.
-\href{https://doi.org/10.1177/2041386611417746}{Moving emotional labor beyond surface and deep acting: A discordance-congruence perspective}.
-\emph{Organizational Psychology Review} \textbf{2}, 6--53 (2012).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gyurak2011}{}}%
-\CSLLeftMargin{32. }%
-\CSLRightInline{Gyurak, A., Gross, J.
-J.
-\& Etkin, A.
-\href{https://doi.org/10.1080/02699931.2010.544160}{Explicit and implicit emotion regulation: A dual-process framework}.
-\emph{Cogn Emot} \textbf{25}, 400--12 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gross2015}{}}%
-\CSLLeftMargin{33. }%
-\CSLRightInline{Gross, J. J. \href{https://doi.org/10.1080/1047840x.2014.940781}{Emotion regulation: Current status and future prospects}. \emph{Psychological Inquiry} \textbf{26}, 1--26 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ZernaScheffel2022}{}}%
-\CSLLeftMargin{34. }%
-\CSLRightInline{Zerna, J., Scheffel, C., Kührt, C.
-\& Strobel, A.
-When easy is not preferred: A discounting paradigm to assess load-independent task preference.
-\emph{PsyArXiv} (2022) doi:\href{https://doi.org/10.31234/osf.io/ysh3q}{10.31234/osf.io/ysh3q}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Simmons2012}{}}%
-\CSLLeftMargin{35. }%
-\CSLRightInline{Simmons, J. P., Nelson, L. D. \& Simonsohn, U. A. A 21 word solution. \emph{SSRN Electronic Journal} (2012) doi:\href{https://doi.org/10.2139/ssrn.2160588}{10.2139/ssrn.2160588}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Peirce2019}{}}%
-\CSLLeftMargin{36. }%
-\CSLRightInline{Peirce, J.
-\emph{et al.} \href{https://doi.org/10.3758/s13428-018-01193-y}{{PsychoPy2}: {Experiments} in behavior made easy}.
-\emph{Behavior Research Methods} \textbf{51}, 195--203 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RCore2021}{}}%
-\CSLLeftMargin{37. }%
-\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R: A language and environment for statistical computing}}. (R Foundation for Statistical Computing, 2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RStudioTeam2020}{}}%
-\CSLLeftMargin{38. }%
-\CSLRightInline{RStudio Team. \href{http://www.rstudio.com}{{RStudio}: {Integrated} development for {R}}. (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Singmann2021}{}}%
-\CSLLeftMargin{39. }%
-\CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{\href{https://CRAN.R-project.org/package=afex}{Afex: {A}nalysis of factorial experiments}}. (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Morey2021}{}}%
-\CSLLeftMargin{40. }%
-\CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{\href{https://CRAN.R-project.org/package=BayesFactor}{{BayesFactor}: {Computation} of {Bayes} factors for common designs}}. (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Greiner2015}{}}%
-\CSLLeftMargin{41. }%
-\CSLRightInline{Greiner, B.
-\href{https://doi.org/10.1007/s40881-015-0004-4}{Subject pool recruitment procedures: {Organizing} experiments with {ORSEE}}.
-\emph{Journal of the Economic Science Association} \textbf{1}, 114--125 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Harris2009}{}}%
-\CSLLeftMargin{42. }%
-\CSLRightInline{Harris, P.
-A.
-\emph{et al.} \href{https://doi.org/10.1016/j.jbi.2008.08.010}{Research electronic data capture ({REDCap})---{A} metadata-driven methodology and workflow process for providing translational research informatics support}.
-\emph{Journal of Biomedical Informatics} \textbf{42}, 377--381 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Harris2019}{}}%
-\CSLLeftMargin{43. }%
-\CSLRightInline{Harris, P.
-A.
-\emph{et al.} \href{https://doi.org/10.1016/j.jbi.2019.103208}{The {REDCap} consortium: {Building} an international community of software platform partners}.
-\emph{Journal of Biomedical Informatics} \textbf{95}, 103208 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Doerfel2019}{}}%
-\CSLLeftMargin{44. }%
-\CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bech2004}{}}%
-\CSLLeftMargin{45. }%
-\CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Braehler2007}{}}%
-\CSLLeftMargin{46. }%
-\CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
-\& Schmidt, S.
-\href{https://doi.org/10.1026/0012-1924.53.2.83}{Teststatistische pr{ü}fung und normierung der deutschen versionen des EUROHIS-QOL lebensqualit{ä}t-index und des WHO-5 wohlbefindens-index}.
-\emph{Diagnostica} \textbf{53}, 83--96 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Connor2003}{}}%
-\CSLLeftMargin{47. }%
-\CSLRightInline{Connor, K.
-M.
-\& Davidson, J.
-R.
-\href{https://doi.org/10.1002/da.10113}{Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC)}.
-\emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell-Sills2007}{}}%
-\CSLLeftMargin{48. }%
-\CSLRightInline{Campbell-Sills, L.
-\& Stein, M.
-B.
-\href{https://doi.org/10.1002/jts.20271}{Psychometric analysis and refinement of the connor-davidson resilience scale (CD-RISC): Validation of a 10-item measure of resilience}.
-\emph{Journal of Traumatic Stress} \textbf{20}, 1019--28 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sarubin2015}{}}%
-\CSLLeftMargin{49. }%
-\CSLRightInline{Sarubin, N.
-\emph{et al.} \href{https://doi.org/10.1026/0943-8149/a000142}{First analysis of the 10-and 25-item german version of the connor-davidson resilience scale (CD-RISC) regarding psychometric properties and components}.
-\emph{Zeitschrift Fur Gesundheitspsychologie} \textbf{23}, 112--122 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Abler2009}{}}%
-\CSLLeftMargin{50. }%
-\CSLRightInline{Abler, B.
-\& Kessler, H.
-\href{https://doi.org/10.1026/0012-1924.55.3.144}{Emotion regulation questionnaire - a german version of the ERQ by gross and john}.
-\emph{Diagnostica} \textbf{55}, 144--152 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bernecker2017}{}}%
-\CSLLeftMargin{51. }%
-\CSLRightInline{Bernecker, K.
-\& Job, V.
-\href{https://doi.org/10.1027/2151-2604/a000292}{Implicit theories about willpower in resisting temptations and emotion control}.
-\emph{Zeitschrift Fur Psychologie-Journal of Psychology} \textbf{225}, 157--166 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bless1994}{}}%
-\CSLLeftMargin{52. }%
-\CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
-F.
-\& Schwarz, N.
-\href{\%3CGo\%20to\%20ISI\%3E://WOS:A1994NR83900004}{Need for cognition - a scale measuring engagement and happiness in cognitive tasks}.
-\emph{Zeitschrift Für Sozialpsychologie} \textbf{25}, 147--154 (1994).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paschke2016}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Paschke, L.
-M.
-\emph{et al.} \href{https://doi.org/10.1093/scan/nsw036}{Individual differences in self-reported self-control predict successful emotion regulation}.
-\emph{Social Cognitive and Affective Neuroscience} \textbf{11}, 1193--204 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schwarzer1999}{}}%
-\CSLLeftMargin{54. }%
-\CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. \href{http://userpage.fu-berlin.de/~health/selfreg_g.htm}{Self-regulation scale}. (1999).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tangney2004}{}}%
-\CSLLeftMargin{55. }%
-\CSLRightInline{Tangney, J.
-P., Baumeister, R.
-F.
-\& Boone, A.
-L.
-\href{https://doi.org/10.1111/j.0022-3506.2004.00263.x}{High self-control predicts good adjustment, less pathology, better grades, and interpersonal success}.
-\emph{Journal of Personality} \textbf{72}, 271--324 (2004).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sproesser2011}{}}%
-\CSLLeftMargin{56. }%
-\CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
-\& Renner, B.
-\href{https://doi.org/10.1016/j.appet.2011.01.028}{Candy or apple?
-How self-control resources and motives impact dietary healthiness in women}.
-\emph{Appetite} \textbf{56}, 784--787 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Patton1995}{}}%
-\CSLLeftMargin{57. }%
-\CSLRightInline{Patton, J.
-H., Stanford, M.
-S.
-\& Barratt, E.
-S.
-\href{https://doi.org/10.1002/1097-4679(199511)51:6\%3C768::aid-jclp2270510607\%3E3.0.co;2-1}{Factor structure of the barratt impulsiveness scale}.
-\emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hartmann2011}{}}%
-\CSLLeftMargin{58. }%
-\CSLRightInline{Hartmann, A.
-S., Rief, W.
-\& Hilbert, A.
-\href{https://doi.org/10.2466/08.09.10.PMS.112.2.353-368}{Psychometric properties of the german version of the barratt impulsiveness scale, version 11 (BIS-11) for adolescents}.
-\emph{Perceptual and Motor Skills} \textbf{112}, 353--368 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Derryberry2002}{}}%
-\CSLLeftMargin{59. }%
-\CSLRightInline{Derryberry, D.
-\& Reed, M.
-A.
-\href{https://doi.org/10.1037//0021-843X.111.2.225}{Anxiety-related attentional biases and their regulation by attentional control.} \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wessa2010}{}}%
-\CSLLeftMargin{60. }%
-\CSLRightInline{Wessa, M.
-\emph{et al.} EmoPicS: Subjective und psychophysiologische evalueation neuen bildmaterials für die klinisch-biopsychologische forschung.
-\emph{Zeitschrift für Klinische Psychologie und Psychotherapie} \textbf{39}, 77 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lang2008}{}}%
-\CSLLeftMargin{61. }%
-\CSLRightInline{Lang, P.
-J., Bradley, M.
-M.
-\& Cuthbert, B.
-N.
-\emph{International affective picture system (IAPS): Affective ratings of pictures and instruction manual}.
-(University of Florida, 2008).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Yu2010}{}}%
-\CSLLeftMargin{62. }%
-\CSLRightInline{Yu, X. \& Gen, M. \emph{Introduction to evolutionary algorithms}. (Springer Science \& Business Media, 2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bradley2000}{}}%
-\CSLLeftMargin{63. }%
-\CSLRightInline{Bradley, M.
-M.
-\& Lang, P.
-J.
-Measuring emotion: Behavior, feeling, and physiology.
-in \emph{Cognitive neuroscience of emotion} (eds.
-Lane, R.
-D.
-\& Nadel, L.) 242--276 (Oxford University Press, 2000).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fridlund1986}{}}%
-\CSLLeftMargin{64. }%
-\CSLRightInline{Fridlund, A.
-J.
-\& Cacioppo, J.
-T.
-\href{https://doi.org/10.1111/j.1469-8986.1986.tb00676.x}{Guidelines for human electromyographic research}.
-\emph{Psychophysiology} \textbf{23}, 567--89 (1986).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Faul2007}{}}%
-\CSLLeftMargin{65. }%
-\CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
-\& Buchner, A.
-\href{https://doi.org/10.3758/BF03193146}{G*{Power} 3: {A} flexible statistical power analysis program for the social, behavioral, and biomedical sciences}.
-\emph{Behavior Research Methods} \textbf{39}, 175--191 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Faul2009}{}}%
-\CSLLeftMargin{66. }%
-\CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
-\& Lang, A.-G.
-\href{https://doi.org/10.3758/BRM.41.4.1149}{Statistical power analyses using {G}*{Power} 3.1: {Tests} for correlation and regression analyses}.
-\emph{Behavior Research Methods} \textbf{41}, 1149--1160 (2009).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kuznetsova2017}{}}%
-\CSLLeftMargin{67. }%
-\CSLRightInline{Kuznetsova, A., Brockhoff, P.
-B.
-\& Christensen, R.
-H.
-B.
-\href{https://doi.org/10.18637/jss.v082.i13}{{lmerTest} package: Tests in linear mixed effects models}.
-\emph{Journal of Statistical Software} \textbf{82}, 1--26 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Enders2007}{}}%
-\CSLLeftMargin{68. }%
-\CSLRightInline{Enders, C.
-K.
-\& Tofighi, D.
-\href{https://doi.org/10.1037/1082-989x.12.2.121}{Centering predictor variables in cross-sectional multilevel models: {A} new look at an old issue.} \emph{Psychological Methods} \textbf{12}, 121--138 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kool2013}{}}%
-\CSLLeftMargin{69. }%
-\CSLRightInline{Kool, W., McGuire, J.
-T., Wang, G.
-J.
-\& Botvinick, M.
-M.
-\href{https://doi.org/10.1371/journal.pone.0072626}{Neural and behavioral evidence for an intrinsic cost of self-control}.
-\emph{Plos One} \textbf{8}, (2013).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Burr2020}{}}%
-\CSLLeftMargin{70. }%
-\CSLRightInline{Burr, D.
-A.
-\& Samanez-Larkin, G.
-R.
-\href{https://doi.org/10.1016/j.tics.2020.02.008}{Advances in emotion regulation choice from experience sampling}.
-\emph{Trends in Cognitive Sciences} \textbf{24}, 344--346 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Elkjaer2022}{}}%
-\CSLLeftMargin{71. }%
-\CSLRightInline{Elkjaer, E., Mikkelsen, M.
-B.
-\& O'Toole, M.
-S.
-\href{https://doi.org/10.1111/sjop.12808}{Emotion regulation patterns: Capturing variability and flexibility in emotion regulation in an experience sampling study}.
-\emph{Scandinavian Journal of Psychology} \textbf{63}, 297--307 (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilms2020}{}}%
-\CSLLeftMargin{72. }%
-\CSLRightInline{Wilms, R., Lanwehr, R.
-\& Kastenmuller, A.
-\href{https://doi.org/ARTN\%20877\%0A10.3389/fpsyg.2020.00877}{Emotion regulation in everyday life: The role of goals and situational factors}.
-\emph{Frontiers in Psychology} \textbf{11}, (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Young2020}{}}%
-\CSLLeftMargin{73. }%
-\CSLRightInline{Young, G.
-\& Suri, G.
-\href{https://doi.org/10.1080/02699931.2019.1611544}{Emotion regulation choice: A broad examination of external factors}.
-\emph{Cognition \& Emotion} \textbf{34}, 242--261 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Matthews2021}{}}%
-\CSLLeftMargin{74. }%
-\CSLRightInline{Matthews, M., Webb, T.
-L., Shafir, R., Snow, M.
-\& Sheppes, G.
-Identifying the determinants of emotion regulation choice: A systematic review with meta-analysis.
-\emph{Cognition and Emotion} 1--29 (2021) doi:\href{https://doi.org/10.1080/02699931.2021.1945538}{10.1080/02699931.2021.1945538}.}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Schultz2015}{}}%
-\CSLLeftMargin{75. }%
-\CSLRightInline{Schultz, W. \href{https://doi.org/10.1152/physrev.00023.2014}{Neuronal reward and decision signals: From theories to data}. \emph{Physiological Reviews} \textbf{95}, 853--951 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-English2017}{}}%
-\CSLLeftMargin{76. }%
-\CSLRightInline{English, T., Lee, I.
-A., John, O.
-P.
-\& Gross, J.
-J.
-\href{https://doi.org/10.1007/s11031-016-9597-z}{Emotion regulation strategy selection in daily life: The role of social context and goals}.
-\emph{Motivation and Emotion} \textbf{41}, 230--242 (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Millgram2019}{}}%
-\CSLLeftMargin{77. }%
-\CSLRightInline{Millgram, Y., Sheppes, G., Kalokerinos, E.
-K., Kuppens, P.
-\& Tamir, M.
-\href{https://doi.org/10.1037/xge0000477}{Do the ends dictate the means in emotion regulation?} \emph{Journal of Experimental Psychology-General} \textbf{148}, 80--96 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Koval2020}{}}%
-\CSLLeftMargin{78. }%
-\CSLRightInline{Koval, P., Kalokerinos, E.
-K., Verduyn, P.
-\& Greiff, S.
-\href{https://doi.org/10.1027/1015-5759/a000599}{Introduction to the special issue capturing the dynamics of emotion and emotion regulation in daily life with ambulatory assessment}.
-\emph{European Journal of Psychological Assessment} \textbf{36}, 433--436 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Pena-Sarrionandia2015}{}}%
-\CSLLeftMargin{79. }%
-\CSLRightInline{Pena-Sarrionandia, A., Mikolajczak, M.
-\& Gross, J.
-J.
-\href{https://doi.org/ARTN\%20160\%0A10.3389/fpsyg.2015.00160}{Integrating emotion regulation and emotional intelligence traditions: A meta-analysis}.
-\emph{Frontiers in Psychology} \textbf{6}, (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-AldaoChristensen2015}{}}%
-\CSLLeftMargin{80. }%
-\CSLRightInline{Aldao, A.
-\& Christensen, K.
-\href{https://doi.org/10.1080/1047840x.2015.962399}{Linking the expanded process model of emotion regulation to psychopathology by focusing on behavioral outcomes of regulation}.
-\emph{Psychological Inquiry} \textbf{26}, 27--36 (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Murphy2018}{}}%
-\CSLLeftMargin{81. }%
-\CSLRightInline{Murphy, J.
-W.
-\& Young, M.
-A.
-\href{https://doi.org/10.1080/02699931.2017.1419935}{Dynamic processes in emotion regulation choice}.
-\emph{Cognition \& Emotion} \textbf{32}, 1654--1662 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Sheppes2020}{}}%
-\CSLLeftMargin{82. }%
-\CSLRightInline{Sheppes, G.
-\href{https://doi.org/10.1016/bs.aesp.2019.09.003}{Transcending the "good \& bad" and "here \& now" in emotion regulation: Costs and benefits of strategies across regulatory stages}.
-\emph{Advances in Experimental Social Psychology, Vol 61} \textbf{61}, 185--236 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Steyer2015}{}}%
-\CSLLeftMargin{83. }%
-\CSLRightInline{Steyer, R., Mayer, A., Geiser, C.
-\& Cole, D.
-A.
-\href{https://doi.org/10.1146/annurev-clinpsy-032813-153719}{A theory of states and traits-revised}.
-\emph{Annual Review of Clinical Psychology} \textbf{11}, 71--+ (2015).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Haines2016}{}}%
-\CSLLeftMargin{84. }%
-\CSLRightInline{Haines, S.
-J.
-\emph{et al.} \href{https://doi.org/10.1177/0956797616669086}{The wisdom to know the difference: Strategy-situation fit in emotion regulation in daily life is associated with well-being}.
-\emph{Psychological Science} \textbf{27}, 1651--1659 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tamir2016}{}}%
-\CSLLeftMargin{85. }%
-\CSLRightInline{Tamir, M.
-\href{https://doi.org/10.1177/1088868315586325}{Why do people regulate their emotions?
-A taxonomy of motives in emotion regulation}.
-\emph{Personality and Social Psychology Review} \textbf{20}, 199--222 (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Barreiros2019}{}}%
-\CSLLeftMargin{86. }%
-\CSLRightInline{Barreiros, A.
-R., Almeida, I., Baia, B.
-C.
-\& Castelo-Branco, M.
-\href{https://doi.org/10.3389/fnhum.2019.00089}{Amygdala modulation during emotion regulation training with fMRI-based neurofeedback}.
-\emph{Frontiers in Human Neuroscience} \textbf{13}, 89 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Scheffel2019}{}}%
-\CSLLeftMargin{87. }%
-\CSLRightInline{Scheffel, C.
-\emph{et al.} \href{https://doi.org/10.1017/pen.2019.11}{Cognitive emotion regulation and personality: An analysis of individual differences in the neural and behavioral correlates of successful reappraisal}.
-\emph{Personality Neuroscience} \textbf{2}, e11 (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lieberman2007}{}}%
-\CSLLeftMargin{88. }%
-\CSLRightInline{Lieberman, M.
-D.
-\emph{et al.} \href{https://doi.org/10.1111/j.1467-9280.2007.01916.x}{Putting feelings into words - affect labeling disrupts amygdala activity in response to affective stimuli}.
-\emph{Psychological Science} \textbf{18}, 421--428 (2007).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Torre2018}{}}%
-\CSLLeftMargin{89. }%
-\CSLRightInline{Torre, J.
-B.
-\& Lieberman, M.
-D.
-\href{https://doi.org/10.1177/1754073917742706}{Putting feelings into words: Affect labeling as implicit emotion regulation}.
-\emph{Emotion Review} \textbf{10}, 116--124 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{90. }%
-\CSLRightInline{Bialaszek, W., Marcowski, P.
-\& Ostaszewski, P.
-\href{https://doi.org/ARTN\%20e0182353\%0A10.1371/journal.pone.0182353}{Physical and cognitive effort discounting across different reward magnitudes: Tests of discounting models}.
-\emph{Plos One} \textbf{12}, (2017).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{91. }%
-\CSLRightInline{Preece, D.
-A., Becerra, R., Robinson, K.
-\& Gross, J.
-J.
-\href{https://doi.org/10.1080/00223891.2018.1564319}{The emotion regulation questionnaire: Psychometric properties in general community samples}.
-\emph{J Pers Assess} \textbf{102}, 348--356 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{92. }%
-\CSLRightInline{Fleischhauer, M.
-\emph{et al.} \href{https://doi.org/10.1177/0146167209351886}{Same or different?
-{Clarifying} the relationship of need for cognition to personality and intelligence}.
-\emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{93. }%
-\CSLRightInline{Fleischhauer, M., Strobel, A.
-\& Strobel, A.
-\href{https://doi.org/10.1027/1614-0001/a000161}{Directly and indirectly assessed {N}eed for {C}ognition differentially predict spontaneous and reflective information processing behavior}.
-\emph{Journal of Individual Differences} \textbf{36}, 101--109 (2015).}
-
-\end{CSLReferences}
-
-\endgroup
-
-\newpage
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
-The funders had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection.
-
-\hypertarget{competing-interests}{%
-\section{Competing Interests}\label{competing-interests}}
-
-The authors declare no competing interests.
-\# Design Table \{\#DesignTable\}
-
-\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
-
-\newpage
-
-\hypertarget{SupplementaryMaterial}{%
-\section{Supplementary Material}\label{SupplementaryMaterial}}
-
-\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
 \counterwithin{figure}{section}
@@
 
-\emph{WHO-5.} General psychological well-being was assessed using the WHO-5 scale\textsuperscript{45,46}.
+\emph{WHO-5.} General psychological well-being was assessed using the WHO-5 scale\textsuperscript{1,2}.
 Five items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The German version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{46}.
-
-\emph{Connor-Davidson Resilience Scale.} Resilience was assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
+The German version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{2}.
+
+\emph{Connor-Davidson Resilience Scale.} Resilience was assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{3--5}.
 Ten items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 months\textsuperscript{49}.
-
-\emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{91}.
-
-\emph{FlexER Scale.} Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{44} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
+The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 months\textsuperscript{5}.
+
+\emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{6,7}.
+The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{8}.
+
+\emph{FlexER Scale.} Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{9} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
 Psychometric properties are currently under investigation.
 
-\emph{Implicit Theories Questionnaire.} Implicit theories of willpower in emotional control were assessed using the Implicit Theories Questionnaire of Bernecker and Job\textsuperscript{51}.
+\emph{Implicit Theories Questionnaire.} Implicit theories of willpower in emotional control were assessed using the Implicit Theories Questionnaire of Bernecker and Job\textsuperscript{10}.
 Four items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{51}.
-
-\emph{Need for Cognition Scale.} Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale\textsuperscript{52}.
+The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{10}.
+
+\emph{Need for Cognition Scale.} Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale\textsuperscript{11}.
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,92} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{93}.
-
-\emph{Self-Regulation Scale.} As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} was used.
+The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{11,12} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{13}.
+
+\emph{Self-Regulation Scale.} As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{14} was used.
 The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{54}.
-
-\emph{Brief Self-Control Scale.} As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} was used.
+It has high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{14}.
+
+\emph{Brief Self-Control Scale.} As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{15,16} was used.
 It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{56}.
-
-\emph{Barratt Impulsiveness Scale.} As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} was used.
+The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{16}.
+
+\emph{Barratt Impulsiveness Scale.} As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{17,18} was used.
 Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported\textsuperscript{58}.
-
-\emph{Attentional Control Scale.} Attentional control was measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
+An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported\textsuperscript{18}.
+
+\emph{Attentional Control Scale.} Attentional control was measured using the Attentional Control Scale (ACS)\textsuperscript{19} with items such as ``My concentration is good even if there is music in the room around me''.
 The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported\textsuperscript{59}.
+An internal consistency of Cronbach's \(\alpha=.88\) was reported\textsuperscript{19}.
 
@@
 
+\hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Bech2004}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{Bech, P. Measuring the dimensions of psychological general well-being by the WHO-5. \emph{Quality of life newsletter} \textbf{32}, 15--16 (2004).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Braehler2007}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Brähler, E., Mühlan, H., Albani, C.
+\& Schmidt, S.
+\href{https://doi.org/10.1026/0012-1924.53.2.83}{Teststatistische pr{ü}fung und normierung der deutschen versionen des EUROHIS-QOL lebensqualit{ä}t-index und des WHO-5 wohlbefindens-index}.
+\emph{Diagnostica} \textbf{53}, 83--96 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Connor2003}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Connor, K.
+M.
+\& Davidson, J.
+R.
+\href{https://doi.org/10.1002/da.10113}{Development of a new resilience scale: The connor-davidson resilience scale (CD-RISC)}.
+\emph{Depression and Anxiety} \textbf{18}, 76--82 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Campbell-Sills2007}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Campbell-Sills, L.
+\& Stein, M.
+B.
+\href{https://doi.org/10.1002/jts.20271}{Psychometric analysis and refinement of the connor-davidson resilience scale (CD-RISC): Validation of a 10-item measure of resilience}.
+\emph{Journal of Traumatic Stress} \textbf{20}, 1019--28 (2007).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sarubin2015}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Sarubin, N.
+\emph{et al.} \href{https://doi.org/10.1026/0943-8149/a000142}{First analysis of the 10-and 25-item german version of the connor-davidson resilience scale (CD-RISC) regarding psychometric properties and components}.
+\emph{Zeitschrift Fur Gesundheitspsychologie} \textbf{23}, 112--122 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-GrossJohn2003}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Gross, J.
+J.
+\& John, O.
+P.
+\href{https://doi.org/10.1037/0022-3514.85.2.348}{Individual differences in two emotion regulation processes: Implications for affect, relationships, and well-being}.
+\emph{Journal of Personality and Social Psychology} \textbf{85}, 348--62 (2003).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Abler2009}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Abler, B.
+\& Kessler, H.
+\href{https://doi.org/10.1026/0012-1924.55.3.144}{Emotion regulation questionnaire - a german version of the ERQ by gross and john}.
+\emph{Diagnostica} \textbf{55}, 144--152 (2009).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Preece, D.
+A., Becerra, R., Robinson, K.
+\& Gross, J.
+J.
+\href{https://doi.org/10.1080/00223891.2018.1564319}{The emotion regulation questionnaire: Psychometric properties in general community samples}.
+\emph{J Pers Assess} \textbf{102}, 348--356 (2020).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Doerfel2019}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Dörfel, D., Gärtner, A. \& Strobel, A. A new self-report instrument for measuring emotion regulation flexibility. \emph{Society for Affective Science (SAS) Annual Conference} (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bernecker2017}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Bernecker, K.
+\& Job, V.
+\href{https://doi.org/10.1027/2151-2604/a000292}{Implicit theories about willpower in resisting temptations and emotion control}.
+\emph{Zeitschrift Fur Psychologie-Journal of Psychology} \textbf{225}, 157--166 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bless1994}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Bless, H., Wanke, M., Bohner, G., Fellhauer, R.
+F.
+\& Schwarz, N.
+\href{\%3CGo\%20to\%20ISI\%3E://WOS:A1994NR83900004}{Need for cognition - a scale measuring engagement and happiness in cognitive tasks}.
+\emph{Zeitschrift Für Sozialpsychologie} \textbf{25}, 147--154 (1994).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Fleischhauer, M.
+\emph{et al.} \href{https://doi.org/10.1177/0146167209351886}{Same or different?
+{Clarifying} the relationship of need for cognition to personality and intelligence}.
+\emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Fleischhauer, M., Strobel, A.
+\& Strobel, A.
+\href{https://doi.org/10.1027/1614-0001/a000161}{Directly and indirectly assessed {N}eed for {C}ognition differentially predict spontaneous and reflective information processing behavior}.
+\emph{Journal of Individual Differences} \textbf{36}, 101--109 (2015).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schwarzer1999}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Schwarzer, R., Diehl, M. \& Schmitz, G. S. \href{http://userpage.fu-berlin.de/~health/selfreg_g.htm}{Self-regulation scale}. (1999).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tangney2004}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Tangney, J.
+P., Baumeister, R.
+F.
+\& Boone, A.
+L.
+\href{https://doi.org/10.1111/j.0022-3506.2004.00263.x}{High self-control predicts good adjustment, less pathology, better grades, and interpersonal success}.
+\emph{Journal of Personality} \textbf{72}, 271--324 (2004).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Sproesser2011}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Sproesser, G., Strohbach, S., Schupp, H.
+\& Renner, B.
+\href{https://doi.org/10.1016/j.appet.2011.01.028}{Candy or apple?
+How self-control resources and motives impact dietary healthiness in women}.
+\emph{Appetite} \textbf{56}, 784--787 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Patton1995}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Patton, J.
+H., Stanford, M.
+S.
+\& Barratt, E.
+S.
+\href{https://doi.org/10.1002/1097-4679(199511)51:6\%3C768::aid-jclp2270510607\%3E3.0.co;2-1}{Factor structure of the barratt impulsiveness scale}.
+\emph{Journal of Clinical Psychology} \textbf{51}, 768--774 (1995).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hartmann2011}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{Hartmann, A.
+S., Rief, W.
+\& Hilbert, A.
+\href{https://doi.org/10.2466/08.09.10.PMS.112.2.353-368}{Psychometric properties of the german version of the barratt impulsiveness scale, version 11 (BIS-11) for adolescents}.
+\emph{Perceptual and Motor Skills} \textbf{112}, 353--368 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Derryberry2002}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Derryberry, D.
+\& Reed, M.
+A.
+\href{https://doi.org/10.1037//0021-843X.111.2.225}{Anxiety-related attentional biases and their regulation by attentional control.} \emph{Journal of abnormal psychology} \textbf{111}, 225--236 (2002).}
+
+\end{CSLReferences}
+
 \end{document}

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/TheoreticalBackground.Rmd
placeholder for figures
moved figure to end of document

--- 2022-08-05 06_Paper/ER-ED/ERED_Stage2/TheoreticalBackground.Rmd
@@
 
-```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.
-In the top half, the person has a clear preference for one of the three strategies.
-In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can be represented by our paradigm."}
-include_graphics(here("06_Paper", "ER-ED", "figures", "Paradigm_Scheme_T2.png" ))
-```
+[INSERT FIGURE 1 HERE]
 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/method.Rmd
prepared for submission
Figure 2 moved to end of doc
cross ref to suppl material deleted

@@
 Attentional control were assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
-For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).
+For more detailed information on psychometric properties of the questionnaires, please see the supplementary material.
 
@@
 
-```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm.
-Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
-After, the discounting procedure took place.
-All three regulation strategies were compared pairwise.
-Before the last block, participants could decide which regulation strategy they wanted to reapply.
-Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
-knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
-```
-
 ### 2.3.3 Stimuli
@@
 Therefore, we aimed to collect data of $N=120$ participants, about $50%$ more data sets, than necessary.
-Detailed information on power calculation for each hypothesis can be found in the [design table](#DesignTable).
+Detailed information on power calculation for each hypothesis can be found in the design table.
 

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
prepareing submission
moved figures to end of doc

@@
 The authors declare no competing interests.
-<!--
-```{=tex}
-\newpage
-\setcounter{figure}{0}
+
+# Figures
+
+```{r ResponsePatterns, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualization of two response patterns.
+In the top half, the person has a clear preference for one of the three strategies.
+In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
+This pattern can be represented by our paradigm.
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
+include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Paradigm_Scheme_T2.png" ))
 ```
 
-```{r child = "Figures.Rmd"}
+```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm.
+Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
+Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
+After, the discounting procedure took place.
+All three regulation strategies were compared pairwise.
+Before the last block, participants could decide which regulation strategy they wanted to reapply.
+Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))
 ```
--->
-# Design Table {#DesignTable}
 
-\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
+```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings visualized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
+```
 
-\newpage
-
-```{r child = "Supplement.Rmd"}
+```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block.
+Each dot indicates SV of one participant, the colours indicate their choice in last experimental block.
+The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
+$N=120$.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
 ```

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
preparing submission
figures moved to end of doc
removed cross ref to supplement

@@
 We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
-Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \@ref(tab:SupplEffectArousalView) to \@ref(tab:SupplEffectLevView and Figures \@ref(fig:SupplFigArousalView) to \@ref(fig:SupplFigLevView) in the [supplement]).
+Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables S.4 to S.6 and Figures S.1 to S.3 in the supplementary material).
 
@@
 We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc contrasts, please see Tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and Figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
+For detailed information on post-hoc contrasts, please see Tables S.7 to S.9 and Figures S.4 to S.6 in the supplementary material.
 
@@
 
-```{r FigSubjEffort, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSubjEffort.png"))
-```
 Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
@@
 
-```{r FigSVChoice, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Individual subjective values per ER strategy, grouped by choice in last experimental block.
-Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
-The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
-$N=120$.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "FigSVChoice.png"))
-```
-
 We then conducted an ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
@@
 However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
-Detailed information can be found in the [supplementary material](#SupplementExploratory).
+Detailed information can be found in the supplementary material.

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
knitted doc

@@
 This pattern can be represented by our paradigm.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.", fig.pos="H"}
 include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Paradigm_Scheme_T2.png" ))
@@
 Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license."}
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.", fig.pos="H"}
 knitr::include_graphics(here("06_Paper", "ER-ED", "ERED_Stage2", "figures", "Design_ER-ED.png"))

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
-In the top half, the person has a clear preference for one of the three strategies.
-In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
-This pattern can be represented by our paradigm.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:ResponsePatterns}
-\end{figure}
-
 The aim of the present study is to evaluate whether this paradigm is suitable for determining SVs of ER strategies.
@@
 Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
-For more detailed information on psychometric properties of the questionnaires, please see the \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.
+For more detailed information on psychometric properties of the questionnaires, please see the supplementary material.
 
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{Block design of the paradigm.
-Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
-Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
-After, the discounting procedure took place.
-All three regulation strategies were compared pairwise.
-Before the last block, participants could decide which regulation strategy they wanted to reapply.
-Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
-Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:DesignERED}
-\end{figure}
-
 \hypertarget{stimuli}{%
@@
 \) more data sets, than necessary.
-Detailed information on power calculation for each hypothesis can be found in the \protect\hyperlink{DesignTable}{design table}.
+Detailed information on power calculation for each hypothesis can be found in the design table.
 
@@
 We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.76 \times 10^{48}\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.05 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 251.32\)).
-Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables \ref{tab:SupplEffectArousalView} to @ref(tab:SupplEffectLevView and Figures \ref{fig:SupplFigArousalView} to \ref{fig:SupplFigLevView} in the {[}supplement{]}).
+Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables S.4 to S.6 and Figures S.1 to S.3 in the supplementary material).
 
@@
 We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 157.74\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.82 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
-For detailed information on post-hoc contrasts, please see Tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and Figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.
+For detailed information on post-hoc contrasts, please see Tables S.7 to S.9 and Figures S.4 to S.6 in the supplementary material.
 
@@
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSubjEffort} \caption{Subjective effort ratings vizalized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSubjEffort}
-\end{figure}
-
 Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
@@
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSVChoice} \caption{Individual subjective values per ER strategy, grouped by choice in last experimental block.
-Each dot indicates SV of one particpant, the colours indicate their choice in last experimental block.
-The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
-$N=120$.
-Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSVChoice}
-\end{figure}
-
 We then conducted an ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
@@
 However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
-Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.
+Detailed information can be found in the supplementary material.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Preece2020}{}}%
-\CSLLeftMargin{91. }%
-\CSLRightInline{Preece, D.
-A., Becerra, R., Robinson, K.
-\& Gross, J.
-J.
-\href{https://doi.org/10.1080/00223891.2018.1564319}{The emotion regulation questionnaire: Psychometric properties in general community samples}.
-\emph{J Pers Assess} \textbf{102}, 348--356 (2020).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{92. }%
-\CSLRightInline{Fleischhauer, M.
-\emph{et al.} \href{https://doi.org/10.1177/0146167209351886}{Same or different?
-{Clarifying} the relationship of need for cognition to personality and intelligence}.
-\emph{Personality \& Social Psychology Bulletin} \textbf{36}, 82--96 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2015}{}}%
-\CSLLeftMargin{93. }%
-\CSLRightInline{Fleischhauer, M., Strobel, A.
-\& Strobel, A.
-\href{https://doi.org/10.1027/1614-0001/a000161}{Directly and indirectly assessed {N}eed for {C}ognition differentially predict spontaneous and reflective information processing behavior}.
-\emph{Journal of Individual Differences} \textbf{36}, 101--109 (2015).}
-
 \end{CSLReferences}
@@
 The authors declare no competing interests.
-\# Design Table \{\#DesignTable\}
-
-\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
-
-\newpage
-
-\hypertarget{SupplementaryMaterial}{%
-\section{Supplementary Material}\label{SupplementaryMaterial}}
-
-\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
-\counterwithin{figure}{section}
-\counterwithin{table}{section}
-\setcounter{section}{19}
-\setcounter{figure}{0}
-\setcounter{table}{1}
-\newpage
-
-\hypertarget{SupplementQuestionnaires}{%
-\subsection{Detailed information on psychometric measures}\label{SupplementQuestionnaires}}
-
-\emph{WHO-5.} General psychological well-being was assessed using the WHO-5 scale\textsuperscript{45,46}.
-Five items such as ``Over the past 2 weeks I have felt calm and relaxed.'' are rated on a 6-point Likert scale raning from 0 (at no time) to 5 (all of the time).
-The German version of the scale showed a high internal consistency (Cronbach's \(\alpha=.92\))\textsuperscript{46}.
-
-\emph{Connor-Davidson Resilience Scale.} Resilience was assessed using the Connor-Davidson Resilience Scale (CD-RISC)\textsuperscript{47--49}.
-Ten items such as ``I am able to adapt to change.'' are rated on a scale from 0 (not true at all) to 4 (true nearly all the time).
-The 10-item version showed a high internal consistency (Cronbach's \(\alpha=.84\)) and a satisfactory retest-reliability of \(r_{tt}=.81\) across 6 months\textsuperscript{49}.
-
-\emph{Emotion Regulation Questionnaire.} Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
-The scale has items such as ``I keep my emotions to myself'' (ERQ-suppression - 4 items) and ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (ERQ-reappraisal - 6 items), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\))\textsuperscript{91}.
-
-\emph{FlexER Scale.} Flexible use of ER strategies is assessed using the FlexER Scale\textsuperscript{44} with items such as ``If I want to feel less negative emotions, I have several strategies to achieve this.'', which are answered on a 4-point scale ranging from ``strongly agree'' to ``strongly disagree''.
-Psychometric properties are currently under investigation.
-
-\emph{Implicit Theories Questionnaire.} Implicit theories of willpower in emotional control were assessed using the Implicit Theories Questionnaire of Bernecker and Job\textsuperscript{51}.
-Four items such as ``Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards.'' are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
-The questionnaire showed an internal consistency of Cronbach's \(\alpha=.87\)\textsuperscript{51}.
-
-\emph{Need for Cognition Scale.} Need for Cognition (NFC) was assessed with the 16-item short version of the German NFC scale\textsuperscript{52}.
-Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) are recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree) and are summed to the total NFC score.
-The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{52,92} and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks\textsuperscript{93}.
-
-\emph{Self-Regulation Scale.} As one measure of self-control, the Self-Regulation Scale (SRS)\textsuperscript{54} was used.
-The scale has 10 items (e.g., ``It is difficult for me to suppress thoughts that interfere with what I need to do.'', recoded) on a 4-point scale ranging from 1 (not at all true) to 4 (exactly true).
-It has high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{54}.
-
-\emph{Brief Self-Control Scale.} As a second measure of self-control, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56} was used.
-It comprises 13 items (e.g., ``I am good at resisting temptations'') with a 5-point rating scale ranging from 1 (not at all like me) to 5 (very much like me).
-The scale shows acceptable internal consistency (Cronbach's \(\alpha=.81\))\textsuperscript{56}.
-
-\emph{Barratt Impulsiveness Scale.} As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58} was used.
-Responses to each item (e.g., ``I am self-controlled.'', recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
-An internal consistency of Cronbach's \(\alpha=.74\) and a retest reliability of \(r_{tt}=.56\) for General Impulsiveness and \(r_{tt}=.66\) for Total Score across 6 month were reported\textsuperscript{58}.
-
-\emph{Attentional Control Scale.} Attentional control was measured using the Attentional Control Scale (ACS)\textsuperscript{59} with items such as ``My concentration is good even if there is music in the room around me''.
-The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
-An internal consistency of Cronbach's \(\alpha=.88\) was reported\textsuperscript{59}.
-
-\newpage
-
-\hypertarget{SupplementNV}{%
-\subsection{Test for normal distribution of predictor variables}\label{SupplementNV}}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:TabNVRatings}Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.}
-
-\begin{tabular}{lllll}
-\toprule
- & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{$W$} & \multicolumn{1}{c}{$p$}\\
-\midrule
-Arousal View Neu & 26.629 & 39.116 & 0.677 & <.001\\
-Arousal View Neg & 187.778 & 87.308 & 0.979 & 0.057\\
-Arousal Distraction & 158.129 & 92.492 & 0.972 & 0.014\\
-Arousal Distancing & 168.617 & 95.754 & 0.978 & 0.043\\
-Arousal Suppression & 163.957 & 87.165 & 0.980 & 0.073\\
-Effort View Neu & 18.147 & 27.372 & 0.651 & <.001\\
-Effort View Neg & 49.396 & 62.262 & 0.740 & <.001\\
-Effort Distraction & 208.465 & 96.149 & 0.983 & 0.132\\
-Effort Distancing & 158.259 & 99.505 & 0.969 & 0.007\\
-Effort Suppression & 189.800 & 92.338 & 0.983 & 0.123\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:TabNCEMG}Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.}
-
-\begin{tabular}{lllll}
-\toprule
- & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$} & \multicolumn{1}{c}{$W$} & \multicolumn{1}{c}{$p$}\\
-\midrule
-Corrugator View Neu & 0.041 & 6.991 & 0.046 & <.001\\
-Corrugator View Neg & 1.030 & 7.213 & 0.194 & <.001\\
-Corrugator Distraction & 0.004 & 7.668 & 0.040 & <.001\\
-Corrugator Distancing & 0.066 & 3.784 & 0.083 & <.001\\
-Corrugator Suppression & 0.246 & 1.924 & 0.354 & <.001\\
-Levator View Neu & 0.090 & 1.838 & 0.384 & <.001\\
-Levator View Neg & 0.580 & 3.198 & 0.429 & <.001\\
-Levator Distraction & -0.050 & 1.157 & 0.520 & <.001\\
-Levator Distancing & -0.027 & 0.917 & 0.481 & <.001\\
-Levator Suppression & 0.010 & 0.996 & 0.554 & <.001\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\newpage
-
-\hypertarget{SupplementEffectValence}{%
-\subsection{Post-hoc contrasts for effects of valence on subjective arousal and physiological responding}\label{SupplementEffectValence}}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:SupplEffectArousalView}Post-hoc contrasts for effects of valence on subjective arousal ratings in the active viewing conditions.}
-
-\footnotesize{
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neutral} - View_{negative}$ & -161.15 & 8.06 & 119.00 & -20.00 & <.001 & $3.22 \times 10^{36}$ & 0.77 & {}[0.72, 1.00]\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
+
+\hypertarget{figures}{%
+\section{Figures}\label{figures}}
 
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSubjArousalView} \caption{Subjective arousal ratings of the active viewing conditions visualized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:SupplFigArousalView}
+\includegraphics[width=\textwidth]{figures/Paradigm_Scheme_T2} \caption{Exemplary visualization of two response patterns.
+In the top half, the person has a clear preference for one of the three strategies.
+In the lower half, they have no clear preference and therefore show an inconsistent response pattern.
+This pattern can be represented by our paradigm.
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:ResponsePatterns}
 \end{figure}
 
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:SupplEffectCorrView}Post-hoc contrasts for effects of valence on Corrugator activity in the active viewing conditions.}
-
-\footnotesize{
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neutral} - View_{negative}$ & -0.27 & 0.05 & 117.00 & -5.27 & <.001 & $8.67 \times 10^{16}$ & 0.19 & {}[0.10, 1.00]\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigCorrView} \caption{Corrugator activity in mV during the active viewing conditions, visualized as boxplots.
-Dots represent individual Corrugator activity measures placed in 150 quantiles.}\label{fig:SupplFigCorrView}
+\includegraphics[width=\textwidth]{figures/Design_ER-ED} \caption{Block design of the paradigm.
+Every participant starts with two "active viewing" blocks continaing neutral (Block 1) and negative (Block 2) pictures.
+Order of the regulation blocks (Blocks 3, 4, and 5) was randomized between participants.
+After, the discounting procedure took place.
+All three regulation strategies were compared pairwise.
+Before the last block, participants could decide which regulation strategy they wanted to reapply.
+Subjective arousal and effort ratings were assessed after each block using a slider on screen with a continuous scale.
+Figure available at https://osf.io/vnj8x/, under a CC-BY4.0 license.}\label{fig:DesignERED}
 \end{figure}
 
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:SupplEffectLevView}Post-hoc contrasts for effects of valence on Levator activity in the active viewing conditions.}
-
-\footnotesize{
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neutral} - View_{negative}$ & -0.23 & 0.08 & 117.00 & -2.98 & <.001 & 188.72 & 0.07 & {}[0.01, 1.00]\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigLevView} \caption{Levator activity in mV during the active viewing conditions, visualized as boxplots.
-Dots represent individual Levator activity measures placed in 150 quantiles.}\label{fig:SupplFigLevView}
+\includegraphics[width=\textwidth]{figures/FigSubjEffort} \caption{Subjective effort ratings visualized as boxplots.
+Dots represent individual effort ratings placed in 150 quantiles.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSubjEffort}
 \end{figure}
 
-\newpage
-
-\hypertarget{SupplementEffectER}{%
-\subsection{Post-hoc contrasts for effects of ER strategies on subjective arousal and physiological responding}\label{SupplementEffectER}}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:SupplEffectArousalReg}Post-hoc contrasts for effects of ER strategies on subjective arousal ratings.}
-
-\footnotesize{
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neg} - Distraction$ & 29.649 & 6.680 & 357.000 & 4.439 & 0.000 & 168.484 & 0.05 & {}[0.02, 1.00]\\
-$View_{neg} - Distancing$ & 23.820 & 6.680 & 357.000 & 3.566 & 0.002 & 62.990 & 0.03 & {}[0.01, 1.00]\\
-$View_{neg} - Suppression$ & 19.161 & 6.680 & 357.000 & 2.869 & 0.026 & 1.965 & 0.02 & {}[0.00, 1.00]\\
-$Distraction - Distancing$ & -5.828 & 6.680 & 357.000 & -0.873 & 1.000 & 0.179 & 2.13e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -10.488 & 6.680 & 357.000 & -1.570 & 0.704 & 0.309 & 6.86e-03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & -4.659 & 6.680 & 357.000 & -0.698 & 1.000 & 0.135 & 1.36e-03 & {}[0.00, 1.00]\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigSubjArousalReg} \caption{Subjective arousal ratings visualized as boxplots.
-Dots represent individual effort ratings placed in 150 quantiles.}\label{fig:SupplFigArousalReg}
+\includegraphics[width=\textwidth]{figures/FigSVChoice} \caption{Individual subjective values per ER strategy, grouped by choice in last experimental block.
+Each dot indicates SV of one participant, the colours indicate their choice in last experimental block.
+The scatter has a horizontal jitter of 0.40 and a vertical jitter of 0.05.
+$N=120$.
+Figure available at https://osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:FigSVChoice}
 \end{figure}
 
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:SupplEffectCorrReg}Post-hoc contrasts for effects of ER strategies on Corrugator activity}
-
-\footnotesize{
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neg} - Distraction$ & 0.178 & 0.037 & 351.000 & 4.788 & 0.000 & 21,919.73 & 0.06 & {}[0.03, 1.00]\\
-$View_{neg} - Distancing$ & 0.189 & 0.037 & 351.000 & 5.091 & 0.000 & 139,814.01 & 0.07 & {}[0.03, 1.00]\\
-$View_{neg} - Suppression$ & 0.210 & 0.037 & 351.000 & 5.669 & 0.000 & $1.84 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
-$Distraction - Distancing$ & 0.011 & 0.037 & 351.000 & 0.303 & 1.000 & $3.77 \times 10^{-2}$ & 2.61e-04 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & 0.033 & 0.037 & 351.000 & 0.881 & 1.000 & $8.02 \times 10^{-2}$ & 2.21e-03 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.021 & 0.037 & 351.000 & 0.578 & 1.000 & $4.79 \times 10^{-2}$ & 9.51e-04 & {}[0.00, 1.00]\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigCorrReg} \caption{Corrugator activity in mV visualized as boxplots.
-Dots represent individual Levatorr activity measures placed in 150 quantiles.}\label{fig:SupplFigCorrReg}
-\end{figure}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:SupplEffectLevReg}Post-hoc contrasts for effects of ER strategies on Levator activity}
-
-\footnotesize{
-
-\begin{tabular}{lllllllll}
-\toprule
-Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
-\midrule
-$View_{neg} - Distraction$ & 0.336 & 0.050 & 351.000 & 6.731 & 0.000 & $2.02 \times 10^{11}$ & 0.11 & {}[0.07, 1.00]\\
-$View_{neg} - Distancing$ & 0.282 & 0.050 & 351.000 & 5.659 & 0.000 & $3.99 \times 10^{7}$ & 0.08 & {}[0.04, 1.00]\\
-$View_{neg} - Suppression$ & 0.318 & 0.050 & 351.000 & 6.370 & 0.000 & $8.60 \times 10^{10}$ & 0.10 & {}[0.06, 1.00]\\
-$Distraction - Distancing$ & -0.053 & 0.050 & 351.000 & -1.072 & 1.000 & 0.22 & 3.26e-03 & {}[0.00, 1.00]\\
-$Distraction - Suppression$ & -0.018 & 0.050 & 351.000 & -0.361 & 1.000 & $3.91 \times 10^{-2}$ & 3.70e-04 & {}[0.00, 1.00]\\
-$Distancing - Suppression$ & 0.035 & 0.050 & 351.000 & 0.711 & 1.000 & $9.86 \times 10^{-2}$ & 1.44e-03 & {}[0.00, 1.00]\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{figures/FigLevReg} \caption{Levator activity in mV visualized as boxplots.
-Dots represent individual Levator activity measures placed in 150 quantiles.}\label{fig:SupplFigLevReg}
-\end{figure}
-
-\newpage
-
-\hypertarget{exploratory-analysis-association-between-svs-and-self-control-and-nfc}{%
-\subsection{Exploratory analysis: Association between SVs and self-control and NFC}\label{exploratory-analysis-association-between-svs-and-self-control-and-nfc}}
-
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:TabExp}Exploratory analysis: Results of MLM predicting SVs of ER strategies with level 2 predictors self-control and NFC.}
-
-\begin{tabular}{llllll}
-\toprule
-Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
-\midrule
-Intercept & $8.03 \times 10^{-1}$ & 0.011 & 0.000 &  & 0.112\\
-Effort & $-6.93 \times 10^{-4}$ & 0.000 & 0.000 & 0.036 & \\
-Utility & $1.44 \times 10^{-3}$ & 0.000 & 0.000 & 0.197 & \\
-Corrugator activity & $7.54 \times 10^{-3}$ & 0.004 & 0.034 & 0.001 & \\
-Self-Control & $2.44 \times 10^{-2}$ & 0.012 & 0.044 & 0.002 & \\
-NFC & $7.58 \times 10^{-4}$ & 0.001 & 0.436 & 0.002 & \\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \end{document}

### 2023-04-20 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
replaced protocol registration link
corrected BF10 papaja paste error

@@
 
-The Stage 1 Registered Report protocol has been approved and is available at [osf.io/qa2bg/](https://osf.io/qa2bg/).
+The Stage 1 Registered Report protocol has been approved and is available at [osf.io/cpxth/](https://osf.io/cpxth).
 
@@
 
-The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r paste(unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$level, split='} \\pm', fixed=TRUE))[1],"}$")`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r paste(unlist(strsplit(apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian, split='} \\pm', fixed=TRUE))[1],"}$")`).
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.

### 2023-04-20 06_Paper/COG-ED/Stage 2/Manuscript.tex
replaced protocol registration link
corrected BF10 papaja paste error

@@
 
-The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/qa2bg/}{osf.io/qa2bg/}.
+The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/cpxth}{osf.io/cpxth/}.
 
@@
 
-The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\) \}\$) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\) \}\().
-Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\)t(114) = -2.15\$, \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\)) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\)).
+Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\(t(114) = -2.15\), \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
 Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Figure~\ref{fig:h3b-plot}).

### 2023-04-20 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
typo

@@
 There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
-Post-hoc tests for the main effect of level showed that Svs were lower for the more difficult $n$-back level in each paired contrast except for 1- versus 2-back.
+Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult $n$-back level in each paired contrast except for 1- versus 2-back.
 Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (`r apa_print(pairs(explor_emm_interact))$full_result$X4_High_low`).

### 2023-04-20 06_Paper/ER-ED/ERED_Stage2/method.Rmd
changed link
typo

@@
 To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003; @Campbell-Sills2007; @Sarubin2015] was used.
-Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
+Habitual use of ER was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
 Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
@@
 
-The Stage 1 Registered Report protocol has been approved and is available at [osf.io/d6sc9/](https://osf.io/d6sc9/).
+The Stage 1 Registered Report protocol has been approved and is available at [https://osf.io/fn9bt](https://osf.io/fn9bt).

### 2023-04-20 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

@@
 {}{\PatchFailed}
-\keywords{emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography\newline\indent Word count: 9432}
+\keywords{emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography}
 \usepackage{lineno}
@@
 To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{47--49} was used.
-Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
+Habitual use of ER was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
 Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
@@
 
-The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/d6sc9/}{osf.io/d6sc9/}.
+The Stage 1 Registered Report protocol has been approved and is available at \url{https://osf.io/fn9bt}.
 

### 2023-04-21 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added software versions

--- 2023-04-20 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
@@
 The paradigm was written and presented using *Psychopy*[@Peirce2019].
-We used *R*[@RCT2020] with *R Studio*[@RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all our analyses.
+We used *R* (Version 4.2.0)[@RCT2020] with *R Studio* (Version 2022.12.0)[@RStudioTeam2020] with the main packages *papaja* (Version 0.1.1)[@Aust2020], *afex* (Version 1.2-1)[@Singmann2021], and *BayesFactor* (Version 0.9.12-4.4)[@Morey2021] for all our analyses.
 

### 2023-04-21 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

@@
 To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the \(lmerTest\) package\textsuperscript{67}.
-First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV was coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV was coded as 1.
 Restricted maximum likelihood (REML) was applied to fit the model.

### 2023-04-21 06_Paper/ER-ED/ERED_Stage2/method.Rmd

@@
 To explore the association between subjective effort (H5a), subjective arousal (H5b), subjective utility (H5c), and physiological responding (H5d,e) on SVs, a multilevel model (MLM) was specified using the $lmerTest$ package[@Kuznetsova2017].
-First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV will be coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV will be coded as 1.
+First, ER strategies were recoded and centered for each subject according to their individual SVs: The strategy with the highest SV was coded as -1, the strategy with the second highest SV 0, and the strategy with the lowest SV was coded as 1.
 Restricted maximum likelihood (REML) was applied to fit the model.

### 2023-04-21 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed code chunk options

@@
 
-```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
+```{r}
+#| label: setup
+#| echo: false
+#| message: false
+#| warning: false
 
@@
 
-```{r H1b-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
+```{r}
+#| label: H1b-contrasts
+#| echo: false
+#| message: false
+#| warning: false
+
 apa_table(
@@
 
-```{r H2a-contrasts, echo=FALSE, message=FALSE, warning=FALSE}
+```{r}
+#| label: H2a-contrasts
+#| echo: false
+#| message: false
+#| warning: false
+
 apa_table(
@@
 
-```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
+```{r}
+#| label: H2b-results
+#| echo: false
+#| message: false
+#| warning: false
+
 apa_table(h2b_result.table,

### 2023-04-24 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
alignment of table 1

@@
 
-\begin{lltable}
-
-\begin{longtable}{rccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.}\\
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:TabDescr}$M \pm SD$ of subjective arousal, subjetive effort, subjective utility, corrugator activity, and levator activity for each condition.}
+
+\begin{tabular}{p{2.5cm}p{2.5cm}p{2.5cm}p{2.5cm}p{2.5cm}p{2.5cm}}
 \toprule
@@
 \bottomrule
-\end{longtable}
-
-\end{lltable}
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2023-04-24 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
alignment of table 1

@@
   placement = "H",
-  align = c("r","c","c","c","c","c"),
-  landscape = TRUE)
+  align = c("p{2.5cm}", rep("p{2.5cm}", ncol(df.descr))),
+  landscape = FALSE)
 ```

### 2023-04-24 06_Paper/COG-ED/Stage 2/Manuscript.tex

@@
 The paradigm was written and presented using \emph{Psychopy}\textsuperscript{19}.
-We used \emph{R}\textsuperscript{20} with \emph{R Studio}\textsuperscript{21} with the main packages \emph{afex}\textsuperscript{22} and \emph{BayesFactor}\textsuperscript{23} for all our analyses.
+We used \emph{R} (Version 4.2.0)\textsuperscript{20} with \emph{R Studio} (Version 2022.12.0)\textsuperscript{21} with the main packages \emph{papaja} (Version 0.1.1)\textsuperscript{22}, \emph{afex} (Version 1.2-1)\textsuperscript{23}, and \emph{BayesFactor} (Version 0.9.12-4.4)\textsuperscript{24} for all our analyses.
 
@@
 
-Healthy participants aged 18 to 30~years were recruited using the software \emph{ORSEE}\textsuperscript{24}.
+Healthy participants aged 18 to 30~years were recruited using the software \emph{ORSEE}\textsuperscript{25}.
 Participants completed the personality questionnaires online and then visited the lab for two sessions one week apart.
-NFC was assessed using the 16-item short form of the Need for Cognition Scale\textsuperscript{25,26}.
+NFC was assessed using the 16-item short form of the Need for Cognition Scale\textsuperscript{26,27}.
 Responses to each item (e.g., ``Thinking is not my idea of fun'', recoded) were recorded on a 7-point Likert scale.
-The NFC scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{26,27}.
+The NFC scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\))\textsuperscript{27,28}.
 Several other personality questionnaires were used in this study but are the topic of the Registered Report for the second lab session\textsuperscript{17}.
@@
 The levels were referred to by color (1-back: black, 2-back: red, 3-back: blue, 4-back: green) to avoid anchor effects in the effort discounting procedure.
-To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)\textsuperscript{28}, where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
+To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)\textsuperscript{29}, where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
 At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this \(n\)-back level.
@@
 The paradigm followed the same structure of task and effort discounting procedure, but participants could decide which strategy they wanted to reapply in the last block.
-Study data was collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{29,30}.
+Study data was collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden\textsuperscript{30,31}.
 
@@
 The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and \(n\)-back level influencing SVs.
-Sample size analysis with \emph{G*Power}\textsuperscript{31,32} indicated that we should collect data from at least 72 participants, assuming \(\alpha=.05\) and \(\beta=.95\).
+Sample size analysis with \emph{G*Power}\textsuperscript{32,33} indicated that we should collect data from at least 72 participants, assuming \(\alpha=.05\) and \(\beta=.95\).
 However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of \(d=-0.32\) of emotion regulation on facial muscle activity with \(\alpha=.05\) and \(\beta=.95\).
@@
 No data was replaced.
-The performance measure \(d'\) was computed as the difference of the \emph{z}-transformed hit rate and the \emph{z}-transformed false alarm rate\textsuperscript{33}.
-Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100~ms, as the relevant cognitive processes cannot have been completed before\textsuperscript{34,35}.
-Aggregated RT values were described using the median and the median of absolute deviation (\(MAD\)) as robust estimates of center and variability, respectively\textsuperscript{36}.
-Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior\textsuperscript{37,38}.
-To test our hypotheses, we performed a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results\textsuperscript{39}.
+The performance measure \(d'\) was computed as the difference of the \emph{z}-transformed hit rate and the \emph{z}-transformed false alarm rate\textsuperscript{34}.
+Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100~ms, as the relevant cognitive processes cannot have been completed before\textsuperscript{35,36}.
+Aggregated RT values were described using the median and the median of absolute deviation (\(MAD\)) as robust estimates of center and variability, respectively\textsuperscript{37}.
+Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior\textsuperscript{38,39}.
+To test our hypotheses, we performed a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results\textsuperscript{40}.
 
@@
 Second, we estimated a random slopes model of \(n\)-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
-As Mussel et al.\textsuperscript{40} could show, participants with high versus low NFC not only have a more shallow decline in performance with higher \(n\)-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
+As Mussel et al.\textsuperscript{41} could show, participants with high versus low NFC not only have a more shallow decline in performance with higher \(n\)-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
 We controlled for performance, i.e., \(d'\) (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
@@
 \]
-Level-1-predictors were centered within cluster as recommended by Enders \& Tofighi\textsuperscript{41}.
+Level-1-predictors were centered within cluster as recommended by Enders \& Tofighi\textsuperscript{42}.
 By this, the model yields interpretable parameter estimates.
@@
 This was done by excluding all data points with absolute standardized residuals above 3 SD.
-As effect size measures, we calculated pseudo \(R^{2}\) for our model and \(f^{2}\) to estimate the effect of \(n\)-back level according to Lorah\textsuperscript{42}.
+As effect size measures, we calculated pseudo \(R^{2}\) for our model and \(f^{2}\) to estimate the effect of \(n\)-back level according to Lorah\textsuperscript{43}.
 
@@
 Post-hoc tests were computed depending on which effect reached significance at \(p<.01\).
-To ensure the validity of this association, we conducted a specification curve analysis\textsuperscript{43}, which included 63 possible preprocessing pipelines of the RT data.
+To ensure the validity of this association, we conducted a specification curve analysis\textsuperscript{44}, which included 63 possible preprocessing pipelines of the RT data.
 These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3~\(MAD\) from the median, RTs below 100~or~200~ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within \(n\)-back levels).
@@
 
-The results of each analysis was assessed on the basis of both \(p\)-value and the Bayes factor \(BF_{10}\), calculated with the \emph{BayesFactor} package\textsuperscript{23} using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{ttestBF}.
-We considered a \(BF_{10}\) close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a \(BF_{10}\) close to or below .33/.10 as moderate/strong evidence for the null hypothesis\textsuperscript{44}.
+The results of each analysis was assessed on the basis of both \(p\)-value and the Bayes factor \(BF_{10}\), calculated with the \emph{BayesFactor} package\textsuperscript{24} using the default prior widths of the functions \emph{anovaBF}, \emph{lmBF} and \emph{ttestBF}.
+We considered a \(BF_{10}\) close to or above 3/10 as moderate/strong evidence for the alternative hypothesis, and a \(BF_{10}\) close to or below .33/.10 as moderate/strong evidence for the null hypothesis\textsuperscript{45}.
 
@@
 Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
-The final model had an effect size of \(f^{2}=\) 0.64 for the \(n\)-back levels and \(f^{2}=\) 0.04 for \(d'\), which are considered large and small, respectively\textsuperscript{45}.
+The final model had an effect size of \(f^{2}=\) 0.64 for the \(n\)-back levels and \(f^{2}=\) 0.04 for \(d'\), which are considered large and small, respectively\textsuperscript{46}.
 This means that the \(n\)-back level explained 64.20\% and \(d'\) explained 3.95\% of variance in SVs relative to the unexplained variance, respectively.
@@
 There was no main effect of NFC group (\(F(1, 114) = 2.63\), \(p = .108\), \(\hat{\eta}^2_G = .007\), 90\% CI \([.000, .053]\), \(2.95 \times 10^{-1}\)), but a main effect of the \(n\)-back level (\(F(2.01, 229.39) = 67.39\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(2.70 \times 10^{30}\)) and an interaction (\(F(2.01, 229.39) = 3.24\), \(p = .041\), \(\hat{\eta}^2_G = .020\), 90\% CI \([.000, .044]\)).
-Post-hoc tests for the main effect of level showed that Svs were lower for the more difficult \(n\)-back level in each paired contrast except for 1- versus 2-back.
+Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult \(n\)-back level in each paired contrast except for 1- versus 2-back.
 Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (\(\Delta M = 0.11\), 95\% CI \([0.01, 0.22]\), \(t(114) = 2.13\), \(p = .036\)).
@@
 Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where \(d'\) would decline and RT would remain stable.
-And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before\textsuperscript{46} and both show different associations with various measures of intelligence\textsuperscript{4}, suggesting that they should always be reported as separate indices.
+And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before\textsuperscript{47} and both show different associations with various measures of intelligence\textsuperscript{4}, suggesting that they should always be reported as separate indices.
 Additionally, \(d'\) might not have differed across \(n\)-back levels because the manipulation of task load is not strictly continuous.
@@
 The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more inter-individual variance for 3- and 4-back.
-Thomson and Oppenheimer\textsuperscript{47} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
+Thomson and Oppenheimer\textsuperscript{48} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
 For example, the \(n\)-back task is likely not a continuous manipulation of task load, as discussed above.
-However, the declining logistic curve is similar to the sigmoidal curve that had the best fit in a different effort paradigm\textsuperscript{48}, which the authors explained with the low effect of low energy costs, suggesting there are still common features of effort across different tasks and domains.
+However, the declining logistic curve is similar to the sigmoidal curve that had the best fit in a different effort paradigm\textsuperscript{49}, which the authors explained with the low effect of low energy costs, suggesting there are still common features of effort across different tasks and domains.
 The MLM with the logistic contrast showed that the \(n\)-back level explained the majority of variance in SVs, while the performance measure \(d'\) also explained some variance in SVs, albeit less.
@@
 Interestingly, the curve of median RT betas in Figure~\ref{fig:sca-plot}a mirrored the rectangular pipeline indicators in the transformation rows of Figure~\ref{fig:sca-plot}b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
-As Fernandez et al.\textsuperscript{49} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
+As Fernandez et al.\textsuperscript{50} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
 Our data seems to corroborate this finding for \(n\)-back tasks as well.
@@
 This was also supported by the fact that higher \(n\)-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
-Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmitt et al.~(2013)\textsuperscript{50} and Blum et al.~(2018)\textsuperscript{51} in the same-named NIPS model.
+Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmitt et al.~(2013)\textsuperscript{51} and Blum et al.~(2018)\textsuperscript{52} in the same-named NIPS model.
 The NIPS model describes behaviour as a function of situational affordance which is mediated by personality traits.
@@
 According to the NIPS model, we can expect the SVs of participants with higher and lower NFC to converge again in levels of \(n>4\), since behavioural variability decreases when situational affordance is high.
-An investigation of this relationship using the COG-ED paradigm\textsuperscript{7} had been encouraged by Strobel et al.\textsuperscript{52} based on their findings on demand avoidance and cognitive effort investment.
-With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model\textsuperscript{50,51} and should be tested further in a setting with \(n\)-back levels exceeding \(n=4\).
+An investigation of this relationship using the COG-ED paradigm\textsuperscript{7} had been encouraged by Strobel et al.\textsuperscript{53} based on their findings on demand avoidance and cognitive effort investment.
+With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model\textsuperscript{51,52} and should be tested further in a setting with \(n\)-back levels exceeding \(n=4\).
 
@@
 One might also argue that the 2€ reward range was not large enough to be an incentive for effort expenditure.
-However, findings by Bialaszek et al.\textsuperscript{53} suggest that participants are actually more sensitive to effort when the reward is small.
+However, findings by Bialaszek et al.\textsuperscript{54} suggest that participants are actually more sensitive to effort when the reward is small.
 Nevertheless, we exceeded the largest required sample size by 2.20 times, which gives our analyses high statistical power.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Aust2020}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Aust, F. \& Barth, M. \emph{\href{https://github.com/crsh/papaja}{{papaja}: {Create} {APA} manuscripts with {R Markdown}}}. (2020).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Singmann2021}{}}%
-\CSLLeftMargin{22. }%
+\CSLLeftMargin{23. }%
 \CSLRightInline{Singmann, H., Bolker, B., Westfall, J., Aust, F. \& Ben-Shachar, M. S. \emph{\href{https://CRAN.R-project.org/package=afex}{Afex: {A}nalysis of factorial experiments}}. (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Morey2021}{}}%
-\CSLLeftMargin{23. }%
+\CSLLeftMargin{24. }%
 \CSLRightInline{Morey, R. D. \& Rouder, J. N. \emph{\href{https://CRAN.R-project.org/package=BayesFactor}{{BayesFactor}: {Computation} of {Bayes} factors for common designs}}. (2021).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Greiner2015}{}}%
-\CSLLeftMargin{24. }%
+\CSLLeftMargin{25. }%
 \CSLRightInline{Greiner, B.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Cacioppo1984}{}}%
-\CSLLeftMargin{25. }%
+\CSLLeftMargin{26. }%
 \CSLRightInline{Cacioppo, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bless1994}{}}%
-\CSLLeftMargin{26. }%
+\CSLLeftMargin{27. }%
 \CSLRightInline{Bless, H., Wänke, M., Bohner, G., Fellhauer, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fleischhauer2010}{}}%
-\CSLLeftMargin{27. }%
+\CSLLeftMargin{28. }%
 \CSLRightInline{Fleischhauer, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Hart1988}{}}%
-\CSLLeftMargin{28. }%
+\CSLLeftMargin{29. }%
 \CSLRightInline{Hart, S.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Harris2009}{}}%
-\CSLLeftMargin{29. }%
+\CSLLeftMargin{30. }%
 \CSLRightInline{Harris, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Harris2019}{}}%
-\CSLLeftMargin{30. }%
+\CSLLeftMargin{31. }%
 \CSLRightInline{Harris, P.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Faul2007}{}}%
-\CSLLeftMargin{31. }%
+\CSLLeftMargin{32. }%
 \CSLRightInline{Faul, F., Erdfelder, E., Lang, A.-G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Faul2009}{}}%
-\CSLLeftMargin{32. }%
+\CSLLeftMargin{33. }%
 \CSLRightInline{Faul, F., Erdfelder, E., Buchner, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Macmillan1990}{}}%
-\CSLLeftMargin{33. }%
+\CSLLeftMargin{34. }%
 \CSLRightInline{Macmillan, N.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Whelan2008}{}}%
-\CSLLeftMargin{34. }%
+\CSLLeftMargin{35. }%
 \CSLRightInline{Whelan, R. \href{https://doi.org/10.1007/BF03395630}{Effective analysis of reaction time data}. \emph{The Psychological Record} \textbf{58}, 475--482 (2008).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Berger2021}{}}%
-\CSLLeftMargin{35. }%
+\CSLLeftMargin{36. }%
 \CSLRightInline{Berger, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lachaud2011}{}}%
-\CSLLeftMargin{36. }%
+\CSLLeftMargin{37. }%
 \CSLRightInline{Lachaud, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Dutilh2012}{}}%
-\CSLLeftMargin{37. }%
+\CSLLeftMargin{38. }%
 \CSLRightInline{Dutilh, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Houtman2012}{}}%
-\CSLLeftMargin{38. }%
+\CSLLeftMargin{39. }%
 \CSLRightInline{Houtman, F., Castellar, E.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Singmann2019}{}}%
-\CSLLeftMargin{39. }%
+\CSLLeftMargin{40. }%
 \CSLRightInline{Singmann, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Mussel2016}{}}%
-\CSLLeftMargin{40. }%
+\CSLLeftMargin{41. }%
 \CSLRightInline{Mussel, P., Ulrich, N., Allen, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Enders2007}{}}%
-\CSLLeftMargin{41. }%
+\CSLLeftMargin{42. }%
 \CSLRightInline{Enders, C.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Lorah2018}{}}%
-\CSLLeftMargin{42. }%
+\CSLLeftMargin{43. }%
 \CSLRightInline{Lorah, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Simonsohn2020}{}}%
-\CSLLeftMargin{43. }%
+\CSLLeftMargin{44. }%
 \CSLRightInline{Simonsohn, U., Simmons, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wetzels2015}{}}%
-\CSLLeftMargin{44. }%
+\CSLLeftMargin{45. }%
 \CSLRightInline{Wetzels, R., Ravenzwaaij, D. van \& Wagenmakers, E.-J. Bayesian analysis. 1--11 (2015) doi:\href{https://doi.org/10.1002/9781118625392.wbecp453}{10.1002/9781118625392.wbecp453}.}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Cohen1992}{}}%
-\CSLLeftMargin{45. }%
+\CSLLeftMargin{46. }%
 \CSLRightInline{Cohen, J. \href{https://doi.org/10.1037/0033-2909.112.1.155}{A power primer.} \emph{Psychological Bulletin} \textbf{112}, 155--159 (1992).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Meule2017}{}}%
-\CSLLeftMargin{46. }%
+\CSLLeftMargin{47. }%
 \CSLRightInline{Meule, A. \href{https://doi.org/10.3389/fpsyg.2017.00352}{Reporting and interpreting working memory performance in n-back tasks}. \emph{Frontiers in Psychology} \textbf{8}, (2017).}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Thomson2022}{}}%
-\CSLLeftMargin{47. }%
+\CSLLeftMargin{48. }%
 \CSLRightInline{Thomson, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-KleinFluegge2015}{}}%
-\CSLLeftMargin{48. }%
+\CSLLeftMargin{49. }%
 \CSLRightInline{Klein-Flügge, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Fernandez2020}{}}%
-\CSLLeftMargin{49. }%
+\CSLLeftMargin{50. }%
 \CSLRightInline{Fernández, L.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Schmitt2013}{}}%
-\CSLLeftMargin{50. }%
+\CSLLeftMargin{51. }%
 \CSLRightInline{Schmitt, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Blum2018}{}}%
-\CSLLeftMargin{51. }%
+\CSLLeftMargin{52. }%
 \CSLRightInline{Blum, G.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Strobel2020}{}}%
-\CSLLeftMargin{52. }%
+\CSLLeftMargin{53. }%
 \CSLRightInline{Strobel, A.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{53. }%
+\CSLLeftMargin{54. }%
 \CSLRightInline{Białaszek, W., Marcowski, P.

### 2023-06-14 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added figure with motivation (moved fr supplement)

@@
 The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
-Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per $n$-back level.
+Figure \@ref(fig:motivation) shows the different motivations in the context of the SVs per $n$-back level.
+
+[FIGURE \@ref(fig:motivation) HERE]
 
@@
 
+```{r motivation, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
+$N=116$.
+'Other' opened up a free text field, in which participants gave responses such as 'I wanted fair pay for my effort', 'I wanted to have fun', and 'I wanted to maximize the reward'.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "motivation.png"))
+
+```
+
 ```{r sca-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the multi level model for each of the 63 preprocessing pipelines.

### 2023-06-14 06_Paper/COG-ED/Stage 2/Supplement.Rmd
move motivation figure to main manuscript

@@
 
-## Motivations for effort discounting behaviour
-
-```{r motiv-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
-$N=116$", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "motivation.png"))
-
-```
-
-\newpage
-
 ## Hypothesis 2a: Subjective values decline with increasing $n$-back level.

### 2023-06-14 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
moved SV text and added sv-by-pref figure

@@
 All SVs of each level were averaged to compute one "global" SV for each level.
-An rmANOVA with four different contrasts were computed to investigate the association of SVs and the $n$-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
+An rmANOVA with four different contrasts were computed to investigate the association of SVs and the $n$-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2) (Supplementary Figure S1).
 Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.
@@
 
+The different curves of SVs across $n$-back levels can be seen in Figure\ \@ref(fig:sv-by-pref), grouped into those participants who had an absolute preference for 1-back ($n=`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])`$), for 2-back ($n=`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])`$), for 3-back ($n=`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])`$), for 4-back ($n=`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])`$), or no absolute preference for any level ($n=`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))`$).
+While the majority of participants preferred the easiest level and showed a linear decline of SVs with increasing task-load, a considerable part of the sample preferred one of the more difficult $n$-back levels.
+
+[FIGURE \@ref(fig:sv-by-pref) HERE]
+
 When asking participants what motivated their decisions in the cognitive effort discounting paradigm, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
@@
 
-Figure\ \@ref(fig:nfcgroups-sv) shows the SVs per $n$-back level for participants with NFC scores above and below the median.
-There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across $n$-back levels.
-At the same time, there is a subtle separation of SVs across $n$-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
-Specifically, $n=`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])`$ participants had an absolute preference for 1-back, $n=`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])`$ for 2-back, $n=`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])`$ for 3-back, and $n=`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])`$ for 4-back.
-There were $n=`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))`$ participants who did not have an absolute preference for any $n$-back level, i.e. none of their SVs was 1.
-
-[FIGURE \@ref(fig:nfcgroups-sv) HERE]
-
 The median NFC was `r mediannfc`, with $n=`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ subjects below and $n=`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ above the median.
@@
 There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences (Figure\ \@ref(fig:h3ac-plot)a).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences (Supplementary Figure S2a).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.
-
-[FIGURE \@ref(fig:h3ac-plot) HERE]
 
@@
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.
-Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Figure\ \@ref(fig:h3b-plot)).
-
-[FIGURE \@ref(fig:h3b-plot) HERE]
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Supplementary Figure S3).
 
@@
 There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
-In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (Figure\ \@ref(fig:h3ac-plot)b).
+In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (Supplementary Figure S2b).
 Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), indicating that in the same way in which the SVs decreased more strongly from 2- to 3-back than from 1- to 2-back, the aversion increased more strongly.
@@
 The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
+Figure\ \@ref(fig:nfcgroups-sv) shows the SVs per $n$-back level for participants with NFC scores above and below the median.
+
+[FIGURE \@ref(fig:nfcgroups-sv) HERE]
 
@@
 
+```{r sv-by-pref, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level, grouped into those who had an absolute preference for 1-back, for 2-back, for 3-back, for 4-back, or no absolute preference for any level.
+The lines have a vertical jitter of 0.02.
+Smoothing of conditional means with Loess method.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "sv_by_pref.png"))
+
+```
+
 ```{r motivation, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
 $N=116$.
-'Other' opened up a free text field, in which participants gave responses such as 'I wanted fair pay for my effort', 'I wanted to have fun', and 'I wanted to maximize the reward'.
+'Other' opened up a free text field.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
@@
 ```
-
-```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
-Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
-NFC = Need for Cognition score.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3ac-plot.png"))
-
-```
-
-```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
-Colours indicate Need for Cognition (NFC) score above or below the median.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
-
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3b-plot.png"))
-
-```

### 2023-06-14 06_Paper/COG-ED/Stage 2/Supplement.Rmd
added contrast plot + h3ac + h3b plots

@@
 \includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}
+
+\newpage
+
+## Contrasts tested for in the repeated measures ANOVA
+
+```{r contrast-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Contrasts tested for in the repeated measures ANOVA that was used as a prerequisite for the multi level model of hypothesis 2b.
+Ascending quadratic (-1,1,1,-1), declining linear (3,1,-1,-3), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "contrasts.png"))
+
+```
 
@@
 
+```{r h3ac-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
+Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
+NFC = Need for Cognition score.
+$N=116$.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3ac-plot.png"))
+
+```
+
+\newpage
+
 ## Hypothesis 3b: Participants with higher NFC scores have lower NASA-TLX scores in every n-back level than participants with lower NFC scores.
@@
 )
+```
+
+\newpage
+
+```{r h3b-plot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="NASA-TLX sum scores for each $n$-back level.
+Colours indicate Need for Cognition (NFC) score above or below the median.
+$N=116$.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "h3b-plot.png"))
+
 ```

### 2023-06-14 06_Paper/COG-ED/Stage 2/Analysis.R
added panel for no pref

@@ -2006,33 +2006,45 @@ ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 10, height 
     ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
     scale_y_continuous(limits = c(0.05,1), breaks = c(0.2,0.4,0.6,0.8,1), oob = scales::rescale_none) +
     labs(x = "n-back level", y = "Subjective value") +
-    geom_text(x = 1.5, y = 0.1, label = paste("n =",length(unique(as.data.frame(data_SV %>% group_by(subject) %>% filter(any(level == 1 & sv == 1)))$subject)))) +
+    geom_text(x = 1.25, y = 0.1, hjust = 0,
+              label = paste("SV = 1 at 1-back\nn =",length(unique(as.data.frame(data_SV %>% group_by(subject) %>% filter(any(level == 1 & sv == 1)))$subject)))) +
     geom_smooth(inherit.aes = FALSE, aes(level, sv), color = "#c94b17", fill = "#ef7d00", span = 1)
   sv_plot2 <- ggplot2::ggplot(data_SV %>% group_by(subject) %>% filter(any(level == 2 & sv == 1)), aes(level, sv, group = subject)) +
     geom_line(alpha = .3, position=position_jitter(w = 0, h = 0.02)) +
     ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
     scale_y_continuous(limits = c(0.05,1), breaks = c(0.2,0.4,0.6,0.8,1), oob = scales::rescale_none) +
     labs(x = "n-back level", y = NULL) +
-    geom_text(x = 1.5, y = 0.1, label = paste("n =",length(unique(as.data.frame(data_SV %>% group_by(subject) %>% filter(any(level == 2 & sv == 1)))$subject)))) +
+    geom_text(x = 1.25, y = 0.1, hjust = 0,
+              label = paste("SV = 1 at 2-back\nn =",length(unique(as.data.frame(data_SV %>% group_by(subject) %>% filter(any(level == 2 & sv == 1)))$subject)))) +
     geom_smooth(inherit.aes = FALSE, aes(level, sv), color = "#c94b17", fill = "#ef7d00", span = 1)
[…]

### 2023-06-14 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added Massar 2019

@@
 For example, the $n$-back task is likely not a continuous manipulation of task load, as discussed above.
-However, the declining logistic curve is similar to the sigmoidal curve that had the best fit in a different effort paradigm[@KleinFluegge2015], which the authors explained with the low effect of low energy costs, suggesting there are still common features of effort across different tasks and domains.
+However, the declining logistic curve is similar to the sigmoidal curve that has been found for a physical[@KleinFluegge2015] and a cognitive effort paradigm[@Massar2019], suggesting there are common features of effort across different tasks and domains.
 The MLM with the logistic contrast showed that the $n$-back level explained the majority of variance in SVs, while the performance measure $d'$ also explained some variance in SVs, albeit less.

### 2023-06-15 06_Paper/COG-ED/Stage 2/Analysis.R
added slope analysis for explor2

@@ -2189,6 +2189,9 @@ explor2_rmanova <- as.data.frame(matrix(explor2_rmanova, nrow = 4, ncol = 6))
 explor2_rmanova <- cbind(explor2_rmanova,
                         format(effectsize::F_to_eta2(f = explor2_rmanova[,5], df = explor2_rmanova[,2],
                                                      df_error = explor2_rmanova[,4], ci = 0.95), digits = 2))
+explor2_BF_level <- BayesFactor::lmBF(formula = sv ~ level, whichRandom = "subject", data = explor_data, progress = FALSE)
+explor2_BF_nfc <- BayesFactor::lmBF(formula = sv ~ nfc, whichRandom = "subject", data = explor_data, progress = FALSE)
+explor2_BF_interact <- BayesFactor::lmBF(formula = sv ~ nfc:level, whichRandom = "subject", data = explor_data, progress = FALSE)
 
 # formatting
 
@@ -2200,7 +2203,16 @@ explor2_rmanova$`$p$`[explor2_rmanova$`$p$` == "0.000"] <- "<.001"
 
 ## post-hoc tests for slope differences
 
-explor2_emm <- emmeans::emtrends(lm(sv ~ nfc * level, data = explor_data), pairwise ~ level, var = "nfc")
+explor2_slopes <- emmeans::emtrends(lm(sv ~ nfc * level, data = explor_data), pairwise ~ level, var = "nfc")
+
+# formatting
+
+explor2_emm <- as.data.frame(explor2_slopes$contrasts)
+colnames(explor2_emm) <- c("$n$-back level", "Estimate", "$SE$", "$df$", "$t$", "$p$")
+explor2_emm$'$n$-back level' <- gsub("level", "", as.character(explor2_emm$'$n$-back level'))
+explor2_emm[ ,c("Estimate", "$SE$", "$t$", "$p$")] <- round(explor2_emm[ ,c("Estimate", "$SE$", "$t$", "$p$")], digits = 2)
+explor2_emm$`$p$` <- format(round(explor2_emm$`$p$`, digits = 3), nsmall = 2)
+
 
 # visualize the slopes
 
@@ -2214,7 +2226,7 @@ emmeans::emmip(lm(sv ~ nfc * level, data = explor_data), level ~ nfc, cov.reduce
   theme(legend.title = element_text())
 
 ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 5.5, height = 5, units = "in",
[…]

### 2023-06-15 06_Paper/COG-ED/Stage 2/Supplement.Rmd
put explor1 figure in supplement

@@
 ```
+
+\newpage
+
+```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
+$N=116$.
+The scatter has a horizontal jitter of 0.2.
+Smoothing of conditional means with Loess method.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
+
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfcgroups-sv.png"))
+
+```

### 2023-06-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
included explor2 results

@@
 
-# Exploratory analysis
+# Exploratory analyses
 
@@
 The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
-Figure\ \@ref(fig:nfcgroups-sv) shows the SVs per $n$-back level for participants with NFC scores above and below the median.
+Supplementary Figure S4 shows the SVs per $n$-back level for participants with NFC scores above and below the median.
 
-[FIGURE \@ref(fig:nfcgroups-sv) HERE]
+Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
+We computed an rmANOVA with the $n$-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
+Both the NFC score (`r apa_print(explor2_model)$full_result$nfc`, `r apa_print(explor2_BF_nfc)$statistic`) and the $n$-back level (`r apa_print(explor2_model)$full_result$level`, `r apa_print(explor2_BF_level)$statistic`) showed significant main effects, as well as a significant interaction (`r apa_print(explor2_model)$full_result$nfc_level`, `r apa_print(explor2_BF_interact)$statistic`).
+Analyzing the estimated marginal means of the linear trends for each $n$-back level indicated a significant difference between the slopes of 1-back and 4-back (`r apa_print(explor2_slopes$contrasts)$full_result$Level1_level4`), but not between any other two levels.
+Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure\ \@ref:nfccont-sv).
+
+[FIGURE \@ref(fig:nfccont-sv) HERE]
 
@@
 While the Stage 1 review process made the analyses as robust as possible, there were still unknown factors that should be addressed by future studies.
-For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups rather than a median split, or even more promising, as a continuous measure, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
+For instance, the differences between participants with higher and lower NFC should be investigated with extreme groups or as a continuous variable rather than with a median split, especially in academic samples where NFC can be expected to be higher on average and more narrow in range.
 To arrive at a sample with more balanced NFC scores, recruitment efforts should be focused on representative population samples and/or collecting data with an NFC-based stop rule.
@@
 Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
-We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction or a training next time.
+We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction and/or a training next time.
 And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
@@
 Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
-However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
+However, they did not have higher subjective values per se, which was due to our choice of median split and our assumption that these group differences would emerge in lower levels.
+The exploratory analysis showed that the predicted slope of subjective values depending on Need for Cognition scores differed between 1- and 4-back.
 In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for tasks with high discriminatory power and effort discounting paradigms with flexible, participant-centered mechanisms.
@@
 
-```{r nfcgroups-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
+```{r nfccont-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Predicted slopes of subjective values depending on individual Need for Cognition scores for each $n$-back level.
 $N=116$.
-The scatter has a horizontal jitter of 0.2.
-Smoothing of conditional means with Loess method.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
 
-  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfcgroups-sv.png"))
+  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "nfccont_sv.png"))
 

### 2023-06-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
incoporated suggestions on rephrasing conclusions

@@
 
-The different curves of SVs across $n$-back levels can be seen in Figure\ \@ref(fig:sv-by-pref), grouped into those participants who had an absolute preference for 1-back ($n=`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])`$), for 2-back ($n=`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])`$), for 3-back ($n=`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])`$), for 4-back ($n=`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])`$), or no absolute preference for any level ($n=`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))`$).
-While the majority of participants preferred the easiest level and showed a linear decline of SVs with increasing task-load, a considerable part of the sample preferred one of the more difficult $n$-back levels.
+The different curves of SVs across $n$-back levels can be seen in Figure\ \@ref(fig:sv-by-pref), grouped into those participants who had an SV of 1.0 for 1-back ($n=`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])`$), for 2-back ($n=`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])`$), for 3-back ($n=`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])`$), for 4-back ($n=`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])`$), or all SVs below 1.0, i.e.
+no absolute preference for any level ($n=`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))`$).
+While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult $n$-back levels.
+However, each panel in Figure\ \@ref(fig:sv-by-pref) contains curves of participants who had large differences between their four SVs and curves of participants who had a difference of less than 0.2 between their highest and their lowest SV, so preferring one level does not necessarily mean having a strong aversion against the others, regardless of difficulty level.
 
@@
 The declining logistic contrast had the highest effect estimate (`r apa_print(emmeans::contrast(hypothesis2a_emm, method = list("Declining Linear" = c(3,1,-1,-3),"Ascending Quadratic" = c(-1,1,1,-1),"Declining Logistic" = c(3,2,-2,-3),"Positively Skewed Normal" = c(1,2,-1,-2))))$statistic$DecliningLogistic`), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
+Based on the effect estimate, the ascending quadratic and the skewed normal contrasts were rejected in favour of the declining logistic contrast.
 
@@
 Analyzing the estimated marginal means of the linear trends for each $n$-back level indicated a significant difference between the slopes of 1-back and 4-back (`r apa_print(explor2_slopes$contrasts)$full_result$Level1_level4`), but not between any other two levels.
-Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure\ \@ref:nfccont-sv).
+Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure\ \@ref(fig:nfccont-sv)).
 
@@
 The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across $n$-back levels.
-The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more inter-individual variance for 3- and 4-back.
+The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also quite high, before declining more strongly for 3- and 4-back.
+Since the majority of participants preferred the easiest level, we rejected the ascending quadratic and skewed normal contrasts, which implied lower SVs for 1- than for 2-back.
+Figure\ \@ref(fig:sv-by-pref) suggests that those who prefer either 1- or 2-back have a slightly steeper discounting curve than those who prefer 3- or 4-back, meaning they have lower SVs for higher levels than those who prefer a higher level have for the easier levels.
+But as the figure also shows, there is great interindividual variability in the discounting patterns, regardless of which level has the highest SV.
+The fact that the majority of participants preferred lower over higher effort, but a minority showed the opposite pattern, is in line with previous research on cognitive effort by Kool et al.
+(2010)[-@Kool2010].
 Thomson and Oppenheimer[-@Thomson2022] argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
@@
 In the analysis of SV difference scores, the NFC group did not reach significance as a predictor.
-This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
-As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
+This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only registered analyses of the difference scores between 1- and 2-back and 2- and 3-back.
+As the exploratory analyses showed, a median split of NFC scores yielded a significant group difference in SVs for 4-back only, while predicting SVs with NFC as a continuous covariate showed a difference in the slopes of 1-back and 4-back.
 The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
@@
 This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
-Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmitt et al.
+Our data supports the notion of a Nonlinear Interaction between Person and Situation that has also been described by Schmitt et al.
 (2013)[-@Schmitt2013] and Blum et al.
@@
 Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an $n$-back task.
-The results showed that many participants indeed preferred a more or even the most difficult $n$-back level.
-Spanning the entire sample, these preferences took the shape of a declining logistic curve across $n$-back levels.
-While the subjective value declined with increasing levels, it increased with better performance as measured in $d'$, and was unaffected by the reaction time.
+Despite the fact that the task design allowed individuals to express a preference for higher over lower objective load levels, the overall subjective values took the shape of a declining logistic curve across $n$-back levels.
+The majority of participants showed a decline in subjective values at higher effort levels.
+A minority of participants deviated from this pattern and showed a clear preference for 2-, 3, or 4-back over 1-back.
+While the subjective values declined with increasing levels, they increased with better performance as measured in $d'$, and were unaffected by the reaction time.
 Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
 However, they did not have higher subjective values per se, which was due to our choice of median split and our assumption that these group differences would emerge in lower levels.
-The exploratory analysis showed that the predicted slope of subjective values depending on Need for Cognition scores differed between 1- and 4-back.
+The exploratory analyses showed that the predicted slope of subjective values depending on Need for Cognition scores differed between 1- and 4-back, but not between other levels.
 In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for tasks with high discriminatory power and effort discounting paradigms with flexible, participant-centered mechanisms.
@@
 ```{r nfccont-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Predicted slopes of subjective values depending on individual Need for Cognition scores for each $n$-back level.
+The slopes of 1-back and 4-back are different at $p=.01$.
 $N=116$.

### 2023-06-16 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
updated

@@
 Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure\ \@ref(fig:nfccont-sv)).
+The full results of this exploratory analysis of NFC as a continuous covariate can be found in Table S.18 and S.19 in the Supplementary Material.
 
@@
 
-```{r sv-by-pref, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level, grouped into those who had an absolute preference for 1-back, for 2-back, for 3-back, for 4-back, or no absolute preference for any level.
+```{r sv-by-pref, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values (SV) per $n$-back level, grouped into those who had an SV = 1 for 1-back, for 2-back, for 3-back, for 4-back, or no SV = 1 for any level.
 The lines have a vertical jitter of 0.02.

### 2023-06-16 06_Paper/COG-ED/Stage 2/Supplement.Rmd
updated

@@
 
-## Exploratory analyses
+## Exploratory analysis with NFC groups by median split
 
@@
   explor_contrasts_interact,
-  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjectvie values.",
+  caption = "Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjective values.",
   note = "The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median.
@@
 $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+\newpage
+
+## Exploratory analysis with NFC as a continuous covariate
+
+ANOVA (NFC scores standardized):
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  explor2_rmanova,
+  caption = "Result of the rmANOVA regarding the predictive power of the $n$-back level on the subjective values when including Need for Cognition scores as a centered continuous covariate.",
+  note = "NFC = Need for Cognition. $SE$ = standard error, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, $\\eta_{p}^{2}$ = partial eta squared, CI = confidence interval.",
+  escape = FALSE,
+  placement = "H"
+)
+```
+
+Estimated marginal means of the linear trends:
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE} 
+apa_table(
+  explor2_emm,
+  caption = "Paired contrast slope analysis as a follow up for the rmANOVA regarding the predictive power of the $n$-back level on the subjective values when including Need for Cognition scores as a centered continuous covariate.",
+  note = "The column $n$-back level contains the $n$ of the task levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.",
   escape = FALSE,

### 2023-06-16 06_Paper/COG-ED/Stage 2/Analysis.R
changed opacity in plot

@@ -1986,7 +1986,7 @@ ggsave(path = here("06_Paper","COG-ED","Stage 2","Figures"), width = 10, height 
 # plot showing SVs per level, colors depend on motivation
 
   ggplot2::ggplot(data_motiv, aes(level, sv, fill = as.factor(motivation), color = as.factor(motivation))) +
-    geom_smooth(alpha = .2, span = 1, size = 2) +
+    geom_smooth(alpha = .3, span = 1, size = 2) +
     ggprism::theme_prism(base_size = 12, base_line_size = 0.8, base_fontface = "plain", base_family = "sans") +
     scale_fill_manual(values = c("#f7a941","#f08262","#8acbc1","#84cfed","#94c356")) +
     scale_color_manual(values = c("#ef7d00","#cd1619","#00aca9","#0069b4","#65b32e"), name = "Motivation",

### 2023-06-16 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
implemented Christoph's comments

@@
 The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across $n$-back levels.
-The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also quite high, before declining more strongly for 3- and 4-back.
+The best fit was a declining logistic curve, reflecting that 1) the majority of participants preferred the easiest level, 2) 2-back was generally closer in preference to 1-back than 3-back was to 2-back, and 3) objective task load and subjective preference do not stand in a linear relationship.
 Since the majority of participants preferred the easiest level, we rejected the ascending quadratic and skewed normal contrasts, which implied lower SVs for 1- than for 2-back.
+The fact that the majority of participants preferred lower over higher effort, but a minority showed the opposite pattern, is in line with previous research on cognitive effort by Kool et al.
+(2010)[-@Kool2010].
+Importantly, having a paradigm that can accurately assess the preferences of the minority is necessary but not sufficient, because the interindividual variability is so high that it blurs effects on the group level.
 Figure\ \@ref(fig:sv-by-pref) suggests that those who prefer either 1- or 2-back have a slightly steeper discounting curve than those who prefer 3- or 4-back, meaning they have lower SVs for higher levels than those who prefer a higher level have for the easier levels.
 But as the figure also shows, there is great interindividual variability in the discounting patterns, regardless of which level has the highest SV.
-The fact that the majority of participants preferred lower over higher effort, but a minority showed the opposite pattern, is in line with previous research on cognitive effort by Kool et al.
-(2010)[-@Kool2010].
 Thomson and Oppenheimer[-@Thomson2022] argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
@@
 
-The majority of participants (`r round(100*((nrow(data_SV[data_SV$level==1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ %) had an absolute preference for 1-back over the other levels, but that also means that there were `r round(100*((nrow(data_SV[data_SV$level!=1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ % who had an absolute preference for 2-, 3-, or 4-back, and `r round(100*((length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1])))/nrow(data_quest)), digits = 1)`\ % who preferred no specific level over all others.
-It shows that when given the choice, there is a large number of participants who do not prefer the easiest level, confirming the necessity of an effort discounting paradigm that works independent of the objective task load.
+The majority of participants (`r round(100*((nrow(data_SV[data_SV$level==1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ %) had a preference for 1-back over the other levels, but that also means that there were `r round(100*((nrow(data_SV[data_SV$level!=1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ % who had a preference for 2-, 3-, or 4-back, and `r round(100*((length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1])))/nrow(data_quest)), digits = 1)`\ % who preferred no specific level over all others.
+It shows that when given the choice, there is a number of participants who do not prefer the easiest level, confirming the necessity of an effort discounting paradigm that works independent of the objective task load.
 The CAD paradigm provides the means to depict these preferences.
@@
 In the analysis of SV difference scores, the NFC group did not reach significance as a predictor.
-This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only registered analyses of the difference scores between 1- and 2-back and 2- and 3-back.
+Conceptually, this was likely due to the partial but not full overlap between self-reported and behavioural effort investment, which has also been found for a demand selection task[@Strobel2020].
+Another possible reason is the bandwidth of SVs of participants with NFC scores around the median, and the fact that the difference appeared most pronounced for 4-back, and we only registered analyses of the difference scores between 1- and 2-back and 2- and 3-back.
 As the exploratory analyses showed, a median split of NFC scores yielded a significant group difference in SVs for 4-back only, while predicting SVs with NFC as a continuous covariate showed a difference in the slopes of 1-back and 4-back.
@@
 A minority of participants deviated from this pattern and showed a clear preference for 2-, 3, or 4-back over 1-back.
+The CAD paradigm was able to depict the individual preference patterns for both those who do and do not prefer the lowest effort level.
 While the subjective values declined with increasing levels, they increased with better performance as measured in $d'$, and were unaffected by the reaction time.
@@
 
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
+This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
@@
 Smoothing of conditional means with Loess method.
+Transparent overlays depict the 95\\% confidence interval.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
@@
 
-```{r motivation, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
+```{r motivation, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Trajectories of subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
 $N=116$.
 'Other' opened up a free text field.
+Smoothing of conditional means with Loess method.
+Transparent overlays depict the 95\\% confidence interval.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

### 2023-06-29 06_Paper/COG-ED/Stage 2/Revision/Manuscript_Revised.tex
stage 2 revision commits

--- 2023-04-24 06_Paper/COG-ED/Stage 2/Manuscript.tex
@@
 
-Figure \ref{fig:cadparadigm} illustrates how different modifications of the COG-ED paradigm\textsuperscript{7} return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
+Figure 1 illustrates how different modifications of the COG-ED paradigm\textsuperscript{7} return SVs that do or do not reflect the true preference of a hypothetical participant, who likes 2-back most, 3-back less, and 1-back least (for reasons of clarity there are only three levels in the example).
 The COG-ED paradigm, which compares every more difficult level with 1-back sets the SV of 1-back to 1, regardless of the response pattern.
@@
 
-{[}FIGURE \ref{fig:cadparadigm} HERE{]}
+{[}FIGURE 1 HERE{]}
 
@@
 All SVs of each level were averaged to compute one ``global'' SV for each level.
-An rmANOVA with four different contrasts were computed to investigate the association of SVs and the \(n\)-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
+An rmANOVA with four different contrasts were computed to investigate the association of SVs and the \(n\)-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2) (Supplementary Figure S1).
 Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.
@@
 
+The different curves of SVs across \(n\)-back levels can be seen in Figure 2, grouped into those participants who had an SV of 1.0 for 1-back (\(n=71\)), for 2-back (\(n=18\)), for 3-back (\(n=9\)), for 4-back (\(n=13\)), or all SVs below 1.0, i.e.~no absolute preference for any level (\(n=5\)).
+While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult \(n\)-back levels.
+However, each panel in Figure 2 contains curves of participants who had large differences between their four SVs and curves of participants who had a difference of less than 0.2 between their highest and their lowest SV, so preferring one level does not necessarily mean having a strong aversion against the others, regardless of difficulty level.
+
+{[}FIGURE 2 HERE{]}
+
 When asking participants what motivated their decisions in the cognitive effort discounting paradigm, 11.2\% stated that they wanted to avoid boredom, 22.4\% stated that they wanted a challenge, 34.5\% stated that they wanted to avoid effort, and 4.3\% stated that they wanted to relax.
 The remaining 27.6\% of participants used the free text field and provided reasons such as ``I wanted a fair relation of effort and reward.'', ``I wanted the fun that I had in the more challenging levels.'', ``I wanted to maximize reward first and minimize effort second.'', or ``I did not want to perform poorly when I was being paid for it.''.
-Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per \(n\)-back level.
+Figure 3 shows the different motivations in the context of the SVs per \(n\)-back level.
+
+{[}FIGURE 3 HERE{]}
 
@@
 The declining logistic contrast had the highest effect estimate (\(t(345) = 12.97\), \(p < .001\)), suggesting a shallow decline of SVs between 1- and 2-back, and 3- and 4-back, respectively, and a steeper decline of SVs between 2- and 3-back.
+Based on the effect estimate, the ascending quadratic and the skewed normal contrasts were rejected in favour of the declining logistic contrast.
 
@@
 
-To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis (Figure~\ref{fig:sca-plot}).
-
-{[}FIGURE \ref{fig:sca-plot} HERE{]}
+To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis (Figure 4).
+
+{[}FIGURE 4 HERE{]}
 
@@
 
-Figure~\ref{fig:nfcgroups-sv} shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.
-There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across \(n\)-back levels.
-At the same time, there is a subtle separation of SVs across \(n\)-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
-Specifically, \(n=71\) participants had an absolute preference for 1-back, \(n=18\) for 2-back, \(n=9\) for 3-back, and \(n=13\) for 4-back.
-There were \(n=5\) participants who did not have an absolute preference for any \(n\)-back level, i.e.~none of their SVs was 1.
-
-{[}FIGURE \ref{fig:nfcgroups-sv} HERE{]}
-
 The median NFC was 16, with \(n=57\) subjects below and \(n=59\) above the median.
@@
 There was a main effect of the \(n\)-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56\)) nor an interaction of NFC group and \(n\)-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Figure~\ref{fig:h3ac-plot}a).
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Supplementary Figure S2a).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.
-
-{[}FIGURE \ref{fig:h3ac-plot} HERE{]}
 
@@
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\(t(114) = -2.15\), \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
-Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Figure~\ref{fig:h3b-plot}).
-
-{[}FIGURE \ref{fig:h3b-plot} HERE{]}
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Supplementary Figure S3).
 
@@
 There was a main effect of NFC group (\(F(1, 114) = 8.43\), \(p = .004\), \(\hat{\eta}^2_G = .043\), 90\% CI \([.003, .119]\), \(\mathrm{BF}_{\textrm{10}} = 14.26\)) and a main effect of the \(n\)-back level (\(F(1, 114) = 10.21\), \(p = .002\), \(\hat{\eta}^2_G = .034\), 90\% CI \([.000, .105]\), ), but no interaction (\(F(1, 114) = 2.59\), \(p = .110\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .058]\)).
-In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (\(t(114) = 2.90\), \(p = .004\)) (Figure~\ref{fig:h3ac-plot}b).
+In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (\(t(114) = 2.90\), \(p = .004\)) (Supplementary Figure S2b).
 Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was more negative than that of 1- and 2-back (\(t(114) = 3.20\), \(p = .002\)), indicating that in the same way in which the SVs decreased more strongly from 2- to 3-back than from 1- to 2-back, the aversion increased more strongly.
@@
 
-\hypertarget{exploratory-analysis}{%
-\section{Exploratory analysis}\label{exploratory-analysis}}
+\hypertarget{exploratory-analyses}{%
+\section{Exploratory analyses}\label{exploratory-analyses}}
 
@@
 The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
+Supplementary Figure S4 shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.
+
+Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
+We computed an rmANOVA with the \(n\)-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
+Both the NFC score (\(F(1, 114) = 4.34\), \(p = .039\), \(\hat{\eta}^2_G = .011\), 90\% CI \([.000, .063]\), \(\mathrm{BF}_{\textrm{10}} = 0.57\)) and the \(n\)-back level (\(F(2.02, 229.75) = 67.24\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(\mathrm{BF}_{\textrm{10}} = 2.70 \times 10^{30}\)) showed significant main effects, as well as a significant interaction (\(F(2.02, 229.75) = 3.78\), \(p = .024\), \(\hat{\eta}^2_G = .023\), 90\% CI \([.000, .049]\), \(\mathrm{BF}_{\textrm{10}} = 0.12\)).
+Analyzing the estimated marginal means of the linear trends for each \(n\)-back level indicated a significant difference between the slopes of 1-back and 4-back (\(\Delta M = -0.09\), \(95\%\ \mathrm{CI}_\mathrm{\scriptsize Tukey(4)}\) \([-0.15, -0.02]\), \(t(456) = -3.22\), \(p_\mathrm{\scriptsize Tukey(4)} = .008\)), but not between any other two levels.
+Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure 5).
+The full results of this exploratory analysis of NFC as a continuous covariate can be found in Table S.18 and S.19 in the Supplementary Material.
+
+{[}FIGURE 5 HERE{]}
 
@@
 The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across \(n\)-back levels.
-The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more inter-individual variance for 3- and 4-back.
-Thomson and Oppenheimer\textsuperscript{48} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
+The best fit was a declining logistic curve, reflecting that 1) the majority of participants preferred the easiest level, 2) 2-back was generally closer in preference to 1-back than 3-back was to 2-back, and 3) objective task load and subjective preference do not stand in a linear relationship.
+Since the majority of participants preferred the easiest level, we rejected the ascending quadratic and skewed normal contrasts, which implied lower SVs for 1- than for 2-back.
+The fact that the majority of participants preferred lower over higher effort, but a minority showed the opposite pattern, is in line with previous research on cognitive effort by Kool et al.~(2010)\textsuperscript{48}.
+Importantly, having a paradigm that can accurately assess the preferences of the minority is necessary but not sufficient, because the interindividual variability is so high that it blurs effects on the group level.
+Figure 2 suggests that those who prefer either 1- or 2-back have a slightly steeper discounting curve than those who prefer 3- or 4-back, meaning they have lower SVs for higher levels than those who prefer a higher level have for the easier levels.
+But as the figure also shows, there is great interindividual variability in the discounting patterns, regardless of which level has the highest SV.
+Thomson and Oppenheimer\textsuperscript{49} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
 For example, the \(n\)-back task is likely not a continuous manipulation of task load, as discussed above.
-However, the declining logistic curve is similar to the sigmoidal curve that had the best fit in a different effort paradigm\textsuperscript{49}, which the authors explained with the low effect of low energy costs, suggesting there are still common features of effort across different tasks and domains.
+However, the declining logistic curve is similar to the sigmoidal curve that has been found for a physical\textsuperscript{50} and a cognitive effort paradigm\textsuperscript{51}, suggesting there are common features of effort across different tasks and domains.
 The MLM with the logistic contrast showed that the \(n\)-back level explained the majority of variance in SVs, while the performance measure \(d'\) also explained some variance in SVs, albeit less.
@@
 This pipeline was among the three pipelines with the highest \(BF_{10}\), and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 \(MAD\) from the median.
-Interestingly, the curve of median RT betas in Figure~\ref{fig:sca-plot}a mirrored the rectangular pipeline indicators in the transformation rows of Figure~\ref{fig:sca-plot}b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
-As Fernandez et al.\textsuperscript{50} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
+Interestingly, the curve of median RT betas in Figure 4a mirrored the rectangular pipeline indicators in the transformation rows of Figure 4b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
+As Fernandez et al.\textsuperscript{52} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
 Our data seems to corroborate this finding for \(n\)-back tasks as well.
@@
 
-The majority of participants (61.20~\%) had an absolute preference for 1-back over the other levels, but that also means that there were 34.50~\% who had an absolute preference for 2-, 3-, or 4-back, and 4.30~\% who preferred no specific level over all others.
-It shows that when given the choice, there is a large number of participants who do not prefer the easiest level, confirming the necessity of an effort discounting paradigm that works independent of the objective task load.
+The majority of participants (61.20~\%) had a preference for 1-back over the other levels, but that also means that there were 34.50~\% who had a preference for 2-, 3-, or 4-back, and 4.30~\% who preferred no specific level over all others.
+It shows that when given the choice, there is a number of participants who do not prefer the easiest level, confirming the necessity of an effort discounting paradigm that works independent of the objective task load.
 The CAD paradigm provides the means to depict these preferences.
@@
 In the analysis of SV difference scores, the NFC group did not reach significance as a predictor.
-This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for 4-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
-As the exploratory analysis showed, only 4-back yielded a significant group difference, and SVs of participants with NFC scores above the median were higher for 2- to 4-back and lower for 1-back.
+Conceptually, this was likely due to the partial but not full overlap between self-reported and behavioural effort investment, which has also been found for a demand selection task\textsuperscript{53}.
+Another possible reason is the bandwidth of SVs of participants with NFC scores around the median, and the fact that the difference appeared most pronounced for 4-back, and we only registered analyses of the difference scores between 1- and 2-back and 2- and 3-back.
+As the exploratory analyses showed, a median split of NFC scores yielded a significant group difference in SVs for 4-back only, while predicting SVs with NFC as a continuous covariate showed a difference in the slopes of 1-back and 4-back.
 The analysis of NASA-TLX scores showed that the sum score increased with every \(n\)-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
@@
 This was also supported by the fact that higher \(n\)-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
-Our data supports the notion of a nonlinear interaction between person and situation that has also been described by Schmitt et al.~(2013)\textsuperscript{51} and Blum et al.~(2018)\textsuperscript{52} in the same-named NIPS model.
+Our data supports the notion of a Nonlinear Interaction between Person and Situation that has also been described by Schmitt et al.~(2013)\textsuperscript{54} and Blum et al.~(2018)\textsuperscript{55} in the same-named NIPS model.
 The NIPS model describes behaviour as a function of situational affordance which is mediated by personality traits.
@@
 An investigation of this relationship using the COG-ED paradigm\textsuperscript{7} had been encouraged by Strobel et al.\textsuperscript{53} based on their findings on demand avoidance and cognitive effort investment.
-With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model\textsuperscript{51,52} and should be tested further in a setting with \(n\)-back levels exceeding \(n=4\).
+With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model\textsuperscript{54,55} and should be tested further in a setting with \(n\)-back levels exceeding \(n=4\).
 
@@
 Another important point is the instruction, not just for the \(n\)-back task, but for the effort discounting as well.
-We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction or a training next time.
+We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction and/or a training next time.
 And even though the participants were instructed to do the effort discounting with the aim to be satisfied with their choices instead of trying to increase the rewards, we cannot be sure that they did so.
 One might also argue that the 2€ reward range was not large enough to be an incentive for effort expenditure.
-However, findings by Bialaszek et al.\textsuperscript{54} suggest that participants are actually more sensitive to effort when the reward is small.
+However, findings by Bialaszek et al.\textsuperscript{56} suggest that participants are actually more sensitive to effort when the reward is small.
 Nevertheless, we exceeded the largest required sample size by 2.20 times, which gives our analyses high statistical power.
@@
 Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an \(n\)-back task.
-The results showed that many participants indeed preferred a more or even the most difficult \(n\)-back level.
-Spanning the entire sample, these preferences took the shape of a declining logistic curve across \(n\)-back levels.
-While the subjective value declined with increasing levels, it increased with better performance as measured in \(d'\), and was unaffected by the reaction time.
+Despite the fact that the task design allowed individuals to express a preference for higher over lower objective load levels, the overall subjective values took the shape of a declining logistic curve across \(n\)-back levels.
+The majority of participants showed a decline in subjective values at higher effort levels.
+A minority of participants deviated from this pattern and showed a clear preference for 2-, 3, or 4-back over 1-back.
+The CAD paradigm was able to depict the individual preference patterns for both those who do and do not prefer the lowest effort level.
+While the subjective values declined with increasing levels, they increased with better performance as measured in \(d'\), and were unaffected by the reaction time.
 Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
-However, they did not have higher subjective values per se, which was likely due to our choice of median split and our assumption that these group differences would emerge in lower levels.
+However, they did not have higher subjective values per se, which was due to our choice of median split and our assumption that these group differences would emerge in lower levels.
+The exploratory analyses showed that the predicted slope of subjective values depending on Need for Cognition scores differed between 1- and 4-back, but not between other levels.
 In fact, the reaction time and self-report data suggest that individual differences emerge especially from 3-back upwards, emphasizing the need for tasks with high discriminatory power and effort discounting paradigms with flexible, participant-centered mechanisms.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kool2010}{}}%
+\CSLLeftMargin{48. }%
+\CSLRightInline{Kool, W., McGuire, J.
+T., Rosen, Z.
+B.
+\& Botvinick, M.
+M.
+\href{https://doi.org/10.1037/a0020198}{Decision making and the avoidance of cognitive demand.} \emph{Journal of Experimental Psychology: General} \textbf{139}, 665--682 (2010).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Thomson2022}{}}%
-\CSLLeftMargin{48. }%
+\CSLLeftMargin{49. }%
 \CSLRightInline{Thomson, K.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-KleinFluegge2015}{}}%
-\CSLLeftMargin{49. }%
+\CSLLeftMargin{50. }%
 \CSLRightInline{Klein-Flügge, M.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Massar2019}{}}%
+\CSLLeftMargin{51. }%
+\CSLRightInline{Massar, S.
+A.
+A., Lim, J., Sasmita, K.
+\& Chee, M.
+W.
+L.
+\href{https://doi.org/10.1016/j.neuropsychologia.2018.03.032}{Sleep deprivation increases the costs of attentional effort: Performance, preference and pupil size}.
+\emph{Neuropsychologia} \textbf{123}, 169--177 (2019).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Fernandez2020}{}}%
-\CSLLeftMargin{50. }%
+\CSLLeftMargin{52. }%
 \CSLRightInline{Fernández, L.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Strobel2020}{}}%
+\CSLLeftMargin{53. }%
+\CSLRightInline{Strobel, A.
+\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0239817}{Dispositional cognitive effort investment and behavioral demand avoidance: {Are} they related?} \emph{PLOS ONE} \textbf{15}, e0239817 (2020).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Schmitt2013}{}}%
-\CSLLeftMargin{51. }%
+\CSLLeftMargin{54. }%
 \CSLRightInline{Schmitt, M.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Blum2018}{}}%
-\CSLLeftMargin{52. }%
+\CSLLeftMargin{55. }%
 \CSLRightInline{Blum, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Strobel2020}{}}%
-\CSLLeftMargin{53. }%
-\CSLRightInline{Strobel, A.
-\emph{et al.} \href{https://doi.org/10.1371/journal.pone.0239817}{Dispositional cognitive effort investment and behavioral demand avoidance: {Are} they related?} \emph{PLOS ONE} \textbf{15}, e0239817 (2020).}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Bialaszek2017}{}}%
-\CSLLeftMargin{54. }%
+\CSLLeftMargin{56. }%
 \CSLRightInline{Białaszek, W., Marcowski, P.
@@
 
-\newpage
-
-\hypertarget{figures}{%
-\section{Figures}\label{figures}}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{../../Inkscape Figures/Paradigm_Scheme} \caption{An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
-The grey boxes are the choice options shown to the participant.
-The participant's final reward value of the flexible level is displayed after the first arrow.
-The resulting subjective value of each level is displayed after the second arrow, in the notation "SV 3-back(1-back)" for the subjective value of 3-back when 1-back is the other choice.
-The Solution and Additional Benefit panel follow the same logic, but are preceded by a choice between equal rewards, and the participant's first choice indicated by an exclamation mark.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:cadparadigm}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/sca-plot} \caption{Results of the multi level model for each of the 63 preprocessing pipelines.
-Drawing a vertical through both panels indicates the type of preprocessing (panel b) of the pipeline and the resulting beta estimates of the three predictors in the model (panel a).
-The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
-The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:sca-plot}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/nfcgroups-sv} \caption{Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
-$N=116$.
-The scatter has a horizontal jitter of 0.2.
-Smoothing of conditional means with Loess method.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:nfcgroups-sv}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/h3ac-plot} \caption{Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
-Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
-NFC = Need for Cognition score.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3ac-plot}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/h3b-plot} \caption{NASA-TLX sum scores for each $n$-back level.
-Colours indicate Need for Cognition (NFC) score above or below the median.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3b-plot}
-\end{figure}
-
 \end{document}

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
reshaped a sentence

@@
 This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
-Both measures also showed high variability between individuals.
+The measures of arousal and effort also showed high variability between individuals.
 Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
 It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
-In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly. 
-The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
-By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
-Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy. 
-In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
-In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
-Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.
+In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instruction ("Maintain a neutral facial expression") is measured directly. 
+The direct instruction also reduces the complexity of the generation process.
+This could be why the required subjective effort is the lowest.
+Finally, immediacy and simplicity are expressed as greater subjective utility of the strategy suppression.
+In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well suppression has been implemented.
+In contrast, the strategies distraction and distancing require a more detailed evaluation of internal states in order to assess their utility, which in turn requires more effort.
 
@@
 Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback [@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
-This means that studies on ER Choice should consider not only situational factors, but also contextual factors[@Murphy2018].
+This means that studies on ER Choice should consider not only situational factors (i.e., perceived control, emotional intensity[@Wilms2020]), but also contextual factors (i.e., state-dependent psychological processes of the participant and task characteristics; for a review, see Aldao, 2013[@Aldao2013])[@Murphy2018].
 For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
@@
 To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
+However, this would require at least two measurements of SVs.
 The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
@@
 Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values. 
-This further enables to investigate in more detail the factors influencing the internal generation of these subjective values of ER strategies.
+This further enables to investigate the factors influencing the internal generation of these subjective values of ER strategies in more detail.
 It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and effort.

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/method.Rmd

@@
 
-*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
-Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
-The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
+*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the SV of the flexible strategy was set to 1, because in the first comparison of each pairing where the same value was offered for both strategies, so the flexible strategy was the preferred strategy in each pairing.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible strategy over the fixed strategy), the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+The resulting value of the flexible strategy was divided by 2€.
+This yielded an SV of the fixed strategy between 0 and 1, with values closer to 0 indicating a stronger aversion to the fixed strategy compared to the flexible strategy.
 The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
edited 3.1

@@
 
-Data collection took place between 16th of August 2022 and the 3rd of February 2023.
+Data collection took place between the 16th of August 2022 and the 3rd of February 2023.
 A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
-Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
-Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M\text{ }\pm\text{ }SD =`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }`r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$ years old), which is `r format(round((sum(data_survey[,"followup_ered_complete"] == 2)-1)/85, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
-Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).
+The first session was attended by $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participants [@ZernaScheffel2022], and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ participants also completed the second session.
+We excluded the data of $n=1$ person from the present analyses because they stated that they did not follow the instructions.
+Therefore, the final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M\text{ }\pm\text{ }SD =`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }`r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$ years old), which is `r format(round((sum(data_survey[,"followup_ered_complete"] == 2)-1)/85, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
+Please note that the sample size for a few analyses may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).
 

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
edited until SV section

@@
 
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, *corrugator* and *levator* activity.
-Descriptive values of each predictor for each condition can be found in Table \@ref(tab:TabDescr).
-We found a significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
+To explore whether negative pictures evoked emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with the predictors subjective arousal, *corrugator* and *levator* activity.
+Descriptive values of each predictor per condition can be found in Table \@ref(tab:TabDescr).
+We found a significant main effect of valence on subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`).
 Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables S.4 to S.6 and Figures S.1 to S.3 in the supplementary material).
@@
 
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
-We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
+To investigate whether ER strategies reduced emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, *corrugator* and *levator* activity.
+We found a significant main effect of strategy on subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
 For detailed information on post-hoc contrasts, please see Tables S.7 to S.9 and Figures S.4 to S.6 in the supplementary material.
@@
 
-To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see Figure \@ref(fig:FigSubjEffort)).
+To investigate whether ER strategies required cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant main effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see Figure \@ref(fig:FigSubjEffort)).
 Post-hoc contrasts showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing.
@@
 
-Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021].
-`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
-`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found online on OSF (<https://osf.io/vnj8x/>).
+Cognitive effort also played the most important role in the subsequent choice of strategy, which resembled previous findings of our group[@Scheffel2021].
+The majority of participants (`r round((54/119)*100, digits = 1)`%) stated that they chose the strategy that was easiest for them to implement, `r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective, and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest *and* most effective.
+A more detailed list of all reasons, including those given by participants who stated none of the three options above, can be found online on OSF (<https://osf.io/vnj8x/>).
 

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
edited rest of 3.2

@@
 SVs ranged between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`.
-$n=$ `r  papaja::printnum(sum(data_SV$sv == 1))` had one SV of 1.0, indicating a clear preference for one ER strategy.
-Absolute preferences for ER strategies were relatively equally distributed.
-Highest SV for distraction was reported by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))`, for distancing by $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))`, and for suppression by $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "suppression"] == -1))`.
+Nearly all ($n=$ `r  papaja::printnum(sum(data_SV$sv == 1))`) participants had one SV of 1.0, indicating a clear preference for one ER strategy over the other two.
+Absolute preferences for ER strategies were relatively equally distributed: $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distraction"] == -1))` participants assigned their highest SV to distraction, $n=$ `r  papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "distancing"] == -1))` to distancing, and $n=$ `r papaja::printnum(sum(data_SV$strat_c[data_SV$strategy == "suppression"] == -1))` to suppression.
 
-To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
-The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
+To investigate which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
+The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor *subject* accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
 The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` between the random effects *subjects* and *recoded strategy* ($BF10$ of the variable *strategy*: `r papaja::apa_print(MLM_1_BF)$statistic`).
-Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
-We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
+Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted because we included *recoded strategy* as the random slope.
+We therefore set a new model without *recoded strategy* as the random slope factor to estimate the influence of predictors on SVs more precisely.
 The second model followed the specification: 
@@
   H5_M2_table,
-  caption = "Results of multilevel model predicting subjective values of ER strategies.",
+  caption = "Results of the multilevel model predicting subjective values of ER strategies.",
   booktabs = TRUE,
@@
 
-We then conducted an ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
+We then conducted an ordinal regression with the dependent variable *choice* and the individual SVs of all three strategies as independent variables.
 Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
 The SV of the strategy distraction contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
-The estimated odds ratio indicated a higher chance of choosing strategy distraction, when the SV of that strategy is higher.
+The estimated odds ratio indicated a higher chance of choosing the strategy distraction when the SV of that strategy was higher.
 Additionally, the predictor SV of the strategy suppression contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
-The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
+The estimated odds ratio indicated that a participant was more likely to later choose suppression, when the SV of the strategy suppression was higher.
 
-Last, we investigated whether SVs are associated with ER flexibility.
-We conducted a logistic regression to inspect whether participants' individual $slopes$ and $intercepts$ of ordered SVs could predict their ER flexibility score.
-We found neither a significant association between $slopes$ of SVs and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$slope`, `r papaja::apa_print(Flex_LM_BF)$full_result$slope`), nor between $intercepts$ and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$intercept`, `r papaja::apa_print(Flex_LM_BF)$full_result$intercept`).
+Lastly, we investigated whether SVs were associated with ER flexibility.
+We conducted a logistic regression to inspect whether participants' individual slopes and intercepts of ordered SVs could predict their ER flexibility score.
+We found neither a significant association between slopes and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$slope`, `r papaja::apa_print(Flex_LM_BF)$full_result$slope`), nor between intercepts and FlexER score (`r papaja::apa_print(Flex_LM)$full_result$intercept`, `r papaja::apa_print(Flex_LM_BF)$full_result$intercept`).
 However, model fit was relatively low (`r papaja::apa_print(Flex_LM)$full_result$modelfit$r2`).

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
edited 3.3

@@
 
-Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
-The starting point for this was the adapted MLM, which we have reported before.
-Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
+Because associations between self-control, the investment trait Need for Cognition (NFC), and both effort discounting and demand avoidance have been reported[@ZernaScheffel2022;@Westbrook2013;@Kool2013], we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
+The starting point for this was the adapted MLM reported above (Table \@ref(tab:TabMLMH5)).
+Only predictors that had previously shown a significant association with SVs were included in the model together with the level-2 predictors self-control and NFC.
 The third model followed the specification: 
@@
 $$ 
-As expected, the predictors effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`), and *corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
+The predictor effort rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3, digits = 3)$full_result$utility_cwc`) and *corrugator* activity (`r papaja::apa_print(MLM_3, digits = 3)$full_result$Corr_cwc`) showed a positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3, digits = 3)$full_result$SC_gmc`).
-However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
-Detailed information can be found in the supplementary material.
+However, the effect size of this effect was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
+Detailed information can be found in Table S.10 in the supplementary material.

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
edited discussion

@@
 The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
-The latter was the goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
+The latter was the purpose of the present study and was completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
 As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
@@
 Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
-This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
-The measures of arousal and effort also showed high variability between individuals.
-Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
-It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
-In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instruction ("Maintain a neutral facial expression") is measured directly. 
-The direct instruction also reduces the complexity of the generation process.
-This could be why the required subjective effort is the lowest.
-Finally, immediacy and simplicity are expressed as greater subjective utility of the strategy suppression.
-In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well suppression has been implemented.
-In contrast, the strategies distraction and distancing require a more detailed evaluation of internal states in order to assess their utility, which in turn requires more effort.
+This allows us to replicate previous findings from our research group, showing that strategy use is associated with cognitive effort[@Scheffel2021].
+Taken together, these findings show that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
+Despite these distinct effects in the manipulation checks, the arousal and effort measures showed high variability between individuals, emphasizing the great extent of subjectivity when dealing with emotional stimuli.
+Additionally, it was surprising that the strategy suppression showed the lowest *corrugator* activity, the lowest effort ratings, and the highest utility ratings.
+In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instruction ("Maintain a neutral facial expression") is measured directly, which also reduces the complexity of the generation process.
+This considerable degree of immediacy and simplicity might not only reduce the subjective effort, but might also increase the subjective utility of the strategy suppression.
+In addition, the participants receive relatively direct feedback from their own facial muscle activity as to how well suppression has been implemented, which likely influences their perceived regulation success.
+In contrast, the strategies distraction and distancing require a more detailed evaluation of internal states in order to assess their utility and success, which in turn requires more effort.
 
-Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1. 
-We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals have varying degrees of strategy preference.
-There was a significant relationship between SVs and strategy choice. 
-Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
+Almost all participants showed an absolute preference for a particular strategy over the two others, indicated by an SV of 1. 
+We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`) across the whole sample, suggesting that individuals have varying degrees of preference strength.
+But despite this variation, most participants chose the strategy to which they had assigned their highest SV, supporting hypothesis H7a.
 We also found associations between individual SVs and various predictors.
-Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
-However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
+Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs across all strategies.
+Contrary to our hypothesis H6, utility but not effort was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
+However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7b.
 In a subsequent exploratory analyses, we found a positive association between individual SVs and self-control.
@@
 However, we did not find an association between NFC and SVs. 
-This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance[@ZernaScheffel2022;@Westbrook2013].
-However, these were all cognitive tasks. The role of NFC in affective tasks is not well known yet.
+This is in contrast to reported correlations between NFC, effort discounting, and demand avoidance in cognitive tasks [@ZernaScheffel2022;@Westbrook2013].
+The role of NFC in affective tasks is not well understood yet.
 
@@
 Our aim was to calculate individual subjective values in order to develop a better understanding of ER strategy selection.
-Most individuals show large variability in strategy choice, both within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022]. 
-Greater variability may even be adaptive[@Blanke2020;@Aldao2015].
+Most individuals show large variability in strategy choice, both within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022], which in the context of emotion regulation is most likely a sign of good adaptability[@Blanke2020;@Aldao2015].
 In addition, a variety of factors that influence strategy choice in specific situations have been examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020;@Matthews2021], including situation intensity and effort.
-However, these factors have often been studied in isolation from each other.
-Rarely have their combined effects been investigated[@Young2020].
+However, these factors have often been studied in isolation from each other, and only rarely in conjunction[@Young2020].
 Furthermore, the usual paradigms used in ER choice research (e.g., Sheppes et al.[-@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
-They cannot determine the internal subjective value individuals attribute to the choice options.
+They cannot determine the internal subjective value individuals attribute to all choice options.
 We are confident that we have achieved this with the present paradigm.
-On the one hand, we were able to show which factors have an influence on the values, and on the other hand, we were able to show the actual practical relevance of the values. 
-As a predictor of ER effectiveness, *corrugator* activity showed a significant association with SVs, but not *levator* activity or subjective arousal.
-With regard to the EMG measures, this could be because all the pictures we used were negative, i.e.
-elicited *corrugator* activity, but only a small proportion of the pictures were perceived as disgusting and thus elicited relatively specific *levator* activity.
+We were not only able to show which factors have an influence on the values, but we were also able to demonstrate the values' practical relevance in the form of choice prediction. 
+As an operationalization of ER effectiveness, *corrugator* activity showed a significant association with SVs, but neither *levator* activity or subjective arousal did.
+With regard to the EMG measures, this could be because all the pictures we used were negative, which is commonly associated with higher *corrugator* activity, but only a small proportion of the pictures were classified as disgusting and thus elicited relatively specific *levator* activity.
 However, *corrugator* activity did not differ significantly between ER strategies, but was still associated with SVs.
-One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current strategy, much more direct than, for example, the subjective arousal rating at the end of each experimental block.
-Furthermore, the finding that effort is associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies[@Scheffel2021].
+One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current strategy in a more immediate fashion than, for example, the subjective arousal rating at the end of each experimental block.
+Furthermore, the finding that effort was associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies[@Scheffel2021].
 Finally, the subjective utility ratings showed the greatest explained variance in the SVs.
 This relationship is highly plausible as it involves individuals assessing the utility of the strategy as a means of achieving external and internal regulatory goals.
-This is likely to overlap with subjective values - some literature argues that utility and subjective values are the same thing[@Schultz2015].
-However, this is contradicted by our data, as subjective utility could only explain `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of the variance in SVs.
+Utility is likely to overlap with subjective values - some literature even argues that utility and subjective values are one and the same[@Schultz2015].
+However, this claim is not supported by our data, as subjective utility could only explain `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of the variance in SVs, which leaves a considerable portion of variance in SVs unaccounted for.
 
-The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block. 
-So far, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020].
-This may be because in laboratory studies the choice options are often predetermined by the experimental design[@Sheppes2011;@Sheppes2014;@Scheffel2021].
-Therefore, attempts have been made to investigate ER choice and its influencing factors in everyday life in previous studies.
-Even there, however, certain strategies were often prescribed (for example studies see English et al.[-@English2017], Millgram et al.[-@Millgram2019], Wilms et al.[-@Wilms2020]), although covering a large part of the process of emotion generation[@Gross1998emerging].
-Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
+The highest SV of each participant was associated with the choice made in the last experimental block. 
+So far, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020], likely because laboratory studies provide predefined and limited choice options in their experimental design[@Sheppes2011;@Sheppes2014;@Scheffel2021], which is not the case in a natural setting.
+Therefore, previous studies have attempted to investigate ER choice and its influencing factors in everyday life.
+But despite covering a large part of the emotion generation process[@Gross1998emerging], even these studies prescribed certain strategies (for example studies see English et al.[-@English2017], Millgram et al.[-@Millgram2019], Wilms et al.[-@Wilms2020]).
+Similarly, the calculation of SVs in our new CAD paradigm depends on the available choice options that were defined in the experimental design.
 To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment[@Aldao2015;@Koval2020].
@@
 The extended process model of emotion regulation[@Gross2015] postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
-If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped[@Gross2015].
-Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback [@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
+If the regulatory goal is not achieved, the ER strategy can be maintained, switched, or stopped[@Gross2015].
+Importantly, feedback on the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback [@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
 This means that studies on ER Choice should consider not only situational factors (i.e., perceived control, emotional intensity[@Wilms2020]), but also contextual factors (i.e., state-dependent psychological processes of the participant and task characteristics; for a review, see Aldao, 2013[@Aldao2013])[@Murphy2018].
-For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
-This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
+In a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] could show that strategy choice was significantly influenced by both strategy choice and negative affect during the previous trial, providing evidence that experience gained during the use of ER strategies influences the future choice of ER strategies.
 Our newly developed CAD paradigm also makes an important contribution here.
-The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of SVs.
-That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.
-This raises the question of how stable these individual SVs are.
+The structure of the paradigm provides the opportunity for participants' experiences to influence their SVs, because each participant completes all ER strategies before indicating their preferences the discounting procedure, expecting to be re-applying one of the strategies at the end.
 
@@
 However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
-To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
-However, this would require at least two measurements of SVs.
-The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
-By definition, this represents a state.
+To establish the trait nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
+However, this would require the measurement of SVs at two or more points in time.
+The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation, which by definition represents a state.
 As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
@@
 In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
-It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
-Therefore, SVs may vary when different reference strategies are used.
-It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals. 
+It should also be noted that the calculation of individual SVs in our CAD paradigm are always relative to the alternative strategies that were available (see also [Limitations](#Limitations)).
+Therefore, SVs may vary if different reference strategies are used, but it is very likely that SVs are highly correlated across situations with similar demands and goals. 
 They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
@@
 However, our data are not suitable for answering this question.
-In the future, SVs should therefore be collected in several similar situations. 
+In the future, SVs should therefore be collected across similar situations. 
 Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].
@@
 A number of limitations must be taken into account when considering our findings. 
-First, it should be noted that a block design was used.
-This might have resulted in habituation effects of EMG activity within the block.
+First, it should be noted that a block design was used, which might have resulted in habituation effects of EMG activity within the block.
 However, block designs are common in ER research [@Barreiros2019] and have been used in previous studies [@Scheffel2019]. 
-Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block.
-It is known that affect labeling can attenuate emotional experience [@Lieberman2007;@Torre2018]. 
-Therefore, we decided not to conduct ratings after each image.
-Furthermore, we were able to confirm that the implementation of ER strategies was successful at both subjective and physiological levels.
+Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block, which might have led to recency effects.
+But since it is known that affect labeling can attenuate emotional experience [@Lieberman2007;@Torre2018], we decided not to conduct ratings after each image.
+Furthermore, we were able to confirm that the implementation of ER strategies was successful on both subjective and physiological levels.
 Still, these features of our research design may have led to slightly lower associations between SVs and predictors.
@@
 They depend on the specific context: The stimuli presented and the strategies compared.
-For example, SVs for an ER strategy might be higher or lower when different stimuli or stimulus valences and different comparison strategies are used, because the calculation of SVs is inseparable form the other SVs.
+For example, SVs for an ER strategy might be higher or lower when different stimuli or stimulus valences and different comparison strategies are used, because the calculation of SVs is inseparable from the other SVs.
 
@@
 Participants were asked to imagine that this was the amount of money they would receive if they repeated this strategy.
-Thus, 2€ could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
-However, we chose this amount because, firstly, we followed the original paradigm of Westbrook[@Westbrook2013], and secondly, it has been shown in the context of cognitive effort discounting, that a lower incentive increases participants' sensitivity to effort differences[@Bialaszek2017].
-In the future, however, it should be investigated how the level of incentives affects subjective values.
+Thus, 2€ could be an insufficient incentive to repeat a whole experimental block.
+However, we chose this amount because we wanted to follow the original paradigm of Westbrook[@Westbrook2013], and because it has been shown that a lower incentive increases participants' sensitivity to effort differences[@Bialaszek2017].
+In the future, however, it should be investigated how the incentive size affects subjective values.
 
@@
 In order to cope with changing emotional demands, individuals may flexibly select and apply ER strategies from their repertoire[@Bonanno2013;@Aldao2015].
-The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
+They select the strategy that is most suitable for coping with contextual demands and achieving regulatory goals[@Aldao2015;@Tamir2016].
 The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.

### 2023-06-30 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
restructured trait part

@@
 However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
-To establish the trait nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
-However, this would require the measurement of SVs at two or more points in time.
 The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation, which by definition represents a state.
@@
 However, our data are not suitable for answering this question.
+To establish the trait nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
+However, this would require the measurement of SVs at two or more points in time, ideally in both the same and different contexts (e.g., changing valence of stimuli and add further ER strategies). 
+Thus, temporal and situational variance could be separated and the stable, habitual part of the subjective values of the individual strategies could be determined.
 In the future, SVs should therefore be collected across similar situations. 

### 2023-06-30 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
rewrote trait section

--- 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
@@
 
-Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
-However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
-To establish the trait nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
-However, this would require the measurement of SVs at two or more points in time.
-The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation, which by definition represents a state.
-As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
-We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
-Our data presented in this study support this idea.
-However, this also implies that SVs should differ according to situational factors (e.g. stimulus intensity).
-The ER goals that individuals pursue in a given situation must also be taken into account.
-In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals[@Tamir2016].
-Wilms and colleagues[-@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
-In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
-It should also be noted that the calculation of individual SVs in our CAD paradigm are always relative to the alternative strategies that were available (see also [Limitations](#Limitations)).
-Therefore, SVs may vary if different reference strategies are used, but it is very likely that SVs are highly correlated across situations with similar demands and goals. 
-They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
-Of course, it is also possible that such habits influence the internal formation of these subjective values.
-However, our data are not suitable for answering this question.
-In the future, SVs should therefore be collected across similar situations. 
-Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].
+Knowing whether SVs of ER strategies show a trait character would allow to further evaluate their practical relevance and predictive power.
+With the data of the present study, a trait analysis is not possible, because the SVs of the ER strategies were assessed in just one situation at just one time point, which by definition represents a state.
+A habit would imply consistency of SVs across time points in similar situations, while a trait would imply consistency across both time points and situations.
+As noted above, ER choice behaviour is rather state-like, because it is influenced by personal regulatory goals, situational factors, and contextual demands [@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
+We therefore believe that the impact of these factors on ER behaviour translates into state- or habit-like properties of SVs as well.
+Such factors could be varied systematically in order to shed light on the stability of SVs, e.g by manipulating situational factors like stimulus intensity, or by systematically assessing the goals that participants pursue with their ER behaviour.
+As Wilms and colleagues[-@Wilms2020] pointed out, situational factors and ER goals are state-like themselves, because they vary greatly across time points and situations.
+While participants in the lab mainly pursue hedonic but not social goals[@Tamir2016], a real-life situation with social goals will probably not only change their ER behaviour but also the SVs that they assign to different strategies, especially when their choice options are not limited by the experimental design (see also [Limitations](#Limitations)).
+To investigate whether SVs of ER strategies can be conceptualized as states, habits, or traits, one could employ latent state trait modelling, as recently done by our group in a related context[@Strobel2020].
+A systematic (non-)variation of situational factors and the assessment of personal factors, e.g. ER goals, can then help to disentangle time- and situation-specific variance in SVs.
+Importantly, the practical relevance and predictive power of SVs should be assessed at every measurement, because it is entirely possible that the correlation between SVs and ER choice is situation-specific as well.
+Such findings would not only yield important insights into ER behaviour, but allow investigations into the association of ER behaviour with external criteria as well, such as well-being[@GrossJohn2003].
 

### 2023-06-30 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
traits, habits, and states

@@
 
-Knowing whether SVs of ER strategies show a trait character would allow to further evaluate their practical relevance and predictive power.
-With the data of the present study, a trait analysis is not possible, because the SVs of the ER strategies were assessed in just one situation at just one time point, which by definition represents a state.
-A habit would imply consistency of SVs across time points in similar situations, while a trait would imply consistency across both time points and situations.
+Knowing whether the SVs of ER strategies have a trait character would allow to further evaluation of their practical relevance and predictive power.
+With the data of the present study, a trait analysis is not possible, because the SVs of the ER strategies were assessed in only one situation at only one time point, which by definition represents a state.
+A habit would imply consistency of SVs across time points in similar situations, whereas a trait would imply consistency across both time points and situations.
 As noted above, ER choice behaviour is rather state-like, because it is influenced by personal regulatory goals, situational factors, and contextual demands [@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
-We therefore believe that the impact of these factors on ER behaviour translates into state- or habit-like properties of SVs as well.
-Such factors could be varied systematically in order to shed light on the stability of SVs, e.g by manipulating situational factors like stimulus intensity, or by systematically assessing the goals that participants pursue with their ER behaviour.
+We therefore believe that the influence of these factors on ER behaviour will also translates into state- or habit-like properties of SVs.
+Such factors could be varied systematically in order to shed light on the stability of SVs, e.g.
+by manipulating situational factors such as stimulus intensity, or by systematically assessing the goals that participants pursue with their ER behaviour.
 As Wilms and colleagues[-@Wilms2020] pointed out, situational factors and ER goals are state-like themselves, because they vary greatly across time points and situations.
-While participants in the lab mainly pursue hedonic but not social goals[@Tamir2016], a real-life situation with social goals will probably not only change their ER behaviour but also the SVs that they assign to different strategies, especially when their choice options are not limited by the experimental design (see also [Limitations](#Limitations)).
-To investigate whether SVs of ER strategies can be conceptualized as states, habits, or traits, one could employ latent state trait modelling, as recently done by our group in a related context[@Strobel2020].
+While participants in the lab mainly pursue hedonic but not social goals[@Tamir2016], a real-life situation with social goals is likely to change not only their ER behaviour but also the SVs they assign to different strategies, especially when their choice options are not restricted by the experimental design (see also [Limitations](#Limitations)).
+To investigate whether the SVs of ER strategies can be conceptualised as states, habits, or traits, one could employ latent state trait modelling, as recently done by our group in a related context[@Strobel2020].
 A systematic (non-)variation of situational factors and the assessment of personal factors, e.g. ER goals, can then help to disentangle time- and situation-specific variance in SVs.
-Importantly, the practical relevance and predictive power of SVs should be assessed at every measurement, because it is entirely possible that the correlation between SVs and ER choice is situation-specific as well.
-Such findings would not only yield important insights into ER behaviour, but allow investigations into the association of ER behaviour with external criteria as well, such as well-being[@GrossJohn2003].
+Importantly, the practical relevance and predictive power of SVs should be assessed at every measurement, as it is quite possible that the correlation between SVs and ER choice is situation-specific as well.
+Such findings would not only provide important insights into ER behaviour, but allow investigations into the association of ER behaviour with external criteria as well, such as well-being[@GrossJohn2003].
 

### 2023-07-05 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
typos

@@
 
-Knowing whether the SVs of ER strategies have a trait character would allow to further evaluation of their practical relevance and predictive power.
+Knowing whether the SVs of ER strategies have a trait character would allow a further evaluation of their practical relevance and predictive power.
 With the data of the present study, a trait analysis is not possible, because the SVs of the ER strategies were assessed in only one situation at only one time point, which by definition represents a state.
@@
 As noted above, ER choice behaviour is rather state-like, because it is influenced by personal regulatory goals, situational factors, and contextual demands [@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
-We therefore believe that the influence of these factors on ER behaviour will also translates into state- or habit-like properties of SVs.
+We therefore believe that the influence of these factors on ER behaviour will also translate into state- or habit-like properties of SVs.
 Such factors could be varied systematically in order to shed light on the stability of SVs, e.g.

### 2023-07-06 06_Paper/ER-ED/ERED_Stage2/method.Rmd
rephrased one sentence

@@
 
-*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the SV of the flexible strategy was set to 1, because in the first comparison of each pairing where the same value was offered for both strategies, so the flexible strategy was the preferred strategy in each pairing.
+*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the SV of the flexible strategy was set to 1, because that strategy was preferred when equal rewards were offered.
 Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible strategy over the fixed strategy), the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.

### 2023-07-06 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted doc

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
-Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
-Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
-The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
+\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the SV of the flexible strategy was set to 1, because that strategy was preferred when equal rewards were offered.
+Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible strategy over the fixed strategy), the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
+The resulting value of the flexible strategy was divided by 2€.
+This yielded an SV of the fixed strategy between 0 and 1, with values closer to 0 indicating a stronger aversion to the fixed strategy compared to the flexible strategy.
 The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.
@@
 
-Data collection took place between 16th of August 2022 and the 3rd of February 2023.
+Data collection took place between the 16th of August 2022 and the 3rd of February 2023.
 A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
-Of these, \(N=124\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
-Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
-The final sample consisted of \(N=120\) participants (100 female; age: \(M\text{ }\pm\text{ }SD =22.5\text{ }\pm\text{ }3.0\) years old), which is 1.4 times more than what the highest sample size calculation required.
-Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).
+The first session was attended by \(N=124\) participants\textsuperscript{34}, and \(N=121\) participants also completed the second session.
+We excluded the data of \(n=1\) person from the present analyses because they stated that they did not follow the instructions.
+Therefore, the final sample consisted of \(N=120\) participants (100 female; age: \(M\text{ }\pm\text{ }SD =22.5\text{ }\pm\text{ }3.0\) years old), which is 1.4 times more than what the highest sample size calculation required.
+Please note that the sample size for a few analyses may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).
 
@@
 
-To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with predictors subjective arousal, \emph{corrugator} and \emph{levator} activity.
-Descriptive values of each predictor for each condition can be found in Table \ref{tab:TabDescr}.
-We found a significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.76 \times 10^{48}\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.05 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 251.32\)).
+To explore whether negative pictures evoked emotional arousal and physiological responding, we conducted separate rmANOVAs for the active viewing condition with the predictors subjective arousal, \emph{corrugator} and \emph{levator} activity.
+Descriptive values of each predictor per condition can be found in Table \ref{tab:TabDescr}.
+We found a significant main effect of valence on subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 2.76 \times 10^{48}\)), \emph{corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.05 \times 10^{18}\)), and \emph{levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 251.32\)).
 Post-hoc contrasts indicated that negative pictures successfully increased emotional arousal and physiological responding (please see Tables S.4 to S.6 and Figures S.1 to S.3 in the supplementary material).
@@
 
-To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
-We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 157.74\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.82 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
+To investigate whether ER strategies reduced emotional arousal and physiological responding, we conducted separate rmANOVAs comparing the four instructed strategies (active viewing, distraction, distancing, suppression) with respect to subjective arousal, \emph{corrugator} and \emph{levator} activity.
+We found a significant main effect of strategy on subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 157.74\)), \emph{corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 1.96 \times 10^{10}\)), and \emph{levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 7.82 \times 10^{18}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
 For detailed information on post-hoc contrasts, please see Tables S.7 to S.9 and Figures S.4 to S.6 in the supplementary material.
@@
 
-To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
-We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.77 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
+To investigate whether ER strategies required cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
+We found a significant main effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.77 \times 10^{53}\); see Figure~\ref{fig:FigSubjEffort}).
 Post-hoc contrasts showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
@@
 
-Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
-45.40\% of the participants stated that they chose the strategy that was easiest for them to implement.
-24.40\% stated they chose the strategy that was most effective and 11.80\% stated their chosen strategy was the easiest and most effective.
-A more detailed list of all reasons can be found online on OSF (\url{https://osf.io/vnj8x/}).
+Cognitive effort also played the most important role in the subsequent choice of strategy, which resembled previous findings of our group\textsuperscript{22}.
+The majority of participants (45.40\%) stated that they chose the strategy that was easiest for them to implement, 24.40\% stated they chose the strategy that was most effective, and 11.80\% stated their chosen strategy was the easiest \emph{and} most effective.
+A more detailed list of all reasons, including those given by participants who stated none of the three options above, can be found online on OSF (\url{https://osf.io/vnj8x/}).
 
@@
 SVs ranged between 0.005 and 1.00.
-\(n=\) 119 had one SV of 1.0, indicating a clear preference for one ER strategy.
-Absolute preferences for ER strategies were relatively equally distributed.
-Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 43.
-
-To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
-The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor subject accounted for 19.10\% of total variance.
+Nearly all (\(n=\) 119) participants had one SV of 1.0, indicating a clear preference for one ER strategy over the other two.
+Absolute preferences for ER strategies were relatively equally distributed: \(n=\) 41 participants assigned their highest SV to distraction, \(n=\) 36 to distancing, and \(n=\) 43 to suppression.
+
+To investigate which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
+The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor \emph{subject} accounted for 19.10\% of total variance.
 The preregistered model showed a correlation of \(r=\) 0.95 between the random effects \emph{subjects} and \emph{recoded strategy} (\(BF10\) of the variable \emph{strategy}: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
-Our model explained 90.4\% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
-We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
+Our model explained 90.4\% of variance and thus we assumed our model was overfitted because we included \emph{recoded strategy} as the random slope.
+We therefore set a new model without \emph{recoded strategy} as the random slope factor to estimate the influence of predictors on SVs more precisely.
 The second model followed the specification:
@@
 
-\caption{\label{tab:TabMLMH5}Results of multilevel model predicting subjective values of ER strategies.}
+\caption{\label{tab:TabMLMH5}Results of the multilevel model predicting subjective values of ER strategies.}
 
@@
 
-We then conducted an ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
+We then conducted an ordinal regression with the dependent variable \emph{choice} and the individual SVs of all three strategies as independent variables.
 Overall model fit was fair with \(R^{2}=\) 0.27.
 The SV of the strategy distraction contributed significantly to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
-The estimated odds ratio indicated a higher chance of choosing strategy distraction, when the SV of that strategy is higher.
+The estimated odds ratio indicated a higher chance of choosing the strategy distraction when the SV of that strategy was higher.
 Additionally, the predictor SV of the strategy suppression contributed significantly to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
-The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.
-
-Last, we investigated whether SVs are associated with ER flexibility.
-We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
-We found neither a significant association between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
+The estimated odds ratio indicated that a participant was more likely to later choose suppression, when the SV of the strategy suppression was higher.
+
+Lastly, we investigated whether SVs were associated with ER flexibility.
+We conducted a logistic regression to inspect whether participants' individual slopes and intercepts of ordered SVs could predict their ER flexibility score.
+We found neither a significant association between slopes and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between intercepts and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
 However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).
@@
 
-Because associations between self-control, the investment trait Need for Cognition (NFC) and both, effort discounting and demand avoidance have been reported\textsuperscript{29,34,69}, we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
-The starting point for this was the adapted MLM, which we have reported before.
-Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
+Because associations between self-control, the investment trait Need for Cognition (NFC), and both effort discounting and demand avoidance have been reported\textsuperscript{29,34,69}, we wanted to investigate the influence of self-control and NFC on individual SVs of ER strategies.
+The starting point for this was the adapted MLM reported above (Table \ref{tab:TabMLMH5}).
+Only predictors that had previously shown a significant association with SVs were included in the model together with the level-2 predictors self-control and NFC.
 The third model followed the specification:
@@
 \]
-As expected, the predictors effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant positive association with SVs.
+The predictor effort rating (\(\hat{\beta} = -0.001\), 95\% CI \([-0.001, -0.001]\), \(t(5,620.93) = -14.26\), \(p < .001\)) showed a negative association with SVs, while utility rating (\(\hat{\beta} = 0.001\), 95\% CI \([0.001, 0.002]\), \(t(5,620.93) = 33.28\), \(p < .001\)) and \emph{corrugator} activity (\(\hat{\beta} = 0.008\), 95\% CI \([0.001, 0.015]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a positive association with SVs.
 In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.024\), 95\% CI \([0.001, 0.048]\), \(t(97.97) = 2.04\), \(p = .044\)).
-However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
-Detailed information can be found in the supplementary material.
+However, the effect size of this effect was negligibly small (\(f^{2}=\) 0.002).
+Detailed information can be found in Table S.10 in the supplementary material.
 
@@
 The new paradigm was tested on an \emph{n}-back task\textsuperscript{34} and a classic ER paradigm.
-The latter was the goal of the present study and completed by \(N=120\) participants.
+The latter was the purpose of the present study and was completed by \(N=120\) participants.
 As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
@@
 Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing.
-This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort\textsuperscript{22}.
-Both measures also showed high variability between individuals.
-Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
-It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest \emph{corrugator} activity, the lowest effort ratings and the highest utility ratings.
-In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions (``Maintain a neutral facial expression'') is measured directly.
-The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
-By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
-Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy.
-In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
-In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
-Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.
-
-Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1.
-We also found a wide range of SVs (between 0.005 and 1.00), suggesting that individuals have varying degrees of strategy preference.
-There was a significant relationship between SVs and strategy choice.
-Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
+This allows us to replicate previous findings from our research group, showing that strategy use is associated with cognitive effort\textsuperscript{22}.
+Taken together, these findings show that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
+Despite these distinct effects in the manipulation checks, the arousal and effort measures showed high variability between individuals, emphasizing the great extent of subjectivity when dealing with emotional stimuli.
+Additionally, it was surprising that the strategy suppression showed the lowest \emph{corrugator} activity, the lowest effort ratings, and the highest utility ratings.
+In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instruction (``Maintain a neutral facial expression'') is measured directly, which also reduces the complexity of the generation process.
+This considerable degree of immediacy and simplicity might not only reduce the subjective effort, but might also increase the subjective utility of the strategy suppression.
+In addition, the participants receive relatively direct feedback from their own facial muscle activity as to how well suppression has been implemented, which likely influences their perceived regulation success.
+In contrast, the strategies distraction and distancing require a more detailed evaluation of internal states in order to assess their utility and success, which in turn requires more effort.
+
+Almost all participants showed an absolute preference for a particular strategy over the two others, indicated by an SV of 1.
+We also found a wide range of SVs (between 0.005 and 1.00) across the whole sample, suggesting that individuals have varying degrees of preference strength.
+But despite this variation, most participants chose the strategy to which they had assigned their highest SV, supporting hypothesis H7a.
 We also found associations between individual SVs and various predictors.
-Subjective effort, utility, and \emph{corrugator} muscle activity significantly predicted individual SVs.
-Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining 15.5\% of variance in SVs.
-However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
+Subjective effort, utility, and \emph{corrugator} muscle activity significantly predicted individual SVs across all strategies.
+Contrary to our hypothesis H6, utility but not effort was the best predictor for individual SVs, explaining 15.5\% of variance in SVs.
+However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7b.
 In a subsequent exploratory analyses, we found a positive association between individual SVs and self-control.
@@
 However, we did not find an association between NFC and SVs.
-This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance\textsuperscript{29,34}.
-However, these were all cognitive tasks. The role of NFC in affective tasks is not well known yet.
+This is in contrast to reported correlations between NFC, effort discounting, and demand avoidance in cognitive tasks\textsuperscript{29,34}.
+The role of NFC in affective tasks is not well understood yet.
 
@@
 Our aim was to calculate individual subjective values in order to develop a better understanding of ER strategy selection.
-Most individuals show large variability in strategy choice, both within-strategy and between-strategy\textsuperscript{17,70,71}.
-Greater variability may even be adaptive\textsuperscript{12,17}.
+Most individuals show large variability in strategy choice, both within-strategy and between-strategy\textsuperscript{17,70,71}, which in the context of emotion regulation is most likely a sign of good adaptability\textsuperscript{12,17}.
 In addition, a variety of factors that influence strategy choice in specific situations have been examined\textsuperscript{20--22,72--74}, including situation intensity and effort.
-However, these factors have often been studied in isolation from each other.
-Rarely have their combined effects been investigated\textsuperscript{73}.
+However, these factors have often been studied in isolation from each other, and only rarely in conjunction\textsuperscript{73}.
 Furthermore, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) can only estimate how a factor tends to drive the choice in one direction or the other.
-They cannot determine the internal subjective value individuals attribute to the choice options.
+They cannot determine the internal subjective value individuals attribute to all choice options.
 We are confident that we have achieved this with the present paradigm.
-On the one hand, we were able to show which factors have an influence on the values, and on the other hand, we were able to show the actual practical relevance of the values.
-As a predictor of ER effectiveness, \emph{corrugator} activity showed a significant association with SVs, but not \emph{levator} activity or subjective arousal.
-With regard to the EMG measures, this could be because all the pictures we used were negative, i.e.~elicited \emph{corrugator} activity, but only a small proportion of the pictures were perceived as disgusting and thus elicited relatively specific \emph{levator} activity.
+We were not only able to show which factors have an influence on the values, but we were also able to demonstrate the values' practical relevance in the form of choice prediction.
+As an operationalization of ER effectiveness, \emph{corrugator} activity showed a significant association with SVs, but neither \emph{levator} activity or subjective arousal did.
+With regard to the EMG measures, this could be because all the pictures we used were negative, which is commonly associated with higher \emph{corrugator} activity, but only a small proportion of the pictures were classified as disgusting and thus elicited relatively specific \emph{levator} activity.
 However, \emph{corrugator} activity did not differ significantly between ER strategies, but was still associated with SVs.
-One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current strategy, much more direct than, for example, the subjective arousal rating at the end of each experimental block.
-Furthermore, the finding that effort is associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies\textsuperscript{22}.
+One possible reason for this could be that muscle activity provides direct feedback on the effectiveness of the current strategy in a more immediate fashion than, for example, the subjective arousal rating at the end of each experimental block.
+Furthermore, the finding that effort was associated with SVs confirms previous research by our group showing that individuals strive to minimise effort when choosing ER strategies\textsuperscript{22}.
 Finally, the subjective utility ratings showed the greatest explained variance in the SVs.
 This relationship is highly plausible as it involves individuals assessing the utility of the strategy as a means of achieving external and internal regulatory goals.
-This is likely to overlap with subjective values - some literature argues that utility and subjective values are the same thing\textsuperscript{75}.
-However, this is contradicted by our data, as subjective utility could only explain 15.5\% of the variance in SVs.
-
-The highest SVs of the individuals were associated with the choice made by the participants in the last experimental block.
-So far, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{72}.
-This may be because in laboratory studies the choice options are often predetermined by the experimental design\textsuperscript{20--22}.
-Therefore, attempts have been made to investigate ER choice and its influencing factors in everyday life in previous studies.
-Even there, however, certain strategies were often prescribed (for example studies see English et al.\textsuperscript{76}, Millgram et al.\textsuperscript{77}, Wilms et al.\textsuperscript{72}), although covering a large part of the process of emotion generation\textsuperscript{2}.
-Of course, the calculation of SVs in our new CAD paradigm is similarly tied to the strategies with which the strategy of interest is compared.
+Utility is likely to overlap with subjective values - some literature even argues that utility and subjective values are one and the same\textsuperscript{75}.
+However, this claim is not supported by our data, as subjective utility could only explain 15.5\% of the variance in SVs, which leaves a considerable portion of variance in SVs unaccounted for.
+
+The highest SV of each participant was associated with the choice made in the last experimental block.
+So far, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{72}, likely because laboratory studies provide predefined and limited choice options in their experimental design\textsuperscript{20--22}, which is not the case in a natural setting.
+Therefore, previous studies have attempted to investigate ER choice and its influencing factors in everyday life.
+But despite covering a large part of the emotion generation process\textsuperscript{2}, even these studies prescribed certain strategies (for example studies see English et al.\textsuperscript{76}, Millgram et al.\textsuperscript{77}, Wilms et al.\textsuperscript{72}).
+Similarly, the calculation of SVs in our new CAD paradigm depends on the available choice options that were defined in the experimental design.
 To allow all strategies in the ER repertoire to be recorded for each individual, a study might use ecological momentary assessment\textsuperscript{12,78}.
@@
 The extended process model of emotion regulation\textsuperscript{33} postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
-If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped\textsuperscript{33}.
-Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback\textsuperscript{33,80--82}.
-This means that studies on ER Choice should consider not only situational factors, but also contextual factors\textsuperscript{81}.
-For example, in a classic ER choice paradigm\textsuperscript{21}, Murphy and Young\textsuperscript{81} showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
-This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
+If the regulatory goal is not achieved, the ER strategy can be maintained, switched, or stopped\textsuperscript{33}.
+Importantly, feedback on the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback\textsuperscript{33,80--82}.
+This means that studies on ER Choice should consider not only situational factors (i.e., perceived control, emotional intensity\textsuperscript{72}), but also contextual factors (i.e., state-dependent psychological processes of the participant and task characteristics; for a review, see Aldao, 2013\textsuperscript{83})\textsuperscript{81}.
+In a classic ER choice paradigm\textsuperscript{21}, Murphy and Young\textsuperscript{81} could show that strategy choice was significantly influenced by both strategy choice and negative affect during the previous trial, providing evidence that experience gained during the use of ER strategies influences the future choice of ER strategies.
 Our newly developed CAD paradigm also makes an important contribution here.
-The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of SVs.
-That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.
-This raises the question of how stable these individual SVs are.
+The structure of the paradigm provides the opportunity for participants' experiences to influence their SVs, because each participant completes all ER strategies before indicating their preferences the discounting procedure, expecting to be re-applying one of the strategies at the end.
 
@@
 
-Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
-However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
-To establish the \emph{trait} nature of a measure, one could for instance resort to latent state trait modeling\textsuperscript{83}, as recently employed by our group in a related context\textsuperscript{30}.
-The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation.
-By definition, this represents a state.
-As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies\textsuperscript{21}.
-We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
-Our data presented in this study support this idea.
-However, this also implies that SVs should differ according to situational factors (e.g.~stimulus intensity).
-The ER goals that individuals pursue in a given situation must also be taken into account.
-In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals\textsuperscript{85}.
-Wilms and colleagues\textsuperscript{72} pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
-In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
-It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also \protect\hyperlink{Limitations}{Limitations}).
-Therefore, SVs may vary when different reference strategies are used.
-It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals.
-They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires\textsuperscript{9}.
-Of course, it is also possible that such habits influence the internal formation of these subjective values.
-However, our data are not suitable for answering this question.
-In the future, SVs should therefore be collected in several similar situations.
-Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being\textsuperscript{9}.
+Knowing whether the SVs of ER strategies have a trait character would allow a further evaluation of their practical relevance and predictive power.
+With the data of the present study, a trait analysis is not possible, because the SVs of the ER strategies were assessed in only one situation at only one time point, which by definition represents a state.
+A habit would imply consistency of SVs across time points in similar situations, whereas a trait would imply consistency across both time points and situations.
+As noted above, ER choice behaviour is rather state-like, because it is influenced by personal regulatory goals, situational factors, and contextual demands\textsuperscript{21}.
+We therefore believe that the influence of these factors on ER behaviour will also translate into state- or habit-like properties of SVs.
+Such factors could be varied systematically in order to shed light on the stability of SVs, e.g.~by manipulating situational factors such as stimulus intensity, or by systematically assessing the goals that participants pursue with their ER behaviour.
+As Wilms and colleagues\textsuperscript{72} pointed out, situational factors and ER goals are state-like themselves, because they vary greatly across time points and situations.
+While participants in the lab mainly pursue hedonic but not social goals\textsuperscript{85}, a real-life situation with social goals is likely to change not only their ER behaviour but also the SVs they assign to different strategies, especially when their choice options are not restricted by the experimental design (see also \protect\hyperlink{Limitations}{Limitations}).
+To investigate whether the SVs of ER strategies can be conceptualised as states, habits, or traits, one could employ latent state trait modelling, as recently done by our group in a related context\textsuperscript{30}.
+A systematic (non-)variation of situational factors and the assessment of personal factors, e.g.~ER goals, can then help to disentangle time- and situation-specific variance in SVs.
+Importantly, the practical relevance and predictive power of SVs should be assessed at every measurement, as it is quite possible that the correlation between SVs and ER choice is situation-specific as well.
+Such findings would not only provide important insights into ER behaviour, but allow investigations into the association of ER behaviour with external criteria as well, such as well-being\textsuperscript{9}.
 
@@
 A number of limitations must be taken into account when considering our findings.
-First, it should be noted that a block design was used.
-This might have resulted in habituation effects of EMG activity within the block.
+First, it should be noted that a block design was used, which might have resulted in habituation effects of EMG activity within the block.
 However, block designs are common in ER research\textsuperscript{86} and have been used in previous studies\textsuperscript{87}.
-Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block.
-It is known that affect labeling can attenuate emotional experience\textsuperscript{88,89}.
-Therefore, we decided not to conduct ratings after each image.
-Furthermore, we were able to confirm that the implementation of ER strategies was successful at both subjective and physiological levels.
+Secondly, it should be mentioned that subjective arousal, effort, and utility ratings were made retrospectively at the end of each block, which might have led to recency effects.
+But since it is known that affect labeling can attenuate emotional experience\textsuperscript{88,89}, we decided not to conduct ratings after each image.
+Furthermore, we were able to confirm that the implementation of ER strategies was successful on both subjective and physiological levels.
 Still, these features of our research design may have led to slightly lower associations between SVs and predictors.
@@
 Participants were asked to imagine that this was the amount of money they would receive if they repeated this strategy.
-Thus, 2€ could be quite low as an incentive to repeat an whole experimental block of emotion regulation.
-However, we chose this amount because, firstly, we followed the original paradigm of Westbrook\textsuperscript{29}, and secondly, it has been shown in the context of cognitive effort discounting, that a lower incentive increases participants' sensitivity to effort differences\textsuperscript{90}.
-In the future, however, it should be investigated how the level of incentives affects subjective values.
+Thus, 2€ could be an insufficient incentive to repeat a whole experimental block.
+However, we chose this amount because we wanted to follow the original paradigm of Westbrook\textsuperscript{29}, and because it has been shown that a lower incentive increases participants' sensitivity to effort differences\textsuperscript{90}.
+In the future, however, it should be investigated how the incentive size affects subjective values.
 
@@
 In order to cope with changing emotional demands, individuals may flexibly select and apply ER strategies from their repertoire\textsuperscript{12,13}.
-The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected\textsuperscript{12,85}.
+They select the strategy that is most suitable for coping with contextual demands and achieving regulatory goals\textsuperscript{12,85}.
 The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Steyer2015}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-Aldao2013}{}}%
 \CSLLeftMargin{83. }%
-\CSLRightInline{Steyer, R., Mayer, A., Geiser, C.
-\& Cole, D.
-A.
-\href{https://doi.org/10.1146/annurev-clinpsy-032813-153719}{A theory of states and traits-revised}.
-\emph{Annual Review of Clinical Psychology} \textbf{11}, 71--+ (2015).}
+\CSLRightInline{Aldao, A.
+\href{https://doi.org/10.1177/1745691612459518}{The future of emotion regulation research: Capturing context}.
+\emph{Perspectives on Psychological Science} \textbf{8}, 155--172 (2013).}
 

### 2023-08-31 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
implemented non-standardization of HR & FAR in d'

@@
       - Writing - review & editing
+  - name          : "Georgia Clay"
+    orcid         : "0000-0001-5641-6804"
+    affiliation   : "2"
+    role:
+      - Formal analysis
   - name          : "Alexander Strobel"
@@
   - id            : "1"
-    institution   : "Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany"
+    institution   : "Faculty of Psychology, Dresden University of Technology, 01062 Dresden, Germany"
+  - id            : "2"
+    institution   : "Faculty of Psychology, University of Vienna, Vienna 1010, Austria"
 authornote        :
@@
 
-There were two necessary adjustments of the methods.
+There were three necessary adjustments of the methods.
 First, we failed to update the necessary sample size after the analyses changed with the first review round.
 Instead of the 72 subjects stated above, the largest minimum sample size was actually 53 subjects (see hypothesis 1b in the Design Table in the Supplementary Material).
-And secondly, we changed to which hypothesis we applied the specification curve analysis (SCA).
+Secondly, we changed to which hypothesis we applied the specification curve analysis (SCA).
 In the initial Stage 1 submission, we had applied it to the MLM of hypothesis 2b, which at this point included NFC as a predictor.
@@
 Therefore, we applied it to the MLM.
+The final adjustment was made during the Stage 2 revision.
+A fellow researcher made us aware that by using the z-transformed hit and false alarm rates for the computation of $d'$, the mean of $d'$ would be approximately 0 for each $n$-back level by design.
+Consequently, $d'$ could not show changes across $n$-back levels in the manipulation check and would likely yield different results in the MLM.
+Therefore, we computed $d'$ with unstandardized hit and false alarm rates.
+We would like to thank G.C. for pointing us to this fallacy and included her as a co-author.
 
@@
 For each rmANOVA we report the generalized eta squared $\hat{\eta}^2_G$, which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
-The performance measure $d'$ did not change across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`, `r apa_print(hypothesis1a_BF)$statistic`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`), evidence was not in favour of H1a but in favour of H1b.
+In line with hypothesis H1a, the performance measure $d'$ decreased across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result`, `r apa_print(hypothesis1a_BF)$statistic`).
+It decreased more strongly from 2- to 3-back (`r apa_print(pairs(hypothesis1a_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) than from 1- to 2-back (`r apa_print(pairs(hypothesis1a_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 1], y = h1a_data$dprime[h1a_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) or 3- to 4-back (`r apa_print(pairs(hypothesis1a_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
+Similarly, the median RT increased across $n$-back levels (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`), supporting hypothesis H1b.
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
@@
 Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
-The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered large and small, respectively [@Cohen1992].
+The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered medium and small, respectively [@Cohen1992].
 This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
@@
 Regardless of the preprocessing pipeline, $n$-back level and $d'$ were significant predictors of SVs, and had stable effect estimates across all pipelines.
-There was only one pipeline in which the median RT was a significant predictor of SVs.
-This pipeline contained data that had been inverse transformed across subjects but within conditions, i.e.
-within the round of an $n$-back level, and RTs beyond 2 $MAD$ from the median had been excluded.
+There was no pipeline in which the median RT was a significant predictor of SVs, but it showed volatile effect estimates across pipelines.
+The pipelines that yielded the highest estimates for $d'$ and the median RT used log-transformed data, irrespective of the dimension and exclusion criteria.
 
@@
 
-The performance measure $d'$ did not differ across $n$-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
-This points to three important characteristics of the $n$-back task in this context.
-Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to $n=3$, and could be used to investigate inter-individual differences for $n>3$.
-Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where $d'$ would decline and RT would remain stable.
+Both $d'$ and the median RT changed across $n$-back levels, indicating that there was an increase in objective task load.
+The steepest decrease in $d'$ between levels was from 2- to 3-back, resembling the declining logistic curve of the SVs.
+Interestingly, the median RT increased from 2- to 3-back, but did not differ between 2- and 4-back.
+Since feedback was given after each round, this pattern could be interpreted in such a way that participants tried to compensate their lower accuracy in 3-back by relying more on luck than on memory in 4-back and prioritized speed over accuracy.
+Furthermore, several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when $n$ was an even number than when $n$ was an odd number.
+This would support the notion that the manipulation of task load in an $n$-back task is not strictly continuous.
 And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010], suggesting that they should always be reported as separate indices.
-Additionally, $d'$ might not have differed across $n$-back levels because the manipulation of task load is not strictly continuous.
-Several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when $n$ was an even number than when $n$ was an odd number.
 
@@
 With increasing $n$-back level and decreasing $d'$, the SV decreased.
-The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not $d'$ yielded significant differences across levels in the manipulation checks.
-However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per $n$-back level, as an anchor during the effort discounting.
+The median RT was not a significant predictor in this model.
+Participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per $n$-back level, as an anchor during the effort discounting.
 This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
@@
 
-The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis, with betas that varied by less than 0.01.
-In contrast to this stood the variability of the median RT betas, which ranged from about `r round(max(sca_results$beta_r), digits = 2)` to `r round(min(sca_results$beta_r), digits = 2)`, and reached significance in only one pipeline.
-This pipeline was among the three pipelines with the highest $BF_{10}$, and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 $MAD$ from the median.
-Interestingly, the curve of median RT betas in Figure\ \@ref(fig:sca-plot)a mirrored the rectangular pipeline indicators in the transformation rows of Figure\ \@ref(fig:sca-plot)b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
+The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis.
+The effect estimates of the $n$-back level varied by about `r round(diff(range(sca_results$beta_n)), digits = 3)`, those of $d'$ by about `r round(diff(range(sca_results$beta_d)), digits = 3)`.
+In contrast to this stood the variability of the median RT effect estimates (around `r round(diff(range(sca_results$beta_r)), digits = 3)`), which did not reach significance in any pipeline.
+Interestingly, the curve of median RT betas in Figure\ \@ref(fig:sca-plot)a roughly mirrored the rectangular pipeline indicators in the transformation rows of Figure\ \@ref(fig:sca-plot)b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
 As Fernandez et al.[-@Fernandez2020] found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond $\alpha=.05$, and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
 Our data seems to corroborate this finding for $n$-back tasks as well.
-Surprisingly, the $d'$ betas appear almost unaffected by the preprocessing pipeline, even though $d'$ was computed after the outlier exclusion.
+Surprisingly, the $d'$ betas appeared almost unaffected by the preprocessing pipeline, even though $d'$ was computed after the outlier exclusion.
 This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.
@@
 JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
-JZ, CS, and CK did the formal analysis.
+JZ, CS, GC, and CK did the formal analysis.
 JZ visualized the results.
@@
 The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
-The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level.
+The pipelines in both panels are sorted left to right in ascending order of the magnitude of the beta estimate of the predictor $d'$.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

### 2023-08-31 06_Paper/COG-ED/Stage 2/Supplement.Rmd
implemented non-standardization of HR & FAR in d'

@@
     institution   : "Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
+  - id            : "2"
+    institution   : "Faculty of Psychology, University of Vienna, Vienna 1010, Austria"
 keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, $n$-back"

### 2023-08-31 06_Paper/COG-ED/Stage 2/Analysis.R

@@ -744,32 +744,35 @@ for (j in 1:length(pipelines_data)) {
   }
   
   # z-transform the hit rate and the false alarm rate
-  
+
   dprime$hitrate.z = NA
   dprime$falsealarmrate.z = NA
-  
+
   for (i in 1:4) { # for each n-back level
-    
+
     for (z in 1:2) { # for each round
-      
+
       dprime$hitrate.z[which(dprime$level == i & dprime$round == z)]        <- scale(dprime$hitrate[which(dprime$level == i & dprime$round == z)])
       dprime$falsealarmrate.z[which(dprime$level == i & dprime$round == z)] <- scale(dprime$falsealarmrate[which(dprime$level == i & dprime$round == z)])
-      
+
     }
   }
   
   # calculate d'
   
-  dprime$d <- dprime$hitrate.z - dprime$falsealarmrate.z
+  dprime$d.z <- dprime$hitrate.z - dprime$falsealarmrate.z
+  dprime$d <- dprime$hitrate - dprime$falsealarmrate
   
   # feed d' trialwise into the pipeline data frame
   
   for (i in 1:nrow(pipelines_data[[j]])) {
     
+    pipelines_data[[j]]$dprime.z[i] <- dprime$d.z[dprime$subject == pipelines_data[[j]]$subject[i] &
+                                                dprime$level == pipelines_data[[j]]$level[i] &
+                                                dprime$round == pipelines_data[[j]]$round[i]]
     pipelines_data[[j]]$dprime[i] <- dprime$d[dprime$subject == pipelines_data[[j]]$subject[i] &
                                                 dprime$level == pipelines_data[[j]]$level[i] &
                                                 dprime$round == pipelines_data[[j]]$round[i]]
-    
   }
 }
 
@@ -835,8 +838,14 @@ base::remove(mylevel, myround, mysubject, mymedianRT, newdata, medianRT)
 
 for (j in 1:length(pipelines_data)) {
   
-  pipelines_data[[j]] <- unique(pipelines_data[[j]][ ,c("subject","level","round","sv","nfc","dprime","medianRT")])
+  pipelines_data[[j]] <- unique(pipelines_data[[j]][ ,c("subject","level","round","sv","nfc","dprime","dprime.z","medianRT")])
   
+}
+
+#somehow the first row of every data frame has not been removed, so I'll do that here
+#this is a quick fix for working on something else, I'll take care of it later
[…]

### 2023-09-01 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
included acknowledgement and fixed 3 digit format

@@
       - Writing - review & editing
-  - name          : "Georgia Clay"
-    orcid         : "0000-0001-5641-6804"
-    affiliation   : "2"
-    role:
-      - Formal analysis
   - name          : "Alexander Strobel"
@@
     institution   : "Faculty of Psychology, Dresden University of Technology, 01062 Dresden, Germany"
-  - id            : "2"
-    institution   : "Faculty of Psychology, University of Vienna, Vienna 1010, Austria"
 authornote        :
@@
 Therefore, we computed $d'$ with unstandardized hit and false alarm rates.
-We would like to thank G.C. for pointing us to this fallacy and included her as a co-author.
+We would like to thank Georgia Clay for pointing us to this fallacy.
 
@@
 The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis.
-The effect estimates of the $n$-back level varied by about `r round(diff(range(sca_results$beta_n)), digits = 3)`, those of $d'$ by about `r round(diff(range(sca_results$beta_d)), digits = 3)`.
+The effect estimates of the $n$-back level varied by about `r format(round(diff(range(sca_results$beta_n)), digits = 3), digits = 3)`, those of $d'$ by about `r format(round(diff(range(sca_results$beta_d)), digits = 3), digits = 3)`.
 In contrast to this stood the variability of the median RT effect estimates (around `r round(diff(range(sca_results$beta_r)), digits = 3)`), which did not reach significance in any pipeline.
@@
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection.
+The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection, and Georgia Clay for noticing and calling our attention to the fallacy of z-transforming the hit and false alarm rates.
 
@@
 JZ and CS developed the methodology, investigated, administered the project, and wrote the software.
-JZ, CS, GC, and CK did the formal analysis.
+JZ, CS, and CK did the formal analysis.
 JZ visualized the results.

### 2023-09-01 06_Paper/COG-ED/Stage 2/Manuscript.tex
included acknowledgement and fixed 3 digit format

@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Dresden University of Technology, 01062 Dresden, Germany}
 
@@
 Therefore, we applied it to the MLM.
+The final adjustment was made during the Stage 2 revision.
+A fellow researcher made us aware that by using the z-transformed hit and false alarm rates for the computation of \(d'\), the mean of \(d'\) would be approximately 0 for each \(n\)-back level by design.
+Consequently, \(d'\) could not show changes across \(n\)-back levels in the manipulation check and would likely yield different results in the MLM.
+Therefore, we computed \(d'\) with unstandardized hit and false alarm rates.
+We would like to thank Georgia Clay for pointing us to this fallacy.
 
@@
 For each rmANOVA we report the generalized eta squared \(\hat{\eta}^2_G\), which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
-The performance measure \(d'\) did not change across \(n\)-back levels (\(F(2.85, 327.28) = 0.01\), \(p = .999\), \(\hat{\eta}^2_G = .000\), 90\% CI \([.000, .000]\), \(\mathrm{BF}_{\textrm{10}} = 3.31 \times 10^{-3}\)), but the median RT did (\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)), evidence was not in favour of H1a but in favour of H1b.
+In line with hypothesis H1a, the performance measure \(d'\) decreased across \(n\)-back levels (\(F(2.74, 315.51) = 197.18\), \(p < .001\), \(\hat{\eta}^2_G = .464\), 90\% CI \([.403, .516]\), \(\mathrm{BF}_{\textrm{10}} = 1.56 \times 10^{101}\)).
+It decreased more strongly from 2- to 3-back (\(t(345) = 10.41\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.71 \times 10^{23}\)) than from 1- to 2-back (\(t(345) = 4.31\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 93,954.04\)) or 3- to 4-back (\(t(345) = 7.18\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 2.45 \times 10^{14}\)).
+Similarly, the median RT increased across \(n\)-back levels (\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)), supporting hypothesis H1b.
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
@@
 
+The different curves of SVs across \(n\)-back levels can be seen in Figure~\ref{fig:sv-by-pref}, grouped into those participants who had an SV of 1.0 for 1-back (\(n=71\)), for 2-back (\(n=18\)), for 3-back (\(n=9\)), for 4-back (\(n=13\)), or all SVs below 1.0, i.e.~no absolute preference for any level (\(n=5\)).
+While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult \(n\)-back levels.
+However, each panel in Figure~\ref{fig:sv-by-pref} contains curves of participants who had large differences between their four SVs and curves of participants who had a difference of less than 0.2 between their highest and their lowest SV, so preferring one level does not necessarily mean having a strong aversion against the others, regardless of difficulty level.
+
+{[}FIGURE \ref{fig:sv-by-pref} HERE{]}
+
 When asking participants what motivated their decisions in the cognitive effort discounting paradigm, 11.2\% stated that they wanted to avoid boredom, 22.4\% stated that they wanted a challenge, 34.5\% stated that they wanted to avoid effort, and 4.3\% stated that they wanted to relax.
 The remaining 27.6\% of participants used the free text field and provided reasons such as ``I wanted a fair relation of effort and reward.'', ``I wanted the fun that I had in the more challenging levels.'', ``I wanted to maximize reward first and minimize effort second.'', or ``I did not want to perform poorly when I was being paid for it.''.
-Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per \(n\)-back level.
+Figure \ref{fig:motivation} shows the different motivations in the context of the SVs per \(n\)-back level.
+
+{[}FIGURE \ref{fig:motivation} HERE{]}
 
@@
 We did not use an optimization algorithm to improve the fit of the random intercept model.
-A total of 9 data points from 6 participants were excluded, because the residuals exceeded 3 SD above the mean.
+A total of 10 data points from 6 participants were excluded, because the residuals exceeded 3 SD above the mean.
 The results of the final model are displayed in Table~\ref{tab:H2b-results}.
@@
 \midrule
-Intercept & 0.81 & 0.01 & 114.82 & 78.34 & <.001 &  & 0.09\\
-n-back level & 0.05 & 0.00 & 799.38 & 18.22 & <.001 & 0.64 & \\
-d' & 0.02 & 0.00 & 798.75 & 5.60 & <.001 & 0.04 & \\
-median RT & 0.02 & 0.07 & 798.58 & 0.30 & 0.768 & 0.00 & \\
+Intercept & 0.81 & 0.01 & 115.00 & 78.68 & <.001 &  & 0.09\\
+n-back level & 0.03 & 0.00 & 797.54 & 9.99 & <.001 & 0.21 & \\
+d' & 0.21 & 0.03 & 797.63 & 6.28 & <.001 & 0.05 & \\
+median RT & 0.03 & 0.07 & 797.80 & 0.42 & 0.674 & 0.00 & \\
 \bottomrule
@@
 
-An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other (\(\chi^2 (2)\) = 34.48, \(p<.001\)), and with an Akaike Information Criterion of \(AIC=-492.61\) and a Bayesian Information Criterion of \(BIC=-454.02\) the declining logistic model was superior to the linear model (\(AIC=-462.12\), \(BIC=-433.18\)).
+An exploratory ANOVA was used to compare the fit of the final model with a linear random intercept model, confirming that the two models were different from each other (\(\chi^2 (2)\) = 28.35, \(p<.001\)), and with an Akaike Information Criterion of \(AIC=-510.93\) and a Bayesian Information Criterion of \(BIC=-472.35\) the declining logistic model was superior to the linear model (\(AIC=-486.58\), \(BIC=-457.65\)).
 Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
-The final model had an effect size of \(f^{2}=\) 0.64 for the \(n\)-back levels and \(f^{2}=\) 0.04 for \(d'\), which are considered large and small, respectively\textsuperscript{46}.
-This means that the \(n\)-back level explained 64.20\% and \(d'\) explained 3.95\% of variance in SVs relative to the unexplained variance, respectively.
-The beta coefficient indicated that with every 1-unit increase in \(d'\), the SV increased by 0.02.
+The final model had an effect size of \(f^{2}=\) 0.21 for the \(n\)-back levels and \(f^{2}=\) 0.05 for \(d'\), which are considered medium and small, respectively\textsuperscript{46}.
+This means that the \(n\)-back level explained 20.67\% and \(d'\) explained 4.90\% of variance in SVs relative to the unexplained variance, respectively.
+The beta coefficient indicated that with every 1-unit increase in \(d'\), the SV increased by 0.21.
 Due to the coding scheme of the logistic contrast, the beta coefficient of the \(n\)-back level has to be interpreted inversely, so SVs decline with increasing \(n\)-back level.
@@
 Regardless of the preprocessing pipeline, \(n\)-back level and \(d'\) were significant predictors of SVs, and had stable effect estimates across all pipelines.
-There was only one pipeline in which the median RT was a significant predictor of SVs.
-This pipeline contained data that had been inverse transformed across subjects but within conditions, i.e.~within the round of an \(n\)-back level, and RTs beyond 2 \(MAD\) from the median had been excluded.
+There was no pipeline in which the median RT was a significant predictor of SVs, but it showed volatile effect estimates across pipelines.
+The pipelines that yielded the highest estimates for \(d'\) and the median RT used log-transformed data, irrespective of the dimension and exclusion criteria.
 
@@
 
-Figure~\ref{fig:nfcgroups-sv} shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.
-There is a concentration of participants who have assigned their highest SV to 1-back, and this concentration fades across \(n\)-back levels.
-At the same time, there is a subtle separation of SVs across \(n\)-back levels, depending on the participant's NFC score: While the SVs of those with higher NFC scores remain elevated, the SVs of those with lower NFC scores decline more strongly.
-Specifically, \(n=71\) participants had an absolute preference for 1-back, \(n=18\) for 2-back, \(n=9\) for 3-back, and \(n=13\) for 4-back.
-There were \(n=5\) participants who did not have an absolute preference for any \(n\)-back level, i.e.~none of their SVs was 1.
-
-{[}FIGURE \ref{fig:nfcgroups-sv} HERE{]}
-
 The median NFC was 16, with \(n=57\) subjects below and \(n=59\) above the median.
 We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of the \(n\)-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56\)) nor an interaction of NFC group and \(n\)-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
-Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Figure~\ref{fig:h3ac-plot}a).
+There was a main effect of the \(n\)-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68 \pm 0.00\%\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56 \pm 0.03\%\)) nor an interaction of NFC group and \(n\)-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
+Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Supplementary Figure S2a).
 This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, again resembling the declining logistic function.
-
-{[}FIGURE \ref{fig:h3ac-plot} HERE{]}
 
@@
 The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
+Supplementary Figure S4 shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.
+
+Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
+We computed an rmANOVA with the \(n\)-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
+Both the NFC score (\(F(1, 114) = 4.34\), \(p = .039\), \(\hat{\eta}^2_G = .011\), 90\% CI \([.000, .063]\), \(\mathrm{BF}_{\textrm{10}} = 0.57\)) and the \(n\)-back level (\(F(2.02, 229.75) = 67.24\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(\mathrm{BF}_{\textrm{10}} = 2.70 \times 10^{30}\)) showed significant main effects, as well as a significant interaction (\(F(2.02, 229.75) = 3.78\), \(p = .024\), \(\hat{\eta}^2_G = .023\), 90\% CI \([.000, .049]\), \(\mathrm{BF}_{\textrm{10}} = 0.12\)).
+Analyzing the estimated marginal means of the linear trends for each \(n\)-back level indicated a significant difference between the slopes of 1-back and 4-back (\(\Delta M = -0.09\), \(95\%\ \mathrm{CI}_\mathrm{\scriptsize Tukey(4)}\) \([-0.15, -0.02]\), \(t(456) = -3.22\), \(p_\mathrm{\scriptsize Tukey(4)} = .008\)), but not between any other two levels.
+Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure~\ref{fig:nfccont-sv}).
+The full results of this exploratory analysis of NFC as a continuous covariate can be found in Table S.18 and S.19 in the Supplementary Material.
+
+{[}FIGURE \ref{fig:nfccont-sv} HERE{]}
 
@@
 
-The performance measure \(d'\) did not differ across \(n\)-back levels, but the RT increased from 1- to 2- to 3-back and then remained on a high level for 4-back.
-This points to three important characteristics of the \(n\)-back task in this context.
-Firstly, RT as a valid group-level indicator of performance might only be useful for levels up to \(n=3\), and could be used to investigate inter-individual differences for \(n>3\).
-Secondly, there is a speed-accuracy tradeoff in the first three levels, that might even re-emerge in higher levels, where \(d'\) would decline and RT would remain stable.
+Both \(d'\) and the median RT changed across \(n\)-back levels, indicating that there was an increase in objective task load.
+The steepest decrease in \(d'\) between levels was from 2- to 3-back, resembling the declining logistic curve of the SVs.
+Interestingly, the median RT increased from 2- to 3-back, but did not differ between 2- and 4-back.
+Since feedback was given after each round, this pattern could be interpreted in such a way that participants tried to compensate their lower accuracy in 3-back by relying more on luck than on memory in 4-back and prioritized speed over accuracy.
+Furthermore, several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when \(n\) was an even number than when \(n\) was an odd number.
+This would support the notion that the manipulation of task load in an \(n\)-back task is not strictly continuous.
 And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before\textsuperscript{47} and both show different associations with various measures of intelligence\textsuperscript{4}, suggesting that they should always be reported as separate indices.
-Additionally, \(d'\) might not have differed across \(n\)-back levels because the manipulation of task load is not strictly continuous.
-Several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when \(n\) was an even number than when \(n\) was an odd number.
 
@@
 The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across \(n\)-back levels.
-The best fit was a declining logistic curve, reflecting that the majority of participants preferred 1-back and that SVs for 2-back were also high, before having more inter-individual variance for 3- and 4-back.
-Thomson and Oppenheimer\textsuperscript{48} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
+The best fit was a declining logistic curve, reflecting that 1) the majority of participants preferred the easiest level, 2) 2-back was generally closer in preference to 1-back than 3-back was to 2-back, and 3) objective task load and subjective preference do not stand in a linear relationship.
+Since the majority of participants preferred the easiest level, we rejected the ascending quadratic and skewed normal contrasts, which implied lower SVs for 1- than for 2-back.
+The fact that the majority of participants preferred lower over higher effort, but a minority showed the opposite pattern, is in line with previous research on cognitive effort by Kool et al.~(2010)\textsuperscript{48}.
+Importantly, having a paradigm that can accurately assess the preferences of the minority is necessary but not sufficient, because the interindividual variability is so high that it blurs effects on the group level.
+Figure~\ref{fig:sv-by-pref} suggests that those who prefer either 1- or 2-back have a slightly steeper discounting curve than those who prefer 3- or 4-back, meaning they have lower SVs for higher levels than those who prefer a higher level have for the easier levels.
+But as the figure also shows, there is great interindividual variability in the discounting patterns, regardless of which level has the highest SV.
+Thomson and Oppenheimer\textsuperscript{49} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
 For example, the \(n\)-back task is likely not a continuous manipulation of task load, as discussed above.
-However, the declining logistic curve is similar to the sigmoidal curve that had the best fit in a different effort paradigm\textsuperscript{49}, which the authors explained with the low effect of low energy costs, suggesting there are still common features of effort across different tasks and domains.
+However, the declining logistic curve is similar to the sigmoidal curve that has been found for a physical\textsuperscript{50} and a cognitive effort paradigm\textsuperscript{51}, suggesting there are common features of effort across different tasks and domains.
 The MLM with the logistic contrast showed that the \(n\)-back level explained the majority of variance in SVs, while the performance measure \(d'\) also explained some variance in SVs, albeit less.
 With increasing \(n\)-back level and decreasing \(d'\), the SV decreased.
-The median RT was not a significant predictor in this model, which was somewhat surprising because RT but not \(d'\) yielded significant differences across levels in the manipulation checks.
-However, participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e.~twice per \(n\)-back level, as an anchor during the effort discounting.
+The median RT was not a significant predictor in this model.
+Participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e.~twice per \(n\)-back level, as an anchor during the effort discounting.
 This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
@@
 
-The declining logistic \(n\)-back levels and \(d'\) remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis, with betas that varied by less than 0.01.
-In contrast to this stood the variability of the median RT betas, which ranged from about 0.10 to -0.03, and reached significance in only one pipeline.
-This pipeline was among the three pipelines with the highest \(BF_{10}\), and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 \(MAD\) from the median.
-Interestingly, the curve of median RT betas in Figure~\ref{fig:sca-plot}a mirrored the rectangular pipeline indicators in the transformation rows of Figure~\ref{fig:sca-plot}b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
-As Fernandez et al.\textsuperscript{50} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
+The declining logistic \(n\)-back levels and \(d'\) remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis.
+The effect estimates of the \(n\)-back level varied by about 0.00, those of \(d'\) by about 0.07.
+In contrast to this stood the variability of the median RT effect estimates (around 0.16), which did not reach significance in any pipeline.
+Interestingly, the curve of median RT betas in Figure~\ref{fig:sca-plot}a roughly mirrored the rectangular pipeline indicators in the transformation rows of Figure~\ref{fig:sca-plot}b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
+As Fernandez et al.\textsuperscript{52} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
 Our data seems to corroborate this finding for \(n\)-back tasks as well.
-Surprisingly, the \(d'\) betas appear almost unaffected by the preprocessing pipeline, even though \(d'\) was computed after the outlier exclusion.
+Surprisingly, the \(d'\) betas appeared almost unaffected by the preprocessing pipeline, even though \(d'\) was computed after the outlier exclusion.
 This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.
@@
 
-This research is partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
+This research was partly funded by the German Research Foundation (DFG) as part of the Collaborative Research Center (CRC) 940, and partly funded by centralized funds of the Faculty of Psychology at Technische Universität Dresden.
 The funders have/had no role in study design, data collection and analysis, decision to publish or preparation of the manuscript.
-The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection.
+The authors would like to thank Juliana Krause and Maja Hentschel for their help with data collection, and Georgia Clay for noticing and calling our attention to the fallacy of z-transforming the hit and false alarm rates.
 
@@
 \begin{figure}[H]
+\includegraphics[width=\textwidth]{Figures/sv_by_pref} \caption{Subjective values (SV) per $n$-back level, grouped into those who had an SV = 1 for 1-back, for 2-back, for 3-back, for 4-back, or no SV = 1 for any level.
+The lines have a vertical jitter of 0.02.
+Smoothing of conditional means with Loess method.
+Transparent overlays depict the 95\% confidence interval.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:sv-by-pref}
+\end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=\textwidth]{Figures/motivation} \caption{Trajectories of subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
+$N=116$.
+'Other' opened up a free text field.
+Smoothing of conditional means with Loess method.
+Transparent overlays depict the 95\% confidence interval.
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:motivation}
+\end{figure}
+
+\begin{figure}[H]
 \includegraphics[width=\textwidth]{Figures/sca-plot} \caption{Results of the multi level model for each of the 63 preprocessing pipelines.
@@
 The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
-The pipelines in both panels are sorted left to right in descending order of the magnitude of the beta estimate of the predictor n-back level.
+The pipelines in both panels are sorted left to right in ascending order of the magnitude of the beta estimate of the predictor $d'$.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:sca-plot}
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/nfcgroups-sv} \caption{Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median.
+\includegraphics[width=\textwidth]{Figures/nfccont_sv} \caption{Predicted slopes of subjective values depending on individual Need for Cognition scores for each $n$-back level.
+The slopes of 1-back and 4-back are different at $p=.01$.
 $N=116$.
-The scatter has a horizontal jitter of 0.2.
-Smoothing of conditional means with Loess method.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:nfcgroups-sv}
+Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:nfccont-sv}
 \end{figure}
 
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/h3ac-plot} \caption{Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back.
-Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges.
-NFC = Need for Cognition score.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3ac-plot}
-\end{figure}
-
-\begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/h3b-plot} \caption{NASA-TLX sum scores for each $n$-back level.
-Colours indicate Need for Cognition (NFC) score above or below the median.
-$N=116$.
-Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3b-plot}
-\end{figure}
-
 \end{document}

### 2023-10-11 06_Paper/COG-ED/Stage 2/Manuscript.tex
updated title

@@
 {}{\PatchFailed}
-\keywords{effort discounting, registered report, specification curve analysis, need for cognition, $n$-back\newline\indent Word count: ~ 7000}
+\keywords{effort discounting, registered report, specification curve analysis, need for cognition, *n*-back\newline\indent Word count: ~ 7000}
 \usepackage{lineno}
@@
 \hypersetup{
-  pdftitle={When easy is not preferred: A discounting paradigm to assess load-independent task preference},
+  pdftitle={Need for cognition is associated with a preference for higher task load in effort discounting},
   pdfauthor={Josephine Zerna,1, Christoph Scheffel,1, Corinna Kührt1, \& Alexander Strobel1},
   pdflang={en-EN},
-  pdfkeywords={effort discounting, registered report, specification curve analysis, need for cognition, \(n\)-back},
+  pdfkeywords={effort discounting, registered report, specification curve analysis, need for cognition, \emph{n}-back},
   hidelinks,
@@
 
-\title{When easy is not preferred: A discounting paradigm to assess load-independent task preference}
+\title{Need for cognition is associated with a preference for higher task load in effort discounting}
 \author{Josephine Zerna\textsuperscript{$\dagger{}$,1}, Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Corinna Kührt\textsuperscript{1}, \& Alexander Strobel\textsuperscript{1}}
@@
 Results show that many of the 116 participants preferred a more or the most difficult level.
-Variance in SVs was best explained by a declining logistic contrast of the \(n\)-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
-Participants with higher Need for Cognition scores perceived higher \(n\)-back levels as less effortful and found them less aversive.
+Variance in SVs was best explained by a declining logistic contrast of the \emph{n}-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
+Participants with higher Need for Cognition scores perceived higher \emph{n}-back levels as less effortful and found them less aversive.
 Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences only emerged in higher levels.
@@
 
-One task that is often used to investigate effort is the \(n\)-back task, a working memory task in which a continuous stream of stimuli, e.g.~letters, is presented on screen.
-Participants indicate via button press whether the current stimulus is the same as \(n\) stimuli before, with \(n\) being the level of difficulty between one and six\textsuperscript{3}.
-The \(n\)-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times\textsuperscript{4}, and brain activity in areas associated with working memory\textsuperscript{5,6}.
-However, its reliability measures are mixed, and associations of \(n\)-back performance and measures such as executive functioning and fluid intelligence are often inconsistent\textsuperscript{4}.
-
-A way to quantify the subjective cost of each \(n\)-back level has been developed by Westbrook, Kester, and Braver\textsuperscript{7}, called the Cognitive Effort Discounting Paradigm (COG-ED).
-First, the participants complete the \(n\)-back levels to familiarize themselves with the task.
+One task that is often used to investigate effort is the \emph{n}-back task, a working memory task in which a continuous stream of stimuli, e.g.~letters, is presented on screen.
+Participants indicate via button press whether the current stimulus is the same as \emph{n} stimuli before, with \emph{n} being the level of difficulty between one and six\textsuperscript{3}.
+The \emph{n}-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times\textsuperscript{4}, and brain activity in areas associated with working memory\textsuperscript{5,6}.
+However, its reliability measures are mixed, and associations of \emph{n}-back performance and measures such as executive functioning and fluid intelligence are often inconsistent\textsuperscript{4}.
+
+A way to quantify the subjective cost of each \emph{n}-back level has been developed by Westbrook, Kester, and Braver\textsuperscript{7}, called the Cognitive Effort Discounting Paradigm (COG-ED).
+First, the participants complete the \emph{n}-back levels to familiarize themselves with the task.
 Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
@@
 
-With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest \(n\)-back level has the highest SV.
-We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different \(n\)-back levels without presuming that all individuals inherently prefer the easiest level.
+With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest \emph{n}-back level has the highest SV.
+We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different \emph{n}-back levels without presuming that all individuals inherently prefer the easiest level.
 Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks\textsuperscript{17}, we call it the Cognitive and Affective Discounting Paradigm (CAD).
 In the present study, we validated the CAD paradigm by conceptually replicating the findings of Westbrook et al.\textsuperscript{7}.
-Additionally, we compared the effort discounting behavior of participants regarding the \(n\)-back task and an emotion regulation task.
+Additionally, we compared the effort discounting behavior of participants regarding the \emph{n}-back task and an emotion regulation task.
 The full results of the latter are published in a second Registered Report\textsuperscript{17}.
@@
 Our hypotheses were derived from the results of Westbrook et al.\textsuperscript{7}.
-As a manipulation check, we hypothesized that with increasing \(n\)-back level the (1a) the signal detection parameter \(d'\) declines, while (1b) reaction time and (1c) perceived task load increase.
-Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing \(n\)-back level, and (2b) they do so even after controlling for declining task performance.
+As a manipulation check, we hypothesized that with increasing \emph{n}-back level the (1a) the signal detection parameter \emph{d'} declines, while (1b) reaction time and (1c) perceived task load increase.
+Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing \emph{n}-back level, and (2b) they do so even after controlling for declining task performance.
 And finally, we hypothesized that the CAD paradigm can show inter-individual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
@@
 In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
-The paradigm started with the \(n\)-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The paradigm started with the \emph{n}-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
 The levels were referred to by color (1-back: black, 2-back: red, 3-back: blue, 4-back: green) to avoid anchor effects in the effort discounting procedure.
 To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)\textsuperscript{29}, where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this \(n\)-back level.
-After the \(n\)-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
-They were told that one of their choices would be randomly picked for the final run of \(n\)-back.
+At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this \emph{n}-back level.
+After the \emph{n}-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
+They were told that one of their choices would be randomly picked for the final run of \emph{n}-back.
 However, this data was not analyzed as it only served to incentivise truthful behavior and to stay close to the design of Westbrook et al.\textsuperscript{7}.
@@
 Sample size determination was mainly based on the results of the analyses of Westbrook et al.\textsuperscript{7} (see Design Table in the Supplementary Material).
-The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and \(n\)-back level influencing SVs.
+The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and \emph{n}-back level influencing SVs.
 Sample size analysis with \emph{G*Power}\textsuperscript{32,33} indicated that we should collect data from at least 72 participants, assuming \(\alpha=.05\) and \(\beta=.95\).
@@
 No data was replaced.
-The performance measure \(d'\) was computed as the difference of the \emph{z}-transformed hit rate and the \emph{z}-transformed false alarm rate\textsuperscript{34}.
+The performance measure \emph{d'} was computed as the difference of the \emph{z}-transformed hit rate and the \emph{z}-transformed false alarm rate\textsuperscript{34}.
 Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100~ms, as the relevant cognitive processes cannot have been completed before\textsuperscript{35,36}.
-Aggregated RT values were described using the median and the median of absolute deviation (\(MAD\)) as robust estimates of center and variability, respectively\textsuperscript{37}.
+Aggregated RT values were described using the median and the median of absolute deviation (\emph{MAD}) as robust estimates of center and variability, respectively\textsuperscript{37}.
 Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior\textsuperscript{38,39}.
@@
 \emph{Manipulation check.}
-Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing \(d'\) between two levels of 1- to 4-back at a time.
+Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing \emph{d'} between two levels of 1- to 4-back at a time.
 Another rmANOVA with six paired contrasts was computed to compare the median RT between two levels of 1- to 4-back at a time.
@@
 All SVs of each level were averaged to compute one ``global'' SV for each level.
-An rmANOVA with four different contrasts were computed to investigate the association of SVs and the \(n\)-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2) (Supplementary Figure S1).
+An rmANOVA with four different contrasts were computed to investigate the association of SVs and the \emph{n}-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2) (Supplementary Figure S1).
 Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.
 
-To determine the influence of task performance on the association of SVs and \(n\)-back level, we performed MLM.
+To determine the influence of task performance on the association of SVs and \emph{n}-back level, we performed MLM.
 We applied restricted maximum likelihood (REML) to fit the model.
 As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we estimated a random slopes model of \(n\)-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
-As Mussel et al.\textsuperscript{41} could show, participants with high versus low NFC not only have a more shallow decline in performance with higher \(n\)-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
-We controlled for performance, i.e., \(d'\) (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
+Second, we estimated a random slopes model of \emph{n}-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
+As Mussel et al.\textsuperscript{41} could show, participants with high versus low NFC not only have a more shallow decline in performance with higher \emph{n}-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
+We controlled for performance, i.e., \emph{d'} (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
 \[
@@
 This was done by excluding all data points with absolute standardized residuals above 3 SD.
-As effect size measures, we calculated pseudo \(R^{2}\) for our model and \(f^{2}\) to estimate the effect of \(n\)-back level according to Lorah\textsuperscript{43}.
+As effect size measures, we calculated pseudo \(R^{2}\) for our model and \(f^{2}\) to estimate the effect of \emph{n}-back level according to Lorah\textsuperscript{43}.
 
@@
 The sample was divided into participants with low and high NFC using a median split.
-We then computed an rmANOVA with the within-factor \(n\)-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
+We then computed an rmANOVA with the within-factor \emph{n}-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
 Post-hoc tests were computed depending on which effect reached significance at \(p<.01\).
 To ensure the validity of this association, we conducted a specification curve analysis\textsuperscript{44}, which included 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3~\(MAD\) from the median, RTs below 100~or~200~ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within \(n\)-back levels).
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3~\emph{MAD} from the median, RTs below 100~or~200~ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within \emph{n}-back levels).
 The rmANOVA was run with each of the 63~pipelines, which also included our main pipeline (untransformed data, exclusion of RTs below 100~ms).
@@
 The association of subjective task load with NFC was examined similarly.
-We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor \(n\)-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at \(p<.01\).
+We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor \emph{n}-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at \(p<.01\).
 And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e.~as the SV rises, the aversiveness declines, and vice versa.
 We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
-Then, we computed an rmANOVA with the within-factor \(n\)-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at \(p<.01\).
+Then, we computed an rmANOVA with the within-factor \emph{n}-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at \(p<.01\).
 
@@
 Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA-TLX were analyzed with \(n=14\) data sets.
-The results showed increases in subjective and objective task load measures with higher \(n\)-back level.
-Importantly, SVs were lower for higher \(n\)-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
-The MLM revealed \(n\)-back level as a reliable predictor of SV, even after controlling for declining task performance (\(d'\) and median RT).
-NASA-TLX scores were higher with higher \(n\), and lower for the group with lower NFC scores, but NFC and \(n\)-back level did not interact.
+The results showed increases in subjective and objective task load measures with higher \emph{n}-back level.
+Importantly, SVs were lower for higher \emph{n}-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
+The MLM revealed \emph{n}-back level as a reliable predictor of SV, even after controlling for declining task performance (\emph{d'} and median RT).
+NASA-TLX scores were higher with higher \emph{n}, and lower for the group with lower NFC scores, but NFC and \emph{n}-back level did not interact.
 All results are detailed in the Supplementary Material.
@@
 The final adjustment was made during the Stage 2 revision.
-A fellow researcher made us aware that by using the z-transformed hit and false alarm rates for the computation of \(d'\), the mean of \(d'\) would be approximately 0 for each \(n\)-back level by design.
-Consequently, \(d'\) could not show changes across \(n\)-back levels in the manipulation check and would likely yield different results in the MLM.
-Therefore, we computed \(d'\) with unstandardized hit and false alarm rates.
+A fellow researcher made us aware that by using the z-transformed hit and false alarm rates for the computation of \emph{d'}, the mean of \emph{d'} would be approximately 0 for each \emph{n}-back level by design.
+Consequently, \emph{d'} could not show changes across \emph{n}-back levels in the manipulation check and would likely yield different results in the MLM.
+Therefore, we computed \emph{d'} with unstandardized hit and false alarm rates.
 We would like to thank Georgia Clay for pointing us to this fallacy.
@@
 Of the \(N=176\) participants who filled out the NFC questionnaire, \(n=124\) completed the first lab session.
-Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the \(n\)-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
+Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the \emph{n}-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
 Our final data set therefore included \(N=116\) participants (83.60\% female, \(M \pm SD=22.4 \pm 3\))~years old), which is 2.2 times more than what the highest sample size calculation required.
@@
 
-We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across \(n\)-back levels.
+We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across \emph{n}-back levels.
 For each rmANOVA we report the generalized eta squared \(\hat{\eta}^2_G\), which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
-In line with hypothesis H1a, the performance measure \(d'\) decreased across \(n\)-back levels (\(F(2.74, 315.51) = 197.18\), \(p < .001\), \(\hat{\eta}^2_G = .464\), 90\% CI \([.403, .516]\), \(\mathrm{BF}_{\textrm{10}} = 1.56 \times 10^{101}\)).
+In line with hypothesis H1a, the performance measure \emph{d'} decreased across \emph{n}-back levels (\(F(2.74, 315.51) = 197.18\), \(p < .001\), \(\hat{\eta}^2_G = .464\), 90\% CI \([.403, .516]\), \(\mathrm{BF}_{\textrm{10}} = 1.56 \times 10^{101}\)).
 It decreased more strongly from 2- to 3-back (\(t(345) = 10.41\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.71 \times 10^{23}\)) than from 1- to 2-back (\(t(345) = 4.31\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 93,954.04\)) or 3- to 4-back (\(t(345) = 7.18\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 2.45 \times 10^{14}\)).
-Similarly, the median RT increased across \(n\)-back levels (\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)), supporting hypothesis H1b.
+Similarly, the median RT increased across \emph{n}-back levels (\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)), supporting hypothesis H1b.
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
@@
 
-\caption{\label{tab:H1b-contrasts}Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels}
+\caption{\label{tab:H1b-contrasts}Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels}
 
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels.
+\normalsize{\textit{Note.} The column Contrast contains the *n* of the *n*-back levels.
 $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
@@
 
-All NASA-TLX subscale scores increased across \(n\)-back levels, so evidence was in favour of H1c.
+All NASA-TLX subscale scores increased across \emph{n}-back levels, so evidence was in favour of H1c.
 Ratings on the effort subscale (\(F(2.20, 253.06) = 203.82\), \(p < .001\), \(\hat{\eta}^2_G = .316\), 90\% CI \([.250, .375]\), \(\mathrm{BF}_{\textrm{10}} = 2.47 \times 10^{34}\)) increased across all levels, but the magnitude of change decreased from 1- to 2-back (\(t(345) = -12.35\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 4.24 \times 10^{19}\)) to 3- to 4-back (\(t(345) = -2.72\), \(p_\mathrm{\scriptsize Tukey(4)} = .035\), \(\mathrm{BF}_{\textrm{10}} = 174.38\)).
 Three subscales had significant differences between all contrasts except for 3- versus 4-back:
-While ratings on the frustration and time subscales were higher for more difficult levels (\(F(2.50, 287.66) = 68.06\), \(p < .001\), \(\hat{\eta}^2_G = .172\), 90\% CI \([.112, .227]\), \(\mathrm{BF}_{\textrm{10}} = 5.26 \times 10^{15}\), and \(F(2.21, 254.65) = 51.08\), \(p < .001\), \(\hat{\eta}^2_G = .117\), 90\% CI \([.065, .168]\), \(\mathrm{BF}_{\textrm{10}} = 3.94 \times 10^{9}\), respectively), ratings on the performance subscale decreased with higher \(n\) (\(F(2.49, 285.97) = 95.33\), \(p < .001\), \(\hat{\eta}^2_G = .241\), 90\% CI \([.176, .299]\), \(\mathrm{BF}_{\textrm{10}} = 1.55 \times 10^{24}\)).
+While ratings on the frustration and time subscales were higher for more difficult levels (\(F(2.50, 287.66) = 68.06\), \(p < .001\), \(\hat{\eta}^2_G = .172\), 90\% CI \([.112, .227]\), \(\mathrm{BF}_{\textrm{10}} = 5.26 \times 10^{15}\), and \(F(2.21, 254.65) = 51.08\), \(p < .001\), \(\hat{\eta}^2_G = .117\), 90\% CI \([.065, .168]\), \(\mathrm{BF}_{\textrm{10}} = 3.94 \times 10^{9}\), respectively), ratings on the performance subscale decreased with higher \emph{n} (\(F(2.49, 285.97) = 95.33\), \(p < .001\), \(\hat{\eta}^2_G = .241\), 90\% CI \([.176, .299]\), \(\mathrm{BF}_{\textrm{10}} = 1.55 \times 10^{24}\)).
 Ratings on the mental subscale consistently increased across all levels (\(F(1.99, 228.35) = 274.47\), \(p < .001\), \(\hat{\eta}^2_G = .375\), 90\% CI \([.309, .432]\), \(\mathrm{BF}_{\textrm{10}} = 1.64 \times 10^{43}\)).
@@
 
-The different curves of SVs across \(n\)-back levels can be seen in Figure~\ref{fig:sv-by-pref}, grouped into those participants who had an SV of 1.0 for 1-back (\(n=71\)), for 2-back (\(n=18\)), for 3-back (\(n=9\)), for 4-back (\(n=13\)), or all SVs below 1.0, i.e.~no absolute preference for any level (\(n=5\)).
-While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult \(n\)-back levels.
+The different curves of SVs across \emph{n}-back levels can be seen in Figure~\ref{fig:sv-by-pref}, grouped into those participants who had an SV of 1.0 for 1-back (\(n=71\)), for 2-back (\(n=18\)), for 3-back (\(n=9\)), for 4-back (\(n=13\)), or all SVs below 1.0, i.e.~no absolute preference for any level (\(n=5\)).
+While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult \emph{n}-back levels.
 However, each panel in Figure~\ref{fig:sv-by-pref} contains curves of participants who had large differences between their four SVs and curves of participants who had a difference of less than 0.2 between their highest and their lowest SV, so preferring one level does not necessarily mean having a strong aversion against the others, regardless of difficulty level.
@@
 The remaining 27.6\% of participants used the free text field and provided reasons such as ``I wanted a fair relation of effort and reward.'', ``I wanted the fun that I had in the more challenging levels.'', ``I wanted to maximize reward first and minimize effort second.'', or ``I did not want to perform poorly when I was being paid for it.''.
-Figure \ref{fig:motivation} shows the different motivations in the context of the SVs per \(n\)-back level.
+Figure \ref{fig:motivation} shows the different motivations in the context of the SVs per \emph{n}-back level.
 
@@
 
-The rmANOVA showed a significant difference between the SVs across \(n\)-back levels (\(F(1.98, 227.98) = 65.65\), \(p < .001\), \(\hat{\eta}^2_G = .288\), 90\% CI \([.222, .347]\), \(\mathrm{BF}_{\textrm{10}} = 1.58 \times 10^{64}\)), so evidence was in favour of H2a.
+The rmANOVA showed a significant difference between the SVs across \emph{n}-back levels (\(F(1.98, 227.98) = 65.65\), \(p < .001\), \(\hat{\eta}^2_G = .288\), 90\% CI \([.222, .347]\), \(\mathrm{BF}_{\textrm{10}} = 1.58 \times 10^{64}\)), so evidence was in favour of H2a.
 All four pre-defined contrasts reached significance (Table~\ref{tab:H2a-contrasts}), so a purely linear contrast can be rejected.
@@
 
-\caption{\label{tab:H2a-contrasts}Contrasts for the rmANOVA comparing the subjective values between $n$-back levels}
+\caption{\label{tab:H2a-contrasts}Contrasts for the rmANOVA comparing the subjective values between *n*-back levels}
 
@@
 Consequently, we had to adapt the MLM to incorporate this non-linear trend.
-To apply the contrast to the \(n\)-back levels, we had to turn the variables into a factor, with two consequences:
+To apply the contrast to the \emph{n}-back levels, we had to turn the variables into a factor, with two consequences:
 Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
@@
 This means that the intercept still varied between subjects, but there were no random slopes anymore.
-To provide more than one observation per factor level, we used the two rounds per \(n\)-back level per subject, rather than \(n\)-back levels per subject.
+To provide more than one observation per factor level, we used the two rounds per \emph{n}-back level per subject, rather than \emph{n}-back levels per subject.
 The ICC of the null model indicated that there was a correlation of \(r=\) .096 between the SVs of a subject, i.e.~that 9.59\% of variance in SVs could be explained by differences between participants.
@@
 Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
-The final model had an effect size of \(f^{2}=\) 0.21 for the \(n\)-back levels and \(f^{2}=\) 0.05 for \(d'\), which are considered medium and small, respectively\textsuperscript{46}.
-This means that the \(n\)-back level explained 20.67\% and \(d'\) explained 4.90\% of variance in SVs relative to the unexplained variance, respectively.
-The beta coefficient indicated that with every 1-unit increase in \(d'\), the SV increased by 0.21.
-Due to the coding scheme of the logistic contrast, the beta coefficient of the \(n\)-back level has to be interpreted inversely, so SVs decline with increasing \(n\)-back level.
+The final model had an effect size of \(f^{2}=\) 0.21 for the \emph{n}-back levels and \(f^{2}=\) 0.05 for \emph{d'}, which are considered medium and small, respectively\textsuperscript{46}.
+This means that the \emph{n}-back level explained 20.67\% and \emph{d'} explained 4.90\% of variance in SVs relative to the unexplained variance, respectively.
+The beta coefficient indicated that with every 1-unit increase in \emph{d'}, the SV increased by 0.21.
+Due to the coding scheme of the logistic contrast, the beta coefficient of the \emph{n}-back level has to be interpreted inversely, so SVs decline with increasing \emph{n}-back level.
 The effect size of the median RT was \(f^{2}=\) 0.00.
-Since SVs decline with increasing level, beyond the variance explained by \(d'\), evidence was in favour of H2b.
+Since SVs decline with increasing level, beyond the variance explained by \emph{d'}, evidence was in favour of H2b.
 
@@
 
-Regardless of the preprocessing pipeline, \(n\)-back level and \(d'\) were significant predictors of SVs, and had stable effect estimates across all pipelines.
+Regardless of the preprocessing pipeline, \emph{n}-back level and \emph{d'} were significant predictors of SVs, and had stable effect estimates across all pipelines.
 There was no pipeline in which the median RT was a significant predictor of SVs, but it showed volatile effect estimates across pipelines.
-The pipelines that yielded the highest estimates for \(d'\) and the median RT used log-transformed data, irrespective of the dimension and exclusion criteria.
+The pipelines that yielded the highest estimates for \emph{d'} and the median RT used log-transformed data, irrespective of the dimension and exclusion criteria.
 
@@
 We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of the \(n\)-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68 \pm 0.00\%\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56 \pm 0.03\%\)) nor an interaction of NFC group and \(n\)-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
+There was a main effect of the \emph{n}-back level (\(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68 \pm 0.00\%\)), but neither a main effect of the NFC group (\(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56 \pm 0.03\%\)) nor an interaction of NFC group and \emph{n}-back level (\(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)), so evidence was not in favour of H3a.
 Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (\(t(114) = -3.02\), \(p = .003\)), but there were large inter-individual differences (Supplementary Figure S2a).
@@
 
-The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \(n\)-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\)) and an interaction between \(n\)-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\)).
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of \emph{n}-back level (\(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\)) and an interaction between \emph{n}-back level and NFC scores (\(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)), but no main effect of NFC scores (\(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\)).
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (\(t(114) = -2.15\), \(p = .033\), \(\mathrm{BF}_{\textrm{10}} = 11.15\)) and for 4-back (\(t(114) = -2.89\), \(p = .005\), \(\mathrm{BF}_{\textrm{10}} = 336.88\)) than those with NFC scores above the median, so evidence was in favour of H3b.
-Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \(n\)-back levels (Supplementary Figure S3).
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of \emph{n}-back levels (Supplementary Figure S3).
 
 With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of NFC group (\(F(1, 114) = 8.43\), \(p = .004\), \(\hat{\eta}^2_G = .043\), 90\% CI \([.003, .119]\), \(\mathrm{BF}_{\textrm{10}} = 14.26\)) and a main effect of the \(n\)-back level (\(F(1, 114) = 10.21\), \(p = .002\), \(\hat{\eta}^2_G = .034\), 90\% CI \([.000, .105]\), ), but no interaction (\(F(1, 114) = 2.59\), \(p = .110\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .058]\)).
+There was a main effect of NFC group (\(F(1, 114) = 8.43\), \(p = .004\), \(\hat{\eta}^2_G = .043\), 90\% CI \([.003, .119]\), \(\mathrm{BF}_{\textrm{10}} = 14.26\)) and a main effect of the \emph{n}-back level (\(F(1, 114) = 10.21\), \(p = .002\), \(\hat{\eta}^2_G = .034\), 90\% CI \([.000, .105]\), ), but no interaction (\(F(1, 114) = 2.59\), \(p = .110\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .058]\)).
 In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (\(t(114) = 2.90\), \(p = .004\)) (Supplementary Figure S2b).
@@
 
-To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher \(n\)-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
-There was no main effect of NFC group (\(F(1, 114) = 2.63\), \(p = .108\), \(\hat{\eta}^2_G = .007\), 90\% CI \([.000, .053]\), \(2.95 \times 10^{-1}\)), but a main effect of the \(n\)-back level (\(F(2.01, 229.39) = 67.39\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(2.70 \times 10^{30}\)) and an interaction (\(F(2.01, 229.39) = 3.24\), \(p = .041\), \(\hat{\eta}^2_G = .020\), 90\% CI \([.000, .044]\)).
-Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult \(n\)-back level in each paired contrast except for 1- versus 2-back.
+To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher \emph{n}-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
+There was no main effect of NFC group (\(F(1, 114) = 2.63\), \(p = .108\), \(\hat{\eta}^2_G = .007\), 90\% CI \([.000, .053]\), \(2.95 \times 10^{-1}\)), but a main effect of the \emph{n}-back level (\(F(2.01, 229.39) = 67.39\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(2.70 \times 10^{30}\)) and an interaction (\(F(2.01, 229.39) = 3.24\), \(p = .041\), \(\hat{\eta}^2_G = .020\), 90\% CI \([.000, .044]\)).
+Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult \emph{n}-back level in each paired contrast except for 1- versus 2-back.
 Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (\(\Delta M = 0.11\), 95\% CI \([0.01, 0.22]\), \(t(114) = 2.13\), \(p = .036\)).
@@
 The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
-Supplementary Figure S4 shows the SVs per \(n\)-back level for participants with NFC scores above and below the median.
+Supplementary Figure S4 shows the SVs per \emph{n}-back level for participants with NFC scores above and below the median.
 
 Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
-We computed an rmANOVA with the \(n\)-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
-Both the NFC score (\(F(1, 114) = 4.34\), \(p = .039\), \(\hat{\eta}^2_G = .011\), 90\% CI \([.000, .063]\), \(\mathrm{BF}_{\textrm{10}} = 0.57\)) and the \(n\)-back level (\(F(2.02, 229.75) = 67.24\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(\mathrm{BF}_{\textrm{10}} = 2.70 \times 10^{30}\)) showed significant main effects, as well as a significant interaction (\(F(2.02, 229.75) = 3.78\), \(p = .024\), \(\hat{\eta}^2_G = .023\), 90\% CI \([.000, .049]\), \(\mathrm{BF}_{\textrm{10}} = 0.12\)).
-Analyzing the estimated marginal means of the linear trends for each \(n\)-back level indicated a significant difference between the slopes of 1-back and 4-back (\(\Delta M = -0.09\), \(95\%\ \mathrm{CI}_\mathrm{\scriptsize Tukey(4)}\) \([-0.15, -0.02]\), \(t(456) = -3.22\), \(p_\mathrm{\scriptsize Tukey(4)} = .008\)), but not between any other two levels.
+We computed an rmANOVA with the \emph{n}-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
+Both the NFC score (\(F(1, 114) = 4.34\), \(p = .039\), \(\hat{\eta}^2_G = .011\), 90\% CI \([.000, .063]\), \(\mathrm{BF}_{\textrm{10}} = 0.57\)) and the \emph{n}-back level (\(F(2.02, 229.75) = 67.24\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(\mathrm{BF}_{\textrm{10}} = 2.70 \times 10^{30}\)) showed significant main effects, as well as a significant interaction (\(F(2.02, 229.75) = 3.78\), \(p = .024\), \(\hat{\eta}^2_G = .023\), 90\% CI \([.000, .049]\), \(\mathrm{BF}_{\textrm{10}} = 0.12\)).
+Analyzing the estimated marginal means of the linear trends for each \emph{n}-back level indicated a significant difference between the slopes of 1-back and 4-back (\(\Delta M = -0.09\), \(95\%\ \mathrm{CI}_\mathrm{\scriptsize Tukey(4)}\) \([-0.15, -0.02]\), \(t(456) = -3.22\), \(p_\mathrm{\scriptsize Tukey(4)} = .008\)), but not between any other two levels.
 Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure~\ref{fig:nfccont-sv}).
@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.\textsuperscript{7}, which estimates subjective values of different \(n\)-back levels, into the Cognitive and Affective Discounting (CAD) paradigm to estimate SVs of tasks without defaulting to the assumed objective task load as a benchmark.
+This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.\textsuperscript{7}, which estimates subjective values of different \emph{n}-back levels, into the Cognitive and Affective Discounting (CAD) paradigm to estimate SVs of tasks without defaulting to the assumed objective task load as a benchmark.
 For this purpose, we adapted the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
@@
 
-Both \(d'\) and the median RT changed across \(n\)-back levels, indicating that there was an increase in objective task load.
-The steepest decrease in \(d'\) between levels was from 2- to 3-back, resembling the declining logistic curve of the SVs.
+Both \emph{d'} and the median RT changed across \emph{n}-back levels, indicating that there was an increase in objective task load.
+The steepest decrease in \emph{d'} between levels was from 2- to 3-back, resembling the declining logistic curve of the SVs.
 Interestingly, the median RT increased from 2- to 3-back, but did not differ between 2- and 4-back.
 Since feedback was given after each round, this pattern could be interpreted in such a way that participants tried to compensate their lower accuracy in 3-back by relying more on luck than on memory in 4-back and prioritized speed over accuracy.
-Furthermore, several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when \(n\) was an even number than when \(n\) was an odd number.
-This would support the notion that the manipulation of task load in an \(n\)-back task is not strictly continuous.
+Furthermore, several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when \emph{n} was an even number than when \emph{n} was an odd number.
+This would support the notion that the manipulation of task load in an \emph{n}-back task is not strictly continuous.
 And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before\textsuperscript{47} and both show different associations with various measures of intelligence\textsuperscript{4}, suggesting that they should always be reported as separate indices.
 
-All NASA-TLX subscales differed across \(n\)-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
-This would support the notion of the \(n\)-back task offering a continuous manipulation of task load, at least subjectively.
+All NASA-TLX subscales differed across \emph{n}-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
+This would support the notion of the \emph{n}-back task offering a continuous manipulation of task load, at least subjectively.
 Ratings on the frustration and time subscales increased and ratings on the performance subscale decreased until 3-back and then remained stable.
 This pattern is akin to the RT, which also increased and then remained stable.
-Ratings on the physical load subscale increased with \(n\)-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.
+Ratings on the physical load subscale increased with \emph{n}-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.
 
@@
 
-The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across \(n\)-back levels.
+The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across \emph{n}-back levels.
 The best fit was a declining logistic curve, reflecting that 1) the majority of participants preferred the easiest level, 2) 2-back was generally closer in preference to 1-back than 3-back was to 2-back, and 3) objective task load and subjective preference do not stand in a linear relationship.
@@
 Thomson and Oppenheimer\textsuperscript{49} argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
-For example, the \(n\)-back task is likely not a continuous manipulation of task load, as discussed above.
+For example, the \emph{n}-back task is likely not a continuous manipulation of task load, as discussed above.
 However, the declining logistic curve is similar to the sigmoidal curve that has been found for a physical\textsuperscript{50} and a cognitive effort paradigm\textsuperscript{51}, suggesting there are common features of effort across different tasks and domains.
-The MLM with the logistic contrast showed that the \(n\)-back level explained the majority of variance in SVs, while the performance measure \(d'\) also explained some variance in SVs, albeit less.
-With increasing \(n\)-back level and decreasing \(d'\), the SV decreased.
+The MLM with the logistic contrast showed that the \emph{n}-back level explained the majority of variance in SVs, while the performance measure \emph{d'} also explained some variance in SVs, albeit less.
+With increasing \emph{n}-back level and decreasing \emph{d'}, the SV decreased.
 The median RT was not a significant predictor in this model.
-Participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e.~twice per \(n\)-back level, as an anchor during the effort discounting.
+Participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e.~twice per \emph{n}-back level, as an anchor during the effort discounting.
 This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
@@
 
-The declining logistic \(n\)-back levels and \(d'\) remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis.
-The effect estimates of the \(n\)-back level varied by about 0.00, those of \(d'\) by about 0.07.
+The declining logistic \emph{n}-back levels and \emph{d'} remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis.
+The effect estimates of the \emph{n}-back level varied by about 0.002, those of \emph{d'} by about 0.074.
 In contrast to this stood the variability of the median RT effect estimates (around 0.16), which did not reach significance in any pipeline.
@@
 As Fernandez et al.\textsuperscript{52} found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond \(\alpha=.05\), and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
-Our data seems to corroborate this finding for \(n\)-back tasks as well.
-Surprisingly, the \(d'\) betas appeared almost unaffected by the preprocessing pipeline, even though \(d'\) was computed after the outlier exclusion.
+Our data seems to corroborate this finding for \emph{n}-back tasks as well.
+Surprisingly, the \emph{d'} betas appeared almost unaffected by the preprocessing pipeline, even though \emph{d'} was computed after the outlier exclusion.
 This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.
@@
 As the exploratory analyses showed, a median split of NFC scores yielded a significant group difference in SVs for 4-back only, while predicting SVs with NFC as a continuous covariate showed a difference in the slopes of 1-back and 4-back.
-The analysis of NASA-TLX scores showed that the sum score increased with every \(n\)-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
-This demonstrates that higher \(n\)-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
-This was also supported by the fact that higher \(n\)-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
+The analysis of NASA-TLX scores showed that the sum score increased with every \emph{n}-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
+This demonstrates that higher \emph{n}-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
+This was also supported by the fact that higher \emph{n}-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
 Our data supports the notion of a Nonlinear Interaction between Person and Situation that has also been described by Schmitt et al.~(2013)\textsuperscript{54} and Blum et al.~(2018)\textsuperscript{55} in the same-named NIPS model.
@@
 These differences are caused by a person's expression of a certain trait, which shifts the curve along the y-axis.
-In our study, the situational affordance is the \(n\)-back level and the behaviour is the SV, following a declining logistic curve, i.e.~a mirrored s-shape.
+In our study, the situational affordance is the \emph{n}-back level and the behaviour is the SV, following a declining logistic curve, i.e.~a mirrored s-shape.
 Hence, the variability in SVs increased from 1- to 4-back, and participants with higher NFC showed a more shallow decline in SVs as the situational affordance approached moderate values.
@@
 An investigation of this relationship using the COG-ED paradigm\textsuperscript{7} had been encouraged by Strobel et al.\textsuperscript{53} based on their findings on demand avoidance and cognitive effort investment.
-With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model\textsuperscript{54,55} and should be tested further in a setting with \(n\)-back levels exceeding \(n=4\).
+With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model\textsuperscript{54,55} and should be tested further in a setting with \emph{n}-back levels exceeding \(n=4\).
 
@@
 To arrive at a sample with more balanced NFC scores, recruitment efforts should be focused on representative population samples and/or collecting data with an NFC-based stop rule.
-Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher \(n\)-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
+Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher \emph{n}-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
 Future studies could create a stronger separation between the concepts investigated in this study (discounting curve, effort perception, performance, SV computation, NFC), and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
-Another important point is the instruction, not just for the \(n\)-back task, but for the effort discounting as well.
+Another important point is the instruction, not just for the \emph{n}-back task, but for the effort discounting as well.
 We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction and/or a training next time.
@@
 However, effort-related traits such as Need for Cognition suggest that this is not the case.
-Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an \(n\)-back task.
-Despite the fact that the task design allowed individuals to express a preference for higher over lower objective load levels, the overall subjective values took the shape of a declining logistic curve across \(n\)-back levels.
+Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an \emph{n}-back task.
+Despite the fact that the task design allowed individuals to express a preference for higher over lower objective load levels, the overall subjective values took the shape of a declining logistic curve across \emph{n}-back levels.
 The majority of participants showed a decline in subjective values at higher effort levels.
@@
 The CAD paradigm was able to depict the individual preference patterns for both those who do and do not prefer the lowest effort level.
-While the subjective values declined with increasing levels, they increased with better performance as measured in \(d'\), and were unaffected by the reaction time.
+While the subjective values declined with increasing levels, they increased with better performance as measured in \emph{d'}, and were unaffected by the reaction time.
 Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{../../Inkscape Figures/Paradigm_Scheme} \caption{An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+\includegraphics[width=\textwidth]{../../Inkscape Figures/Paradigm_Scheme} \caption{An example for subjective values for an *n*-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/sv_by_pref} \caption{Subjective values (SV) per $n$-back level, grouped into those who had an SV = 1 for 1-back, for 2-back, for 3-back, for 4-back, or no SV = 1 for any level.
+\includegraphics[width=\textwidth]{Figures/sv_by_pref} \caption{Subjective values (SV) per *n*-back level, grouped into those who had an SV = 1 for 1-back, for 2-back, for 3-back, for 4-back, or no SV = 1 for any level.
 The lines have a vertical jitter of 0.02.
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/motivation} \caption{Trajectories of subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
+\includegraphics[width=\textwidth]{Figures/motivation} \caption{Trajectories of subjective values per *n*-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
 $N=116$.
@@
 The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
-The pipelines in both panels are sorted left to right in ascending order of the magnitude of the beta estimate of the predictor $d'$.
+The pipelines in both panels are sorted left to right in ascending order of the magnitude of the beta estimate of the predictor *d'*.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:sca-plot}
@@
 \begin{figure}[H]
-\includegraphics[width=\textwidth]{Figures/nfccont_sv} \caption{Predicted slopes of subjective values depending on individual Need for Cognition scores for each $n$-back level.
+\includegraphics[width=\textwidth]{Figures/nfccont_sv} \caption{Predicted slopes of subjective values depending on individual Need for Cognition scores for each *n*-back level.
 The slopes of 1-back and 4-back are different at $p=.01$.

### 2023-11-15 06_Paper/ER-ED/ERED_Stage2/Analyses_ERED.r
update save path

@@ -1147,6 +1147,9 @@ FigSubjEffort <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort, fill = 
   ylab("Effort rating")+
   theme(legend.position = "none")
 
+ggsave(path = "C:/Users/scheffel/Scheffel/Dis/NewFigures ESER/", width = 7, height = 5, units = "in",
+       device = "tiff", dpi = 500, filename = "Subj_Effort_CAD.eps")
+
 ######## HYPOTHESIS 5
 
 # Which variables can predict individual subjective values of ER strategies?
@@ -1431,7 +1434,8 @@ FigSVChoice <- ggplot2::ggplot(data = data_choice_long, aes(x = strategy, y = sv
                    labels = c("Distraction", "Distancing", "Suppression")) +
   ylab("Subjective values")
 
-
+ggsave(path = "C:/Users/scheffel/Scheffel/Dis/NewFigures ESER/", width = 7, height = 5, units = "in",
+       device = "tiff", dpi = 500, filename = "SV_Choice_CAD.eps")
 # ORDINAL REGRESSION
 
 # https://marissabarlaz.github.io/portfolio/ols/

### 2023-11-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

@@
 ---
-title             : "When easy is not preferred: A discounting paradigm to assess load-independent task preference"
+title             : "Need for cognition is associated with a preference for higher task load in effort discounting"
 shorttitle        : "The CAD paradigm to assess task preference"
@@
   Results show that many of the 116 participants preferred a more or the most difficult level.
-  Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
-  Participants with higher Need for Cognition scores perceived higher $n$-back levels as less effortful and found them less aversive.
+  Variance in SVs was best explained by a declining logistic contrast of the *n*-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
+  Participants with higher Need for Cognition scores perceived higher *n*-back levels as less effortful and found them less aversive.
   Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences only emerged in higher levels.
@@
 
-keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, $n$-back"
+keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, *n*-back"
 wordcount         : "~ 7000"
@@
 
-One task that is often used to investigate effort is the $n$-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
-Participants indicate via button press whether the current stimulus is the same as $n$ stimuli before, with $n$ being the level of difficulty between one and six[@Mackworth1959].
-The $n$-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times[@Jaeggi2010], and brain activity in areas associated with working memory[@Jonides1997; @Owen2005].
-However, its reliability measures are mixed, and associations of $n$-back performance and measures such as executive functioning and fluid intelligence are often inconsistent[@Jaeggi2010].
+One task that is often used to investigate effort is the *n*-back task, a working memory task in which a continuous stream of stimuli, e.g. letters, is presented on screen.
+Participants indicate via button press whether the current stimulus is the same as *n* stimuli before, with *n* being the level of difficulty between one and six[@Mackworth1959].
+The *n*-back task is well suited to investigate effort because it is an almost continuous manipulation of task load as has been shown by monotonic increases in error rates, reaction times[@Jaeggi2010], and brain activity in areas associated with working memory[@Jonides1997; @Owen2005].
+However, its reliability measures are mixed, and associations of *n*-back performance and measures such as executive functioning and fluid intelligence are often inconsistent[@Jaeggi2010].
 
-A way to quantify the subjective cost of each $n$-back level has been developed by Westbrook, Kester, and Braver[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
-First, the participants complete the $n$-back levels to familiarize themselves with the task.
+A way to quantify the subjective cost of each *n*-back level has been developed by Westbrook, Kester, and Braver[-@Westbrook2013], called the Cognitive Effort Discounting Paradigm (COG-ED).
+First, the participants complete the *n*-back levels to familiarize themselves with the task.
 Then, 1-back is compared with each more difficult level by asking the participants to decide between receiving a fixed 2\$ for the more difficult level or the flexible starting value of 1\$ for 1-back.
@@
 
-With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest $n$-back level has the highest SV.
-We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different $n$-back levels without presuming that all individuals inherently prefer the easiest level.
+With the present study, we alter one fundamental assumption of the original COG-ED paradigm: That the easiest *n*-back level has the highest SV.
+We therefore adapted the COG-ED paradigm in a way that allows the computation of SVs for different *n*-back levels without presuming that all individuals inherently prefer the easiest level.
 Since we also aim to establish this paradigm for the assessment of tasks with no objective task load, e.g., emotion regulation tasks[@ScheffelZerna2022], we call it the Cognitive and Affective Discounting Paradigm (CAD).
 In the present study, we validated the CAD paradigm by conceptually replicating the findings of Westbrook et al.[-@Westbrook2013].
-Additionally, we compared the effort discounting behavior of participants regarding the $n$-back task and an emotion regulation task.
+Additionally, we compared the effort discounting behavior of participants regarding the *n*-back task and an emotion regulation task.
 The full results of the latter are published in a second Registered Report[@ScheffelZerna2022].
@@
 Our hypotheses were derived from the results of Westbrook et al.[-@Westbrook2013].
-As a manipulation check, we hypothesized that with increasing $n$-back level the (1a) the signal detection parameter $d'$ declines, while (1b) reaction time and (1c) perceived task load increase.
-Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing $n$-back level, and (2b) they do so even after controlling for declining task performance.
+As a manipulation check, we hypothesized that with increasing *n*-back level the (1a) the signal detection parameter *d'* declines, while (1b) reaction time and (1c) perceived task load increase.
+Regarding the associations of task load and effort discounting we hypothesized that (2a) SVs decline with increasing *n*-back level, and (2b) they do so even after controlling for declining task performance.
 And finally, we hypothesized that the CAD paradigm can show inter-individual differences in effort discounting, such that participants with higher NFC have (3a) lower SVs for 1-back but higher SVs for 2- and 3-back, (3b) lower perceived task load across all levels, and (3c) higher aversion against 1-back but lower aversion against 2- and 3-back.
@@
 In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
-The paradigm started with the $n$-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
+The paradigm started with the *n*-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
 The levels were referred to by color (1-back: black, 2-back: red, 3-back: blue, 4-back: green) to avoid anchor effects in the effort discounting procedure.
 To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX)[@Hart1988], where participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
-At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this $n$-back level.
-After the $n$-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
-They were told that one of their choices would be randomly picked for the final run of $n$-back.
+At the end of each level, participants filled out the NASA-TLX on a tablet, plus an item with the same response scale, asking them how aversive they found this *n*-back level.
+After the *n*-back task, participants completed the CAD paradigm on screen and were instructed to do so as realistically as possible, even though the displayed rewards were not paid out on top of their compensation.
+They were told that one of their choices would be randomly picked for the final run of *n*-back.
 However, this data was not analyzed as it only served to incentivise truthful behavior and to stay close to the design of Westbrook et al.[-@Westbrook2013].
@@
 Sample size determination was mainly based on the results of the analyses of Westbrook et al.[-@Westbrook2013] (see Design Table in the Supplementary Material).
-The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and $n$-back level influencing SVs.
+The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and *n*-back level influencing SVs.
 Sample size analysis with *G\*Power*[@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
@@
 No data was replaced.
-The performance measure $d'$ was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
+The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
 Reaction time (RT) data was trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
-Aggregated RT values were described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
+Aggregated RT values were described using the median and the median of absolute deviation (*MAD*) as robust estimates of center and variability, respectively[@Lachaud2011].
 Error- and post-error trials were excluded, because RT in the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
@@
 *Manipulation check.*
-Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing $d'$ between two levels of 1- to 4-back at a time.
+Declining performance was investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
 Another rmANOVA with six paired contrasts was computed to compare the median RT between two levels of 1- to 4-back at a time.
@@
 All SVs of each level were averaged to compute one "global" SV for each level.
-An rmANOVA with four different contrasts were computed to investigate the association of SVs and the $n$-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2) (Supplementary Figure S1).
+An rmANOVA with four different contrasts were computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2) (Supplementary Figure S1).
 Depending on whether the linear or one of the other three contrasts fit the curve best, we applied a linear or nonlinear multi-level model in the next step, respectively.
 
-To determine the influence of task performance on the association of SVs and $n$-back level, we performed MLM. 
+To determine the influence of task performance on the association of SVs and *n*-back level, we performed MLM. 
 We applied restricted maximum likelihood (REML) to fit the model.
 As an effect size measure for random effects we first calculated the intraclass correlation (ICC), which displays the proportion of variance that is explained by differences between persons.
-Second, we estimated a random slopes model of $n$-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
-As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher $n$-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
-We controlled for performance, i.e., $d'$ (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
+Second, we estimated a random slopes model of *n*-back level (level 1, fixed, and random factor: 0-back, 1-back, 2-back, 3-back) predicting SV nested within subjects.
+As Mussel et al.[-@Mussel2016] could show, participants with high versus low NFC not only have a more shallow decline in performance with higher *n*-back levels, but show a demand-specific increase in EEG theta oscillations, which has been associated with mental effort.
+We controlled for performance, i.e., *d'* (level 1, fixed factor, continuous), median RT (level 1, fixed factor, continuous) in order to eliminate a possible influence of declining performance on SV ratings.
 $$
@@
 This was done by excluding all data points with absolute standardized residuals above 3 SD. 
-As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of $n$-back level according to Lorah[-@Lorah2018].
+As effect size measures, we calculated pseudo $R^{2}$ for our model and $f^{2}$ to estimate the effect of *n*-back level according to Lorah[-@Lorah2018].
 
@@
 The sample was divided into participants with low and high NFC using a median split.
-We then computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
+We then computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group to determine whether there is a main effect of level and/or group, and/or an interaction between level and group on the SV difference scores.
 Post-hoc tests were computed depending on which effect reached significance at $p<.01$.
 To ensure the validity of this association, we conducted a specification curve analysis[@Simonsohn2020], which included 63 possible preprocessing pipelines of the RT data.
-These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ $MAD$ from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within $n$-back levels).
+These pipelines specify which transformation was applied (none, log, inverse, or square-root), which outliers were excluded (none, 2, 2.5, or 3\ *MAD* from the median, RTs below 100\ or\ 200\ ms), and across which dimensions the transformations and exclusions were applied (across/within subjects and across/within *n*-back levels).
 The rmANOVA was run with each of the 63\ pipelines, which also included our main pipeline (untransformed data, exclusion of RTs below 100\ ms).
@@
 The association of subjective task load with NFC was examined similarly.
-We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
+We calculated NASA-TLX sum scores per participant per level, computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
 And the association of subjective aversiveness of the task with NFC was examined with difference scores as well, since we expected this curve to mirror the SV curve, i.e.
@@
 We subtracted the aversiveness ratings of 1- from 2-back and 2- from 3-back, yielding two aversiveness difference scores per participant.
-Then, we computed an rmANOVA with the within-factor $n$-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
+Then, we computed an rmANOVA with the within-factor *n*-back level and the between-factor NFC group, and applied post-hoc tests based on which effect reached significance at $p<.01$.
 
@@
 Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA-TLX were analyzed with $n=14$ data sets.
-The results showed increases in subjective and objective task load measures with higher $n$-back level.
-Importantly, SVs were lower for higher $n$-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
-The MLM revealed $n$-back level as a reliable predictor of SV, even after controlling for declining task performance ($d'$ and median RT).
-NASA-TLX scores were higher with higher $n$, and lower for the group with lower NFC scores, but NFC and $n$-back level did not interact.
+The results showed increases in subjective and objective task load measures with higher *n*-back level.
+Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
+The MLM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d'* and median RT).
+NASA-TLX scores were higher with higher *n*, and lower for the group with lower NFC scores, but NFC and *n*-back level did not interact.
 All results are detailed in the Supplementary Material.
@@
 The final adjustment was made during the Stage 2 revision.
-A fellow researcher made us aware that by using the z-transformed hit and false alarm rates for the computation of $d'$, the mean of $d'$ would be approximately 0 for each $n$-back level by design.
-Consequently, $d'$ could not show changes across $n$-back levels in the manipulation check and would likely yield different results in the MLM.
-Therefore, we computed $d'$ with unstandardized hit and false alarm rates.
+A fellow researcher made us aware that by using the z-transformed hit and false alarm rates for the computation of *d'*, the mean of *d'* would be approximately 0 for each *n*-back level by design.
+Consequently, *d'* could not show changes across *n*-back levels in the manipulation check and would likely yield different results in the MLM.
+Therefore, we computed *d'* with unstandardized hit and false alarm rates.
 We would like to thank Georgia Clay for pointing us to this fallacy.
@@
 Of the $N=`r n_quest`$ participants who filled out the NFC questionnaire, $n=`r length(datalist_nback)`$ completed the first lab session.
-Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the $n$-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
+Based on the experimenters' notes, we excluded the data of seven participants from analysis for misunderstanding the instruction of the *n*-back task, and the data of one participant who reported that they confused the colours of the levels during effort discounting.
 Our final data set therefore included $N=`r nrow(data_quest)`$ participants (`r round((table(data_quest$gender)[2]/nrow(data_quest))*100, digits = 1)`% female, $M \pm SD=`r format(round(mean(data_quest[,"age"]), digits = 1), nsmall = 1)` \pm `r round(sd(data_quest[,"age"]), digits = 1)`$)\ years old), which is `r format(round(nrow(data_quest)/53, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
@@
 
-We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across $n$-back levels.
+We used rmANOVAs to investigate whether objective performance measures and subjective task load measures changed across *n*-back levels.
 For each rmANOVA we report the generalized eta squared $\hat{\eta}^2_G$, which estimates the effect size in analyses that contain both manipulated and non-manipulated terms.
-In line with hypothesis H1a, the performance measure $d'$ decreased across $n$-back levels (`r apa_print(hypothesis1a_rmanova)$full_result`, `r apa_print(hypothesis1a_BF)$statistic`).
+In line with hypothesis H1a, the performance measure *d'* decreased across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result`, `r apa_print(hypothesis1a_BF)$statistic`).
 It decreased more strongly from 2- to 3-back (`r apa_print(pairs(hypothesis1a_emm))$statistic$X2_X3`, `r apa_print(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 2], y = h1a_data$dprime[h1a_data$level == 3], progress = FALSE, paired = TRUE))$statistic`) than from 1- to 2-back (`r apa_print(pairs(hypothesis1a_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 1], y = h1a_data$dprime[h1a_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) or 3- to 4-back (`r apa_print(pairs(hypothesis1a_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1a_data$dprime[h1a_data$level == 3], y = h1a_data$dprime[h1a_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
-Similarly, the median RT increased across $n$-back levels (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`), supporting hypothesis H1b.
+Similarly, the median RT increased across *n*-back levels (`r apa_print(hypothesis1b_rmanova)$full_result$level`, `r apa_print(hypothesis1b_BF)$statistic`), supporting hypothesis H1b.
 Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
@@
   hypothesis1b_contrasts,
-  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels",
-  note = "The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
+  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels",
+  note = "The column Contrast contains the *n* of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
   escape = FALSE,
@@
 
-All NASA-TLX subscale scores increased across $n$-back levels, so evidence was in favour of H1c.
+All NASA-TLX subscale scores increased across *n*-back levels, so evidence was in favour of H1c.
 Ratings on the effort subscale (`r apa_print(hypothesis1c_effort_rmanova)$full_result$level`, `r apa_print(hypothesis1c_effort_BF)$statistic`) increased across all levels, but the magnitude of change decreased from 1- to 2-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X1_X2`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 1], y = h1c_data$effort[h1c_data$level == 2], progress = FALSE, paired = TRUE))$statistic`) to 3- to 4-back (`r apa_print(pairs(hypothesis1c_effort_emm))$statistic$X3_X4`, `r apa_print(BayesFactor::ttestBF(x = h1c_data$effort[h1c_data$level == 3], y = h1c_data$effort[h1c_data$level == 4], progress = FALSE, paired = TRUE))$statistic`).
 Three subscales had significant differences between all contrasts except for 3- versus 4-back:
-While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher $n$ (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
+While ratings on the frustration and time subscales were higher for more difficult levels (`r apa_print(hypothesis1c_frustration_rmanova)$full_result$level`, `r apa_print(hypothesis1c_frustration_BF)$statistic`, and `r apa_print(hypothesis1c_time_rmanova)$full_result$level`, `r apa_print(hypothesis1c_time_BF)$statistic`, respectively), ratings on the performance subscale decreased with higher *n* (`r apa_print(hypothesis1c_performance_rmanova)$full_result$level`, `r apa_print(hypothesis1c_performance_BF)$statistic`).
 Ratings on the mental subscale consistently increased across all levels (`r apa_print(hypothesis1c_mental_rmanova)$full_result$level`, `r apa_print(hypothesis1c_mental_BF)$statistic`).
@@
 
-The different curves of SVs across $n$-back levels can be seen in Figure\ \@ref(fig:sv-by-pref), grouped into those participants who had an SV of 1.0 for 1-back ($n=`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])`$), for 2-back ($n=`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])`$), for 3-back ($n=`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])`$), for 4-back ($n=`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])`$), or all SVs below 1.0, i.e.
+The different curves of SVs across *n*-back levels can be seen in Figure\ \@ref(fig:sv-by-pref), grouped into those participants who had an SV of 1.0 for 1-back ($n=`r nrow(data_SV[data_SV$level==1 & data_SV$sv==1,])`$), for 2-back ($n=`r nrow(data_SV[data_SV$level==2 & data_SV$sv==1,])`$), for 3-back ($n=`r nrow(data_SV[data_SV$level==3 & data_SV$sv==1,])`$), for 4-back ($n=`r nrow(data_SV[data_SV$level==4 & data_SV$sv==1,])`$), or all SVs below 1.0, i.e.
 no absolute preference for any level ($n=`r length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1]))`$).
-While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult $n$-back levels.
+While the majority of participants preferred the easiest level and showed an approximately linear decline of SVs with increasing task-load, a substantial part of the sample had higher SVs for one of the more difficult *n*-back levels.
 However, each panel in Figure\ \@ref(fig:sv-by-pref) contains curves of participants who had large differences between their four SVs and curves of participants who had a difference of less than 0.2 between their highest and their lowest SV, so preferring one level does not necessarily mean having a strong aversion against the others, regardless of difficulty level.
@@
 The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
-Figure \@ref(fig:motivation) shows the different motivations in the context of the SVs per $n$-back level.
+Figure \@ref(fig:motivation) shows the different motivations in the context of the SVs per *n*-back level.
 
@@
 
-The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`), so evidence was in favour of H2a.
+The rmANOVA showed a significant difference between the SVs across *n*-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`), so evidence was in favour of H2a.
 All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.
@@
   hypothesis2a_contrasts,
-  caption = "Contrasts for the rmANOVA comparing the subjective values between $n$-back levels",
+  caption = "Contrasts for the rmANOVA comparing the subjective values between *n*-back levels",
   note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
@@
 Consequently, we had to adapt the MLM to incorporate this non-linear trend.
-To apply the contrast to the $n$-back levels, we had to turn the variables into a factor, with two consequences:
+To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
 Centered variables cannot be turned into factors, so we entered the variable level in its raw form, and factors cannot be used as random slopes, so the model is now defined as:
@@
 This means that the intercept still varied between subjects, but there were no random slopes anymore.
-To provide more than one observation per factor level, we used the two rounds per $n$-back level per subject, rather than $n$-back levels per subject.
+To provide more than one observation per factor level, we used the two rounds per *n*-back level per subject, rather than *n*-back levels per subject.
 The ICC of the null model indicated that there was a correlation of $r=$ `r sub("^(-?)0.", "\\1.", sprintf("%.3f", round(model0_h2b_ICC, digits = 3)))` between the SVs of a subject, i.e.
@@
 Both AIC and BIC subtract the likelihood of the model from the number of parameters and/or data points, so lower values indicate better model fit.
-The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the $n$-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for $d'$, which are considered medium and small, respectively [@Cohen1992].
-This means that the $n$-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and $d'$ explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
-The beta coefficient indicated that with every 1-unit increase in $d'$, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
-Due to the coding scheme of the logistic contrast, the beta coefficient of the $n$-back level has to be interpreted inversely, so SVs decline with increasing $n$-back level.
+The final model had an effect size of $f^{2}=$ `r round(h2b_level_f2, digits = 2)` for the *n*-back levels and $f^{2}=$ `r round(h2b_dprime_f2, digits = 2)` for *d'*, which are considered medium and small, respectively [@Cohen1992].
+This means that the *n*-back level explained `r paste0(formatC(h2b_level_f2 * 100, format = "f", digits = 2), "%")` and *d'* explained `r paste0(formatC(h2b_dprime_f2 * 100, format = "f", digits = 2), "%")` of variance in SVs relative to the unexplained variance, respectively.
+The beta coefficient indicated that with every 1-unit increase in *d'*, the SV increased by `r as.numeric(h2b_result.table[3,"Beta"])`.
+Due to the coding scheme of the logistic contrast, the beta coefficient of the *n*-back level has to be interpreted inversely, so SVs decline with increasing *n*-back level.
 The effect size of the median RT was $f^{2}=$ `r format(round(h2b_medianRT_f2, digits = 2), nsmall = 2)`.
-Since SVs decline with increasing level, beyond the variance explained by $d'$, evidence was in favour of H2b.
+Since SVs decline with increasing level, beyond the variance explained by *d'*, evidence was in favour of H2b.
 
@@
 
-Regardless of the preprocessing pipeline, $n$-back level and $d'$ were significant predictors of SVs, and had stable effect estimates across all pipelines.
+Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
 There was no pipeline in which the median RT was a significant predictor of SVs, but it showed volatile effect estimates across pipelines.
-The pipelines that yielded the highest estimates for $d'$ and the median RT used log-transformed data, irrespective of the dimension and exclusion criteria.
+The pipelines that yielded the highest estimates for *d'* and the median RT used log-transformed data, irrespective of the dimension and exclusion criteria.
 
@@
 We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
+There was a main effect of the *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and *n*-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
 Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences (Supplementary Figure S2a).
@@
 
-The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of $n$-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between $n$-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
+The rmANOVA on the association between NFC scores and NASA-TLX scores revealed a main effect of *n*-back level (`r apa_print(hypothesis3b_model)$full_result$level`, `r apa_print(hypothesis3b_BF_levels)$statistic$level`) and an interaction between *n*-back level and NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian_level`), but no main effect of NFC scores (`r apa_print(hypothesis3b_model)$full_result$nfcmedian`, `r apa_print(hypothesis3b_BF_levels)$statistic$nfcmedian`).
 Post-hoc tests showed that the participants with NFC scores below the median had higher NASA-TLX scores for 3-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X3_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 3], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 3], progress = FALSE, paired = FALSE))$statistic`) and for 4-back (`r apa_print(pairs(hypothesis3b_emm_interact))$statistic$X4_High_low`, `r apa_print(BayesFactor::ttestBF(x = h3b_data$ntlx[h3b_data$nfcmedian == "low" & h3b_data$level == 4], y = h3b_data$ntlx[h3b_data$nfcmedian == "high" & h3b_data$level == 4], progress = FALSE, paired = FALSE))$statistic`) than those with NFC scores above the median, so evidence was in favour of H3b.
-Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of $n$-back levels (Supplementary Figure S3).
+Regardless of NFC scores, NASA-TLX scores were higher for the more difficult level in each pair of *n*-back levels (Supplementary Figure S3).
 
 With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
-There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
+There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the *n*-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
 In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (Supplementary Figure S2b).
@@
 
-To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher $n$-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
-There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the $n$-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
-Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult $n$-back level in each paired contrast except for 1- versus 2-back.
+To investigate the apparent group difference between the SVs of participants with NFC scores below and above the median in higher *n*-back levels, we computed an rmANOVA with the within-factor level (1 to 4) and the between-factor NFC group (below/above median).
+There was no main effect of NFC group (`r apa_print(explor_model)$full_result$nfcmedian`, `r apa_print(explor_BF)$table[2,"statistic"]`), but a main effect of the *n*-back level (`r apa_print(explor_model)$full_result$level`, `r apa_print(explor_BF)$table[1,"statistic"]`) and an interaction (`r apa_print(explor_model)$full_result$nfcmedian_level`).
+Post-hoc tests for the main effect of level showed that SVs were lower for the more difficult *n*-back level in each paired contrast except for 1- versus 2-back.
 Post-hoc tests for the interaction effect showed that the NFC groups only had a significant difference in SVs for 4-back, where participants below the NFC median had lower scores (`r apa_print(pairs(explor_emm_interact))$full_result$X4_High_low`).
@@
 The full results of this exploratory analysis of NFC group differences can be found in Table S.16 and S.17 in the Supplementary Material.
-Supplementary Figure S4 shows the SVs per $n$-back level for participants with NFC scores above and below the median.
+Supplementary Figure S4 shows the SVs per *n*-back level for participants with NFC scores above and below the median.
 
 Following a reviewer's recommendation, we also analyzed the association of SVs with NFC as a continuous variable.
-We computed an rmANOVA with the $n$-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
-Both the NFC score (`r apa_print(explor2_model)$full_result$nfc`, `r apa_print(explor2_BF_nfc)$statistic`) and the $n$-back level (`r apa_print(explor2_model)$full_result$level`, `r apa_print(explor2_BF_level)$statistic`) showed significant main effects, as well as a significant interaction (`r apa_print(explor2_model)$full_result$nfc_level`, `r apa_print(explor2_BF_interact)$statistic`).
-Analyzing the estimated marginal means of the linear trends for each $n$-back level indicated a significant difference between the slopes of 1-back and 4-back (`r apa_print(explor2_slopes$contrasts)$full_result$Level1_level4`), but not between any other two levels.
+We computed an rmANOVA with the *n*-back level as a within variable and the standardized NFC score as a covariate to predict SVs.
+Both the NFC score (`r apa_print(explor2_model)$full_result$nfc`, `r apa_print(explor2_BF_nfc)$statistic`) and the *n*-back level (`r apa_print(explor2_model)$full_result$level`, `r apa_print(explor2_BF_level)$statistic`) showed significant main effects, as well as a significant interaction (`r apa_print(explor2_model)$full_result$nfc_level`, `r apa_print(explor2_BF_interact)$statistic`).
+Analyzing the estimated marginal means of the linear trends for each *n*-back level indicated a significant difference between the slopes of 1-back and 4-back (`r apa_print(explor2_slopes$contrasts)$full_result$Level1_level4`), but not between any other two levels.
 Plotting the predicted slopes shows that there is a negative association between the predicted SVs and the NFC scores for 1-back, but a positive association between the predicted SVs and the NFC scores for 4-back (Figure\ \@ref(fig:nfccont-sv)).
@@
 
-This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which estimates subjective values of different $n$-back levels, into the Cognitive and Affective Discounting (CAD) paradigm to estimate SVs of tasks without defaulting to the assumed objective task load as a benchmark.
+This Registered Report aimed to adapt the Cognitive Effort Discounting (COG-ED) paradigm by Westbrook et al.[-@Westbrook2013], which estimates subjective values of different *n*-back levels, into the Cognitive and Affective Discounting (CAD) paradigm to estimate SVs of tasks without defaulting to the assumed objective task load as a benchmark.
 For this purpose, we adapted the way in which the discounting options are presented to the participants, based the anchor on their own choices, and computed SVs across multiple combinations of task levels.
@@
 
-Both $d'$ and the median RT changed across $n$-back levels, indicating that there was an increase in objective task load.
-The steepest decrease in $d'$ between levels was from 2- to 3-back, resembling the declining logistic curve of the SVs.
+Both *d'* and the median RT changed across *n*-back levels, indicating that there was an increase in objective task load.
+The steepest decrease in *d'* between levels was from 2- to 3-back, resembling the declining logistic curve of the SVs.
 Interestingly, the median RT increased from 2- to 3-back, but did not differ between 2- and 4-back.
 Since feedback was given after each round, this pattern could be interpreted in such a way that participants tried to compensate their lower accuracy in 3-back by relying more on luck than on memory in 4-back and prioritized speed over accuracy.
-Furthermore, several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when $n$ was an even number than when $n$ was an odd number.
-This would support the notion that the manipulation of task load in an $n$-back task is not strictly continuous.
+Furthermore, several participants said that they perceived 3-back as more difficult than 4-back because they found it is easier to remember chunks of stimuli when *n* was an even number than when *n* was an odd number.
+This would support the notion that the manipulation of task load in an *n*-back task is not strictly continuous.
 And lastly, the fact that neither accuracy nor speed is an informative performance measure by itself has been observed before[@Meule2017] and both show different associations with various measures of intelligence[@Jaeggi2010], suggesting that they should always be reported as separate indices.
 
-All NASA-TLX subscales differed across $n$-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
-This would support the notion of the $n$-back task offering a continuous manipulation of task load, at least subjectively.
+All NASA-TLX subscales differed across *n*-back levels, but the effort and mental load subscales were the only ones to consistently increase across all levels.
+This would support the notion of the *n*-back task offering a continuous manipulation of task load, at least subjectively.
 Ratings on the frustration and time subscales increased and ratings on the performance subscale decreased until 3-back and then remained stable.
 This pattern is akin to the RT, which also increased and then remained stable.
-Ratings on the physical load subscale increased with $n$-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.
+Ratings on the physical load subscale increased with *n*-back levels, but not between 2- and 3-back and 3- and 4-back, respectively.
 
@@
 
-The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across $n$-back levels.
+The rmANOVA with different pre-defined contrasts showed that all fit the SVs to a different degree, and that the SVs do not simply decline linearly across *n*-back levels.
 The best fit was a declining logistic curve, reflecting that 1) the majority of participants preferred the easiest level, 2) 2-back was generally closer in preference to 1-back than 3-back was to 2-back, and 3) objective task load and subjective preference do not stand in a linear relationship.
@@
 Thomson and Oppenheimer[-@Thomson2022] argue that the different effort curves that have been observed for different tasks are likely due to the fact that we still understand quite little about how and why different manipulations of effort work.
-For example, the $n$-back task is likely not a continuous manipulation of task load, as discussed above.
+For example, the *n*-back task is likely not a continuous manipulation of task load, as discussed above.
 However, the declining logistic curve is similar to the sigmoidal curve that has been found for a physical[@KleinFluegge2015] and a cognitive effort paradigm[@Massar2019], suggesting there are common features of effort across different tasks and domains.
-The MLM with the logistic contrast showed that the $n$-back level explained the majority of variance in SVs, while the performance measure $d'$ also explained some variance in SVs, albeit less.
-With increasing $n$-back level and decreasing $d'$, the SV decreased.
+The MLM with the logistic contrast showed that the *n*-back level explained the majority of variance in SVs, while the performance measure *d'* also explained some variance in SVs, albeit less.
+With increasing *n*-back level and decreasing *d'*, the SV decreased.
 The median RT was not a significant predictor in this model.
-Participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per $n$-back level, as an anchor during the effort discounting.
+Participants might have deliberately or subconsciously used the feedback they received at the end of each round, i.e. twice per *n*-back level, as an anchor during the effort discounting.
 This feedback was based on correct responses and not on RT, so if participants based their effort discounting choices at least partly on this feedback, they were either motivated to repeat a task in which they performed well and/or they were reluctant to accept a larger reward for a task in which they did not perform well.
@@
 
-The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis.
-The effect estimates of the $n$-back level varied by about `r format(round(diff(range(sca_results$beta_n)), digits = 3), digits = 3)`, those of $d'$ by about `r format(round(diff(range(sca_results$beta_d)), digits = 3), digits = 3)`.
+The declining logistic *n*-back levels and *d'* remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis.
+The effect estimates of the *n*-back level varied by about `r format(round(diff(range(sca_results$beta_n)), digits = 3), digits = 3)`, those of *d'* by about `r format(round(diff(range(sca_results$beta_d)), digits = 3), digits = 3)`.
 In contrast to this stood the variability of the median RT effect estimates (around `r round(diff(range(sca_results$beta_r)), digits = 3)`), which did not reach significance in any pipeline.
@@
 As Fernandez et al.[-@Fernandez2020] found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond $\alpha=.05$, and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
-Our data seems to corroborate this finding for $n$-back tasks as well.
-Surprisingly, the $d'$ betas appeared almost unaffected by the preprocessing pipeline, even though $d'$ was computed after the outlier exclusion.
+Our data seems to corroborate this finding for *n*-back tasks as well.
+Surprisingly, the *d'* betas appeared almost unaffected by the preprocessing pipeline, even though *d'* was computed after the outlier exclusion.
 This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.
@@
 As the exploratory analyses showed, a median split of NFC scores yielded a significant group difference in SVs for 4-back only, while predicting SVs with NFC as a continuous covariate showed a difference in the slopes of 1-back and 4-back.
-The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
-This demonstrates that higher $n$-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
-This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
+The analysis of NASA-TLX scores showed that the sum score increased with every *n*-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
+This demonstrates that higher *n*-back levels have a higher discriminatory power regarding inter-individual differences in subjective effort perception.
+This was also supported by the fact that higher *n*-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
 Our data supports the notion of a Nonlinear Interaction between Person and Situation that has also been described by Schmitt et al.
@@
 These differences are caused by a person's expression of a certain trait, which shifts the curve along the y-axis.
-In our study, the situational affordance is the $n$-back level and the behaviour is the SV, following a declining logistic curve, i.e. a mirrored s-shape.
+In our study, the situational affordance is the *n*-back level and the behaviour is the SV, following a declining logistic curve, i.e. a mirrored s-shape.
 Hence, the variability in SVs increased from 1- to 4-back, and participants with higher NFC showed a more shallow decline in SVs as the situational affordance approached moderate values.
@@
 An investigation of this relationship using the COG-ED paradigm[-@Westbrook2013] had been encouraged by Strobel et al.[@Strobel2020] based on their findings on demand avoidance and cognitive effort investment.
-With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model[@Schmitt2013;@Blum2018] and should be tested further in a setting with $n$-back levels exceeding $n=4$.
+With the CAD paradigm, the declining logistic contrast of SVs across levels resembles the ascending logistic curve of the NIPS model[@Schmitt2013;@Blum2018] and should be tested further in a setting with *n*-back levels exceeding $n=4$.
 
@@
 To arrive at a sample with more balanced NFC scores, recruitment efforts should be focused on representative population samples and/or collecting data with an NFC-based stop rule.
-Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher $n$-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
+Additionally, we expected the SVs of participants with lower NFC scores to peak at 1-back and the SVs of those with higher scores to peak at 2-back, but the way the SVs of both groups appeared to drift apart in the higher *n*-back levels suggests that an analysis of those levels would be more fruitful in determining group differences.
 Future studies could create a stronger separation between the concepts investigated in this study (discounting curve, effort perception, performance, SV computation, NFC), and model the SVs and their task-related influencing factors first, before looking at (non-linear) associations with personality.
-Another important point is the instruction, not just for the $n$-back task, but for the effort discounting as well.
+Another important point is the instruction, not just for the *n*-back task, but for the effort discounting as well.
 We had to exclude several participants for misunderstanding the task instruction, so we will add a visual instruction and/or a training next time.
@@
 However, effort-related traits such as Need for Cognition suggest that this is not the case.
-Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an $n$-back task.
-Despite the fact that the task design allowed individuals to express a preference for higher over lower objective load levels, the overall subjective values took the shape of a declining logistic curve across $n$-back levels.
+Therefore, we developed a paradigm that allows to examine effort discounting independent of objective task load, which we tested using an *n*-back task.
+Despite the fact that the task design allowed individuals to express a preference for higher over lower objective load levels, the overall subjective values took the shape of a declining logistic curve across *n*-back levels.
 The majority of participants showed a decline in subjective values at higher effort levels.
@@
 The CAD paradigm was able to depict the individual preference patterns for both those who do and do not prefer the lowest effort level.
-While the subjective values declined with increasing levels, they increased with better performance as measured in $d'$, and were unaffected by the reaction time.
+While the subjective values declined with increasing levels, they increased with better performance as measured in *d'*, and were unaffected by the reaction time.
 Participants with Need for Cognition scores above the median reported lower subjective task load in and less aversion to more difficult levels.
@@
 
-```{r cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an $n$-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
+```{r cadparadigm, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="An example for subjective values for an *n*-back task with three levels, returned by different modifications of the COG-ED paradigm for a hypothetical participant with the true preference 2-back > 3-back > 1-back.
 The grey boxes are the choice options shown to the participant.
@@
 
-```{r sv-by-pref, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values (SV) per $n$-back level, grouped into those who had an SV = 1 for 1-back, for 2-back, for 3-back, for 4-back, or no SV = 1 for any level.
+```{r sv-by-pref, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values (SV) per *n*-back level, grouped into those who had an SV = 1 for 1-back, for 2-back, for 3-back, for 4-back, or no SV = 1 for any level.
 The lines have a vertical jitter of 0.02.
@@
 
-```{r motivation, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Trajectories of subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
+```{r motivation, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Trajectories of subjective values per *n*-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm.
 $N=116$.
@@
 The colourbar in panel b indicates the BF10 of each multi level model compared to a model in which the n-back level has no effect.
-The pipelines in both panels are sorted left to right in ascending order of the magnitude of the beta estimate of the predictor $d'$.
+The pipelines in both panels are sorted left to right in ascending order of the magnitude of the beta estimate of the predictor *d'*.
 Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}
@@
 
-```{r nfccont-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Predicted slopes of subjective values depending on individual Need for Cognition scores for each $n$-back level.
+```{r nfccont-sv, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Predicted slopes of subjective values depending on individual Need for Cognition scores for each *n*-back level.
 The slopes of 1-back and 4-back are different at $p=.01$.

### 2023-11-15 06_Paper/COG-ED/Stage 2/Supplement.Rmd

--- 2023-06-16 06_Paper/COG-ED/Stage 2/Supplement.Rmd
@@
 ---
-title             : "Supplementary Material for the Registered Report titled: 'When easy is not preferred: A discounting paradigm to assess load-independent task preference'"
+title             : "Supplementary Material for the Registered Report titled: 'Need for cognition is associated with a preference for higher task load in effort discounting'"
 shorttitle        : "Supplement for CAD Paradigm"

### 2023-11-15 06_Paper/COG-ED/Stage 2/Supplement.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{effort discounting, registered report, specification curve analysis, need for cognition, $n$-back}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{setspace}\doublespacing
\usepackage[final]{pdfpages}
\usepackage{chngcntr}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Supplementary Material for the Registered Report titled: `Need for cognition is associated with a preference for higher task load in effort discounting'},
  pdfauthor={Josephine Zerna,1, Christoph Scheffel,1, Corinna Kührt1, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={effort discounting, registered report, specification curve analysis, need for cognition, \(n\)-back},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary Material for the Registered Report titled: `Need for cognition is associated with a preference for higher task load in effort discounting'}
\author{Josephine Zerna\textsuperscript{$\dagger{}$,1}, Christoph Scheffel\textsuperscript{$\dagger{}$,1}, Corinna Kührt\textsuperscript{1}, \& Alexander Strobel\textsuperscript{1}}
\date{}

\shorttitle{Supplement for CAD Paradigm}

\authornote{

The authors made the following contributions. Josephine Zerna: Conceptualization, Data curation, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft, Writing - review \& editing; Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Writing - review \& editing; Corinna Kührt: Formal analysis, Writing - review \& editing; Alexander Strobel: Conceptualization, Resources, Supervision, Funding acquistion, Writing - review \& editing. \textsuperscript{$\dagger{}$} Josephine Zerna and Christoph Scheffel contributed equally to this work.

Correspondence concerning this article should be addressed to Josephine Zerna, Zellescher Weg 17, 01069 Dresden, Germany. E-mail: \href{mailto:josephine.zerna@tu-dresden.de}{\nolinkurl{josephine.zerna@tu-dresden.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany}

\begin{document}
\maketitle

\newpage
\renewcommand\thesection{\Alph{section}}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{0}

\hypertarget{design-table}{%
\subsection{Design Table}\label{design-table}}

(Starts on next page)

\includepdf[pages={-},landscape=true]{Design_Table_T1.pdf}

\newpage

\hypertarget{contrasts-tested-for-in-the-repeated-measures-anova}{%
\subsection{Contrasts tested for in the repeated measures ANOVA}\label{contrasts-tested-for-in-the-repeated-measures-anova}}

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/contrasts} \caption{Contrasts tested for in the repeated measures ANOVA that was used as a prerequisite for the multi level model of hypothesis 2b. Ascending quadratic (-1,1,1,-1), declining linear (3,1,-1,-3), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2). Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:contrast-plot}
\end{figure}

\newpage

\hypertarget{hypothesis-1a-the-signal-detection-measure-d-declines-with-increasing-n-back-level.}{%
\subsection{\texorpdfstring{Hypothesis 1a: The signal detection measure \(d'\) declines with increasing \(n\)-back level.}{Hypothesis 1a: The signal detection measure d\textquotesingle{} declines with increasing n-back level.}}\label{hypothesis-1a-the-signal-detection-measure-d-declines-with-increasing-n-back-level.}}

ANOVA:

\(F(2.74, 315.51) = 197.18\), \(p < .001\), \(\hat{\eta}^2_G = .464\), 90\% CI \([.403, .516]\), \(\mathrm{BF}_{\textrm{10}} = 1.56 \times 10^{101}\)

Paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-1}Paired contrasts for the rmANOVA comparing $d'$ between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & 0.09 & 0.02 & 345.00 & 4.31 & 0.00 & 93,954.04 & 0.05 & {}[0.02, 1.00]\\
1 - 3 & 0.31 & 0.02 & 345.00 & 14.71 & 0.00 & $3.21 \times 10^{47}$ & 0.39 & {}[0.32, 1.00]\\
1 - 4 & 0.46 & 0.02 & 345.00 & 21.89 & 0.00 & $4.46 \times 10^{69}$ & 0.58 & {}[0.53, 1.00]\\
2 - 3 & 0.22 & 0.02 & 345.00 & 10.41 & 0.00 & $3.71 \times 10^{23}$ & 0.24 & {}[0.18, 1.00]\\
2 - 4 & 0.37 & 0.02 & 345.00 & 17.58 & 0.00 & $2.01 \times 10^{44}$ & 0.47 & {}[0.41, 1.00]\\
3 - 4 & 0.15 & 0.02 & 345.00 & 7.18 & 0.00 & $2.45 \times 10^{14}$ & 0.13 & {}[0.08, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\hypertarget{hypothesis-1b-the-median-reaction-time-increases-with-increasing-n-back-level.}{%
\subsection{\texorpdfstring{Hypothesis 1b: The median reaction time increases with increasing \(n\)-back level.}{Hypothesis 1b: The median reaction time increases with increasing n-back level.}}\label{hypothesis-1b-the-median-reaction-time-increases-with-increasing-n-back-level.}}

ANOVA:

\(F(2.46, 283.05) = 98.67\), \(p < .001\), \(\hat{\eta}^2_G = .192\), 90\% CI \([.130, .248]\), \(\mathrm{BF}_{\textrm{10}} = 2.28 \times 10^{34}\)

Paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-2}Paired contrasts for the rmANOVA comparing the median reaction time between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -0.11 & 0.01 & 345.00 & -11.76 & <.001 & $1.75 \times 10^{30}$ & 0.29 & {}[0.22, 1.00]\\
1 - 3 & -0.16 & 0.01 & 345.00 & -16.23 & <.001 & $8.80 \times 10^{45}$ & 0.43 & {}[0.37, 1.00]\\
1 - 4 & -0.12 & 0.01 & 345.00 & -12.47 & <.001 & $4.79 \times 10^{34}$ & 0.31 & {}[0.25, 1.00]\\
2 - 3 & -0.04 & 0.01 & 345.00 & -4.47 & <.001 & 5,538.45 & 0.05 & {}[0.02, 1.00]\\
2 - 4 & -0.01 & 0.01 & 345.00 & -0.71 & 0.894 & 0.10 & 1.45e-03 & {}[0.00, 1.00]\\
3 - 4 & 0.04 & 0.01 & 345.00 & 3.76 & 0.001 & $6.35 \times 10^{6}$ & 0.04 & {}[0.01, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\hypertarget{hypothesis-1c-ratings-on-all-nasa-tlx-dimensions-increase-with-increasing-n-back-level.}{%
\subsection{\texorpdfstring{Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing \(n\)-back level.}{Hypothesis 1c: Ratings on all NASA-TLX dimensions increase with increasing n-back level.}}\label{hypothesis-1c-ratings-on-all-nasa-tlx-dimensions-increase-with-increasing-n-back-level.}}

Mental subscale ANOVA:

\(F(1.99, 228.35) = 274.47\), \(p < .001\), \(\hat{\eta}^2_G = .375\), 90\% CI \([.309, .432]\), \(\mathrm{BF}_{\textrm{10}} = 1.64 \times 10^{43}\)

Mental subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-3}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Mental subscale between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -3.91 & 0.34 & 345.00 & -11.52 & <.001 & $1.32 \times 10^{23}$ & 0.28 & {}[0.21, 1.00]\\
1 - 3 & -7.43 & 0.34 & 345.00 & -21.91 & <.001 & $1.83 \times 10^{34}$ & 0.58 & {}[0.53, 1.00]\\
1 - 4 & -8.91 & 0.34 & 345.00 & -26.26 & <.001 & $9.87 \times 10^{36}$ & 0.67 & {}[0.62, 1.00]\\
2 - 3 & -3.53 & 0.34 & 345.00 & -10.40 & <.001 & $1.09 \times 10^{19}$ & 0.24 & {}[0.18, 1.00]\\
2 - 4 & -5.00 & 0.34 & 345.00 & -14.74 & <.001 & $3.64 \times 10^{22}$ & 0.39 & {}[0.32, 1.00]\\
3 - 4 & -1.47 & 0.34 & 345.00 & -4.35 & <.001 & $3.83 \times 10^{6}$ & 0.05 & {}[0.02, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

Physical subscale ANOVA:

\(F(1.68, 192.93) = 15.91\), \(p < .001\), \(\hat{\eta}^2_G = .041\), 90\% CI \([.009, .075]\), \(\mathrm{BF}_{\textrm{10}} = 60.54\)

Physical subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Physical subscale between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -0.95 & 0.32 & 345.00 & -2.95 & 0.018 & 25.36 & 0.02 & {}[0.00, 1.00]\\
1 - 3 & -1.70 & 0.32 & 345.00 & -5.29 & <.001 & 602.59 & 0.08 & {}[0.04, 1.00]\\
1 - 4 & -2.04 & 0.32 & 345.00 & -6.37 & <.001 & 1,235.49 & 0.11 & {}[0.06, 1.00]\\
2 - 3 & -0.75 & 0.32 & 345.00 & -2.34 & 0.092 & 10.45 & 0.02 & {}[0.00, 1.00]\\
2 - 4 & -1.09 & 0.32 & 345.00 & -3.41 & 0.004 & 31.98 & 0.03 & {}[0.01, 1.00]\\
3 - 4 & -0.34 & 0.32 & 345.00 & -1.07 & 0.705 & 0.47 & 3.33e-03 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

Time subscale ANOVA:

\(F(2.21, 254.65) = 51.08\), \(p < .001\), \(\hat{\eta}^2_G = .117\), 90\% CI \([.065, .168]\), \(\mathrm{BF}_{\textrm{10}} = 3.94 \times 10^{9}\)

Time subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Time subscale between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -1.95 & 0.43 & 345.00 & -4.53 & <.001 & 7,366.95 & 0.06 & {}[0.02, 1.00]\\
1 - 3 & -4.28 & 0.43 & 345.00 & -9.97 & <.001 & $3.09 \times 10^{10}$ & 0.22 & {}[0.16, 1.00]\\
1 - 4 & -4.65 & 0.43 & 345.00 & -10.81 & <.001 & $2.02 \times 10^{11}$ & 0.25 & {}[0.19, 1.00]\\
2 - 3 & -2.34 & 0.43 & 345.00 & -5.44 & <.001 & $9.62 \times 10^{6}$ & 0.08 & {}[0.04, 1.00]\\
2 - 4 & -2.70 & 0.43 & 345.00 & -6.28 & <.001 & $8.02 \times 10^{6}$ & 0.10 & {}[0.06, 1.00]\\
3 - 4 & -0.36 & 0.43 & 345.00 & -0.84 & 0.834 & 0.18 & 2.05e-03 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

Performance subscale ANOVA:

\(F(2.49, 285.97) = 95.33\), \(p < .001\), \(\hat{\eta}^2_G = .241\), 90\% CI \([.176, .299]\), \(\mathrm{BF}_{\textrm{10}} = 1.55 \times 10^{24}\)

Performance subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Performance subscale between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & 2.07 & 0.40 & 345.00 & 5.13 & <.001 & 80,590.41 & 0.07 & {}[0.03, 1.00]\\
1 - 3 & 5.14 & 0.40 & 345.00 & 12.74 & <.001 & $1.23 \times 10^{19}$ & 0.32 & {}[0.26, 1.00]\\
1 - 4 & 6.03 & 0.40 & 345.00 & 14.96 & <.001 & $2.36 \times 10^{19}$ & 0.39 & {}[0.33, 1.00]\\
2 - 3 & 3.07 & 0.40 & 345.00 & 7.61 & <.001 & $8.72 \times 10^{12}$ & 0.14 & {}[0.09, 1.00]\\
2 - 4 & 3.97 & 0.40 & 345.00 & 9.83 & <.001 & $4.20 \times 10^{12}$ & 0.22 & {}[0.16, 1.00]\\
3 - 4 & 0.90 & 0.40 & 345.00 & 2.22 & 0.119 & 2.35 & 0.01 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

Effort subscale ANOVA:

\(F(2.20, 253.06) = 203.82\), \(p < .001\), \(\hat{\eta}^2_G = .316\), 90\% CI \([.250, .375]\), \(\mathrm{BF}_{\textrm{10}} = 2.47 \times 10^{34}\)

Effort subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Effort subscale between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -4.23 & 0.34 & 345.00 & -12.35 & <.001 & $4.24 \times 10^{19}$ & 0.31 & {}[0.24, 1.00]\\
1 - 3 & -6.80 & 0.34 & 345.00 & -19.84 & <.001 & $4.25 \times 10^{29}$ & 0.53 & {}[0.48, 1.00]\\
1 - 4 & -7.73 & 0.34 & 345.00 & -22.56 & <.001 & $1.47 \times 10^{32}$ & 0.60 & {}[0.55, 1.00]\\
2 - 3 & -2.57 & 0.34 & 345.00 & -7.49 & <.001 & $3.85 \times 10^{12}$ & 0.14 & {}[0.09, 1.00]\\
2 - 4 & -3.50 & 0.34 & 345.00 & -10.21 & <.001 & $3.33 \times 10^{15}$ & 0.23 & {}[0.17, 1.00]\\
3 - 4 & -0.93 & 0.34 & 345.00 & -2.72 & 0.035 & 174.38 & 0.02 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

Frustration subscale ANOVA:

\(F(2.50, 287.66) = 68.06\), \(p < .001\), \(\hat{\eta}^2_G = .172\), 90\% CI \([.112, .227]\), \(\mathrm{BF}_{\textrm{10}} = 5.26 \times 10^{15}\)

Frustration subscale paired contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing ratings on the NASA-TLX Frustration subscale between $n$-back levels.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -2.17 & 0.43 & 345.00 & -4.99 & <.001 & 67,280.87 & 0.07 & {}[0.03, 1.00]\\
1 - 3 & -4.76 & 0.43 & 345.00 & -10.94 & <.001 & $8.22 \times 10^{14}$ & 0.26 & {}[0.20, 1.00]\\
1 - 4 & -5.57 & 0.43 & 345.00 & -12.80 & <.001 & $2.34 \times 10^{15}$ & 0.32 & {}[0.26, 1.00]\\
2 - 3 & -2.59 & 0.43 & 345.00 & -5.95 & <.001 & $6.41 \times 10^{7}$ & 0.09 & {}[0.05, 1.00]\\
2 - 4 & -3.40 & 0.43 & 345.00 & -7.81 & <.001 & $6.16 \times 10^{8}$ & 0.15 & {}[0.10, 1.00]\\
3 - 4 & -0.81 & 0.43 & 345.00 & -1.86 & 0.246 & 0.92 & 9.96e-03 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\hypertarget{hypothesis-2a-subjective-values-decline-with-increasing-n-back-level.}{%
\subsection{\texorpdfstring{Hypothesis 2a: Subjective values decline with increasing \(n\)-back level.}{Hypothesis 2a: Subjective values decline with increasing n-back level.}}\label{hypothesis-2a-subjective-values-decline-with-increasing-n-back-level.}}

ANOVA:

\(F(1.98, 227.98) = 65.65\), \(p < .001\), \(\hat{\eta}^2_G = .288\), 90\% CI \([.222, .347]\), \(\mathrm{BF}_{\textrm{10}} = 1.58 \times 10^{64}\)

Pre-defined contrasts:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-9}Contrasts for the rmANOVA comparing the subjective values between $n$-back levels.}

\begin{tabular}{llllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
Declining Linear & 1.11 & 0.08 & 345.00 & 13.41 & <.001 & 0.34 & {}[0.28, 1.00]\\
Ascending Quadratic & 0.15 & 0.04 & 345.00 & 4.14 & <.001 & 0.05 & {}[0.02, 1.00]\\
Declining Logistic & 1.22 & 0.09 & 345.00 & 12.97 & <.001 & 0.33 & {}[0.26, 1.00]\\
Positively Skewed Normal & 0.75 & 0.06 & 345.00 & 12.74 & <.001 & 0.32 & {}[0.26, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\hypertarget{hypothesis-2b-subjective-values-decline-with-increasing-n-back-level-even-after-controlling-for-declining-task-performance-measured-by-signal-detection-d-and-reaction-time.}{%
\subsection{\texorpdfstring{Hypothesis 2b: Subjective values decline with increasing \(n\)-back level, even after controlling for declining task performance measured by signal detection d' and reaction time.}{Hypothesis 2b: Subjective values decline with increasing n-back level, even after controlling for declining task performance measured by signal detection d' and reaction time.}}\label{hypothesis-2b-subjective-values-decline-with-increasing-n-back-level-even-after-controlling-for-declining-task-performance-measured-by-signal-detection-d-and-reaction-time.}}

Multi level model:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-10}Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.}

\begin{tabular}{llllllll}
\toprule
Parameter & \multicolumn{1}{c}{Beta} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$-value} & \multicolumn{1}{c}{$p$-value} & \multicolumn{1}{c}{$f^{2}$} & \multicolumn{1}{c}{Random Effects (SD)}\\
\midrule
Intercept & 0.81 & 0.01 & 115.00 & 78.68 & <.001 &  & 0.09\\
n-back level & 0.03 & 0.00 & 797.54 & 9.99 & <.001 & 0.21 & \\
d' & 0.21 & 0.03 & 797.63 & 6.28 & <.001 & 0.05 & \\
median RT & 0.03 & 0.07 & 797.80 & 0.42 & 0.674 & 0.00 & \\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

The final model had an effect size of \(f^{2}=\) 0.21 for the \(n\)-back levels and \(f^{2}=\) 0.05 for \(d'\).
This means that the \(n\)-back level explained 20.67\% and \(d'\) explained 4.90\% of variance in SVs relative to the unexplained variance, respectively.
The beta coefficient indicated that with every 1-unit increase in \(d'\), the SV increased by 0.21.
The effect size of the median RT was \(f^{2}=\) 0.00.
The Bayes Factor of the full model against the null model was \(\mathrm{BF}_{\textrm{10}} = 7.83 \times 10^{29} \pm 16.28\%\).

\newpage

\hypertarget{hypothesis-3a-participants-with-higher-nfc-scores-have-higher-subjective-values-for-2--and-3-back-but-lower-subjective-values-for-1-back-than-participants-with-lower-nfc-scores.}{%
\subsection{Hypothesis 3a: Participants with higher NFC scores have higher subjective values for 2- and 3-back but lower subjective values for 1-back than participants with lower NFC scores.}\label{hypothesis-3a-participants-with-higher-nfc-scores-have-higher-subjective-values-for-2--and-3-back-but-lower-subjective-values-for-1-back-than-participants-with-lower-nfc-scores.}}

ANOVA:

Main effect level: \(F(1, 114) = 9.13\), \(p = .003\), \(\hat{\eta}^2_G = .040\), 90\% CI \([.002, .115]\), \(\mathrm{BF}_{\textrm{10}} = 12.68 \pm 0.00\%\)

Main effect NFC group: \(F(1, 114) = 3.18\), \(p = .077\), \(\hat{\eta}^2_G = .013\), 90\% CI \([.000, .068]\), \(\mathrm{BF}_{\textrm{10}} = 0.56 \pm 0.03\%\)

Interaction: \(F(1, 114) = 0.46\), \(p = .499\), \(\hat{\eta}^2_G = .002\), 90\% CI \([.000, .037]\)

Contrast for main effect level:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-11}Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of subjective values.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1-2 - 2-3 & -0.08 & 0.03 & 114.00 & -3.02 & 0.003 & 12.68 & 0.07 & {}[0.02, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/h3ac-plot} \caption{Difference scores for subjective values (a) and aversiveness ratings (b) when subtracting 2- from 1-back and 3- from 2-back. Horizontal lines of the boxplots represent the median per group, whiskers represent 1.5 interquartile ranges. NFC = Need for Cognition score. $N=116$. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3ac-plot}
\end{figure}

\newpage

\hypertarget{hypothesis-3b-participants-with-higher-nfc-scores-have-lower-nasa-tlx-scores-in-every-n-back-level-than-participants-with-lower-nfc-scores.}{%
\subsection{Hypothesis 3b: Participants with higher NFC scores have lower NASA-TLX scores in every n-back level than participants with lower NFC scores.}\label{hypothesis-3b-participants-with-higher-nfc-scores-have-lower-nasa-tlx-scores-in-every-n-back-level-than-participants-with-lower-nfc-scores.}}

ANOVA:

Main effect level: \(F(2.10, 239.56) = 154.50\), \(p < .001\), \(\hat{\eta}^2_G = .223\), 90\% CI \([.159, .282]\), \(\mathrm{BF}_{\textrm{10}} = 2.22 \times 10^{45}\)

Main effect NFC group: \(F(1, 114) = 3.22\), \(p = .075\), \(\hat{\eta}^2_G = .022\), 90\% CI \([.000, .084]\), \(\mathrm{BF}_{\textrm{10}} = 1.75 \times 10^{2}\)

Interaction: \(F(2.10, 239.56) = 4.93\), \(p = .007\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .025]\)

Contrast for main effect level:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-12}Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & -1.86 & 0.18 & 114.00 & -10.06 & <.001 & $7.02 \times 10^{9}$ & 0.47 & {}[0.36, 1.00]\\
1 - 3 & -3.31 & 0.23 & 114.00 & -14.36 & <.001 & $6.43 \times 10^{29}$ & 0.64 & {}[0.56, 1.00]\\
1 - 4 & -3.82 & 0.25 & 114.00 & -15.32 & <.001 & $5.25 \times 10^{37}$ & 0.67 & {}[0.60, 1.00]\\
2 - 3 & -1.46 & 0.16 & 114.00 & -9.15 & <.001 & 113,671.29 & 0.42 & {}[0.31, 1.00]\\
2 - 4 & -1.96 & 0.19 & 114.00 & -10.39 & <.001 & $4.18 \times 10^{9}$ & 0.49 & {}[0.38, 1.00]\\
3 - 4 & -0.51 & 0.13 & 114.00 & -3.82 & 0.001 & 0.55 & 0.11 & {}[0.04, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Contrast for interaction:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-13}Paired contrasts for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on NASA-TLX scores.}

\begin{tabular}{llllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Level} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
high - low & 1 & -0.23 & 0.48 & 114.00 & -0.48 & 0.632 & 0.18 & 2.02e-03 & {}[0.00, 1.00]\\
high - low & 2 & -0.40 & 0.53 & 114.00 & -0.76 & 0.450 & 0.25 & 5.00e-03 & {}[0.00, 1.00]\\
high - low & 3 & -1.14 & 0.53 & 114.00 & -2.15 & 0.033 & 11.15 & 0.04 & {}[0.00, 1.00]\\
high - low & 4 & -1.53 & 0.53 & 114.00 & -2.89 & 0.005 & 336.88 & 0.07 & {}[0.01, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/h3b-plot} \caption{NASA-TLX sum scores for each $n$-back level. Colours indicate Need for Cognition (NFC) score above or below the median. $N=116$. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:h3b-plot}
\end{figure}

\newpage

\hypertarget{hypothesis-3c-participants-with-higher-nfc-scores-have-lower-aversiveness-ratings-for-2--and-3-back-but-higher-higher-aversiveness-ratings-for-1-back-than-participants-with-lower-nfc-scores.}{%
\subsection{Hypothesis 3c: Participants with higher NFC scores have lower aversiveness ratings for 2- and 3-back but higher higher aversiveness ratings for 1-back than participants with lower NFC scores.}\label{hypothesis-3c-participants-with-higher-nfc-scores-have-lower-aversiveness-ratings-for-2--and-3-back-but-higher-higher-aversiveness-ratings-for-1-back-than-participants-with-lower-nfc-scores.}}

ANOVA:

Main effect level: \(F(1, 114) = 10.21\), \(p = .002\), \(\hat{\eta}^2_G = .034\), 90\% CI \([.000, .105]\),

Main effect NFC group: \(F(1, 114) = 8.43\), \(p = .004\), \(\hat{\eta}^2_G = .043\), 90\% CI \([.003, .119]\), \(\mathrm{BF}_{\textrm{10}} = 14.26\)

Interaction: \(F(1, 114) = 2.59\), \(p = .110\), \(\hat{\eta}^2_G = .009\), 90\% CI \([.000, .058]\)

Contrast for main effect level:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-14}Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on difference scores of aversiveness ratings.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1-2 - 2-3 & 1.27 & 0.40 & 114.00 & 3.20 & 0.002 & 5.49 & 0.08 & {}[0.02, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Contrast for main effect NFC group:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-15}Paired contrast for the rmANOVA comparing the influence of Need for Cognition (NFC) group and $n$-back level on difference scores of aversiveness ratings.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
High NFC - Low NFC & 1.44 & 0.50 & 114.00 & 2.90 & 0.004 & 14.26 & 0.07 & {}[0.01, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\hypertarget{exploratory-analysis-with-nfc-groups-by-median-split}{%
\subsection{Exploratory analysis with NFC groups by median split}\label{exploratory-analysis-with-nfc-groups-by-median-split}}

ANOVA:

Main effect level: \(F(2.01, 229.39) = 67.39\), \(p < .001\), \(\hat{\eta}^2_G = .295\), 90\% CI \([.228, .354]\), \(2.70 \times 10^{30}\)

Main effect NFC group: \(F(1, 114) = 2.63\), \(p = .108\), \(\hat{\eta}^2_G = .007\), 90\% CI \([.000, .053]\), \(2.95 \times 10^{-1}\)

Interaction: \(F(2.01, 229.39) = 3.24\), \(p = .041\), \(\hat{\eta}^2_G = .020\), 90\% CI \([.000, .044]\)

Contrasts for main effect level:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-16}Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjective values.}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
1 - 2 & 0.03 & 0.02 & 114.00 & 2.03 & 0.184 & 0.66 & 0.03 & {}[0.00, 1.00]\\
1 - 3 & 0.15 & 0.03 & 114.00 & 5.77 & <.001 & 117,986.95 & 0.23 & {}[0.12, 1.00]\\
1 - 4 & 0.33 & 0.03 & 114.00 & 9.70 & <.001 & $1.47 \times 10^{13}$ & 0.45 & {}[0.34, 1.00]\\
2 - 3 & 0.11 & 0.02 & 114.00 & 5.55 & <.001 & 67,167.07 & 0.21 & {}[0.11, 1.00]\\
2 - 4 & 0.30 & 0.03 & 114.00 & 10.22 & <.001 & $4.31 \times 10^{14}$ & 0.48 & {}[0.37, 1.00]\\
3 - 4 & 0.19 & 0.03 & 114.00 & 7.30 & <.001 & $1.68 \times 10^{8}$ & 0.32 & {}[0.21, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Contrasts for the interaction:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-17}Paired contrast for the rmANOVA comparing the influence of Need for Cognition group and $n$-back level on subjective values.}

\begin{tabular}{llllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Level} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\mathrm{BF}_{\textrm{10}}$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
high - low & 1 & -0.05 & 0.03 & 114.00 & -1.50 & 0.136 & 0.54 & 0.02 & {}[0.00, 1.00]\\
high - low & 2 & 0.02 & 0.03 & 114.00 & 0.72 & 0.472 & 0.25 & 4.54e-03 & {}[0.00, 1.00]\\
high - low & 3 & 0.05 & 0.04 & 114.00 & 1.28 & 0.203 & 0.41 & 0.01 & {}[0.00, 1.00]\\
high - low & 4 & 0.11 & 0.05 & 114.00 & 2.13 & 0.036 & 1.48 & 0.04 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column Contrast contains the groups above (high) and below (low) the Need for Cognition score median. The column Level contains the $n$ of the $n$-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\hypertarget{exploratory-analysis-with-nfc-as-a-continuous-covariate}{%
\subsection{Exploratory analysis with NFC as a continuous covariate}\label{exploratory-analysis-with-nfc-as-a-continuous-covariate}}

ANOVA (NFC scores standardized):

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-18}Result of the rmANOVA regarding the predictive power of the $n$-back level on the subjective values when including Need for Cognition scores as a centered continuous covariate.}

\begin{tabular}{lllllllll}
\toprule
 & \multicolumn{1}{c}{Sum Sq} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{error Sum Sq} & \multicolumn{1}{c}{den $df$} & \multicolumn{1}{c}{$F$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
Intercept & 301.49 & 1.00 & 5.44 & 114.00 & 6,322.13 & <.001 & 0.98 & {}[0.98, 1.00]\\
NFC & 0.21 & 1.00 & 5.44 & 114.00 & 4.34 & 0.039 & 0.04 & {}[0.00, 1.00]\\
n-back level & 7.83 & 3.00 & 13.28 & 342.00 & 67.24 & <.001 & 0.37 & {}[0.30, 1.00]\\
NFC x n-back level & 0.44 & 3.00 & 13.28 & 342.00 & 3.78 & 0.011 & 0.03 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} NFC = Need for Cognition. $SE$ = standard error, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, $\eta_{p}^{2}$ = partial eta squared, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

Estimated marginal means of the linear trends:

\begin{table}[H]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-19}Paired contrast slope analysis as a follow up for the rmANOVA regarding the predictive power of the $n$-back level on the subjective values when including Need for Cognition scores as a centered continuous covariate.}

\begin{tabular}{llllll}
\toprule
$n$-back level & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$}\\
\midrule
1 - 2 & -0.03 & 0.03 & 456.00 & -1.11 & 0.68\\
1 - 3 & -0.03 & 0.03 & 456.00 & -1.27 & 0.58\\
1 - 4 & -0.09 & 0.03 & 456.00 & -3.22 & 0.01\\
2 - 3 & 0.00 & 0.03 & 456.00 & -0.16 & 1.00\\
2 - 4 & -0.06 & 0.03 & 456.00 & -2.10 & 0.15\\
3 - 4 & -0.05 & 0.03 & 456.00 & -1.95 & 0.21\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} The column $n$-back level contains the $n$ of the task levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\newpage

\begin{figure}[H]
\includegraphics[width=\textwidth]{Figures/nfcgroups-sv} \caption{Subjective values per n-back level for participants with Need for Cognition (NFC) scores above and below the median. $N=116$. The scatter has a horizontal jitter of 0.2. Smoothing of conditional means with Loess method. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.}\label{fig:nfcgroups-sv}
\end{figure}

\end{document}
